### 2019-04-09 analysis/02_analysis.Rmd
Move analysis to its own directory

---
title: "Results"
author: "Andrew Heiss, Marc Dotson, and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
    pandoc_args:
      - "--default-image-extension=png"
editor_options: 
  chunk_output_type: console
---

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(donorheuristics)
library(ggraph)
library(ggdag)
library(here)

# General settings
source(here("analysis", "options.R"))

# Make all the randomness reproducible
set.seed(1234)

# Load data
# results <- readRDS(here("data", "derived_data", "results.rds"))
```

# Causal pathway

Our theory and hypotheses are laid out in the causal pathway below. Our outcomes (Y: % likely to donate and amount donated) "listen to" or respond to C (crackdown), which is our main treatment or exposure. Funding (F) and issue (I) serve as heuristics for donation and influence a government's decision to crack down on NGOs, hence the dual arrows to C and Y.

```{r causal-dag, fig.width=13/3, fig.height=2}
node_colors <- tribble(
  ~name, ~type,
  "D", "Outcome",
  "I", "Organizational factor",
  "F", "Organizational factor",
  "O", "Organizational factor",
  "G", "Structural factor"
)

# Set up DAG structure
theory_dag <- dagify(D ~ I + F + O + G,
                     G ~ I + F,
                     outcome = "D",
                     exposure = "C") %>% 
  tidy_dagitty(layout = "dh", seed = 1234)

# Add node types/colors to DAG data
theory_dag$data <- theory_dag$data %>% 
  left_join(node_colors, by = "name")

# Make DAG plot
plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_point(size = 6, mapping = aes(color = type)) +
  geom_dag_edges(start_cap = circle(4, "mm"),
                 end_cap = circle(4, "mm")) +
  geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
  scale_dag() +
  theme_ngo() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank())

# Show and save plot
plot_dag
ggsave(plot_dag, filename = here("analysis", "output", "figures", "causal-path.pdf"),
       width = 13/3, height = 2, units = "in", device = cairo_pdf)
ggsave(plot_dag, filename = here("analysis", "output", "figures", "causal-path.png"),
       width = 13/3, height = 2, units = "in", type = "cairo", dpi = 300)
```

# Original computing environment

<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>

<div id="sessioninfo" class="collapse">

```{r show-session-info, echo=TRUE, width=100}
writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))

devtools::session_info()
```

</div>

### 2019-04-09 analysis/experiment.Rmd
Move analysis to its own directory

---
title: "Experiment"
date: "Last run: `r format(Sys.time(), '%F')`"
---

# Survey experiment {.survey}

```{r child = "survey/experiment.md"}
```

### 2019-04-09 analysis/index.Rmd
Move analysis to its own directory

---
title: "Why Donors Donate"
author: "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
---

## Abstract

As space for civil society has closed around the world, transnational NGOs have faced a crisis of funding. We explore how NGOs have shifted from traditionally Northern funding sources toward grassroots private philanthropic money. How do individual donors in the US feel about donating to legally besieged NGOs abroad? Do legal restrictions on NGOs influence donors’ decision to donate? We use a conjoint survey experiment to argue that domestic political environments of NGO host countries influence preferences of private donors and that legal crackdowns on NGOs serve as a heuristic of organizational deservingness.

### 2019-04-09 analysis/preregistration.Rmd
Move analysis to its own directory

---
title: "Pre-registration details"
date: "Last run: `r format(Sys.time(), '%F')`"
---

# Study Information

## Title

TODO

## Authorship

- Suparna Chaudhry
- Marc Dotson
- Andrew Heiss

## Research Questions

> Please list each research question included in this study.

- What makes donors donate?
- Structural factors - relationship with government - organizational level
- Organizational -

- Individuals

TODO: Find that other conjoin article

## Hypotheses

> For each of the research questions listed in the previous section, provide one or multiple specific and testable hypotheses. Please state if the hypotheses are directional or non-directional. If directional, state the direction. A predicted effect is also appropriate here.

- TODO
- TODO

EGAP - conjoint examples

Subgroups, like people who have donated a lot vs. not

TODO: Check distribution of donation frequency

Size of donation - separate models
Volunteering 
Political views
Prosocial views
Demographic stuff

---

# Sampling Plan

## Existing data

Registration prior to creation of data

## Explanation of existing data

We will not use any existing data.

## Data collection procedures

> Please describe the process by which you will collect your data. If you are using human subjects, this should include the population from which you obtain subjects, recruitment efforts, payment for participation, how subjects will be selected for eligibility from the initial pool (e.g. inclusion and exclusion rules), and your study timeline. For studies that don’t include human subjects, include information about how you will collect samples, duration of data gathering efforts, source or location of samples, or batch numbers you will use.

TODO

## Sample size

> Describe the sample size of your study. How many units will be analyzed in the study? This could be the number of people, birds, classrooms, plots, interactions, or countries included. If the units are not individuals, then describe the size requirements for each unit. If you are using a clustered or multilevel design, how many units are you collecting at each level of the analysis?

TODO

## Sample size rationale

> This could include a power analysis or an arbitrary constraint such as time, money, or personnel.

TODO

## Stopping rule

> If your data collection procedures do not give you full control over your exact sample size, specify how you will decide when to terminate your data collection.

TODO

---

# Variables

## Manipulated variables

> Describe all variables you plan to manipulate and the levels or treatment arms of each variable. For observational studies and meta-analyses, simply state that this is not applicable.

TODO

## Measured variables

> Describe each variable that you will measure. This will include outcome measures, as well as any predictors or covariates that you will measure. You do not need to include any variables that you plan on collecting if they are not going to be included in the confirmatory analyses of this study.

TODO

## Indices

> If any measurements are  going to be combined into an index (or even a mean), what measures will you use and how will they be combined? Include either a formula or a precise description of your method. If your are using a more complicated statistical method to combine measures (e.g. a factor analysis), you can note that here but describe the exact method in the analysis plan section.

TODO

---

# Design plan

## Study type

Experiment - A researcher randomly assigns treatments to study subjects, this includes field or lab experiments. This is also known as an intervention experiment and includes randomized controlled trials.

## Blinding

For studies that involve human subjects, they will not know the treatment group to which they have been assigned.

## Study design

> Describe your study design. Examples include two-group, factorial, randomized block, and repeated measures. Is it a between (unpaired), within-subject (paired), or mixed design? Describe any counterbalancing required. Typical study designs for observation studies include cohort, cross sectional, and case-control studies.

TODO - conjoint design

## Randomization

> If you are doing a randomized study, how will you randomize, and at what level?

TODO

---

# Analysis Plan

## Statistical models

> What statistical model will you use to test each hypothesis? Please include the type of model (e.g. ANOVA, multiple regression, SEM, etc) and the specification of the model (this includes each variable that will be included as predictors, outcomes, or covariates). Please specify any interactions that will be tested and remember that any test not included here must be noted as an exploratory test in your final article.

TODO

## Transformations

> If you plan on transforming, centering, recoding the data, or will require a coding scheme for categorical variables, please describe that process.

TODO

## Follow-up analyses

> If not specified previously, will you be conducting any confirmatory analyses to follow up on effects in your statistical model, such as subgroup analyses, pairwise or complex contrasts, or follow-up tests from interactions? Remember that any analyses not specified in this research plan must be noted as exploratory.

TODO

## Inference criteria

> What criteria will you use to make inferences? Please describe the information you’ll use (e.g. specify the p-values, Bayes factors, specific model fit indices), as well as cut-off criterion, where appropriate. Will you be using one or two tailed tests for each of your analyses? If you are comparing multiple conditions or testing multiple hypotheses, will you account for this?

TODO

## Data exclusion

> How will you determine which data points or samples (if any) to exclude from your analyses? How will outliers be handled?

TODO

## Missing data

> How will you deal with incomplete or missing data?

TODO

## Exploratory analysis (optional)

> If you plan to explore your data set to look for unexpected differences or relationships, you may describe those tests here. An exploratory test is any test where a prediction is not made up front, or there are multiple possible tests that you are going to use. A statistically significant finding in an exploratory test is a great way to form a new confirmatory hypothesis, which could be registered at a later time.

TODO

---

# Script (optional)

> Upload an analysis script with clear comments. This optional step is helpful in order to create a process that is completely transparent and increase the likelihood that your analysis can be replicated. We recommend that you run the code on a simulated dataset in order to check that it will run without errors.

MAYBE: This would be cool, but we'd need to create fake data in Qualtrics and run the analysis on that and make sure it all works before plugging in the real Qualtrics data (more time upfront)

---

# Other

> If there is any additional information that you feel needs to be included in your preregistration, please enter it here.

TODO

### 2019-04-09 analysis/options.R

@@ -1,0 +1,28 @@
+# Universal pandoc options ------------------------------------------------
+
+pander::panderOptions("table.split.table", Inf)
+pander::panderOptions("table.split.cells", Inf)
+pander::panderOptions("missing", "")
+pander::panderOptions("big.mark", ",")
+pander::panderOptions("digits", 3)
+pander::panderOptions("round", 3)
+pander::panderOptions("table.alignment.default", "left")
+
+
+# Bayes options -----------------------------------------------------------
+
+CHAINS <- 4
+ITER <- 4000
+WARMUP <- 2000
+BAYES_SEED <- 1234
+options(mc.cores = parallel::detectCores())
+
+
+# Ordered factor modeling setup -------------------------------------------
+
+# By default, R uses polynomial contrasts for ordered factors in linear models
+# options("contrasts")
+# So make ordered factors use treatment contrasts instead
+options(contrasts = rep("contr.treatment", 2))
+# Or do it on a single variable:
+# contrasts(df$x) <- "contr.treatment"

### 2019-04-09 README.Rmd
Package-ize this puppy!

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

Title <- "Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy"
Authors <- "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
Year <- "2019"
```

# `r Title`

[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Christopher Newport University  
[Marc Dotson](https://marriottschool.byu.edu/directory/details?id=50683) • Brigham Young University  
[Andrew Heiss](https://www.andrewheiss.com) • Brigham Young University

---

## Abstract

As space for civil society has closed around the world, transnational NGOs have faced a crisis of funding. We explore how NGOs have shifted from traditionally Northern funding sources toward grassroots private philanthropic money. How do individual donors in the US feel about donating to legally besieged NGOs abroad? Do legal restrictions on NGOs influence donors’ decision to donate? We use a conjoint survey experiment to argue that domestic political environments of NGO host countries influence preferences of private donors and that legal crackdowns on NGOs serve as a heuristic of organizational deservingness.

---

This repository contains the data and code for our paper. Our pre-print is online here:

> `r Authors`. (`r Year`). *`r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at `FUTURE_URL`

Our analysis notebook is accessible at <https://stats.andrewheiss.com/why-donors-donate/>.

## How to cite

Please cite this compendium as:

> `r Authors`. (`r format(Sys.Date(), "%Y")`). *Compendium of R code and data for `r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at `FUTURE_URL`

## How to download and install

You can either [download the compendium as a ZIP file](/archive/master.zip) or use GitHub to clone or fork the compendium repository (see the green "Clone or download" button at the top of the GitHub page).

In order to reproduce this project, you'll need to install the compendium as an R package. After downloading the compendium, do the following:

1. Open the compendium as a project in RStudio (double click on `donorheuristics.proj`).
2. Build the compendium package by clicking on the "Install and Restart" button in RStudio's "Build" panel.

You should now be able to run `library(donorheuristics)` and reproduce all the findings in the paper (as well as the paper itself).

To reproduce the analysis, run `make build` from RStudio's "Terminal" panel. Open `analysis/_site/` to see the results. Run `make serve` to serve the site at <http://localhost:7000>.

To reproduce the paper, run `make html` or `make tex` or `make docx` or `make paper` (for all three output formats) from the terminal. Open `manuscript/` (or `manuscript/tex_out/` for PDFs) to see the results.

---

## Project layout

There are several subdirectories with specific purposes:

**Tracked with git**

- `/data`: Data goes here. ***Temporarily* not tracked with git.**
- `/analysis`: All analysis related files go here as standalone R Markdown files dedicated to specific tasks (like `01_clean-data.Rmd` and `02_analysis.Rmd`, etc.). The most current version of this analysis notebook is accessible online at <https://stats.andrewheiss.com/why-donors-donate/>.
- `/R`: Various project-specific R scripts and functions go here. These are built as part of the package and are accessible after loading `library(donorheuristics)`.
- `/manuscript`: The actual writing goes here. A separate Makefile here generates the output as HTML, PDF (through XeTeX), and Word. For now, that Makefile depends on a bunch of helper scripts that only live on Andrew Heiss's computer, so he's the only one that can build the actual paper. Eventually he'll move those scripts (into the `/manuscript/pandoc` folder) here so anyone can build it.

**Not tracked with git**

These folders are ignored with `.gitignore` and instead live in a shared Dropbox folder.

- `/analysis/_site`: This is where the generated website lives. Don't edit anything here—it gets deleted and rewritten all the time.
- `/analysis/output`: All exported tables and figures go here.
- `/admin`: For administrative tasks, like IRB, pre-registration, readings, and other general files.
- `/manuscript/submissions`: For journal and conference sub missions.

## Project workflow

This project is designed to work with [RStudio](https://www.rstudio.com/), and it is built as an [R Markdown website](https://bookdown.org/yihui/rmarkdown/rmarkdown-site.html) which gets [uploaded to the internet](https://stats.andrewheiss.com/why-donors-donate/) via a Makefile. Because of SSH keys and server credentials, only Andrew Heiss can upload the compiled site.

To build the site, click on the "Build Website" button in the Build tab in RStudio. All `.Rmd` files in the root of the project will be knit individually in isolated R sessions. `.Rmd` files not in the project root are not knit when building the site.

We follow a few style and workflow guidelines:

- Write code in R Markdown files. 
- Try to follow the [tidyverse style guide](https://style.tidyverse.org/)
- Use `here::here()` to specify file paths. This makes it easier to move work from the `sandbox` folder to an actual R Markdown file. Here are some examples of using it in scripts:

    ```r
    library(tidyverse)
    library(donorheuristics)
    library(here)

    # Load general global options
    source(here("analysis", "options.R"))

    # Save a plot
    ggsave(plot_name, filename = here("analysis", "output", "figures", "figure1.pdf"), 
           width = 6, height = 4)

    # Save a table
    some_data_frame %>% 
      pandoc.table.return(caption = "Some table {#tbl:table-id}") %>% 
      cat(file = here("analysis", "output", "tables", "tbl-some-table.md"))
    ```

## Collaboration

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

Because not all collaborators use git, we use Dropbox as the main method for sharing code and data. Contact [Andrew Heiss](mailto:andrew@andrewheiss.com) to get access to the shared Dropbox folder.

At the same time, though, having actual version control with Git is nice. To make Git and Dropbox work correctly together, [we follow this system](http://www.math.cmu.edu/~gautam/sj/blog/20160406-dropbox-git.html). Here's how it works:

- The shared Dropbox folder contains everything for the project—the current git repository + all untracked files.
- **If you *are not* a git user**, make edits in the Dropbox folder and let Andrew know what you've done. He'll commit changes for you.
- **If you *are* a git user**, fork this repository to somewhere on your computer that's *not* in Dropbox. You'll work on your own local copy, pull any upstream changes, make edits, create branches, submit pull requests, and do all regular git things. Do not make any changes to the Dropbox folder itself, unless you're adding files to the folders that aren't tracked by git (e.g. adding a new paper to `/readings`).
- When pull requests are accepted or other commits are made, Andrew will pull those changes into the shared Dropbox folder.

tl;dr version:

- If you don't use git, edit files in the shared Dropbox folder and let Andrew know what you've done.
- If you do use git, fork this repository, edit files wherever you want on your computer (not in Dropbox, though), and make pull requests to the [main repository](https://github.com/andrewheiss/why-donors-donate). Only do stuff with the shared Dropbox folder if you're changing things that aren't tracked with git.

### 2019-04-09 R/donorheuristics-package.R

@@ -1,0 +1,9 @@
+#' The 'donorheuristics' package.
+#'
+#' @description Research on how donors respond to organizational and structural
+#'   NGO characteristics
+#'
+#' @docType package
+#' @name donorheuristics-package
+#' @aliases donorheuristics
+NULL

### 2019-04-09 R/graphics.R

@@ -1,23 +1,20 @@
-# Colors ------------------------------------------------------------------
-
-# This palette was generated with 7 values from scico's "roma" palette, but
-# ignoring the extra light greenish 4th color
-# https://github.com/thomasp85/scico
-#
-# scico(7, palette = "roma")
-ngo_red <- "#7E1900"
-ngo_orange <- "#AC7825"
-ngo_yellow <- "#D9D26A"
-ngo_blue_lt <- "#60C3D4"
-ngo_blue <- "#3877B6"
-ngo_blue_dk <- "#1A3399"
-
-
 # ggplot themes -----------------------------------------------------------
 
-update_geom_defaults("label", list(family = "Roboto Condensed Light"))
-update_geom_defaults("text", list(family = "Roboto Condensed Light"))
-
+#' theme_ngo
+#'
+#' A custom ggplot2 theme used throughout this project
+#'
+#' @param base_size base font size (default is 9)
+#' @param base_family base font family (default is Roboto Condensed)
+#'
+#' @export
+#'
+#' @examples
+#' library(ggplot2)
+#'
+#' ggplot(mtcars, aes(x = mpg, y = wt)) +
+#'   geom_point() +
+#'   theme_ngo()
 theme_ngo <- function(base_size = 9, base_family = "Roboto Condensed") {
   ret <- theme_bw(base_size, base_family) +
     theme(plot.title = element_text(size = rel(1.4), face = "bold",
@@ -42,16 +39,29 @@ theme_ngo <- function(base_size = 9, base_family = "Roboto Condensed") {
           legend.box.margin = margin(t = -0.5, unit = "lines"),
           legend.margin = margin(t = 0),
           legend.position = "bottom")
-  
+
   ret
 }
 
-theme_ngo_map <- function(base_size = 11, base_family = "Roboto Condensed") {
-  ret <- theme_void(base_size, base_family) +
-    theme(legend.position = "bottom",
-          legend.text = element_text(size = rel(1), family = "Roboto Condensed Light", face = "plain"),
-          legend.title = element_text(family = "Roboto Condensed", face = "bold"),
-          legend.key.size = unit(0.7, "lines"))
-  
-  ret
+
+# Conversion and formatting help ------------------------------------------
+
+#' Convert mms to pts
+#'
[…]

### 2019-04-11 analysis/simulated_data.R
Transfered simulated_data R script

@@ -1,0 +1,141 @@
+# Load libraries.
+library(tidyverse)
+
+# Number of responents.
+nresp <- 1000
+
+# Simulate data.
+Q2.1 <- runif(nresp, min = 1, max = 5) %>% 
+  round()
+Q2.2 <- runif(nresp, min = 1, max = 3) %>% 
+  round() 
+Q2.3 <- runif(nresp, min = 1, max = 6) %>% 
+  round() 
+Q5.1 <- runif(nresp, min = 1, max = 2) %>% 
+  round() 
+Q5.2 <- runif(nresp, min = 1, max = 8)
+Q5.6 <- runif(nresp, min = 1, max = 8)
+
+sim_data1 <-tibble(Q2.1, Q2.2, Q2.3, Q5.1, Q5.2, Q5.6)
+
+sim_data2 <- sim_data1 %>% 
+  mutate(Q2.1 = factor(
+    Q2.1, 
+    levels = c(1:5),
+    labels = c("Multiple times a day", "Every day", "Once a week", "Hardly ever","Never"),
+    ordered = TRUE)
+  ) %>% 
+  mutate(Q2.2 = factor(
+    Q2.2, 
+    levels = c(1:3),
+    labels = c("Always", "Sometimes", "Never"),
+    ordered = TRUE)) %>% 
+  mutate(Q2.3 = factor(
+    Q2.3, 
+    levels = c(1:6),
+    labels = c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters"),
+  )) %>% 
+  mutate(Q5.1 = factor(
+    Q5.1, 
+    levels = c(1:2),
+    labels = c("True", "False"),
+    ordered = TRUE))
+
+sim_data2
+
+-----------------------------------------
+
+# graph discrete 
+sim_data2 %>% 
+  ggplot(aes(x = Q5.1)) + 
+  geom_bar() +
+  labs(title = "Did you Vote in Last Election",
+       subtitle = "Q5.1 in the Survey")
+
+-----------------------------------------
+  
+# graph discrete vs discrete 
+sim_data2 %>% 
+  ggplot(aes(x = Q2.2, fill = Q5.1)) +
+  geom_bar(position = "fill") +
+  scale_fill_manual(
+    name = "Vote in Last Election", 
+    values = c("darkred", "tomato2")) +
+  labs(
+    x = "How Often Follow International News",
+    y = "Proportions", 
[…]

### 2019-05-02 analysis/preregistration.Rmd
Add generic IRB

@@
 date: "Last run: `r format(Sys.time(), '%F')`"
+bibliography: ../manuscript/references.bib
 ---
 
-# Study Information
+# Preregistration
 
-## Title
+We preregistered this study with the [Center for Open Science's](https://cos.io/) [Open Science Framework](https://osf.io/).
 
-TODO
+<p><a href="https://osf.io/dx973/register/565fb3678c5e4a66b5582f67" class="btn btn-md btn-success disabled" target="_blank" role="button">
+<i class="fa fa-pencil-square" aria-hidden="true"></i>&nbsp;
+OSF preregistration protocol &raquo;
+</a></p>
 
-## Authorship
-
-- Suparna Chaudhry
-- Marc Dotson
-- Andrew Heiss
-
-## Research Questions
-
-> Please list each research question included in this study.
-
-- What makes donors donate?
-- Structural factors - relationship with government - organizational level
-- Organizational -
-
-- Individuals
-
-TODO: Find that other conjoin article
-
-## Hypotheses
-
-> For each of the research questions listed in the previous section, provide one or multiple specific and testable hypotheses.
-Please state if the hypotheses are directional or non-directional.
-If directional, state the direction.
-A predicted effect is also appropriate here.
-
-- TODO
-- TODO
-
-EGAP - conjoint examples
-
-Subgroups, like people who have donated a lot vs. not
-
-TODO: Check distribution of donation frequency
-
-Size of donation - separate models
-Volunteering 
-Political views
-Prosocial views
-Demographic stuff
+\
 
@@
 
-# Sampling Plan
+# Human subjects and IRB approval
 
-## Existing data
+This project has received IRB approval from the human subjects research committees at BYU, Georgia State, and Christopher Newport. We have included a generic version of our protocol below.
 
-Registration prior to creation of data
+<p><a href="files/byu-irb-approval.pdf" class="btn btn-md btn-success disabled" target="_blank" role="button">
+<i class="fa fa-check-circle" aria-hidden="true"></i>&nbsp;
+BYU IRB approval
+</a> 
+&nbsp;
+<a href="files/cnu-irb-approval.pdf" class="btn btn-md btn-success disabled" target="_blank">
+<i class="fa fa-check-circle" aria-hidden="true" role="button"></i>&nbsp;
+Christopher Newport IRB approval
+</a>
+&nbsp;
+<a href="files/gsu-irb-approval.pdf" class="btn btn-info btn-md disabled" target="_blank" role="button">
+<i class="fa fa-check-circle" aria-hidden="true"></i>&nbsp;
+Georgia State IRB approval
+</a></p>
 
-## Explanation of existing data
+\
 
-We will not use any existing data.
+```{r child = "survey/irb.md"}
+```
 
-## Data collection procedures
-
-> Please describe the process by which you will collect your data.
-If you are using human subjects, this should include the population from which you obtain subjects, recruitment efforts, payment for participation, how subjects will be selected for eligibility from the initial pool (e.g.
-inclusion and exclusion rules), and your study timeline.
-For studies that don’t include human subjects, include information about how you will collect samples, duration of data gathering efforts, source or location of samples, or batch numbers you will use.
-
-TODO
-
-## Sample size
-
-> Describe the sample size of your study.
-How many units will be analyzed in the study?
-This could be the number of people, birds, classrooms, plots, interactions, or countries included.
-If the units are not individuals, then describe the size requirements for each unit.
-If you are using a clustered or multilevel design, how many units are you collecting at each level of the analysis?
-
-TODO
-
-## Sample size rationale
-
-> This could include a power analysis or an arbitrary constraint such as time, money, or personnel.
-
-TODO
-
-## Stopping rule
-
-> If your data collection procedures do not give you full control over your exact sample size, specify how you will decide when to terminate your data collection.
-
-TODO
-
----
-
-# Variables
-
-## Manipulated variables
-
-> Describe all variables you plan to manipulate and the levels or treatment arms of each variable. For observational studies and meta-analyses, simply state that this is not applicable.
-
-TODO
-
-## Measured variables
-
-> Describe each variable that you will measure.
-This will include outcome measures, as well as any predictors or covariates that you will measure.
-You do not need to include any variables that you plan on collecting if they are not going to be included in the confirmatory analyses of this study.
-
-TODO
-
-## Indices
-
-> If any measurements are  going to be combined into an index (or even a mean), what measures will you use and how will they be combined?
-Include either a formula or a precise description of your method.
-If your are using a more complicated statistical method to combine measures (e.g.
-a factor analysis), you can note that here but describe the exact method in the analysis plan section.
-
-TODO
-
----
-
-# Design plan
-
-## Study type
-
-Experiment - A researcher randomly assigns treatments to study subjects, this includes field or lab experiments.
-This is also known as an intervention experiment and includes randomized controlled trials.
-
-## Blinding
-
-For studies that involve human subjects, they will not know the treatment group to which they have been assigned.
-
-## Study design
-
-> Describe your study design.
-Examples include two-group, factorial, randomized block, and repeated measures.
-Is it a between (unpaired), within-subject (paired), or mixed design?
-Describe any counterbalancing required.
-Typical study designs for observation studies include cohort, cross sectional, and case-control studies.
-
-TODO - conjoint design
-
-## Randomization
-
-> If you are doing a randomized study, how will you randomize, and at what level?
-
-TODO
-
----
-
-# Analysis Plan
-
-## Statistical models
-
-> What statistical model will you use to test each hypothesis?
-Please include the type of model (e.g.
-ANOVA, multiple regression, SEM, etc) and the specification of the model (this includes each variable that will be included as predictors, outcomes, or covariates).
-Please specify any interactions that will be tested and remember that any test not included here must be noted as an exploratory test in your final article.
-
-TODO
-
-## Transformations
-
-> If you plan on transforming, centering, recoding the data, or will require a coding scheme for categorical variables, please describe that process.
-
-TODO
-
-## Follow-up analyses
-
-> If not specified previously, will you be conducting any confirmatory analyses to follow up on effects in your statistical model, such as subgroup analyses, pairwise or complex contrasts, or follow-up tests from interactions?
-Remember that any analyses not specified in this research plan must be noted as exploratory.
-
-TODO
-
-## Inference criteria
-
-> What criteria will you use to make inferences?
-Please describe the information you’ll use (e.g.
-specify the p-values, Bayes factors, specific model fit indices), as well as cut-off criterion, where appropriate.
-Will you be using one or two tailed tests for each of your analyses?
-If you are comparing multiple conditions or testing multiple hypotheses, will you account for this?
-
-TODO
-
-## Data exclusion
-
-> How will you determine which data points or samples (if any) to exclude from your analyses? How will outliers be handled?
-
-TODO
-
-## Missing data
-
-> How will you deal with incomplete or missing data?
-
-TODO
-
-## Exploratory analysis (optional)
-
-> If you plan to explore your data set to look for unexpected differences or relationships, you may describe those tests here.
-An exploratory test is any test where a prediction is not made up front, or there are multiple possible tests that you are going to use.
-A statistically significant finding in an exploratory test is a great way to form a new confirmatory hypothesis, which could be registered at a later time.
-
-TODO
-
----
-
-# Script (optional)
-
-> Upload an analysis script with clear comments.
-This optional step is helpful in order to create a process that is completely transparent and increase the likelihood that your analysis can be replicated.
-We recommend that you run the code on a simulated dataset in order to check that it will run without errors.
-
-MAYBE: This would be cool, but we'd need to create fake data in Qualtrics and run the analysis on that and make sure it all works before plugging in the real Qualtrics data (more time upfront)
-
----
-
-# Other
-
-> If there is any additional information that you feel needs to be included in your preregistration, please enter it here.
-
-TODO
+# References

### 2019-05-02 analysis/experiment.Rmd
Add section about experimental design

@@
 
+# Design
+
+We use a partial fractional factorial design using the following organizational attributes:
+
+**Organizations**
+
+- Amnesty International
+- Greenpeace
+- Oxfam
+- Red Cross
+
+**Issue areas**
+
+- Emergency response
+- Environment
+- Human rights
+- Refugee relief
+
+**Organizational practices**
+
+- Financial transparency
+- Accountability
+
+**Funding sources**
+
+- Funded primarily by many small private donations
+- Funded primarily by a handful of wealthy private donors
+- Funded primarily by government grants
+
+**Relationship with host government**
+
+- Friendly relationship with government
+- Criticized by government
+- Under government crackdown
+
+\
+
+Participants are then presented with random combinations of these attributes and asked to select which hypothetical organization they'd be willing to donate to.
+Participants see 12 iterations of a question that looks like this:
+
+> *Q4.x*: For each of the next 12 questions, imagine you are selecting an organization you will donate to and that each of the listed organizations exists.
+Which of the following organizations would you donate to?
+
+```{r conjoint-table, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
+library(dplyr)
+library(pander)
+set.seed(12345)
+
+orgs <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
+issues <- c("Emergency response", "Environment", "Human rights", "Refugee relief")
+orgal_practices <- c("Financial transparency", "Accountability")
+funding <- c("Many small private donations", "Handful of wealthy private donors", "Government grants")
+govt <- c("Friendly relationship", "Criticized", "Under crackdown")
+
+tribble(
+  ~Attribute, ~`Option 1`, ~`Option 2`, ~`Option 3`, ~None,
+  "Organization", sample(orgs, 1), sample(orgs, 1), sample(orgs, 1), "—",
+  "Issue area", sample(issues, 1), sample(issues, 1), sample(issues, 1), "—",
+  "Organizational practices", sample(orgal_practices, 1), sample(orgal_practices, 1), sample(orgal_practices, 1), "—",
+  "Funding sources", sample(funding, 1), sample(funding, 1), sample(funding, 1), "—",
+  "Relationship with host government", sample(govt, 1), sample(govt, 1), sample(govt, 1), "—"
+) %>% 
+  mutate(Attribute = pandoc.strong.return(Attribute)) %>% 
+  pandoc.table(justify = "lcccc", split.tables = Inf)
+```
+
+\
+
+Our sample size is 1,000, which constitutes a sufficient size for model estimation.
+A sample size of at least 500 respondents is typical for estimating a hierarchical Bayesian model based on conjoint data.
+We double this amount because we are interested in analyzing subpopulations of respondents, which requires a larger sample.
+We present respondents with 4 hypothetical organizations that have 4 randomly assigned features.
+Respondents will be shown 12 sets of hypothetical organizations.
+This partial fractional factorial design results in 288 (4 × 4 × 2 × 3 × 3) possible combinations of organization features, and no single respondent will be offered every combination.
+To provide better coverage and arrive at better individual-level estimates, we use a larger sample size.
+
 # Survey experiment {.survey}

### 2019-05-02 analysis/survey/preregistration.Rmd
Add initial preregistration content

---
title: "Results"
author: "Andrew Heiss, Marc Dotson, and Suparna Chaudhry"
---

See Chaudhry and Heiss (2019) preregistration for reference: <https://osf.io/dx973>

---

# Study Information

## Title

Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

## Authorship

- Suparna Chaudhry
- Marc Dotson
- Andrew Heiss

## Research Questions

> Please list each research question included in this study.

ANDREW TODO: Finish this section

We use a conjoint survey experiment to examine the impact of organizational and structural features of nongovernmental organizations (NGOs) on their donors’ decisions to engage in philanthropy. We explore three research questions in this study:

1. Donors rely on shortcuts, signals, and heuristics to determine the trustworthiness of NGOs, since seeking out complete information about an organization's deservingness and efficiency is costly and time-consuming. Previous research has found that structural characterists are common heuristics for donors. Organizational vs. structural heuristics

2. How those interact with individual characteristics

3. What is the optimal mix of attributes?

We are interested in whether the contentiousness of an NGO’s relationship with its host government influences donor decision making. Do donors care if nonprofits they care about are criticized by or kicked out of the countries they work in?

We are also interested in the effect of organizational characteristics on donor decision making. Do managerial practices (financial transparency and accountability systems), funding sources (private donations and government grants), and issue areas (emergency response, environmental issues, human rights, and refugee relief) also serve as heuristics that signal an organization’s deservingness to donors?

To test possible confounding and mediating effects, we also plan to see how donor characteristics influence the decision to donate, including political ideology, political knowledge, religious attendance, involvement in charitable activities, involvement in activism, and other demographic characteristics.

## Hypotheses

> For each of the research questions listed in the previous section, provide one or multiple specific and testable hypotheses. Please state if the hypotheses are directional or non-directional. If directional, state the direction. A predicted effect is also appropriate here.

ANDREW TODO: write these

---

# Sampling Plan

## Existing data

Registration prior to creation of data

## Explanation of existing data

We will not use any existing data.

## Data collection procedures

> Please describe the process by which you will collect your data. If you are using human subjects, this should include the population from which you obtain subjects, recruitment efforts, payment for participation, how subjects will be selected for eligibility from the initial pool (e.g. inclusion and exclusion rules), and your study timeline. For studies that don’t include human subjects, include information about how you will collect samples, duration of data gathering efforts, source or location of samples, or batch numbers you will use.

Participants of the survey experiment will be recruited through Centiment, a commercial online provider of high quality nonprobability opt-in survey panels. Centiment ensures panel quality by actively recruiting representative samples of the US population and provides monetary incentives and rewards to participants.

To see how varying NGO characteristics influence the decision to donate, our sample will be representative of a population of people who are likely to donate to charity. We ask potential participants a screening question early in the survey (“Q2.5: How often do you donate to charity”). If a participant responds that they give to once every few years or never, they will be disqualified from the study and the survey will end early.

We will provide Centiment with a link to the survey, which is hosted by Qualtrics. Centiment will then distribute the link to their panel. Participants are compensated through Centiment’s internal reward system through cash, points, and other incentives. Centiment does not provide precise details of participant compensation. Centiment states that their compensation is “fair,” and the company’s business model encourages the company to find and maintain high quality panelists. We thus infer that the amount provided is fair and justified. Centiment users receive compensation from the company following the completion of the survey.

## Sample size

> Describe the sample size of your study. How many units will be analyzed in the study? This could be the number of people, birds, classrooms, plots, interactions, or countries included. If the units are not individuals, then describe the size requirements for each unit. If you are using a clustered or multilevel design, how many units are you collecting at each level of the analysis?

Our target sample size is 1,000 participants.

## Sample size rationale

> This could include a power analysis or an arbitrary constraint such as time, money, or personnel.

TODO: Add citation here maybe, or clarify the language so it's accurate

1,000 respondents constitutes a sufficient size for model estimation. A sample size of at least 500 respondents is typical for estimating a hierarchical Bayesian model based on conjoint data. We double this amount because we are interested in analyzing subpopulations of respondents, which requires a larger sample.

## Stopping rule

> If your data collection procedures do not give you full control over your exact sample size, specify how you will decide when to terminate your data collection.

Centiment will monitor how many surveys are successfully completed and will solicit responses until our 1,000 target is met.

---

# Variables

## Manipulated variables

> Describe all variables you plan to manipulate and the levels or treatment arms of each variable. For observational studies and meta-analyses, simply state that this is not applicable.

We use a partial fractional factorial design with the following attributes:

**Organizations:**

- *Amnesty International*: A London-based non-governmental organization known for its focus on human rights.
- *Greenpeace*: An independent, nonprofit, global campaigning organization known for using non-violent, creative confrontation to expose global environmental problems and their causes.
- *Oxfam*: An international group known for providing help to poor countries and disaster areas, with a focus on helping create lasting solutions to the injustice of poverty. 
- *Red Cross*: An international organization known for caring for the wounded, sick, and homeless in wartime and following natural disasters.

**Issue areas:**

- *Emergency response*: Respond to situations that pose an immediate risk to health, life, property, or the environment.
- *Environment*: Protecting the natural world and the impact of human activity on its condition.
- *Human rights*: Protect the inalienable fundamental rights to which a person is inherently entitled simply because he or she is a human being.
- *Refugee relief*: Provide relief for those who have been forced to flee his or her country because of persecution, war or violence.

**Organizational practices:**

- *Financial transparency*: Timely and reliable disclosure regarding donations and financial allocations. 
- *Accountability*: An obligation or willingness to accept responsibility or to account for one's actions.

**Funding sources:**

- *Funded primarily by many small private donations*: Funds by individuals who make small independent contributions.
- *Funded primarily by a handful of wealthy private donors*: Funds by wealthy individuals or families, who receive tax deductions for donations.
- *Funded primarily by government grants*: Non-repayable funds gifted by a government department.

**Relationship with host government:**

- *Friendly relationship with government*: Organization has a friendly relationship with its host government.
- *Criticized by government*: Organization faces public condemnation from the government.
- *Under government crackdown*: Host government has undertaken official action to limit or stop the organization.

Participants are then presented with random combinations of these attributes and asked to select which of three hypothetical organizations they'd be willing to donate to.

This results in five manipulated variables:

- Organization
- Issue area
- Organizational practices
- Funding source
- Relationship with host government

## Measured variables

> Describe each variable that you will measure. This will include outcome measures, as well as any predictors or covariates that you will measure. You do not need to include any variables that you plan on collecting if they are not going to be included in the confirmatory analyses of this study.

We collect one outcome measure, which we use as a dependent variable in our analysis. After displaying a table of randomized organizational attributes, we ask respondents "Imagine you are selecting an organization you will donate to and that each of the listed organizations exists. Which of the following organizations would you donate to?". Respondents are shown 12 of these sets, and their responses constitute our outcome.

We measure several other covariates that inform and predict an individual's choice of donating to a hypothetical organization (see survey instrument for complete question and response wording):

**Public affairs knowledge**

- *Q2.1*: How often do you follow national news?
- *Q2.2*: How often do you follow international news?
- *Q2.3*: Which mediums do you use to follow news?
- *Q2.4*: How often would you say you follow what's going on in government and public affairs?
- *Q5.7*: Have you ever traveled to a developing country?

**Public affairs trust**

- *Q5.6*: Here is a 7-point scale on which you trust political institutions and the state. The scale is arranged from no trust (left) to complete trust (right). Where would you place yourself on this scale?

**Public affairs activity**

- *Q5.1*: Did you vote in the last election?

**Political ideology**

- *Q5.2*: 7-point scale on which the political views that people might hold are arranged from extremely liberal (left) to extremely conservative (right).

**Social ideology**

- *Q5.11*: Here is a 7-point scale of your prosocial views. The scale is arranged from equality (left) to altruism (right). Where would you place yourself on this scale?

**Charity trust**

- *Q2.7*: How important is it that you trust a charity before giving to it?
- *Q2.8*: How much do you trust charities?

**Charity activity**

- *Q2.5*: How often do you donate to charity?
- *Q2.6*: How much did you donate to charity last year?

**Volunteer activity**

- *Q2.9*: Have you volunteered in the past 12 months?
- *Q2.10*: How often do you volunteer?

**Activism activity**

- *Q5.4*: Historically, how involved have you been in activist causes?
- *Q5.5*: Historically, how involved has your family been in activist causes?

**Voluntary association membership**

- *Q5.3*: Here is a list of different types of voluntary organizations. For each organization, indicate whether you are an active member, an inactive member, or not a member of that type of organization:

    - Church or religious organization
    - Sport or recreational organization
    - Art, music, or educational organization
    - Labor union
    - Political party
    - Environmental organization
    - Professional association
    - Humanitarian or charitable organization
    - Consumer organization
    - Other organization

**Religiosity**

- *Q5.8*: How often do you attend religious or worship services, not including weddings and funerals?
- *Q5.9*: How important is religion in your life?
- *Q5.10*: What is your current religion, if any?

**Demographics**

- *Q5.12*: What is your gender?
- *Q5.13*: Are you now married, widowed, divorced, separated, or never married?
- *Q5.14*: What is the highest degree or level of school you have completed?
- *Q5.15*: What is your annual household income before taxes?
- *Q5.16*: Choose one or more races that you consider yourself to be:
- *Q5.17*: How old are you?
- *Q5.18*: What is your ZIP code?

## Indices

> If any measurements are  going to be combined into an index (or even a mean), what measures will you use and how will they be combined? Include either a formula or a precise description of your method. If your are using a more complicated statistical method to combine measures (e.g. a factor analysis), you can note that here but describe the exact method in the analysis plan section.

TODO: The paper at <https://osf.io/u43yg> uses Bayesian hierarchical stuff and they talk a lot about index stuff. I'm not familiar with the model, though, so I don't know what applies here.

---

# Design plan

## Study type

Experiment - A researcher randomly assigns treatments to study subjects, this includes field or lab experiments. This is also known as an intervention experiment and includes randomized controlled trials.

## Blinding

For studies that involve human subjects, they will not know the treatment group to which they have been assigned.

## Study design

> Describe your study design. Examples include two-group, factorial, randomized block, and repeated measures. Is it a between (unpaired), within-subject (paired), or mixed design? Describe any counterbalancing required. Typical study designs for observation studies include cohort, cross sectional, and case-control studies.

TODO: Explain conjoint design

## Randomization

> If you are doing a randomized study, how will you randomize, and at what level?

TODO: Explain randomization

---

# Analysis Plan

## Statistical models

> What statistical model will you use to test each hypothesis? Please include the type of model (e.g. ANOVA, multiple regression, SEM, etc) and the specification of the model (this includes each variable that will be included as predictors, outcomes, or covariates). Please specify any interactions that will be tested and remember that any test not included here must be noted as an exploratory test in your final article.

TODO: Explain statistical model

TODO: Make sure all this mathy stuff is right

TODO: Maybe specify priors?

Bayesian hierarchical multinomial logit

$$
\begin{aligned}
\beta &\sim \text{MVN}(Z \Gamma, \xi) \\
y &\sim \text{MNL}(X \beta, \varepsilon)
\end{aligned}
$$

where $y$ = choice to donate, $X$ = design matrix of attribute levels, $\beta$ = latent individual preferences, $\Z$ = SOMETHING, $\Gamma$ = individual covariates, and $\varepsilon$ and $\xi$ = errors.

## Transformations

> If you plan on transforming, centering, recoding the data, or will require a coding scheme for categorical variables, please describe that process.

TODO: Are there any others we should collapse?

We collapse several of our variables into dichotomous and trichotomous versions, following this system:

*Q2.1*: How often do you follow national news?

    - Multiple times a day → At least once a day
    - Every day → At least once a day
    - Once a week → Once a week
    - Hardly ever → Rarely (base case)
    - Never → Rarely

*Q2.4*: How often would you say you follow what's going on in government and public affairs?

    - Most of the time → Often
    - Some of the time → Often
    - Only now and then → Not often (base case)
    - Hardly at all → Not often (base case)

*Q2.5*: How often do you donate to charity (with either cash or in-kind)?

    - Once a week → At least once a month
    - Once a month → At least once a month
    - Once every three months → More than once a month, less than once a year
    - Once every six months → More than once a month, less than once a year
    - Once a year → More than once a month, less than once a year
    - Once every few years → Rarely (base case)
    - Never → Rarely

*Q2.10*: How often do you volunteer?

    - Once a week → At least once a month
    - Once a month → At least once a month
    - Once every three months → More than once a month, less than once a year
    - Once every six months → More than once a month, less than once a year
    - Once a year → More than once a month, less than once a year
    - Once every few years → Rarely (base case)
    - Never → Rarely

*Q5.4*: Historically, how involved have you been in activist causes?

    - Extremely involved → Involved
    - Very involved → Involved
    - Moderately involved → Involved
    - Slightly involved → Not involved (base case)
    - Never involved → Not involved

*Q5.5*: Historically, how involved has your family been in activist causes?

    - Extremely involved → Involved
    - Very involved → Involved
    - Moderately involved → Involved
    - Slightly involved → Not involved (base case)
    - Never involved → Not involved

*Q5.8*: How often do you attend religious or worship services, not including weddings and funerals?

    - More than once a week → At least once a month
    - Once a week → At least once a month
    - Once or twice a month → At least once a month
    - A few times a year → Rarely (base case)
    - Seldom → Rarely
    - Never → Rarely
    - Don't know → NULL

*Q5.9*: How important is religion in your life?

    - Extremely important → Important
    - Very important → Important
    - Moderately important → Important
    - Slightly important → Not important (base case)
    - Not at all important → Not important

*Q5.15*: What is your annual household income before taxes?

    - Less than $10,000 → More/less than median (base case = less than median)
    - \$10,000 to \$19,999 → More/less than median
    - \$20,000 to \$29,999 → More/less than median
    - \$30,000 to \$39,999 → More/less than median
    - \$40,000 to \$49,999 → More/less than median
    - \$50,000 to \$59,999 → More/less than median
    - \$60,000 to \$69,999 → More/less than median
    - \$70,000 to \$79,999 → More/less than median
    - \$80,000 to \$89,999 → More/less than median
    - \$90,000 to \$99,999 → More/less than median
    - \$100,000 to \$149,999 → More/less than median
    - \$150,000 to \$199,999 → More/less than median
    - \$200,000 to \$299,999 → More/less than median
    - \$300,000 or more → More/less than median

*Q5.17*: How old are you?

    - Under 18 → More/less than median (base case = less than median)
    - 18 - 24 → More/less than median
    - 25 - 34 → More/less than median
    - 35 - 44 → More/less than median
    - 45 - 54 → More/less than median
    - 55 - 64 → More/less than median
    - 65 - 74 → More/less than median
    - 75 - 84 → More/less than median
    - 85 or older → More/less than median

## Follow-up analyses

> If not specified previously, will you be conducting any confirmatory analyses to follow up on effects in your statistical model, such as subgroup analyses, pairwise or complex contrasts, or follow-up tests from interactions? Remember that any analyses not specified in this research plan must be noted as exploratory.

TODO: Do we do this?

## Inference criteria

> What criteria will you use to make inferences? Please describe the information you’ll use (e.g. specify the p-values, Bayes factors, specific model fit indices), as well as cut-off criterion, where appropriate. Will you be using one or two tailed tests for each of your analyses? If you are comparing multiple conditions or testing multiple hypotheses, will you account for this?

NOTE: Here's a preregistration from another Bayesian hierarchical multinomial logit for reference: <https://osf.io/u43yg>

TODO: What criteria do we use?

Possibilities:

- Market simulation based on the β - determines the optimal policies
- Or look at the posteriors of the βs
- β importance - we find most important attribute + most important levels inside

## Data exclusion

> How will you determine which data points or samples (if any) to exclude from your analyses? How will outliers be handled?

We ask potential participants a screening question early in the survey ("Q2.5: How often do you donate to charity"). If a participant responds that they give to once every few years or never, they will be disqualified from the study and the survey will end early.

We include one question ("*Q2.11*: Please select blue from the following list:") to monitor respondent attention. In our analysis we will exclude respondents who fail this question.

## Missing data

> How will you deal with incomplete or missing data?

Because all survey questions are required, we do not anticipate issues with incomplete or missing data.

## Exploratory analysis (optional)

> If you plan to explore your data set to look for unexpected differences or relationships, you may describe those tests here. An exploratory test is any test where a prediction is not made up front, or there are multiple possible tests that you are going to use. A statistically significant finding in an exploratory test is a great way to form a new confirmatory hypothesis, which could be registered at a later time.

TODO: NA?

---

# Script (optional)

> Upload an analysis script with clear comments. This optional step is helpful in order to create a process that is completely transparent and increase the likelihood that your analysis can be replicated. We recommend that you run the code on a simulated dataset in order to check that it will run without errors.

Nothing.

---

# Other

> If there is any additional information that you feel needs to be included in your preregistration, please enter it here.

Nothing.

### 2019-05-02 analysis/survey/preregistration.Rmd
Fix list indentation
Fix incorrect TeX

@@
 
-where $y$ = choice to donate, $X$ = design matrix of attribute levels, $\beta$ = latent individual preferences, $\Z$ = SOMETHING, $\Gamma$ = individual covariates, and $\varepsilon$ and $\xi$ = errors.
+where $y$ = choice to donate, $X$ = design matrix of attribute levels, $\beta$ = latent individual preferences, $Z$ = SOMETHING, $\Gamma$ = individual covariates, and $\varepsilon$ and $\xi$ = errors.
 

### 2019-05-02 analysis/simulated_data.R
Revert "Transfered simulated_data R script"
This reverts commit 2110a037b97d12be7d8688da72c7a0a3ced9df32.

@@ -1,141 +1,0 @@
-# Load libraries.
-library(tidyverse)
-
-# Number of responents.
-nresp <- 1000
-
-# Simulate data.
-Q2.1 <- runif(nresp, min = 1, max = 5) %>% 
-  round()
-Q2.2 <- runif(nresp, min = 1, max = 3) %>% 
-  round() 
-Q2.3 <- runif(nresp, min = 1, max = 6) %>% 
-  round() 
-Q5.1 <- runif(nresp, min = 1, max = 2) %>% 
-  round() 
-Q5.2 <- runif(nresp, min = 1, max = 8)
-Q5.6 <- runif(nresp, min = 1, max = 8)
-
-sim_data1 <-tibble(Q2.1, Q2.2, Q2.3, Q5.1, Q5.2, Q5.6)
-
-sim_data2 <- sim_data1 %>% 
-  mutate(Q2.1 = factor(
-    Q2.1, 
-    levels = c(1:5),
-    labels = c("Multiple times a day", "Every day", "Once a week", "Hardly ever","Never"),
-    ordered = TRUE)
-  ) %>% 
-  mutate(Q2.2 = factor(
-    Q2.2, 
-    levels = c(1:3),
-    labels = c("Always", "Sometimes", "Never"),
-    ordered = TRUE)) %>% 
-  mutate(Q2.3 = factor(
-    Q2.3, 
-    levels = c(1:6),
-    labels = c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters"),
-  )) %>% 
-  mutate(Q5.1 = factor(
-    Q5.1, 
-    levels = c(1:2),
-    labels = c("True", "False"),
-    ordered = TRUE))
-
-sim_data2
-
------------------------------------------
-
-# graph discrete 
-sim_data2 %>% 
-  ggplot(aes(x = Q5.1)) + 
-  geom_bar() +
-  labs(title = "Did you Vote in Last Election",
-       subtitle = "Q5.1 in the Survey")
-
------------------------------------------
-  
-# graph discrete vs discrete 
-sim_data2 %>% 
-  ggplot(aes(x = Q2.2, fill = Q5.1)) +
-  geom_bar(position = "fill") +
-  scale_fill_manual(
-    name = "Vote in Last Election", 
-    values = c("darkred", "tomato2")) +
-  labs(
-    x = "How Often Follow International News",
-    y = "Proportions", 
[…]

### 2019-05-02 analysis/survey/preregistration.Rmd
Added details to pre-registration

@@
 
-3. What is the optimal mix of attributes?
+3. What is the optimal mix of attribute levels?
 
@@
 
-TODO: Add citation here maybe, or clarify the language so it's accurate
-
-1,000 respondents constitutes a sufficient size for model estimation.
 A sample size of at least 500 respondents is typical for estimating a hierarchical Bayesian model based on conjoint data.
-We double this amount because we are interested in analyzing subpopulations of respondents, which requires a larger sample.
+We double this amount because we are interested in analyzing subpopulations of respondents, which requires a larger sample, and we had sufficient budget to acquire up to 1,000 respondents.
 
@@
 
-TODO: Explain conjoint design
+We use a fractional factorial design.
+Since no single respondent can possibly see all possible combinations of the attribute levels, we create a number of different versions of the experimental design.
+We utilize a hierarchical Bayesian model in part to allow for information sharing across like respondents when estimating individual-level preferences for the attribute levels.
 
@@
 
-TODO: Explain randomization
+Every respondent will be randomly assigned a version of the fractional factorial experimental design.
 
@@
 
-TODO: Explain statistical model
-
-TODO: Make sure all this mathy stuff is right
-
-TODO: Maybe specify priors?
-
-Bayesian hierarchical multinomial logit
+We will use a hierarchical Bayesian multinomial logit model with conjugate or otherwise typical priors.
+The individual-level model is the multinomial logit and the upper-level model of heterogeneity is multivariate normal,
 
@@
 
-where $y$ = choice to donate, $X$ = design matrix of attribute levels, $\beta$ = latent individual preferences, $Z$ = SOMETHING, $\Gamma$ = individual covariates, and $\varepsilon$ and $\xi$ = errors.
+where $y$ = which alternative the respondent chooses to donate, $X$ = design matrix of attribute levels, $\beta$ = latent individual preferences for the attribute levels, $Z$ = matrix of individual-level covariates, $\Gamma$ = matrix of coefficients mapping individual-level covariates onto the latent individual-level preferences, and $\varepsilon$ and $\xi$ = errors.
 
@@
 
-TODO: What criteria do we use?
+TODO: Specify what the "competing sets of covariates" are that we'll include in the distribution of heterogeneity.
 
-Possibilities:
+We will examine the aggregate marginal posterior distributions of the attribute levels and utilize 95% credible intervals to establish "significance." Effects are "significant" if the 95% credible intervals don't include 0.
+Similarly, marginal posterior distributions are "significantly" different if the 95% credible intervals don't overlap.
 
-- Market simulation based on the β - determines the optimal policies
-- Or look at the posteriors of the βs
-- β importance - we find most important attribute + most important levels inside
+We will examine the marginal posterior distributions of the following models:
+
+- Organizational and structural attribute levels with an intercept-only distribution of heterogeneity
+- Organizational and structural attribute levels with competing sets of covariates in the distribution of heterogeneity
+
+Finally, we will employ the posterior distribution of model parameters to conduct counterfactual analyses via a market simulator to determine optimal policies.
 

### 2019-05-02 analysis/survey/preregistration.Rmd
Added comments to the pre-registration

@@
 
+COMMENT: I don't see a need to index (i.e., use dimension reduction).
+We should just be collapsing covariates via Transformations in a way motivated by your experience and theory with respect to the "competing sets of covariates in the distribution of heterogeneity" that we'd like to use to compare effects on the marginal posteriors of the preference parameters.
+
 ---
@@
 TODO: Are there any others we should collapse?
+
+COMMENT: See comment for Indices.
 
@@
 
+COMMENT: No, it's really just looking at/comparing the posterior marginals on their own vs. the posterior marginals with different covariates includes, plus the market simulation.
+
 ## Inference criteria
@@
 
-TODO: Specify what the "competing sets of covariates" are that we'll include in the distribution of heterogeneity.
+COMMENT: Specify what the "competing sets of covariates" are that we'll include in the distribution of heterogeneity. This should be the motivation of the collapses specified in Transformations.
 
@@
 
-TODO: NA?
+NA.
 

### 2019-05-03 analysis/survey/preregistration.Rmd
Add reserach questions

@@
 
-ANDREW TODO: Finish this section
-
 We use a conjoint survey experiment to examine the impact of organizational and structural features of nongovernmental organizations (NGOs) on their donors’ decisions to engage in philanthropy.
@@
 
-1.
+1. **Do donors rely on structural characteristics of NGOs as heuristics when deciding to donate? How do structural heuristics compare to organizational heuristics?**
+
 	Donors rely on shortcuts, signals, and heuristics to determine the trustworthiness of NGOs, since seeking out complete information about an organization's deservingness and efficiency is costly and time-consuming.
-Previous research has found that structural characterists are common heuristics for donors.
-Organizational vs.
-structural heuristics
+Previous research has found that an NGO's organizational characteristics commonly serve as heuristics for donors.
+Donors use an organization's overhead costs, the issues it works on, its transparency and accountability practices, and a host of other organizational practices as signals of an organization's efficiency and deservingness, which then influences their decision to make a donation.
+These kinds of heuristics are attributes that organizations can typically control—NGOs can publish annual reports, restructure their management, and engage in other strategies to appear more worthy of donation.
 
-2. How those interact with individual characteristics
-
-3. What is the optimal mix of attribute levels?
-
+	Structural characteristics, such as the political and legal environment an NGO faces in its host country, may also serve as signals to donors of NGO deservingness.
 We are interested in whether the contentiousness of an NGO’s relationship with its host government influences donor decision making.
-Do donors care if nonprofits they care about are criticized by or kicked out of the countries they work in?
+Do donors care if nonprofits they care about are criticized by, persecuted by, or expelled from the countries they work in?
 
 	We are also interested in the effect of organizational characteristics on donor decision making.
-Do managerial practices (financial transparency and accountability systems), funding sources (private donations and government grants), and issue areas (emergency response, environmental issues, human rights, and refugee relief) also serve as heuristics that signal an organization’s deservingness to donors?
+How do managerial practices (financial transparency and accountability systems), funding sources (private donations and government grants), and issue areas (emergency response, environmental issues, human rights, and refugee relief) compare to structural characteristics when deciding to donate?
+Which heuristics are more influential?
 
-To test possible confounding and mediating effects, we also plan to see how donor characteristics influence the decision to donate, including political ideology, political knowledge, religious attendance, involvement in charitable activities, involvement in activism, and other demographic characteristics.
+2.
+**How do individual-level donor characteristics interact with structural and organizational heuristics?
+Which kinds of people are more or less likely to consider an NGO's host country political environment, managerial practices, funding sources, or issue area?**
+
+	The decision to donate to an NGO is not determined solely by an organization's characteristics.
+Donors themselves have personality traits, preferences, and experiences that make them more or less likely to engage in philanthropy.
+We are interested in how individual donor characteristics, such as political ideology, political knowledge, religious attendance, involvement in charitable activities, involvement in activism, and demographic attributes interact with organizational- and structural-level factors.
+
+3. **What is the optimal mix of attribute levels for NGOs interested in maximizing donations?**
+
+	Finally, given individual donor characteristics and preferences, we are interested in finding the optimal mix of organizational and structural attributes.
+What might an NGO try to emphasize in its marketing campaigns?
+Should it highlight its funding sources, managerial practices, issue area, or relationship with its host governments (even if that relationship is negative)?
 

### 2019-05-03 analysis/survey/preregistration.Rmd
No indexes

@@
 
-TODO: The paper at <https://osf.io/u43yg> uses Bayesian hierarchical stuff and they talk a lot about index stuff. I'm not familiar with the model, though, so I don't know what applies here.
-
-COMMENT: I don't see a need to index (i.e., use dimension reduction).
-We should just be collapsing covariates via Transformations in a way motivated by your experience and theory with respect to the "competing sets of covariates in the distribution of heterogeneity" that we'd like to use to compare effects on the marginal posteriors of the preference parameters.
+We will not combine any measures to create indicies.
 

### 2019-05-04 analysis/survey/preregistration.Rmd
Nicer LaTeX
No confirmatory analyses
Clean up metadata

@@
 ---
-title: "Results"
+title: "Preregistration"
 author: "Andrew Heiss, Marc Dotson, and Suparna Chaudhry"
----
-
-See Chaudhry and Heiss (2019) preregistration for reference: <https://osf.io/dx973>
-
 ---
@@
 \begin{aligned}
-\beta &\sim \text{MVN}(Z \Gamma, \xi) \\
-y &\sim \text{MNL}(X \beta, \varepsilon)
+\beta &\sim \operatorname{Multivariate} \mathcal{N}(Z \Gamma, \xi) \\
+y &\sim \operatorname{Multinomial logit}(X \beta, \varepsilon)
 \end{aligned}
@@
 
-TODO: Do we do this?
-
-COMMENT: No, it's really just looking at/comparing the posterior marginals on their own vs. the posterior marginals with different covariates includes, plus the market simulation.
+NA.
 

### 2019-05-04 analysis/survey/preregistration.Rmd
Initial hypotheses

@@
 
-ANDREW TODO: write these
+For our first set of questions, we predict that: (TODO: finish these)
 
----
+- Donors will be more likely to donate to NGOs facing government criticism and crackdown
+- Donors will be more likely to donate to less contentious NGOs (i.e. those focused on emergency response and refugee relief)
+- Donors will be more likely to donate to NGOs that are privately funded and that many small private donations will have a larger effect than a handful of wealthy donors.
+- Donors will be more likely to donate to NGOs that engage in financial transparency
+- Donors will be more likely to donate to NGOs that engage in accountability
+
+Because of the nature of our statistical methods, we do not have exact hypotheses for the second and third set of questions.
+We describe how we answer these questions in the "Follow-up analyses" section below.
 

### 2019-05-04 analysis/survey/preregistration.Rmd
Refine wording for transparency and accountability

@@
 
-- *Financial transparency*: Timely and reliable disclosure regarding donations and financial allocations. 
-- *Accountability*: An obligation or willingness to accept responsibility or to account for one's actions.
+- *Financial transparency*: Organization discloses information regarding its donations and financial allocations in a timely and reliable manner.
+- *Accountability*: Organization undergoes a regular third-party audit to ensure that it is meeting its program goals and obligations.
 

### 2019-05-04 analysis/survey/preregistration.Rmd
Confirmatory stuff

@@
 
-NA.
+In our second set of research questions, we explore how individual-level donor characteristics interact with structural and organizational heuristics.
+We are interested in finding which kinds of people are more or less likely to consider an NGO's host country political environment, managerial practices, funding sources, or issue area when deciding to donate.
+
+There is substantial literature regarding individual factors that motivate people to donate to charities, and a full test of each of these factors goes beyond the scope of this research.
+In general, those who trust charities, are more involved in philanthropy, advocacy, and other voluntary associations, and are more religious tend to be more likely to donate to charity.
+In this study, however, we are less interested in the effects of single characteristics and more interested in how constellations of characteristics interact with specific heuristics.
+For instance, we suspect that politically conservative, religiously active donors who have a history of volunteering would be more likely to donate to a disaster relief organization facing government crackdown.
+
+Specifying every possible combination of individual- and organization-level attributes, however, would result in hundreds of hypotheses.
+The statistical method we are using lends itself to this kind of analysis.
+Rather than look at the effects of specific coefficients, we measure the difference in the marginal posterior distribution before and after including collections of covariates, which allows us to see which sets of individual characteristics shape the propensity to donate given organizational and structural heuristics.
+
+We will run the upper level of our model using these sets of covariates: (TODO)
+
+- Public affairs stuff: `donation preferences ~ public affairs knowledge + public affairs trust + public affairs activity`
+- Ideology: `donation preferences ~ political ideology + social ideology + (religiosity?)`
+- Charity and voluntarism: `donation preferences ~ charity trust + charity activity + volunteer activity + activism activity + association membership`
+- Demographics: `donation preferences ~ gender + marital status + education + income + race + age`
+- Kitchen sink model??: `donation preferences ~ EVERYTHING??`
+
+In our third research question, we are interested in finding the optimal mix of attribute levels for NGOs interested in maximizing donations.
+This is an exercise of prediction, based on the organizational- and individual-level results of our first two sets of research questions.
+We answer this question using marketing simulations and suggesting direct policies for specific segments of the population (hypothetical example: NGOs should signal that they engage in financial transparency when they face government criticism if they want to reach religious liberals with a history of activism).
+We do not know *a priori* what the results of these simulations might be, so we do not state precise hypotheses.
 

### 2019-05-04 analysis/experiment.Rmd
Add new questions

@@
 issues <- c("Emergency response", "Environment", "Human rights", "Refugee relief")
-orgal_practices <- c("Financial transparency", "Accountability")
+transparency <- c("Engages in transparency", "Doesn't engage in transparency")
+accountability <- c("Engages in accountability", "Doesn't engage in accountability")
 funding <- c("Many small private donations", "Handful of wealthy private donors", "Government grants")
@@
   "Issue area", sample(issues, 1), sample(issues, 1), sample(issues, 1), "—",
-  "Organizational practices", sample(orgal_practices, 1), sample(orgal_practices, 1), sample(orgal_practices, 1), "—",
+  "Transparency", sample(transparency, 1), sample(transparency, 1), sample(transparency, 1), "—",
+  "Accountability", sample(accountability, 1), sample(accountability, 1), sample(accountability, 1), "—",
   "Funding sources", sample(funding, 1), sample(funding, 1), sample(funding, 1), "—",

### 2019-05-05 analysis/survey/preregistration.Rmd
Initial foray into describing 2nd and 3rd set of "hypotheses"

@@
 Because of the nature of our statistical methods, we do not have exact hypotheses for the second and third set of questions.
-We describe how we answer these questions in the "Follow-up analyses" section below.
+We describe how we answer these questions in the "Follow-up analyses" and "Exploratory analysis" sections below.
 
@@
 
-TODO: Are there any others we should collapse?
-
-COMMENT: See comment for Indices.
-
 We collapse several of our variables into dichotomous and trichotomous versions, following this system:
@@
 
-We will run the upper level of our model using these sets of covariates: (TODO)
+We will run the upper level of our model using these sets of covariates:
 
-- Public affairs stuff: `donation preferences ~ public affairs knowledge + public affairs trust + public affairs activity`
-- Ideology: `donation preferences ~ political ideology + social ideology + (religiosity?)`
-- Charity and voluntarism: `donation preferences ~ charity trust + charity activity + volunteer activity + activism activity + association membership`
-- Demographics: `donation preferences ~ gender + marital status + education + income + race + age`
-- Kitchen sink model??: `donation preferences ~ EVERYTHING??`
+- Public affairs: `Donation preferences ~ Public affairs knowledge + Public affairs trust + Public affairs activity`
+- Ideology: `Dnation preferences ~ Political ideology + Social ideology + Religiosity`
+- Charity and voluntarism: `Donation preferences ~ Charity trust + Charity activity + Volunteer activity + Activism activity + Association membership`
+- Demographics: `Donation preferences ~ Gender + Marital status + Education + Income + Race + Age`
 
-In our third research question, we are interested in finding the optimal mix of attribute levels for NGOs interested in maximizing donations.
-This is an exercise of prediction, based on the organizational- and individual-level results of our first two sets of research questions.
-We answer this question using marketing simulations and suggesting direct policies for specific segments of the population (hypothetical example: NGOs should signal that they engage in financial transparency when they face government criticism if they want to reach religious liberals with a history of activism).
-We do not know *a priori* what the results of these simulations might be, so we do not state precise hypotheses.
+We will also include these groups of variables simultaneously as we check the performance of different models:
+
+- `Donation preferences ~ Public affairs + Ideology`
+- `Donation preferences ~ Public affairs + Ideology + Charity and voluntarism`
+- `Donation preferences ~ Public affairs + Ideology + Charity and voluntarism + Demographics`
 
@@
 
-NOTE: Here's a preregistration from another Bayesian hierarchical multinomial logit for reference: <https://osf.io/u43yg>
-
-COMMENT: Specify what the "competing sets of covariates" are that we'll include in the distribution of heterogeneity. This should be the motivation of the collapses specified in Transformations.
-
-We will examine the aggregate marginal posterior distributions of the attribute levels and utilize 95% credible intervals to establish "significance." Effects are "significant" if the 95% credible intervals don't include 0.
+We will examine the aggregate marginal posterior distributions of the attribute levels and use 95% credible intervals to establish "significance." Effects are "significant" if the 95% credible intervals don't include 0.
 Similarly, marginal posterior distributions are "significantly" different if the 95% credible intervals don't overlap.
@@
 
-NA.
+In our third research question, we are interested in finding the optimal mix of attribute levels for NGOs interested in maximizing donations.
+This is an exercise of prediction, based on the organizational- and individual-level results of our first two sets of research questions.
+We answer this question using marketing simulations and suggesting direct policies for specific segments of the population (hypothetical example: NGOs should signal that they engage in financial transparency when they face government criticism if they want to reach religious liberals with a history of activism).
+We do not know *a priori* what the results of these simulations might be, so we do not state precise hypotheses.
 

### 2019-05-06 R/experimental-design.R
Updated and checked levels balance for new design

@@ -1,0 +1,75 @@
+# Load libraries.
+library(AlgDesign)
+library(tidyverse)
+
+# Generate a full factorial design.
+full_design <- gen.factorial(
+  levels = c(16, 6, 7, 4, 2, 4, 5, 17),
+  nVars = 8,
+  center = FALSE,
+  varNames = c("brand", "year", "miles", "warranty", "seller", "mpg", "safety", "price")
+)
+
+ntask <- 12  # Number of choice tasks.
+nalts <- 4   # Number of alternatives (exclusing the outside option).
+nvers <- 500 # Number of versions of the design.
+
+# Create a fractional factorial design by sampling from the full factorial.
+frac_design <- matrix(double(ntask * nalts * nvers * (ncol(full_design) + 3)), ncol = (ncol(full_design) + 3))
+row_index <- c(1:nrow(full_design))
+ii <- 1
+for(i in 1:nvers) {
+  for(j in 1:ntask) {
+    ind <- sample(row_index, nalts)           # Sample nalts row indicators from row_index.
+    x_temp <- full_design[ind,]               # Create a temp design for this task.
+    x_temp <- cbind(c(1:nalts), x_temp)       # Append the alternative numbers.
+    frac_design[c(ii:(ii+(nalts-1))), 1] <- i # Append the version number.
+    frac_design[c(ii:(ii+(nalts-1))), 2] <- j # Append the task number.
+
+    # Save out the temp design and increment ii.
+    frac_design[c(ii:(ii+(nalts-1))), -c(1:2)] <- as.matrix(x_temp)
+    ii <- ii + nalts
+  }
+}
+colnames(frac_design) <- c("version", "task", "alt", colnames(full_design))
+
+# frac_design <- read_csv(here::here("data", "design.csv"))
+#
+# # Check to make sure there is a balance across levels.
+# as_tibble(frac_design) %>%
+#   select(Organization:`Relationship with host government`) %>%
+#   gather(key = atts, value = lvls) %>%
+#   ggplot(aes(x = lvls)) +
+#   geom_bar() +
+#   facet_wrap(~ atts, scales = "free", nrow = 2)
+#
+# ggsave("design_balance.png", width = 8, height = 4, units = "in")
+
+# Check to make sure there is a balance across levels.
+as_tibble(frac_design) %>%
+  select(brand:price) %>%
+  gather(key = atts, value = lvls) %>%
[…]

### 2019-05-10 analysis/preregistration.Rmd
Add BYU IRB

@@
 
-<p><a href="files/byu-irb-approval.pdf" class="btn btn-md btn-success disabled" target="_blank" role="button">
+<p><a href="files/byu-irb-approval.pdf" class="btn btn-md btn-success" target="_blank" role="button">
 <i class="fa fa-check-circle" aria-hidden="true"></i>&nbsp;

### 2019-05-13 analysis/survey/preregistration.Rmd
Flesh out hypotheses

@@
 
-We use a conjoint survey experiment to examine the impact of organizational and structural features of nongovernmental organizations (NGOs) on their donors’ decisions to engage in philanthropy.
+We use a conjoint survey experiment to examine the impact of organizational features of nongovernmental organizations (NGOs) and the structural factors in target countries in which they operate on donors’ decisions to engage in philanthropy.
 We explore three research questions in this study:
@@
 
-For our first set of questions, we predict that: (TODO: finish these)
+For our first set of questions, we predict that:
 
-- Donors will be more likely to donate to NGOs facing government criticism and crackdown
-- Donors will be more likely to donate to less contentious NGOs (i.e. those focused on emergency response and refugee relief)
-- Donors will be more likely to donate to NGOs that are privately funded and that many small private donations will have a larger effect than a handful of wealthy donors.
-- Donors will be more likely to donate to NGOs that engage in financial transparency
-- Donors will be more likely to donate to NGOs that engage in accountability
+1. **Branding**
+
+    - Donors will be more likely to donate to Oxfam and Red Cross compared to Amnesty International and Greenpeace [Mechanism: awareness of need and contentiousness of issue area]
+
+2. **Government crackdown**
+
+    - Donors will show increased willingness to donate to NGOs that are facing government crackdown or criticism [Mechanism: Governments wouldn't be cracking down on them if they didn't perceive a threat from them which means organizations implementing their missions effectively.
+This perception of efficacy leads to increased donations.]
+    - Donors will show increased willingness to donate to Oxfam and Red Cross when they are facing government crackdown or criticism compared to when Amnesty or Greenpeace is facing crackdown.
+
+3. **Issue area**
+
+    - Donors will show increased willingness to donate to NGOs working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights)
+    - Donors will show increased willingness to donate to NGOs facing government crackdown/criticism working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights) [Mechanisms: Perceptions of deservingness of NGOs dealing with emergency response and refugee relief.
+Donors are also more likely to donate to programs that are compatible with government preferences and have easily measurable outputs, which environment and human rights programs often lack.
+NGOs working on more contentious issue areas may be expelled or shut down, which would be a waste of donor resources, make it less likely that they donate to these groups.]
+
+4. **Funding sources**
+
+    - Donors will show increased willingness to donate to NGOs that are funded primarily by numerous small private donors compared to NGOs that are funded by a handful of wealhty private donors and government grants [Mechanism: Perception of efficacy - your contribution matters as a small donor.
+Government funding may also imply lack of independence of government which can reduce the efficiency of an organization.]
+    - Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors
+    - Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors and work in less contentious areas (emergency response and refugee relief)
+
+5. **Organizational practices**
+
+    - Donors will show increased willingness to donate to NGOs that are financially transparent [Mechanism: Perception of efficacy]
+    - Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent
+    - Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and are funded primarily by numerous small private donors
+    - Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief)
+    - Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief) and are funded by numerous small donors
+    - Donors should be no more or less likely to donate to NGOs that are accountable and hold regular third party audits [Mechanism: Donors don't necessarily seek assurance through third-party programs/audits and charity watchdogs, but rather through word of mouth, personal scrutiny and local networks]
 
@@
 
-- Public affairs: `Donation preferences ~ Public affairs knowledge + Public affairs trust + Public affairs activity`
-- Ideology: `Dnation preferences ~ Political ideology + Social ideology + Religiosity`
+- Public affairs: `Donation preferences ~ Public affairs knowledge + Public affairs activity`
+- Political ideology: `Donation preferences ~ Political ideology`
+- Social views: `Donation preferences ~ Public affairs trust + Social ideology + Religiosity`
 - Charity and voluntarism: `Donation preferences ~ Charity trust + Charity activity + Volunteer activity + Activism activity + Association membership`
@@
 
-- `Donation preferences ~ Public affairs + Ideology`
-- `Donation preferences ~ Public affairs + Ideology + Charity and voluntarism`
-- `Donation preferences ~ Public affairs + Ideology + Charity and voluntarism + Demographics`
+- `Donation preferences ~ (Public affairs) + (Political ideology)`
+- `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views)`
+- `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views) + (Charity and voluntarism)`
+- `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views) + (Charity and voluntarism) + (Demographics)`
 

### 2019-05-13 analysis/preregistration.Rmd
Cross out CNU and GSU for now
Make preregistration link live

@@
 
-<p><a href="https://osf.io/dx973/register/565fb3678c5e4a66b5582f67" class="btn btn-md btn-success disabled" target="_blank" role="button">
+<p><a href="https://osf.io/hsbyd" class="btn btn-md btn-success" target="_blank" role="button">
 <i class="fa fa-pencil-square" aria-hidden="true"></i>&nbsp;
-OSF preregistration protocol &raquo;
+OSF preregistered pre-analysis plan &raquo;
 </a></p>
@@
 
-This project has received IRB approval from the human subjects research committees at BYU, Georgia State, and Christopher Newport. We have included a generic version of our protocol below.
+This project has received IRB approval from the human subjects research committees at BYU, ~~Christopher Newport, and Georgia State~~. We have included a generic version of our protocol below.
 

### 2019-05-16 analysis/preregistration.Rmd
Add CNU IRB

@@
 
-This project has received IRB approval from the human subjects research committees at BYU, ~~Christopher Newport, and Georgia State~~. We have included a generic version of our protocol below.
+This project has received IRB approval from the human subjects research committees at BYU, Christopher Newport, ~~and Georgia State~~. We have included a generic version of our protocol below.
 
@@
 &nbsp;
-<a href="files/cnu-irb-approval.pdf" class="btn btn-md btn-success disabled" target="_blank">
+<a href="files/cnu-irb-approval.pdf" class="btn btn-md btn-success" target="_blank">
 <i class="fa fa-check-circle" aria-hidden="true" role="button"></i>&nbsp;
@@
 &nbsp;
-<a href="files/gsu-irb-approval.pdf" class="btn btn-info btn-md disabled" target="_blank" role="button">
+<a href="files/gsu-irb-approval.pdf" class="btn btn-success btn-md disabled" target="_blank" role="button">
 <i class="fa fa-check-circle" aria-hidden="true"></i>&nbsp;

### 2019-05-22 analysis/01_check-design.Rmd
Cleaned up experiment, added a check for the design and dummy coding and created Rmd for model runs

---
title: "Check experimental design"
author: "Andrew Heiss, Marc Dotson, and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
output: 
  html_document:
    code_folding: show
editor_options: 
  chunk_output_type: console
---

# Load the design and check level balance

```{r clean-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(donorheuristics)
library(here)

# Load design
design <- read_csv(here("data", "design.csv"))

# Check to make sure there is a balance across levels
as_tibble(design) %>%
  select(Organization:`Relationship with host government`) %>%
  gather(key = atts, value = lvls) %>%
  ggplot(aes(x = lvls)) +
  geom_bar() +
  facet_wrap(~ atts, scales = "free", nrow = 2)
```

# Dummy-code the design

```{r}
# Convert the attributes in design into factors
dummy_design <- as.data.frame(design)
for(i in 4:ncol(dummy_design)) {
  dummy_design[,i] <- as.factor(dummy_design[,i])
}

# Use the output of lm to get a dummy-coded version of the design
dummy_design$y <- matrix(rnorm(nrow(dummy_design)), ncol=1)
out <- lm(y ~ ., dummy_design, x = TRUE)
dummy_design <- out$x[,-1]
rownames(dummy_design) <- NULL

# Save dummy-coded design output
write.csv(dummy_design, here("data", "dummy_design.csv"))
```

# Original computing environment

<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>

<div id="sessioninfo" class="collapse">

```{r show-session-info, echo=TRUE, width=90}
writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))

devtools::session_info()
```

</div>

### 2019-05-22 analysis/03_run-models.Rmd
Cleaned up experiment, added a check for the design and dummy coding and created Rmd for model runs

---
title: "Run models"
author: "Andrew Heiss, Marc Dotson, and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
    pandoc_args:
      - "--default-image-extension=png"
editor_options: 
  chunk_output_type: console
---

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(donorheuristics)
library(ggraph)
library(ggdag)
library(here)

# General settings
source(here("analysis", "options.R"))

# Make all the randomness reproducible
set.seed(1234)
```

# Run models

### 2019-05-22 R/experimental-design.R

@@ -1,75 +1,0 @@
-# Load libraries.
-library(AlgDesign)
-library(tidyverse)
-
-# Generate a full factorial design.
-full_design <- gen.factorial(
-  levels = c(16, 6, 7, 4, 2, 4, 5, 17),
-  nVars = 8,
-  center = FALSE,
-  varNames = c("brand", "year", "miles", "warranty", "seller", "mpg", "safety", "price")
-)
-
-ntask <- 12  # Number of choice tasks.
-nalts <- 4   # Number of alternatives (exclusing the outside option).
-nvers <- 500 # Number of versions of the design.
-
-# Create a fractional factorial design by sampling from the full factorial.
-frac_design <- matrix(double(ntask * nalts * nvers * (ncol(full_design) + 3)), ncol = (ncol(full_design) + 3))
-row_index <- c(1:nrow(full_design))
-ii <- 1
-for(i in 1:nvers) {
-  for(j in 1:ntask) {
-    ind <- sample(row_index, nalts)           # Sample nalts row indicators from row_index.
-    x_temp <- full_design[ind,]               # Create a temp design for this task.
-    x_temp <- cbind(c(1:nalts), x_temp)       # Append the alternative numbers.
-    frac_design[c(ii:(ii+(nalts-1))), 1] <- i # Append the version number.
-    frac_design[c(ii:(ii+(nalts-1))), 2] <- j # Append the task number.
-
-    # Save out the temp design and increment ii.
-    frac_design[c(ii:(ii+(nalts-1))), -c(1:2)] <- as.matrix(x_temp)
-    ii <- ii + nalts
-  }
-}
-colnames(frac_design) <- c("version", "task", "alt", colnames(full_design))
-
-# frac_design <- read_csv(here::here("data", "design.csv"))
-#
-# # Check to make sure there is a balance across levels.
-# as_tibble(frac_design) %>%
-#   select(Organization:`Relationship with host government`) %>%
-#   gather(key = atts, value = lvls) %>%
-#   ggplot(aes(x = lvls)) +
-#   geom_bar() +
-#   facet_wrap(~ atts, scales = "free", nrow = 2)
-#
-# ggsave("design_balance.png", width = 8, height = 4, units = "in")
-
-# Check to make sure there is a balance across levels.
-as_tibble(frac_design) %>%
-  select(brand:price) %>%
-  gather(key = atts, value = lvls) %>%
[…]

### 2019-05-22 analysis/01_check-design.Rmd
Changed language of 7-point scales from left to right to 1 to 7 (since its vertical on mobile)

@@
 
-```{r clean-data, warning=FALSE, message=FALSE}
+```{r check-design, warning=FALSE, message=FALSE}
 library(tidyverse)
@@
 
-```{r}
+```{r check-design, warning=FALSE, message=FALSE}
 # Convert the attributes in design into factors

### 2019-05-25 analysis/02_clean-data.Rmd

---
title: "Clean data"
author: "Andrew Heiss, Marc Dotson, and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
output: 
  html_document:
    code_folding: show
editor_options: 
  chunk_output_type: console
---

# Load and clean data

```{r clean-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(donorheuristics)
library(here)

# Load data
# results_raw <- read_csv(here("data", "raw_data", "whatever.csv"))

# Do stuff to results_raw
# results <- results_raw %>% 
#   do() %>% stuff() %>% here()

# Save cleaned data
# saveRDS(results, here("data", "derived_data", "results.rds"))
# write_csv(results, here("data", "derived_data", "results.csv"))
```

# Original computing environment

<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>

<div id="sessioninfo" class="collapse">

```{r show-session-info, echo=TRUE, width=90}
writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))

devtools::session_info()
```

</div>

### 2019-05-25 analysis/04_analysis.Rmd

--- 2019-04-09 analysis/02_analysis.Rmd
@@
 Our theory and hypotheses are laid out in the causal pathway below.
-Our outcomes (Y: % likely to donate and amount donated) "listen to" or respond to C (crackdown), which is our main treatment or exposure.
-Funding (F) and issue (I) serve as heuristics for donation and influence a government's decision to crack down on NGOs, hence the dual arrows to C and Y.
+Organizational factors (**O**, or organizational practices like financial disclosure and accountability practices; **I**, or issue area; and **F**, or funding) all influence the decision to donate (**D**).
+Structural factors like an NGO's relationship with its host government (**G**) also influence donation behavior, but the relationship itself is shaped by both funding and issue area.
 

### 2019-06-19 analysis/check-data.R
Checking the data

@@ -1,0 +1,85 @@
+# Load packages
+library(tidyverse)
+
+# Load data
+col_names <- names(read_csv(here::here("data", "conjointqsf_final.csv")))
+data <- read_csv(
+  here::here("data", "conjointqsf_final.csv"),
+  skip = 2,
+  col_names = col_names
+)
+
+# Who finished?
+data %>%
+  summarize(
+    n = n(),
+    count = sum(V10)
+  )
+
+# 1437 completes
+
+# Check Q1.1
+data %>%
+  count(Q1.1)
+
+data %>%
+  count(Q1.1, Q2.1)
+
+# 30 didn't give consent
+
+# Check Q2.5
+data %>%
+  count(Q2.5)
+
+data %>%
+  count(Q2.5, Q2.6)
+
+# 15 were disqualified
+
+# Check Q2.9 and Q2.10
+data %>%
+  count(Q2.9)
+
+data %>%
+  count(Q2.9, Q2.10)
+
+# Check Q2.11
+data %>%
+  count(Q2.11)
+
+# Everyone made the attention check
+
+# Check Q5.17
+data %>%
+  count(Q5.17)
+
+# No one under 18
+
+# Check the assigned design
+data %>%
+  count(vers_CBCONJOINT) %>%
+  arrange(desc(n))
+
+# Everyone assigned to a difference version
+
+# Check the choice data
+data %>%
+  count(Q4.1)
+
+data %>%
+  select(Q4.1:Q4.12) %>%
+  gather(key = "task", value = "choice") %>%
+  count(choice)
+
+20 * 12
+
+# Unqualified respondents don't see the conjoint
+
+# # Check to make sure there is a balance across levels
+# as_tibble(design) %>%
+#   select(Organization:`Relationship with host government`) %>%
+#   gather(key = atts, value = lvls) %>%
+#   ggplot(aes(x = lvls)) +
+#   geom_bar() +
+#   facet_wrap(~ atts, scales = "free", nrow = 2)
+

### 2019-06-19 src/hier_mnl.R
Added samplers in both R and Stan

@@ -1,0 +1,195 @@
+hier_mnl = function (Data, Prior, Mcmc, Cont) {
+  # This function implements an MCMC estimation algorithm for a hierarchical MNL with a multivariate 
+  # normal distribution of heterogeneity.
+  
+  # Describe and Assign Function Arguments ----------------------------------
+  # Data = list(y,X,Z,Beta,Gamma).
+  y = Data$y                                              # List of choices.
+  X = Data$X                                              # List of design matrices.
+  Z = Data$Z                                              # Covariates for the upper-level model.
+  if (Mcmc$sim_ind==1) {
+    Beta = Data$Beta                                      # True values of Beta for parameter recovery.
+    # Gamma = Data$Gamma                                    # True values of Gamma for parameter recovery.
+    # Vbeta = Data$Vbeta                                    # True values of Vbeta for parameter recovery.
+  }
+  
+  # Prior = list(gammabar,Agamma,nu,V).
+  gammabar = Prior$gammabar                               # Means for normal prior on Gamma.
+  Agamma = Prior$Agamma                                   # Precision matrix for normal prior on Gamma.
+  nu = Prior$nu                                           # DF for IW prior on Vbeta.
+  V = Prior$V                                             # Location for IW prior on Vbeta.
+  
+  # Mcmc = list(R,keep,step,sim_ind,cont_ind).
+  R = Mcmc$R                                              # Number of iterations in the Markov chain.
+  keep = Mcmc$keep                                        # Thinning parameter.
+  step = Mcmc$step                                        # RW step (scaling factor) for the beta draws.
+  sim_ind = Mcmc$sim_ind                                  # Indicates a simulation experiment.
+  cont_ind = Mcmc$cont_ind                                # Indicates a run continuation.
+  
+  # Choice variables.
+  nresp = length(y)                                       # Number of respondents.
+  nvars = ncol(X[[1]])                                    # Number of attribute levels.
[…]

### 2019-06-19 analysis/02_clean-data.Rmd
Checking and cleaning data

@@
 
-# Load and clean data
+# Check data
+
+## Load data
 
@@
 
-# Load data
-# results_raw <- read_csv(here("data", "raw_data", "whatever.csv"))
+col_names <- names(read_csv(here::here("data", "conjointqsf_final.csv")))
+data <- read_csv(
+  here::here("data", "conjointqsf_final.csv"),
+  skip = 2,
+  col_names = col_names
+)
+```
 
-# Do stuff to results_raw
-# results <- results_raw %>% 
-#   do() %>% stuff() %>% here()
+## Respondents who finished
 
-# Save cleaned data
-# saveRDS(results, here("data", "derived_data", "results.rds"))
-# write_csv(results, here("data", "derived_data", "results.csv"))
+```{r clean-data, warning=FALSE, message=FALSE}
+data %>%
+  summarize(
+    total = n(),
+    finished = sum(V10)
+  )
 ```
+
+Out of 1508 respondents, 1437 "finished" the survey and 71 didn't.
+
+## Consent
+
+```{r clean-data, warning=FALSE, message=FALSE}
+data %>%
+  count(Q1.1)
+
+data %>%
+  count(Q1.1, Q2.1)
+```
+
+30 respondents didn't give consent while 3 respondents gave consent and didn't respond starting in Q2.1.
+
+## Screening
+
+```{r clean-data, warning=FALSE, message=FALSE}
+data %>%
+  count(Q2.5)
+
+data %>%
+  count(Q2.5, Q2.6) %>% 
+  filter(is.na(Q2.6) == TRUE)
+```
+
+An additional 12 respondents drop out by Q2.5 (a total of 45). 385 respondents are screened at Q2.5. 2 more respondents drop off by Q2.6 (a total of 47).
+
+## Check display logic
+
+```{r clean-data, warning=FALSE, message=FALSE}
+data %>%
+  count(Q2.9)
+
+data %>%
+  count(Q2.9, Q2.10)
+```
+
+8 more respondents have dropped out (a total of 55). The 445 people who don't volunteer in the past 12 months properly skip Q2.10.
+
+## Attention check
+
+```{r clean-data, warning=FALSE, message=FALSE}
+data %>%
+  count(Q2.11)
+```
+
+6 respondents don't make the attention check.
+
+## Confirm ages
+
+```{r clean-data, warning=FALSE, message=FALSE}
+data %>%
+  count(Q5.17)
+```
+
+By the end of the survey, 44 more respondents have dropped out (a total of 99) but no one is under 18, as they indicated as part of the consent.
+
+# Clean data
+
+## Clean based on initial criteria
+
+```{r clean-data, warning=FALSE, message=FALSE}
+data_clean <- data %>%
+  filter(V10 == 1) %>%         # Keep respondents who completed the entire survey
+  filter(Q1.1 == 1) %>%        # Keep respondents who gave consent
+  filter(Q2.5 %in% c(1:5)) %>% # Keep respondents who passed the screener
+  filter(Q2.11 == 3)           # Keep respondents who passed the attention check
+```
+
+## Confirm the data is clean
+
+```{r clean-data, warning=FALSE, message=FALSE}
+# Finished respondents
+data_clean %>% 
+  summarize(
+    total = n(),
+    finished = sum(V10)
+  )
+
+# Consent
+data_clean %>%
+  count(Q1.1)
+
+# Screening
+data_clean %>%
+  count(Q2.5)
+
+# Attention check
+data_clean %>% 
+  count(Q2.11)
+```
+
+We have 1016 total respondents who have finished the entire survey, given consent, and passed the screening and attention check.
+
+## Confirm the choice data is clean
+
+```{r clean-data, warning=FALSE, message=FALSE}
+data_clean %>%
+  count(vers_CBCONJOINT) %>%
+  count(n)
+```
+
+The design version appears to be properly assigned at random.
+
+```{r clean-data, warning=FALSE, message=FALSE}
+data_clean %>%
+  select(Q4.1:Q4.12) %>%
+  gather(key = "task", value = "choice") %>%
+  count(choice)
+```
+
+Everyone in the clean data responds to every choice task and the "none of the above" option doesn't appear to be abused.
+
+```{r clean-data, warning=FALSE, message=FALSE}
+levels_check <- data_clean %>% 
+  select(contains("CBCONJOINT"), -revision_CBCONJOINT) %>% 
+  gather(key = "temp", value = "level_name", -vers_CBCONJOINT) %>% 
+  separate(temp, into = c("atts", "task", "alt"), sep = "\\.") %>% 
+  separate(alt, into = c("alt", "temp")) %>% 
+  select(vers_CBCONJOINT, task, alt, atts, level_name) %>% 
+  rename(version = vers_CBCONJOINT) %>% 
+  mutate(
+    task = as.numeric(task),
+    alt = as.numeric(task),
+    atts = recode(
+      atts,
+      "732d72a6-25a3-4194-8416-461acae30837" = "Organization",
+      "bd54b90a-efb3-4ac8-b65a-1ebeefcaf703" = "Issue area",
+      "a6836e28-fd7a-4b71-b65e-f6269e5c883f" = "Financial transparency",
+      "c2249c1a-11fa-4395-a0a3-61d9648a2e55" = "Accountability",
+      "db44c406-390e-4fc4-875b-65796aa95ffa" = "Funding sources",
+      "85f14c50-61cc-461c-8e77-19453b83d76d" = "Relationship with host government"
+    )
+  ) %>% 
+  left_join(
+    read_csv(here("data", "design.csv")) %>% 
+      rename(
+        version = question_set,
+        task = question,
+        alt = choice
+      ) %>% 
+      gather(key = "atts", value = "levels", -c(version:alt)),
+    by = c("version", "task", "alt", "atts")
+  )
+
+levels_check %>% 
+  count(atts)
+
+levels_check %>% 
+  count(levels, level_name) %>% 
+  arrange(desc(n))
+```
+
+Why are there NAs?
+
+<!-- select(-c("732d72a6-25a3-4194-8416-461acae30837.1.1_CBCONJOINT":"revision_CBCONJOINT")) -->
+<!-- design <- read_csv( -->
+<!--   here::here("data", "conjointqsf_final.csv"), -->
+<!--   skip = 2, -->
+<!--   col_names = col_names -->
+<!-- ) %>%  -->
+<!--   select(contains("CBCONJOINT")) -->
 

### 2019-06-19 analysis/check-data.R

@@ -1,85 +1,0 @@
-# Load packages
-library(tidyverse)
-
-# Load data
-col_names <- names(read_csv(here::here("data", "conjointqsf_final.csv")))
-data <- read_csv(
-  here::here("data", "conjointqsf_final.csv"),
-  skip = 2,
-  col_names = col_names
-)
-
-# Who finished?
-data %>%
-  summarize(
-    n = n(),
-    count = sum(V10)
-  )
-
-# 1437 completes
-
-# Check Q1.1
-data %>%
-  count(Q1.1)
-
-data %>%
-  count(Q1.1, Q2.1)
-
-# 30 didn't give consent
-
-# Check Q2.5
-data %>%
-  count(Q2.5)
-
-data %>%
-  count(Q2.5, Q2.6)
-
-# 15 were disqualified
-
-# Check Q2.9 and Q2.10
-data %>%
-  count(Q2.9)
-
-data %>%
-  count(Q2.9, Q2.10)
-
-# Check Q2.11
-data %>%
-  count(Q2.11)
-
-# Everyone made the attention check
-
-# Check Q5.17
-data %>%
-  count(Q5.17)
-
-# No one under 18
-
-# Check the assigned design
-data %>%
-  count(vers_CBCONJOINT) %>%
-  arrange(desc(n))
-
-# Everyone assigned to a difference version
-
-# Check the choice data
-data %>%
-  count(Q4.1)
-
-data %>%
-  select(Q4.1:Q4.12) %>%
-  gather(key = "task", value = "choice") %>%
-  count(choice)
-
-20 * 12
-
-# Unqualified respondents don't see the conjoint
-
-# # Check to make sure there is a balance across levels
-# as_tibble(design) %>%
-#   select(Organization:`Relationship with host government`) %>%
-#   gather(key = atts, value = lvls) %>%
-#   ggplot(aes(x = lvls)) +
-#   geom_bar() +
-#   facet_wrap(~ atts, scales = "free", nrow = 2)
-

### 2019-06-20 analysis/02_clean-data.Rmd
Finished checking and cleaning data, exporting the cleaned final data

@@
 ```{r clean-data, warning=FALSE, message=FALSE}
-levels_check <- data_clean %>% 
+design_orig <- read_csv(here("data", "design.csv")) %>% 
+  rename(
+    version = question_set,
+    task = question,
+    alt = choice
+  ) %>% 
+  gather(key = "atts", value = "levels", -c(version:alt))
+
+design_surv <- data_clean %>% 
   select(contains("CBCONJOINT"), -revision_CBCONJOINT) %>% 
-  gather(key = "temp", value = "level_name", -vers_CBCONJOINT) %>% 
+  gather(key = "temp", value = "level_names", -vers_CBCONJOINT) %>% 
   separate(temp, into = c("atts", "task", "alt"), sep = "\\.") %>% 
   separate(alt, into = c("alt", "temp")) %>% 
-  select(vers_CBCONJOINT, task, alt, atts, level_name) %>% 
+  select(vers_CBCONJOINT, task, alt, atts, level_names) %>% 
   rename(version = vers_CBCONJOINT) %>% 
@@
     task = as.numeric(task),
-    alt = as.numeric(task),
+    alt = as.numeric(alt),
     atts = recode(
@@
   ) %>%
+  distinct() %>% 
+  arrange(version, task, alt)
+
+design_orig %>% 
+  count(atts, levels) %>% 
+  mutate(prop = n/sum(n))
+
+design_surv %>% 
+  count(atts, level_names) %>% 
+  mutate(prop = n/sum(n))
+
+design_surv %>% 
   left_join(
-    read_csv(here("data", "design.csv")) %>% 
-      rename(
-        version = question_set,
-        task = question,
-        alt = choice
+    design_orig,
+    by = c("version", "task", "alt", "atts")
   ) %>% 
-      gather(key = "atts", value = "levels", -c(version:alt)),
-    by = c("version", "task", "alt", "atts")
-  )
-
-levels_check %>% 
-  count(atts)
-
-levels_check %>% 
-  count(levels, level_name) %>% 
-  arrange(desc(n))
+  count(atts, levels, level_names)
 ```
 
-Why are there NAs?
+The design matrix as reported in the survey is correct. We can use the separate design file matched by design version for estimation.
+
+## Save clean data
+
+```{r clean-data, warning=FALSE, message=FALSE}
+data <- data_clean
+
+write_csv(data, here("data", "final_data.csv"))
+```
 

### 2019-06-20 analysis/preregistration.Rmd
Add GSU IRB

@@
 
-This project has received IRB approval from the human subjects research committees at BYU, Christopher Newport, ~~and Georgia State~~. We have included a generic version of our protocol below.
+This project has received IRB approval from the human subjects research committees at BYU, Christopher Newport, and Georgia State. We have included a generic version of our protocol below.
 
@@
 &nbsp;
-<a href="files/cnu-irb-approval.pdf" class="btn btn-md btn-success" target="_blank">
-<i class="fa fa-check-circle" aria-hidden="true" role="button"></i>&nbsp;
+<a href="files/cnu-irb-approval.pdf" class="btn btn-md btn-success" target="_blank" role="button">
+<i class="fa fa-check-circle" aria-hidden="true"></i>&nbsp;
 Christopher Newport IRB approval
@@
 &nbsp;
-<a href="files/gsu-irb-approval.pdf" class="btn btn-success btn-md disabled" target="_blank" role="button">
+<a href="files/gsu-irb-approval.pdf" class="btn btn-success btn-md" target="_blank" role="button">
 <i class="fa fa-check-circle" aria-hidden="true"></i>&nbsp;

### 2019-06-20 manuscript/manuscript.Rmd
Rmd-ize the manuscript

---
title: "Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy"
author:
- name: Suparna Chaudhry
  affiliation: Christopher Newport University
  url: http://www.suparnachaudhry.com/
  email: suparna.chaudhry@cnu.edu
- name: Marc Dotson
  affiliation: Brigham Young University
  email: marc_dotson@byu.edu
- name: Andrew Heiss
  affiliation: Brigham Young University
  url: https://www.andrewheiss.com/
  email: andrew_heiss@byu.edu
date: March 24, 2019
git-repo: https://github.com/andrewheiss/why-donors-donate
reference-section-title: References
toc: false
---

# Brief note on our overarching project

We are interested in the organizational and structural factors that influence donors to contribute money to international nongovernmental organizations (INGOs) and other nonprofit organizations. Existing research has found that donors respond to a host of heuristics and signals when deciding whether to donate to an NGO, since seeking out complete information about an organization's deservingness and efficiency is costly and time-consuming.

One common signal for donors is organizational efficiency, such as the amount an organization spends on overhead costs, whether an organization makes its finances public, or whether an organization participates in voluntary accountability practices, such as listing organizational details on websites like GuideStar and Charity Navigator. Another heuristic for deservingness is the issue area an NGO engages in. Organizations that address humanitarian issues such as disaster relief and international aid and development have broader appeal to donors who might shy away from NGOs dealing with more political causes like human rights. Finally, the source of NGO funding can also serve as a helpful signal of how effective and useful an individual donor's action might be. Donors are likely to not contribute to NGOs that rely heavily on government grants since their donation might feel more impersonal and less needed, while donors are likely to give to organizations that rely primarily on private donations given that they may feel personally invested in the organization. Each of these signals is *organizational*. NGOs typically have direct control over its organizational practices, mission and issue area, and funding sources.

NGOs have less control over *structural* issues, and the role of political and legal institutions in donor decision making has been understudied. However, over the past decade international NGOs have become increasingly politicized and legally restricted around the world. Dozens of countries have imposed legal restrictions on international NGO funding, missions, and programs, and in many countries, NGOs have been forced to close down operations and leave. How do individual donors respond when NGOs are kicked out of their host countries? How does legal crackdown abroad affect perceptions of an NGO's deservingness or efficiency?

In our larger project (which has unfortunately faced some substantial delays), we will use a conjoint survey experiment to disentangle these different questions. We theorize that organizational characteristics like managerial practices, issue area, and funding sources all influence the decision to donate to an NGO (see @fig:big-dag). At the same time, however, we propose that structural characteristics like an NGO's host-country political and legal environment can also serve as donor heuristics. Donors who see that an NGO has been kicked out of a country or that an NGO faces general legal trouble abroad will use that knowledge to decide whether or not to donate.

![Causal diagram showing causes of donor behavior. D = donation to NGO (outcome); G = NGO-government relationship, I = NGO issue area, F = NGO funding source, O = NGO organizational and managerial practices.](output/figures/causal-path-full.pdf){#fig:big-dag}

Identifying the causal link between structural factors and donor behavior is trickier than measuring the link between organizational factors and donor behavior, however, because (1) NGOs have less direct control over their political environments, and (2) organizational characteristics like issue area and funding can both sour the NGO-government relationship (as we explain in further detail below, governments are more likely to crack down on NGOs that address human rights and that receive government funding). @fig:big-dag helps disentangle this complex relationship. Organizational factors (**O**, or organizational practices like financial disclosure and accountability practices; **I**, or issue area; and **F**, or funding) all influence the decision to donate (**D**). Structural factors like an NGO's relationship with its host government (**G**) also influence donation behavior, but the relationship itself is shaped by both funding and issue area.

Through our conjoint survey experiment, we will be able to measure how strongly each of these factors shapes the propensity to donate and discover how much donors are swayed by the political and legal environments of NGO host countries.

What follows here is a smaller foray into one aspect of this causal diagram. We use a vignette-based survey experiment to measure donor response to just crackdown, issue area, and funding.

We will field our larger conjoint survey experiment very soon and we look forward to your comments and suggestions before we launch it!

### 2019-06-21 analysis/01_check-design.Rmd
Create data subfolders, update import/export code

@@
 # Load design
-design <- read_csv(here("data", "design.csv"))
+design <- read_csv(here("data", "derived_data", "design.csv"))
 
@@
 # Save dummy-coded design output
-write.csv(dummy_design, here("data", "dummy_design.csv"))
+write.csv(dummy_design, here("data", "derived_data", "dummy_design.csv"))
 ```

### 2019-06-21 analysis/02_clean-data.Rmd
Removed duplicate design information from final data
Create data subfolders, update import/export code

@@
 
-col_names <- names(read_csv(here::here("data", "conjointqsf_final.csv")))
+col_names <- names(read_csv(here::here("data", "raw_data", "conjointqsf_final.csv")))
 data <- read_csv(
@@
 ```{r clean-data, warning=FALSE, message=FALSE}
-design_orig <- read_csv(here("data", "design.csv")) %>% 
+design_orig <- read_csv(here("data", "derived_data", "design.csv")) %>% 
   rename(
@@
 ```{r clean-data, warning=FALSE, message=FALSE}
-data <- data_clean
+data <- data_clean %>% 
+  select(-c("732d72a6-25a3-4194-8416-461acae30837.1.1_CBCONJOINT":"revision_CBCONJOINT"))
 
-write_csv(data, here("data", "final_data.csv"))
+write_csv(data, here("data", "derived_data", "final_data.csv"))
 ```

### 2019-06-21 analysis/model-calibration.R

@@ -1,0 +1,271 @@
+# Import and Restructure Data ---------------------------------------------
+# Load packages.
+library(tidyverse)
+library(rstan)
+# library(mvtnorm)
+# library(bayesm)
+
+# Load data and design.
+final_data <- read_csv(here::here("data", "218329_Final_Excel_050619.csv"))
+survey_design <- read_csv(here::here("Data", "survey_design.csv")) %>% select(-X1)
+dummy_design <- read_csv(here::here("Data", "dummy_design.csv")) %>% select(-X1)
+
+intercept <- 0 # Intercept-only.
+geo_locat <- 1 # Geolocation covariates.
+demo_vars <- 0 # Demographic covariates.
+geo_demos <- 0 # Geolocation and demographic covariates.
+bnd_demos <- 0 # Brand covariates.
+all_three <- 0 # Geolocation, demographic, and brand covariates.
+
+# Restructure choice data Y.
+Y <- final_data %>%
+  select(record, contains("Q3")) %>%
+  select(-c(record, Q3_Version)) %>%
+  as.matrix()
+
+# Recode price in the design X.
+price_scale <- 10000
+design <- dummy_design %>%
+  select(-contains("price")) %>%
+  left_join(
+    survey_design %>%
+      select(version, task, alt, price)
+  ) %>%
+  mutate(
+    price = recode(
+      price,
+      `1` = 20000/price_scale,
+      `2` = 25000/price_scale,
+      `3` = 30000/price_scale,
+      `4` = 35000/price_scale,
+      `5` = 40000/price_scale,
+      `6` = 45000/price_scale,
+      `7` = 50000/price_scale,
+      `8` = 55000/price_scale,
+      `9` = 60000/price_scale,
+      `10` = 65000/price_scale,
+      `11` = 70000/price_scale,
+      `12` = 75000/price_scale,
+      `13` = 80000/price_scale,
+      `14` = 85000/price_scale,
+      `15` = 90000/price_scale,
+      `16` = 95000/price_scale,
+      `17` = 100000/price_scale
+    )
+  )
+
+# Restructure the design X.
+X <- array(
+  data = NA,
+  dim = c(
+    nrow(Y),                # Number of respondents.
[…]

### 2019-06-21 analysis/model-checking.R

@@ -1,0 +1,538 @@
+# Load Packages -----------------------------------------------------------
+library(tidyverse)
+library(bayesplot)
+library(tidybayes)
+library(bayesm)
+library(ggridges)
+
+# General MCMC ------------------------------------------------------------
+intercept <- 0 # Intercept-only.
+geo_locat <- 0 # Geolocation covariates.
+demo_vars <- 0 # Demographic covariates.
+geo_demos <- 0 # Geolocation and demographic covariates.
+bnd_demos <- 0 # Brand covariates.
+all_three <- 1 # Geolocation, demographic, and brand covariates.
+
+# Load model output.
+if (intercept == 1) run <- read_rds(here::here("Output", "hmnl_intercept-100k_ho.RDS"))
+if (geo_locat == 1) run <- read_rds(here::here("Output", "hmnl_more-geo-locat-100k_ho.RDS"))
+if (demo_vars == 1) run <- read_rds(here::here("Output", "hmnl_demo-vars-100k_ho.RDS"))
+if (geo_demos == 1) run <- read_rds(here::here("Output", "hmnl_more-geo-demos-100k_ho.RDS"))
+if (bnd_demos == 1) run <- read_rds(here::here("Output", "hmnl_bnd-demos-100k_ho.RDS"))
+if (all_three == 1) run <- read_rds(here::here("Output", "hmnl_all-three-100k_ho.RDS"))
+
+# Extract Data, Prior, Mcmc, and fit objects.
+Data <- run$Data
+Prior <- run$Prior
+Mcmc <- run$Mcmc
+fit <- run$fit
+
+# Check trace plots.
+fit$llikedraw %>% 
+  matrix(dimnames = list(NULL, "llike")) %>% 
+  mcmc_trace(
+    n_warmup = 500
+  )
+
+# colnames(fit$Gammadraw) <- str_c("Gamma[", c(1:ncol(fit$Gammadraw)), ",1]")
+# fit$Gammadraw %>%
+#   mcmc_trace(
+#     n_warmup = 500,
+#     facet_args = list(nrow = 5, labeller = label_parsed)
+#   )
+# 
+# ggsave(
+#   "mcmc_trace_conjugate.png",
+#   path = here::here("Figures"),
+#   width = 12, height = 6, units = "in"
+# )
+
+# Import model fit table.
+# model_fit_table <- matrix(NA, nrow = 6, ncol = 6) %>%
+#   as_tibble() %>%
+#   rename(
[…]

### 2019-06-21 analysis/model-calibration.R
Model calibration set-up

@@ -2,59 +2,28 @@
 # Load packages.
 library(tidyverse)
 library(rstan)
-# library(mvtnorm)
-# library(bayesm)
+library(mvtnorm)
+library(bayesm)
 
 # Load data and design.
-final_data <- read_csv(here::here("data", "218329_Final_Excel_050619.csv"))
-survey_design <- read_csv(here::here("Data", "survey_design.csv")) %>% select(-X1)
-dummy_design <- read_csv(here::here("Data", "dummy_design.csv")) %>% select(-X1)
+final_data <- read_csv(here::here("data", "derived_data", "final_data.csv"))
+design <- read_csv(here::here("data", "derived_data", "dummy_design.csv")) %>%
+  select(-X1) %>%
+  rename(
+    version = question_set,
+    task = question,
+    alt = choice
+  )
 
-intercept <- 0 # Intercept-only.
-geo_locat <- 1 # Geolocation covariates.
-demo_vars <- 0 # Demographic covariates.
-geo_demos <- 0 # Geolocation and demographic covariates.
-bnd_demos <- 0 # Brand covariates.
-all_three <- 0 # Geolocation, demographic, and brand covariates.
+# Specify the model to load.
+intercept <- 1 # Intercept-only.
 
 # Restructure choice data Y.
 Y <- final_data %>%
-  select(record, contains("Q3")) %>%
-  select(-c(record, Q3_Version)) %>%
+  select(contains("Q4")) %>%
   as.matrix()
 
-# Recode price in the design X.
-price_scale <- 10000
-design <- dummy_design %>%
-  select(-contains("price")) %>%
-  left_join(
-    survey_design %>%
-      select(version, task, alt, price)
-  ) %>%
-  mutate(
-    price = recode(
-      price,
-      `1` = 20000/price_scale,
-      `2` = 25000/price_scale,
-      `3` = 30000/price_scale,
-      `4` = 35000/price_scale,
-      `5` = 40000/price_scale,
-      `6` = 45000/price_scale,
-      `7` = 50000/price_scale,
-      `8` = 55000/price_scale,
-      `9` = 60000/price_scale,
-      `10` = 65000/price_scale,
-      `11` = 70000/price_scale,
-      `12` = 75000/price_scale,
-      `13` = 80000/price_scale,
[…]

### 2019-06-22 analysis/model-checking.R
Finished an initial run using the noncentered parameterization

@@ -1,538 +1,0 @@
-# Load Packages -----------------------------------------------------------
-library(tidyverse)
-library(bayesplot)
-library(tidybayes)
-library(bayesm)
-library(ggridges)
-
-# General MCMC ------------------------------------------------------------
-intercept <- 0 # Intercept-only.
-geo_locat <- 0 # Geolocation covariates.
-demo_vars <- 0 # Demographic covariates.
-geo_demos <- 0 # Geolocation and demographic covariates.
-bnd_demos <- 0 # Brand covariates.
-all_three <- 1 # Geolocation, demographic, and brand covariates.
-
-# Load model output.
-if (intercept == 1) run <- read_rds(here::here("Output", "hmnl_intercept-100k_ho.RDS"))
-if (geo_locat == 1) run <- read_rds(here::here("Output", "hmnl_more-geo-locat-100k_ho.RDS"))
-if (demo_vars == 1) run <- read_rds(here::here("Output", "hmnl_demo-vars-100k_ho.RDS"))
-if (geo_demos == 1) run <- read_rds(here::here("Output", "hmnl_more-geo-demos-100k_ho.RDS"))
-if (bnd_demos == 1) run <- read_rds(here::here("Output", "hmnl_bnd-demos-100k_ho.RDS"))
-if (all_three == 1) run <- read_rds(here::here("Output", "hmnl_all-three-100k_ho.RDS"))
-
-# Extract Data, Prior, Mcmc, and fit objects.
-Data <- run$Data
-Prior <- run$Prior
-Mcmc <- run$Mcmc
-fit <- run$fit
-
-# Check trace plots.
-fit$llikedraw %>% 
-  matrix(dimnames = list(NULL, "llike")) %>% 
-  mcmc_trace(
-    n_warmup = 500
-  )
-
-# colnames(fit$Gammadraw) <- str_c("Gamma[", c(1:ncol(fit$Gammadraw)), ",1]")
-# fit$Gammadraw %>%
-#   mcmc_trace(
-#     n_warmup = 500,
-#     facet_args = list(nrow = 5, labeller = label_parsed)
-#   )
-# 
-# ggsave(
-#   "mcmc_trace_conjugate.png",
-#   path = here::here("Figures"),
-#   width = 12, height = 6, units = "in"
-# )
-
-# Import model fit table.
-# model_fit_table <- matrix(NA, nrow = 6, ncol = 6) %>%
-#   as_tibble() %>%
-#   rename(
[…]

### 2019-06-22 analysis/02_clean-data.Rmd

@@
 data <- read_csv(
-  here::here("data", "conjointqsf_final.csv"),
+  here::here("data", "raw_data", "conjointqsf_final.csv"),
   skip = 2,
@@
 
+## Remove identifying and extraneous information
+
+```{r clean-data, warning=FALSE, message=FALSE}
+data <- data_clean %>% 
+  mutate(id = row_number()) %>% 
+  rename(version = vers_CBCONJOINT) %>% 
+  select(id, version, Q1.1:Q5.18)
+```
+
 ## Save clean data
@@
 ```{r clean-data, warning=FALSE, message=FALSE}
-data <- data_clean %>% 
-  select(-c("732d72a6-25a3-4194-8416-461acae30837.1.1_CBCONJOINT":"revision_CBCONJOINT"))
-
 write_csv(data, here("data", "derived_data", "final_data.csv"))

### 2019-06-22 analysis/03_analysis.Rmd

--- 2019-05-25 analysis/04_analysis.Rmd
@@
 
+# Load data and model output
+
 ```{r load-libraries-data, warning=FALSE, message=FALSE}
@@
 library(donorheuristics)
+library(rstan)
+library(bayesplot)
+library(tidybayes)
+library(bayesm)
+library(ggridges)
 library(ggraph)
@@
 
-# Load data
-# results <- readRDS(here("data", "derived_data", "results.rds"))
+# Specify the model to load
+intercept <- 1 # Intercept-only
+
+# Load and extract data and model output (see model-calibration.R)
+if (intercept == 1) {
+  run <- read_rds(here::here("analysis", "output", "model_runs", "hmnl-intercept_noncentered.RDS"))
+  data <- run$data
+  fit <- run$fit
+}
 ```
@@
 
+# Model checking
+
+```{r model-checking, warning=FALSE, message=FALSE}
+source(here::here("R", "stan_utility.R"))
+
+# Check for divergences
+check_div(fit)
+
+# # Check the effective sample size (not working for a hierarchical model?)
+# check_n_eff(fit)
+# 
+# # Check the Rhat statistic (not working for a hierarchical model?)
+# check_rhat(fit)
+
+# Check trace plots
+fit %>%
+  extract(
+    inc_warmup = TRUE,
+    permuted = FALSE
+  ) %>%
+  mcmc_trace(
+    regex_pars = "Theta",
+    n_warmup = 1000,
+    facet_args = list(nrow = 2, labeller = label_parsed)
+  )
+
+ggsave(
+  "mcmc-trace_noncentered.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12, height = 6, units = "in"
+)
+```
+
+# Plot marginals
+
+```{r plot-marginals, warning=FALSE, message=FALSE}
+# Extract posterior draws
+draws <- fit %>% 
+  spread_draws(Theta[i, j]) %>% 
+  ungroup() %>% 
+  filter(.iteration > 500)
+
+# Plot marginals
+level_labels <- c(
+  str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
+  str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
+  "Financial transparency: Yes",
+  "Accountability: Yes",
+  str_c("Funding sources: ", c("Funded primarily by a handful of wealthy private donors", "Funded primarily by government grants")),
+  str_c("Relationship with host government: ", c("Criticized by government", "Under government crackdown"))
+)
+draws %>% 
+  mutate(
+    levels = factor(
+      i,
+      labels = level_labels
+    )
+  ) %>%
+  ggplot(aes(x = Theta, y = levels)) + 
+  geom_halfeyeh(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Attribute Levels")
+
+# Save plot
+ggsave(
+  "marginal_posteriors.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12, height = 6, units = "in"
+)
+```
+
 # Original computing environment

### 2019-06-22 analysis/02_clean-data.Rmd
Add raw and clean data

--- 2019-06-20 analysis/02_clean-data.Rmd
@@
 
-```{r clean-data, warning=FALSE, message=FALSE}
+We downloaded the `conjointqsf_final.csv` file directly from Qualtrics and ran this code to remove identifying information.
+We then saved that CSV file as `conjointqsf_final.csv` and include it in `data/raw_data` for distribution.
+We use the de-identified file in the rest of our data cleaning and analysis.
+
+```r
 library(tidyverse)
@@
 
-col_names <- names(read_csv(here::here("data", "conjointqsf_final.csv")))
+col_names <- names(read_csv(here::here("data", "private_data", "conjointqsf_final.csv")))
 data <- read_csv(
-  here::here("data", "conjointqsf_final.csv"),
-  skip = 2,
-  col_names = col_names
+  here::here("data", "private_data", "conjointqsf_final.csv"),
+  skip = 3,
+  col_names = col_names,
+  guess_max = 1500
+)
+
+# Remove IP address and location information
+data %>% 
+  select(-V6, -LocationLatitude, -LocationLongitude, -LocationAccuracy) %>% 
+  write_csv(here::here("data", "raw_data", "conjointqsf_final.csv"))
+```
+
+```{r load-raw-data, warning=FALSE, message=FALSE}
+library(tidyverse)
+library(donorheuristics)
+library(here)
+
+data <- read_csv(
+  here::here("data", "raw_data", "conjointqsf_final.csv"),
+  guess_max = 1500
 )
@@
 
-```{r clean-data, warning=FALSE, message=FALSE}
+```{r number-finished}
 data %>%
@@
 
-```{r clean-data, warning=FALSE, message=FALSE}
+```{r consent}
 data %>%
@@
 
-```{r clean-data, warning=FALSE, message=FALSE}
+```{r screening}
 data %>%
@@
 
-```{r clean-data, warning=FALSE, message=FALSE}
+```{r display-logic}
 data %>%
@@
 
-```{r clean-data, warning=FALSE, message=FALSE}
+```{r attention-check}
 data %>%
@@
 
-```{r clean-data, warning=FALSE, message=FALSE}
+```{r confirm-ages}
 data %>%
@@
 
-```{r clean-data, warning=FALSE, message=FALSE}
+```{r clean-data}
 data_clean <- data %>%
@@
 
-```{r clean-data, warning=FALSE, message=FALSE}
+```{r clean-data-confirmation}
 # Finished respondents
@@
 
-```{r clean-data, warning=FALSE, message=FALSE}
+```{r choice-clean}
 data_clean %>%
@@
 
-```{r clean-data, warning=FALSE, message=FALSE}
+```{r design-random-assignment}
 data_clean %>%
@@
 
-```{r clean-data, warning=FALSE, message=FALSE}
-design_orig <- read_csv(here("data", "design.csv")) %>% 
+```{r check-design, warning=FALSE, message=FALSE}
+design_orig <- read_csv(here("data", "derived_data", "design.csv")) %>% 
   rename(
@@
 
+## Remove extraneous information
+
+```{r shrink-data}
+data <- data_clean %>% 
+  mutate(id = row_number()) %>% 
+  rename(version = vers_CBCONJOINT) %>% 
+  select(id, version, Q1.1:Q5.18)
+```
+
 ## Save clean data
 
-```{r clean-data, warning=FALSE, message=FALSE}
-data <- data_clean
-
-write_csv(data, here("data", "final_data.csv"))
+```{r save-clean-data}
+write_csv(data, here("data", "derived_data", "final_data.csv"))
 ```

### 2019-06-24 analysis/03_analysis.Rmd

--- 2019-05-25 analysis/04_analysis.Rmd
@@
 
-# Load data
-# results <- readRDS(here("data", "derived_data", "results.rds"))
+# Specify the model to load
+intercept <- 1 # Intercept-only
+
+# Load and extract data and model output (see model-calibration.R)
+if (intercept == 1) {
+  run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.RDS"))
+  data <- run$data
+  fit <- run$fit
+}
 ```
@@
 
+# Model checking
+
+```{r model-checking}
+source(here::here("R", "stan_utility.R"))
+
+# Check for divergences
+check_div(fit)
+
+# # Check the effective sample size (not working for a hierarchical model?)
+# check_n_eff(fit)
+# 
+# # Check the Rhat statistic (not working for a hierarchical model?)
+# check_rhat(fit)
+
+# Check trace plots
+fit %>%
+  extract(
+    inc_warmup = TRUE,
+    permuted = FALSE
+  ) %>%
+  mcmc_trace(
+    regex_pars = "Theta",
+    n_warmup = 1000,
+    facet_args = list(nrow = 2, labeller = label_parsed)
+  )
+
+# colnames(fit$Gammadraw) <- str_c("Gamma[", c(1:ncol(fit$Gammadraw)), ",1]")
+# fit$Gammadraw %>%
+#   mcmc_trace(
+#     n_warmup = 500,
+#     facet_args = list(nrow = 5, labeller = label_parsed)
+#   )
+
+ggsave(
+  "intercept_trace_noncentered.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12, height = 6, units = "in"
+)
+```
+
+# Extract draws
+
+```{r extract-draws}
+# Extract posterior draws
+draws <- fit %>% 
+  spread_draws(Theta[i, j]) %>% 
+  ungroup() %>% 
+  filter(.iteration > 500)
+
+# colnames(fit$Gammadraw) <- str_c("Gamma[", c(1:ncol(fit$Gammadraw)), ",1]")
+# draws <- as_tibble(fit$Gammadraw) %>%
+#   mutate(
+#     .draw = row_number(),
+#     .iteration = row_number()
+#   ) %>%
+#   gather(key = i, value = Gamma, -c(.draw, .iteration)) %>%
+#   separate(col = i, into = c("temp1", "i"), sep = "\\[") %>%
+#   separate(col = i, into = c("i", "j"), sep = ",") %>%
+#   separate(col = j, into = c("j", "temp2"), sep = "\\]") %>%
+#   mutate(
+#     .chain = as.integer(1),
+#     i = as.integer(i),
+#     j = as.integer(j)
+#   ) %>%
+#   select(.chain, .iteration, .draw, i, j, Gamma) %>%
+#   arrange(.iteration) %>%
+#   filter(.iteration > 500)
+
+# Save draws
+write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept_noncentered.rds"))
+```
+
+# Plot marginals
+
+```{r plot-marginals}
+# Plot marginals
+level_labels <- c(
+  str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
+  str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
+  "Financial transparency: Yes",
+  "Accountability: Yes",
+  str_c("Funding sources: ", c("Funded primarily by a handful of wealthy private donors", "Funded primarily by government grants")),
+  str_c("Relationship with host government: ", c("Criticized by government", "Under government crackdown"))
+)
+draws %>% 
+  mutate(
+    levels = factor(
+      i,
+      labels = level_labels
+    )
+  ) %>%
+  ggplot(aes(x = Theta, y = levels)) + 
+  geom_halfeyeh(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Attribute Levels")
+
+# Save plot
+ggsave(
+  "intercept_marginal-posteriors_noncentered.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12, height = 6, units = "in"
+)
+```
+
 # Original computing environment

### 2019-06-25 manuscript/manuscript.Rmd
Placeholders for Methods and Results sections
Outline model results

@@
 We will field our larger conjoint survey experiment very soon and we look forward to your comments and suggestions before we launch it!
+
+# Methods
+
+# Results
+
+- First set of questions (hypotheses) can be answered using the results of the intercept-only model.
+- Second set of questions (confirmatory) can be answered using the following upper-level models:
+  - Public affairs: `Donation preferences ~ Public affairs knowledge + Public affairs activity`
+  - Political ideology: `Donation preferences ~ Political ideology`
+  - Social views: `Donation preferences ~ Public affairs trust + Social ideology + Religiosity`
+  - Charity and voluntarism: `Donation preferences ~ Charity trust + Charity activity + Volunteer activity + Activism activity + Association membership`
+  - Demographics: `Donation preferences ~ Gender + Marital status + Education + Income + Race + Age`
+  - `Donation preferences ~ (Public affairs) + (Political ideology)`
+  - `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views)`
+  - `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views) + (Charity and voluntarism)`
+  - `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views) + (Charity and voluntarism) + (Demographics)`
+- Third set of questions (exploratory) can be answered using a market simulator.

### 2019-06-25 analysis/02_clean-data.Rmd
Added outline of needed transformations

@@
 
-## Save clean data
+# Transform data
+
+```{r transform-data}
+data %>% 
+  mutate(
+    # *Q2.1*: How often do you follow national news? 
+    # 
+    # - Multiple times a day → At least once a day
+    # - Every day → At least once a day
+    # - Once a week → Once a week
+    # - Hardly ever → Rarely (base case)
+    # - Never → Rarely
+    Q2.1 = factor(
+      case_when(
+        Q2.1 == 1 ~ "At least once a day",
+        Q2.1 == 2 ~ "At least once a day",
+        Q2.1 == 3 ~ "Once a week",
+        Q2.1 == 4 ~ "Rarely",
+        Q2.1 == 5 ~ "Rarely"
+      )
+    ),
+    # *Q2.4*: How often would you say you follow what's going on in government and public affairs?
+    # 
+    # - Most of the time → Often
+    # - Some of the time → Often
+    # - Only now and then → Not often (base case)
+    # - Hardly at all → Not often (base case)
+    Q2.4 = factor(
+      case_when(
+        Q2.4 == 1 ~ "Often",
+        Q2.4 == 2 ~ "Often",
+        Q2.4 == 3 ~ "Not often",
+        Q2.4 == 4 ~ "Not often"
+      )
+    ),
+    # *Q2.5*: How often do you donate to charity (with either cash or in-kind)?
+    # 
+    # - Once a week → At least once a month
+    # - Once a month → At least once a month
+    # - Once every three months → More than once a month, less than once a year
+    # - Once every six months → More than once a month, less than once a year
+    # - Once a year → More than once a month, less than once a year
+    # - Once every few years → Rarely (base case) TERMINATED
+    # - Never → Rarely TERMINATED
+    Q2.5 = factor(
+      case_when(
+        Q2.5 == 1 ~ "At least once a month",
+        Q2.5 == 2 ~ "At least once a month",
+        Q2.5 == 3 ~ "More than once a month, less than once a year",
+        Q2.5 == 4 ~ "More than once a month, less than once a year",
+        Q2.5 == 5 ~ "More than once a month, less than once a year"
+      )
+    ),
+    # *Q2.10*: How often do you volunteer?
+    # 
+    # - Once a week → At least once a month
+    # - Once a month → At least once a month
+    # - Once every three months → More than once a month, less than once a year
+    # - Once every six months → More than once a month, less than once a year
+    # - Once a year → More than once a month, less than once a year
+    # - Once every few years → Rarely (base case)
+    # - Never → Rarely NOT INCLUDED
+    Q2.10 = factor(
+      case_when(
+        Q2.6 == 1 ~ "At least once a month",
+        Q2.6 == 2 ~ "At least once a month",
+        Q2.6 == 3 ~ "More than once a month, less than once a year",
+        Q2.6 == 4 ~ "More than once a month, less than once a year",
+        Q2.6 == 5 ~ "More than once a month, less than once a year",
+        Q2.6 == 6 ~ "Rarely"
+      )
+    ),
+    # *Q5.4*: Historically, how involved have you been in activist causes?
+    # 
+    # - Extremely involved → Involved
+    # - Very involved → Involved
+    # - Moderately involved → Involved
+    # - Slightly involved → Not involved (base case)
+    # - Never involved → Not involved
+    Q5.4 = factor(
+      case_when(
+        Q5.4 == 1 ~ "Involved",
+        Q5.4 == 2 ~ "Involved",
+        Q5.4 == 3 ~ "Involved",
+        Q5.4 == 4 ~ "Not involved",
+        Q5.4 == 5 ~ "Not involved"
+      )
+    ),
+    # *Q5.5*: Historically, how involved has your family been in activist causes?
+    # 
+    # - Extremely involved → Involved
+    # - Very involved → Involved
+    # - Moderately involved → Involved
+    # - Slightly involved → Not involved (base case)
+    # - Never involved → Not involved
+    Q5.5 = factor(
+      case_when(
+        Q5.5 == 1 ~ "Involved",
+        Q5.5 == 2 ~ "Involved",
+        Q5.5 == 3 ~ "Involved",
+        Q5.5 == 4 ~ "Not involved",
+        Q5.5 == 5 ~ "Not involved"
+      )
+    ),
+    # *Q5.8*: How often do you attend religious or worship services, not including weddings and funerals?
+    # 
+    # - More than once a week → At least once a month
+    # - Once a week → At least once a month
+    # - Once or twice a month → At least once a month
+    # - A few times a year → Rarely (base case)
+    # - Seldom → Rarely
+    # - Never → Rarely
+    # - Don't know → NULL
+    Q5.8 = factor(
+      case_when(
+        Q5.8 == 1 ~ "At least once a month",
+        Q5.8 == 2 ~ "At least once a month",
+        Q5.8 == 3 ~ "At least once a month",
+        Q5.8 == 4 ~ "Rarely",
+        Q5.8 == 5 ~ "Rarely",
+        Q5.8 == 6 ~ "Rarely",
+        Q5.8 == 7 ~ "NULL"
+      )
+    ),
+    # *Q5.9*: How important is religion in your life?
+    # 
+    # - Extremely important → Important
+    # - Very important → Important
+    # - Moderately important → Important
+    # - Slightly important → Not important (base case)
+    # - Not at all important → Not important
+    Q5.9 = factor(
+      case_when(
+        Q5.9 == 1 ~ "Important",
+        Q5.9 == 2 ~ "Important",
+        Q5.9 == 3 ~ "Important",
+        Q5.9 == 4 ~ "Not important",
+        Q5.9 == 5 ~ "Not important"
+      )
+    ),
+    # *Q5.15*: What is your annual household income before taxes?
+    # 
+    # - Less than $10,000 → More/less than median (base case = less than median)
+    # - \$10,000 to \$19,999 → More/less than median
+    # - \$20,000 to \$29,999 → More/less than median
+    # - \$30,000 to \$39,999 → More/less than median
+    # - \$40,000 to \$49,999 → More/less than median
+    # - \$50,000 to \$59,999 → More/less than median
+    # - \$60,000 to \$69,999 → More/less than median
+    # - \$70,000 to \$79,999 → More/less than median
+    # - \$80,000 to \$89,999 → More/less than median
+    # - \$90,000 to \$99,999 → More/less than median
+    # - \$100,000 to \$149,999 → More/less than median
+    # - \$150,000 to \$199,999 → More/less than median
+    # - \$200,000 to \$299,999 → More/less than median
+    # - \$300,000 or more → More/less than median
+    Q5.15 = factor(
+      case_when(
+        Q5.15 > median(Q5.15) ~ "More than median",
+        Q5.15 <= median(Q5.15) ~ "Less than median"
+      )
+    ),
+    # *Q5.17*: How old are you?
+    # 
+    # - Under 18 → More/less than median (base case = less than median)
+    # - 18 - 24 → More/less than median
+    # - 25 - 34 → More/less than median
+    # - 35 - 44 → More/less than median
+    # - 45 - 54 → More/less than median
+    # - 55 - 64 → More/less than median
+    # - 65 - 74 → More/less than median
+    # - 75 - 84 → More/less than median
+    # - 85 or older → More/less than median
+    Q5.17 = factor(
+      case_when(
+        Q5.17 > median(Q5.17) ~ "More than median",
+        Q5.17 <= median(Q5.17) ~ "Less than median"
+      )
+    )
+  )
+```
+
+# Save clean data with transformations
 

### 2019-06-25 analysis/02_clean-data.Rmd
Fixed errors, used external data to set income and age medians

@@
     # - Once a year → More than once a month, less than once a year
-    # - Once every few years → Rarely (base case) TERMINATED
-    # - Never → Rarely TERMINATED
     Q2.5 = factor(
@@
     # - Once every few years → Rarely (base case)
-    # - Never → Rarely NOT INCLUDED
     Q2.10 = factor(
       case_when(
-        Q2.6 == 1 ~ "At least once a month",
-        Q2.6 == 2 ~ "At least once a month",
-        Q2.6 == 3 ~ "More than once a month, less than once a year",
-        Q2.6 == 4 ~ "More than once a month, less than once a year",
-        Q2.6 == 5 ~ "More than once a month, less than once a year",
-        Q2.6 == 6 ~ "Rarely"
+        Q2.10 == 1 ~ "At least once a month",
+        Q2.10 == 2 ~ "At least once a month",
+        Q2.10 == 3 ~ "More than once a month, less than once a year",
+        Q2.10 == 4 ~ "More than once a month, less than once a year",
+        Q2.10 == 5 ~ "More than once a month, less than once a year",
+        Q2.10 == 6 ~ "Rarely"
       )
@@
       case_when(
-        Q5.15 > median(Q5.15) ~ "More than median",
-        Q5.15 <= median(Q5.15) ~ "Less than median"
+        Q5.15 > 5 ~ "More than median", # Median income in 2017 was $61,372
+        Q5.15 <= 5 ~ "Less than median"
       )
@@
       case_when(
-        Q5.17 > median(Q5.17) ~ "More than median",
-        Q5.17 <= median(Q5.17) ~ "Less than median"
+        Q5.17 >= 3 ~ "More than median", # Median age in 2017 was 36
+        Q5.17 < 3 ~ "Less than median"
       )

### 2019-06-25 analysis/02_clean-data.Rmd
Cleaned up transformations (including base cases)

@@
 ```{r transform-data}
-data %>% 
+data <- data %>% 
   mutate(
@@
         Q2.1 == 5 ~ "Rarely"
-      )
+      ),
+      levels = c("Rarely", "Once a week", "At least once a day")
     ),
@@
         Q2.4 == 4 ~ "Not often"
-      )
+      ),
+      levels = c("Not often", "Often")
     ),
@@
     # - Once every six months → More than once a month, less than once a year
-    # - Once a year → More than once a month, less than once a year
+    # - Once a year → More than once a month, less than once a year (base case)
     Q2.5 = factor(
@@
         Q2.5 == 5 ~ "More than once a month, less than once a year"
-      )
+      ),
+      levels = c("More than once a month, less than once a year", "At least once a month")
     ),
@@
     # 
+    # - NA → Haven't volunteered in past 12 months (base case)
     # - Once a week → At least once a month
@@
     # - Once a year → More than once a month, less than once a year
-    # - Once every few years → Rarely (base case)
+    # - Once every few years → Rarely
     Q2.10 = factor(
       case_when(
+        is.na(Q2.10) == TRUE ~ "Haven't volunteered in past 12 months",
         Q2.10 == 1 ~ "At least once a month",
@@
         Q2.10 == 6 ~ "Rarely"
-      )
+      ),
+      levels = c("Haven't volunteered in past 12 months", "Rarely", "More than once a month, less than once a year", "At least once a month")
     ),
@@
         Q5.4 == 4 ~ "Not involved",
-        Q5.4 == 5 ~ "Not involved"
-      )
+        Q5.4 == 5 ~ "Not involved",
+      ),
+      levels = c("Not involved", "Involved")
     ),
@@
         Q5.5 == 5 ~ "Not involved"
-      )
+      ),
+      levels = c("Not involved", "Involved")
     ),
@@
     # - Never → Rarely
-    # - Don't know → NULL
+    # - Don't know → Not sure
     Q5.8 = factor(
@@
         Q5.8 == 6 ~ "Rarely",
-        Q5.8 == 7 ~ "NULL"
-      )
+        Q5.8 == 7 ~ "Not sure"
+      ),
+      levels = c("Not sure", "Rarely", "At least once a month")
     ),
@@
         Q5.9 == 5 ~ "Not important"
-      )
+      ),
+      levels = c("Not important", "Important")
     ),
@@
         Q5.15 <= 5 ~ "Less than median"
-      )
+      ),
+      levels = c("Less than median", "More than median")
     ),
@@
         Q5.17 < 3 ~ "Less than median"
-      )
+      ),
+      levels = c("Less than median", "More than median")
     )

### 2019-06-25 analysis/model-calibration.R
Setup for running each of the models in the pre-registration

@@ -6,7 +6,7 @@ library(mvtnorm)
 library(bayesm)
 
 # Load data and design.
-final_data <- read_csv(here::here("data", "derived_data", "final_data.csv"))
+final_data <- read_rds(here::here("data", "derived_data", "final_data.rds"))
 design <- read_csv(here::here("data", "derived_data", "dummy_design.csv")) %>%
   select(-X1) %>%
   rename(
@@ -15,8 +15,19 @@ design <- read_csv(here::here("data", "derived_data", "dummy_design.csv")) %>%
     alt = choice
   )
 
-# Specify the model to load.
-intercept <- 1 # Intercept-only.
+# Main covariate models.
+intercept <- 0           # Intercept-only.
+public_affairs <- 1      # Public affairs: Public affairs knowledge + Public affairs activity.
+political_ideology <- 0  # Political ideology.
+social_views <- 0        # Social views: Public affairs trust + Social ideology + Religiosity.
+charity_voluntarism <- 0 # Charity and voluntarism: Charity trust, Charity activity, Volunteer activity, Activism activity, Association membership
+demographics <- 0        # Demographics: Gender, Marital status, Education, Income, Race, Age
+
+# Many covariate models.
+public_political <- 0                     # Public affairs + Political ideology
+public_political_social <- 0              # Public affairs + Political ideology + Social views
+public_political_social_charity <- 0      # Public affairs + Political ideology + Social views + Charity and voluntarism
+public_political_social_charity_demo <- 0 # Public affairs + Political ideology + Social views + Charity and voluntarism + Demographics
 
 # Restructure choice data Y.
 Y <- final_data %>%
@@ -60,8 +71,113 @@ for (n in 1:dim(X)[1]) {
 
 # Restructure covariates Z.
 if (intercept == 1) Z <- matrix(data = 1, nrow = dim(X)[1], ncol = 1)
+if (public_affairs == 1) {
+  Z <- tibble(intercept = rep(1, dim(X)[1])) %>%
+    bind_cols(
+      final_data %>%
+        select(Q2.1, Q2.2, Q2.3_1:Q2.3_7, Q2.4, Q5.7) %>%
+        mutate_if(is.factor, as.integer) %>%
[…]

### 2019-06-27 analysis/03_analysis.Rmd
All the things (draws)

--- 2019-05-25 analysis/04_analysis.Rmd
@@
 
-# Load data
-# results <- readRDS(here("data", "derived_data", "results.rds"))
+intercept <- 0                            # Intercept-only
+public_affairs <- 0                       # Public affairs
+political_ideology <- 0                   # Political ideology
+social_views <- 0                         # Social views
+charity_voluntarism <- 0                  # Charity and voluntarism
+demographics <- 0                         # Demographics
+public_political <- 0                     # Public affairs + Political ideology
+public_political_social <- 0              # + Social views
+public_political_social_charity <- 0      # + Charity and voluntarism
+public_political_social_charity_demo <- 1 # + Demographics
+
+# Load and extract data and model output (see model-calibration.R)
+if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.RDS"))
+if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
+if (political_ideology == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
+if (social_views == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
+if (charity_voluntarism == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
+if (demographics == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
+if (public_political == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
+if (public_political_social == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
+if (public_political_social_charity == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
+if (public_political_social_charity_demo == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
+data <- run$data
+fit <- run$fit
 ```
@@
 
+# Model checking
+
+```{r model-checking}
+source(here::here("R", "stan_utility.R"))
+
+# Check for divergences
+check_div(fit)
+
+# # Check the effective sample size (not working for a hierarchical model?)
+# check_n_eff(fit)
+# 
+# # Check the Rhat statistic (not working for a hierarchical model?)
+# check_rhat(fit)
+
+# Check trace plots (SUBSET?)
+fit %>%
+  extract(
+    inc_warmup = TRUE,
+    permuted = FALSE
+  ) %>%
+  mcmc_trace(
+    regex_pars = "Theta",
+    n_warmup = 1000,
+    facet_args = list(
+      nrow = round((data$L * data$C)/7), 
+      labeller = label_parsed
+    )
+  )
+
+# ggsave(
+#   "intercept_trace_noncentered.png",
+#   path = here::here("analysis", "output", "figures"),
+#   width = 12, height = 6, units = "in"
+# )
+```
+
+# Extract draws
+
+```{r extract-draws}
+# Extract posterior draws
+draws <- fit %>% 
+  spread_draws(Theta[i, j]) %>% 
+  ungroup() %>% 
+  filter(.iteration > 500)
+
+# Save draws
+if (intercept == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept_noncentered.rds"))
+if (public_affairs == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))
+if (political_ideology == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "political_ideology.rds"))
+if (social_views == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "social_views.rds"))
+if (charity_voluntarism == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds"))
+if (demographics == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "demographics.rds"))
+if (public_political == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political.rds"))
+if (public_political_social == 1)  write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social.rds"))
+if (public_political_social_charity == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds"))
+if (public_political_social_charity_demo == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity_demo.rds"))
+```
+
+# Plot marginals
+
+```{r plot-marginals}
+# Plot marginals
+level_labels <- c(
+  str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
+  str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
+  "Financial transparency: Yes",
+  "Accountability: Yes",
+  str_c("Funding sources: ", c("Funded primarily by a handful of wealthy private donors", "Funded primarily by government grants")),
+  str_c("Relationship with host government: ", c("Criticized by government", "Under government crackdown"))
+)
+
+# Covariates...
+
+draws %>% 
+  mutate(
+    levels = factor(
+      i,
+      labels = level_labels
+    )
+  ) %>%
+  ggplot(aes(x = Theta, y = levels)) + 
+  geom_halfeyeh(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Attribute Levels")
+
+# Save plot
+ggsave(
+  "intercept_marginal-posteriors_noncentered.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12, height = 6, units = "in"
+)
+```
+
 # Original computing environment

### 2019-06-27 analysis/model-calibration.R

@@ -15,19 +15,16 @@ design <- read_csv(here::here("data", "derived_data", "dummy_design.csv")) %>%
     alt = choice
   )
 
-# Main covariate models.
-intercept <- 0           # Intercept-only.
-public_affairs <- 1      # Public affairs: Public affairs knowledge + Public affairs activity.
-political_ideology <- 0  # Political ideology.
-social_views <- 0        # Social views: Public affairs trust + Social ideology + Religiosity.
-charity_voluntarism <- 0 # Charity and voluntarism: Charity trust, Charity activity, Volunteer activity, Activism activity, Association membership
-demographics <- 0        # Demographics: Gender, Marital status, Education, Income, Race, Age
-
-# Many covariate models.
+intercept <- 0                            # Intercept-only.
+public_affairs <- 0                       # Public affairs: Public affairs knowledge + Public affairs activity.
+political_ideology <- 0                   # Political ideology.
+social_views <- 0                         # Social views: Public affairs trust + Social ideology + Religiosity.
+charity_voluntarism <- 0                  # Charity and voluntarism: Charity trust, Charity activity, Volunteer activity, etc.
+demographics <- 0                         # Demographics: Gender, Marital status, Education, Income, Race, Age
 public_political <- 0                     # Public affairs + Political ideology
 public_political_social <- 0              # Public affairs + Political ideology + Social views
 public_political_social_charity <- 0      # Public affairs + Political ideology + Social views + Charity and voluntarism
-public_political_social_charity_demo <- 0 # Public affairs + Political ideology + Social views + Charity and voluntarism + Demographics
+public_political_social_charity_demo <- 1 # Public affairs + Political ideology + Social views + Charity and voluntarism + Demographics
 
 # Restructure choice data Y.
 Y <- final_data %>%
@@ -215,7 +212,7 @@ if (social_views == 1) write_rds(run, here::here("analysis", "output", "model_ru
 if (charity_voluntarism == 1) write_rds(run, here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
 if (demographics == 1) write_rds(run, here::here("analysis", "output", "model_runs", "demographics.rds"))
 if (public_political == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political.rds"))
-if (public_political_social == 1)  write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social.rds"))
[…]

### 2019-07-25 analysis/03_analysis.Rmd
Initial model results for covariate models

@@
 
-# Load data and model output
+# Load packages
 
-```{r load-libraries-data, warning=FALSE, message=FALSE}
+```{r load-packages, warning=FALSE, message=FALSE}
 library(tidyverse)
@@
 set.seed(1234)
-
-intercept <- 0                            # Intercept-only
-public_affairs <- 0                       # Public affairs
-political_ideology <- 0                   # Political ideology
-social_views <- 0                         # Social views
-charity_voluntarism <- 0                  # Charity and voluntarism
-demographics <- 0                         # Demographics
-public_political <- 0                     # Public affairs + Political ideology
-public_political_social <- 0              # + Social views
-public_political_social_charity <- 0      # + Charity and voluntarism
-public_political_social_charity_demo <- 1 # + Demographics
-
-# Load and extract data and model output (see model-calibration.R)
-if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.RDS"))
-if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
-if (political_ideology == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
-if (social_views == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
-if (charity_voluntarism == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
-if (demographics == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
-if (public_political == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
-if (public_political_social == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
-if (public_political_social_charity == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
-if (public_political_social_charity_demo == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
-data <- run$data
-fit <- run$fit
 ```
@@
        width = 13/3, height = 2, units = "in", type = "cairo", dpi = 300)
+```
+
+# Load data and model output
+
+```{r load-data-output, warning=FALSE, message=FALSE}
+intercept <- 0                            # Intercept-only
+public_affairs <- 1                       # Public affairs
+political_ideology <- 0                   # Political ideology
+social_views <- 0                         # Social views
+charity_voluntarism <- 0                  # Charity and voluntarism
+demographics <- 0                         # Demographics
+public_political <- 0                     # Public affairs + Political ideology
+public_political_social <- 0              # + Social views
+public_political_social_charity <- 0      # + Charity and voluntarism
+public_political_social_charity_demo <- 0 # + Demographics
+
+# Load and extract data and model output (see model-calibration.R)
+if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.RDS"))
+if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
+if (political_ideology == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
+if (social_views == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
+if (charity_voluntarism == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
+if (demographics == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
+if (public_political == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
+if (public_political_social == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
+if (public_political_social_charity == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
+if (public_political_social_charity_demo == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
+data <- run$data
+fit <- run$fit
 ```
@@
 ```{r plot-marginals}
-# Plot marginals
+intercept <- 0                            # Intercept-only
+public_affairs <- 0                       # Public affairs
+political_ideology <- 0                   # Political ideology
+social_views <- 0                         # Social views
+charity_voluntarism <- 0                  # Charity and voluntarism
+demographics <- 0                         # Demographics
+public_political <- 0                     # Public affairs + Political ideology
+public_political_social <- 0              # + Social views
+public_political_social_charity <- 0      # + Charity and voluntarism
+public_political_social_charity_demo <- 1 # + Demographics
+
+# Load draws
+if (intercept == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "intercept_noncentered.rds"))
+if (public_affairs == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))
+if (political_ideology == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "political_ideology.rds"))
+if (social_views == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "social_views.rds"))
+if (charity_voluntarism == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds"))
+if (demographics == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "demographics.rds"))
+if (public_political == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political.rds"))
+if (public_political_social == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political_social.rds"))
+if (public_political_social_charity == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds"))
+if (public_political_social_charity_demo == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political_social_charity_demo.rds"))
+
+# Name labels
 level_labels <- c(
@@
   "Accountability: Yes",
-  str_c("Funding sources: ", c("Funded primarily by a handful of wealthy private donors", "Funded primarily by government grants")),
-  str_c("Relationship with host government: ", c("Criticized by government", "Under government crackdown"))
+  str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants")),
+  str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))
 )
 
-# Covariates...
+# Name covariates
+if (public_affairs == 1) {
+  covariate_labels <- c(
+    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
+    str_c(
+      "Medium to follow news: ", 
+      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
+    ),
+    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: Yes to No"
+  )
+}
+if (political_ideology == 1) {
+  covariate_labels <- c(
+    "Liberal to Conservative"
+  )
+}
+if (social_views == 1) {
+  covariate_labels <- c(
+    "Trust in political institutions: None to Complete", "People should be more charitable: Agree to Disagree",
+    "Religious and worship service attendance: Multiple times a week to Never", "Importance of religion: Extremely to Not at all",
+    "Religion: Catholic to Atheist"
+  )
+}
+if (charity_voluntarism == 1) {
+  covariate_labels <- c(
+    "Importance of trusing charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",
+    "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: Yes to No", "Volunteer frequency: Weekly to Every few years",
+    "History of activism: Extreme to Never", "History of family activism: Extreme to Never", 
+    str_c(
+      c(
+        "Church or religious organization: ", "Sport or recreational organization: ", "Art, music, or educational organization: ",
+        "Labor union: ", "Political party: ", "Environmental organization: ", "Professional association: ", 
+        "Humanitarian or charitable organization: ", "Consumer organization: ", "Other organization: "
+      ), 
+      "Member to Not"
+    )
+  )
+}
+if (demographics == 1) {
+  covariate_labels <- c(
+    "Gender: Male to Prefer not to say", "Marital status: Married to Never married", "Education: Less than high school to Doctorate",
+    "Income: Less than $10,000 to $300,000 or more",
+    str_c(
+      "Race/ethnicity: ", 
+      c("White", "Black or African American", "American Indian or Alaska Native", "Asian", "Native Hawaiian or Pacific Islander", "Other")
+    ),
+    "Age: Under 18 to 85 or older"
+  )
+}
+if (public_political == 1) {
+  covariate_labels <- c(
+    # Public affairs
+    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
+    str_c(
+      "Medium to follow news: ", 
+      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
+    ),
+    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: Yes to No",
+    # Political ideology
+    "Liberal to Conservative"
+  )
+}
+if (public_political_social == 1) {
+  covariate_labels <- c(
+    # Public affairs
+    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
+    str_c(
+      "Medium to follow news: ", 
+      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
+    ),
+    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: Yes to No",
+    # Political ideology
+    "Liberal to Conservative",
+    # Social views
+    "Trust in political institutions: None to Complete", "People should be more charitable: Agree to Disagree",
+    "Religious and worship service attendance: Multiple times a week to Never", "Importance of religion: Extremely to Not at all",
+    "Religion: Catholic to Atheist"
+  )
+}
+if (public_political_social_charity == 1) {
+  covariate_labels <- c(
+    # Public affairs
+    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
+    str_c(
+      "Medium to follow news: ", 
+      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
+    ),
+    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: Yes to No",
+    # Political ideology
+    "Liberal to Conservative",
+    # Social views
+    "Trust in political institutions: None to Complete", "People should be more charitable: Agree to Disagree",
+    "Religious and worship service attendance: Multiple times a week to Never", "Importance of religion: Extremely to Not at all",
+    "Religion: Catholic to Atheist",
+    # Charity and voluntarism
+    "Importance of trusing charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",
+    "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: Yes to No", "Volunteer frequency: Weekly to Every few years",
+    "History of activism: Extreme to Never", "History of family activism: Extreme to Never", 
+    str_c(
+      c(
+        "Church or religious organization: ", "Sport or recreational organization: ", "Art, music, or educational organization: ",
+        "Labor union: ", "Political party: ", "Environmental organization: ", "Professional association: ", 
+        "Humanitarian or charitable organization: ", "Consumer organization: ", "Other organization: "
+      ), 
+      "Member to Not"
+    )
+  )
+}
+if (public_political_social_charity_demo == 1) {
+  covariate_labels <- c(
+    # Public affairs
+    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
+    str_c(
+      "Medium to follow news: ", 
+      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
+    ),
+    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: Yes to No",
+    # Political ideology
+    "Liberal to Conservative",
+    # Social views
+    "Trust in political institutions: None to Complete", "People should be more charitable: Agree to Disagree",
+    "Religious and worship service attendance: Multiple times a week to Never", "Importance of religion: Extremely to Not at all",
+    "Religion: Catholic to Atheist",
+    # Charity and voluntarism
+    "Importance of trusing charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",
+    "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: Yes to No", "Volunteer frequency: Weekly to Every few years",
+    "History of activism: Extreme to Never", "History of family activism: Extreme to Never", 
+    str_c(
+      c(
+        "Church or religious organization: ", "Sport or recreational organization: ", "Art, music, or educational organization: ",
+        "Labor union: ", "Political party: ", "Environmental organization: ", "Professional association: ", 
+        "Humanitarian or charitable organization: ", "Consumer organization: ", "Other organization: "
+      ), 
+      "Member to Not"
+    ),
+    # Demographics
+    "Gender: Male to Prefer not to say", "Marital status: Married to Never married", "Education: Less than high school to Doctorate",
+    "Income: Less than $10,000 to $300,000 or more",
+    str_c(
+      "Race/ethnicity: ", 
+      c("White", "Black or African American", "American Indian or Alaska Native", "Asian", "Native Hawaiian or Pacific Islander", "Other")
+    ),
+    "Age: Under 18 to 85 or older"
+  )
+}
 
+# Plot marginals
+if (intercept == 1) {
   draws %>% 
     mutate(
-    levels = factor(
-      i,
-      labels = level_labels
-    )
+      levels = factor(i, labels = level_labels)
     ) %>%
@@
     labs(y = "Attribute Levels")
+}
+if (intercept != 1) {
+  draws %>% 
+    filter(j != 1) %>% 
+    mutate(
+      levels = factor(i, labels = level_labels),
+      covariates = factor(j, labels = covariate_labels)
+    ) %>%
+    ggplot(aes(x = Theta, y = covariates)) + 
+    geom_halfeyeh(.width = .95) +
+    geom_vline(xintercept = 0, color = "grey") +
+    labs(y = "Attribute Levels") +
+    facet_wrap(~ levels, ncol = 5)
+}
 
 # Save plot
+if (intercept == 1) file_name <- paste("intercept_marginal-posteriors.png")
+if (public_affairs == 1) file_name <- paste("public-affairs_marginal-posteriors.png")
+if (political_ideology == 1) file_name <- paste("political-ideology_marginal-posteriors.png")
+if (social_views == 1) file_name <- paste("social-views_marginal-posteriors.png")
+if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_marginal-posteriors.png")
+if (demographics == 1) file_name <- paste("demographics_marginal-posteriors.png")
+if (public_political == 1) file_name <- paste("public-political_marginal-posteriors.png")
+if (public_political_social == 1) file_name <- paste("public-political-social_marginal-posteriors.png")
+if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_marginal-posteriors.png")
+if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_marginal-posteriors.png")
 ggsave(
-  "intercept_marginal-posteriors_noncentered.png",
+  file_name,
   path = here::here("analysis", "output", "figures"),
-  width = 12, height = 6, units = "in"
+  width = 20, height = 20, units = "in"
 )

### 2019-07-25 analysis/model-calibration.R

@@ -16,7 +16,7 @@ design <- read_csv(here::here("data", "derived_data", "dummy_design.csv")) %>%
   )
 
 intercept <- 0                            # Intercept-only.
-public_affairs <- 0                       # Public affairs: Public affairs knowledge + Public affairs activity.
+public_affairs <- 1                       # Public affairs: Public affairs knowledge + Public affairs activity.
 political_ideology <- 0                   # Political ideology.
 social_views <- 0                         # Social views: Public affairs trust + Social ideology + Religiosity.
 charity_voluntarism <- 0                  # Charity and voluntarism: Charity trust, Charity activity, Volunteer activity, etc.
@@ -24,7 +24,7 @@ demographics <- 0                         # Demographics: Gender, Marital status
 public_political <- 0                     # Public affairs + Political ideology
 public_political_social <- 0              # Public affairs + Political ideology + Social views
 public_political_social_charity <- 0      # Public affairs + Political ideology + Social views + Charity and voluntarism
-public_political_social_charity_demo <- 1 # Public affairs + Political ideology + Social views + Charity and voluntarism + Demographics
+public_political_social_charity_demo <- 0 # Public affairs + Political ideology + Social views + Charity and voluntarism + Demographics
 
 # Restructure choice data Y.
 Y <- final_data %>%

### 2019-07-27 analysis/model-calibration.R
Set up model runs with discretized covariates

@@ -16,7 +16,7 @@ design <- read_csv(here::here("data", "derived_data", "dummy_design.csv")) %>%
   )
 
 intercept <- 0                            # Intercept-only.
-public_affairs <- 1                       # Public affairs: Public affairs knowledge + Public affairs activity.
+public_affairs <- 0                       # Public affairs: Public affairs knowledge + Public affairs activity.
 political_ideology <- 0                   # Political ideology.
 social_views <- 0                         # Social views: Public affairs trust + Social ideology + Religiosity.
 charity_voluntarism <- 0                  # Charity and voluntarism: Charity trust, Charity activity, Volunteer activity, etc.
@@ -24,7 +24,7 @@ demographics <- 0                         # Demographics: Gender, Marital status
 public_political <- 0                     # Public affairs + Political ideology
 public_political_social <- 0              # Public affairs + Political ideology + Social views
 public_political_social_charity <- 0      # Public affairs + Political ideology + Social views + Charity and voluntarism
-public_political_social_charity_demo <- 0 # Public affairs + Political ideology + Social views + Charity and voluntarism + Demographics
+public_political_social_charity_demo <- 1 # Public affairs + Political ideology + Social views + Charity and voluntarism + Demographics
 
 # Restructure choice data Y.
 Y <- final_data %>%
@@ -74,7 +74,11 @@ if (public_affairs == 1) {
       final_data %>%
         select(Q2.1, Q2.2, Q2.3_1:Q2.3_7, Q2.4, Q5.7) %>%
         mutate_if(is.factor, as.integer) %>%
-        mutate_at(vars(contains("Q2.3")), coalesce, 0)
+        mutate_at(vars(contains("Q2.3")), coalesce, 0) %>%
+        mutate(
+          Q5.7_2 = if_else(Q5.7 == 2, 1, 0)
[…]

### 2019-07-30 analysis/model-calibration.R
Doubled the number of iterations

@@ -304,6 +304,7 @@ data <- list(
 fit <- stan(
   file = here::here("src", "stan_files", "hmnl_noncentered.stan"),
   data = data,
+  iter = 4000,
   seed = 42
 )
 run <- list(data = data, fit = fit)

### 2019-07-30 analysis/model-calibration.R
Testing mixing of the intercept-only model

@@ -15,7 +15,7 @@ design <- read_csv(here::here("data", "derived_data", "dummy_design.csv")) %>%
     alt = choice
   )
 
-intercept <- 0                            # Intercept-only.
+intercept <- 1                            # Intercept-only.
 public_affairs <- 0                       # Public affairs: Public affairs knowledge + Public affairs activity.
 political_ideology <- 0                   # Political ideology.
 social_views <- 0                         # Social views: Public affairs trust + Social ideology + Religiosity.
@@ -24,7 +24,7 @@ demographics <- 0                         # Demographics: Gender, Marital status
 public_political <- 0                     # Public affairs + Political ideology
 public_political_social <- 0              # Public affairs + Political ideology + Social views
 public_political_social_charity <- 0      # Public affairs + Political ideology + Social views + Charity and voluntarism
-public_political_social_charity_demo <- 1 # Public affairs + Political ideology + Social views + Charity and voluntarism + Demographics
+public_political_social_charity_demo <- 0 # Public affairs + Political ideology + Social views + Charity and voluntarism + Demographics
 
 # Restructure choice data Y.
 Y <- final_data %>%

### 2019-08-01 analysis/03_analysis.Rmd
HMC diagnostics, starting with intercept-only

@@
 ```{r load-data-output, warning=FALSE, message=FALSE}
-intercept <- 0                            # Intercept-only
-public_affairs <- 1                       # Public affairs
+intercept <- 1                            # Intercept-only
+public_affairs <- 0                       # Public affairs
 political_ideology <- 0                   # Political ideology
@@
 # Load and extract data and model output (see model-calibration.R)
-if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.RDS"))
+if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.rds"))
 if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
@@
 
+# Thetas
+draws_theta <- fit %>% 
+  extract(
+    pars = str_c("Theta[", 1:13, ",1]"),
+    inc_warmup = TRUE,
+    permuted = FALSE
+  )
+
+draws_theta %>% 
+  mcmc_hist_by_chain()
+
+draws_theta %>% 
+  mcmc_trace(
+    n_warmup = 2000,
+    facet_args = list(
+      nrow = 4, 
+      labeller = label_parsed
+    )
+  )
+
+# Extract the L_Omega parameters only and look at trace plots, etc.
+
+# L_Omega
+draws_L_Omega <- fit %>% 
+  extract(
+    regex_pars = c("L_Omega"),
+    inc_warmup = TRUE,
+    permuted = FALSE
+  )
+
+draws_theta %>% 
+  mcmc_hist_by_chain()
+
+draws_theta %>% 
+  mcmc_trace(
+    n_warmup = 2000,
+    facet_args = list(
+      nrow = 4, 
+      labeller = label_parsed
+    )
+  )
+
+# # Check diagnostics
+# check_all_diagnostics(fit)
+
 # Check for divergences
@@
 
-# # Check the effective sample size (not working for a hierarchical model?)
+# # Check the effective sample size (NOT WORKING?)
 # check_n_eff(fit)
 # 
-# # Check the Rhat statistic (not working for a hierarchical model?)
+# # Check the Rhat statistic (NOT WORKING?)
 # check_rhat(fit)
@@
 # Check trace plots (SUBSET?)
+color_scheme_set("mix-blue-red")
 fit %>%
@@
   mcmc_trace(
-    regex_pars = "Theta",
-    n_warmup = 1000,
+    pars = str_c("Theta[", 1:13, ",1]"),
+    n_warmup = 2000,
     facet_args = list(
-      nrow = round((data$L * data$C)/7), 
+      nrow = 2, 
       labeller = label_parsed
@@
   ungroup() %>% 
-  filter(.iteration > 500)
+  filter(.iteration > 1000)
 

### 2019-08-01 R/stan_utility.R

@@ -25,7 +25,7 @@ check_treedepth <- function(fit, max_depth = 10, quiet=FALSE) {
   if (!quiet)
     print(sprintf('%s of %s iterations saturated the maximum tree depth of %s (%s%%)',
                             n, N, max_depth, 100 * n / N))
-  
+
   if (n > 0) {
     if (!quiet) print('  Run again with max_treedepth set to a larger value to avoid saturation')
     if (quiet) return(FALSE)
@@ -67,6 +67,7 @@ check_n_eff <- function(fit, quiet=FALSE) {
   for (n in 1:N) {
     ratio <- fit_summary[,5][n] / iter
     if (ratio < 0.001) {
+    # if (is.nan(ratio) == FALSE & ratio < 0.001) {
       if (!quiet) print(sprintf('n_eff / iter for parameter %s is %s!',
                         rownames(fit_summary)[n], ratio))
       no_warning <- FALSE
@@ -114,7 +115,7 @@ check_all_diagnostics <- function(fit, quiet=FALSE) {
     check_energy(fit)
   } else {
     warning_code <- 0
-    
+
     if (!check_n_eff(fit, quiet=TRUE))
       warning_code <- bitwOr(warning_code, bitwShiftL(1, 0))
     if (!check_rhat(fit, quiet=TRUE))

### 2019-08-14 analysis/03_analysis.Rmd
Updated marginal posterior plots

@@
   ungroup() %>% 
-  filter(.iteration > 1000)
+  filter(.iteration > 500)
 
@@
 ```{r plot-marginals}
-intercept <- 0                            # Intercept-only
+intercept <- 1                            # Intercept-only
 public_affairs <- 0                       # Public affairs
@@
 public_political_social_charity <- 0      # + Charity and voluntarism
-public_political_social_charity_demo <- 1 # + Demographics
+public_political_social_charity_demo <- 0 # + Demographics
 
@@
     ),
-    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: Yes to No"
+    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No"
   )
@@
     "Religious and worship service attendance: Multiple times a week to Never", "Importance of religion: Extremely to Not at all",
-    "Religion: Catholic to Atheist"
+    str_c(
+      "Religion: ", 
+      c("Protestant", "Christian Orthodox", "Jewish", "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")
+    )
   )
@@
     "Importance of trusing charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",
-    "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: Yes to No", "Volunteer frequency: Weekly to Every few years",
+    "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: No", "Volunteer frequency: Weekly to Every few years",
     "History of activism: Extreme to Never", "History of family activism: Extreme to Never", 
@@
   covariate_labels <- c(
-    "Gender: Male to Prefer not to say", "Marital status: Married to Never married", "Education: Less than high school to Doctorate",
+    str_c(
+      "Gender: ", 
+      c("Female", "Transgender", "Prefer not to say", "Other")
+    ), 
+    str_c(
+      "Marital status: ", 
+      c("Widowed", "Divorced", "Separated", "Never married")
+    ), 
+    "Education: Less than high school to Doctorate",
     "Income: Less than $10,000 to $300,000 or more",
@@
     ),
-    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: Yes to No",
+    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No",
     # Political ideology
@@
     "Religious and worship service attendance: Multiple times a week to Never", "Importance of religion: Extremely to Not at all",
-    "Religion: Catholic to Atheist",
+    str_c(
+      "Religion: ", 
+      c("Protestant", "Christian Orthodox", "Jewish", "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")
+    ),
     # Charity and voluntarism
     "Importance of trusing charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",
-    "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: Yes to No", "Volunteer frequency: Weekly to Every few years",
+    "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: No", "Volunteer frequency: Weekly to Every few years",
     "History of activism: Extreme to Never", "History of family activism: Extreme to Never", 
@@
     # Demographics
-    "Gender: Male to Prefer not to say", "Marital status: Married to Never married", "Education: Less than high school to Doctorate",
+    str_c(
+      "Gender: ", 
+      c("Female", "Transgender", "Prefer not to say", "Other")
+    ), 
+    str_c(
+      "Marital status: ", 
+      c("Widowed", "Divorced", "Separated", "Never married")
+    ), 
+    "Education: Less than high school to Doctorate",
     "Income: Less than $10,000 to $300,000 or more",
@@
     geom_vline(xintercept = 0, color = "grey") +
-    labs(y = "Attribute Levels") +
+    labs(y = "Covariates") +
     facet_wrap(~ levels, ncol = 5)
@@
   path = here::here("analysis", "output", "figures"),
-  width = 20, height = 20, units = "in"
+  width = ifelse(intercept == 1, 12, 20), 
+  height = ifelse(sum(intercept, public_affairs, political_ideology, social_views, charity_voluntarism, demographics) == 1, 12, 20), 
+  units = "in"
 )

### 2019-08-14 analysis/model-calibration.R

@@ -15,7 +15,7 @@ design <- read_csv(here::here("data", "derived_data", "dummy_design.csv")) %>%
     alt = choice
   )
 
-intercept <- 1                            # Intercept-only.
+intercept <- 0                            # Intercept-only.
 public_affairs <- 0                       # Public affairs: Public affairs knowledge + Public affairs activity.
 political_ideology <- 0                   # Political ideology.
 social_views <- 0                         # Social views: Public affairs trust + Social ideology + Religiosity.
@@ -24,7 +24,7 @@ demographics <- 0                         # Demographics: Gender, Marital status
 public_political <- 0                     # Public affairs + Political ideology
 public_political_social <- 0              # Public affairs + Political ideology + Social views
 public_political_social_charity <- 0      # Public affairs + Political ideology + Social views + Charity and voluntarism
-public_political_social_charity_demo <- 0 # Public affairs + Political ideology + Social views + Charity and voluntarism + Demographics
+public_political_social_charity_demo <- 1 # Public affairs + Political ideology + Social views + Charity and voluntarism + Demographics
 
 # Restructure choice data Y.
 Y <- final_data %>%
@@ -304,7 +304,8 @@ data <- list(
 fit <- stan(
   file = here::here("src", "stan_files", "hmnl_noncentered.stan"),
   data = data,
-  iter = 4000,
+  iter = 10000,
+  thin = 5,
   seed = 42
 )
 run <- list(data = data, fit = fit)

### 2019-09-10 analysis/03_analysis.Rmd
Commented out plotting for now

@@
 
-# Save plot
-if (intercept == 1) file_name <- paste("intercept_marginal-posteriors.png")
-if (public_affairs == 1) file_name <- paste("public-affairs_marginal-posteriors.png")
-if (political_ideology == 1) file_name <- paste("political-ideology_marginal-posteriors.png")
-if (social_views == 1) file_name <- paste("social-views_marginal-posteriors.png")
-if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_marginal-posteriors.png")
-if (demographics == 1) file_name <- paste("demographics_marginal-posteriors.png")
-if (public_political == 1) file_name <- paste("public-political_marginal-posteriors.png")
-if (public_political_social == 1) file_name <- paste("public-political-social_marginal-posteriors.png")
-if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_marginal-posteriors.png")
-if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_marginal-posteriors.png")
-ggsave(
-  file_name,
-  path = here::here("analysis", "output", "figures"),
-  width = ifelse(intercept == 1, 12, 20), 
-  height = ifelse(sum(intercept, public_affairs, political_ideology, social_views, charity_voluntarism, demographics) == 1, 12, 20), 
-  units = "in"
-)
+# # Save plot
+# if (intercept == 1) file_name <- paste("intercept_marginal-posteriors.png")
+# if (public_affairs == 1) file_name <- paste("public-affairs_marginal-posteriors.png")
+# if (political_ideology == 1) file_name <- paste("political-ideology_marginal-posteriors.png")
+# if (social_views == 1) file_name <- paste("social-views_marginal-posteriors.png")
+# if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_marginal-posteriors.png")
+# if (demographics == 1) file_name <- paste("demographics_marginal-posteriors.png")
+# if (public_political == 1) file_name <- paste("public-political_marginal-posteriors.png")
+# if (public_political_social == 1) file_name <- paste("public-political-social_marginal-posteriors.png")
+# if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_marginal-posteriors.png")
+# if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_marginal-posteriors.png")
+# ggsave(
+#   file_name,
+#   path = here::here("analysis", "output", "figures"),
+#   width = ifelse(intercept == 1, 12, 20), 
+#   height = ifelse(sum(intercept, public_affairs, political_ideology, social_views, charity_voluntarism, demographics) == 1, 12, 20), 
+#   units = "in"
+# )
 ```

### 2019-09-18 analysis/03_analysis.Rmd
errors encountered loading packages

@@
 ```{r load-packages, warning=FALSE, message=FALSE}
+#install.packages("donorheuristics")
+# Error: package ‘donorheuristics’ is not available (for R version 3.6.1)
+#install.packages("rstan")
+#install.packages("bayesplot")
+#install.packages("tidybayes")
+#install.packages("bayesm")
+#install.packages("ggridges")
+#install.packages("ggraph")
+#install.packages("ggdag")
+#install.packages("here")
+
 library(tidyverse)
@@
 source(here("analysis", "options.R"))
+
+# giving me the error: "Error in loadNamespace(name) : there is no package called ‘pander’"
 
@@
 ```{r plot-marginals}
-intercept <- 1                            # Intercept-only
+intercept <- 0                            # Intercept-only
 public_affairs <- 0                       # Public affairs
 political_ideology <- 0                   # Political ideology
-social_views <- 0                         # Social views
+social_views <- 1                         # Social views
 charity_voluntarism <- 0                  # Charity and voluntarism
@@
     ggplot(aes(x = Theta, y = covariates)) + 
+    # what other geoms could we use
+    # how to filter to zoom in on a certain part of the graph
     geom_halfeyeh(.width = .95) +

### 2019-09-19 analysis/03_analysis.Rmd
Experimenting with geom_ridgeline for marginal posterior visualizations

--- 2019-09-10 analysis/03_analysis.Rmd
@@
 ```{r load-packages, warning=FALSE, message=FALSE}
+#install.packages("donorheuristics")
+# overcame error through library(bookdown), library(devtools), library(pander)
+#install.packages("rstan")
+#install.packages("bayesplot")
+#install.packages("tidybayes")
+#install.packages("bayesm")
+#install.packages("ggridges")
+#install.packages("ggraph")
+#install.packages("ggdag")
+#install.packages("here")
+
 library(tidyverse)
@@
   geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
-  scale_dag() +
+  scale_adjusted() +
   theme_ngo() +
@@
 ```{r load-data-output, warning=FALSE, message=FALSE}
-intercept <- 1                            # Intercept-only
-public_affairs <- 0                       # Public affairs
+intercept <- 0                           # Intercept-only
+public_affairs <- 1                       # Public affairs
 political_ideology <- 0                   # Political ideology
@@
 ```{r plot-marginals}
-intercept <- 1                            # Intercept-only
+intercept <- 0                            # Intercept-only
 public_affairs <- 0                       # Public affairs
-political_ideology <- 0                   # Political ideology
+political_ideology <- 1                   # Political ideology
 social_views <- 0                         # Social views
@@
     ) %>%
-    ggplot(aes(x = Theta, y = covariates)) + 
-    geom_halfeyeh(.width = .95) +
+    ggplot(aes(x = Theta, y = covariates, height = Theta)) + 
+    # what other geoms could we use
+    # - geom_ridgeline
+    geom_ridgeline(fill="lightblue") +
+    # - geom_density_ridges
+    # - geom_halfeyeh
+    # geom_halfeyeh(.width = .95) +
     geom_vline(xintercept = 0, color = "grey") +
@@
 }
+
+# Notes to self:
+# how to filter to zoom in on a certain part of the graph
+# load the rethinking package and use the draws and summarize them
+# we have the draws, sum/distribution of counts of samples of the posterior
 

### 2019-09-19 analysis/03_analysis.Rmd
Experimenting with geom_density_ridges for marginal posterior visualizations

@@
 public_affairs <- 0                       # Public affairs
-political_ideology <- 1                   # Political ideology
-social_views <- 0                         # Social views
+political_ideology <- 0                   # Political ideology
+social_views <- 1                         # Social views
 charity_voluntarism <- 0                  # Charity and voluntarism
@@
     ) %>%
-    ggplot(aes(x = Theta, y = covariates, height = Theta)) + 
+    ggplot(aes(x = Theta, y = covariates)) + 
     # what other geoms could we use
-    # - geom_ridgeline
-    geom_ridgeline(fill="lightblue") +
-    # - geom_density_ridges
-    # - geom_halfeyeh
+    # geom_ridgeline(fill="lightblue") +
+    geom_density_ridges() +
+    # geom_density_ridges2
+    # geom_density_ridges_gradient
     # geom_halfeyeh(.width = .95) +

### 2019-09-19 analysis/03_analysis.Rmd
Updating visualizations and working on ggridges code.

@@
      geom_density_ridges() +
-    # geom_density_ridges2
+    # geom_density_ridges2 - includes bottom line
+    # geom_density_ridges(rel_min_height = 0.01) - shortens tails
     # geom_density_ridges_gradient

### 2019-09-20 analysis/03_analysis.Rmd
Visualize using geom_density_ridges.

--- 2019-09-19 analysis/03_analysis.Rmd
@@
 public_affairs <- 0                       # Public affairs
-political_ideology <- 1                   # Political ideology
+political_ideology <- 0                   # Political ideology
 social_views <- 0                         # Social views
 charity_voluntarism <- 0                  # Charity and voluntarism
-demographics <- 0                         # Demographics
+demographics <- 1                         # Demographics
 public_political <- 0                     # Public affairs + Political ideology
@@
 }
+# zoom in on a certain part of the graph
 if (intercept != 1) {
@@
     ) %>%
-    ggplot(aes(x = Theta, y = covariates, height = Theta)) + 
-    # what other geoms could we use
-    # - geom_ridgeline
-    geom_ridgeline(fill="lightblue") +
-    # - geom_density_ridges
-    # - geom_halfeyeh
+    ggplot(aes(x = Theta, y = covariates)) +
+# 1. geom_ridgeline 
+    # geom_ridgeline(fill = "blue") +
+# 2. geom_density_ridges seems to be the better option for overlapping distributions.
+    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.001) +
+        # geom_density_ridges(scale = 3) - control overlap
+        # geom_density_ridges2 - includes bottom line
+        # geom_density_ridges(rel_min_height = 0.01) - shortens tails
     # geom_halfeyeh(.width = .95) +
-    geom_vline(xintercept = 0, color = "grey") +
+    geom_vline(xintercept = 0, color = "white") +
     labs(y = "Covariates") +
@@
 # Notes to self:
-# how to filter to zoom in on a certain part of the graph
+
 # load the rethinking package and use the draws and summarize them

### 2019-09-24 analysis/03_analysis.Rmd
Done using 03_analysis for posterior visualizations -- moving to Hypotheses R Markdown

--- 2019-09-19 analysis/03_analysis.Rmd
@@
 ```{r load-packages, warning=FALSE, message=FALSE}
-#install.packages("donorheuristics")
-# overcame error through library(bookdown), library(devtools), library(pander)
-#install.packages("rstan")
-#install.packages("bayesplot")
-#install.packages("tidybayes")
-#install.packages("bayesm")
-#install.packages("ggridges")
-#install.packages("ggraph")
-#install.packages("ggdag")
-#install.packages("here")
-
 library(tidyverse)
@@
 ```{r plot-marginals}
-intercept <- 0                            # Intercept-only
+intercept <- 1                            # Intercept-only
 public_affairs <- 0                       # Public affairs
 political_ideology <- 0                   # Political ideology
-social_views <- 1                         # Social views
+social_views <- 0                         # Social views
 charity_voluntarism <- 0                  # Charity and voluntarism
@@
     ggplot(aes(x = Theta, y = levels)) + 
-    geom_halfeyeh(.width = .95) +
+    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+    # geom_halfeyeh(.width = .95) +
     geom_vline(xintercept = 0, color = "grey") +
@@
 }
+
 if (intercept != 1) {
@@
     ggplot(aes(x = Theta, y = covariates)) +
-    # what other geoms could we use
-    # geom_ridgeline(fill="lightblue") +
-    geom_density_ridges() +
-    # geom_density_ridges2
-    # geom_density_ridges_gradient
+       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
        # geom_halfeyeh(.width = .95) +
-    geom_vline(xintercept = 0, color = "grey") +
+       geom_vline(xintercept = 0, color = "white") +
        labs(y = "Covariates") +
@@
 }
-
-# Notes to self:
-# how to filter to zoom in on a certain part of the graph
-# load the rethinking package and use the draws and summarize them
-# we have the draws, sum/distribution of counts of samples of the posterior
 

### 2019-09-24 analysis/output/figures/Marginal Posterior Visualizations/Hypotheses.Rmd
Creating R Markdown to show posterior visualizations for hypotheses stated in the paper.

--- 2019-09-24 analysis/03_analysis.Rmd
@@
 ---
-title: "Results"
-author: "Andrew Heiss, Marc Dotson, and Suparna Chaudhry"
-date: "Last run: `r format(Sys.time(), '%F')`"
-output: 
-  html_document:
-    code_folding: hide
-    pandoc_args:
-      - "--default-image-extension=png"
-editor_options: 
-  chunk_output_type: console
+title: "Hypothesis Testing"
+output: github_document
 ---
 
-# Load packages
+The purpose of this R Markdown is to visualize the results to the hypotheses proposed at the beginning of the paper.
 
@@
 library(here)
-
-# General settings
-source(here("analysis", "options.R"))
-
-# Make all the randomness reproducible
-set.seed(1234)
 ```
 
-# Causal pathway
-
-Our theory and hypotheses are laid out in the causal pathway below.
-Organizational factors (**O**, or organizational practices like financial disclosure and accountability practices; **I**, or issue area; and **F**, or funding) all influence the decision to donate (**D**).
-Structural factors like an NGO's relationship with its host government (**G**) also influence donation behavior, but the relationship itself is shaped by both funding and issue area.
-
-```{r causal-dag, fig.width=13/3, fig.height=2}
-node_colors <- tribble(
-  ~name, ~type,
-  "D", "Outcome",
-  "I", "Organizational factor",
-  "F", "Organizational factor",
-  "O", "Organizational factor",
-  "G", "Structural factor"
-)
-
-# Set up DAG structure
-theory_dag <- dagify(D ~ I + F + O + G,
-                     G ~ I + F,
-                     outcome = "D",
-                     exposure = "C") %>% 
-  tidy_dagitty(layout = "dh", seed = 1234)
-
-# Add node types/colors to DAG data
-theory_dag$data <- theory_dag$data %>% 
-  left_join(node_colors, by = "name")
-
-# Make DAG plot
-plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
-  geom_dag_point(size = 6, mapping = aes(color = type)) +
-  geom_dag_edges(start_cap = circle(4, "mm"),
-                 end_cap = circle(4, "mm")) +
-  geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
-  scale_adjusted() +
-  theme_ngo() +
-  theme(panel.grid = element_blank(),
-        panel.border = element_blank(),
-        axis.title = element_blank(),
-        axis.text = element_blank())
-
-# Show and save plot
-plot_dag
-ggsave(plot_dag, filename = here("analysis", "output", "figures", "causal-path.pdf"),
-       width = 13/3, height = 2, units = "in", device = cairo_pdf)
-ggsave(plot_dag, filename = here("analysis", "output", "figures", "causal-path.png"),
-       width = 13/3, height = 2, units = "in", type = "cairo", dpi = 300)
-```
-
-# Load data and model output
-
-```{r load-data-output, warning=FALSE, message=FALSE}
-intercept <- 0                           # Intercept-only
-public_affairs <- 1                       # Public affairs
-political_ideology <- 0                   # Political ideology
-social_views <- 0                         # Social views
-charity_voluntarism <- 0                  # Charity and voluntarism
-demographics <- 0                         # Demographics
-public_political <- 0                     # Public affairs + Political ideology
-public_political_social <- 0              # + Social views
-public_political_social_charity <- 0      # + Charity and voluntarism
-public_political_social_charity_demo <- 0 # + Demographics
-
-# Load and extract data and model output (see model-calibration.R)
-if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.rds"))
-if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
-if (political_ideology == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
-if (social_views == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
-if (charity_voluntarism == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
-if (demographics == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
-if (public_political == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
-if (public_political_social == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
-if (public_political_social_charity == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
-if (public_political_social_charity_demo == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
-data <- run$data
-fit <- run$fit
-```
-
-# Model checking
-
-```{r model-checking}
-source(here::here("R", "stan_utility.R"))
-
-# Thetas
-draws_theta <- fit %>% 
-  extract(
-    pars = str_c("Theta[", 1:13, ",1]"),
-    inc_warmup = TRUE,
-    permuted = FALSE
-  )
-
-draws_theta %>% 
-  mcmc_hist_by_chain()
-
-draws_theta %>% 
-  mcmc_trace(
-    n_warmup = 2000,
-    facet_args = list(
-      nrow = 4, 
-      labeller = label_parsed
-    )
-  )
-
-# Extract the L_Omega parameters only and look at trace plots, etc.
-
-# L_Omega
-draws_L_Omega <- fit %>% 
-  extract(
-    regex_pars = c("L_Omega"),
-    inc_warmup = TRUE,
-    permuted = FALSE
-  )
-
-draws_theta %>% 
-  mcmc_hist_by_chain()
-
-draws_theta %>% 
-  mcmc_trace(
-    n_warmup = 2000,
-    facet_args = list(
-      nrow = 4, 
-      labeller = label_parsed
-    )
-  )
-
-# # Check diagnostics
-# check_all_diagnostics(fit)
-
-# Check for divergences
-check_div(fit)
-
-# # Check the effective sample size (NOT WORKING?)
-# check_n_eff(fit)
-# 
-# # Check the Rhat statistic (NOT WORKING?)
-# check_rhat(fit)
-
-# Check trace plots (SUBSET?)
-color_scheme_set("mix-blue-red")
-fit %>%
-  extract(
-    inc_warmup = TRUE,
-    permuted = FALSE
-  ) %>%
-  mcmc_trace(
-    pars = str_c("Theta[", 1:13, ",1]"),
-    n_warmup = 2000,
-    facet_args = list(
-      nrow = 2, 
-      labeller = label_parsed
-    )
-  )
-
-# ggsave(
-#   "intercept_trace_noncentered.png",
-#   path = here::here("analysis", "output", "figures"),
-#   width = 12, height = 6, units = "in"
-# )
-```
-
-# Extract draws
-
-```{r extract-draws}
-# Extract posterior draws
-draws <- fit %>% 
-  spread_draws(Theta[i, j]) %>% 
-  ungroup() %>% 
-  filter(.iteration > 500)
-
-# Save draws
-if (intercept == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept_noncentered.rds"))
-if (public_affairs == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))
-if (political_ideology == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "political_ideology.rds"))
-if (social_views == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "social_views.rds"))
-if (charity_voluntarism == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds"))
-if (demographics == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "demographics.rds"))
-if (public_political == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political.rds"))
-if (public_political_social == 1)  write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social.rds"))
-if (public_political_social_charity == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds"))
-if (public_political_social_charity_demo == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity_demo.rds"))
-```
-
-# Plot marginals
-
+Run this code below to specify the covariate.
 ```{r plot-marginals}
@@
 
+```
+
+#### Do donors care if nonprofits they care about are criticized by or kicked out of the countries they work in?
+
+```{r}
 # Plot marginals
@@
     ) %>%
+    filter(levels == str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))) %>% 
     ggplot(aes(x = Theta, y = levels)) + 
     geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
-    # geom_halfeyeh(.width = .95) +
     geom_vline(xintercept = 0, color = "grey") +
@@
 }
-
 if (intercept != 1) {
@@
        geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
-       # geom_halfeyeh(.width = .95) +
        geom_vline(xintercept = 0, color = "white") +
@@
 
-# # Save plot
-# if (intercept == 1) file_name <- paste("intercept_marginal-posteriors.png")
-# if (public_affairs == 1) file_name <- paste("public-affairs_marginal-posteriors.png")
-# if (political_ideology == 1) file_name <- paste("political-ideology_marginal-posteriors.png")
-# if (social_views == 1) file_name <- paste("social-views_marginal-posteriors.png")
-# if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_marginal-posteriors.png")
-# if (demographics == 1) file_name <- paste("demographics_marginal-posteriors.png")
-# if (public_political == 1) file_name <- paste("public-political_marginal-posteriors.png")
-# if (public_political_social == 1) file_name <- paste("public-political-social_marginal-posteriors.png")
-# if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_marginal-posteriors.png")
-# if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_marginal-posteriors.png")
-# ggsave(
-#   file_name,
-#   path = here::here("analysis", "output", "figures"),
-#   width = ifelse(intercept == 1, 12, 20), 
-#   height = ifelse(sum(intercept, public_affairs, political_ideology, social_views, charity_voluntarism, demographics) == 1, 12, 20), 
-#   units = "in"
-# )
 ```
 
-# Original computing environment
+#### Do managerial practices (financial transparency and accountability systems), funding sources (private donations and government grants), and issue areas (emergency response, environmental issues, human rights, and refugee relief) also serve as heuristics that signal an organization’s deservingness to donors?
 
-<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>
+```{r}
 
-<div id="sessioninfo" class="collapse">
-
-```{r show-session-info, echo=TRUE, width=100}
-writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))
-
-devtools::session_info()
 ```
 
-</div>
+# Hypotheses:
+# We theorize that structural characteristics like an NGO’s host-country political and legal environment can serve as heuristics and shortcuts for donors.
+# Donors who see that an NGO faces general legal trouble abroad will use that knowledge to decide whether or not to donate.
+# We also theorize that non-structural organizational characteristics like managerial practices, funding sources, and issue area also serve as heuristics and influence donation patterns.
+# In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics.
+We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we’re unsure of the direction of that effect.

### 2019-09-24 analysis/output/figures/Marginal Posterior Visualizations/Hypotheses.Rmd
Adding graphs to Markdown.

@@
 ---
-title: "Hypothesis Testing"
+title: "Hypotheses"
 output: github_document
@@
 
-```{r load-packages, warning=FALSE, message=FALSE}
+```{r load-packages, warning = FALSE, message = FALSE, echo = FALSE}
 library(tidyverse)
@@
 
-Run this code below to specify the covariate.
-```{r plot-marginals}
+```{r plot-marginals, echo = FALSE}
+# Specify the covariate.
 intercept <- 1                            # Intercept-only
@@
 
-```{r}
+```{r echo = FALSE}
 # Plot marginals
@@
     ggplot(aes(x = Theta, y = levels)) + 
-    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+    geom_density_ridges(scale = 5, height = 1, rel_min_height = 0.01) +
     geom_vline(xintercept = 0, color = "grey") +
@@
 
+#### 1. Managerial Practices
+
+```{r echo = FALSE}
+# Plot marginals
+if (intercept == 1) {
+  draws %>% 
+    mutate(
+      levels = factor(i, labels = level_labels)
+    ) %>%
+    filter(levels == c( "Financial transparency: Yes",
+  "Accountability: Yes")) %>% 
+    ggplot(aes(x = Theta, y = levels)) + 
+    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+    geom_vline(xintercept = 0, color = "grey") +
+    labs(y = "Attribute Levels")
+}
+if (intercept != 1) {
+  draws %>% 
+    filter(j != 1) %>% 
+    mutate(
+      levels = factor(i, labels = level_labels), 
+      covariates = factor(j, labels = covariate_labels)  
+    ) %>%
+    ggplot(aes(x = Theta, y = covariates)) +
+       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+       geom_vline(xintercept = 0, color = "white") +
+       labs(y = "Covariates") +
+       facet_wrap(~ levels, ncol = 5)
+}
+```
+
+#### 2. Funding Sources
+```{r echo = FALSE}
+# Plot marginals
+if (intercept == 1) {
+  draws %>% 
+    mutate(
+      levels = factor(i, labels = level_labels)
+    ) %>%
+    filter(levels ==   str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants"))) %>% 
+    ggplot(aes(x = Theta, y = levels)) + 
+    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+    geom_vline(xintercept = 0, color = "grey") +
+    labs(y = "Attribute Levels")
+}
+if (intercept != 1) {
+  draws %>% 
+    filter(j != 1) %>% 
+    mutate(
+      levels = factor(i, labels = level_labels), 
+      covariates = factor(j, labels = covariate_labels)  
+    ) %>%
+    ggplot(aes(x = Theta, y = covariates)) +
+       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+       geom_vline(xintercept = 0, color = "white") +
+       labs(y = "Covariates") +
+       facet_wrap(~ levels, ncol = 5)
+}
+```
+
+#### 3. Issue Areas
+
+```{r echo = FALSE}
+# Plot marginals
+if (intercept == 1) {
+  draws %>% 
+    mutate(
+      levels = factor(i, labels = level_labels)
+    ) %>%
+    filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>% 
+    ggplot(aes(x = Theta, y = levels, fill = levels)) + 
+    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+    geom_vline(xintercept = 0, color = "grey") +
+    labs(y = "Attribute Levels")
+}
+if (intercept != 1) {
+  draws %>% 
+    filter(j != 1) %>% 
+    mutate(
+      levels = factor(i, labels = level_labels), 
+      covariates = factor(j, labels = covariate_labels)  
+    ) %>%
+    ggplot(aes(x = Theta, y = covariates)) +
+       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+       geom_vline(xintercept = 0, color = "white") +
+       labs(y = "Covariates") +
+       facet_wrap(~ levels, ncol = 5)
+}
+
+```
+
+#### We theorize that structural characteristics like an NGO’s host-country political and legal environment can serve as heuristics and shortcuts for donors.
+
+#### Donors who see that an NGO faces general legal trouble abroad will use that knowledge to decide whether or not to donate.
 ```{r}
@@
 
-# Hypotheses:
-# We theorize that structural characteristics like an NGO’s host-country political and legal environment can serve as heuristics and shortcuts for donors.
-# Donors who see that an NGO faces general legal trouble abroad will use that knowledge to decide whether or not to donate.
-# We also theorize that non-structural organizational characteristics like managerial practices, funding sources, and issue area also serve as heuristics and influence donation patterns.
-# In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics.
+#### We also theorize that non-structural organizational characteristics like managerial practices, funding sources, and issue area also serve as heuristics and influence donation patterns.
+
+```{r}
+
+```
+
+#### In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics.
 We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we’re unsure of the direction of that effect.

### 2019-09-26 analysis/output/figures/Marginal Posterior Visualizations/Hypotheses.Rmd
Working on the four basic plots. Need to figure out how to specify different covariates.

--- 2019-09-24 analysis/output/figures/Marginal Posterior Visualizations/Hypotheses.Rmd
@@
 
+#### In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics.
+We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we’re unsure of the direction of that effect.
+
+```{r overall, echo = FALSE, warning = FALSE}
+# Plot marginals
+if (intercept == 1) {
+  draws %>% 
+    mutate(
+      levels = factor(i, labels = level_labels)
+    ) %>%
+   # filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>% 
+    ggplot(aes(x = Theta, y = levels)) + 
+    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+    geom_vline(xintercept = 0, color = "white") +
+    labs(y = "Attribute Levels")
+}
+if (intercept != 1) {
+  draws %>% 
+    filter(j != 1) %>% 
+    mutate(
+      levels = factor(i, labels = level_labels), 
+      covariates = factor(j, labels = covariate_labels)  
+    ) %>%
+    ggplot(aes(x = Theta, y = covariates)) +
+       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+       geom_vline(xintercept = 0, color = "white") +
+       labs(y = "Covariates") +
+       facet_wrap(~ levels, ncol = 5)
+}
+```
+
 #### Do donors care if nonprofits they care about are criticized by or kicked out of the countries they work in?
 
-```{r}
+We theorize that structural characteristics like an NGO’s host-country political and legal environment can serve as heuristics and shortcuts for donors.
+Donors who see that an NGO faces general legal trouble abroad will use that knowledge to decide whether or not to donate.
+
+```{r relationship-with-gov, echo = FALSE}
 # Plot marginals
@@
 
-```{r}
+We theorize that non-structural organizational characteristics like managerial practices, funding sources, and issue area also serve as heuristics and influence donation patterns.
+
+#### 1. Managerial Practices
+
+```{r managerial-practices, echo = FALSE}
+# Plot marginals
+if (intercept == 1) {
+  draws %>% 
+    mutate(
+      levels = factor(i, labels = level_labels)
+    ) %>%
+    filter(levels == c( "Financial transparency: Yes",
+  "Accountability: Yes")) %>% 
+    ggplot(aes(x = Theta, y = levels)) + 
+    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+    geom_vline(xintercept = 0, color = "white") +
+    labs(y = "Attribute Levels")
+}
+if (intercept != 1) {
+  draws %>% 
+    filter(j != 1) %>% 
+    mutate(
+      levels = factor(i, labels = level_labels), 
+      covariates = factor(j, labels = covariate_labels)  
+    ) %>%
+    ggplot(aes(x = Theta, y = covariates)) +
+       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+       geom_vline(xintercept = 0, color = "white") +
+       labs(y = "Covariates") +
+       facet_wrap(~ levels, ncol = 5)
+}
+```
+
+#### 2. Funding Sources
+```{r funding_sources, echo = FALSE}
+# Plot marginals
+if (intercept == 1) {
+  draws %>% 
+    mutate(
+      levels = factor(i, labels = level_labels)
+    ) %>%
+    filter(levels ==   str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants"))) %>% 
+    ggplot(aes(x = Theta, y = levels)) + 
+    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+    geom_vline(xintercept = 0, color = "white") +
+    labs(y = "Attribute Levels")
+}
+if (intercept != 1) {
+  draws %>% 
+    filter(j != 1) %>% 
+    mutate(
+      levels = factor(i, labels = level_labels), 
+      covariates = factor(j, labels = covariate_labels)  
+    ) %>%
+    ggplot(aes(x = Theta, y = covariates)) +
+       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+       geom_vline(xintercept = 0, color = "white") +
+       labs(y = "Covariates") +
+       facet_wrap(~ levels, ncol = 5)
+}
+```
+
+#### 3. Issue Areas
+
+```{r issue-areas, echo = FALSE, warning = FALSE}
+# Plot marginals
+if (intercept == 1) {
+  draws %>% 
+    mutate(
+      levels = factor(i, labels = level_labels)
+    ) %>%
+    filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>% 
+    ggplot(aes(x = Theta, y = levels, fill = levels)) + 
+    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+    geom_vline(xintercept = 0, color = "white") +
+    labs(y = "Attribute Levels")
+}
+if (intercept != 1) {
+  draws %>% 
+    filter(j != 1) %>% 
+    mutate(
+      levels = factor(i, labels = level_labels), 
+      covariates = factor(j, labels = covariate_labels)  
+    ) %>%
+    ggplot(aes(x = Theta, y = covariates)) +
+       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+       geom_vline(xintercept = 0, color = "white") +
+       labs(y = "Covariates") +
+       facet_wrap(~ levels, ncol = 5)
+}
 
 ```
-
-# Hypotheses:
-# We theorize that structural characteristics like an NGO’s host-country political and legal environment can serve as heuristics and shortcuts for donors.
-# Donors who see that an NGO faces general legal trouble abroad will use that knowledge to decide whether or not to donate.
-# We also theorize that non-structural organizational characteristics like managerial practices, funding sources, and issue area also serve as heuristics and influence donation patterns.
-# In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics.
-We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we’re unsure of the direction of that effect.

### 2019-09-27 analysis/output/figures/Marginal Posterior Visualizations/Hypotheses.Rmd
Updating R Markdown to include plots of all attribute levels.

@@
 title: "Hypotheses"
+date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
 output: github_document
 ---
-
-The purpose of this R Markdown is to visualize the results to the hypotheses proposed at the beginning of the paper.
+In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics.
+We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we’re unsure of the direction of that effect.
 
@@
 
-#### In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics.
-We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we’re unsure of the direction of that effect.
+### Combined Results
 
-```{r overall, echo = FALSE, warning = FALSE}
-# Plot marginals
+```{r combined-results, echo = FALSE, warning = FALSE}
+
 if (intercept == 1) {
@@
     ggplot(aes(x = Theta, y = levels)) + 
+    # error.bars() +
     geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
@@
 
-#### Do donors care if nonprofits they care about are criticized by or kicked out of the countries they work in?
+### Relationship With Host Government
 
@@
 
-#### Do managerial practices (financial transparency and accountability systems), funding sources (private donations and government grants), and issue areas (emergency response, environmental issues, human rights, and refugee relief) also serve as heuristics that signal an organization’s deservingness to donors?
+### Organizational Characteristics
 
@@
     geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
-    geom_vline(xintercept = 0, color = "white") +
+    geom_vline(xintercept = 0, color = "grey") +
     labs(y = "Attribute Levels")
@@
     filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>% 
-    ggplot(aes(x = Theta, y = levels, fill = levels)) + 
+    ggplot(aes(x = Theta, y = levels)) + 
     geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
-    geom_vline(xintercept = 0, color = "white") +
+    geom_vline(xintercept = 0, color = "grey") +
     labs(y = "Attribute Levels")
@@
 ```
+### Organization
+```{r organization, echo = FALSE, warning = FALSE}
+# Plot marginals
+if (intercept == 1) {
+  draws %>% 
+    mutate(
+      levels = factor(i, labels = level_labels)
+    ) %>%
+    filter(levels == str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"))) %>% 
+    ggplot(aes(x = Theta, y = levels)) + 
+    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+    geom_vline(xintercept = 0, color = "grey") +
+    labs(y = "Attribute Levels")
+}
+if (intercept != 1) {
+  draws %>% 
+    filter(j != 1) %>% 
+    mutate(
+      levels = factor(i, labels = level_labels), 
+      covariates = factor(j, labels = covariate_labels)  
+    ) %>%
+    ggplot(aes(x = Theta, y = covariates)) +
+       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+       geom_vline(xintercept = 0, color = "white") +
+       labs(y = "Covariates") +
+       facet_wrap(~ levels, ncol = 5)
+}
+
+```

### 2019-09-27 analysis/output/figures/Marginal Posterior Visualizations/Hypotheses.Rmd
Updating code for Hypotheses R Markdown.

@@
 title: "Hypotheses"
-date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
-output: github_document
+author: "Andrew Heiss, Marc Dotson, and Suparna Chaudhry"
+date: "Last run: `r format(Sys.time(), '%F')`"
+output: 
+  html_document:
+    code_folding: hide
+    pandoc_args:
+      - "--default-image-extension=png"
+editor_options: 
+  chunk_output_type: console
 ---

### 2019-10-01 manuscript/manuscript.Rmd
Organizing plots into right folder to add to manuscript.Rmd
Added plots into marginal.Rmd with interpretations.

@@
 ![Causal diagram showing causes of donor behavior.
-D = donation to NGO (outcome); G = NGO-government relationship, I = NGO issue area, F = NGO funding source, O = NGO organizational and managerial practices.](output/figures/causal-path-full.pdf){#fig:big-dag}
+D = donation to NGO (outcome); G = NGO-government relationship, I = NGO issue area, F = NGO funding source, O = NGO organizational and managerial practices.](output/figures/causal-path.pdf){#fig:big-dag}
 
@@
 - First set of questions (hypotheses) can be answered using the results of the intercept-only model.
+
+![Combined Results](output/figures/combined-results.png)
+We hypothesized that each of these structural and organizational characteristics would have a significant effect on donor behavior, though we were unsure of the direction of that effect.
+
+The following plots zoom in on how strongly each of the attributes serve as heuristics.
+
+![Relationship With Host Government](output/figures/relationship-with-gov.png)
+Donors are less likely to donate when government is under crackdown than when it is criticized. In both cases, there is a clear negative effect.
+
+![Organizational Characteristics: Managerial Practices](output/figures/managerial-practices.png)
+Donors are more likely to donate when organizations are accountable and financially transparent.
+
+![Organizational Characteristics: Funding Sources](output/figures/funding-sources.png)
+Donors are less likely to donate when an NGO is subsidized by government grants, and even less likely when an NGO is funded by a few private donors.
+(look further into demographic info to see if there is any explanation or insight there)
+
+![Organizational Characteristics: Issue Areas](output/figures/issue-areas.png)
+* Emergency response is mentioned in Hypothesis but isn't included in plot?
+Issue Areas
+
+![Organization](output/figures/organization.png)
+All organizations were percieved positively by respondents. The Red Cross was significantly more favored.
+
 - Second set of questions (confirmatory) can be answered using the following upper-level models:

### 2019-10-03 analysis/output/figures/hypotheses/Hypotheses.Rmd
Generated plots for second set of questions using hypotheses.Rmd

--- 2019-09-27 analysis/output/figures/Marginal Posterior Visualizations/Hypotheses.Rmd
@@
 # Specify the covariate.
-intercept <- 1                            # Intercept-only
+intercept <- 0                            # Intercept-only
 public_affairs <- 0                       # Public affairs
@@
 public_political_social_charity <- 0      # + Charity and voluntarism
-public_political_social_charity_demo <- 0 # + Demographics
+public_political_social_charity_demo <- 1 # + Demographics
 
@@
     ggplot(aes(x = Theta, y = levels)) + 
-    # error.bars() +
     geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
@@
        labs(y = "Covariates") +
-       facet_wrap(~ levels, ncol = 5)
+       facet_wrap(~ levels, ncol = 7)
 }
@@
     ) %>%
+    filter(covariates == c("Follow national news: Multiple times a day to Never", "Follow international news: Always to Never")) %>% 
     ggplot(aes(x = Theta, y = covariates)) +

### 2019-10-03 manuscript/manuscript.Rmd
Generated plots for second set of questions using hypotheses.Rmd

--- 2019-06-20 manuscript/manuscript.Rmd
@@
 We will field our larger conjoint survey experiment very soon and we look forward to your comments and suggestions before we launch it!
+
+# Methods
+
+# Results
+
+- First set of questions (hypotheses) can be answered using the results of the intercept-only model.
+
+We hypothesized that each of these structural and organizational characteristics would have a significant effect on donor behavior, though we were unsure of the direction of that effect.
+
+![Combined Results](output/figures/combined-results.png)
+
+The following plots zoom in on the strength of the effects that these characteristics have.
+
+Compared to when an NGO has a friendly relationship with the host government, donors are much less likely to donate when government is under crackdown or criticized.
+
+![Relationship With Host Government](output/figures/relationship-with-gov.png)
+
+Donors are more likely to donate when organizations are accountable and financially transparent.
+
+![Organizational Characteristics: Managerial Practices](output/figures/managerial-practices.png)
+
+Donors are most likely to donate when an NGO is funded primarily by many small private donations.
+Donors are less likely to donate when the organization is subsidized by government grants, and even less likely when it is funded by a few private donors.
+
+![Organizational Characteristics: Funding Sources](output/figures/funding-sources.png)
+
+Of all issue areas, donations to emergency response were most likely, followed by human rights and then environment. Refugee relief was the least likely issue area to be donated to.
+
+![Organizational Characteristics: Issue Areas](output/figures/issue-areas.png)
+
+All organizations were positively percieved by respondents. The Red Cross was significantly more favored.
+
+![Organization](output/figures/organization.png)
+
+- Second set of questions (confirmatory) can be answered using the following upper-level models:
+  - Public affairs: `Donation preferences ~ Public affairs knowledge + Public affairs activity`
+![](output/figures/public-affairs.png)
+
+  - Political ideology: `Donation preferences ~ Political ideology`
+
+![](output/figures/political-ideology.png)
+
+  - Social views: `Donation preferences ~ Public affairs trust + Social ideology + Religiosity`
+
+  ![](output/figures/social-views.png)
+
+  - Charity and voluntarism: `Donation preferences ~ Charity trust + Charity activity + Volunteer activity + Activism activity + Association membership`
+
+![](output/figures/charity-and-volunteerism.png)
+
+  - Demographics: `Donation preferences ~ Gender + Marital status + Education + Income + Race + Age`
+
+  ![](output/figures/demographics.png)
+
+  - `Donation preferences ~ (Public affairs) + (Political ideology)`
+
+  ![](output/figures/public-political.png)
+
+  - `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views)`
+
+![](output/figures/public-political-social.png)
+
+  - `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views) + (Charity and voluntarism)`
+
+![](output/figures/public-political-social-charity.png)
+
+  - `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views) + (Charity and voluntarism) + (Demographics)`
+
+![](output/figures/public-political-social-charity-demo.png)
+
+- Third set of questions (exploratory) can be answered using a market simulator.

### 2019-10-04 analysis/output/figures/hypotheses/Hypotheses.Rmd
Working on filtering plots on specific levels and covariates.

@@
     ) %>%
+    filter(
+      levels == str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
+      covariates == c("Religion: Christian")
+# package to help with filtering: stringr
+# r4ds chapter 14 (detect matches)
+    )
     ggplot(aes(x = Theta, y = covariates)) +

### 2019-10-04 analysis/output/figures/hypotheses/Hypotheses.Rmd
Updated filtering code

--- 2019-10-03 analysis/output/figures/hypotheses/Hypotheses.Rmd
@@
     ) %>%
+    filter(
+      levels ==   str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
+      covariates == c("Religion: Hindu", "Religion: Protestant", "Religion: Christian Orthodox", "Religion: Jewish")) %>% 
     ggplot(aes(x = Theta, y = covariates)) +
@@
        labs(y = "Covariates") +
-       facet_wrap(~ levels, ncol = 7)
+       facet_wrap(~ levels, ncol = 5)
 }

### 2019-10-04 manuscript/manuscript.Rmd
Updated filtering code

@@
 
-![Combined Results](output/figures/combined-results.png)
+![](output/figures/combined-results.png)
 
@@
 
-![Relationship With Host Government](output/figures/relationship-with-gov.png)
+![](output/figures/relationship-with-gov.png)
 
@@
 
-![Organizational Characteristics: Managerial Practices](output/figures/managerial-practices.png)
+![](output/figures/managerial-practices.png)
 
@@
 
-![Organizational Characteristics: Funding Sources](output/figures/funding-sources.png)
+![](output/figures/funding-sources.png)
 
@@
 
-![Organizational Characteristics: Issue Areas](output/figures/issue-areas.png)
+![](output/figures/issue-areas.png)
 
@@
 
-![Organization](output/figures/organization.png)
+![](output/figures/organization.png)
 
@@
   ![](output/figures/demographics.png)
-
   - `Donation preferences ~ (Public affairs) + (Political ideology)`

### 2019-10-07 analysis/output/figures/hypotheses/Hypotheses.Rmd
Adding some more granular demographic plots.

--- 2019-10-03 analysis/output/figures/hypotheses/Hypotheses.Rmd
@@
 charity_voluntarism <- 0                  # Charity and voluntarism
-demographics <- 0                         # Demographics
+demographics <- 1                         # Demographics
 public_political <- 0                     # Public affairs + Political ideology
@@
     ) %>%
+    filter(
+    # levels ==   str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
+      covariates ==  "Income: Less than $10,000 to $300,000 or more") %>% 
     ggplot(aes(x = Theta, y = covariates)) +

### 2019-10-07 manuscript/manuscript.Rmd
Adding some more granular demographic plots.

@@
   ![](output/figures/demographics.png)
+    - Gender
+    - Marital Status
+  ![](output/figures/marital-status.png)  
+  Question: it seems that levels like emergency response are omitted because they're considered the base to compare to. Why is there not a "Marital status: Married" though? It can't be the same thing
+
+    - Education
+  ![](output/figures/education.png)
+    - Income
+  ![](output/figures/income.png)
+    - Race 
+    - Age
+
   - `Donation preferences ~ (Public affairs) + (Political ideology)`

### 2019-10-09 analysis/output/figures/hypotheses/Hypotheses.Rmd
Added age and race plots

@@
     filter(
-    # levels ==   str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
-      covariates ==  "Income: Less than $10,000 to $300,000 or more") %>% 
+    # levels == str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
+      covariates == c( "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
+    str_c(
+      "Medium to follow news: ", 
+      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
+    ),
+    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No")) %>% 
     ggplot(aes(x = Theta, y = covariates)) +

### 2019-10-09 manuscript/manuscript.Rmd
Added age and race plots

--- 2019-10-04 manuscript/manuscript.Rmd
@@
 
-The following plots zoom in on the strength of the effects that these characteristics have.
+The following plots zoom in on the strength of the effects of these characteristics.
 
@@
   ![](output/figures/demographics.png)
+    - Gender
+
+    - Marital Status
+  ![](output/figures/marital-status.png)  
+  Question: it seems that levels like emergency response are omitted because they're considered the base to compare to. Why is there not a "Marital status: Married" though? It can't be the same thing
+
+  - Education
+  ![](output/figures/education.png)
+    - Income
+  ![](output/figures/income.png)
+    - Race 
+    ![](output/figures/race.png)
+    - Age 
+  ![](output/figures/age.png)
+
   - `Donation preferences ~ (Public affairs) + (Political ideology)`

### 2019-10-10 analysis/output/figures/hypotheses/Hypotheses.Rmd
Working on more plots but keep running into errors

--- 2019-10-07 analysis/output/figures/hypotheses/Hypotheses.Rmd
@@
 intercept <- 0                            # Intercept-only
-public_affairs <- 0                       # Public affairs
+public_affairs <- 1                       # Public affairs
 political_ideology <- 0                   # Political ideology
@@
 charity_voluntarism <- 0                  # Charity and voluntarism
-demographics <- 1                         # Demographics
+demographics <- 0                         # Demographics
 public_political <- 0                     # Public affairs + Political ideology
@@
     filter(
-    # levels ==   str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
-      covariates ==  "Income: Less than $10,000 to $300,000 or more") %>% 
+    # levels == str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
+      covariates ==  "Liberal to Conservative") %>% 
     ggplot(aes(x = Theta, y = covariates)) +
@@
        labs(y = "Covariates") +
-       facet_wrap(~ levels, ncol = 5)
+       facet_wrap(~ levels, ncol = 4)
 }
 ```
+
+Error: Faceting variables must have at least one value
 

### 2019-10-17 analysis/output/figures/hypotheses/Hypotheses.Rmd
Adding more granular plots

--- 2019-10-07 analysis/output/figures/hypotheses/Hypotheses.Rmd
@@
 social_views <- 0                         # Social views
-charity_voluntarism <- 0                  # Charity and voluntarism
-demographics <- 1                         # Demographics
+charity_voluntarism <- 1                  # Charity and voluntarism
+demographics <- 0                         # Demographics
 public_political <- 0                     # Public affairs + Political ideology
@@
   covariate_labels <- c(
-    "Importance of trusing charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",
+    "Importance of trusting charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",
     "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: No", "Volunteer frequency: Weekly to Every few years",
@@
     # Charity and voluntarism
-    "Importance of trusing charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",
+    "Importance of trusting charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",
     "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: No", "Volunteer frequency: Weekly to Every few years",
@@
     filter(
-    # levels ==   str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
-      covariates ==  "Income: Less than $10,000 to $300,000 or more") %>% 
+      # levels == str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
+      covariates == str_c(
+      c("Church or religious organization: ", "Sport or recreational organization: ", "Art, music, or educational organization: ",
+        "Labor union: ", "Political party: ", "Environmental organization: ", "Professional association: ", 
+        "Humanitarian or charitable organization: ", "Consumer organization: ", "Other organization: "
+      ), 
+      "Member to Not")) %>% 
     ggplot(aes(x = Theta, y = covariates)) +
@@
        labs(y = "Covariates") +
-       facet_wrap(~ levels, ncol = 5)
+       facet_wrap(~ levels, ncol = 4)
 }

### 2019-10-17 manuscript/manuscript.Rmd
Adding more granular plots

@@
 
-Compared to when an NGO has a friendly relationship with the host government, donors are much less likely to donate when government is under crackdown or criticized.
+Compared to when an NGO has a friendly relationship with the host government, donors who see that an NGO faces general legal trouble abroad are less likely to donate.
 
@@
 
+    - Traveled Internationally: No
+    ![](output/figures/traveled.png)
+
+    - Medium to follow news: Online (excluding social media) with all attributes
+      ![](output/figures/following-news.png)
+
+    - Medium to follow news: Online (excluding social media) with organization
+      ![](output/figures/following-news2.png)
+
   - Political ideology: `Donation preferences ~ Political ideology`
@@
 ![](output/figures/social-views.png)
+
+    - Can't get a plot of Religiosity to work.
 
@@
   ![](output/figures/marital-status.png)
-  Question: it seems that levels like emergency response are omitted because they're considered the base to compare to. Why is there not a "Marital status: Married" though? It can't be the same thing
 

### 2019-10-17 analysis/output/figures/hypotheses/Hypotheses.Rmd
Added gender, other organizations, and religion.

--- 2019-10-09 analysis/output/figures/hypotheses/Hypotheses.Rmd
@@
       # levels == str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
-      covariates == c( "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
-    str_c(
-      "Medium to follow news: ", 
-      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
-    ),
-    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No")) %>% 
+      covariates == str_c("Gender: ", 
+      c("Female", "Transgender", "Prefer not to say", "Other")
+    ))  %>% 
     ggplot(aes(x = Theta, y = covariates)) +

### 2019-10-18 manuscript/manuscript.Rmd
Added gender, other organizations, and religion.
Fixing formatting but now having trouble displaying some of the plots (travel, following news).

@@
 
+A few paragraphs about the context of what has been done with conjoint analysis within the political and/or public policy field.
+
 # Results
 
-- First set of questions (hypotheses) can be answered using the results of the intercept-only model.
+### First Set of Questions
+The first set of questions (hypotheses) can be answered using the results of the intercept-only model.
 
@@
 
-- Second set of questions (confirmatory) can be answered using the following upper-level models:
+### Second Set of Questions
+The second set of questions (confirmatory) can be answered using the following upper-level models:
   - Public affairs: `Donation preferences ~ Public affairs knowledge + Public affairs activity`
@@
 ![](output/figures/social-views.png)
-
-    - Can't get a plot of Religiosity to work.
+      - Religiosity
+  ![](output/figures/religion.png)
 
@@
 
-![](output/figures/charity-and-volunteerism.png)
+![](output/figures/charity-and-voluntarism.png)  
+      - Association membership
+  ![](output/figures/other-organizations.png)
 
@@
       - Gender
-
+  ![](output/figures/gender.png)  
       - Marital Status
   ![](output/figures/marital-status.png)  
-
       - Education
@@
 
-- Third set of questions (exploratory) can be answered using a market simulator.
+### Third Set of Questions
+The third set of questions (exploratory) can be answered using a market simulator.

### 2019-10-22 manuscript/manuscript.Rmd
Adding to the Methods section.

@@
 
-A few paragraphs about the context of what has been done with conjoint analysis within the political and/or public policy field.
+Conjoint analysis has been widely used within social sciences but has only recently been used in the political and public policy field.
+Helfer (2016) and Mummolo (2016) both used conjoint analysis to assess tradeoffs made in political communications.
+Conjoint is key in political research because helps it captures multidimensional causal relations.
+
+Knudsen and Johannesson (2018) showed that political communication requires conjoint analysis because __________.
+
+"Conjoint addresses [the issues of the traditional survey] by separately identifying several component-specific causal effects." (pg. 11)
 

### 2019-10-24 manuscript/manuscript.Rmd
Adding to methods section.

--- 2019-10-18 manuscript/manuscript.Rmd
@@
 
-A few paragraphs about the context of what has been done with conjoint analysis within the political and/or public policy field.
+Causality can be inferred through conjoint analysis because it shows which components of a choice hold the most weight.
+Conjoint analysis has been widely used within social sciences and has recently begun to be used in political and public policy fields.
+Helfer (2016) and Mummolo (2016) both used conjoint analysis to assess tradeoffs made in political communications.
+### rewrite in more detail so that it's clear that consumers are making the tradeoffs ### Conjoint is key in political research because it captures multidimensional causal relations.
+
+Knudsen and Johannesson (2018) argue that political communication research requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgement of credibility.
+Public policy research would benefit from conjoint analysis for the same reasons.
 

### 2019-10-25 manuscript/manuscript.Rmd
Working on methods section. First set of questions looks good. Need to add interpretations to second set of plots.

--- 2019-10-18 manuscript/manuscript.Rmd
@@
 
-A few paragraphs about the context of what has been done with conjoint analysis within the political and/or public policy field.
+Conjoint analysis shows which components of a choice hold the most weight.
+Conjoint analysis has been widely used within social sciences to explain causality and has recently begun to be used in political and public policy fields.
+Helfer (2016) and Mummolo (2016) both used conjoint analysis to assess consumer perceptions of political communications.
+Conjoint is key in political research because it captures multidimensional causal relations.
+
+Knudsen and Johannesson (2018) argue that political communication research requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgement of credibility.
+Public policy research would benefit from conjoint analysis for the same reasons.
 

### 2019-10-29 manuscript/manuscript.Rmd
Added interpretations to second set of questions

@@
 
-Conjoint analysis shows which components of a choice hold the most weight.
+Conjoint analysis forces a consumer to choose between alternatives, revealing which components of a choice are the most important to that consumer.
 Conjoint analysis has been widely used within social sciences to explain causality and has recently begun to be used in political and public policy fields.
@@
 
-Knudsen and Johannesson (2018) argue that political communication research requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgement of credibility.
-Public policy research would benefit from conjoint analysis for the same reasons.
+Knudsen and Johannesson (2018) argue that political communication research requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgment of credibility.
+Because we also want to capture the complexity of a respondent's judgment of whether they should donate to an NGO or not, we used conjoint analysis to draw our conclusions.
 
@@
 
-The following plots zoom in on the strength of the effects of these characteristics.
+The following plots zoom in on the strength and direction of the effects of these characteristics.
 
-Compared to when an NGO has a friendly relationship with the host government, donors who see that an NGO faces general legal trouble abroad are less likely to donate.
+Compared to when an NGO has a friendly relationship with the host government, donors who see that an NGO faces general legal trouble abroad (under crackdown or criticized) are less likely to donate.
 
@@
 
-    - Traveled Internationally: No
+Those that haven't traveled internationally are significantly less likely to donate to NGOs than those who have.
 ![](output/figures/traveled.png)
 
-    - Medium to follow news: Online (excluding social media) with all attributes
+Of all media sources, those that follow the news through an app or email newsletter are more likely to donate in general.
+Interestingly, those that read newsletters are the most likely to donate overall.
+They feel most comfortable donating to environmental causes.
+They care significantly less about managerial practices and funding sources than other groups.
       ![](output/figures/following-news.png)
 
-    - Medium to follow news: Online (excluding social media) with organization
+When it comes to donating to organizations, those whose top news medium is online sources (excluding social media) are least likely to donate.
 ![](output/figures/following-news2.png)
@@
 
+Those that are conservative are significantly more likely to donate to the Red Cross.
 ![](output/figures/political-ideology.png)
@@
 ![](output/figures/social-views.png)
-      - Religiosity
+
+Hindus are very unlikely to donate to human rights or refugee relief, whereas Muslims are very likely to donate to human rights and refugee relief.
+Muslims are also very willing to donate to organizations that are facing government criticism or crackdown in the country.
   ![](output/figures/religion.png)
@@
 
+Those that have a history of either family or personal activism are most likely to donate to organizations. Those that haven't volunteered in the past 12 months are also more likely to donate.   
 ![](output/figures/charity-and-voluntarism.png)  
-      - Association membership
+Those that are in a professional or humanitarian organization are most likely to donate.
+It's odd that those that belong to an environmental organization are less likely to donate to environmental NGOs.
   ![](output/figures/other-organizations.png)
@@
 
+Demographics are broken down further and analyzed below.
   ![](output/figures/demographics.png)
-      - Gender
+Note: not sure if "other" indicates "male" or if male is the intercept everything else is compared to.
   ![](output/figures/gender.png)  
-      - Marital Status
+Overall, those that are widowed are less likely to donate to organizations than others.
+They also don't pay attention to financial transparency and accountability, though those that have never married do.
   ![](output/figures/marital-status.png)  
-      - Education
+Financial transparency was important to everyone regardless of education level. 
   ![](output/figures/education.png)
-      - Income
+Income doesn't impact the various attributes except when it comes to organization. There is a lot more spread when it comes to choosing an organization.
   ![](output/figures/income.png)
-      - Race 
+Not seeing obvious patterns across races.
     ![](output/figures/race.png)
-      - Age 
+  Across all ages, people are most likely to donate to emergency response efforts more than any other issue area. 
   ![](output/figures/age.png)
@@
 
+Those that read printed news are least likely to donate to any of these organizations.
+Those that follow international news multiple times are day are more likely to donate and are less concerned when an organization is criticized by the government.
 ![](output/figures/public-political.png)
@@
 
+For the most part, these plots have too much information to gain useful insight.
 ![](output/figures/public-political-social.png)

### 2019-11-06 analysis/output/figures/hypotheses/Hypotheses.Rmd
Changed vizualization of first set of plots from ggridges to geom_halfeyeh

@@
 # Specify the covariate.
-intercept <- 0                            # Intercept-only
+intercept <- 1                            # Intercept-only
 public_affairs <- 0                       # Public affairs
@@
     ggplot(aes(x = Theta, y = levels)) + 
-    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+    geom_halfeyeh(.width = .95) +
     geom_vline(xintercept = 0, color = "white") +
@@
     ggplot(aes(x = Theta, y = levels)) + 
-    geom_density_ridges(scale = 5, height = 1, rel_min_height = 0.01) +
+    geom_halfeyeh(.width = .95) +
     geom_vline(xintercept = 0, color = "grey") +
@@
     ggplot(aes(x = Theta, y = levels)) + 
-    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+    geom_halfeyeh(.width = .95) +
     geom_vline(xintercept = 0, color = "grey") +
@@
     ggplot(aes(x = Theta, y = levels)) +
-    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+    geom_halfeyeh(.width = .95) +
     geom_vline(xintercept = 0, color = "grey") +

### 2019-11-08 manuscript/manuscript.Rmd
Changed vizualization of first set of plots from ggridges to geom_halfeyeh
Cleaned up initial results draft

@@
 
-### First Set of Questions
-The first set of questions (hypotheses) can be answered using the results of the intercept-only model.
+## Hypotheses
 
-We hypothesized that each of these structural and organizational characteristics would have a significant effect on donor behavior, though we were unsure of the direction of that effect.
+We hypothesized that each of these structural and organizational characteristics would have a significant effect on donor behavior, and that's what we can clearly see here.
+Each of the marginal posterior distributions representing the relationship between the structural and organizational characteristics and likelihood of donating have 95% credible intervals that don't include zero.
+Note that these are the aggregate results.
+For the influence of various covariate effects, see the second set of questions/hypotheses.
 
-![](output/figures/combined-results.png)
+![](output/figures/combined-results-halfeye.png)
 
-The following plots zoom in on the strength and direction of the effects of these characteristics.
+Starting with the relationship with the host government, compared to when an NGO has a friendly relationship with the host government (the reference level), donors who see that an NGO faces general trouble (under crackdown or criticized) are less likely to donate, with the stronger negative effect of being under crackdown significantly different than the less negative effect of being criticized.
 
-Compared to when an NGO has a friendly relationship with the host government, donors who see that an NGO faces general legal trouble abroad (under crackdown or criticized) are less likely to donate.
+![](output/figures/relationship-with-gov-halfeye.png)
 
-![](output/figures/relationship-with-gov.png)
+Donors are more likely to donate when organizations are accountable and financially transparent (not being accountable or financially transparent are the respective reference levels) with no significant difference between being accountable or financially transparent.
 
-Donors are more likely to donate when organizations are accountable and financially transparent.
+![](output/figures/managerial-practices-halfeye.png)
 
-![](output/figures/managerial-practices.png)
+Donors are most likely to donate when an NGO is funded primarily by many small private donations (the reference level).
+Donors are less likely to donate when the organization is subsidized by government grants, and even less likely when it is funded by a few private donors, though there is no significant difference between the negative effect of funding by government grants and a handful of wealthy private donors.
 
-Donors are most likely to donate when an NGO is funded primarily by many small private donations.
-Donors are less likely to donate when the organization is subsidized by government grants, and even less likely when it is funded by a few private donors.
+![](output/figures/funding-sources-halfeye.png)
 
-![](output/figures/funding-sources.png)
+Of all issue areas, donations to emergency response were most likely (the reference level) followed by human rights and then environment.
+Refugee relief was the least likely issue area to be donated to, though there is no significant difference between the negative effect of environment and refugee relief on donation intent.
 
-Of all issue areas, donations to emergency response were most likely, followed by human rights and then environment. Refugee relief was the least likely issue area to be donated to.
+![](output/figures/issue-areas-halfeye.png)
 
-![](output/figures/issue-areas.png)
+All organizations were positively perceived by respondents, with the Red Cross significantly more favored (no reference level needed since organization doubles as the intercept).
+There is no significant difference in the effect of each of the other organizations on donation intent.
 
-All organizations were positively percieved by respondents. The Red Cross was significantly more favored.
+![](output/figures/organization-halfeye.png)
 
-![](output/figures/organization.png)
+## Exploratory Analysis
 
-### Second Set of Questions
-The second set of questions (confirmatory) can be answered using the following upper-level models:
-  - Public affairs: `Donation preferences ~ Public affairs knowledge + Public affairs activity`
+REPLACE RIDGE PLOTS WITH A HISTOGRAM, FOCUS ON SPECIFIC MARGINALS OF INTEREST USING HALFEYE PLOTS AS ABOVE.
+
+The second set of questions (confirmatory) can be answered using the following upper-level models.
+
+### Public affairs: `Donation preferences ~ Public affairs knowledge + Public affairs activity`
+
 ![](output/figures/public-affairs.png)
@@
 Those that haven't traveled internationally are significantly less likely to donate to NGOs than those who have.
+
 ![](output/figures/traveled.png)
@@
 They care significantly less about managerial practices and funding sources than other groups.
+
 ![](output/figures/following-news.png)
@@
 When it comes to donating to organizations, those whose top news medium is online sources (excluding social media) are least likely to donate.
+
 ![](output/figures/following-news2.png)
 
-  - Political ideology: `Donation preferences ~ Political ideology`
+### Political ideology: `Donation preferences ~ Political ideology`
 
 Those that are conservative are significantly more likely to donate to the Red Cross.
+
 ![](output/figures/political-ideology.png)
 
-  - Social views: `Donation preferences ~ Public affairs trust + Social ideology + Religiosity`
+### Social views: `Donation preferences ~ Public affairs trust + Social ideology + Religiosity`
 
@@
 Muslims are also very willing to donate to organizations that are facing government criticism or crackdown in the country.
+
 ![](output/figures/religion.png)
 
-  - Charity and voluntarism: `Donation preferences ~ Charity trust + Charity activity + Volunteer activity + Activism activity + Association membership`
+### Charity and voluntarism: `Donation preferences ~ Charity trust + Charity activity + Volunteer activity + Activism activity + Association membership`
 
 Those that have a history of either family or personal activism are most likely to donate to organizations. Those that haven't volunteered in the past 12 months are also more likely to donate.
+
 ![](output/figures/charity-and-voluntarism.png)
+
 Those that are in a professional or humanitarian organization are most likely to donate.
 It's odd that those that belong to an environmental organization are less likely to donate to environmental NGOs.
+
 ![](output/figures/other-organizations.png)
 
-  - Demographics: `Donation preferences ~ Gender + Marital status + Education + Income + Race + Age`
+### Demographics: `Donation preferences ~ Gender + Marital status + Education + Income + Race + Age`
 
 Demographics are broken down further and analyzed below.
+
 ![](output/figures/demographics.png)
+
 Note: not sure if "other" indicates "male" or if male is the intercept everything else is compared to.
+
 ![](output/figures/gender.png)
+
 Overall, those that are widowed are less likely to donate to organizations than others.
 They also don't pay attention to financial transparency and accountability, though those that have never married do.
+
 ![](output/figures/marital-status.png)
+
 Financial transparency was important to everyone regardless of education level.
+
 ![](output/figures/education.png)
+
 Income doesn't impact the various attributes except when it comes to organization. There is a lot more spread when it comes to choosing an organization.
+
 ![](output/figures/income.png)
+
 Not seeing obvious patterns across races.
+
 ![](output/figures/race.png)
+
 Across all ages, people are most likely to donate to emergency response efforts more than any other issue area.
+
 ![](output/figures/age.png)
 
-  - `Donation preferences ~ (Public affairs) + (Political ideology)`
+### `Donation preferences ~ (Public affairs) + (Political ideology)`
 
@@
 Those that follow international news multiple times are day are more likely to donate and are less concerned when an organization is criticized by the government.
+
 ![](output/figures/public-political.png)
 
-  - `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views)`
+### `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views)`
 
 For the most part, these plots have too much information to gain useful insight.
+
 ![](output/figures/public-political-social.png)
 
-  - `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views) + (Charity and voluntarism)`
+### `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views) + (Charity and voluntarism)`
 
@@
 
-  - `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views) + (Charity and voluntarism) + (Demographics)`
+### `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views) + (Charity and voluntarism) + (Demographics)`
 
@@
 
-### Third Set of Questions
-The third set of questions (exploratory) can be answered using a market simulator.
+### Market Simulator
+
+TBD.

### 2019-11-08 analysis/03b_hypotheses.Rmd

--- 2019-11-06 analysis/output/figures/hypotheses/Hypotheses.Rmd
@@
 ---
+
 In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics.

### 2019-11-08 analysis/03c_hypothesis-testing.Rmd

--- 2019-09-24 analysis/03_analysis.Rmd
@@
        geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
-       # geom_halfeyeh(.width = .95) +
        geom_vline(xintercept = 0, color = "white") +
        labs(y = "Covariates") +
-       facet_wrap(~ levels, ncol = 5)
+       facet_wrap(~ levels, ncol = 5))
 }
 
-# # Save plot
-# if (intercept == 1) file_name <- paste("intercept_marginal-posteriors.png")
-# if (public_affairs == 1) file_name <- paste("public-affairs_marginal-posteriors.png")
-# if (political_ideology == 1) file_name <- paste("political-ideology_marginal-posteriors.png")
-# if (social_views == 1) file_name <- paste("social-views_marginal-posteriors.png")
-# if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_marginal-posteriors.png")
-# if (demographics == 1) file_name <- paste("demographics_marginal-posteriors.png")
-# if (public_political == 1) file_name <- paste("public-political_marginal-posteriors.png")
-# if (public_political_social == 1) file_name <- paste("public-political-social_marginal-posteriors.png")
-# if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_marginal-posteriors.png")
-# if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_marginal-posteriors.png")
-# ggsave(
-#   file_name,
-#   path = here::here("analysis", "output", "figures"),
-#   width = ifelse(intercept == 1, 12, 20), 
-#   height = ifelse(sum(intercept, public_affairs, political_ideology, social_views, charity_voluntarism, demographics) == 1, 12, 20), 
-#   units = "in"
-# )
 ```
 
-# Original computing environment
+#### Do managerial practices (financial transparency and accountability systems), funding sources (private donations and government grants), and issue areas (emergency response, environmental issues, human rights, and refugee relief) also serve as heuristics that signal an organization’s deservingness to donors?
 
-<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>
+```{r}
 
-<div id="sessioninfo" class="collapse">
-
-```{r show-session-info, echo=TRUE, width=100}
-writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))
-
-devtools::session_info()
 ```
 
-</div>
+# Hypotheses:
+# We theorize that structural characteristics like an NGO’s host-country political and legal environment can serve as heuristics and shortcuts for donors.
+# Donors who see that an NGO faces general legal trouble abroad will use that knowledge to decide whether or not to donate.
+# We also theorize that non-structural organizational characteristics like managerial practices, funding sources, and issue area also serve as heuristics and influence donation patterns.
+# In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics.
+We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we’re unsure of the direction of that effect.

### 2019-11-14 manuscript/manuscript.Rmd
Added rough draft of Methods section

@@
 
-Conjoint analysis forces a consumer to choose between alternatives, revealing which components of a choice are the most important to that consumer.
+Conjoint anlysis is a common research method used to evaluate which attributes of a choice are most important to a consumer.
+A conjoint analysis survey includes sets of alternatives that consumers must choose between.
+These choice sets are made up of attributes such as price, brand, and features.
+However, the alternatives have different levels within these attributes.
+Price may be 20 dollars for Option A and 30 dollars for Option B, however Option A may not include a specific feature while Option B does.
+
+Conjoint analysis reflects a real world experience where the consumer has to weigh tradeoffs and choose between alternatives.
+This reveals which components of a choice are the most important to that consumer.
+Aggregated results from all participants show which attributes have the greatest weight on a decision.
+Further insights can be concluded by analyzing responses of specific groups (i.e.
+according to gender, age, member of an organization).
+
 Conjoint analysis has been widely used within social sciences to explain causality and has recently begun to be used in political and public policy fields.

### 2019-11-15 manuscript/manuscript.Rmd
Updated draft methods section

--- 2019-11-08 manuscript/manuscript.Rmd
@@
 
-Conjoint analysis forces a consumer to choose between alternatives, revealing which components of a choice are the most important to that consumer.
+## Conjoint Analysis
+
+Conjoint analysis is a staple in marketing research for evaluating which product attributes are most important to consumers.
+It has been extensively used in new product development and product line optimization.
+However, conjoint analysis is generally applicable whenever individuals face complex, multi-dimensional tradeoffs such that explicitly eliciting preferences isn't productive or even possible.
+In the context of our project, we are evaluating donor rather than consumer preferences as they choose NGOs to donate to based on both organizational and structural heuristics.
+
 Conjoint analysis has been widely used within social sciences to explain causality and has recently begun to be used in political and public policy fields.
-Helfer (2016) and Mummolo (2016) both used conjoint analysis to assess consumer perceptions of political communications.
-Conjoint is key in political research because it captures multidimensional causal relations.
+Helfer (2016) and Mummolo (2016) both used conjoint analysis to assess perceptions of political communications.
+Knudsen and Johannesson (2018) argue that political communication research requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgment of credibility.
+Because we also want to capture the complexity of a respondent's judgment of which NGO they should donate to, if any, we saw potential to expand the application of conjoint analysis within public policy.
 
-Knudsen and Johannesson (2018) argue that political communication research requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgment of credibility.
-Because we also want to capture the complexity of a respondent's judgment of whether they should donate to an NGO or not, we used conjoint analysis to draw our conclusions.
+Respondents were presented with 4 hypothetical organizations that each had 4 randomly assigned features.
+Respondents were shown 12 sets of these hypothetical organizations.
+This partial fractional factorial design resulted in 288 (4 × 4 × 2 × 3 × 3) possible combinations of features, and no single respondent was offered every combination.
+
+## Sample
+
+We used an online survey, hosted at Qualtrics, to collect our data.
+We designed this survey to measure and test each of our hypotheses.
+After collecting demographic information about respondents, the survey presented 12 random combinations of managerial practices, issue areas, funding sources, and relationships with host governments for 4 alternative organizations and asked respondents which of the 4 organizations they would most prefer to donate to, if any.
+
+Participants of the survey experiment were recruited through Centiment, a commercial online provider of high quality non-probability opt-in survey panels.
+Centiment ensures panel quality by actively recruiting representative samples of the US population and provides monetary incentives and rewards to participants.
+
+To see how varying NGO characteristics influence the decision to donate, our sample was representative of the population of people who are likely to donate to charity.
+We asked potential participants a screening question early in the survey (“Q2.5: How often do you donate to charity”).
+If a participant responded that they give once every few years or never, they were be disqualified from the study.
+
+The 1,000 subjects constituted a sufficient size for model estimation.
+A sample size of at least 500 respondents is typical for estimating a hierarchical Bayesian model based on conjoint data.
+We doubled this amount because we are interested in analyzing subpopulations of respondents, which requires a larger sample.
+The first page of the survey contained a consent statement that participants must agree to before continuing with the experiment.
 

### 2019-11-16 analysis/03_analysis.Rmd
Added heatmaps to help illustrate research question 2

@@
 ```{r plot-marginals}
-intercept <- 1                            # Intercept-only
+intercept <- 0                            # Intercept-only
 public_affairs <- 0                       # Public affairs
@@
 
+As an experiment, it might be helpful to use a heatmap to identify where there are significant differences in the non-intercept models, which can then be narrowed down using the marginal plots.
+
+```{r heatmaps}
+if (public_affairs == 1) plot_title <- paste("Public Affairs")
+if (political_ideology == 1) plot_title <- paste("Political Ideology")
+if (social_views == 1) plot_title <- paste("Social Views")
+if (charity_voluntarism == 1) plot_title <- paste("Charity and Voluntarism")
+if (demographics == 1) plot_title <- paste("Demographics")
+if (public_political == 1) plot_title <- paste("Public Affairs and Political Ideology")
+if (public_political_social == 1) plot_title <- paste("Public Affairs, Political Ideology, and Social Views")
+if (public_political_social_charity == 1) plot_title <- paste("Public Affairs, Political Ideology, Social Views, and Charity and Voluntarism")
+if (public_political_social_charity_demo == 1) plot_title <- paste("Public Affairs, Political Ideology, Social Views, Charity and Voluntarism, and Demographics")
+if (intercept != 1) {
+  # Posterior means.
+  posterior_means <- draws %>% 
+    filter(j != 1) %>% 
+    mutate(
+      levels = factor(i, labels = level_labels), 
+      # covariates = factor(j, labels = covariate_labels)
+      covariates = factor(j, labels = 1:length(covariate_labels))
+    ) %>% 
+    group_by(levels, covariates) %>% 
+    summarize(
+      mean = mean(Theta),
+      ci_lower = quantile(Theta, .025),
+      ci_upper = quantile(Theta, .975),
+      gt_zero = if_else(ci_lower > 0 & ci_upper > 0, 1, 0),
+      lt_zero = if_else(ci_lower < 0 & ci_upper < 0, -1, 0)
+    )
+
+  # Heatmap of Theta matrix.
+  posterior_means %>% 
+    mutate(
+      gt_lt_zero = gt_zero + lt_zero,
+      Coefficients = factor(
+        gt_lt_zero, 
+        levels = -1:1,
+        labels = c("Negative", "Not Significant", "Positive"))
+    ) %>% 
+    ggplot(aes(x = covariates, y = levels, fill = Coefficients)) +
+    geom_raster() +
+    scale_fill_brewer(palette = "Blues") +
+    scale_x_discrete(expand=c(0.001,0.001)) +
+    scale_y_discrete(expand=c(0.001,0.001)) +
+    # theme(axis.text.x = element_text(angle = 90)) +
+    labs(
+      title = plot_title,
+      x = "Covariates",
+      y = "Attribute Levels"
+    )
+}
+
+# Save plot
+if (public_affairs == 1) file_name <- paste("public-affairs_coefficient-matrix.png")
+if (political_ideology == 1) file_name <- paste("political-ideology_coefficient-matrix.png")
+if (social_views == 1) file_name <- paste("social-views_coefficient-matrix.png")
+if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_coefficient-matrix.png")
+if (demographics == 1) file_name <- paste("demographics_coefficient-matrix.png")
+if (public_political == 1) file_name <- paste("public-political_coefficient-matrix.png")
+if (public_political_social == 1) file_name <- paste("public-political-social_coefficient-matrix.png")
+if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_coefficient-matrix.png")
+if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_coefficient-matrix.png")
+ggsave(
+  file_name,
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
+```
+
 # Original computing environment

### 2020-01-14 analysis/02_clean-data.Rmd
Add other factor levels for summary table

@@
   )
+
+# Add other factor levels
+data <- data %>% 
+  mutate(
+    Q2.2 = factor(Q2.2, labels = c("Always", "Sometimes", "Never"), ordered = TRUE),
+    Q2.6 = factor(Q2.6, 
+                  labels = c("$1-$49", "$50-$99", "$100-$499", "$500-$999", 
+                             "$1000-$4,999", "$5000-$9,999", "$10,000+"),
+                  ordered = TRUE),
+    Q2.7_f = factor(Q2.7, ordered = TRUE),
+    Q2.8_f = factor(Q2.8, ordered = TRUE),
+    Q2.9 = factor(Q2.9, labels = c("Yes", "No"), ordered = TRUE),
+    Q5.1 = factor(Q5.1, labels = c("Yes", "No"), ordered = TRUE),
+    Q5.2_f = factor(Q5.2, ordered = TRUE),
+    Q5.6_f = factor(Q5.6, ordered = TRUE),
+    Q5.7 = factor(Q5.7, labels = c("Yes", "No"), ordered = TRUE),
+    Q5.11_f = factor(Q5.11, ordered = TRUE),
+    Q5.12 = factor(Q5.12, labels = c("Male", "Female", "Transgender", 
+                                     "Prefer not to say", "Other"), 
+                   ordered = TRUE),
+    Q5.13 = factor(Q5.13, labels = c("Married", "Widowed", "Divorced", 
+                                     "Separated", "Never married"), 
+                   ordered = TRUE),
+    Q5.14 = factor(Q5.14, 
+                   labels = c("Less than high school", "High school graduate", 
+                              "Some college", "2 year degree", "4 year degree", 
+                              "Graduate or professional degree", "Doctorate"),
+                   ordered = TRUE)
+  )
 ```
@@
 ```{r save-clean-data}
-write_csv(data, here("data", "derived_data", "final_data.csv"))
+write_rds(data, here("data", "derived_data", "final_data.rds"))
 ```

### 2020-01-14 R/graphics.R
Add color palette

@@ -31,7 +31,7 @@ theme_ngo <- function(base_size = 9, base_family = "Roboto Condensed") {
                                     family = "Roboto Condensed", face = "bold"),
           strip.background = element_rect(fill = "#ffffff", colour = NA),
           axis.ticks = element_blank(),
-          axis.title.x = element_text(margin = margin(t = 10)),
+          axis.title.x = element_text(margin = margin(t = 5)),
           axis.text = element_text(family = "Roboto Condensed Light", face = "plain"),
           legend.key = element_blank(),
           legend.text = element_text(size = rel(1), family = "Roboto Condensed Light", face = "plain"),

### 2020-01-14 analysis/options.R

@@ -9,6 +9,30 @@ pander::panderOptions("round", 3)
 pander::panderOptions("table.alignment.default", "left")
 
 
+# Colors ------------------------------------------------------------------
+
+# Colors via http://clrs.cc/
+clrs <- list(
+  navy = "#001F3F",
+  blue = "#0074D9",
+  aqua = "#7FDBFF",
+  teal = "#39CCCC",
+  olive = "#3D9970",
+  green = "#2ECC40",
+  lime = "#01FF70",
+  yellow = "#FFDC00",
+  orange = "#FF851B",
+  red = "#FF4136",
+  fuchsia = "#F012BE",
+  purple = "#B10DC9",
+  maroon = "#85144B",
+  white = "#FFFFFF",
+  silver = "#DDDDDD",
+  gray = "#AAAAAA",
+  black = "#111111"
+)
+
+
 # Bayes options -----------------------------------------------------------
 
 CHAINS <- 4

### 2020-01-14 analysis/03_analysis.Rmd
Consistent and pretty graphs and tables

--- 2019-09-24 analysis/03_analysis.Rmd
@@
 
-# Causal pathway
-
-Our theory and hypotheses are laid out in the causal pathway below.
-Organizational factors (**O**, or organizational practices like financial disclosure and accountability practices; **I**, or issue area; and **F**, or funding) all influence the decision to donate (**D**).
-Structural factors like an NGO's relationship with its host government (**G**) also influence donation behavior, but the relationship itself is shaped by both funding and issue area.
-
-```{r causal-dag, fig.width=13/3, fig.height=2}
-node_colors <- tribble(
-  ~name, ~type,
-  "D", "Outcome",
-  "I", "Organizational factor",
-  "F", "Organizational factor",
-  "O", "Organizational factor",
-  "G", "Structural factor"
-)
-
-# Set up DAG structure
-theory_dag <- dagify(D ~ I + F + O + G,
-                     G ~ I + F,
-                     outcome = "D",
-                     exposure = "C") %>% 
-  tidy_dagitty(layout = "dh", seed = 1234)
-
-# Add node types/colors to DAG data
-theory_dag$data <- theory_dag$data %>% 
-  left_join(node_colors, by = "name")
-
-# Make DAG plot
-plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
-  geom_dag_point(size = 6, mapping = aes(color = type)) +
-  geom_dag_edges(start_cap = circle(4, "mm"),
-                 end_cap = circle(4, "mm")) +
-  geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
-  scale_adjusted() +
-  theme_ngo() +
-  theme(panel.grid = element_blank(),
-        panel.border = element_blank(),
-        axis.title = element_blank(),
-        axis.text = element_blank())
-
-# Show and save plot
-plot_dag
-ggsave(plot_dag, filename = here("analysis", "output", "figures", "causal-path.pdf"),
-       width = 13/3, height = 2, units = "in", device = cairo_pdf)
-ggsave(plot_dag, filename = here("analysis", "output", "figures", "causal-path.png"),
-       width = 13/3, height = 2, units = "in", type = "cairo", dpi = 300)
-```
-
 # Load data and model output
@@
 intercept <- 0                           # Intercept-only
-public_affairs <- 1                       # Public affairs
+public_affairs <- 0                       # Public affairs
 political_ideology <- 0                   # Political ideology
 social_views <- 0                         # Social views
-charity_voluntarism <- 0                  # Charity and voluntarism
+charity_voluntarism <- 1                  # Charity and voluntarism
 demographics <- 0                         # Demographics
@@
 social_views <- 0                         # Social views
-charity_voluntarism <- 0                  # Charity and voluntarism
+charity_voluntarism <- 1                  # Charity and voluntarism
 demographics <- 0                         # Demographics
@@
 # Plot marginals
-if (intercept == 1) {
-  draws %>% 
-    mutate(
-      levels = factor(i, labels = level_labels)
-    ) %>%
-    ggplot(aes(x = Theta, y = levels)) + 
-    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
-    # geom_halfeyeh(.width = .95) +
-    geom_vline(xintercept = 0, color = "grey") +
-    labs(y = "Attribute Levels")
-}
+# if (intercept == 1) {
+#   draws %>% 
+#     mutate(
+#       levels = factor(i, labels = level_labels)
+#     ) %>%
+#     ggplot(aes(x = Theta, y = levels)) + 
+#     geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+#     # geom_halfeyeh(.width = .95) +
+#     geom_vline(xintercept = 0, color = "grey") +
+#     labs(y = "Attribute Levels")
+# }
 
-if (intercept != 1) {
-  draws %>% 
-    filter(j != 1) %>% 
-    mutate(
-      levels = factor(i, labels = level_labels), 
-      covariates = factor(j, labels = covariate_labels)  
-    ) %>%
-    ggplot(aes(x = Theta, y = covariates)) +
-       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
-       # geom_halfeyeh(.width = .95) +
-       geom_vline(xintercept = 0, color = "white") +
-       labs(y = "Covariates") +
-       facet_wrap(~ levels, ncol = 5)
-}
+# if (intercept != 1) {
+#   draws %>% 
+#     filter(j != 1) %>% 
+#     mutate(
+#       levels = factor(i, labels = level_labels), 
+#       covariates = factor(j, labels = covariate_labels)  
+#     ) %>%
+#     ggplot(aes(x = Theta, y = covariates)) +
+#        geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+#        # geom_halfeyeh(.width = .95) +
+#        geom_vline(xintercept = 0, color = "white") +
+#        labs(y = "Covariates") +
+#        facet_wrap(~ levels, ncol = 5)
+# }
 
@@
 
+As an experiment, it might be helpful to use a heatmap to identify where there are significant differences in the non-intercept models, which can then be narrowed down using the marginal plots.
+
+```{r heatmaps}
+if (public_affairs == 1) plot_title <- paste("Public Affairs")
+if (political_ideology == 1) plot_title <- paste("Political Ideology")
+if (social_views == 1) plot_title <- paste("Social Views")
+if (charity_voluntarism == 1) plot_title <- paste("Covariates related to charity and voluntarism")
+if (demographics == 1) plot_title <- paste("Demographics")
+if (public_political == 1) plot_title <- paste("Public Affairs and Political Ideology")
+if (public_political_social == 1) plot_title <- paste("Public Affairs, Political Ideology, and Social Views")
+if (public_political_social_charity == 1) plot_title <- paste("Public Affairs, Political Ideology, Social Views, and Charity and Voluntarism")
+if (public_political_social_charity_demo == 1) plot_title <- paste("Public Affairs, Political Ideology, Social Views, Charity and Voluntarism, and Demographics")
+
+if (charity_voluntarism == 1) {
+  j_labels <- tribble(
+    ~j, ~j_label,
+    2, "Importance of trusting charities", 
+    3, "Trust charities", 
+    4, "Frequency of donation", 
+    5, "Amount of donation", 
+    6, "Volunteered", 
+    7, "Volunteer frequency", 
+    8, "Personal involvement in activism", 
+    9, "Family involvement in activism", 
+    10, "Membership in church", 
+    11, "Membership in sports", 
+    12, "Membership in art, music, or educational organization", 
+    13, "Membership in labor union", 
+    14, "Membership in political party", 
+    15, "Membership in envrionmental organization", 
+    16, "Membership in professional association", 
+    17, "Membership in humanitarian organization", 
+    18, "Membership in consumer organization", 
+    19, "Membership in other organization"
+  ) %>% 
+    mutate(j_label = fct_inorder(j_label))
+}
+
+if (intercept != 1) {
+  # Posterior means.
+  posterior_means <- draws %>% 
+    filter(j != 1) %>% 
+    left_join(j_labels, by = "j") %>% 
+    left_join(level_lookup, by = "i") %>% 
+    mutate(
+      levels = factor(i, labels = level_labels), 
+      # covariates = factor(j, labels = covariate_labels)
+      covariates = factor(j, labels = 1:length(covariate_labels))
+    ) %>% 
+    group_by(category, attribute, j_label) %>% 
+    summarize(
+      mean = mean(Theta),
+      ci_lower = quantile(Theta, .025),
+      ci_upper = quantile(Theta, .975),
+      gt_zero = if_else(ci_lower > 0 & ci_upper > 0, 1, 0),
+      lt_zero = if_else(ci_lower < 0 & ci_upper < 0, -1, 0)
+    )
+
+  # Heatmap of Theta matrix.
+  plot_heatmap <- posterior_means %>% 
+    mutate(
+      gt_lt_zero = gt_zero + lt_zero,
+      Coefficients = factor(
+        gt_lt_zero, 
+        levels = -1:1,
+        labels = c("Negative", "Not Significant", "Positive"))
+    ) %>% 
+    ggplot(aes(x = j_label, y = attribute, fill = Coefficients)) +
+    geom_tile(color = "white", size = 0.25) +
+    # scale_fill_brewer(palette = "Blues") +
+    scale_fill_manual(values = c(clrs$orange, "grey80", clrs$olive)) +
+    scale_x_discrete(expand = c(0.001, 0.001)) +
+    scale_y_discrete(expand = c(0.001, 0.001)) +
+    # guides(fill = guide_legend(override.aes = list(key.height = 0.5, key.width = 0.5))) +
+    guides(fill = guide_legend(keywidth = 0.5, keyheight = 0.5)) +
+    theme_ngo(base_size = 14) +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
+          legend.position = "bottom",
+          strip.placement = "outside") +
+    labs(
+      title = plot_title,
+      x = "Covariates",
+      y = "Attribute Levels"
+    ) + 
+    # facet_wrap(~ category, ncol = 1, scales = "free_y")
+    facet_grid(vars(category), scales = "free_y", space = "free_y")
+}
+
+plot_heatmap
+ggsave(plot_heatmap, filename = here("analysis", "output", "figures", "q2-heatmap.pdf"),
+       width = 26/3, height = 6.5, units = "in", device = cairo_pdf)
+ggsave(plot_heatmap, filename = here("analysis", "output", "figures", "q2-heatmap.png"),
+       width = 26/3, height = 6.5, units = "in", type = "cairo", dpi = 300)
+
+# Save plot
+if (public_affairs == 1) file_name <- paste("public-affairs_coefficient-matrix.png")
+if (political_ideology == 1) file_name <- paste("political-ideology_coefficient-matrix.png")
+if (social_views == 1) file_name <- paste("social-views_coefficient-matrix.png")
+if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_coefficient-matrix.png")
+if (demographics == 1) file_name <- paste("demographics_coefficient-matrix.png")
+if (public_political == 1) file_name <- paste("public-political_coefficient-matrix.png")
+if (public_political_social == 1) file_name <- paste("public-political-social_coefficient-matrix.png")
+if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_coefficient-matrix.png")
+if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_coefficient-matrix.png")
+ggsave(
+  file_name,
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
+```
+
 # Original computing environment

### 2020-01-14 analysis/03b_hypotheses.Rmd
Consistent and pretty graphs and tables

@@
     mutate(
-      levels = factor(i, labels = level_labels)
+      levels = factor(i, labels = level_labels),
+      Theta_exp = exp(Theta)
     ) %>%
     filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>% 
-    ggplot(aes(x = Theta, y = levels)) + 
+    ggplot(aes(x = Theta_exp, y = levels)) + 
     geom_halfeyeh(.width = .95) +
-    geom_vline(xintercept = 0, color = "grey") +
+    geom_vline(xintercept = 1, color = "grey") +
     labs(y = "Attribute Levels")
@@
     filter(levels == str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"))) %>% 
-    ggplot(aes(x = Theta, y = levels)) +
+    ggplot(aes(x = exp(Theta), y = levels)) +
     geom_halfeyeh(.width = .95) +
-    geom_vline(xintercept = 0, color = "grey") +
+    geom_vline(xintercept = 1, color = "grey") +
     labs(y = "Attribute Levels")

### 2020-01-14 analysis/04_figs_tables.Rmd
Consistent and pretty graphs and tables

---
title: "Figures and tables for paper"
author: "Andrew Heiss, Marc Dotson, and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
    pandoc_args:
      - "--default-image-extension=png"
editor_options: 
  chunk_output_type: console
---

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(magrittr)
library(donorheuristics)
# library(rstan)
# library(bayesplot)
library(tidybayes)
library(broom)
# library(bayesm)
# library(ggridges)
library(ggraph)
library(ggdag)
library(pander)
library(patchwork)
library(scales)
library(here)

# General settings
source(here("analysis", "options.R"))

# Make all the randomness reproducible
set.seed(1234)

# Load data
results <- read_rds(here("data", "derived_data", "final_data.rds"))

# Name labels
level_labels <- c(
  str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
  str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
  str_c("Organizational practices: ", c("Financial transparency", "Accountability")),
  str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants")),
  str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))
)

level_lookup <- tibble(levels = level_labels) %>% 
  separate(levels, c("category", "attribute"), sep = ": ") %>% 
  mutate(attributes_long = paste0(category, ": ", attribute),
         i = 1:n()) %>% 
  mutate_at(vars(category, attribute, attributes_long), list(fct_inorder))

draws <- read_rds(here("analysis", "output", "posterior_draws", 
                       "intercept_noncentered.rds")) %>% 
  mutate(model = "Intercept only") %>% 
  left_join(level_lookup, by = "i")
```

```{r}
diff_cols <- function(col1, col2) {
  posterior_diffs <- draws %>% 
    filter(attribute %in% c({{col1}}, {{col2}})) %>% 
    select(.chain, .iteration, Theta, attribute) %>% 
    pivot_wider(names_from = "attribute", values_from = "Theta") %>% 
    mutate(diff_theta = .[[4]] - .[[3]],
           diff_theta_e = exp(.[[4]]) - exp(.[[3]]))

  diff_theta <- mean(posterior_diffs$diff_theta_e)
  p_greater0 <- mean(posterior_diffs$diff_theta_e > 0)
  p_less0 <- mean(posterior_diffs$diff_theta_e < 0)
  p_not0 <- ifelse(median(posterior_diffs$diff_theta_e) > 0, p_greater0, p_less0)

  phrase <- paste0("∆θ = ", round(diff_theta, 3), "; p(∆ ≠ 0) = ", round(p_not0, 3))

  return(list(posterior_diffs = posterior_diffs, diff_theta = diff_theta,
              p_greater0 = p_greater0, p_less0 = p_less0, p_not0 = p_not0,
              phrase = phrase))
}
```

# Causal pathway

Our theory and hypotheses are laid out in the causal pathway below. Organizational factors (**O**, or organizational practices like financial disclosure and accountability practices; **I**, or issue area; and **F**, or funding) all influence the decision to donate (**D**). Structural factors like an NGO's relationship with its host government (**G**) also influence donation behavior, but the relationship itself is shaped by both funding and issue area.

```{r causal-dag, fig.width=13/3, fig.height=2}
node_colors <- tribble(
  ~name, ~type,
  "D", "Outcome",
  "I", "Organizational factor",
  "F", "Organizational factor",
  "O", "Organizational factor",
  "G", "Structural factor"
) %>% 
  mutate(type = fct_inorder(type))

# Set up DAG structure
theory_dag <- dagify(D ~ I + F + O + G,
                     G ~ I + F,
                     outcome = "D",
                     exposure = "C") %>% 
  tidy_dagitty(layout = "dh", seed = 1234)

# Add node types/colors to DAG data
theory_dag$data <- theory_dag$data %>% 
  left_join(node_colors, by = "name")

# Make DAG plot
plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_point(size = 6, mapping = aes(color = type)) +
  geom_dag_edges(start_cap = circle(4, "mm"),
                 end_cap = circle(4, "mm")) +
  geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
  scale_color_manual(values = c(clrs$blue, clrs$red, clrs$orange), name = NULL) +
  theme_ngo() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank())

# Show and save plot
plot_dag
ggsave(plot_dag, filename = here("analysis", "output", "figures", "causal-path.pdf"),
       width = 13/3, height = 2, units = "in", device = cairo_pdf)
ggsave(plot_dag, filename = here("analysis", "output", "figures", "causal-path.png"),
       width = 13/3, height = 2, units = "in", type = "cairo", dpi = 300)
```

# Sample details

```{r}
vars_to_summarize <- tribble(
  ~category, ~variable, ~clean_name,
  "Demographics", "Q5.12", "Gender",
  "Demographics", "Q5.17", "Age",
  "Demographics", "Q5.13", "Marital status",
  "Demographics", "Q5.14", "Education",
  "Demographics", "Q5.15", "Income",
  "Attitudes toward charity", "Q2.5", "Frequency of donating to charity",
  "Attitudes toward charity", "Q2.6", "Amount of donations to charity last year",
  "Attitudes toward charity", "Q2.7_f", "Importance of trusting charities",
  "Attitudes toward charity", "Q2.8_f", "Level of trust in charities",
  "Attitudes toward charity", "Q2.10", "Frequency of volunteering",
  "Politics, ideology, and religion", "Q2.1", "Frequency of following national news",
  "Politics, ideology, and religion", "Q5.7", "Traveled to a developing country",
  "Politics, ideology, and religion", "Q5.1", "Voted in last election",
  "Politics, ideology, and religion", "Q5.6_f", "Trust in political institutions and the state",
  "Politics, ideology, and religion", "Q5.2_f", "Political ideology",
  "Politics, ideology, and religion", "Q5.4", "Involvement in activist causes",
  "Politics, ideology, and religion", "Q5.8", "Frequency of attending religious services",
  "Politics, ideology, and religion", "Q5.9", "Importance of religion"
)

summarize_factor <- function(x) {
  output <- table(x) %>% 
    as_tibble() %>% 
    magrittr::set_colnames(., c("level", "count")) %>% 
    mutate(level = factor(level, levels = levels(x), ordered = TRUE)) %>%
    mutate(prop = count / sum(count),
           nice_prop = scales::percent(prop))

  return(list(output))
}

participant_summary <- results %>% 
  select(one_of(vars_to_summarize$variable)) %>% 
  summarize_all(summarize_factor) %>% 
  pivot_longer(cols = everything(), names_to = "variable", values_to = "details") %>% 
  left_join(vars_to_summarize, by = "variable") %>% 
  unnest(details) %>% 
  mutate(level = as.character(level)) %>% 
  mutate(level = case_when(
    variable == "Q2.7_f" & level == "1" ~ "1 (not important)",
    variable == "Q2.7_f" & level == "7" ~ "7 (important)",
    variable == "Q2.8_f" & level == "1" ~ "1 (no trust)",
    variable == "Q2.8_f" & level == "7" ~ "7 (complete trust)",
    variable == "Q5.6_f" & level == "1" ~ "1 (no trust)",
    variable == "Q5.6_f" & level == "7" ~ "7 (complete trust)",
    variable == "Q5.2_f" & level == "1" ~ "1 (extremely liberal)",
    variable == "Q5.2_f" & level == "7" ~ "7 (extremely conservative)",
    variable == "Q5.15" & level == "Less than median" ~ "Less than 2017 national median ($61,372)",
    variable == "Q5.17" & level == "Less than median" ~ "Less than 2017 national median (36)",
    TRUE ~ level
  )) %>% 
  mutate(clean_name_shrunk = ifelse(clean_name == lag(clean_name), "", clean_name),
         clean_name_shrunk = ifelse(is.na(clean_name_shrunk), 
                                    clean_name[1], 
                                    clean_name_shrunk),
         category_shrunk = ifelse(category == lag(category), "", category),
         category_shrunk = ifelse(is.na(category_shrunk), 
                                    category[1], 
                                    category_shrunk))
```

```{r results="asis"}
participant_summary %>% 
  select(" " = category_shrunk, "  " = clean_name_shrunk, 
         "Response" = level, "N" = count, "%" = nice_prop) %>% 
  pandoc.table.return(caption = 'Summary of individual respondent characteristics {#tbl:sample-details}',
                      justify = "lllcc") %T>%
  cat() %>%
  cat(file = here("analysis", "output", "tables", "tbl-sample-details.md"))
```

# Results

## Baseline probabilities

```{r probs-baseline, fig.width=4.5, fig.height=4}
orgs <- draws %>% 
  filter(category == "Organization") %>% 
  mutate(prob = plogis(Theta))

fig_baseline <- ggplot(orgs, aes(x = prob, y = attribute)) +
  geom_halfeyeh(.width = 0.95, aes(fill = attribute)) +
  scale_fill_manual(values = c(clrs$yellow, clrs$olive, clrs$lime, clrs$red),
                    guide = FALSE) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Baseline probability of selecting organization", y = NULL) +
  theme_ngo()

fig_baseline
ggsave(fig_baseline, filename = here("analysis", "output", "figures", "probs-org.pdf"),
       width = 13/3, height = 3, units = "in", device = cairo_pdf)
ggsave(fig_baseline, filename = here("analysis", "output", "figures", "probs-org.png"),
       width = 13/3, height = 3, units = "in", type = "cairo", dpi = 300)
```

```{r}
orgs %>% 
  group_by(attribute) %>% 
  nest() %>% 
  mutate(tidy = data %>% map(~ median_hdci(.$prob))) %>% 
  unnest(tidy)
```

## Coefficients and marginal effects

```{r first-hypotheses-coefficients, fig.width=26/3, fig.height=5.5}
diff_refugee_hr <- diff_cols("Refugee relief", "Human rights")
diff_hr_env <- diff_cols("Human rights", "Environment")
diff_env_refugee <- diff_cols("Environment", "Refugee relief")

plot_issue <- ggplot(filter(draws, category == "Issue area"), 
                     aes(x = exp(Theta), y = attribute)) + 
  stat_halfeyeh(.width = 0.95, fill = clrs$blue) +
  geom_vline(xintercept = 1, color = clrs$red, size = 0.5, linetype = "dotted") +
  # annotate(geom = "linerange", x = 0.7, ymin = 2.1, ymax = 2.9, size = 0.25) +
  # annotate(geom = "label", x = 0.7, y = 2.5, hjust = 0.5, size = pts(7),
  #          family = "Roboto Condensed Light",
  #          label = diff_refugee_hr$phrase) +
  # annotate(geom = "linerange", x = 0.8, ymin = 1.1, ymax = 1.9, size = 0.25) +
  # annotate(geom = "label", x = 0.8, y = 1.5, hjust = 0.5, size = pts(7),
  #          family = "Roboto Condensed Light",
  #          label = diff_hr_env$phrase) +
  # annotate(geom = "linerange", x = 0.585, ymin = 1.1, ymax = 2.9, size = 0.25) +
  # annotate(geom = "label", x = 0.585, y = 2.05, hjust = 0.5, size = pts(7),
  #          family = "Roboto Condensed Light",
  #          label = diff_env_refugee$phrase) +
  labs(x = "exp(θ)", y = NULL,
       title = "Issue area",
       subtitle = "Reference group = emergency response") +
  theme_ngo()

diff_govt_richpeople <- diff_cols("Government grants", 
                                  "Handful of wealthy private donors")

plot_funding <- ggplot(filter(draws, category == "Funding sources"), 
                       aes(x = exp(Theta), y = attribute)) + 
  geom_halfeyeh(.width = 0.95, fill = clrs$maroon) +
  geom_vline(xintercept = 1, color = clrs$red, size = 0.5, linetype = "dotted") +
  # annotate(geom = "linerange", x = 0.825, ymin = 1.1, ymax = 1.9, size = 0.25) +
  # annotate(geom = "label", x = 0.825, y = 1.5, hjust = 0.5, size = pts(7),
  #          family = "Roboto Condensed Light",
  #          label = diff_govt_richpeople$phrase) +
  labs(x = "exp(θ)", y = NULL,
       title = "Funding sources",
       subtitle = "Reference group = many small private donations") +
  theme_ngo()

diff_account_trans <- diff_cols("Accountability", "Financial transparency")

plot_org <- ggplot(filter(draws, category == "Organizational practices"), 
                   aes(x = exp(Theta), y = attribute)) + 
  geom_halfeyeh(.width = 0.95, fill = clrs$orange) +
  geom_vline(xintercept = 1, color = clrs$red, size = 0.5, linetype = "dotted") +
  # annotate(geom = "linerange", x = 1.85, ymin = 1.1, ymax = 1.9, size = 0.25) +
  # annotate(geom = "label", x = 1.85, y = 1.5, hjust = 0.5, size = pts(7),
  #          family = "Roboto Condensed Light",
  #          label = diff_account_trans$phrase) +
  labs(x = "exp(θ)", y = NULL,
       title = "Organizational practices",
       subtitle = "Reference groups = no accountability; no transparency") +
  theme_ngo()

diff_govt <- diff_cols("Under crackdown", "Criticized")

plot_government <- ggplot(filter(draws, category == "Relationship with host government"), 
                          aes(x = exp(Theta), y = attribute)) + 
  geom_halfeyeh(.width = 0.95, fill = clrs$teal) +
  geom_vline(xintercept = 1, color = clrs$red, size = 0.5, linetype = "dotted") +
  # annotate(geom = "linerange", x = 0.75, ymin = 1.1, ymax = 1.9, size = 0.25) +
  # annotate(geom = "label", x = 0.75, y = 1.5, hjust = 0.5, size = pts(7),
  #          family = "Roboto Condensed Light",
  #          label = diff_govt$phrase) +
  labs(x = "exp(θ)", y = NULL,
       title = "Relationship with host government",
       subtitle = "Reference group = friendly relationship with government") +
  theme_ngo()

plot_first_hypotheses <- (plot_org + plot_issue + plot_funding + plot_government)

plot_first_hypotheses
ggsave(plot_first_hypotheses, filename = here("analysis", "output", "figures", "results-h1-4.pdf"),
       width = 26/3, height = 5.5, units = "in", device = cairo_pdf)
ggsave(plot_first_hypotheses, filename = here("analysis", "output", "figures", "results-h1-4.png"),
       width = 26/3, height = 5.5, units = "in", type = "cairo", dpi = 300)
```

```{r}
draws %>% 
  filter(category != "Organization") %>% 
  group_by(attribute) %>% 
  nest() %>% 
  mutate(tidy = data %>% map(~ median_hdci(.$Theta))) %>% 
  unnest(tidy) %>% 
  mutate(exp_y = exp(y))
```

## Differences in means

According to Kruschke 8.4, we can look at the posterior distribution of the difference in thetas, then calculate the proportion of those differences that are greater/less than 0

$$
\operatorname{mean}(\theta_\text{Government grants} - \theta_\text{Private donors}) = 
$$

$$
\Delta \theta = 4; p(\Delta > 0) = 5
$$

```{r eval=FALSE}
col1 <- "Government grants"
col2 <- "Handful of wealthy private donors"

posterior_diffs <- draws %>% 
  filter(attribute %in% c({{col1}}, {{col2}})) %>% 
  select(.chain, .iteration, Theta, attribute) %>% 
  pivot_wider(names_from = "attribute", values_from = "Theta") %>% 
  mutate(diff_theta = .[[4]] - .[[3]],
         diff_theta_e = exp(.[[4]]) - exp(.[[3]]))

mean(posterior_diffs$diff_theta_e)

asdf <- draws %>% 
  filter(category == "Funding sources") %>% 
  select(.chain, .iteration, Theta, attribute) %>% 
  pivot_wider(names_from = "attribute", values_from = "Theta") %>% 
  mutate(diff_theta = .[[4]] - .[[3]]) %>% 
  mutate(diff_theta_e = exp(.[[4]]) - exp(.[[3]]))

draws %>% 
  filter(category == "Funding sources") %>% 
  group_by(attribute) %>% 
  summarize(bloop = exp(mean(Theta)),
            bloop1 = mean(exp(Theta)))

mean(asdf$diff_theta_e)
tidybayes::hdi(asdf$diff_theta_e)

mean(asdf$diff_theta > 0)
mean(asdf$diff_theta_e > 0)

asdf <- draws %>% 
  filter(category == "Organizational practices") %>% 
  select(.chain, .iteration, Theta, attribute) %>% 
  pivot_wider(names_from = "attribute", values_from = "Theta") %>% 
  mutate(diff_theta = .[[4]] - .[[3]]) %>% 
  mutate(diff_theta_e = exp(.[[4]]) - exp(.[[3]]))

mean(asdf$diff_theta > 0)
mean(asdf$diff_theta_e > 0)

ggplot(asdf, aes(x = diff_theta_e, y = 1)) +
  geom_halfeyeh(.width = 0.95)

draws %>% 
  filter(category == "Funding sources") %>% 
  group_by(attribute) %>% 
  summarize(bloop = mean(Theta),
            bloop1 = exp(mean(Theta)))

qwer <- draws %>% 
  filter(category == "Funding sources") %>% 
  group_by(attribute) %>% 
  nest() %>% 
  mutate(hdi = data %>% map(~ exp(tidybayes::hdi(.$Theta, .width = 0.95))))
asdf %>% 
  unnest(hdi)
mean(asdf$Theta)
tidybayes::hdi(asdf$Theta, .width = 0.95)
```

### 2020-01-14 manuscript/pandoc/bin/word_count.R
Add standalone pandoc support files

@@ -1,37 +1,67 @@
-suppressPackageStartupMessages(library(tidyverse))
+#!/usr/bin/Rscript
+
+# string::stri_count_words() counts, um, words. That's its whole job. But it
+# doesn't count them like Microsoft Word counts them, and academic publishing
+# portals tend to care about Word-like counts. For instance, Word considers
+# hyphenated words to be one word, while stringr counts them as two (and even
+# worse, stringi counts / as word boundaries, so URLs can severely inflate your
+# word count).
+#
+# Also, academic writing typically doesn't count the title, abstract, table
+# text, figure captions, or equations as words in the manuscript (and it
+# SHOULDN'T count bibliographies, but it always seems to ugh).
+#
+# This script parses the rendered manuscript HTML, removes extra elements,
+# adjusts the text so that stringi treats it more like Word, and then provides a
+# more accurate word count.
+
+suppressPackageStartupMessages(library(magrittr))
+suppressPackageStartupMessages(library(stringr))
+suppressPackageStartupMessages(library(purrr))
 suppressPackageStartupMessages(library(rvest))
-suppressPackageStartupMessages(library(here))
 suppressPackageStartupMessages(library(stringi))
 
-ms_raw <- read_html(here("manuscript", "arnova.html"))
+args <- commandArgs(trailingOnly = TRUE)
+
+if (length(args) < 1) {
+  ms_file <- "paper.html"
+} else {
+  ms_file <- args[1]
+}
+
+# Read the HTML file
+ms_raw <- read_html(ms_file)
 
 # Extract just the article, ignoring title, abstract, etc.
-ms <- ms_raw %>% 
-  html_nodes("article") 
+ms <- ms_raw %>%
+  html_nodes("article")
 
 # Get rid of figures, tables, and math
 xml_remove(ms %>% html_nodes("figure"))
 xml_remove(ms %>% html_nodes("table"))
 xml_remove(ms %>% html_nodes(".display"))  # Block math
-xml_replace(ms %>% html_nodes(".inline"), read_xml("<span>MATH</span>")) %>% 
+xml_replace(ms %>% html_nodes(".inline"), read_xml("<span>MATH</span>")) %>%
   invisible()
 
 # Go through each child element in the article and extract it
 ms_cleaned_list <- map(html_children(ms), ~ {
-  .x %>% 
-    html_text(trim = TRUE) %>% 
+  .x %>%
[…]

### 2020-01-22 analysis/05_market_simulator.Rmd
Added first iteration of the dashboard

---
title: "Data Dashboard"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
runtime: shiny
---

```{r packages, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(flexdashboard)
library(plotly)
```

Column {data-width=200 .sidebar}
-------------------------------------------------------------------------------------

```{r Inputs}

```

Row
------------------------------------------------------------------------------------

```{r plot}
#barchart <- ggplot()

#ggplotly(barchart)
```

Row 
--------------------------------------------------------------------------------------
### Amnest International Expected Utility

```{r}
renderValueBox({
  ai_exp_util <- 15
  valueBox(ai_exp_util,
           color = "#FFC30B")
})
```

### Greenpeace Expected Utility

```{r}
renderValueBox({
  gp_exp_util <- 15
  valueBox(gp_exp_util,
           color = "green")
})
```

### Oxfam Expected Utility

```{r}
renderValueBox({
  ox_exp_util <- 15
  valueBox(ox_exp_util,
           color = "teal")
})
```

### Redcross Expected Utility

```{r}
renderValueBox({
  rc_exp_util <- 15
  valueBox(rc_exp_util,
           color = "maroon")
})
```

Row 
--------------------------------------------------------------------------------------

### Amnesty International Expected Donors

```{r echo=FALSE}
renderGauge({
  ai_rate <- 15
  gauge(ai_rate, 
        min = 0, 
        max = 1000,
        gaugeSectors(colors = "#FFC30B"))
})
```

### Greenpeace Expected Donors

```{r echo=FALSE}
renderGauge({
  gp_rate <- 15
  gauge(gp_rate, 
        min = 0, 
        max = 1000,
        gaugeSectors(colors = "green"))
})
```

### Oxfam Expected Donors

```{r echo=FALSE}
renderGauge({
  ox_rate <- 15
  gauge(ox_rate, 
        min = 0, 
        max = 1000,
        gaugeSectors(colors = "teal"))
})
```

### Red Cross Expected Donors

```{r echo=FALSE}
renderGauge({
  rc_rate <- 15
  gauge(rc_rate, 
        min = 0, 
        max = 1000,
        gaugeSectors(colors = "maroon"))
})
```

Row 
--------------------------------------------------------------------------------------

### Amnesty International Inputs

```{r echo=FALSE}
selectInput("ai_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

selectInput("ai_fin_trans",
            label = "Select Financial transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"))

selectInput("ai_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in financial accountability"))

selectInput("ai_funding",
            label = "Select Funding source:",
            choices = c("Handful of wealthy private donors",
                        "Government Grants",
                        "Many small private donations"))

selectInput("ai_gov_relat",
            label = "Select Relationship with host government",
            choices = c("Friendly relationship with government",
                        "Criticized by government", 
                        "Under government crackdown"))
```

### Greenpeace Inputs

```{r echo=FALSE}
selectInput("gp_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

selectInput("gp_fin_trans",
            label = "Select Financial transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"))

selectInput("gp_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in financial accountability"))

selectInput("gp_funding",
            label = "Select Funding source:",
            choices = c("Handful of wealthy private donors",
                        "Government Grants",
                        "Many small private donations"))

selectInput("gp_gov_relat",
            label = "Select Relationship with host government",
            choices = c("Friendly relationship with government",
                        "Criticized by government", 
                        "Under government crackdown"))
```

### Oxfam Inputs

```{r echo=FALSE}
selectInput("ox_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

selectInput("ox_fin_trans",
            label = "Select Financial transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"))

selectInput("ox_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in financial accountability"))

selectInput("ox_funding",
            label = "Select Funding source:",
            choices = c("Handful of wealthy private donors",
                        "Government Grants",
                        "Many small private donations"))

selectInput("ox_gov_relat",
            label = "Select Relationship with host government",
            choices = c("Friendly relationship with government",
                        "Criticized by government", 
                        "Under government crackdown"))
```

### Red Cross Inputs

```{r echo=FALSE}
selectInput("rc_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

selectInput("rc_fin_trans",
            label = "Select Financial transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"))

selectInput("rc_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in financial accountability"))

selectInput("rc_funding",
            label = "Select Funding source:",
            choices = c("Handful of wealthy private donors",
                        "Government Grants",
                        "Many small private donations"))

selectInput("rc_gov_relat",
            label = "Select Relationship with host government",
            choices = c("Friendly relationship with government",
                        "Criticized by government", 
                        "Under government crackdown"))
```

### 2020-01-23 analysis/05_market_simulator.Rmd
Loaded in the incercept model and got the means for the data, next we need to: 1. drop missing variables for the inputs 2. set up the matrix multiplication for the betas 3. set the inputs to work with

@@
 library(plotly)
+library(here)
+```
+
+```{r load data}
+intercept_mod <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_noncentered.rds')) %>% 
+  group_by(i) %>% 
+  summarize(theta_mean = mean(Theta))
+
 ```

### 2020-01-27 analysis/05_market_simulator.Rmd
Added levels

--- 2020-01-22 analysis/05_market_simulator.Rmd
@@
 library(plotly)
+library(shiny)
+library(here)
+```
+
+```{r load data}
+intercept_mod <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_noncentered.rds')) %>% 
+  group_by(i) %>% 
+  summarize(theta_mean = mean(Theta))
+intercept_mod
+#Levels (This is a guess):            Means:
+#   1. Amnesty International          0.805
+#   2. Greenpeace                     0.923
+#   3. Oxfam                          0.620
+#   4. Red Cross                      1.820
+#   5. Environment                   -0.444
+#   6. Human Rights                  -0.164
+#   7. Refugee Relief                -0.582
+#   8. Financially Transparent        1.080
+#   9. Accountable                    1.130
+#   10. Small wealthy donars         -0.376
+#   11. Government Grants            -0.252
+#   12. Critized by Government       -0.663
+#   13. Under Government Crackdown   -1.010
+
 ```

### 2020-02-10 analysis/05_market_simulator.Rmd
Working on how to set up matrix multiplication
Created a reactive dataframe based on user inputs

@@
   summarize(theta_mean = mean(Theta))
-intercept_mod
 #Levels (This is a guess):            Means:
@@
 #   12. Critized by Government       -0.663
-#   13. Under Government Crackdown   -1.010
+#   13. Under Government Crackdown   -1.011
 
+beta <- as.data.frame(matrix(rep(0), nrow = 13))
+beta$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human Rights", "Refugee Relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")
+
+####################################################################################
+
+df <- reactive({
+  #Amnesty International
+    beta$ai_value <- 0
+    beta$ai_value[beta$levels == 'Amnesty International'] <- 1
+    beta$ai_value[beta$levels %in% input$ai_issue] <- 1
+    beta$ai_value[beta$levels %in% input$ai_fin_trans] <- 1
+    beta$ai_value[beta$levels %in% input$ai_account] <- 1
+    beta$ai_value[beta$levels %in% input$ai_funding] <- 1
+    beta$ai_value[beta$levels %in% input$ai_gov_relat] <- 1
+  #Greenpeace
+    beta$gp_value <- 0
+    beta$gp_value[beta$levels == 'Greenpeace'] <- 1
+    beta$gp_value[beta$levels %in% input$gp_issue] <- 1
+    beta$gp_value[beta$levels %in% input$gp_fin_trans] <- 1
+    beta$gp_value[beta$levels %in% input$gp_account] <- 1
+    beta$gp_value[beta$levels %in% input$gp_funding] <- 1
+    beta$gp_value[beta$levels %in% input$gp_gov_relat] <- 1
+  #Oxfam
+    beta$ox_value <- 0
+    beta$ox_value[beta$levels == 'Oxfam'] <- 1
+    beta$ox_value[beta$levels %in% input$ox_issue] <- 1
+    beta$ox_value[beta$levels %in% input$ox_fin_trans] <- 1
+    beta$ox_value[beta$levels %in% input$ox_account] <- 1
+    beta$ox_value[beta$levels %in% input$ox_funding] <- 1
+    beta$ox_value[beta$levels %in% input$ox_gov_relat] <- 1
+  #Redcross
+    beta$rc_value <- 0
+    beta$rc_value[beta$levels == 'Red Cross'] <- 1
+    beta$rc_value[beta$levels %in% input$rc_issue] <- 1
+    beta$rc_value[beta$levels %in% input$rc_fin_trans] <- 1
+    beta$rc_value[beta$levels %in% input$rc_account] <- 1
+    beta$rc_value[beta$levels %in% input$rc_funding] <- 1
+    beta$rc_value[beta$levels %in% input$rc_gov_relat] <- 1
+    beta
+
+})
+
+output$data <- renderTable({
+    df()
+})
+
+renderTable({
+    df()
+})
+
+```
+
+```{r matrix multiplication, eval=FALSE, include=FALSE}
+library(shiny)
+
+beta <- data.frame(
+  value = c(0,0,0),
+  levels = c("Environment", "Human rights", "Refugee relief")
+)
+
+ui <- fluidPage(
+  fluidRow(
+    column(6,
+      selectInput("ai_issue", 
+                  label = "Select Issue Area:",
+                  choices = beta$levels,
+                  multiple = TRUE)
+    ),
+    column(6,
+      tableOutput("data")
+    )
+  )
+)
+
+server = function(input, output) {
+
+  df <- reactive({
+    beta$value[beta$levels %in% input$ai_issue] <- 1
+    beta
+  })
+
+  output$data <- renderTable({
+    df()
+  })
+}
 ```
@@
 --------------------------------------------------------------------------------------
-### Amnest International Expected Utility
+### Amnesty International Expected Utility
 
@@
             label = "Select Funding source:",
-            choices = c("Handful of wealthy private donors",
-                        "Government Grants",
-                        "Many small private donations"))
+            choices = c("Many small private donations",
+                        "Handful of wealthy private donors",
+                        "Government Grants"))
 

### 2020-03-03 analysis/05_market_simulator.Rmd
Fixed values

@@
 beta <- as.data.frame(matrix(rep(0), nrow = 13))
-beta$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human Rights", "Refugee Relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")
+beta$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")
 
+testlevels <- as.data.frame(matrix(0, 12, 1))
+testlevels[c(3,4,8),] <- 1
+testlevels[11,] <- 22.4
+testWeights <- c(.4, .15, .53, .19, .32, .09, .00, .1,.14, .16, -.08, 1.24)
+testWeights <- as.data.frame(matrix(testWeights, nrow = 12, ncol = 1))
+
+exp(t(testlevels) %*% as.matrix(testWeights))
 ####################################################################################
@@
 
-output$data <- renderTable({
+renderTable({
     df()
@@
 renderTable({
-    df()
+    choice = df()
+    t(choice[,3]) %*% as.matrix(intercept_mod[,2])
+
+})
+
+ai_util <- renderTable({
+    choice = df()
+    exp(t(choice[,3]) %*% as.matrix(intercept_mod[,2]))
+
 })
@@
 renderValueBox({
-  ai_exp_util <- 15
+  choice = df()
+  ai_exp_util <- round(exp(t(choice[,3]) %*% as.matrix(intercept_mod[,2])),2)
   valueBox(ai_exp_util,
@@
 renderValueBox({
-  gp_exp_util <- 15
+  choice = df()
+  gp_exp_util <- round(exp(t(choice[,4]) %*% as.matrix(intercept_mod[,2])),2)
   valueBox(gp_exp_util,
@@
 renderValueBox({
-  ox_exp_util <- 15
+  choice = df()
+  ox_exp_util <- round(exp(t(choice[,5]) %*% as.matrix(intercept_mod[,2])),2)
   valueBox(ox_exp_util,
@@
 renderValueBox({
-  rc_exp_util <- 15
+  choice = df()
+  rc_exp_util <- round(exp(t(choice[,6]) %*% as.matrix(intercept_mod[,2])),2)
   valueBox(rc_exp_util,
@@
 renderGauge({
-  ai_rate <- 15
+  choice = df()
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_mod[,2])),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_mod[,2])),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_mod[,2])),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_mod[,2])),2)
+
+  ai_rate <- round(1000 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
   gauge(ai_rate, 
@@
 renderGauge({
-  gp_rate <- 15
+  choice = df()
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_mod[,2])),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_mod[,2])),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_mod[,2])),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_mod[,2])),2)
+
+  gp_rate <- round(1000 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
   gauge(gp_rate, 
@@
 renderGauge({
-  ox_rate <- 15
+  choice = df()
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_mod[,2])),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_mod[,2])),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_mod[,2])),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_mod[,2])),2)
+
+  ox_rate <- round(1000 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
   gauge(ox_rate, 
@@
 renderGauge({
-  rc_rate <- 15
+  choice = df()
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_mod[,2])),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_mod[,2])),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_mod[,2])),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_mod[,2])),2)
+
+  rc_rate <- round(1000 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
   gauge(rc_rate, 
@@
             label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in accountability",
+            choices = c("Doesn’t engage in financial accountability",
                         "Engages in financial accountability"))

### 2020-03-04 analysis/05_market_simulator.Rmd
Fixed the formatting and chart

@@
     orientation: rows
-    vertical_layout: fill
+    vertical_layout: scroll
 runtime: shiny
@@
 
-testlevels <- as.data.frame(matrix(0, 12, 1))
-testlevels[c(3,4,8),] <- 1
-testlevels[11,] <- 22.4
-testWeights <- c(.4, .15, .53, .19, .32, .09, .00, .1,.14, .16, -.08, 1.24)
-testWeights <- as.data.frame(matrix(testWeights, nrow = 12, ncol = 1))
-
-exp(t(testlevels) %*% as.matrix(testWeights))
 ####################################################################################
@@
     beta
-
-})
-
-renderTable({
-    df()
-})
-
-renderTable({
-    choice = df()
-    t(choice[,3]) %*% as.matrix(intercept_mod[,2])
-
-})
-
-ai_util <- renderTable({
-    choice = df()
-    exp(t(choice[,3]) %*% as.matrix(intercept_mod[,2]))
 
@@
 
-Column {data-width=200 .sidebar}
--------------------------------------------------------------------------------------
+Row
+-------------------------------------
 
-```{r Inputs}
+```{r plot}
+renderPlotly({
+  choice = df()
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_mod[,2])),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_mod[,2])),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_mod[,2])),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_mod[,2])),2)
+  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
 
+  data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate)
+  df <- as.data.frame(matrix(data, 8, 1))
+  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
+  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
+  colnames(df) <- c('Value', 'Organization', "Type")
+
+  ggplotly(ggplot(df, aes(y = Value, x = Organization, fill = Type)) +
+             geom_col() +
+             labs(x="") + 
+             #scale_fill_manual(values = c("Amnesty International" = "#FFC30B", "Greenpeace" = "#3fad48", "Oxfam" = "#006633", "Red Cross" = "#660000"))+
+             theme(legend.position = "none", axis.text.x = element_text(angle = 10, hjust = 1)) +
+             facet_wrap(~Type)
+    )
+})
 ```
@@
 Row 
-------------------------------------------------------------------------------------
-
-```{r plot}
-#barchart <- ggplot()
-
-#ggplotly(barchart)
-```
-
-Row 
---------------------------------------------------------------------------------------
+-------------------------------------
 ### Amnesty International Expected Utility
@@
   valueBox(gp_exp_util,
-           color = "green")
+           color = "#3fad48")
 })
@@
   valueBox(ox_exp_util,
-           color = "teal")
+           color = "#006633")
 })
@@
   valueBox(rc_exp_util,
-           color = "maroon")
+           color = "#660000")
 })
@@
 Row 
---------------------------------------------------------------------------------------
+-------------------------------------
 
@@
 
-  ai_rate <- round(1000 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
   gauge(ai_rate, 
         min = 0, 
-        max = 1000,
-        gaugeSectors(colors = "#FFC30B"))
+        max = 100,
+        gaugeSectors(colors = "#FFC30B"),
+        symbol = "%")
 })
@@
 
-  gp_rate <- round(1000 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
   gauge(gp_rate, 
         min = 0, 
-        max = 1000,
-        gaugeSectors(colors = "green"))
+        max = 100,
+        gaugeSectors(colors = "#3fad48"),
+        symbol = "%")
 })
@@
 
-  ox_rate <- round(1000 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
   gauge(ox_rate, 
         min = 0, 
-        max = 1000,
-        gaugeSectors(colors = "teal"))
+        max = 100,
+        gaugeSectors(colors = "#006633"),
+        symbol = "%")
 })
@@
 
-  rc_rate <- round(1000 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
   gauge(rc_rate, 
         min = 0, 
-        max = 1000,
-        gaugeSectors(colors = "maroon"))
+        max = 100,
+        gaugeSectors(colors = "#660000"),
+        symbol = "%")
 })

### 2020-05-13 analysis/05_market_simulator.Rmd

@@
 ```{r load data}
-intercept_mod <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_noncentered.rds')) %>% 
+charity_voluntarism <- readRDS(here('analysis', 'output', 'posterior_draws', 'charity_voluntarism.rds')) %>% 
   group_by(i) %>% 
   summarize(theta_mean = mean(Theta))
+
+demographics <- readRDS(here('analysis', 'output', 'posterior_draws', 'demographics.rds')) %>% 
+  group_by(i) %>% 
+  summarize(theta_mean = mean(Theta))
+
+intercept_centered <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_centered.rds')) %>% 
+  group_by(i) %>% 
+  summarize(theta_mean = mean(Theta))
+
+intercept_conjugate <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_conjugate.rds')) %>% 
+  group_by(i) %>% 
+  summarize(theta_mean = mean(Gamma))
+
+intercept_noncentered <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_noncentered.rds')) %>% 
+  group_by(i) %>% 
+  summarize(theta_mean = mean(Theta))
+
+political_ideology <- readRDS(here('analysis', 'output', 'posterior_draws', 'political_ideology.rds')) %>% 
+  group_by(i) %>% 
+  summarize(theta_mean = mean(Theta))
+
+public_affairs <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_affairs.rds')) %>% 
+  group_by(i) %>% 
+  summarize(theta_mean = mean(Theta))
+
+public_political <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political.rds')) %>% 
+  group_by(i) %>% 
+  summarize(theta_mean = mean(Theta))
+
+public_political_social <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social.rds')) %>% 
+  group_by(i) %>% 
+  summarize(theta_mean = mean(Theta))
+
+public_political_social_charity <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity.rds')) %>% 
+  group_by(i) %>% 
+  summarize(theta_mean = mean(Theta))
+
+public_political_social_charity_demo <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
+  group_by(i) %>% 
+  summarize(theta_mean = mean(Theta))
+
+social_views <- readRDS(here('analysis', 'output', 'posterior_draws', 'social_views.rds')) %>% 
+  group_by(i) %>% 
+  summarize(theta_mean = mean(Theta))
+
 #Levels (This is a guess):            Means:
@@
 
+Inputs {.sidebar}
+-------------------------------------------------------
+
+```{r echo=FALSE}
+selectInput("model_choice", 
+            label = "Select Model:",
+            choices = c("charity_voluntarism",
+                        "demographics",
+                        "intercept_centered",
+                        "intercept_conjugate",
+                        "intercept_noncentered",
+                        "political_ideology",
+                        "public_affairs",
+                        "public_political",
+                        "public_political_social",
+                        "public_political_social_charity",
+                        "public_political_social_charity_demo",
+                        "social_views"))
+
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
+    selectInput("charity_importance", 
+              label = "Charity Importance:",
+              choices = c("0", '1', '2', '3','4','5','6','7'))
+  }
+})
+
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+  selectInput("trust_in_charity", 
+              label = "Charity Trust:",
+              choices = c("0", '1', '2', '3','4','5','6','7'))
+  }
+})
+
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("donation_frequency", 
+               label = "Donation Frequency:",
+               choices = c('Once a week', 'Once a Month', 'Once every three months', 'Once every six months', 'Once a year', 'Once every few years', 'Never'))
+  }
+})
+
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("donation_amount", 
+               label = "Donation Amount:",
+               choices = c("$1-$49", '$50-$99', '$100-$499', '$500-$999','$1,000-$4,999','$5,000-$9,999','$10,000+'))
+}})
+
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("volunteer_12", 
+               label = "Volunteered in last 12 Months:",
+               choices = c("Yes", "No"))
+}})
+
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("volunteer_frequency", 
+               label = "Volunteer Frequency:",
+               choices = c('Once a week', 'Once a Month', 'Once every three months', 'Once every six months', 'Once a year', 'Once every few years', 'Never'))
+}})
+
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("personal_activism", 
+               label = "Personal Activism:",
+               choices = c('Extremely involved', 
+               'Very involved', 
+               'Moderately involved', 
+               'Slightly involved',
+               'Never involved'))
+}})
+
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("family_activism", 
+               label = "Family Activism:",
+               choices = c('Extremely involved', 
+               'Very involved', 
+               'Moderately involved', 
+               'Slightly involved',
+               'Never involved'))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("religious_member", 
+               label = "Church Membership:",
+               choices = c('Active Member', 
+               'Inactive Member', 
+               "Don't belong"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("sport_member", 
+               label = "Sport or Recreational Membership:",
+               choices = c('Active Member', 
+               'Inactive Member', 
+               "Don't belong"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("art_member", 
+               label = "Art, Music, or Educational Membership:",
+               choices = c('Active Member', 
+               'Inactive Member', 
+               "Don't belong"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("labor_member", 
+               label = "Labor Union Membership:",
+               choices = c('Active Member', 
+               'Inactive Member', 
+               "Don't belong"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("political_member", 
+               label = "Political Party Membership:",
+               choices = c('Active Member', 
+               'Inactive Member', 
+               "Don't belong"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("environmental_member", 
+               label = "Enviornmental Org. Membership:",
+               choices = c('Active Member', 
+               'Inactive Member', 
+               "Don't belong"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("professional_member", 
+               label = "Professional Membership:",
+               choices = c('Active Member', 
+               'Inactive Member', 
+               "Don't belong"))
+  }})
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("humanitarian_member", 
+               label = "Humanitarian Org. Membership:",
+               choices = c('Active Member', 
+               'Inactive Member', 
+               "Don't belong"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("consumer_member", 
+               label = "Consumer Org. Membership:",
+               choices = c('Active Member', 
+               'Inactive Member', 
+               "Don't belong"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("religious_member", 
+               label = "Church Membership:",
+               choices = c('Active Member', 
+               'Inactive Member', 
+               "Don't belong"))
+
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("other_member", 
+               label = "Other Org. Membership:",
+               choices = c('Active Member', 
+               'Inactive Member', 
+               "Don't belong"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("national_news", 
+               label = "Follow national news:",
+               choices = c('Multiple times a day', 
+               'Every day', 
+               "Once a week",
+               "Hardly ever",
+               "Never"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("international_news", 
+               label = "Follow international news:",
+               choices = c('Always',
+                           "Sometimes",
+                           "Never"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("news_medium", 
+               label = "Medium to follow news:",
+               choices = c('TV', 
+               'Print', 
+               "Online",
+               "Social Media",
+               "Radio",
+               "Email newsletters",
+               "News app"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("international_news", 
+               label = "Follow international news:",
+               choices = c('Multiple times a day', 
+               'Every day', 
+               "Once a week",
+               "Hardly ever",
+               "Never"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("follow_gov", 
+               label = "Follow government & public affairs:",
+               choices = c('Most of the time', 
+               'Some of the time', 
+               "Only now and then",
+               "Hardly at all"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("travel_developing", 
+               label = "Travel to developing country:",
+               choices = c('Yes', 
+               'No'))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("political_ideology", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("polical_pref", 
+               label = "Polical views from liberal to conservative:",
+               choices = c('0', 
+               '1', 
+               "2",
+               "3",
+               "4",
+               "5",
+               "6",
+               "7"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("institution_trust", 
+               label = "Political institution trust from none to complete:",
+               choices = c('0', 
+               '1', 
+               "2",
+               "3",
+               "4",
+               "5",
+               "6",
+               "7"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("others_charitable", 
+               label = "People should be more charitable:",
+               choices = c('0', 
+               '1', 
+               "2",
+               "3",
+               "4",
+               "5",
+               "6",
+               "7"))
+  }}) #??
+
+renderUI({
+  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("worship_attendance", 
+               label = "Worship service attendance:",
+               choices = c('Multiple times a week', 
+               'Once a week', 
+               "Once a month",
+               "Once a year",
+               "Never"))
+  }}) #??
+
+renderUI({
+  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("religion_importance", 
+               label = "Importance of religion:",
+               choices = c('Extremely important',
+                           'Very important',
+                           'Moderately important',
+                           'Slightly important',
+                           'Not at all important'))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+     selectInput("religion", 
+               label = "Religion:",
+               choices = c('Catholic',
+                           'Protestant',
+                           'Christian Orthodox',
+                           'Jewish',
+                           'Muslim',
+                           'Sikh',
+                           'Hindu',
+                           'Buddhist',
+                           'Atheist',
+                           'Other'))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
+     selectInput("gender", 
+               label = "Gender:",
+               choices = c("Male",
+                           "Female",
+                           "Transgender",
+                           "Prefer not to say",
+                           "Other"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
+     selectInput("marital_status", 
+               label = "Marital Status:",
+               choices = c("Married",
+                           "Widowed",
+                           "Divorced",
+                           "Separated",
+                           "Never married"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
+     selectInput("education", 
+               label = "Education:",
+               choices = c("Less than high school",
+                           "High school",
+                           "Some college",
+                           "2 year degree",
+                           "4 year degree",
+                           "Graduate degree",
+                           "Doctorate"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
+     selectInput("income", 
+               label = "Income:",
+               choices = c('Less than $10,000', 
+                           '$10,000 to $19,999',
+                           '$20,000 to $29,999',
+                           '$30,000 to $39,999',
+                           '$40,000 to $49,999',
+                           '$50,000 to $59,999',
+                           '$60,000 to $69,999',
+                           '$70,000 to $79,999',
+                           '$80,000 to $89,999',
+                           '$90,000 to $99,999',
+                           '$100,000 to $149,999',
+                           '$150,000 to $199,999',
+                           '$200,000 to $299,999',
+                           '$300,000 or more'))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
+     selectInput("race", 
+               label = "Race(s):",
+               choices = c('White',
+                           'Black or African American','American Indian or Alaska Native','Asian','Native Hawaiian or Pacific Islander', 'Other'), 
+               multiple = TRUE)
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
+     selectInput("education", 
+               label = "Education:",
+               choices = c("Less than high school",
+                           "High school",
+                           "Some college",
+                           "2 year degree",
+                           "4 year degree",
+                           "Graduate degree",
+                           "Doctorate"))
+  }})
+
+renderUI({
+  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
+     selectInput("age", 
+               label = "Age:",
+               choices = c('Under 18',
+                           '18 - 24',
+                           '25 - 34',
+                           '35 - 44',
+                           '45 - 54',
+                           '55 - 64',
+                           '65 - 74',
+                           '75 - 84',
+                           '85 or older'))
+  }})
+
+```
+
 Row
@@
   choice = df()
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_mod[,2])),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_mod[,2])),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_mod[,2])),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_mod[,2])),2)
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_noncentered[,2])),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_noncentered[,2])),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_noncentered[,2])),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_noncentered[,2])),2)
   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
@@
              #scale_fill_manual(values = c("Amnesty International" = "#FFC30B", "Greenpeace" = "#3fad48", "Oxfam" = "#006633", "Red Cross" = "#660000"))+
-             theme(legend.position = "none", axis.text.x = element_text(angle = 10, hjust = 1)) +
+             theme(legend.position = "none") +
              facet_wrap(~Type)
@@
   choice = df()
-  ai_exp_util <- round(exp(t(choice[,3]) %*% as.matrix(intercept_mod[,2])),2)
+  ai_exp_util <- round(exp(t(choice[,3]) %*% as.matrix(intercept_noncentered[,2])),2)
   valueBox(ai_exp_util,
@@
   choice = df()
-  gp_exp_util <- round(exp(t(choice[,4]) %*% as.matrix(intercept_mod[,2])),2)
+  gp_exp_util <- round(exp(t(choice[,4]) %*% as.matrix(intercept_noncentered[,2])),2)
   valueBox(gp_exp_util,
@@
   choice = df()
-  ox_exp_util <- round(exp(t(choice[,5]) %*% as.matrix(intercept_mod[,2])),2)
+  ox_exp_util <- round(exp(t(choice[,5]) %*% as.matrix(intercept_noncentered[,2])),2)
   valueBox(ox_exp_util,
@@
   choice = df()
-  rc_exp_util <- round(exp(t(choice[,6]) %*% as.matrix(intercept_mod[,2])),2)
+  rc_exp_util <- round(exp(t(choice[,6]) %*% as.matrix(intercept_noncentered[,2])),2)
   valueBox(rc_exp_util,
@@
   choice = df()
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_mod[,2])),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_mod[,2])),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_mod[,2])),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_mod[,2])),2)
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_noncentered[,2])),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_noncentered[,2])),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_noncentered[,2])),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_noncentered[,2])),2)
 

### 2020-06-19 analysis/shiny_walkthrough.Rmd
Added a Shiny walk through document

---
title: "Shiny Walkthrough"
output: html_notebook
---

## Shiny

Shiny dashboard structure (UI - user interface)

3 Main parts:

* Header - dashboardHeader()
* Sidebar - dashboardSidebar()
* Body - dashboardBody()

## How to build a Sidebar Dashboard

sidebar <- dashboardSidebar(
  sidebarMenu(
    menuItem("Data",
      tabName = "data") #Used for linking in the body
  )
)

You can have users input information - 
Different input functions:
selectInput() # Allows user to select a singular item from a list
textInput() # Allows user to input text
dateInput() # Allows user to input a date
checkboxInput() # Allows user to select multiple items

How to build user input

selectInput(
  inputId = "object", # This is the name you described the object elsewhere in the application
  label = "Favorite Character", # The label you want to show to the user
  choices = c(...) # List the choices the user has to pick from
)

### Render Functions 
Functions that you use in your application's server side code, assigning them to outputs that appear in your user interface.

renderPrint()
renderText()
renderPlot()
renderUI() # HTML or a shiny tag object

## Example Using Star Wars df
```{r}
library(shiny)
library(tidyverse)
library(flexdashboard)
library(shinydashboard)

sidebar <- dashboardSidebar(
  selectInput(
    inputId = "name",
    label = "Favorite Character",
    choices = c(starwars$name)
  )
)

body <- dashboardBody(
  textOutput("name")
)

ui <- dashboardPage(header = dashboardHeader(),
                    sidebar = sidebar,
                    body = body
                    )

server <- function(input, output) {
  output$name <- renderText({
      input$name
    })
}

shinyApp(ui, server)

```

### 2020-06-22 analysis/shiny_walkthrough.Rmd
Added a flexdashboard section

@@
 
-## Shiny
+# Shiny
 
-Shiny dashboard structure (UI - user interface)
+Shiny is an R package that makes it easy to build interactive web apps straight from R.
+You can host standalone apps on a webpage or embed them in R Markdown documents or build dashboards.
+You can also extend your Shiny apps with CSS themes, htmlwidgets, and JavaScript actions.
+
+Shiny is most often used with the packages "shinydashboard" or "flexdashboard" to build interactive dashboards.
+We will walk through how to use both shinydashboard and flexdashboard to give you options when using shiny.
+
+## Shiny dashboard structure (UI - user interface)
 
@@
 
-## How to build a Sidebar Dashboard
+### How to build a Sidebar Dashboard
+
+```{r}
+library(shinydashboard)
 
@@
 )
+```
 
-You can have users input information - 
+You can also have users input information - 
 Different input functions:
-selectInput() # Allows user to select a singular item from a list
-textInput() # Allows user to input text
-dateInput() # Allows user to input a date
-checkboxInput() # Allows user to select multiple items
+* selectInput() # Allows user to select a singular item from a list
+* textInput() # Allows user to input text
+* dateInput() # Allows user to input a date
+* checkboxInput() # Allows user to select multiple items
 
-How to build user input
+### How to build user input with shinydashboard
 
+```{r}
 selectInput(
@@
   label = "Favorite Character", # The label you want to show to the user
-  choices = c(...) # List the choices the user has to pick from
+  choices = c(starwars$name) # List the choices the user has to pick from
  )
+```
 
@@
 
-renderPrint()
-renderText()
-renderPlot()
-renderUI() # HTML or a shiny tag object
+* renderPrint()
+* renderText()
+* renderPlot()
+* renderUI() # HTML or a shiny tag object
 
@@
 library(tidyverse)
-library(flexdashboard)
 library(shinydashboard)
@@
 ```
+
+# Flexdashboard
+
+Flexdashboard is a similar dashboard system as shiny. A flexdashboard is filled with charts. To create a flexdashboard, you will first need to adjust the YAML header.
+
+title: "title of document"
+output: 
+  flexdashboard::flex_dashboard
+
+Now your Rmarkdown file will be interpreted as a flexdashboard file.
+
+The flexdashboard default layout is in columns. To separate the columns, you will use the following syntax:
+
+```{r}
+library(flexdashboard)
+```
+
+Column
+----------------------------------------------------------------------------------------
+## Chart A
+```{r}
+
+```
+
+Column
+-----------------------------------------------------------------------------------------
+## Chart B
+```{r}
+
+```
+
+## Chart C
+```{r}
+
+```

### 2020-06-22 analysis/shiny_walkthrough.Rmd
Added a flexdashboard section - fixed issues so it works properly

@@
 ```{r}
+library("shiny")
+library("tidyverse")
 selectInput(

### 2020-06-22 analysis/shiny_walkthrough.Rmd

--- 2020-06-22 analysis/shiny_walkthrough.Rmd
@@
 ```{r}
+library("shiny")
+library("tidyverse")
+
 selectInput(

### 2020-06-23 analysis/shiny_walkthrough.Rmd
Include shiny layout - building rows and columns

@@
 
-You can also have users input information - 
+If you want more interactivity on your dashboard, shiny has some functions that enables you to do that.
+You can use a number of different input options using shiny.
+This allows the user of the website to input information - whether it's text, a date, or to select options from data that you provide.
+
 Different input functions:
@@
 * dateInput() # Allows user to input a date
-* checkboxInput() # Allows user to select multiple items
+* checkboxInput()
 
@@
 
+header <- dashboardHeader(
+  title = "Example Dashboard Header",
+  titleWidth = 300
+)
+
 sidebar <- dashboardSidebar(
@@
 )
+```
 
-ui <- dashboardPage(header = dashboardHeader(),
+After you code the sidebar and body, you can then create the User Interface, or "ui".
+The User Interface is built from a header, sidebar, and body.
+When you modify any of these options, the easiest way is to save it as an object called "header", "sidebar", or "body".
+The user interface is most often coded into the dashboardPage() function.
+
+```{r}
+ui <- dashboardPage(header = header,
                     sidebar = sidebar,
@@
 
+```
+
+## Shinydashboard Layout
+
+There are two main types of layouts that shiny uses. The first is a "row" based layout, while the other is a "column" based layout. You can use either one, or even a mix of the two.
+The way to create the layouts is by using the "fluidRow()" function.
+
+These functions are used inside of the dashboardBody() section. Each time "fluidRow()" is called, a new row is created.
+
+Row layout
+```{r}
+body <- dashboardBody(
+  fluidRow(
+# Row 1
+  box(
+  width = 12, # 12 width spans the entire width of the screen
+  title = "Regular Box, Row 1",
+  "Text inside of box"
+  )),
+  fluidRow(
+# Row 2
+  box(
+  width = 12,
+  title = "Regular Box, Row 2",
+  "Text inside of box 2"
+  )
+)
+)
+ui <- dashboardPage(header = dashboardHeader(),
+                    sidebar = dashboardSidebar(),
+                    body = body
+                    )
+
+ui
+```
+
+Column Layout
+```{r}
+body <- dashboardBody(
+    fluidRow(
+    #   Column 1
+      column(width = 6,
+      infoBox(
+        width = NULL, # The width must be "NULL" when using a column layout
+        title = "Regular Box, Column 1",
+        "Text inside of box"
+         )      
+   ),
+  column(width = 6,
+    #   Column 2
+      infoBox(
+        width = NULL, # The width must be "NULL" when using a column layout
+        title = "Regular Box, Column 2",
+        "Text inside of box"
+         )      
+   )
+)
+)
+ui <- dashboardPage(header = dashboardHeader(),
+                    sidebar = dashboardSidebar(),
+                    body = body
+                    )
+
+shinyApp(ui, server)
+```
+
+### Mix of Column and Row Layout
+Note:
+To create a new row, you call another fluidRow() function. 
+```{r}
+body <- dashboardBody(
+    fluidRow(
+    #   Row 1
+      box(
+        width = 12, # The width must be "NULL" when using a column layout
+        title = "Regular Box, Row 1",
+        "Text inside of box"
+         ),
+    ),
+  fluidRow(
+    column(width = 6,
+    #   Column 2
+      infoBox(
+        width = NULL, # The width must be "NULL" when using a column layout
+        title = "Regular Box, Row 2, Column 1",
+        subtitle = "Text inside of box"
+         )
+    ),
+    column(width = 6,
+      infoBox(
+        width = NULL,
+        title = "Regular Box, Row 2, Column 2",
+        subtitle = "Text inside of box"
+      )
+    )
+  )
+)
+
+ui <- dashboardPage(header = dashboardHeader(),
+                    sidebar = dashboardSidebar(),
+                    body = body
+                    )
+
+shinyApp(ui, server)
 ```

### 2020-06-24 analysis/shiny_walkthrough.Rmd
Fix minor bugs and insert more clear directions

@@
 
-Row layout
+### Row layout
 ```{r}
@@
 
-Column Layout
+### Column Layout
+The next layout option is to build columns. The difference in using columns instead of rows is to use the "column()" function inside of "fluidRow()".
+
+You can set the width of the column, but when you insert a box or chart, the width needs to be "NULL".
+
 ```{r}
@@
 Note:
-To create a new row, you call another fluidRow() function. 
+To create a new row, call another fluidRow() function. 
 ```{r}
@@
 ```
-
-# Flexdashboard
-
-Flexdashboard is a similar dashboard system as shiny. A flexdashboard is filled with charts. To create a flexdashboard, you will first need to adjust the YAML header.
-
-title: "title of document"
-output: 
-  flexdashboard::flex_dashboard
-
-Now your Rmarkdown file will be interpreted as a flexdashboard file.
-
-The flexdashboard default layout is in columns. To separate the columns, you will use the following syntax:
-
-```{r}
-library(flexdashboard)
-```
-
-Column
-----------------------------------------------------------------------------------------
-## Chart A
-```{r}
-
-```
-
-Column
------------------------------------------------------------------------------------------
-## Chart B
-```{r}
-
-```
-
-## Chart C
-```{r}
-
-```

### 2020-06-24 analysis/flexdashboard_walkthrough.Rmd
Create a flexdashboard walkthrough

---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
```

Column {data-width=650}
-----------------------------------------------------------------------
### Chart A

```{r}
starwars10 <- starwars %>% 
  filter(height >= 180)

starwars10 %>% 
  ggplot(aes(x = name, y = height)) +
    geom_col() +
    coord_flip()
```

Column {data-width=350}
-----------------------------------------------------------------------
### Chart B

```{r}

```

### Chart C

```{r}

```

### 2020-06-24 analysis/flexdashboard_walkthrough.Rmd
Input a description about Flexdashboards.

@@
 ---
+
+Flexdashboards are often used along with shiny to build interactive dashboards.
+Dashboards are divided into columns and rows, with output components delineated using level 3 markdown headers (###).
+By default, dashboards are laid out within a single column, with charts stacked vertically within a column and sized to fill available browser height.
+
+To lay out charts using multiple columns you introduce a level 2 markdown header (--------------) for each column.
+
+You can also choose to orient dashboards row-wise rather than column-wise by specifying the orientation: rows option.
 

### 2020-06-25 analysis/shiny_walkthrough.Rmd
@marcdotson @evanwride I added in some things from my notes from the R user group/other research and added a little more code to show the basic example of a shiny app at the beginning to see the flow of how it works and looks before going into more depth on each component

@@
 
+## Shiny Outline
+
+If you were to open a Shiny app while creating a new file in R, an outline of the an app will be shown using the Old Faithful Geyser Data.
+This example app shows eruption wait times in a histogram with a side panel to change the number of bins in the histogram.
+A simple example of what these apps are intended for, user interaction.
+
+```{r}
+## Old Faithful Geyser Example
+
+library(shiny)
+
+# Define UI for application that draws a histogram
+ui <- fluidPage(
+
+    # Application title
+    titlePanel("Old Faithful Geyser Data"),
+
+    # Sidebar with a slider input for number of bins 
+    sidebarLayout(
+        sidebarPanel(
+            sliderInput("bins",
+                        "Number of bins:",
+                        min = 1,
+                        max = 50,
+                        value = 30)
+        ),
+
+        # Show a plot of the generated distribution
+        mainPanel(
+           plotOutput("distPlot")
+        )
+    )
+)
+
+# Define server logic required to draw a histogram
+server <- function(input, output) {
+
+    output$distPlot <- renderPlot({
+        # generate bins based on input$bins from ui.R
+        x    <- faithful[, 2]
+        bins <- seq(min(x), max(x), length.out = input$bins + 1)
+
+        # draw the histogram with the specified number of bins
+        hist(x, breaks = bins, col = 'darkgray', border = 'white')
+    })
+}
+
+# Run the application 
+shinyApp(ui = ui, server = server)
+
+```
+
+Viewing this example can be useful to see the flow of the user interface and processes. So let's go through what those terms mean. There are essentially three steps to any Shiny App:
+
+1. Create the User interface -- __ui__
+2. Create the processes -- __server__
+3. Run the app -- __shinyApp__
+
+The two main parts of the Shiny app are the __ui__ and the __server__.
+These objects are the arguments used in the function to run the app, __shinyApp(ui, server)__.
+We will create an ui and server object for these arguments and name them what they are, _ui_ and _server_.
+This will help us from mixing up them up and make our lives easier.
+
+## Shiny and Shinydashboard
+
+We will mostly be talking about shinydashboard in this walkthrough.
+There is no reason to worry as the two packages are essentially the same, but shinydashboard puts your code into an already styled theme in the ui without having to write the code yourself.
+
 ## Shiny dashboard structure (UI - user interface)
+
+The __ui__ object controls the layout and appearance of the app.
+This includes formatting, color, text, input panels, main panels, etc.
+(maybe go into detail here).
+ui writes your code into html for you.
+Alternatively, you could use the html functions as well.
+
+For shinydashboard we design parts of the ui and then combine it together in a function called dashboardPage().
+To keep things simple, we will go through each of the main parts individually.
+Then show how they can be combined in this dashboardPage() to make the comeplete user interface.
 
@@
 )
+
 ui <- dashboardPage(header = dashboardHeader(),

### 2020-07-21 analysis/05_market_simulator.Rmd
Working on getting simulator to work

@@
 ```{r load data}
+
+### Commented out the beta's we don't need right now. We only need the one that contains all the factors.
+
 charity_voluntarism <- readRDS(here('analysis', 'output', 'posterior_draws', 'charity_voluntarism.rds')) %>%
@@
 
-beta <- as.data.frame(matrix(rep(0), nrow = 13))
+##### Updated the beta's to be just the betas from the public_political_social_chartiy_demo Thetas
+
+beta <- public_political_social_charity_demo
+
 beta$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")
@@
   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_noncentered[,2])),2)
+
   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
@@
              labs(x="") + 
-             #scale_fill_manual(values = c("Amnesty International" = "#FFC30B", "Greenpeace" = "#3fad48", "Oxfam" = "#006633", "Red Cross" = "#660000"))+
+             scale_fill_manual(values = c("Amnesty International" = "#FFC30B", "Greenpeace" = "#3fad48", "Oxfam" = "#006633", "Red Cross" = "#660000"))+
              theme(legend.position = "none") +

### 2020-07-22 analysis/05_market_simulator.Rmd
updated public_political_social_charity_demo beta
changed beta's for plotly to public_political_social_charity_demo

@@
 
-##### Updated the beta's to be just the betas from the public_political_social_chartiy_demo Thetas
+##### Updated the beta's to be just the betas from the public_political_social_charity_demo Thetas
 
-beta <- public_political_social_charity_demo
+beta <- as.data.frame(matrix(rep(0), nrow = 13))
 
@@
   #Amnesty International
-    beta$ai_value <- 0
+  beta$ai_
+  value <- 0
     beta$ai_value[beta$levels == 'Amnesty International'] <- 1
@@
   choice = df()
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_noncentered[,2])),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_noncentered[,2])),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_noncentered[,2])),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_noncentered[,2])),2)
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
 
@@
   df <- as.data.frame(matrix(data, 8, 1))
+
   df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
@@
   choice = df()
-  ai_exp_util <- round(exp(t(choice[,3]) %*% as.matrix(intercept_noncentered[,2])),2)
+  ai_exp_util <- round(exp(t(choice[,3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
   valueBox(ai_exp_util,
@@
   choice = df()
-  gp_exp_util <- round(exp(t(choice[,4]) %*% as.matrix(intercept_noncentered[,2])),2)
+  gp_exp_util <- round(exp(t(choice[,4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
   valueBox(gp_exp_util,

### 2020-07-22 analysis/05_market_simulator.Rmd
Got some of the charts to work with the new beta value. Just need to fix the main renderPlotly to show the data.

--- 2020-07-21 analysis/05_market_simulator.Rmd
@@
 })
+
+```
+
+Practice
+-------------------------------------------------------
+```{r practice code}
+
+#### this chunk is for testing code and making sure things work before adding it into the dashboard
+
+# # Beta's we want for the plotly
+# public_political_social_charity_demo <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
+#   group_by(i) %>% 
+#   summarize(theta_mean = mean(Theta))
+# 
+# # RenderPlotly code for testing
+# 
+# renderPlotly({
+#   choice <- df()
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
+#   
+#   data <- c(ai_exp_util, gp_exp_util)
+#   df <- as.data.frame(matrix(data, 8, 1))
+#   
+#   df[,2] <- c("Amnesty International", "Green Peace")
+#   df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
+#   colnames(df) <- c("Value", "Organization", "Type")
+#   
+# 
+#   
+#   ggplotly(ggplot(df, aes(y = Value, x = Organization, fill = Type)) +
+#            geom_col() +
+#            labs(x="") + 
+#            scale_fill_manual(values = c("Amnesty International" = "#FFC30B", "Greenpeace" = "#3fad48")) +
+#            theme(legend.position = "none") +
+#            facet_wrap(~Type)
+#   )
+# })
+
+  # ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
+  # rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
+  # 
+  # ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+  # gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+  # ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+  # rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+  # 
+  # data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate)
+  # df <- as.data.frame(matrix(data, 8, 1))
+  # 
+  # df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
+  # df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
+  # colnames(df) <- c('Value', 'Organization', "Type")
 
@@
   choice = df()
-  ox_exp_util <- round(exp(t(choice[,5]) %*% as.matrix(intercept_noncentered[,2])),2)
+  ox_exp_util <- round(exp(t(choice[,5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
   valueBox(ox_exp_util,
@@
   choice = df()
-  rc_exp_util <- round(exp(t(choice[,6]) %*% as.matrix(intercept_noncentered[,2])),2)
+  rc_exp_util <- round(exp(t(choice[,6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
   valueBox(rc_exp_util,

### 2020-07-22 analysis/05_market_simulator.Rmd
Got the main renderPlotly to display data

@@
   # colnames(df) <- c("Value", "Organization", "Type")
+
+# test <- as.data.frame(matrix(runif(10), 8, 1))
 # 
+# test[,2] <- c("Amnesty International", "Green Peace", "Oxfam", "Red Cross")
+# test[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
+# colnames(test) <- c("Value", "Organization", "Type")
 # 
+# colors <- c("#ffc30b", "#3fad48", "#006633", "#660000")
 # 
-#   ggplotly(ggplot(df, aes(y = Value, x = Organization, fill = Type)) +
+#   ggplotly(
+#     ggplot(test, aes(y = Value, x = Organization, fill = Organization)) +
 #            geom_col() +
 #            labs(x="") +
-#            scale_fill_manual(values = c("Amnesty International" = "#FFC30B", "Greenpeace" = "#3fad48")) +
+#            scale_fill_manual(values = colors) +
 #            theme(legend.position = "none") +
@@
 # })
-
-  # ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  # rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  # 
-  # ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-  # gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-  # ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-  # rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-  # 
-  # data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate)
-  # df <- as.data.frame(matrix(data, 8, 1))
-  # 
-  # df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
-  # df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
-  # colnames(df) <- c('Value', 'Organization', "Type")
 
@@
 
-  ggplotly(ggplot(df, aes(y = Value, x = Organization, fill = Type)) +
+  ggplotly(ggplot(df, aes(y = Value, x = Organization, fill = Organization)) +
              geom_col() +
              labs(x="") + 
-             scale_fill_manual(values = c("Amnesty International" = "#FFC30B", "Greenpeace" = "#3fad48", "Oxfam" = "#006633", "Red Cross" = "#660000"))+
+             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
              theme(legend.position = "none") +

### 2020-07-23 analysis/05_market_simulator.Rmd
Updated some information and changed layout

@@
 ---
-title: "Data Dashboard"
+title: "Market Simulator"
 output: 
   flexdashboard::flex_dashboard:
-    orientation: rows
-    vertical_layout: scroll
+    orientation: columns
+    vertical_layout: fill
 runtime: shiny
@@
 
-##### Updated the beta's to be just the betas from the public_political_social_charity_demo Thetas
-
 beta <- as.data.frame(matrix(rep(0), nrow = 13))
@@
 
-Practice
--------------------------------------------------------
 ```{r practice code}
@@
 
-Inputs {.sidebar}
+Inputs {.sidebar data-width=50}
 -------------------------------------------------------
@@
                         "social_views"))
+
+```
+
+``` {r echo=FALSE}
 
@@
 
-Row
--------------------------------------
+Market Share and Expected Utility
+--------------------------------------------------
 
@@
 
-Row 
+Organization Utility
 -------------------------------------
-### Amnesty International Expected Utility
+Amnesty International Expected Utility
 
@@
 
-### Greenpeace Expected Utility
+## Greenpeace Expected Utility
 
@@
 
-### Oxfam Expected Utility
+## Oxfam Expected Utility
 
@@
 
-### Redcross Expected Utility
+## Redcross Expected Utility
 
@@
 
-Row 
+Expected Donors {.tabset .tabset-fade}
 -------------------------------------
-
 ### Amnesty International Expected Donors
@@
 
-Row 
+Organizational Inputs {.tabset .tabset-fade}
 -------------------------------------
-
 ### Amnesty International Inputs

### 2020-07-23 analysis/05_market_simulator.Rmd
small updates getting sidebar to work

@@
 #   9. Accountable                    1.130
-#   10. Small wealthy donars         -0.376
+#   10. Small wealthy donors         -0.376
 #   11. Government Grants            -0.252
-#   12. Critized by Government       -0.663
+#   12. Criticized by Government       -0.663
 #   13. Under Government Crackdown   -1.011
@@
 })
+
+```
+
+```{r functions}
+#### This chunk can be used for writing function to calculate the utilities and what not
 
@@
 
-Inputs {.sidebar data-width=50}
+Inputs {.sidebar}
 -------------------------------------------------------
@@
                         "social_views"))
-
-```
-
-``` {r echo=FALSE}
 
@@
 -------------------------------------
-Amnesty International Expected Utility
+## Amnesty International Expected Utility
 

### 2020-08-04 analysis/05_market_simulator.Rmd
Updated with persona beta calculated

@@
   flexdashboard::flex_dashboard:
-    orientation: columns
-    vertical_layout: fill
+    orientation: rows
+    vertical_layout: scroll
 runtime: shiny
@@
 
-### Commented out the beta's we don't need right now. We only need the one that contains all the factors.
-
-charity_voluntarism <- readRDS(here('analysis', 'output', 'posterior_draws', 'charity_voluntarism.rds')) %>%
-  group_by(i) %>%
-  summarize(theta_mean = mean(Theta))
-
-demographics <- readRDS(here('analysis', 'output', 'posterior_draws', 'demographics.rds')) %>%
-  group_by(i) %>%
-  summarize(theta_mean = mean(Theta))
-
-intercept_centered <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_centered.rds')) %>%
-  group_by(i) %>%
-  summarize(theta_mean = mean(Theta))
-
-intercept_conjugate <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_conjugate.rds')) %>%
-  group_by(i) %>%
-  summarize(theta_mean = mean(Gamma))
-
-intercept_noncentered <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_noncentered.rds')) %>%
-  group_by(i) %>%
-  summarize(theta_mean = mean(Theta))
-
-political_ideology <- readRDS(here('analysis', 'output', 'posterior_draws', 'political_ideology.rds')) %>%
-  group_by(i) %>%
-  summarize(theta_mean = mean(Theta))
-
-public_affairs <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_affairs.rds')) %>%
-  group_by(i) %>%
-  summarize(theta_mean = mean(Theta))
-
-public_political <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political.rds')) %>%
-  group_by(i) %>%
-  summarize(theta_mean = mean(Theta))
-
-public_political_social <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social.rds')) %>%
-  group_by(i) %>%
-  summarize(theta_mean = mean(Theta))
-
-public_political_social_charity <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity.rds')) %>%
-  group_by(i) %>%
-  summarize(theta_mean = mean(Theta))
-
+# Beta's of everything. The only model we care about right now
 public_political_social_charity_demo <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
-  group_by(i) %>% 
-  summarize(theta_mean = mean(Theta))
-
-social_views <- readRDS(here('analysis', 'output', 'posterior_draws', 'social_views.rds')) %>%
-  group_by(i) %>%
-  summarize(theta_mean = mean(Theta))
+  group_by(i, j) %>% 
+  summarize(theta_mean = mean(Theta)) %>% 
+  ungroup() %>% 
+  pivot_wider(names_from = j, values_from = theta_mean) %>% 
+  select(-i)
+
+# Persona Data from Market Simulator Workbook
+persona_data <- readxl::read_xlsx(here('analysis', 'output', "persona_config.xlsx"))
 
@@
 })
-
-```
-
-```{r functions}
-#### This chunk can be used for writing function to calculate the utilities and what not
-
 ```
@@
 
-Inputs {.sidebar}
--------------------------------------------------------
-
-```{r echo=FALSE}
-selectInput("model_choice", 
-            label = "Select Model:",
-            choices = c("charity_voluntarism",
-                        "demographics",
-                        "intercept_centered",
-                        "intercept_conjugate",
-                        "intercept_noncentered",
-                        "political_ideology",
-                        "public_affairs",
-                        "public_political",
-                        "public_political_social",
-                        "public_political_social_charity",
-                        "public_political_social_charity_demo",
-                        "social_views"))
-
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+Persona Inputs {.sidebar}
+=================================================
+
+## Persona Inputs
+
+```{r sidebar inputs, echo=FALSE}
+
+# selectInput("model_choice", 
+#             label = "Select Model:",
+#             choices = c("public_political_social_charity_demo"))
 
@@
           choices = c("0", '1', '2', '3','4','5','6','7'))
-  }
-})
-
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("trust_in_charity", 
@@
             choices = c("0", '1', '2', '3','4','5','6','7'))
-  }
-})
-
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("donation_frequency", 
          label = "Donation Frequency:",
-               choices = c('Once a week', 'Once a Month', 'Once every three months', 'Once every six months', 'Once a year', 'Once every few years', 'Never'))
-  }
-})
-
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+         choices = c('Once a week', 
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months', 
+                     'Once a year', 
+                     'Once every few years',
+                     'Never'))
+
 selectInput("donation_amount", 
          label = "Donation Amount:",
-               choices = c("$1-$49", '$50-$99', '$100-$499', '$500-$999','$1,000-$4,999','$5,000-$9,999','$10,000+'))
-}})
-
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+         choices = c("$1-$49", 
+                     '$50-$99', 
+                     '$100-$499',
+                     '$500-$999',
+                     '$1,000-$4,999',
+                     '$5,000-$9,999',
+                     '$10,000+'))
+
 selectInput("volunteer_12", 
@@
          choices = c("Yes", "No"))
-}})
-
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("volunteer_frequency", 
          label = "Volunteer Frequency:",
-               choices = c('Once a week', 'Once a Month', 'Once every three months', 'Once every six months', 'Once a year', 'Once every few years', 'Never'))
-}})
-
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months', 
+                     'Once every six months', 
+                     'Once a year', 
+                     'Once every few years',
+                     'Never'))
+
 selectInput("personal_activism", 
@@
                      'Never involved'))
-}})
-
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("family_activism", 
@@
                      'Never involved'))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("religious_member", 
@@
                      "Don't belong"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("sport_member", 
@@
                      "Don't belong"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("art_member", 
@@
                      "Don't belong"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("labor_member", 
@@
                      "Don't belong"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("political_member", 
@@
                      "Don't belong"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("environmental_member", 
@@
                      "Don't belong"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("professional_member", 
@@
                      "Don't belong"))
-  }})
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("humanitarian_member", 
@@
                      "Don't belong"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("consumer_member", 
@@
                      "Don't belong"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("religious_member", 
@@
 
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
 selectInput("other_member", 
@@
                      "Don't belong"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("national_news", 
@@
                      "Never"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("international_news", 
@@
                      "Never"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("news_medium", 
@@
                      "News app"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("international_news", 
@@
                      "Never"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("follow_gov", 
@@
                      "Hardly at all"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("travel_developing", 
          label = "Travel to developing country:",
-               choices = c('Yes', 
-               'No'))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("political_ideology", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+         choices = c('Yes', 'No'))
+
 selectInput("polical_pref", 
          label = "Polical views from liberal to conservative:",
-               choices = c('0', 
-               '1', 
-               "2",
-               "3",
-               "4",
-               "5",
-               "6",
-               "7"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
 selectInput("institution_trust", 
          label = "Political institution trust from none to complete:",
-               choices = c('0', 
-               '1', 
-               "2",
-               "3",
-               "4",
-               "5",
-               "6",
-               "7"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
 selectInput("others_charitable", 
          label = "People should be more charitable:",
-               choices = c('0', 
-               '1', 
-               "2",
-               "3",
-               "4",
-               "5",
-               "6",
-               "7"))
-  }}) #??
-
-renderUI({
-  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
 selectInput("worship_attendance", 
@@
                      "Never"))
-  }}) #??
-
-renderUI({
-  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("religion_importance", 
@@
                      'Not at all important'))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
+
 selectInput("religion", 
@@
                      'Other'))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
+
 selectInput("gender", 
@@
                      "Other"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
+
 selectInput("marital_status", 
@@
                      "Never married"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
+
 selectInput("education", 
@@
                      "Doctorate"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
+
 selectInput("income", 
@@
                      '$300,000 or more'))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
+
 selectInput("race", 
@@
          choices = c('White',
-                           'Black or African American','American Indian or Alaska Native','Asian','Native Hawaiian or Pacific Islander', 'Other'), 
+                     'Black or African American',
+                     'American Indian or Alaska Native',
+                     'Asian',
+                     'Native Hawaiian or Pacific Islander',
+                     'Other'), 
          multiple = TRUE)
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
+
 selectInput("education", 
@@
                      "Doctorate"))
-  }})
-
-renderUI({
-  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
+
 selectInput("age", 
@@
                      '85 or older'))
-  }})
-
-```
+
+```
+
+```{r persona betas}
+
+### Calculating the Persona betas ###
+
+# Persona 1
+persona1 <- persona_data[,2]
+
+p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona1)
+
+# Persona 2
+persona2 <- persona_data[,3]
+
+p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona2)
+
+# Persona 3
+persona3 <- persona_data[,4]
+
+p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona3)
+
+```
+
+<!-- Main page Chart with All Personas -->
+
+Market Share Per Persona
+==================================================
+
+### Market Share Per Persona
+
+```{r plot all personas}
+
+renderPlotly({
+  choice = df()
+
+    persona1 = p_beta1 # Choose the persona
+
+  ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
+  gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
+  ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
+  rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+
+  ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+
+    persona2 = p_beta2 # Choose the persona
+
+  ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
+  gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
+  ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
+  rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+
+  ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+
+      persona3 = p_beta3 # Choose the persona
+
+  ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
+  gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
+  ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
+  rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+
+  ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+
+  data <- c(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1, ai_rate1, gp_rate1, ox_rate1, rc_rate1, 
+            ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2, ai_rate2, gp_rate2, ox_rate2, rc_rate2,
+            ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3, ai_rate3, gp_rate3, ox_rate3, rc_rate3)
+
+  df <- as.data.frame(matrix(data, 24, 1))
+
+  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
+  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
+  df[,4] <- c(rep("Persona 1",8), rep("Persona 2", 8), rep("Persona 3", 8))
+  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+
+  ggplotly(df %>% filter(Type == "Market Share") %>% 
+             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+             geom_bar(position = "dodge", stat = "identity") +
+             labs(x="") + 
+             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+             theme(legend.position = "none")
+    )
+})
+```
+
+<!-- Persona 1 page -->
+
+Persona 1 
+====================================================
 
@@
 
-```{r plot}
+```{r plot person 1}
 renderPlotly({
   choice = df()
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
+  persona = p_beta1 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
 
@@
   df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
-  colnames(df) <- c('Value', 'Organization', "Type")
-
-  ggplotly(ggplot(df, aes(y = Value, x = Organization, fill = Organization)) +
+  df[,4] <- rep(c("Persona 1","Persona 2", "Persona 3"), length.out = 8)
+  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+
+  ggplotly(df %>% filter(Type == "Market Share") %>% 
+             ggplot(aes(y = Value, x = Organization, fill = Organization)) +
              geom_col() +
@@
 
-Organization Utility
+Organization Market Share
 -------------------------------------
-## Amnesty International Expected Utility
-
-```{r}
+### Amnesty International Market Share
+
+```{r valuebox ai persona 1}
 renderValueBox({
   choice = df()
-  ai_exp_util <- round(exp(t(choice[,3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  valueBox(ai_exp_util,
-           color = "#FFC30B")
-})
-```
-
-## Greenpeace Expected Utility
-
-```{r}
+
+  persona = p_beta1 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  valueBox(ai_rate,
+           color = "#FFC30B",
+           icon = "fa-percent")
+})
+```
+
+### Greenpeace Market Share
+
+```{r valuebox gp persona 1}
 renderValueBox({
   choice = df()
-  gp_exp_util <- round(exp(t(choice[,4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  valueBox(gp_exp_util,
-           color = "#3fad48")
-})
-```
-
-## Oxfam Expected Utility
-
-```{r}
+  persona = p_beta1 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  valueBox(gp_rate,
+           color = "#3fad48",
+           icon = "fa-percent")
+})
+```
+
+### Oxfam Market Share
+
+```{r valuebox ox persona 1}
 renderValueBox({
   choice = df()
-  ox_exp_util <- round(exp(t(choice[,5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  valueBox(ox_exp_util,
-           color = "#006633")
-})
-```
-
-## Redcross Expected Utility
-
-```{r}
+
+  persona = p_beta1 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  valueBox(ox_rate,
+           color = "#006633",
+           icon = "fa-percent")
+})
+```
+
+### Redcross Market Share
+
+```{r valuebox rc persona 1}
 renderValueBox({
   choice = df()
-  rc_exp_util <- round(exp(t(choice[,6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  valueBox(rc_exp_util,
-           color = "#660000")
-})
-```
-
-Expected Donors {.tabset .tabset-fade}
--------------------------------------
-### Amnesty International Expected Donors
-
-```{r echo=FALSE}
-renderGauge({
-  choice = df()
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-
-  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-  gauge(ai_rate, 
-        min = 0, 
-        max = 100,
-        gaugeSectors(colors = "#FFC30B"),
-        symbol = "%")
-})
-```
-
-### Greenpeace Expected Donors
-
-```{r echo=FALSE}
-renderGauge({
-  choice = df()
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-
-  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-  gauge(gp_rate, 
-        min = 0, 
-        max = 100,
-        gaugeSectors(colors = "#3fad48"),
-        symbol = "%")
-})
-```
-
-### Oxfam Expected Donors
-
-```{r echo=FALSE}
-renderGauge({
-  choice = df()
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-
-  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-  gauge(ox_rate, 
-        min = 0, 
-        max = 100,
-        gaugeSectors(colors = "#006633"),
-        symbol = "%")
-})
-```
-
-### Red Cross Expected Donors
-
-```{r echo=FALSE}
-renderGauge({
-  choice = df()
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
+
+  persona = p_beta1 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
 
   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-  gauge(rc_rate, 
-        min = 0, 
-        max = 100,
-        gaugeSectors(colors = "#660000"),
-        symbol = "%")
+
+  valueBox(rc_rate,
+           color = "#660000",
+           icon = "fa-percent")
 })
@@
 ```
+
+<!-- There is an issue of not being able to see the last selectInput options when drop down box appears -->
+
+Bottom of page buffer
+-----------------------------------------------
+
+<!-- Persona 2 Page -->
+
+Persona 2
+===============================================
+
+Market Share
+--------------------------------------------------
+```{r plot persona 2}
+renderPlotly({
+  choice = df()
+
+  persona = p_beta2 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate)
+  df <- as.data.frame(matrix(data, 8, 1))
+
+  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
+  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
+  df[,4] <- rep(c("Persona 1","Persona 2", "Persona 3"), length.out = 8)
+  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+
+  ggplotly(df %>% filter(Type == "Market Share") %>% 
+             ggplot(aes(y = Value, x = Organization, fill = Organization)) +
+             geom_col() +
+             labs(x="") + 
+             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+             theme(legend.position = "none") +
+             facet_wrap(~Type)
+    )
+})
+```
+
+Organization Market Share
+-------------------------------------
+### Amnesty International Market Share
+
+```{r valuebox ai persona 2}
+renderValueBox({
+  choice = df()
+
+  persona = p_beta2 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  valueBox(ai_rate,
+           color = "#FFC30B",
+           icon = "fa-percent")
+})
+```
+
+### Greenpeace Market Share
+
+```{r valuebox gp persona 2}
+renderValueBox({
+  choice = df()
+
+  persona = p_beta2 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  valueBox(gp_rate,
+           color = "#3fad48",
+           icon = "fa-percent")
+})
+```
+
+### Oxfam Market Share
+
+```{r valuebox ox persona 2}
+renderValueBox({
+  choice = df()
+
+  persona = p_beta2 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  valueBox(ox_rate,
+           color = "#006633",
+           icon = "fa-percent")
+})
+```
+
+### Redcross Market Share
+
+```{r valuebox rc persona 2}
+renderValueBox({
+  choice = df()
+
+  persona = p_beta2 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  valueBox(rc_rate,
+           color = "#660000",
+           icon = "fa-percent")
+})
+```
+
+Organizational Inputs {.tabset .tabset-fade}
+-------------------------------------
+### Amnesty International Inputs
+
+```{r echo=FALSE}
+selectInput("ai_issue", 
+            label = "Select Issue Area:",
+            choices = c("Emergency response",
+                        "Environment",
+                        "Human rights",
+                        "Refugee relief"))
+
+selectInput("ai_fin_trans",
+            label = "Select Financial transparency:",
+            choices = c("Doesn’t engage in transparency",
+                        "Engages in transparency"))
+
+selectInput("ai_account",
+            label = "Select Financial Accountability:",
+            choices = c("Doesn’t engage in financial accountability",
+                        "Engages in financial accountability"))
+
+selectInput("ai_funding",
+            label = "Select Funding source:",
+            choices = c("Many small private donations",
+                        "Handful of wealthy private donors",
+                        "Government Grants"))
+
+selectInput("ai_gov_relat",
+            label = "Select Relationship with host government",
+            choices = c("Friendly relationship with government",
+                        "Criticized by government", 
+                        "Under government crackdown"))
+```
+
+### Greenpeace Inputs
+
+```{r echo=FALSE}
+selectInput("gp_issue", 
+            label = "Select Issue Area:",
+            choices = c("Emergency response",
+                        "Environment",
+                        "Human rights",
+                        "Refugee relief"))
+
+selectInput("gp_fin_trans",
+            label = "Select Financial transparency:",
+            choices = c("Doesn’t engage in transparency",
+                        "Engages in transparency"))
+
+selectInput("gp_account",
+            label = "Select Financial Accountability:",
+            choices = c("Doesn’t engage in accountability",
+                        "Engages in financial accountability"))
+
+selectInput("gp_funding",
+            label = "Select Funding source:",
+            choices = c("Many small private donations",
+                        "Handful of wealthy private donors",
+                        "Government Grants"))
+
+selectInput("gp_gov_relat",
+            label = "Select Relationship with host government",
+            choices = c("Friendly relationship with government",
+                        "Criticized by government", 
+                        "Under government crackdown"))
+```
+
+### Oxfam Inputs
+
+```{r echo=FALSE}
+selectInput("ox_issue", 
+            label = "Select Issue Area:",
+            choices = c("Emergency response",
+                        "Environment",
+                        "Human rights",
+                        "Refugee relief"))
+
+selectInput("ox_fin_trans",
+            label = "Select Financial transparency:",
+            choices = c("Doesn’t engage in transparency",
+                        "Engages in transparency"))
+
+selectInput("ox_account",
+            label = "Select Financial Accountability:",
+            choices = c("Doesn’t engage in accountability",
+                        "Engages in financial accountability"))
+
+selectInput("ox_funding",
+            label = "Select Funding source:",
+            choices = c("Many small private donations",
+                        "Handful of wealthy private donors",
+                        "Government Grants"))
+
+selectInput("ox_gov_relat",
+            label = "Select Relationship with host government",
+            choices = c("Friendly relationship with government",
+                        "Criticized by government", 
+                        "Under government crackdown"))
+```
+
+### Red Cross Inputs
+
+```{r echo=FALSE}
+selectInput("rc_issue", 
+            label = "Select Issue Area:",
+            choices = c("Emergency response",
+                        "Environment",
+                        "Human rights",
+                        "Refugee relief"))
+
+selectInput("rc_fin_trans",
+            label = "Select Financial transparency:",
+            choices = c("Doesn’t engage in transparency",
+                        "Engages in transparency"))
+
+selectInput("rc_account",
+            label = "Select Financial Accountability:",
+            choices = c("Doesn’t engage in accountability",
+                        "Engages in financial accountability"))
+
+selectInput("rc_funding",
+            label = "Select Funding source:",
+            choices = c("Many small private donations",
+                        "Handful of wealthy private donors",
+                        "Government Grants"))
+
+selectInput("rc_gov_relat",
+            label = "Select Relationship with host government",
+            choices = c("Friendly relationship with government",
+                        "Criticized by government", 
+                        "Under government crackdown"))
+```
+
+Bottom of page buffer
+-----------------------------------------------
+
+<!-- Persona 3 Page  -->
+
+Persona 3
+===============================================
+
+Market Share 
+------------------------------------------------
+```{r plot persona 3}
+renderPlotly({
+  choice = df()
+
+  persona = p_beta3 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2)
+
+  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate)
+  df <- as.data.frame(matrix(data, 8, 1))
+
+  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
+  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
+  df[,4] <- rep(c("Persona 1","Persona 2", "Persona 3"), length.out = 8)
+  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+
+  ggplotly(df %>% filter(Type == "Market Share") %>% 
+             ggplot(aes(y = Value, x = Organization, fill = Organization)) +
+             geom_col() +
+             labs(x="") + 
+             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+             theme(legend.position = "none") +
+             facet_wrap(~Type)
+    )
+})
+```
+
+Organization Market Share
+-------------------------------------
+### Amnesty International Market Share
+
+```{r valuebox ai persona 3}
+renderValueBox({
+  choice = df()
+
+  persona = p_beta3 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2)
+
+  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  valueBox(ai_rate,
+           color = "#FFC30B",
+           icon = "fa-percent")
+})
+```
+
+### Greenpeace Market Share
+
+```{r valuebox gp persona 3}
+renderValueBox({
+  choice = df()
+
+  persona = p_beta3 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2)
+
+  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  valueBox(gp_rate,
+           color = "#3fad48",
+           icon = "fa-percent")
+})
+```
+
+### Oxfam Market Share
+
+```{r valuebox ox persona 3}
+renderValueBox({
+  choice = df()
+
+  persona = p_beta3 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2)
+
+  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  valueBox(ox_rate,
+           color = "#006633",
+           icon = "fa-percent")
+})
+```
+
+### Redcross Market Share
+
+```{r valuebox rc persona 3}
+renderValueBox({
+  choice = df()
+
+  persona = p_beta3 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2)
+
+  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  valueBox(rc_rate,
+           color = "#660000",
+           icon = "fa-percent")
+})
+```
+
+Organizational Inputs {.tabset .tabset-fade}
+-------------------------------------
+### Amnesty International Inputs
+
+```{r echo=FALSE}
+selectInput("ai_issue", 
+            label = "Select Issue Area:",
+            choices = c("Emergency response",
+                        "Environment",
+                        "Human rights",
+                        "Refugee relief"))
+
+selectInput("ai_fin_trans",
+            label = "Select Financial transparency:",
+            choices = c("Doesn’t engage in transparency",
+                        "Engages in transparency"))
+
+selectInput("ai_account",
+            label = "Select Financial Accountability:",
+            choices = c("Doesn’t engage in financial accountability",
+                        "Engages in financial accountability"))
+
+selectInput("ai_funding",
+            label = "Select Funding source:",
+            choices = c("Many small private donations",
+                        "Handful of wealthy private donors",
+                        "Government Grants"))
+
+selectInput("ai_gov_relat",
+            label = "Select Relationship with host government",
+            choices = c("Friendly relationship with government",
+                        "Criticized by government", 
+                        "Under government crackdown"))
+```
+
+### Greenpeace Inputs
+
+```{r echo=FALSE}
+selectInput("gp_issue", 
+            label = "Select Issue Area:",
+            choices = c("Emergency response",
+                        "Environment",
+                        "Human rights",
+                        "Refugee relief"))
+
+selectInput("gp_fin_trans",
+            label = "Select Financial transparency:",
+            choices = c("Doesn’t engage in transparency",
+                        "Engages in transparency"))
+
+selectInput("gp_account",
+            label = "Select Financial Accountability:",
+            choices = c("Doesn’t engage in accountability",
+                        "Engages in financial accountability"))
+
+selectInput("gp_funding",
+            label = "Select Funding source:",
+            choices = c("Many small private donations",
+                        "Handful of wealthy private donors",
+                        "Government Grants"))
+
+selectInput("gp_gov_relat",
+            label = "Select Relationship with host government",
+            choices = c("Friendly relationship with government",
+                        "Criticized by government", 
+                        "Under government crackdown"))
+```
+
+### Oxfam Inputs
+
+```{r echo=FALSE}
+selectInput("ox_issue", 
+            label = "Select Issue Area:",
+            choices = c("Emergency response",
+                        "Environment",
+                        "Human rights",
+                        "Refugee relief"))
+
+selectInput("ox_fin_trans",
+            label = "Select Financial transparency:",
+            choices = c("Doesn’t engage in transparency",
+                        "Engages in transparency"))
+
+selectInput("ox_account",
+            label = "Select Financial Accountability:",
+            choices = c("Doesn’t engage in accountability",
+                        "Engages in financial accountability"))
+
+selectInput("ox_funding",
+            label = "Select Funding source:",
+            choices = c("Many small private donations",
+                        "Handful of wealthy private donors",
+                        "Government Grants"))
+
+selectInput("ox_gov_relat",
+            label = "Select Relationship with host government",
+            choices = c("Friendly relationship with government",
+                        "Criticized by government", 
+                        "Under government crackdown"))
+```
+
+### Red Cross Inputs
+
+```{r echo=FALSE}
+selectInput("rc_issue", 
+            label = "Select Issue Area:",
+            choices = c("Emergency response",
+                        "Environment",
+                        "Human rights",
+                        "Refugee relief"))
+
+selectInput("rc_fin_trans",
+            label = "Select Financial transparency:",
+            choices = c("Doesn’t engage in transparency",
+                        "Engages in transparency"))
+
+selectInput("rc_account",
+            label = "Select Financial Accountability:",
+            choices = c("Doesn’t engage in accountability",
+                        "Engages in financial accountability"))
+
+selectInput("rc_funding",
+            label = "Select Funding source:",
+            choices = c("Many small private donations",
+                        "Handful of wealthy private donors",
+                        "Government Grants"))
+
+selectInput("rc_gov_relat",
+            label = "Select Relationship with host government",
+            choices = c("Friendly relationship with government",
+                        "Criticized by government", 
+                        "Under government crackdown"))
+```
+
+Bottom of page buffer
+-----------------------------------------------
+
+<!-- Old Code from before is below this line It is just commented out  ( Cmd Shift C ) -->
+
+<!-- Organization Utility -->
+<!-- ------------------------------------- -->
+<!-- ## Amnesty International Expected Utility -->
+
+<!-- ```{r} -->
+<!-- renderValueBox({ -->
+<!--   choice = df() -->
+<!--   ai_exp_util <- round(exp(t(choice[,3]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   valueBox(ai_exp_util, -->
+<!--            color = "#FFC30B") -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- ## Greenpeace Expected Utility -->
+
+<!-- ```{r} -->
+<!-- renderValueBox({ -->
+<!--   choice = df() -->
+<!--   gp_exp_util <- round(exp(t(choice[,4]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   valueBox(gp_exp_util, -->
+<!--            color = "#3fad48") -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- ## Oxfam Expected Utility -->
+
+<!-- ```{r} -->
+<!-- renderValueBox({ -->
+<!--   choice = df() -->
+<!--   ox_exp_util <- round(exp(t(choice[,5]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   valueBox(ox_exp_util, -->
+<!--            color = "#006633") -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- ## Redcross Expected Utility -->
+
+<!-- ```{r} -->
+<!-- renderValueBox({ -->
+<!--   choice = df() -->
+<!--   rc_exp_util <- round(exp(t(choice[,6]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   valueBox(rc_exp_util, -->
+<!--            color = "#660000") -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- Expected Donors {.tabset .tabset-fade} -->
+<!-- ------------------------------------- -->
+<!-- ### Amnesty International Expected Donors -->
+
+<!-- ```{r echo=FALSE} -->
+<!-- renderGauge({ -->
+<!--   choice = df() -->
+<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+
+<!--   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+<!--   gauge(ai_rate,  -->
+<!--         min = 0,  -->
+<!--         max = 100, -->
+<!--         gaugeSectors(colors = "#FFC30B"), -->
+<!--         symbol = "%") -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- ### Greenpeace Expected Donors -->
+
+<!-- ```{r echo=FALSE} -->
+<!-- renderGauge({ -->
+<!--   choice = df() -->
+<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+
+<!--   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+<!--   gauge(gp_rate,  -->
+<!--         min = 0,  -->
+<!--         max = 100, -->
+<!--         gaugeSectors(colors = "#3fad48"), -->
+<!--         symbol = "%") -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- ### Oxfam Expected Donors -->
+
+<!-- ```{r echo=FALSE} -->
+<!-- renderGauge({ -->
+<!--   choice = df() -->
+<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+
+<!--   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+<!--   gauge(ox_rate,  -->
+<!--         min = 0,  -->
+<!--         max = 100, -->
+<!--         gaugeSectors(colors = "#006633"), -->
+<!--         symbol = "%") -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- ### Red Cross Expected Donors -->
+
+<!-- ```{r echo=FALSE} -->
+<!-- renderGauge({ -->
+<!--   choice = df() -->
+<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+
+<!--   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+<!--   gauge(rc_rate,  -->
+<!--         min = 0,  -->
+<!--         max = 100, -->
+<!--         gaugeSectors(colors = "#660000"), -->
+<!--         symbol = "%") -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- Organizational Inputs {.tabset .tabset-fade} -->
+<!-- ------------------------------------- -->
+<!-- ### Amnesty International Inputs -->
+
+<!-- ```{r echo=FALSE} -->
+<!-- selectInput("ai_issue",  -->
+<!--             label = "Select Issue Area:", -->
+<!--             choices = c("Emergency response", -->
+<!--                         "Environment", -->
+<!--                         "Human rights", -->
+<!--                         "Refugee relief")) -->
+
+<!-- selectInput("ai_fin_trans", -->
+<!--             label = "Select Financial transparency:", -->
+<!--             choices = c("Doesn’t engage in transparency", -->
+<!--                         "Engages in transparency")) -->
+
+<!-- selectInput("ai_account", -->
+<!--             label = "Select Financial Accountability:", -->
+<!--             choices = c("Doesn’t engage in financial accountability", -->
+<!--                         "Engages in financial accountability")) -->
+
+<!-- selectInput("ai_funding", -->
+<!--             label = "Select Funding source:", -->
+<!--             choices = c("Many small private donations", -->
+<!--                         "Handful of wealthy private donors", -->
+<!--                         "Government Grants")) -->
+
+<!-- selectInput("ai_gov_relat", -->
+<!--             label = "Select Relationship with host government", -->
+<!--             choices = c("Friendly relationship with government", -->
+<!--                         "Criticized by government",  -->
+<!--                         "Under government crackdown")) -->
+<!-- ``` -->
+
+<!-- ### Greenpeace Inputs -->
+
+<!-- ```{r echo=FALSE} -->
+<!-- selectInput("gp_issue",  -->
+<!--             label = "Select Issue Area:", -->
+<!--             choices = c("Emergency response", -->
+<!--                         "Environment", -->
+<!--                         "Human rights", -->
+<!--                         "Refugee relief")) -->
+
+<!-- selectInput("gp_fin_trans", -->
+<!--             label = "Select Financial transparency:", -->
+<!--             choices = c("Doesn’t engage in transparency", -->
+<!--                         "Engages in transparency")) -->
+
+<!-- selectInput("gp_account", -->
+<!--             label = "Select Financial Accountability:", -->
+<!--             choices = c("Doesn’t engage in accountability", -->
+<!--                         "Engages in financial accountability")) -->
+
+<!-- selectInput("gp_funding", -->
+<!--             label = "Select Funding source:", -->
+<!--             choices = c("Many small private donations", -->
+<!--                         "Handful of wealthy private donors", -->
+<!--                         "Government Grants")) -->
+
+<!-- selectInput("gp_gov_relat", -->
+<!--             label = "Select Relationship with host government", -->
+<!--             choices = c("Friendly relationship with government", -->
+<!--                         "Criticized by government",  -->
+<!--                         "Under government crackdown")) -->
+<!-- ``` -->
+
+<!-- ### Oxfam Inputs -->
+
+<!-- ```{r echo=FALSE} -->
+<!-- selectInput("ox_issue",  -->
+<!--             label = "Select Issue Area:", -->
+<!--             choices = c("Emergency response", -->
+<!--                         "Environment", -->
+<!--                         "Human rights", -->
+<!--                         "Refugee relief")) -->
+
+<!-- selectInput("ox_fin_trans", -->
+<!--             label = "Select Financial transparency:", -->
+<!--             choices = c("Doesn’t engage in transparency", -->
+<!--                         "Engages in transparency")) -->
+
+<!-- selectInput("ox_account", -->
+<!--             label = "Select Financial Accountability:", -->
+<!--             choices = c("Doesn’t engage in accountability", -->
+<!--                         "Engages in financial accountability")) -->
+
+<!-- selectInput("ox_funding", -->
+<!--             label = "Select Funding source:", -->
+<!--             choices = c("Many small private donations", -->
+<!--                         "Handful of wealthy private donors", -->
+<!--                         "Government Grants")) -->
+
+<!-- selectInput("ox_gov_relat", -->
+<!--             label = "Select Relationship with host government", -->
+<!--             choices = c("Friendly relationship with government", -->
+<!--                         "Criticized by government",  -->
+<!--                         "Under government crackdown")) -->
+<!-- ``` -->
+
+<!-- ### Red Cross Inputs -->
+
+<!-- ```{r echo=FALSE} -->
+<!-- selectInput("rc_issue",  -->
+<!--             label = "Select Issue Area:", -->
+<!--             choices = c("Emergency response", -->
+<!--                         "Environment", -->
+<!--                         "Human rights", -->
+<!--                         "Refugee relief")) -->
+
+<!-- selectInput("rc_fin_trans", -->
+<!--             label = "Select Financial transparency:", -->
+<!--             choices = c("Doesn’t engage in transparency", -->
+<!--                         "Engages in transparency")) -->
+
+<!-- selectInput("rc_account", -->
+<!--             label = "Select Financial Accountability:", -->
+<!--             choices = c("Doesn’t engage in accountability", -->
+<!--                         "Engages in financial accountability")) -->
+
+<!-- selectInput("rc_funding", -->
+<!--             label = "Select Funding source:", -->
+<!--             choices = c("Many small private donations", -->
+<!--                         "Handful of wealthy private donors", -->
+<!--                         "Government Grants")) -->
+
+<!-- selectInput("rc_gov_relat", -->
+<!--             label = "Select Relationship with host government", -->
+<!--             choices = c("Friendly relationship with government", -->
+<!--                         "Criticized by government",  -->
+<!--                         "Under government crackdown")) -->
+<!-- ``` -->

### 2020-08-05 analysis/05_market_simulator.Rmd
Commented out Sidebar. Change page layout from Pages to Rows. Added tabset placeholders

@@
 
-Persona Inputs {.sidebar}
-=================================================
-
-## Persona Inputs
-
-```{r sidebar inputs, echo=FALSE}
-
-# selectInput("model_choice", 
-#             label = "Select Model:",
-#             choices = c("public_political_social_charity_demo"))
-
-selectInput("charity_importance", 
-          label = "Charity Importance:",
-          choices = c("0", '1', '2', '3','4','5','6','7'))
-
-selectInput("trust_in_charity", 
-            label = "Charity Trust:",
-            choices = c("0", '1', '2', '3','4','5','6','7'))
-
-selectInput("donation_frequency", 
-         label = "Donation Frequency:",
-         choices = c('Once a week', 
-                     'Once a Month',
-                     'Once every three months',
-                     'Once every six months', 
-                     'Once a year', 
-                     'Once every few years',
-                     'Never'))
-
-selectInput("donation_amount", 
-         label = "Donation Amount:",
-         choices = c("$1-$49", 
-                     '$50-$99', 
-                     '$100-$499',
-                     '$500-$999',
-                     '$1,000-$4,999',
-                     '$5,000-$9,999',
-                     '$10,000+'))
-
-selectInput("volunteer_12", 
-         label = "Volunteered in last 12 Months:",
-         choices = c("Yes", "No"))
-
-selectInput("volunteer_frequency", 
-         label = "Volunteer Frequency:",
-         choices = c('Once a week',
-                     'Once a Month',
-                     'Once every three months', 
-                     'Once every six months', 
-                     'Once a year', 
-                     'Once every few years',
-                     'Never'))
-
-selectInput("personal_activism", 
-         label = "Personal Activism:",
-         choices = c('Extremely involved',
-                     'Very involved', 
-                     'Moderately involved', 
-                     'Slightly involved',
-                     'Never involved'))
-
-selectInput("family_activism", 
-         label = "Family Activism:",
-         choices = c('Extremely involved', 
-                     'Very involved', 
-                     'Moderately involved', 
-                     'Slightly involved',
-                     'Never involved'))
-
-selectInput("religious_member", 
-         label = "Church Membership:",
-         choices = c('Active Member', 
-                     'Inactive Member', 
-                     "Don't belong"))
-
-selectInput("sport_member", 
-         label = "Sport or Recreational Membership:",
-         choices = c('Active Member', 
-                     'Inactive Member', 
-                     "Don't belong"))
-
-selectInput("art_member", 
-         label = "Art, Music, or Educational Membership:",
-         choices = c('Active Member', 
-                     'Inactive Member', 
-                     "Don't belong"))
-
-selectInput("labor_member", 
-         label = "Labor Union Membership:",
-         choices = c('Active Member', 
-                     'Inactive Member', 
-                     "Don't belong"))
-
-selectInput("political_member", 
-         label = "Political Party Membership:",
-         choices = c('Active Member', 
-                     'Inactive Member', 
-                     "Don't belong"))
-
-selectInput("environmental_member", 
-         label = "Enviornmental Org. Membership:",
-         choices = c('Active Member', 
-                     'Inactive Member', 
-                     "Don't belong"))
-
-selectInput("professional_member", 
-         label = "Professional Membership:",
-         choices = c('Active Member', 
-                     'Inactive Member', 
-                     "Don't belong"))
-
-selectInput("humanitarian_member", 
-         label = "Humanitarian Org. Membership:",
-         choices = c('Active Member', 
-                     'Inactive Member', 
-                     "Don't belong"))
-
-selectInput("consumer_member", 
-         label = "Consumer Org. Membership:",
-         choices = c('Active Member', 
-                     'Inactive Member', 
-                     "Don't belong"))
-
-selectInput("religious_member", 
-         label = "Church Membership:",
-         choices = c('Active Member', 
-                     'Inactive Member', 
-                     "Don't belong"))
-
-selectInput("other_member", 
-         label = "Other Org. Membership:",
-         choices = c('Active Member', 
-                     'Inactive Member', 
-                     "Don't belong"))
-
-selectInput("national_news", 
-         label = "Follow national news:",
-         choices = c('Multiple times a day', 
-                     'Every day', 
-                     "Once a week",
-                     "Hardly ever",
-                     "Never"))
-
-selectInput("international_news", 
-         label = "Follow international news:",
-         choices = c('Always',
-                     "Sometimes",
-                     "Never"))
-
-selectInput("news_medium", 
-         label = "Medium to follow news:",
-         choices = c('TV', 
-                     'Print', 
-                     "Online",
-                     "Social Media",
-                     "Radio",
-                     "Email newsletters",
-                     "News app"))
-
-selectInput("international_news", 
-         label = "Follow international news:",
-         choices = c('Multiple times a day', 
-                     'Every day', 
-                     "Once a week",
-                     "Hardly ever",
-                     "Never"))
-
-selectInput("follow_gov", 
-         label = "Follow government & public affairs:",
-         choices = c('Most of the time', 
-                     'Some of the time', 
-                     "Only now and then",
-                     "Hardly at all"))
-
-selectInput("travel_developing", 
-         label = "Travel to developing country:",
-         choices = c('Yes', 'No'))
-
-selectInput("polical_pref", 
-         label = "Polical views from liberal to conservative:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
-
-selectInput("institution_trust", 
-         label = "Political institution trust from none to complete:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
-
-selectInput("others_charitable", 
-         label = "People should be more charitable:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
-
-selectInput("worship_attendance", 
-         label = "Worship service attendance:",
-         choices = c('Multiple times a week', 
-                     'Once a week', 
-                     "Once a month",
-                     "Once a year",
-                     "Never"))
-
-selectInput("religion_importance", 
-         label = "Importance of religion:",
-         choices = c('Extremely important',
-                     'Very important',
-                     'Moderately important',
-                     'Slightly important',
-                     'Not at all important'))
-
-selectInput("religion", 
-         label = "Religion:",
-         choices = c('Catholic',
-                     'Protestant',
-                     'Christian Orthodox',
-                     'Jewish',
-                     'Muslim',
-                     'Sikh',
-                     'Hindu',
-                     'Buddhist',
-                     'Atheist',
-                     'Other'))
-
-selectInput("gender", 
-         label = "Gender:",
-         choices = c("Male",
-                     "Female",
-                     "Transgender",
-                     "Prefer not to say",
-                     "Other"))
-
-selectInput("marital_status", 
-         label = "Marital Status:",
-         choices = c("Married",
-                     "Widowed",
-                     "Divorced",
-                     "Separated",
-                     "Never married"))
-
-selectInput("education", 
-         label = "Education:",
-         choices = c("Less than high school",
-                     "High school",
-                     "Some college",
-                     "2 year degree",
-                     "4 year degree",
-                     "Graduate degree",
-                     "Doctorate"))
-
-selectInput("income", 
-         label = "Income:",
-         choices = c('Less than $10,000', 
-                     '$10,000 to $19,999',
-                     '$20,000 to $29,999',
-                     '$30,000 to $39,999',
-                     '$40,000 to $49,999',
-                     '$50,000 to $59,999',
-                     '$60,000 to $69,999',
-                     '$70,000 to $79,999',
-                     '$80,000 to $89,999',
-                     '$90,000 to $99,999',
-                     '$100,000 to $149,999',
-                     '$150,000 to $199,999',
-                     '$200,000 to $299,999',
-                     '$300,000 or more'))
-
-selectInput("race", 
-         label = "Race(s):",
-         choices = c('White',
-                     'Black or African American',
-                     'American Indian or Alaska Native',
-                     'Asian',
-                     'Native Hawaiian or Pacific Islander',
-                     'Other'), 
-         multiple = TRUE)
-
-selectInput("education", 
-         label = "Education:",
-         choices = c("Less than high school",
-                     "High school",
-                     "Some college",
-                     "2 year degree",
-                     "4 year degree",
-                     "Graduate degree",
-                     "Doctorate"))
-
-selectInput("age", 
-         label = "Age:",
-         choices = c('Under 18',
-                     '18 - 24',
-                     '25 - 34',
-                     '35 - 44',
-                     '45 - 54',
-                     '55 - 64',
-                     '65 - 74',
-                     '75 - 84',
-                     '85 or older'))
-
-```
+<!-- Persona Inputs {.sidebar} -->
+<!-- ================================================= -->
+
+<!-- ## Persona Inputs -->
+
+<!-- ```{r sidebar inputs, echo=FALSE} -->
+
+<!-- # selectInput("model_choice",  -->
+<!-- #             label = "Select Model:", -->
+<!-- #             choices = c("public_political_social_charity_demo")) -->
+
+<!-- selectInput("charity_importance",  -->
+<!--           label = "Charity Importance:", -->
+<!--           choices = c("0", '1', '2', '3','4','5','6','7')) -->
+
+<!-- selectInput("trust_in_charity",  -->
+<!--             label = "Charity Trust:", -->
+<!--             choices = c("0", '1', '2', '3','4','5','6','7')) -->
+
+<!-- selectInput("donation_frequency",  -->
+<!--          label = "Donation Frequency:", -->
+<!--          choices = c('Once a week',  -->
+<!--                      'Once a Month', -->
+<!--                      'Once every three months', -->
+<!--                      'Once every six months',  -->
+<!--                      'Once a year',  -->
+<!--                      'Once every few years', -->
+<!--                      'Never')) -->
+
+<!-- selectInput("donation_amount",  -->
+<!--          label = "Donation Amount:", -->
+<!--          choices = c("$1-$49",  -->
+<!--                      '$50-$99',  -->
+<!--                      '$100-$499', -->
+<!--                      '$500-$999', -->
+<!--                      '$1,000-$4,999', -->
+<!--                      '$5,000-$9,999', -->
+<!--                      '$10,000+')) -->
+
+<!-- selectInput("volunteer_12",  -->
+<!--          label = "Volunteered in last 12 Months:", -->
+<!--          choices = c("Yes", "No")) -->
+
+<!-- selectInput("volunteer_frequency",  -->
+<!--          label = "Volunteer Frequency:", -->
+<!--          choices = c('Once a week', -->
+<!--                      'Once a Month', -->
+<!--                      'Once every three months',  -->
+<!--                      'Once every six months',  -->
+<!--                      'Once a year',  -->
+<!--                      'Once every few years', -->
+<!--                      'Never')) -->
+
+<!-- selectInput("personal_activism",  -->
+<!--          label = "Personal Activism:", -->
+<!--          choices = c('Extremely involved', -->
+<!--                      'Very involved',  -->
+<!--                      'Moderately involved',  -->
+<!--                      'Slightly involved', -->
+<!--                      'Never involved')) -->
+
+<!-- selectInput("family_activism",  -->
+<!--          label = "Family Activism:", -->
+<!--          choices = c('Extremely involved',  -->
+<!--                      'Very involved',  -->
+<!--                      'Moderately involved',  -->
+<!--                      'Slightly involved', -->
+<!--                      'Never involved')) -->
+
+<!-- selectInput("religious_member",  -->
+<!--          label = "Church Membership:", -->
+<!--          choices = c('Active Member',  -->
+<!--                      'Inactive Member',  -->
+<!--                      "Don't belong")) -->
+
+<!-- selectInput("sport_member",  -->
+<!--          label = "Sport or Recreational Membership:", -->
+<!--          choices = c('Active Member',  -->
+<!--                      'Inactive Member',  -->
+<!--                      "Don't belong")) -->
+
+<!-- selectInput("art_member",  -->
+<!--          label = "Art, Music, or Educational Membership:", -->
+<!--          choices = c('Active Member',  -->
+<!--                      'Inactive Member',  -->
+<!--                      "Don't belong")) -->
+
+<!-- selectInput("labor_member",  -->
+<!--          label = "Labor Union Membership:", -->
+<!--          choices = c('Active Member',  -->
+<!--                      'Inactive Member',  -->
+<!--                      "Don't belong")) -->
+
+<!-- selectInput("political_member",  -->
+<!--          label = "Political Party Membership:", -->
+<!--          choices = c('Active Member',  -->
+<!--                      'Inactive Member',  -->
+<!--                      "Don't belong")) -->
+
+<!-- selectInput("environmental_member",  -->
+<!--          label = "Enviornmental Org. Membership:", -->
+<!--          choices = c('Active Member',  -->
+<!--                      'Inactive Member',  -->
+<!--                      "Don't belong")) -->
+
+<!-- selectInput("professional_member",  -->
+<!--          label = "Professional Membership:", -->
+<!--          choices = c('Active Member',  -->
+<!--                      'Inactive Member',  -->
+<!--                      "Don't belong")) -->
+
+<!-- selectInput("humanitarian_member",  -->
+<!--          label = "Humanitarian Org. Membership:", -->
+<!--          choices = c('Active Member',  -->
+<!--                      'Inactive Member',  -->
+<!--                      "Don't belong")) -->
+
+<!-- selectInput("consumer_member",  -->
+<!--          label = "Consumer Org. Membership:", -->
+<!--          choices = c('Active Member',  -->
+<!--                      'Inactive Member',  -->
+<!--                      "Don't belong")) -->
+
+<!-- selectInput("religious_member",  -->
+<!--          label = "Church Membership:", -->
+<!--          choices = c('Active Member',  -->
+<!--                      'Inactive Member',  -->
+<!--                      "Don't belong")) -->
+
+<!-- selectInput("other_member",  -->
+<!--          label = "Other Org. Membership:", -->
+<!--          choices = c('Active Member',  -->
+<!--                      'Inactive Member',  -->
+<!--                      "Don't belong")) -->
+
+<!-- selectInput("national_news",  -->
+<!--          label = "Follow national news:", -->
+<!--          choices = c('Multiple times a day',  -->
+<!--                      'Every day',  -->
+<!--                      "Once a week", -->
+<!--                      "Hardly ever", -->
+<!--                      "Never")) -->
+
+<!-- selectInput("international_news",  -->
+<!--          label = "Follow international news:", -->
+<!--          choices = c('Always', -->
+<!--                      "Sometimes", -->
+<!--                      "Never")) -->
+
+<!-- selectInput("news_medium",  -->
+<!--          label = "Medium to follow news:", -->
+<!--          choices = c('TV',  -->
+<!--                      'Print',  -->
+<!--                      "Online", -->
+<!--                      "Social Media", -->
+<!--                      "Radio", -->
+<!--                      "Email newsletters", -->
+<!--                      "News app")) -->
+
+<!-- selectInput("international_news",  -->
+<!--          label = "Follow international news:", -->
+<!--          choices = c('Multiple times a day',  -->
+<!--                      'Every day',  -->
+<!--                      "Once a week", -->
+<!--                      "Hardly ever", -->
+<!--                      "Never")) -->
+
+<!-- selectInput("follow_gov",  -->
+<!--          label = "Follow government & public affairs:", -->
+<!--          choices = c('Most of the time',  -->
+<!--                      'Some of the time',  -->
+<!--                      "Only now and then", -->
+<!--                      "Hardly at all")) -->
+
+<!-- selectInput("travel_developing",  -->
+<!--          label = "Travel to developing country:", -->
+<!--          choices = c('Yes', 'No')) -->
+
+<!-- selectInput("polical_pref",  -->
+<!--          label = "Polical views from liberal to conservative:", -->
+<!--          choices = c("0", '1', '2', '3','4','5','6','7')) -->
+
+<!-- selectInput("institution_trust",  -->
+<!--          label = "Political institution trust from none to complete:", -->
+<!--          choices = c("0", '1', '2', '3','4','5','6','7')) -->
+
+<!-- selectInput("others_charitable",  -->
+<!--          label = "People should be more charitable:", -->
+<!--          choices = c("0", '1', '2', '3','4','5','6','7')) -->
+
+<!-- selectInput("worship_attendance",  -->
+<!--          label = "Worship service attendance:", -->
+<!--          choices = c('Multiple times a week',  -->
+<!--                      'Once a week',  -->
+<!--                      "Once a month", -->
+<!--                      "Once a year", -->
+<!--                      "Never")) -->
+
+<!-- selectInput("religion_importance",  -->
+<!--          label = "Importance of religion:", -->
+<!--          choices = c('Extremely important', -->
+<!--                      'Very important', -->
+<!--                      'Moderately important', -->
+<!--                      'Slightly important', -->
+<!--                      'Not at all important')) -->
+
+<!-- selectInput("religion",  -->
+<!--          label = "Religion:", -->
+<!--          choices = c('Catholic', -->
+<!--                      'Protestant', -->
+<!--                      'Christian Orthodox', -->
+<!--                      'Jewish', -->
+<!--                      'Muslim', -->
+<!--                      'Sikh', -->
+<!--                      'Hindu', -->
+<!--                      'Buddhist', -->
+<!--                      'Atheist', -->
+<!--                      'Other')) -->
+
+<!-- selectInput("gender",  -->
+<!--          label = "Gender:", -->
+<!--          choices = c("Male", -->
+<!--                      "Female", -->
+<!--                      "Transgender", -->
+<!--                      "Prefer not to say", -->
+<!--                      "Other")) -->
+
+<!-- selectInput("marital_status",  -->
+<!--          label = "Marital Status:", -->
+<!--          choices = c("Married", -->
+<!--                      "Widowed", -->
+<!--                      "Divorced", -->
+<!--                      "Separated", -->
+<!--                      "Never married")) -->
+
+<!-- selectInput("education",  -->
+<!--          label = "Education:", -->
+<!--          choices = c("Less than high school", -->
+<!--                      "High school", -->
+<!--                      "Some college", -->
+<!--                      "2 year degree", -->
+<!--                      "4 year degree", -->
+<!--                      "Graduate degree", -->
+<!--                      "Doctorate")) -->
+
+<!-- selectInput("income",  -->
+<!--          label = "Income:", -->
+<!--          choices = c('Less than $10,000',  -->
+<!--                      '$10,000 to $19,999', -->
+<!--                      '$20,000 to $29,999', -->
+<!--                      '$30,000 to $39,999', -->
+<!--                      '$40,000 to $49,999', -->
+<!--                      '$50,000 to $59,999', -->
+<!--                      '$60,000 to $69,999', -->
+<!--                      '$70,000 to $79,999', -->
+<!--                      '$80,000 to $89,999', -->
+<!--                      '$90,000 to $99,999', -->
+<!--                      '$100,000 to $149,999', -->
+<!--                      '$150,000 to $199,999', -->
+<!--                      '$200,000 to $299,999', -->
+<!--                      '$300,000 or more')) -->
+
+<!-- selectInput("race",  -->
+<!--          label = "Race(s):", -->
+<!--          choices = c('White', -->
+<!--                      'Black or African American', -->
+<!--                      'American Indian or Alaska Native', -->
+<!--                      'Asian', -->
+<!--                      'Native Hawaiian or Pacific Islander', -->
+<!--                      'Other'),  -->
+<!--          multiple = TRUE) -->
+
+<!-- selectInput("education",  -->
+<!--          label = "Education:", -->
+<!--          choices = c("Less than high school", -->
+<!--                      "High school", -->
+<!--                      "Some college", -->
+<!--                      "2 year degree", -->
+<!--                      "4 year degree", -->
+<!--                      "Graduate degree", -->
+<!--                      "Doctorate")) -->
+
+<!-- selectInput("age",  -->
+<!--          label = "Age:", -->
+<!--          choices = c('Under 18', -->
+<!--                      '18 - 24', -->
+<!--                      '25 - 34', -->
+<!--                      '35 - 44', -->
+<!--                      '45 - 54', -->
+<!--                      '55 - 64', -->
+<!--                      '65 - 74', -->
+<!--                      '75 - 84', -->
+<!--                      '85 or older')) -->
+
+<!-- ``` -->
 
@@
 Market Share Per Persona 
-==================================================
-
-### Market Share Per Persona
+--------------------------------------
 
@@
 
-Persona 1 
-====================================================
-
-Market Share and Expected Utility
+Persona 1 (change this to Org 1) {.tabset .tabset-fade}
 --------------------------------------------------
+
+### Market Share Chart Persona 1
+<!-- Might get rid of this graph -->
 
@@
 
-Organization Market Share
--------------------------------------
 ### Amnesty International Market Share
@@
 
-Organizational Inputs {.tabset .tabset-fade}
+Organizations {.tabset .tabset-fade}
 -------------------------------------
-### Amnesty International Inputs
+### Amnesty International
 
@@
 
-### Greenpeace Inputs
+```{r echo=FALSE}
+renderGauge({
+  choice = df()
+  persona = p_beta1 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(ai_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#FFC30B"),
+        symbol = "%")
+})
+```
+
+### Greenpeace
 
@@
 
-### Oxfam Inputs
+### Oxfam
 
@@
 
-### Red Cross Inputs
+### Red Cross
 
@@
 
-Bottom of page buffer
------------------------------------------------
-
 <!-- Persona 2 Page -->
 
-Persona 2
-===============================================
-
-Market Share
+Persona 2 {.tabset .tabset-fade}
 --------------------------------------------------
+
+### Market Share Persona 2
+
 ```{r plot persona 2}
@@
 
-Bottom of page buffer
------------------------------------------------
-
 <!-- Persona 3 Page  -->
 
-Persona 3
-===============================================
-
-Market Share 
-------------------------------------------------
+Persona 3 {.tabset .tabset-fade}
+--------------------------------------------------
+
+### Market Share Persona 3
 ```{r plot persona 3}
@@
 ```
-
-Bottom of page buffer
------------------------------------------------
 
@@
 
-<!-- Expected Donors {.tabset .tabset-fade} -->
-<!-- ------------------------------------- -->
-<!-- ### Amnesty International Expected Donors -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- renderGauge({ -->
-<!--   choice = df() -->
-<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-
-<!--   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-<!--   gauge(ai_rate,  -->
-<!--         min = 0,  -->
-<!--         max = 100, -->
-<!--         gaugeSectors(colors = "#FFC30B"), -->
-<!--         symbol = "%") -->
-<!-- }) -->
-<!-- ``` -->
+Expected Donors {.tabset .tabset-fade}
+-------------------------------------
+### Amnesty International Expected Donors
+
+```{r echo=FALSE}
+renderGauge({
+  choice = df()
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
+
+  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+  gauge(ai_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#FFC30B"),
+        symbol = "%")
+})
+```
 

### 2020-08-05 analysis/05_market_simulator.Rmd
Reorganized the layout made only one set of tabs of each organizations with personas, org inputs, and gauges

@@
 
-<!-- Persona 1 page -->
-
-Persona 1 (change this to Org 1) {.tabset .tabset-fade}
+<!-- Organizational Tabs -->
+
+Organization Breakdown {.tabset .tabset-fade}
 --------------------------------------------------
-
-### Market Share Chart Persona 1
-<!-- Might get rid of this graph -->
-
-```{r plot person 1}
+### Amnesty International Market Share
+
+```{r plot ai plot}
 renderPlotly({
   choice = df()
+
+    persona1 = p_beta1 # Choose the persona
+
+  ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
+  gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
+  ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
+  rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+
+  ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+
+    persona2 = p_beta2 # Choose the persona
+
+  ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
+  gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
+  ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
+  rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+
+  ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+
+      persona3 = p_beta3 # Choose the persona
+
+  ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
+  gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
+  ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
+  rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+
+  ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+
+  data <- c(ai_exp_util1, ai_rate1, 
+            ai_exp_util2, ai_rate2,
+            ai_exp_util3, ai_rate3)
+
+  df <- as.data.frame(matrix(data, 6, 1))
+
+  df[,2] <- c("Amnesty International")
+  df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
+  df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
+  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+
+  ggplotly(df %>% filter(Type == "Market Share") %>% 
+             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+             geom_bar(position = "dodge", stat = "identity") +
+             labs(x="") + 
+             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+             theme(legend.position = "none")
+    )
+})
+```
+
+```{r valuebox ai}
+renderValueBox({
+  choice = df()
+
   persona = p_beta1 # Choose the persona
@@
   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate)
-  df <- as.data.frame(matrix(data, 8, 1))
-
-  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
-  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
-  df[,4] <- rep(c("Persona 1","Persona 2", "Persona 3"), length.out = 8)
-  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
-
-  ggplotly(df %>% filter(Type == "Market Share") %>% 
-             ggplot(aes(y = Value, x = Organization, fill = Organization)) +
-             geom_col() +
-             labs(x="") + 
-             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
-             theme(legend.position = "none") +
-             facet_wrap(~Type)
-    )
-})
-```
-
-### Amnesty International Market Share
-
-```{r valuebox ai persona 1}
-renderValueBox({
-  choice = df()
-
-  persona = p_beta1 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-
-  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
 
@@
 
-### Greenpeace Market Share
-
-```{r valuebox gp persona 1}
-renderValueBox({
-  choice = df()
-  persona = p_beta1 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-
-  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(gp_rate,
-           color = "#3fad48",
-           icon = "fa-percent")
-})
-```
-
-### Oxfam Market Share
-
-```{r valuebox ox persona 1}
-renderValueBox({
-  choice = df()
-
-  persona = p_beta1 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-
-  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(ox_rate,
-           color = "#006633",
-           icon = "fa-percent")
-})
-```
-
-### Redcross Market Share
-
-```{r valuebox rc persona 1}
-renderValueBox({
-  choice = df()
-
-  persona = p_beta1 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-
-  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(rc_rate,
-           color = "#660000",
-           icon = "fa-percent")
-})
-```
-
-Organizations {.tabset .tabset-fade}
--------------------------------------
-### Amnesty International
-
-```{r echo=FALSE}
+```{r ai org inputs}
 selectInput("ai_issue", 
@@
 
-```{r echo=FALSE}
+```{r ai gauge}
 renderGauge({
@@
 
-### Greenpeace
-
-```{r echo=FALSE}
+### Greenpeace Market Share
+
+```{r plot gp plot}
+renderPlotly({
+  choice = df()
+
+    persona1 = p_beta1 # Choose the persona
+
+  ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
+  gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
+  ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
+  rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+
+  ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+
+    persona2 = p_beta2 # Choose the persona
+
+  ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
+  gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
+  ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
+  rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+
+  ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+
+      persona3 = p_beta3 # Choose the persona
+
+  ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
+  gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
+  ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
+  rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+
+  ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+
+  data <- c(gp_exp_util1, gp_rate1, 
+            gp_exp_util2, gp_rate2,
+            gp_exp_util3, gp_rate3)
+
+  df <- as.data.frame(matrix(data, 6, 1))
+
+  df[,2] <- c("Greenpeace")
+  df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
+  df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
+  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+
+  ggplotly(df %>% filter(Type == "Market Share") %>% 
+             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+             geom_bar(position = "dodge", stat = "identity") +
+             labs(x="") + 
+             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+             theme(legend.position = "none")
+    )
+})
+```
+
+```{r valuebox gp}
+renderValueBox({
+  choice = df()
+  persona = p_beta1 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  valueBox(gp_rate,
+           color = "#3fad48",
+           icon = "fa-percent")
+})
+```
+
+```{r gp org inputs}
 selectInput("gp_issue", 
@@
 
-### Oxfam
-
-```{r echo=FALSE}
+```{r gp gauge}
+renderGauge({
+  choice = df()
+  persona = p_beta1 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(gp_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#3fad48"),
+        symbol = "%")
+})
+```
+
+### Oxfam Market Share
+
+```{r plot ox plot}
+renderPlotly({
+  choice = df()
+
+    persona1 = p_beta1 # Choose the persona
+
+  ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
+  gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
+  ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
+  rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+
+  ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+
+    persona2 = p_beta2 # Choose the persona
+
+  ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
+  gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
+  ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
+  rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+
+  ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+
+      persona3 = p_beta3 # Choose the persona
+
+  ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
+  gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
+  ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
+  rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+
+  ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+
+  data <- c(ox_exp_util1, ox_rate1, 
+            ox_exp_util2, ox_rate2,
+            ox_exp_util3, ox_rate3)
+
+  df <- as.data.frame(matrix(data, 6, 1))
+
+  df[,2] <- c("Oxfam")
+  df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
+  df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
+  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+
+  ggplotly(df %>% filter(Type == "Market Share") %>% 
+             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+             geom_bar(position = "dodge", stat = "identity") +
+             labs(x="") + 
+             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+             theme(legend.position = "none")
+    )
+})
+```
+
+```{r valuebox ox}
+renderValueBox({
+  choice = df()
+
+  persona = p_beta1 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  valueBox(ox_rate,
+           color = "#006633",
+           icon = "fa-percent")
+})
+```
+
+```{r ox org inputs}
 selectInput("ox_issue", 
@@
 
-### Red Cross
-
-```{r echo=FALSE}
+```{r ox gauge}
+renderGauge({
+  choice = df()
+  persona = p_beta1 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(ox_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#006633"),
+        symbol = "%")
+})
+```
+
+### Redcross Market Share
+
+```{r plot rc plot}
+renderPlotly({
+  choice = df()
+
+    persona1 = p_beta1 # Choose the persona
+
+  ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
+  gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
+  ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
+  rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+
+  ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+
+    persona2 = p_beta2 # Choose the persona
+
+  ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
+  gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
+  ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
+  rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+
+  ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+
+      persona3 = p_beta3 # Choose the persona
+
+  ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
+  gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
+  ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
+  rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+
+  ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+
+  data <- c(rc_exp_util1, rc_rate1, 
+            rc_exp_util2, rc_rate2,
+            rc_exp_util3, rc_rate3)
+
+  df <- as.data.frame(matrix(data, 6, 1))
+
+  df[,2] <- c("Red Cross")
+  df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
+  df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
+  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+
+  ggplotly(df %>% filter(Type == "Market Share") %>% 
+             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+             geom_bar(position = "dodge", stat = "identity") +
+             labs(x="") + 
+             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+             theme(legend.position = "none")
+    )
+})
+```
+
+```{r valuebox rc}
+renderValueBox({
+  choice = df()
+
+  persona = p_beta1 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  valueBox(rc_rate,
+           color = "#660000",
+           icon = "fa-percent")
+})
+```
+
+```{r rc org inputs}
 selectInput("rc_issue", 
@@
 
-<!-- There is an issue of not being able to see the last selectInput options when drop down box appears -->
-
-<!-- Persona 2 Page -->
-
-Persona 2 {.tabset .tabset-fade}
---------------------------------------------------
-
-### Market Share Persona 2
-
-```{r plot persona 2}
-renderPlotly({
+```{r rc gauge}
+renderGauge({
   choice = df()
-
-  persona = p_beta2 # Choose the persona
+  persona = p_beta1 # Choose the persona
 
@@
 
-  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
 
-  data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate)
-  df <- as.data.frame(matrix(data, 8, 1))
-
-  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
-  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
-  df[,4] <- rep(c("Persona 1","Persona 2", "Persona 3"), length.out = 8)
-  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
-
-  ggplotly(df %>% filter(Type == "Market Share") %>% 
-             ggplot(aes(y = Value, x = Organization, fill = Organization)) +
-             geom_col() +
-             labs(x="") + 
-             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
-             theme(legend.position = "none") +
-             facet_wrap(~Type)
-    )
+  gauge(rc_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#660000"),
+        symbol = "%")
 })
@@
 
-### Amnesty International Market Share
-
-```{r valuebox ai persona 2}
-renderValueBox({
-  choice = df()
-
-  persona = p_beta2 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-
-  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(ai_rate,
-           color = "#FFC30B",
-           icon = "fa-percent")
-})
-```
-
-### Greenpeace Market Share
-
-```{r valuebox gp persona 2}
-renderValueBox({
-  choice = df()
-
-  persona = p_beta2 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-
-  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(gp_rate,
-           color = "#3fad48",
-           icon = "fa-percent")
-})
-```
-
-### Oxfam Market Share
-
-```{r valuebox ox persona 2}
-renderValueBox({
-  choice = df()
-
-  persona = p_beta2 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-
-  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(ox_rate,
-           color = "#006633",
-           icon = "fa-percent")
-})
-```
-
-### Redcross Market Share
-
-```{r valuebox rc persona 2}
-renderValueBox({
-  choice = df()
-
-  persona = p_beta2 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-
-  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(rc_rate,
-           color = "#660000",
-           icon = "fa-percent")
-})
-```
-
-Organizational Inputs {.tabset .tabset-fade}
--------------------------------------
-### Amnesty International Inputs
-
-```{r echo=FALSE}
-selectInput("ai_issue", 
-            label = "Select Issue Area:",
-            choices = c("Emergency response",
-                        "Environment",
-                        "Human rights",
-                        "Refugee relief"))
-
-selectInput("ai_fin_trans",
-            label = "Select Financial transparency:",
-            choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"))
-
-selectInput("ai_account",
-            label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in financial accountability",
-                        "Engages in financial accountability"))
-
-selectInput("ai_funding",
-            label = "Select Funding source:",
-            choices = c("Many small private donations",
-                        "Handful of wealthy private donors",
-                        "Government Grants"))
-
-selectInput("ai_gov_relat",
-            label = "Select Relationship with host government",
-            choices = c("Friendly relationship with government",
-                        "Criticized by government", 
-                        "Under government crackdown"))
-```
-
-### Greenpeace Inputs
-
-```{r echo=FALSE}
-selectInput("gp_issue", 
-            label = "Select Issue Area:",
-            choices = c("Emergency response",
-                        "Environment",
-                        "Human rights",
-                        "Refugee relief"))
-
-selectInput("gp_fin_trans",
-            label = "Select Financial transparency:",
-            choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"))
-
-selectInput("gp_account",
-            label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in accountability",
-                        "Engages in financial accountability"))
-
-selectInput("gp_funding",
-            label = "Select Funding source:",
-            choices = c("Many small private donations",
-                        "Handful of wealthy private donors",
-                        "Government Grants"))
-
-selectInput("gp_gov_relat",
-            label = "Select Relationship with host government",
-            choices = c("Friendly relationship with government",
-                        "Criticized by government", 
-                        "Under government crackdown"))
-```
-
-### Oxfam Inputs
-
-```{r echo=FALSE}
-selectInput("ox_issue", 
-            label = "Select Issue Area:",
-            choices = c("Emergency response",
-                        "Environment",
-                        "Human rights",
-                        "Refugee relief"))
-
-selectInput("ox_fin_trans",
-            label = "Select Financial transparency:",
-            choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"))
-
-selectInput("ox_account",
-            label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in accountability",
-                        "Engages in financial accountability"))
-
-selectInput("ox_funding",
-            label = "Select Funding source:",
-            choices = c("Many small private donations",
-                        "Handful of wealthy private donors",
-                        "Government Grants"))
-
-selectInput("ox_gov_relat",
-            label = "Select Relationship with host government",
-            choices = c("Friendly relationship with government",
-                        "Criticized by government", 
-                        "Under government crackdown"))
-```
-
-### Red Cross Inputs
-
-```{r echo=FALSE}
-selectInput("rc_issue", 
-            label = "Select Issue Area:",
-            choices = c("Emergency response",
-                        "Environment",
-                        "Human rights",
-                        "Refugee relief"))
-
-selectInput("rc_fin_trans",
-            label = "Select Financial transparency:",
-            choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"))
-
-selectInput("rc_account",
-            label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in accountability",
-                        "Engages in financial accountability"))
-
-selectInput("rc_funding",
-            label = "Select Funding source:",
-            choices = c("Many small private donations",
-                        "Handful of wealthy private donors",
-                        "Government Grants"))
-
-selectInput("rc_gov_relat",
-            label = "Select Relationship with host government",
-            choices = c("Friendly relationship with government",
-                        "Criticized by government", 
-                        "Under government crackdown"))
-```
+<!-- There is an issue of not being able to see the last selectInput options when drop down box appears -->
+
+<!-- Persona 2 Page -->
+
+<!-- Persona 2 {.tabset .tabset-fade} -->
+<!-- -------------------------------------------------- -->
+
+<!-- ### Market Share Persona 2 -->
+
+<!-- ```{r plot persona 2} -->
+<!-- renderPlotly({ -->
+<!--   choice = df() -->
+
+<!--   persona = p_beta2 # Choose the persona -->
+
+<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2) -->
+<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2) -->
+<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2) -->
+<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2) -->
+
+<!--   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+<!--   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+<!--   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+<!--   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+
+<!--   data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate) -->
+<!--   df <- as.data.frame(matrix(data, 8, 1)) -->
+
+<!--   df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross") -->
+<!--   df[,3] <- c(rep("Utility", 4), rep("Market Share", 4)) -->
+<!--   df[,4] <- rep(c("Persona 1","Persona 2", "Persona 3"), length.out = 8) -->
+<!--   colnames(df) <- c('Value', 'Organization', "Type", "Persona") -->
+
+<!--   ggplotly(df %>% filter(Type == "Market Share") %>%  -->
+<!--              ggplot(aes(y = Value, x = Organization, fill = Organization)) + -->
+<!--              geom_col() + -->
+<!--              labs(x="") +  -->
+<!--              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) + -->
+<!--              theme(legend.position = "none") + -->
+<!--              facet_wrap(~Type) -->
+<!--     ) -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- ### Amnesty International Market Share -->
+
+<!-- ```{r valuebox ai persona 2} -->
+<!-- renderValueBox({ -->
+<!--   choice = df() -->
+
+<!--   persona = p_beta2 # Choose the persona -->
+
+<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2) -->
+<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2) -->
+<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2) -->
+<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2) -->
+
+<!--   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+
+<!--   valueBox(ai_rate, -->
+<!--            color = "#FFC30B", -->
+<!--            icon = "fa-percent") -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- ### Greenpeace Market Share -->
+
+<!-- ```{r valuebox gp persona 2} -->
+<!-- renderValueBox({ -->
+<!--   choice = df() -->
+
+<!--   persona = p_beta2 # Choose the persona -->
+
+<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2) -->
+<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2) -->
+<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2) -->
+<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2) -->
+
+<!--   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+
+<!--   valueBox(gp_rate, -->
+<!--            color = "#3fad48", -->
+<!--            icon = "fa-percent") -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- ### Oxfam Market Share -->
+
+<!-- ```{r valuebox ox persona 2} -->
+<!-- renderValueBox({ -->
+<!--   choice = df() -->
+
+<!--   persona = p_beta2 # Choose the persona -->
+
+<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2) -->
+<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2) -->
+<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2) -->
+<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2) -->
+
+<!--   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+
+<!--   valueBox(ox_rate, -->
+<!--            color = "#006633", -->
+<!--            icon = "fa-percent") -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- ### Redcross Market Share -->
+
+<!-- ```{r valuebox rc persona 2} -->
+<!-- renderValueBox({ -->
+<!--   choice = df() -->
+
+<!--   persona = p_beta2 # Choose the persona -->
+
+<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2) -->
+<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2) -->
+<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2) -->
+<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2) -->
+
+<!--   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+
+<!--   valueBox(rc_rate, -->
+<!--            color = "#660000", -->
+<!--            icon = "fa-percent") -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- Organizational Inputs {.tabset .tabset-fade} -->
+<!-- ------------------------------------- -->
+<!-- ### Amnesty International Inputs -->
+
+<!-- ```{r echo=FALSE} -->
+<!-- selectInput("ai_issue",  -->
+<!--             label = "Select Issue Area:", -->
+<!--             choices = c("Emergency response", -->
+<!--                         "Environment", -->
+<!--                         "Human rights", -->
+<!--                         "Refugee relief")) -->
+
+<!-- selectInput("ai_fin_trans", -->
+<!--             label = "Select Financial transparency:", -->
+<!--             choices = c("Doesn’t engage in transparency", -->
+<!--                         "Engages in transparency")) -->
+
+<!-- selectInput("ai_account", -->
+<!--             label = "Select Financial Accountability:", -->
+<!--             choices = c("Doesn’t engage in financial accountability", -->
+<!--                         "Engages in financial accountability")) -->
+
+<!-- selectInput("ai_funding", -->
+<!--             label = "Select Funding source:", -->
+<!--             choices = c("Many small private donations", -->
+<!--                         "Handful of wealthy private donors", -->
+<!--                         "Government Grants")) -->
+
+<!-- selectInput("ai_gov_relat", -->
+<!--             label = "Select Relationship with host government", -->
+<!--             choices = c("Friendly relationship with government", -->
+<!--                         "Criticized by government",  -->
+<!--                         "Under government crackdown")) -->
+<!-- ``` -->
+
+<!-- ### Greenpeace Inputs -->
+
+<!-- ```{r echo=FALSE} -->
+<!-- selectInput("gp_issue",  -->
+<!--             label = "Select Issue Area:", -->
+<!--             choices = c("Emergency response", -->
+<!--                         "Environment", -->
+<!--                         "Human rights", -->
+<!--                         "Refugee relief")) -->
+
+<!-- selectInput("gp_fin_trans", -->
+<!--             label = "Select Financial transparency:", -->
+<!--             choices = c("Doesn’t engage in transparency", -->
+<!--                         "Engages in transparency")) -->
+
+<!-- selectInput("gp_account", -->
+<!--             label = "Select Financial Accountability:", -->
+<!--             choices = c("Doesn’t engage in accountability", -->
+<!--                         "Engages in financial accountability")) -->
+
+<!-- selectInput("gp_funding", -->
+<!--             label = "Select Funding source:", -->
+<!--             choices = c("Many small private donations", -->
+<!--                         "Handful of wealthy private donors", -->
+<!--                         "Government Grants")) -->
+
+<!-- selectInput("gp_gov_relat", -->
+<!--             label = "Select Relationship with host government", -->
+<!--             choices = c("Friendly relationship with government", -->
+<!--                         "Criticized by government",  -->
+<!--                         "Under government crackdown")) -->
+<!-- ``` -->
+
+<!-- ### Oxfam Inputs -->
+
+<!-- ```{r echo=FALSE} -->
+<!-- selectInput("ox_issue",  -->
+<!--             label = "Select Issue Area:", -->
+<!--             choices = c("Emergency response", -->
+<!--                         "Environment", -->
+<!--                         "Human rights", -->
+<!--                         "Refugee relief")) -->
+
+<!-- selectInput("ox_fin_trans", -->
+<!--             label = "Select Financial transparency:", -->
+<!--             choices = c("Doesn’t engage in transparency", -->
+<!--                         "Engages in transparency")) -->
+
+<!-- selectInput("ox_account", -->
+<!--             label = "Select Financial Accountability:", -->
+<!--             choices = c("Doesn’t engage in accountability", -->
+<!--                         "Engages in financial accountability")) -->
+
+<!-- selectInput("ox_funding", -->
+<!--             label = "Select Funding source:", -->
+<!--             choices = c("Many small private donations", -->
+<!--                         "Handful of wealthy private donors", -->
+<!--                         "Government Grants")) -->
+
+<!-- selectInput("ox_gov_relat", -->
+<!--             label = "Select Relationship with host government", -->
+<!--             choices = c("Friendly relationship with government", -->
+<!--                         "Criticized by government",  -->
+<!--                         "Under government crackdown")) -->
+<!-- ``` -->
+
+<!-- ### Red Cross Inputs -->
+
+<!-- ```{r echo=FALSE} -->
+<!-- selectInput("rc_issue",  -->
+<!--             label = "Select Issue Area:", -->
+<!--             choices = c("Emergency response", -->
+<!--                         "Environment", -->
+<!--                         "Human rights", -->
+<!--                         "Refugee relief")) -->
+
+<!-- selectInput("rc_fin_trans", -->
+<!--             label = "Select Financial transparency:", -->
+<!--             choices = c("Doesn’t engage in transparency", -->
+<!--                         "Engages in transparency")) -->
+
+<!-- selectInput("rc_account", -->
+<!--             label = "Select Financial Accountability:", -->
+<!--             choices = c("Doesn’t engage in accountability", -->
+<!--                         "Engages in financial accountability")) -->
+
+<!-- selectInput("rc_funding", -->
+<!--             label = "Select Funding source:", -->
+<!--             choices = c("Many small private donations", -->
+<!--                         "Handful of wealthy private donors", -->
+<!--                         "Government Grants")) -->
+
+<!-- selectInput("rc_gov_relat", -->
+<!--             label = "Select Relationship with host government", -->
+<!--             choices = c("Friendly relationship with government", -->
+<!--                         "Criticized by government",  -->
+<!--                         "Under government crackdown")) -->
+<!-- ``` -->
 
@@
 
-Persona 3 {.tabset .tabset-fade}
---------------------------------------------------
-
-### Market Share Persona 3
-```{r plot persona 3}
-renderPlotly({
-  choice = df()
-
-  persona = p_beta3 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2)
-
-  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate)
-  df <- as.data.frame(matrix(data, 8, 1))
-
-  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
-  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
-  df[,4] <- rep(c("Persona 1","Persona 2", "Persona 3"), length.out = 8)
-  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
-
-  ggplotly(df %>% filter(Type == "Market Share") %>% 
-             ggplot(aes(y = Value, x = Organization, fill = Organization)) +
-             geom_col() +
-             labs(x="") + 
-             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
-             theme(legend.position = "none") +
-             facet_wrap(~Type)
-    )
-})
-```
-
-### Amnesty International Market Share
-
-```{r valuebox ai persona 3}
-renderValueBox({
-  choice = df()
-
-  persona = p_beta3 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2)
-
-  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(ai_rate,
-           color = "#FFC30B",
-           icon = "fa-percent")
-})
-```
-
-### Greenpeace Market Share
-
-```{r valuebox gp persona 3}
-renderValueBox({
-  choice = df()
-
-  persona = p_beta3 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2)
-
-  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(gp_rate,
-           color = "#3fad48",
-           icon = "fa-percent")
-})
-```
-
-### Oxfam Market Share
-
-```{r valuebox ox persona 3}
-renderValueBox({
-  choice = df()
-
-  persona = p_beta3 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2)
-
-  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(ox_rate,
-           color = "#006633",
-           icon = "fa-percent")
-})
-```
-
-### Redcross Market Share
-
-```{r valuebox rc persona 3}
-renderValueBox({
-  choice = df()
-
-  persona = p_beta3 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2)
-
-  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(rc_rate,
-           color = "#660000",
-           icon = "fa-percent")
-})
-```
-
-Organizational Inputs {.tabset .tabset-fade}
--------------------------------------
-### Amnesty International Inputs
-
-```{r echo=FALSE}
-selectInput("ai_issue", 
-            label = "Select Issue Area:",
-            choices = c("Emergency response",
-                        "Environment",
-                        "Human rights",
-                        "Refugee relief"))
-
-selectInput("ai_fin_trans",
-            label = "Select Financial transparency:",
-            choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"))
-
-selectInput("ai_account",
-            label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in financial accountability",
-                        "Engages in financial accountability"))
-
-selectInput("ai_funding",
-            label = "Select Funding source:",
-            choices = c("Many small private donations",
-                        "Handful of wealthy private donors",
-                        "Government Grants"))
-
-selectInput("ai_gov_relat",
-            label = "Select Relationship with host government",
-            choices = c("Friendly relationship with government",
-                        "Criticized by government", 
-                        "Under government crackdown"))
-```
-
-### Greenpeace Inputs
-
-```{r echo=FALSE}
-selectInput("gp_issue", 
-            label = "Select Issue Area:",
-            choices = c("Emergency response",
-                        "Environment",
-                        "Human rights",
-                        "Refugee relief"))
-
-selectInput("gp_fin_trans",
-            label = "Select Financial transparency:",
-            choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"))
-
-selectInput("gp_account",
-            label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in accountability",
-                        "Engages in financial accountability"))
-
-selectInput("gp_funding",
-            label = "Select Funding source:",
-            choices = c("Many small private donations",
-                        "Handful of wealthy private donors",
-                        "Government Grants"))
-
-selectInput("gp_gov_relat",
-            label = "Select Relationship with host government",
-            choices = c("Friendly relationship with government",
-                        "Criticized by government", 
-                        "Under government crackdown"))
-```
-
-### Oxfam Inputs
-
-```{r echo=FALSE}
-selectInput("ox_issue", 
-            label = "Select Issue Area:",
-            choices = c("Emergency response",
-                        "Environment",
-                        "Human rights",
-                        "Refugee relief"))
-
-selectInput("ox_fin_trans",
-            label = "Select Financial transparency:",
-            choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"))
-
-selectInput("ox_account",
-            label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in accountability",
-                        "Engages in financial accountability"))
-
-selectInput("ox_funding",
-            label = "Select Funding source:",
-            choices = c("Many small private donations",
-                        "Handful of wealthy private donors",
-                        "Government Grants"))
-
-selectInput("ox_gov_relat",
-            label = "Select Relationship with host government",
-            choices = c("Friendly relationship with government",
-                        "Criticized by government", 
-                        "Under government crackdown"))
-```
-
-### Red Cross Inputs
-
-```{r echo=FALSE}
-selectInput("rc_issue", 
-            label = "Select Issue Area:",
-            choices = c("Emergency response",
-                        "Environment",
-                        "Human rights",
-                        "Refugee relief"))
-
-selectInput("rc_fin_trans",
-            label = "Select Financial transparency:",
-            choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"))
-
-selectInput("rc_account",
-            label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in accountability",
-                        "Engages in financial accountability"))
-
-selectInput("rc_funding",
-            label = "Select Funding source:",
-            choices = c("Many small private donations",
-                        "Handful of wealthy private donors",
-                        "Government Grants"))
-
-selectInput("rc_gov_relat",
-            label = "Select Relationship with host government",
-            choices = c("Friendly relationship with government",
-                        "Criticized by government", 
-                        "Under government crackdown"))
-```
+<!-- Persona 3 {.tabset .tabset-fade} -->
+<!-- -------------------------------------------------- -->
+
+<!-- ### Market Share Persona 3 -->
+<!-- ```{r plot persona 3} -->
+<!-- renderPlotly({ -->
+<!--   choice = df() -->
+
+<!--   persona = p_beta3 # Choose the persona -->
+
+<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2) -->
+<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2) -->
+<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2) -->
+<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2) -->
+
+<!--   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+<!--   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+<!--   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+<!--   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+
+<!--   data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate) -->
+<!--   df <- as.data.frame(matrix(data, 8, 1)) -->
+
+<!--   df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross") -->
+<!--   df[,3] <- c(rep("Utility", 4), rep("Market Share", 4)) -->
+<!--   df[,4] <- rep(c("Persona 1","Persona 2", "Persona 3"), length.out = 8) -->
+<!--   colnames(df) <- c('Value', 'Organization', "Type", "Persona") -->
+
+<!--   ggplotly(df %>% filter(Type == "Market Share") %>%  -->
+<!--              ggplot(aes(y = Value, x = Organization, fill = Organization)) + -->
+<!--              geom_col() + -->
+<!--              labs(x="") +  -->
+<!--              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) + -->
+<!--              theme(legend.position = "none") + -->
+<!--              facet_wrap(~Type) -->
+<!--     ) -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- ### Amnesty International Market Share -->
+
+<!-- ```{r valuebox ai persona 3} -->
+<!-- renderValueBox({ -->
+<!--   choice = df() -->
+
+<!--   persona = p_beta3 # Choose the persona -->
+
+<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2) -->
+<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2) -->
+<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2) -->
+<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2) -->
+
+<!--   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+
+<!--   valueBox(ai_rate, -->
+<!--            color = "#FFC30B", -->
+<!--            icon = "fa-percent") -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- ### Greenpeace Market Share -->
+
+<!-- ```{r valuebox gp persona 3} -->
+<!-- renderValueBox({ -->
+<!--   choice = df() -->
+
+<!--   persona = p_beta3 # Choose the persona -->
+
+<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2) -->
+<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2) -->
+<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2) -->
+<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2) -->
+
+<!--   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+
+<!--   valueBox(gp_rate, -->
+<!--            color = "#3fad48", -->
+<!--            icon = "fa-percent") -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- ### Oxfam Market Share -->
+
+<!-- ```{r valuebox ox persona 3} -->
+<!-- renderValueBox({ -->
+<!--   choice = df() -->
+
+<!--   persona = p_beta3 # Choose the persona -->
+
+<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2) -->
+<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2) -->
+<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2) -->
+<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2) -->
+
+<!--   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+
+<!--   valueBox(ox_rate, -->
+<!--            color = "#006633", -->
+<!--            icon = "fa-percent") -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- ### Redcross Market Share -->
+
+<!-- ```{r valuebox rc persona 3} -->
+<!-- renderValueBox({ -->
+<!--   choice = df() -->
+
+<!--   persona = p_beta3 # Choose the persona -->
+
+<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2) -->
+<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2) -->
+<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2) -->
+<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2) -->
+
+<!--   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+
+<!--   valueBox(rc_rate, -->
+<!--            color = "#660000", -->
+<!--            icon = "fa-percent") -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- Organizational Inputs {.tabset .tabset-fade} -->
+<!-- ------------------------------------- -->
+<!-- ### Amnesty International Inputs -->
+
+<!-- ```{r echo=FALSE} -->
+<!-- selectInput("ai_issue",  -->
+<!--             label = "Select Issue Area:", -->
+<!--             choices = c("Emergency response", -->
+<!--                         "Environment", -->
+<!--                         "Human rights", -->
+<!--                         "Refugee relief")) -->
+
+<!-- selectInput("ai_fin_trans", -->
+<!--             label = "Select Financial transparency:", -->
+<!--             choices = c("Doesn’t engage in transparency", -->
+<!--                         "Engages in transparency")) -->
+
+<!-- selectInput("ai_account", -->
+<!--             label = "Select Financial Accountability:", -->
+<!--             choices = c("Doesn’t engage in financial accountability", -->
+<!--                         "Engages in financial accountability")) -->
+
+<!-- selectInput("ai_funding", -->
+<!--             label = "Select Funding source:", -->
+<!--             choices = c("Many small private donations", -->
+<!--                         "Handful of wealthy private donors", -->
+<!--                         "Government Grants")) -->
+
+<!-- selectInput("ai_gov_relat", -->
+<!--             label = "Select Relationship with host government", -->
+<!--             choices = c("Friendly relationship with government", -->
+<!--                         "Criticized by government",  -->
+<!--                         "Under government crackdown")) -->
+<!-- ``` -->
+
+<!-- ### Greenpeace Inputs -->
+
+<!-- ```{r echo=FALSE} -->
+<!-- selectInput("gp_issue",  -->
+<!--             label = "Select Issue Area:", -->
+<!--             choices = c("Emergency response", -->
+<!--                         "Environment", -->
+<!--                         "Human rights", -->
+<!--                         "Refugee relief")) -->
+
+<!-- selectInput("gp_fin_trans", -->
+<!--             label = "Select Financial transparency:", -->
+<!--             choices = c("Doesn’t engage in transparency", -->
+<!--                         "Engages in transparency")) -->
+
+<!-- selectInput("gp_account", -->
+<!--             label = "Select Financial Accountability:", -->
+<!--             choices = c("Doesn’t engage in accountability", -->
+<!--                         "Engages in financial accountability")) -->
+
+<!-- selectInput("gp_funding", -->
+<!--             label = "Select Funding source:", -->
+<!--             choices = c("Many small private donations", -->
+<!--                         "Handful of wealthy private donors", -->
+<!--                         "Government Grants")) -->
+
+<!-- selectInput("gp_gov_relat", -->
+<!--             label = "Select Relationship with host government", -->
+<!--             choices = c("Friendly relationship with government", -->
+<!--                         "Criticized by government",  -->
+<!--                         "Under government crackdown")) -->
+<!-- ``` -->
+
+<!-- ### Oxfam Inputs -->
+
+<!-- ```{r echo=FALSE} -->
+<!-- selectInput("ox_issue",  -->
+<!--             label = "Select Issue Area:", -->
+<!--             choices = c("Emergency response", -->
+<!--                         "Environment", -->
+<!--                         "Human rights", -->
+<!--                         "Refugee relief")) -->
+
+<!-- selectInput("ox_fin_trans", -->
+<!--             label = "Select Financial transparency:", -->
+<!--             choices = c("Doesn’t engage in transparency", -->
+<!--                         "Engages in transparency")) -->
+
+<!-- selectInput("ox_account", -->
+<!--             label = "Select Financial Accountability:", -->
+<!--             choices = c("Doesn’t engage in accountability", -->
+<!--                         "Engages in financial accountability")) -->
+
+<!-- selectInput("ox_funding", -->
+<!--             label = "Select Funding source:", -->
+<!--             choices = c("Many small private donations", -->
+<!--                         "Handful of wealthy private donors", -->
+<!--                         "Government Grants")) -->
+
+<!-- selectInput("ox_gov_relat", -->
+<!--             label = "Select Relationship with host government", -->
+<!--             choices = c("Friendly relationship with government", -->
+<!--                         "Criticized by government",  -->
+<!--                         "Under government crackdown")) -->
+<!-- ``` -->
+
+<!-- ### Red Cross Inputs -->
+
+<!-- ```{r echo=FALSE} -->
+<!-- selectInput("rc_issue",  -->
+<!--             label = "Select Issue Area:", -->
+<!--             choices = c("Emergency response", -->
+<!--                         "Environment", -->
+<!--                         "Human rights", -->
+<!--                         "Refugee relief")) -->
+
+<!-- selectInput("rc_fin_trans", -->
+<!--             label = "Select Financial transparency:", -->
+<!--             choices = c("Doesn’t engage in transparency", -->
+<!--                         "Engages in transparency")) -->
+
+<!-- selectInput("rc_account", -->
+<!--             label = "Select Financial Accountability:", -->
+<!--             choices = c("Doesn’t engage in accountability", -->
+<!--                         "Engages in financial accountability")) -->
+
+<!-- selectInput("rc_funding", -->
+<!--             label = "Select Funding source:", -->
+<!--             choices = c("Many small private donations", -->
+<!--                         "Handful of wealthy private donors", -->
+<!--                         "Government Grants")) -->
+
+<!-- selectInput("rc_gov_relat", -->
+<!--             label = "Select Relationship with host government", -->
+<!--             choices = c("Friendly relationship with government", -->
+<!--                         "Criticized by government",  -->
+<!--                         "Under government crackdown")) -->
+<!-- ``` -->
 
@@
 
-Expected Donors {.tabset .tabset-fade}
--------------------------------------
-### Amnesty International Expected Donors
-
-```{r echo=FALSE}
-renderGauge({
-  choice = df()
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-
-  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-  gauge(ai_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#FFC30B"),
-        symbol = "%")
-})
-```
-
-<!-- ### Greenpeace Expected Donors -->
+<!-- Expected Donors {.tabset .tabset-fade} -->
+<!-- ------------------------------------- -->
+<!-- ### Amnesty International Expected Donors -->
 
@@
 
+<!--   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
+<!--   gauge(ai_rate, -->
+<!--         min = 0, -->
+<!--         max = 100, -->
+<!--         gaugeSectors(colors = "#FFC30B"), -->
+<!--         symbol = "%") -->
+<!-- }) -->
+<!-- ``` -->
+
+<!-- ### Greenpeace Expected Donors -->
+
+<!-- ```{r echo=FALSE} -->
+<!-- renderGauge({ -->
+<!--   choice = df() -->
+<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
+
 <!--   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->

### 2020-08-07 analysis/05_market_simulator.Rmd
Valueboxes taken out

@@
 --------------------------------------------------
-### Amnesty International Market Share
+### Amnesty International
 
@@
 ```{r valuebox ai}
-renderValueBox({
-  choice = df()
-
-  persona = p_beta1 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-
-  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(ai_rate,
-           color = "#FFC30B",
-           icon = "fa-percent")
-})
+# renderValueBox({
+#   choice = df()
+#   
+#   persona = p_beta1 # Choose the persona
+#   
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+#   
+#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   valueBox(ai_rate,
+#            color = "#FFC30B",
+#            icon = "fa-percent")
+# })
 ```
@@
 
-### Greenpeace Market Share
+### Greenpeace
 
@@
 ```{r valuebox gp}
-renderValueBox({
-  choice = df()
-  persona = p_beta1 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-
-  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(gp_rate,
-           color = "#3fad48",
-           icon = "fa-percent")
-})
+# renderValueBox({
+#   choice = df()
+#   persona = p_beta1 # Choose the persona
+#   
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+#   
+#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   valueBox(gp_rate,
+#            color = "#3fad48",
+#            icon = "fa-percent")
+# })
 ```
@@
 
-### Oxfam Market Share
+### Oxfam
 
@@
 ```{r valuebox ox}
-renderValueBox({
-  choice = df()
-
-  persona = p_beta1 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-
-  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(ox_rate,
-           color = "#006633",
-           icon = "fa-percent")
-})
+# renderValueBox({
+#   choice = df()
+#   
+#   persona = p_beta1 # Choose the persona
+#   
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+#   
+#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   valueBox(ox_rate,
+#            color = "#006633",
+#            icon = "fa-percent")
+# })
 ```
@@
 
-### Redcross Market Share
+### Redcross
 
@@
 ```{r valuebox rc}
-renderValueBox({
-  choice = df()
-
-  persona = p_beta1 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-
-  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(rc_rate,
-           color = "#660000",
-           icon = "fa-percent")
-})
+# renderValueBox({
+#   choice = df()
+#   
+#   persona = p_beta1 # Choose the persona
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+#   
+#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   valueBox(rc_rate,
+#            color = "#660000",
+#            icon = "fa-percent")
+# })
 ```

### 2020-08-07 analysis/05_market_simulator.Rmd
Added Persona tabs. need reactive element for personas

@@
 
-Market Share Per Persona 
+Market Share Per Persona {data-height=600}
 --------------------------------------
@@
 })
+
 ```
@@
 --------------------------------------------------
-### Amnesty International
+### Org 1
 
@@
 })
-```
-
-### Greenpeace
+
+renderGauge({
+  choice = df()
+  persona = p_beta2 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(ai_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#3fad48"),
+        symbol = "%")
+})
+
+renderGauge({
+  choice = df()
+  persona = p_beta3 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(ai_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#006633"),
+        symbol = "%")
+})
+```
+
+### Org 2
 
@@
 
-### Oxfam
+### Org 3
 
@@
 
-### Redcross
+### Org 4
 
@@
 })
+```
+
+### Persona 1
+
+```{r persona 1 inputs}
+
+```
+
+### Persona 2
+
+```{r persona 2 inputs}
+
+```
+
+### Persona 3
+
+```{r persona 3 inputs}
+
 ```

### 2020-08-13 analysis/05_market_simulator.Rmd
started builing the persona reactive element. Need to change the input_ids in the selectInputs to match

--- 2020-08-05 analysis/05_market_simulator.Rmd
@@
 
+# Org Reactive Element
 df <- reactive({
@@
 })
+
+# Persona Reactive Element
+p <- reactive({
+  #Amnesty International
+    beta$p1_value <- 0
+    beta$p1_value[beta$levels == 'Persona 1'] <- 1
+    beta$p1_value[beta$levels %in% input$p1_charity_importance] <- 1
+    beta$p1_value[beta$levels %in% input$p1_trust_in_charity] <- 1
+    beta$p1_value[beta$levels %in% input$p1_donation_frequency] <- 1
+    beta$p1_value[beta$levels %in% input$p1_donation_amount] <- 1
+    beta$p1_value[beta$levels %in% input$p1_volunteer_12] <- 1
+  #Greenpeace
+    beta$p2_value <- 0
+    beta$p2_value[beta$levels == 'Persona 2'] <- 1
+    beta$p2_value[beta$levels %in% input$gp_issue] <- 1
+    beta$p2_value[beta$levels %in% input$gp_fin_trans] <- 1
+    beta$p2_value[beta$levels %in% input$gp_account] <- 1
+    beta$p2_value[beta$levels %in% input$gp_funding] <- 1
+    beta$p2_value[beta$levels %in% input$gp_gov_relat] <- 1
+  #Oxfam
+    beta$p3_value <- 0
+    beta$p3_value[beta$levels == 'Persona 3'] <- 1
+    beta$p3_value[beta$levels %in% input$ox_issue] <- 1
+    beta$p3_value[beta$levels %in% input$ox_fin_trans] <- 1
+    beta$p3_value[beta$levels %in% input$ox_account] <- 1
+    beta$p3_value[beta$levels %in% input$ox_funding] <- 1
+    beta$p3_value[beta$levels %in% input$ox_gov_relat] <- 1
+    beta
+
+})
 ```
@@
 
-<!-- Persona Inputs {.sidebar} -->
+<!-- Persona Inputs  -->
 <!-- ================================================= -->
@@
 
-<!-- ```{r sidebar inputs, echo=FALSE} -->
-
-<!-- # selectInput("model_choice",  -->
-<!-- #             label = "Select Model:", -->
-<!-- #             choices = c("public_political_social_charity_demo")) -->
-
-<!-- selectInput("charity_importance",  -->
-<!--           label = "Charity Importance:", -->
-<!--           choices = c("0", '1', '2', '3','4','5','6','7')) -->
-
-<!-- selectInput("trust_in_charity",  -->
-<!--             label = "Charity Trust:", -->
-<!--             choices = c("0", '1', '2', '3','4','5','6','7')) -->
-
-<!-- selectInput("donation_frequency",  -->
-<!--          label = "Donation Frequency:", -->
-<!--          choices = c('Once a week',  -->
-<!--                      'Once a Month', -->
-<!--                      'Once every three months', -->
-<!--                      'Once every six months',  -->
-<!--                      'Once a year',  -->
-<!--                      'Once every few years', -->
-<!--                      'Never')) -->
-
-<!-- selectInput("donation_amount",  -->
-<!--          label = "Donation Amount:", -->
-<!--          choices = c("$1-$49",  -->
-<!--                      '$50-$99',  -->
-<!--                      '$100-$499', -->
-<!--                      '$500-$999', -->
-<!--                      '$1,000-$4,999', -->
-<!--                      '$5,000-$9,999', -->
-<!--                      '$10,000+')) -->
-
-<!-- selectInput("volunteer_12",  -->
-<!--          label = "Volunteered in last 12 Months:", -->
-<!--          choices = c("Yes", "No")) -->
-
-<!-- selectInput("volunteer_frequency",  -->
-<!--          label = "Volunteer Frequency:", -->
-<!--          choices = c('Once a week', -->
-<!--                      'Once a Month', -->
-<!--                      'Once every three months',  -->
-<!--                      'Once every six months',  -->
-<!--                      'Once a year',  -->
-<!--                      'Once every few years', -->
-<!--                      'Never')) -->
-
-<!-- selectInput("personal_activism",  -->
-<!--          label = "Personal Activism:", -->
-<!--          choices = c('Extremely involved', -->
-<!--                      'Very involved',  -->
-<!--                      'Moderately involved',  -->
-<!--                      'Slightly involved', -->
-<!--                      'Never involved')) -->
-
-<!-- selectInput("family_activism",  -->
-<!--          label = "Family Activism:", -->
-<!--          choices = c('Extremely involved',  -->
-<!--                      'Very involved',  -->
-<!--                      'Moderately involved',  -->
-<!--                      'Slightly involved', -->
-<!--                      'Never involved')) -->
-
-<!-- selectInput("religious_member",  -->
-<!--          label = "Church Membership:", -->
-<!--          choices = c('Active Member',  -->
-<!--                      'Inactive Member',  -->
-<!--                      "Don't belong")) -->
-
-<!-- selectInput("sport_member",  -->
-<!--          label = "Sport or Recreational Membership:", -->
-<!--          choices = c('Active Member',  -->
-<!--                      'Inactive Member',  -->
-<!--                      "Don't belong")) -->
-
-<!-- selectInput("art_member",  -->
-<!--          label = "Art, Music, or Educational Membership:", -->
-<!--          choices = c('Active Member',  -->
-<!--                      'Inactive Member',  -->
-<!--                      "Don't belong")) -->
-
-<!-- selectInput("labor_member",  -->
-<!--          label = "Labor Union Membership:", -->
-<!--          choices = c('Active Member',  -->
-<!--                      'Inactive Member',  -->
-<!--                      "Don't belong")) -->
-
-<!-- selectInput("political_member",  -->
-<!--          label = "Political Party Membership:", -->
-<!--          choices = c('Active Member',  -->
-<!--                      'Inactive Member',  -->
-<!--                      "Don't belong")) -->
-
-<!-- selectInput("environmental_member",  -->
-<!--          label = "Enviornmental Org. Membership:", -->
-<!--          choices = c('Active Member',  -->
-<!--                      'Inactive Member',  -->
-<!--                      "Don't belong")) -->
-
-<!-- selectInput("professional_member",  -->
-<!--          label = "Professional Membership:", -->
-<!--          choices = c('Active Member',  -->
-<!--                      'Inactive Member',  -->
-<!--                      "Don't belong")) -->
-
-<!-- selectInput("humanitarian_member",  -->
-<!--          label = "Humanitarian Org. Membership:", -->
-<!--          choices = c('Active Member',  -->
-<!--                      'Inactive Member',  -->
-<!--                      "Don't belong")) -->
-
-<!-- selectInput("consumer_member",  -->
-<!--          label = "Consumer Org. Membership:", -->
-<!--          choices = c('Active Member',  -->
-<!--                      'Inactive Member',  -->
-<!--                      "Don't belong")) -->
-
-<!-- selectInput("religious_member",  -->
-<!--          label = "Church Membership:", -->
-<!--          choices = c('Active Member',  -->
-<!--                      'Inactive Member',  -->
-<!--                      "Don't belong")) -->
-
-<!-- selectInput("other_member",  -->
-<!--          label = "Other Org. Membership:", -->
-<!--          choices = c('Active Member',  -->
-<!--                      'Inactive Member',  -->
-<!--                      "Don't belong")) -->
-
-<!-- selectInput("national_news",  -->
-<!--          label = "Follow national news:", -->
-<!--          choices = c('Multiple times a day',  -->
-<!--                      'Every day',  -->
-<!--                      "Once a week", -->
-<!--                      "Hardly ever", -->
-<!--                      "Never")) -->
-
-<!-- selectInput("international_news",  -->
-<!--          label = "Follow international news:", -->
-<!--          choices = c('Always', -->
-<!--                      "Sometimes", -->
-<!--                      "Never")) -->
-
-<!-- selectInput("news_medium",  -->
-<!--          label = "Medium to follow news:", -->
-<!--          choices = c('TV',  -->
-<!--                      'Print',  -->
-<!--                      "Online", -->
-<!--                      "Social Media", -->
-<!--                      "Radio", -->
-<!--                      "Email newsletters", -->
-<!--                      "News app")) -->
-
-<!-- selectInput("international_news",  -->
-<!--          label = "Follow international news:", -->
-<!--          choices = c('Multiple times a day',  -->
-<!--                      'Every day',  -->
-<!--                      "Once a week", -->
-<!--                      "Hardly ever", -->
-<!--                      "Never")) -->
-
-<!-- selectInput("follow_gov",  -->
-<!--          label = "Follow government & public affairs:", -->
-<!--          choices = c('Most of the time',  -->
-<!--                      'Some of the time',  -->
-<!--                      "Only now and then", -->
-<!--                      "Hardly at all")) -->
-
-<!-- selectInput("travel_developing",  -->
-<!--          label = "Travel to developing country:", -->
-<!--          choices = c('Yes', 'No')) -->
-
-<!-- selectInput("polical_pref",  -->
-<!--          label = "Polical views from liberal to conservative:", -->
-<!--          choices = c("0", '1', '2', '3','4','5','6','7')) -->
-
-<!-- selectInput("institution_trust",  -->
-<!--          label = "Political institution trust from none to complete:", -->
-<!--          choices = c("0", '1', '2', '3','4','5','6','7')) -->
-
-<!-- selectInput("others_charitable",  -->
-<!--          label = "People should be more charitable:", -->
-<!--          choices = c("0", '1', '2', '3','4','5','6','7')) -->
-
-<!-- selectInput("worship_attendance",  -->
-<!--          label = "Worship service attendance:", -->
-<!--          choices = c('Multiple times a week',  -->
-<!--                      'Once a week',  -->
-<!--                      "Once a month", -->
-<!--                      "Once a year", -->
-<!--                      "Never")) -->
-
-<!-- selectInput("religion_importance",  -->
-<!--          label = "Importance of religion:", -->
-<!--          choices = c('Extremely important', -->
-<!--                      'Very important', -->
-<!--                      'Moderately important', -->
-<!--                      'Slightly important', -->
-<!--                      'Not at all important')) -->
-
-<!-- selectInput("religion",  -->
-<!--          label = "Religion:", -->
-<!--          choices = c('Catholic', -->
-<!--                      'Protestant', -->
-<!--                      'Christian Orthodox', -->
-<!--                      'Jewish', -->
-<!--                      'Muslim', -->
-<!--                      'Sikh', -->
-<!--                      'Hindu', -->
-<!--                      'Buddhist', -->
-<!--                      'Atheist', -->
-<!--                      'Other')) -->
-
-<!-- selectInput("gender",  -->
-<!--          label = "Gender:", -->
-<!--          choices = c("Male", -->
-<!--                      "Female", -->
-<!--                      "Transgender", -->
-<!--                      "Prefer not to say", -->
-<!--                      "Other")) -->
-
-<!-- selectInput("marital_status",  -->
-<!--          label = "Marital Status:", -->
-<!--          choices = c("Married", -->
-<!--                      "Widowed", -->
-<!--                      "Divorced", -->
-<!--                      "Separated", -->
-<!--                      "Never married")) -->
-
-<!-- selectInput("education",  -->
-<!--          label = "Education:", -->
-<!--          choices = c("Less than high school", -->
-<!--                      "High school", -->
-<!--                      "Some college", -->
-<!--                      "2 year degree", -->
-<!--                      "4 year degree", -->
-<!--                      "Graduate degree", -->
-<!--                      "Doctorate")) -->
-
-<!-- selectInput("income",  -->
-<!--          label = "Income:", -->
-<!--          choices = c('Less than $10,000',  -->
-<!--                      '$10,000 to $19,999', -->
-<!--                      '$20,000 to $29,999', -->
-<!--                      '$30,000 to $39,999', -->
-<!--                      '$40,000 to $49,999', -->
-<!--                      '$50,000 to $59,999', -->
-<!--                      '$60,000 to $69,999', -->
-<!--                      '$70,000 to $79,999', -->
-<!--                      '$80,000 to $89,999', -->
-<!--                      '$90,000 to $99,999', -->
-<!--                      '$100,000 to $149,999', -->
-<!--                      '$150,000 to $199,999', -->
-<!--                      '$200,000 to $299,999', -->
-<!--                      '$300,000 or more')) -->
-
-<!-- selectInput("race",  -->
-<!--          label = "Race(s):", -->
-<!--          choices = c('White', -->
-<!--                      'Black or African American', -->
-<!--                      'American Indian or Alaska Native', -->
-<!--                      'Asian', -->
-<!--                      'Native Hawaiian or Pacific Islander', -->
-<!--                      'Other'),  -->
-<!--          multiple = TRUE) -->
-
-<!-- selectInput("education",  -->
-<!--          label = "Education:", -->
-<!--          choices = c("Less than high school", -->
-<!--                      "High school", -->
-<!--                      "Some college", -->
-<!--                      "2 year degree", -->
-<!--                      "4 year degree", -->
-<!--                      "Graduate degree", -->
-<!--                      "Doctorate")) -->
-
-<!-- selectInput("age",  -->
-<!--          label = "Age:", -->
-<!--          choices = c('Under 18', -->
-<!--                      '18 - 24', -->
-<!--                      '25 - 34', -->
-<!--                      '35 - 44', -->
-<!--                      '45 - 54', -->
-<!--                      '55 - 64', -->
-<!--                      '65 - 74', -->
-<!--                      '75 - 84', -->
-<!--                      '85 or older')) -->
-
-<!-- ``` -->
+```{r sidebar inputs, echo=FALSE}
+
+# # selectInput("model_choice",
+# #             label = "Select Model:",
+# #             choices = c("public_political_social_charity_demo"))
+# 
+# 
+# selectInput("charity_importance",
+#           label = "Charity Importance:",
+#           choices = c("0", '1', '2', '3','4','5','6','7'))
+# 
+# 
+# selectInput("trust_in_charity",
+#             label = "Charity Trust:",
+#             choices = c("0", '1', '2', '3','4','5','6','7'))
+# 
+# 
+# 
+# selectInput("donation_frequency",
+#          label = "Donation Frequency:",
+#          choices = c('Once a week',
+#                      'Once a Month',
+#                      'Once every three months',
+#                      'Once every six months',
+#                      'Once a year',
+#                      'Once every few years',
+#                      'Never'))
+# 
+# 
+# 
+# selectInput("donation_amount",
+#          label = "Donation Amount:",
+#          choices = c("$1-$49",
+#                      '$50-$99',
+#                      '$100-$499',
+#                      '$500-$999',
+#                      '$1,000-$4,999',
+#                      '$5,000-$9,999',
+#                      '$10,000+'))
+# 
+# 
+# selectInput("volunteer_12",
+#          label = "Volunteered in last 12 Months:",
+#          choices = c("Yes", "No"))
+# 
+# 
+# 
+# selectInput("volunteer_frequency",
+#          label = "Volunteer Frequency:",
+#          choices = c('Once a week',
+#                      'Once a Month',
+#                      'Once every three months',
+#                      'Once every six months',
+#                      'Once a year',
+#                      'Once every few years',
+#                      'Never'))
+# 
+# 
+# selectInput("personal_activism",
+#          label = "Personal Activism:",
+#          choices = c('Extremely involved',
+#                      'Very involved',
+#                      'Moderately involved',
+#                      'Slightly involved',
+#                      'Never involved'))
+# 
+# 
+# selectInput("family_activism",
+#          label = "Family Activism:",
+#          choices = c('Extremely involved',
+#                      'Very involved',
+#                      'Moderately involved',
+#                      'Slightly involved',
+#                      'Never involved'))
+# 
+# 
+# selectInput("religious_member",
+#          label = "Church Membership:",
+#          choices = c('Active Member',
+#                      'Inactive Member',
+#                      "Don't belong"))
+# 
+# 
+# selectInput("sport_member",
+#          label = "Sport or Recreational Membership:",
+#          choices = c('Active Member',
+#                      'Inactive Member',
+#                      "Don't belong"))
+# 
+# 
+# selectInput("art_member",
+#          label = "Art, Music, or Educational Membership:",
+#          choices = c('Active Member',
+#                      'Inactive Member',
+#                      "Don't belong"))
+# 
+# 
+# selectInput("labor_member",
+#          label = "Labor Union Membership:",
+#          choices = c('Active Member',
+#                      'Inactive Member',
+#                      "Don't belong"))
+# 
+# 
+# selectInput("political_member",
+#          label = "Political Party Membership:",
+#          choices = c('Active Member',
+#                      'Inactive Member',
+#                      "Don't belong"))
+# 
+# 
+# selectInput("environmental_member",
+#          label = "Enviornmental Org. Membership:",
+#          choices = c('Active Member',
+#                      'Inactive Member',
+#                      "Don't belong"))
+# 
+# 
+# selectInput("professional_member",
+#          label = "Professional Membership:",
+#          choices = c('Active Member',
+#                      'Inactive Member',
+#                      "Don't belong"))
+# 
+# 
+# selectInput("humanitarian_member",
+#          label = "Humanitarian Org. Membership:",
+#          choices = c('Active Member',
+#                      'Inactive Member',
+#                      "Don't belong"))
+# 
+# 
+# selectInput("consumer_member",
+#          label = "Consumer Org. Membership:",
+#          choices = c('Active Member',
+#                      'Inactive Member',
+#                      "Don't belong"))
+# 
+# 
+# selectInput("religious_member",
+#          label = "Church Membership:",
+#          choices = c('Active Member',
+#                      'Inactive Member',
+#                      "Don't belong"))
+# 
+# 
+# 
+# 
+# selectInput("other_member",
+#          label = "Other Org. Membership:",
+#          choices = c('Active Member',
+#                      'Inactive Member',
+#                      "Don't belong"))
+# 
+# 
+# 
+# selectInput("national_news",
+#          label = "Follow national news:",
+#          choices = c('Multiple times a day',
+#                      'Every day',
+#                      "Once a week",
+#                      "Hardly ever",
+#                      "Never"))
+# 
+# 
+# selectInput("international_news",
+#          label = "Follow international news:",
+#          choices = c('Always',
+#                      "Sometimes",
+#                      "Never"))
+# 
+# 
+# selectInput("news_medium",
+#          label = "Medium to follow news:",
+#          choices = c('TV',
+#                      'Print',
+#                      "Online",
+#                      "Social Media",
+#                      "Radio",
+#                      "Email newsletters",
+#                      "News app"))
+# 
+# 
+# 
+# selectInput("international_news",
+#          label = "Follow international news:",
+#          choices = c('Multiple times a day',
+#                      'Every day',
+#                      "Once a week",
+#                      "Hardly ever",
+#                      "Never"))
+# 
+# selectInput("follow_gov",
+#          label = "Follow government & public affairs:",
+#          choices = c('Most of the time',
+#                      'Some of the time',
+#                      "Only now and then",
+#                      "Hardly at all"))
+# 
+# 
+# selectInput("travel_developing",
+#          label = "Travel to developing country:",
+#          choices = c('Yes', 'No'))
+# 
+# 
+# 
+# selectInput("polical_pref",
+#          label = "Polical views from liberal to conservative:",
+#          choices = c("0", '1', '2', '3','4','5','6','7'))
+# 
+# 
+# selectInput("institution_trust",
+#          label = "Political institution trust from none to complete:",
+#          choices = c("0", '1', '2', '3','4','5','6','7'))
+# 
+# 
+# 
+# selectInput("others_charitable",
+#          label = "People should be more charitable:",
+#          choices = c("0", '1', '2', '3','4','5','6','7'))
+# 
+# 
+# selectInput("worship_attendance",
+#          label = "Worship service attendance:",
+#          choices = c('Multiple times a week',
+#                      'Once a week',
+#                      "Once a month",
+#                      "Once a year",
+#                      "Never"))
+# 
+# 
+# selectInput("religion_importance",
+#          label = "Importance of religion:",
+#          choices = c('Extremely important',
+#                      'Very important',
+#                      'Moderately important',
+#                      'Slightly important',
+#                      'Not at all important'))
+# 
+# 
+# selectInput("religion",
+#          label = "Religion:",
+#          choices = c('Catholic',
+#                      'Protestant',
+#                      'Christian Orthodox',
+#                      'Jewish',
+#                      'Muslim',
+#                      'Sikh',
+#                      'Hindu',
+#                      'Buddhist',
+#                      'Atheist',
+#                      'Other'))
+# 
+# 
+# selectInput("gender",
+#          label = "Gender:",
+#          choices = c("Male",
+#                      "Female",
+#                      "Transgender",
+#                      "Prefer not to say",
+#                      "Other"))
+# 
+# 
+# selectInput("marital_status",
+#          label = "Marital Status:",
+#          choices = c("Married",
+#                      "Widowed",
+#                      "Divorced",
+#                      "Separated",
+#                      "Never married"))
+# 
+# 
+# selectInput("education",
+#          label = "Education:",
+#          choices = c("Less than high school",
+#                      "High school",
+#                      "Some college",
+#                      "2 year degree",
+#                      "4 year degree",
+#                      "Graduate degree",
+#                      "Doctorate"))
+# 
+# selectInput("income",
+#          label = "Income:",
+#          choices = c('Less than $10,000',
+#                      '$10,000 to $19,999',
+#                      '$20,000 to $29,999',
+#                      '$30,000 to $39,999',
+#                      '$40,000 to $49,999',
+#                      '$50,000 to $59,999',
+#                      '$60,000 to $69,999',
+#                      '$70,000 to $79,999',
+#                      '$80,000 to $89,999',
+#                      '$90,000 to $99,999',
+#                      '$100,000 to $149,999',
+#                      '$150,000 to $199,999',
+#                      '$200,000 to $299,999',
+#                      '$300,000 or more'))
+# 
+# 
+# 
+# selectInput("race",
+#          label = "Race(s):",
+#          choices = c('White',
+#                      'Black or African American',
+#                      'American Indian or Alaska Native',
+#                      'Asian',
+#                      'Native Hawaiian or Pacific Islander',
+#                      'Other'),
+#          multiple = TRUE)
+# 
+# 
+# selectInput("education",
+#          label = "Education:",
+#          choices = c("Less than high school",
+#                      "High school",
+#                      "Some college",
+#                      "2 year degree",
+#                      "4 year degree",
+#                      "Graduate degree",
+#                      "Doctorate"))
+# 
+# 
+# selectInput("age",
+#          label = "Age:",
+#          choices = c('Under 18',
+#                      '18 - 24',
+#                      '25 - 34',
+#                      '35 - 44',
+#                      '45 - 54',
+#                      '55 - 64',
+#                      '65 - 74',
+#                      '75 - 84',
+#                      '85 or older'))
+
+```
 
@@
   df[,4] <- c(rep("Persona 1",8), rep("Persona 2", 8), rep("Persona 3", 8))
+  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+
+  ggplotly(df %>% filter(Type == "Market Share") %>% 
+             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+             geom_bar(position = "dodge", stat = "identity") +
+             labs(x="") + 
+             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+             theme(legend.position = "none")
+    )
+})
+
+```
+
+<!-- Organizational Tabs -->
+
+Organization Breakdown {.tabset .tabset-fade}
+--------------------------------------------------
+### Org 1
+
+```{r plot ai plot}
+renderPlotly({
+  choice = df()
+
+    persona1 = p_beta1 # Choose the persona
+
+  ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
+  gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
+  ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
+  rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+
+  ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+
+    persona2 = p_beta2 # Choose the persona
+
+  ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
+  gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
+  ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
+  rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+
+  ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+
+      persona3 = p_beta3 # Choose the persona
+
+  ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
+  gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
+  ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
+  rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+
+  ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+
+  data <- c(ai_exp_util1, ai_rate1, 
+            ai_exp_util2, ai_rate2,
+            ai_exp_util3, ai_rate3)
+
+  df <- as.data.frame(matrix(data, 6, 1))
+
+  df[,2] <- c("Amnesty International")
+  df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
+  df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
@@
 
-<!-- Organizational Tabs -->
-
-Organization Breakdown {.tabset .tabset-fade}
---------------------------------------------------
-### Amnesty International Market Share
-
-```{r plot ai plot}
+```{r valuebox ai commented}
+# renderValueBox({
+#   choice = df()
+#   
+#   persona = p_beta1 # Choose the persona
+#   
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+#   
+#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   valueBox(ai_rate,
+#            color = "#FFC30B",
+#            icon = "fa-percent")
+# })
+```
+
+```{r ai org inputs}
+
+# Some kind of Org Id that could select the organization you are looking at? Not sure how to make it change the label in the graph
+selectInput("org_id",
+            label = "Select Organization:",
+            choices = c("Amnesity International",
+                        "Green Peace",
+                        "Oxfam",
+                        "Red Cross"))
+
+selectInput("ai_issue", 
+            label = "Select Issue Area:",
+            choices = c("Emergency response",
+                        "Environment",
+                        "Human rights",
+                        "Refugee relief"))
+
+selectInput("ai_fin_trans",
+            label = "Select Financial transparency:",
+            choices = c("Doesn’t engage in transparency",
+                        "Engages in transparency"))
+
+selectInput("ai_account",
+            label = "Select Financial Accountability:",
+            choices = c("Doesn’t engage in financial accountability",
+                        "Engages in financial accountability"))
+
+selectInput("ai_funding",
+            label = "Select Funding source:",
+            choices = c("Many small private donations",
+                        "Handful of wealthy private donors",
+                        "Government Grants"))
+
+selectInput("ai_gov_relat",
+            label = "Select Relationship with host government",
+            choices = c("Friendly relationship with government",
+                        "Criticized by government", 
+                        "Under government crackdown"))
+```
+
+```{r ai gauge}
+renderGauge({
+  choice = df()
+  persona = p_beta1 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(ai_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#FFC30B"),
+        symbol = "%")
+})
+
+renderGauge({
+  choice = df()
+  persona = p_beta2 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(ai_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#3fad48"),
+        symbol = "%")
+})
+
+renderGauge({
+  choice = df()
+  persona = p_beta3 # Choose the persona
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+
+  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(ai_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#006633"),
+        symbol = "%")
+})
+```
+
+### Org 2
+
+```{r plot gp plot}
 renderPlotly({
@@
 
-  data <- c(ai_exp_util1, ai_rate1, 
-            ai_exp_util2, ai_rate2,
-            ai_exp_util3, ai_rate3)
+  data <- c(gp_exp_util1, gp_rate1, 
+            gp_exp_util2, gp_rate2,
+            gp_exp_util3, gp_rate3)
 
@@
 
-  df[,2] <- c("Amnesty International")
+  df[,2] <- c("Greenpeace")
   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
@@
 
-```{r valuebox ai}
-renderValueBox({
-  choice = df()
-
-  persona = p_beta1 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-
-  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(ai_rate,
-           color = "#FFC30B",
-           icon = "fa-percent")
-})
+```{r valuebox gp commented}
+# renderValueBox({
+#   choice = df()
+#   persona = p_beta1 # Choose the persona
+#   
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+#   
+#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   valueBox(gp_rate,
+#            color = "#3fad48",
+#            icon = "fa-percent")
+# })
 ```
 
-```{r ai org inputs}
-selectInput("ai_issue", 
+```{r gp org inputs}
+selectInput("gp_issue", 
             label = "Select Issue Area:",
@@
 
-selectInput("ai_fin_trans",
+selectInput("gp_fin_trans",
             label = "Select Financial transparency:",
@@
 
-selectInput("ai_account",
+selectInput("gp_account",
             label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in financial accountability",
+            choices = c("Doesn’t engage in accountability",
                         "Engages in financial accountability"))
 
-selectInput("ai_funding",
+selectInput("gp_funding",
             label = "Select Funding source:",
@@
 
-selectInput("ai_gov_relat",
+selectInput("gp_gov_relat",
             label = "Select Relationship with host government",
@@
 
-```{r ai gauge}
+```{r gp gauge}
 renderGauge({
@@
 
-  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(ai_rate,
+  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(gp_rate,
         min = 0,
         max = 100,
-        gaugeSectors(colors = "#FFC30B"),
+        gaugeSectors(colors = "#3fad48"),
         symbol = "%")
@@
 
-### Greenpeace Market Share
-
-```{r plot gp plot}
+### Org 3
+
+```{r plot ox plot}
 renderPlotly({
@@
 
-  data <- c(gp_exp_util1, gp_rate1, 
-            gp_exp_util2, gp_rate2,
-            gp_exp_util3, gp_rate3)
+  data <- c(ox_exp_util1, ox_rate1, 
+            ox_exp_util2, ox_rate2,
+            ox_exp_util3, ox_rate3)
 
@@
 
-  df[,2] <- c("Greenpeace")
+  df[,2] <- c("Oxfam")
   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
@@
 
-```{r valuebox gp}
-renderValueBox({
-  choice = df()
-  persona = p_beta1 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-
-  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(gp_rate,
-           color = "#3fad48",
-           icon = "fa-percent")
-})
+```{r valuebox ox commented}
+# renderValueBox({
+#   choice = df()
+#   
+#   persona = p_beta1 # Choose the persona
+#   
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+#   
+#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   valueBox(ox_rate,
+#            color = "#006633",
+#            icon = "fa-percent")
+# })
 ```
 
-```{r gp org inputs}
-selectInput("gp_issue", 
+```{r ox org inputs}
+selectInput("ox_issue", 
             label = "Select Issue Area:",
@@
 
-selectInput("gp_fin_trans",
+selectInput("ox_fin_trans",
             label = "Select Financial transparency:",
@@
 
-selectInput("gp_account",
+selectInput("ox_account",
             label = "Select Financial Accountability:",
@@
 
-selectInput("gp_funding",
+selectInput("ox_funding",
             label = "Select Funding source:",
@@
 
-selectInput("gp_gov_relat",
+selectInput("ox_gov_relat",
             label = "Select Relationship with host government",
@@
 
-```{r gp gauge}
+```{r ox gauge}
 renderGauge({
@@
 
-  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(gp_rate,
+  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(ox_rate,
         min = 0,
         max = 100,
-        gaugeSectors(colors = "#3fad48"),
+        gaugeSectors(colors = "#006633"),
         symbol = "%")
@@
 
-### Oxfam Market Share
-
-```{r plot ox plot}
+### Org 4
+
+```{r plot rc plot}
 renderPlotly({
@@
 
-  data <- c(ox_exp_util1, ox_rate1, 
-            ox_exp_util2, ox_rate2,
-            ox_exp_util3, ox_rate3)
+  data <- c(rc_exp_util1, rc_rate1, 
+            rc_exp_util2, rc_rate2,
+            rc_exp_util3, rc_rate3)
 
@@
 
-  df[,2] <- c("Oxfam")
+  df[,2] <- c("Red Cross")
   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
@@
 
-```{r valuebox ox}
-renderValueBox({
-  choice = df()
-
-  persona = p_beta1 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-
-  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(ox_rate,
-           color = "#006633",
-           icon = "fa-percent")
-})
-```
-
-```{r ox org inputs}
-selectInput("ox_issue", 
-            label = "Select Issue Area:",
-            choices = c("Emergency response",
-                        "Environment",
-                        "Human rights",
-                        "Refugee relief"))
-
-selectInput("ox_fin_trans",
-            label = "Select Financial transparency:",
-            choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"))
-
-selectInput("ox_account",
-            label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in accountability",
-                        "Engages in financial accountability"))
-
-selectInput("ox_funding",
-            label = "Select Funding source:",
-            choices = c("Many small private donations",
-                        "Handful of wealthy private donors",
-                        "Government Grants"))
-
-selectInput("ox_gov_relat",
-            label = "Select Relationship with host government",
-            choices = c("Friendly relationship with government",
-                        "Criticized by government", 
-                        "Under government crackdown"))
-```
-
-```{r ox gauge}
-renderGauge({
-  choice = df()
-  persona = p_beta1 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-
-  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(ox_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#006633"),
-        symbol = "%")
-})
-```
-
-### Redcross Market Share
-
-```{r plot rc plot}
-renderPlotly({
-  choice = df()
-
-    persona1 = p_beta1 # Choose the persona
-
-  ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
-  gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
-  ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
-  rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
-
-  ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-
-    persona2 = p_beta2 # Choose the persona
-
-  ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
-  gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
-  ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
-  rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
-
-  ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-  gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-  ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-  rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-
-      persona3 = p_beta3 # Choose the persona
-
-  ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
-  gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
-  ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
-  rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
-
-  ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-  gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-  ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-  rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-
-  data <- c(rc_exp_util1, rc_rate1, 
-            rc_exp_util2, rc_rate2,
-            rc_exp_util3, rc_rate3)
-
-  df <- as.data.frame(matrix(data, 6, 1))
-
-  df[,2] <- c("Red Cross")
-  df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
-  df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
-  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
-
-  ggplotly(df %>% filter(Type == "Market Share") %>% 
-             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
-             geom_bar(position = "dodge", stat = "identity") +
-             labs(x="") + 
-             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
-             theme(legend.position = "none")
-    )
-})
-```
-
-```{r valuebox rc}
-renderValueBox({
-  choice = df()
-
-  persona = p_beta1 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-
-  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  valueBox(rc_rate,
-           color = "#660000",
-           icon = "fa-percent")
-})
+```{r valuebox rc commented}
+# renderValueBox({
+#   choice = df()
+#   
+#   persona = p_beta1 # Choose the persona
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+#   
+#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   valueBox(rc_rate,
+#            color = "#660000",
+#            icon = "fa-percent")
+# })
 ```
@@
 })
+```
+
+### Persona 1
+
+```{r persona 1 inputs}
+
+# selectInput("model_choice",
+#             label = "Select Model:",
+#             choices = c("public_political_social_charity_demo"))
+
+selectInput("charity_importance",
+          label = "Charity Importance:",
+          choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("trust_in_charity",
+            label = "Charity Trust:",
+            choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("donation_frequency",
+         label = "Donation Frequency:",
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+selectInput("donation_amount",
+         label = "Donation Amount:",
+         choices = c("$1-$49",
+                     '$50-$99',
+                     '$100-$499',
+                     '$500-$999',
+                     '$1,000-$4,999',
+                     '$5,000-$9,999',
+                     '$10,000+'))
+
+selectInput("volunteer_12",
+         label = "Volunteered in last 12 Months:",
+         choices = c("Yes", "No"))
+
+selectInput("volunteer_frequency",
+         label = "Volunteer Frequency:",
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+selectInput("personal_activism",
+         label = "Personal Activism:",
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+selectInput("family_activism",
+         label = "Family Activism:",
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+selectInput("religious_member",
+         label = "Church Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("sport_member",
+         label = "Sport or Recreational Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("art_member",
+         label = "Art, Music, or Educational Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("labor_member",
+         label = "Labor Union Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("political_member",
+         label = "Political Party Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("environmental_member",
+         label = "Enviornmental Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("professional_member",
+         label = "Professional Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("humanitarian_member",
+         label = "Humanitarian Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("consumer_member",
+         label = "Consumer Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("other_member",
+         label = "Other Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("national_news",
+         label = "Follow national news:",
+         choices = c('Multiple times a day',
+                     'Every day',
+                     "Once a week",
+                     "Hardly ever",
+                     "Never"))
+
+selectInput("international_news",
+         label = "Follow international news:",
+         choices = c('Always',
+                     "Sometimes",
+                     "Never"))
+
+selectInput("news_medium",
+         label = "Medium to follow news:",
+         choices = c('TV',
+                     'Print',
+                     "Online",
+                     "Social Media",
+                     "Radio",
+                     "Email newsletters",
+                     "News app"))
+
+selectInput("international_news",
+         label = "Follow international news:",
+         choices = c('Multiple times a day',
+                     'Every day',
+                     "Once a week",
+                     "Hardly ever",
+                     "Never"))
+
+selectInput("follow_gov",
+         label = "Follow government & public affairs:",
+         choices = c('Most of the time',
+                     'Some of the time',
+                     "Only now and then",
+                     "Hardly at all"))
+
+selectInput("travel_developing",
+         label = "Travel to developing country:",
+         choices = c('Yes', 'No'))
+
+selectInput("political_pref",
+         label = "Political views from liberal to conservative:",
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("institution_trust",
+         label = "Political institution trust from none to complete:",
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("others_charitable",
+         label = "People should be more charitable:",
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("worship_attendance",
+         label = "Worship service attendance:",
+         choices = c('Multiple times a week',
+                     'Once a week',
+                     "Once a month",
+                     "Once a year",
+                     "Never"))
+
+selectInput("religion_importance",
+         label = "Importance of religion:",
+         choices = c('Extremely important',
+                     'Very important',
+                     'Moderately important',
+                     'Slightly important',
+                     'Not at all important'))
+
+selectInput("religion",
+         label = "Religion:",
+         choices = c('Catholic',
+                     'Protestant',
+                     'Christian Orthodox',
+                     'Jewish',
+                     'Muslim',
+                     'Sikh',
+                     'Hindu',
+                     'Buddhist',
+                     'Atheist',
+                     'Other'))
+
+selectInput("gender",
+         label = "Gender:",
+         choices = c("Male",
+                     "Female",
+                     "Transgender",
+                     "Prefer not to say",
+                     "Other"))
+
+selectInput("marital_status",
+         label = "Marital Status:",
+         choices = c("Married",
+                     "Widowed",
+                     "Divorced",
+                     "Separated",
+                     "Never married"))
+
+selectInput("education",
+         label = "Education:",
+         choices = c("Less than high school",
+                     "High school",
+                     "Some college",
+                     "2 year degree",
+                     "4 year degree",
+                     "Graduate degree",
+                     "Doctorate"))
+
+selectInput("income",
+         label = "Income:",
+         choices = c('Less than $10,000',
+                     '$10,000 to $19,999',
+                     '$20,000 to $29,999',
+                     '$30,000 to $39,999',
+                     '$40,000 to $49,999',
+                     '$50,000 to $59,999',
+                     '$60,000 to $69,999',
+                     '$70,000 to $79,999',
+                     '$80,000 to $89,999',
+                     '$90,000 to $99,999',
+                     '$100,000 to $149,999',
+                     '$150,000 to $199,999',
+                     '$200,000 to $299,999',
+                     '$300,000 or more'))
+
+selectInput("race",
+         label = "Race(s):",
+         choices = c('White',
+                     'Black or African American',
+                     'American Indian or Alaska Native',
+                     'Asian',
+                     'Native Hawaiian or Pacific Islander',
+                     'Other'),
+         multiple = TRUE)
+
+selectInput("age",
+         label = "Age:",
+         choices = c('Under 18',
+                     '18 - 24',
+                     '25 - 34',
+                     '35 - 44',
+                     '45 - 54',
+                     '55 - 64',
+                     '65 - 74',
+                     '75 - 84',
+                     '85 or older'))
+
+```
+
+### Persona 2
+
+```{r persona 2 inputs}
+
+# selectInput("model_choice",
+#             label = "Select Model:",
+#             choices = c("public_political_social_charity_demo"))
+
+selectInput("charity_importance",
+          label = "Charity Importance:",
+          choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("trust_in_charity",
+            label = "Charity Trust:",
+            choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("donation_frequency",
+         label = "Donation Frequency:",
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+selectInput("donation_amount",
+         label = "Donation Amount:",
+         choices = c("$1-$49",
+                     '$50-$99',
+                     '$100-$499',
+                     '$500-$999',
+                     '$1,000-$4,999',
+                     '$5,000-$9,999',
+                     '$10,000+'))
+
+selectInput("volunteer_12",
+         label = "Volunteered in last 12 Months:",
+         choices = c("Yes", "No"))
+
+selectInput("volunteer_frequency",
+         label = "Volunteer Frequency:",
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+selectInput("personal_activism",
+         label = "Personal Activism:",
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+selectInput("family_activism",
+         label = "Family Activism:",
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+selectInput("religious_member",
+         label = "Church Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("sport_member",
+         label = "Sport or Recreational Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("art_member",
+         label = "Art, Music, or Educational Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("labor_member",
+         label = "Labor Union Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("political_member",
+         label = "Political Party Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("environmental_member",
+         label = "Enviornmental Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("professional_member",
+         label = "Professional Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("humanitarian_member",
+         label = "Humanitarian Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("consumer_member",
+         label = "Consumer Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("religious_member",
+         label = "Church Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("other_member",
+         label = "Other Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("national_news",
+         label = "Follow national news:",
+         choices = c('Multiple times a day',
+                     'Every day',
+                     "Once a week",
+                     "Hardly ever",
+                     "Never"))
+
+selectInput("international_news",
+         label = "Follow international news:",
+         choices = c('Always',
+                     "Sometimes",
+                     "Never"))
+
+selectInput("news_medium",
+         label = "Medium to follow news:",
+         choices = c('TV',
+                     'Print',
+                     "Online",
+                     "Social Media",
+                     "Radio",
+                     "Email newsletters",
+                     "News app"))
+
+selectInput("international_news",
+         label = "Follow international news:",
+         choices = c('Multiple times a day',
+                     'Every day',
+                     "Once a week",
+                     "Hardly ever",
+                     "Never"))
+
+selectInput("follow_gov",
+         label = "Follow government & public affairs:",
+         choices = c('Most of the time',
+                     'Some of the time',
+                     "Only now and then",
+                     "Hardly at all"))
+
+selectInput("travel_developing",
+         label = "Travel to developing country:",
+         choices = c('Yes', 'No'))
+
+selectInput("polical_pref",
+         label = "Polical views from liberal to conservative:",
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("institution_trust",
+         label = "Political institution trust from none to complete:",
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("others_charitable",
+         label = "People should be more charitable:",
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("worship_attendance",
+         label = "Worship service attendance:",
+         choices = c('Multiple times a week',
+                     'Once a week',
+                     "Once a month",
+                     "Once a year",
+                     "Never"))
+
+selectInput("religion_importance",
+         label = "Importance of religion:",
+         choices = c('Extremely important',
+                     'Very important',
+                     'Moderately important',
+                     'Slightly important',
+                     'Not at all important'))
+
+selectInput("religion",
+         label = "Religion:",
+         choices = c('Catholic',
+                     'Protestant',
+                     'Christian Orthodox',
+                     'Jewish',
+                     'Muslim',
+                     'Sikh',
+                     'Hindu',
+                     'Buddhist',
+                     'Atheist',
+                     'Other'))
+
+selectInput("gender",
+         label = "Gender:",
+         choices = c("Male",
+                     "Female",
+                     "Transgender",
+                     "Prefer not to say",
+                     "Other"))
+
+selectInput("marital_status",
+         label = "Marital Status:",
+         choices = c("Married",
+                     "Widowed",
+                     "Divorced",
+                     "Separated",
+                     "Never married"))
+
+selectInput("education",
+         label = "Education:",
+         choices = c("Less than high school",
+                     "High school",
+                     "Some college",
+                     "2 year degree",
+                     "4 year degree",
+                     "Graduate degree",
+                     "Doctorate"))
+
+selectInput("income",
+         label = "Income:",
+         choices = c('Less than $10,000',
+                     '$10,000 to $19,999',
+                     '$20,000 to $29,999',
+                     '$30,000 to $39,999',
+                     '$40,000 to $49,999',
+                     '$50,000 to $59,999',
+                     '$60,000 to $69,999',
+                     '$70,000 to $79,999',
+                     '$80,000 to $89,999',
+                     '$90,000 to $99,999',
+                     '$100,000 to $149,999',
+                     '$150,000 to $199,999',
+                     '$200,000 to $299,999',
+                     '$300,000 or more'))
+
+selectInput("race",
+         label = "Race(s):",
+         choices = c('White',
+                     'Black or African American',
+                     'American Indian or Alaska Native',
+                     'Asian',
+                     'Native Hawaiian or Pacific Islander',
+                     'Other'),
+         multiple = TRUE)
+
+selectInput("education",
+         label = "Education:",
+         choices = c("Less than high school",
+                     "High school",
+                     "Some college",
+                     "2 year degree",
+                     "4 year degree",
+                     "Graduate degree",
+                     "Doctorate"))
+
+selectInput("age",
+         label = "Age:",
+         choices = c('Under 18',
+                     '18 - 24',
+                     '25 - 34',
+                     '35 - 44',
+                     '45 - 54',
+                     '55 - 64',
+                     '65 - 74',
+                     '75 - 84',
+                     '85 or older'))
+
+```
+
+### Persona 3
+
+```{r persona 3 inputs}
+
+# selectInput("model_choice",
+#             label = "Select Model:",
+#             choices = c("public_political_social_charity_demo"))
+
+selectInput("charity_importance",
+          label = "Charity Importance:",
+          choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("trust_in_charity",
+            label = "Charity Trust:",
+            choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("donation_frequency",
+         label = "Donation Frequency:",
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+selectInput("donation_amount",
+         label = "Donation Amount:",
+         choices = c("$1-$49",
+                     '$50-$99',
+                     '$100-$499',
+                     '$500-$999',
+                     '$1,000-$4,999',
+                     '$5,000-$9,999',
+                     '$10,000+'))
+
+selectInput("volunteer_12",
+         label = "Volunteered in last 12 Months:",
+         choices = c("Yes", "No"))
+
+selectInput("volunteer_frequency",
+         label = "Volunteer Frequency:",
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+selectInput("personal_activism",
+         label = "Personal Activism:",
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+selectInput("family_activism",
+         label = "Family Activism:",
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+selectInput("religious_member",
+         label = "Church Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("sport_member",
+         label = "Sport or Recreational Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("art_member",
+         label = "Art, Music, or Educational Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("labor_member",
+         label = "Labor Union Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("political_member",
+         label = "Political Party Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("environmental_member",
+         label = "Enviornmental Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("professional_member",
+         label = "Professional Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("humanitarian_member",
+         label = "Humanitarian Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("consumer_member",
+         label = "Consumer Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("religious_member",
+         label = "Church Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("other_member",
+         label = "Other Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("national_news",
+         label = "Follow national news:",
+         choices = c('Multiple times a day',
+                     'Every day',
+                     "Once a week",
+                     "Hardly ever",
+                     "Never"))
+
+selectInput("international_news",
+         label = "Follow international news:",
+         choices = c('Always',
+                     "Sometimes",
+                     "Never"))
+
+selectInput("news_medium",
+         label = "Medium to follow news:",
+         choices = c('TV',
+                     'Print',
+                     "Online",
+                     "Social Media",
+                     "Radio",
+                     "Email newsletters",
+                     "News app"))
+
+selectInput("international_news",
+         label = "Follow international news:",
+         choices = c('Multiple times a day',
+                     'Every day',
+                     "Once a week",
+                     "Hardly ever",
+                     "Never"))
+
+selectInput("follow_gov",
+         label = "Follow government & public affairs:",
+         choices = c('Most of the time',
+                     'Some of the time',
+                     "Only now and then",
+                     "Hardly at all"))
+
+selectInput("travel_developing",
+         label = "Travel to developing country:",
+         choices = c('Yes', 'No'))
+
+selectInput("polical_pref",
+         label = "Polical views from liberal to conservative:",
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("institution_trust",
+         label = "Political institution trust from none to complete:",
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("others_charitable",
+         label = "People should be more charitable:",
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("worship_attendance",
+         label = "Worship service attendance:",
+         choices = c('Multiple times a week',
+                     'Once a week',
+                     "Once a month",
+                     "Once a year",
+                     "Never"))
+
+selectInput("religion_importance",
+         label = "Importance of religion:",
+         choices = c('Extremely important',
+                     'Very important',
+                     'Moderately important',
+                     'Slightly important',
+                     'Not at all important'))
+
+selectInput("religion",
+         label = "Religion:",
+         choices = c('Catholic',
+                     'Protestant',
+                     'Christian Orthodox',
+                     'Jewish',
+                     'Muslim',
+                     'Sikh',
+                     'Hindu',
+                     'Buddhist',
+                     'Atheist',
+                     'Other'))
+
+selectInput("gender",
+         label = "Gender:",
+         choices = c("Male",
+                     "Female",
+                     "Transgender",
+                     "Prefer not to say",
+                     "Other"))
+
+selectInput("marital_status",
+         label = "Marital Status:",
+         choices = c("Married",
+                     "Widowed",
+                     "Divorced",
+                     "Separated",
+                     "Never married"))
+
+selectInput("education",
+         label = "Education:",
+         choices = c("Less than high school",
+                     "High school",
+                     "Some college",
+                     "2 year degree",
+                     "4 year degree",
+                     "Graduate degree",
+                     "Doctorate"))
+
+selectInput("income",
+         label = "Income:",
+         choices = c('Less than $10,000',
+                     '$10,000 to $19,999',
+                     '$20,000 to $29,999',
+                     '$30,000 to $39,999',
+                     '$40,000 to $49,999',
+                     '$50,000 to $59,999',
+                     '$60,000 to $69,999',
+                     '$70,000 to $79,999',
+                     '$80,000 to $89,999',
+                     '$90,000 to $99,999',
+                     '$100,000 to $149,999',
+                     '$150,000 to $199,999',
+                     '$200,000 to $299,999',
+                     '$300,000 or more'))
+
+selectInput("race",
+         label = "Race(s):",
+         choices = c('White',
+                     'Black or African American',
+                     'American Indian or Alaska Native',
+                     'Asian',
+                     'Native Hawaiian or Pacific Islander',
+                     'Other'),
+         multiple = TRUE)
+
+selectInput("education",
+         label = "Education:",
+         choices = c("Less than high school",
+                     "High school",
+                     "Some college",
+                     "2 year degree",
+                     "4 year degree",
+                     "Graduate degree",
+                     "Doctorate"))
+
+selectInput("age",
+         label = "Age:",
+         choices = c('Under 18',
+                     '18 - 24',
+                     '25 - 34',
+                     '35 - 44',
+                     '45 - 54',
+                     '55 - 64',
+                     '65 - 74',
+                     '75 - 84',
+                     '85 or older'))
+
 ```

### 2020-08-13 analysis/05_market_simulator.Rmd
Building out more of the persona reactive element. Need to create the empty dataframe for it with appropriate levels to correspond with the input questions.

@@
 
+####################################################################################
+
 beta <- as.data.frame(matrix(rep(0), nrow = 13))
@@
 beta$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")
-
-####################################################################################
 
@@
 
+####################################################################
+
+beta <- as.data.frame(matrix(rep(0), nrow = 28))
+
+beta$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "filler","filler", "filler", "filler", "filler", "filler","filler", "filler", "filler", "filler", "filler","filler", "filler", "filler", "filler", "filler","filler", "filler", "filler", "filler")
+
 # Persona Reactive Element
 p <- reactive({
-  #Amnesty International
+  #Persona 1
     beta$p1_value <- 0
@@
     beta$p1_value[beta$levels %in% input$p1_volunteer_12] <- 1
-  #Greenpeace
+  #Persona 2
     beta$p2_value <- 0
     beta$p2_value[beta$levels == 'Persona 2'] <- 1
-    beta$p2_value[beta$levels %in% input$gp_issue] <- 1
-    beta$p2_value[beta$levels %in% input$gp_fin_trans] <- 1
-    beta$p2_value[beta$levels %in% input$gp_account] <- 1
-    beta$p2_value[beta$levels %in% input$gp_funding] <- 1
-    beta$p2_value[beta$levels %in% input$gp_gov_relat] <- 1
-  #Oxfam
+    beta$p2_value[beta$levels %in% input$p2_charity_importance] <- 1
+    beta$p2_value[beta$levels %in% input$p2_trust_in_charity] <- 1
+    beta$p2_value[beta$levels %in% input$p2_donation_frequency] <- 1
+    beta$p2_value[beta$levels %in% input$p2_donation_amount] <- 1
+    beta$p2_value[beta$levels %in% input$p2_volunteer_12] <- 1
+  #Persona 3
     beta$p3_value <- 0
     beta$p3_value[beta$levels == 'Persona 3'] <- 1
-    beta$p3_value[beta$levels %in% input$ox_issue] <- 1
-    beta$p3_value[beta$levels %in% input$ox_fin_trans] <- 1
-    beta$p3_value[beta$levels %in% input$ox_account] <- 1
-    beta$p3_value[beta$levels %in% input$ox_funding] <- 1
-    beta$p3_value[beta$levels %in% input$ox_gov_relat] <- 1
+    beta$p3_value[beta$levels %in% input$p3_charity_importance] <- 1
+    beta$p3_value[beta$levels %in% input$p3_trust_in_charity] <- 1
+    beta$p3_value[beta$levels %in% input$p3_donation_frequency] <- 1
+    beta$p3_value[beta$levels %in% input$p3_donation_amount] <- 1
+    beta$p3_value[beta$levels %in% input$p3_volunteer_12] <- 1
     beta
@@
 
-```{r sidebar inputs, echo=FALSE}
+```{r sidebar inputs commented}
 
@@
 
-Organization Breakdown {.tabset .tabset-fade}
+Organizations and Personas {.tabset .tabset-fade}
 --------------------------------------------------
@@
 
+selectInput("p1_charity_importance",
+          label = "Charity Importance:",
+          choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("p1_trust_in_charity",
+            label = "Charity Trust:",
+            choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("p1_donation_frequency",
+         label = "Donation Frequency:",
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+selectInput("p1_donation_amount",
+         label = "Donation Amount:",
+         choices = c("$1-$49",
+                     '$50-$99',
+                     '$100-$499',
+                     '$500-$999',
+                     '$1,000-$4,999',
+                     '$5,000-$9,999',
+                     '$10,000+'))
+
+selectInput("p1_volunteer_12",
+         label = "Volunteered in last 12 Months:",
+         choices = c("Yes", "No"))
+
+selectInput("p1_volunteer_frequency",
+         label = "Volunteer Frequency:",
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+selectInput("p1_personal_activism",
+         label = "Personal Activism:",
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+selectInput("p1_family_activism",
+         label = "Family Activism:",
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+selectInput("p1_religious_member",
+         label = "Church Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_sport_member",
+         label = "Sport or Recreational Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_art_member",
+         label = "Art, Music, or Educational Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_labor_member",
+         label = "Labor Union Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_political_member",
+         label = "Political Party Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_environmental_member",
+         label = "Enviornmental Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_professional_member",
+         label = "Professional Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_humanitarian_member",
+         label = "Humanitarian Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_consumer_member",
+         label = "Consumer Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_other_member",
+         label = "Other Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_national_news",
+         label = "Follow national news:",
+         choices = c('Multiple times a day',
+                     'Every day',
+                     "Once a week",
+                     "Hardly ever",
+                     "Never"))
+
+selectInput("p1_international_news",
+         label = "Follow international news:",
+         choices = c('Always',
+                     "Sometimes",
+                     "Never"))
+
+selectInput("p1_news_medium",
+         label = "Medium to follow news:",
+         choices = c('TV',
+                     'Print',
+                     "Online",
+                     "Social Media",
+                     "Radio",
+                     "Email newsletters",
+                     "News app"))
+
+selectInput("p1_follow_gov",
+         label = "Follow government & public affairs:",
+         choices = c('Most of the time',
+                     'Some of the time',
+                     "Only now and then",
+                     "Hardly at all"))
+
+selectInput("p1_travel_developing",
+         label = "Travel to developing country:",
+         choices = c('Yes', 'No'))
+
+selectInput("p1_political_pref",
+         label = "Political views from liberal to conservative:",
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("p1_institution_trust",
+         label = "Political institution trust from none to complete:",
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("p1_others_charitable",
+         label = "People should be more charitable:",
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("p1_worship_attendance",
+         label = "Worship service attendance:",
+         choices = c('Multiple times a week',
+                     'Once a week',
+                     "Once a month",
+                     "Once a year",
+                     "Never"))
+
+selectInput("p1_religion_importance",
+         label = "Importance of religion:",
+         choices = c('Extremely important',
+                     'Very important',
+                     'Moderately important',
+                     'Slightly important',
+                     'Not at all important'))
+
+selectInput("p1_religion",
+         label = "Religion:",
+         choices = c('Catholic',
+                     'Protestant',
+                     'Christian Orthodox',
+                     'Jewish',
+                     'Muslim',
+                     'Sikh',
+                     'Hindu',
+                     'Buddhist',
+                     'Atheist',
+                     'Other'))
+
+selectInput("p1_gender",
+         label = "Gender:",
+         choices = c("Male",
+                     "Female",
+                     "Transgender",
+                     "Prefer not to say",
+                     "Other"))
+
+selectInput("p1_marital_status",
+         label = "Marital Status:",
+         choices = c("Married",
+                     "Widowed",
+                     "Divorced",
+                     "Separated",
+                     "Never married"))
+
+selectInput("p1_education",
+         label = "Education:",
+         choices = c("Less than high school",
+                     "High school",
+                     "Some college",
+                     "2 year degree",
+                     "4 year degree",
+                     "Graduate degree",
+                     "Doctorate"))
+
+selectInput("p1_income",
+         label = "Income:",
+         choices = c('Less than $10,000',
+                     '$10,000 to $19,999',
+                     '$20,000 to $29,999',
+                     '$30,000 to $39,999',
+                     '$40,000 to $49,999',
+                     '$50,000 to $59,999',
+                     '$60,000 to $69,999',
+                     '$70,000 to $79,999',
+                     '$80,000 to $89,999',
+                     '$90,000 to $99,999',
+                     '$100,000 to $149,999',
+                     '$150,000 to $199,999',
+                     '$200,000 to $299,999',
+                     '$300,000 or more'))
+
+selectInput("p1_race",
+         label = "Race(s):",
+         choices = c('White',
+                     'Black or African American',
+                     'American Indian or Alaska Native',
+                     'Asian',
+                     'Native Hawaiian or Pacific Islander',
+                     'Other'),
+         multiple = TRUE)
+
+selectInput("p1_age",
+         label = "Age:",
+         choices = c('Under 18',
+                     '18 - 24',
+                     '25 - 34',
+                     '35 - 44',
+                     '45 - 54',
+                     '55 - 64',
+                     '65 - 74',
+                     '75 - 84',
+                     '85 or older'))
+
+```
+
+### Persona 2
+
+```{r persona 2 inputs}
+
+# selectInput("model_choice",
+#             label = "Select Model:",
+#             choices = c("public_political_social_charity_demo"))
+
 selectInput("charity_importance",
@@
 
-selectInput("international_news",
-         label = "Follow international news:",
-         choices = c('Multiple times a day',
-                     'Every day',
-                     "Once a week",
-                     "Hardly ever",
-                     "Never"))
-
 selectInput("follow_gov",
@@
 
-selectInput("political_pref",
-         label = "Political views from liberal to conservative:",
+selectInput("polical_pref",
+         label = "Polical views from liberal to conservative:",
          choices = c("0", '1', '2', '3','4','5','6','7'))
@@
 
-### Persona 2
-
-```{r persona 2 inputs}
+### Persona 3
+
+```{r persona 3 inputs}
 
@@
 
-selectInput("religious_member",
-         label = "Church Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
 selectInput("other_member",
@@
                      "News app"))
-
-selectInput("international_news",
-         label = "Follow international news:",
-         choices = c('Multiple times a day',
-                     'Every day',
-                     "Once a week",
-                     "Hardly ever",
-                     "Never"))
 
@@
 
-selectInput("education",
-         label = "Education:",
-         choices = c("Less than high school",
-                     "High school",
-                     "Some college",
-                     "2 year degree",
-                     "4 year degree",
-                     "Graduate degree",
-                     "Doctorate"))
-
 selectInput("age",
@@
 
-### Persona 3
-
-```{r persona 3 inputs}
-
-# selectInput("model_choice",
-#             label = "Select Model:",
-#             choices = c("public_political_social_charity_demo"))
-
-selectInput("charity_importance",
-          label = "Charity Importance:",
-          choices = c("0", '1', '2', '3','4','5','6','7'))
-
-selectInput("trust_in_charity",
-            label = "Charity Trust:",
-            choices = c("0", '1', '2', '3','4','5','6','7'))
-
-selectInput("donation_frequency",
-         label = "Donation Frequency:",
-         choices = c('Once a week',
-                     'Once a Month',
-                     'Once every three months',
-                     'Once every six months',
-                     'Once a year',
-                     'Once every few years',
-                     'Never'))
-
-selectInput("donation_amount",
-         label = "Donation Amount:",
-         choices = c("$1-$49",
-                     '$50-$99',
-                     '$100-$499',
-                     '$500-$999',
-                     '$1,000-$4,999',
-                     '$5,000-$9,999',
-                     '$10,000+'))
-
-selectInput("volunteer_12",
-         label = "Volunteered in last 12 Months:",
-         choices = c("Yes", "No"))
-
-selectInput("volunteer_frequency",
-         label = "Volunteer Frequency:",
-         choices = c('Once a week',
-                     'Once a Month',
-                     'Once every three months',
-                     'Once every six months',
-                     'Once a year',
-                     'Once every few years',
-                     'Never'))
-
-selectInput("personal_activism",
-         label = "Personal Activism:",
-         choices = c('Extremely involved',
-                     'Very involved',
-                     'Moderately involved',
-                     'Slightly involved',
-                     'Never involved'))
-
-selectInput("family_activism",
-         label = "Family Activism:",
-         choices = c('Extremely involved',
-                     'Very involved',
-                     'Moderately involved',
-                     'Slightly involved',
-                     'Never involved'))
-
-selectInput("religious_member",
-         label = "Church Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("sport_member",
-         label = "Sport or Recreational Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("art_member",
-         label = "Art, Music, or Educational Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("labor_member",
-         label = "Labor Union Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("political_member",
-         label = "Political Party Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("environmental_member",
-         label = "Enviornmental Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("professional_member",
-         label = "Professional Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("humanitarian_member",
-         label = "Humanitarian Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("consumer_member",
-         label = "Consumer Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("religious_member",
-         label = "Church Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("other_member",
-         label = "Other Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("national_news",
-         label = "Follow national news:",
-         choices = c('Multiple times a day',
-                     'Every day',
-                     "Once a week",
-                     "Hardly ever",
-                     "Never"))
-
-selectInput("international_news",
-         label = "Follow international news:",
-         choices = c('Always',
-                     "Sometimes",
-                     "Never"))
-
-selectInput("news_medium",
-         label = "Medium to follow news:",
-         choices = c('TV',
-                     'Print',
-                     "Online",
-                     "Social Media",
-                     "Radio",
-                     "Email newsletters",
-                     "News app"))
-
-selectInput("international_news",
-         label = "Follow international news:",
-         choices = c('Multiple times a day',
-                     'Every day',
-                     "Once a week",
-                     "Hardly ever",
-                     "Never"))
-
-selectInput("follow_gov",
-         label = "Follow government & public affairs:",
-         choices = c('Most of the time',
-                     'Some of the time',
-                     "Only now and then",
-                     "Hardly at all"))
-
-selectInput("travel_developing",
-         label = "Travel to developing country:",
-         choices = c('Yes', 'No'))
-
-selectInput("polical_pref",
-         label = "Polical views from liberal to conservative:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
-
-selectInput("institution_trust",
-         label = "Political institution trust from none to complete:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
-
-selectInput("others_charitable",
-         label = "People should be more charitable:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
-
-selectInput("worship_attendance",
-         label = "Worship service attendance:",
-         choices = c('Multiple times a week',
-                     'Once a week',
-                     "Once a month",
-                     "Once a year",
-                     "Never"))
-
-selectInput("religion_importance",
-         label = "Importance of religion:",
-         choices = c('Extremely important',
-                     'Very important',
-                     'Moderately important',
-                     'Slightly important',
-                     'Not at all important'))
-
-selectInput("religion",
-         label = "Religion:",
-         choices = c('Catholic',
-                     'Protestant',
-                     'Christian Orthodox',
-                     'Jewish',
-                     'Muslim',
-                     'Sikh',
-                     'Hindu',
-                     'Buddhist',
-                     'Atheist',
-                     'Other'))
-
-selectInput("gender",
-         label = "Gender:",
-         choices = c("Male",
-                     "Female",
-                     "Transgender",
-                     "Prefer not to say",
-                     "Other"))
-
-selectInput("marital_status",
-         label = "Marital Status:",
-         choices = c("Married",
-                     "Widowed",
-                     "Divorced",
-                     "Separated",
-                     "Never married"))
-
-selectInput("education",
-         label = "Education:",
-         choices = c("Less than high school",
-                     "High school",
-                     "Some college",
-                     "2 year degree",
-                     "4 year degree",
-                     "Graduate degree",
-                     "Doctorate"))
-
-selectInput("income",
-         label = "Income:",
-         choices = c('Less than $10,000',
-                     '$10,000 to $19,999',
-                     '$20,000 to $29,999',
-                     '$30,000 to $39,999',
-                     '$40,000 to $49,999',
-                     '$50,000 to $59,999',
-                     '$60,000 to $69,999',
-                     '$70,000 to $79,999',
-                     '$80,000 to $89,999',
-                     '$90,000 to $99,999',
-                     '$100,000 to $149,999',
-                     '$150,000 to $199,999',
-                     '$200,000 to $299,999',
-                     '$300,000 or more'))
-
-selectInput("race",
-         label = "Race(s):",
-         choices = c('White',
-                     'Black or African American',
-                     'American Indian or Alaska Native',
-                     'Asian',
-                     'Native Hawaiian or Pacific Islander',
-                     'Other'),
-         multiple = TRUE)
-
-selectInput("education",
-         label = "Education:",
-         choices = c("Less than high school",
-                     "High school",
-                     "Some college",
-                     "2 year degree",
-                     "4 year degree",
-                     "Graduate degree",
-                     "Doctorate"))
-
-selectInput("age",
-         label = "Age:",
-         choices = c('Under 18',
-                     '18 - 24',
-                     '25 - 34',
-                     '35 - 44',
-                     '45 - 54',
-                     '55 - 64',
-                     '65 - 74',
-                     '75 - 84',
-                     '85 or older'))
-
-```
-
 <!-- There is an issue of not being able to see the last selectInput options when drop down box appears -->

### 2020-08-13 analysis/05_market_simulator.Rmd
Updated the Persona Inputs to connect to Persona Reactive elements.

@@
 
-beta <- as.data.frame(matrix(rep(0), nrow = 28))
-
-beta$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "filler","filler", "filler", "filler", "filler", "filler","filler", "filler", "filler", "filler", "filler","filler", "filler", "filler", "filler", "filler","filler", "filler", "filler", "filler")
+beta <- as.data.frame(matrix(rep(0), nrow = 38))
+
+beta$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
 
@@
     beta$p1_value[beta$levels %in% input$p1_volunteer_12] <- 1
+    beta$p1_value[beta$levels %in% input$p1_volunteer_frequency] <- 1
+    beta$p1_value[beta$levels %in% input$p1_personal_activism] <- 1
+    beta$p1_value[beta$levels %in% input$p1_family_activism] <- 1
+    beta$p1_value[beta$levels %in% input$p1_religious_member] <- 1
+    beta$p1_value[beta$levels %in% input$p1_sport_member] <- 1
+    beta$p1_value[beta$levels %in% input$p1_art_member] <- 1
+    beta$p1_value[beta$levels %in% input$p1_labor_member] <- 1
+    beta$p1_value[beta$levels %in% input$p1_political_member] <- 1
+    beta$p1_value[beta$levels %in% input$p1_environmental_member] <- 1
+    beta$p1_value[beta$levels %in% input$p1_professional_member] <- 1
+    beta$p1_value[beta$levels %in% input$p1_humanitarian_member] <- 1
+    beta$p1_value[beta$levels %in% input$p1_consumer_member] <- 1
+    beta$p1_value[beta$levels %in% input$p1_other_member] <- 1
+    beta$p1_value[beta$levels %in% input$p1_national_news] <- 1
+    beta$p1_value[beta$levels %in% input$p1_international_news] <- 1
+    beta$p1_value[beta$levels %in% input$p1_news_medium] <- 1
+    beta$p1_value[beta$levels %in% input$p1_follow_gov] <- 1
+    beta$p1_value[beta$levels %in% input$p1_travel_developing] <- 1
+    beta$p1_value[beta$levels %in% input$p1_political_pref] <- 1
+    beta$p1_value[beta$levels %in% input$p1_institution_trust] <- 1
+    beta$p1_value[beta$levels %in% input$p1_others_charitable] <- 1
+    beta$p1_value[beta$levels %in% input$p1_worship_attendence] <- 1
+    beta$p1_value[beta$levels %in% input$p1_religion_importance] <- 1
+    beta$p1_value[beta$levels %in% input$p1_religion] <- 1
+    beta$p1_value[beta$levels %in% input$p1_gender] <- 1
+    beta$p1_value[beta$levels %in% input$p1_marital_status] <- 1
+    beta$p1_value[beta$levels %in% input$p1_education] <- 1
+    beta$p1_value[beta$levels %in% input$p1_income] <- 1
+    beta$p1_value[beta$levels %in% input$p1_race] <- 1
+    beta$p1_value[beta$levels %in% input$p1_age] <- 1
   #Persona 2
@@
     beta$p2_value[beta$levels %in% input$p2_volunteer_12] <- 1
+    beta$p2_value[beta$levels %in% input$p2_volunteer_frequency] <- 1
+    beta$p2_value[beta$levels %in% input$p2_personal_activism] <- 1
+    beta$p2_value[beta$levels %in% input$p2_family_activism] <- 1
+    beta$p2_value[beta$levels %in% input$p2_religious_member] <- 1
+    beta$p2_value[beta$levels %in% input$p2_sport_member] <- 1
+    beta$p2_value[beta$levels %in% input$p2_art_member] <- 1
+    beta$p2_value[beta$levels %in% input$p2_labor_member] <- 1
+    beta$p2_value[beta$levels %in% input$p2_political_member] <- 1
+    beta$p2_value[beta$levels %in% input$p2_environmental_member] <- 1
+    beta$p2_value[beta$levels %in% input$p2_professional_member] <- 1
+    beta$p2_value[beta$levels %in% input$p2_humanitarian_member] <- 1
+    beta$p2_value[beta$levels %in% input$p2_consumer_member] <- 1
+    beta$p2_value[beta$levels %in% input$p2_other_member] <- 1
+    beta$p2_value[beta$levels %in% input$p2_national_news] <- 1
+    beta$p2_value[beta$levels %in% input$p2_international_news] <- 1
+    beta$p2_value[beta$levels %in% input$p2_news_medium] <- 1
+    beta$p2_value[beta$levels %in% input$p2_follow_gov] <- 1
+    beta$p2_value[beta$levels %in% input$p2_travel_developing] <- 1
+    beta$p2_value[beta$levels %in% input$p2_political_pref] <- 1
+    beta$p2_value[beta$levels %in% input$p2_institution_trust] <- 1
+    beta$p2_value[beta$levels %in% input$p2_others_charitable] <- 1
+    beta$p2_value[beta$levels %in% input$p2_worship_attendence] <- 1
+    beta$p2_value[beta$levels %in% input$p2_religion_importance] <- 1
+    beta$p2_value[beta$levels %in% input$p2_religion] <- 1
+    beta$p2_value[beta$levels %in% input$p2_gender] <- 1
+    beta$p2_value[beta$levels %in% input$p2_marital_status] <- 1
+    beta$p2_value[beta$levels %in% input$p2_education] <- 1
+    beta$p2_value[beta$levels %in% input$p2_income] <- 1
+    beta$p2_value[beta$levels %in% input$p2_race] <- 1
+    beta$p2_value[beta$levels %in% input$p2_age] <- 1
   #Persona 3
@@
     beta$p3_value[beta$levels %in% input$p3_volunteer_12] <- 1
+    beta$p3_value[beta$levels %in% input$p3_volunteer_frequency] <- 1
+    beta$p3_value[beta$levels %in% input$p3_personal_activism] <- 1
+    beta$p3_value[beta$levels %in% input$p3_family_activism] <- 1
+    beta$p3_value[beta$levels %in% input$p3_religious_member] <- 1
+    beta$p3_value[beta$levels %in% input$p3_sport_member] <- 1
+    beta$p3_value[beta$levels %in% input$p3_art_member] <- 1
+    beta$p3_value[beta$levels %in% input$p3_labor_member] <- 1
+    beta$p3_value[beta$levels %in% input$p3_political_member] <- 1
+    beta$p3_value[beta$levels %in% input$p3_environmental_member] <- 1
+    beta$p3_value[beta$levels %in% input$p3_professional_member] <- 1
+    beta$p3_value[beta$levels %in% input$p3_humanitarian_member] <- 1
+    beta$p3_value[beta$levels %in% input$p3_consumer_member] <- 1
+    beta$p3_value[beta$levels %in% input$p3_other_member] <- 1
+    beta$p3_value[beta$levels %in% input$p3_national_news] <- 1
+    beta$p3_value[beta$levels %in% input$p3_international_news] <- 1
+    beta$p3_value[beta$levels %in% input$p3_news_medium] <- 1
+    beta$p3_value[beta$levels %in% input$p3_follow_gov] <- 1
+    beta$p3_value[beta$levels %in% input$p3_travel_developing] <- 1
+    beta$p3_value[beta$levels %in% input$p3_political_pref] <- 1
+    beta$p3_value[beta$levels %in% input$p3_institution_trust] <- 1
+    beta$p3_value[beta$levels %in% input$p3_others_charitable] <- 1
+    beta$p3_value[beta$levels %in% input$p3_worship_attendence] <- 1
+    beta$p3_value[beta$levels %in% input$p3_religion_importance] <- 1
+    beta$p3_value[beta$levels %in% input$p3_religion] <- 1
+    beta$p3_value[beta$levels %in% input$p3_gender] <- 1
+    beta$p3_value[beta$levels %in% input$p3_marital_status] <- 1
+    beta$p3_value[beta$levels %in% input$p3_education] <- 1
+    beta$p3_value[beta$levels %in% input$p3_income] <- 1
+    beta$p3_value[beta$levels %in% input$p3_race] <- 1
+    beta$p3_value[beta$levels %in% input$p3_age] <- 1
     beta
@@
 
-selectInput("charity_importance",
+selectInput("p2_charity_importance",
           label = "Charity Importance:",
@@
 
-selectInput("trust_in_charity",
+selectInput("p2_trust_in_charity",
             label = "Charity Trust:",
@@
 
-selectInput("donation_frequency",
+selectInput("p2_donation_frequency",
          label = "Donation Frequency:",
@@
 
-selectInput("donation_amount",
+selectInput("p2_donation_amount",
          label = "Donation Amount:",
@@
 
-selectInput("volunteer_12",
+selectInput("p2_volunteer_12",
          label = "Volunteered in last 12 Months:",
@@
 
-selectInput("volunteer_frequency",
+selectInput("p2_volunteer_frequency",
          label = "Volunteer Frequency:",
@@
 
-selectInput("personal_activism",
+selectInput("p2_personal_activism",
          label = "Personal Activism:",
@@
 
-selectInput("family_activism",
+selectInput("p2_family_activism",
          label = "Family Activism:",
@@
 
-selectInput("religious_member",
+selectInput("p2_religious_member",
          label = "Church Membership:",
@@
 
-selectInput("sport_member",
+selectInput("p2_sport_member",
          label = "Sport or Recreational Membership:",
@@
 
-selectInput("art_member",
+selectInput("p2_art_member",
          label = "Art, Music, or Educational Membership:",
@@
 
-selectInput("labor_member",
+selectInput("p2_labor_member",
          label = "Labor Union Membership:",
@@
 
-selectInput("political_member",
+selectInput("p2_political_member",
          label = "Political Party Membership:",
@@
 
-selectInput("environmental_member",
+selectInput("p2_environmental_member",
          label = "Enviornmental Org. Membership:",
@@
 
-selectInput("professional_member",
+selectInput("p2_professional_member",
          label = "Professional Membership:",
@@
 
-selectInput("humanitarian_member",
+selectInput("p2_humanitarian_member",
          label = "Humanitarian Org. Membership:",
@@
 
-selectInput("consumer_member",
+selectInput("p2_consumer_member",
          label = "Consumer Org. Membership:",
@@
 
-selectInput("other_member",
+selectInput("p2_other_member",
          label = "Other Org. Membership:",
@@
 
-selectInput("national_news",
+selectInput("p2_national_news",
          label = "Follow national news:",
@@
 
-selectInput("international_news",
+selectInput("p2_international_news",
          label = "Follow international news:",
@@
 
-selectInput("news_medium",
+selectInput("p2_news_medium",
          label = "Medium to follow news:",
@@
 
-selectInput("follow_gov",
+selectInput("p2_follow_gov",
          label = "Follow government & public affairs:",
@@
 
-selectInput("travel_developing",
+selectInput("p2_travel_developing",
          label = "Travel to developing country:",
@@
 
-selectInput("polical_pref",
+selectInput("p2_polical_pref",
          label = "Polical views from liberal to conservative:",
@@
 
-selectInput("institution_trust",
+selectInput("p2_institution_trust",
          label = "Political institution trust from none to complete:",
@@
 
-selectInput("others_charitable",
+selectInput("p2_others_charitable",
          label = "People should be more charitable:",
@@
 
-selectInput("worship_attendance",
+selectInput("p2_worship_attendance",
          label = "Worship service attendance:",
@@
 
-selectInput("religion_importance",
+selectInput("p2_religion_importance",
          label = "Importance of religion:",
@@
 
-selectInput("religion",
+selectInput("p2_religion",
          label = "Religion:",
@@
 
-selectInput("gender",
+selectInput("p2_gender",
          label = "Gender:",
@@
 
-selectInput("marital_status",
+selectInput("p2_marital_status",
          label = "Marital Status:",
@@
 
-selectInput("education",
+selectInput("p2_education",
          label = "Education:",
@@
 
-selectInput("income",
+selectInput("p2_income",
          label = "Income:",
@@
 
-selectInput("race",
+selectInput("p2_race",
          label = "Race(s):",
@@
 
-selectInput("age",
+selectInput("p2_age",
          label = "Age:",
@@
 
-selectInput("charity_importance",
+selectInput("p3_charity_importance",
           label = "Charity Importance:",
@@
 
-selectInput("trust_in_charity",
+selectInput("p3_trust_in_charity",
             label = "Charity Trust:",
@@
 
-selectInput("donation_frequency",
+selectInput("p3_donation_frequency",
          label = "Donation Frequency:",
@@
 
-selectInput("donation_amount",
+selectInput("p3_donation_amount",
          label = "Donation Amount:",
@@
 
-selectInput("volunteer_12",
+selectInput("p3_volunteer_12",
          label = "Volunteered in last 12 Months:",
@@
 
-selectInput("volunteer_frequency",
+selectInput("p3_volunteer_frequency",
          label = "Volunteer Frequency:",
@@
 
-selectInput("personal_activism",
+selectInput("p3_personal_activism",
          label = "Personal Activism:",
@@
 
-selectInput("family_activism",
+selectInput("p3_family_activism",
          label = "Family Activism:",
@@
 
-selectInput("religious_member",
+selectInput("p3_religious_member",
          label = "Church Membership:",
@@
 
-selectInput("sport_member",
+selectInput("p3_sport_member",
          label = "Sport or Recreational Membership:",
@@
 
-selectInput("art_member",
+selectInput("p3_art_member",
          label = "Art, Music, or Educational Membership:",
@@
 
-selectInput("labor_member",
+selectInput("p3_labor_member",
          label = "Labor Union Membership:",
@@
 
-selectInput("political_member",
+selectInput("p3_political_member",
          label = "Political Party Membership:",
@@
 
-selectInput("environmental_member",
+selectInput("p3_environmental_member",
          label = "Enviornmental Org. Membership:",
@@
 
-selectInput("professional_member",
+selectInput("p3_professional_member",
          label = "Professional Membership:",
@@
 
-selectInput("humanitarian_member",
+selectInput("p3_humanitarian_member",
          label = "Humanitarian Org. Membership:",
@@
 
-selectInput("consumer_member",
+selectInput("p3_consumer_member",
          label = "Consumer Org. Membership:",
@@
 
-selectInput("other_member",
+selectInput("p3_other_member",
          label = "Other Org. Membership:",
@@
 
-selectInput("national_news",
+selectInput("p3_national_news",
          label = "Follow national news:",
@@
 
-selectInput("international_news",
+selectInput("p3_international_news",
          label = "Follow international news:",
@@
 
-selectInput("news_medium",
+selectInput("p3_news_medium",
          label = "Medium to follow news:",
@@
 
-selectInput("follow_gov",
+selectInput("p3_follow_gov",
          label = "Follow government & public affairs:",
@@
 
-selectInput("travel_developing",
+selectInput("p3_travel_developing",
          label = "Travel to developing country:",
@@
 
-selectInput("polical_pref",
+selectInput("p3_polical_pref",
          label = "Polical views from liberal to conservative:",
@@
 
-selectInput("institution_trust",
+selectInput("p3_institution_trust",
          label = "Political institution trust from none to complete:",
@@
 
-selectInput("others_charitable",
+selectInput("p3_others_charitable",
          label = "People should be more charitable:",
@@
 
-selectInput("worship_attendance",
+selectInput("p3_worship_attendance",
          label = "Worship service attendance:",
@@
 
-selectInput("religion_importance",
+selectInput("p3_religion_importance",
          label = "Importance of religion:",
@@
 
-selectInput("religion",
+selectInput("p3_religion",
          label = "Religion:",
@@
 
-selectInput("gender",
+selectInput("p3_gender",
          label = "Gender:",
@@
 
-selectInput("marital_status",
+selectInput("p3_marital_status",
          label = "Marital Status:",
@@
 
-selectInput("education",
+selectInput("p3_education",
          label = "Education:",
@@
 
-selectInput("income",
+selectInput("p3_income",
          label = "Income:",
@@
 
-selectInput("race",
+selectInput("p3_race",
          label = "Race(s):",
@@
 
-selectInput("age",
+selectInput("p3_age",
          label = "Age:",

### 2020-08-14 analysis/05_market_simulator.Rmd
small changes

@@
 
-beta <- as.data.frame(matrix(rep(0), nrow = 38))
-
-beta$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
-
-# Persona Reactive Element
-p <- reactive({
-  #Persona 1
-    beta$p1_value <- 0
-    beta$p1_value[beta$levels == 'Persona 1'] <- 1
-    beta$p1_value[beta$levels %in% input$p1_charity_importance] <- 1
-    beta$p1_value[beta$levels %in% input$p1_trust_in_charity] <- 1
-    beta$p1_value[beta$levels %in% input$p1_donation_frequency] <- 1
-    beta$p1_value[beta$levels %in% input$p1_donation_amount] <- 1
-    beta$p1_value[beta$levels %in% input$p1_volunteer_12] <- 1
-    beta$p1_value[beta$levels %in% input$p1_volunteer_frequency] <- 1
-    beta$p1_value[beta$levels %in% input$p1_personal_activism] <- 1
-    beta$p1_value[beta$levels %in% input$p1_family_activism] <- 1
-    beta$p1_value[beta$levels %in% input$p1_religious_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_sport_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_art_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_labor_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_political_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_environmental_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_professional_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_humanitarian_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_consumer_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_other_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_national_news] <- 1
-    beta$p1_value[beta$levels %in% input$p1_international_news] <- 1
-    beta$p1_value[beta$levels %in% input$p1_news_medium] <- 1
-    beta$p1_value[beta$levels %in% input$p1_follow_gov] <- 1
-    beta$p1_value[beta$levels %in% input$p1_travel_developing] <- 1
-    beta$p1_value[beta$levels %in% input$p1_political_pref] <- 1
-    beta$p1_value[beta$levels %in% input$p1_institution_trust] <- 1
-    beta$p1_value[beta$levels %in% input$p1_others_charitable] <- 1
-    beta$p1_value[beta$levels %in% input$p1_worship_attendence] <- 1
-    beta$p1_value[beta$levels %in% input$p1_religion_importance] <- 1
-    beta$p1_value[beta$levels %in% input$p1_religion] <- 1
-    beta$p1_value[beta$levels %in% input$p1_gender] <- 1
-    beta$p1_value[beta$levels %in% input$p1_marital_status] <- 1
-    beta$p1_value[beta$levels %in% input$p1_education] <- 1
-    beta$p1_value[beta$levels %in% input$p1_income] <- 1
-    beta$p1_value[beta$levels %in% input$p1_race] <- 1
-    beta$p1_value[beta$levels %in% input$p1_age] <- 1
-  #Persona 2
-    beta$p2_value <- 0
-    beta$p2_value[beta$levels == 'Persona 2'] <- 1
-    beta$p2_value[beta$levels %in% input$p2_charity_importance] <- 1
-    beta$p2_value[beta$levels %in% input$p2_trust_in_charity] <- 1
-    beta$p2_value[beta$levels %in% input$p2_donation_frequency] <- 1
-    beta$p2_value[beta$levels %in% input$p2_donation_amount] <- 1
-    beta$p2_value[beta$levels %in% input$p2_volunteer_12] <- 1
-    beta$p2_value[beta$levels %in% input$p2_volunteer_frequency] <- 1
-    beta$p2_value[beta$levels %in% input$p2_personal_activism] <- 1
-    beta$p2_value[beta$levels %in% input$p2_family_activism] <- 1
-    beta$p2_value[beta$levels %in% input$p2_religious_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_sport_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_art_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_labor_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_political_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_environmental_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_professional_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_humanitarian_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_consumer_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_other_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_national_news] <- 1
-    beta$p2_value[beta$levels %in% input$p2_international_news] <- 1
-    beta$p2_value[beta$levels %in% input$p2_news_medium] <- 1
-    beta$p2_value[beta$levels %in% input$p2_follow_gov] <- 1
-    beta$p2_value[beta$levels %in% input$p2_travel_developing] <- 1
-    beta$p2_value[beta$levels %in% input$p2_political_pref] <- 1
-    beta$p2_value[beta$levels %in% input$p2_institution_trust] <- 1
-    beta$p2_value[beta$levels %in% input$p2_others_charitable] <- 1
-    beta$p2_value[beta$levels %in% input$p2_worship_attendence] <- 1
-    beta$p2_value[beta$levels %in% input$p2_religion_importance] <- 1
-    beta$p2_value[beta$levels %in% input$p2_religion] <- 1
-    beta$p2_value[beta$levels %in% input$p2_gender] <- 1
-    beta$p2_value[beta$levels %in% input$p2_marital_status] <- 1
-    beta$p2_value[beta$levels %in% input$p2_education] <- 1
-    beta$p2_value[beta$levels %in% input$p2_income] <- 1
-    beta$p2_value[beta$levels %in% input$p2_race] <- 1
-    beta$p2_value[beta$levels %in% input$p2_age] <- 1
-  #Persona 3
-    beta$p3_value <- 0
-    beta$p3_value[beta$levels == 'Persona 3'] <- 1
-    beta$p3_value[beta$levels %in% input$p3_charity_importance] <- 1
-    beta$p3_value[beta$levels %in% input$p3_trust_in_charity] <- 1
-    beta$p3_value[beta$levels %in% input$p3_donation_frequency] <- 1
-    beta$p3_value[beta$levels %in% input$p3_donation_amount] <- 1
-    beta$p3_value[beta$levels %in% input$p3_volunteer_12] <- 1
-    beta$p3_value[beta$levels %in% input$p3_volunteer_frequency] <- 1
-    beta$p3_value[beta$levels %in% input$p3_personal_activism] <- 1
-    beta$p3_value[beta$levels %in% input$p3_family_activism] <- 1
-    beta$p3_value[beta$levels %in% input$p3_religious_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_sport_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_art_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_labor_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_political_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_environmental_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_professional_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_humanitarian_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_consumer_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_other_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_national_news] <- 1
-    beta$p3_value[beta$levels %in% input$p3_international_news] <- 1
-    beta$p3_value[beta$levels %in% input$p3_news_medium] <- 1
-    beta$p3_value[beta$levels %in% input$p3_follow_gov] <- 1
-    beta$p3_value[beta$levels %in% input$p3_travel_developing] <- 1
-    beta$p3_value[beta$levels %in% input$p3_political_pref] <- 1
-    beta$p3_value[beta$levels %in% input$p3_institution_trust] <- 1
-    beta$p3_value[beta$levels %in% input$p3_others_charitable] <- 1
-    beta$p3_value[beta$levels %in% input$p3_worship_attendence] <- 1
-    beta$p3_value[beta$levels %in% input$p3_religion_importance] <- 1
-    beta$p3_value[beta$levels %in% input$p3_religion] <- 1
-    beta$p3_value[beta$levels %in% input$p3_gender] <- 1
-    beta$p3_value[beta$levels %in% input$p3_marital_status] <- 1
-    beta$p3_value[beta$levels %in% input$p3_education] <- 1
-    beta$p3_value[beta$levels %in% input$p3_income] <- 1
-    beta$p3_value[beta$levels %in% input$p3_race] <- 1
-    beta$p3_value[beta$levels %in% input$p3_age] <- 1
-    beta
-
-})
+# beta <- as.data.frame(matrix(rep(0), nrow = 38))
+# 
+# beta$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
+# 
+#
+#
+# # Persona Reactive Element
+#
+#
+# p <- reactive({
+#   #Persona 1
+#     beta$p1_value <- 0
+#     beta$p1_value[beta$levels == 'Persona 1'] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_charity_importance] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_trust_in_charity] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_donation_frequency] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_donation_amount] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_volunteer_12] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_volunteer_frequency] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_personal_activism] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_family_activism] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_religious_member] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_sport_member] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_art_member] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_labor_member] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_political_member] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_environmental_member] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_professional_member] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_humanitarian_member] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_consumer_member] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_other_member] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_national_news] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_international_news] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_news_medium] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_follow_gov] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_travel_developing] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_political_pref] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_institution_trust] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_others_charitable] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_worship_attendence] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_religion_importance] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_religion] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_gender] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_marital_status] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_education] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_income] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_race] <- 1
+#     beta$p1_value[beta$levels %in% input$p1_age] <- 1
+#   #Persona 2
+#     beta$p2_value <- 0
+#     beta$p2_value[beta$levels == 'Persona 2'] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_charity_importance] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_trust_in_charity] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_donation_frequency] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_donation_amount] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_volunteer_12] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_volunteer_frequency] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_personal_activism] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_family_activism] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_religious_member] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_sport_member] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_art_member] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_labor_member] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_political_member] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_environmental_member] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_professional_member] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_humanitarian_member] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_consumer_member] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_other_member] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_national_news] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_international_news] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_news_medium] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_follow_gov] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_travel_developing] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_political_pref] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_institution_trust] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_others_charitable] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_worship_attendence] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_religion_importance] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_religion] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_gender] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_marital_status] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_education] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_income] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_race] <- 1
+#     beta$p2_value[beta$levels %in% input$p2_age] <- 1
+#   #Persona 3
+#     beta$p3_value <- 0
+#     beta$p3_value[beta$levels == 'Persona 3'] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_charity_importance] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_trust_in_charity] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_donation_frequency] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_donation_amount] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_volunteer_12] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_volunteer_frequency] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_personal_activism] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_family_activism] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_religious_member] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_sport_member] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_art_member] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_labor_member] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_political_member] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_environmental_member] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_professional_member] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_humanitarian_member] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_consumer_member] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_other_member] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_national_news] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_international_news] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_news_medium] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_follow_gov] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_travel_developing] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_political_pref] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_institution_trust] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_others_charitable] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_worship_attendence] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_religion_importance] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_religion] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_gender] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_marital_status] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_education] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_income] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_race] <- 1
+#     beta$p3_value[beta$levels %in% input$p3_age] <- 1
+#     beta
+#     
+# })
 ```

### 2020-08-14 analysis/05_market_simulator.Rmd
persona Reactive element needs to be rearranged to match market simulator workbook

--- 2020-08-13 analysis/05_market_simulator.Rmd
@@
 
-beta <- as.data.frame(matrix(rep(0), nrow = 38))
-
-beta$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
+beta_persona <- as.data.frame(matrix(rep(0), nrow = 38))
+
+beta_persona$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
 
 # Persona Reactive Element
+
 p <- reactive({
@@
 
-    persona1 = p_beta1 # Choose the persona
+    persona1 = p_beta1 # add step to matrix multiply the persona reactive element to the persona data and the public_political beta table.
 

### 2020-08-14 analysis/05_market_simulator.Rmd
fixed beta in persona reactive table and the data-width

@@
   #Persona 1
-    beta$p1_value <- 0
-    beta$p1_value[beta$levels == 'Persona 1'] <- 1
-    beta$p1_value[beta$levels %in% input$p1_charity_importance] <- 1
-    beta$p1_value[beta$levels %in% input$p1_trust_in_charity] <- 1
-    beta$p1_value[beta$levels %in% input$p1_donation_frequency] <- 1
-    beta$p1_value[beta$levels %in% input$p1_donation_amount] <- 1
-    beta$p1_value[beta$levels %in% input$p1_volunteer_12] <- 1
-    beta$p1_value[beta$levels %in% input$p1_volunteer_frequency] <- 1
-    beta$p1_value[beta$levels %in% input$p1_personal_activism] <- 1
-    beta$p1_value[beta$levels %in% input$p1_family_activism] <- 1
-    beta$p1_value[beta$levels %in% input$p1_religious_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_sport_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_art_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_labor_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_political_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_environmental_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_professional_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_humanitarian_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_consumer_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_other_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_national_news] <- 1
-    beta$p1_value[beta$levels %in% input$p1_international_news] <- 1
-    beta$p1_value[beta$levels %in% input$p1_news_medium] <- 1
-    beta$p1_value[beta$levels %in% input$p1_follow_gov] <- 1
-    beta$p1_value[beta$levels %in% input$p1_travel_developing] <- 1
-    beta$p1_value[beta$levels %in% input$p1_political_pref] <- 1
-    beta$p1_value[beta$levels %in% input$p1_institution_trust] <- 1
-    beta$p1_value[beta$levels %in% input$p1_others_charitable] <- 1
-    beta$p1_value[beta$levels %in% input$p1_worship_attendence] <- 1
-    beta$p1_value[beta$levels %in% input$p1_religion_importance] <- 1
-    beta$p1_value[beta$levels %in% input$p1_religion] <- 1
-    beta$p1_value[beta$levels %in% input$p1_gender] <- 1
-    beta$p1_value[beta$levels %in% input$p1_marital_status] <- 1
-    beta$p1_value[beta$levels %in% input$p1_education] <- 1
-    beta$p1_value[beta$levels %in% input$p1_income] <- 1
-    beta$p1_value[beta$levels %in% input$p1_race] <- 1
-    beta$p1_value[beta$levels %in% input$p1_age] <- 1
+    beta_persona$p1_value <- 0
+    beta_persona$p1_value[beta$levels == 'Persona 1'] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_charity_importance] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_trust_in_charity] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_donation_frequency] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_donation_amount] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_volunteer_12] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_volunteer_frequency] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_personal_activism] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_family_activism] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_religious_member] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_sport_member] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_art_member] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_labor_member] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_political_member] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_environmental_member] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_professional_member] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_humanitarian_member] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_consumer_member] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_other_member] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_national_news] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_international_news] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_news_medium] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_follow_gov] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_travel_developing] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_political_pref] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_institution_trust] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_others_charitable] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_worship_attendence] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_religion_importance] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_religion] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_gender] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_marital_status] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_education] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_income] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_race] <- 1
+    beta_persona$p1_value[beta$levels %in% input$p1_age] <- 1
   #Persona 2
-    beta$p2_value <- 0
-    beta$p2_value[beta$levels == 'Persona 2'] <- 1
-    beta$p2_value[beta$levels %in% input$p2_charity_importance] <- 1
-    beta$p2_value[beta$levels %in% input$p2_trust_in_charity] <- 1
-    beta$p2_value[beta$levels %in% input$p2_donation_frequency] <- 1
-    beta$p2_value[beta$levels %in% input$p2_donation_amount] <- 1
-    beta$p2_value[beta$levels %in% input$p2_volunteer_12] <- 1
-    beta$p2_value[beta$levels %in% input$p2_volunteer_frequency] <- 1
-    beta$p2_value[beta$levels %in% input$p2_personal_activism] <- 1
-    beta$p2_value[beta$levels %in% input$p2_family_activism] <- 1
-    beta$p2_value[beta$levels %in% input$p2_religious_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_sport_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_art_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_labor_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_political_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_environmental_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_professional_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_humanitarian_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_consumer_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_other_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_national_news] <- 1
-    beta$p2_value[beta$levels %in% input$p2_international_news] <- 1
-    beta$p2_value[beta$levels %in% input$p2_news_medium] <- 1
-    beta$p2_value[beta$levels %in% input$p2_follow_gov] <- 1
-    beta$p2_value[beta$levels %in% input$p2_travel_developing] <- 1
-    beta$p2_value[beta$levels %in% input$p2_political_pref] <- 1
-    beta$p2_value[beta$levels %in% input$p2_institution_trust] <- 1
-    beta$p2_value[beta$levels %in% input$p2_others_charitable] <- 1
-    beta$p2_value[beta$levels %in% input$p2_worship_attendence] <- 1
-    beta$p2_value[beta$levels %in% input$p2_religion_importance] <- 1
-    beta$p2_value[beta$levels %in% input$p2_religion] <- 1
-    beta$p2_value[beta$levels %in% input$p2_gender] <- 1
-    beta$p2_value[beta$levels %in% input$p2_marital_status] <- 1
-    beta$p2_value[beta$levels %in% input$p2_education] <- 1
-    beta$p2_value[beta$levels %in% input$p2_income] <- 1
-    beta$p2_value[beta$levels %in% input$p2_race] <- 1
-    beta$p2_value[beta$levels %in% input$p2_age] <- 1
+    beta_persona$p2_value <- 0
+    beta_persona$p2_value[beta$levels == 'Persona 2'] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_charity_importance] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_trust_in_charity] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_donation_frequency] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_donation_amount] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_volunteer_12] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_volunteer_frequency] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_personal_activism] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_family_activism] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_religious_member] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_sport_member] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_art_member] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_labor_member] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_political_member] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_environmental_member] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_professional_member] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_humanitarian_member] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_consumer_member] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_other_member] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_national_news] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_international_news] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_news_medium] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_follow_gov] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_travel_developing] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_political_pref] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_institution_trust] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_others_charitable] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_worship_attendence] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_religion_importance] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_religion] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_gender] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_marital_status] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_education] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_income] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_race] <- 1
+    beta_persona$p2_value[beta$levels %in% input$p2_age] <- 1
   #Persona 3
-    beta$p3_value <- 0
-    beta$p3_value[beta$levels == 'Persona 3'] <- 1
-    beta$p3_value[beta$levels %in% input$p3_charity_importance] <- 1
-    beta$p3_value[beta$levels %in% input$p3_trust_in_charity] <- 1
-    beta$p3_value[beta$levels %in% input$p3_donation_frequency] <- 1
-    beta$p3_value[beta$levels %in% input$p3_donation_amount] <- 1
-    beta$p3_value[beta$levels %in% input$p3_volunteer_12] <- 1
-    beta$p3_value[beta$levels %in% input$p3_volunteer_frequency] <- 1
-    beta$p3_value[beta$levels %in% input$p3_personal_activism] <- 1
-    beta$p3_value[beta$levels %in% input$p3_family_activism] <- 1
-    beta$p3_value[beta$levels %in% input$p3_religious_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_sport_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_art_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_labor_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_political_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_environmental_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_professional_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_humanitarian_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_consumer_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_other_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_national_news] <- 1
-    beta$p3_value[beta$levels %in% input$p3_international_news] <- 1
-    beta$p3_value[beta$levels %in% input$p3_news_medium] <- 1
-    beta$p3_value[beta$levels %in% input$p3_follow_gov] <- 1
-    beta$p3_value[beta$levels %in% input$p3_travel_developing] <- 1
-    beta$p3_value[beta$levels %in% input$p3_political_pref] <- 1
-    beta$p3_value[beta$levels %in% input$p3_institution_trust] <- 1
-    beta$p3_value[beta$levels %in% input$p3_others_charitable] <- 1
-    beta$p3_value[beta$levels %in% input$p3_worship_attendence] <- 1
-    beta$p3_value[beta$levels %in% input$p3_religion_importance] <- 1
-    beta$p3_value[beta$levels %in% input$p3_religion] <- 1
-    beta$p3_value[beta$levels %in% input$p3_gender] <- 1
-    beta$p3_value[beta$levels %in% input$p3_marital_status] <- 1
-    beta$p3_value[beta$levels %in% input$p3_education] <- 1
-    beta$p3_value[beta$levels %in% input$p3_income] <- 1
-    beta$p3_value[beta$levels %in% input$p3_race] <- 1
-    beta$p3_value[beta$levels %in% input$p3_age] <- 1
-    beta
+    beta_persona$p3_value <- 0
+    beta_persona$p3_value[beta$levels == 'Persona 3'] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_charity_importance] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_trust_in_charity] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_donation_frequency] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_donation_amount] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_volunteer_12] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_volunteer_frequency] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_personal_activism] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_family_activism] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_religious_member] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_sport_member] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_art_member] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_labor_member] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_political_member] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_environmental_member] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_professional_member] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_humanitarian_member] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_consumer_member] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_other_member] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_national_news] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_international_news] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_news_medium] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_follow_gov] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_travel_developing] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_political_pref] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_institution_trust] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_others_charitable] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_worship_attendence] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_religion_importance] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_religion] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_gender] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_marital_status] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_education] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_income] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_race] <- 1
+    beta_persona$p3_value[beta$levels %in% input$p3_age] <- 1
+    beta_persona
 
@@
 
-Market Share Per Persona {data-height=600}
+Market Share Per Persona
 --------------------------------------

### 2020-08-14 analysis/05_market_simulator.Rmd
some more beta_persona changes

--- 2020-08-14 analysis/05_market_simulator.Rmd
@@
   #Persona 1
-    beta$p1_value <- 0
-    beta$p1_value[beta$levels == 'Persona 1'] <- 1
-    beta$p1_value[beta$levels %in% input$p1_charity_importance] <- 1
-    beta$p1_value[beta$levels %in% input$p1_trust_in_charity] <- 1
-    beta$p1_value[beta$levels %in% input$p1_donation_frequency] <- 1
-    beta$p1_value[beta$levels %in% input$p1_donation_amount] <- 1
-    beta$p1_value[beta$levels %in% input$p1_volunteer_12] <- 1
-    beta$p1_value[beta$levels %in% input$p1_volunteer_frequency] <- 1
-    beta$p1_value[beta$levels %in% input$p1_personal_activism] <- 1
-    beta$p1_value[beta$levels %in% input$p1_family_activism] <- 1
-    beta$p1_value[beta$levels %in% input$p1_religious_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_sport_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_art_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_labor_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_political_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_environmental_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_professional_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_humanitarian_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_consumer_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_other_member] <- 1
-    beta$p1_value[beta$levels %in% input$p1_national_news] <- 1
-    beta$p1_value[beta$levels %in% input$p1_international_news] <- 1
-    beta$p1_value[beta$levels %in% input$p1_news_medium] <- 1
-    beta$p1_value[beta$levels %in% input$p1_follow_gov] <- 1
-    beta$p1_value[beta$levels %in% input$p1_travel_developing] <- 1
-    beta$p1_value[beta$levels %in% input$p1_political_pref] <- 1
-    beta$p1_value[beta$levels %in% input$p1_institution_trust] <- 1
-    beta$p1_value[beta$levels %in% input$p1_others_charitable] <- 1
-    beta$p1_value[beta$levels %in% input$p1_worship_attendence] <- 1
-    beta$p1_value[beta$levels %in% input$p1_religion_importance] <- 1
-    beta$p1_value[beta$levels %in% input$p1_religion] <- 1
-    beta$p1_value[beta$levels %in% input$p1_gender] <- 1
-    beta$p1_value[beta$levels %in% input$p1_marital_status] <- 1
-    beta$p1_value[beta$levels %in% input$p1_education] <- 1
-    beta$p1_value[beta$levels %in% input$p1_income] <- 1
-    beta$p1_value[beta$levels %in% input$p1_race] <- 1
-    beta$p1_value[beta$levels %in% input$p1_age] <- 1
+    beta_persona$p1_value <- 0
+    beta_persona$p1_value[beta_persona$levels == 'Persona 1'] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_charity_importance] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_trust_in_charity] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_frequency] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_amount] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_12] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_frequency] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_personal_activism] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_family_activism] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_religious_member] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_sport_member] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_art_member] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_labor_member] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_member] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_environmental_member] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_professional_member] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_humanitarian_member] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_consumer_member] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_other_member] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_international_news] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_news_medium] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_follow_gov] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_travel_developing] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_institution_trust] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_others_charitable] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_worship_attendence] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion_importance] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_gender] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_marital_status] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_education] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_income] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_race] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_age] <- 1
   #Persona 2
-    beta$p2_value <- 0
-    beta$p2_value[beta$levels == 'Persona 2'] <- 1
-    beta$p2_value[beta$levels %in% input$p2_charity_importance] <- 1
-    beta$p2_value[beta$levels %in% input$p2_trust_in_charity] <- 1
-    beta$p2_value[beta$levels %in% input$p2_donation_frequency] <- 1
-    beta$p2_value[beta$levels %in% input$p2_donation_amount] <- 1
-    beta$p2_value[beta$levels %in% input$p2_volunteer_12] <- 1
-    beta$p2_value[beta$levels %in% input$p2_volunteer_frequency] <- 1
-    beta$p2_value[beta$levels %in% input$p2_personal_activism] <- 1
-    beta$p2_value[beta$levels %in% input$p2_family_activism] <- 1
-    beta$p2_value[beta$levels %in% input$p2_religious_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_sport_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_art_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_labor_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_political_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_environmental_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_professional_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_humanitarian_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_consumer_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_other_member] <- 1
-    beta$p2_value[beta$levels %in% input$p2_national_news] <- 1
-    beta$p2_value[beta$levels %in% input$p2_international_news] <- 1
-    beta$p2_value[beta$levels %in% input$p2_news_medium] <- 1
-    beta$p2_value[beta$levels %in% input$p2_follow_gov] <- 1
-    beta$p2_value[beta$levels %in% input$p2_travel_developing] <- 1
-    beta$p2_value[beta$levels %in% input$p2_political_pref] <- 1
-    beta$p2_value[beta$levels %in% input$p2_institution_trust] <- 1
-    beta$p2_value[beta$levels %in% input$p2_others_charitable] <- 1
-    beta$p2_value[beta$levels %in% input$p2_worship_attendence] <- 1
-    beta$p2_value[beta$levels %in% input$p2_religion_importance] <- 1
-    beta$p2_value[beta$levels %in% input$p2_religion] <- 1
-    beta$p2_value[beta$levels %in% input$p2_gender] <- 1
-    beta$p2_value[beta$levels %in% input$p2_marital_status] <- 1
-    beta$p2_value[beta$levels %in% input$p2_education] <- 1
-    beta$p2_value[beta$levels %in% input$p2_income] <- 1
-    beta$p2_value[beta$levels %in% input$p2_race] <- 1
-    beta$p2_value[beta$levels %in% input$p2_age] <- 1
+    beta_persona$p2_value <- 0
+    beta_persona$p2_value[beta_persona$levels == 'Persona 2'] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_charity_importance] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_trust_in_charity] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_donation_frequency] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_donation_amount] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_volunteer_12] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_volunteer_frequency] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_personal_activism] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_family_activism] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_religious_member] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_sport_member] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_art_member] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_labor_member] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_political_member] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_environmental_member] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_professional_member] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_humanitarian_member] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_consumer_member] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_other_member] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_national_news] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_international_news] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_news_medium] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_follow_gov] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_travel_developing] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_political_pref] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_institution_trust] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_others_charitable] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_worship_attendence] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion_importance] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_gender] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_marital_status] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_education] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_income] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_race] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_age] <- 1
   #Persona 3
-    beta$p3_value <- 0
-    beta$p3_value[beta$levels == 'Persona 3'] <- 1
-    beta$p3_value[beta$levels %in% input$p3_charity_importance] <- 1
-    beta$p3_value[beta$levels %in% input$p3_trust_in_charity] <- 1
-    beta$p3_value[beta$levels %in% input$p3_donation_frequency] <- 1
-    beta$p3_value[beta$levels %in% input$p3_donation_amount] <- 1
-    beta$p3_value[beta$levels %in% input$p3_volunteer_12] <- 1
-    beta$p3_value[beta$levels %in% input$p3_volunteer_frequency] <- 1
-    beta$p3_value[beta$levels %in% input$p3_personal_activism] <- 1
-    beta$p3_value[beta$levels %in% input$p3_family_activism] <- 1
-    beta$p3_value[beta$levels %in% input$p3_religious_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_sport_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_art_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_labor_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_political_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_environmental_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_professional_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_humanitarian_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_consumer_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_other_member] <- 1
-    beta$p3_value[beta$levels %in% input$p3_national_news] <- 1
-    beta$p3_value[beta$levels %in% input$p3_international_news] <- 1
-    beta$p3_value[beta$levels %in% input$p3_news_medium] <- 1
-    beta$p3_value[beta$levels %in% input$p3_follow_gov] <- 1
-    beta$p3_value[beta$levels %in% input$p3_travel_developing] <- 1
-    beta$p3_value[beta$levels %in% input$p3_political_pref] <- 1
-    beta$p3_value[beta$levels %in% input$p3_institution_trust] <- 1
-    beta$p3_value[beta$levels %in% input$p3_others_charitable] <- 1
-    beta$p3_value[beta$levels %in% input$p3_worship_attendence] <- 1
-    beta$p3_value[beta$levels %in% input$p3_religion_importance] <- 1
-    beta$p3_value[beta$levels %in% input$p3_religion] <- 1
-    beta$p3_value[beta$levels %in% input$p3_gender] <- 1
-    beta$p3_value[beta$levels %in% input$p3_marital_status] <- 1
-    beta$p3_value[beta$levels %in% input$p3_education] <- 1
-    beta$p3_value[beta$levels %in% input$p3_income] <- 1
-    beta$p3_value[beta$levels %in% input$p3_race] <- 1
-    beta$p3_value[beta$levels %in% input$p3_age] <- 1
-    beta
+    beta_persona$p3_value <- 0
+    beta_persona$p3_value[beta_persona$levels == 'Persona 3'] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_charity_importance] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_trust_in_charity] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_frequency] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_amount] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_12] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_frequency] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_personal_activism] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_family_activism] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_religious_member] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_sport_member] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_art_member] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_labor_member] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_member] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_environmental_member] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_professional_member] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_humanitarian_member] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_consumer_member] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_other_member] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_national_news] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_international_news] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_news_medium] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_follow_gov] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_travel_developing] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_pref] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_institution_trust] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_others_charitable] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_worship_attendence] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion_importance] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_gender] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_marital_status] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_education] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_income] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_race] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_age] <- 1
+    beta_persona
 

### 2020-08-17 analysis/05_market_simulator.Rmd
working on persona matrix multiplication

@@
 
-# # Beta's we want for the plotly
-# public_political_social_charity_demo <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
-#   group_by(i) %>% 
-#   summarize(theta_mean = mean(Theta))
-# 
-# # RenderPlotly code for testing
-# 
-# renderPlotly({
-#   choice <- df()
-  # ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  # gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
-  # 
-  # data <- c(ai_exp_util, gp_exp_util)
-  # df <- as.data.frame(matrix(data, 8, 1))
-  # 
-  # df[,2] <- c("Amnesty International", "Green Peace")
-  # df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
-  # colnames(df) <- c("Value", "Organization", "Type")
-
-# test <- as.data.frame(matrix(runif(10), 8, 1))
-# 
-# test[,2] <- c("Amnesty International", "Green Peace", "Oxfam", "Red Cross")
-# test[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
-# colnames(test) <- c("Value", "Organization", "Type")
-# 
-# colors <- c("#ffc30b", "#3fad48", "#006633", "#660000")
-# 
-#   ggplotly(
-#     ggplot(test, aes(y = Value, x = Organization, fill = Organization)) +
-#            geom_col() +
-#            labs(x="") +
-#            scale_fill_manual(values = colors) +
-#            theme(legend.position = "none") +
-#            facet_wrap(~Type)
-#   )
-# })
+beta_persona_test <- as.data.frame(matrix(rep(0), nrow = 38))
+
+beta_persona_test$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
+
+# Persona Reactive Element
+
+beta_persona_test$p1 <- 1
+
+beta_persona_test$p2 <- 2
+
+beta_persona_test$p3 <- 3
+
+persona1 <- persona_data[,2]
+
+p_beta1 <- as.matrix(public_political_social_charity_demo) %*%
+
+  as.matrix(persona1) %*% beta_persona_test[,3]
 
@@
 renderPlotly({
-  choice = df()
-
-    persona1 = p_beta1 # add step to matrix multiply the persona reactive element to the persona data and the public_political beta table.
-
-  ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
-  gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
-  ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
-  rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+  org_choice = df()
+  per_choice = p()
+
+    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% exp(as.matrix(persona1) %*% t(per_choice[,3]))
+#add step to matrix multiply the persona reactive element to the persona data and the public_political beta table.
+
+  ai_exp_util1 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta1)),2)
+  gp_exp_util1 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta1)),2)
+  ox_exp_util1 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta1)),2)
+  rc_exp_util1 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta1)),2)
 
@@
 
-    persona2 = p_beta2 # Choose the persona
-
-  ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
-  gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
-  ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
-  rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+    # p_beta2 <- as.matrix(public_political_social_charity_demo) %*% (t(per_choice[,4]) %*% as.matrix(persona2))
+
+  ai_exp_util2 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta2)),2)
+  gp_exp_util2 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta2)),2)
+  ox_exp_util2 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta2)),2)
+  rc_exp_util2 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta2)),2)
 
@@
 
-      persona3 = p_beta3 # Choose the persona
-
-  ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
-  gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
-  ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
-  rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+    # p_beta3 =  as.matrix(public_political_social_charity_demo) %*% (t(per_choice[,5]) %*% as.matrix(persona3))
+
+  ai_exp_util3 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta3)),2)
+  gp_exp_util3 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta3)),2)
+  ox_exp_util3 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta3)),2)
+  rc_exp_util3 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta3)),2)
 
@@
 ```{r plot ai plot}
-renderPlotly({
-  choice = df()
-
-    persona1 = p_beta1 # Choose the persona
-
-  ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
-  gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
-  ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
-  rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
-
-  ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-
-    persona2 = p_beta2 # Choose the persona
-
-  ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
-  gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
-  ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
-  rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
-
-  ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-  gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-  ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-  rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-
-      persona3 = p_beta3 # Choose the persona
-
-  ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
-  gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
-  ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
-  rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
-
-  ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-  gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-  ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-  rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-
-  data <- c(ai_exp_util1, ai_rate1, 
-            ai_exp_util2, ai_rate2,
-            ai_exp_util3, ai_rate3)
-
-  df <- as.data.frame(matrix(data, 6, 1))
-
-  df[,2] <- c("Amnesty International")
-  df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
-  df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
-  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
-
-  ggplotly(df %>% filter(Type == "Market Share") %>% 
-             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
-             geom_bar(position = "dodge", stat = "identity") +
-             labs(x="") + 
-             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
-             theme(legend.position = "none")
-    )
-})
+# renderPlotly({
+#   choice = df()
+#   
+#     persona1 = p_beta1 # Choose the persona
+#   
+#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
+#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
+#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
+#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+#   
+#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   
+#     persona2 = p_beta2 # Choose the persona
+#   
+#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
+#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
+#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
+#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+#   
+#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   
+#       persona3 = p_beta3 # Choose the persona
+#   
+#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
+#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
+#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
+#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+#   
+#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   
+#   data <- c(ai_exp_util1, ai_rate1, 
+#             ai_exp_util2, ai_rate2,
+#             ai_exp_util3, ai_rate3)
+#   
+#   
+#   df <- as.data.frame(matrix(data, 6, 1))
+#   
+#   df[,2] <- c("Amnesty International")
+#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
+#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
+#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+#   
+#   ggplotly(df %>% filter(Type == "Market Share") %>% 
+#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+#              geom_bar(position = "dodge", stat = "identity") +
+#              labs(x="") + 
+#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+#              theme(legend.position = "none")
+#     )
+# })
 ```
@@
 # Some kind of Org Id that could select the organization you are looking at? Not sure how to make it change the label in the graph
-selectInput("org_id",
-            label = "Select Organization:",
-            choices = c("Amnesity International",
-                        "Green Peace",
-                        "Oxfam",
-                        "Red Cross"))
 
@@
 ```{r plot gp plot}
-renderPlotly({
-  choice = df()
-
-    persona1 = p_beta1 # Choose the persona
-
-  ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
-  gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
-  ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
-  rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
-
-  ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-
-    persona2 = p_beta2 # Choose the persona
-
-  ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
-  gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
-  ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
-  rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
-
-  ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-  gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-  ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-  rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-
-      persona3 = p_beta3 # Choose the persona
-
-  ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
-  gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
-  ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
-  rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
-
-  ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-  gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-  ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-  rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-
-  data <- c(gp_exp_util1, gp_rate1, 
-            gp_exp_util2, gp_rate2,
-            gp_exp_util3, gp_rate3)
-
-  df <- as.data.frame(matrix(data, 6, 1))
-
-  df[,2] <- c("Greenpeace")
-  df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
-  df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
-  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
-
-  ggplotly(df %>% filter(Type == "Market Share") %>% 
-             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
-             geom_bar(position = "dodge", stat = "identity") +
-             labs(x="") + 
-             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
-             theme(legend.position = "none")
-    )
-})
+# renderPlotly({
+#   choice = df()
+#   
+#     persona1 = p_beta1 # Choose the persona
+#   
+#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
+#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
+#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
+#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+#   
+#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   
+#     persona2 = p_beta2 # Choose the persona
+#   
+#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
+#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
+#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
+#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+#   
+#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   
+#       persona3 = p_beta3 # Choose the persona
+#   
+#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
+#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
+#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
+#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+#   
+#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   
+#   data <- c(gp_exp_util1, gp_rate1, 
+#             gp_exp_util2, gp_rate2,
+#             gp_exp_util3, gp_rate3)
+#   
+#   
+#   df <- as.data.frame(matrix(data, 6, 1))
+#   
+#   df[,2] <- c("Greenpeace")
+#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
+#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
+#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+#   
+#   ggplotly(df %>% filter(Type == "Market Share") %>% 
+#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+#              geom_bar(position = "dodge", stat = "identity") +
+#              labs(x="") + 
+#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+#              theme(legend.position = "none")
+#     )
+# })
 ```
@@
 ```{r plot ox plot}
-renderPlotly({
-  choice = df()
-
-    persona1 = p_beta1 # Choose the persona
-
-  ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
-  gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
-  ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
-  rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
-
-  ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-
-    persona2 = p_beta2 # Choose the persona
-
-  ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
-  gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
-  ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
-  rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
-
-  ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-  gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-  ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-  rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-
-      persona3 = p_beta3 # Choose the persona
-
-  ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
-  gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
-  ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
-  rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
-
-  ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-  gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-  ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-  rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-
-  data <- c(ox_exp_util1, ox_rate1, 
-            ox_exp_util2, ox_rate2,
-            ox_exp_util3, ox_rate3)
-
-  df <- as.data.frame(matrix(data, 6, 1))
-
-  df[,2] <- c("Oxfam")
-  df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
-  df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
-  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
-
-  ggplotly(df %>% filter(Type == "Market Share") %>% 
-             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
-             geom_bar(position = "dodge", stat = "identity") +
-             labs(x="") + 
-             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
-             theme(legend.position = "none")
-    )
-})
+# renderPlotly({
+#   choice = df()
+#   
+#     persona1 = p_beta1 # Choose the persona
+#   
+#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
+#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
+#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
+#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+#   
+#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   
+#     persona2 = p_beta2 # Choose the persona
+#   
+#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
+#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
+#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
+#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+#   
+#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   
+#       persona3 = p_beta3 # Choose the persona
+#   
+#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
+#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
+#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
+#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+#   
+#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   
+#   data <- c(ox_exp_util1, ox_rate1, 
+#             ox_exp_util2, ox_rate2,
+#             ox_exp_util3, ox_rate3)
+#   
+#   
+#   df <- as.data.frame(matrix(data, 6, 1))
+#   
+#   df[,2] <- c("Oxfam")
+#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
+#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
+#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+#   
+#   ggplotly(df %>% filter(Type == "Market Share") %>% 
+#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+#              geom_bar(position = "dodge", stat = "identity") +
+#              labs(x="") + 
+#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+#              theme(legend.position = "none")
+#     )
+# })
 ```
@@
 ```{r plot rc plot}
-renderPlotly({
-  choice = df()
-
-    persona1 = p_beta1 # Choose the persona
-
-  ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
-  gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
-  ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
-  rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
-
-  ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-
-    persona2 = p_beta2 # Choose the persona
-
-  ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
-  gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
-  ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
-  rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
-
-  ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-  gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-  ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-  rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-
-      persona3 = p_beta3 # Choose the persona
-
-  ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
-  gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
-  ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
-  rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
-
-  ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-  gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-  ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-  rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-
-  data <- c(rc_exp_util1, rc_rate1, 
-            rc_exp_util2, rc_rate2,
-            rc_exp_util3, rc_rate3)
-
-  df <- as.data.frame(matrix(data, 6, 1))
-
-  df[,2] <- c("Red Cross")
-  df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
-  df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
-  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
-
-  ggplotly(df %>% filter(Type == "Market Share") %>% 
-             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
-             geom_bar(position = "dodge", stat = "identity") +
-             labs(x="") + 
-             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
-             theme(legend.position = "none")
-    )
-})
+# renderPlotly({
+#   choice = df()
+#   
+#     persona1 = p_beta1 # Choose the persona
+#   
+#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
+#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
+#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
+#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+#   
+#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   
+#     persona2 = p_beta2 # Choose the persona
+#   
+#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
+#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
+#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
+#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+#   
+#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   
+#       persona3 = p_beta3 # Choose the persona
+#   
+#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
+#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
+#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
+#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+#   
+#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   
+#   data <- c(rc_exp_util1, rc_rate1, 
+#             rc_exp_util2, rc_rate2,
+#             rc_exp_util3, rc_rate3)
+#   
+#   
+#   df <- as.data.frame(matrix(data, 6, 1))
+#   
+#   df[,2] <- c("Red Cross")
+#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
+#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
+#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+#   
+#   ggplotly(df %>% filter(Type == "Market Share") %>% 
+#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+#              geom_bar(position = "dodge", stat = "identity") +
+#              labs(x="") + 
+#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+#              theme(legend.position = "none")
+#     )
+# })
 ```
@@
                      "Email newsletters",
-                     "News app"))
+                     "News app"),
+         multiple = TRUE)
 

### 2020-08-17 analysis/05_market_simulator.Rmd
Reordered Personas to match Market Simulator Excel document

--- 2020-08-14 analysis/05_market_simulator.Rmd
@@
 
-beta_persona$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
+beta_persona$levels = c("Persona 1", "Persona 2", "Persona 3", "Follow National News", "Follow International News", "News Medium", "Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Charity Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
 
@@
     beta_persona$p1_value[beta_persona$levels == 'Persona 1'] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_international_news] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_news_medium] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_follow_gov] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_travel_developing] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_institution_trust] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_others_charitable] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_worship_attendence] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion_importance] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion] <- 1
     beta_persona$p1_value[beta_persona$levels %in% input$p1_charity_importance] <- 1
@@
     beta_persona$p1_value[beta_persona$levels %in% input$p1_other_member] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_international_news] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_news_medium] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_follow_gov] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_travel_developing] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_institution_trust] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_others_charitable] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_worship_attendence] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion_importance] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion] <- 1
     beta_persona$p1_value[beta_persona$levels %in% input$p1_gender] <- 1
@@
     beta_persona$p2_value[beta_persona$levels == 'Persona 2'] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_national_news] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_international_news] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_news_medium] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_follow_gov] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_travel_developing] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_political_pref] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_institution_trust] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_others_charitable] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_worship_attendence] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion_importance] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion] <- 1
     beta_persona$p2_value[beta_persona$levels %in% input$p2_charity_importance] <- 1
@@
     beta_persona$p2_value[beta_persona$levels %in% input$p2_other_member] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_national_news] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_international_news] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_news_medium] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_follow_gov] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_travel_developing] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_political_pref] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_institution_trust] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_others_charitable] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_worship_attendence] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion_importance] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion] <- 1
     beta_persona$p2_value[beta_persona$levels %in% input$p2_gender] <- 1
@@
     beta_persona$p3_value[beta_persona$levels == 'Persona 3'] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_national_news] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_international_news] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_news_medium] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_follow_gov] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_travel_developing] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_pref] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_institution_trust] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_others_charitable] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_worship_attendence] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion_importance] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion] <- 1
     beta_persona$p3_value[beta_persona$levels %in% input$p3_charity_importance] <- 1
@@
     beta_persona$p3_value[beta_persona$levels %in% input$p3_other_member] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_national_news] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_international_news] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_news_medium] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_follow_gov] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_travel_developing] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_pref] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_institution_trust] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_others_charitable] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_worship_attendence] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion_importance] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion] <- 1
     beta_persona$p3_value[beta_persona$levels %in% input$p3_gender] <- 1
@@
 
-selectInput("p1_charity_importance",
-          label = "Charity Importance:",
-          choices = c("0", '1', '2', '3','4','5','6','7'))
-
-selectInput("p1_trust_in_charity",
-            label = "Charity Trust:",
-            choices = c("0", '1', '2', '3','4','5','6','7'))
-
-selectInput("p1_donation_frequency",
-         label = "Donation Frequency:",
-         choices = c('Once a week',
-                     'Once a Month',
-                     'Once every three months',
-                     'Once every six months',
-                     'Once a year',
-                     'Once every few years',
-                     'Never'))
-
-selectInput("p1_donation_amount",
-         label = "Donation Amount:",
-         choices = c("$1-$49",
-                     '$50-$99',
-                     '$100-$499',
-                     '$500-$999',
-                     '$1,000-$4,999',
-                     '$5,000-$9,999',
-                     '$10,000+'))
-
-selectInput("p1_volunteer_12",
-         label = "Volunteered in last 12 Months:",
-         choices = c("Yes", "No"))
-
-selectInput("p1_volunteer_frequency",
-         label = "Volunteer Frequency:",
-         choices = c('Once a week',
-                     'Once a Month',
-                     'Once every three months',
-                     'Once every six months',
-                     'Once a year',
-                     'Once every few years',
-                     'Never'))
-
-selectInput("p1_personal_activism",
-         label = "Personal Activism:",
-         choices = c('Extremely involved',
-                     'Very involved',
-                     'Moderately involved',
-                     'Slightly involved',
-                     'Never involved'))
-
-selectInput("p1_family_activism",
-         label = "Family Activism:",
-         choices = c('Extremely involved',
-                     'Very involved',
-                     'Moderately involved',
-                     'Slightly involved',
-                     'Never involved'))
-
-selectInput("p1_religious_member",
-         label = "Church Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p1_sport_member",
-         label = "Sport or Recreational Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p1_art_member",
-         label = "Art, Music, or Educational Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p1_labor_member",
-         label = "Labor Union Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p1_political_member",
-         label = "Political Party Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p1_environmental_member",
-         label = "Enviornmental Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p1_professional_member",
-         label = "Professional Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p1_humanitarian_member",
-         label = "Humanitarian Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p1_consumer_member",
-         label = "Consumer Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p1_other_member",
-         label = "Other Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
 selectInput("p1_national_news",
@@
                      'Other'))
+
+selectInput("p1_charity_importance",
+          label = "Charity Importance:",
+          choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("p1_trust_in_charity",
+            label = "Charity Trust:",
+            choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("p1_donation_frequency",
+         label = "Donation Frequency:",
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+selectInput("p1_donation_amount",
+         label = "Donation Amount:",
+         choices = c("$1-$49",
+                     '$50-$99',
+                     '$100-$499',
+                     '$500-$999',
+                     '$1,000-$4,999',
+                     '$5,000-$9,999',
+                     '$10,000+'))
+
+selectInput("p1_volunteer_12",
+         label = "Volunteered in last 12 Months:",
+         choices = c("Yes", "No"))
+
+selectInput("p1_volunteer_frequency",
+         label = "Volunteer Frequency:",
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+selectInput("p1_personal_activism",
+         label = "Personal Activism:",
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+selectInput("p1_family_activism",
+         label = "Family Activism:",
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+selectInput("p1_religious_member",
+         label = "Church Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_sport_member",
+         label = "Sport or Recreational Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_art_member",
+         label = "Art, Music, or Educational Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_labor_member",
+         label = "Labor Union Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_political_member",
+         label = "Political Party Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_environmental_member",
+         label = "Enviornmental Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_professional_member",
+         label = "Professional Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_humanitarian_member",
+         label = "Humanitarian Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_consumer_member",
+         label = "Consumer Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p1_other_member",
+         label = "Other Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
 
@@
 
-selectInput("p2_charity_importance",
-          label = "Charity Importance:",
-          choices = c("0", '1', '2', '3','4','5','6','7'))
-
-selectInput("p2_trust_in_charity",
-            label = "Charity Trust:",
-            choices = c("0", '1', '2', '3','4','5','6','7'))
-
-selectInput("p2_donation_frequency",
-         label = "Donation Frequency:",
-         choices = c('Once a week',
-                     'Once a Month',
-                     'Once every three months',
-                     'Once every six months',
-                     'Once a year',
-                     'Once every few years',
-                     'Never'))
-
-selectInput("p2_donation_amount",
-         label = "Donation Amount:",
-         choices = c("$1-$49",
-                     '$50-$99',
-                     '$100-$499',
-                     '$500-$999',
-                     '$1,000-$4,999',
-                     '$5,000-$9,999',
-                     '$10,000+'))
-
-selectInput("p2_volunteer_12",
-         label = "Volunteered in last 12 Months:",
-         choices = c("Yes", "No"))
-
-selectInput("p2_volunteer_frequency",
-         label = "Volunteer Frequency:",
-         choices = c('Once a week',
-                     'Once a Month',
-                     'Once every three months',
-                     'Once every six months',
-                     'Once a year',
-                     'Once every few years',
-                     'Never'))
-
-selectInput("p2_personal_activism",
-         label = "Personal Activism:",
-         choices = c('Extremely involved',
-                     'Very involved',
-                     'Moderately involved',
-                     'Slightly involved',
-                     'Never involved'))
-
-selectInput("p2_family_activism",
-         label = "Family Activism:",
-         choices = c('Extremely involved',
-                     'Very involved',
-                     'Moderately involved',
-                     'Slightly involved',
-                     'Never involved'))
-
-selectInput("p2_religious_member",
-         label = "Church Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p2_sport_member",
-         label = "Sport or Recreational Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p2_art_member",
-         label = "Art, Music, or Educational Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p2_labor_member",
-         label = "Labor Union Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p2_political_member",
-         label = "Political Party Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p2_environmental_member",
-         label = "Enviornmental Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p2_professional_member",
-         label = "Professional Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p2_humanitarian_member",
-         label = "Humanitarian Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p2_consumer_member",
-         label = "Consumer Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p2_other_member",
-         label = "Other Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
 selectInput("p2_national_news",
@@
                      'Other'))
+
+selectInput("p2_charity_importance",
+          label = "Charity Importance:",
+          choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("p2_trust_in_charity",
+            label = "Charity Trust:",
+            choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("p2_donation_frequency",
+         label = "Donation Frequency:",
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+selectInput("p2_donation_amount",
+         label = "Donation Amount:",
+         choices = c("$1-$49",
+                     '$50-$99',
+                     '$100-$499',
+                     '$500-$999',
+                     '$1,000-$4,999',
+                     '$5,000-$9,999',
+                     '$10,000+'))
+
+selectInput("p2_volunteer_12",
+         label = "Volunteered in last 12 Months:",
+         choices = c("Yes", "No"))
+
+selectInput("p2_volunteer_frequency",
+         label = "Volunteer Frequency:",
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+selectInput("p2_personal_activism",
+         label = "Personal Activism:",
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+selectInput("p2_family_activism",
+         label = "Family Activism:",
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+selectInput("p2_religious_member",
+         label = "Church Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p2_sport_member",
+         label = "Sport or Recreational Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p2_art_member",
+         label = "Art, Music, or Educational Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p2_labor_member",
+         label = "Labor Union Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p2_political_member",
+         label = "Political Party Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p2_environmental_member",
+         label = "Enviornmental Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p2_professional_member",
+         label = "Professional Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p2_humanitarian_member",
+         label = "Humanitarian Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p2_consumer_member",
+         label = "Consumer Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p2_other_member",
+         label = "Other Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
 
@@
 
-selectInput("p3_charity_importance",
-          label = "Charity Importance:",
-          choices = c("0", '1', '2', '3','4','5','6','7'))
-
-selectInput("p3_trust_in_charity",
-            label = "Charity Trust:",
-            choices = c("0", '1', '2', '3','4','5','6','7'))
-
-selectInput("p3_donation_frequency",
-         label = "Donation Frequency:",
-         choices = c('Once a week',
-                     'Once a Month',
-                     'Once every three months',
-                     'Once every six months',
-                     'Once a year',
-                     'Once every few years',
-                     'Never'))
-
-selectInput("p3_donation_amount",
-         label = "Donation Amount:",
-         choices = c("$1-$49",
-                     '$50-$99',
-                     '$100-$499',
-                     '$500-$999',
-                     '$1,000-$4,999',
-                     '$5,000-$9,999',
-                     '$10,000+'))
-
-selectInput("p3_volunteer_12",
-         label = "Volunteered in last 12 Months:",
-         choices = c("Yes", "No"))
-
-selectInput("p3_volunteer_frequency",
-         label = "Volunteer Frequency:",
-         choices = c('Once a week',
-                     'Once a Month',
-                     'Once every three months',
-                     'Once every six months',
-                     'Once a year',
-                     'Once every few years',
-                     'Never'))
-
-selectInput("p3_personal_activism",
-         label = "Personal Activism:",
-         choices = c('Extremely involved',
-                     'Very involved',
-                     'Moderately involved',
-                     'Slightly involved',
-                     'Never involved'))
-
-selectInput("p3_family_activism",
-         label = "Family Activism:",
-         choices = c('Extremely involved',
-                     'Very involved',
-                     'Moderately involved',
-                     'Slightly involved',
-                     'Never involved'))
-
-selectInput("p3_religious_member",
-         label = "Church Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p3_sport_member",
-         label = "Sport or Recreational Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p3_art_member",
-         label = "Art, Music, or Educational Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p3_labor_member",
-         label = "Labor Union Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p3_political_member",
-         label = "Political Party Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p3_environmental_member",
-         label = "Enviornmental Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p3_professional_member",
-         label = "Professional Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p3_humanitarian_member",
-         label = "Humanitarian Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p3_consumer_member",
-         label = "Consumer Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-selectInput("p3_other_member",
-         label = "Other Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
 selectInput("p3_national_news",
@@
                      'Other'))
+
+selectInput("p3_charity_importance",
+          label = "Charity Importance:",
+          choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("p3_trust_in_charity",
+            label = "Charity Trust:",
+            choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("p3_donation_frequency",
+         label = "Donation Frequency:",
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+selectInput("p3_donation_amount",
+         label = "Donation Amount:",
+         choices = c("$1-$49",
+                     '$50-$99',
+                     '$100-$499',
+                     '$500-$999',
+                     '$1,000-$4,999',
+                     '$5,000-$9,999',
+                     '$10,000+'))
+
+selectInput("p3_volunteer_12",
+         label = "Volunteered in last 12 Months:",
+         choices = c("Yes", "No"))
+
+selectInput("p3_volunteer_frequency",
+         label = "Volunteer Frequency:",
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+selectInput("p3_personal_activism",
+         label = "Personal Activism:",
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+selectInput("p3_family_activism",
+         label = "Family Activism:",
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+selectInput("p3_religious_member",
+         label = "Church Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p3_sport_member",
+         label = "Sport or Recreational Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p3_art_member",
+         label = "Art, Music, or Educational Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p3_labor_member",
+         label = "Labor Union Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p3_political_member",
+         label = "Political Party Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p3_environmental_member",
+         label = "Enviornmental Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p3_professional_member",
+         label = "Professional Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p3_humanitarian_member",
+         label = "Humanitarian Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p3_consumer_member",
+         label = "Consumer Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+selectInput("p3_other_member",
+         label = "Other Org. Membership:",
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
 

### 2020-08-17 analysis/05_market_simulator.Rmd
Persona input

--- 2020-08-17 analysis/05_market_simulator.Rmd
@@
 
-####################################################################
-
-beta_persona <- as.data.frame(matrix(rep(0), nrow = 38))
-
-beta_persona$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
-
-# Persona Reactive Element
+# persona beta levels -----
+
+beta_persona <- as.data.frame(matrix(rep(0), nrow = 61))
+
+beta_persona$levels = c("Intercept",
+                        "Follow National News", 
+                        "Follow International News",
+                        "News Medium - TV",
+                        "News Medium - Print",
+                        "News Medium - Online",
+                        "News Medium - Social Media",
+                        "News Medium - Radio",
+                        "News Medium - Email",
+                        "News Medium - Newsapp",
+                        "Follow Government or Public Affairs", 
+                        "No Travel to Developing Countries", 
+                        "Political Preference", 
+                        "Trust in Political Institutions",
+                        "Others Should be Charitable",
+                        "Worship Service Attendence",
+                        "Religious Importance",
+                        "Religion - Protestant",
+                        "Religion - Christian Orthodox",
+                        "Religion - Jewish",
+                        "Religion - Muslim",
+                        "Religion - Sikh",
+                        "Religion - Hindu",
+                        "Religion - Buddhist",
+                        "Religion - Atheist",
+                        "Religion - Other",
+                        "Chartiy Trust Importance",
+                        "Trust in Charity", 
+                        "Donation Frequency", 
+                        "Donation Amount",
+                        "Volunteer 12 Months",
+                        "Volunteer Frequence",
+                        "Personal Activism",
+                        "Family Activism",
+                        "Religious Membership", 
+                        "Sport or Recreational Membership", 
+                        "Art, Music, or Educational Membership",
+                        "Labor Union Membership",
+                        "Political Party Membership",
+                        "Environmental Organization Membership",
+                        "Professional Association", 
+                        "Humanitarian or Charity Membership",
+                        "Consumer Organization Membership",
+                        "Other Organization Membership",
+                        "Gender - Female",
+                        "Gender - Transgender",
+                        "Gender - Prefer not to say",
+                        "Gender - Other",
+                        "Marital Status - Widowed",
+                        "Marital Status - Divorced",
+                        "Marital Status - Separated",
+                        "Marital Status - Never Married",
+                        "Education", 
+                        "Income", 
+                        "Race - White", 
+                        "Race - Black", 
+                        "Race - American Indian", 
+                        "Race - Asian", 
+                        "Race - Pacific Islander", 
+                        "Race - Other", 
+                        "Age")
+
+# Persona Reactive Element --------
 
 p <- reactive({
+
   #Persona 1
     beta_persona$p1_value <- 0
-    beta_persona$p1_value[beta_persona$levels == 'Persona 1'] <- 1
+
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_international_news] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_news_medium] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_follow_gov] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_travel_developing] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_institution_trust] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_others_charitable] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_worship_attendence] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion_importance] <- 1
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion] <- 1
     beta_persona$p1_value[beta_persona$levels %in% input$p1_charity_importance] <- 1
@@
     beta_persona$p1_value[beta_persona$levels %in% input$p1_age] <- 1
+
   #Persona 2
     beta_persona$p2_value <- 0
-    beta_persona$p2_value[beta_persona$levels == 'Persona 2'] <- 1
+
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_national_news] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_international_news] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_news_medium] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_follow_gov] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_travel_developing] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_political_pref] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_institution_trust] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_others_charitable] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_worship_attendence] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion_importance] <- 1
+    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion] <- 1
     beta_persona$p2_value[beta_persona$levels %in% input$p2_charity_importance] <- 1
@@
     beta_persona$p2_value[beta_persona$levels %in% input$p2_age] <- 1
+
   #Persona 3
     beta_persona$p3_value <- 0
-    beta_persona$p3_value[beta_persona$levels == 'Persona 3'] <- 1
+
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_national_news] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_international_news] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_news_medium] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_follow_gov] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_travel_developing] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_pref] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_institution_trust] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_others_charitable] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_worship_attendence] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion_importance] <- 1
+    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion] <- 1
     beta_persona$p3_value[beta_persona$levels %in% input$p3_charity_importance] <- 1
@@
 
-beta_persona_test <- as.data.frame(matrix(rep(0), nrow = 38))
-
-beta_persona_test$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
-
-# Persona Reactive Element
-
-beta_persona_test$p1 <- 1
-
-beta_persona_test$p2 <- 2
-
-beta_persona_test$p3 <- 3
-
-persona1 <- persona_data[,2]
-
-p_beta1 <- as.matrix(public_political_social_charity_demo) %*%
-
-  as.matrix(persona1) %*% beta_persona_test[,3]
+# beta_persona_test <- as.data.frame(matrix(rep(0), nrow = 38))
+# 
+# beta_persona_test$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
+# 
+# 
+# 
+# # Persona Reactive Element
+# 
+# beta_persona_test$p1 <- 1
+# 
+# beta_persona_test$p2 <- 2
+# 
+# beta_persona_test$p3 <- 3
+#         
+# persona1 <- persona_data[,2]
+# 
+# p_beta1 <- as.matrix(public_political_social_charity_demo) %*%   
+#   
+#   as.matrix(persona1) %*% beta_persona_test[,3]
 

### 2020-08-18 analysis/05_market_simulator.Rmd
Added in persona reactive element to Global Chart

@@
 
-####################################################################################
+################### Org Reactive Element####################################
 
@@
 
-# persona beta levels -----
+################### Persona Reactive Element####################################
+
+# Persona beta levels -----
 
@@
                         "Follow International News",
-                        "News Medium - TV",
-                        "News Medium - Print",
-                        "News Medium - Online",
-                        "News Medium - Social Media",
-                        "News Medium - Radio",
-                        "News Medium - Email",
-                        "News Medium - Newsapp",
+                        "TV",
+                        "Print",
+                        "Online",
+                        "Social Media",
+                        "Radio",
+                        "Email",
+                        "Newsapp",
                         "Follow Government or Public Affairs", 
@@
                         "Religious Importance",
-                        "Religion - Protestant",
-                        "Religion - Christian Orthodox",
-                        "Religion - Jewish",
-                        "Religion - Muslim",
-                        "Religion - Sikh",
-                        "Religion - Hindu",
-                        "Religion - Buddhist",
-                        "Religion - Atheist",
-                        "Religion - Other",
+                        "Protestant",
+                        "Christian Orthodox",
+                        "Jewish",
+                        "Muslim",
+                        "Sikh",
+                        "Hindu",
+                        "Buddhist",
+                        "Atheist",
+                        "Other",
                         "Chartiy Trust Importance",
@@
                         "Other Organization Membership",
-                        "Gender - Female",
-                        "Gender - Transgender",
-                        "Gender - Prefer not to say",
-                        "Gender - Other",
-                        "Marital Status - Widowed",
-                        "Marital Status - Divorced",
-                        "Marital Status - Separated",
-                        "Marital Status - Never Married",
+                        "Female",
+                        "Transgender",
+                        "Prefer not to say",
+                        "Other",
+                        "Widowed",
+                        "Divorced",
+                        "Separated",
+                        "Never Married",
                         "Education", 
                         "Income", 
-                        "Race - White", 
-                        "Race - Black", 
-                        "Race - American Indian", 
-                        "Race - Asian", 
-                        "Race - Pacific Islander", 
-                        "Race - Other", 
+                        "White", 
+                        "Black", 
+                        "American Indian", 
+                        "Asian", 
+                        "Pacific Islander", 
+                        "Other", 
                         "Age")
 
-# Persona Reactive Element --------
+# p reactive element ----
 
@@
 
+    beta_persona$p1_value[beta_persona$levels == 'Persona 1'] <- 1
     beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news] <- 1
@@
 
+    beta_persona$p2_value[beta_persona$levels == 'Persona 2'] <- 1
     beta_persona$p2_value[beta_persona$levels %in% input$p2_national_news] <- 1
@@
     beta_persona$p3_value <- 0
+
+    beta_persona$p3_value[beta_persona$levels == 'Persona 3'] <- 1
 
@@
 
-```{r sidebar inputs commented}
-
-# # selectInput("model_choice",
-# #             label = "Select Model:",
-# #             choices = c("public_political_social_charity_demo"))
-# 
-# 
-# selectInput("charity_importance",
-#           label = "Charity Importance:",
-#           choices = c("0", '1', '2', '3','4','5','6','7'))
-# 
-# 
-# selectInput("trust_in_charity",
-#             label = "Charity Trust:",
-#             choices = c("0", '1', '2', '3','4','5','6','7'))
-# 
-# 
-# 
-# selectInput("donation_frequency",
-#          label = "Donation Frequency:",
-#          choices = c('Once a week',
-#                      'Once a Month',
-#                      'Once every three months',
-#                      'Once every six months',
-#                      'Once a year',
-#                      'Once every few years',
-#                      'Never'))
-# 
-# 
-# 
-# selectInput("donation_amount",
-#          label = "Donation Amount:",
-#          choices = c("$1-$49",
-#                      '$50-$99',
-#                      '$100-$499',
-#                      '$500-$999',
-#                      '$1,000-$4,999',
-#                      '$5,000-$9,999',
-#                      '$10,000+'))
-# 
-# 
-# selectInput("volunteer_12",
-#          label = "Volunteered in last 12 Months:",
-#          choices = c("Yes", "No"))
-# 
-# 
-# 
-# selectInput("volunteer_frequency",
-#          label = "Volunteer Frequency:",
-#          choices = c('Once a week',
-#                      'Once a Month',
-#                      'Once every three months',
-#                      'Once every six months',
-#                      'Once a year',
-#                      'Once every few years',
-#                      'Never'))
-# 
-# 
-# selectInput("personal_activism",
-#          label = "Personal Activism:",
-#          choices = c('Extremely involved',
-#                      'Very involved',
-#                      'Moderately involved',
-#                      'Slightly involved',
-#                      'Never involved'))
-# 
-# 
-# selectInput("family_activism",
-#          label = "Family Activism:",
-#          choices = c('Extremely involved',
-#                      'Very involved',
-#                      'Moderately involved',
-#                      'Slightly involved',
-#                      'Never involved'))
-# 
-# 
-# selectInput("religious_member",
-#          label = "Church Membership:",
-#          choices = c('Active Member',
-#                      'Inactive Member',
-#                      "Don't belong"))
-# 
-# 
-# selectInput("sport_member",
-#          label = "Sport or Recreational Membership:",
-#          choices = c('Active Member',
-#                      'Inactive Member',
-#                      "Don't belong"))
-# 
-# 
-# selectInput("art_member",
-#          label = "Art, Music, or Educational Membership:",
-#          choices = c('Active Member',
-#                      'Inactive Member',
-#                      "Don't belong"))
-# 
-# 
-# selectInput("labor_member",
-#          label = "Labor Union Membership:",
-#          choices = c('Active Member',
-#                      'Inactive Member',
-#                      "Don't belong"))
-# 
-# 
-# selectInput("political_member",
-#          label = "Political Party Membership:",
-#          choices = c('Active Member',
-#                      'Inactive Member',
-#                      "Don't belong"))
-# 
-# 
-# selectInput("environmental_member",
-#          label = "Enviornmental Org. Membership:",
-#          choices = c('Active Member',
-#                      'Inactive Member',
-#                      "Don't belong"))
-# 
-# 
-# selectInput("professional_member",
-#          label = "Professional Membership:",
-#          choices = c('Active Member',
-#                      'Inactive Member',
-#                      "Don't belong"))
-# 
-# 
-# selectInput("humanitarian_member",
-#          label = "Humanitarian Org. Membership:",
-#          choices = c('Active Member',
-#                      'Inactive Member',
-#                      "Don't belong"))
-# 
-# 
-# selectInput("consumer_member",
-#          label = "Consumer Org. Membership:",
-#          choices = c('Active Member',
-#                      'Inactive Member',
-#                      "Don't belong"))
-# 
-# 
-# selectInput("religious_member",
-#          label = "Church Membership:",
-#          choices = c('Active Member',
-#                      'Inactive Member',
-#                      "Don't belong"))
-# 
-# 
-# 
-# 
-# selectInput("other_member",
-#          label = "Other Org. Membership:",
-#          choices = c('Active Member',
-#                      'Inactive Member',
-#                      "Don't belong"))
-# 
-# 
-# 
-# selectInput("national_news",
-#          label = "Follow national news:",
-#          choices = c('Multiple times a day',
-#                      'Every day',
-#                      "Once a week",
-#                      "Hardly ever",
-#                      "Never"))
-# 
-# 
-# selectInput("international_news",
-#          label = "Follow international news:",
-#          choices = c('Always',
-#                      "Sometimes",
-#                      "Never"))
-# 
-# 
-# selectInput("news_medium",
-#          label = "Medium to follow news:",
-#          choices = c('TV',
-#                      'Print',
-#                      "Online",
-#                      "Social Media",
-#                      "Radio",
-#                      "Email newsletters",
-#                      "News app"))
-# 
-# 
-# 
-# selectInput("international_news",
-#          label = "Follow international news:",
-#          choices = c('Multiple times a day',
-#                      'Every day',
-#                      "Once a week",
-#                      "Hardly ever",
-#                      "Never"))
-# 
-# selectInput("follow_gov",
-#          label = "Follow government & public affairs:",
-#          choices = c('Most of the time',
-#                      'Some of the time',
-#                      "Only now and then",
-#                      "Hardly at all"))
-# 
-# 
-# selectInput("travel_developing",
-#          label = "Travel to developing country:",
-#          choices = c('Yes', 'No'))
-# 
-# 
-# 
-# selectInput("polical_pref",
-#          label = "Polical views from liberal to conservative:",
-#          choices = c("0", '1', '2', '3','4','5','6','7'))
-# 
-# 
-# selectInput("institution_trust",
-#          label = "Political institution trust from none to complete:",
-#          choices = c("0", '1', '2', '3','4','5','6','7'))
-# 
-# 
-# 
-# selectInput("others_charitable",
-#          label = "People should be more charitable:",
-#          choices = c("0", '1', '2', '3','4','5','6','7'))
-# 
-# 
-# selectInput("worship_attendance",
-#          label = "Worship service attendance:",
-#          choices = c('Multiple times a week',
-#                      'Once a week',
-#                      "Once a month",
-#                      "Once a year",
-#                      "Never"))
-# 
-# 
-# selectInput("religion_importance",
-#          label = "Importance of religion:",
-#          choices = c('Extremely important',
-#                      'Very important',
-#                      'Moderately important',
-#                      'Slightly important',
-#                      'Not at all important'))
-# 
-# 
-# selectInput("religion",
-#          label = "Religion:",
-#          choices = c('Catholic',
-#                      'Protestant',
-#                      'Christian Orthodox',
-#                      'Jewish',
-#                      'Muslim',
-#                      'Sikh',
-#                      'Hindu',
-#                      'Buddhist',
-#                      'Atheist',
-#                      'Other'))
-# 
-# 
-# selectInput("gender",
-#          label = "Gender:",
-#          choices = c("Male",
-#                      "Female",
-#                      "Transgender",
-#                      "Prefer not to say",
-#                      "Other"))
-# 
-# 
-# selectInput("marital_status",
-#          label = "Marital Status:",
-#          choices = c("Married",
-#                      "Widowed",
-#                      "Divorced",
-#                      "Separated",
-#                      "Never married"))
-# 
-# 
-# selectInput("education",
-#          label = "Education:",
-#          choices = c("Less than high school",
-#                      "High school",
-#                      "Some college",
-#                      "2 year degree",
-#                      "4 year degree",
-#                      "Graduate degree",
-#                      "Doctorate"))
-# 
-# selectInput("income",
-#          label = "Income:",
-#          choices = c('Less than $10,000',
-#                      '$10,000 to $19,999',
-#                      '$20,000 to $29,999',
-#                      '$30,000 to $39,999',
-#                      '$40,000 to $49,999',
-#                      '$50,000 to $59,999',
-#                      '$60,000 to $69,999',
-#                      '$70,000 to $79,999',
-#                      '$80,000 to $89,999',
-#                      '$90,000 to $99,999',
-#                      '$100,000 to $149,999',
-#                      '$150,000 to $199,999',
-#                      '$200,000 to $299,999',
-#                      '$300,000 or more'))
-# 
-# 
-# 
-# selectInput("race",
-#          label = "Race(s):",
-#          choices = c('White',
-#                      'Black or African American',
-#                      'American Indian or Alaska Native',
-#                      'Asian',
-#                      'Native Hawaiian or Pacific Islander',
-#                      'Other'),
-#          multiple = TRUE)
-# 
-# 
-# selectInput("education",
-#          label = "Education:",
-#          choices = c("Less than high school",
-#                      "High school",
-#                      "Some college",
-#                      "2 year degree",
-#                      "4 year degree",
-#                      "Graduate degree",
-#                      "Doctorate"))
-# 
-# 
-# selectInput("age",
-#          label = "Age:",
-#          choices = c('Under 18',
-#                      '18 - 24',
-#                      '25 - 34',
-#                      '35 - 44',
-#                      '45 - 54',
-#                      '55 - 64',
-#                      '65 - 74',
-#                      '75 - 84',
-#                      '85 or older'))
-
-```
-
 ```{r persona betas}
@@
 
-    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% exp(as.matrix(persona1) %*% t(per_choice[,3]))
+    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
 #add step to matrix multiply the persona reactive element to the persona data and the public_political beta table.
@@
 
-    # p_beta2 <- as.matrix(public_political_social_charity_demo) %*% (t(per_choice[,4]) %*% as.matrix(persona2))
+    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
 
@@
 
-    # p_beta3 =  as.matrix(public_political_social_charity_demo) %*% (t(per_choice[,5]) %*% as.matrix(persona3))
+    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
 
@@
          multiple = TRUE)
+
+selectInput("p1_follow_gov",
+         label = "Follow government & public affairs:",
+         choices = c('Most of the time',
+                     'Some of the time',
+                     "Only now and then",
+                     "Hardly at all"))
+
+selectInput("p1_travel_developing",
+         label = "Travel to developing country:",
+         choices = c('Yes', 'No'))
+
+selectInput("p1_political_pref",
+         label = "Political views from liberal to conservative:",
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("p1_institution_trust",
+         label = "Political institution trust from none to complete:",
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("p1_others_charitable",
+         label = "People should be more charitable:",
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+selectInput("p1_worship_attendance",
+         label = "Worship service attendance:",
+         choices = c('Multiple times a week',
+                     'Once a week',
+                     "Once a month",
+                     "Once a year",
+                     "Never"))
+
+selectInput("p1_religion_importance",
+         label = "Importance of religion:",
+         choices = c('Extremely important',
+                     'Very important',
+                     'Moderately important',
+                     'Slightly important',
+                     'Not at all important'))
+
+selectInput("p1_religion",
+         label = "Religion:",
+         choices = c('Catholic',
+                     'Protestant',
+                     'Christian Orthodox',
+                     'Jewish',
+                     'Muslim',
+                     'Sikh',
+                     'Hindu',
+                     'Buddhist',
+                     'Atheist',
+                     'Other'))
+
+selectInput("p1_national_news",
+         label = "Follow national news:",
+         choices = c('Multiple times a day',
+                     'Every day',
+                     "Once a week",
+                     "Hardly ever",
+                     "Never"))
+
+selectInput("p1_international_news",
+         label = "Follow international news:",
+         choices = c('Always',
+                     "Sometimes",
+                     "Never"))
+
+selectInput("p1_news_medium",
+         label = "Medium to follow news:",
+         choices = c('TV',
+                     'Print',
+                     "Online",
+                     "Social Media",
+                     "Radio",
+                     "Email newsletters",
+                     "News app"))
 

### 2020-08-18 analysis/05_market_simulator.Rmd
fixing person inputs and multi level inputs

--- 2020-08-17 analysis/05_market_simulator.Rmd
@@
     beta_persona$p1_value <- 0
+
+    beta_persona$p1_value[beta_persona$levels == 'Persona 1'] <- 1
+
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news == '0'] <- 0
+    beta_persona$p1_value[beta_persona$levels == '1'] <- 1
+    beta_persona$p1_value[beta_persona$levels == '2'] <- 2
+    beta_persona$p1_value[beta_persona$levels == '3'] <- 3
+    beta_persona$p1_value[beta_persona$levels == '4'] <- 4
+    beta_persona$p1_value[beta_persona$levels == '5'] <- 5
+    beta_persona$p1_value[beta_persona$levels == '6'] <- 6
+    beta_persona$p1_value[beta_persona$levels == '7'] <- 7
 
@@
 
+    beta_persona$p2_value[beta_persona$levels == 'Persona 2'] <- 1
+
+    beta_persona$p2_value[beta_persona$levels == '0'] <- 0
+    beta_persona$p2_value[beta_persona$levels == '1'] <- 1
+    beta_persona$p2_value[beta_persona$levels == '2'] <- 2
+    beta_persona$p2_value[beta_persona$levels == '3'] <- 3
+    beta_persona$p2_value[beta_persona$levels == '4'] <- 4
+    beta_persona$p2_value[beta_persona$levels == '5'] <- 5
+    beta_persona$p2_value[beta_persona$levels == '6'] <- 6
+    beta_persona$p2_value[beta_persona$levels == '7'] <- 7
+
     beta_persona$p2_value[beta_persona$levels %in% input$p2_national_news] <- 1
@@
 
+beta_test <- as.data.frame(matrix(rep(0), nrow = 13))
+
+beta_test$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")
+
+beta_test$ai_issue <- 0
+beta_test$ai_issue[4] <- 1
+beta_test$ai_issue[8] <- 1
+beta_test$ai_issue[9] <- 1
+
+beta_test$gp_issue <- 0
+beta_test$gp_issue[4] <- 1
+beta_test$gp_issue[5] <- 1
+beta_test$gp_issue[8] <- 1
+beta_test$gp_issue[9] <- 1
+
+beta_test$ox_issue <- 0
+beta_test$ox_issue[4] <- 1
+beta_test$ox_issue[6] <- 1
+beta_test$ox_issue[8] <- 1
+beta_test$ox_issue[9] <- 1
+
+beta_test$rc_issue <- 0
+beta_test$rc_issue[4] <- 1
+beta_test$rc_issue[7] <- 1
+beta_test$rc_issue[8] <- 1
+beta_test$rc_issue[9] <- 1
+
+  ai_exp_util1 <- round(exp(t(beta_test[, 3]) %*% as.matrix(p_beta1)),2)
+  gp_exp_util1 <- round(exp(t(beta_test[, 4]) %*% as.matrix(p_beta1)),2)
+  ox_exp_util1 <- round(exp(t(beta_test[, 5]) %*% as.matrix(p_beta1)),2)
+  rc_exp_util1 <- round(exp(t(beta_test[, 6]) %*% as.matrix(p_beta1)),2)
+
+  ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+
 # Persona 2
@@
 
+exp_util2 <- round(exp(t(beta_test[, 4]) %*% as.matrix(p_beta2)),2)
+
 # Persona 3
@@
 p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona3)
+
+exp_util3 <- round(exp(t(beta_test[, 5]) %*% as.matrix(p_beta3)),2)
 
@@
          label = "Follow national news:",
-         choices = c('Multiple times a day',
-                     'Every day',
-                     "Once a week",
-                     "Hardly ever",
-                     "Never"))
+         choices = c('Multiple times a day' = "1",
+                     'Every day' = "2",
+                     "Once a week" = "3",
+                     "Hardly ever" = "4",
+                     "Never" = "5"),
+         width = "200px")
 

### 2020-08-18 analysis/05_market_simulator.Rmd
Working through getting a sliderInput for some Persona Inputs

@@
 
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news == '0'] <- 0
-    beta_persona$p1_value[beta_persona$levels == '1'] <- 1
-    beta_persona$p1_value[beta_persona$levels == '2'] <- 2
-    beta_persona$p1_value[beta_persona$levels == '3'] <- 3
-    beta_persona$p1_value[beta_persona$levels == '4'] <- 4
-    beta_persona$p1_value[beta_persona$levels == '5'] <- 5
-    beta_persona$p1_value[beta_persona$levels == '6'] <- 6
-    beta_persona$p1_value[beta_persona$levels == '7'] <- 7
+    # beta_persona$p1_value[beta_persona$levels %in% input == '0'] <- 0
+    # beta_persona$p1_value[beta_persona$levels %in% input == '1'] <- 1
+    # beta_persona$p1_value[beta_persona$levels %in% input == '2'] <- 2
+    # beta_persona$p1_value[beta_persona$levels %in% input == '3'] <- 3
+    # beta_persona$p1_value[beta_persona$levels %in% input == '4'] <- 4
+    # beta_persona$p1_value[beta_persona$levels %in% input == '5'] <- 5
+    # beta_persona$p1_value[beta_persona$levels %in% input == '6'] <- 6
+    # beta_persona$p1_value[beta_persona$levels %in% input == '7'] <- 7
 
@@
     beta_persona$p1_value[beta_persona$levels %in% input$p1_travel_developing] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
+
+    beta_persona$p1_value[beta_persona$levels == "Political Preference"] = p1_pol_pref()
+
     beta_persona$p1_value[beta_persona$levels %in% input$p1_institution_trust] <- 1
@@
 
-    beta_persona$p2_value[beta_persona$levels == '0'] <- 0
-    beta_persona$p2_value[beta_persona$levels == '1'] <- 1
-    beta_persona$p2_value[beta_persona$levels == '2'] <- 2
-    beta_persona$p2_value[beta_persona$levels == '3'] <- 3
-    beta_persona$p2_value[beta_persona$levels == '4'] <- 4
-    beta_persona$p2_value[beta_persona$levels == '5'] <- 5
-    beta_persona$p2_value[beta_persona$levels == '6'] <- 6
-    beta_persona$p2_value[beta_persona$levels == '7'] <- 7
+    # beta_persona$p2_value[beta_persona$levels == '0'] <- 0
+    # beta_persona$p2_value[beta_persona$levels == '1'] <- 1
+    # beta_persona$p2_value[beta_persona$levels == '2'] <- 2
+    # beta_persona$p2_value[beta_persona$levels == '3'] <- 3
+    # beta_persona$p2_value[beta_persona$levels == '4'] <- 4
+    # beta_persona$p2_value[beta_persona$levels == '5'] <- 5
+    # beta_persona$p2_value[beta_persona$levels == '6'] <- 6
+    # beta_persona$p2_value[beta_persona$levels == '7'] <- 7
 
@@
     beta_persona$p3_value[beta_persona$levels %in% input$p3_political_pref] <- 1
+    # 
+    # beta_persona$p3_value[beta_persona$levels == "Political Preference"] <- input$p3_political_pref
+
     beta_persona$p3_value[beta_persona$levels %in% input$p3_institution_trust] <- 1
@@
 })
+
+# reactive slider input ----
+
+p1_pol_pref <- reactive({
+  input$p1_political_pref
+})
 ```
@@
 #### this chunk is for testing code and making sure things work before adding it into the dashboard
+
+df <- as.data.frame(matrix(rep(0), nrow = 1))
+
+df$levels = "Rating"
+
+df$p1[df$levels == "Rating"] = p1_pol_pref()
+
+p1_pol_pref <- reactive({
+  input$p1_political_pref
+})
 
@@
 
-selectInput("p1_political_pref",
+sliderInput("p1_political_pref",
        label = "Political views from liberal to conservative:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
+       min = 0,
+       max = 7,
+       value = 0)
 

### 2020-08-18 analysis/05_market_simulator.Rmd
trouble shooting to get a reactive value from sliderInput as the value for the beta_persona levels that have rating.

@@
 
+p1_politic_pref <- reactive({
+  input$p1_political_pref
+})
+
 p <- reactive({
@@
 
-    beta_persona$p1_value[beta_persona$levels == "Political Preference"] = p1_pol_pref()
+    beta_persona$p1_value[beta_persona$levels == "Political Preference"] <- p1_politic_pref()
 
@@
     beta_persona$p2_value[beta_persona$levels == 'Persona 2'] <- 1
-
-    # beta_persona$p2_value[beta_persona$levels == '0'] <- 0
-    # beta_persona$p2_value[beta_persona$levels == '1'] <- 1
-    # beta_persona$p2_value[beta_persona$levels == '2'] <- 2
-    # beta_persona$p2_value[beta_persona$levels == '3'] <- 3
-    # beta_persona$p2_value[beta_persona$levels == '4'] <- 4
-    # beta_persona$p2_value[beta_persona$levels == '5'] <- 5
-    # beta_persona$p2_value[beta_persona$levels == '6'] <- 6
-    # beta_persona$p2_value[beta_persona$levels == '7'] <- 7
 
@@
 
-p1_pol_pref <- reactive({
-  input$p1_political_pref
-})
 ```
@@
 
-df <- as.data.frame(matrix(rep(0), nrow = 1))
-
-df$levels = "Rating"
-
-df$p1[df$levels == "Rating"] = p1_pol_pref()
-
-p1_pol_pref <- reactive({
-  input$p1_political_pref
-})
+# df <- as.data.frame(matrix(rep(0), nrow = 1))
+# 
+# df$levels = "Rating"
+#                         
+#                         
+# df$p1[df$levels == "Rating"] <- input$rating_id
+# 
+# 
+# p1_pol_pref <- reactive({
+#   input$p1_political_pref
+# })
+# 
+# 
+# sliderInput("rating_id",
+#        label = "Rating",
+#        min = 0,
+#        max = 7,
+#        value = 0)
 
@@
 
-beta_test <- as.data.frame(matrix(rep(0), nrow = 13))
-
-beta_test$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")
-
-beta_test$ai_issue <- 0
-beta_test$ai_issue[4] <- 1
-beta_test$ai_issue[8] <- 1
-beta_test$ai_issue[9] <- 1
-
-beta_test$gp_issue <- 0
-beta_test$gp_issue[4] <- 1
-beta_test$gp_issue[5] <- 1
-beta_test$gp_issue[8] <- 1
-beta_test$gp_issue[9] <- 1
-
-beta_test$ox_issue <- 0
-beta_test$ox_issue[4] <- 1
-beta_test$ox_issue[6] <- 1
-beta_test$ox_issue[8] <- 1
-beta_test$ox_issue[9] <- 1
-
-beta_test$rc_issue <- 0
-beta_test$rc_issue[4] <- 1
-beta_test$rc_issue[7] <- 1
-beta_test$rc_issue[8] <- 1
-beta_test$rc_issue[9] <- 1
-
-  ai_exp_util1 <- round(exp(t(beta_test[, 3]) %*% as.matrix(p_beta1)),2)
-  gp_exp_util1 <- round(exp(t(beta_test[, 4]) %*% as.matrix(p_beta1)),2)
-  ox_exp_util1 <- round(exp(t(beta_test[, 5]) %*% as.matrix(p_beta1)),2)
-  rc_exp_util1 <- round(exp(t(beta_test[, 6]) %*% as.matrix(p_beta1)),2)
+# beta_test <- as.data.frame(matrix(rep(0), nrow = 13))
+# 
+# beta_test$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")
+# 
+# beta_test$ai_issue <- 0
+# beta_test$ai_issue[4] <- 1
+# beta_test$ai_issue[8] <- 1
+# beta_test$ai_issue[9] <- 1
+# 
+# 
+# beta_test$gp_issue <- 0
+# beta_test$gp_issue[4] <- 1
+# beta_test$gp_issue[5] <- 1
+# beta_test$gp_issue[8] <- 1
+# beta_test$gp_issue[9] <- 1
+# 
+# 
+# beta_test$ox_issue <- 0
+# beta_test$ox_issue[4] <- 1
+# beta_test$ox_issue[6] <- 1
+# beta_test$ox_issue[8] <- 1
+# beta_test$ox_issue[9] <- 1
+# 
+# beta_test$rc_issue <- 0
+# beta_test$rc_issue[4] <- 1
+# beta_test$rc_issue[7] <- 1
+# beta_test$rc_issue[8] <- 1
+# beta_test$rc_issue[9] <- 1
+# 
+# 
+# 
+#   ai_exp_util1 <- round(exp(t(beta_test[, 3]) %*% as.matrix(p_beta1)),2)
+#   gp_exp_util1 <- round(exp(t(beta_test[, 4]) %*% as.matrix(p_beta1)),2)
+#   ox_exp_util1 <- round(exp(t(beta_test[, 5]) %*% as.matrix(p_beta1)),2)
+#   rc_exp_util1 <- round(exp(t(beta_test[, 6]) %*% as.matrix(p_beta1)),2)
+# 
+#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+
+# Persona 2
+persona2 <- persona_data[,3]
+
+p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona2)
+
+# 
+# exp_util2 <- round(exp(t(beta_test[, 4]) %*% as.matrix(p_beta2)),2)
+
+# Persona 3
+persona3 <- persona_data[,4]
+
+p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona3)
+
+# 
+# exp_util3 <- round(exp(t(beta_test[, 5]) %*% as.matrix(p_beta3)),2)
+
+```
+
+<!-- Main page Chart with All Personas -->
+
+Market Share Per Persona
+--------------------------------------
+
+```{r plot all personas}
+
+renderPlotly({
+  org_choice = df()
+  per_choice = p()
+
+    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+#add step to matrix multiply the persona reactive element to the persona data and the public_political beta table.
+
+  ai_exp_util1 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta1)),2)
+  gp_exp_util1 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta1)),2)
+  ox_exp_util1 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta1)),2)
+  rc_exp_util1 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta1)),2)
 
@@
 
-# Persona 2
-persona2 <- persona_data[,3]
-
-p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona2)
-
-exp_util2 <- round(exp(t(beta_test[, 4]) %*% as.matrix(p_beta2)),2)
-
-# Persona 3
-persona3 <- persona_data[,4]
-
-p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona3)
-
-exp_util3 <- round(exp(t(beta_test[, 5]) %*% as.matrix(p_beta3)),2)
-
-```
-
-<!-- Main page Chart with All Personas -->
-
-Market Share Per Persona
---------------------------------------
-
-```{r plot all personas}
-
-renderPlotly({
-  org_choice = df()
-  per_choice = p()
-
-    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-#add step to matrix multiply the persona reactive element to the persona data and the public_political beta table.
-
-  ai_exp_util1 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta1)),2)
-  gp_exp_util1 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta1)),2)
-  ox_exp_util1 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta1)),2)
-  rc_exp_util1 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta1)),2)
-
-  ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-
     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
@@
   df <- as.data.frame(matrix(data, 24, 1))
-
-  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
-  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
-  df[,4] <- c(rep("Persona 1",8), rep("Persona 2", 8), rep("Persona 3", 8))
-  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
 
@@
 #             choices = c("public_political_social_charity_demo"))
+
+sliderInput("p1_political_pref",
+       label = "Political Preference",
+       min = 0,
+       max = 7,
+       value = 0)
 
@@
          choices = c('Yes', 'No'))
-
-sliderInput("p1_political_pref",
-       label = "Political views from liberal to conservative:",
-       min = 0,
-       max = 7,
-       value = 0)
 

### 2020-08-19 analysis/05_market_simulator.Rmd
updates

@@
 p1_politic_pref <- reactive({
-  input$p1_political_pref
+  max(input$p1_political_pref)
 })
@@
 
-    # beta_persona$p1_value[beta_persona$levels %in% input == '0'] <- 0
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
     # beta_persona$p1_value[beta_persona$levels %in% input == '1'] <- 1
@@
 
-    beta_persona$p1_value[beta_persona$levels == "Political Preference"] <- p1_politic_pref()
+    # beta_persona$p1_value[beta_persona$levels == "Political Preference"] <- 1
 
@@
 
+  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
+  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
+  df[,4] <- c(rep("Persona 1",8), rep("Persona 2", 8), rep("Persona 3", 8))
+
+  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+
   ggplotly(df %>% filter(Type == "Market Share") %>% 
@@
 
-sliderInput("p1_political_pref",
-       label = "Political Preference",
-       min = 0,
-       max = 7,
-       value = 0)
+# sliderInput("p1_political_pref",
+#        label = "Political Preference",
+#        min = 0,
+#        max = 7,
+#        value = 0)
+
+selectInput("p1_political_pref",
+         label = "Political views from liberal to conservative:",
+         choices = c("0", '1', '2', '3','4','5','6','7'))
 
@@
          label = "Follow national news:",
-         choices = c('Multiple times a day' = "1",
-                     'Every day' = "2",
-                     "Once a week" = "3",
-                     "Hardly ever" = "4",
-                     "Never" = "5"),
-         width = "200px")
+         choices = c('Multiple times a day' = 1,
+                     'Every day' = 2,
+                     "Once a week" = 3,
+                     "Hardly ever" = 4,
+                     "Never" = 5))
 
@@
 
-selectInput("p1_political_pref",
-         label = "Political views from liberal to conservative:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
+# selectInput("p1_political_pref",
+#          label = "Political views from liberal to conservative:",
+#          choices = c("0", '1', '2', '3','4','5','6','7'))
 

### 2020-08-20 analysis/05_market_simulator.Rmd
small change

@@
     beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
-    # beta_persona$p1_value[beta_persona$levels %in% input == '1'] <- 1
-    # beta_persona$p1_value[beta_persona$levels %in% input == '2'] <- 2
-    # beta_persona$p1_value[beta_persona$levels %in% input == '3'] <- 3
-    # beta_persona$p1_value[beta_persona$levels %in% input == '4'] <- 4
-    # beta_persona$p1_value[beta_persona$levels %in% input == '5'] <- 5
-    # beta_persona$p1_value[beta_persona$levels %in% input == '6'] <- 6
-    # beta_persona$p1_value[beta_persona$levels %in% input == '7'] <- 7
 

### 2020-08-20 analysis/05_market_simulator.Rmd
added org name inputs and render gauges for orgs and personas

@@
 
-  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
+  df[,2] <- c(input$ai_id, input$gp_id, input$ox_id, input$rc_id)
   df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
@@
 
-```{r plot ai plot}
-# renderPlotly({
-#   choice = df()
-#   
-#     persona1 = p_beta1 # Choose the persona
-#   
-#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
-#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
-#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
-#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
-#   
-#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   
-#     persona2 = p_beta2 # Choose the persona
-#   
-#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
-#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
-#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
-#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
-#   
-#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   
-#       persona3 = p_beta3 # Choose the persona
-#   
-#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
-#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
-#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
-#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
-#   
-#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   
-#   data <- c(ai_exp_util1, ai_rate1, 
-#             ai_exp_util2, ai_rate2,
-#             ai_exp_util3, ai_rate3)
-#   
-#   
-#   df <- as.data.frame(matrix(data, 6, 1))
-#   
-#   df[,2] <- c("Amnesty International")
-#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
-#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
-#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
-#   
-#   ggplotly(df %>% filter(Type == "Market Share") %>% 
-#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
-#              geom_bar(position = "dodge", stat = "identity") +
-#              labs(x="") + 
-#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
-#              theme(legend.position = "none")
-#     )
-# })
-```
-
-```{r valuebox ai commented}
-# renderValueBox({
-#   choice = df()
-#   
-#   persona = p_beta1 # Choose the persona
-#   
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-#   
-#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   valueBox(ai_rate,
-#            color = "#FFC30B",
-#            icon = "fa-percent")
-# })
-```
-
 ```{r ai org inputs}
@@
 # Some kind of Org Id that could select the organization you are looking at? Not sure how to make it change the label in the graph
+
+textInput("ai_id",
+          label = "Organization Name",
+          value = "Organization 1",
+          placeholder = "Enter Organiation Name",
+          width = "200px")
 
@@
                         "Human rights",
-                        "Refugee relief"))
+                        "Refugee relief"),
+            width = "200px")
 
@@
             choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"))
+                        "Engages in transparency"),
+            width = "200px")
 
@@
             choices = c("Doesn’t engage in financial accountability",
-                        "Engages in financial accountability"))
+                        "Engages in financial accountability"),
+            width = "200px")
 
@@
                         "Handful of wealthy private donors",
-                        "Government Grants"))
+                        "Government Grants"),
+            width = "200px")
 
@@
                         "Criticized by government", 
-                        "Under government crackdown"))
+                        "Under government crackdown"),
+            width = "200px")
+
 ```
@@
   choice = df()
-  persona = p_beta1 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+  per_choice = p()
+
+    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
 
@@
   choice = df()
-  persona = p_beta2 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+  per_choice = p()
+
+    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
 
@@
   choice = df()
-  persona = p_beta3 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+  per_choice = p()
+
+    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
 
@@
 
-```{r plot gp plot}
-# renderPlotly({
-#   choice = df()
-#   
-#     persona1 = p_beta1 # Choose the persona
-#   
-#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
-#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
-#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
-#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
-#   
-#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   
-#     persona2 = p_beta2 # Choose the persona
-#   
-#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
-#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
-#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
-#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
-#   
-#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   
-#       persona3 = p_beta3 # Choose the persona
-#   
-#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
-#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
-#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
-#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
-#   
-#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   
-#   data <- c(gp_exp_util1, gp_rate1, 
-#             gp_exp_util2, gp_rate2,
-#             gp_exp_util3, gp_rate3)
-#   
-#   
-#   df <- as.data.frame(matrix(data, 6, 1))
-#   
-#   df[,2] <- c("Greenpeace")
-#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
-#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
-#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
-#   
-#   ggplotly(df %>% filter(Type == "Market Share") %>% 
-#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
-#              geom_bar(position = "dodge", stat = "identity") +
-#              labs(x="") + 
-#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
-#              theme(legend.position = "none")
-#     )
-# })
-```
-
-```{r valuebox gp commented}
-# renderValueBox({
-#   choice = df()
-#   persona = p_beta1 # Choose the persona
-#   
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-#   
-#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   valueBox(gp_rate,
-#            color = "#3fad48",
-#            icon = "fa-percent")
-# })
-```
-
 ```{r gp org inputs}
+
+textInput("gp_id",
+          label = "Organization Name",
+          value = "Organization 2",
+          placeholder = "Enter Organiation Name"
+)
+
 selectInput("gp_issue", 
@@
   choice = df()
-  persona = p_beta1 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+  per_choice = p()
+
+    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+
+  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(gp_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#FFC30B"),
+        symbol = "%")
+})
+
+renderGauge({
+  choice = df()
+  per_choice = p()
+
+    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
 
@@
 })
+
+renderGauge({
+  choice = df()
+  per_choice = p()
+
+    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+
+  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(gp_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#006633"),
+        symbol = "%")
+})
 ```
@@
 
-```{r plot ox plot}
-# renderPlotly({
-#   choice = df()
-#   
-#     persona1 = p_beta1 # Choose the persona
-#   
-#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
-#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
-#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
-#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
-#   
-#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   
-#     persona2 = p_beta2 # Choose the persona
-#   
-#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
-#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
-#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
-#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
-#   
-#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   
-#       persona3 = p_beta3 # Choose the persona
-#   
-#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
-#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
-#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
-#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
-#   
-#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   
-#   data <- c(ox_exp_util1, ox_rate1, 
-#             ox_exp_util2, ox_rate2,
-#             ox_exp_util3, ox_rate3)
-#   
-#   
-#   df <- as.data.frame(matrix(data, 6, 1))
-#   
-#   df[,2] <- c("Oxfam")
-#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
-#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
-#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
-#   
-#   ggplotly(df %>% filter(Type == "Market Share") %>% 
-#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
-#              geom_bar(position = "dodge", stat = "identity") +
-#              labs(x="") + 
-#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
-#              theme(legend.position = "none")
-#     )
-# })
-```
-
-```{r valuebox ox commented}
-# renderValueBox({
-#   choice = df()
-#   
-#   persona = p_beta1 # Choose the persona
-#   
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-#   
-#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   valueBox(ox_rate,
-#            color = "#006633",
-#            icon = "fa-percent")
-# })
-```
-
 ```{r ox org inputs}
+
+textInput("ox_id",
+          label = "Organization Name",
+          value = "Organization 3",
+          placeholder = "Enter Organiation Name"
+)
+
 selectInput("ox_issue", 
@@
   choice = df()
-  persona = p_beta1 # Choose the persona
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+  per_choice = p()
+
+    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+
+  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(ox_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#FFC30B"),
+        symbol = "%")
+})
+
+renderGauge({
+  choice = df()
+  per_choice = p()
+
+    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+
+  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(ox_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#3fad48"),
+        symbol = "%")
+})
+
+renderGauge({
+  choice = df()
+  per_choice = p()
+
+    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
 
@@
 
-```{r plot rc plot}
-# renderPlotly({
-#   choice = df()
-#   
-#     persona1 = p_beta1 # Choose the persona
-#   
-#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
-#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
-#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
-#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
-#   
-#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   
-#     persona2 = p_beta2 # Choose the persona
-#   
-#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
-#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
-#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
-#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
-#   
-#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   
-#       persona3 = p_beta3 # Choose the persona
-#   
-#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
-#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
-#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
-#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
-#   
-#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   
-#   data <- c(rc_exp_util1, rc_rate1, 
-#             rc_exp_util2, rc_rate2,
-#             rc_exp_util3, rc_rate3)
-#   
-#   
-#   df <- as.data.frame(matrix(data, 6, 1))
-#   
-#   df[,2] <- c("Red Cross")
-#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
-#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
-#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
-#   
-#   ggplotly(df %>% filter(Type == "Market Share") %>% 
-#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
-#              geom_bar(position = "dodge", stat = "identity") +
-#              labs(x="") + 
-#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
-#              theme(legend.position = "none")
-#     )
-# })
-```
-
-```{r valuebox rc commented}
-# renderValueBox({
-#   choice = df()
-#   
-#   persona = p_beta1 # Choose the persona
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-#   
-#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   valueBox(rc_rate,
-#            color = "#660000",
-#            icon = "fa-percent")
-# })
-```
-
 ```{r rc org inputs}
+
+textInput("rc_id",
+          label = "Organization Name",
+          value = "Organization 4",
+          placeholder = "Enter Organiation Name"
+)
+
 selectInput("rc_issue", 
@@
         max = 100,
-        gaugeSectors(colors = "#660000"),
+        gaugeSectors(colors = "#FFC30B"),
+        symbol = "%")
+})
+
+renderGauge({
+  choice = df()
+  per_choice = p()
+
+    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+
+  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(rc_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#3fad48"),
+        symbol = "%")
+})
+
+renderGauge({
+  choice = df()
+  per_choice = p()
+
+    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+
+  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(rc_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#006633"),
         symbol = "%")
@@
 #        value = 0)
-
-selectInput("p1_political_pref",
-         label = "Political views from liberal to conservative:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
 
@@
 
-# selectInput("p1_political_pref",
-#          label = "Political views from liberal to conservative:",
-#          choices = c("0", '1', '2', '3','4','5','6','7'))
+selectInput("p1_political_pref",
+         label = "Political views from liberal to conservative:",
+         choices = c("0", '1', '2', '3','4','5','6','7'))
 
@@
 
+```{r persona 1 gauge}
+renderGauge({
+  choice = df()
+  per_choice = p()
+
+    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+
+  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(ai_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#FFC30B"),
+        symbol = "%")
+})
+
+renderGauge({
+  choice = df()
+  per_choice = p()
+
+    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+
+  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(gp_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#3fad48"),
+        symbol = "%")
+})
+
+renderGauge({
+  choice = df()
+  per_choice = p()
+
+    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+
+  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(ox_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#006633"),
+        symbol = "%")
+})
+
+renderGauge({
+  choice = df()
+  per_choice = p()
+
+    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+
+  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(rc_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#660000"),
+        symbol = "%")
+})
+```
+
 ### Persona 2
@@
 
+```{r persona 2 gauge}
+renderGauge({
+  choice = df()
+  per_choice = p()
+
+    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+
+  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(ai_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#FFC30B"),
+        symbol = "%")
+})
+
+renderGauge({
+  choice = df()
+  per_choice = p()
+
+    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+
+  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(gp_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#3fad48"),
+        symbol = "%")
+})
+
+renderGauge({
+  choice = df()
+  per_choice = p()
+
+    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+
+  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(ox_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#006633"),
+        symbol = "%")
+})
+
+renderGauge({
+  choice = df()
+  per_choice = p()
+
+    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+
+  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(rc_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#660000"),
+        symbol = "%")
+})
+```
+
 ### Persona 3
@@
 
+```{r persona 3 gauge}
+renderGauge({
+  choice = df()
+  per_choice = p()
+
+    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+
+  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(ai_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#FFC30B"),
+        symbol = "%")
+})
+
+renderGauge({
+  choice = df()
+  per_choice = p()
+
+    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+
+  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(gp_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#3fad48"),
+        symbol = "%")
+})
+
+renderGauge({
+  choice = df()
+  per_choice = p()
+
+    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+
+  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(ox_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#006633"),
+        symbol = "%")
+})
+
+renderGauge({
+  choice = df()
+  per_choice = p()
+
+    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+
+  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+
+  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+
+  gauge(rc_rate,
+        min = 0,
+        max = 100,
+        gaugeSectors(colors = "#660000"),
+        symbol = "%")
+})
+```
+
 <!-- There is an issue of not being able to see the last selectInput options when drop down box appears -->
+
+<!-- This is for commented out code -->
+
+```{r plot ai plot}
+# renderPlotly({
+#   choice = df()
+#   
+#     persona1 = p_beta1 # Choose the persona
+#   
+#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
+#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
+#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
+#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+#   
+#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   
+#     persona2 = p_beta2 # Choose the persona
+#   
+#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
+#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
+#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
+#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+#   
+#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   
+#       persona3 = p_beta3 # Choose the persona
+#   
+#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
+#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
+#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
+#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+#   
+#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   
+#   data <- c(ai_exp_util1, ai_rate1, 
+#             ai_exp_util2, ai_rate2,
+#             ai_exp_util3, ai_rate3)
+#   
+#   
+#   df <- as.data.frame(matrix(data, 6, 1))
+#   
+#   df[,2] <- c("Amnesty International")
+#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
+#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
+#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+#   
+#   ggplotly(df %>% filter(Type == "Market Share") %>% 
+#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+#              geom_bar(position = "dodge", stat = "identity") +
+#              labs(x="") + 
+#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+#              theme(legend.position = "none")
+#     )
+# })
+```
+
+```{r valuebox ai commented}
+# renderValueBox({
+#   choice = df()
+#   
+#   persona = p_beta1 # Choose the persona
+#   
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+#   
+#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   valueBox(ai_rate,
+#            color = "#FFC30B",
+#            icon = "fa-percent")
+# })
+```
+
+```{r plot gp plot}
+# renderPlotly({
+#   choice = df()
+#   
+#     persona1 = p_beta1 # Choose the persona
+#   
+#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
+#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
+#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
+#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+#   
+#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   
+#     persona2 = p_beta2 # Choose the persona
+#   
+#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
+#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
+#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
+#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+#   
+#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   
+#       persona3 = p_beta3 # Choose the persona
+#   
+#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
+#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
+#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
+#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+#   
+#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   
+#   data <- c(gp_exp_util1, gp_rate1, 
+#             gp_exp_util2, gp_rate2,
+#             gp_exp_util3, gp_rate3)
+#   
+#   
+#   df <- as.data.frame(matrix(data, 6, 1))
+#   
+#   df[,2] <- c("Greenpeace")
+#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
+#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
+#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+#   
+#   ggplotly(df %>% filter(Type == "Market Share") %>% 
+#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+#              geom_bar(position = "dodge", stat = "identity") +
+#              labs(x="") + 
+#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+#              theme(legend.position = "none")
+#     )
+# })
+```
+
+```{r valuebox gp commented}
+# renderValueBox({
+#   choice = df()
+#   persona = p_beta1 # Choose the persona
+#   
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+#   
+#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   valueBox(gp_rate,
+#            color = "#3fad48",
+#            icon = "fa-percent")
+# })
+```
+
+```{r plot ox plot}
+# renderPlotly({
+#   choice = df()
+#   
+#     persona1 = p_beta1 # Choose the persona
+#   
+#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
+#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
+#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
+#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+#   
+#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   
+#     persona2 = p_beta2 # Choose the persona
+#   
+#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
+#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
+#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
+#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+#   
+#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   
+#       persona3 = p_beta3 # Choose the persona
+#   
+#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
+#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
+#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
+#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+#   
+#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   
+#   data <- c(ox_exp_util1, ox_rate1, 
+#             ox_exp_util2, ox_rate2,
+#             ox_exp_util3, ox_rate3)
+#   
+#   
+#   df <- as.data.frame(matrix(data, 6, 1))
+#   
+#   df[,2] <- c("Oxfam")
+#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
+#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
+#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+#   
+#   ggplotly(df %>% filter(Type == "Market Share") %>% 
+#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+#              geom_bar(position = "dodge", stat = "identity") +
+#              labs(x="") + 
+#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+#              theme(legend.position = "none")
+#     )
+# })
+```
+
+```{r valuebox ox commented}
+# renderValueBox({
+#   choice = df()
+#   
+#   persona = p_beta1 # Choose the persona
+#   
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+#   
+#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   valueBox(ox_rate,
+#            color = "#006633",
+#            icon = "fa-percent")
+# })
+```
+
+```{r plot rc plot}
+# renderPlotly({
+#   choice = df()
+#   
+#     persona1 = p_beta1 # Choose the persona
+#   
+#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
+#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
+#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
+#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+#   
+#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   
+#     persona2 = p_beta2 # Choose the persona
+#   
+#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
+#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
+#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
+#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+#   
+#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   
+#       persona3 = p_beta3 # Choose the persona
+#   
+#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
+#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
+#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
+#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+#   
+#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   
+#   data <- c(rc_exp_util1, rc_rate1, 
+#             rc_exp_util2, rc_rate2,
+#             rc_exp_util3, rc_rate3)
+#   
+#   
+#   df <- as.data.frame(matrix(data, 6, 1))
+#   
+#   df[,2] <- c("Red Cross")
+#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
+#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
+#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+#   
+#   ggplotly(df %>% filter(Type == "Market Share") %>% 
+#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+#              geom_bar(position = "dodge", stat = "identity") +
+#              labs(x="") + 
+#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+#              theme(legend.position = "none")
+#     )
+# })
+```
+
+```{r valuebox rc commented}
+# renderValueBox({
+#   choice = df()
+#   
+#   persona = p_beta1 # Choose the persona
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+#   
+#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   valueBox(rc_rate,
+#            color = "#660000",
+#            icon = "fa-percent")
+# })
+```
 

### 2020-08-25 analysis/05_market_simulator.Rmd
Changed a travel to developing county input
Added Persona naming inputs and added legend for interrepting the Plotly easier

@@
   df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
-  df[,4] <- c(rep("Persona 1",8), rep("Persona 2", 8), rep("Persona 3", 8))
+  df[,4] <- c(rep(input$p1_id,8), rep(input$p2_id, 8), rep(input$p3_id, 8))
 
@@
              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
-             theme(legend.position = "none")
+             theme(legend.position = "right")
     )
@@
 #        value = 0)
+
+textInput("p1_id",
+          label = "Persona Name",
+          value = "Persona 1",
+          placeholder = "Enter Persona Name")
 
@@
          label = "Travel to developing country:",
-         choices = c('Yes', 'No'))
+         choices = c("Yes", 'No' = "No Travel to Developing Countries"))
 
@@
 
-# selectInput("model_choice",
-#             label = "Select Model:",
-#             choices = c("public_political_social_charity_demo"))
+textInput("p2_id",
+          label = "Persona Name",
+          value = "Persona 2",
+          placeholder = "Enter Persona Name")
 
@@
 
-# selectInput("model_choice",
-#             label = "Select Model:",
-#             choices = c("public_political_social_charity_demo"))
+textInput("p3_id",
+          label = "Persona Name",
+          value = "Persona 3",
+          placeholder = "Enter Persona Name")
 

### 2020-08-25 analysis/05_market_simulator.Rmd
Fixed some persona inputs to work with reactive element. Still need work on inputs that are scaled, perhaps make them discrete or dummys. Also fixed some of the persona beta levels to match persona inputs

@@
                         "Print",
-                        "Online",
+                        "Online (excluding social media)",
                         "Social Media",
@@
                         "Email",
-                        "Newsapp",
+                        "News app",
                         "Follow Government or Public Affairs", 
-                        "No Travel to Developing Countries", 
+                        "Doesn't Travel", 
                         "Political Preference", 
@@
                         "Atheist",
-                        "Other",
+                        "Other (Religion)",
                         "Chartiy Trust Importance",
@@
                         "Donation Amount",
-                        "Volunteer 12 Months",
+                        "Not Volunteered",
                         "Volunteer Frequence",
@@
                         "Prefer not to say",
-                        "Other",
+                        "Other (Gender)",
                         "Widowed",
@@
                         "Pacific Islander", 
-                        "Other", 
+                        "Other (Race)", 
                         "Age")
@@
   ggplotly(df %>% filter(Type == "Market Share") %>%
+             mutate(
+               Organization = factor(Organization, levels = c(input$ai_id, input$gp_id, input$ox_id, input$rc_id), ordered = TRUE),
+               Persona = factor(Persona, levels = c(input$p1_id, input$p2_id, input$p3_id), ordered = TRUE)) %>% 
              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
@@
              labs(x="") + 
-             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+             scale_fill_manual(values = c( "#FFC30B", "#006633", "#660000")) +
              theme(legend.position = "right")
@@
 
-# selectInput("model_choice",
-#             label = "Select Model:",
-#             choices = c("public_political_social_charity_demo"))
-
-# sliderInput("p1_political_pref",
-#        label = "Political Preference",
-#        min = 0,
-#        max = 7,
-#        value = 0)
-
 textInput("p1_id",
@@
 
+# Need to Fix
 selectInput("p1_national_news",
          label = "Follow national news:",
-         choices = c('Multiple times a day' = 1,
-                     'Every day' = 2,
-                     "Once a week" = 3,
-                     "Hardly ever" = 4,
-                     "Never" = 5))
-
+         choices = c('Multiple times a day',
+                     'Every day',
+                     "Once a week",
+                     "Hardly ever",
+                     "Never"))
+
+# Need to Fix
 selectInput("p1_international_news",
@@
                      'Print',
-                     "Online",
+                     "Online (excluding social media)",
                      "Social Media",
                      "Radio",
-                     "Email newsletters",
+                     "Email",
                      "News app"),
@@
 
+# Need to Fix
 selectInput("p1_follow_gov",
@@
          label = "Travel to developing country:",
-         choices = c('Yes', 'No'))
-
+         choices = c('Does Travel', "Doesn't Travel"))
+
+# Need to Fix
 selectInput("p1_political_pref",
@@
 
+# Need to Fix
 selectInput("p1_institution_trust",
@@
 
+# Need to Fix
 selectInput("p1_others_charitable",
@@
 
+# Need to Fix
 selectInput("p1_worship_attendance",
@@
 
+# Need to Fix
 selectInput("p1_religion_importance",
@@
                      'Atheist',
-                     'Other'))
-
-selectInput("p1_national_news",
-         label = "Follow national news:",
-         choices = c('Multiple times a day',
-                     'Every day',
-                     "Once a week",
-                     "Hardly ever",
-                     "Never"))
-
-selectInput("p1_international_news",
-         label = "Follow international news:",
-         choices = c('Always',
-                     "Sometimes",
-                     "Never"))
-
-selectInput("p1_news_medium",
-         label = "Medium to follow news:",
-         choices = c('TV',
-                     'Print',
-                     "Online",
-                     "Social Media",
-                     "Radio",
-                     "Email newsletters",
-                     "News app"))
-
-selectInput("p1_follow_gov",
-         label = "Follow government & public affairs:",
-         choices = c('Most of the time',
-                     'Some of the time',
-                     "Only now and then",
-                     "Hardly at all"))
-
-selectInput("p1_travel_developing",
-         label = "Travel to developing country:",
-         choices = c("Yes", 'No' = "No Travel to Developing Countries"))
-
-selectInput("p1_institution_trust",
-         label = "Political institution trust from none to complete:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
-
-selectInput("p1_others_charitable",
-         label = "People should be more charitable:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
-
-selectInput("p1_worship_attendance",
-         label = "Worship service attendance:",
-         choices = c('Multiple times a week',
-                     'Once a week',
-                     "Once a month",
-                     "Once a year",
-                     "Never"))
-
-selectInput("p1_religion_importance",
-         label = "Importance of religion:",
-         choices = c('Extremely important',
-                     'Very important',
-                     'Moderately important',
-                     'Slightly important',
-                     'Not at all important'))
-
-selectInput("p1_religion",
-         label = "Religion:",
-         choices = c('Catholic',
-                     'Protestant',
-                     'Christian Orthodox',
-                     'Jewish',
-                     'Muslim',
-                     'Sikh',
-                     'Hindu',
-                     'Buddhist',
-                     'Atheist',
-                     'Other'))
-
+                     'Other (Religion)'))
+
+# Need to Fix
 selectInput("p1_charity_importance",
@@
 
+# Need to Fix
 selectInput("p1_trust_in_charity",
@@
             choices = c("0", '1', '2', '3','4','5','6','7'))
+
+# Need to Fix
 
@@
 
+# Need to Fix
 selectInput("p1_donation_amount",
@@
          label = "Volunteered in last 12 Months:",
-         choices = c("Yes", "No"))
-
+         choices = c("Volunteered", "Not Volunteered"))
+
+# Need to Fix
 selectInput("p1_volunteer_frequency",
@@
 
+# Need to Fix
 selectInput("p1_personal_activism",
@@
 
+# Need to Fix
 selectInput("p1_family_activism",
@@
 
+# Need to Fix
 selectInput("p1_religious_member",
@@
 
+# Need to Fix
 selectInput("p1_sport_member",
@@
 
+# Need to Fix
 selectInput("p1_art_member",
@@
 
+# Need to Fix
 selectInput("p1_labor_member",
@@
 
+# Need to Fix
 selectInput("p1_political_member",
@@
 
+# Need to Fix
 selectInput("p1_environmental_member",
@@
 
+# Need to Fix
 selectInput("p1_professional_member",
@@
 
+# Need to Fix
 selectInput("p1_humanitarian_member",
@@
 
+# Need to Fix
 selectInput("p1_consumer_member",
@@
 
+# Need to Fix
 selectInput("p1_other_member",
@@
                      "Prefer not to say",
-                     "Other"))
+                     "Other (Gender)"))
 
@@
 
+# Need to Fix
 selectInput("p1_education",
@@
                      "Doctorate"))
-
+# Need to Fix
 selectInput("p1_income",
@@
                      'Native Hawaiian or Pacific Islander',
-                     'Other'),
+                     'Other (Race)'),
          multiple = TRUE)
 
+# Need to Fix
 selectInput("p1_age",
@@
 
+# Need to Fix
 selectInput("p2_national_news",
@@
 
+# Need to Fix
 selectInput("p2_international_news",
@@
          label = "Medium to follow news:",
-         choices = c('TV',
+         choices = c("",
+                     'TV',
                      'Print',
-                     "Online",
+                     "Online (excluding social media)",
                      "Social Media",
                      "Radio",
-                     "Email newsletters",
-                     "News app"))
-
+                     "Email",
+                     "News app"),
+         multiple = TRUE)
+
+# Need to Fix
 selectInput("p2_follow_gov",
@@
          label = "Travel to developing country:",
-         choices = c('Yes', 'No'))
-
-selectInput("p2_polical_pref",
-         label = "Polical views from liberal to conservative:",
+         choices = c('Does Travel', "Doesn't Travel"))
+
+# Need to Fix
+selectInput("p2_political_pref",
+         label = "Political views from liberal to conservative:",
          choices = c("0", '1', '2', '3','4','5','6','7'))
 
+# Need to Fix
 selectInput("p2_institution_trust",
@@
 
+# Need to Fix
 selectInput("p2_others_charitable",
@@
 
+# Need to Fix
 selectInput("p2_worship_attendance",
@@
 
+# Need to Fix
 selectInput("p2_religion_importance",
@@
                      'Atheist',
-                     'Other'))
-
+                     'Other (Religion)'))
+
+# Need to Fix
 selectInput("p2_charity_importance",
@@
 
+# Need to Fix
 selectInput("p2_trust_in_charity",
@@
 
+# Need to Fix
 selectInput("p2_donation_amount",
@@
          label = "Volunteered in last 12 Months:",
-         choices = c("Yes", "No"))
-
+         choices = c("Volunteered", "Not Volunteered"))
+
+# Need to Fix
 selectInput("p2_volunteer_frequency",
@@
 
+# Need to Fix
 selectInput("p2_personal_activism",
@@
 
+# Need to Fix
 selectInput("p2_family_activism",
@@
 
+# Need to Fix
 selectInput("p2_religious_member",
@@
 
+# Need to Fix
 selectInput("p2_sport_member",
@@
 
+# Need to Fix
 selectInput("p2_art_member",
@@
 
+# Need to Fix
 selectInput("p2_labor_member",
@@
 
+# Need to Fix
 selectInput("p2_political_member",
@@
 
+# Need to Fix
 selectInput("p2_environmental_member",
@@
 
+# Need to Fix
 selectInput("p2_professional_member",
@@
 
+# Need to Fix
 selectInput("p2_humanitarian_member",
@@
 
+# Need to Fix
 selectInput("p2_consumer_member",
@@
 
+# Need to Fix
 selectInput("p2_other_member",
@@
 
+# Need to Fix
 selectInput("p2_education",
@@
                      "Doctorate"))
-
+# Need to Fix
 selectInput("p2_income",
@@
          label = "Race(s):",
-         choices = c('White',
+         choices = c("",
+                     'White',
                      'Black or African American',
@@
                      'Native Hawaiian or Pacific Islander',
-                     'Other'),
+                     'Other (Race)'),
          multiple = TRUE)
 
+# Need to Fix
 selectInput("p2_age",
@@
 
+# Need to Fix
 selectInput("p3_national_news",
@@
 
+# Need to Fix
 selectInput("p3_international_news",
@@
          label = "Medium to follow news:",
-         choices = c('TV',
+         choices = c("",
+                     'TV',
                      'Print',
-                     "Online",
+                     "Online (excluding social media)",
                      "Social Media",
                      "Radio",
-                     "Email newsletters",
-                     "News app"))
-
+                     "Email",
+                     "News app"),
+         multiple = TRUE)
+
+# Need to Fix
 selectInput("p3_follow_gov",
@@
          label = "Travel to developing country:",
-         choices = c('Yes', 'No'))
-
-selectInput("p3_polical_pref",
-         label = "Polical views from liberal to conservative:",
+         choices = c('Does Travel', "Doesn't Travel"))
+
+# Need to Fix
+selectInput("p3_political_pref",
+         label = "Political views from liberal to conservative:",
          choices = c("0", '1', '2', '3','4','5','6','7'))
 
+# Need to Fix
 selectInput("p3_institution_trust",
@@
 
+# Need to Fix
 selectInput("p3_others_charitable",
@@
 
+# Need to Fix
 selectInput("p3_worship_attendance",
@@
 
+# Need to Fix
 selectInput("p3_religion_importance",
@@
                      'Atheist',
-                     'Other'))
-
+                     'Other (Religion)'))
+
+# Need to Fix
 selectInput("p3_charity_importance",
@@
 
+# Need to Fix
 selectInput("p3_trust_in_charity",
@@
 
+# Need to Fix
 selectInput("p3_donation_amount",
@@
          label = "Volunteered in last 12 Months:",
-         choices = c("Yes", "No"))
-
+         choices = c("Volunteered", "Not Volunteered"))
+
+# Need to Fix
 selectInput("p3_volunteer_frequency",
@@
 
+# Need to Fix
 selectInput("p3_personal_activism",
@@
 
+# Need to Fix
 selectInput("p3_family_activism",
@@
 
+# Need to Fix
 selectInput("p3_religious_member",
@@
 
+# Need to Fix
 selectInput("p3_sport_member",
@@
 
+# Need to Fix
 selectInput("p3_art_member",
@@
 
+# Need to Fix
 selectInput("p3_labor_member",
@@
 
+# Need to Fix
 selectInput("p3_political_member",
@@
 
+# Need to Fix
 selectInput("p3_environmental_member",
@@
 
+# Need to Fix
 selectInput("p3_professional_member",
@@
 
+# Need to Fix
 selectInput("p3_humanitarian_member",
@@
 
+# Need to Fix
 selectInput("p3_consumer_member",
@@
 
+# Need to Fix
 selectInput("p3_other_member",
@@
 
+# Need to Fix
 selectInput("p3_education",
@@
                      "Doctorate"))
-
+# Need to Fix
 selectInput("p3_income",
@@
                      'Native Hawaiian or Pacific Islander',
-                     'Other'),
+                     'Other (Race)'),
          multiple = TRUE)
 
+# Need to Fix
 selectInput("p3_age",
@@
 ```
-
-<!-- Persona 2 Page -->
-
-<!-- Persona 2 {.tabset .tabset-fade} -->
-<!-- -------------------------------------------------- -->
-
-<!-- ### Market Share Persona 2 -->
-
-<!-- ```{r plot persona 2} -->
-<!-- renderPlotly({ -->
-<!--   choice = df() -->
-
-<!--   persona = p_beta2 # Choose the persona -->
-
-<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2) -->
-<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2) -->
-<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2) -->
-<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2) -->
-
-<!--   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-<!--   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-<!--   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-<!--   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-
-<!--   data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate) -->
-<!--   df <- as.data.frame(matrix(data, 8, 1)) -->
-
-<!--   df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross") -->
-<!--   df[,3] <- c(rep("Utility", 4), rep("Market Share", 4)) -->
-<!--   df[,4] <- rep(c("Persona 1","Persona 2", "Persona 3"), length.out = 8) -->
-<!--   colnames(df) <- c('Value', 'Organization', "Type", "Persona") -->
-
-<!--   ggplotly(df %>% filter(Type == "Market Share") %>%  -->
-<!--              ggplot(aes(y = Value, x = Organization, fill = Organization)) + -->
-<!--              geom_col() + -->
-<!--              labs(x="") +  -->
-<!--              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) + -->
-<!--              theme(legend.position = "none") + -->
-<!--              facet_wrap(~Type) -->
-<!--     ) -->
-<!-- }) -->
-<!-- ``` -->
-
-<!-- ### Amnesty International Market Share -->
-
-<!-- ```{r valuebox ai persona 2} -->
-<!-- renderValueBox({ -->
-<!--   choice = df() -->
-
-<!--   persona = p_beta2 # Choose the persona -->
-
-<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2) -->
-<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2) -->
-<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2) -->
-<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2) -->
-
-<!--   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-
-<!--   valueBox(ai_rate, -->
-<!--            color = "#FFC30B", -->
-<!--            icon = "fa-percent") -->
-<!-- }) -->
-<!-- ``` -->
-
-<!-- ### Greenpeace Market Share -->
-
-<!-- ```{r valuebox gp persona 2} -->
-<!-- renderValueBox({ -->
-<!--   choice = df() -->
-
-<!--   persona = p_beta2 # Choose the persona -->
-
-<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2) -->
-<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2) -->
-<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2) -->
-<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2) -->
-
-<!--   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-
-<!--   valueBox(gp_rate, -->
-<!--            color = "#3fad48", -->
-<!--            icon = "fa-percent") -->
-<!-- }) -->
-<!-- ``` -->
-
-<!-- ### Oxfam Market Share -->
-
-<!-- ```{r valuebox ox persona 2} -->
-<!-- renderValueBox({ -->
-<!--   choice = df() -->
-
-<!--   persona = p_beta2 # Choose the persona -->
-
-<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2) -->
-<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2) -->
-<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2) -->
-<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2) -->
-
-<!--   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-
-<!--   valueBox(ox_rate, -->
-<!--            color = "#006633", -->
-<!--            icon = "fa-percent") -->
-<!-- }) -->
-<!-- ``` -->
-
-<!-- ### Redcross Market Share -->
-
-<!-- ```{r valuebox rc persona 2} -->
-<!-- renderValueBox({ -->
-<!--   choice = df() -->
-
-<!--   persona = p_beta2 # Choose the persona -->
-
-<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2) -->
-<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2) -->
-<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2) -->
-<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2) -->
-
-<!--   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-
-<!--   valueBox(rc_rate, -->
-<!--            color = "#660000", -->
-<!--            icon = "fa-percent") -->
-<!-- }) -->
-<!-- ``` -->
-
-<!-- Organizational Inputs {.tabset .tabset-fade} -->
-<!-- ------------------------------------- -->
-<!-- ### Amnesty International Inputs -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- selectInput("ai_issue",  -->
-<!--             label = "Select Issue Area:", -->
-<!--             choices = c("Emergency response", -->
-<!--                         "Environment", -->
-<!--                         "Human rights", -->
-<!--                         "Refugee relief")) -->
-
-<!-- selectInput("ai_fin_trans", -->
-<!--             label = "Select Financial transparency:", -->
-<!--             choices = c("Doesn’t engage in transparency", -->
-<!--                         "Engages in transparency")) -->
-
-<!-- selectInput("ai_account", -->
-<!--             label = "Select Financial Accountability:", -->
-<!--             choices = c("Doesn’t engage in financial accountability", -->
-<!--                         "Engages in financial accountability")) -->
-
-<!-- selectInput("ai_funding", -->
-<!--             label = "Select Funding source:", -->
-<!--             choices = c("Many small private donations", -->
-<!--                         "Handful of wealthy private donors", -->
-<!--                         "Government Grants")) -->
-
-<!-- selectInput("ai_gov_relat", -->
-<!--             label = "Select Relationship with host government", -->
-<!--             choices = c("Friendly relationship with government", -->
-<!--                         "Criticized by government",  -->
-<!--                         "Under government crackdown")) -->
-<!-- ``` -->
-
-<!-- ### Greenpeace Inputs -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- selectInput("gp_issue",  -->
-<!--             label = "Select Issue Area:", -->
-<!--             choices = c("Emergency response", -->
-<!--                         "Environment", -->
-<!--                         "Human rights", -->
-<!--                         "Refugee relief")) -->
-
-<!-- selectInput("gp_fin_trans", -->
-<!--             label = "Select Financial transparency:", -->
-<!--             choices = c("Doesn’t engage in transparency", -->
-<!--                         "Engages in transparency")) -->
-
-<!-- selectInput("gp_account", -->
-<!--             label = "Select Financial Accountability:", -->
-<!--             choices = c("Doesn’t engage in accountability", -->
-<!--                         "Engages in financial accountability")) -->
-
-<!-- selectInput("gp_funding", -->
-<!--             label = "Select Funding source:", -->
-<!--             choices = c("Many small private donations", -->
-<!--                         "Handful of wealthy private donors", -->
-<!--                         "Government Grants")) -->
-
-<!-- selectInput("gp_gov_relat", -->
-<!--             label = "Select Relationship with host government", -->
-<!--             choices = c("Friendly relationship with government", -->
-<!--                         "Criticized by government",  -->
-<!--                         "Under government crackdown")) -->
-<!-- ``` -->
-
-<!-- ### Oxfam Inputs -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- selectInput("ox_issue",  -->
-<!--             label = "Select Issue Area:", -->
-<!--             choices = c("Emergency response", -->
-<!--                         "Environment", -->
-<!--                         "Human rights", -->
-<!--                         "Refugee relief")) -->
-
-<!-- selectInput("ox_fin_trans", -->
-<!--             label = "Select Financial transparency:", -->
-<!--             choices = c("Doesn’t engage in transparency", -->
-<!--                         "Engages in transparency")) -->
-
-<!-- selectInput("ox_account", -->
-<!--             label = "Select Financial Accountability:", -->
-<!--             choices = c("Doesn’t engage in accountability", -->
-<!--                         "Engages in financial accountability")) -->
-
-<!-- selectInput("ox_funding", -->
-<!--             label = "Select Funding source:", -->
-<!--             choices = c("Many small private donations", -->
-<!--                         "Handful of wealthy private donors", -->
-<!--                         "Government Grants")) -->
-
-<!-- selectInput("ox_gov_relat", -->
-<!--             label = "Select Relationship with host government", -->
-<!--             choices = c("Friendly relationship with government", -->
-<!--                         "Criticized by government",  -->
-<!--                         "Under government crackdown")) -->
-<!-- ``` -->
-
-<!-- ### Red Cross Inputs -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- selectInput("rc_issue",  -->
-<!--             label = "Select Issue Area:", -->
-<!--             choices = c("Emergency response", -->
-<!--                         "Environment", -->
-<!--                         "Human rights", -->
-<!--                         "Refugee relief")) -->
-
-<!-- selectInput("rc_fin_trans", -->
-<!--             label = "Select Financial transparency:", -->
-<!--             choices = c("Doesn’t engage in transparency", -->
-<!--                         "Engages in transparency")) -->
-
-<!-- selectInput("rc_account", -->
-<!--             label = "Select Financial Accountability:", -->
-<!--             choices = c("Doesn’t engage in accountability", -->
-<!--                         "Engages in financial accountability")) -->
-
-<!-- selectInput("rc_funding", -->
-<!--             label = "Select Funding source:", -->
-<!--             choices = c("Many small private donations", -->
-<!--                         "Handful of wealthy private donors", -->
-<!--                         "Government Grants")) -->
-
-<!-- selectInput("rc_gov_relat", -->
-<!--             label = "Select Relationship with host government", -->
-<!--             choices = c("Friendly relationship with government", -->
-<!--                         "Criticized by government",  -->
-<!--                         "Under government crackdown")) -->
-<!-- ``` -->
-
-<!-- Persona 3 Page  -->
-
-<!-- Persona 3 {.tabset .tabset-fade} -->
-<!-- -------------------------------------------------- -->
-
-<!-- ### Market Share Persona 3 -->
-<!-- ```{r plot persona 3} -->
-<!-- renderPlotly({ -->
-<!--   choice = df() -->
-
-<!--   persona = p_beta3 # Choose the persona -->
-
-<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2) -->
-<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2) -->
-<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2) -->
-<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2) -->
-
-<!--   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-<!--   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-<!--   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-<!--   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-
-<!--   data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate) -->
-<!--   df <- as.data.frame(matrix(data, 8, 1)) -->
-
-<!--   df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross") -->
-<!--   df[,3] <- c(rep("Utility", 4), rep("Market Share", 4)) -->
-<!--   df[,4] <- rep(c("Persona 1","Persona 2", "Persona 3"), length.out = 8) -->
-<!--   colnames(df) <- c('Value', 'Organization', "Type", "Persona") -->
-
-<!--   ggplotly(df %>% filter(Type == "Market Share") %>%  -->
-<!--              ggplot(aes(y = Value, x = Organization, fill = Organization)) + -->
-<!--              geom_col() + -->
-<!--              labs(x="") +  -->
-<!--              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) + -->
-<!--              theme(legend.position = "none") + -->
-<!--              facet_wrap(~Type) -->
-<!--     ) -->
-<!-- }) -->
-<!-- ``` -->
-
-<!-- ### Amnesty International Market Share -->
-
-<!-- ```{r valuebox ai persona 3} -->
-<!-- renderValueBox({ -->
-<!--   choice = df() -->
-
-<!--   persona = p_beta3 # Choose the persona -->
-
-<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2) -->
-<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2) -->
-<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2) -->
-<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2) -->
-
-<!--   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-
-<!--   valueBox(ai_rate, -->
-<!--            color = "#FFC30B", -->
-<!--            icon = "fa-percent") -->
-<!-- }) -->
-<!-- ``` -->
-
-<!-- ### Greenpeace Market Share -->
-
-<!-- ```{r valuebox gp persona 3} -->
-<!-- renderValueBox({ -->
-<!--   choice = df() -->
-
-<!--   persona = p_beta3 # Choose the persona -->
-
-<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2) -->
-<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2) -->
-<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2) -->
-<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2) -->
-
-<!--   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-
-<!--   valueBox(gp_rate, -->
-<!--            color = "#3fad48", -->
-<!--            icon = "fa-percent") -->
-<!-- }) -->
-<!-- ``` -->
-
-<!-- ### Oxfam Market Share -->
-
-<!-- ```{r valuebox ox persona 3} -->
-<!-- renderValueBox({ -->
-<!--   choice = df() -->
-
-<!--   persona = p_beta3 # Choose the persona -->
-
-<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2) -->
-<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2) -->
-<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2) -->
-<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2) -->
-
-<!--   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-
-<!--   valueBox(ox_rate, -->
-<!--            color = "#006633", -->
-<!--            icon = "fa-percent") -->
-<!-- }) -->
-<!-- ``` -->
-
-<!-- ### Redcross Market Share -->
-
-<!-- ```{r valuebox rc persona 3} -->
-<!-- renderValueBox({ -->
-<!--   choice = df() -->
-
-<!--   persona = p_beta3 # Choose the persona -->
-
-<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2) -->
-<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2) -->
-<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2) -->
-<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2) -->
-
-<!--   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-
-<!--   valueBox(rc_rate, -->
-<!--            color = "#660000", -->
-<!--            icon = "fa-percent") -->
-<!-- }) -->
-<!-- ``` -->
-
-<!-- Organizational Inputs {.tabset .tabset-fade} -->
-<!-- ------------------------------------- -->
-<!-- ### Amnesty International Inputs -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- selectInput("ai_issue",  -->
-<!--             label = "Select Issue Area:", -->
-<!--             choices = c("Emergency response", -->
-<!--                         "Environment", -->
-<!--                         "Human rights", -->
-<!--                         "Refugee relief")) -->
-
-<!-- selectInput("ai_fin_trans", -->
-<!--             label = "Select Financial transparency:", -->
-<!--             choices = c("Doesn’t engage in transparency", -->
-<!--                         "Engages in transparency")) -->
-
-<!-- selectInput("ai_account", -->
-<!--             label = "Select Financial Accountability:", -->
-<!--             choices = c("Doesn’t engage in financial accountability", -->
-<!--                         "Engages in financial accountability")) -->
-
-<!-- selectInput("ai_funding", -->
-<!--             label = "Select Funding source:", -->
-<!--             choices = c("Many small private donations", -->
-<!--                         "Handful of wealthy private donors", -->
-<!--                         "Government Grants")) -->
-
-<!-- selectInput("ai_gov_relat", -->
-<!--             label = "Select Relationship with host government", -->
-<!--             choices = c("Friendly relationship with government", -->
-<!--                         "Criticized by government",  -->
-<!--                         "Under government crackdown")) -->
-<!-- ``` -->
-
-<!-- ### Greenpeace Inputs -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- selectInput("gp_issue",  -->
-<!--             label = "Select Issue Area:", -->
-<!--             choices = c("Emergency response", -->
-<!--                         "Environment", -->
-<!--                         "Human rights", -->
-<!--                         "Refugee relief")) -->
-
-<!-- selectInput("gp_fin_trans", -->
-<!--             label = "Select Financial transparency:", -->
-<!--             choices = c("Doesn’t engage in transparency", -->
-<!--                         "Engages in transparency")) -->
-
-<!-- selectInput("gp_account", -->
-<!--             label = "Select Financial Accountability:", -->
-<!--             choices = c("Doesn’t engage in accountability", -->
-<!--                         "Engages in financial accountability")) -->
-
-<!-- selectInput("gp_funding", -->
-<!--             label = "Select Funding source:", -->
-<!--             choices = c("Many small private donations", -->
-<!--                         "Handful of wealthy private donors", -->
-<!--                         "Government Grants")) -->
-
-<!-- selectInput("gp_gov_relat", -->
-<!--             label = "Select Relationship with host government", -->
-<!--             choices = c("Friendly relationship with government", -->
-<!--                         "Criticized by government",  -->
-<!--                         "Under government crackdown")) -->
-<!-- ``` -->
-
-<!-- ### Oxfam Inputs -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- selectInput("ox_issue",  -->
-<!--             label = "Select Issue Area:", -->
-<!--             choices = c("Emergency response", -->
-<!--                         "Environment", -->
-<!--                         "Human rights", -->
-<!--                         "Refugee relief")) -->
-
-<!-- selectInput("ox_fin_trans", -->
-<!--             label = "Select Financial transparency:", -->
-<!--             choices = c("Doesn’t engage in transparency", -->
-<!--                         "Engages in transparency")) -->
-
-<!-- selectInput("ox_account", -->
-<!--             label = "Select Financial Accountability:", -->
-<!--             choices = c("Doesn’t engage in accountability", -->
-<!--                         "Engages in financial accountability")) -->
-
-<!-- selectInput("ox_funding", -->
-<!--             label = "Select Funding source:", -->
-<!--             choices = c("Many small private donations", -->
-<!--                         "Handful of wealthy private donors", -->
-<!--                         "Government Grants")) -->
-
-<!-- selectInput("ox_gov_relat", -->
-<!--             label = "Select Relationship with host government", -->
-<!--             choices = c("Friendly relationship with government", -->
-<!--                         "Criticized by government",  -->
-<!--                         "Under government crackdown")) -->
-<!-- ``` -->
-
-<!-- ### Red Cross Inputs -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- selectInput("rc_issue",  -->
-<!--             label = "Select Issue Area:", -->
-<!--             choices = c("Emergency response", -->
-<!--                         "Environment", -->
-<!--                         "Human rights", -->
-<!--                         "Refugee relief")) -->
-
-<!-- selectInput("rc_fin_trans", -->
-<!--             label = "Select Financial transparency:", -->
-<!--             choices = c("Doesn’t engage in transparency", -->
-<!--                         "Engages in transparency")) -->
-
-<!-- selectInput("rc_account", -->
-<!--             label = "Select Financial Accountability:", -->
-<!--             choices = c("Doesn’t engage in accountability", -->
-<!--                         "Engages in financial accountability")) -->
-
-<!-- selectInput("rc_funding", -->
-<!--             label = "Select Funding source:", -->
-<!--             choices = c("Many small private donations", -->
-<!--                         "Handful of wealthy private donors", -->
-<!--                         "Government Grants")) -->
-
-<!-- selectInput("rc_gov_relat", -->
-<!--             label = "Select Relationship with host government", -->
-<!--             choices = c("Friendly relationship with government", -->
-<!--                         "Criticized by government",  -->
-<!--                         "Under government crackdown")) -->
-<!-- ``` -->
-
-<!-- Old Code from before is below this line It is just commented out  ( Cmd Shift C ) -->
-
-<!-- Organization Utility -->
-<!-- ------------------------------------- -->
-<!-- ## Amnesty International Expected Utility -->
-
-<!-- ```{r} -->
-<!-- renderValueBox({ -->
-<!--   choice = df() -->
-<!--   ai_exp_util <- round(exp(t(choice[,3]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   valueBox(ai_exp_util, -->
-<!--            color = "#FFC30B") -->
-<!-- }) -->
-<!-- ``` -->
-
-<!-- ## Greenpeace Expected Utility -->
-
-<!-- ```{r} -->
-<!-- renderValueBox({ -->
-<!--   choice = df() -->
-<!--   gp_exp_util <- round(exp(t(choice[,4]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   valueBox(gp_exp_util, -->
-<!--            color = "#3fad48") -->
-<!-- }) -->
-<!-- ``` -->
-
-<!-- ## Oxfam Expected Utility -->
-
-<!-- ```{r} -->
-<!-- renderValueBox({ -->
-<!--   choice = df() -->
-<!--   ox_exp_util <- round(exp(t(choice[,5]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   valueBox(ox_exp_util, -->
-<!--            color = "#006633") -->
-<!-- }) -->
-<!-- ``` -->
-
-<!-- ## Redcross Expected Utility -->
-
-<!-- ```{r} -->
-<!-- renderValueBox({ -->
-<!--   choice = df() -->
-<!--   rc_exp_util <- round(exp(t(choice[,6]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   valueBox(rc_exp_util, -->
-<!--            color = "#660000") -->
-<!-- }) -->
-<!-- ``` -->
-
-<!-- Expected Donors {.tabset .tabset-fade} -->
-<!-- ------------------------------------- -->
-<!-- ### Amnesty International Expected Donors -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- renderGauge({ -->
-<!--   choice = df() -->
-<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-
-<!--   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-<!--   gauge(ai_rate, -->
-<!--         min = 0, -->
-<!--         max = 100, -->
-<!--         gaugeSectors(colors = "#FFC30B"), -->
-<!--         symbol = "%") -->
-<!-- }) -->
-<!-- ``` -->
-
-<!-- ### Greenpeace Expected Donors -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- renderGauge({ -->
-<!--   choice = df() -->
-<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-
-<!--   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-<!--   gauge(gp_rate,  -->
-<!--         min = 0,  -->
-<!--         max = 100, -->
-<!--         gaugeSectors(colors = "#3fad48"), -->
-<!--         symbol = "%") -->
-<!-- }) -->
-<!-- ``` -->
-
-<!-- ### Oxfam Expected Donors -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- renderGauge({ -->
-<!--   choice = df() -->
-<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-
-<!--   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-<!--   gauge(ox_rate,  -->
-<!--         min = 0,  -->
-<!--         max = 100, -->
-<!--         gaugeSectors(colors = "#006633"), -->
-<!--         symbol = "%") -->
-<!-- }) -->
-<!-- ``` -->
-
-<!-- ### Red Cross Expected Donors -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- renderGauge({ -->
-<!--   choice = df() -->
-<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2) -->
-
-<!--   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
-<!--   gauge(rc_rate,  -->
-<!--         min = 0,  -->
-<!--         max = 100, -->
-<!--         gaugeSectors(colors = "#660000"), -->
-<!--         symbol = "%") -->
-<!-- }) -->
-<!-- ``` -->
-
-<!-- Organizational Inputs {.tabset .tabset-fade} -->
-<!-- ------------------------------------- -->
-<!-- ### Amnesty International Inputs -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- selectInput("ai_issue",  -->
-<!--             label = "Select Issue Area:", -->
-<!--             choices = c("Emergency response", -->
-<!--                         "Environment", -->
-<!--                         "Human rights", -->
-<!--                         "Refugee relief")) -->
-
-<!-- selectInput("ai_fin_trans", -->
-<!--             label = "Select Financial transparency:", -->
-<!--             choices = c("Doesn’t engage in transparency", -->
-<!--                         "Engages in transparency")) -->
-
-<!-- selectInput("ai_account", -->
-<!--             label = "Select Financial Accountability:", -->
-<!--             choices = c("Doesn’t engage in financial accountability", -->
-<!--                         "Engages in financial accountability")) -->
-
-<!-- selectInput("ai_funding", -->
-<!--             label = "Select Funding source:", -->
-<!--             choices = c("Many small private donations", -->
-<!--                         "Handful of wealthy private donors", -->
-<!--                         "Government Grants")) -->
-
-<!-- selectInput("ai_gov_relat", -->
-<!--             label = "Select Relationship with host government", -->
-<!--             choices = c("Friendly relationship with government", -->
-<!--                         "Criticized by government",  -->
-<!--                         "Under government crackdown")) -->
-<!-- ``` -->
-
-<!-- ### Greenpeace Inputs -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- selectInput("gp_issue",  -->
-<!--             label = "Select Issue Area:", -->
-<!--             choices = c("Emergency response", -->
-<!--                         "Environment", -->
-<!--                         "Human rights", -->
-<!--                         "Refugee relief")) -->
-
-<!-- selectInput("gp_fin_trans", -->
-<!--             label = "Select Financial transparency:", -->
-<!--             choices = c("Doesn’t engage in transparency", -->
-<!--                         "Engages in transparency")) -->
-
-<!-- selectInput("gp_account", -->
-<!--             label = "Select Financial Accountability:", -->
-<!--             choices = c("Doesn’t engage in accountability", -->
-<!--                         "Engages in financial accountability")) -->
-
-<!-- selectInput("gp_funding", -->
-<!--             label = "Select Funding source:", -->
-<!--             choices = c("Many small private donations", -->
-<!--                         "Handful of wealthy private donors", -->
-<!--                         "Government Grants")) -->
-
-<!-- selectInput("gp_gov_relat", -->
-<!--             label = "Select Relationship with host government", -->
-<!--             choices = c("Friendly relationship with government", -->
-<!--                         "Criticized by government",  -->
-<!--                         "Under government crackdown")) -->
-<!-- ``` -->
-
-<!-- ### Oxfam Inputs -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- selectInput("ox_issue",  -->
-<!--             label = "Select Issue Area:", -->
-<!--             choices = c("Emergency response", -->
-<!--                         "Environment", -->
-<!--                         "Human rights", -->
-<!--                         "Refugee relief")) -->
-
-<!-- selectInput("ox_fin_trans", -->
-<!--             label = "Select Financial transparency:", -->
-<!--             choices = c("Doesn’t engage in transparency", -->
-<!--                         "Engages in transparency")) -->
-
-<!-- selectInput("ox_account", -->
-<!--             label = "Select Financial Accountability:", -->
-<!--             choices = c("Doesn’t engage in accountability", -->
-<!--                         "Engages in financial accountability")) -->
-
-<!-- selectInput("ox_funding", -->
-<!--             label = "Select Funding source:", -->
-<!--             choices = c("Many small private donations", -->
-<!--                         "Handful of wealthy private donors", -->
-<!--                         "Government Grants")) -->
-
-<!-- selectInput("ox_gov_relat", -->
-<!--             label = "Select Relationship with host government", -->
-<!--             choices = c("Friendly relationship with government", -->
-<!--                         "Criticized by government",  -->
-<!--                         "Under government crackdown")) -->
-<!-- ``` -->
-
-<!-- ### Red Cross Inputs -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- selectInput("rc_issue",  -->
-<!--             label = "Select Issue Area:", -->
-<!--             choices = c("Emergency response", -->
-<!--                         "Environment", -->
-<!--                         "Human rights", -->
-<!--                         "Refugee relief")) -->
-
-<!-- selectInput("rc_fin_trans", -->
-<!--             label = "Select Financial transparency:", -->
-<!--             choices = c("Doesn’t engage in transparency", -->
-<!--                         "Engages in transparency")) -->
-
-<!-- selectInput("rc_account", -->
-<!--             label = "Select Financial Accountability:", -->
-<!--             choices = c("Doesn’t engage in accountability", -->
-<!--                         "Engages in financial accountability")) -->
-
-<!-- selectInput("rc_funding", -->
-<!--             label = "Select Funding source:", -->
-<!--             choices = c("Many small private donations", -->
-<!--                         "Handful of wealthy private donors", -->
-<!--                         "Government Grants")) -->
-
-<!-- selectInput("rc_gov_relat", -->
-<!--             label = "Select Relationship with host government", -->
-<!--             choices = c("Friendly relationship with government", -->
-<!--                         "Criticized by government",  -->
-<!--                         "Under government crackdown")) -->
-<!-- ``` -->

### 2020-08-25 analysis/05_market_simulator.Rmd
Reformatted the RenderPlotly

@@
 ---
-title: "Market Simulator"
+title: "Why Donors Donate?"
 output: 
@@
 
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
-
     beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news] <- 1
@@
     beta_persona$p1_value[beta_persona$levels %in% input$p1_travel_developing] <- 1
-
-    # beta_persona$p1_value[beta_persona$levels == "Political Preference"] <- 1
-
+    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
     beta_persona$p1_value[beta_persona$levels %in% input$p1_institution_trust] <- 1
@@
     beta_persona$p3_value[beta_persona$levels %in% input$p3_political_pref] <- 1
-    # 
-    # beta_persona$p3_value[beta_persona$levels == "Political Preference"] <- input$p3_political_pref
-
     beta_persona$p3_value[beta_persona$levels %in% input$p3_institution_trust] <- 1
@@
 
-# reactive slider input ----
-
 ```
@@
 
-Market Share Per Persona
+Market Share
 --------------------------------------
@@
              geom_bar(position = "dodge", stat = "identity") +
-             labs(x="") + 
+             labs(x="", y = "Market Share") + 
              scale_fill_manual(values = c( "#FFC30B", "#006633", "#660000")) +
-             theme(legend.position = "right")
+             theme(legend.position = "right",
+                   panel.background = element_blank(),
+                   panel.grid.major.y = element_line(color = "#D3D3D3"))
     )

### 2020-08-28 analysis/05_market_simulator.Rmd
Changed Color, Reordered the Tabs, and Commented out the gauges

@@
              labs(x="", y = "Market Share") + 
-             scale_fill_manual(values = c( "#FFC30B", "#006633", "#660000")) +
+             scale_fill_manual(values = c( "#FFC30B", "#28a153", "#c23838")) +
              theme(legend.position = "right",
@@
 
-Organizations and Personas {.tabset .tabset-fade}
+Personas And Organizations {.tabset .tabset-fade}
 --------------------------------------------------
-### Org 1
-
-```{r ai org inputs}
-
-# Some kind of Org Id that could select the organization you are looking at? Not sure how to make it change the label in the graph
-
-textInput("ai_id",
-          label = "Organization Name",
-          value = "Organization 1",
-          placeholder = "Enter Organiation Name",
-          width = "200px")
-
-selectInput("ai_issue", 
-            label = "Select Issue Area:",
-            choices = c("Emergency response",
-                        "Environment",
-                        "Human rights",
-                        "Refugee relief"),
-            width = "200px")
-
-selectInput("ai_fin_trans",
-            label = "Select Financial transparency:",
-            choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"),
-            width = "200px")
-
-selectInput("ai_account",
-            label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in financial accountability",
-                        "Engages in financial accountability"),
-            width = "200px")
-
-selectInput("ai_funding",
-            label = "Select Funding source:",
-            choices = c("Many small private donations",
-                        "Handful of wealthy private donors",
-                        "Government Grants"),
-            width = "200px")
-
-selectInput("ai_gov_relat",
-            label = "Select Relationship with host government",
-            choices = c("Friendly relationship with government",
-                        "Criticized by government", 
-                        "Under government crackdown"),
-            width = "200px")
-
-```
-
-```{r ai gauge}
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
-
-  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(ai_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#FFC30B"),
-        symbol = "%")
-})
-
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
-
-  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(ai_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#3fad48"),
-        symbol = "%")
-})
-
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-
-  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(ai_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#006633"),
-        symbol = "%")
-})
-```
-
-### Org 2
-
-```{r gp org inputs}
-
-textInput("gp_id",
-          label = "Organization Name",
-          value = "Organization 2",
-          placeholder = "Enter Organiation Name"
-)
-
-selectInput("gp_issue", 
-            label = "Select Issue Area:",
-            choices = c("Emergency response",
-                        "Environment",
-                        "Human rights",
-                        "Refugee relief"))
-
-selectInput("gp_fin_trans",
-            label = "Select Financial transparency:",
-            choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"))
-
-selectInput("gp_account",
-            label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in accountability",
-                        "Engages in financial accountability"))
-
-selectInput("gp_funding",
-            label = "Select Funding source:",
-            choices = c("Many small private donations",
-                        "Handful of wealthy private donors",
-                        "Government Grants"))
-
-selectInput("gp_gov_relat",
-            label = "Select Relationship with host government",
-            choices = c("Friendly relationship with government",
-                        "Criticized by government", 
-                        "Under government crackdown"))
-```
-
-```{r gp gauge}
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
-
-  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(gp_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#FFC30B"),
-        symbol = "%")
-})
-
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
-
-  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(gp_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#3fad48"),
-        symbol = "%")
-})
-
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-
-  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(gp_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#006633"),
-        symbol = "%")
-})
-```
-
-### Org 3
-
-```{r ox org inputs}
-
-textInput("ox_id",
-          label = "Organization Name",
-          value = "Organization 3",
-          placeholder = "Enter Organiation Name"
-)
-
-selectInput("ox_issue", 
-            label = "Select Issue Area:",
-            choices = c("Emergency response",
-                        "Environment",
-                        "Human rights",
-                        "Refugee relief"))
-
-selectInput("ox_fin_trans",
-            label = "Select Financial transparency:",
-            choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"))
-
-selectInput("ox_account",
-            label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in accountability",
-                        "Engages in financial accountability"))
-
-selectInput("ox_funding",
-            label = "Select Funding source:",
-            choices = c("Many small private donations",
-                        "Handful of wealthy private donors",
-                        "Government Grants"))
-
-selectInput("ox_gov_relat",
-            label = "Select Relationship with host government",
-            choices = c("Friendly relationship with government",
-                        "Criticized by government", 
-                        "Under government crackdown"))
-```
-
-```{r ox gauge}
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
-
-  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(ox_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#FFC30B"),
-        symbol = "%")
-})
-
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
-
-  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(ox_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#3fad48"),
-        symbol = "%")
-})
-
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-
-  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(ox_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#006633"),
-        symbol = "%")
-})
-```
-
-### Org 4
-
-```{r rc org inputs}
-
-textInput("rc_id",
-          label = "Organization Name",
-          value = "Organization 4",
-          placeholder = "Enter Organiation Name"
-)
-
-selectInput("rc_issue", 
-            label = "Select Issue Area:",
-            choices = c("Emergency response",
-                        "Environment",
-                        "Human rights",
-                        "Refugee relief"))
-
-selectInput("rc_fin_trans",
-            label = "Select Financial transparency:",
-            choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"))
-
-selectInput("rc_account",
-            label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in accountability",
-                        "Engages in financial accountability"))
-
-selectInput("rc_funding",
-            label = "Select Funding source:",
-            choices = c("Many small private donations",
-                        "Handful of wealthy private donors",
-                        "Government Grants"))
-
-selectInput("rc_gov_relat",
-            label = "Select Relationship with host government",
-            choices = c("Friendly relationship with government",
-                        "Criticized by government", 
-                        "Under government crackdown"))
-```
-
-```{r rc gauge}
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
-
-  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(rc_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#FFC30B"),
-        symbol = "%")
-})
-
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
-
-  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(rc_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#3fad48"),
-        symbol = "%")
-})
-
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-
-  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(rc_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#006633"),
-        symbol = "%")
-})
-```
 
@@
 
-```{r persona 1 gauge}
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
-
-  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(ai_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#FFC30B"),
-        symbol = "%")
-})
-
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
-
-  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(gp_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#3fad48"),
-        symbol = "%")
-})
-
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-
-  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(ox_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#006633"),
-        symbol = "%")
-})
-
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-
-  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(rc_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#660000"),
-        symbol = "%")
-})
-```
-
 ### Persona 2
@@
 
-```{r persona 2 gauge}
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
-
-  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(ai_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#FFC30B"),
-        symbol = "%")
-})
-
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
-
-  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(gp_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#3fad48"),
-        symbol = "%")
-})
-
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-
-  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(ox_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#006633"),
-        symbol = "%")
-})
-
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-
-  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(rc_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#660000"),
-        symbol = "%")
-})
-```
-
 ### Persona 3
@@
 
-```{r persona 3 gauge}
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
-
-  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(ai_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#FFC30B"),
-        symbol = "%")
-})
-
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
-
-  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(gp_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#3fad48"),
-        symbol = "%")
-})
-
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-
-  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(ox_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#006633"),
-        symbol = "%")
-})
-
-renderGauge({
-  choice = df()
-  per_choice = p()
-
-    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
-
-  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-
-  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-
-  gauge(rc_rate,
-        min = 0,
-        max = 100,
-        gaugeSectors(colors = "#660000"),
-        symbol = "%")
-})
+### Org 1
+
+```{r ai org inputs}
+
+# Some kind of Org Id that could select the organization you are looking at? Not sure how to make it change the label in the graph
+
+textInput("ai_id",
+          label = "Organization Name",
+          value = "Organization 1",
+          placeholder = "Enter Organiation Name")
+
+selectInput("ai_issue", 
+            label = "Select Issue Area:",
+            choices = c("Emergency response",
+                        "Environment",
+                        "Human rights",
+                        "Refugee relief"))
+
+selectInput("ai_fin_trans",
+            label = "Select Financial transparency:",
+            choices = c("Doesn’t engage in transparency",
+                        "Engages in transparency"))
+
+selectInput("ai_account",
+            label = "Select Financial Accountability:",
+            choices = c("Doesn’t engage in financial accountability",
+                        "Engages in financial accountability"))
+
+selectInput("ai_funding",
+            label = "Select Funding source:",
+            choices = c("Many small private donations",
+                        "Handful of wealthy private donors",
+                        "Government Grants"))
+
+selectInput("ai_gov_relat",
+            label = "Select Relationship with host government",
+            choices = c("Friendly relationship with government",
+                        "Criticized by government", 
+                        "Under government crackdown"))
+
+```
+
+### Org 2
+
+```{r gp org inputs}
+
+textInput("gp_id",
+          label = "Organization Name",
+          value = "Organization 2",
+          placeholder = "Enter Organiation Name"
+)
+
+selectInput("gp_issue", 
+            label = "Select Issue Area:",
+            choices = c("Emergency response",
+                        "Environment",
+                        "Human rights",
+                        "Refugee relief"))
+
+selectInput("gp_fin_trans",
+            label = "Select Financial transparency:",
+            choices = c("Doesn’t engage in transparency",
+                        "Engages in transparency"))
+
+selectInput("gp_account",
+            label = "Select Financial Accountability:",
+            choices = c("Doesn’t engage in accountability",
+                        "Engages in financial accountability"))
+
+selectInput("gp_funding",
+            label = "Select Funding source:",
+            choices = c("Many small private donations",
+                        "Handful of wealthy private donors",
+                        "Government Grants"))
+
+selectInput("gp_gov_relat",
+            label = "Select Relationship with host government",
+            choices = c("Friendly relationship with government",
+                        "Criticized by government", 
+                        "Under government crackdown"))
+```
+
+### Org 3
+
+```{r ox org inputs}
+
+textInput("ox_id",
+          label = "Organization Name",
+          value = "Organization 3",
+          placeholder = "Enter Organiation Name"
+)
+
+selectInput("ox_issue", 
+            label = "Select Issue Area:",
+            choices = c("Emergency response",
+                        "Environment",
+                        "Human rights",
+                        "Refugee relief"))
+
+selectInput("ox_fin_trans",
+            label = "Select Financial transparency:",
+            choices = c("Doesn’t engage in transparency",
+                        "Engages in transparency"))
+
+selectInput("ox_account",
+            label = "Select Financial Accountability:",
+            choices = c("Doesn’t engage in accountability",
+                        "Engages in financial accountability"))
+
+selectInput("ox_funding",
+            label = "Select Funding source:",
+            choices = c("Many small private donations",
+                        "Handful of wealthy private donors",
+                        "Government Grants"))
+
+selectInput("ox_gov_relat",
+            label = "Select Relationship with host government",
+            choices = c("Friendly relationship with government",
+                        "Criticized by government", 
+                        "Under government crackdown"))
+```
+
+### Org 4
+
+```{r rc org inputs}
+
+textInput("rc_id",
+          label = "Organization Name",
+          value = "Organization 4",
+          placeholder = "Enter Organiation Name"
+)
+
+selectInput("rc_issue", 
+            label = "Select Issue Area:",
+            choices = c("Emergency response",
+                        "Environment",
+                        "Human rights",
+                        "Refugee relief"))
+
+selectInput("rc_fin_trans",
+            label = "Select Financial transparency:",
+            choices = c("Doesn’t engage in transparency",
+                        "Engages in transparency"))
+
+selectInput("rc_account",
+            label = "Select Financial Accountability:",
+            choices = c("Doesn’t engage in accountability",
+                        "Engages in financial accountability"))
+
+selectInput("rc_funding",
+            label = "Select Funding source:",
+            choices = c("Many small private donations",
+                        "Handful of wealthy private donors",
+                        "Government Grants"))
+
+selectInput("rc_gov_relat",
+            label = "Select Relationship with host government",
+            choices = c("Friendly relationship with government",
+                        "Criticized by government", 
+                        "Under government crackdown"))
 ```
@@
 
-```{r plot ai plot}
+```{r persona 1 gauge commented}
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#     
+#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+# 
+#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ai_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#FFC30B"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+# 
+#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(gp_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#3fad48"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ox_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#006633"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(rc_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#660000"),
+#         symbol = "%")
+# })
+```
+
+```{r persona 2 gauge commented}
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#     
+#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+# 
+#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ai_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#FFC30B"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+# 
+#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(gp_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#3fad48"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ox_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#006633"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(rc_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#660000"),
+#         symbol = "%")
+# })
+```
+
+```{r persona 3 gauge commented}
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#     
+#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+# 
+#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ai_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#FFC30B"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+# 
+#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(gp_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#3fad48"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ox_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#006633"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(rc_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#660000"),
+#         symbol = "%")
+# })
+```
+
+```{r ai gauge commented}
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#     
+#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+# 
+#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ai_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#FFC30B"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+# 
+#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ai_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#006633"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ai_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#b50909"),
+#         symbol = "%")
+# })
+```
+
+```{r plot ai plot commented}
 # renderPlotly({
@@
 
-```{r plot gp plot}
+```{r gp gauge commented}
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#     
+#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+# 
+#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(gp_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#FFC30B"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+# 
+#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(gp_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#3fad48"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(gp_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#006633"),
+#         symbol = "%")
+# })
+```
+
+```{r plot gp plot commented}
 # renderPlotly({
@@
 
-```{r plot ox plot}
+```{r ox gauge commented}
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#     
+#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+# 
+#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ox_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#FFC30B"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+# 
+#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ox_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#3fad48"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ox_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#006633"),
+#         symbol = "%")
+# })
+```
+
+```{r plot ox plot commented}
 # renderPlotly({
@@
 
-```{r plot rc plot}
+```{r rc gauge commented}
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#     
+#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+# 
+#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(rc_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#FFC30B"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+# 
+#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(rc_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#3fad48"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(rc_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#006633"),
+#         symbol = "%")
+# })
+```
+
+```{r plot rc plot commented}
 # renderPlotly({

### 2020-08-31 analysis/05_market_simulator.Rmd
Added commented to explain plotly code

@@
 
+  # Persona 1 
     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-#add step to matrix multiply the persona reactive element to the persona data and the public_political beta table.
-
+
+  # Expected Utility
   ai_exp_util1 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta1)),2)
@@
 
+  # Market Share
   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
@@
 
+  # Persona 2
     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
 
+  # Expected Utility
   ai_exp_util2 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta2)),2)
@@
 
+  # Market Share
   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
@@
 
+  # Persona 3
     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
 
+  # Expected Utility
   ai_exp_util3 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta3)),2)
@@
 
+  # Market Share
   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
@@
 
+  # Data for Plotly
   data <- c(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1, ai_rate1, gp_rate1, ox_rate1, rc_rate1, 
@@
 
+  # Empty dataframe
   df <- as.data.frame(matrix(data, 24, 1))
 
+  # Organization name inputs
   df[,2] <- c(input$ai_id, input$gp_id, input$ox_id, input$rc_id)
+  # Type of value
   df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
+  # Persona name inputs
   df[,4] <- c(rep(input$p1_id,8), rep(input$p2_id, 8), rep(input$p3_id, 8))
 
+  # Rename columns
   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
 
-  ggplotly(df %>% filter(Type == "Market Share") %>%
+  ggplotly(df %>% 
+             # Only care about the Market Share right now
+             filter(Type == "Market Share") %>% 
+             # Factor Organization and Persona with ordered=TRUE so the order doesn't change to alphabetical as names are created
              mutate(

### 2020-09-01 analysis/01_experimental-design.Rmd
Confirming hold-out levels and recoding continuous variables

--- 2019-06-21 analysis/01_check-design.Rmd
@@
 # Load the design and check level balance
+
+The experimental design was created as part of the conjoint study in Qualtrics.
+Here we check to make sure that there is a balance across attribute levels (i.e., levels show up a roughly equal number of times for each attribute).
 
@@
 
+Now we prepare the experimental design for use in estimating the model by dropping the first level of each attribute, which are all discrete, as the reference level.
+
 ```{r check-design, warning=FALSE, message=FALSE}
@@
 }
+
+# Rename the variables.
+colnames(dummy_design)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")
 

### 2020-09-01 analysis/02_clean-data.Rmd
Confirming hold-out levels and recoding continuous variables

--- 2019-06-25 analysis/02_clean-data.Rmd
@@
     ),
+    # *Q2.2*: How often do you follow international news? 
+    # 
+    # - Always
+    # - Sometimes
+    # - Never
+    Q2.2 = fct_relevel(
+      factor(Q2.2, labels = c("Always", "Sometimes", "Never")), 
+      c("Never", "Sometimes", "Always")
+    ),
     # *Q2.4*: How often would you say you follow what's going on in government and public affairs?
@@
     ),
+    # *Q2.6*: How much did you donate to charity last year?
+    # 
+    # - \$1 to \$49
+    # - \$50 to \$99
+    # - \$100 to \$499
+    # - \$500 to \$999
+    # - \$1000 to \$4,999
+    # - \$5000 to \$9,999
+    # - \$10,000 or more
+    Q2.6 = factor(
+      Q2.6, 
+      labels = c(
+        "$1-$49", "$50-$99", "$100-$499", "$500-$999", 
+        "$1000-$4,999", "$5000-$9,999", "$10,000+"),
+      ordered = TRUE
+    ),
+    # *Q2.7*: On a scale of not at all important (1) to essential (7), how important is it for you to trust charities?
+    # 
+    # - 1 (Not at all important)
+    # - 2
+    # - 3
+    # - 4
+    # - 5
+    # - 6
+    # - 7 (Essential)
+    Q2.7 = factor(
+      Q2.7,
+      labels = c(
+        "Not at all important", "Very unimportant", "Somewhat unimportant", 
+        "Neutral", "Somewhat important", "Very important", "Essential"
+      ),
+      ordered = TRUE
+    ),
+    # *Q2.8*: On a scale of no trust at all (1) to complete trust (7), how much do you trust charities?
+    # 
+    # - 1 (No trust at all)
+    # - 2
+    # - 3
+    # - 4
+    # - 5
+    # - 6
+    # - 7 (Complete trust)
+    Q2.8 = factor(
+      Q2.8,
+      labels = c(
+        "No trust at all", "Very little trust", "Little trust", 
+        "Neutral", "Some trust", "A lot of trust", "Complete trust"
+      ),
+      ordered = TRUE
+    ),
+    # *Q2.9*: Have you volunteered in the past 12 months?
+    # 
+    # - Yes
+    # - No
+    Q2.9 = fct_relevel(
+      factor(Q2.9, labels = c("Yes", "No")), 
+      c("No", "Yes")
+    ),
     # *Q2.10*: How often do you volunteer?
@@
       levels = c("Haven't volunteered in past 12 months", "Rarely", "More than once a month, less than once a year", "At least once a month")
+    ),
+    # *Q5.1*: Did you vote in the last election?
+    # 
+    # - Yes
+    # - No
+    Q5.1 = fct_relevel(
+      factor(Q5.1, labels = c("Yes", "No")), 
+      c("No", "Yes")
+    ),
+    # *Q5.2*: On a scale of extremely liberal (1) to extremely conservative (7), how would you describe your political views?
+    # 
+    # - 1 (Extremely liberal)
+    # - 2
+    # - 3
+    # - 4
+    # - 5
+    # - 6
+    # - 7 (Extremely conservative)
+    Q5.2 = factor(
+      Q5.2,
+      labels = c(
+        "Extremely liberal", "Somewhat liberal", "Slightly liberal", "Moderate",
+        "Slightly conservative", "Somewhat conservative", "Extremely conservative"
+      ),
+      ordered = TRUE
     ),
@@
       levels = c("Not involved", "Involved")
+    ),
+    # *Q5.6*: On a scale of no trust (1) to complete trust (7), how much do you trust political institutions and the state?
+    # 
+    # - 1 (No trust)
+    # - 2
+    # - 3
+    # - 4
+    # - 5
+    # - 6
+    # - 7 (Complete trust)
+    Q5.6 = factor(
+      Q5.6,
+      labels = c(
+        "No trust at all", "Very little trust", "Little trust", 
+        "Neutral", "Some trust", "A lot of trust", "Complete trust"
+      ),
+      ordered = TRUE
+    ),
+    # *Q5.7*: Have you ever traveled to a developing country? 
+    # 
+    # - Yes
+    # - No
+    Q5.7 = fct_relevel(
+      factor(Q5.7, labels = c("Yes", "No")), 
+      c("No", "Yes")
     ),
@@
       levels = c("Not important", "Important")
+    ),
+    # *Q5.11*: On a scale of strongly agree (1) to strongly disagree (7), rate your response to the following statement: People should be more charitable towards others in society.
+    # 
+    # - 1 (Strongly agree)
+    # - 2
+    # - 3
+    # - 4
+    # - 5
+    # - 6
+    # - 7 (Strongly disagree)
+    Q5.11 = fct_relevel(
+      factor(
+        Q5.11,
+        labels = c(
+          "Strongly agree", "Agree", "Somewhat agree", 
+          "Neutral", "Somewhat disagree", "Disagree", "Strongly disagree"
+        ),
+        c(
+          "Strongly disagree", "Disagree", "Somewhat disagree",
+          "Neutral", "Somewhat agree", "Agree", "Strongly agree"
+        )
+      )
+    ),
+    # *Q5.12*: What is your gender?
+    # 
+    # - Male
+    # - Female
+    # - Transgender
+    # - Prefer not to say
+    # - Other: _________
+    Q5.12 = factor(
+      Q5.12, 
+      labels = c(
+        "Male", "Female", "Transgender", 
+        "Prefer not to say", "Other"
+      ), 
+      ordered = TRUE
+    ),
+    # *Q5.13*: Are you now married, widowed, divorced, separated, or never married?
+    # 
+    # - Married
+    # - Widowed
+    # - Divorced
+    # - Separated
+    # - Never married
+    Q5.13 = factor(
+      Q5.13, 
+      labels = c(
+        "Married", "Widowed", "Divorced", 
+        "Separated", "Never married"
+      ), 
+      ordered = TRUE
+    ),
+    # *Q5.14*: What is the highest degree or level of school you have completed?
+    # 
+    # - Less than high school
+    # - High school graduate
+    # - Some college
+    # - 2 year degree
+    # - 4 year degree 
+    # - Graduate or professional degree
+    # - Doctorate
+    Q5.14 = factor(
+      Q5.14, 
+      labels = c(
+        "Less than high school", "High school graduate", 
+        "Some college", "2 year degree", "4 year degree", 
+        "Graduate or professional degree", "Doctorate"
+      ),
+      ordered = TRUE
     ),

### 2020-09-02 analysis/02_clean-data.Rmd
Moved all of the data transformation into the data transformation block of 02_clean-data.Rmd

@@
   rename(version = vers_CBCONJOINT) %>% 
+  select(-contains("_TEXT")) %>% 
   select(id, version, Q1.1:Q5.18)
@@
       c("Never", "Sometimes", "Always")
-    ),
+    )
+  ) %>% 
+  mutate_at(
+    # *Q2.3*: Which mediums do you use to follow news? (Select all that apply.)
+    # 
+    # - TV
+    # - Print 
+    # - Online (excluding social media) 
+    # - Social media
+    # - Radio
+    # - Email newsletters
+    # - News app
+    vars(contains("Q2.3")), coalesce, 0
+  ) %>%
+  mutate(
     # *Q2.4*: How often would you say you follow what's going on in government and public affairs?
@@
     ),
+    # *Q5.10*: What is your current religion, if any?
+    # 
+    # - Catholic (including Roman Catholic and Orthodox)
+    # - Protestant (United Church of Canada, Anglican, Orthodox, Baptist, Lutheran)
+    # - Christian Orthodox
+    # - Jewish
+    # - Muslim
+    # - Sikh
+    # - Hindu
+    # - Buddhist
+    # - Atheist (do not believe in God)
+    # - Other: _________
+    Q5.10 = factor(
+      Q5.10, 
+      labels = c(
+        "Catholic", "Protestant", "Christian Orthodox", "Jewish", 
+        "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other"), 
+      ordered = TRUE
+    ),
     # *Q5.11*: On a scale of strongly agree (1) to strongly disagree (7), rate your response to the following statement: People should be more charitable towards others in society.
@@
       levels = c("Less than median", "More than median")
-    ),
+    )
+  ) %>% 
+  mutate_at(
+    # *Q5.16*: Choose one or more races that you consider yourself to be:
+    # 
+    # - White
+    # - Black or African American
+    # - American Indian or Alaska Native
+    # - Asian
+    # - Native Hawaiian or Pacific Islander
+    # - Other: _________
+    vars(contains("Q5.16")), coalesce, 0
+  ) %>% 
+  mutate(
     # *Q5.17*: How old are you?

### 2020-09-02 analysis/model-calibration.R

@@ -16,7 +16,7 @@ design <- read_csv(here::here("data", "derived_data", "dummy_design.csv")) %>%
   )
 
 intercept <- 0                            # Intercept-only.
-public_affairs <- 0                       # Public affairs: Public affairs knowledge + Public affairs activity.
+public_affairs <- 1                       # Public affairs: Public affairs knowledge + Public affairs activity.
 political_ideology <- 0                   # Political ideology.
 social_views <- 0                         # Social views: Public affairs trust + Social ideology + Religiosity.
 charity_voluntarism <- 0                  # Charity and voluntarism: Charity trust, Charity activity, Volunteer activity, etc.
@@ -24,7 +24,7 @@ demographics <- 0                         # Demographics: Gender, Marital status
 public_political <- 0                     # Public affairs + Political ideology
 public_political_social <- 0              # Public affairs + Political ideology + Social views
 public_political_social_charity <- 0      # Public affairs + Political ideology + Social views + Charity and voluntarism
-public_political_social_charity_demo <- 1 # Public affairs + Political ideology + Social views + Charity and voluntarism + Demographics
+public_political_social_charity_demo <- 0 # Public affairs + Political ideology + Social views + Charity and voluntarism + Demographics
 
 # Restructure choice data Y.
 Y <- final_data %>%
@@ -42,12 +42,12 @@ X <- array(
   )
 )
 
-# Add the outside option coded as all zeros.
+# Reintroduce org1 and add the outside option coded as all zeros.
 for (n in 1:dim(X)[1]) {
   # Filter for respondent n.
   X_n <- design %>% filter(version == final_data$version[n])
   for (s in 1:dim(X)[2]) {
-    # Filter for task s.
[…]

### 2020-09-02 analysis/02_clean-data.Rmd
Save out final design so we can load it for each model run

@@
 
-```{r transform-data}
+## Covariates
+
+```{r transform-covariates}
 data <- data %>% 
@@
 
+## Design matrix
+
+```{r transform-design}
+# Load design
+design <- read_csv(here::here("data", "derived_data", "dummy_design.csv")) %>%
+  select(-X1) %>%
+  rename(
+    version = question_set,
+    task = question,
+    alt = choice
+  )
+
+# Create the array for design X.
+X <- array(
+  data = NA,
+  dim = c(
+    nrow(data),             # Number of respondents.
+    max(design$task),       # Number of choice tasks per respondent.
+    (max(design$alt) + 1),  # Number of product alternatives per choice task.
+    (ncol(design) - 3 + 1)  # Number of (estimable) attribute levels.
+  )
+)
+
+# Reintroduce org1 and add the outside option coded as all zeros.
+for (n in 1:dim(X)[1]) {
+  # Filter for respondent n.
+  X_n <- design %>% filter(version == data$version[n])
+  for (s in 1:dim(X)[2]) {
+    # Filter for task s and include placeholder for org1.
+    X_s <- X_n %>%
+      filter(task == s) %>%
+      mutate(org1 = 0) %>%
+      select(org1, org2:gov_rel3)
+    for (p in 1:(dim(X)[3]-1)) {
+      # Filter for task s and alt p orgs.
+      X_p <- X_n %>%
+        filter(task == s, alt == p) %>%
+        select(org2:org4) %>%
+        as_vector()
+      # Fill in org1 to complte org intercept.
+      X_s[p, "org1"] <- ifelse(sum(X_p) == 1, 0, 1)
+    }
+    # Save modified design, including outside option.
+    X[n, s,,] <- rbind(X_s, rep(0, ncol(X_s))) %>% as.matrix()
+  }
+}
+```
+
 # Save clean data with transformations
@@
 write_rds(data, here("data", "derived_data", "final_data.rds"))
+write_rds(X, here("data", "derived_data", "final_design.rds"))
 ```

### 2020-09-02 analysis/02_clean-data.Rmd
Model calibration is now detailed (but not evaluted) in 03_analysis.Rmd

@@
   mutate(
+    Q2.3_1 = factor(Q2.3_1, labels = c("No TV", "TV")),
+    Q2.3_2 = factor(Q2.3_2, labels = c("No Print", "Print")),
+    Q2.3_3 = factor(Q2.3_3, labels = c("No Online (excluding social media)", "Online (excluding social media)")),
+    Q2.3_4 = factor(Q2.3_4, labels = c("No Social media", "Social media")),
+    Q2.3_5 = factor(Q2.3_5, labels = c("No Radio", "Radio")),
+    Q2.3_6 = factor(Q2.3_6, labels = c("No Email newsletters", "Email newsletters")),
+    Q2.3_7 = factor(Q2.3_7, labels = c("No News app", "News app")),
     # *Q2.4*: How often would you say you follow what's going on in government and public affairs?

### 2020-09-02 analysis/03_analysis.Rmd
Model calibration is now detailed (but not evaluted) in 03_analysis.Rmd

@@
 ---
-title: "Results"
+title: "Analysis and results"
 author: "Andrew Heiss, Marc Dotson, and Suparna Chaudhry"
@@
 library(tidybayes)
-library(bayesm)
 library(ggridges)
@@
 set.seed(1234)
+
+# Set Stan options
+options(mc.cores = parallel::detectCores())
+rstan_options(auto_write = TRUE)
+```
+
+# Model calibration
+
+After selecting the model we'd like to run, model calibration proceeds as follows.
+Note that model calibration is run in a separate R script given how long it takes to run each model.
+Model output can be loaded for analysis in the next section.
+
+```{r model-calibration, eval=FALSE}
+intercept <- 0                            # Intercept-only
+public_affairs <- 1                       # Public affairs
+political_ideology <- 0                   # Political ideology
+social_views <- 0                         # Social views
+charity_voluntarism <- 0                  # Charity and voluntarism
+demographics <- 0                         # Demographics
+public_political <- 0                     # Public affairs + Political ideology
+public_political_social <- 0              # + Social views
+public_political_social_charity <- 0      # + Charity and voluntarism
+public_political_social_charity_demo <- 0 # + Demographics
+
+# Load data and design
+final_data <- read_rds(here::here("data", "derived_data", "final_data.rds"))
+X <- read_rds(here::here("data", "derived_data", "final_design.rds"))
+
+# Restructure choice data Y
+Y <- final_data %>%
+  select(contains("Q4")) %>%
+  as.matrix()
+
+# Restructure covariate matrix Z
+if (intercept == 1) {
+  Z <- matrix(data = 1, nrow = dim(X)[1], ncol = 1)
+}
+if (public_affairs == 1) {
+  Z <- final_data %>%
+    select(
+      Q2.1, Q2.2, Q2.3_1:Q2.3_7, Q2.4, Q5.7 # Public affairs
+    )
+}
+if (political_ideology == 1) {
+  Z <- final_data %>%
+    select(
+      Q5.2 # Political ideology
+    )
+}
+if (social_views == 1) {
+  Z <- final_data %>%
+    select(
+      Q5.6, Q5.11, Q5.8, Q5.9, Q5.10 # Social views
+    )
+}
+if (charity_voluntarism == 1) {
+  Z <- final_data %>%
+    select(
+      Q2.7, Q2.8, Q2.5, Q2.6, Q2.9, Q2.10, Q5.4, Q5.5, Q5.3_1:Q5.3_10 # Charity and voluntarism
+    )
+}
+if (demographics == 1) {
+  Z <- final_data %>%
+    select(
+      Q5.12, Q5.13, Q5.14, Q5.15, Q5.16_1:Q5.16_6, Q5.17 # Demographics
+    )
+}
+if (public_political == 1) {
+  Z <- final_data %>%
+    select(
+      Q2.1, Q2.2, Q2.3_1:Q2.3_7, Q2.4, Q5.7, # Public affairs
+      Q5.2                                   # Political ideology
+    )
+}
+if (public_political_social == 1) {
+  Z <- final_data %>%
+    select(
+      Q2.1, Q2.2, Q2.3_1:Q2.3_7, Q2.4, Q5.7, # Public affairs
+      Q5.2,                                  # Political ideology
+      Q5.6, Q5.11, Q5.8, Q5.9, Q5.10         # Social views
+    )
+}
+if (public_political_social_charity == 1) {
+  Z <- final_data %>%
+    select(
+      Q2.1, Q2.2, Q2.3_1:Q2.3_7, Q2.4, Q5.7,                           # Public affairs
+      Q5.2,                                                            # Political ideology
+      Q5.6, Q5.11, Q5.8, Q5.9, Q5.10,                                  # Social views
+      Q2.7, Q2.8, Q2.5, Q2.6, Q2.9, Q2.10, Q5.4, Q5.5, Q5.3_1:Q5.3_10  # Charity and voluntarism
+    )
+}
+if (public_political_social_charity_demo == 1) {
+  Z <- final_data %>%
+    select(
+      Q2.1, Q2.2, Q2.3_1:Q2.3_7, Q2.4, Q5.7,                           # Public affairs
+      Q5.2,                                                            # Political ideology
+      Q5.6, Q5.11, Q5.8, Q5.9, Q5.10,                                  # Social views
+      Q2.7, Q2.8, Q2.5, Q2.6, Q2.9, Q2.10, Q5.4, Q5.5, Q5.3_1:Q5.3_10, # Charity and voluntarism
+      Q5.12, Q5.13, Q5.14, Q5.15, Q5.16_1:Q5.16_6, Q5.17               # Demographics
+    )
+}
+
+# Replace factor labels with levels
+Z <- Z %>%
+  mutate_if(is.factor, as.integer) %>%
+  mutate_if(is.integer, as.factor)
+
+# Pad the variables names with _
+colnames(Z) <- str_c(colnames(Z), "_")
+
+# Use the output of lm to get a dummy-coded version of the covariate matrix Z
+Z$y <- matrix(rnorm(nrow(Z)), ncol = 1)
+out <- lm(y ~ ., Z, x = TRUE)
+
+# Save out Z as a matrix, including an intercept
+Z <- tibble(intercept = rep(1, dim(X)[1])) %>%
+  bind_cols(as_tibble(out$x[,-1])) %>%
+  as.matrix()
+
+# Specify the data for calibration in a list
+data <- list(
+  R = dim(X)[1],      # Number of respondents
+  S = dim(X)[2],      # Number of choice tasks
+  A = dim(X)[3],      # Number of choice alternatives
+  I = dim(X)[4],      # Number of (estimable) attribute levels
+  J = ncol(Z),        # Number of respondent-level covariates
+
+  Gamma_mean = 0,      # Mean of population-level means
+  Gamma_scale = 1,     # Scale of population-level means
+  Omega_shape = 5,     # Shape of population-level scale
+  tau_mean = 0,        # Mean of population-level scale
+  tau_scale = 10,      # Scale of population-level scale
+
+  Y = Y,               # Matrix of observed choices
+  X = X,               # Array of experimental designs per choice task
+  Z = Z                # Matrix of respondent-level covariates
+)
+
+# Run the model and save data and model output
+fit <- stan(
+  file = here::here("src", "stan_files", "hmnl_noncentered.stan"),
+  data = data,
+  iter = 10000,
+  thin = 5,
+  seed = 42
+)
+run <- list(data = data, fit = fit)
+if (intercept == 1) write_rds(run, here::here("analysis", "output", "model_runs", "intercept_noncentered.rds"))
+if (public_affairs == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_affairs.rds"))
+if (political_ideology == 1) write_rds(run, here::here("analysis", "output", "model_runs", "political_ideology.rds"))
+if (social_views == 1) write_rds(run, here::here("analysis", "output", "model_runs", "social_views.rds"))
+if (charity_voluntarism == 1) write_rds(run, here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
+if (demographics == 1) write_rds(run, here::here("analysis", "output", "model_runs", "demographics.rds"))
+if (public_political == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political.rds"))
+if (public_political_social == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social.rds"))
+if (public_political_social_charity == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
+if (public_political_social_charity_demo == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
+```
+
+The model is calibrated using a non-centered parameterization of a hierarchical multinomial logit model.
+
+```{stan hmnl-noncentered, output.var="hmnl_noncentered", eval=FALSE}
+// Index values, hyperprior values, observations, and covariates.
+data {
+  int<lower = 1> R;                  // Number of respondents.
+  int<lower = 1> S;                  // Number of choice tasks.
+  int<lower = 2> A;                  // Number of choice alternatives.
+  int<lower = 1> I;                  // Number of observation-level covariates.
+  int<lower = 1> J;                  // Number of population-level covariates.
+
+  real Gamma_mean;                   // Mean of population-level means.
+  real<lower=0> Gamma_scale;         // Scale of population-level means.
+  real<lower=0> Omega_shape;         // Shape of population-level scale.
+  real tau_mean;                     // Mean of population-level scale.
+  real<lower=0> tau_scale;           // Scale of population-level scale.
+
+  int<lower = 1, upper = A> Y[R, S]; // Matrix of observations.
+  matrix[A, I] X[R, S];              // Array of observation-level covariates.
+  matrix[R, J] Z;                    // Matrix of population-level covariates.
+}
+
+// Parameters and hyperparameters.
+parameters {
+  matrix[J, I] Gamma;                // Matrix of population-level hyperparameters.
+  corr_matrix[I] Omega;              // Population model correlation matrix hyperparameters.
+  vector<lower = 0>[I] tau;          // Population model vector of scale hyperparameters.
+  matrix[R, I] Delta;                // Matrix of non-centered observation-level parameters.
+}
+
+// Deterministic transformation.
+transformed parameters {
+  // Matrix of centered observation-level parameters.
+  matrix[R, I] Beta;
+
+  // Non-centered parameterization.
+  for (r in 1:R) {
+    Beta[r,] = Z[r,] * Gamma + Delta[r,] * quad_form_diag(Omega, tau);
+  }
+}
+
+// Hierarchical multinomial logit model.
+model {
+  // Hyperpriors.
+  to_vector(Gamma) ~ normal(Gamma_mean, Gamma_scale);
+  Omega ~ lkj_corr(Omega_shape);
+  tau ~ normal(tau_mean, tau_scale);
+
+  // Non-centered population model and likelihood.
+  for (r in 1:R) {
+    Delta[r,] ~ normal(0, 1);
+    for (s in 1:S) {
+      Y[r, s] ~ categorical_logit(X[r, s] * Beta[r,]');
+    }
+  }
+}
+
+// Generated quantities conditioned on parameter draws.
+generated quantities {
+  // Compute log likelihood for model fit.
+  matrix[R, S] log_lik;
+  for (r in 1:R) {
+    for (s in 1:S) {
+      log_lik[r, s] = categorical_logit_lpmf(Y[r, s] | X[r, s] * Beta[r,]');
+    }
+  }
+}
 ```
@@
 # Load data and model output
+
+Once we specify the model we'd like to evaluate, the following analysis follows.
 

### 2020-09-02 analysis/model-calibration.R

@@ -1,306 +1,142 @@
-# Import and Restructure Data ---------------------------------------------
-# Load packages.
+# Preamble ----------------------------------------------------------------
+# Load packages
 library(tidyverse)
 library(rstan)
-library(mvtnorm)
-library(bayesm)
+library(bayesplot)
 
-# Load data and design.
-final_data <- read_rds(here::here("data", "derived_data", "final_data.rds"))
-design <- read_csv(here::here("data", "derived_data", "dummy_design.csv")) %>%
-  select(-X1) %>%
-  rename(
-    version = question_set,
-    task = question,
-    alt = choice
-  )
+# Set Stan options
+options(mc.cores = parallel::detectCores())
+rstan_options(auto_write = TRUE)
 
-intercept <- 0                            # Intercept-only.
-public_affairs <- 1                       # Public affairs: Public affairs knowledge + Public affairs activity.
-political_ideology <- 0                   # Political ideology.
-social_views <- 0                         # Social views: Public affairs trust + Social ideology + Religiosity.
-charity_voluntarism <- 0                  # Charity and voluntarism: Charity trust, Charity activity, Volunteer activity, etc.
+# Choose the Model to Run -------------------------------------------------
+intercept <- 0                            # Intercept-only
+public_affairs <- 1                       # Public affairs: Public affairs knowledge + Public affairs activity
+political_ideology <- 0                   # Political ideology
+social_views <- 0                         # Social views: Public affairs trust + Social ideology + Religiosity
+charity_voluntarism <- 0                  # Charity and voluntarism: Charity trust, Charity activity, Volunteer activity, etc
 demographics <- 0                         # Demographics: Gender, Marital status, Education, Income, Race, Age
[…]

### 2020-09-02 analysis/05_market_simulator.Rmd
format change
Recoding some input levels

@@
                      "Once a month",
+                     "Few times a year",
                      "Once a year",
@@
                      'Once a year',
-                     'Once every few years',
-                     'Never'))
+                     'Once every few years'))
 

### 2020-09-02 analysis/05_market_simulator.Rmd
Changing inputs cont.

@@
          label = "Follow national news:",
-         choices = c('Multiple times a day',
-                     'Every day',
+         choices = c("Atleast once a day",
                      "Once a week",
-                     "Hardly ever",
-                     "Never"))
+                     "Rarely"
+                     ))
 

### 2020-09-02 analysis/02_clean-data.Rmd
Discretized the Q5.3 block

@@
     ),
+    # *Q5.3*: Here is a list of different types of voluntary organizations.
+For each organization, indicate whether you are an active member, an inactive member, or not a member of that type of organization:
+    # 
+    # |                                         | Active member | Inactive member | Don't belong |
+    # | --------------------------------------- | :-----------: | :-------------: | :----------: |
+    # | Church or religious organization        |       •       |        •        |      •       |
+    # | Sport or recreational organization      |       •       |        •        |      •       |
+    # | Art, music, or educational organization |       •       |        •        |      •       |
+    # | Labor union                             |       •       |        •        |      •       |
+    # | Political party                         |       •       |        •        |      •       |
+    # | Environmental organization              |       •       |        •        |      •       |
+    # | Professional association                |       •       |        •        |      •       |
+    # | Humanitarian or charitable organization |       •       |        •        |      •       |
+    # | Consumer organization                   |       •       |        •        |      •       |
+    # | Other organization                      |       •       |        •        |      •       |
+    Q5.3_1 = fct_relevel(
+      factor(Q5.3_1, labels = c("Active member", "Inactive member", "Don't belong")), 
+      c("Don't belong", "Inactive member", "Active member")
+    ),
+    Q5.3_2 = fct_relevel(
+      factor(Q5.3_2, labels = c("Active member", "Inactive member", "Don't belong")), 
+      c("Don't belong", "Inactive member", "Active member")
+    ),
+    Q5.3_3 = fct_relevel(
+      factor(Q5.3_3, labels = c("Active member", "Inactive member", "Don't belong")), 
+      c("Don't belong", "Inactive member", "Active member")
+    ),
+    Q5.3_4 = fct_relevel(
+      factor(Q5.3_4, labels = c("Active member", "Inactive member", "Don't belong")), 
+      c("Don't belong", "Inactive member", "Active member")
+    ),
+    Q5.3_5 = fct_relevel(
+      factor(Q5.3_5, labels = c("Active member", "Inactive member", "Don't belong")), 
+      c("Don't belong", "Inactive member", "Active member")
+    ),
+    Q5.3_6 = fct_relevel(
+      factor(Q5.3_6, labels = c("Active member", "Inactive member", "Don't belong")), 
+      c("Don't belong", "Inactive member", "Active member")
+    ),
+    Q5.3_7 = fct_relevel(
+      factor(Q5.3_7, labels = c("Active member", "Inactive member", "Don't belong")), 
+      c("Don't belong", "Inactive member", "Active member")
+    ),
+    Q5.3_8 = fct_relevel(
+      factor(Q5.3_8, labels = c("Active member", "Inactive member", "Don't belong")), 
+      c("Don't belong", "Inactive member", "Active member")
+    ),
+    Q5.3_9 = fct_relevel(
+      factor(Q5.3_9, labels = c("Active member", "Inactive member", "Don't belong")), 
+      c("Don't belong", "Inactive member", "Active member")
+    ),
+    Q5.3_10 = fct_relevel(
+      factor(Q5.3_10, labels = c("Active member", "Inactive member", "Don't belong")), 
+      c("Don't belong", "Inactive member", "Active member")
+    ),
     # *Q5.4*: Historically, how involved have you been in activist causes?
@@
           "Neutral", "Somewhat disagree", "Disagree", "Strongly disagree"
+        )
       ),
@@
         "Neutral", "Somewhat agree", "Agree", "Strongly agree"
-        )
       )

### 2020-09-02 analysis/03_analysis.Rmd
Discretized the Q5.3 block

@@
 
-# Plot marginals
+# Plot marginals and contrasts
 
 ```{r plot-marginals}
+#########
+
+# Update covariate labels
+# Add contrasts where appropriate (see hypotheses Rmd documents)
+
+#########
+
 intercept <- 0                            # Intercept-only

### 2020-09-02 analysis/model-calibration.R

@@ -2,7 +2,6 @@
 # Load packages
 library(tidyverse)
 library(rstan)
-library(bayesplot)
 
 # Set Stan options
 options(mc.cores = parallel::detectCores())
@@ -10,10 +9,10 @@ rstan_options(auto_write = TRUE)
 
 # Choose the Model to Run -------------------------------------------------
 intercept <- 0                            # Intercept-only
-public_affairs <- 1                       # Public affairs: Public affairs knowledge + Public affairs activity
+public_affairs <- 0                       # Public affairs: Public affairs knowledge + Public affairs activity
 political_ideology <- 0                   # Political ideology
 social_views <- 0                         # Social views: Public affairs trust + Social ideology + Religiosity
-charity_voluntarism <- 0                  # Charity and voluntarism: Charity trust, Charity activity, Volunteer activity, etc
+charity_voluntarism <- 1                  # Charity and voluntarism: Charity trust, Charity activity, Volunteer activity, etc
 demographics <- 0                         # Demographics: Gender, Marital status, Education, Income, Race, Age
 public_political <- 0                     # Public affairs + Political ideology
 public_political_social <- 0              # Public affairs + Political ideology + Social views

### 2020-09-09 analysis/05_market_simulator.Rmd
Added Sections for persona inputs in the beta_persona levels

@@
 beta_persona$levels = c("Intercept",
-                        "Follow National News", 
-                        "Follow International News",
+                        # Follow National News
+                        "Rarely", 
+                        "Once a Week",
+                        "At least once a day",
+                        # Follow International News
+                        "Never",
+                        "Sometimes",
+                        "Always",
+                        # News Mediums
                         "TV",
@@
                         "News app",
-                        "Follow Government or Public Affairs", 
+                        # Follow Government or Public Affairs
+                        "", 
+                        # Travel to Countries
                         "Doesn't Travel", 
+                        # Political Preference
                         "Political Preference", 
+                        # Trust in Political Institute
                         "Trust in Political Institutions",
+                        # Should Others be Charitable
                         "Others Should be Charitable",
+                        # Worship Service Attendence
                         "Worship Service Attendence",
+                        # Religious Importance
                         "Religious Importance",
+                        # Religion
                         "Protestant",
@@
                         "Other (Religion)",
+                        # Charity Trust Importance
                         "Chartiy Trust Importance",
+                        # Trust in Charities
                         "Trust in Charity", 
+                        # Donation Frequency
                         "Donation Frequency", 
+                        # Donation Amount
                         "Donation Amount",
+                        # Volunteered last 12 months
                         "Not Volunteered",
-                        "Volunteer Frequence",
+                        # Volunteer Frequency
+                        "Volunteer Frequency",
+                        # Personal Activism
                         "Personal Activism",
+                        # Family Activism
                         "Family Activism",
+                        # Relgious Membership
                         "Religious Membership", 
+                        # Sport or Recreational Membership
                         "Sport or Recreational Membership", 
+                        # Art, Music, or Educational Membership
                         "Art, Music, or Educational Membership",
+                        # Labor Union Membership
                         "Labor Union Membership",
+                        # Political Party Membership
                         "Political Party Membership",
+                        # Environmental Organization Membership
                         "Environmental Organization Membership",
+                        # Professional Association
                         "Professional Association", 
+                        # Humanitarian or Charity Membership
                         "Humanitarian or Charity Membership",
+                        # Consumer Organization Membership
                         "Consumer Organization Membership",
+                        #Other Organization Membership
                         "Other Organization Membership",
+                        # Gender
                         "Female",
@@
                         "Other (Gender)",
+                        # Marital Status
                         "Widowed",
@@
                         "Never Married",
+                        # Education
                         "Education", 
+                        # Income
                         "Income", 
+                        # Race
                         "White", 
@@
                         "Other (Race)", 
+                        # Age
                         "Age")

### 2020-09-09 analysis/05_market_simulator.Rmd
Added section labels for persona beta levels
updating persona beta levels
Finished persona beta levels
Fixing up persona inputs

@@
                         # Follow National News
-                        "Rarely", 
                         "Once a Week",
@@
                         # Follow International News
-                        "Never",
                         "Sometimes",
@@
                         # Follow Government or Public Affairs
-                        "", 
-                        # Travel to Countries
-                        "Doesn't Travel", 
+                        "Often", 
+                        # Travel to developing Countries
+                        "Yes", 
                         # Political Preference
-                        "Political Preference", 
+                        "Somewhat Liberal",
+                        "Slightly Liberal",
+                        "Moderate",
+                        "Slightly Conservative",
+                        "Somewhat Conservative",
+                        "Extremely Conservative",
                         # Trust in Political Institute
-                        "Trust in Political Institutions",
+                        "Very little trust",
+                        "Little trust",
+                        "Nuetral",
+                        "Some trust",
+                        "A lot of trust",
+                        "Complete trust",
                         # Should Others be Charitable
-                        "Others Should be Charitable",
-                        # Worship Service Attendence
-                        "Worship Service Attendence",
+                        "Disagree",
+                        "Somewhat Disagree",
+                        "Nuetral",
+                        "Somewhat Agree",
+                        "Agree",
+                        "Strongly Agree",
+                        # Worship Service Attendance
+                        "Rarely",
+                        "At least once a month",
                         # Religious Importance
-                        "Religious Importance",
+                        "Important",
                         # Religion
@@
                         # Charity Trust Importance
-                        "Chartiy Trust Importance",
+                        "Very Unimportant",
+                        "Somewhat Unimportant",
+                        "Nuetral",
+                        "Somewhat Important",
+                        "Very Important",
+                        "Essential",
                         # Trust in Charities
-                        "Trust in Charity", 
+                        "Very little trust",
+                        "Little trust",
+                        "Nuetral",
+                        "Some trust",
+                        "A lot of trust",
+                        "Complete trust",
                         # Donation Frequency
-                        "Donation Frequency", 
+                        "At least once a month", 
                         # Donation Amount
-                        "Donation Amount",
+                        "$50-$99",
+                        "$100-$499",
+                        "$500-$999",
+                        "$1,000-$4,999",
+                        "$5,000-$9,999",
+                        "$10,000 +",
                         # Volunteered last 12 months
-                        "Not Volunteered",
+                        "Yes",
                         # Volunteer Frequency
-                        "Volunteer Frequency",
+                        "Rarely",
+                        "More than once a month, less than once a year",
+                        "Atleast once a month",
                         # Personal Activism
-                        "Personal Activism",
+                        "Involved",
                         # Family Activism
-                        "Family Activism",
-                        # Relgious Membership
-                        "Religious Membership", 
+                        "Involved",
+                        # Religious Membership
+                        "Inactive Member",
+                        "Active Member",
                         # Sport or Recreational Membership
-                        "Sport or Recreational Membership", 
+                        "Inactive Member",
+                        "Active Member", 
                         # Art, Music, or Educational Membership
-                        "Art, Music, or Educational Membership",
+                        "Inactive Member",
+                        "Active Member",
                         # Labor Union Membership
-                        "Labor Union Membership",
+                        "Inactive Member",
+                        "Active Member",
                         # Political Party Membership
-                        "Political Party Membership",
+                        "Inactive Member",
+                        "Active Member",
                         # Environmental Organization Membership
-                        "Environmental Organization Membership",
+                        "Inactive Member",
+                        "Active Member",
                         # Professional Association
-                        "Professional Association", 
+                        "Inactive Member",
+                        "Active Member",
                         # Humanitarian or Charity Membership
-                        "Humanitarian or Charity Membership",
+                        "Inactive Member",
+                        "Active Member",
                         # Consumer Organization Membership
-                        "Consumer Organization Membership",
+                        "Inactive Member",
+                        "Active Member",
                         #Other Organization Membership
-                        "Other Organization Membership",
+                        "Inactive Member",
+                        "Active Member",
                         # Gender
@@
                         # Education
-                        "Education", 
+                        "Highschool Graduate", 
+                        "Some College",
+                        "2 Year College",
+                        "4 Year College",
+                        "Graduate or Professional Degree",
+                        "Doctorate",
                         # Income
-                        "Income", 
+                        "More than Median - $61,372", 
                         # Race
@@
                         # Age
-                        "Age")
+                        "More than Median (> 36)")
 
 # p reactive element ----
-
-p1_politic_pref <- reactive({
-  max(input$p1_political_pref)
-})
 
@@
          label = "Education:",
-         choices = c("Less than high school",
-                     "High school",
-                     "Some college",
-                     "2 year degree",
-                     "4 year degree",
-                     "Graduate degree",
+         choices = c("Less than Highschool",
+                     "Highschool Graduate",
+                     "Some College",
+                     "2 Year College",
+                     "4 Year College",
+                     "Graduate or Professional Degree",
                      "Doctorate"))
@@
          label = "Age:",
-         choices = c('Under 18',
-                     '18 - 24',
-                     '25 - 34',
-                     '35 - 44',
-                     '45 - 54',
-                     '55 - 64',
-                     '65 - 74',
-                     '75 - 84',
-                     '85 or older'))
+         choices = c('Less than Median Age (< 36)',
+                     "More than Median Age (> 36)"))
 

### 2020-09-09 analysis/05_market_simulator.Rmd
In process of finishing Persona Inputs

@@
             label = "Charity Trust:",
-            choices = c("0", '1', '2', '3','4','5','6','7'))
-
-# Need to Fix
-
+            choices = c("Very little Trust"))
+
+# Double Check this one
 selectInput("p1_donation_frequency",
          label = "Donation Frequency:",
-         choices = c('Once a week',
-                     'Once a Month',
-                     'Once every three months',
-                     'Once every six months',
-                     'Once a year',
-                     'Once every few years',
-                     'Never'))
-
-# Need to Fix
+         choices = c('Rarely',
+                     'Atleast once a month'))
+
 selectInput("p1_donation_amount",
@@
 
+# Need to Change the Inputs
 selectInput("p1_volunteer_12",
          label = "Volunteered in last 12 Months:",
-         choices = c("Volunteered", "Not Volunteered"))
+         choices = c("No", "Yes"))
 
@@
          label = "Volunteer Frequency:",
-         choices = c('Once a week',
-                     'Once a Month',
-                     'Once every three months',
-                     'Once every six months',
-                     'Once a year',
-                     'Once every few years'))
+         choices = c("Haven't Volunteered",
+                     "Rarely",
+                     "More than once a month, less than once a year",
+                     "At least once a month"))
 
@@
          label = "Personal Activism:",
-         choices = c('Extremely involved',
-                     'Very involved',
-                     'Moderately involved',
-                     'Slightly involved',
-                     'Never involved'))
+         choices = c('Not Involved',
+                     'Involved'))
 
@@
          label = "Family Activism:",
-         choices = c('Extremely involved',
-                     'Very involved',
-                     'Moderately involved',
-                     'Slightly involved',
-                     'Never involved'))
+         choices = c('Not Involved',
+                     'Involved'))
 
@@
          label = "Church Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
+         choices = c("Don't belong",
+                     'Inactive Member',
+                     'Active Member'))
 
@@
          label = "Sport or Recreational Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
+         choices = c("Don't belong",
+                     'Inactive Member',
+                     'Active Member'))
 
@@
          label = "Art, Music, or Educational Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
+         choices = c("Don't belong",
+                     'Inactive Member',
+                     'Active Member'))
 
@@
          label = "Labor Union Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
+         choices = c("Don't belong",
+                     'Inactive Member',
+                     'Active Member'))
 
@@
          label = "Political Party Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
+         choices = c("Don't belong",
+                     'Inactive Member',
+                     'Active Member'))
 
@@
          label = "Enviornmental Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
+         choices = c("Don't belong",
+                     'Inactive Member',
+                     'Active Member'))
 
@@
          label = "Professional Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
+         choices = c("Don't belong",
+                     'Inactive Member',
+                     'Active Member'))
 
@@
          label = "Humanitarian Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
+         choices = c("Don't belong",
+                     'Inactive Member',
+                     'Active Member'))
 
@@
          label = "Consumer Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
+         choices = c("Don't belong",
+                     'Inactive Member',
+                     'Active Member'))
 
@@
          label = "Other Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
+         choices = c("Don't belong",
+                     'Inactive Member',
+                     'Active Member'))
 
@@
          choices = c('Less than $10,000',
-                     '$10,000 to $19,999',
-                     '$20,000 to $29,999',
-                     '$30,000 to $39,999',
-                     '$40,000 to $49,999',
-                     '$50,000 to $59,999',
-                     '$60,000 to $69,999',
-                     '$70,000 to $79,999',
-                     '$80,000 to $89,999',
-                     '$90,000 to $99,999',
-                     '$100,000 to $149,999',
-                     '$150,000 to $199,999',
-                     '$200,000 to $299,999',
-                     '$300,000 or more'))
+                     'More than Median (>$61,372)'))
 

### 2020-09-10 analysis/05_market_simulator.Rmd
Fixing Inputs

@@
                         "Print",
-                        "Online (excluding social media)",
-                        "Social Media",
+                        "Online (not social media)",
+                        "Social media",
                         "Radio",
-                        "Email",
+                        "Email newsletter",
                         "News app",
@@
                         # Political Preference
-                        "Somewhat Liberal",
-                        "Slightly Liberal",
+                        "Somewhat liberal",
+                        "Slightly liberal",
                         "Moderate",
-                        "Slightly Conservative",
-                        "Somewhat Conservative",
-                        "Extremely Conservative",
+                        "Slightly conservative",
+                        "Somewhat conservative",
+                        "Extremely conservative",
                         # Trust in Political Institute
@@
                         "Disagree",
-                        "Somewhat Disagree",
+                        "Somewhat disagree",
                         "Nuetral",
-                        "Somewhat Agree",
+                        "Somewhat agree",
                         "Agree",
-                        "Strongly Agree",
+                        "Strongly agree",
                         # Worship Service Attendance
@@
                         # Charity Trust Importance
-                        "Very Unimportant",
-                        "Somewhat Unimportant",
+                        "Very unimportant",
+                        "Somewhat unimportant",
                         "Nuetral",
-                        "Somewhat Important",
-                        "Very Important",
+                        "Somewhat important",
+                        "Very important",
                         "Essential",
@@
                         "More than once a month, less than once a year",
-                        "Atleast once a month",
+                        "At least once a month",
                         # Personal Activism
@@
                         # Religious Membership
-                        "Inactive Member",
-                        "Active Member",
+                        "Inactive member",
+                        "Active member",
                         # Sport or Recreational Membership
-                        "Inactive Member",
-                        "Active Member", 
+                        "Inactive member",
+                        "Active member", 
                         # Art, Music, or Educational Membership
-                        "Inactive Member",
-                        "Active Member",
+                        "Inactive member",
+                        "Active member",
                         # Labor Union Membership
-                        "Inactive Member",
-                        "Active Member",
+                        "Inactive member",
+                        "Active member",
                         # Political Party Membership
-                        "Inactive Member",
-                        "Active Member",
+                        "Inactive member",
+                        "Active member",
                         # Environmental Organization Membership
-                        "Inactive Member",
-                        "Active Member",
+                        "Inactive member",
+                        "Active member",
                         # Professional Association
-                        "Inactive Member",
-                        "Active Member",
+                        "Inactive member",
+                        "Active member",
                         # Humanitarian or Charity Membership
-                        "Inactive Member",
-                        "Active Member",
+                        "Inactive member",
+                        "Active member",
                         # Consumer Organization Membership
-                        "Inactive Member",
-                        "Active Member",
+                        "Inactive member",
+                        "Active member",
                         #Other Organization Membership
-                        "Inactive Member",
-                        "Active Member",
+                        "Inactive member",
+                        "Active member",
                         # Gender
@@
                         "Separated",
-                        "Never Married",
+                        "Never married",
                         # Education
-                        "Highschool Graduate", 
-                        "Some College",
-                        "2 Year College",
-                        "4 Year College",
-                        "Graduate or Professional Degree",
+                        "Highschool graduate", 
+                        "Some college",
+                        "2 year college",
+                        "4 year college",
+                        "Graduate or orofessional degree",
                         "Doctorate",
                         # Income
-                        "More than Median - $61,372", 
+                        "More than median of $61,372", 
                         # Race
                         "White", 
-                        "Black", 
-                        "American Indian", 
+                        "Black or African American", 
+                        "American Indian or Alaska Native", 
                         "Asian", 
-                        "Pacific Islander", 
+                        "Native Hawaiian or Pacific Islander", 
                         "Other (Race)", 
                         # Age
-                        "More than Median (> 36)")
+                        "More than median age of 36")
 
@@
 
-# Need to Fix
 selectInput("p1_national_news",
          label = "Follow national news:",
-         choices = c("Atleast once a day",
+         choices = c("Rarely",
                      "Once a week",
-                     "Rarely"
-                     ))
-
-# Need to Fix
+                     "Atleast once a day"))
+
 selectInput("p1_international_news",
          label = "Follow international news:",
-         choices = c('Always',
+         choices = c("Never",
                      "Sometimes",
-                     "Never"))
+                     'Always'))
 
@@
                      'Print',
-                     "Online (excluding social media)",
-                     "Social Media",
+                     "Online (not social media)",
+                     "Social media",
                      "Radio",
-                     "Email",
+                     "Email newsletter",
                      "News app"),
@@
 
-# Need to Fix
+# Need to Check on Hold out
 selectInput("p1_follow_gov",
          label = "Follow government & public affairs:",
-         choices = c('Most of the time',
-                     'Some of the time',
-                     "Only now and then",
-                     "Hardly at all"))
+         choices = c("Not Often",
+                     "Often"))
 
@@
          label = "Travel to developing country:",
-         choices = c('Does Travel', "Doesn't Travel"))
-
-# Need to Fix
+         choices = c('No', "Yes"))
+
 selectInput("p1_political_pref",
          label = "Political views from liberal to conservative:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
+         choices = c("Extremely liberal",
+                     "Somewhat liberal",
+                     "Slightly liberal",
+                     "Moderate",
+                     "Slightly conservative",
+                     "Somewhat conservative",
+                     "Extremely conservative"))
 

### 2020-09-10 analysis/05_market_simulator.Rmd
Only need to check a few of the hold out levels for the inputs

@@
 
-# Need to Fix
+# Need to check hold out level
 selectInput("p1_institution_trust",
          label = "Political institution trust from none to complete:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
-
-# Need to Fix
+         choices = c("No trust at all",
+                     "Very little trust",
+                     "Little trust",
+                     "Nuetral",
+                     "Some trust",
+                     "A lot of trust",
+                     "Complete trust"))
+
 selectInput("p1_others_charitable",
          label = "People should be more charitable:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
-
-# Need to Fix
+         choices = c("Strongly Disagree",
+                     "Disagree",
+                     "Somewhat disagree",
+                     "Nuetral",
+                     "Somewhat agree",
+                     "Agree",
+                     "Strongly Agree"))
+
+# Need to check hold out 
 selectInput("p1_worship_attendance",
          label = "Worship service attendance:",
-         choices = c('Multiple times a week',
-                     'Once a week',
-                     "Once a month",
-                     "Few times a year",
-                     "Once a year",
-                     "Never"))
-
-# Need to Fix
+         choices = c("Never",
+                     "Rarely",
+                     "At least once a month"))
+
+# Need to check hold out
 selectInput("p1_religion_importance",
          label = "Importance of religion:",
-         choices = c('Extremely important',
-                     'Very important',
-                     'Moderately important',
-                     'Slightly important',
-                     'Not at all important'))
+         choices = c("Not important",
+                     "Important"))
 
@@
 
-# Need to Fix
+# Need to check hold out level
 selectInput("p1_charity_importance",
           label = "Charity Importance:",
-          choices = c("0", '1', '2', '3','4','5','6','7'))
-
-# Need to Fix
+          choices = c("Hold out",
+                      "Very unimportant",
+                      "Somewhat unimportant",
+                      "Nuetral",
+                      "Somewhat important",
+                      "Very important",
+                      "Essential"))
+
+# Need to check hold out level
 selectInput("p1_trust_in_charity",
             label = "Charity Trust:",
-            choices = c("Very little Trust"))
-
-# Double Check this one
+            choices = c("No trust at all",
+                        "Very little trust",
+                        "Little trust",
+                        "Nuetral",
+                        "Some trust",
+                        "A lot of trust",
+                        "Complete trust"))
+
+# Need to check hold out level
 selectInput("p1_donation_frequency",
@@
 
-# Need to Fix
+# Need to check hold out level
 selectInput("p1_volunteer_frequency",
          label = "Volunteer Frequency:",
-         choices = c("Haven't Volunteered",
+         choices = c("Haven't volunteered",
                      "Rarely",
@@
 
-# Need to Fix
 selectInput("p1_personal_activism",
          label = "Personal Activism:",
-         choices = c('Not Involved',
+         choices = c('Not involved',
                      'Involved'))
 
-# Need to Fix
 selectInput("p1_family_activism",
          label = "Family Activism:",
-         choices = c('Not Involved',
+         choices = c('Not involved',
                      'Involved'))
 
-# Need to Fix
 selectInput("p1_religious_member",
@@
          choices = c("Don't belong",
-                     'Inactive Member',
-                     'Active Member'))
-
-# Need to Fix
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p1_sport_member",
@@
          choices = c("Don't belong",
-                     'Inactive Member',
-                     'Active Member'))
-
-# Need to Fix
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p1_art_member",
@@
          choices = c("Don't belong",
-                     'Inactive Member',
-                     'Active Member'))
-
-# Need to Fix
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p1_labor_member",
@@
          choices = c("Don't belong",
-                     'Inactive Member',
-                     'Active Member'))
-
-# Need to Fix
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p1_political_member",
@@
          choices = c("Don't belong",
-                     'Inactive Member',
-                     'Active Member'))
-
-# Need to Fix
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p1_environmental_member",
@@
          choices = c("Don't belong",
-                     'Inactive Member',
-                     'Active Member'))
-
-# Need to Fix
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p1_professional_member",
@@
          choices = c("Don't belong",
-                     'Inactive Member',
-                     'Active Member'))
-
-# Need to Fix
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p1_humanitarian_member",
@@
          choices = c("Don't belong",
-                     'Inactive Member',
-                     'Active Member'))
-
-# Need to Fix
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p1_consumer_member",
@@
          choices = c("Don't belong",
-                     'Inactive Member',
-                     'Active Member'))
-
-# Need to Fix
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p1_other_member",
@@
          choices = c("Don't belong",
-                     'Inactive Member',
-                     'Active Member'))
+                     'Inactive member',
+                     'Active member'))
 
@@
 
-# Need to Fix
 selectInput("p1_education",
          label = "Education:",
-         choices = c("Less than Highschool",
-                     "Highschool Graduate",
-                     "Some College",
-                     "2 Year College",
-                     "4 Year College",
-                     "Graduate or Professional Degree",
+         choices = c("Less than highschool",
+                     "Highschool graduate",
+                     "Some college",
+                     "2 year college",
+                     "4 year college",
+                     "Graduate or professional degree",
                      "Doctorate"))
-# Need to Fix
+
 selectInput("p1_income",
          label = "Income:",
-         choices = c('Less than $10,000',
-                     'More than Median (>$61,372)'))
+         choices = c('Less than median of $61,372',
+                     'More than median of $61,372'))
 
@@
 
-# Need to Fix
 selectInput("p1_age",
          label = "Age:",
-         choices = c('Less than Median Age (< 36)',
-                     "More than Median Age (> 36)"))
+         choices = c('Less than median age of 36',
+                     "More than median age of 36"))
 

### 2020-09-10 analysis/03_analysis.Rmd

@@
 social_views <- 0                         # Social views
-charity_voluntarism <- 1                  # Charity and voluntarism
+charity_voluntarism <- 0                  # Charity and voluntarism
 demographics <- 0                         # Demographics
@@
 
-# Thetas
-draws_theta <- fit %>% 
+# Gamma
+draws_gamma <- fit %>% 
   extract(
-    pars = str_c("Theta[", 1:13, ",1]"),
+    pars = str_c("Gamma[", 1:13, ",1]"),
     inc_warmup = TRUE,
@@
 
-draws_theta %>% 
+draws_gamma %>% 
   mcmc_hist_by_chain()
 
-draws_theta %>% 
+draws_gamma %>% 
   mcmc_trace(
@@
 
-# Extract the L_Omega parameters only and look at trace plots, etc.
+# Extract the Omega parameters only and look at trace plots, etc.
 
-# L_Omega
-draws_L_Omega <- fit %>% 
+# Omega
+draws_Omega <- fit %>% 
   extract(
-    regex_pars = c("L_Omega"),
+    regex_pars = c("Omega"),
     inc_warmup = TRUE,
@@
   mcmc_trace(
-    pars = str_c("Theta[", 1:13, ",1]"),
+    pars = str_c("Gamma[", 1:13, ",1]"),
     n_warmup = 2000,
@@
 draws <- fit %>% 
-  spread_draws(Theta[i, j]) %>% 
+  spread_draws(Gamma[i, j]) %>% 
   ungroup() %>% 
@@
 #     ) %>%
-#     ggplot(aes(x = Theta, y = levels)) + 
+#     ggplot(aes(x = Gamma, y = levels)) + 
 #     geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
@@
 #     ) %>%
-#     ggplot(aes(x = Theta, y = covariates)) +
+#     ggplot(aes(x = Gamma, y = covariates)) +
 #        geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
@@
     summarize(
-      mean = mean(Theta),
-      ci_lower = quantile(Theta, .025),
-      ci_upper = quantile(Theta, .975),
+      mean = mean(Gamma),
+      ci_lower = quantile(Gamma, .025),
+      ci_upper = quantile(Gamma, .975),
       gt_zero = if_else(ci_lower > 0 & ci_upper > 0, 1, 0),
@@
 
-  # Heatmap of Theta matrix.
+  # Heatmap of Gamma matrix.
   plot_heatmap <- posterior_means %>% 

### 2020-09-10 analysis/05_market_simulator.Rmd
Last changes to inputs

@@
                         # Education
-                        "Highschool graduate", 
+                        "High school graduate", 
                         "Some college",
-                        "2 year college",
-                        "4 year college",
-                        "Graduate or orofessional degree",
+                        "2 year degree",
+                        "4 year degree",
+                        "Graduate or professional degree",
                         "Doctorate",
@@
 
-# Need to Check on Hold out
 selectInput("p1_follow_gov",
@@
 
-# Need to check hold out 
 selectInput("p1_worship_attendance",
          label = "Worship service attendance:",
-         choices = c("Never",
+         choices = c("Not sure",
                      "Rarely",
@@
 
-# Need to check hold out level
 selectInput("p1_charity_importance",
           label = "Charity Importance:",
-          choices = c("Hold out",
+          choices = c("Not at all important",
                       "Very unimportant",
@@
 
-# Need to check hold out level
 selectInput("p1_trust_in_charity",
@@
 
-# Need to check hold out level
 selectInput("p1_donation_frequency",
          label = "Donation Frequency:",
-         choices = c('Rarely',
+         choices = c('More than once a month, less than once a year',
                      'Atleast once a month'))
@@
 
-# Need to Change the Inputs
 selectInput("p1_volunteer_12",
@@
 
-# Need to check hold out level
 selectInput("p1_volunteer_frequency",
          label = "Volunteer Frequency:",
-         choices = c("Haven't volunteered",
+         choices = c("Haven't volunteered in past 12 months",
                      "Rarely",
@@
          label = "Education:",
-         choices = c("Less than highschool",
-                     "Highschool graduate",
+         choices = c("Less than high school",
+                     "High school graduate",
                      "Some college",
-                     "2 year college",
-                     "4 year college",
+                     "2 year degree",
+                     "4 year degree",
                      "Graduate or professional degree",

### 2020-09-10 analysis/03_analysis.Rmd
Model output

@@
 library(tidybayes)
+library(loo)
 library(ggridges)
@@
 
-After selecting the model we'd like to run, model calibration proceeds as follows.
-Note that model calibration is run in a separate R script given how long it takes to run each model.
-Model output can be loaded for analysis in the next section.
+After selecting the model we'd like to run, model calibration proceeds as follows. Note that model calibration is run in a separate R script given how long it takes to run each model.
 
@@
 The model is calibrated using a non-centered parameterization of a hierarchical multinomial logit model.
+Each model passed diagnostics checks, including the absence of divergent transitions, as part of model calibration.
 
@@
 
-# Load data and model output
+# Compute model fit and extract draws
 
-Once we specify the model we'd like to evaluate, the following analysis follows.
+The following analysis follows specifying the model we'd like to evaluate. Note that the output of the model calibration is too large to push to GitHub.
 
-```{r load-data-output, warning=FALSE, message=FALSE}
-intercept <- 0                            # Intercept-only
+## Load model output
+
+```{r load-data-output, warning=FALSE, message=FALSE, eval=FALSE}
+# Load all model output
+intercept_run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.rds"))
+public_affairs_run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
+political_ideology_run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
+social_views_run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
+charity_voluntarism_run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
+demographics_run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
+public_political_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
+public_political_social_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
+public_political_social_charity_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
+public_political_social_charity_demo_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
+```
+
+## Compute model fit
+
+```{r compute-fit, eval=FALSE}
+# Compute fit using PSIS-LOO
+intercept_loo <- loo(intercept_run$fit, save_psis = TRUE)
+public_affairs_loo <- loo(public_affairs_run$fit, save_psis = TRUE)
+political_ideology_loo <- loo(political_ideology_run$fit, save_psis = TRUE)
+social_views_loo <- loo(social_views_run$fit, save_psis = TRUE)
+charity_voluntarism_loo <- loo(charity_voluntarism_run$fit, save_psis = TRUE)
+demographics_loo <- loo(demographics_run$fit, save_psis = TRUE)
+public_political_loo <- loo(public_political_run$fit, save_psis = TRUE)
+public_political_social_loo <- loo(public_political_social_run$fit, save_psis = TRUE)
+public_political_social_charity_loo <- loo(public_political_social_charity_run$fit, save_psis = TRUE)
+public_political_social_charity_demo_loo <- loo(public_political_social_charity_demo_run$fit, save_psis = TRUE)
+
+# Compare model fit
+loo_compare(intercept_loo, public_affairs_loo, political_ideology_loo, social_views_loo, charity_voluntarism_loo, demographics_loo, public_political_loo, public_political_social_loo, public_political_social_charity_loo, public_political_social_charity_demo_loo)
+```
+
+```
+        elpd_diff se_diff
+model1     0.0       0.0 
+model3   -23.5       8.6 
+model2   -37.5      12.9 
+model6   -54.0      15.6 
+model7   -70.2      15.4 
+model4   -74.4      16.6 
+model8  -163.9      23.6 
+model5  -174.4      24.6 
+model9  -401.3      38.4 
+model10 -518.3      44.6
+```
+
+The intercept-only model works best in terms of PSIS-LOO, followed by models with political ideology, public affairs and demographics covariates.
+While PSIS-LOO doesn't properly account for the specific benefits of a hierarchical model, it suggests that political ideology above all other covariate sets specified, has the most explanatory power.
+
+```{r save-fit, eval=FALSE}
+# Create data frame
+model_fit <- tibble(model = rep(NA, 10), elpd_loo = rep(NA, 10))
+
+# Extract PSIS-LOO fit
+model_fit$model[1] <- "intercept"; model_fit$loo[1] <- intercept_loo$elpd_loo
+model_fit$model[2] <- "public_affairs"; model_fit$loo[2] <- public_affairs_loo$elpd_loo
+model_fit$model[3] <- "political_ideology"; model_fit$loo[3] <- political_ideology_loo$elpd_loo
+model_fit$model[4] <- "social_views"; model_fit$loo[4] <- social_views_loo$elpd_loo
+model_fit$model[5] <- "charity_voluntarism"; model_fit$loo[5] <- charity_voluntarism_loo$elpd_loo
+model_fit$model[6] <- "demographics"; model_fit$loo[6] <- demographics_loo$elpd_loo
+model_fit$model[7] <- "public_political"; model_fit$loo[7] <- public_political_loo$elpd_loo
+model_fit$model[8] <- "public_political_social"; model_fit$loo[8] <- public_political_social_loo$elpd_loo
+model_fit$model[9] <- "public_political_social_charity"; model_fit$loo[9] <- public_political_social_charity_loo$elpd_loo
+model_fit$model[10] <- "public_political_social_charity_demo"; model_fit$loo[10] <- public_political_social_charity_demo_loo$elpd_loo
+
+# Save model output
+write_rds(model_fit, here::here("analysis", "output", "model_fit.rds"))
+```
+
+## Load model fit and extract and save draws
+
+```{r extract-draws, eval=FALSE}
+intercept <- 1                            # Intercept-only
 public_affairs <- 0                       # Public affairs
@@
 public_political_social_charity <- 0      # + Charity and voluntarism
-public_political_social_charity_demo <- 1 # + Demographics
+public_political_social_charity_demo <- 0 # + Demographics
 
-# Load and extract data and model output (see model-calibration.R)
+# Load and extract data and model output
 if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.rds"))
@@
 fit <- run$fit
-```
 
-# Model checking
-
-```{r model-checking}
-source(here::here("R", "stan_utility.R"))
-
-# Gamma
-draws_gamma <- fit %>% 
-  extract(
-    pars = str_c("Gamma[", 1:13, ",1]"),
-    inc_warmup = TRUE,
-    permuted = FALSE
-  )
-
-draws_gamma %>% 
-  mcmc_hist_by_chain()
-
-draws_gamma %>% 
-  mcmc_trace(
-    n_warmup = 2000,
-    facet_args = list(
-      nrow = 4, 
-      labeller = label_parsed
-    )
-  )
-
-# Extract the Omega parameters only and look at trace plots, etc.
-
-# Omega
-draws_Omega <- fit %>% 
-  extract(
-    regex_pars = c("Omega"),
-    inc_warmup = TRUE,
-    permuted = FALSE
-  )
-
-draws_gamma %>% 
-  mcmc_hist_by_chain()
-
-draws_gamma %>% 
-  mcmc_trace(
-    n_warmup = 2000,
-    facet_args = list(
-      nrow = 4, 
-      labeller = label_parsed
-    )
-  )
-
-# # Check diagnostics
-# check_all_diagnostics(fit)
-
-# Check for divergences
-check_div(fit)
-
-# # Check the effective sample size (NOT WORKING?)
-# check_n_eff(fit)
-# 
-# # Check the Rhat statistic (NOT WORKING?)
-# check_rhat(fit)
-
-# Check trace plots (SUBSET?)
-color_scheme_set("mix-blue-red")
-fit %>%
-  extract(
-    inc_warmup = TRUE,
-    permuted = FALSE
-  ) %>%
-  mcmc_trace(
-    pars = str_c("Gamma[", 1:13, ",1]"),
-    n_warmup = 2000,
-    facet_args = list(
-      nrow = 2, 
-      labeller = label_parsed
-    )
-  )
-
-# ggsave(
-#   "intercept_trace_noncentered.png",
-#   path = here::here("analysis", "output", "figures"),
-#   width = 12, height = 6, units = "in"
-# )
-```
-
-# Extract draws
-
-```{r extract-draws}
 # Extract posterior draws
@@
 
-# Plot marginals and contrasts
+# Load draws and plot marginals and contrasts
 
@@
 
+# # Create matrix of Gammas.
+# gamma_draws <- draws %>% 
+#   group_by(i, j) %>% 
+#   summarize(gamma_mean = mean(Gamma))
+# 
+# gamma_matrix <- matrix(as.matrix(gamma_draws)[,3], nrow = max(draws$j), ncol = max(draws$i))
+# write.csv(gamma_matrix, file = here::here("analysis", "output", "posterior_means.csv"))
+
 # Plot marginals

### 2020-09-11 analysis/05_market_simulator.Rmd
All persona inputs fixed. Now to import new data

@@
 
-# Need to check hold out level
 selectInput("p1_institution_trust",
@@
 
-# Need to check hold out
 selectInput("p1_religion_importance",
@@
 
-# Need to Fix
 selectInput("p2_national_news",
          label = "Follow national news:",
-         choices = c('Multiple times a day',
-                     'Every day',
+         choices = c("Rarely",
                      "Once a week",
-                     "Hardly ever",
-                     "Never"))
-
-# Need to Fix
+                     "Atleast once a day"))
+
 selectInput("p2_international_news",
          label = "Follow international news:",
-         choices = c('Always',
+         choices = c("Never",
                      "Sometimes",
-                     "Never"))
+                     'Always'))
 
@@
          label = "Medium to follow news:",
-         choices = c("",
-                     'TV',
+         choices = c('TV',
                      'Print',
-                     "Online (excluding social media)",
-                     "Social Media",
+                     "Online (not social media)",
+                     "Social media",
                      "Radio",
-                     "Email",
+                     "Email newsletter",
                      "News app"),
@@
 
-# Need to Fix
 selectInput("p2_follow_gov",
          label = "Follow government & public affairs:",
-         choices = c('Most of the time',
-                     'Some of the time',
-                     "Only now and then",
-                     "Hardly at all"))
+         choices = c("Not Often",
+                     "Often"))
 
@@
          label = "Travel to developing country:",
-         choices = c('Does Travel', "Doesn't Travel"))
-
-# Need to Fix
+         choices = c('No', "Yes"))
+
 selectInput("p2_political_pref",
          label = "Political views from liberal to conservative:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
-
-# Need to Fix
+         choices = c("Extremely liberal",
+                     "Somewhat liberal",
+                     "Slightly liberal",
+                     "Moderate",
+                     "Slightly conservative",
+                     "Somewhat conservative",
+                     "Extremely conservative"))
+
 selectInput("p2_institution_trust",
          label = "Political institution trust from none to complete:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
-
-# Need to Fix
+         choices = c("No trust at all",
+                     "Very little trust",
+                     "Little trust",
+                     "Nuetral",
+                     "Some trust",
+                     "A lot of trust",
+                     "Complete trust"))
+
 selectInput("p2_others_charitable",
          label = "People should be more charitable:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
-
-# Need to Fix
+         choices = c("Strongly Disagree",
+                     "Disagree",
+                     "Somewhat disagree",
+                     "Nuetral",
+                     "Somewhat agree",
+                     "Agree",
+                     "Strongly Agree"))
+
 selectInput("p2_worship_attendance",
          label = "Worship service attendance:",
-         choices = c('Multiple times a week',
-                     'Once a week',
-                     "Once a month",
-                     "Once a year",
-                     "Never"))
-
-# Need to Fix
+         choices = c("Not sure",
+                     "Rarely",
+                     "At least once a month"))
+
 selectInput("p2_religion_importance",
          label = "Importance of religion:",
-         choices = c('Extremely important',
-                     'Very important',
-                     'Moderately important',
-                     'Slightly important',
-                     'Not at all important'))
+         choices = c("Not important",
+                     "Important"))
 
@@
 
-# Need to Fix
 selectInput("p2_charity_importance",
           label = "Charity Importance:",
-          choices = c("0", '1', '2', '3','4','5','6','7'))
-
-# Need to Fix
+          choices = c("Not at all important",
+                      "Very unimportant",
+                      "Somewhat unimportant",
+                      "Nuetral",
+                      "Somewhat important",
+                      "Very important",
+                      "Essential"))
+
 selectInput("p2_trust_in_charity",
             label = "Charity Trust:",
-            choices = c("0", '1', '2', '3','4','5','6','7'))
-
-# Need to Fix
+            choices = c("No trust at all",
+                        "Very little trust",
+                        "Little trust",
+                        "Nuetral",
+                        "Some trust",
+                        "A lot of trust",
+                        "Complete trust"))
 
@@
          label = "Donation Frequency:",
-         choices = c('Once a week',
-                     'Once a Month',
-                     'Once every three months',
-                     'Once every six months',
-                     'Once a year',
-                     'Once every few years',
-                     'Never'))
-
-# Need to Fix
+         choices = c('More than once a month, less than once a year',
+                     'Atleast once a month'))
+
 selectInput("p2_donation_amount",
@@
          label = "Volunteered in last 12 Months:",
-         choices = c("Volunteered", "Not Volunteered"))
-
-# Need to Fix
+         choices = c("No", "Yes"))
+
 selectInput("p2_volunteer_frequency",
          label = "Volunteer Frequency:",
-         choices = c('Once a week',
-                     'Once a Month',
-                     'Once every three months',
-                     'Once every six months',
-                     'Once a year',
-                     'Once every few years',
-                     'Never'))
-
-# Need to Fix
+         choices = c("Haven't volunteered in past 12 months",
+                     "Rarely",
+                     "More than once a month, less than once a year",
+                     "At least once a month"))
+
 selectInput("p2_personal_activism",
          label = "Personal Activism:",
-         choices = c('Extremely involved',
-                     'Very involved',
-                     'Moderately involved',
-                     'Slightly involved',
-                     'Never involved'))
-
-# Need to Fix
+         choices = c('Not involved',
+                     'Involved'))
+
 selectInput("p2_family_activism",
          label = "Family Activism:",
-         choices = c('Extremely involved',
-                     'Very involved',
-                     'Moderately involved',
-                     'Slightly involved',
-                     'Never involved'))
-
-# Need to Fix
+         choices = c('Not involved',
+                     'Involved'))
+
 selectInput("p2_religious_member",
          label = "Church Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-# Need to Fix
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p2_sport_member",
          label = "Sport or Recreational Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-# Need to Fix
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p2_art_member",
          label = "Art, Music, or Educational Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-# Need to Fix
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p2_labor_member",
          label = "Labor Union Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-# Need to Fix
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p2_political_member",
          label = "Political Party Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-# Need to Fix
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p2_environmental_member",
          label = "Enviornmental Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-# Need to Fix
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p2_professional_member",
          label = "Professional Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-# Need to Fix
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p2_humanitarian_member",
          label = "Humanitarian Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-# Need to Fix
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p2_consumer_member",
          label = "Consumer Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-# Need to Fix
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p2_other_member",
          label = "Other Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
 
@@
 
-# Need to Fix
 selectInput("p2_education",
@@
          choices = c("Less than high school",
-                     "High school",
+                     "High school graduate",
                      "Some college",
@@
                      "4 year degree",
-                     "Graduate degree",
+                     "Graduate or professional degree",
                      "Doctorate"))
-# Need to Fix
+
 selectInput("p2_income",
          label = "Income:",
-         choices = c('Less than $10,000',
-                     '$10,000 to $19,999',
-                     '$20,000 to $29,999',
-                     '$30,000 to $39,999',
-                     '$40,000 to $49,999',
-                     '$50,000 to $59,999',
-                     '$60,000 to $69,999',
-                     '$70,000 to $79,999',
-                     '$80,000 to $89,999',
-                     '$90,000 to $99,999',
-                     '$100,000 to $149,999',
-                     '$150,000 to $199,999',
-                     '$200,000 to $299,999',
-                     '$300,000 or more'))
+         choices = c('Less than median of $61,372',
+                     'More than median of $61,372'))
 
@@
          label = "Race(s):",
-         choices = c("",
-                     'White',
+         choices = c('White',
                      'Black or African American',
@@
 
-# Need to Fix
 selectInput("p2_age",
          label = "Age:",
-         choices = c('Less than Median Age (< 36)',
-                     "More than Median Age (> 36)"))
+         choices = c('Less than median age of 36',
+                     "More than median age of 36"))
 
@@
 
-# Need to Fix
 selectInput("p3_national_news",
          label = "Follow national news:",
-         choices = c('Multiple times a day',
-                     'Every day',
+         choices = c("Rarely",
                      "Once a week",
-                     "Hardly ever",
-                     "Never"))
-
-# Need to Fix
+                     "Atleast once a day"))
+
 selectInput("p3_international_news",
          label = "Follow international news:",
-         choices = c('Always',
+         choices = c("Never",
                      "Sometimes",
-                     "Never"))
+                     'Always'))
 
@@
 
-# Need to Fix
 selectInput("p3_follow_gov",
          label = "Follow government & public affairs:",
-         choices = c('Most of the time',
-                     'Some of the time',
-                     "Only now and then",
-                     "Hardly at all"))
+         choices = c("Not Often",
+                     "Often"))
 
@@
          label = "Travel to developing country:",
-         choices = c('Does Travel', "Doesn't Travel"))
-
-# Need to Fix
+         choices = c('No', "Yes"))
+
 selectInput("p3_political_pref",
          label = "Political views from liberal to conservative:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
-
-# Need to Fix
+         choices = c("Extremely liberal",
+                     "Somewhat liberal",
+                     "Slightly liberal",
+                     "Moderate",
+                     "Slightly conservative",
+                     "Somewhat conservative",
+                     "Extremely conservative"))
+
 selectInput("p3_institution_trust",
          label = "Political institution trust from none to complete:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
-
-# Need to Fix
+         choices = c("No trust at all",
+                     "Very little trust",
+                     "Little trust",
+                     "Nuetral",
+                     "Some trust",
+                     "A lot of trust",
+                     "Complete trust"))
+
 selectInput("p3_others_charitable",
          label = "People should be more charitable:",
-         choices = c("0", '1', '2', '3','4','5','6','7'))
-
-# Need to Fix
+         choices = c("Strongly Disagree",
+                     "Disagree",
+                     "Somewhat disagree",
+                     "Nuetral",
+                     "Somewhat agree",
+                     "Agree",
+                     "Strongly Agree"))
+
 selectInput("p3_worship_attendance",
          label = "Worship service attendance:",
-         choices = c('Multiple times a week',
-                     'Once a week',
-                     "Once a month",
-                     "Once a year",
-                     "Never"))
-
-# Need to Fix
+         choices = c("Not sure",
+                     "Rarely",
+                     "At least once a month"))
+
 selectInput("p3_religion_importance",
          label = "Importance of religion:",
-         choices = c('Extremely important',
-                     'Very important',
-                     'Moderately important',
-                     'Slightly important',
-                     'Not at all important'))
+         choices = c("Not important",
+                     "Important"))
 
@@
 
-# Need to Fix
 selectInput("p3_charity_importance",
           label = "Charity Importance:",
-          choices = c("0", '1', '2', '3','4','5','6','7'))
-
-# Need to Fix
+          choices = c("Not at all important",
+                      "Very unimportant",
+                      "Somewhat unimportant",
+                      "Nuetral",
+                      "Somewhat important",
+                      "Very important",
+                      "Essential"))
+
 selectInput("p3_trust_in_charity",
             label = "Charity Trust:",
-            choices = c("0", '1', '2', '3','4','5','6','7'))
-
-# Need to Fix
+            choices = c("No trust at all",
+                        "Very little trust",
+                        "Little trust",
+                        "Nuetral",
+                        "Some trust",
+                        "A lot of trust",
+                        "Complete trust"))
 
@@
          label = "Donation Frequency:",
-         choices = c('Once a week',
-                     'Once a Month',
-                     'Once every three months',
-                     'Once every six months',
-                     'Once a year',
-                     'Once every few years',
-                     'Never'))
-
-# Need to Fix
+         choices = c('More than once a month, less than once a year',
+                     'Atleast once a month'))
+
 selectInput("p3_donation_amount",
@@
          label = "Volunteered in last 12 Months:",
-         choices = c("Volunteered", "Not Volunteered"))
-
-# Need to Fix
+         choices = c("No", "Yes"))
+
 selectInput("p3_volunteer_frequency",
          label = "Volunteer Frequency:",
-         choices = c('Once a week',
-                     'Once a Month',
-                     'Once every three months',
-                     'Once every six months',
-                     'Once a year',
-                     'Once every few years',
-                     'Never'))
-
-# Need to Fix
+         choices = c("Haven't volunteered in past 12 months",
+                     "Rarely",
+                     "More than once a month, less than once a year",
+                     "At least once a month"))
+
 selectInput("p3_personal_activism",
          label = "Personal Activism:",
-         choices = c('Extremely involved',
-                     'Very involved',
-                     'Moderately involved',
-                     'Slightly involved',
-                     'Never involved'))
-
-# Need to Fix
+         choices = c('Not involved',
+                     'Involved'))
+
 selectInput("p3_family_activism",
          label = "Family Activism:",
-         choices = c('Extremely involved',
-                     'Very involved',
-                     'Moderately involved',
-                     'Slightly involved',
-                     'Never involved'))
-
-# Need to Fix
+         choices = c('Not involved',
+                     'Involved'))
+
 selectInput("p3_religious_member",
          label = "Church Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-# Need to Fix
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p3_sport_member",
          label = "Sport or Recreational Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-# Need to Fix
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p3_art_member",
          label = "Art, Music, or Educational Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-# Need to Fix
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p3_labor_member",
          label = "Labor Union Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-# Need to Fix
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p3_political_member",
          label = "Political Party Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-# Need to Fix
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p3_environmental_member",
          label = "Enviornmental Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-# Need to Fix
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p3_professional_member",
          label = "Professional Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-# Need to Fix
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p3_humanitarian_member",
          label = "Humanitarian Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-# Need to Fix
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p3_consumer_member",
          label = "Consumer Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
-
-# Need to Fix
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
+
 selectInput("p3_other_member",
          label = "Other Org. Membership:",
-         choices = c('Active Member',
-                     'Inactive Member',
-                     "Don't belong"))
+         choices = c("Don't belong",
+                     'Inactive member',
+                     'Active member'))
 
@@
 
-# Need to Fix
 selectInput("p3_education",
@@
                      "4 year degree",
-                     "Graduate degree",
+                     "Graduate or professional degree",
                      "Doctorate"))
-# Need to Fix
+
 selectInput("p3_income",
          label = "Income:",
-         choices = c('Less than $10,000',
-                     '$10,000 to $19,999',
-                     '$20,000 to $29,999',
-                     '$30,000 to $39,999',
-                     '$40,000 to $49,999',
-                     '$50,000 to $59,999',
-                     '$60,000 to $69,999',
-                     '$70,000 to $79,999',
-                     '$80,000 to $89,999',
-                     '$90,000 to $99,999',
-                     '$100,000 to $149,999',
-                     '$150,000 to $199,999',
-                     '$200,000 to $299,999',
-                     '$300,000 or more'))
+         choices = c('Less than median of $61,372',
+                     'More than median of $61,372'))
 
@@
 
-# Need to Fix
 selectInput("p3_age",
          label = "Age:",
-         choices = c('Less than Median Age (< 36)',
-                     "More than Median Age (> 36)"))
+         choices = c('Less than median age of 36',
+                     "More than median age of 36"))
 

### 2020-09-11 analysis/05_market_simulator.Rmd
Changed Persona Data file. Need corrected posterior draws now

@@
 # Persona Data from Market Simulator Workbook
-persona_data <- readxl::read_xlsx(here('analysis', 'output', "persona_config.xlsx"))
+persona_data <- readxl::read_xlsx(here('analysis', 'output', "persona_configV06.xlsx"))
 
@@
 
-beta$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")
+beta$levels = c("Amnesty International",
+                "Greenpeace", 
+                "Oxfam", 
+                "Red Cross",
+                # Org Issue
+                "Environment", 
+                "Human rights",
+                "Refugee relief",
+                # Transparency
+                "Engages in transparency",
+                # Financial Accountability
+                "Engages in financial accountability",
+                # Funding
+                "Handful of wealthy private donors", 
+                "Government grants",
+                # Gov Relations
+                "Criticized by government",
+                "Under government crackdown")
 
@@
 
-beta_persona <- as.data.frame(matrix(rep(0), nrow = 61))
+beta_persona <- as.data.frame(matrix(rep(0), nrow = 111))
 
@@
                         "Handful of wealthy private donors",
-                        "Government Grants"))
+                        "Government grants"))
 

### 2020-09-11 analysis/03_analysis.Rmd

@@
 run <- list(data = data, fit = fit)
-if (intercept == 1) write_rds(run, here::here("analysis", "output", "model_runs", "intercept_noncentered.rds"))
+if (intercept == 1) write_rds(run, here::here("analysis", "output", "model_runs", "intercept.rds"))
 if (public_affairs == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_affairs.rds"))
@@
 
-The following analysis follows specifying the model we'd like to evaluate. Note that the output of the model calibration is too large to push to GitHub.
+The following analysis follows specifying the model we'd like to evaluate. Note that the output of the model calibration is too large to push to GitHub, but we can push the draws once we extract them.
 
@@
 # Load all model output
-intercept_run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.rds"))
+intercept_run <- read_rds(here::here("analysis", "output", "model_runs", "intercept.rds"))
 public_affairs_run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
@@
 ```{r extract-draws, eval=FALSE}
-intercept <- 1                            # Intercept-only
+intercept <- 0                            # Intercept-only
 public_affairs <- 0                       # Public affairs
@@
 public_political_social_charity <- 0      # + Charity and voluntarism
-public_political_social_charity_demo <- 0 # + Demographics
+public_political_social_charity_demo <- 1 # + Demographics
 
 # Load and extract data and model output
-if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.rds"))
+if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept.rds"))
 if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
@@
 # Save draws
-if (intercept == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept_noncentered.rds"))
+if (intercept == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept.rds"))
 if (public_affairs == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))
@@
 # Load draws
-if (intercept == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "intercept_noncentered.rds"))
+if (intercept == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "intercept.rds"))
 if (public_affairs == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))

### 2020-09-11 analysis/05_market_simulator.Rmd
added new posterior means
Changed theta to gamma

@@
   group_by(i, j) %>% 
-  summarize(theta_mean = mean(Theta)) %>% 
+  summarize(gamma_mean = mean(Gamma)) %>% 
   ungroup() %>% 
-  pivot_wider(names_from = j, values_from = theta_mean) %>% 
+  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
   select(-i)

### 2020-09-11 analysis/05_market_simulator.Rmd
Updated posterior draws for public_political_social_charity_demo beta

@@
   pivot_wider(names_from = j, values_from = gamma_mean) %>% 
-  select(-i)
+  select(-i) %>% 
+  t()
 
@@
 
-# beta_test <- as.data.frame(matrix(rep(0), nrow = 13))
-# 
-# beta_test$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")
-# 
-# beta_test$ai_issue <- 0
-# beta_test$ai_issue[4] <- 1
-# beta_test$ai_issue[8] <- 1
-# beta_test$ai_issue[9] <- 1
-# 
-# 
-# beta_test$gp_issue <- 0
-# beta_test$gp_issue[4] <- 1
-# beta_test$gp_issue[5] <- 1
-# beta_test$gp_issue[8] <- 1
-# beta_test$gp_issue[9] <- 1
-# 
-# 
-# beta_test$ox_issue <- 0
-# beta_test$ox_issue[4] <- 1
-# beta_test$ox_issue[6] <- 1
-# beta_test$ox_issue[8] <- 1
-# beta_test$ox_issue[9] <- 1
-# 
-# beta_test$rc_issue <- 0
-# beta_test$rc_issue[4] <- 1
-# beta_test$rc_issue[7] <- 1
-# beta_test$rc_issue[8] <- 1
-# beta_test$rc_issue[9] <- 1
-# 
-# 
-# 
-#   ai_exp_util1 <- round(exp(t(beta_test[, 3]) %*% as.matrix(p_beta1)),2)
-#   gp_exp_util1 <- round(exp(t(beta_test[, 4]) %*% as.matrix(p_beta1)),2)
-#   ox_exp_util1 <- round(exp(t(beta_test[, 5]) %*% as.matrix(p_beta1)),2)
-#   rc_exp_util1 <- round(exp(t(beta_test[, 6]) %*% as.matrix(p_beta1)),2)
-# 
-#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-
 # Persona 2

### 2020-09-11 analysis/05_market_simulator.Rmd
Persona Inputs and Reactive Persona Levels double checked to match

@@
                      "Once a week",
-                     "Atleast once a day"))
+                     "At least once a day"))
 
@@
 
-# Some kind of Org Id that could select the organization you are looking at? Not sure how to make it change the label in the graph
-
 textInput("ai_id",
@@
 selectInput("ai_fin_trans",
-            label = "Select Financial transparency:",
+            label = "Select Financial Transparency:",
             choices = c("Doesn’t engage in transparency",
@@
 selectInput("ai_funding",
-            label = "Select Funding source:",
+            label = "Select Funding Source:",
             choices = c("Many small private donations",
@@
 selectInput("ai_gov_relat",
-            label = "Select Relationship with host government",
+            label = "Select Relationship With Host Government",
             choices = c("Friendly relationship with government",
@@
 selectInput("gp_fin_trans",
-            label = "Select Financial transparency:",
+            label = "Select Financial Transparency:",
             choices = c("Doesn’t engage in transparency",
@@
 selectInput("gp_funding",
-            label = "Select Funding source:",
+            label = "Select Funding Source:",
             choices = c("Many small private donations",
@@
 selectInput("gp_gov_relat",
-            label = "Select Relationship with host government",
+            label = "Select Relationship With Host Government",
             choices = c("Friendly relationship with government",
@@
 selectInput("ox_fin_trans",
-            label = "Select Financial transparency:",
+            label = "Select Financial Transparency:",
             choices = c("Doesn’t engage in transparency",
@@
 selectInput("ox_funding",
-            label = "Select Funding source:",
+            label = "Select Funding Source:",
             choices = c("Many small private donations",
@@
 selectInput("ox_gov_relat",
-            label = "Select Relationship with host government",
+            label = "Select Relationship With Host Government",
             choices = c("Friendly relationship with government",
@@
 selectInput("rc_fin_trans",
-            label = "Select Financial transparency:",
+            label = "Select Financial Transparency:",
             choices = c("Doesn’t engage in transparency",
@@
 selectInput("rc_funding",
-            label = "Select Funding source:",
+            label = "Select Funding Source:",
             choices = c("Many small private donations",
@@
 selectInput("rc_gov_relat",
-            label = "Select Relationship with host government",
+            label = "Select Relationship With Host Government",
             choices = c("Friendly relationship with government",
@@
 ```
-
-<!-- There is an issue of not being able to see the last selectInput options when drop down box appears -->
-
-<!-- This is for commented out code -->
-
-```{r persona 1 gauge commented}
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#     
-#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
-# 
-#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(ai_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#FFC30B"),
-#         symbol = "%")
-# })
-# 
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#   
-#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
-# 
-#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(gp_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#3fad48"),
-#         symbol = "%")
-# })
-# 
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#   
-#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-# 
-#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(ox_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#006633"),
-#         symbol = "%")
-# })
-# 
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#   
-#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-# 
-#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(rc_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#660000"),
-#         symbol = "%")
-# })
-```
-
-```{r persona 2 gauge commented}
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#     
-#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
-# 
-#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(ai_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#FFC30B"),
-#         symbol = "%")
-# })
-# 
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#   
-#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
-# 
-#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(gp_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#3fad48"),
-#         symbol = "%")
-# })
-# 
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#   
-#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-# 
-#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(ox_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#006633"),
-#         symbol = "%")
-# })
-# 
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#   
-#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-# 
-#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(rc_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#660000"),
-#         symbol = "%")
-# })
-```
-
-```{r persona 3 gauge commented}
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#     
-#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
-# 
-#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(ai_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#FFC30B"),
-#         symbol = "%")
-# })
-# 
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#   
-#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
-# 
-#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(gp_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#3fad48"),
-#         symbol = "%")
-# })
-# 
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#   
-#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-# 
-#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(ox_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#006633"),
-#         symbol = "%")
-# })
-# 
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#   
-#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-# 
-#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(rc_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#660000"),
-#         symbol = "%")
-# })
-```
-
-```{r ai gauge commented}
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#     
-#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
-# 
-#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(ai_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#FFC30B"),
-#         symbol = "%")
-# })
-# 
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#   
-#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
-# 
-#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(ai_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#006633"),
-#         symbol = "%")
-# })
-# 
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#   
-#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-# 
-#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(ai_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#b50909"),
-#         symbol = "%")
-# })
-```
-
-```{r plot ai plot commented}
-# renderPlotly({
-#   choice = df()
-#   
-#     persona1 = p_beta1 # Choose the persona
-#   
-#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
-#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
-#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
-#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
-#   
-#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   
-#     persona2 = p_beta2 # Choose the persona
-#   
-#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
-#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
-#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
-#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
-#   
-#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   
-#       persona3 = p_beta3 # Choose the persona
-#   
-#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
-#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
-#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
-#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
-#   
-#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   
-#   data <- c(ai_exp_util1, ai_rate1, 
-#             ai_exp_util2, ai_rate2,
-#             ai_exp_util3, ai_rate3)
-#   
-#   
-#   df <- as.data.frame(matrix(data, 6, 1))
-#   
-#   df[,2] <- c("Amnesty International")
-#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
-#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
-#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
-#   
-#   ggplotly(df %>% filter(Type == "Market Share") %>% 
-#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
-#              geom_bar(position = "dodge", stat = "identity") +
-#              labs(x="") + 
-#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
-#              theme(legend.position = "none")
-#     )
-# })
-```
-
-```{r valuebox ai commented}
-# renderValueBox({
-#   choice = df()
-#   
-#   persona = p_beta1 # Choose the persona
-#   
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-#   
-#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   valueBox(ai_rate,
-#            color = "#FFC30B",
-#            icon = "fa-percent")
-# })
-```
-
-```{r gp gauge commented}
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#     
-#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
-# 
-#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(gp_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#FFC30B"),
-#         symbol = "%")
-# })
-# 
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#   
-#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
-# 
-#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(gp_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#3fad48"),
-#         symbol = "%")
-# })
-# 
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#   
-#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-# 
-#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(gp_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#006633"),
-#         symbol = "%")
-# })
-```
-
-```{r plot gp plot commented}
-# renderPlotly({
-#   choice = df()
-#   
-#     persona1 = p_beta1 # Choose the persona
-#   
-#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
-#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
-#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
-#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
-#   
-#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   
-#     persona2 = p_beta2 # Choose the persona
-#   
-#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
-#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
-#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
-#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
-#   
-#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   
-#       persona3 = p_beta3 # Choose the persona
-#   
-#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
-#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
-#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
-#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
-#   
-#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   
-#   data <- c(gp_exp_util1, gp_rate1, 
-#             gp_exp_util2, gp_rate2,
-#             gp_exp_util3, gp_rate3)
-#   
-#   
-#   df <- as.data.frame(matrix(data, 6, 1))
-#   
-#   df[,2] <- c("Greenpeace")
-#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
-#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
-#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
-#   
-#   ggplotly(df %>% filter(Type == "Market Share") %>% 
-#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
-#              geom_bar(position = "dodge", stat = "identity") +
-#              labs(x="") + 
-#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
-#              theme(legend.position = "none")
-#     )
-# })
-```
-
-```{r valuebox gp commented}
-# renderValueBox({
-#   choice = df()
-#   persona = p_beta1 # Choose the persona
-#   
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-#   
-#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   valueBox(gp_rate,
-#            color = "#3fad48",
-#            icon = "fa-percent")
-# })
-```
-
-```{r ox gauge commented}
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#     
-#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
-# 
-#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(ox_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#FFC30B"),
-#         symbol = "%")
-# })
-# 
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#   
-#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
-# 
-#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(ox_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#3fad48"),
-#         symbol = "%")
-# })
-# 
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#   
-#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-# 
-#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(ox_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#006633"),
-#         symbol = "%")
-# })
-```
-
-```{r plot ox plot commented}
-# renderPlotly({
-#   choice = df()
-#   
-#     persona1 = p_beta1 # Choose the persona
-#   
-#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
-#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
-#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
-#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
-#   
-#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   
-#     persona2 = p_beta2 # Choose the persona
-#   
-#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
-#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
-#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
-#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
-#   
-#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   
-#       persona3 = p_beta3 # Choose the persona
-#   
-#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
-#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
-#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
-#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
-#   
-#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   
-#   data <- c(ox_exp_util1, ox_rate1, 
-#             ox_exp_util2, ox_rate2,
-#             ox_exp_util3, ox_rate3)
-#   
-#   
-#   df <- as.data.frame(matrix(data, 6, 1))
-#   
-#   df[,2] <- c("Oxfam")
-#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
-#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
-#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
-#   
-#   ggplotly(df %>% filter(Type == "Market Share") %>% 
-#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
-#              geom_bar(position = "dodge", stat = "identity") +
-#              labs(x="") + 
-#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
-#              theme(legend.position = "none")
-#     )
-# })
-```
-
-```{r valuebox ox commented}
-# renderValueBox({
-#   choice = df()
-#   
-#   persona = p_beta1 # Choose the persona
-#   
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-#   
-#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   valueBox(ox_rate,
-#            color = "#006633",
-#            icon = "fa-percent")
-# })
-```
-
-```{r rc gauge commented}
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#     
-#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
-# 
-#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(rc_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#FFC30B"),
-#         symbol = "%")
-# })
-# 
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#   
-#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
-# 
-#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(rc_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#3fad48"),
-#         symbol = "%")
-# })
-# 
-# renderGauge({
-#   choice = df()
-#   per_choice = p()
-#   
-#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
-# 
-#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   gauge(rc_rate,
-#         min = 0,
-#         max = 100,
-#         gaugeSectors(colors = "#006633"),
-#         symbol = "%")
-# })
-```
-
-```{r plot rc plot commented}
-# renderPlotly({
-#   choice = df()
-#   
-#     persona1 = p_beta1 # Choose the persona
-#   
-#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
-#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
-#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
-#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
-#   
-#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-#   
-#     persona2 = p_beta2 # Choose the persona
-#   
-#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
-#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
-#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
-#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
-#   
-#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-#   
-#       persona3 = p_beta3 # Choose the persona
-#   
-#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
-#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
-#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
-#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
-#   
-#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-#   
-#   data <- c(rc_exp_util1, rc_rate1, 
-#             rc_exp_util2, rc_rate2,
-#             rc_exp_util3, rc_rate3)
-#   
-#   
-#   df <- as.data.frame(matrix(data, 6, 1))
-#   
-#   df[,2] <- c("Red Cross")
-#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
-#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
-#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
-#   
-#   ggplotly(df %>% filter(Type == "Market Share") %>% 
-#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
-#              geom_bar(position = "dodge", stat = "identity") +
-#              labs(x="") + 
-#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
-#              theme(legend.position = "none")
-#     )
-# })
-```
-
-```{r valuebox rc commented}
-# renderValueBox({
-#   choice = df()
-#   
-#   persona = p_beta1 # Choose the persona
-#    
-#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
-#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
-#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
-#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
-#   
-#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
-#   
-#   valueBox(rc_rate,
-#            color = "#660000",
-#            icon = "fa-percent")
-# })
-```

### 2020-09-11 analysis/05_market_simulator.Rmd
Checked Organization inputs and persona inputs

@@
                      "Sometimes",
-                     'Always'))
+                     "Always"))
 
@@
          label = "Medium to follow news:",
-         choices = c('TV',
-                     'Print',
+         choices = c("TV",
+                     "Print",
                      "Online (not social media)",
@@
                      "Agree",
-                     "Strongly Agree"))
+                     "Strongly agree"))
 
@@
          choices = c('More than once a month, less than once a year',
-                     'Atleast once a month'))
+                     'At least once a month'))
 
@@
           value = "Organization 2",
-          placeholder = "Enter Organiation Name"
-)
+          placeholder = "Enter Organiation Name")
 
@@
           value = "Organization 3",
-          placeholder = "Enter Organiation Name"
-)
+          placeholder = "Enter Organiation Name")
 
@@
           value = "Organization 4",
-          placeholder = "Enter Organiation Name"
-)
+          placeholder = "Enter Organiation Name")
 

### 2020-09-11 analysis/05_market_simulator.Rmd
Took out rounding the market values

@@
 
-################### Org Reactive Element####################################
+################### Org Reactive Element ####################################
 
@@
 
-################### Persona Reactive Element####################################
+################### Persona Reactive Element ####################################
 
@@
 
+<!-- Practice Code -->
+
 ```{r practice code}
@@
 <!-- Persona Inputs -->
-<!-- ================================================= -->
-
-<!-- ## Persona Inputs -->
-
 ```{r persona betas}
@@
   # Expected Utility
-  ai_exp_util1 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta1)),2)
-  gp_exp_util1 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta1)),2)
-  ox_exp_util1 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta1)),2)
-  rc_exp_util1 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta1)),2)
+  ai_exp_util1 <- exp(t(org_choice[, 3]) %*% as.matrix(p_beta1))
+  gp_exp_util1 <- exp(t(org_choice[, 4]) %*% as.matrix(p_beta1))
+  ox_exp_util1 <- exp(t(org_choice[, 5]) %*% as.matrix(p_beta1))
+  rc_exp_util1 <- exp(t(org_choice[, 6]) %*% as.matrix(p_beta1))
 
   # Market Share
-  ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
-  rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+  ai_rate1 <- 100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1)
+  gp_rate1 <- 100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1)
+  ox_rate1 <- 100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1)
+  rc_rate1 <- 100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1)
 
@@
   # Expected Utility
-  ai_exp_util2 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta2)),2)
-  gp_exp_util2 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta2)),2)
-  ox_exp_util2 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta2)),2)
-  rc_exp_util2 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta2)),2)
+  ai_exp_util2 <- exp(t(org_choice[, 3]) %*% as.matrix(p_beta2))
+  gp_exp_util2 <- exp(t(org_choice[, 4]) %*% as.matrix(p_beta2))
+  ox_exp_util2 <- exp(t(org_choice[, 5]) %*% as.matrix(p_beta2))
+  rc_exp_util2 <- exp(t(org_choice[, 6]) %*% as.matrix(p_beta2))
 
   # Market Share
-  ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-  gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-  ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
-  rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+  ai_rate2 <- 100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2)
+  gp_rate2 <- 100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2)
+  ox_rate2 <- 100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2)
+  rc_rate2 <- 100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2)
 
@@
   # Expected Utility
-  ai_exp_util3 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta3)),2)
-  gp_exp_util3 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta3)),2)
-  ox_exp_util3 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta3)),2)
-  rc_exp_util3 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta3)),2)
+  ai_exp_util3 <- exp(t(org_choice[, 3]) %*% as.matrix(p_beta3))
+  gp_exp_util3 <- exp(t(org_choice[, 4]) %*% as.matrix(p_beta3))
+  ox_exp_util3 <- exp(t(org_choice[, 5]) %*% as.matrix(p_beta3))
+  rc_exp_util3 <- exp(t(org_choice[, 6]) %*% as.matrix(p_beta3))
 
   # Market Share
-  ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-  gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-  ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
-  rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+  ai_rate3 <- 100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3)
+  gp_rate3 <- 100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3)
+  ox_rate3 <- 100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3)
+  rc_rate3 <- 100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3)
 
@@
 
-<!-- Organizational Tabs -->
+<!-- Persona and Organizational Tabs -->
 

### 2020-09-11 analysis/05_market_simulator.Rmd
small changes to some code

@@
 <!-- Practice Code -->
-
 ```{r practice code}
@@
 <!-- Main page Chart with All Personas -->
-
 Market Share
@@
 
-```{r plot all personas}
+```{r global plot}
 
@@
 <!-- Persona and Organizational Tabs -->
-
 Personas And Organizations {.tabset .tabset-fade}

### 2020-09-11 analysis/03_analysis.Rmd
Updated covariate labels

@@
 
-# Load draws and plot marginals and contrasts
+# Load draws and plot marginals, contrasts, and heatmaps
 
-```{r plot-marginals}
-#########
+Now that we have the draws extracted, we can load draws from the model of interest and plot marginals, contrasts, and heatmaps.
 
-# Update covariate labels
-# Add contrasts where appropriate (see hypotheses Rmd documents)
+## Load draws and assign labels
 
-#########
-
-intercept <- 0                            # Intercept-only
+```{r load-draws}
+intercept <- 1                            # Intercept-only
 public_affairs <- 0                       # Public affairs
@@
 
-# Name labels
+# Assign level labels
 level_labels <- c(
@@
 
-# Name covariates
-if (public_affairs == 1) {
-  covariate_labels <- c(
-    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
+# Assign covariate covariates
+public_affairs_labels <- c(
+  # *Q2.1*: How often do you follow national news? 
+  str_c(
+    "Follow national news: ", 
+    c("Once a week", "At least once a day")
+  ),
+  # *Q2.3*: Which mediums do you use to follow news? (Select all that apply.)
   str_c(
     "Medium to follow news: ", 
-      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
+    c(
+      "TV", "Print", "Online (excluding social media)", "Social media", 
+      "Radio", "Email newsletters", "News app"
+    )
   ),
-    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No"
+  # *Q2.4*: How often would you say you follow what's going on in government and public affairs?
+  "Follow government and public affairs: Often", 
+  # *Q5.7*: Have you ever traveled to a developing country? 
+  "Traveled to a developing country: No"
 )
-}
-if (political_ideology == 1) {
-  covariate_labels <- c(
-    "Liberal to Conservative"
+political_ideology_labels <- c(
+  # *Q5.2*: On a scale of extremely liberal (1) to extremely conservative (7), how would you describe your political views?
+  str_c(
+    "Liberal to Conservative: ", 
+    c(
+      "Somewhat liberal", "Slightly liberal", "Moderate",
+      "Slightly conservative", "Somewhat conservative", "Extremely conservative"
     )
-}
-if (social_views == 1) {
-  covariate_labels <- c(
-    "Trust in political institutions: None to Complete", "People should be more charitable: Agree to Disagree",
-    "Religious and worship service attendance: Multiple times a week to Never", "Importance of religion: Extremely to Not at all",
+  )
+)
+social_views_labels <- c(
+  # *Q5.6*: On a scale of no trust (1) to complete trust (7), how much do you trust political institutions and the state?
+  str_c(
+    "Trust in political institutions: ", 
+    c(
+      "Very little trust", "Little trust", 
+      "Neutral", "Some trust", "A lot of trust", "Complete trust"
+    )
+  ),
+  # *Q5.11*: On a scale of strongly agree (1) to strongly disagree (7), rate your response to the following statement: People should be more charitable towards others in society.
+  str_c(
+    "People should be more charitable: ", 
+    c(
+      "Agree", "Somewhat agree", "Neutral", 
+      "Somewhat disagree", "Disagree", "Strongly disagree"
+    )
+  ),
+  # *Q5.8*: How often do you attend religious or worship services, not including weddings and funerals?
+  str_c(
+    "Religious and worship service attendance: ", 
+    c("Rarely", "At least once a month")
+  ),
+  # *Q5.9*: How important is religion in your life?
+  "Importance of religion: Important",
+  # *Q5.10*: What is your current religion, if any?
   str_c(
     "Religion: ", 
-      c("Protestant", "Christian Orthodox", "Jewish", "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")
+    c(
+      "Protestant", "Christian Orthodox", "Jewish", "Muslim", 
+      "Sikh", "Hindu", "Buddhist", "Atheist", "Other"
     )
   )
-}
-if (charity_voluntarism == 1) {
-  covariate_labels <- c(
-    "Importance of trusing charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",
-    "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: No", "Volunteer frequency: Weekly to Every few years",
-    "History of activism: Extreme to Never", "History of family activism: Extreme to Never", 
+)
+charity_voluntarism_labels <- c(
+  # *Q2.7*: On a scale of not at all important (1) to essential (7), how important is it for you to trust charities?
   str_c(
+    "Importance of trusing charities: ", 
     c(
-        "Church or religious organization: ", "Sport or recreational organization: ", "Art, music, or educational organization: ",
-        "Labor union: ", "Political party: ", "Environmental organization: ", "Professional association: ", 
-        "Humanitarian or charitable organization: ", "Consumer organization: ", "Other organization: "
+      "Very unimportant", "Somewhat unimportant", 
+      "Neutral", "Somewhat important", "Very important", "Essential"
+    )
   ),
-      "Member to Not"
+  # *Q2.8*: On a scale of no trust at all (1) to complete trust (7), how much do you trust charities?
+  str_c(
+    "Trust in charities: ", 
+    c(
+      "Very little trust", "Little trust", 
+      "Neutral", "Some trust", "A lot of trust", "Complete trust"
+    )
+  ),
+  # *Q2.5*: How often do you donate to charity (with either cash or in-kind)?
+  "Donation frequency: At least once a month",
+  # *Q2.6*: How much did you donate to charity last year?
+  str_c(
+    "Donated last year: ",
+    c(
+      "$50-$99", "$100-$499", "$500-$999", 
+      "$1000-$4,999", "$5000-$9,999", "$10,000+"
+    )
+  ),
+  # *Q2.9*: Have you volunteered in the past 12 months?
+  "Volunteered in past 12 months: Yes", 
+  # *Q2.10*: How often do you volunteer?
+  str_c(
+    "Volunteer frequency: ",
+    c("Rarely", "More than once a month, less than once a year", "At least once a month")
+  ),
+  # *Q5.4*: Historically, how involved have you been in activist causes?
+  "History of activism: Involved",
+  # *Q5.5*: Historically, how involved has your family been in activist causes?
+  "History of family activism: Involved",
+  # *Q5.3*: Here is a list of different types of voluntary organizations.
+For each organization, indicate whether you are an active member, an inactive member, or not a member of that type of organization:
+  str_c(
+    "Church or religious organization: ",
+    c("Inactive member", "Active member")
+  ),
+  str_c(
+    "Sport or recreational organization: ",
+    c("Inactive member", "Active member")
+  ),
+  str_c(
+    "Art, music, or educational organization: ",
+    c("Inactive member", "Active member")
+  ),
+  str_c(
+    "Labor union: ",
+    c("Inactive member", "Active member")
+  ),
+  str_c(
+    "Political party: ",
+    c("Inactive member", "Active member")
+  ),
+  str_c(
+    "Environmental organization: ",
+    c("Inactive member", "Active member")
+  ),
+  str_c(
+    "Professional association: ",
+    c("Inactive member", "Active member")
+  ),
+  str_c(
+    "Humanitarian or charitable organization: ",
+    c("Inactive member", "Active member")
+  ),
+  str_c(
+    "Consumer organization: ",
+    c("Inactive member", "Active member")
+  ),
+  str_c(
+    "Other organization: ",
+    c("Inactive member", "Active member")
   )
 )
-}
-if (demographics == 1) {
-  covariate_labels <- c(
+demographics_labels <- c(
+  # *Q5.12*: What is your gender?
   str_c(
@@
   ), 
+  # *Q5.13*: Are you now married, widowed, divorced, separated, or never married?
   str_c(
@@
   ), 
-    "Education: Less than high school to Doctorate",
-    "Income: Less than $10,000 to $300,000 or more",
+  # *Q5.14*: What is the highest degree or level of school you have completed?
+  str_c(
+    "Education: ", 
+    c(
+      "High school graduate", 
+      "Some college", "2 year degree", "4 year degree", 
+      "Graduate or professional degree", "Doctorate"
+    )
+  ), 
+  # *Q5.15*: What is your annual household income before taxes?
+  "Income: More than median",
+  # *Q5.16*: Choose one or more races that you consider yourself to be:
   str_c(
     "Race/ethnicity: ",
-      c("White", "Black or African American", "American Indian or Alaska Native", "Asian", "Native Hawaiian or Pacific Islander", "Other")
+    c(
+      "White", "Black or African American", "American Indian or Alaska Native", 
+      "Asian", "Native Hawaiian or Pacific Islander", "Other"
+    )
   ),
-    "Age: Under 18 to 85 or older"
+  # *Q5.17*: How old are you?
+  "Age: More than median"
 )
-}
+if (public_affairs == 1) covariate_labels <- public_affairs_labels
+if (political_ideology == 1) covariate_labels <- political_ideology_labels
+if (social_views == 1) covariate_labels <- social_views_labels
+if (charity_voluntarism == 1) covariate_labels <- charity_voluntarism_labels
+if (demographics == 1) covariate_labels <- demographics_labels
 if (public_political == 1) {
-  covariate_labels <- c(
-    # Public affairs
-    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
-    str_c(
-      "Medium to follow news: ", 
-      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
-    ),
-    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No",
-    # Political ideology
-    "Liberal to Conservative"
-  )
+  covariate_labels <- c(public_affairs_labels, political_ideology_labels)
 }
 if (public_political_social == 1) {
-  covariate_labels <- c(
-    # Public affairs
-    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
-    str_c(
-      "Medium to follow news: ", 
-      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
-    ),
-    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No",
-    # Political ideology
-    "Liberal to Conservative",
-    # Social views
-    "Trust in political institutions: None to Complete", "People should be more charitable: Agree to Disagree",
-    "Religious and worship service attendance: Multiple times a week to Never", "Importance of religion: Extremely to Not at all",
-    str_c(
-      "Religion: ", 
-      c("Protestant", "Christian Orthodox", "Jewish", "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")
-    )
-  )
+  covariate_labels <- c(public_affairs_labels, political_ideology_labels, social_views_labels)
 }
@@
   covariate_labels <- c(
-    # Public affairs
-    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
-    str_c(
-      "Medium to follow news: ", 
-      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
-    ),
-    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No",
-    # Political ideology
-    "Liberal to Conservative",
-    # Social views
-    "Trust in political institutions: None to Complete", "People should be more charitable: Agree to Disagree",
-    "Religious and worship service attendance: Multiple times a week to Never", "Importance of religion: Extremely to Not at all",
-    str_c(
-      "Religion: ", 
-      c("Protestant", "Christian Orthodox", "Jewish", "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")
-    ),
-    # Charity and voluntarism
-    "Importance of trusing charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",
-    "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: No", "Volunteer frequency: Weekly to Every few years",
-    "History of activism: Extreme to Never", "History of family activism: Extreme to Never", 
-    str_c(
-      c(
-        "Church or religious organization: ", "Sport or recreational organization: ", "Art, music, or educational organization: ",
-        "Labor union: ", "Political party: ", "Environmental organization: ", "Professional association: ", 
-        "Humanitarian or charitable organization: ", "Consumer organization: ", "Other organization: "
-      ), 
-      "Member to Not"
-    )
+    public_affairs_labels, political_ideology_labels, 
+    social_views_labels, charity_voluntarism_labels
   )
@@
   covariate_labels <- c(
-    # Public affairs
-    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
-    str_c(
-      "Medium to follow news: ", 
-      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
-    ),
-    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No",
-    # Political ideology
-    "Liberal to Conservative",
-    # Social views
-    "Trust in political institutions: None to Complete", "People should be more charitable: Agree to Disagree",
-    "Religious and worship service attendance: Multiple times a week to Never", "Importance of religion: Extremely to Not at all",
-    str_c(
-      "Religion: ", 
-      c("Protestant", "Christian Orthodox", "Jewish", "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")
-    ),
-    # Charity and voluntarism
-    "Importance of trusing charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",
-    "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: No", "Volunteer frequency: Weekly to Every few years",
-    "History of activism: Extreme to Never", "History of family activism: Extreme to Never", 
-    str_c(
-      c(
-        "Church or religious organization: ", "Sport or recreational organization: ", "Art, music, or educational organization: ",
-        "Labor union: ", "Political party: ", "Environmental organization: ", "Professional association: ", 
-        "Humanitarian or charitable organization: ", "Consumer organization: ", "Other organization: "
-      ), 
-      "Member to Not"
-    ),
-    # Demographics
-    str_c(
-      "Gender: ", 
-      c("Female", "Transgender", "Prefer not to say", "Other")
-    ), 
-    str_c(
-      "Marital status: ", 
-      c("Widowed", "Divorced", "Separated", "Never married")
-    ), 
-    "Education: Less than high school to Doctorate",
-    "Income: Less than $10,000 to $300,000 or more",
-    str_c(
-      "Race/ethnicity: ", 
-      c("White", "Black or African American", "American Indian or Alaska Native", "Asian", "Native Hawaiian or Pacific Islander", "Other")
-    ),
-    "Age: Under 18 to 85 or older"
+    public_affairs_labels, political_ideology_labels, 
+    social_views_labels, charity_voluntarism_labels, demographics_labels
   )
 }
-
-# # Create matrix of Gammas.
-# gamma_draws <- draws %>% 
-#   group_by(i, j) %>% 
-#   summarize(gamma_mean = mean(Gamma))
-# 
-# gamma_matrix <- matrix(as.matrix(gamma_draws)[,3], nrow = max(draws$j), ncol = max(draws$i))
-# write.csv(gamma_matrix, file = here::here("analysis", "output", "posterior_means.csv"))
-
-# Plot marginals
-# if (intercept == 1) {
-#   draws %>% 
-#     mutate(
-#       levels = factor(i, labels = level_labels)
-#     ) %>%
-#     ggplot(aes(x = Gamma, y = levels)) + 
-#     geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
-#     # geom_halfeyeh(.width = .95) +
-#     geom_vline(xintercept = 0, color = "grey") +
-#     labs(y = "Attribute Levels")
-# }
-
-# if (intercept != 1) {
-#   draws %>% 
-#     filter(j != 1) %>% 
-#     mutate(
-#       levels = factor(i, labels = level_labels), 
-#       covariates = factor(j, labels = covariate_labels)  
-#     ) %>%
-#     ggplot(aes(x = Gamma, y = covariates)) +
-#        geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
-#        # geom_halfeyeh(.width = .95) +
-#        geom_vline(xintercept = 0, color = "white") +
-#        labs(y = "Covariates") +
-#        facet_wrap(~ levels, ncol = 5)
-# }
-
-# # Save plot
-# if (intercept == 1) file_name <- paste("intercept_marginal-posteriors.png")
-# if (public_affairs == 1) file_name <- paste("public-affairs_marginal-posteriors.png")
-# if (political_ideology == 1) file_name <- paste("political-ideology_marginal-posteriors.png")
-# if (social_views == 1) file_name <- paste("social-views_marginal-posteriors.png")
-# if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_marginal-posteriors.png")
-# if (demographics == 1) file_name <- paste("demographics_marginal-posteriors.png")
-# if (public_political == 1) file_name <- paste("public-political_marginal-posteriors.png")
-# if (public_political_social == 1) file_name <- paste("public-political-social_marginal-posteriors.png")
-# if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_marginal-posteriors.png")
-# if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_marginal-posteriors.png")
-# ggsave(
-#   file_name,
-#   path = here::here("analysis", "output", "figures"),
-#   width = ifelse(intercept == 1, 12, 20), 
-#   height = ifelse(sum(intercept, public_affairs, political_ideology, social_views, charity_voluntarism, demographics) == 1, 12, 20), 
-#   units = "in"
-# )
 ```
 
-As an experiment, it might be helpful to use a heatmap to identify where there are significant differences in the non-intercept models, which can then be narrowed down using the marginal plots.
+## Plot marginals
 
-```{r heatmaps}
+```{r plot-marginals}
+# Plot marginals
+if (intercept == 1) {
+  draws %>%
+    mutate(
+      levels = factor(j, labels = level_labels)
+    ) %>%
+    ggplot(aes(x = Gamma, y = levels)) +
+    geom_halfeye(.width = .95) +
+    geom_vline(xintercept = 0, color = "grey") +
+    labs(y = "Attribute Levels")
+}
+if (intercept != 1) {
+  draws %>%
+    filter(j != 1) %>%
+    mutate(
+      levels = factor(i, labels = level_labels),
+      covariates = factor(j, labels = covariate_labels)
+    ) %>%
+    ggplot(aes(x = Gamma, y = covariates)) +
+       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+       # geom_halfeyeh(.width = .95) +
+       geom_vline(xintercept = 0, color = "white") +
+       labs(y = "Covariates") +
+       facet_wrap(~ levels, ncol = 5)
+}
+
+# Save plot
+if (intercept == 1) file_name <- paste("intercept_marginal-posteriors.png")
+if (public_affairs == 1) file_name <- paste("public-affairs_marginal-posteriors.png")
+if (political_ideology == 1) file_name <- paste("political-ideology_marginal-posteriors.png")
+if (social_views == 1) file_name <- paste("social-views_marginal-posteriors.png")
+if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_marginal-posteriors.png")
+if (demographics == 1) file_name <- paste("demographics_marginal-posteriors.png")
+if (public_political == 1) file_name <- paste("public-political_marginal-posteriors.png")
+if (public_political_social == 1) file_name <- paste("public-political-social_marginal-posteriors.png")
+if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_marginal-posteriors.png")
+if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_marginal-posteriors.png")
+ggsave(
+  file_name,
+  path = here::here("analysis", "output", "figures"),
+  width = ifelse(intercept == 1, 12, 20),
+  height = ifelse(sum(intercept, public_affairs, political_ideology, social_views, charity_voluntarism, demographics) == 1, 12, 20),
+  units = "in"
+)
+```
+
+## Plot contrasts
+
+```{r plot-contrasts}
+
+```
+
+## Plot heatmaps
+
+Instead of plotting marginals or contrasts, we can use a heatmap to identify where there are significant differences in the non-intercept models, which can then be narrowed down using the marginal plots.
+
+```{r plot-heatmaps}
 if (public_affairs == 1) plot_title <- paste("Public Affairs")

### 2020-09-11 analysis/05_market_simulator.Rmd

--- 2020-09-11 analysis/05_market_simulator.Rmd
@@
   pivot_wider(names_from = j, values_from = gamma_mean) %>% 
-  select(-i) %>% 
-  t()
+  select(-i)
 
 # Persona Data from Market Simulator Workbook
-persona_data <- readxl::read_xlsx(here('analysis', 'output', "persona_configV06.xlsx"))
+persona_data <- readxl::read_xlsx(here('analysis', 'output', "persona_config.xlsx"))
 
@@
 
-beta$levels = c("Amnesty International",
-                "Greenpeace", 
-                "Oxfam", 
-                "Red Cross",
-                # Org Issue
-                "Environment", 
-                "Human rights",
-                "Refugee relief",
-                # Transparency
-                "Engages in transparency",
-                # Financial Accountability
-                "Engages in financial accountability",
-                # Funding
-                "Handful of wealthy private donors", 
-                "Government grants",
-                # Gov Relations
-                "Criticized by government",
-                "Under government crackdown")
+beta$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")
 
@@
 
-beta_persona <- as.data.frame(matrix(rep(0), nrow = 111))
+beta_persona <- as.data.frame(matrix(rep(0), nrow = 61))
 
@@
                         # Follow National News
+                        "Rarely", 
                         "Once a Week",
@@
                         # Follow International News
+                        "Never",
                         "Sometimes",
@@
                         "Print",
-                        "Online (not social media)",
-                        "Social media",
+                        "Online (excluding social media)",
+                        "Social Media",
                         "Radio",
-                        "Email newsletter",
+                        "Email",
                         "News app",
                         # Follow Government or Public Affairs
-                        "Often", 
-                        # Travel to developing Countries
-                        "Yes", 
+                        "", 
+                        # Travel to Countries
+                        "Doesn't Travel", 
                         # Political Preference
-                        "Somewhat liberal",
-                        "Slightly liberal",
-                        "Moderate",
-                        "Slightly conservative",
-                        "Somewhat conservative",
-                        "Extremely conservative",
+                        "Political Preference", 
                         # Trust in Political Institute
-                        "Very little trust",
-                        "Little trust",
-                        "Nuetral",
-                        "Some trust",
-                        "A lot of trust",
-                        "Complete trust",
+                        "Trust in Political Institutions",
                         # Should Others be Charitable
-                        "Disagree",
-                        "Somewhat disagree",
-                        "Nuetral",
-                        "Somewhat agree",
-                        "Agree",
-                        "Strongly agree",
-                        # Worship Service Attendance
-                        "Rarely",
-                        "At least once a month",
+                        "Others Should be Charitable",
+                        # Worship Service Attendence
+                        "Worship Service Attendence",
                         # Religious Importance
-                        "Important",
+                        "Religious Importance",
                         # Religion
@@
                         # Charity Trust Importance
-                        "Very unimportant",
-                        "Somewhat unimportant",
-                        "Nuetral",
-                        "Somewhat important",
-                        "Very important",
-                        "Essential",
+                        "Chartiy Trust Importance",
                         # Trust in Charities
-                        "Very little trust",
-                        "Little trust",
-                        "Nuetral",
-                        "Some trust",
-                        "A lot of trust",
-                        "Complete trust",
+                        "Trust in Charity", 
                         # Donation Frequency
-                        "At least once a month", 
+                        "Donation Frequency", 
                         # Donation Amount
-                        "$50-$99",
-                        "$100-$499",
-                        "$500-$999",
-                        "$1,000-$4,999",
-                        "$5,000-$9,999",
-                        "$10,000 +",
+                        "Donation Amount",
                         # Volunteered last 12 months
-                        "Yes",
+                        "Not Volunteered",
                         # Volunteer Frequency
-                        "Rarely",
-                        "More than once a month, less than once a year",
-                        "At least once a month",
+                        "Volunteer Frequency",
                         # Personal Activism
-                        "Involved",
+                        "Personal Activism",
                         # Family Activism
-                        "Involved",
-                        # Religious Membership
-                        "Inactive member",
-                        "Active member",
+                        "Family Activism",
+                        # Relgious Membership
+                        "Religious Membership", 
                         # Sport or Recreational Membership
-                        "Inactive member",
-                        "Active member", 
+                        "Sport or Recreational Membership", 
                         # Art, Music, or Educational Membership
-                        "Inactive member",
-                        "Active member",
+                        "Art, Music, or Educational Membership",
                         # Labor Union Membership
-                        "Inactive member",
-                        "Active member",
+                        "Labor Union Membership",
                         # Political Party Membership
-                        "Inactive member",
-                        "Active member",
+                        "Political Party Membership",
                         # Environmental Organization Membership
-                        "Inactive member",
-                        "Active member",
+                        "Environmental Organization Membership",
                         # Professional Association
-                        "Inactive member",
-                        "Active member",
+                        "Professional Association", 
                         # Humanitarian or Charity Membership
-                        "Inactive member",
-                        "Active member",
+                        "Humanitarian or Charity Membership",
                         # Consumer Organization Membership
-                        "Inactive member",
-                        "Active member",
+                        "Consumer Organization Membership",
                         #Other Organization Membership
-                        "Inactive member",
-                        "Active member",
+                        "Other Organization Membership",
                         # Gender
@@
                         "Separated",
-                        "Never married",
+                        "Never Married",
                         # Education
-                        "High school graduate", 
-                        "Some college",
-                        "2 year degree",
-                        "4 year degree",
-                        "Graduate or professional degree",
-                        "Doctorate",
+                        "Education", 
                         # Income
-                        "More than median of $61,372", 
+                        "Income", 
                         # Race
                         "White", 
-                        "Black or African American", 
-                        "American Indian or Alaska Native", 
+                        "Black", 
+                        "American Indian", 
                         "Asian", 
-                        "Native Hawaiian or Pacific Islander", 
+                        "Pacific Islander", 
                         "Other (Race)", 
                         # Age
-                        "More than median age of 36")
+                        "Age")
 
 # p reactive element ----
+
+p1_politic_pref <- reactive({
+  max(input$p1_political_pref)
+})
 
@@
 
+# beta_test <- as.data.frame(matrix(rep(0), nrow = 13))
+# 
+# beta_test$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")
+# 
+# beta_test$ai_issue <- 0
+# beta_test$ai_issue[4] <- 1
+# beta_test$ai_issue[8] <- 1
+# beta_test$ai_issue[9] <- 1
+# 
+# 
+# beta_test$gp_issue <- 0
+# beta_test$gp_issue[4] <- 1
+# beta_test$gp_issue[5] <- 1
+# beta_test$gp_issue[8] <- 1
+# beta_test$gp_issue[9] <- 1
+# 
+# 
+# beta_test$ox_issue <- 0
+# beta_test$ox_issue[4] <- 1
+# beta_test$ox_issue[6] <- 1
+# beta_test$ox_issue[8] <- 1
+# beta_test$ox_issue[9] <- 1
+# 
+# beta_test$rc_issue <- 0
+# beta_test$rc_issue[4] <- 1
+# beta_test$rc_issue[7] <- 1
+# beta_test$rc_issue[8] <- 1
+# beta_test$rc_issue[9] <- 1
+# 
+# 
+# 
+#   ai_exp_util1 <- round(exp(t(beta_test[, 3]) %*% as.matrix(p_beta1)),2)
+#   gp_exp_util1 <- round(exp(t(beta_test[, 4]) %*% as.matrix(p_beta1)),2)
+#   ox_exp_util1 <- round(exp(t(beta_test[, 5]) %*% as.matrix(p_beta1)),2)
+#   rc_exp_util1 <- round(exp(t(beta_test[, 6]) %*% as.matrix(p_beta1)),2)
+# 
+#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+
 # Persona 2
@@
 
+# Need to Fix
 selectInput("p1_national_news",
          label = "Follow national news:",
-         choices = c("Rarely",
+         choices = c("Atleast once a day",
                      "Once a week",
-                     "At least once a day"))
-
+                     "Rarely"
+                     ))
+
+# Need to Fix
 selectInput("p1_international_news",
          label = "Follow international news:",
-         choices = c("Never",
+         choices = c('Always',
                      "Sometimes",
-                     "Always"))
+                     "Never"))
 
@@
          label = "Medium to follow news:",
-         choices = c("TV",
-                     "Print",
-                     "Online (not social media)",
-                     "Social media",
+         choices = c('TV',
+                     'Print',
+                     "Online (excluding social media)",
+                     "Social Media",
                      "Radio",
-                     "Email newsletter",
+                     "Email",
                      "News app"),
@@
 
+# Need to Fix
 selectInput("p1_follow_gov",
          label = "Follow government & public affairs:",
-         choices = c("Not Often",
-                     "Often"))
+         choices = c('Most of the time',
+                     'Some of the time',
+                     "Only now and then",
+                     "Hardly at all"))
 
@@
          label = "Travel to developing country:",
-         choices = c('No', "Yes"))
-
+         choices = c('Does Travel', "Doesn't Travel"))
+
+# Need to Fix
 selectInput("p1_political_pref",
          label = "Political views from liberal to conservative:",
-         choices = c("Extremely liberal",
-                     "Somewhat liberal",
-                     "Slightly liberal",
-                     "Moderate",
-                     "Slightly conservative",
-                     "Somewhat conservative",
-                     "Extremely conservative"))
-
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+# Need to Fix
 selectInput("p1_institution_trust",
          label = "Political institution trust from none to complete:",
-         choices = c("No trust at all",
-                     "Very little trust",
-                     "Little trust",
-                     "Nuetral",
-                     "Some trust",
-                     "A lot of trust",
-                     "Complete trust"))
-
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+# Need to Fix
 selectInput("p1_others_charitable",
          label = "People should be more charitable:",
-         choices = c("Strongly Disagree",
-                     "Disagree",
-                     "Somewhat disagree",
-                     "Nuetral",
-                     "Somewhat agree",
-                     "Agree",
-                     "Strongly agree"))
-
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+# Need to Fix
 selectInput("p1_worship_attendance",
          label = "Worship service attendance:",
-         choices = c("Not sure",
-                     "Rarely",
-                     "At least once a month"))
-
+         choices = c('Multiple times a week',
+                     'Once a week',
+                     "Once a month",
+                     "Few times a year",
+                     "Once a year",
+                     "Never"))
+
+# Need to Fix
 selectInput("p1_religion_importance",
          label = "Importance of religion:",
-         choices = c("Not important",
-                     "Important"))
+         choices = c('Extremely important',
+                     'Very important',
+                     'Moderately important',
+                     'Slightly important',
+                     'Not at all important'))
 
@@
 
+# Need to Fix
 selectInput("p1_charity_importance",
           label = "Charity Importance:",
-          choices = c("Not at all important",
-                      "Very unimportant",
-                      "Somewhat unimportant",
-                      "Nuetral",
-                      "Somewhat important",
-                      "Very important",
-                      "Essential"))
-
+          choices = c("0", '1', '2', '3','4','5','6','7'))
+
+# Need to Fix
 selectInput("p1_trust_in_charity",
             label = "Charity Trust:",
-            choices = c("No trust at all",
-                        "Very little trust",
-                        "Little trust",
-                        "Nuetral",
-                        "Some trust",
-                        "A lot of trust",
-                        "Complete trust"))
+            choices = c("0", '1', '2', '3','4','5','6','7'))
+
+# Need to Fix
 
@@
          label = "Donation Frequency:",
-         choices = c('More than once a month, less than once a year',
-                     'At least once a month'))
-
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+# Need to Fix
 selectInput("p1_donation_amount",
@@
          label = "Volunteered in last 12 Months:",
-         choices = c("No", "Yes"))
-
+         choices = c("Volunteered", "Not Volunteered"))
+
+# Need to Fix
 selectInput("p1_volunteer_frequency",
          label = "Volunteer Frequency:",
-         choices = c("Haven't volunteered in past 12 months",
-                     "Rarely",
-                     "More than once a month, less than once a year",
-                     "At least once a month"))
-
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years'))
+
+# Need to Fix
 selectInput("p1_personal_activism",
          label = "Personal Activism:",
-         choices = c('Not involved',
-                     'Involved'))
-
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+# Need to Fix
 selectInput("p1_family_activism",
          label = "Family Activism:",
-         choices = c('Not involved',
-                     'Involved'))
-
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+# Need to Fix
 selectInput("p1_religious_member",
          label = "Church Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p1_sport_member",
          label = "Sport or Recreational Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p1_art_member",
          label = "Art, Music, or Educational Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p1_labor_member",
          label = "Labor Union Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p1_political_member",
          label = "Political Party Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p1_environmental_member",
          label = "Enviornmental Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p1_professional_member",
          label = "Professional Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p1_humanitarian_member",
          label = "Humanitarian Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p1_consumer_member",
          label = "Consumer Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p1_other_member",
          label = "Other Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
 
@@
          choices = c("Less than high school",
-                     "High school graduate",
+                     "High school",
                      "Some college",
@@
                      "4 year degree",
-                     "Graduate or professional degree",
+                     "Graduate degree",
                      "Doctorate"))
-
+# Need to Fix
 selectInput("p1_income",
          label = "Income:",
-         choices = c('Less than median of $61,372',
-                     'More than median of $61,372'))
+         choices = c('Less than $10,000',
+                     '$10,000 to $19,999',
+                     '$20,000 to $29,999',
+                     '$30,000 to $39,999',
+                     '$40,000 to $49,999',
+                     '$50,000 to $59,999',
+                     '$60,000 to $69,999',
+                     '$70,000 to $79,999',
+                     '$80,000 to $89,999',
+                     '$90,000 to $99,999',
+                     '$100,000 to $149,999',
+                     '$150,000 to $199,999',
+                     '$200,000 to $299,999',
+                     '$300,000 or more'))
 
@@
 
+# Need to Fix
 selectInput("p1_age",
          label = "Age:",
-         choices = c('Less than median age of 36',
-                     "More than median age of 36"))
+         choices = c('Under 18',
+                     '18 - 24',
+                     '25 - 34',
+                     '35 - 44',
+                     '45 - 54',
+                     '55 - 64',
+                     '65 - 74',
+                     '75 - 84',
+                     '85 or older'))
 
@@
 
+# Need to Fix
 selectInput("p2_national_news",
          label = "Follow national news:",
-         choices = c("Rarely",
+         choices = c('Multiple times a day',
+                     'Every day',
                      "Once a week",
-                     "At least once a day"))
-
+                     "Hardly ever",
+                     "Never"))
+
+# Need to Fix
 selectInput("p2_international_news",
          label = "Follow international news:",
-         choices = c("Never",
+         choices = c('Always',
                      "Sometimes",
-                     'Always'))
+                     "Never"))
 
@@
          label = "Medium to follow news:",
-         choices = c('TV',
+         choices = c("",
+                     'TV',
                      'Print',
-                     "Online (not social media)",
-                     "Social media",
+                     "Online (excluding social media)",
+                     "Social Media",
                      "Radio",
-                     "Email newsletter",
+                     "Email",
                      "News app"),
@@
 
+# Need to Fix
 selectInput("p2_follow_gov",
          label = "Follow government & public affairs:",
-         choices = c("Not Often",
-                     "Often"))
+         choices = c('Most of the time',
+                     'Some of the time',
+                     "Only now and then",
+                     "Hardly at all"))
 
@@
          label = "Travel to developing country:",
-         choices = c('No', "Yes"))
-
+         choices = c('Does Travel', "Doesn't Travel"))
+
+# Need to Fix
 selectInput("p2_political_pref",
          label = "Political views from liberal to conservative:",
-         choices = c("Extremely liberal",
-                     "Somewhat liberal",
-                     "Slightly liberal",
-                     "Moderate",
-                     "Slightly conservative",
-                     "Somewhat conservative",
-                     "Extremely conservative"))
-
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+# Need to Fix
 selectInput("p2_institution_trust",
          label = "Political institution trust from none to complete:",
-         choices = c("No trust at all",
-                     "Very little trust",
-                     "Little trust",
-                     "Nuetral",
-                     "Some trust",
-                     "A lot of trust",
-                     "Complete trust"))
-
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+# Need to Fix
 selectInput("p2_others_charitable",
          label = "People should be more charitable:",
-         choices = c("Strongly Disagree",
-                     "Disagree",
-                     "Somewhat disagree",
-                     "Nuetral",
-                     "Somewhat agree",
-                     "Agree",
-                     "Strongly agree"))
-
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+# Need to Fix
 selectInput("p2_worship_attendance",
          label = "Worship service attendance:",
-         choices = c("Not sure",
-                     "Rarely",
-                     "At least once a month"))
-
+         choices = c('Multiple times a week',
+                     'Once a week',
+                     "Once a month",
+                     "Once a year",
+                     "Never"))
+
+# Need to Fix
 selectInput("p2_religion_importance",
          label = "Importance of religion:",
-         choices = c("Not important",
-                     "Important"))
+         choices = c('Extremely important',
+                     'Very important',
+                     'Moderately important',
+                     'Slightly important',
+                     'Not at all important'))
 
@@
 
+# Need to Fix
 selectInput("p2_charity_importance",
           label = "Charity Importance:",
-          choices = c("Not at all important",
-                      "Very unimportant",
-                      "Somewhat unimportant",
-                      "Nuetral",
-                      "Somewhat important",
-                      "Very important",
-                      "Essential"))
-
+          choices = c("0", '1', '2', '3','4','5','6','7'))
+
+# Need to Fix
 selectInput("p2_trust_in_charity",
             label = "Charity Trust:",
-            choices = c("No trust at all",
-                        "Very little trust",
-                        "Little trust",
-                        "Nuetral",
-                        "Some trust",
-                        "A lot of trust",
-                        "Complete trust"))
+            choices = c("0", '1', '2', '3','4','5','6','7'))
+
+# Need to Fix
 
@@
          label = "Donation Frequency:",
-         choices = c('More than once a month, less than once a year',
-                     'At least once a month'))
-
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+# Need to Fix
 selectInput("p2_donation_amount",
@@
          label = "Volunteered in last 12 Months:",
-         choices = c("No", "Yes"))
-
+         choices = c("Volunteered", "Not Volunteered"))
+
+# Need to Fix
 selectInput("p2_volunteer_frequency",
          label = "Volunteer Frequency:",
-         choices = c("Haven't volunteered in past 12 months",
-                     "Rarely",
-                     "More than once a month, less than once a year",
-                     "At least once a month"))
-
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+# Need to Fix
 selectInput("p2_personal_activism",
          label = "Personal Activism:",
-         choices = c('Not involved',
-                     'Involved'))
-
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+# Need to Fix
 selectInput("p2_family_activism",
          label = "Family Activism:",
-         choices = c('Not involved',
-                     'Involved'))
-
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+# Need to Fix
 selectInput("p2_religious_member",
          label = "Church Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p2_sport_member",
          label = "Sport or Recreational Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p2_art_member",
          label = "Art, Music, or Educational Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p2_labor_member",
          label = "Labor Union Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p2_political_member",
          label = "Political Party Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p2_environmental_member",
          label = "Enviornmental Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p2_professional_member",
          label = "Professional Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p2_humanitarian_member",
          label = "Humanitarian Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p2_consumer_member",
          label = "Consumer Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p2_other_member",
          label = "Other Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
 
@@
                      "4 year degree",
-                     "Graduate or professional degree",
+                     "Graduate degree",
                      "Doctorate"))
-
+# Need to Fix
 selectInput("p2_income",
          label = "Income:",
-         choices = c('Less than median of $61,372',
-                     'More than median of $61,372'))
+         choices = c('Less than $10,000',
+                     '$10,000 to $19,999',
+                     '$20,000 to $29,999',
+                     '$30,000 to $39,999',
+                     '$40,000 to $49,999',
+                     '$50,000 to $59,999',
+                     '$60,000 to $69,999',
+                     '$70,000 to $79,999',
+                     '$80,000 to $89,999',
+                     '$90,000 to $99,999',
+                     '$100,000 to $149,999',
+                     '$150,000 to $199,999',
+                     '$200,000 to $299,999',
+                     '$300,000 or more'))
 
@@
 
+# Need to Fix
 selectInput("p2_age",
          label = "Age:",
-         choices = c('Less than median age of 36',
-                     "More than median age of 36"))
+         choices = c('Under 18',
+                     '18 - 24',
+                     '25 - 34',
+                     '35 - 44',
+                     '45 - 54',
+                     '55 - 64',
+                     '65 - 74',
+                     '75 - 84',
+                     '85 or older'))
 
@@
 
+# Need to Fix
 selectInput("p3_national_news",
          label = "Follow national news:",
-         choices = c("Rarely",
+         choices = c('Multiple times a day',
+                     'Every day',
                      "Once a week",
-                     "At least once a day"))
-
+                     "Hardly ever",
+                     "Never"))
+
+# Need to Fix
 selectInput("p3_international_news",
          label = "Follow international news:",
-         choices = c("Never",
+         choices = c('Always',
                      "Sometimes",
-                     'Always'))
+                     "Never"))
 
@@
 
+# Need to Fix
 selectInput("p3_follow_gov",
          label = "Follow government & public affairs:",
-         choices = c("Not Often",
-                     "Often"))
+         choices = c('Most of the time',
+                     'Some of the time',
+                     "Only now and then",
+                     "Hardly at all"))
 
@@
          label = "Travel to developing country:",
-         choices = c('No', "Yes"))
-
+         choices = c('Does Travel', "Doesn't Travel"))
+
+# Need to Fix
 selectInput("p3_political_pref",
          label = "Political views from liberal to conservative:",
-         choices = c("Extremely liberal",
-                     "Somewhat liberal",
-                     "Slightly liberal",
-                     "Moderate",
-                     "Slightly conservative",
-                     "Somewhat conservative",
-                     "Extremely conservative"))
-
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+# Need to Fix
 selectInput("p3_institution_trust",
          label = "Political institution trust from none to complete:",
-         choices = c("No trust at all",
-                     "Very little trust",
-                     "Little trust",
-                     "Nuetral",
-                     "Some trust",
-                     "A lot of trust",
-                     "Complete trust"))
-
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+# Need to Fix
 selectInput("p3_others_charitable",
          label = "People should be more charitable:",
-         choices = c("Strongly Disagree",
-                     "Disagree",
-                     "Somewhat disagree",
-                     "Nuetral",
-                     "Somewhat agree",
-                     "Agree",
-                     "Strongly agree"))
-
+         choices = c("0", '1', '2', '3','4','5','6','7'))
+
+# Need to Fix
 selectInput("p3_worship_attendance",
          label = "Worship service attendance:",
-         choices = c("Not sure",
-                     "Rarely",
-                     "At least once a month"))
-
+         choices = c('Multiple times a week',
+                     'Once a week',
+                     "Once a month",
+                     "Once a year",
+                     "Never"))
+
+# Need to Fix
 selectInput("p3_religion_importance",
          label = "Importance of religion:",
-         choices = c("Not important",
-                     "Important"))
+         choices = c('Extremely important',
+                     'Very important',
+                     'Moderately important',
+                     'Slightly important',
+                     'Not at all important'))
 
@@
 
+# Need to Fix
 selectInput("p3_charity_importance",
           label = "Charity Importance:",
-          choices = c("Not at all important",
-                      "Very unimportant",
-                      "Somewhat unimportant",
-                      "Nuetral",
-                      "Somewhat important",
-                      "Very important",
-                      "Essential"))
-
+          choices = c("0", '1', '2', '3','4','5','6','7'))
+
+# Need to Fix
 selectInput("p3_trust_in_charity",
             label = "Charity Trust:",
-            choices = c("No trust at all",
-                        "Very little trust",
-                        "Little trust",
-                        "Nuetral",
-                        "Some trust",
-                        "A lot of trust",
-                        "Complete trust"))
+            choices = c("0", '1', '2', '3','4','5','6','7'))
+
+# Need to Fix
 
@@
          label = "Donation Frequency:",
-         choices = c('More than once a month, less than once a year',
-                     'At least once a month'))
-
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+# Need to Fix
 selectInput("p3_donation_amount",
@@
          label = "Volunteered in last 12 Months:",
-         choices = c("No", "Yes"))
-
+         choices = c("Volunteered", "Not Volunteered"))
+
+# Need to Fix
 selectInput("p3_volunteer_frequency",
          label = "Volunteer Frequency:",
-         choices = c("Haven't volunteered in past 12 months",
-                     "Rarely",
-                     "More than once a month, less than once a year",
-                     "At least once a month"))
-
+         choices = c('Once a week',
+                     'Once a Month',
+                     'Once every three months',
+                     'Once every six months',
+                     'Once a year',
+                     'Once every few years',
+                     'Never'))
+
+# Need to Fix
 selectInput("p3_personal_activism",
          label = "Personal Activism:",
-         choices = c('Not involved',
-                     'Involved'))
-
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+# Need to Fix
 selectInput("p3_family_activism",
          label = "Family Activism:",
-         choices = c('Not involved',
-                     'Involved'))
-
+         choices = c('Extremely involved',
+                     'Very involved',
+                     'Moderately involved',
+                     'Slightly involved',
+                     'Never involved'))
+
+# Need to Fix
 selectInput("p3_religious_member",
          label = "Church Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p3_sport_member",
          label = "Sport or Recreational Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p3_art_member",
          label = "Art, Music, or Educational Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p3_labor_member",
          label = "Labor Union Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p3_political_member",
          label = "Political Party Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p3_environmental_member",
          label = "Enviornmental Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p3_professional_member",
          label = "Professional Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p3_humanitarian_member",
          label = "Humanitarian Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p3_consumer_member",
          label = "Consumer Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
+
+# Need to Fix
 selectInput("p3_other_member",
          label = "Other Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
+         choices = c('Active Member',
+                     'Inactive Member',
+                     "Don't belong"))
 
@@
                      "4 year degree",
-                     "Graduate or professional degree",
+                     "Graduate degree",
                      "Doctorate"))
-
+# Need to Fix
 selectInput("p3_income",
          label = "Income:",
-         choices = c('Less than median of $61,372',
-                     'More than median of $61,372'))
+         choices = c('Less than $10,000',
+                     '$10,000 to $19,999',
+                     '$20,000 to $29,999',
+                     '$30,000 to $39,999',
+                     '$40,000 to $49,999',
+                     '$50,000 to $59,999',
+                     '$60,000 to $69,999',
+                     '$70,000 to $79,999',
+                     '$80,000 to $89,999',
+                     '$90,000 to $99,999',
+                     '$100,000 to $149,999',
+                     '$150,000 to $199,999',
+                     '$200,000 to $299,999',
+                     '$300,000 or more'))
 
@@
 
+# Need to Fix
 selectInput("p3_age",
          label = "Age:",
-         choices = c('Less than median age of 36',
-                     "More than median age of 36"))
+         choices = c('Under 18',
+                     '18 - 24',
+                     '25 - 34',
+                     '35 - 44',
+                     '45 - 54',
+                     '55 - 64',
+                     '65 - 74',
+                     '75 - 84',
+                     '85 or older'))
 
@@
 ```{r ai org inputs}
+
+# Some kind of Org Id that could select the organization you are looking at? Not sure how to make it change the label in the graph
 
@@
 selectInput("ai_fin_trans",
-            label = "Select Financial Transparency:",
+            label = "Select Financial transparency:",
             choices = c("Doesn’t engage in transparency",
@@
 selectInput("ai_funding",
-            label = "Select Funding Source:",
+            label = "Select Funding source:",
             choices = c("Many small private donations",
                         "Handful of wealthy private donors",
-                        "Government grants"))
+                        "Government Grants"))
 
 selectInput("ai_gov_relat",
-            label = "Select Relationship With Host Government",
+            label = "Select Relationship with host government",
             choices = c("Friendly relationship with government",
@@
           value = "Organization 2",
-          placeholder = "Enter Organiation Name")
+          placeholder = "Enter Organiation Name"
+)
 
@@
 selectInput("gp_fin_trans",
-            label = "Select Financial Transparency:",
+            label = "Select Financial transparency:",
             choices = c("Doesn’t engage in transparency",
@@
             label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in financial accountability",
+            choices = c("Doesn’t engage in accountability",
                         "Engages in financial accountability"))
@@
 selectInput("gp_funding",
-            label = "Select Funding Source:",
+            label = "Select Funding source:",
             choices = c("Many small private donations",
                         "Handful of wealthy private donors",
-                        "Government grants"))
+                        "Government Grants"))
 
 selectInput("gp_gov_relat",
-            label = "Select Relationship With Host Government",
+            label = "Select Relationship with host government",
             choices = c("Friendly relationship with government",
@@
           value = "Organization 3",
-          placeholder = "Enter Organiation Name")
+          placeholder = "Enter Organiation Name"
+)
 
@@
 selectInput("ox_fin_trans",
-            label = "Select Financial Transparency:",
+            label = "Select Financial transparency:",
             choices = c("Doesn’t engage in transparency",
@@
 selectInput("ox_funding",
-            label = "Select Funding Source:",
+            label = "Select Funding source:",
             choices = c("Many small private donations",
                         "Handful of wealthy private donors",
-                        "Government grants"))
+                        "Government Grants"))
 
 selectInput("ox_gov_relat",
-            label = "Select Relationship With Host Government",
+            label = "Select Relationship with host government",
             choices = c("Friendly relationship with government",
@@
           value = "Organization 4",
-          placeholder = "Enter Organiation Name")
+          placeholder = "Enter Organiation Name"
+)
 
@@
 selectInput("rc_fin_trans",
-            label = "Select Financial Transparency:",
+            label = "Select Financial transparency:",
             choices = c("Doesn’t engage in transparency",
@@
 selectInput("rc_funding",
-            label = "Select Funding Source:",
+            label = "Select Funding source:",
             choices = c("Many small private donations",
                         "Handful of wealthy private donors",
-                        "Government grants"))
+                        "Government Grants"))
 
 selectInput("rc_gov_relat",
-            label = "Select Relationship With Host Government",
+            label = "Select Relationship with host government",
             choices = c("Friendly relationship with government",
@@
 ```
+
+<!-- There is an issue of not being able to see the last selectInput options when drop down box appears -->
+
+<!-- This is for commented out code -->
+
+```{r persona 1 gauge commented}
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#     
+#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+# 
+#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ai_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#FFC30B"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+# 
+#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(gp_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#3fad48"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ox_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#006633"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(rc_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#660000"),
+#         symbol = "%")
+# })
+```
+
+```{r persona 2 gauge commented}
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#     
+#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+# 
+#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ai_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#FFC30B"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+# 
+#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(gp_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#3fad48"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ox_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#006633"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(rc_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#660000"),
+#         symbol = "%")
+# })
+```
+
+```{r persona 3 gauge commented}
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#     
+#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+# 
+#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ai_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#FFC30B"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+# 
+#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(gp_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#3fad48"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ox_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#006633"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(rc_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#660000"),
+#         symbol = "%")
+# })
+```
+
+```{r ai gauge commented}
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#     
+#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+# 
+#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ai_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#FFC30B"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+# 
+#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ai_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#006633"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ai_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#b50909"),
+#         symbol = "%")
+# })
+```
+
+```{r plot ai plot commented}
+# renderPlotly({
+#   choice = df()
+#   
+#     persona1 = p_beta1 # Choose the persona
+#   
+#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
+#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
+#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
+#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+#   
+#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   
+#     persona2 = p_beta2 # Choose the persona
+#   
+#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
+#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
+#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
+#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+#   
+#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   
+#       persona3 = p_beta3 # Choose the persona
+#   
+#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
+#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
+#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
+#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+#   
+#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   
+#   data <- c(ai_exp_util1, ai_rate1, 
+#             ai_exp_util2, ai_rate2,
+#             ai_exp_util3, ai_rate3)
+#   
+#   
+#   df <- as.data.frame(matrix(data, 6, 1))
+#   
+#   df[,2] <- c("Amnesty International")
+#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
+#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
+#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+#   
+#   ggplotly(df %>% filter(Type == "Market Share") %>% 
+#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+#              geom_bar(position = "dodge", stat = "identity") +
+#              labs(x="") + 
+#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+#              theme(legend.position = "none")
+#     )
+# })
+```
+
+```{r valuebox ai commented}
+# renderValueBox({
+#   choice = df()
+#   
+#   persona = p_beta1 # Choose the persona
+#   
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+#   
+#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   valueBox(ai_rate,
+#            color = "#FFC30B",
+#            icon = "fa-percent")
+# })
+```
+
+```{r gp gauge commented}
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#     
+#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+# 
+#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(gp_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#FFC30B"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+# 
+#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(gp_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#3fad48"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(gp_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#006633"),
+#         symbol = "%")
+# })
+```
+
+```{r plot gp plot commented}
+# renderPlotly({
+#   choice = df()
+#   
+#     persona1 = p_beta1 # Choose the persona
+#   
+#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
+#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
+#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
+#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+#   
+#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   
+#     persona2 = p_beta2 # Choose the persona
+#   
+#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
+#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
+#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
+#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+#   
+#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   
+#       persona3 = p_beta3 # Choose the persona
+#   
+#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
+#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
+#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
+#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+#   
+#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   
+#   data <- c(gp_exp_util1, gp_rate1, 
+#             gp_exp_util2, gp_rate2,
+#             gp_exp_util3, gp_rate3)
+#   
+#   
+#   df <- as.data.frame(matrix(data, 6, 1))
+#   
+#   df[,2] <- c("Greenpeace")
+#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
+#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
+#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+#   
+#   ggplotly(df %>% filter(Type == "Market Share") %>% 
+#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+#              geom_bar(position = "dodge", stat = "identity") +
+#              labs(x="") + 
+#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+#              theme(legend.position = "none")
+#     )
+# })
+```
+
+```{r valuebox gp commented}
+# renderValueBox({
+#   choice = df()
+#   persona = p_beta1 # Choose the persona
+#   
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+#   
+#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   valueBox(gp_rate,
+#            color = "#3fad48",
+#            icon = "fa-percent")
+# })
+```
+
+```{r ox gauge commented}
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#     
+#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+# 
+#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ox_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#FFC30B"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+# 
+#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ox_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#3fad48"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(ox_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#006633"),
+#         symbol = "%")
+# })
+```
+
+```{r plot ox plot commented}
+# renderPlotly({
+#   choice = df()
+#   
+#     persona1 = p_beta1 # Choose the persona
+#   
+#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
+#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
+#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
+#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+#   
+#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   
+#     persona2 = p_beta2 # Choose the persona
+#   
+#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
+#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
+#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
+#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+#   
+#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   
+#       persona3 = p_beta3 # Choose the persona
+#   
+#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
+#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
+#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
+#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+#   
+#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   
+#   data <- c(ox_exp_util1, ox_rate1, 
+#             ox_exp_util2, ox_rate2,
+#             ox_exp_util3, ox_rate3)
+#   
+#   
+#   df <- as.data.frame(matrix(data, 6, 1))
+#   
+#   df[,2] <- c("Oxfam")
+#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
+#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
+#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+#   
+#   ggplotly(df %>% filter(Type == "Market Share") %>% 
+#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+#              geom_bar(position = "dodge", stat = "identity") +
+#              labs(x="") + 
+#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+#              theme(legend.position = "none")
+#     )
+# })
+```
+
+```{r valuebox ox commented}
+# renderValueBox({
+#   choice = df()
+#   
+#   persona = p_beta1 # Choose the persona
+#   
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+#   
+#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   valueBox(ox_rate,
+#            color = "#006633",
+#            icon = "fa-percent")
+# })
+```
+
+```{r rc gauge commented}
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#     
+#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
+# 
+#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(rc_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#FFC30B"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
+# 
+#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(rc_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#3fad48"),
+#         symbol = "%")
+# })
+# 
+# renderGauge({
+#   choice = df()
+#   per_choice = p()
+#   
+#     p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
+# 
+#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   gauge(rc_rate,
+#         min = 0,
+#         max = 100,
+#         gaugeSectors(colors = "#006633"),
+#         symbol = "%")
+# })
+```
+
+```{r plot rc plot commented}
+# renderPlotly({
+#   choice = df()
+#   
+#     persona1 = p_beta1 # Choose the persona
+#   
+#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
+#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
+#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
+#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
+#   
+#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
+#   
+#     persona2 = p_beta2 # Choose the persona
+#   
+#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
+#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
+#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
+#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
+#   
+#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
+#   
+#       persona3 = p_beta3 # Choose the persona
+#   
+#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
+#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
+#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
+#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
+#   
+#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
+#   
+#   data <- c(rc_exp_util1, rc_rate1, 
+#             rc_exp_util2, rc_rate2,
+#             rc_exp_util3, rc_rate3)
+#   
+#   
+#   df <- as.data.frame(matrix(data, 6, 1))
+#   
+#   df[,2] <- c("Red Cross")
+#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
+#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
+#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
+#   
+#   ggplotly(df %>% filter(Type == "Market Share") %>% 
+#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+#              geom_bar(position = "dodge", stat = "identity") +
+#              labs(x="") + 
+#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
+#              theme(legend.position = "none")
+#     )
+# })
+```
+
+```{r valuebox rc commented}
+# renderValueBox({
+#   choice = df()
+#   
+#   persona = p_beta1 # Choose the persona
+#    
+#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
+#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
+#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
+#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
+#   
+#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
+#   
+#   valueBox(rc_rate,
+#            color = "#660000",
+#            icon = "fa-percent")
+# })
+```

### 2020-09-12 analysis/03_analysis.Rmd
I and J index switched in model output (i.e., that's what I get for transposing) but corrected for new posterior draws; removed old figures; plotted new posterior draws

@@
 ```{r extract-draws, eval=FALSE}
-intercept <- 0                            # Intercept-only
+intercept <- 1                            # Intercept-only
 public_affairs <- 0                       # Public affairs
@@
   ungroup() %>% 
-  filter(.iteration > 500)
+  filter(.iteration > 500) %>% 
+  rename(
+    i = j,
+    j = i
+  )
 
@@
 ```{r load-draws}
-intercept <- 1                            # Intercept-only
+intercept <- 0                            # Intercept-only
 public_affairs <- 0                       # Public affairs
@@
 public_political_social <- 0              # + Social views
-public_political_social_charity <- 0      # + Charity and voluntarism
+public_political_social_charity <- 1      # + Charity and voluntarism
 public_political_social_charity_demo <- 0 # + Demographics
@@
     c("Once a week", "At least once a day")
+  ),
+  # *Q2.2*: How often do you follow international news? 
+  str_c(
+    "Follow international news: ", 
+    c("Sometimes", "Always")
   ),
@@
     mutate(
-      levels = factor(j, labels = level_labels)
+      levels = factor(i, labels = level_labels)
     ) %>%
     ggplot(aes(x = Gamma, y = levels)) +
-    geom_halfeye(.width = .95) +
+    stat_halfeye(.width = .95) +
     geom_vline(xintercept = 0, color = "grey") +
@@
     ggplot(aes(x = Gamma, y = covariates)) +
-       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
-       # geom_halfeyeh(.width = .95) +
+      stat_halfeye(.width = .95) +
       geom_vline(xintercept = 0, color = "white") +
@@
 # Save plot
-if (intercept == 1) file_name <- paste("intercept_marginal-posteriors.png")
-if (public_affairs == 1) file_name <- paste("public-affairs_marginal-posteriors.png")
-if (political_ideology == 1) file_name <- paste("political-ideology_marginal-posteriors.png")
-if (social_views == 1) file_name <- paste("social-views_marginal-posteriors.png")
-if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_marginal-posteriors.png")
-if (demographics == 1) file_name <- paste("demographics_marginal-posteriors.png")
-if (public_political == 1) file_name <- paste("public-political_marginal-posteriors.png")
-if (public_political_social == 1) file_name <- paste("public-political-social_marginal-posteriors.png")
-if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_marginal-posteriors.png")
-if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_marginal-posteriors.png")
+if (intercept == 1) file_name <- paste("marginal-posteriors_intercept.png")
+if (public_affairs == 1) file_name <- paste("marginal-posteriors_public-affairs.png")
+if (political_ideology == 1) file_name <- paste("marginal-posteriors_political-ideology.png")
+if (social_views == 1) file_name <- paste("marginal-posteriors_social-views.png")
+if (charity_voluntarism == 1) file_name <- paste("marginal-posteriors_charity-voluntarism.png")
+if (demographics == 1) file_name <- paste("marginal-posteriors_demographics.png")
+if (public_political == 1) file_name <- paste("marginal-posteriors_public-political.png")
+if (public_political_social == 1) file_name <- paste("marginal-posteriors_public-political-social.png")
+if (public_political_social_charity == 1) file_name <- paste("marginal-posteriors_public-political-social-charity.png")
+if (public_political_social_charity_demo == 1) file_name <- paste("marginal-posteriors_public-political-social-charity-demos.png")
+if (intercept == 1) width_length <- c(10, 10)
+if (intercept != 1) width_length <- c(20, 20)
+if (public_political_social_charity == 1) width_length <- c(20, 30)
+if (public_political_social_charity_demo == 1) width_length <- c(20, 30)
 ggsave(
@@
   path = here::here("analysis", "output", "figures"),
-  width = ifelse(intercept == 1, 12, 20),
-  height = ifelse(sum(intercept, public_affairs, political_ideology, social_views, charity_voluntarism, demographics) == 1, 12, 20),
+  width = width_length[1],
+  height = width_length[2],
   units = "in"

### 2020-09-12 analysis/03_analysis.Rmd
Collapsing analysis R markdowns

@@
 
-## Plot contrasts
-
-```{r plot-contrasts}
-
-```
-
 ## Plot heatmaps
@@
 
+## Plot contrasts/hypotheses?
+
+A better approach to address the hypotheses (taken from the former 03b and 03c).
+
+- We theorize that structural characteristics like an NGO’s host-country political and legal environment can serve as heuristics and shortcuts for donors.
+- Donors who see that an NGO faces general legal trouble abroad will use that knowledge to decide whether or not to donate.
+- We also theorize that non-structural organizational characteristics like managerial practices, funding sources, and issue area also serve as heuristics and influence donation patterns.
+- In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics.
+We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we’re unsure of the direction of that effect.
+
+> In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics.
+We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we're unsure of the direction of that effect.
+
+### Combined Results
+
+```{r combined-results, echo = FALSE, warning = FALSE}
+if (intercept == 1) {
+  draws %>% 
+    mutate(
+      levels = factor(i, labels = level_labels)
+    ) %>%
+   # filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>%
+    ggplot(aes(x = Theta, y = levels)) + 
+    geom_halfeyeh(.width = .95) +
+    geom_vline(xintercept = 0, color = "white") +
+    labs(y = "Attribute Levels")
+}
+if (intercept != 1) {
+    draws %>% 
+    filter(j != 1) %>% 
+    mutate(
+      levels = factor(i, labels = level_labels), 
+      covariates = factor(j, labels = covariate_labels)  
+    ) %>%
+    filter(
+      # levels == str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
+      covariates == str_c("Gender: ", 
+      c("Female", "Transgender", "Prefer not to say", "Other")
+    ))  %>% 
+    ggplot(aes(x = Theta, y = covariates)) +
+       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+       geom_vline(xintercept = 0, color = "white") +
+       labs(y = "Covariates") +
+       facet_wrap(~ levels, ncol = 5)
+}
+```
+
+### Relationship With Host Government
+
+We theorize that structural characteristics like an NGO’s host-country political and legal environment can serve as heuristics and shortcuts for donors.
+Donors who see that an NGO faces general legal trouble abroad will use that knowledge to decide whether or not to donate.
+
+```{r relationship-with-gov, echo = FALSE}
+# Plot marginals
+if (intercept == 1) {
+  draws %>% 
+    mutate(
+      levels = factor(i, labels = level_labels)
+    ) %>%
+    filter(levels == str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))) %>% 
+    ggplot(aes(x = Theta, y = levels)) + 
+    geom_halfeyeh(.width = .95) +
+    geom_vline(xintercept = 0, color = "grey") +
+    labs(y = "Attribute Levels")
+}
+if (intercept != 1) {
+  draws %>% 
+    filter(j != 1) %>% 
+    mutate(
+      levels = factor(i, labels = level_labels), 
+      covariates = factor(j, labels = covariate_labels)  
+    ) %>%
+    filter(covariates == c("Follow national news: Multiple times a day to Never", "Follow international news: Always to Never")) %>% 
+    ggplot(aes(x = Theta, y = covariates)) +
+       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+       geom_vline(xintercept = 0, color = "white") +
+       labs(y = "Covariates") +
+       facet_wrap(~ levels, ncol = 5)
+}
+
+```
+
+### Organizational Characteristics
+
+We theorize that non-structural organizational characteristics like managerial practices, funding sources, and issue area also serve as heuristics and influence donation patterns.
+
+#### 1. Managerial Practices
+
+```{r managerial-practices, echo = FALSE}
+# Plot marginals
+if (intercept == 1) {
+  draws %>% 
+    mutate(
+      levels = factor(i, labels = level_labels)
+    ) %>%
+    filter(levels == c( "Financial transparency: Yes",
+  "Accountability: Yes")) %>% 
+    ggplot(aes(x = Theta, y = levels)) + 
+    geom_halfeyeh(.width = .95) +
+    geom_vline(xintercept = 0, color = "grey") +
+    labs(y = "Attribute Levels")
+}
+if (intercept != 1) {
+  draws %>% 
+    filter(j != 1) %>% 
+    mutate(
+      levels = factor(i, labels = level_labels), 
+      covariates = factor(j, labels = covariate_labels)  
+    ) %>%
+    ggplot(aes(x = Theta, y = covariates)) +
+       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+       geom_vline(xintercept = 0, color = "white") +
+       labs(y = "Covariates") +
+       facet_wrap(~ levels, ncol = 5)
+}
+```
+
+#### 2. Funding Sources
+
+```{r funding_sources, echo = FALSE}
+# Plot marginals
+if (intercept == 1) {
+  draws %>% 
+    mutate(
+      levels = factor(i, labels = level_labels)
+    ) %>%
+    filter(levels ==  str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants"))) %>% 
+    ggplot(aes(x = Theta, y = levels)) + 
+    geom_halfeyeh(.width = .95) +
+    geom_vline(xintercept = 0, color = "grey") +
+    labs(y = "Attribute Levels")
+}
+if (intercept != 1) {
+  draws %>% 
+    filter(j != 1) %>% 
+    mutate(
+      levels = factor(i, labels = level_labels), 
+      covariates = factor(j, labels = covariate_labels)  
+    ) %>%
+    ggplot(aes(x = Theta, y = covariates)) +
+       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+       geom_vline(xintercept = 0, color = "white") +
+       labs(y = "Covariates") +
+       facet_wrap(~ levels, ncol = 5)
+}
+```
+
+#### 3. Issue Areas
+
+```{r issue-areas, echo = FALSE, warning = FALSE}
+# Plot marginals
+if (intercept == 1) {
+  draws %>% 
+    mutate(
+      levels = factor(i, labels = level_labels),
+      Theta_exp = exp(Theta)
+    ) %>%
+    filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>% 
+    ggplot(aes(x = Theta_exp, y = levels)) + 
+    geom_halfeyeh(.width = .95) +
+    geom_vline(xintercept = 1, color = "grey") +
+    labs(y = "Attribute Levels")
+}
+if (intercept != 1) {
+  draws %>% 
+    filter(j != 1) %>% 
+    mutate(
+      levels = factor(i, labels = level_labels), 
+      covariates = factor(j, labels = covariate_labels)  
+    ) %>%
+    ggplot(aes(x = Theta, y = covariates)) +
+       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+       geom_vline(xintercept = 0, color = "white") +
+       labs(y = "Covariates") +
+       facet_wrap(~ levels, ncol = 5)
+}
+
+```
+
+### Organization
+
+```{r organization, echo = FALSE, warning = FALSE}
+# Plot marginals
+if (intercept == 1) {
+  draws %>% 
+    mutate(
+      levels = factor(i, labels = level_labels)
+    ) %>%
+    filter(levels == str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"))) %>% 
+    ggplot(aes(x = exp(Theta), y = levels)) +
+    geom_halfeyeh(.width = .95) +
+    geom_vline(xintercept = 1, color = "grey") +
+    labs(y = "Attribute Levels")
+}
+if (intercept != 1) {
+  draws %>% 
+    filter(j != 1) %>% 
+    mutate(
+      levels = factor(i, labels = level_labels), 
+      covariates = factor(j, labels = covariate_labels)  
+    ) %>%
+    ggplot(aes(x = Theta, y = covariates)) +
+       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+       geom_vline(xintercept = 0, color = "white") +
+       labs(y = "Covariates") +
+       facet_wrap(~ levels, ncol = 5)
+}
+
+```
+
+### Do donors care if nonprofits they care about are criticized by or kicked out of the countries they work in?
+
+```{r}
+# Plot marginals
+if (intercept == 1) {
+  draws %>% 
+    mutate(
+      levels = factor(i, labels = level_labels)
+    ) %>%
+    filter(levels == str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))) %>% 
+    ggplot(aes(x = Theta, y = levels)) + 
+    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+    geom_vline(xintercept = 0, color = "grey") +
+    labs(y = "Attribute Levels")
+}
+if (intercept != 1) {
+  draws %>% 
+    filter(j != 1) %>% 
+    mutate(
+      levels = factor(i, labels = level_labels), 
+      covariates = factor(j, labels = covariate_labels)  
+    ) %>%
+    ggplot(aes(x = Theta, y = covariates)) +
+       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
+       geom_vline(xintercept = 0, color = "white") +
+       labs(y = "Covariates") +
+       facet_wrap(~ levels, ncol = 5)
+}
+
+```
+
+### Do managerial practices (financial transparency and accountability systems), funding sources (private donations and government grants), and issue areas (emergency response, environmental issues, human rights, and refugee relief) also serve as heuristics that signal an organization’s deservingness to donors?
+
 # Original computing environment

### 2020-09-13 analysis/03_analysis.Rmd
Another pass at plotting 03_analysis.Rmd

@@
 public_political_social <- 0              # + Social views
-public_political_social_charity <- 1      # + Charity and voluntarism
-public_political_social_charity_demo <- 0 # + Demographics
+public_political_social_charity <- 0      # + Charity and voluntarism
+public_political_social_charity_demo <- 1 # + Demographics
 
@@
 
-Instead of plotting marginals or contrasts, we can use a heatmap to identify where there are significant differences in the non-intercept models, which can then be narrowed down using the marginal plots.
+Instead of plotting marginals, we can use a heatmap to identify where there are significant differences in the non-intercept models, which can then be narrowed down using the marginal plots.
 
@@
       levels = factor(i, labels = level_labels), 
-      # covariates = factor(j, labels = covariate_labels)
       covariates = factor(j, labels = 1:length(covariate_labels))
@@
 
-## Plot contrasts/hypotheses?
+## Plot contrasts
 
@@
 
-### Do donors care if nonprofits they care about are criticized by or kicked out of the countries they work in?
+Do donors care if nonprofits they care about are criticized by or kicked out of the countries they work in?
 
@@
 
-### Do managerial practices (financial transparency and accountability systems), funding sources (private donations and government grants), and issue areas (emergency response, environmental issues, human rights, and refugee relief) also serve as heuristics that signal an organization’s deservingness to donors?
+Do managerial practices (financial transparency and accountability systems), funding sources (private donations and government grants), and issue areas (emergency response, environmental issues, human rights, and refugee relief) also serve as heuristics that signal an organization’s deservingness to donors?
 

### 2020-09-13 analysis/05_market_simulator.Rmd
Testing Simulator with Excel Results. Something might be wrong with how Org 1 is computed.

--- 2020-09-11 analysis/05_market_simulator.Rmd
@@
 # Persona Data from Market Simulator Workbook
-persona_data <- readxl::read_xlsx(here('analysis', 'output', "persona_configV06.xlsx"))
+persona_data <- readxl::read_xlsx(here('analysis', 'output', "persona_configV07.xlsx"))
+
+# Org Data from Market Simulator Workbook
+org_data <- readxl::read_xlsx(here('analysis', 'output', "org_config.xlsx"))
 
@@
     beta$ai_value <- 0
-    beta$ai_value[beta$levels == 'Amnesty International'] <- 1
+    # beta$ai_value[beta$levels == 'Amnesty International'] <- 1
+    beta$ai_value[beta$levels %in% input$org1_id] <- 1
     beta$ai_value[beta$levels %in% input$ai_issue] <- 1
@@
     beta$gp_value <- 0
-    beta$gp_value[beta$levels == 'Greenpeace'] <- 1
+    # beta$gp_value[beta$levels == 'Greenpeace'] <- 1
+    beta$ai_value[beta$levels %in% input$org2_id] <- 1
     beta$gp_value[beta$levels %in% input$gp_issue] <- 1
@@
     beta$ox_value <- 0
-    beta$ox_value[beta$levels == 'Oxfam'] <- 1
+    # beta$ox_value[beta$levels == 'Oxfam'] <- 1
+    beta$ai_value[beta$levels %in% input$org3_id] <- 1
     beta$ox_value[beta$levels %in% input$ox_issue] <- 1
@@
     beta$rc_value <- 0
-    beta$rc_value[beta$levels == 'Red Cross'] <- 1
+    # beta$rc_value[beta$levels == 'Red Cross'] <- 1
+    beta$ai_value[beta$levels %in% input$org4_id] <- 1
     beta$rc_value[beta$levels %in% input$rc_issue] <- 1
@@
 
-    beta_persona$p1_value[beta_persona$levels == 'Persona 1'] <- 1
+    beta_persona$p1_value[beta_persona$levels == 'Intercept'] <- 1
 
@@
 
-    beta_persona$p2_value[beta_persona$levels == 'Persona 2'] <- 1
+    beta_persona$p2_value[beta_persona$levels == 'Intercept'] <- 1
 
@@
 
-    beta_persona$p3_value[beta_persona$levels == 'Persona 3'] <- 1
+    beta_persona$p3_value[beta_persona$levels == 'Intercept'] <- 1
 
@@
 <!-- Persona Inputs -->
-```{r persona betas}
+```{r Manual Testing Matrix Multiplication}
 
@@
 
-p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona1)
+# matrix multiplication between persona data and betas
+beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona1)
 
@@
 
-p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona2)
-
-# 
-# exp_util2 <- round(exp(t(beta_test[, 4]) %*% as.matrix(p_beta2)),2)
+# matrix multiplication between persona data and betas
+beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona2)
 
@@
 
-p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona3)
-
-# 
-# exp_util3 <- round(exp(t(beta_test[, 5]) %*% as.matrix(p_beta3)),2)
+# matrix multiplication between persona data and betas
+beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona3)
+
+# Orgnization
+org1 <- org_data[,2]
+
+org2 <- org_data[,3]
+
+org3 <- org_data[,4]
+
+org4 <- org_data[,5]
+
+# Expected utility matrix multiplication between computed persona betas and org data for persona 1
+org1_exp_util1 <- exp(t(org1) %*% as.matrix(beta1))
+org2_exp_util1 <- exp(t(org2) %*% as.matrix(beta1))
+org3_exp_util1 <- exp(t(org3) %*% as.matrix(beta1))
+org4_exp_util1 <- exp(t(org4) %*% as.matrix(beta1))
+
+# Market Share computation from expected utilities between organization
+org1_rate1 <- 100 * org1_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
+org2_rate1 <- 100 * org2_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
+org3_rate1 <- 100 * org3_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
+org4_rate1 <- 100 * org4_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
+
+# org1_exp_util2 <- exp(t(org1) %*% as.matrix(p_beta2))
+# org2_exp_util2 <- exp(t(org2) %*% as.matrix(p_beta2))
+# org3_exp_util2 <- exp(t(org3) %*% as.matrix(p_beta2))
+# org4_exp_util2 <- exp(t(org4) %*% as.matrix(p_beta2))
+# 
+# 
+# org1_exp_util3 <- exp(t(org1) %*% as.matrix(p_beta3))
+# org2_exp_util3 <- exp(t(org2) %*% as.matrix(p_beta3))
+# org3_exp_util3 <- exp(t(org3) %*% as.matrix(p_beta3))
+# org4_exp_util3 <- exp(t(org4) %*% as.matrix(p_beta3))
 
@@
 
+selectInput("org1_id",
+            label = "Select Organization:",
+            choice = c("Amnesty International",
+                       "Green Peace",
+                       "Oxfam",
+                       "Red Cross"))
+
 selectInput("ai_issue", 
@@
 
+selectInput("org2_id",
+            label = "Select Organization:",
+            choice = c("Amnesty International",
+                       "Green Peace",
+                       "Oxfam",
+                       "Red Cross"))
+
 selectInput("gp_issue", 
@@
 
+selectInput("org3_id",
+            label = "Select Organization:",
+            choice = c("Amnesty International",
+                       "Green Peace",
+                       "Oxfam",
+                       "Red Cross"))
+
 selectInput("ox_issue", 
@@
 
+selectInput("org4_id",
+            label = "Select Organization:",
+            choice = c("Amnesty International",
+                       "Green Peace",
+                       "Oxfam",
+                       "Red Cross"))
+
 selectInput("rc_issue", 

### 2020-09-14 analysis/05_market_simulator.Rmd
Fixed issue with Org 1 and duplicate selectInput for Persona 1. Market Share values still not exactly matching with excel version.

@@
                 "Refugee relief",
-                # Transparency
+                # Financial Transparency
                 "Engages in transparency",
                 # Financial Accountability
-                "Engages in financial accountability",
+                "Engages in accountability",
                 # Funding
@@
 df <- reactive({
+
   #Amnesty International
@@
     beta$ai_value[beta$levels %in% input$ai_gov_relat] <- 1
+
   #Greenpeace
@@
     # beta$gp_value[beta$levels == 'Greenpeace'] <- 1
-    beta$ai_value[beta$levels %in% input$org2_id] <- 1
+    beta$gp_value[beta$levels %in% input$org2_id] <- 1
     beta$gp_value[beta$levels %in% input$gp_issue] <- 1
@@
     beta$gp_value[beta$levels %in% input$gp_gov_relat] <- 1
+
   #Oxfam
@@
     # beta$ox_value[beta$levels == 'Oxfam'] <- 1
-    beta$ai_value[beta$levels %in% input$org3_id] <- 1
+    beta$ox_value[beta$levels %in% input$org3_id] <- 1
     beta$ox_value[beta$levels %in% input$ox_issue] <- 1
@@
     beta$ox_value[beta$levels %in% input$ox_gov_relat] <- 1
+
   #Redcross
@@
     # beta$rc_value[beta$levels == 'Red Cross'] <- 1
-    beta$ai_value[beta$levels %in% input$org4_id] <- 1
+    beta$rc_value[beta$levels %in% input$org4_id] <- 1
     beta$rc_value[beta$levels %in% input$rc_issue] <- 1
@@
                         # Travel to developing Countries
-                        "Yes", 
+                        "Yes (1)", 
                         # Political Preference
@@
                         "A lot of trust",
-                        "Complete trust",
+                        "Complete trust (1)",
                         # Should Others be Charitable
@@
                         "Rarely",
-                        "At least once a month",
+                        "At least once a month (1)",
                         # Religious Importance
@@
                         "A lot of trust",
-                        "Complete trust",
+                        "Complete trust (2)",
                         # Donation Frequency
-                        "At least once a month", 
+                        "At least once a month (2)", 
                         # Donation Amount
@@
                         # Volunteered last 12 months
-                        "Yes",
+                        "Yes (2)",
                         # Volunteer Frequency
@@
                         "More than once a month, less than once a year",
-                        "At least once a month",
+                        "At least once a month (3)",
                         # Personal Activism
-                        "Involved",
+                        "Involved (1)",
                         # Family Activism
-                        "Involved",
+                        "Involved (2)",
                         # Religious Membership
@@
                         "Inactive member",
-                        "Active member",
+                        "Active member (1)",
                         # Environmental Organization Membership
@@
                         "Inactive member",
-                        "Active member",
+                        "Active member (2)",
                         # Consumer Organization Membership
@@
     beta_persona$p1_value[beta_persona$levels %in% input$p1_travel_developing] <- 1
+
     beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
@@
     beta_persona$p1_value[beta_persona$levels %in% input$p1_religion_importance] <- 1
+
     beta_persona$p1_value[beta_persona$levels %in% input$p1_religion] <- 1
@@
     beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_amount] <- 1
+
     beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_12] <- 1
@@
     beta_persona$p1_value[beta_persona$levels %in% input$p1_religious_member] <- 1
+
     beta_persona$p1_value[beta_persona$levels %in% input$p1_sport_member] <- 1
@@
     beta_persona$p1_value[beta_persona$levels %in% input$p1_environmental_member] <- 1
+
     beta_persona$p1_value[beta_persona$levels %in% input$p1_professional_member] <- 1
@@
     beta_persona$p1_value[beta_persona$levels %in% input$p1_gender] <- 1
+
     beta_persona$p1_value[beta_persona$levels %in% input$p1_marital_status] <- 1
@@
     beta_persona$p2_value[beta_persona$levels %in% input$p2_travel_developing] <- 1
+
     beta_persona$p2_value[beta_persona$levels %in% input$p2_political_pref] <- 1
@@
     beta_persona$p2_value[beta_persona$levels %in% input$p2_religion_importance] <- 1
+
     beta_persona$p2_value[beta_persona$levels %in% input$p2_religion] <- 1
@@
     beta_persona$p2_value[beta_persona$levels %in% input$p2_donation_amount] <- 1
+
     beta_persona$p2_value[beta_persona$levels %in% input$p2_volunteer_12] <- 1
@@
     beta_persona$p2_value[beta_persona$levels %in% input$p2_religious_member] <- 1
+
     beta_persona$p2_value[beta_persona$levels %in% input$p2_sport_member] <- 1
@@
     beta_persona$p2_value[beta_persona$levels %in% input$p2_environmental_member] <- 1
+
     beta_persona$p2_value[beta_persona$levels %in% input$p2_professional_member] <- 1
@@
     beta_persona$p2_value[beta_persona$levels %in% input$p2_gender] <- 1
+
     beta_persona$p2_value[beta_persona$levels %in% input$p2_marital_status] <- 1
@@
     beta_persona$p3_value[beta_persona$levels %in% input$p3_travel_developing] <- 1
+
     beta_persona$p3_value[beta_persona$levels %in% input$p3_political_pref] <- 1
@@
     beta_persona$p3_value[beta_persona$levels %in% input$p3_religion_importance] <- 1
+
     beta_persona$p3_value[beta_persona$levels %in% input$p3_religion] <- 1
@@
     beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_amount] <- 1
+
     beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_12] <- 1
@@
     beta_persona$p3_value[beta_persona$levels %in% input$p3_religious_member] <- 1
+
     beta_persona$p3_value[beta_persona$levels %in% input$p3_sport_member] <- 1
@@
     beta_persona$p3_value[beta_persona$levels %in% input$p3_environmental_member] <- 1
+
     beta_persona$p3_value[beta_persona$levels %in% input$p3_professional_member] <- 1
@@
     beta_persona$p3_value[beta_persona$levels %in% input$p3_gender] <- 1
+
     beta_persona$p3_value[beta_persona$levels %in% input$p3_marital_status] <- 1
@@
 
-# Orgnization
+# Organization
 org1 <- org_data[,2]
@@
   # Organization name inputs
-  df[,2] <- c(input$ai_id, input$gp_id, input$ox_id, input$rc_id)
+  df[,2] <- rep(c(input$ai_id, input$gp_id, input$ox_id, input$rc_id),6)
   # Type of value
@@
              labs(x="", y = "Market Share") + 
-             scale_fill_manual(values = c( "#FFC30B", "#28a153", "#c23838")) +
+             scale_fill_manual(values = c("#FFC30B", "#28a153", "#c23838")) +
              theme(legend.position = "right",
@@
          label = "Travel to developing country:",
-         choices = c('No', "Yes"))
+         choices = c('No', "Yes (1)"))
 
@@
                      "A lot of trust",
-                     "Complete trust"))
+                     "Complete trust (1)"))
 
@@
                      "Rarely",
-                     "At least once a month"))
+                     "At least once a month (1)"))
 
@@
                         "A lot of trust",
-                        "Complete trust"))
+                        "Complete trust (2)"))
 
@@
          choices = c('More than once a month, less than once a year',
-                     'At least once a month'))
+                     'At least once a month (2)'))
 
@@
          label = "Volunteered in last 12 Months:",
-         choices = c("No", "Yes"))
+         choices = c("No", "Yes (2)"))
 
@@
                      "More than once a month, less than once a year",
-                     "At least once a month"))
+                     "At least once a month (3)"))
 
@@
          choices = c('Not involved',
-                     'Involved'))
+                     'Involved (1)'))
 
@@
          choices = c('Not involved',
-                     'Involved'))
+                     'Involved (2)'))
 
@@
                      'Inactive member',
-                     'Active member'))
+                     'Active member (1)'))
 
@@
                      'Inactive member',
-                     'Active member'))
+                     'Active member (2)'))
 
@@
           value = "Organization 1",
-          placeholder = "Enter Organiation Name")
+          placeholder = "Enter Organization Name")
 
@@
             choice = c("Amnesty International",
-                       "Green Peace",
+                       "Greenpeace",
                        "Oxfam",
@@
             label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in financial accountability",
-                        "Engages in financial accountability"))
+            choices = c("Doesn’t engage in accountability",
+                        "Engages in accountability"))
 

### 2020-09-14 analysis/05_market_simulator.Rmd
Added default choices for orgs to match excel simulator

@@
                      "Once a week",
-                     "At least once a day"))
+                     "At least once a day"),
+         selected = "At least once a day")
 
@@
                      "Sometimes",
-                     "Always"))
+                     "Always"),
+         selected = "Always")
 
@@
                      "News app"),
-         multiple = TRUE)
+         multiple = TRUE,
+         selected = c("TV", "Print", "Social media"))
 
@@
          choices = c("Not Often",
-                     "Often"))
-
+                     "Often"),
+         selected = "Often")
+
+#Fix
 selectInput("p1_travel_developing",
          label = "Travel to developing country:",
-         choices = c('No', "Yes (1)"))
+         choices = c("Doesn't travel", "Does travel"),
+         selected = "Does travel")
 
@@
                      "Somewhat conservative",
-                     "Extremely conservative"))
-
+                     "Extremely conservative"),
+         selected = "Somewhat liberal")
+
+#Fix
 selectInput("p1_institution_trust",
          label = "Political institution trust from none to complete:",
-         choices = c("No trust at all",
-                     "Very little trust",
-                     "Little trust",
-                     "Nuetral",
-                     "Some trust",
-                     "A lot of trust",
-                     "Complete trust (1)"))
+         choices = c("No trust at all in political institutions",
+                     "Very little trust in political institutions",
+                     "Little trust in political institutions",
+                     "Nuetral trust in political institutions",
+                     "Some trust in political institutions",
+                     "A lot of trust in political institutions",
+                     "Complete trust in political institutions"),
+         selected = "Complete trust in political institutions ")
 
@@
                      "Agree",
-                     "Strongly agree"))
-
+                     "Strongly agree",),
+         selected = "Strongly agree")
+
+# Fix
 selectInput("p1_worship_attendance",
@@
          choices = c("Not sure",
-                     "Rarely",
-                     "At least once a month (1)"))
+                     "Rarely attend services",
+                     "Attend at least once a month"),
+         selected = "Attend at least once a month")
 
@@
          choices = c("Not important",
-                     "Important"))
+                     "Important"),
+         selected = "Important")
 
@@
                      'Atheist',
-                     'Other (Religion)'))
+                     'Other (Religion)'),
+         selected = 'Protestant')
 
@@
                       "Very important",
-                      "Essential"))
-
+                      "Essential"),
+          selected = "Somewhat unimportant")
+
+#Fix
 selectInput("p1_trust_in_charity",
             label = "Charity Trust:",
-            choices = c("No trust at all",
-                        "Very little trust",
-                        "Little trust",
-                        "Nuetral",
-                        "Some trust",
-                        "A lot of trust",
-                        "Complete trust (2)"))
-
+            choices = c("No trust at all in charities",
+                        "Very little trust in charities",
+                        "Little trust in charities",
+                        "Nuetral trust in charities",
+                        "Some trust in charities",
+                        "A lot of trust in charities",
+                        "Complete trust in charities"),
+            selected = "Complete trust in charities")
+
+#Fix
 selectInput("p1_donation_frequency",
          label = "Donation Frequency:",
-         choices = c('More than once a month, less than once a year',
-                     'At least once a month (2)'))
+         choices = c('Donate more than once a month, less than once a year',
+                     'Donate at least once a month'),
+         selected = "Donate at least once a month")
 
@@
                      '$5,000-$9,999',
-                     '$10,000+'))
-
+                     '$10,000+'),
+         selected = "$100-$499")
+
+#Fix
 selectInput("p1_volunteer_12",
          label = "Volunteered in last 12 Months:",
-         choices = c("No", "Yes (2)"))
-
+         choices = c("Haven't volunteered", "Have volunteered"),
+         selected = "Have volunteered")
+
+#Fix
 selectInput("p1_volunteer_frequency",
@@
          choices = c("Haven't volunteered in past 12 months",
-                     "Rarely",
-                     "More than once a month, less than once a year",
-                     "At least once a month (3)"))
-
+                     "Rarely volunteer",
+                     "Volunteer more than once a month, less than once a year",
+                     "Volunteer at least once a month"),
+         selected = "Volunteer at least once a month")
+
+# fix
 selectInput("p1_personal_activism",
          label = "Personal Activism:",
-         choices = c('Not involved',
-                     'Involved (1)'))
-
+         choices = c('Not personally involved ',
+                     'Personally involved'),
+         selected = "Personally involved")
+
+#Fix
 selectInput("p1_family_activism",
          label = "Family Activism:",
-         choices = c('Not involved',
-                     'Involved (2)'))
-
+         choices = c('Family not involved',
+                     'Family involved'),
+         selected = "Family involved")
+
+#Fix
 selectInput("p1_religious_member",
          label = "Church Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to church membership",
+                     'Inactive church member',
+                     'Active church member'),
+         selected = "Don't belong to church membership")
+
+#Fix
 selectInput("p1_sport_member",
          label = "Sport or Recreational Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to sports membership",
+                     'Inactive sports member',
+                     'Active sports member'),
+         selected = "Don't belong to sports membership")
+#Fix
 selectInput("p1_art_member",
          label = "Art, Music, or Educational Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to educational membership",
+                     'Inactive educational member',
+                     'Active educational member'),
+         selected = "Don't belong to educational membership")
+#Fix
 selectInput("p1_labor_member",
          label = "Labor Union Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to union",
+                     'Inactive union member',
+                     'Active union member'),
+         selected = "Don't belong to union")
+
+#Fix
 selectInput("p1_political_member",
          label = "Political Party Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member (1)'))
-
+         choices = c("Don't belong to party",
+                     'Inactive party member',
+                     'Active party member'),
+         selected = "Active party member")
+# Fix
 selectInput("p1_environmental_member",
-         label = "Enviornmental Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         label = "Environmental Org. Membership:",
+         choices = c("Don't belong to environmental organization",
+                     'Inactive environmental member',
+                     'Active environmental member'),
+         selected = "Don't belong to environmental organization")
+# Fix
 selectInput("p1_professional_member",
          label = "Professional Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to professional membership",
+                     'Inactive professional member',
+                     'Active professional member'),
+         selected = "Don't belong to professional membership")
+# Fix
 selectInput("p1_humanitarian_member",
          label = "Humanitarian Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member (2)'))
-
+         choices = c("Don't belong to humanitarian organization",
+                     'Inactive humanitarian member',
+                     'Active humanitarian member'),
+         selected = "Active humanitarian member")
+
+# Fix
 selectInput("p1_consumer_member",
          label = "Consumer Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to consumer organization",
+                     'Inactive consumer member',
+                     'Active consumer member'),
+         selected = "Don't belong to consumer organization")
+# Fix
 selectInput("p1_other_member",
          label = "Other Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
+         choices = c("Don't belong to other organization",
+                     'Inactive other member',
+                     'Active other member'),
+         selected = "Don't belong to other organization")
 
@@
                      "Prefer not to say",
-                     "Other (Gender)"))
+                     "Other (Gender)"),
+         selected = "Male")
 
@@
                      "Separated",
-                     "Never married"))
+                     "Never married"),
+         selected = "Married")
 
@@
                      "Graduate or professional degree",
-                     "Doctorate"))
+                     "Doctorate"),
+         selected = "2 year degree")
 
@@
          choices = c('Less than median of $61,372',
-                     'More than median of $61,372'))
+                     'More than median of $61,372'),
+         selected = "More than median of $61,372")
 
@@
                      'Other (Race)'),
-         multiple = TRUE)
+         multiple = TRUE,
+         selected = "White")
 
@@
          choices = c('Less than median age of 36',
-                     "More than median age of 36"))
+                     "More than median age of 36"),
+         selected = "Less than median age of 36")
 
@@
                        "Oxfam",
-                       "Red Cross"))
+                       "Red Cross"),
+            selected = "Red Cross")
 
@@
                         "Human rights",
-                        "Refugee relief"))
+                        "Refugee relief"),
+            selected = "Emergency response")
 
@@
             choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"))
+                        "Engages in transparency"),
+            selected = "Engages in transparency")
 
@@
             choices = c("Doesn’t engage in accountability",
-                        "Engages in accountability"))
+                        "Engages in accountability"),
+            selected = "Engages in accountability")
 
@@
                         "Human rights",
-                        "Refugee relief"))
+                        "Refugee relief"),
+            selected = "Environment")
 
@@
                         "Human rights",
-                        "Refugee relief"))
+                        "Refugee relief"),
+            selected = "Human rights")
 
@@
                         "Human rights",
-                        "Refugee relief"))
+                        "Refugee relief"),
+            selected = "Refugee relief")
 

### 2020-09-14 analysis/05_market_simulator.Rmd
Persona defaults now matching excel workbook

@@
                      "Sometimes",
-                     'Always'))
+                     "Always"),
+         selected = "Always")
 
@@
          choices = c("Not Often",
-                     "Often"))
-
+                     "Often"),
+         selected = "Often")
+
+#Fix
 selectInput("p2_travel_developing",
          label = "Travel to developing country:",
-         choices = c('No', "Yes"))
+         choices = c("Doesn't travel", "Does travel"),
+         selected = "Does travel")
 
@@
                      "Somewhat conservative",
-                     "Extremely conservative"))
-
+                     "Extremely conservative"),
+         selected = "Somewhat liberal")
+
+#Fix
 selectInput("p2_institution_trust",
          label = "Political institution trust from none to complete:",
-         choices = c("No trust at all",
-                     "Very little trust",
-                     "Little trust",
-                     "Nuetral",
-                     "Some trust",
-                     "A lot of trust",
-                     "Complete trust"))
+         choices = c("No trust at all in political institutions",
+                     "Very little trust in political institutions",
+                     "Little trust in political institutions",
+                     "Nuetral trust in political institutions",
+                     "Some trust in political institutions",
+                     "A lot of trust in political institutions",
+                     "Complete trust in political institutions"),
+         selected = "Complete trust in political institutions ")
 
@@
                      "Agree",
-                     "Strongly agree"))
-
+                     "Strongly agree",),
+         selected = "Strongly agree")
+
+# Fix
 selectInput("p2_worship_attendance",
@@
          choices = c("Not sure",
-                     "Rarely",
-                     "At least once a month"))
+                     "Rarely attend services",
+                     "Attend at least once a month"),
+         selected = "Attend at least once a month")
 
@@
                       "Very important",
-                      "Essential"))
-
+                      "Essential"),
+          selected = "Somewhat unimportant")
+
+#Fix
 selectInput("p2_trust_in_charity",
             label = "Charity Trust:",
-            choices = c("No trust at all",
-                        "Very little trust",
-                        "Little trust",
-                        "Nuetral",
-                        "Some trust",
-                        "A lot of trust",
-                        "Complete trust"))
-
+            choices = c("No trust at all in charities",
+                        "Very little trust in charities",
+                        "Little trust in charities",
+                        "Nuetral trust in charities",
+                        "Some trust in charities",
+                        "A lot of trust in charities",
+                        "Complete trust in charities"),
+            selected = "Complete trust in charities")
+
+#Fix
 selectInput("p2_donation_frequency",
          label = "Donation Frequency:",
-         choices = c('More than once a month, less than once a year',
-                     'At least once a month'))
+         choices = c('Donate more than once a month, less than once a year',
+                     'Donate at least once a month'),
+         selected = "Donate at least once a month")
 
@@
                      '$5,000-$9,999',
-                     '$10,000+'))
-
+                     '$10,000+'),
+         selected = "$100-$499")
+
+#Fix
 selectInput("p2_volunteer_12",
          label = "Volunteered in last 12 Months:",
-         choices = c("No", "Yes"))
-
+         choices = c("Haven't volunteered", "Have volunteered"),
+         selected = "Have volunteered")
+
+#Fix
 selectInput("p2_volunteer_frequency",
@@
          choices = c("Haven't volunteered in past 12 months",
-                     "Rarely",
-                     "More than once a month, less than once a year",
-                     "At least once a month"))
-
+                     "Rarely volunteer",
+                     "Volunteer more than once a month, less than once a year",
+                     "Volunteer at least once a month"),
+         selected = "Volunteer at least once a month")
+
+# fix
 selectInput("p2_personal_activism",
          label = "Personal Activism:",
-         choices = c('Not involved',
-                     'Involved'))
-
+         choices = c('Not personally involved ',
+                     'Personally involved'),
+         selected = "Personally involved")
+
+#Fix
 selectInput("p2_family_activism",
          label = "Family Activism:",
-         choices = c('Not involved',
-                     'Involved'))
-
+         choices = c('Family not involved',
+                     'Family involved'),
+         selected = "Family involved")
+
+#Fix
 selectInput("p2_religious_member",
          label = "Church Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to church membership",
+                     'Inactive church member',
+                     'Active church member'),
+         selected = "Don't belong to church membership")
+
+#Fix
 selectInput("p2_sport_member",
          label = "Sport or Recreational Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to sports membership",
+                     'Inactive sports member',
+                     'Active sports member'),
+         selected = "Don't belong to sports membership")
+#Fix
 selectInput("p2_art_member",
          label = "Art, Music, or Educational Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to educational membership",
+                     'Inactive educational member',
+                     'Active educational member'),
+         selected = "Don't belong to educational membership")
+#Fix
 selectInput("p2_labor_member",
          label = "Labor Union Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to union",
+                     'Inactive union member',
+                     'Active union member'),
+         selected = "Don't belong to union")
+
+#Fix
 selectInput("p2_political_member",
          label = "Political Party Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to party",
+                     'Inactive party member',
+                     'Active party member'),
+         selected = "Active party member")
+# Fix
 selectInput("p2_environmental_member",
-         label = "Enviornmental Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         label = "Environmental Org. Membership:",
+         choices = c("Don't belong to environmental organization",
+                     'Inactive environmental member',
+                     'Active environmental member'),
+         selected = "Don't belong to environmental organization")
+# Fix
 selectInput("p2_professional_member",
          label = "Professional Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to professional membership",
+                     'Inactive professional member',
+                     'Active professional member'),
+         selected = "Don't belong to professional membership")
+# Fix
 selectInput("p2_humanitarian_member",
          label = "Humanitarian Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to humanitarian organization",
+                     'Inactive humanitarian member',
+                     'Active humanitarian member'),
+         selected = "Active humanitarian member")
+
+# Fix
 selectInput("p2_consumer_member",
          label = "Consumer Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to consumer organization",
+                     'Inactive consumer member',
+                     'Active consumer member'),
+         selected = "Don't belong to consumer organization")
+# Fix
 selectInput("p2_other_member",
          label = "Other Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
+         choices = c("Don't belong to other organization",
+                     'Inactive other member',
+                     'Active other member'),
+         selected = "Don't belong to other organization")
 
@@
                      "Graduate or professional degree",
-                     "Doctorate"))
+                     "Doctorate"),
+         selected = "Some college")
 
@@
                      'Other (Race)'),
-         multiple = TRUE)
+         multiple = TRUE,
+         selected = "American Indian or Alaska Native")
 
@@
           label = "Persona Name",
-          value = "Persona 3",
+          value = "Persona 1",
           placeholder = "Enter Persona Name")
@@
          choices = c("Not Often",
-                     "Often"))
-
+                     "Often"),
+         selected = "Often")
+
+#Fix
 selectInput("p3_travel_developing",
          label = "Travel to developing country:",
-         choices = c('No', "Yes"))
+         choices = c("Doesn't travel", "Does travel"),
+         selected = "Does travel")
 
@@
                      "Somewhat conservative",
-                     "Extremely conservative"))
-
+                     "Extremely conservative"),
+         selected = "Somewhat liberal")
+
+#Fix
 selectInput("p3_institution_trust",
          label = "Political institution trust from none to complete:",
-         choices = c("No trust at all",
-                     "Very little trust",
-                     "Little trust",
-                     "Nuetral",
-                     "Some trust",
-                     "A lot of trust",
-                     "Complete trust"))
+         choices = c("No trust at all in political institutions",
+                     "Very little trust in political institutions",
+                     "Little trust in political institutions",
+                     "Nuetral trust in political institutions",
+                     "Some trust in political institutions",
+                     "A lot of trust in political institutions",
+                     "Complete trust in political institutions"),
+         selected = "Complete trust in political institutions ")
 
@@
                      "Agree",
-                     "Strongly agree"))
-
+                     "Strongly agree",),
+         selected = "Strongly agree")
+
+# Fix
 selectInput("p3_worship_attendance",
@@
                       "Very important",
-                      "Essential"))
-
+                      "Essential"),
+          selected = "Somewhat unimportant")
+
+#Fix
 selectInput("p3_trust_in_charity",
             label = "Charity Trust:",
-            choices = c("No trust at all",
-                        "Very little trust",
-                        "Little trust",
-                        "Nuetral",
-                        "Some trust",
-                        "A lot of trust",
-                        "Complete trust"))
-
+            choices = c("No trust at all in charities",
+                        "Very little trust in charities",
+                        "Little trust in charities",
+                        "Nuetral trust in charities",
+                        "Some trust in charities",
+                        "A lot of trust in charities",
+                        "Complete trust in charities"),
+            selected = "Complete trust in charities")
+
+#Fix
 selectInput("p3_donation_frequency",
          label = "Donation Frequency:",
-         choices = c('More than once a month, less than once a year',
-                     'At least once a month'))
+         choices = c('Donate more than once a month, less than once a year',
+                     'Donate at least once a month'),
+         selected = "Donate at least once a month")
 
@@
                      '$5,000-$9,999',
-                     '$10,000+'))
-
+                     '$10,000+'),
+         selected = "$100-$499")
+
+#Fix
 selectInput("p3_volunteer_12",
          label = "Volunteered in last 12 Months:",
-         choices = c("No", "Yes"))
-
+         choices = c("Haven't volunteered", "Have volunteered"),
+         selected = "Have volunteered")
+
+#Fix
 selectInput("p3_volunteer_frequency",
@@
          choices = c("Haven't volunteered in past 12 months",
-                     "Rarely",
-                     "More than once a month, less than once a year",
-                     "At least once a month"))
-
+                     "Rarely volunteer",
+                     "Volunteer more than once a month, less than once a year",
+                     "Volunteer at least once a month"),
+         selected = "Volunteer at least once a month")
+
+# fix
 selectInput("p3_personal_activism",
          label = "Personal Activism:",
-         choices = c('Not involved',
-                     'Involved'))
-
+         choices = c('Not personally involved ',
+                     'Personally involved'),
+         selected = "Personally involved")
+
+#Fix
 selectInput("p3_family_activism",
          label = "Family Activism:",
-         choices = c('Not involved',
-                     'Involved'))
-
+         choices = c('Family not involved',
+                     'Family involved'),
+         selected = "Family involved")
+
+#Fix
 selectInput("p3_religious_member",
          label = "Church Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to church membership",
+                     'Inactive church member',
+                     'Active church member'),
+         selected = "Don't belong to church membership")
+
+#Fix
 selectInput("p3_sport_member",
          label = "Sport or Recreational Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to sports membership",
+                     'Inactive sports member',
+                     'Active sports member'),
+         selected = "Don't belong to sports membership")
+#Fix
 selectInput("p3_art_member",
          label = "Art, Music, or Educational Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to educational membership",
+                     'Inactive educational member',
+                     'Active educational member'),
+         selected = "Don't belong to educational membership")
+#Fix
 selectInput("p3_labor_member",
          label = "Labor Union Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to union",
+                     'Inactive union member',
+                     'Active union member'),
+         selected = "Don't belong to union")
+
+#Fix
 selectInput("p3_political_member",
          label = "Political Party Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to party",
+                     'Inactive party member',
+                     'Active party member'),
+         selected = "Active party member")
+# Fix
 selectInput("p3_environmental_member",
-         label = "Enviornmental Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         label = "Environmental Org. Membership:",
+         choices = c("Don't belong to environmental organization",
+                     'Inactive environmental member',
+                     'Active environmental member'),
+         selected = "Don't belong to environmental organization")
+# Fix
 selectInput("p3_professional_member",
          label = "Professional Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to professional membership",
+                     'Inactive professional member',
+                     'Active professional member'),
+         selected = "Don't belong to professional membership")
+# Fix
 selectInput("p3_humanitarian_member",
          label = "Humanitarian Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to humanitarian organization",
+                     'Inactive humanitarian member',
+                     'Active humanitarian member'),
+         selected = "Active humanitarian member")
+
+# Fix
 selectInput("p3_consumer_member",
          label = "Consumer Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to consumer organization",
+                     'Inactive consumer member',
+                     'Active consumer member'),
+         selected = "Don't belong to consumer organization")
+# Fix
 selectInput("p3_other_member",
          label = "Other Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
+         choices = c("Don't belong to other organization",
+                     'Inactive other member',
+                     'Active other member'),
+         selected = "Don't belong to other organization")
 
@@
                      "Prefer not to say",
-                     "Other (Gender)"))
+                     "Other (Gender)"),
+         selected = "Female")
 
@@
                      "Graduate or professional degree",
-                     "Doctorate"))
+                     "Doctorate"),
+         selected = "Graduate or professional degree")
 
@@
                      'Other (Race)'),
-         multiple = TRUE)
+         multiple = TRUE,
+         selected = c("Black or African American", "American Indian or Alaska Native"))
 

### 2020-09-14 analysis/05_market_simulator.Rmd
Fixed beta_persona

@@
                         # Travel to developing Countries
-                        "Yes (1)", 
+                        "Does travel", 
                         # Political Preference
@@
                         # Trust in Political Institute
-                        "Very little trust",
-                        "Little trust",
-                        "Nuetral",
-                        "Some trust",
-                        "A lot of trust",
-                        "Complete trust (1)",
+                        "Very little trust in polticial institutions",
+                        "Little trust in polticial institutions",
+                        "Nuetral trust in polticial institutions",
+                        "Some trust in polticial institutions",
+                        "A lot of trust in polticial institutions",
+                        "Complete trust in polticial institutions",
                         # Should Others be Charitable
@@
                         # Worship Service Attendance
-                        "Rarely",
-                        "At least once a month (1)",
+                        "Rarely attend services",
+                        "Attend at least once a month",
                         # Religious Importance
@@
                         # Trust in Charities
-                        "Very little trust",
-                        "Little trust",
-                        "Nuetral",
-                        "Some trust",
-                        "A lot of trust",
-                        "Complete trust (2)",
+                        "Very little trust in charities",
+                        "Little trust in charities",
+                        "Nuetral trust in charities",
+                        "Some trust in charities",
+                        "A lot of trust in charities",
+                        "Complete trust in charities",
                         # Donation Frequency
-                        "At least once a month (2)", 
+                        "Donate At least once a month", 
                         # Donation Amount
@@
                         # Volunteered last 12 months
-                        "Yes (2)",
+                        "Have volunteered",
                         # Volunteer Frequency
-                        "Rarely",
-                        "More than once a month, less than once a year",
-                        "At least once a month (3)",
+                        "Rarely volunteer",
+                        "Volunteer more than once a month, less than once a year",
+                        "Volunteer at least once a month",
                         # Personal Activism
-                        "Involved (1)",
+                        "Personally involved",
                         # Family Activism
-                        "Involved (2)",
+                        "Family involved",
                         # Religious Membership
-                        "Inactive member",
-                        "Active member",
+                        "Inactive church member",
+                        "Active church member",
                         # Sport or Recreational Membership
-                        "Inactive member",
-                        "Active member", 
+                        "Inactive sports member",
+                        "Active sports member", 
                         # Art, Music, or Educational Membership
-                        "Inactive member",
-                        "Active member",
+                        "Inactive educational member",
+                        "Active educational member",
                         # Labor Union Membership
-                        "Inactive member",
-                        "Active member",
+                        "Inactive union member",
+                        "Active union member",
                         # Political Party Membership
-                        "Inactive member",
-                        "Active member (1)",
+                        "Inactive party member",
+                        "Active party member",
                         # Environmental Organization Membership
-                        "Inactive member",
-                        "Active member",
+                        "Inactive environmental member",
+                        "Active environmental member",
                         # Professional Association
-                        "Inactive member",
-                        "Active member",
+                        "Inactive professional member",
+                        "Active professional member",
                         # Humanitarian or Charity Membership
-                        "Inactive member",
-                        "Active member (2)",
+                        "Inactive humanitarian member",
+                        "Active humanitarian member",
                         # Consumer Organization Membership
-                        "Inactive member",
-                        "Active member",
+                        "Inactive consumer member",
+                        "Active sonsumer member",
                         #Other Organization Membership
-                        "Inactive member",
-                        "Active member",
+                        "Inactive other member",
+                        "Active other member",
                         # Gender
@@
                      "Agree",
-                     "Strongly agree",),
+                     "Strongly agree"),
          selected = "Strongly agree")

### 2020-09-16 analysis/05_market_simulator.Rmd
Cleaning up labels, configurations now an output folder

--- 2020-09-14 analysis/05_market_simulator.Rmd
@@
 ---
-title: "Why Donors Donate?"
+title: "Market simulator"
 output: 
@@
 
-```{r packages, include=FALSE}
+```{r load-packages, include=FALSE}
 knitr::opts_chunk$set(echo = FALSE)
@@
 library(shiny)
-library(here)
 ```
 
-```{r load data}
-
-# Beta's of everything. The only model we care about right now
-public_political_social_charity_demo <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
+```{r load-data}
+# Gammas of the "everything" model
+public_political_social_charity_demo <- read_rds(here::here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
   group_by(i, j) %>% 
@@
 
-# Persona Data from Market Simulator Workbook
-persona_data <- readxl::read_xlsx(here('analysis', 'output', "persona_configV07.xlsx"))
-
-# Org Data from Market Simulator Workbook
-org_data <- readxl::read_xlsx(here('analysis', 'output', "org_config.xlsx"))
-
-#Levels (This is a guess):            Means:
-#   1. Amnesty International          0.805
-#   2. Greenpeace                     0.923
-#   3. Oxfam                          0.620
-#   4. Red Cross                      1.820
-#   5. Environment                   -0.444
-#   6. Human Rights                  -0.164
-#   7. Refugee Relief                -0.582
-#   8. Financially Transparent        1.080
-#   9. Accountable                    1.130
-#   10. Small wealthy donors         -0.376
-#   11. Government Grants            -0.252
-#   12. Criticized by Government       -0.663
-#   13. Under Government Crackdown   -1.011
-
-################### Org Reactive Element ####################################
-
-beta <- as.data.frame(matrix(rep(0), nrow = 13))
-
-beta$levels = c("Amnesty International",
+# Starting organization configuration
+organization_data <- read_csv(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
+
+# Starting persona configuration
+persona_data <- read_csv(here::here('analysis', 'output', 'configurations', 'persona_config01.csv'))
+```
+
+```{r organization-reactive-table}
+# Placeholder for organization gammas
+gamma <- as.data.frame(matrix(rep(0), nrow = 13))
+
+# Assign level labels
+gamma$levels = c(
+  # Organization
+  "Amnesty International",
   "Greenpeace", 
@@
   "Red Cross",
-                # Org Issue
+  # Issue Area
   "Environment", 
@@
   # Financial Transparency
-                "Engages in transparency",
+  "Engages in financial transparency",
   # Financial Accountability
-                "Engages in accountability",
-                # Funding
+  "Engages in financial accountability",
+  # Funding Sourcs
   "Handful of wealthy private donors", 
   "Government grants",
-                # Gov Relations
+  # Relationship with Host Government
   "Criticized by government",
-                "Under government crackdown")
-
-# Org Reactive Element
+  "Under government crackdown"
+)
+
+# Organization configuration reactive element
 df <- reactive({
 
-  #Amnesty International
-    beta$ai_value <- 0
-    # beta$ai_value[beta$levels == 'Amnesty International'] <- 1
-    beta$ai_value[beta$levels %in% input$org1_id] <- 1
-    beta$ai_value[beta$levels %in% input$ai_issue] <- 1
-    beta$ai_value[beta$levels %in% input$ai_fin_trans] <- 1
-    beta$ai_value[beta$levels %in% input$ai_account] <- 1
-    beta$ai_value[beta$levels %in% input$ai_funding] <- 1
-    beta$ai_value[beta$levels %in% input$ai_gov_relat] <- 1
+  # Amnesty International
+    gamma$ai_value <- 0
+    gamma$ai_value[gamma$levels %in% input$org1_id] <- 1
+    gamma$ai_value[gamma$levels %in% input$ai_issue] <- 1
+    gamma$ai_value[gamma$levels %in% input$ai_fin_trans] <- 1
+    gamma$ai_value[gamma$levels %in% input$ai_account] <- 1
+    gamma$ai_value[gamma$levels %in% input$ai_funding] <- 1
+    gamma$ai_value[gamma$levels %in% input$ai_gov_relat] <- 1
 
   #Greenpeace
-    beta$gp_value <- 0
-    # beta$gp_value[beta$levels == 'Greenpeace'] <- 1
-    beta$gp_value[beta$levels %in% input$org2_id] <- 1
-    beta$gp_value[beta$levels %in% input$gp_issue] <- 1
-    beta$gp_value[beta$levels %in% input$gp_fin_trans] <- 1
-    beta$gp_value[beta$levels %in% input$gp_account] <- 1
-    beta$gp_value[beta$levels %in% input$gp_funding] <- 1
-    beta$gp_value[beta$levels %in% input$gp_gov_relat] <- 1
+    gamma$gp_value <- 0
+    # gamma$gp_value[gamma$levels == 'Greenpeace'] <- 1
+    gamma$gp_value[gamma$levels %in% input$org2_id] <- 1
+    gamma$gp_value[gamma$levels %in% input$gp_issue] <- 1
+    gamma$gp_value[gamma$levels %in% input$gp_fin_trans] <- 1
+    gamma$gp_value[gamma$levels %in% input$gp_account] <- 1
+    gamma$gp_value[gamma$levels %in% input$gp_funding] <- 1
+    gamma$gp_value[gamma$levels %in% input$gp_gov_relat] <- 1
 
   #Oxfam
-    beta$ox_value <- 0
-    # beta$ox_value[beta$levels == 'Oxfam'] <- 1
-    beta$ox_value[beta$levels %in% input$org3_id] <- 1
-    beta$ox_value[beta$levels %in% input$ox_issue] <- 1
-    beta$ox_value[beta$levels %in% input$ox_fin_trans] <- 1
-    beta$ox_value[beta$levels %in% input$ox_account] <- 1
-    beta$ox_value[beta$levels %in% input$ox_funding] <- 1
-    beta$ox_value[beta$levels %in% input$ox_gov_relat] <- 1
+    gamma$ox_value <- 0
+    # gamma$ox_value[gamma$levels == 'Oxfam'] <- 1
+    gamma$ox_value[gamma$levels %in% input$org3_id] <- 1
+    gamma$ox_value[gamma$levels %in% input$ox_issue] <- 1
+    gamma$ox_value[gamma$levels %in% input$ox_fin_trans] <- 1
+    gamma$ox_value[gamma$levels %in% input$ox_account] <- 1
+    gamma$ox_value[gamma$levels %in% input$ox_funding] <- 1
+    gamma$ox_value[gamma$levels %in% input$ox_gov_relat] <- 1
 
   #Redcross
-    beta$rc_value <- 0
-    # beta$rc_value[beta$levels == 'Red Cross'] <- 1
-    beta$rc_value[beta$levels %in% input$org4_id] <- 1
-    beta$rc_value[beta$levels %in% input$rc_issue] <- 1
-    beta$rc_value[beta$levels %in% input$rc_fin_trans] <- 1
-    beta$rc_value[beta$levels %in% input$rc_account] <- 1
-    beta$rc_value[beta$levels %in% input$rc_funding] <- 1
-    beta$rc_value[beta$levels %in% input$rc_gov_relat] <- 1
-    beta
+    gamma$rc_value <- 0
+    # gamma$rc_value[gamma$levels == 'Red Cross'] <- 1
+    gamma$rc_value[gamma$levels %in% input$org4_id] <- 1
+    gamma$rc_value[gamma$levels %in% input$rc_issue] <- 1
+    gamma$rc_value[gamma$levels %in% input$rc_fin_trans] <- 1
+    gamma$rc_value[gamma$levels %in% input$rc_account] <- 1
+    gamma$rc_value[gamma$levels %in% input$rc_funding] <- 1
+    gamma$rc_value[gamma$levels %in% input$rc_gov_relat] <- 1
+    gamma
 
 })
-
-################### Persona Reactive Element ####################################
-
-# Persona beta levels -----
-
-beta_persona <- as.data.frame(matrix(rep(0), nrow = 111))
-
-beta_persona$levels = c("Intercept",
-                        # Follow National News
-                        "Once a Week",
+```
+
+```{r persona-reactive-table}
+# Placeholder for persona gammas
+gamma_persona <- as.data.frame(matrix(rep(0), nrow = 111))
+
+# Assign covariate labels
+gamma_persona$levels <- c(
+  "Intercept",
+  # Follow national news
+  "Once a week",
   "At least once a day",
-                        # Follow International News
+  # Follow international news
   "Sometimes",
   "Always",
-                        # News Mediums
+  # Mediums to follow news
   "TV",
@@
   "News app",
-                        # Follow Government or Public Affairs
+  # Follow government and public affairs
   "Often", 
-                        # Travel to developing Countries
-                        "Yes (1)", 
-                        # Political Preference
+  # Traveled to a developing country
+  "Traveled to a developing country", 
+  # Liberal to Conservative
   "Somewhat liberal",
@@
   "Extremely conservative",
-                        # Trust in Political Institute
-                        "Very little trust",
-                        "Little trust",
-                        "Nuetral",
-                        "Some trust",
-                        "A lot of trust",
-                        "Complete trust (1)",
-                        # Should Others be Charitable
+  # Trust in political institutions
+  "Very little trust in political institutions",
+  "Little trust in political institutions",
+  "Neutral trust in political institutions",
+  "Some trust in political institutions",
+  "A lot of trust in political institutions",
+  "Complete trust in political institutions",
+  # People should be more charitable
   "Disagree",
   "Somewhat disagree",
-                        "Nuetral",
+  "Neutral",
   "Somewhat agree",
@@
   "Strongly agree",
-                        # Worship Service Attendance
-                        "Rarely",
-                        "At least once a month (1)",
-                        # Religious Importance
+  # Religious attendance
+  "Rarely attend",
+  "Attend at least once a month",
+  # Importance of religion
   "Important",
@@
   "Atheist",
-                        "Other (Religion)",
-                        # Charity Trust Importance
+  "Other religion",
+  # Importance of trusing charities
   "Very unimportant",
   "Somewhat unimportant",
-                        "Nuetral",
+  "Neutral",
   "Somewhat important",
@@
   "Essential",
-                        # Trust in Charities
-                        "Very little trust",
-                        "Little trust",
-                        "Nuetral",
-                        "Some trust",
-                        "A lot of trust",
-                        "Complete trust (2)",
-                        # Donation Frequency
-                        "At least once a month (2)", 
-                        # Donation Amount
+  # Trust in charities
+  "Very little trust in charities",
+  "Little trust in charities",
+  "Neutral trust in charities",
+  "Some trust in charities",
+  "A lot of trust in charities",
+  "Complete trust in charities",
+  # Donation frequency
+  "Donate at least once a month", 
+  # Donated last year
   "$50-$99",
@@
   "$10,000 +",
-                        # Volunteered last 12 months
-                        "Yes (2)",
-                        # Volunteer Frequency
-                        "Rarely",
-                        "More than once a month, less than once a year",
-                        "At least once a month (3)",
-                        # Personal Activism
-                        "Involved (1)",
-                        # Family Activism
-                        "Involved (2)",
-                        # Religious Membership
-                        "Inactive member",
-                        "Active member",
-                        # Sport or Recreational Membership
-                        "Inactive member",
-                        "Active member", 
-                        # Art, Music, or Educational Membership
-                        "Inactive member",
-                        "Active member",
-                        # Labor Union Membership
-                        "Inactive member",
-                        "Active member",
-                        # Political Party Membership
-                        "Inactive member",
-                        "Active member (1)",
-                        # Environmental Organization Membership
-                        "Inactive member",
-                        "Active member",
-                        # Professional Association
-                        "Inactive member",
-                        "Active member",
-                        # Humanitarian or Charity Membership
-                        "Inactive member",
-                        "Active member (2)",
-                        # Consumer Organization Membership
-                        "Inactive member",
-                        "Active member",
-                        #Other Organization Membership
-                        "Inactive member",
-                        "Active member",
+  # Volunteered in past 12 months
+  "Volunteered in past 12 months",
+  # Volunteer frequency
+  "Rarely volunteer",
+  "Volunteer more than once a month, less than once a year",
+  "Volunteer at least once a month",
+  # History of activism
+  "Personally involved",
+  # History of family activism
+  "Family involved",
+  # Church or religious organization
+  "Inactive church member",
+  "Active church member",
+  # Sport or recreational organization
+  "Inactive sports or rec organization member",
+  "Active sports or rec organization member", 
+  # Art, music, or educational organization
+  "Inactive art, music, or educational organization member",
+  "Active art, music, or educational organization member",
+  # Labor union
+  "Inactive union member",
+  "Active union member",
+  # Political party
+  "Inactive political party member",
+  "Active political party member",
+  # Environmental organization
+  "Inactive environmental organization member",
+  "Active environmental organization member",
+  # Professional association
+  "Inactive professional association member",
+  "Active professional association member",
+  # Humanitarian or charitable organization
+  "Inactive humanitarian or charitable organization member",
+  "Active humanitarian or charitable organization member",
+  # Consumer organization
+  "Inactive consumer organization member",
+  "Active consumer organization member",
+  # Other organization
+  "Inactive member in another organization",
+  "Active member in another organization",
   # Gender
@@
   "Prefer not to say",
-                        "Other (Gender)",
-                        # Marital Status
+  "Other gender",
+  # Marital status
   "Widowed",
@@
   "Black or African American", 
-                        "American Indian or Alaska Native", 
+  "American Indian or Alaskan Native", 
   "Asian", 
   "Native Hawaiian or Pacific Islander",
-                        "Other (Race)", 
+  "Other race",
   # Age
-                        "More than median age of 36")
+  "More than median age of 36"
+)
 
@@
   #Persona 1
-    beta_persona$p1_value <- 0
-
-    beta_persona$p1_value[beta_persona$levels == 'Intercept'] <- 1
-
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_international_news] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_news_medium] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_follow_gov] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_travel_developing] <- 1
-
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_institution_trust] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_others_charitable] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_worship_attendence] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion_importance] <- 1
-
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_charity_importance] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_trust_in_charity] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_frequency] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_amount] <- 1
-
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_12] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_frequency] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_personal_activism] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_family_activism] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_religious_member] <- 1
-
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_sport_member] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_art_member] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_labor_member] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_member] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_environmental_member] <- 1
-
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_professional_member] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_humanitarian_member] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_consumer_member] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_other_member] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_gender] <- 1
-
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_marital_status] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_education] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_income] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_race] <- 1
-    beta_persona$p1_value[beta_persona$levels %in% input$p1_age] <- 1
+    gamma_persona$p1_value <- 0
+
+    gamma_persona$p1_value[gamma_persona$levels == 'Intercept'] <- 1
+
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_national_news] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_international_news] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_news_medium] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_follow_gov] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_travel_developing] <- 1
+
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_political_pref] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_institution_trust] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_others_charitable] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_worship_attendence] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_religion_importance] <- 1
+
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_religion] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_charity_importance] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_trust_in_charity] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_donation_frequency] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_donation_amount] <- 1
+
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_volunteer_12] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_volunteer_frequency] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_personal_activism] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_family_activism] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_religious_member] <- 1
+
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_sport_member] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_art_member] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_labor_member] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_political_member] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_environmental_member] <- 1
+
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_professional_member] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_humanitarian_member] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_consumer_member] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_other_member] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_gender] <- 1
+
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_marital_status] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_education] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_income] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_race] <- 1
+    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_age] <- 1
 
   #Persona 2
-    beta_persona$p2_value <- 0
-
-    beta_persona$p2_value[beta_persona$levels == 'Intercept'] <- 1
-
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_national_news] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_international_news] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_news_medium] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_follow_gov] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_travel_developing] <- 1
-
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_political_pref] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_institution_trust] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_others_charitable] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_worship_attendence] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion_importance] <- 1
-
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_charity_importance] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_trust_in_charity] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_donation_frequency] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_donation_amount] <- 1
-
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_volunteer_12] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_volunteer_frequency] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_personal_activism] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_family_activism] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_religious_member] <- 1
-
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_sport_member] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_art_member] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_labor_member] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_political_member] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_environmental_member] <- 1
-
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_professional_member] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_humanitarian_member] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_consumer_member] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_other_member] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_gender] <- 1
-
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_marital_status] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_education] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_income] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_race] <- 1
-    beta_persona$p2_value[beta_persona$levels %in% input$p2_age] <- 1
+    gamma_persona$p2_value <- 0
+
+    gamma_persona$p2_value[gamma_persona$levels == 'Intercept'] <- 1
+
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_national_news] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_international_news] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_news_medium] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_follow_gov] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_travel_developing] <- 1
+
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_political_pref] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_institution_trust] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_others_charitable] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_worship_attendence] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_religion_importance] <- 1
+
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_religion] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_charity_importance] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_trust_in_charity] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_donation_frequency] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_donation_amount] <- 1
+
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_volunteer_12] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_volunteer_frequency] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_personal_activism] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_family_activism] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_religious_member] <- 1
+
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_sport_member] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_art_member] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_labor_member] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_political_member] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_environmental_member] <- 1
+
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_professional_member] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_humanitarian_member] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_consumer_member] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_other_member] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_gender] <- 1
+
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_marital_status] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_education] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_income] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_race] <- 1
+    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_age] <- 1
 
   #Persona 3
-    beta_persona$p3_value <- 0
-
-    beta_persona$p3_value[beta_persona$levels == 'Intercept'] <- 1
-
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_national_news] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_international_news] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_news_medium] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_follow_gov] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_travel_developing] <- 1
-
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_pref] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_institution_trust] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_others_charitable] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_worship_attendence] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion_importance] <- 1
-
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_charity_importance] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_trust_in_charity] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_frequency] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_amount] <- 1
-
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_12] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_frequency] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_personal_activism] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_family_activism] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_religious_member] <- 1
-
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_sport_member] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_art_member] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_labor_member] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_member] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_environmental_member] <- 1
-
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_professional_member] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_humanitarian_member] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_consumer_member] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_other_member] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_gender] <- 1
-
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_marital_status] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_education] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_income] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_race] <- 1
-    beta_persona$p3_value[beta_persona$levels %in% input$p3_age] <- 1
-    beta_persona
+    gamma_persona$p3_value <- 0
+
+    gamma_persona$p3_value[gamma_persona$levels == 'Intercept'] <- 1
+
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_national_news] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_international_news] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_news_medium] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_follow_gov] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_travel_developing] <- 1
+
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_political_pref] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_institution_trust] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_others_charitable] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_worship_attendence] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_religion_importance] <- 1
+
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_religion] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_charity_importance] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_trust_in_charity] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_donation_frequency] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_donation_amount] <- 1
+
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_volunteer_12] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_volunteer_frequency] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_personal_activism] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_family_activism] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_religious_member] <- 1
+
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_sport_member] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_art_member] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_labor_member] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_political_member] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_environmental_member] <- 1
+
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_professional_member] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_humanitarian_member] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_consumer_member] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_other_member] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_gender] <- 1
+
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_marital_status] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_education] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_income] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_race] <- 1
+    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_age] <- 1
+    gamma_persona
 
@@
 
-<!-- Practice Code -->
-```{r practice code}
-
-#### this chunk is for testing code and making sure things work before adding it into the dashboard
+```{r practice-code}
+
+# this chunk is for testing code and making sure things work before adding it into the dashboard
 
@@
 
-# beta_persona_test <- as.data.frame(matrix(rep(0), nrow = 38))
+# gamma_persona_test <- as.data.frame(matrix(rep(0), nrow = 38))
 # 
-# beta_persona_test$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
+# gamma_persona_test$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
 # 
@@
 # 
-# beta_persona_test$p1 <- 1
+# gamma_persona_test$p1 <- 1
 # 
-# beta_persona_test$p2 <- 2
+# gamma_persona_test$p2 <- 2
 # 
-# beta_persona_test$p3 <- 3
+# gamma_persona_test$p3 <- 3
 #         
@@
 # 
-# p_beta1 <- as.matrix(public_political_social_charity_demo) %*%   
+# p_gamma1 <- as.matrix(public_political_social_charity_demo) %*%   
 #   
-#   as.matrix(persona1) %*% beta_persona_test[,3]
-
+#   as.matrix(persona1) %*% gamma_persona_test[,3]
 ```
@@
 
-beta <- data.frame(
+gamma <- data.frame(
   value = c(0,0,0),
@@
                   label = "Select Issue Area:",
-                  choices = beta$levels,
+                  choices = gamma$levels,
                   multiple = TRUE)
@@
   df <- reactive({
-    beta$value[beta$levels %in% input$ai_issue] <- 1
-    beta
+    gamma$value[gamma$levels %in% input$ai_issue] <- 1
+    gamma
   })
@@
 
-### Calculating the Persona betas ###
+### Calculating the Persona gammas ###
 
@@
 
-# matrix multiplication between persona data and betas
-beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona1)
+# matrix multiplication between persona data and gammas
+gamma1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona1)
 
@@
 
-# matrix multiplication between persona data and betas
-beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona2)
+# matrix multiplication between persona data and gammas
+gamma2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona2)
 
@@
 
-# matrix multiplication between persona data and betas
-beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona3)
+# matrix multiplication between persona data and gammas
+gamma3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona3)
 
@@
 
-# Expected utility matrix multiplication between computed persona betas and org data for persona 1
-org1_exp_util1 <- exp(t(org1) %*% as.matrix(beta1))
-org2_exp_util1 <- exp(t(org2) %*% as.matrix(beta1))
-org3_exp_util1 <- exp(t(org3) %*% as.matrix(beta1))
-org4_exp_util1 <- exp(t(org4) %*% as.matrix(beta1))
+# Expected utility matrix multiplication between computed persona gammas and org data for persona 1
+org1_exp_util1 <- exp(t(org1) %*% as.matrix(gamma1))
+org2_exp_util1 <- exp(t(org2) %*% as.matrix(gamma1))
+org3_exp_util1 <- exp(t(org3) %*% as.matrix(gamma1))
+org4_exp_util1 <- exp(t(org4) %*% as.matrix(gamma1))
 
@@
 
-# org1_exp_util2 <- exp(t(org1) %*% as.matrix(p_beta2))
-# org2_exp_util2 <- exp(t(org2) %*% as.matrix(p_beta2))
-# org3_exp_util2 <- exp(t(org3) %*% as.matrix(p_beta2))
-# org4_exp_util2 <- exp(t(org4) %*% as.matrix(p_beta2))
+# org1_exp_util2 <- exp(t(org1) %*% as.matrix(p_gamma2))
+# org2_exp_util2 <- exp(t(org2) %*% as.matrix(p_gamma2))
+# org3_exp_util2 <- exp(t(org3) %*% as.matrix(p_gamma2))
+# org4_exp_util2 <- exp(t(org4) %*% as.matrix(p_gamma2))
 # 
 # 
-# org1_exp_util3 <- exp(t(org1) %*% as.matrix(p_beta3))
-# org2_exp_util3 <- exp(t(org2) %*% as.matrix(p_beta3))
-# org3_exp_util3 <- exp(t(org3) %*% as.matrix(p_beta3))
-# org4_exp_util3 <- exp(t(org4) %*% as.matrix(p_beta3))
+# org1_exp_util3 <- exp(t(org1) %*% as.matrix(p_gamma3))
+# org2_exp_util3 <- exp(t(org2) %*% as.matrix(p_gamma3))
+# org3_exp_util3 <- exp(t(org3) %*% as.matrix(p_gamma3))
+# org4_exp_util3 <- exp(t(org4) %*% as.matrix(p_gamma3))
 
@@
   # Persona 1 
-    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
+    p_gamma1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
 
   # Expected Utility
-  ai_exp_util1 <- exp(t(org_choice[, 3]) %*% as.matrix(p_beta1))
-  gp_exp_util1 <- exp(t(org_choice[, 4]) %*% as.matrix(p_beta1))
-  ox_exp_util1 <- exp(t(org_choice[, 5]) %*% as.matrix(p_beta1))
-  rc_exp_util1 <- exp(t(org_choice[, 6]) %*% as.matrix(p_beta1))
+  ai_exp_util1 <- exp(t(org_choice[, 3]) %*% as.matrix(p_gamma1))
+  gp_exp_util1 <- exp(t(org_choice[, 4]) %*% as.matrix(p_gamma1))
+  ox_exp_util1 <- exp(t(org_choice[, 5]) %*% as.matrix(p_gamma1))
+  rc_exp_util1 <- exp(t(org_choice[, 6]) %*% as.matrix(p_gamma1))
 
@@
   # Persona 2
-    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
+    p_gamma2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
 
   # Expected Utility
-  ai_exp_util2 <- exp(t(org_choice[, 3]) %*% as.matrix(p_beta2))
-  gp_exp_util2 <- exp(t(org_choice[, 4]) %*% as.matrix(p_beta2))
-  ox_exp_util2 <- exp(t(org_choice[, 5]) %*% as.matrix(p_beta2))
-  rc_exp_util2 <- exp(t(org_choice[, 6]) %*% as.matrix(p_beta2))
+  ai_exp_util2 <- exp(t(org_choice[, 3]) %*% as.matrix(p_gamma2))
+  gp_exp_util2 <- exp(t(org_choice[, 4]) %*% as.matrix(p_gamma2))
+  ox_exp_util2 <- exp(t(org_choice[, 5]) %*% as.matrix(p_gamma2))
+  rc_exp_util2 <- exp(t(org_choice[, 6]) %*% as.matrix(p_gamma2))
 
@@
   # Persona 3
-    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
+    p_gamma3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
 
   # Expected Utility
-  ai_exp_util3 <- exp(t(org_choice[, 3]) %*% as.matrix(p_beta3))
-  gp_exp_util3 <- exp(t(org_choice[, 4]) %*% as.matrix(p_beta3))
-  ox_exp_util3 <- exp(t(org_choice[, 5]) %*% as.matrix(p_beta3))
-  rc_exp_util3 <- exp(t(org_choice[, 6]) %*% as.matrix(p_beta3))
+  ai_exp_util3 <- exp(t(org_choice[, 3]) %*% as.matrix(p_gamma3))
+  gp_exp_util3 <- exp(t(org_choice[, 4]) %*% as.matrix(p_gamma3))
+  ox_exp_util3 <- exp(t(org_choice[, 5]) %*% as.matrix(p_gamma3))
+  rc_exp_util3 <- exp(t(org_choice[, 6]) %*% as.matrix(p_gamma3))
 
@@
   # Organization name inputs
-  df[,2] <- rep(c(input$ai_id, input$gp_id, input$ox_id, input$rc_id),6)
+  df[,2] <- c(input$ai_id, input$gp_id, input$ox_id, input$rc_id)
   # Type of value
@@
           value = "Persona 1",
-          placeholder = "Enter Persona Name")
+          placeholder = "Enter Persona Name",
+          width = "450px")
 
@@
                      "At least once a day"),
-         selected = "At least once a day")
+         selected = "At least once a day",
+         width = "450px")
 
@@
                      "Always"),
-         selected = "Always")
+         selected = "Always",
+         width = "450px")
 
@@
          multiple = TRUE,
-         selected = c("TV", "Print", "Social media"))
+         selected = c("TV", "Print", "Social media"),
+         width = "450px")
 
@@
                      "Often"),
-         selected = "Often")
+         selected = "Often",
+         width = "450px")
 
@@
          choices = c("Doesn't travel", "Does travel"),
-         selected = "Does travel")
+         selected = "Does travel",
+         width = "450px")
 
@@
                      "Extremely conservative"),
-         selected = "Somewhat liberal")
+         selected = "Somewhat liberal",
+         width = "450px")
 
@@
                      "Complete trust in political institutions"),
-         selected = "Complete trust in political institutions ")
+         selected = "Complete trust in political institutions",
+         width = "450px")
 
@@
                      "Agree",
-                     "Strongly agree",),
-         selected = "Strongly agree")
+                     "Strongly agree"),
+         selected = "Strongly agree",
+         width = "450px")
 
@@
                      "Attend at least once a month"),
-         selected = "Attend at least once a month")
+         selected = "Attend at least once a month",
+         width = "450px")
 
@@
                      "Important"),
-         selected = "Important")
+         selected = "Important",
+         width = "450px")
 
@@
                      'Other (Religion)'),
-         selected = 'Protestant')
+         selected = 'Protestant',
+         width = "450px")
 
@@
                       "Essential"),
-          selected = "Somewhat unimportant")
+          selected = "Somewhat unimportant",
+          width = "450px")
 
@@
                         "Complete trust in charities"),
-            selected = "Complete trust in charities")
+            selected = "Complete trust in charities",
+            width = "450px")
 
@@
                      'Donate at least once a month'),
-         selected = "Donate at least once a month")
+         selected = "Donate at least once a month",
+         width = "450px")
 
@@
                      '$10,000+'),
-         selected = "$100-$499")
+         selected = "$100-$499",
+         width = "450px")
 
@@
          choices = c("Haven't volunteered", "Have volunteered"),
-         selected = "Have volunteered")
+         selected = "Have volunteered",
+         width = "450px")
 
@@
                      "Volunteer at least once a month"),
-         selected = "Volunteer at least once a month")
+         selected = "Volunteer at least once a month",
+         width = "450px")
 
@@
                      'Personally involved'),
-         selected = "Personally involved")
+         selected = "Personally involved",
+         width = "450px")
 
@@
                      'Family involved'),
-         selected = "Family involved")
+         selected = "Family involved",
+         width = "450px")
 
@@
                      'Active church member'),
-         selected = "Don't belong to church membership")
+         selected = "Don't belong to church membership",
+         width = "450px")
 
@@
                      'Active sports member'),
-         selected = "Don't belong to sports membership")
+         selected = "Don't belong to sports membership",
+         width = "450px")
 #Fix
@@
                      'Active educational member'),
-         selected = "Don't belong to educational membership")
+         selected = "Don't belong to educational membership",
+         width = "450px")
 #Fix
@@
                      'Active union member'),
-         selected = "Don't belong to union")
+         selected = "Don't belong to union",
+         width = "450px")
 
@@
                      'Active party member'),
-         selected = "Active party member")
+         selected = "Active party member",
+         width = "450px")
 # Fix
@@
                      'Active environmental member'),
-         selected = "Don't belong to environmental organization")
+         selected = "Don't belong to environmental organization",
+         width = "450px")
 # Fix
@@
                      'Active professional member'),
-         selected = "Don't belong to professional membership")
+         selected = "Don't belong to professional membership",
+         width = "450px")
 # Fix
@@
                      'Active humanitarian member'),
-         selected = "Active humanitarian member")
+         selected = "Active humanitarian member",
+         width = "450px")
 
@@
                      'Active consumer member'),
-         selected = "Don't belong to consumer organization")
+         selected = "Don't belong to consumer organization",
+         width = "450px")
 # Fix
@@
                      'Active other member'),
-         selected = "Don't belong to other organization")
+         selected = "Don't belong to other organization",
+         width = "450px")
 
@@
                      "Other (Gender)"),
-         selected = "Male")
+         selected = "Male",
+         width = "450px")
 
@@
                      "Never married"),
-         selected = "Married")
+         selected = "Married",
+         width = "450px")
 
@@
                      "Doctorate"),
-         selected = "2 year degree")
+         selected = "2 year degree",
+         width = "450px")
 
@@
                      'More than median of $61,372'),
-         selected = "More than median of $61,372")
+         selected = "More than median of $61,372",
+         width = "450px")
 
@@
          multiple = TRUE,
-         selected = "White")
+         selected = "White",
+         width = "450px")
 
@@
                      "More than median age of 36"),
-         selected = "Less than median age of 36")
+         selected = "Less than median age of 36",
+         width = "450px")
 
@@
           value = "Persona 2",
-          placeholder = "Enter Persona Name")
+          placeholder = "Enter Persona Name",
+          width = "450px")
 
@@
                      "Once a week",
-                     "At least once a day"))
+                     "At least once a day"),
+         selected = "At least once a day",
+         width = "450px")
 
@@
                      "Sometimes",
-                     'Always'))
+                     "Always"),
+         selected = "Always",
+         width = "450px")
 
@@
                      "News app"),
-         multiple = TRUE)
+         multiple = TRUE,
+         selected = c("TV", "Print", "Social media"),
+         width = "450px")
 
@@
          choices = c("Not Often",
-                     "Often"))
-
+                     "Often"),
+         selected = "Often",
+         width = "450px")
+
+#Fix
 selectInput("p2_travel_developing",
          label = "Travel to developing country:",
-         choices = c('No', "Yes"))
+         choices = c("Doesn't travel", "Does travel"),
+         selected = "Does travel",
+         width = "450px")
 
@@
                      "Somewhat conservative",
-                     "Extremely conservative"))
-
+                     "Extremely conservative"),
+         selected = "Somewhat liberal",
+         width = "450px")
+
+#Fix
 selectInput("p2_institution_trust",
          label = "Political institution trust from none to complete:",
-         choices = c("No trust at all",
-                     "Very little trust",
-                     "Little trust",
-                     "Nuetral",
-                     "Some trust",
-                     "A lot of trust",
-                     "Complete trust"))
+         choices = c("No trust at all in political institutions",
+                     "Very little trust in political institutions",
+                     "Little trust in political institutions",
+                     "Nuetral trust in political institutions",
+                     "Some trust in political institutions",
+                     "A lot of trust in political institutions",
+                     "Complete trust in political institutions"),
+         selected = "Complete trust in political institutions",
+         width = "450px")
 
@@
                      "Agree",
-                     "Strongly agree"))
-
+                     "Strongly agree"),
+         selected = "Strongly agree",
+         width = "450px")
+
+# Fix
 selectInput("p2_worship_attendance",
@@
          choices = c("Not sure",
-                     "Rarely",
-                     "At least once a month"))
+                     "Rarely attend services",
+                     "Attend at least once a month"),
+         selected = "Attend at least once a month",
+         width = "450px")
 
@@
          choices = c("Not important",
-                     "Important"))
+                     "Important"),
+         selected = "Important",
+         width = "450px")
 
@@
                      'Atheist',
-                     'Other (Religion)'))
+                     'Other (Religion)'),
+         selected = 'Protestant',
+         width = "450px")
 
@@
                       "Very important",
-                      "Essential"))
-
+                      "Essential"),
+          selected = "Somewhat unimportant",
+          width = "450px")
+
+#Fix
 selectInput("p2_trust_in_charity",
             label = "Charity Trust:",
-            choices = c("No trust at all",
-                        "Very little trust",
-                        "Little trust",
-                        "Nuetral",
-                        "Some trust",
-                        "A lot of trust",
-                        "Complete trust"))
-
+            choices = c("No trust at all in charities",
+                        "Very little trust in charities",
+                        "Little trust in charities",
+                        "Nuetral trust in charities",
+                        "Some trust in charities",
+                        "A lot of trust in charities",
+                        "Complete trust in charities"),
+            selected = "Complete trust in charities",
+            width = "450px")
+
+#Fix
 selectInput("p2_donation_frequency",
          label = "Donation Frequency:",
-         choices = c('More than once a month, less than once a year',
-                     'At least once a month'))
+         choices = c('Donate more than once a month, less than once a year',
+                     'Donate at least once a month'),
+         selected = "Donate at least once a month",
+         width = "450px")
 
@@
                      '$5,000-$9,999',
-                     '$10,000+'))
-
+                     '$10,000+'),
+         selected = "$100-$499",
+         width = "450px")
+
+#Fix
 selectInput("p2_volunteer_12",
          label = "Volunteered in last 12 Months:",
-         choices = c("No", "Yes"))
-
+         choices = c("Haven't volunteered", "Have volunteered"),
+         selected = "Have volunteered",
+         width = "450px")
+
+#Fix
 selectInput("p2_volunteer_frequency",
@@
          choices = c("Haven't volunteered in past 12 months",
-                     "Rarely",
-                     "More than once a month, less than once a year",
-                     "At least once a month"))
-
+                     "Rarely volunteer",
+                     "Volunteer more than once a month, less than once a year",
+                     "Volunteer at least once a month"),
+         selected = "Volunteer at least once a month",
+         width = "450px")
+
+# fix
 selectInput("p2_personal_activism",
          label = "Personal Activism:",
-         choices = c('Not involved',
-                     'Involved'))
-
+         choices = c('Not personally involved ',
+                     'Personally involved'),
+         selected = "Personally involved",
+         width = "450px")
+
+#Fix
 selectInput("p2_family_activism",
          label = "Family Activism:",
-         choices = c('Not involved',
-                     'Involved'))
-
+         choices = c('Family not involved',
+                     'Family involved'),
+         selected = "Family involved",
+         width = "450px")
+
+#Fix
 selectInput("p2_religious_member",
          label = "Church Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to church membership",
+                     'Inactive church member',
+                     'Active church member'),
+         selected = "Don't belong to church membership",
+         width = "450px")
+
+#Fix
 selectInput("p2_sport_member",
          label = "Sport or Recreational Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to sports membership",
+                     'Inactive sports member',
+                     'Active sports member'),
+         selected = "Don't belong to sports membership",
+         width = "450px")
+#Fix
 selectInput("p2_art_member",
          label = "Art, Music, or Educational Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to educational membership",
+                     'Inactive educational member',
+                     'Active educational member'),
+         selected = "Don't belong to educational membership",
+         width = "450px")
+#Fix
 selectInput("p2_labor_member",
          label = "Labor Union Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to union",
+                     'Inactive union member',
+                     'Active union member'),
+         selected = "Don't belong to union",
+         width = "450px")
+
+#Fix
 selectInput("p2_political_member",
          label = "Political Party Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to party",
+                     'Inactive party member',
+                     'Active party member'),
+         selected = "Active party member",
+         width = "450px")
+# Fix
 selectInput("p2_environmental_member",
-         label = "Enviornmental Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         label = "Environmental Org. Membership:",
+         choices = c("Don't belong to environmental organization",
+                     'Inactive environmental member',
+                     'Active environmental member'),
+         selected = "Don't belong to environmental organization",
+         width = "450px")
+# Fix
 selectInput("p2_professional_member",
          label = "Professional Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to professional membership",
+                     'Inactive professional member',
+                     'Active professional member'),
+         selected = "Don't belong to professional membership",
+         width = "450px")
+# Fix
 selectInput("p2_humanitarian_member",
          label = "Humanitarian Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to humanitarian organization",
+                     'Inactive humanitarian member',
+                     'Active humanitarian member'),
+         selected = "Active humanitarian member",
+         width = "450px")
+
+# Fix
 selectInput("p2_consumer_member",
          label = "Consumer Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to consumer organization",
+                     'Inactive consumer member',
+                     'Active consumer member'),
+         selected = "Don't belong to consumer organization",
+         width = "450px")
+# Fix
 selectInput("p2_other_member",
          label = "Other Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
+         choices = c("Don't belong to other organization",
+                     'Inactive other member',
+                     'Active other member'),
+         selected = "Don't belong to other organization",
+         width = "450px")
 
@@
                      "Prefer not to say",
-                     "Other (Gender)"))
+                     "Other (Gender)"),
+         selected = "Male",
+         width = "450px")
 
@@
                      "Separated",
-                     "Never married"))
+                     "Never married"),
+         selected = "Married",
+         width = "450px")
 
@@
                      "Graduate or professional degree",
-                     "Doctorate"))
+                     "Doctorate"),
+         selected = "Some college",
+         width = "450px")
 
@@
          choices = c('Less than median of $61,372',
-                     'More than median of $61,372'))
+                     'More than median of $61,372'),
+         selected = "More than median of $61,372",
+         width = "450px")
 
@@
                      'Other (Race)'),
-         multiple = TRUE)
+         multiple = TRUE,
+         selected = "American Indian or Alaska Native",
+         width = "450px")
 
@@
          choices = c('Less than median age of 36',
-                     "More than median age of 36"))
+                     "More than median age of 36"),
+         selected = "Less than median age of 36",
+         width = "450px")
 
@@
           value = "Persona 3",
-          placeholder = "Enter Persona Name")
+          placeholder = "Enter Persona Name",
+          width = "450px")
 
@@
          choices = c("Not Often",
-                     "Often"))
-
+                     "Often"),
+         selected = "Often",
+         width = "450px")
+
+#Fix
 selectInput("p3_travel_developing",
          label = "Travel to developing country:",
-         choices = c('No', "Yes"))
+         choices = c("Doesn't travel", "Does travel"),
+         selected = "Does travel",
+         width = "450px")
 
@@
                      "Somewhat conservative",
-                     "Extremely conservative"))
-
+                     "Extremely conservative"),
+         selected = "Somewhat liberal",
+         width = "450px")
+
+#Fix
 selectInput("p3_institution_trust",
          label = "Political institution trust from none to complete:",
-         choices = c("No trust at all",
-                     "Very little trust",
-                     "Little trust",
-                     "Nuetral",
-                     "Some trust",
-                     "A lot of trust",
-                     "Complete trust"))
+         choices = c("No trust at all in political institutions",
+                     "Very little trust in political institutions",
+                     "Little trust in political institutions",
+                     "Nuetral trust in political institutions",
+                     "Some trust in political institutions",
+                     "A lot of trust in political institutions",
+                     "Complete trust in political institutions"),
+         selected = "Complete trust in political institutions",
+         width = "450px")
 
@@
                      "Agree",
-                     "Strongly agree"))
-
+                     "Strongly agree"),
+         selected = "Strongly agree",
+         width = "450px")
+
+# Fix
 selectInput("p3_worship_attendance",
@@
                       "Very important",
-                      "Essential"))
-
+                      "Essential"),
+          selected = "Somewhat unimportant",
+          width = "450px")
+
+#Fix
 selectInput("p3_trust_in_charity",
             label = "Charity Trust:",
-            choices = c("No trust at all",
-                        "Very little trust",
-                        "Little trust",
-                        "Nuetral",
-                        "Some trust",
-                        "A lot of trust",
-                        "Complete trust"))
-
+            choices = c("No trust at all in charities",
+                        "Very little trust in charities",
+                        "Little trust in charities",
+                        "Nuetral trust in charities",
+                        "Some trust in charities",
+                        "A lot of trust in charities",
+                        "Complete trust in charities"),
+            selected = "Complete trust in charities",
+            width = "450px")
+
+#Fix
 selectInput("p3_donation_frequency",
          label = "Donation Frequency:",
-         choices = c('More than once a month, less than once a year',
-                     'At least once a month'))
+         choices = c('Donate more than once a month, less than once a year',
+                     'Donate at least once a month'),
+         selected = "Donate at least once a month",
+         width = "450px")
 
@@
                      '$5,000-$9,999',
-                     '$10,000+'))
-
+                     '$10,000+'),
+         selected = "$100-$499",
+         width = "450px")
+
+#Fix
 selectInput("p3_volunteer_12",
          label = "Volunteered in last 12 Months:",
-         choices = c("No", "Yes"))
-
+         choices = c("Haven't volunteered", "Have volunteered"),
+         selected = "Have volunteered",
+         width = "450px")
+
+#Fix
 selectInput("p3_volunteer_frequency",
@@
          choices = c("Haven't volunteered in past 12 months",
-                     "Rarely",
-                     "More than once a month, less than once a year",
-                     "At least once a month"))
-
+                     "Rarely volunteer",
+                     "Volunteer more than once a month, less than once a year",
+                     "Volunteer at least once a month"),
+         selected = "Volunteer at least once a month",
+         width = "450px")
+
+# fix
 selectInput("p3_personal_activism",
          label = "Personal Activism:",
-         choices = c('Not involved',
-                     'Involved'))
-
+         choices = c('Not personally involved ',
+                     'Personally involved'),
+         selected = "Personally involved",
+         width = "450px")
+
+#Fix
 selectInput("p3_family_activism",
          label = "Family Activism:",
-         choices = c('Not involved',
-                     'Involved'))
-
+         choices = c('Family not involved',
+                     'Family involved'),
+         selected = "Family involved",
+         width = "450px")
+
+#Fix
 selectInput("p3_religious_member",
          label = "Church Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to church membership",
+                     'Inactive church member',
+                     'Active church member'),
+         selected = "Don't belong to church membership",
+         width = "450px")
+
+#Fix
 selectInput("p3_sport_member",
          label = "Sport or Recreational Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to sports membership",
+                     'Inactive sports member',
+                     'Active sports member'),
+         selected = "Don't belong to sports membership",
+         width = "450px")
+#Fix
 selectInput("p3_art_member",
          label = "Art, Music, or Educational Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to educational membership",
+                     'Inactive educational member',
+                     'Active educational member'),
+         selected = "Don't belong to educational membership",
+         width = "450px")
+#Fix
 selectInput("p3_labor_member",
          label = "Labor Union Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to union",
+                     'Inactive union member',
+                     'Active union member'),
+         selected = "Don't belong to union",
+         width = "450px")
+
+#Fix
 selectInput("p3_political_member",
          label = "Political Party Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to party",
+                     'Inactive party member',
+                     'Active party member'),
+         selected = "Active party member",
+         width = "450px")
+# Fix
 selectInput("p3_environmental_member",
-         label = "Enviornmental Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         label = "Environmental Org. Membership:",
+         choices = c("Don't belong to environmental organization",
+                     'Inactive environmental member',
+                     'Active environmental member'),
+         selected = "Don't belong to environmental organization",
+         width = "450px")
+# Fix
 selectInput("p3_professional_member",
          label = "Professional Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to professional membership",
+                     'Inactive professional member',
+                     'Active professional member'),
+         selected = "Don't belong to professional membership",
+         width = "450px")
+# Fix
 selectInput("p3_humanitarian_member",
          label = "Humanitarian Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to humanitarian organization",
+                     'Inactive humanitarian member',
+                     'Active humanitarian member'),
+         selected = "Active humanitarian member",
+         width = "450px")
+
+# Fix
 selectInput("p3_consumer_member",
          label = "Consumer Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
-
+         choices = c("Don't belong to consumer organization",
+                     'Inactive consumer member',
+                     'Active consumer member'),
+         selected = "Don't belong to consumer organization",
+         width = "450px")
+# Fix
 selectInput("p3_other_member",
          label = "Other Org. Membership:",
-         choices = c("Don't belong",
-                     'Inactive member',
-                     'Active member'))
+         choices = c("Don't belong to other organization",
+                     'Inactive other member',
+                     'Active other member'),
+         selected = "Don't belong to other organization",
+         width = "450px")
 
@@
                      "Prefer not to say",
-                     "Other (Gender)"))
+                     "Other (Gender)"),
+         selected = "Female",
+         width = "450px")
 
@@
                      "Graduate or professional degree",
-                     "Doctorate"))
+                     "Doctorate"),
+         selected = "Graduate or professional degree",
+         width = "450px")
 
@@
                      'Other (Race)'),
-         multiple = TRUE)
+         multiple = TRUE,
+         selected = c("Black or African American", "American Indian or Alaska Native"),
+         width = "450px")
 
@@
           value = "Organization 1",
-          placeholder = "Enter Organization Name")
+          placeholder = "Enter Organization Name",
+          width = "450px")
 
@@
                        "Red Cross"),
-            selected = "Red Cross")
+            selected = "Red Cross",
+            width = "450px")
 
@@
                         "Refugee relief"),
-            selected = "Emergency response")
+            selected = "Emergency response",
+            width = "450px")
 
@@
                         "Engages in transparency"),
-            selected = "Engages in transparency")
+            selected = "Engages in transparency",
+            width = "450px")
 
@@
                         "Engages in accountability"),
-            selected = "Engages in accountability")
+            selected = "Engages in accountability",
+            width = "450px")
 
@@
                         "Handful of wealthy private donors",
-                        "Government grants"))
+                        "Government grants"),
+            width = "450px")
 
@@
                         "Criticized by government", 
-                        "Under government crackdown"))
+                        "Under government crackdown"),
+            width = "450px")
 
@@
           value = "Organization 2",
-          placeholder = "Enter Organiation Name")
+          placeholder = "Enter Organiation Name",
+          width = "450px")
 
@@
                         "Refugee relief"),
-            selected = "Environment")
+            selected = "Environment",
+            width = "450px")
 
@@
                         "Criticized by government", 
-                        "Under government crackdown"))
+                        "Under government crackdown"),
+            width = "450px")
 ```
@@
           value = "Organization 3",
-          placeholder = "Enter Organiation Name")
+          placeholder = "Enter Organiation Name",
+          width = "450px")
 
@@
                         "Refugee relief"),
-            selected = "Human rights")
+            selected = "Human rights",
+            width = "450px")
 
@@
           value = "Organization 4",
-          placeholder = "Enter Organiation Name")
+          placeholder = "Enter Organiation Name",
+          width = "450px")
 
@@
                         "Refugee relief"),
-            selected = "Refugee relief")
+            selected = "Refugee relief",
+            width = "450px")
 

### 2020-09-16 analysis/05_market_simulator.Rmd
Still cleaning up and looking for errors

@@
 # Gammas of the "everything" model
-public_political_social_charity_demo <- read_rds(here::here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
+public_political_social_charity_demo <- read_rds(
+  here::here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')
+  ) %>% 
   group_by(i, j) %>% 
@@
 
-# Starting organization configuration
-organization_data <- read_csv(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
-
-# Starting persona configuration
-persona_data <- read_csv(here::here('analysis', 'output', 'configurations', 'persona_config01.csv'))
+# Initial organization configuration
+organization_data <- read_csv(
+  here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
+)
+
+# Initial persona configuration
+persona_data <- read_csv(
+  here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
+)
 ```
@@
 ```{r organization-reactive-table}
-# Placeholder for organization gammas
-gamma <- as.data.frame(matrix(rep(0), nrow = 13))
+# Placeholder for organization reactive table
+org_table <- as.data.frame(matrix(rep(0), nrow = nrow(organization_data)))
 
 # Assign level labels
-gamma$levels = c(
+org_table$levels = c(
   # Organization
@@
   "Red Cross",
-  # Issue Area
+  # Issue area
   "Environment", 
@@
   "Refugee relief",
-  # Financial Transparency
+  # Financial transparency
   "Engages in financial transparency",
-  # Financial Accountability
+  # Financial accountability
   "Engages in financial accountability",
-  # Funding Sourcs
+  # Funding sources
   "Handful of wealthy private donors", 
   "Government grants",
-  # Relationship with Host Government
+  # Relationship with host government
   "Criticized by government",
@@
 # Organization configuration reactive element
-df <- reactive({
-
-  # Amnesty International
-    gamma$ai_value <- 0
-    gamma$ai_value[gamma$levels %in% input$org1_id] <- 1
-    gamma$ai_value[gamma$levels %in% input$ai_issue] <- 1
-    gamma$ai_value[gamma$levels %in% input$ai_fin_trans] <- 1
-    gamma$ai_value[gamma$levels %in% input$ai_account] <- 1
-    gamma$ai_value[gamma$levels %in% input$ai_funding] <- 1
-    gamma$ai_value[gamma$levels %in% input$ai_gov_relat] <- 1
-
-  #Greenpeace
-    gamma$gp_value <- 0
-    # gamma$gp_value[gamma$levels == 'Greenpeace'] <- 1
-    gamma$gp_value[gamma$levels %in% input$org2_id] <- 1
-    gamma$gp_value[gamma$levels %in% input$gp_issue] <- 1
-    gamma$gp_value[gamma$levels %in% input$gp_fin_trans] <- 1
-    gamma$gp_value[gamma$levels %in% input$gp_account] <- 1
-    gamma$gp_value[gamma$levels %in% input$gp_funding] <- 1
-    gamma$gp_value[gamma$levels %in% input$gp_gov_relat] <- 1
-
-  #Oxfam
-    gamma$ox_value <- 0
-    # gamma$ox_value[gamma$levels == 'Oxfam'] <- 1
-    gamma$ox_value[gamma$levels %in% input$org3_id] <- 1
-    gamma$ox_value[gamma$levels %in% input$ox_issue] <- 1
-    gamma$ox_value[gamma$levels %in% input$ox_fin_trans] <- 1
-    gamma$ox_value[gamma$levels %in% input$ox_account] <- 1
-    gamma$ox_value[gamma$levels %in% input$ox_funding] <- 1
-    gamma$ox_value[gamma$levels %in% input$ox_gov_relat] <- 1
-
-  #Redcross
-    gamma$rc_value <- 0
-    # gamma$rc_value[gamma$levels == 'Red Cross'] <- 1
-    gamma$rc_value[gamma$levels %in% input$org4_id] <- 1
-    gamma$rc_value[gamma$levels %in% input$rc_issue] <- 1
-    gamma$rc_value[gamma$levels %in% input$rc_fin_trans] <- 1
-    gamma$rc_value[gamma$levels %in% input$rc_account] <- 1
-    gamma$rc_value[gamma$levels %in% input$rc_funding] <- 1
-    gamma$rc_value[gamma$levels %in% input$rc_gov_relat] <- 1
-    gamma
-
+org_reactive <- reactive({
+  # Organization 1
+  org_table$org1_value <- 0
+  org_table$org1_value[org_table$levels %in% input$org1_id] <- 1
+  org_table$org1_value[org_table$levels %in% input$org1_issue] <- 1
+  org_table$org1_value[org_table$levels %in% input$org1_fin_trans] <- 1
+  org_table$org1_value[org_table$levels %in% input$org1_fin_account] <- 1
+  org_table$org1_value[org_table$levels %in% input$org1_funding] <- 1
+  org_table$org1_value[org_table$levels %in% input$org1_host_gov] <- 1
+
+  # Organization 2
+  org_table$org2_value <- 0
+  org_table$org2_value[org_table$levels %in% input$org2_id] <- 1
+  org_table$org2_value[org_table$levels %in% input$org2_issue] <- 1
+  org_table$org2_value[org_table$levels %in% input$org2_fin_trans] <- 1
+  org_table$org2_value[org_table$levels %in% input$org2_fin_account] <- 1
+  org_table$org2_value[org_table$levels %in% input$org2_funding] <- 1
+  org_table$org2_value[org_table$levels %in% input$org2_host_gov] <- 1
+
+  # Organization 3
+  org_table$org3_value <- 0
+  org_table$org3_value[org_table$levels %in% input$org3_id] <- 1
+  org_table$org3_value[org_table$levels %in% input$org3_issue] <- 1
+  org_table$org3_value[org_table$levels %in% input$org3_fin_trans] <- 1
+  org_table$org3_value[org_table$levels %in% input$org3_fin_account] <- 1
+  org_table$org3_value[org_table$levels %in% input$org3_funding] <- 1
+  org_table$org3_value[org_table$levels %in% input$org3_host_gov] <- 1
+
+  # Organization 4
+  org_table$org4_value <- 0
+  org_table$org4_value[org_table$levels %in% input$org4_id] <- 1
+  org_table$org4_value[org_table$levels %in% input$org4_issue] <- 1
+  org_table$org4_value[org_table$levels %in% input$org4_fin_trans] <- 1
+  org_table$org4_value[org_table$levels %in% input$org4_fin_account] <- 1
+  org_table$org4_value[org_table$levels %in% input$org4_funding] <- 1
+  org_table$org4_value[org_table$levels %in% input$org4_host_gov] <- 1
+  org_table
 })
@@
 # Placeholder for persona gammas
-gamma_persona <- as.data.frame(matrix(rep(0), nrow = 111))
+per_table <- as.data.frame(matrix(rep(0), nrow = 111))
 
 # Assign covariate labels
-gamma_persona$levels <- c(
+per_table$levels <- c(
+  # Intercept
   "Intercept",
@@
 
-# p reactive element ----
-
-p <- reactive({
-
-  #Persona 1
-    gamma_persona$p1_value <- 0
-
-    gamma_persona$p1_value[gamma_persona$levels == 'Intercept'] <- 1
-
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_national_news] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_international_news] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_news_medium] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_follow_gov] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_travel_developing] <- 1
-
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_political_pref] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_institution_trust] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_others_charitable] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_worship_attendence] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_religion_importance] <- 1
-
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_religion] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_charity_importance] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_trust_in_charity] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_donation_frequency] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_donation_amount] <- 1
-
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_volunteer_12] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_volunteer_frequency] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_personal_activism] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_family_activism] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_religious_member] <- 1
-
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_sport_member] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_art_member] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_labor_member] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_political_member] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_environmental_member] <- 1
-
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_professional_member] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_humanitarian_member] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_consumer_member] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_other_member] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_gender] <- 1
-
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_marital_status] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_education] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_income] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_race] <- 1
-    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_age] <- 1
-
-  #Persona 2
-    gamma_persona$p2_value <- 0
-
-    gamma_persona$p2_value[gamma_persona$levels == 'Intercept'] <- 1
-
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_national_news] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_international_news] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_news_medium] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_follow_gov] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_travel_developing] <- 1
-
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_political_pref] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_institution_trust] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_others_charitable] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_worship_attendence] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_religion_importance] <- 1
-
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_religion] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_charity_importance] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_trust_in_charity] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_donation_frequency] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_donation_amount] <- 1
-
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_volunteer_12] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_volunteer_frequency] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_personal_activism] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_family_activism] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_religious_member] <- 1
-
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_sport_member] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_art_member] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_labor_member] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_political_member] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_environmental_member] <- 1
-
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_professional_member] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_humanitarian_member] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_consumer_member] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_other_member] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_gender] <- 1
-
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_marital_status] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_education] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_income] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_race] <- 1
-    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_age] <- 1
-
-  #Persona 3
-    gamma_persona$p3_value <- 0
-
-    gamma_persona$p3_value[gamma_persona$levels == 'Intercept'] <- 1
-
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_national_news] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_international_news] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_news_medium] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_follow_gov] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_travel_developing] <- 1
-
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_political_pref] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_institution_trust] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_others_charitable] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_worship_attendence] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_religion_importance] <- 1
-
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_religion] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_charity_importance] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_trust_in_charity] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_donation_frequency] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_donation_amount] <- 1
-
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_volunteer_12] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_volunteer_frequency] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_personal_activism] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_family_activism] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_religious_member] <- 1
-
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_sport_member] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_art_member] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_labor_member] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_political_member] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_environmental_member] <- 1
-
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_professional_member] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_humanitarian_member] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_consumer_member] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_other_member] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_gender] <- 1
-
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_marital_status] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_education] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_income] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_race] <- 1
-    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_age] <- 1
-    gamma_persona
-
+# Persona configuration reactive element
+per_reactive <- reactive({
+  # Persona 1
+  per_table$per1_value <- 0
+  per_table$per1_value[per_table$levels == 'Intercept'] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_national_news] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_international_news] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_news_medium] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_follow_gov] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_travel_developing] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_political_pref] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_institution_trust] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_others_charitable] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_worship_attendence] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_religion_importance] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_religion] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_charity_importance] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_trust_in_charity] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_donation_frequency] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_donation_amount] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_volunteer_12] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_volunteer_frequency] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_personal_activism] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_family_activism] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_religious_member] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_sport_member] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_art_member] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_labor_member] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_political_member] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_environmental_member] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_professional_member] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_humanitarian_member] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_consumer_member] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_other_member] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_gender] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_marital_status] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_education] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_income] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_race] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_age] <- 1
+
+  # Persona 2
+  per_table$per2_value <- 0
+  per_table$per2_value[per_table$levels == 'Intercept'] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_national_news] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_international_news] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_news_medium] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_follow_gov] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_travel_developing] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_political_pref] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_institution_trust] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_others_charitable] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_worship_attendence] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_religion_importance] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_religion] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_charity_importance] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_trust_in_charity] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_donation_frequency] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_donation_amount] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_volunteer_12] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_volunteer_frequency] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_personal_activism] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_family_activism] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_religious_member] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_sport_member] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_art_member] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_labor_member] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_political_member] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_environmental_member] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_professional_member] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_humanitarian_member] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_consumer_member] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_other_member] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_gender] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_marital_status] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_education] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_income] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_race] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_age] <- 1
+
+  # Persona 3
+  per_table$per3_value <- 0
+  per_table$per3_value[per_table$levels == 'Intercept'] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_national_news] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_international_news] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_news_medium] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_follow_gov] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_travel_developing] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_political_pref] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_institution_trust] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_others_charitable] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_worship_attendence] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_religion_importance] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_religion] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_charity_importance] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_trust_in_charity] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_donation_frequency] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_donation_amount] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_volunteer_12] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_volunteer_frequency] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_personal_activism] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_family_activism] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_religious_member] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_sport_member] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_art_member] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_labor_member] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_political_member] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_environmental_member] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_professional_member] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_humanitarian_member] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_consumer_member] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_other_member] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_gender] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_marital_status] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_education] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_income] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_race] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_age] <- 1
+  per_table
 })
@@
 
-```{r practice-code}
-
-# this chunk is for testing code and making sure things work before adding it into the dashboard
-
-# df <- as.data.frame(matrix(rep(0), nrow = 1))
+```{r matrix-multiplication, eval=FALSE, include=FALSE}
+# # Overwrite gamma??
+# gamma <- data.frame(
+#   value = c(0,0,0),
+#   levels = c("Environment", "Human rights", "Refugee relief")
+# )
 # 
-# df$levels = "Rating"
+# ui <- fluidPage(
+#   fluidRow(
+#     column(6,
+#       selectInput("org1_issue", 
+#                   label = "Select Issue Area:",
+#                   choices = gamma$levels,
+#                   multiple = TRUE)
+#     ),
+#     column(6,
+#       tableOutput("data")
+#     )
+#   )
+# )
 # 
-#                         
-# df$p1[df$levels == "Rating"] <- input$rating_id
-# 
-# 
-# p1_pol_pref <- reactive({
-#   input$p1_political_pref
+# server = function(input, output) {
+#   org_reactive <- reactive({
+#     gamma$value[gamma$levels %in% input$org1_issue] <- 1
+#     gamma
 #   })
 # 
-# 
-# sliderInput("rating_id",
-#        label = "Rating",
-#        min = 0,
-#        max = 7,
-#        value = 0)
-
-# gamma_persona_test <- as.data.frame(matrix(rep(0), nrow = 38))
-# 
-# gamma_persona_test$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
-# 
-# 
-# 
-# # Persona Reactive Element
-# 
-# gamma_persona_test$p1 <- 1
-# 
-# gamma_persona_test$p2 <- 2
-# 
-# gamma_persona_test$p3 <- 3
-#         
-# persona1 <- persona_data[,2]
-# 
-# p_gamma1 <- as.matrix(public_political_social_charity_demo) %*%   
-#   
-#   as.matrix(persona1) %*% gamma_persona_test[,3]
+#   output$data <- renderTable({
+#     organizations()
+#   })
+# }
 ```
 
-```{r matrix multiplication, eval=FALSE, include=FALSE}
-library(shiny)
-
-gamma <- data.frame(
-  value = c(0,0,0),
-  levels = c("Environment", "Human rights", "Refugee relief")
-)
-
-ui <- fluidPage(
-  fluidRow(
-    column(6,
-      selectInput("ai_issue", 
-                  label = "Select Issue Area:",
-                  choices = gamma$levels,
-                  multiple = TRUE)
-    ),
-    column(6,
-      tableOutput("data")
-    )
-  )
-)
-
-server = function(input, output) {
-
-  df <- reactive({
-    gamma$value[gamma$levels %in% input$ai_issue] <- 1
-    gamma
-  })
-
-  output$data <- renderTable({
-    df()
-  })
-}
-```
-
-<!-- Persona Inputs -->
 ```{r Manual Testing Matrix Multiplication}
@@
 # Organization
-org1 <- org_data[,2]
-
-org2 <- org_data[,3]
-
-org3 <- org_data[,4]
-
-org4 <- org_data[,5]
+org1 <- organization_data[,2]
+
+org2 <- organization_data[,3]
+
+org3 <- organization_data[,4]
+
+org4 <- organization_data[,5]
 
@@
 
-# org1_exp_util2 <- exp(t(org1) %*% as.matrix(p_gamma2))
-# org2_exp_util2 <- exp(t(org2) %*% as.matrix(p_gamma2))
-# org3_exp_util2 <- exp(t(org3) %*% as.matrix(p_gamma2))
-# org4_exp_util2 <- exp(t(org4) %*% as.matrix(p_gamma2))
-# 
-# 
-# org1_exp_util3 <- exp(t(org1) %*% as.matrix(p_gamma3))
-# org2_exp_util3 <- exp(t(org2) %*% as.matrix(p_gamma3))
-# org3_exp_util3 <- exp(t(org3) %*% as.matrix(p_gamma3))
-# org4_exp_util3 <- exp(t(org4) %*% as.matrix(p_gamma3))
-
 ```
@@
 ```{r global plot}
-
 renderPlotly({
-  org_choice = df()
-  per_choice = p()
+  org_choice = org_reactive()
+  per_choice = per_reactive()
 
@@
   # Expected Utility
-  ai_exp_util1 <- exp(t(org_choice[, 3]) %*% as.matrix(p_gamma1))
-  gp_exp_util1 <- exp(t(org_choice[, 4]) %*% as.matrix(p_gamma1))
-  ox_exp_util1 <- exp(t(org_choice[, 5]) %*% as.matrix(p_gamma1))
-  rc_exp_util1 <- exp(t(org_choice[, 6]) %*% as.matrix(p_gamma1))
+  org1_exp_util1 <- exp(t(org_choice[, 3]) %*% as.matrix(p_gamma1))
+  org2_exp_util1 <- exp(t(org_choice[, 4]) %*% as.matrix(p_gamma1))
+  org3_exp_util1 <- exp(t(org_choice[, 5]) %*% as.matrix(p_gamma1))
+  org4_exp_util1 <- exp(t(org_choice[, 6]) %*% as.matrix(p_gamma1))
 
   # Market Share
-  ai_rate1 <- 100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1)
-  gp_rate1 <- 100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1)
-  ox_rate1 <- 100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1)
-  rc_rate1 <- 100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1)
+  org1_rate1 <- 100 * org1_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
+  org2_rate1 <- 100 * org2_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
+  org3_rate1 <- 100 * org3_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
+  org4_rate1 <- 100 * org4_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
 
@@
   # Expected Utility
-  ai_exp_util2 <- exp(t(org_choice[, 3]) %*% as.matrix(p_gamma2))
-  gp_exp_util2 <- exp(t(org_choice[, 4]) %*% as.matrix(p_gamma2))
-  ox_exp_util2 <- exp(t(org_choice[, 5]) %*% as.matrix(p_gamma2))
-  rc_exp_util2 <- exp(t(org_choice[, 6]) %*% as.matrix(p_gamma2))
+  org1_exp_util2 <- exp(t(org_choice[, 3]) %*% as.matrix(p_gamma2))
+  org2_exp_util2 <- exp(t(org_choice[, 4]) %*% as.matrix(p_gamma2))
+  org3_exp_util2 <- exp(t(org_choice[, 5]) %*% as.matrix(p_gamma2))
+  org4_exp_util2 <- exp(t(org_choice[, 6]) %*% as.matrix(p_gamma2))
 
   # Market Share
-  ai_rate2 <- 100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2)
-  gp_rate2 <- 100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2)
-  ox_rate2 <- 100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2)
-  rc_rate2 <- 100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2)
+  org1_rate2 <- 100 * org1_exp_util2/sum(org1_exp_util2, org2_exp_util2, org3_exp_util2, org4_exp_util2)
+  org2_rate2 <- 100 * org2_exp_util2/sum(org1_exp_util2, org2_exp_util2, org3_exp_util2, org4_exp_util2)
+  org3_rate2 <- 100 * org3_exp_util2/sum(org1_exp_util2, org2_exp_util2, org3_exp_util2, org4_exp_util2)
+  org4_rate2 <- 100 * org4_exp_util2/sum(org1_exp_util2, org2_exp_util2, org3_exp_util2, org4_exp_util2)
 
@@
   # Expected Utility
-  ai_exp_util3 <- exp(t(org_choice[, 3]) %*% as.matrix(p_gamma3))
-  gp_exp_util3 <- exp(t(org_choice[, 4]) %*% as.matrix(p_gamma3))
-  ox_exp_util3 <- exp(t(org_choice[, 5]) %*% as.matrix(p_gamma3))
-  rc_exp_util3 <- exp(t(org_choice[, 6]) %*% as.matrix(p_gamma3))
+  org1_exp_util3 <- exp(t(org_choice[, 3]) %*% as.matrix(p_gamma3))
+  org2_exp_util3 <- exp(t(org_choice[, 4]) %*% as.matrix(p_gamma3))
+  org3_exp_util3 <- exp(t(org_choice[, 5]) %*% as.matrix(p_gamma3))
+  org4_exp_util3 <- exp(t(org_choice[, 6]) %*% as.matrix(p_gamma3))
 
   # Market Share
-  ai_rate3 <- 100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3)
-  gp_rate3 <- 100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3)
-  ox_rate3 <- 100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3)
-  rc_rate3 <- 100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3)
+  org1_rate3 <- 100 * org1_exp_util3/sum(org1_exp_util3, org2_exp_util3, org3_exp_util3, org4_exp_util3)
+  org2_rate3 <- 100 * org2_exp_util3/sum(org1_exp_util3, org2_exp_util3, org3_exp_util3, org4_exp_util3)
+  org3_rate3 <- 100 * org3_exp_util3/sum(org1_exp_util3, org2_exp_util3, org3_exp_util3, org4_exp_util3)
+  org4_rate3 <- 100 * org4_exp_util3/sum(org1_exp_util3, org2_exp_util3, org3_exp_util3, org4_exp_util3)
 
   # Data for Plotly
-  data <- c(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1, ai_rate1, gp_rate1, ox_rate1, rc_rate1, 
-            ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2, ai_rate2, gp_rate2, ox_rate2, rc_rate2,
-            ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3, ai_rate3, gp_rate3, ox_rate3, rc_rate3)
+  data <- c(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1, org1_rate1, org2_rate1, org3_rate1, org4_rate1, 
+            org1_exp_util2, org2_exp_util2, org3_exp_util2, org4_exp_util2, org1_rate2, org2_rate2, org3_rate2, org4_rate2,
+            org1_exp_util3, org2_exp_util3, org3_exp_util3, org4_exp_util3, org1_rate3, org2_rate3, org3_rate3, org4_rate3)
 
   # Empty dataframe
-  df <- as.data.frame(matrix(data, 24, 1))
+  org_reactive <- as.data.frame(matrix(data, 24, 1))
 
   # Organization name inputs
-  df[,2] <- c(input$ai_id, input$gp_id, input$ox_id, input$rc_id)
+  org_reactive[,2] <- c(input$org1_id, input$org2_id, input$org3_id, input$org4_id)
   # Type of value
-  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
+  org_reactive[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
   # Persona name inputs
-  df[,4] <- c(rep(input$p1_id,8), rep(input$p2_id, 8), rep(input$p3_id, 8))
+  org_reactive[,4] <- c(rep(input$per1_id,8), rep(input$per2_id, 8), rep(input$per3_id, 8))
 
   # Rename columns
-  colnames(df) <- c('Value', 'Organization', "Type", "Persona")
-
-  ggplotly(df %>% 
+  colnames(org_reactive) <- c('Value', 'Organization', "Type", "Persona")
+
+  ggplotly(org_reactive %>% 
              # Only care about the Market Share right now
@@
              mutate(
-               Organization = factor(Organization, levels = c(input$ai_id, input$gp_id, input$ox_id, input$rc_id), ordered = TRUE),
-               Persona = factor(Persona, levels = c(input$p1_id, input$p2_id, input$p3_id), ordered = TRUE)) %>% 
+               Organization = factor(Organization, levels = c(input$org1_id, input$org2_id, input$org3_id, input$org4_id), ordered = TRUE),
+               Persona = factor(Persona, levels = c(input$per1_id, input$per2_id, input$per3_id), ordered = TRUE)) %>% 
              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
@@
 
-textInput("p1_id",
+textInput("per1_id",
           label = "Persona Name",
@@
 
-selectInput("p1_national_news",
+selectInput("per1_national_news",
          label = "Follow national news:",
@@
 
-selectInput("p1_international_news",
+selectInput("per1_international_news",
          label = "Follow international news:",
@@
 
-selectInput("p1_news_medium",
+selectInput("per1_news_medium",
          label = "Medium to follow news:",
@@
 
-selectInput("p1_follow_gov",
+selectInput("per1_follow_gov",
          label = "Follow government & public affairs:",
@@
 #Fix
-selectInput("p1_travel_developing",
+selectInput("per1_travel_developing",
          label = "Travel to developing country:",
@@
 
-selectInput("p1_political_pref",
+selectInput("per1_political_pref",
          label = "Political views from liberal to conservative:",
@@
 #Fix
-selectInput("p1_institution_trust",
+selectInput("per1_institution_trust",
          label = "Political institution trust from none to complete:",
@@
 
-selectInput("p1_others_charitable",
+selectInput("per1_others_charitable",
          label = "People should be more charitable:",
@@
 # Fix
-selectInput("p1_worship_attendance",
+selectInput("per1_worship_attendance",
          label = "Worship service attendance:",
@@
 
-selectInput("p1_religion_importance",
+selectInput("per1_religion_importance",
          label = "Importance of religion:",
@@
 
-selectInput("p1_religion",
+selectInput("per1_religion",
          label = "Religion:",
@@
 
-selectInput("p1_charity_importance",
+selectInput("per1_charity_importance",
           label = "Charity Importance:",
@@
 #Fix
-selectInput("p1_trust_in_charity",
+selectInput("per1_trust_in_charity",
             label = "Charity Trust:",
@@
 #Fix
-selectInput("p1_donation_frequency",
+selectInput("per1_donation_frequency",
          label = "Donation Frequency:",
@@
 
-selectInput("p1_donation_amount",
+selectInput("per1_donation_amount",
          label = "Donation Amount:",
@@
 #Fix
-selectInput("p1_volunteer_12",
+selectInput("per1_volunteer_12",
          label = "Volunteered in last 12 Months:",
@@
 #Fix
-selectInput("p1_volunteer_frequency",
+selectInput("per1_volunteer_frequency",
          label = "Volunteer Frequency:",
@@
 # fix
-selectInput("p1_personal_activism",
+selectInput("per1_personal_activism",
          label = "Personal Activism:",
@@
 #Fix
-selectInput("p1_family_activism",
+selectInput("per1_family_activism",
          label = "Family Activism:",
@@
 #Fix
-selectInput("p1_religious_member",
+selectInput("per1_religious_member",
          label = "Church Membership:",
@@
 #Fix
-selectInput("p1_sport_member",
+selectInput("per1_sport_member",
          label = "Sport or Recreational Membership:",
@@
 #Fix
-selectInput("p1_art_member",
+selectInput("per1_art_member",
          label = "Art, Music, or Educational Membership:",
@@
 #Fix
-selectInput("p1_labor_member",
+selectInput("per1_labor_member",
          label = "Labor Union Membership:",
@@
 #Fix
-selectInput("p1_political_member",
+selectInput("per1_political_member",
          label = "Political Party Membership:",
@@
 # Fix
-selectInput("p1_environmental_member",
+selectInput("per1_environmental_member",
          label = "Environmental Org. Membership:",
@@
 # Fix
-selectInput("p1_professional_member",
+selectInput("per1_professional_member",
          label = "Professional Membership:",
@@
 # Fix
-selectInput("p1_humanitarian_member",
+selectInput("per1_humanitarian_member",
          label = "Humanitarian Org. Membership:",
@@
 # Fix
-selectInput("p1_consumer_member",
+selectInput("per1_consumer_member",
          label = "Consumer Org. Membership:",
@@
 # Fix
-selectInput("p1_other_member",
+selectInput("per1_other_member",
          label = "Other Org. Membership:",
@@
 
-selectInput("p1_gender",
+selectInput("per1_gender",
          label = "Gender:",
@@
 
-selectInput("p1_marital_status",
+selectInput("per1_marital_status",
          label = "Marital Status:",
@@
 
-selectInput("p1_education",
+selectInput("per1_education",
          label = "Education:",
@@
 
-selectInput("p1_income",
+selectInput("per1_income",
          label = "Income:",
@@
 
-selectInput("p1_race",
+selectInput("per1_race",
          label = "Race(s):",
@@
 
-selectInput("p1_age",
+selectInput("per1_age",
          label = "Age:",
@@
 
-textInput("p2_id",
+textInput("per2_id",
           label = "Persona Name",
@@
 
-selectInput("p2_national_news",
+selectInput("per2_national_news",
          label = "Follow national news:",
@@
 
-selectInput("p2_international_news",
+selectInput("per2_international_news",
          label = "Follow international news:",
@@
 
-selectInput("p2_news_medium",
+selectInput("per2_news_medium",
          label = "Medium to follow news:",
@@
 
-selectInput("p2_follow_gov",
+selectInput("per2_follow_gov",
          label = "Follow government & public affairs:",
@@
 #Fix
-selectInput("p2_travel_developing",
+selectInput("per2_travel_developing",
          label = "Travel to developing country:",
@@
 
-selectInput("p2_political_pref",
+selectInput("per2_political_pref",
          label = "Political views from liberal to conservative:",
@@
 #Fix
-selectInput("p2_institution_trust",
+selectInput("per2_institution_trust",
          label = "Political institution trust from none to complete:",
@@
 
-selectInput("p2_others_charitable",
+selectInput("per2_others_charitable",
          label = "People should be more charitable:",
@@
 # Fix
-selectInput("p2_worship_attendance",
+selectInput("per2_worship_attendance",
          label = "Worship service attendance:",
@@
 
-selectInput("p2_religion_importance",
+selectInput("per2_religion_importance",
          label = "Importance of religion:",
@@
 
-selectInput("p2_religion",
+selectInput("per2_religion",
          label = "Religion:",
@@
 
-selectInput("p2_charity_importance",
+selectInput("per2_charity_importance",
           label = "Charity Importance:",
@@
 #Fix
-selectInput("p2_trust_in_charity",
+selectInput("per2_trust_in_charity",
             label = "Charity Trust:",
@@
 #Fix
-selectInput("p2_donation_frequency",
+selectInput("per2_donation_frequency",
          label = "Donation Frequency:",
@@
 
-selectInput("p2_donation_amount",
+selectInput("per2_donation_amount",
          label = "Donation Amount:",
@@
 #Fix
-selectInput("p2_volunteer_12",
+selectInput("per2_volunteer_12",
          label = "Volunteered in last 12 Months:",
@@
 #Fix
-selectInput("p2_volunteer_frequency",
+selectInput("per2_volunteer_frequency",
          label = "Volunteer Frequency:",
@@
 # fix
-selectInput("p2_personal_activism",
+selectInput("per2_personal_activism",
          label = "Personal Activism:",
@@
 #Fix
-selectInput("p2_family_activism",
+selectInput("per2_family_activism",
          label = "Family Activism:",
@@
 #Fix
-selectInput("p2_religious_member",
+selectInput("per2_religious_member",
          label = "Church Membership:",
@@
 #Fix
-selectInput("p2_sport_member",
+selectInput("per2_sport_member",
          label = "Sport or Recreational Membership:",
@@
 #Fix
-selectInput("p2_art_member",
+selectInput("per2_art_member",
          label = "Art, Music, or Educational Membership:",
@@
 #Fix
-selectInput("p2_labor_member",
+selectInput("per2_labor_member",
          label = "Labor Union Membership:",
@@
 #Fix
-selectInput("p2_political_member",
+selectInput("per2_political_member",
          label = "Political Party Membership:",
@@
 # Fix
-selectInput("p2_environmental_member",
+selectInput("per2_environmental_member",
          label = "Environmental Org. Membership:",
@@
 # Fix
-selectInput("p2_professional_member",
+selectInput("per2_professional_member",
          label = "Professional Membership:",
@@
 # Fix
-selectInput("p2_humanitarian_member",
+selectInput("per2_humanitarian_member",
          label = "Humanitarian Org. Membership:",
@@
 # Fix
-selectInput("p2_consumer_member",
+selectInput("per2_consumer_member",
          label = "Consumer Org. Membership:",
@@
 # Fix
-selectInput("p2_other_member",
+selectInput("per2_other_member",
          label = "Other Org. Membership:",
@@
 
-selectInput("p2_gender",
+selectInput("per2_gender",
          label = "Gender:",
@@
 
-selectInput("p2_marital_status",
+selectInput("per2_marital_status",
          label = "Marital Status:",
@@
 
-selectInput("p2_education",
+selectInput("per2_education",
          label = "Education:",
@@
 
-selectInput("p2_income",
+selectInput("per2_income",
          label = "Income:",
@@
 
-selectInput("p2_race",
+selectInput("per2_race",
          label = "Race(s):",
@@
 
-selectInput("p2_age",
+selectInput("per2_age",
          label = "Age:",
@@
 
-textInput("p3_id",
+textInput("per3_id",
           label = "Persona Name",
@@
 
-selectInput("p3_national_news",
+selectInput("per3_national_news",
          label = "Follow national news:",
@@
 
-selectInput("p3_international_news",
+selectInput("per3_international_news",
          label = "Follow international news:",
@@
 
-selectInput("p3_news_medium",
+selectInput("per3_news_medium",
          label = "Medium to follow news:",
@@
 
-selectInput("p3_follow_gov",
+selectInput("per3_follow_gov",
          label = "Follow government & public affairs:",
@@
 #Fix
-selectInput("p3_travel_developing",
+selectInput("per3_travel_developing",
          label = "Travel to developing country:",
@@
 
-selectInput("p3_political_pref",
+selectInput("per3_political_pref",
          label = "Political views from liberal to conservative:",
@@
 #Fix
-selectInput("p3_institution_trust",
+selectInput("per3_institution_trust",
          label = "Political institution trust from none to complete:",
@@
 
-selectInput("p3_others_charitable",
+selectInput("per3_others_charitable",
          label = "People should be more charitable:",
@@
 # Fix
-selectInput("p3_worship_attendance",
+selectInput("per3_worship_attendance",
          label = "Worship service attendance:",
@@
 
-selectInput("p3_religion_importance",
+selectInput("per3_religion_importance",
          label = "Importance of religion:",
@@
 
-selectInput("p3_religion",
+selectInput("per3_religion",
          label = "Religion:",
@@
 
-selectInput("p3_charity_importance",
+selectInput("per3_charity_importance",
           label = "Charity Importance:",
@@
 #Fix
-selectInput("p3_trust_in_charity",
+selectInput("per3_trust_in_charity",
             label = "Charity Trust:",
@@
 #Fix
-selectInput("p3_donation_frequency",
+selectInput("per3_donation_frequency",
          label = "Donation Frequency:",
@@
 
-selectInput("p3_donation_amount",
+selectInput("per3_donation_amount",
          label = "Donation Amount:",
@@
 #Fix
-selectInput("p3_volunteer_12",
+selectInput("per3_volunteer_12",
          label = "Volunteered in last 12 Months:",
@@
 #Fix
-selectInput("p3_volunteer_frequency",
+selectInput("per3_volunteer_frequency",
          label = "Volunteer Frequency:",
@@
 # fix
-selectInput("p3_personal_activism",
+selectInput("per3_personal_activism",
          label = "Personal Activism:",
@@
 #Fix
-selectInput("p3_family_activism",
+selectInput("per3_family_activism",
          label = "Family Activism:",
@@
 #Fix
-selectInput("p3_religious_member",
+selectInput("per3_religious_member",
          label = "Church Membership:",
@@
 #Fix
-selectInput("p3_sport_member",
+selectInput("per3_sport_member",
          label = "Sport or Recreational Membership:",
@@
 #Fix
-selectInput("p3_art_member",
+selectInput("per3_art_member",
          label = "Art, Music, or Educational Membership:",
@@
 #Fix
-selectInput("p3_labor_member",
+selectInput("per3_labor_member",
          label = "Labor Union Membership:",
@@
 #Fix
-selectInput("p3_political_member",
+selectInput("per3_political_member",
          label = "Political Party Membership:",
@@
 # Fix
-selectInput("p3_environmental_member",
+selectInput("per3_environmental_member",
          label = "Environmental Org. Membership:",
@@
 # Fix
-selectInput("p3_professional_member",
+selectInput("per3_professional_member",
          label = "Professional Membership:",
@@
 # Fix
-selectInput("p3_humanitarian_member",
+selectInput("per3_humanitarian_member",
          label = "Humanitarian Org. Membership:",
@@
 # Fix
-selectInput("p3_consumer_member",
+selectInput("per3_consumer_member",
          label = "Consumer Org. Membership:",
@@
 # Fix
-selectInput("p3_other_member",
+selectInput("per3_other_member",
          label = "Other Org. Membership:",
@@
 
-selectInput("p3_gender",
+selectInput("per3_gender",
          label = "Gender:",
@@
 
-selectInput("p3_marital_status",
+selectInput("per3_marital_status",
          label = "Marital Status:",
@@
 
-selectInput("p3_education",
+selectInput("per3_education",
          label = "Education:",
@@
 
-selectInput("p3_income",
+selectInput("per3_income",
          label = "Income:",
@@
 
-selectInput("p3_race",
+selectInput("per3_race",
          label = "Race(s):",
@@
 
-selectInput("p3_age",
+selectInput("per3_age",
          label = "Age:",
@@
 
-```{r ai org inputs}
-
-textInput("ai_id",
+```{r org1 org inputs}
+
+textInput("org1_id",
           label = "Organization Name",
@@
 
-selectInput("ai_issue", 
+selectInput("org1_issue", 
             label = "Select Issue Area:",
@@
 
-selectInput("ai_fin_trans",
+selectInput("org1_fin_trans",
             label = "Select Financial Transparency:",
@@
 
-selectInput("ai_account",
+selectInput("org1_fin_account",
             label = "Select Financial Accountability:",
@@
 
-selectInput("ai_funding",
+selectInput("org1_funding",
             label = "Select Funding Source:",
@@
 
-selectInput("ai_gov_relat",
+selectInput("org1_host_gov",
             label = "Select Relationship With Host Government",
@@
 
-```{r gp org inputs}
-
-textInput("gp_id",
+```{r org2 org inputs}
+
+textInput("org2_id",
           label = "Organization Name",
@@
 
-selectInput("gp_issue", 
+selectInput("org2_issue", 
             label = "Select Issue Area:",
@@
 
-selectInput("gp_fin_trans",
+selectInput("org2_fin_trans",
             label = "Select Financial Transparency:",
@@
 
-selectInput("gp_account",
+selectInput("org2_fin_account",
             label = "Select Financial Accountability:",
@@
 
-selectInput("gp_funding",
+selectInput("org2_funding",
             label = "Select Funding Source:",
@@
 
-selectInput("gp_gov_relat",
+selectInput("org2_host_gov",
             label = "Select Relationship With Host Government",
@@
 
-```{r ox org inputs}
-
-textInput("ox_id",
+```{r org3 org inputs}
+
+textInput("org3_id",
           label = "Organization Name",
@@
 
-selectInput("ox_issue", 
+selectInput("org3_issue", 
             label = "Select Issue Area:",
@@
 
-selectInput("ox_fin_trans",
+selectInput("org3_fin_trans",
             label = "Select Financial Transparency:",
@@
 
-selectInput("ox_account",
+selectInput("org3_fin_account",
             label = "Select Financial Accountability:",
@@
 
-selectInput("ox_funding",
+selectInput("org3_funding",
             label = "Select Funding Source:",
@@
 
-selectInput("ox_gov_relat",
+selectInput("org3_host_gov",
             label = "Select Relationship With Host Government",
@@
 
-```{r rc org inputs}
-
-textInput("rc_id",
+```{r org4 org inputs}
+
+textInput("org4_id",
           label = "Organization Name",
@@
 
-selectInput("rc_issue", 
+selectInput("org4_issue", 
             label = "Select Issue Area:",
@@
 
-selectInput("rc_fin_trans",
+selectInput("org4_fin_trans",
             label = "Select Financial Transparency:",
@@
 
-selectInput("rc_account",
+selectInput("org4_fin_account",
             label = "Select Financial Accountability:",
@@
 
-selectInput("rc_funding",
+selectInput("org4_funding",
             label = "Select Funding Source:",
@@
 
-selectInput("rc_gov_relat",
+selectInput("org4_host_gov",
             label = "Select Relationship With Host Government",

### 2020-09-17 analysis/05_market_simulator.Rmd
testing matrix multiplication to find issue with market shres not lining up with excel sheet. Also made capitalization consistent in inputs

--- 2020-09-14 analysis/05_market_simulator.Rmd
@@
                         # Trust in Political Institute
-                        "Very little trust in polticial institutions",
-                        "Little trust in polticial institutions",
-                        "Nuetral trust in polticial institutions",
-                        "Some trust in polticial institutions",
-                        "A lot of trust in polticial institutions",
-                        "Complete trust in polticial institutions",
+                        "Very little trust in political institutions",
+                        "Little trust in political institutions",
+                        "Nuetral trust in political institutions",
+                        "Some trust in political institutions",
+                        "A lot of trust in political institutions",
+                        "Complete trust in political institutions",
                         # Should Others be Charitable
@@
                         # Donation Frequency
-                        "Donate At least once a month", 
+                        "Donate at least once a month", 
                         # Donation Amount
@@
                         "Inactive consumer member",
-                        "Active sonsumer member",
+                        "Active consumer member",
                         #Other Organization Membership
@@
 
-# beta_persona_test <- as.data.frame(matrix(rep(0), nrow = 38))
-# 
-# beta_persona_test$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
-# 
-# 
-# 
-# # Persona Reactive Element
-# 
-# beta_persona_test$p1 <- 1
-# 
-# beta_persona_test$p2 <- 2
-# 
-# beta_persona_test$p3 <- 3
-#         
-# persona1 <- persona_data[,2]
-# 
-# p_beta1 <- as.matrix(public_political_social_charity_demo) %*%   
-#   
-#   as.matrix(persona1) %*% beta_persona_test[,3]
+test_beta <- as.data.frame(matrix(rep(0), nrow = 12))
+
+test_beta$levels = c("Persona 1", "Persona 2", "Persona 3", "input1", "input2", "input3", "input4", "input5", "input6", "input7", "input8", "input9")
+
+# Persona Reactive Element
+
+test_beta$p1 <- 0
+test_beta$p1[1] <- 1
+
+test_beta$p2 <- 0
+test_beta$p2[2] <- 1
+
+test_beta$p3 <- 0
+test_beta$p3[3] <- 1
+
+test1 <- test_beta[,3]
 
@@
 textInput("p1_id",
-          label = "Persona Name",
+          label = "Persona name",
           value = "Persona 1",
-          placeholder = "Enter Persona Name")
+          placeholder = "Enter persona name",
+          width = "450px")
 
@@
          label = "Follow government & public affairs:",
-         choices = c("Not Often",
+         choices = c("Not often",
                      "Often"),
-         selected = "Often")
+         selected = "Often",
+         width = "450px")
 
@@
          label = "People should be more charitable:",
-         choices = c("Strongly Disagree",
+         choices = c("Strongly disagree",
                      "Disagree",
@@
                      "Strongly agree"),
-         selected = "Strongly agree")
+         selected = "Strongly agree",
+         width = "450px")
 
@@
                      'Other (Religion)'),
-         selected = 'Protestant')
+         selected = 'Protestant',
+         width = "450px")
 
 selectInput("p1_charity_importance",
-          label = "Charity Importance:",
+          label = "Charity importance:",
           choices = c("Not at all important",
@@
 selectInput("p1_trust_in_charity",
-            label = "Charity Trust:",
+            label = "Charity trust:",
             choices = c("No trust at all in charities",
@@
 selectInput("p1_donation_frequency",
-         label = "Donation Frequency:",
+         label = "Donation frequency:",
          choices = c('Donate more than once a month, less than once a year',
                      'Donate at least once a month'),
-         selected = "Donate at least once a month")
+         selected = "Donate at least once a month",
+         width = "450px")
 
 selectInput("p1_donation_amount",
-         label = "Donation Amount:",
+         label = "Donation amount:",
          choices = c("$1-$49",
@@
 selectInput("p1_volunteer_12",
-         label = "Volunteered in last 12 Months:",
+         label = "Volunteered in last 12 months:",
          choices = c("Haven't volunteered", "Have volunteered"),
-         selected = "Have volunteered")
+         selected = "Have volunteered",
+         width = "450px")
 
@@
 selectInput("p1_volunteer_frequency",
-         label = "Volunteer Frequency:",
+         label = "Volunteer frequency:",
          choices = c("Haven't volunteered in past 12 months",
@@
 selectInput("p1_personal_activism",
-         label = "Personal Activism:",
+         label = "Personal activism:",
          choices = c('Not personally involved ',
                      'Personally involved'),
-         selected = "Personally involved")
+         selected = "Personally involved",
+         width = "450px")
 
@@
 selectInput("p1_family_activism",
-         label = "Family Activism:",
+         label = "Family activism:",
          choices = c('Family not involved',
                      'Family involved'),
-         selected = "Family involved")
+         selected = "Family involved",
+         width = "450px")
 
@@
 selectInput("p1_religious_member",
-         label = "Church Membership:",
+         label = "Church membership:",
          choices = c("Don't belong to church membership",
@@
 selectInput("p1_sport_member",
-         label = "Sport or Recreational Membership:",
+         label = "Sport or recreational membership:",
          choices = c("Don't belong to sports membership",
@@
                      'Active sports member'),
-         selected = "Don't belong to sports membership")
+         selected = "Don't belong to sports membership",
+         width = "450px")
 #Fix
 selectInput("p1_art_member",
-         label = "Art, Music, or Educational Membership:",
+         label = "Art, music, or educational membership:",
          choices = c("Don't belong to educational membership",
@@
                      'Active educational member'),
-         selected = "Don't belong to educational membership")
+         selected = "Don't belong to educational membership",
+         width = "450px")
 #Fix
 selectInput("p1_labor_member",
-         label = "Labor Union Membership:",
+         label = "Labor union membership:",
          choices = c("Don't belong to union",
@@
 selectInput("p1_political_member",
-         label = "Political Party Membership:",
+         label = "Political party membership:",
          choices = c("Don't belong to party",
@@
                      'Active party member'),
-         selected = "Active party member")
+         selected = "Active party member",
+         width = "450px")
 # Fix
 selectInput("p1_environmental_member",
-         label = "Environmental Org. Membership:",
+         label = "Environmental organization membership:",
          choices = c("Don't belong to environmental organization",
@@
                      'Active environmental member'),
-         selected = "Don't belong to environmental organization")
+         selected = "Don't belong to environmental organization",
+         width = "450px")
 # Fix
 selectInput("p1_professional_member",
-         label = "Professional Membership:",
+         label = "Professional membership:",
          choices = c("Don't belong to professional membership",
@@
                      'Active professional member'),
-         selected = "Don't belong to professional membership")
+         selected = "Don't belong to professional membership",
+         width = "450px")
 # Fix
 selectInput("p1_humanitarian_member",
-         label = "Humanitarian Org. Membership:",
+         label = "Humanitarian organization membership:",
          choices = c("Don't belong to humanitarian organization",
@@
 selectInput("p1_consumer_member",
-         label = "Consumer Org. Membership:",
+         label = "Consumer organization membership:",
          choices = c("Don't belong to consumer organization",
@@
                      'Active consumer member'),
-         selected = "Don't belong to consumer organization")
+         selected = "Don't belong to consumer organization",
+         width = "450px")
 # Fix
 selectInput("p1_other_member",
-         label = "Other Org. Membership:",
+         label = "Other organization membership:",
          choices = c("Don't belong to other organization",
@@
                      "Other (Gender)"),
-         selected = "Male")
+         selected = "Male",
+         width = "450px")
 
 selectInput("p1_marital_status",
-         label = "Marital Status:",
+         label = "Marital status:",
          choices = c("Married",
@@
 textInput("p2_id",
-          label = "Persona Name",
+          label = "Persona name",
           value = "Persona 2",
-          placeholder = "Enter Persona Name")
+          placeholder = "Enter persona name",
+          width = "450px")
 
@@
          label = "Follow government & public affairs:",
-         choices = c("Not Often",
+         choices = c("Not often",
                      "Often"),
-         selected = "Often")
-
-#Fix
+         selected = "Often",
+         width = "450px")
+
 selectInput("p2_travel_developing",
@@
                      "Extremely conservative"),
-         selected = "Somewhat liberal")
-
-#Fix
+         selected = "Somewhat liberal",
+         width = "450px")
+
 selectInput("p2_institution_trust",
@@
                      "Strongly agree"),
-         selected = "Strongly agree")
-
-# Fix
+         selected = "Strongly agree",
+         width = "450px")
+
 selectInput("p2_worship_attendance",
@@
                      'Other (Religion)'),
-         selected = 'Protestant')
+         selected = 'Protestant',
+         width = "450px")
 
 selectInput("p2_charity_importance",
-          label = "Charity Importance:",
+          label = "Charity importance:",
           choices = c("Not at all important",
@@
                       "Essential"),
-          selected = "Somewhat unimportant")
-
-#Fix
+          selected = "Somewhat unimportant",
+          width = "450px")
+
 selectInput("p2_trust_in_charity",
-            label = "Charity Trust:",
+            label = "Charity trust:",
             choices = c("No trust at all in charities",
@@
                         "Complete trust in charities"),
-            selected = "Complete trust in charities")
-
-#Fix
+            selected = "Complete trust in charities",
+            width = "450px")
+
 selectInput("p2_donation_frequency",
-         label = "Donation Frequency:",
+         label = "Donation frequency:",
          choices = c('Donate more than once a month, less than once a year',
                      'Donate at least once a month'),
-         selected = "Donate at least once a month")
+         selected = "Donate at least once a month",
+         width = "450px")
 
 selectInput("p2_donation_amount",
-         label = "Donation Amount:",
+         label = "Donation amount:",
          choices = c("$1-$49",
@@
                      '$10,000+'),
-         selected = "$100-$499")
-
-#Fix
+         selected = "$100-$499",
+         width = "450px")
+
 selectInput("p2_volunteer_12",
-         label = "Volunteered in last 12 Months:",
+         label = "Volunteered in last 12 months:",
          choices = c("Haven't volunteered", "Have volunteered"),
-         selected = "Have volunteered")
-
-#Fix
+         selected = "Have volunteered",
+         width = "450px")
+
 selectInput("p2_volunteer_frequency",
-         label = "Volunteer Frequency:",
+         label = "Volunteer frequency:",
          choices = c("Haven't volunteered in past 12 months",
@@
                      "Volunteer at least once a month"),
-         selected = "Volunteer at least once a month")
-
-# fix
+         selected = "Volunteer at least once a month",
+         width = "450px")
+
 selectInput("p2_personal_activism",
-         label = "Personal Activism:",
+         label = "Personal activism:",
          choices = c('Not personally involved ',
                      'Personally involved'),
-         selected = "Personally involved")
-
-#Fix
+         selected = "Personally involved",
+         width = "450px")
+
 selectInput("p2_family_activism",
-         label = "Family Activism:",
+         label = "Family activism:",
          choices = c('Family not involved',
                      'Family involved'),
-         selected = "Family involved")
-
-#Fix
+         selected = "Family involved",
+         width = "450px")
+
 selectInput("p2_religious_member",
-         label = "Church Membership:",
+         label = "Church membership:",
          choices = c("Don't belong to church membership",
@@
                      'Active church member'),
-         selected = "Don't belong to church membership")
-
-#Fix
+         selected = "Don't belong to church membership",
+         width = "450px")
+
 selectInput("p2_sport_member",
-         label = "Sport or Recreational Membership:",
+         label = "Sport or recreational membership:",
          choices = c("Don't belong to sports membership",
@@
                      'Active sports member'),
-         selected = "Don't belong to sports membership")
-#Fix
+         selected = "Don't belong to sports membership",
+         width = "450px")
+
 selectInput("p2_art_member",
-         label = "Art, Music, or Educational Membership:",
+         label = "Art, music, or educational membership:",
          choices = c("Don't belong to educational membership",
@@
                      'Active educational member'),
-         selected = "Don't belong to educational membership")
-#Fix
+         selected = "Don't belong to educational membership",
+         width = "450px")
+
 selectInput("p2_labor_member",
-         label = "Labor Union Membership:",
+         label = "Labor union membership:",
          choices = c("Don't belong to union",
@@
                      'Active union member'),
-         selected = "Don't belong to union")
-
-#Fix
+         selected = "Don't belong to union",
+         width = "450px")
+
 selectInput("p2_political_member",
-         label = "Political Party Membership:",
+         label = "Political party membership:",
          choices = c("Don't belong to party",
@@
                      'Active party member'),
-         selected = "Active party member")
-# Fix
+         selected = "Active party member",
+         width = "450px")
+
 selectInput("p2_environmental_member",
-         label = "Environmental Org. Membership:",
+         label = "Environmental organization membership:",
          choices = c("Don't belong to environmental organization",
@@
                      'Active environmental member'),
-         selected = "Don't belong to environmental organization")
-# Fix
+         selected = "Don't belong to environmental organization",
+         width = "450px")
+
 selectInput("p2_professional_member",
-         label = "Professional Membership:",
+         label = "Professional membership:",
          choices = c("Don't belong to professional membership",
@@
                      'Active professional member'),
-         selected = "Don't belong to professional membership")
-# Fix
+         selected = "Don't belong to professional membership",
+         width = "450px")
+
 selectInput("p2_humanitarian_member",
-         label = "Humanitarian Org. Membership:",
+         label = "Humanitarian organization membership:",
          choices = c("Don't belong to humanitarian organization",
@@
                      'Active humanitarian member'),
-         selected = "Active humanitarian member")
-
-# Fix
+         selected = "Active humanitarian member",
+         width = "450px")
+
 selectInput("p2_consumer_member",
-         label = "Consumer Org. Membership:",
+         label = "Consumer organization membership:",
          choices = c("Don't belong to consumer organization",
@@
                      'Active consumer member'),
-         selected = "Don't belong to consumer organization")
-# Fix
+         selected = "Don't belong to consumer organization",
+         width = "450px")
+
 selectInput("p2_other_member",
-         label = "Other Org. Membership:",
+         label = "Other organization membership:",
          choices = c("Don't belong to other organization",
@@
                      "Other (Gender)"),
-         selected = "Male")
+         selected = "Male",
+         width = "450px")
 
 selectInput("p2_marital_status",
-         label = "Marital Status:",
+         label = "Marital status:",
          choices = c("Married",
@@
                      "Doctorate"),
-         selected = "Some college")
+         selected = "Some college",
+         width = "450px")
 
@@
          multiple = TRUE,
-         selected = "American Indian or Alaska Native")
+         selected = 'American Indian or Alaska Native',
+         width = "450px")
 
@@
 textInput("p3_id",
-          label = "Persona Name",
-          value = "Persona 1",
-          placeholder = "Enter Persona Name")
+          label = "Persona name",
+          value = "Persona 3",
+          placeholder = "Enter persona name",
+          width = "450px")
 
@@
          label = "Follow government & public affairs:",
-         choices = c("Not Often",
+         choices = c("Not often",
                      "Often"),
-         selected = "Often")
-
-#Fix
+         selected = "Often",
+         width = "450px")
+
 selectInput("p3_travel_developing",
@@
                      "Extremely conservative"),
-         selected = "Somewhat liberal")
-
-#Fix
+         selected = "Somewhat liberal",
+         width = "450px")
+
 selectInput("p3_institution_trust",
@@
                      "Strongly agree"),
-         selected = "Strongly agree")
-
-# Fix
+         selected = "Strongly agree",
+         width = "450px")
+
 selectInput("p3_worship_attendance",
@@
                      'Other (Religion)'),
-         selected = 'Protestant')
+         selected = 'Protestant',
+         width = "450px")
 
 selectInput("p3_charity_importance",
-          label = "Charity Importance:",
+          label = "Charity importance:",
           choices = c("Not at all important",
@@
                       "Essential"),
-          selected = "Somewhat unimportant")
-
-#Fix
+          selected = "Somewhat unimportant",
+          width = "450px")
+
 selectInput("p3_trust_in_charity",
-            label = "Charity Trust:",
+            label = "Charity trust:",
             choices = c("No trust at all in charities",
@@
                         "Complete trust in charities"),
-            selected = "Complete trust in charities")
-
-#Fix
+            selected = "Complete trust in charities",
+            width = "450px")
+
 selectInput("p3_donation_frequency",
-         label = "Donation Frequency:",
+         label = "Donation frequency:",
          choices = c('Donate more than once a month, less than once a year',
                      'Donate at least once a month'),
-         selected = "Donate at least once a month")
+         selected = "Donate at least once a month",
+         width = "450px")
 
 selectInput("p3_donation_amount",
-         label = "Donation Amount:",
+         label = "Donation amount:",
          choices = c("$1-$49",
@@
                      '$10,000+'),
-         selected = "$100-$499")
-
-#Fix
+         selected = "$100-$499",
+         width = "450px")
+
 selectInput("p3_volunteer_12",
-         label = "Volunteered in last 12 Months:",
+         label = "Volunteered in last 12 months:",
          choices = c("Haven't volunteered", "Have volunteered"),
-         selected = "Have volunteered")
-
-#Fix
+         selected = "Have volunteered",
+         width = "450px")
+
 selectInput("p3_volunteer_frequency",
-         label = "Volunteer Frequency:",
+         label = "Volunteer frequency:",
          choices = c("Haven't volunteered in past 12 months",
@@
                      "Volunteer at least once a month"),
-         selected = "Volunteer at least once a month")
-
-# fix
+         selected = "Volunteer at least once a month",
+         width = "450px")
+
 selectInput("p3_personal_activism",
-         label = "Personal Activism:",
+         label = "Personal activism:",
          choices = c('Not personally involved ',
                      'Personally involved'),
-         selected = "Personally involved")
-
-#Fix
+         selected = "Personally involved",
+         width = "450px")
+
 selectInput("p3_family_activism",
-         label = "Family Activism:",
+         label = "Family activism:",
          choices = c('Family not involved',
                      'Family involved'),
-         selected = "Family involved")
-
-#Fix
+         selected = "Family involved",
+         width = "450px")
+
 selectInput("p3_religious_member",
-         label = "Church Membership:",
+         label = "Church membership:",
          choices = c("Don't belong to church membership",
@@
                      'Active church member'),
-         selected = "Don't belong to church membership")
-
-#Fix
+         selected = "Don't belong to church membership",
+         width = "450px")
+
 selectInput("p3_sport_member",
-         label = "Sport or Recreational Membership:",
+         label = "Sport or recreational membership:",
          choices = c("Don't belong to sports membership",
@@
                      'Active sports member'),
-         selected = "Don't belong to sports membership")
-#Fix
+         selected = "Don't belong to sports membership",
+         width = "450px")
+
 selectInput("p3_art_member",
-         label = "Art, Music, or Educational Membership:",
+         label = "Art, music, or educational membership:",
          choices = c("Don't belong to educational membership",
@@
                      'Active educational member'),
-         selected = "Don't belong to educational membership")
-#Fix
+         selected = "Don't belong to educational membership",
+         width = "450px")
+
 selectInput("p3_labor_member",
-         label = "Labor Union Membership:",
+         label = "Labor union membership:",
          choices = c("Don't belong to union",
@@
                      'Active union member'),
-         selected = "Don't belong to union")
-
-#Fix
+         selected = "Don't belong to union",
+         width = "450px")
+
 selectInput("p3_political_member",
-         label = "Political Party Membership:",
+         label = "Political party membership:",
          choices = c("Don't belong to party",
@@
                      'Active party member'),
-         selected = "Active party member")
-# Fix
+         selected = "Active party member",
+         width = "450px")
+
 selectInput("p3_environmental_member",
-         label = "Environmental Org. Membership:",
+         label = "Environmental organization membership:",
          choices = c("Don't belong to environmental organization",
@@
                      'Active environmental member'),
-         selected = "Don't belong to environmental organization")
-# Fix
+         selected = "Don't belong to environmental organization",
+         width = "450px")
+
 selectInput("p3_professional_member",
-         label = "Professional Membership:",
+         label = "Professional membership:",
          choices = c("Don't belong to professional membership",
@@
                      'Active professional member'),
-         selected = "Don't belong to professional membership")
-# Fix
+         selected = "Don't belong to professional membership",
+         width = "450px")
+
 selectInput("p3_humanitarian_member",
-         label = "Humanitarian Org. Membership:",
+         label = "Humanitarian organization membership:",
          choices = c("Don't belong to humanitarian organization",
@@
                      'Active humanitarian member'),
-         selected = "Active humanitarian member")
-
-# Fix
+         selected = "Active humanitarian member",
+         width = "450px")
+
 selectInput("p3_consumer_member",
-         label = "Consumer Org. Membership:",
+         label = "Consumer organization membership:",
          choices = c("Don't belong to consumer organization",
@@
                      'Active consumer member'),
-         selected = "Don't belong to consumer organization")
-# Fix
+         selected = "Don't belong to consumer organization",
+         width = "450px")
+
 selectInput("p3_other_member",
-         label = "Other Org. Membership:",
+         label = "Other organization membership:",
          choices = c("Don't belong to other organization",
@@
                      "Other (Gender)"),
-         selected = "Female")
+         selected = "Female",
+         width = "450px")
 
 selectInput("p3_marital_status",
-         label = "Marital Status:",
+         label = "Marital status:",
          choices = c("Married",
@@
                      "Doctorate"),
-         selected = "Graduate or professional degree")
+         selected = "Graduate or professional degree",
+         width = "450px")
 
@@
          multiple = TRUE,
-         selected = c("Black or African American", "American Indian or Alaska Native"))
+         selected = c("Black or African American",'American Indian or Alaska Native'),
+         width = "450px")
 
@@
 textInput("ai_id",
-          label = "Organization Name",
+          label = "Organization name",
           value = "Organization 1",
-          placeholder = "Enter Organization Name")
+          placeholder = "Enter organization name",
+          width = "450px")
 
 selectInput("org1_id",
-            label = "Select Organization:",
+            label = "Organization:",
             choice = c("Amnesty International",
@@
                        "Red Cross"),
-            selected = "Red Cross")
+            selected = "Red Cross",
+            width = "450px")
 
 selectInput("ai_issue", 
-            label = "Select Issue Area:",
+            label = "Issue area:",
             choices = c("Emergency response",
@@
                         "Refugee relief"),
-            selected = "Emergency response")
+            selected = "Emergency response",
+            width = "450px")
 
 selectInput("ai_fin_trans",
-            label = "Select Financial Transparency:",
+            label = "Financial transparency:",
             choices = c("Doesn’t engage in transparency",
                         "Engages in transparency"),
-            selected = "Engages in transparency")
+            selected = "Engages in transparency",
+            width = "450px")
 
 selectInput("ai_account",
-            label = "Select Financial Accountability:",
+            label = "Financial accountability:",
             choices = c("Doesn’t engage in accountability",
                         "Engages in accountability"),
-            selected = "Engages in accountability")
+            selected = "Engages in accountability",
+            width = "450px")
 
 selectInput("ai_funding",
-            label = "Select Funding Source:",
+            label = "Funding source:",
             choices = c("Many small private donations",
                         "Handful of wealthy private donors",
-                        "Government grants"))
+                        "Government grants"),
+            selected = "Many small private donations",
+            width = "450px")
 
 selectInput("ai_gov_relat",
-            label = "Select Relationship With Host Government",
+            label = "Relationship with host government",
             choices = c("Friendly relationship with government",
                         "Criticized by government", 
-                        "Under government crackdown"))
+                        "Under government crackdown"),
+            selected = "Friendly relationship with government",
+            width = "450px")
 
@@
 textInput("gp_id",
-          label = "Organization Name",
+          label = "Organization name",
           value = "Organization 2",
-          placeholder = "Enter Organiation Name")
+          placeholder = "Enter organization name",
+          width = "450px")
 
 selectInput("org2_id",
-            label = "Select Organization:",
+            label = "Organization:",
             choice = c("Amnesty International",
@@
                        "Red Cross"),
-            selected = "Red Cross")
+            selected = "Red Cross",
+            width = "450px")
 
 selectInput("gp_issue", 
-            label = "Select Issue Area:",
+            label = "Issue area:",
             choices = c("Emergency response",
@@
                         "Refugee relief"),
-            selected = "Environment")
+            selected = "Environment",
+            width = "450px")
 
 selectInput("gp_fin_trans",
-            label = "Select Financial Transparency:",
+            label = "Financial transparency:",
             choices = c("Doesn’t engage in transparency",
                         "Engages in transparency"),
-            selected = "Engages in transparency")
+            selected = "Engages in transparency",
+            width = "450px")
 
 selectInput("gp_account",
-            label = "Select Financial Accountability:",
+            label = "Financial accountability:",
             choices = c("Doesn’t engage in accountability",
                         "Engages in accountability"),
-            selected = "Engages in accountability")
+            selected = "Engages in accountability",
+            width = "450px")
 
 selectInput("gp_funding",
-            label = "Select Funding Source:",
+            label = "Funding source:",
             choices = c("Many small private donations",
                         "Handful of wealthy private donors",
-                        "Government grants"))
+                        "Government grants"),
+            selected = "Many small private donations",
+            width = "450px")
 
 selectInput("gp_gov_relat",
-            label = "Select Relationship With Host Government",
+            label = "Relationship with host government",
             choices = c("Friendly relationship with government",
                         "Criticized by government", 
-                        "Under government crackdown"))
+                        "Under government crackdown"),
+            selected = "Friendly relationship with government",
+            width = "450px")
+
 ```
@@
 textInput("ox_id",
-          label = "Organization Name",
+          label = "Organization name",
           value = "Organization 3",
-          placeholder = "Enter Organiation Name")
+          placeholder = "Enter organization name",
+          width = "450px")
 
 selectInput("org3_id",
-            label = "Select Organization:",
+            label = "Organization:",
             choice = c("Amnesty International",
@@
                        "Red Cross"),
-            selected = "Red Cross")
+            selected = "Red Cross",
+            width = "450px")
 
 selectInput("ox_issue", 
-            label = "Select Issue Area:",
+            label = "Issue area:",
             choices = c("Emergency response",
@@
                         "Refugee relief"),
-            selected = "Human rights")
+            selected = "Human rights",
+            width = "450px")
 
 selectInput("ox_fin_trans",
-            label = "Select Financial Transparency:",
+            label = "Financial transparency:",
             choices = c("Doesn’t engage in transparency",
                         "Engages in transparency"),
-            selected = "Engages in transparency")
+            selected = "Engages in transparency",
+            width = "450px")
 
 selectInput("ox_account",
-            label = "Select Financial Accountability:",
+            label = "Financial accountability:",
             choices = c("Doesn’t engage in accountability",
                         "Engages in accountability"),
-            selected = "Engages in accountability")
+            selected = "Engages in accountability",
+            width = "450px")
 
 selectInput("ox_funding",
-            label = "Select Funding Source:",
+            label = "Funding source:",
             choices = c("Many small private donations",
                         "Handful of wealthy private donors",
-                        "Government grants"))
+                        "Government grants"),
+            selected = "Many small private donations",
+            width = "450px")
 
 selectInput("ox_gov_relat",
-            label = "Select Relationship With Host Government",
+            label = "Relationship with host government",
             choices = c("Friendly relationship with government",
                         "Criticized by government", 
-                        "Under government crackdown"))
+                        "Under government crackdown"),
+            selected = "Friendly relationship with government",
+            width = "450px")
+
 ```
@@
 textInput("rc_id",
-          label = "Organization Name",
+          label = "Organization name",
           value = "Organization 4",
-          placeholder = "Enter Organiation Name")
+          placeholder = "Enter organization name",
+          width = "450px")
 
 selectInput("org4_id",
-            label = "Select Organization:",
+            label = "Organization:",
             choice = c("Amnesty International",
@@
                        "Red Cross"),
-            selected = "Red Cross")
+            selected = "Red Cross",
+            width = "450px")
 
 selectInput("rc_issue", 
-            label = "Select Issue Area:",
+            label = "Issue area:",
             choices = c("Emergency response",
@@
                         "Refugee relief"),
-            selected = "Refugee relief")
+            selected = "Refugee relief",
+            width = "450px")
 
 selectInput("rc_fin_trans",
-            label = "Select Financial Transparency:",
+            label = "Financial transparency:",
             choices = c("Doesn’t engage in transparency",
                         "Engages in transparency"),
-            selected = "Engages in transparency")
+            selected = "Engages in transparency",
+            width = "450px")
 
 selectInput("rc_account",
-            label = "Select Financial Accountability:",
+            label = "Financial accountability:",
             choices = c("Doesn’t engage in accountability",
                         "Engages in accountability"),
-            selected = "Engages in accountability")
+            selected = "Engages in accountability",
+            width = "450px")
 
 selectInput("rc_funding",
-            label = "Select Funding Source:",
+            label = "Funding source:",
             choices = c("Many small private donations",
                         "Handful of wealthy private donors",
-                        "Government grants"))
+                        "Government grants"),
+            selected = "Many small private donations",
+            width = "450px")
 
 selectInput("rc_gov_relat",
-            label = "Select Relationship With Host Government",
+            label = "Relationship with host government",
             choices = c("Friendly relationship with government",
                         "Criticized by government", 
-                        "Under government crackdown"))
+                        "Under government crackdown"),
+            selected = "Friendly relationship with government",
+            width = "450px")
+
 ```

### 2020-09-18 analysis/05_market_simulator.Rmd
Finished updating labeling

--- 2020-09-16 analysis/05_market_simulator.Rmd
@@
 # Gammas of the "everything" model
-public_political_social_charity_demo <- read_rds(
+gammas <- read_rds(
   here::here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')
@@
 ```{r persona-reactive-table}
-# Placeholder for persona gammas
-per_table <- as.data.frame(matrix(rep(0), nrow = 111))
+# Placeholder for persona reactive table
+per_table <- as.data.frame(matrix(rep(0), nrow = nrow(persona_data)))
 
@@
 })
-
 ```
@@
 
-### Calculating the Persona gammas ###
-
-# Persona 1
-persona1 <- persona_data[,2]
-
-# matrix multiplication between persona data and gammas
-gamma1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona1)
-
-# Persona 2
-persona2 <- persona_data[,3]
-
-# matrix multiplication between persona data and gammas
-gamma2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona2)
-
-# Persona 3
-persona3 <- persona_data[,4]
-
-# matrix multiplication between persona data and gammas
-gamma3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona3)
-
-# Organization
-org1 <- organization_data[,2]
-
-org2 <- organization_data[,3]
-
-org3 <- organization_data[,4]
-
-org4 <- organization_data[,5]
-
-# Expected utility matrix multiplication between computed persona gammas and org data for persona 1
-org1_exp_util1 <- exp(t(org1) %*% as.matrix(gamma1))
-org2_exp_util1 <- exp(t(org2) %*% as.matrix(gamma1))
-org3_exp_util1 <- exp(t(org3) %*% as.matrix(gamma1))
-org4_exp_util1 <- exp(t(org4) %*% as.matrix(gamma1))
-
-# Market Share computation from expected utilities between organization
-org1_rate1 <- 100 * org1_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
-org2_rate1 <- 100 * org2_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
-org3_rate1 <- 100 * org3_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
-org4_rate1 <- 100 * org4_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
+# ### Calculating the Persona gammas ###
+# 
+# # Persona 1
+# persona1 <- persona_data[,2]
+# 
+# # matrix multiplication between persona data and gammas
+# gamma1 <- as.matrix(gammas) %*% as.matrix(persona1)
+# 
+# 
+# # Persona 2
+# persona2 <- persona_data[,3]
+# 
+# # matrix multiplication between persona data and gammas
+# gamma2 <- as.matrix(gammas) %*% as.matrix(persona2)
+# 
+# 
+# # Persona 3
+# persona3 <- persona_data[,4]
+# 
+# # matrix multiplication between persona data and gammas
+# gamma3 <- as.matrix(gammas) %*% as.matrix(persona3)
+# 
+# # Organization
+# org1 <- organization_data[,2]
+# 
+# org2 <- organization_data[,3]
+# 
+# org3 <- organization_data[,4]
+# 
+# org4 <- organization_data[,5]
+# 
+# # Expected utility matrix multiplication between computed persona gammas and org data for persona 1
+# per1_org1_exp <- exp(t(org1) %*% as.matrix(gamma1))
+# per1_org2_exp <- exp(t(org2) %*% as.matrix(gamma1))
+# per1_org3_exp <- exp(t(org3) %*% as.matrix(gamma1))
+# per1_org4_exp <- exp(t(org4) %*% as.matrix(gamma1))
+# 
+# # Market Share computation from expected utilities between organization
+# per1_org1_share <- 100 * per1_org1_exp/sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)
+# per1_org2_share <- 100 * per1_org2_exp/sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)
+# per1_org3_share <- 100 * per1_org3_exp/sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)
+# per1_org4_share <- 100 * per1_org4_exp/sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)
 
@@
 
-<!-- Main page Chart with All Personas -->
 Market Share
@@
 
-```{r global plot}
+```{r compute-and-plot}
+# Compute and render the market share plot
 renderPlotly({
@@
 
+  # Persona 1 predicted betas
+  per1_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,3])
+
+  # Persona 1 expected utilities
+  per1_org1_exp <- exp(t(org_choice[,3]) %*% as.matrix(per1_betas))
+  per1_org2_exp <- exp(t(org_choice[,4]) %*% as.matrix(per1_betas))
+  per1_org3_exp <- exp(t(org_choice[,5]) %*% as.matrix(per1_betas))
+  per1_org4_exp <- exp(t(org_choice[,6]) %*% as.matrix(per1_betas))
+
+  # Persona 1 market shares
+  per1_share_denom <- sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)
+  per1_org1_share <- 100 * (per1_org1_exp / per1_share_denom)
+  per1_org2_share <- 100 * (per1_org2_exp / per1_share_denom)
+  per1_org3_share <- 100 * (per1_org3_exp / per1_share_denom)
+  per1_org4_share <- 100 * (per1_org4_exp / per1_share_denom)
+
+  # Persona 2 predicted betas
+  per2_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,4])
+
+  # Persona 2 expected utilities
+  per2_org1_exp <- exp(t(org_choice[,3]) %*% as.matrix(per2_betas))
+  per2_org2_exp <- exp(t(org_choice[,4]) %*% as.matrix(per2_betas))
+  per2_org3_exp <- exp(t(org_choice[,5]) %*% as.matrix(per2_betas))
+  per2_org3_exp <- exp(t(org_choice[,6]) %*% as.matrix(per2_betas))
+
+  # Persona 2 market shares
+  per2_share_denom <- sum(per2_org1_exp, per2_org2_exp, per2_org3_exp, per2_org3_exp)
+  per2_org1_share <- 100 * (per2_org1_exp / per2_share_denom)
+  per2_org2_share <- 100 * (per2_org2_exp / per2_share_denom)
+  per2_org3_share <- 100 * (per2_org3_exp / per2_share_denom)
+  per2_org4_share <- 100 * (per2_org4_exp / per2_share_denom)
+
+  # Persona 3 predicted betas
+  per3_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,5])
+
+  # Persona 3 expected utilities
+  per3_org1_exp <- exp(t(org_choice[,3]) %*% as.matrix(per3_betas))
+  per3_org2_exp <- exp(t(org_choice[,4]) %*% as.matrix(per3_betas))
+  per3_org3_exp <- exp(t(org_choice[,5]) %*% as.matrix(per3_betas))
+  per3_org4_exp <- exp(t(org_choice[,6]) %*% as.matrix(per3_betas))
+
+  # Persona 3 market shares
+  per3_share_denom <- sum(per3_org1_exp, per3_org2_exp, per3_org3_exp, per3_org4_exp)
+  per3_org1_share <- 100 * (per3_org1_exp / per3_share_denom)
+  per3_org2_share <- 100 * (per3_org2_exp / per3_share_denom)
+  per3_org3_share <- 100 * (per3_org3_exp / per3_share_denom)
+  per3_org4_share <- 100 * (per3_org4_exp / per3_share_denom)
+
+  # Data for plotly
+  data <- c(
     # Persona 1
-  p_gamma1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
-
-  # Expected Utility
-  org1_exp_util1 <- exp(t(org_choice[, 3]) %*% as.matrix(p_gamma1))
-  org2_exp_util1 <- exp(t(org_choice[, 4]) %*% as.matrix(p_gamma1))
-  org3_exp_util1 <- exp(t(org_choice[, 5]) %*% as.matrix(p_gamma1))
-  org4_exp_util1 <- exp(t(org_choice[, 6]) %*% as.matrix(p_gamma1))
-
-  # Market Share
-  org1_rate1 <- 100 * org1_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
-  org2_rate1 <- 100 * org2_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
-  org3_rate1 <- 100 * org3_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
-  org4_rate1 <- 100 * org4_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
-
+    per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp, 
+    per1_org1_share, per1_org2_share, per1_org3_share, per1_org4_share, 
     # Persona 2
-  p_gamma2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
-
-  # Expected Utility
-  org1_exp_util2 <- exp(t(org_choice[, 3]) %*% as.matrix(p_gamma2))
-  org2_exp_util2 <- exp(t(org_choice[, 4]) %*% as.matrix(p_gamma2))
-  org3_exp_util2 <- exp(t(org_choice[, 5]) %*% as.matrix(p_gamma2))
-  org4_exp_util2 <- exp(t(org_choice[, 6]) %*% as.matrix(p_gamma2))
-
-  # Market Share
-  org1_rate2 <- 100 * org1_exp_util2/sum(org1_exp_util2, org2_exp_util2, org3_exp_util2, org4_exp_util2)
-  org2_rate2 <- 100 * org2_exp_util2/sum(org1_exp_util2, org2_exp_util2, org3_exp_util2, org4_exp_util2)
-  org3_rate2 <- 100 * org3_exp_util2/sum(org1_exp_util2, org2_exp_util2, org3_exp_util2, org4_exp_util2)
-  org4_rate2 <- 100 * org4_exp_util2/sum(org1_exp_util2, org2_exp_util2, org3_exp_util2, org4_exp_util2)
-
+    per2_org1_exp, per2_org2_exp, per2_org3_exp, per2_org3_exp, 
+    per2_org1_share, per2_org2_share, per2_org3_share, per2_org4_share,
     # Persona 3
-  p_gamma3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])
-
-  # Expected Utility
-  org1_exp_util3 <- exp(t(org_choice[, 3]) %*% as.matrix(p_gamma3))
-  org2_exp_util3 <- exp(t(org_choice[, 4]) %*% as.matrix(p_gamma3))
-  org3_exp_util3 <- exp(t(org_choice[, 5]) %*% as.matrix(p_gamma3))
-  org4_exp_util3 <- exp(t(org_choice[, 6]) %*% as.matrix(p_gamma3))
-
-  # Market Share
-  org1_rate3 <- 100 * org1_exp_util3/sum(org1_exp_util3, org2_exp_util3, org3_exp_util3, org4_exp_util3)
-  org2_rate3 <- 100 * org2_exp_util3/sum(org1_exp_util3, org2_exp_util3, org3_exp_util3, org4_exp_util3)
-  org3_rate3 <- 100 * org3_exp_util3/sum(org1_exp_util3, org2_exp_util3, org3_exp_util3, org4_exp_util3)
-  org4_rate3 <- 100 * org4_exp_util3/sum(org1_exp_util3, org2_exp_util3, org3_exp_util3, org4_exp_util3)
-
-  # Data for Plotly
-  data <- c(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1, org1_rate1, org2_rate1, org3_rate1, org4_rate1, 
-            org1_exp_util2, org2_exp_util2, org3_exp_util2, org4_exp_util2, org1_rate2, org2_rate2, org3_rate2, org4_rate2,
-            org1_exp_util3, org2_exp_util3, org3_exp_util3, org4_exp_util3, org1_rate3, org2_rate3, org3_rate3, org4_rate3)
-
-  # Empty dataframe
+    per3_org1_exp, per3_org2_exp, per3_org3_exp, per3_org4_exp, 
+    per3_org1_share, per3_org2_share, per3_org3_share, per3_org4_share
+  )
+
+  # Empty organization reactive table
   org_reactive <- as.data.frame(matrix(data, 24, 1))
@@
   org_reactive[,2] <- c(input$org1_id, input$org2_id, input$org3_id, input$org4_id)
-  # Type of value
-  org_reactive[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
+  # Expected utilities and market shares
+  org_reactive[,3] <- c(rep('Expected Utility', 4), rep('Market Share', 4))
   # Persona name inputs
-  org_reactive[,4] <- c(rep(input$per1_id,8), rep(input$per2_id, 8), rep(input$per3_id, 8))
+  org_reactive[,4] <- c(rep(input$per1_id, 8), rep(input$per2_id, 8), rep(input$per3_id, 8))
 
   # Rename columns
-  colnames(org_reactive) <- c('Value', 'Organization', "Type", "Persona")
-
-  ggplotly(org_reactive %>% 
+  colnames(org_reactive) <- c('Value', 'Organization', 'Type', 'Persona')
+
+  ggplotly(
+    org_reactive %>% 
       # Only care about the Market Share right now
@@
       mutate(
-               Organization = factor(Organization, levels = c(input$org1_id, input$org2_id, input$org3_id, input$org4_id), ordered = TRUE),
-               Persona = factor(Persona, levels = c(input$per1_id, input$per2_id, input$per3_id), ordered = TRUE)) %>% 
+        Organization = factor(
+          Organization, 
+          levels = c(input$org1_id, input$org2_id, input$org3_id, input$org4_id), 
+          ordered = TRUE
+        ),
+        Persona = factor(
+          Persona, 
+          levels = c(input$per1_id, input$per2_id, input$per3_id), 
+          ordered = TRUE
+        )
+      ) %>% 
       ggplot(aes(y = Value, x = Organization, fill = Persona)) +
@@
       scale_fill_manual(values = c("#FFC30B", "#28a153", "#c23838")) +
-             theme(legend.position = "right",
+      theme(
+        legend.position = "right",
         panel.background = element_blank(),
-                   panel.grid.major.y = element_line(color = "#D3D3D3"))
+        panel.grid.major.y = element_line(color = "#D3D3D3")
+      )
     )
 })
-
 ```
 
-<!-- Persona and Organizational Tabs -->
-Personas And Organizations {.tabset .tabset-fade}
+Organizations and Personas {.tabset .tabset-fade}
 --------------------------------------------------
 
+### Organization 1
+
+```{r org1-inputs}
+# Naming
+textInput(
+  "org1_id",
+  label = "Organization Name",
+  value = "Organization 1",
+  placeholder = "Enter Organization Name",
+  width = "450px"
+)
+
+# Organization
+selectInput(
+  "org1_id",
+  label = "Select Organization:",
+  choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
+  selected = "Red Cross",
+  width = "450px"
+)
+
+# Issue area
+selectInput(
+  "org1_issue", 
+  label = "Select Issue Area:",
+  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
+  selected = "Emergency response",
+  width = "450px"
+)
+
+# Financial transparency
+selectInput(
+  "org1_fin_trans",
+  label = "Select Financial Transparency:",
+  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
+  selected = "Engages in financial transparency",
+  width = "450px"
+)
+
+# Financial accountability
+selectInput(
+  "org1_fin_account",
+  label = "Select Financial Accountability:",
+  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
+  selected = "Engages in financial accountability",
+  width = "450px"
+)
+
+# Funding sources
+selectInput(
+  "org1_funding",
+  label = "Select Funding Source:",
+  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
+  width = "450px"
+)
+
+# Relationship with host government
+selectInput(
+  "org1_host_gov",
+  label = "Select Relationship With Host Government",
+  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
+  width = "450px"
+)
+```
+
+### Organization 2
+
+```{r org2-inputs}
+# Naming
+textInput(
+  "org2_id",
+  label = "Organization Name",
+  value = "Organization 2",
+  placeholder = "Enter Organization Name",
+  width = "450px"
+)
+
+# Organization
+selectInput(
+  "org2_id",
+  label = "Select Organization:",
+  choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
+  selected = "Red Cross",
+  width = "450px"
+)
+
+# Issue area
+selectInput(
+  "org2_issue", 
+  label = "Select Issue Area:",
+  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
+  selected = "Emergency response",
+  width = "450px"
+)
+
+# Financial transparency
+selectInput(
+  "org2_fin_trans",
+  label = "Select Financial Transparency:",
+  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
+  selected = "Engages in financial transparency",
+  width = "450px"
+)
+
+# Financial accountability
+selectInput(
+  "org2_fin_account",
+  label = "Select Financial Accountability:",
+  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
+  selected = "Engages in financial accountability",
+  width = "450px"
+)
+
+# Funding sources
+selectInput(
+  "org2_funding",
+  label = "Select Funding Source:",
+  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
+  width = "450px"
+)
+
+# Relationship with host government
+selectInput(
+  "org2_host_gov",
+  label = "Select Relationship With Host Government",
+  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
+  width = "450px"
+)
+```
+
+### Organization 3
+
+```{r org3-inputs}
+# Naming
+textInput(
+  "org3_id",
+  label = "Organization Name",
+  value = "Organization 3",
+  placeholder = "Enter Organization Name",
+  width = "450px"
+)
+
+# Organization
+selectInput(
+  "org3_id",
+  label = "Select Organization:",
+  choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
+  selected = "Red Cross",
+  width = "450px"
+)
+
+# Issue area
+selectInput(
+  "org3_issue", 
+  label = "Select Issue Area:",
+  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
+  selected = "Emergency response",
+  width = "450px"
+)
+
+# Financial transparency
+selectInput(
+  "org3_fin_trans",
+  label = "Select Financial Transparency:",
+  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
+  selected = "Engages in financial transparency",
+  width = "450px"
+)
+
+# Financial accountability
+selectInput(
+  "org3_fin_account",
+  label = "Select Financial Accountability:",
+  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
+  selected = "Engages in financial accountability",
+  width = "450px"
+)
+
+# Funding sources
+selectInput(
+  "org3_funding",
+  label = "Select Funding Source:",
+  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
+  width = "450px"
+)
+
+# Relationship with host government
+selectInput(
+  "org3_host_gov",
+  label = "Select Relationship With Host Government",
+  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
+  width = "450px"
+)
+```
+
+### Organization 4
+
+```{r org4-inputs}
+# Naming
+textInput(
+  "org4_id",
+  label = "Organization Name",
+  value = "Organization 4",
+  placeholder = "Enter Organization Name",
+  width = "450px"
+)
+
+# Organization
+selectInput(
+  "org4_id",
+  label = "Select Organization:",
+  choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
+  selected = "Red Cross",
+  width = "450px"
+)
+
+# Issue area
+selectInput(
+  "org4_issue", 
+  label = "Select Issue Area:",
+  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
+  selected = "Emergency response",
+  width = "450px"
+)
+
+# Financial transparency
+selectInput(
+  "org4_fin_trans",
+  label = "Select Financial Transparency:",
+  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
+  selected = "Engages in financial transparency",
+  width = "450px"
+)
+
+# Financial accountability
+selectInput(
+  "org4_fin_account",
+  label = "Select Financial Accountability:",
+  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
+  selected = "Engages in financial accountability",
+  width = "450px"
+)
+
+# Funding sources
+selectInput(
+  "org4_funding",
+  label = "Select Funding Source:",
+  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
+  width = "450px"
+)
+
+# Relationship with host government
+selectInput(
+  "org4_host_gov",
+  label = "Select Relationship With Host Government",
+  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
+  width = "450px"
+)
+```
+
 ### Persona 1
 
-```{r persona 1 inputs}
-
-textInput("per1_id",
+```{r per1-inputs}
+# Naming
+textInput(
+  "per1_id",
   label = "Persona Name",
@@
   placeholder = "Enter Persona Name",
-          width = "450px")
-
-selectInput("per1_national_news",
+  width = "450px"
+)
+
+# Follow national news
+selectInput(
+  "per1_national_news",
   label = "Follow national news:",
-         choices = c("Rarely",
-                     "Once a week",
-                     "At least once a day"),
+  choices = c("Rarely", "Once a week", "At least once a day"),
   selected = "At least once a day",
-         width = "450px")
-
-selectInput("per1_international_news",
+  width = "450px"
+)
+
+# Follow international news
+selectInput(
+  "per1_international_news",
   label = "Follow international news:",
-         choices = c("Never",
-                     "Sometimes",
-                     "Always"),
+  choices = c("Never", "Sometimes", "Always"),
   selected = "Always",
-         width = "450px")
-
-selectInput("per1_news_medium",
+  width = "450px"
+)
+
+# Mediums to follow news
+selectInput(
+  "per1_news_medium",
   label = "Medium to follow news:",
-         choices = c("TV",
+  choices = c(
+    "TV",
     "Print",
@@
     "Email newsletter",
-                     "News app"),
+    "News app"
+  ),
   multiple = TRUE,
   selected = c("TV", "Print", "Social media"),
-         width = "450px")
-
-selectInput("per1_follow_gov",
+  width = "450px"
+)
+
+# Follow government and public affairs
+selectInput(
+  "per1_follow_gov",
   label = "Follow government & public affairs:",
-         choices = c("Not Often",
-                     "Often"),
+  choices = c("Not Often", "Often"),
   selected = "Often",
-         width = "450px")
-
-#Fix
-selectInput("per1_travel_developing",
+  width = "450px"
+)
+
+# Traveled to a developing country
+selectInput(
+  "per1_travel_developing",
   label = "Travel to developing country:",
-         choices = c("Doesn't travel", "Does travel"),
-         selected = "Does travel",
-         width = "450px")
-
-selectInput("per1_political_pref",
+  choices = c("Hasn't traveled to a developing country", "Traveled to a developing country"),
+  selected = "Traveled to a developing country",
+  width = "450px"
+)
+
+# Liberal to Conservative
+selectInput(
+  "per1_political_pref",
   label = "Political views from liberal to conservative:",
-         choices = c("Extremely liberal",
+  choices = c(
+    "Extremely liberal",
     "Somewhat liberal",
@@
     "Somewhat conservative",
-                     "Extremely conservative"),
+    "Extremely conservative"
+  ),
   selected = "Somewhat liberal",
-         width = "450px")
-
-#Fix
-selectInput("per1_institution_trust",
+  width = "450px"
+)
+
+# Trust in political institutions
+selectInput(
+  "per1_institution_trust",
   label = "Political institution trust from none to complete:",
-         choices = c("No trust at all in political institutions",
+  choices = c(
+    "No trust at all in political institutions",
     "Very little trust in political institutions",
     "Little trust in political institutions",
-                     "Nuetral trust in political institutions",
+    "Neutral trust in political institutions",
     "Some trust in political institutions",
     "A lot of trust in political institutions",
-                     "Complete trust in political institutions"),
+    "Complete trust in political institutions"
+  ),
   selected = "Complete trust in political institutions",
-         width = "450px")
-
-selectInput("per1_others_charitable",
+  width = "450px"
+)
+
+# People should be more charitable
+selectInput(
+  "per1_others_charitable",
   label = "People should be more charitable:",
-         choices = c("Strongly Disagree",
+  choices = c(
+    "Strongly Disagree",
     "Disagree",
     "Somewhat disagree",
-                     "Nuetral",
+    "Neutral",
     "Somewhat agree",
     "Agree",
-                     "Strongly agree"),
+    "Strongly agree"
+  ),
   selected = "Strongly agree",
-         width = "450px")
-
-# Fix
-selectInput("per1_worship_attendance",
+  width = "450px"
+)
+
+# Religious attendance
+selectInput(
+  "per1_worship_attendance",
   label = "Worship service attendance:",
-         choices = c("Not sure",
-                     "Rarely attend services",
-                     "Attend at least once a month"),
+  choices = c(
+    "Not sure",
+    "Rarely attend",
+    "Attend at least once a month"
+  ),
   selected = "Attend at least once a month",
-         width = "450px")
-
-selectInput("per1_religion_importance",
+  width = "450px"
+)
+
+# Importance of religion
+selectInput(
+  "per1_religion_importance",
   label = "Importance of religion:",
-         choices = c("Not important",
-                     "Important"),
+  choices = c("Not important", "Important"),
   selected = "Important",
-         width = "450px")
-
-selectInput("per1_religion",
+  width = "450px"
+)
+
+# Religion
+selectInput(
+  "per1_religion",
   label = "Religion:",
-         choices = c('Catholic',
+  choices = c(
+    'Catholic',
     'Protestant',
@@
     'Atheist',
-                     'Other (Religion)'),
+    'Other religion'
+  ),
   selected = 'Protestant',
-         width = "450px")
-
-selectInput("per1_charity_importance",
+  width = "450px"
+)
+
+# Importance of trusting charities
+selectInput(
+  "per1_charity_importance",
   label = "Charity Importance:",
-          choices = c("Not at all important",
+  choices = c(
+    "Not at all important",
     "Very unimportant",
     "Somewhat unimportant",
-                      "Nuetral",
+    "Neutral",
     "Somewhat important",
     "Very important",
-                      "Essential"),
+    "Essential"
+  ),
   selected = "Somewhat unimportant",
-          width = "450px")
-
-#Fix
-selectInput("per1_trust_in_charity",
+  width = "450px"
+)
+
+# Trust in charities
+selectInput(
+  "per1_trust_in_charity",
   label = "Charity Trust:",
-            choices = c("No trust at all in charities",
+  choices = c(
+    "No trust at all in charities",
     "Very little trust in charities",
     "Little trust in charities",
-                        "Nuetral trust in charities",
+    "Neutral trust in charities",
     "Some trust in charities",
     "A lot of trust in charities",
-                        "Complete trust in charities"),
+    "Complete trust in charities"
+  ),
   selected = "Complete trust in charities",
-            width = "450px")
-
-#Fix
-selectInput("per1_donation_frequency",
+  width = "450px"
+)
+
+# Donation frequency
+selectInput(
+  "per1_donation_frequency",
   label = "Donation Frequency:",
-         choices = c('Donate more than once a month, less than once a year',
-                     'Donate at least once a month'),
+  choices = c('Donate more than once a month, less than once a year', 'Donate at least once a month'),
   selected = "Donate at least once a month",
-         width = "450px")
-
-selectInput("per1_donation_amount",
+  width = "450px"
+)
+
+# Donated last year
+selectInput(
+  "per1_donation_amount",
   label = "Donation Amount:",
-         choices = c("$1-$49",
+  choices = c(
+    '$1-$49',
     '$50-$99',
@@
     '$5,000-$9,999',
-                     '$10,000+'),
+    '$10,000+'
+  ),
   selected = "$100-$499",
-         width = "450px")
-
-#Fix
-selectInput("per1_volunteer_12",
+  width = "450px"
+)
+
+# Volunteered in past 12 months
+selectInput(
+  "per1_volunteer_12",
   label = "Volunteered in last 12 Months:",
-         choices = c("Haven't volunteered", "Have volunteered"),
-         selected = "Have volunteered",
-         width = "450px")
-
-#Fix
-selectInput("per1_volunteer_frequency",
+  choices = c("Haven't volunteered in past 12 months", "Volunteered in past 12 months"),
+  selected = "Volunteered in past 12 months",
+  width = "450px"
+)
+
+# Volunteer frequency
+selectInput(
+  "per1_volunteer_frequency",
   label = "Volunteer Frequency:",
-         choices = c("Haven't volunteered in past 12 months",
+  choices = c(
+    "Haven't volunteered in past 12 months",
     "Rarely volunteer",
     "Volunteer more than once a month, less than once a year",
-                     "Volunteer at least once a month"),
+    "Volunteer at least once a month"
+  ),
   selected = "Volunteer at least once a month",
-         width = "450px")
-
-# fix
-selectInput("per1_personal_activism",
+  width = "450px"
+)
+
+# History of activism
+selectInput(
+  "per1_personal_activism",
   label = "Personal Activism:",
-         choices = c('Not personally involved ',
-                     'Personally involved'),
+  choices = c('Not personally involved', 'Personally involved'),
   selected = "Personally involved",
-         width = "450px")
-
-#Fix
-selectInput("per1_family_activism",
+  width = "450px"
+)
+
+# History of family activism
+selectInput(
+  "per1_family_activism",
   label = "Family Activism:",
-         choices = c('Family not involved',
-                     'Family involved'),
+  choices = c('Family not involved', 'Family involved'),
   selected = "Family involved",
-         width = "450px")
-
-#Fix
-selectInput("per1_religious_member",
+  width = "450px"
+)
+
+# Church or religious organization
+selectInput(
+  "per1_religious_member",
   label = "Church Membership:",
-         choices = c("Don't belong to church membership",
-                     'Inactive church member',
-                     'Active church member'),
-         selected = "Don't belong to church membership",
-         width = "450px")
-
-#Fix
-selectInput("per1_sport_member",
+  choices = c("Don't belong to church",'Inactive church member', 'Active church member'),
+  selected = "Don't belong to church",
+  width = "450px"
+)
+
+# Sport or recreational organization
+selectInput(
+  "per1_sport_member",
   label = "Sport or Recreational Membership:",
-         choices = c("Don't belong to sports membership",
-                     'Inactive sports member',
-                     'Active sports member'),
-         selected = "Don't belong to sports membership",
-         width = "450px")
-#Fix
-selectInput("per1_art_member",
+  choices = c(
+    "Don't belong to sports or rec organization", 
+    'Inactive sports or rec organization member',
+    'Active sports or rec organization member'
+  ),
+  selected = "Don't belong to sports or rec organization",
+  width = "450px"
+)
+
+# Art, music, or educational organization
+selectInput(
+  "per1_art_member",
   label = "Art, Music, or Educational Membership:",
-         choices = c("Don't belong to educational membership",
-                     'Inactive educational member',
-                     'Active educational member'),
-         selected = "Don't belong to educational membership",
-         width = "450px")
-#Fix
-selectInput("per1_labor_member",
+  choices = c(
+    "Don't belong to educational organization",
+    'Inactive art, music, or educational organization member',
+    'Active art, music, or educational organization member'
+  ),
+  selected = "Don't belong to educational organization",
+  width = "450px"
+)
+
+# Labor union
+selectInput(
+  "per1_labor_member",
   label = "Labor Union Membership:",
-         choices = c("Don't belong to union",
-                     'Inactive union member',
-                     'Active union member'),
+  choices = c("Don't belong to union", 'Inactive union member', 'Active union member'),
   selected = "Don't belong to union",
-         width = "450px")
-
-#Fix
-selectInput("per1_political_member",
+  width = "450px"
+)
+
+# Political party
+selectInput(
+  "per1_political_member",
   label = "Political Party Membership:",
-         choices = c("Don't belong to party",
-                     'Inactive party member',
-                     'Active party member'),
-         selected = "Active party member",
-         width = "450px")
-# Fix
-selectInput("per1_environmental_member",
-         label = "Environmental Org. Membership:",
-         choices = c("Don't belong to environmental organization",
-                     'Inactive environmental member',
-                     'Active environmental member'),
+  choices = c(
+    "Don't belong to political party",
+    'Inactive political party member',
+    'Active political party member'
+  ),
+  selected = "Active political party member",
+  width = "450px"
+)
+
+# Environmental organization
+selectInput(
+  "per1_environmental_member",
+  label = "Environmental Organization Membership:",
+  choices = c(
+    "Don't belong to environmental organization",
+    'Inactive environmental organization member',
+    'Active environmental organization member'
+  ),
   selected = "Don't belong to environmental organization",
-         width = "450px")
-# Fix
-selectInput("per1_professional_member",
-         label = "Professional Membership:",
-         choices = c("Don't belong to professional membership",
-                     'Inactive professional member',
-                     'Active professional member'),
-         selected = "Don't belong to professional membership",
-         width = "450px")
-# Fix
-selectInput("per1_humanitarian_member",
-         label = "Humanitarian Org. Membership:",
-         choices = c("Don't belong to humanitarian organization",
-                     'Inactive humanitarian member',
-                     'Active humanitarian member'),
-         selected = "Active humanitarian member",
-         width = "450px")
-
-# Fix
-selectInput("per1_consumer_member",
-         label = "Consumer Org. Membership:",
-         choices = c("Don't belong to consumer organization",
-                     'Inactive consumer member',
-                     'Active consumer member'),
+  width = "450px"
+)
+
+# Professional association
+selectInput(
+  "per1_professional_member",
+  label = "Professional Association Membership:",
+  choices = c(
+    "Don't belong to professional association",
+    'Inactive professional association member',
+    'Active professional association member'
+  ),
+  selected = "Don't belong to professional association",
+  width = "450px"
+)
+
+# Humanitarian or charitable organization
+selectInput(
+  "per1_humanitarian_member",
+  label = "Humanitarian or Charitable Organization Membership:",
+  choices = c(
+    "Don't belong to humanitarian or charitable organization",
+    'Inactive humanitarian or charitable organization member',
+    'Active humanitarian or charitable organization member'
+  ),
+  selected = "Active humanitarian or charitable organization member",
+  width = "450px"
+)
+
+# Consumer organization
+selectInput(
+  "per1_consumer_member",
+  label = "Consumer Organization Membership:",
+  choices = c(
+    "Don't belong to consumer organization",
+    'Inactive consumer organization member',
+    'Active consumer organization member'
+  ),
   selected = "Don't belong to consumer organization",
-         width = "450px")
-# Fix
-selectInput("per1_other_member",
-         label = "Other Org. Membership:",
-         choices = c("Don't belong to other organization",
-                     'Inactive other member',
-                     'Active other member'),
-         selected = "Don't belong to other organization",
-         width = "450px")
-
-selectInput("per1_gender",
+  width = "450px"
+)
+
+# Other organization
+selectInput(
+  "per1_other_member",
+  label = "Other Organization Membership:",
+  choices = c(
+    "Don't belong to another organization",
+    'Inactive member in another organization',
+    'Active member in another organization'
+  ),
+  selected = "Don't belong to another organization",
+  width = "450px"
+)
+
+# Gender
+selectInput(
+  "per1_gender",
   label = "Gender:",
-         choices = c("Male",
+  choices = c(
+    "Male",
     "Female",
@@
     "Prefer not to say",
-                     "Other (Gender)"),
+    "Other gender"
+  ),
   selected = "Male",
-         width = "450px")
-
-selectInput("per1_marital_status",
+  width = "450px"
+)
+
+# Marital status
+selectInput(
+  "per1_marital_status",
   label = "Marital Status:",
-         choices = c("Married",
+  choices = c(
+    "Married",
     "Widowed",
@@
     "Separated",
-                     "Never married"),
+    "Never married"
+  ),
   selected = "Married",
-         width = "450px")
-
-selectInput("per1_education",
+  width = "450px"
+)
+
+# Education
+selectInput(
+  "per1_education",
   label = "Education:",
-         choices = c("Less than high school",
+  choices = c(
+    "Less than high school",
     "High school graduate",
@@
     "Graduate or professional degree",
-                     "Doctorate"),
+    "Doctorate"
+  ),
   selected = "2 year degree",
-         width = "450px")
-
-selectInput("per1_income",
+  width = "450px"
+)
+
+# Income
+selectInput(
+  "per1_income",
   label = "Income:",
-         choices = c('Less than median of $61,372',
-                     'More than median of $61,372'),
+  choices = c('Less than median of $61,372', 'More than median of $61,372'),
   selected = "More than median of $61,372",
-         width = "450px")
-
-selectInput("per1_race",
-         label = "Race(s):",
-         choices = c('White',
+  width = "450px"
+)
+
+# Race
+selectInput(
+  "per1_race",
+  label = "Race:",
+  choices = c(
+    'White',
     'Black or African American',
-                     'American Indian or Alaska Native',
+    'American Indian or Alaskan Native',
     'Asian',
     'Native Hawaiian or Pacific Islander',
-                     'Other (Race)'),
+    'Other race'
+  ),
   multiple = TRUE,
   selected = "White",
-         width = "450px")
-
-selectInput("per1_age",
+  width = "450px"
+)
+
+# Age
+selectInput(
+  "per1_age",
   label = "Age:",
-         choices = c('Less than median age of 36',
-                     "More than median age of 36"),
+  choices = c('Less than median age of 36', "More than median age of 36"),
   selected = "Less than median age of 36",
-         width = "450px")
-
+  width = "450px"
+)
 ```
@@
 
-```{r persona 2 inputs}
-
-textInput("per2_id",
+```{r per2-inputs}
+# Naming
+textInput(
+  "per2_id",
   label = "Persona Name",
-          value = "Persona 2",
+  value = "Persona 1",
   placeholder = "Enter Persona Name",
-          width = "450px")
-
-selectInput("per2_national_news",
+  width = "450px"
+)
+
+# Follow national news
+selectInput(
+  "per2_national_news",
   label = "Follow national news:",
-         choices = c("Rarely",
-                     "Once a week",
-                     "At least once a day"),
+  choices = c("Rarely", "Once a week", "At least once a day"),
   selected = "At least once a day",
-         width = "450px")
-
-selectInput("per2_international_news",
+  width = "450px"
+)
+
+# Follow international news
+selectInput(
+  "per2_international_news",
   label = "Follow international news:",
-         choices = c("Never",
-                     "Sometimes",
-                     "Always"),
+  choices = c("Never", "Sometimes", "Always"),
   selected = "Always",
-         width = "450px")
-
-selectInput("per2_news_medium",
+  width = "450px"
+)
+
+# Mediums to follow news
+selectInput(
+  "per2_news_medium",
   label = "Medium to follow news:",
-         choices = c("TV",
+  choices = c(
+    "TV",
     "Print",
@@
     "Email newsletter",
-                     "News app"),
+    "News app"
+  ),
   multiple = TRUE,
   selected = c("TV", "Print", "Social media"),
-         width = "450px")
-
-selectInput("per2_follow_gov",
+  width = "450px"
+)
+
+# Follow government and public affairs
+selectInput(
+  "per2_follow_gov",
   label = "Follow government & public affairs:",
-         choices = c("Not Often",
-                     "Often"),
+  choices = c("Not Often", "Often"),
   selected = "Often",
-         width = "450px")
-
-#Fix
-selectInput("per2_travel_developing",
+  width = "450px"
+)
+
+# Traveled to a developing country
+selectInput(
+  "per2_travel_developing",
   label = "Travel to developing country:",
-         choices = c("Doesn't travel", "Does travel"),
-         selected = "Does travel",
-         width = "450px")
-
-selectInput("per2_political_pref",
+  choices = c("Hasn't traveled to a developing country", "Traveled to a developing country"),
+  selected = "Traveled to a developing country",
+  width = "450px"
+)
+
+# Liberal to Conservative
+selectInput(
+  "per2_political_pref",
   label = "Political views from liberal to conservative:",
-         choices = c("Extremely liberal",
+  choices = c(
+    "Extremely liberal",
     "Somewhat liberal",
@@
     "Somewhat conservative",
-                     "Extremely conservative"),
+    "Extremely conservative"
+  ),
   selected = "Somewhat liberal",
-         width = "450px")
-
-#Fix
-selectInput("per2_institution_trust",
+  width = "450px"
+)
+
+# Trust in political institutions
+selectInput(
+  "per2_institution_trust",
   label = "Political institution trust from none to complete:",
-         choices = c("No trust at all in political institutions",
+  choices = c(
+    "No trust at all in political institutions",
     "Very little trust in political institutions",
     "Little trust in political institutions",
-                     "Nuetral trust in political institutions",
+    "Neutral trust in political institutions",
     "Some trust in political institutions",
     "A lot of trust in political institutions",
-                     "Complete trust in political institutions"),
+    "Complete trust in political institutions"
+  ),
   selected = "Complete trust in political institutions",
-         width = "450px")
-
-selectInput("per2_others_charitable",
+  width = "450px"
+)
+
+# People should be more charitable
+selectInput(
+  "per2_others_charitable",
   label = "People should be more charitable:",
-         choices = c("Strongly Disagree",
+  choices = c(
+    "Strongly Disagree",
     "Disagree",
     "Somewhat disagree",
-                     "Nuetral",
+    "Neutral",
     "Somewhat agree",
     "Agree",
-                     "Strongly agree"),
+    "Strongly agree"
+  ),
   selected = "Strongly agree",
-         width = "450px")
-
-# Fix
-selectInput("per2_worship_attendance",
+  width = "450px"
+)
+
+# Religious attendance
+selectInput(
+  "per2_worship_attendance",
   label = "Worship service attendance:",
-         choices = c("Not sure",
-                     "Rarely attend services",
-                     "Attend at least once a month"),
+  choices = c(
+    "Not sure",
+    "Rarely attend",
+    "Attend at least once a month"
+  ),
   selected = "Attend at least once a month",
-         width = "450px")
-
-selectInput("per2_religion_importance",
+  width = "450px"
+)
+
+# Importance of religion
+selectInput(
+  "per2_religion_importance",
   label = "Importance of religion:",
-         choices = c("Not important",
-                     "Important"),
+  choices = c("Not important", "Important"),
   selected = "Important",
-         width = "450px")
-
-selectInput("per2_religion",
+  width = "450px"
+)
+
+# Religion
+selectInput(
+  "per2_religion",
   label = "Religion:",
-         choices = c('Catholic',
+  choices = c(
+    'Catholic',
     'Protestant',
@@
     'Atheist',
-                     'Other (Religion)'),
+    'Other religion'
+  ),
   selected = 'Protestant',
-         width = "450px")
-
-selectInput("per2_charity_importance",
+  width = "450px"
+)
+
+# Importance of trusting charities
+selectInput(
+  "per2_charity_importance",
   label = "Charity Importance:",
-          choices = c("Not at all important",
+  choices = c(
+    "Not at all important",
     "Very unimportant",
     "Somewhat unimportant",
-                      "Nuetral",
+    "Neutral",
     "Somewhat important",
     "Very important",
-                      "Essential"),
+    "Essential"
+  ),
   selected = "Somewhat unimportant",
-          width = "450px")
-
-#Fix
-selectInput("per2_trust_in_charity",
+  width = "450px"
+)
+
+# Trust in charities
+selectInput(
+  "per2_trust_in_charity",
   label = "Charity Trust:",
-            choices = c("No trust at all in charities",
+  choices = c(
+    "No trust at all in charities",
     "Very little trust in charities",
     "Little trust in charities",
-                        "Nuetral trust in charities",
+    "Neutral trust in charities",
     "Some trust in charities",
     "A lot of trust in charities",
-                        "Complete trust in charities"),
+    "Complete trust in charities"
+  ),
   selected = "Complete trust in charities",
-            width = "450px")
-
-#Fix
-selectInput("per2_donation_frequency",
+  width = "450px"
+)
+
+# Donation frequency
+selectInput(
+  "per2_donation_frequency",
   label = "Donation Frequency:",
-         choices = c('Donate more than once a month, less than once a year',
-                     'Donate at least once a month'),
+  choices = c('Donate more than once a month, less than once a year', 'Donate at least once a month'),
   selected = "Donate at least once a month",
-         width = "450px")
-
-selectInput("per2_donation_amount",
+  width = "450px"
+)
+
+# Donated last year
+selectInput(
+  "per2_donation_amount",
   label = "Donation Amount:",
-         choices = c("$1-$49",
+  choices = c(
+    '$1-$49',
     '$50-$99',
@@
     '$5,000-$9,999',
-                     '$10,000+'),
+    '$10,000+'
+  ),
   selected = "$100-$499",
-         width = "450px")
-
-#Fix
-selectInput("per2_volunteer_12",
+  width = "450px"
+)
+
+# Volunteered in past 12 months
+selectInput(
+  "per2_volunteer_12",
   label = "Volunteered in last 12 Months:",
-         choices = c("Haven't volunteered", "Have volunteered"),
-         selected = "Have volunteered",
-         width = "450px")
-
-#Fix
-selectInput("per2_volunteer_frequency",
+  choices = c("Haven't volunteered in past 12 months", "Volunteered in past 12 months"),
+  selected = "Volunteered in past 12 months",
+  width = "450px"
+)
+
+# Volunteer frequency
+selectInput(
+  "per2_volunteer_frequency",
   label = "Volunteer Frequency:",
-         choices = c("Haven't volunteered in past 12 months",
+  choices = c(
+    "Haven't volunteered in past 12 months",
     "Rarely volunteer",
     "Volunteer more than once a month, less than once a year",
-                     "Volunteer at least once a month"),
+    "Volunteer at least once a month"
+  ),
   selected = "Volunteer at least once a month",
-         width = "450px")
-
-# fix
-selectInput("per2_personal_activism",
+  width = "450px"
+)
+
+# History of activism
+selectInput(
+  "per2_personal_activism",
   label = "Personal Activism:",
-         choices = c('Not personally involved ',
-                     'Personally involved'),
+  choices = c('Not personally involved', 'Personally involved'),
   selected = "Personally involved",
-         width = "450px")
-
-#Fix
-selectInput("per2_family_activism",
+  width = "450px"
+)
+
+# History of family activism
+selectInput(
+  "per2_family_activism",
   label = "Family Activism:",
-         choices = c('Family not involved',
-                     'Family involved'),
+  choices = c('Family not involved', 'Family involved'),
   selected = "Family involved",
-         width = "450px")
-
-#Fix
-selectInput("per2_religious_member",
+  width = "450px"
+)
+
+# Church or religious organization
+selectInput(
+  "per2_religious_member",
   label = "Church Membership:",
-         choices = c("Don't belong to church membership",
-                     'Inactive church member',
-                     'Active church member'),
-         selected = "Don't belong to church membership",
-         width = "450px")
-
-#Fix
-selectInput("per2_sport_member",
+  choices = c("Don't belong to church",'Inactive church member', 'Active church member'),
+  selected = "Don't belong to church",
+  width = "450px"
+)
+
+# Sport or recreational organization
+selectInput(
+  "per2_sport_member",
   label = "Sport or Recreational Membership:",
-         choices = c("Don't belong to sports membership",
-                     'Inactive sports member',
-                     'Active sports member'),
-         selected = "Don't belong to sports membership",
-         width = "450px")
-#Fix
-selectInput("per2_art_member",
+  choices = c(
+    "Don't belong to sports or rec organization", 
+    'Inactive sports or rec organization member',
+    'Active sports or rec organization member'
+  ),
+  selected = "Don't belong to sports or rec organization",
+  width = "450px"
+)
+
+# Art, music, or educational organization
+selectInput(
+  "per2_art_member",
   label = "Art, Music, or Educational Membership:",
-         choices = c("Don't belong to educational membership",
-                     'Inactive educational member',
-                     'Active educational member'),
-         selected = "Don't belong to educational membership",
-         width = "450px")
-#Fix
-selectInput("per2_labor_member",
+  choices = c(
+    "Don't belong to educational organization",
+    'Inactive art, music, or educational organization member',
+    'Active art, music, or educational organization member'
+  ),
+  selected = "Don't belong to educational organization",
+  width = "450px"
+)
+
+# Labor union
+selectInput(
+  "per2_labor_member",
   label = "Labor Union Membership:",
-         choices = c("Don't belong to union",
-                     'Inactive union member',
-                     'Active union member'),
+  choices = c("Don't belong to union", 'Inactive union member', 'Active union member'),
   selected = "Don't belong to union",
-         width = "450px")
-
-#Fix
-selectInput("per2_political_member",
+  width = "450px"
+)
+
+# Political party
+selectInput(
+  "per2_political_member",
   label = "Political Party Membership:",
-         choices = c("Don't belong to party",
-                     'Inactive party member',
-                     'Active party member'),
-         selected = "Active party member",
-         width = "450px")
-# Fix
-selectInput("per2_environmental_member",
-         label = "Environmental Org. Membership:",
-         choices = c("Don't belong to environmental organization",
-                     'Inactive environmental member',
-                     'Active environmental member'),
+  choices = c(
+    "Don't belong to political party",
+    'Inactive political party member',
+    'Active political party member'
+  ),
+  selected = "Active political party member",
+  width = "450px"
+)
+
+# Environmental organization
+selectInput(
+  "per2_environmental_member",
+  label = "Environmental Organization Membership:",
+  choices = c(
+    "Don't belong to environmental organization",
+    'Inactive environmental organization member',
+    'Active environmental organization member'
+  ),
   selected = "Don't belong to environmental organization",
-         width = "450px")
-# Fix
-selectInput("per2_professional_member",
-         label = "Professional Membership:",
-         choices = c("Don't belong to professional membership",
-                     'Inactive professional member',
-                     'Active professional member'),
-         selected = "Don't belong to professional membership",
-         width = "450px")
-# Fix
-selectInput("per2_humanitarian_member",
-         label = "Humanitarian Org. Membership:",
-         choices = c("Don't belong to humanitarian organization",
-                     'Inactive humanitarian member',
-                     'Active humanitarian member'),
-         selected = "Active humanitarian member",
-         width = "450px")
-
-# Fix
-selectInput("per2_consumer_member",
-         label = "Consumer Org. Membership:",
-         choices = c("Don't belong to consumer organization",
-                     'Inactive consumer member',
-                     'Active consumer member'),
+  width = "450px"
+)
+
+# Professional association
+selectInput(
+  "per2_professional_member",
+  label = "Professional Association Membership:",
+  choices = c(
+    "Don't belong to professional association",
+    'Inactive professional association member',
+    'Active professional association member'
+  ),
+  selected = "Don't belong to professional association",
+  width = "450px"
+)
+
+# Humanitarian or charitable organization
+selectInput(
+  "per2_humanitarian_member",
+  label = "Humanitarian or Charitable Organization Membership:",
+  choices = c(
+    "Don't belong to humanitarian or charitable organization",
+    'Inactive humanitarian or charitable organization member',
+    'Active humanitarian or charitable organization member'
+  ),
+  selected = "Active humanitarian or charitable organization member",
+  width = "450px"
+)
+
+# Consumer organization
+selectInput(
+  "per2_consumer_member",
+  label = "Consumer Organization Membership:",
+  choices = c(
+    "Don't belong to consumer organization",
+    'Inactive consumer organization member',
+    'Active consumer organization member'
+  ),
   selected = "Don't belong to consumer organization",
-         width = "450px")
-# Fix
-selectInput("per2_other_member",
-         label = "Other Org. Membership:",
-         choices = c("Don't belong to other organization",
-                     'Inactive other member',
-                     'Active other member'),
-         selected = "Don't belong to other organization",
-         width = "450px")
-
-selectInput("per2_gender",
+  width = "450px"
+)
+
+# Other organization
+selectInput(
+  "per2_other_member",
+  label = "Other Organization Membership:",
+  choices = c(
+    "Don't belong to another organization",
+    'Inactive member in another organization',
+    'Active member in another organization'
+  ),
+  selected = "Don't belong to another organization",
+  width = "450px"
+)
+
+# Gender
+selectInput(
+  "per2_gender",
   label = "Gender:",
-         choices = c("Male",
+  choices = c(
+    "Male",
     "Female",
@@
     "Prefer not to say",
-                     "Other (Gender)"),
+    "Other gender"
+  ),
   selected = "Male",
-         width = "450px")
-
-selectInput("per2_marital_status",
+  width = "450px"
+)
+
+# Marital status
+selectInput(
+  "per2_marital_status",
   label = "Marital Status:",
-         choices = c("Married",
+  choices = c(
+    "Married",
     "Widowed",
@@
     "Separated",
-                     "Never married"),
+    "Never married"
+  ),
   selected = "Married",
-         width = "450px")
-
-selectInput("per2_education",
+  width = "450px"
+)
+
+# Education
+selectInput(
+  "per2_education",
   label = "Education:",
-         choices = c("Less than high school",
+  choices = c(
+    "Less than high school",
     "High school graduate",
@@
     "Graduate or professional degree",
-                     "Doctorate"),
-         selected = "Some college",
-         width = "450px")
-
-selectInput("per2_income",
+    "Doctorate"
+  ),
+  selected = "2 year degree",
+  width = "450px"
+)
+
+# Income
+selectInput(
+  "per2_income",
   label = "Income:",
-         choices = c('Less than median of $61,372',
-                     'More than median of $61,372'),
+  choices = c('Less than median of $61,372', 'More than median of $61,372'),
   selected = "More than median of $61,372",
-         width = "450px")
-
-selectInput("per2_race",
-         label = "Race(s):",
-         choices = c('White',
+  width = "450px"
+)
+
+# Race
+selectInput(
+  "per2_race",
+  label = "Race:",
+  choices = c(
+    'White',
     'Black or African American',
-                     'American Indian or Alaska Native',
+    'American Indian or Alaskan Native',
     'Asian',
     'Native Hawaiian or Pacific Islander',
-                     'Other (Race)'),
+    'Other race'
+  ),
   multiple = TRUE,
-         selected = "American Indian or Alaska Native",
-         width = "450px")
-
-selectInput("per2_age",
+  selected = "White",
+  width = "450px"
+)
+
+# Age
+selectInput(
+  "per2_age",
   label = "Age:",
-         choices = c('Less than median age of 36',
-                     "More than median age of 36"),
+  choices = c('Less than median age of 36', "More than median age of 36"),
   selected = "Less than median age of 36",
-         width = "450px")
-
+  width = "450px"
+)
 ```
@@
 
-```{r persona 3 inputs}
-
-textInput("per3_id",
+```{r per3-inputs}
+# Naming
+textInput(
+  "per3_id",
   label = "Persona Name",
-          value = "Persona 3",
+  value = "Persona 1",
   placeholder = "Enter Persona Name",
-          width = "450px")
-
-selectInput("per3_national_news",
+  width = "450px"
+)
+
+# Follow national news
+selectInput(
+  "per3_national_news",
   label = "Follow national news:",
-         choices = c("Rarely",
-                     "Once a week",
-                     "At least once a day"),
+  choices = c("Rarely", "Once a week", "At least once a day"),
   selected = "At least once a day",
-         width = "450px")
-
-selectInput("per3_international_news",
+  width = "450px"
+)
+
+# Follow international news
+selectInput(
+  "per3_international_news",
   label = "Follow international news:",
-         choices = c("Never",
-                     "Sometimes",
-                     "Always"),
+  choices = c("Never", "Sometimes", "Always"),
   selected = "Always",
-         width = "450px")
-
-selectInput("per3_news_medium",
+  width = "450px"
+)
+
+# Mediums to follow news
+selectInput(
+  "per3_news_medium",
   label = "Medium to follow news:",
-         choices = c("TV",
+  choices = c(
+    "TV",
     "Print",
@@
     "Email newsletter",
-                     "News app"),
+    "News app"
+  ),
   multiple = TRUE,
   selected = c("TV", "Print", "Social media"),
-         width = "450px")
-
-selectInput("per3_follow_gov",
+  width = "450px"
+)
+
+# Follow government and public affairs
+selectInput(
+  "per3_follow_gov",
   label = "Follow government & public affairs:",
-         choices = c("Not Often",
-                     "Often"),
+  choices = c("Not Often", "Often"),
   selected = "Often",
-         width = "450px")
-
-#Fix
-selectInput("per3_travel_developing",
+  width = "450px"
+)
+
+# Traveled to a developing country
+selectInput(
+  "per3_travel_developing",
   label = "Travel to developing country:",
-         choices = c("Doesn't travel", "Does travel"),
-         selected = "Does travel",
-         width = "450px")
-
-selectInput("per3_political_pref",
+  choices = c("Hasn't traveled to a developing country", "Traveled to a developing country"),
+  selected = "Traveled to a developing country",
+  width = "450px"
+)
+
+# Liberal to Conservative
+selectInput(
+  "per3_political_pref",
   label = "Political views from liberal to conservative:",
-         choices = c("Extremely liberal",
+  choices = c(
+    "Extremely liberal",
     "Somewhat liberal",
@@
     "Somewhat conservative",
-                     "Extremely conservative"),
+    "Extremely conservative"
+  ),
   selected = "Somewhat liberal",
-         width = "450px")
-
-#Fix
-selectInput("per3_institution_trust",
+  width = "450px"
+)
+
+# Trust in political institutions
+selectInput(
+  "per3_institution_trust",
   label = "Political institution trust from none to complete:",
-         choices = c("No trust at all in political institutions",
+  choices = c(
+    "No trust at all in political institutions",
     "Very little trust in political institutions",
     "Little trust in political institutions",
-                     "Nuetral trust in political institutions",
+    "Neutral trust in political institutions",
     "Some trust in political institutions",
     "A lot of trust in political institutions",
-                     "Complete trust in political institutions"),
+    "Complete trust in political institutions"
+  ),
   selected = "Complete trust in political institutions",
-         width = "450px")
-
-selectInput("per3_others_charitable",
+  width = "450px"
+)
+
+# People should be more charitable
+selectInput(
+  "per3_others_charitable",
   label = "People should be more charitable:",
-         choices = c("Strongly Disagree",
+  choices = c(
+    "Strongly Disagree",
     "Disagree",
     "Somewhat disagree",
-                     "Nuetral",
+    "Neutral",
     "Somewhat agree",
     "Agree",
-                     "Strongly agree"),
+    "Strongly agree"
+  ),
   selected = "Strongly agree",
-         width = "450px")
-
-# Fix
-selectInput("per3_worship_attendance",
+  width = "450px"
+)
+
+# Religious attendance
+selectInput(
+  "per3_worship_attendance",
   label = "Worship service attendance:",
-         choices = c("Not sure",
-                     "Rarely attend services",
-                     "Attend at least once a month"),
+  choices = c(
+    "Not sure",
+    "Rarely attend",
+    "Attend at least once a month"
+  ),
   selected = "Attend at least once a month",
-         width = "450px")
-
-selectInput("per3_religion_importance",
+  width = "450px"
+)
+
+# Importance of religion
+selectInput(
+  "per3_religion_importance",
   label = "Importance of religion:",
-         choices = c("Not important",
-                     "Important"),
+  choices = c("Not important", "Important"),
   selected = "Important",
-         width = "450px")
-
-selectInput("per3_religion",
+  width = "450px"
+)
+
+# Religion
+selectInput(
+  "per3_religion",
   label = "Religion:",
-         choices = c('Catholic',
+  choices = c(
+    'Catholic',
     'Protestant',
@@
     'Atheist',
-                     'Other (Religion)'),
+    'Other religion'
+  ),
   selected = 'Protestant',
-         width = "450px")
-
-selectInput("per3_charity_importance",
+  width = "450px"
+)
+
+# Importance of trusting charities
+selectInput(
+  "per3_charity_importance",
   label = "Charity Importance:",
-          choices = c("Not at all important",
+  choices = c(
+    "Not at all important",
     "Very unimportant",
     "Somewhat unimportant",
-                      "Nuetral",
+    "Neutral",
     "Somewhat important",
     "Very important",
-                      "Essential"),
+    "Essential"
+  ),
   selected = "Somewhat unimportant",
-          width = "450px")
-
-#Fix
-selectInput("per3_trust_in_charity",
+  width = "450px"
+)
+
+# Trust in charities
+selectInput(
+  "per3_trust_in_charity",
   label = "Charity Trust:",
-            choices = c("No trust at all in charities",
+  choices = c(
+    "No trust at all in charities",
     "Very little trust in charities",
     "Little trust in charities",
-                        "Nuetral trust in charities",
+    "Neutral trust in charities",
     "Some trust in charities",
     "A lot of trust in charities",
-                        "Complete trust in charities"),
+    "Complete trust in charities"
+  ),
   selected = "Complete trust in charities",
-            width = "450px")
-
-#Fix
-selectInput("per3_donation_frequency",
+  width = "450px"
+)
+
+# Donation frequency
+selectInput(
+  "per3_donation_frequency",
   label = "Donation Frequency:",
-         choices = c('Donate more than once a month, less than once a year',
-                     'Donate at least once a month'),
+  choices = c('Donate more than once a month, less than once a year', 'Donate at least once a month'),
   selected = "Donate at least once a month",
-         width = "450px")
-
-selectInput("per3_donation_amount",
+  width = "450px"
+)
+
+# Donated last year
+selectInput(
+  "per3_donation_amount",
   label = "Donation Amount:",
-         choices = c("$1-$49",
+  choices = c(
+    '$1-$49',
     '$50-$99',
@@
     '$5,000-$9,999',
-                     '$10,000+'),
+    '$10,000+'
+  ),
   selected = "$100-$499",
-         width = "450px")
-
-#Fix
-selectInput("per3_volunteer_12",
+  width = "450px"
+)
+
+# Volunteered in past 12 months
+selectInput(
+  "per3_volunteer_12",
   label = "Volunteered in last 12 Months:",
-         choices = c("Haven't volunteered", "Have volunteered"),
-         selected = "Have volunteered",
-         width = "450px")
-
-#Fix
-selectInput("per3_volunteer_frequency",
+  choices = c("Haven't volunteered in past 12 months", "Volunteered in past 12 months"),
+  selected = "Volunteered in past 12 months",
+  width = "450px"
+)
+
+# Volunteer frequency
+selectInput(
+  "per3_volunteer_frequency",
   label = "Volunteer Frequency:",
-         choices = c("Haven't volunteered in past 12 months",
+  choices = c(
+    "Haven't volunteered in past 12 months",
     "Rarely volunteer",
     "Volunteer more than once a month, less than once a year",
-                     "Volunteer at least once a month"),
+    "Volunteer at least once a month"
+  ),
   selected = "Volunteer at least once a month",
-         width = "450px")
-
-# fix
-selectInput("per3_personal_activism",
+  width = "450px"
+)
+
+# History of activism
+selectInput(
+  "per3_personal_activism",
   label = "Personal Activism:",
-         choices = c('Not personally involved ',
-                     'Personally involved'),
+  choices = c('Not personally involved', 'Personally involved'),
   selected = "Personally involved",
-         width = "450px")
-
-#Fix
-selectInput("per3_family_activism",
+  width = "450px"
+)
+
+# History of family activism
+selectInput(
+  "per3_family_activism",
   label = "Family Activism:",
-         choices = c('Family not involved',
-                     'Family involved'),
+  choices = c('Family not involved', 'Family involved'),
   selected = "Family involved",
-         width = "450px")
-
-#Fix
-selectInput("per3_religious_member",
+  width = "450px"
+)
+
+# Church or religious organization
+selectInput(
+  "per3_religious_member",
   label = "Church Membership:",
-         choices = c("Don't belong to church membership",
-                     'Inactive church member',
-                     'Active church member'),
-         selected = "Don't belong to church membership",
-         width = "450px")
-
-#Fix
-selectInput("per3_sport_member",
+  choices = c("Don't belong to church",'Inactive church member', 'Active church member'),
+  selected = "Don't belong to church",
+  width = "450px"
+)
+
+# Sport or recreational organization
+selectInput(
+  "per3_sport_member",
   label = "Sport or Recreational Membership:",
-         choices = c("Don't belong to sports membership",
-                     'Inactive sports member',
-                     'Active sports member'),
-         selected = "Don't belong to sports membership",
-         width = "450px")
-#Fix
-selectInput("per3_art_member",
+  choices = c(
+    "Don't belong to sports or rec organization", 
+    'Inactive sports or rec organization member',
+    'Active sports or rec organization member'
+  ),
+  selected = "Don't belong to sports or rec organization",
+  width = "450px"
+)
+
+# Art, music, or educational organization
+selectInput(
+  "per3_art_member",
   label = "Art, Music, or Educational Membership:",
-         choices = c("Don't belong to educational membership",
-                     'Inactive educational member',
-                     'Active educational member'),
-         selected = "Don't belong to educational membership",
-         width = "450px")
-#Fix
-selectInput("per3_labor_member",
+  choices = c(
+    "Don't belong to educational organization",
+    'Inactive art, music, or educational organization member',
+    'Active art, music, or educational organization member'
+  ),
+  selected = "Don't belong to educational organization",
+  width = "450px"
+)
+
+# Labor union
+selectInput(
+  "per3_labor_member",
   label = "Labor Union Membership:",
-         choices = c("Don't belong to union",
-                     'Inactive union member',
-                     'Active union member'),
+  choices = c("Don't belong to union", 'Inactive union member', 'Active union member'),
   selected = "Don't belong to union",
-         width = "450px")
-
-#Fix
-selectInput("per3_political_member",
+  width = "450px"
+)
+
+# Political party
+selectInput(
+  "per3_political_member",
   label = "Political Party Membership:",
-         choices = c("Don't belong to party",
-                     'Inactive party member',
-                     'Active party member'),
-         selected = "Active party member",
-         width = "450px")
-# Fix
-selectInput("per3_environmental_member",
-         label = "Environmental Org. Membership:",
-         choices = c("Don't belong to environmental organization",
-                     'Inactive environmental member',
-                     'Active environmental member'),
+  choices = c(
+    "Don't belong to political party",
+    'Inactive political party member',
+    'Active political party member'
+  ),
+  selected = "Active political party member",
+  width = "450px"
+)
+
+# Environmental organization
+selectInput(
+  "per3_environmental_member",
+  label = "Environmental Organization Membership:",
+  choices = c(
+    "Don't belong to environmental organization",
+    'Inactive environmental organization member',
+    'Active environmental organization member'
+  ),
   selected = "Don't belong to environmental organization",
-         width = "450px")
-# Fix
-selectInput("per3_professional_member",
-         label = "Professional Membership:",
-         choices = c("Don't belong to professional membership",
-                     'Inactive professional member',
-                     'Active professional member'),
-         selected = "Don't belong to professional membership",
-         width = "450px")
-# Fix
-selectInput("per3_humanitarian_member",
-         label = "Humanitarian Org. Membership:",
-         choices = c("Don't belong to humanitarian organization",
-                     'Inactive humanitarian member',
-                     'Active humanitarian member'),
-         selected = "Active humanitarian member",
-         width = "450px")
-
-# Fix
-selectInput("per3_consumer_member",
-         label = "Consumer Org. Membership:",
-         choices = c("Don't belong to consumer organization",
-                     'Inactive consumer member',
-                     'Active consumer member'),
+  width = "450px"
+)
+
+# Professional association
+selectInput(
+  "per3_professional_member",
+  label = "Professional Association Membership:",
+  choices = c(
+    "Don't belong to professional association",
+    'Inactive professional association member',
+    'Active professional association member'
+  ),
+  selected = "Don't belong to professional association",
+  width = "450px"
+)
+
+# Humanitarian or charitable organization
+selectInput(
+  "per3_humanitarian_member",
+  label = "Humanitarian or Charitable Organization Membership:",
+  choices = c(
+    "Don't belong to humanitarian or charitable organization",
+    'Inactive humanitarian or charitable organization member',
+    'Active humanitarian or charitable organization member'
+  ),
+  selected = "Active humanitarian or charitable organization member",
+  width = "450px"
+)
+
+# Consumer organization
+selectInput(
+  "per3_consumer_member",
+  label = "Consumer Organization Membership:",
+  choices = c(
+    "Don't belong to consumer organization",
+    'Inactive consumer organization member',
+    'Active consumer organization member'
+  ),
   selected = "Don't belong to consumer organization",
-         width = "450px")
-# Fix
-selectInput("per3_other_member",
-         label = "Other Org. Membership:",
-         choices = c("Don't belong to other organization",
-                     'Inactive other member',
-                     'Active other member'),
-         selected = "Don't belong to other organization",
-         width = "450px")
-
-selectInput("per3_gender",
+  width = "450px"
+)
+
+# Other organization
+selectInput(
+  "per3_other_member",
+  label = "Other Organization Membership:",
+  choices = c(
+    "Don't belong to another organization",
+    'Inactive member in another organization',
+    'Active member in another organization'
+  ),
+  selected = "Don't belong to another organization",
+  width = "450px"
+)
+
+# Gender
+selectInput(
+  "per3_gender",
   label = "Gender:",
-         choices = c("Male",
+  choices = c(
+    "Male",
     "Female",
@@
     "Prefer not to say",
-                     "Other (Gender)"),
-         selected = "Female",
-         width = "450px")
-
-selectInput("per3_marital_status",
+    "Other gender"
+  ),
+  selected = "Male",
+  width = "450px"
+)
+
+# Marital status
+selectInput(
+  "per3_marital_status",
   label = "Marital Status:",
-         choices = c("Married",
+  choices = c(
+    "Married",
     "Widowed",
@@
     "Separated",
-                     "Never married"),
+    "Never married"
+  ),
   selected = "Married",
-         width = "450px")
-
-selectInput("per3_education",
+  width = "450px"
+)
+
+# Education
+selectInput(
+  "per3_education",
   label = "Education:",
-         choices = c("Less than high school",
+  choices = c(
+    "Less than high school",
     "High school graduate",
@@
     "Graduate or professional degree",
-                     "Doctorate"),
-         selected = "Graduate or professional degree",
-         width = "450px")
-
-selectInput("per3_income",
+    "Doctorate"
+  ),
+  selected = "2 year degree",
+  width = "450px"
+)
+
+# Income
+selectInput(
+  "per3_income",
   label = "Income:",
-         choices = c('Less than median of $61,372',
-                     'More than median of $61,372'),
+  choices = c('Less than median of $61,372', 'More than median of $61,372'),
   selected = "More than median of $61,372",
-         width = "450px")
-
-selectInput("per3_race",
-         label = "Race(s):",
-         choices = c('White',
+  width = "450px"
+)
+
+# Race
+selectInput(
+  "per3_race",
+  label = "Race:",
+  choices = c(
+    'White',
     'Black or African American',
-                     'American Indian or Alaska Native',
+    'American Indian or Alaskan Native',
     'Asian',
     'Native Hawaiian or Pacific Islander',
-                     'Other (Race)'),
+    'Other race'
+  ),
   multiple = TRUE,
-         selected = c("Black or African American", "American Indian or Alaska Native"),
-         width = "450px")
-
-selectInput("per3_age",
+  selected = "White",
+  width = "450px"
+)
+
+# Age
+selectInput(
+  "per3_age",
   label = "Age:",
-         choices = c('Less than median age of 36',
-                     "More than median age of 36"),
+  choices = c('Less than median age of 36', "More than median age of 36"),
   selected = "Less than median age of 36",
-         width = "450px")
-
+  width = "450px"
+)
 ```
-
-### Org 1
-
-```{r org1 org inputs}
-
-textInput("org1_id",
-          label = "Organization Name",
-          value = "Organization 1",
-          placeholder = "Enter Organization Name",
-          width = "450px")
-
-selectInput("org1_id",
-            label = "Select Organization:",
-            choice = c("Amnesty International",
-                       "Greenpeace",
-                       "Oxfam",
-                       "Red Cross"),
-            selected = "Red Cross",
-            width = "450px")
-
-selectInput("org1_issue", 
-            label = "Select Issue Area:",
-            choices = c("Emergency response",
-                        "Environment",
-                        "Human rights",
-                        "Refugee relief"),
-            selected = "Emergency response",
-            width = "450px")
-
-selectInput("org1_fin_trans",
-            label = "Select Financial Transparency:",
-            choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"),
-            selected = "Engages in transparency",
-            width = "450px")
-
-selectInput("org1_fin_account",
-            label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in accountability",
-                        "Engages in accountability"),
-            selected = "Engages in accountability",
-            width = "450px")
-
-selectInput("org1_funding",
-            label = "Select Funding Source:",
-            choices = c("Many small private donations",
-                        "Handful of wealthy private donors",
-                        "Government grants"),
-            width = "450px")
-
-selectInput("org1_host_gov",
-            label = "Select Relationship With Host Government",
-            choices = c("Friendly relationship with government",
-                        "Criticized by government", 
-                        "Under government crackdown"),
-            width = "450px")
-
-```
-
-### Org 2
-
-```{r org2 org inputs}
-
-textInput("org2_id",
-          label = "Organization Name",
-          value = "Organization 2",
-          placeholder = "Enter Organiation Name",
-          width = "450px")
-
-selectInput("org2_id",
-            label = "Select Organization:",
-            choice = c("Amnesty International",
-                       "Greenpeace",
-                       "Oxfam",
-                       "Red Cross"),
-            selected = "Red Cross",
-            width = "450px")
-
-selectInput("org2_issue", 
-            label = "Select Issue Area:",
-            choices = c("Emergency response",
-                        "Environment",
-                        "Human rights",
-                        "Refugee relief"),
-            selected = "Environment",
-            width = "450px")
-
-selectInput("org2_fin_trans",
-            label = "Select Financial Transparency:",
-            choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"),
-            selected = "Engages in transparency",
-            width = "450px")
-
-selectInput("org2_fin_account",
-            label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in accountability",
-                        "Engages in accountability"),
-            selected = "Engages in accountability",
-            width = "450px")
-
-selectInput("org2_funding",
-            label = "Select Funding Source:",
-            choices = c("Many small private donations",
-                        "Handful of wealthy private donors",
-                        "Government grants"),
-            width = "450px")
-
-selectInput("org2_host_gov",
-            label = "Select Relationship With Host Government",
-            choices = c("Friendly relationship with government",
-                        "Criticized by government", 
-                        "Under government crackdown"),
-            width = "450px")
-```
-
-### Org 3
-
-```{r org3 org inputs}
-
-textInput("org3_id",
-          label = "Organization Name",
-          value = "Organization 3",
-          placeholder = "Enter Organiation Name",
-          width = "450px")
-
-selectInput("org3_id",
-            label = "Select Organization:",
-            choice = c("Amnesty International",
-                       "Greenpeace",
-                       "Oxfam",
-                       "Red Cross"),
-            selected = "Red Cross",
-            width = "450px")
-
-selectInput("org3_issue", 
-            label = "Select Issue Area:",
-            choices = c("Emergency response",
-                        "Environment",
-                        "Human rights",
-                        "Refugee relief"),
-            selected = "Human rights",
-            width = "450px")
-
-selectInput("org3_fin_trans",
-            label = "Select Financial Transparency:",
-            choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"),
-            selected = "Engages in transparency",
-            width = "450px")
-
-selectInput("org3_fin_account",
-            label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in accountability",
-                        "Engages in accountability"),
-            selected = "Engages in accountability",
-            width = "450px")
-
-selectInput("org3_funding",
-            label = "Select Funding Source:",
-            choices = c("Many small private donations",
-                        "Handful of wealthy private donors",
-                        "Government grants"),
-            width = "450px")
-
-selectInput("org3_host_gov",
-            label = "Select Relationship With Host Government",
-            choices = c("Friendly relationship with government",
-                        "Criticized by government", 
-                        "Under government crackdown"),
-            width = "450px")
-```
-
-### Org 4
-
-```{r org4 org inputs}
-
-textInput("org4_id",
-          label = "Organization Name",
-          value = "Organization 4",
-          placeholder = "Enter Organiation Name",
-          width = "450px")
-
-selectInput("org4_id",
-            label = "Select Organization:",
-            choice = c("Amnesty International",
-                       "Greenpeace",
-                       "Oxfam",
-                       "Red Cross"),
-            selected = "Red Cross",
-            width = "450px")
-
-selectInput("org4_issue", 
-            label = "Select Issue Area:",
-            choices = c("Emergency response",
-                        "Environment",
-                        "Human rights",
-                        "Refugee relief"),
-            selected = "Refugee relief",
-            width = "450px")
-
-selectInput("org4_fin_trans",
-            label = "Select Financial Transparency:",
-            choices = c("Doesn’t engage in transparency",
-                        "Engages in transparency"),
-            selected = "Engages in transparency",
-            width = "450px")
-
-selectInput("org4_fin_account",
-            label = "Select Financial Accountability:",
-            choices = c("Doesn’t engage in accountability",
-                        "Engages in accountability"),
-            selected = "Engages in accountability",
-            width = "450px")
-
-selectInput("org4_funding",
-            label = "Select Funding Source:",
-            choices = c("Many small private donations",
-                        "Handful of wealthy private donors",
-                        "Government grants"),
-            width = "450px")
-
-selectInput("org4_host_gov",
-            label = "Select Relationship With Host Government",
-            choices = c("Friendly relationship with government",
-                        "Criticized by government", 
-                        "Under government crackdown"),
-            width = "450px")
-```

### 2020-09-19 analysis/05_market_simulator.Rmd
Revert "testing matrix multiplication to find issue with market shres not lining up with excel sheet. Also made capitalization consistent in inputs"
This reverts commit cab2c11df4e85d3fae0681ce339f458b47698cf9.

--- 2020-09-17 analysis/05_market_simulator.Rmd
@@
 
-test_beta <- as.data.frame(matrix(rep(0), nrow = 12))
-
-test_beta$levels = c("Persona 1", "Persona 2", "Persona 3", "input1", "input2", "input3", "input4", "input5", "input6", "input7", "input8", "input9")
-
-# Persona Reactive Element
-
-test_beta$p1 <- 0
-test_beta$p1[1] <- 1
-
-test_beta$p2 <- 0
-test_beta$p2[2] <- 1
-
-test_beta$p3 <- 0
-test_beta$p3[3] <- 1
-
-test1 <- test_beta[,3]
+# beta_persona_test <- as.data.frame(matrix(rep(0), nrow = 38))
+# 
+# beta_persona_test$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
+# 
+# 
+# 
+# # Persona Reactive Element
+# 
+# beta_persona_test$p1 <- 1
+# 
+# beta_persona_test$p2 <- 2
+# 
+# beta_persona_test$p3 <- 3
+#         
+# persona1 <- persona_data[,2]
+# 
+# p_beta1 <- as.matrix(public_political_social_charity_demo) %*%   
+#   
+#   as.matrix(persona1) %*% beta_persona_test[,3]
 
@@
                      "Doctorate"),
-         selected = "Some college",
+         selected = "2 year degree",
          width = "450px")
@@
          multiple = TRUE,
-         selected = 'American Indian or Alaska Native',
+         selected = "White",
          width = "450px")
@@
                      "Other (Gender)"),
-         selected = "Female",
+         selected = "Male",
          width = "450px")
@@
                      "Doctorate"),
-         selected = "Graduate or professional degree",
+         selected = "2 year degree",
          width = "450px")
@@
          multiple = TRUE,
-         selected = c("Black or African American",'American Indian or Alaska Native'),
+         selected = "White",
          width = "450px")
@@
 textInput("ai_id",
-          label = "Organization name",
+          label = "Organization Name",
           value = "Organization 1",
-          placeholder = "Enter organization name",
+          placeholder = "Enter Organization Name",
           width = "450px")
@@
 selectInput("org1_id",
-            label = "Organization:",
+            label = "Select Organization:",
             choice = c("Amnesty International",
@@
 selectInput("ai_issue", 
-            label = "Issue area:",
+            label = "Select Issue Area:",
             choices = c("Emergency response",
@@
 selectInput("ai_fin_trans",
-            label = "Financial transparency:",
+            label = "Select Financial Transparency:",
             choices = c("Doesn’t engage in transparency",
@@
 selectInput("ai_account",
-            label = "Financial accountability:",
+            label = "Select Financial Accountability:",
             choices = c("Doesn’t engage in accountability",
@@
 selectInput("ai_funding",
-            label = "Funding source:",
+            label = "Select Funding Source:",
             choices = c("Many small private donations",
@@
                         "Government grants"),
-            selected = "Many small private donations",
             width = "450px")
@@
 selectInput("ai_gov_relat",
-            label = "Relationship with host government",
+            label = "Select Relationship With Host Government",
             choices = c("Friendly relationship with government",
@@
                         "Under government crackdown"),
-            selected = "Friendly relationship with government",
             width = "450px")
@@
 textInput("gp_id",
-          label = "Organization name",
+          label = "Organization Name",
           value = "Organization 2",
-          placeholder = "Enter organization name",
+          placeholder = "Enter Organiation Name",
           width = "450px")
@@
 selectInput("org2_id",
-            label = "Organization:",
+            label = "Select Organization:",
             choice = c("Amnesty International",
@@
 selectInput("gp_issue", 
-            label = "Issue area:",
+            label = "Select Issue Area:",
             choices = c("Emergency response",
@@
 selectInput("gp_fin_trans",
-            label = "Financial transparency:",
+            label = "Select Financial Transparency:",
             choices = c("Doesn’t engage in transparency",
@@
 selectInput("gp_account",
-            label = "Financial accountability:",
+            label = "Select Financial Accountability:",
             choices = c("Doesn’t engage in accountability",
@@
 selectInput("gp_funding",
-            label = "Funding source:",
+            label = "Select Funding Source:",
             choices = c("Many small private donations",
@@
 selectInput("gp_gov_relat",
-            label = "Relationship with host government",
+            label = "Select Relationship With Host Government",
             choices = c("Friendly relationship with government",
@@
                         "Under government crackdown"),
-            selected = "Friendly relationship with government",
-            width = "450px")
-
+            width = "450px")
 ```
@@
 textInput("ox_id",
-          label = "Organization name",
+          label = "Organization Name",
           value = "Organization 3",
-          placeholder = "Enter organization name",
+          placeholder = "Enter Organiation Name",
           width = "450px")
@@
 selectInput("org3_id",
-            label = "Organization:",
+            label = "Select Organization:",
             choice = c("Amnesty International",
@@
 selectInput("ox_issue", 
-            label = "Issue area:",
+            label = "Select Issue Area:",
             choices = c("Emergency response",
@@
 selectInput("ox_fin_trans",
-            label = "Financial transparency:",
+            label = "Select Financial Transparency:",
             choices = c("Doesn’t engage in transparency",
@@
 selectInput("ox_account",
-            label = "Financial accountability:",
+            label = "Select Financial Accountability:",
             choices = c("Doesn’t engage in accountability",
@@
 selectInput("ox_funding",
-            label = "Funding source:",
+            label = "Select Funding Source:",
             choices = c("Many small private donations",
@@
 selectInput("ox_gov_relat",
-            label = "Relationship with host government",
+            label = "Select Relationship With Host Government",
             choices = c("Friendly relationship with government",
@@
 textInput("rc_id",
-          label = "Organization name",
+          label = "Organization Name",
           value = "Organization 4",
-          placeholder = "Enter organization name",
+          placeholder = "Enter Organiation Name",
           width = "450px")
@@
 selectInput("org4_id",
-            label = "Organization:",
+            label = "Select Organization:",
             choice = c("Amnesty International",
@@
 selectInput("rc_issue", 
-            label = "Issue area:",
+            label = "Select Issue Area:",
             choices = c("Emergency response",
@@
 selectInput("rc_fin_trans",
-            label = "Financial transparency:",
+            label = "Select Financial Transparency:",
             choices = c("Doesn’t engage in transparency",
@@
 selectInput("rc_account",
-            label = "Financial accountability:",
+            label = "Select Financial Accountability:",
             choices = c("Doesn’t engage in accountability",
@@
 selectInput("rc_funding",
-            label = "Funding source:",
+            label = "Select Funding Source:",
             choices = c("Many small private donations",
@@
 selectInput("rc_gov_relat",
-            label = "Relationship with host government",
+            label = "Select Relationship With Host Government",
             choices = c("Friendly relationship with government",

### 2020-09-19 analysis/05_market_simulator.Rmd
Revert "Persona input mistakes corrected"
This reverts commit bf6eb23043fe7377012c1d3ada2a4fe979faac2d.

@@
                         # Trust in Political Institute
-                        "Very little trust in political institutions",
-                        "Little trust in political institutions",
-                        "Nuetral trust in political institutions",
-                        "Some trust in political institutions",
-                        "A lot of trust in political institutions",
-                        "Complete trust in political institutions",
+                        "Very little trust in polticial institutions",
+                        "Little trust in polticial institutions",
+                        "Nuetral trust in polticial institutions",
+                        "Some trust in polticial institutions",
+                        "A lot of trust in polticial institutions",
+                        "Complete trust in polticial institutions",
                         # Should Others be Charitable
@@
                         # Donation Frequency
-                        "Donate at least once a month", 
+                        "Donate At least once a month", 
                         # Donation Amount
@@
                         "Inactive consumer member",
-                        "Active consumer member",
+                        "Active sonsumer member",
                         #Other Organization Membership
@@
 textInput("p1_id",
-          label = "Persona name",
+          label = "Persona Name",
           value = "Persona 1",
-          placeholder = "Enter persona name",
+          placeholder = "Enter Persona Name",
           width = "450px")
@@
          label = "Follow government & public affairs:",
-         choices = c("Not often",
+         choices = c("Not Often",
                      "Often"),
@@
          label = "People should be more charitable:",
-         choices = c("Strongly disagree",
+         choices = c("Strongly Disagree",
                      "Disagree",
@@
 selectInput("p1_charity_importance",
-          label = "Charity importance:",
+          label = "Charity Importance:",
           choices = c("Not at all important",
@@
 selectInput("p1_trust_in_charity",
-            label = "Charity trust:",
+            label = "Charity Trust:",
             choices = c("No trust at all in charities",
@@
 selectInput("p1_donation_frequency",
-         label = "Donation frequency:",
+         label = "Donation Frequency:",
          choices = c('Donate more than once a month, less than once a year',
@@
 selectInput("p1_donation_amount",
-         label = "Donation amount:",
+         label = "Donation Amount:",
          choices = c("$1-$49",
@@
 selectInput("p1_volunteer_12",
-         label = "Volunteered in last 12 months:",
+         label = "Volunteered in last 12 Months:",
          choices = c("Haven't volunteered", "Have volunteered"),
@@
 selectInput("p1_volunteer_frequency",
-         label = "Volunteer frequency:",
+         label = "Volunteer Frequency:",
          choices = c("Haven't volunteered in past 12 months",
@@
 selectInput("p1_personal_activism",
-         label = "Personal activism:",
+         label = "Personal Activism:",
          choices = c('Not personally involved ',
@@
 selectInput("p1_family_activism",
-         label = "Family activism:",
+         label = "Family Activism:",
          choices = c('Family not involved',
@@
 selectInput("p1_religious_member",
-         label = "Church membership:",
+         label = "Church Membership:",
          choices = c("Don't belong to church membership",
@@
 selectInput("p1_sport_member",
-         label = "Sport or recreational membership:",
+         label = "Sport or Recreational Membership:",
          choices = c("Don't belong to sports membership",
@@
 selectInput("p1_art_member",
-         label = "Art, music, or educational membership:",
+         label = "Art, Music, or Educational Membership:",
          choices = c("Don't belong to educational membership",
@@
 selectInput("p1_labor_member",
-         label = "Labor union membership:",
+         label = "Labor Union Membership:",
          choices = c("Don't belong to union",
@@
 selectInput("p1_political_member",
-         label = "Political party membership:",
+         label = "Political Party Membership:",
          choices = c("Don't belong to party",
@@
 selectInput("p1_environmental_member",
-         label = "Environmental organization membership:",
+         label = "Environmental Org. Membership:",
          choices = c("Don't belong to environmental organization",
@@
 selectInput("p1_professional_member",
-         label = "Professional membership:",
+         label = "Professional Membership:",
          choices = c("Don't belong to professional membership",
@@
 selectInput("p1_humanitarian_member",
-         label = "Humanitarian organization membership:",
+         label = "Humanitarian Org. Membership:",
          choices = c("Don't belong to humanitarian organization",
@@
 selectInput("p1_consumer_member",
-         label = "Consumer organization membership:",
+         label = "Consumer Org. Membership:",
          choices = c("Don't belong to consumer organization",
@@
 selectInput("p1_other_member",
-         label = "Other organization membership:",
+         label = "Other Org. Membership:",
          choices = c("Don't belong to other organization",
@@
 selectInput("p1_marital_status",
-         label = "Marital status:",
+         label = "Marital Status:",
          choices = c("Married",
@@
 textInput("p2_id",
-          label = "Persona name",
+          label = "Persona Name",
           value = "Persona 2",
-          placeholder = "Enter persona name",
+          placeholder = "Enter Persona Name",
           width = "450px")
@@
 
+#Fix
 selectInput("p2_travel_developing",
@@
 
+#Fix
 selectInput("p2_institution_trust",
@@
 
+# Fix
 selectInput("p2_worship_attendance",
@@
 selectInput("p2_charity_importance",
-          label = "Charity importance:",
+          label = "Charity Importance:",
           choices = c("Not at all important",
@@
 
+#Fix
 selectInput("p2_trust_in_charity",
-            label = "Charity trust:",
+            label = "Charity Trust:",
             choices = c("No trust at all in charities",
@@
 
+#Fix
 selectInput("p2_donation_frequency",
-         label = "Donation frequency:",
+         label = "Donation Frequency:",
          choices = c('Donate more than once a month, less than once a year',
@@
 selectInput("p2_donation_amount",
-         label = "Donation amount:",
+         label = "Donation Amount:",
          choices = c("$1-$49",
@@
 
+#Fix
 selectInput("p2_volunteer_12",
-         label = "Volunteered in last 12 months:",
+         label = "Volunteered in last 12 Months:",
          choices = c("Haven't volunteered", "Have volunteered"),
@@
 
+#Fix
 selectInput("p2_volunteer_frequency",
-         label = "Volunteer frequency:",
+         label = "Volunteer Frequency:",
          choices = c("Haven't volunteered in past 12 months",
@@
 
+# fix
 selectInput("p2_personal_activism",
-         label = "Personal activism:",
+         label = "Personal Activism:",
          choices = c('Not personally involved ',
@@
 
+#Fix
 selectInput("p2_family_activism",
-         label = "Family activism:",
+         label = "Family Activism:",
          choices = c('Family not involved',
@@
 
+#Fix
 selectInput("p2_religious_member",
-         label = "Church membership:",
+         label = "Church Membership:",
          choices = c("Don't belong to church membership",
@@
 
+#Fix
 selectInput("p2_sport_member",
-         label = "Sport or recreational membership:",
+         label = "Sport or Recreational Membership:",
          choices = c("Don't belong to sports membership",
@@
          width = "450px")
-
+#Fix
 selectInput("p2_art_member",
-         label = "Art, music, or educational membership:",
+         label = "Art, Music, or Educational Membership:",
          choices = c("Don't belong to educational membership",
@@
          width = "450px")
-
+#Fix
 selectInput("p2_labor_member",
-         label = "Labor union membership:",
+         label = "Labor Union Membership:",
          choices = c("Don't belong to union",
@@
 
+#Fix
 selectInput("p2_political_member",
-         label = "Political party membership:",
+         label = "Political Party Membership:",
          choices = c("Don't belong to party",
@@
          width = "450px")
-
+# Fix
 selectInput("p2_environmental_member",
-         label = "Environmental organization membership:",
+         label = "Environmental Org. Membership:",
          choices = c("Don't belong to environmental organization",
@@
          width = "450px")
-
+# Fix
 selectInput("p2_professional_member",
-         label = "Professional membership:",
+         label = "Professional Membership:",
          choices = c("Don't belong to professional membership",
@@
          width = "450px")
-
+# Fix
 selectInput("p2_humanitarian_member",
-         label = "Humanitarian organization membership:",
+         label = "Humanitarian Org. Membership:",
          choices = c("Don't belong to humanitarian organization",
@@
 
+# Fix
 selectInput("p2_consumer_member",
-         label = "Consumer organization membership:",
+         label = "Consumer Org. Membership:",
          choices = c("Don't belong to consumer organization",
@@
          width = "450px")
-
+# Fix
 selectInput("p2_other_member",
-         label = "Other organization membership:",
+         label = "Other Org. Membership:",
          choices = c("Don't belong to other organization",
@@
 selectInput("p2_marital_status",
-         label = "Marital status:",
+         label = "Marital Status:",
          choices = c("Married",
@@
                      "Doctorate"),
-         selected = "2 year degree",
+         selected = "Some college",
          width = "450px")
@@
          multiple = TRUE,
-         selected = "White",
+         selected = "American Indian or Alaska Native",
          width = "450px")
@@
 textInput("p3_id",
-          label = "Persona name",
+          label = "Persona Name",
           value = "Persona 3",
-          placeholder = "Enter persona name",
+          placeholder = "Enter Persona Name",
           width = "450px")
@@
 
+#Fix
 selectInput("p3_travel_developing",
@@
 
+#Fix
 selectInput("p3_institution_trust",
@@
 
+# Fix
 selectInput("p3_worship_attendance",
@@
 selectInput("p3_charity_importance",
-          label = "Charity importance:",
+          label = "Charity Importance:",
           choices = c("Not at all important",
@@
 
+#Fix
 selectInput("p3_trust_in_charity",
-            label = "Charity trust:",
+            label = "Charity Trust:",
             choices = c("No trust at all in charities",
@@
 
+#Fix
 selectInput("p3_donation_frequency",
-         label = "Donation frequency:",
+         label = "Donation Frequency:",
          choices = c('Donate more than once a month, less than once a year',
@@
 selectInput("p3_donation_amount",
-         label = "Donation amount:",
+         label = "Donation Amount:",
          choices = c("$1-$49",
@@
 
+#Fix
 selectInput("p3_volunteer_12",
-         label = "Volunteered in last 12 months:",
+         label = "Volunteered in last 12 Months:",
          choices = c("Haven't volunteered", "Have volunteered"),
@@
 
+#Fix
 selectInput("p3_volunteer_frequency",
-         label = "Volunteer frequency:",
+         label = "Volunteer Frequency:",
          choices = c("Haven't volunteered in past 12 months",
@@
 
+# fix
 selectInput("p3_personal_activism",
-         label = "Personal activism:",
+         label = "Personal Activism:",
          choices = c('Not personally involved ',
@@
 
+#Fix
 selectInput("p3_family_activism",
-         label = "Family activism:",
+         label = "Family Activism:",
          choices = c('Family not involved',
@@
 
+#Fix
 selectInput("p3_religious_member",
-         label = "Church membership:",
+         label = "Church Membership:",
          choices = c("Don't belong to church membership",
@@
 
+#Fix
 selectInput("p3_sport_member",
-         label = "Sport or recreational membership:",
+         label = "Sport or Recreational Membership:",
          choices = c("Don't belong to sports membership",
@@
          width = "450px")
-
+#Fix
 selectInput("p3_art_member",
-         label = "Art, music, or educational membership:",
+         label = "Art, Music, or Educational Membership:",
          choices = c("Don't belong to educational membership",
@@
          width = "450px")
-
+#Fix
 selectInput("p3_labor_member",
-         label = "Labor union membership:",
+         label = "Labor Union Membership:",
          choices = c("Don't belong to union",
@@
 
+#Fix
 selectInput("p3_political_member",
-         label = "Political party membership:",
+         label = "Political Party Membership:",
          choices = c("Don't belong to party",
@@
          width = "450px")
-
+# Fix
 selectInput("p3_environmental_member",
-         label = "Environmental organization membership:",
+         label = "Environmental Org. Membership:",
          choices = c("Don't belong to environmental organization",
@@
          width = "450px")
-
+# Fix
 selectInput("p3_professional_member",
-         label = "Professional membership:",
+         label = "Professional Membership:",
          choices = c("Don't belong to professional membership",
@@
          width = "450px")
-
+# Fix
 selectInput("p3_humanitarian_member",
-         label = "Humanitarian organization membership:",
+         label = "Humanitarian Org. Membership:",
          choices = c("Don't belong to humanitarian organization",
@@
 
+# Fix
 selectInput("p3_consumer_member",
-         label = "Consumer organization membership:",
+         label = "Consumer Org. Membership:",
          choices = c("Don't belong to consumer organization",
@@
          width = "450px")
-
+# Fix
 selectInput("p3_other_member",
-         label = "Other organization membership:",
+         label = "Other Org. Membership:",
          choices = c("Don't belong to other organization",
@@
                      "Other (Gender)"),
-         selected = "Male",
+         selected = "Female",
          width = "450px")
@@
 selectInput("p3_marital_status",
-         label = "Marital status:",
+         label = "Marital Status:",
          choices = c("Married",
@@
                      "Doctorate"),
-         selected = "2 year degree",
+         selected = "Graduate or professional degree",
          width = "450px")
@@
          multiple = TRUE,
-         selected = "White",
+         selected = c("Black or African American", "American Indian or Alaska Native"),
          width = "450px")

### 2020-09-19 analysis/05_market_simulator.Rmd
Running again, but broken

--- 2020-09-18 analysis/05_market_simulator.Rmd
@@
 
-```{r load-data}
+```{r load-data, message=FALSE}
 # Gammas of the "everything" model
@@
 
-Market Share
+Market share
 --------------------------------------
@@
   per2_org3_exp <- exp(t(org_choice[,5]) %*% as.matrix(per2_betas))
-  per2_org3_exp <- exp(t(org_choice[,6]) %*% as.matrix(per2_betas))
+  per2_org4_exp <- exp(t(org_choice[,6]) %*% as.matrix(per2_betas))
 
@@
   # Organization name inputs
-  org_reactive[,2] <- c(input$org1_id, input$org2_id, input$org3_id, input$org4_id)
+  org_reactive[,2] <- c(input$org1_name, input$org2_name, input$org3_name, input$org4_name)
   # Expected utilities and market shares
@@
           Organization, 
-          levels = c(input$org1_id, input$org2_id, input$org3_id, input$org4_id), 
+          levels = c(input$org1_name, input$org2_name, input$org3_name, input$org4_name), 
           ordered = TRUE
@@
 
-Organizations and Personas {.tabset .tabset-fade}
+Configurations {.tabset .tabset-fade}
 --------------------------------------------------
@@
 textInput(
-  "org1_id",
+  "org1_name",
   label = "Organization Name",
@@
 textInput(
-  "org2_id",
+  "org2_name",
   label = "Organization Name",
@@
 textInput(
-  "org3_id",
+  "org3_name",
   label = "Organization Name",
@@
 textInput(
-  "org4_id",
+  "org4_name",
   label = "Organization Name",
@@
   label = "Persona Name",
-  value = "Persona 1",
+  value = "Persona 2",
   placeholder = "Enter Persona Name",
@@
   label = "Persona Name",
-  value = "Persona 1",
+  value = "Persona 3",
   placeholder = "Enter Persona Name",

### 2020-09-22 analysis/05_market_simulator.Rmd
Cleaning stuff up with Zack

@@
 
-# Initial organization configuration
-organization_data <- read_csv(
-  here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
-)
-
-# Initial persona configuration
-persona_data <- read_csv(
-  here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
-)
+# # Initial organization configuration
+# organization_data <- read_csv(
+#   here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
+# )
+# 
+# # Initial persona configuration
+# persona_data <- read_csv(
+#   here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
+# )
 ```
@@
 
-  # Empty organization reactive table
-  org_reactive <- as.data.frame(matrix(data, 24, 1))
+  # Make data into a data frame
+  plot_data <- as.data.frame(matrix(data, 24, 1))
 
   # Organization name inputs
-  org_reactive[,2] <- c(input$org1_name, input$org2_name, input$org3_name, input$org4_name)
+  plot_data[,2] <- c(input$org1_name, input$org2_name, input$org3_name, input$org4_name)
   # Expected utilities and market shares
-  org_reactive[,3] <- c(rep('Expected Utility', 4), rep('Market Share', 4))
+  plot_data[,3] <- c(rep('Expected Utility', 4), rep('Market Share', 4))
   # Persona name inputs
-  org_reactive[,4] <- c(rep(input$per1_id, 8), rep(input$per2_id, 8), rep(input$per3_id, 8))
+  plot_data[,4] <- c(rep(input$per1_id, 8), rep(input$per2_id, 8), rep(input$per3_id, 8))
 
   # Rename columns
-  colnames(org_reactive) <- c('Value', 'Organization', 'Type', 'Persona')
+  colnames(plot_data) <- c('Value', 'Organization', 'Type', 'Persona')
 
   ggplotly(
-    org_reactive %>% 
+    plot_data %>% 
       # Only care about the Market Share right now
@@
   choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
-  selected = "Emergency response",
+  selected = "Environment",
   width = "450px"
@@
   choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
-  selected = "Emergency response",
+  selected = "Human rights",
   width = "450px"
@@
   choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
-  selected = "Emergency response",
+  selected = "Refugee relief",
   width = "450px"

### 2020-09-22 analysis/05_market_simulator.Rmd
One more time

@@
 
-# # Initial organization configuration
-# organization_data <- read_csv(
-#   here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
-# )
-# 
-# # Initial persona configuration
-# persona_data <- read_csv(
-#   here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
-# )
+# Initial organization configuration
+organization_data <- read_csv(
+  here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
+)
+
+# Initial persona configuration
+persona_data <- read_csv(
+  here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
+)
 ```

### 2020-09-23 analysis/05_market_simulator.Rmd
It LIVES!

@@
 # Placeholder for organization reactive table
-org_table <- as.data.frame(matrix(rep(0), nrow = nrow(organization_data)))
+org_table <- as.data.frame(matrix(0, nrow = nrow(organization_data)))
 
@@
   org_table$org1_value <- 0
-  org_table$org1_value[org_table$levels %in% input$org1_id] <- 1
+  org_table$org1_value[org_table$levels %in% input$org1_org] <- 1
   org_table$org1_value[org_table$levels %in% input$org1_issue] <- 1
@@
   org_table$org2_value <- 0
-  org_table$org2_value[org_table$levels %in% input$org2_id] <- 1
+  org_table$org2_value[org_table$levels %in% input$org2_org] <- 1
   org_table$org2_value[org_table$levels %in% input$org2_issue] <- 1
@@
   org_table$org3_value <- 0
-  org_table$org3_value[org_table$levels %in% input$org3_id] <- 1
+  org_table$org3_value[org_table$levels %in% input$org3_org] <- 1
   org_table$org3_value[org_table$levels %in% input$org3_issue] <- 1
@@
   org_table$org4_value <- 0
-  org_table$org4_value[org_table$levels %in% input$org4_id] <- 1
+  org_table$org4_value[org_table$levels %in% input$org4_org] <- 1
   org_table$org4_value[org_table$levels %in% input$org4_issue] <- 1
@@
 # Placeholder for persona reactive table
-per_table <- as.data.frame(matrix(rep(0), nrow = nrow(persona_data)))
+per_table <- as.data.frame(matrix(0, nrow = nrow(persona_data)))
 
@@
   per_table$per1_value[per_table$levels %in% input$per1_others_charitable] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_worship_attendence] <- 1
+  per_table$per1_value[per_table$levels %in% input$per1_worship_attendance] <- 1
   per_table$per1_value[per_table$levels %in% input$per1_religion_importance] <- 1
@@
   per_table$per2_value[per_table$levels %in% input$per2_others_charitable] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_worship_attendence] <- 1
+  per_table$per2_value[per_table$levels %in% input$per2_worship_attendance] <- 1
   per_table$per2_value[per_table$levels %in% input$per2_religion_importance] <- 1
@@
   per_table$per3_value[per_table$levels %in% input$per3_others_charitable] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_worship_attendence] <- 1
+  per_table$per3_value[per_table$levels %in% input$per3_worship_attendance] <- 1
   per_table$per3_value[per_table$levels %in% input$per3_religion_importance] <- 1
@@
 
-```{r matrix-multiplication, eval=FALSE, include=FALSE}
-# # Overwrite gamma??
-# gamma <- data.frame(
-#   value = c(0,0,0),
-#   levels = c("Environment", "Human rights", "Refugee relief")
-# )
-# 
-# ui <- fluidPage(
-#   fluidRow(
-#     column(6,
-#       selectInput("org1_issue", 
-#                   label = "Select Issue Area:",
-#                   choices = gamma$levels,
-#                   multiple = TRUE)
-#     ),
-#     column(6,
-#       tableOutput("data")
-#     )
-#   )
-# )
-# 
-# server = function(input, output) {
-#   org_reactive <- reactive({
-#     gamma$value[gamma$levels %in% input$org1_issue] <- 1
-#     gamma
-#   })
-# 
-#   output$data <- renderTable({
-#     organizations()
-#   })
-# }
-```
-
-```{r Manual Testing Matrix Multiplication}
-
-# ### Calculating the Persona gammas ###
-# 
-# # Persona 1
-# persona1 <- persona_data[,2]
-# 
-# # matrix multiplication between persona data and gammas
-# gamma1 <- as.matrix(gammas) %*% as.matrix(persona1)
-# 
-# 
-# # Persona 2
-# persona2 <- persona_data[,3]
-# 
-# # matrix multiplication between persona data and gammas
-# gamma2 <- as.matrix(gammas) %*% as.matrix(persona2)
-# 
-# 
-# # Persona 3
-# persona3 <- persona_data[,4]
-# 
-# # matrix multiplication between persona data and gammas
-# gamma3 <- as.matrix(gammas) %*% as.matrix(persona3)
-# 
-# # Organization
-# org1 <- organization_data[,2]
-# 
-# org2 <- organization_data[,3]
-# 
-# org3 <- organization_data[,4]
-# 
-# org4 <- organization_data[,5]
-# 
-# # Expected utility matrix multiplication between computed persona gammas and org data for persona 1
-# per1_org1_exp <- exp(t(org1) %*% as.matrix(gamma1))
-# per1_org2_exp <- exp(t(org2) %*% as.matrix(gamma1))
-# per1_org3_exp <- exp(t(org3) %*% as.matrix(gamma1))
-# per1_org4_exp <- exp(t(org4) %*% as.matrix(gamma1))
-# 
-# # Market Share computation from expected utilities between organization
-# per1_org1_share <- 100 * per1_org1_exp/sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)
-# per1_org2_share <- 100 * per1_org2_exp/sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)
-# per1_org3_share <- 100 * per1_org3_exp/sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)
-# per1_org4_share <- 100 * per1_org4_exp/sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)
-
-```
-
 Market share
@@
   # Persona 2 market shares
-  per2_share_denom <- sum(per2_org1_exp, per2_org2_exp, per2_org3_exp, per2_org3_exp)
+  per2_share_denom <- sum(per2_org1_exp, per2_org2_exp, per2_org3_exp, per2_org4_exp)
   per2_org1_share <- 100 * (per2_org1_exp / per2_share_denom)
@@
   # Data for plotly
-  data <- c(
+  plot_data <- data.frame(
+    Value = c(
       # Persona 1
-    per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp, 
       per1_org1_share, per1_org2_share, per1_org3_share, per1_org4_share, 
       # Persona 2
-    per2_org1_exp, per2_org2_exp, per2_org3_exp, per2_org3_exp, 
       per2_org1_share, per2_org2_share, per2_org3_share, per2_org4_share,
       # Persona 3
-    per3_org1_exp, per3_org2_exp, per3_org3_exp, per3_org4_exp, 
       per3_org1_share, per3_org2_share, per3_org3_share, per3_org4_share
-  )
-
-  # Make data into a data frame
-  plot_data <- as.data.frame(matrix(data, 24, 1))
-
-  # Organization name inputs
-  plot_data[,2] <- c(input$org1_name, input$org2_name, input$org3_name, input$org4_name)
-  # Expected utilities and market shares
-  plot_data[,3] <- c(rep('Expected Utility', 4), rep('Market Share', 4))
-  # Persona name inputs
-  plot_data[,4] <- c(rep(input$per1_id, 8), rep(input$per2_id, 8), rep(input$per3_id, 8))
-
-  # Rename columns
-  colnames(plot_data) <- c('Value', 'Organization', 'Type', 'Persona')
+    ),
+    Organization = c(input$org1_name, input$org2_name, input$org3_name, input$org4_name),
+    Persona = c(
+      rep(input$per1_name, 4), 
+      rep(input$per2_name, 4), 
+      rep(input$per3_name, 4)
+    )
+  )
 
@@
     plot_data %>% 
-      # Only care about the Market Share right now
-      filter(Type == "Market Share") %>% 
-      # Factor Organization and Persona with ordered=TRUE so the order doesn't change to alphabetical as names are created
+      # Factor Organization and Persona with ordered=TRUE
       mutate(
@@
           Persona, 
-          levels = c(input$per1_id, input$per2_id, input$per3_id), 
+          levels = c(input$per1_name, input$per2_name, input$per3_name), 
           ordered = TRUE
@@
   "org1_name",
-  label = "Organization Name",
+  label = "Organization Name:",
   value = "Organization 1",
@@
 selectInput(
-  "org1_id",
-  label = "Select Organization:",
+  "org1_org",
+  label = "Organization:",
   choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
@@
   "org1_issue", 
-  label = "Select Issue Area:",
+  label = "Issue Area:",
   choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
@@
   "org1_fin_trans",
-  label = "Select Financial Transparency:",
+  label = "Financial Transparency:",
   choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
@@
   "org1_fin_account",
-  label = "Select Financial Accountability:",
+  label = "Financial Accountability:",
   choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
@@
   "org1_funding",
-  label = "Select Funding Source:",
+  label = "Funding Source:",
   choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
+  selected = "Many small private donations",
   width = "450px"
@@
   "org1_host_gov",
-  label = "Select Relationship With Host Government",
+  label = "Relationship With Host Government",
   choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
+  selected = "Friendly relationship with government",
   width = "450px"
@@
   "org2_name",
-  label = "Organization Name",
+  label = "Organization Name:",
   value = "Organization 2",
@@
 selectInput(
-  "org2_id",
-  label = "Select Organization:",
+  "org2_org",
+  label = "Organization:",
   choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
@@
   "org2_issue", 
-  label = "Select Issue Area:",
+  label = "Issue Area:",
   choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
@@
   "org2_fin_trans",
-  label = "Select Financial Transparency:",
+  label = "Financial Transparency:",
   choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
@@
   "org2_fin_account",
-  label = "Select Financial Accountability:",
+  label = "Financial Accountability:",
   choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
@@
   "org2_funding",
-  label = "Select Funding Source:",
+  label = "Funding Source:",
   choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
+  selected = "Many small private donations",
   width = "450px"
@@
   "org2_host_gov",
-  label = "Select Relationship With Host Government",
+  label = "Relationship With Host Government",
   choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
+  selected = "Friendly relationship with government",
   width = "450px"
@@
   "org3_name",
-  label = "Organization Name",
+  label = "Organization Name:",
   value = "Organization 3",
@@
 selectInput(
-  "org3_id",
-  label = "Select Organization:",
+  "org3_org",
+  label = "Organization:",
   choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
@@
   "org3_issue", 
-  label = "Select Issue Area:",
+  label = "Issue Area:",
   choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
@@
   "org3_fin_trans",
-  label = "Select Financial Transparency:",
+  label = "Financial Transparency:",
   choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
@@
   "org3_fin_account",
-  label = "Select Financial Accountability:",
+  label = "Financial Accountability:",
   choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
@@
   "org3_funding",
-  label = "Select Funding Source:",
+  label = "Funding Source:",
   choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
+  selected = "Many small private donations",
   width = "450px"
@@
   "org3_host_gov",
-  label = "Select Relationship With Host Government",
+  label = "Relationship With Host Government",
   choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
+  selected = "Friendly relationship with government",
   width = "450px"
@@
   "org4_name",
-  label = "Organization Name",
+  label = "Organization Name:",
   value = "Organization 4",
@@
 selectInput(
-  "org4_id",
-  label = "Select Organization:",
+  "org4_org",
+  label = "Organization:",
   choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
@@
   "org4_issue", 
-  label = "Select Issue Area:",
+  label = "Issue Area:",
   choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
@@
   "org4_fin_trans",
-  label = "Select Financial Transparency:",
+  label = "Financial Transparency:",
   choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
@@
   "org4_fin_account",
-  label = "Select Financial Accountability:",
+  label = "Financial Accountability:",
   choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
@@
   "org4_funding",
-  label = "Select Funding Source:",
+  label = "Funding Source:",
   choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
+  selected = "Many small private donations",
   width = "450px"
@@
   "org4_host_gov",
-  label = "Select Relationship With Host Government",
+  label = "Relationship With Host Government",
   choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
+  selected = "Friendly relationship with government",
   width = "450px"
@@
 textInput(
-  "per1_id",
-  label = "Persona Name",
+  "per1_name",
+  label = "Persona Name:",
   value = "Persona 1",
@@
 textInput(
-  "per2_id",
-  label = "Persona Name",
+  "per2_name",
+  label = "Persona Name:",
   value = "Persona 2",
@@
   ),
-  selected = "2 year degree",
+  selected = "Some college",
   width = "450px"
@@
   multiple = TRUE,
-  selected = "White",
+  selected = "American Indian or Alaskan Native",
   width = "450px"
@@
 textInput(
-  "per3_id",
-  label = "Persona Name",
+  "per3_name",
+  label = "Persona Name:",
   value = "Persona 3",
@@
   ),
-  selected = "Male",
+  selected = "Female",
   width = "450px"
@@
   ),
-  selected = "2 year degree",
+  selected = "Graduate or professional degree",
   width = "450px"
@@
   multiple = TRUE,
-  selected = "White",
+  selected = c("Black or African American", "American Indian or Alaskan Native"),
   width = "450px"

### 2020-09-24 analysis/05_market_simulator.Rmd

@@
   "Other religion",
-  # Importance of trusing charities
+  # Importance of trusting charities
   "Very unimportant",
   "Somewhat unimportant",
-  "Neutral",
+  "Neutral importance",
   "Somewhat important",
@@
   "$5,000-$9,999",
-  "$10,000 +",
+  "$10,000+",
   # Volunteered in past 12 months
@@
 })
+
+# Compute and render the market share as a table
+renderTable({
+  org_choice = org_reactive()
+  per_choice = per_reactive()
+
+  # Persona 1 predicted betas
+  per1_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,3])
+
+  # Persona 1 expected utilities
+  per1_org1_exp <- exp(t(org_choice[,3]) %*% as.matrix(per1_betas))
+  per1_org2_exp <- exp(t(org_choice[,4]) %*% as.matrix(per1_betas))
+  per1_org3_exp <- exp(t(org_choice[,5]) %*% as.matrix(per1_betas))
+  per1_org4_exp <- exp(t(org_choice[,6]) %*% as.matrix(per1_betas))
+
+  # Persona 1 market shares
+  per1_share_denom <- sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)
+  per1_org1_share <- 100 * (per1_org1_exp / per1_share_denom)
+  per1_org2_share <- 100 * (per1_org2_exp / per1_share_denom)
+  per1_org3_share <- 100 * (per1_org3_exp / per1_share_denom)
+  per1_org4_share <- 100 * (per1_org4_exp / per1_share_denom)
+
+  # Persona 2 predicted betas
+  per2_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,4])
+
+  # Persona 2 expected utilities
+  per2_org1_exp <- exp(t(org_choice[,3]) %*% as.matrix(per2_betas))
+  per2_org2_exp <- exp(t(org_choice[,4]) %*% as.matrix(per2_betas))
+  per2_org3_exp <- exp(t(org_choice[,5]) %*% as.matrix(per2_betas))
+  per2_org4_exp <- exp(t(org_choice[,6]) %*% as.matrix(per2_betas))
+
+  # Persona 2 market shares
+  per2_share_denom <- sum(per2_org1_exp, per2_org2_exp, per2_org3_exp, per2_org4_exp)
+  per2_org1_share <- 100 * (per2_org1_exp / per2_share_denom)
+  per2_org2_share <- 100 * (per2_org2_exp / per2_share_denom)
+  per2_org3_share <- 100 * (per2_org3_exp / per2_share_denom)
+  per2_org4_share <- 100 * (per2_org4_exp / per2_share_denom)
+
+  # Persona 3 predicted betas
+  per3_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,5])
+
+  # Persona 3 expected utilities
+  per3_org1_exp <- exp(t(org_choice[,3]) %*% as.matrix(per3_betas))
+  per3_org2_exp <- exp(t(org_choice[,4]) %*% as.matrix(per3_betas))
+  per3_org3_exp <- exp(t(org_choice[,5]) %*% as.matrix(per3_betas))
+  per3_org4_exp <- exp(t(org_choice[,6]) %*% as.matrix(per3_betas))
+
+  # Persona 3 market shares
+  per3_share_denom <- sum(per3_org1_exp, per3_org2_exp, per3_org3_exp, per3_org4_exp)
+  per3_org1_share <- 100 * (per3_org1_exp / per3_share_denom)
+  per3_org2_share <- 100 * (per3_org2_exp / per3_share_denom)
+  per3_org3_share <- 100 * (per3_org3_exp / per3_share_denom)
+  per3_org4_share <- 100 * (per3_org4_exp / per3_share_denom)
+
+  # Table
+  data <- data.frame(
+    Shares = c(
+      # Persona 1
+      per1_org1_share, per1_org2_share, per1_org3_share, per1_org4_share, 
+      # Persona 2
+      per2_org1_share, per2_org2_share, per2_org3_share, per2_org4_share,
+      # Persona 3
+      per3_org1_share, per3_org2_share, per3_org3_share, per3_org4_share
+    ),
+    Organization = c(input$org1_name, input$org2_name, input$org3_name, input$org4_name),
+    Persona = c(
+      rep(input$per1_name, 4), 
+      rep(input$per2_name, 4), 
+      rep(input$per3_name, 4)
+    )
+  ) %>% 
+    pivot_wider(names_from = Persona, values_from = Shares)
+
+  data
+})
 ```
@@
   choices = c(
-    "Strongly Disagree",
+    "Strongly disagree",
     "Disagree",
@@
     "Somewhat unimportant",
-    "Neutral",
+    "Neutral importance",
     "Somewhat important",
@@
   "per1_donation_amount",
-  label = "Donation Amount:",
+  label = "Donation Amount Last Year:",
   choices = c(
@@
   "per2_donation_amount",
-  label = "Donation Amount:",
+  label = "Donation Amount Last Year:",
   choices = c(
@@
   "per3_donation_amount",
-  label = "Donation Amount:",
+  label = "Donation Amount Last Year:",
   choices = c(

### 2020-09-28 analysis/05_market_simulator.Rmd
Create an export tab
Added Download Buttons into Export Tab

@@
 ```
+
+### Export
+
+```{r export}
+# Render the organization configurations as a table
+renderTable({
+  org_choice = org_reactive()
+
+  org_choice
+})
+
+# Download Button
+downloadButton("download_org", label = "Download Organization Data")
+
+downloadHandler(
+  filename = function() {
+    paste0("org_data_",Sys.time(),".csv")
+  },
+  content = function(file) {
+    write.csv(org_reactive(), file)
+  }
+)
+
+# Render the persona configurations as a table
+renderTable({
+  per_choice = per_reactive()
+
+  per_choice
+})
+
+# Download Button
+downloadButton("download_per", label = "Download Persona Data")
+
+downloadHandler(
+  filename = function() {
+    paste0("persona_data_",Sys.time(),".csv")
+  },
+  content = function(file) {
+    write.csv(per_reactive(), file)
+  }
+)
+
+```

### 2020-09-28 analysis/05_market_simulator.Rmd
Added fileInputs. Not connected to anything yet.

@@
   here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
+)
+
+# Organization file input
+fileInput(
+  "file_org",
+  "Import Organization Data"
+)
+
+# Persona file input
+fileInput(
+  "file_per",
+  "Import Persona Data"
 )

### 2020-10-05 analysis/05_market_simulator.Rmd
New tab to render imported data to make sure it worked.
Comments about next steps

@@
 org_table <- as.data.frame(matrix(0, nrow = nrow(organization_data)))
+# org_table <- reactive({read.csv(input$file_org$datapath)})
 
@@
 )
+
+# I think what we need to do to import data to fill this reactive element we need it look something like this
+
+# org_table$org1_value[where (input$file_org == 1) and the corresponding level matches %in% org_table$levels] <- 1
 
@@
 ```
+
+### Imports
+
+```{r import}
+# Render the organization configurations as a table
+renderTable({
+  org_import = read.csv(input$file_org$datapath)
+
+  org_import
+})
+
+# Render the persona configurations as a table
+renderTable({
+  per_import = read.csv(input$file_per$datapath)
+
+  per_import
+})
+
+```

### 2020-10-05 analysis/05_market_simulator.Rmd
Added references for organization and persona defaults using imported data, removed the superfluous first column, and updated indexing

--- 2020-09-28 analysis/05_market_simulator.Rmd
@@
 ```{r organization-reactive-table}
-# Placeholder for organization reactive table
-org_table <- as.data.frame(matrix(0, nrow = nrow(organization_data)))
-
 # Assign level labels
-org_table$levels = c(
+org_table <- data.frame(
+  levels = c(
     # Organization
@@
   )
+)
 
@@
 ```{r persona-reactive-table}
-# Placeholder for persona reactive table
-per_table <- as.data.frame(matrix(0, nrow = nrow(persona_data)))
-
 # Assign covariate labels
-per_table$levels <- c(
+per_table <- data.frame(
+  levels = c(
     # Intercept
@@
   # Persona 1 predicted betas
-  per1_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,3])
+  per1_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,2])
 
   # Persona 1 expected utilities
-  per1_org1_exp <- exp(t(org_choice[,3]) %*% as.matrix(per1_betas))
-  per1_org2_exp <- exp(t(org_choice[,4]) %*% as.matrix(per1_betas))
-  per1_org3_exp <- exp(t(org_choice[,5]) %*% as.matrix(per1_betas))
-  per1_org4_exp <- exp(t(org_choice[,6]) %*% as.matrix(per1_betas))
+  per1_org1_exp <- exp(t(org_choice[,2]) %*% as.matrix(per1_betas))
+  per1_org2_exp <- exp(t(org_choice[,3]) %*% as.matrix(per1_betas))
+  per1_org3_exp <- exp(t(org_choice[,4]) %*% as.matrix(per1_betas))
+  per1_org4_exp <- exp(t(org_choice[,5]) %*% as.matrix(per1_betas))
 
@@
   # Persona 2 predicted betas
-  per2_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,4])
+  per2_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,3])
 
   # Persona 2 expected utilities
-  per2_org1_exp <- exp(t(org_choice[,3]) %*% as.matrix(per2_betas))
-  per2_org2_exp <- exp(t(org_choice[,4]) %*% as.matrix(per2_betas))
-  per2_org3_exp <- exp(t(org_choice[,5]) %*% as.matrix(per2_betas))
-  per2_org4_exp <- exp(t(org_choice[,6]) %*% as.matrix(per2_betas))
+  per2_org1_exp <- exp(t(org_choice[,2]) %*% as.matrix(per2_betas))
+  per2_org2_exp <- exp(t(org_choice[,3]) %*% as.matrix(per2_betas))
+  per2_org3_exp <- exp(t(org_choice[,4]) %*% as.matrix(per2_betas))
+  per2_org4_exp <- exp(t(org_choice[,5]) %*% as.matrix(per2_betas))
 
@@
   # Persona 3 predicted betas
-  per3_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,5])
+  per3_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,4])
 
   # Persona 3 expected utilities
-  per3_org1_exp <- exp(t(org_choice[,3]) %*% as.matrix(per3_betas))
-  per3_org2_exp <- exp(t(org_choice[,4]) %*% as.matrix(per3_betas))
-  per3_org3_exp <- exp(t(org_choice[,5]) %*% as.matrix(per3_betas))
-  per3_org4_exp <- exp(t(org_choice[,6]) %*% as.matrix(per3_betas))
+  per3_org1_exp <- exp(t(org_choice[,2]) %*% as.matrix(per3_betas))
+  per3_org2_exp <- exp(t(org_choice[,3]) %*% as.matrix(per3_betas))
+  per3_org3_exp <- exp(t(org_choice[,4]) %*% as.matrix(per3_betas))
+  per3_org4_exp <- exp(t(org_choice[,5]) %*% as.matrix(per3_betas))
 
@@
   choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
-  selected = "Red Cross",
+  # selected = "Red Cross",
+  selected = as.character(organization_data[1:4,][which(organization_data[1:4,2] == 1), 1]),
   width = "450px"
@@
   choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
-  selected = "Emergency response",
+  # selected = "Emergency response",
+  selected = ifelse(
+    sum(organization_data[5:7,2]) == 0, "Emergency response",
+    as.character(organization_data[5:7,][which(organization_data[5:7,2] == 1), 1])
+  ),
   width = "450px"
@@
   multiple = TRUE,
-  selected = c("TV", "Print", "Social media"),
+  # selected = c("TV", "Print", "Social media"),
+  selected = deframe(persona_data[6:12,][which(persona_data[6:12,2] == 1), 1]),
   width = "450px"
@@
   content = function(file) {
-    write.csv(org_reactive(), file)
+    write_csv(org_reactive(), file)
   }
@@
   content = function(file) {
-    write.csv(per_reactive(), file)
+    write_csv(per_reactive(), file)
   }
@@
 ```
+
+### Imports
+
+```{r import}
+# Render the organization configurations as a table
+renderTable({
+  org_import = read_csv(input$file_org$datapath)
+
+  org_import
+})
+
+# Render the persona configurations as a table
+renderTable({
+  per_import = read_csv(input$file_per$datapath)
+
+  per_import
+})
+
+# Conditional argument to run IF new data is imported
+# organization_data <- file_org
+# persona_data <- file_per
+```

### 2020-10-08 analysis/05_market_simulator.Rmd
fixed formating error

@@
 ```{r organization-reactive-table}
+
+# Placeholder for organization reactive table
+org_table <- as.data.frame(matrix(0, nrow = nrow(organization_data)))
+# org_table <- reactive({read.csv(input$file_org$datapath)})
+
 # Assign level labels

### 2020-10-08 analysis/05_market_simulator.Rmd
Moved File Inputs to Import tab

@@
 
-# Organization file input
-fileInput(
-  "file_org",
-  "Import Organization Data"
-)
-
-# Persona file input
-fileInput(
-  "file_per",
-  "Import Persona Data"
-)
 ```
@@
 ```{r import}
+# Organization file input
+fileInput(
+  "file_org",
+  "Import Organization Data"
+)
+
+# Persona file input
+fileInput(
+  "file_per",
+  "Import Persona Data"
+)
+
 # Render the organization configurations as a table

### 2020-10-08 analysis/05_market_simulator.Rmd
Org input selected values fixed

@@
   choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
-  selected = "Engages in financial transparency",
+  # selected = "Engages in financial transparency",
+  selected = ifelse(
+    sum(organization_data[8,2]) == 0, "Doesn’t engage in financial transparency",
+    as.character(organization_data[8,][which(organization_data[8,2] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
-  selected = "Engages in financial accountability",
+  # selected = "Engages in financial accountability",
+  selected = ifelse(
+    sum(organization_data[9,2]) == 0, "Doesn’t engage in financial accountability",
+    as.character(organization_data[9,][which(organization_data[9,2] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
-  selected = "Many small private donations",
+  # selected = "Many small private donations",
+  selected = ifelse(
+    sum(organization_data[10:11,2]) == 0, "Many small private donations",
+    as.character(organization_data[10:11,][which(organization_data[10:11,2] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
-  selected = "Friendly relationship with government",
+  # selected = "Friendly relationship with government",
+  selected = ifelse(
+    sum(organization_data[12:13,2]) == 0, "Friendly relationship with government",
+    as.character(organization_data[12:13,][which(organization_data[12:13,2] == 1), 1])
+  ),
   width = "450px"
@@
   choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
-  selected = "Red Cross",
+  # selected = "Red Cross",
+  selected = as.character(organization_data[1:4,][which(organization_data[1:4,3] == 1), 1]),
   width = "450px"
@@
   choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
-  selected = "Environment",
+  # selected = "Environment",
+  selected = ifelse(
+    sum(organization_data[5:7,3]) == 0, "Emergency response",
+    as.character(organization_data[5:7,][which(organization_data[5:7,3] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
-  selected = "Engages in financial transparency",
+  # selected = "Engages in financial transparency",
+  selected = ifelse(
+    sum(organization_data[8,3]) == 0, "Doesn’t engage in financial transparency",
+    as.character(organization_data[8,][which(organization_data[8,3] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
-  selected = "Engages in financial accountability",
+  # selected = "Engages in financial accountability",
+  selected = ifelse(
+    sum(organization_data[9,3]) == 0, "Doesn’t engage in financial accountability",
+    as.character(organization_data[9,][which(organization_data[9,3] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
-  selected = "Many small private donations",
+  # selected = "Many small private donations",
+  selected = ifelse(
+    sum(organization_data[10:11,3]) == 0, "Many small private donations",
+    as.character(organization_data[10:11,][which(organization_data[10:11,3] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
-  selected = "Friendly relationship with government",
+  # selected = "Friendly relationship with government",
+  selected = ifelse(
+    sum(organization_data[12:13,3]) == 0, "Friendly relationship with government",
+    as.character(organization_data[12:13,][which(organization_data[12:13,3] == 1), 1])
+  ),
   width = "450px"
@@
   choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
-  selected = "Red Cross",
+  # selected = "Red Cross",
+  selected = as.character(organization_data[1:4,][which(organization_data[1:4,4] == 1), 1]),
   width = "450px"
@@
   choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
-  selected = "Human rights",
+  # selected = "Human rights",
+  selected = ifelse(
+    sum(organization_data[5:7,4]) == 0, "Emergency response",
+    as.character(organization_data[5:7,][which(organization_data[5:7,4] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
-  selected = "Engages in financial transparency",
+  # selected = "Engages in financial transparency",
+  selected = ifelse(
+    sum(organization_data[8,4]) == 0, "Doesn’t engage in financial transparency",
+    as.character(organization_data[8,][which(organization_data[8,4] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
-  selected = "Engages in financial accountability",
+  # selected = "Engages in financial accountability",
+  selected = ifelse(
+    sum(organization_data[9,4]) == 0, "Doesn’t engage in financial accountability",
+    as.character(organization_data[9,][which(organization_data[9,4] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
-  selected = "Many small private donations",
+  # selected = "Many small private donations",
+  selected = ifelse(
+    sum(organization_data[10:11,4]) == 0, "Many small private donations",
+    as.character(organization_data[10:11,][which(organization_data[10:11,4] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
-  selected = "Friendly relationship with government",
+  # selected = "Friendly relationship with government",
+  selected = ifelse(
+    sum(organization_data[12:13,4]) == 0, "Friendly relationship with government",
+    as.character(organization_data[12:13,][which(organization_data[12:13,4] == 1), 1])
+  ),
   width = "450px"
@@
   choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
-  selected = "Red Cross",
+  # selected = "Red Cross",
+  selected = as.character(organization_data[1:4,][which(organization_data[1:4,5] == 1), 1]),
   width = "450px"
@@
   choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
-  selected = "Refugee relief",
+  # selected = "Refugee relief",
+  selected = ifelse(
+    sum(organization_data[5:7,5]) == 0, "Emergency response",
+    as.character(organization_data[5:7,][which(organization_data[5:7,5] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
-  selected = "Engages in financial transparency",
+  # selected = "Engages in financial transparency",
+  selected = ifelse(
+    sum(organization_data[8,5]) == 0, "Doesn’t engage in financial transparency",
+    as.character(organization_data[8,][which(organization_data[8,5] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
-  selected = "Engages in financial accountability",
+  # selected = "Engages in financial accountability",
+  selected = ifelse(
+    sum(organization_data[9,5]) == 0, "Doesn’t engage in financial accountability",
+    as.character(organization_data[9,][which(organization_data[9,5] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
-  selected = "Many small private donations",
+  # selected = "Many small private donations",
+  selected = ifelse(
+    sum(organization_data[10:11,5]) == 0, "Many small private donations",
+    as.character(organization_data[10:11,][which(organization_data[10:11,5] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
-  selected = "Friendly relationship with government",
+  # selected = "Friendly relationship with government",
+  selected = ifelse(
+    sum(organization_data[12:13,5]) == 0, "Friendly relationship with government",
+    as.character(organization_data[12:13,][which(organization_data[12:13,5] == 1), 1])
+  ),
   width = "450px"

### 2020-10-08 analysis/05_market_simulator.Rmd
Working on Persona Input selected values

@@
   choices = c("Rarely", "Once a week", "At least once a day"),
-  selected = "At least once a day",
+  # selected = "At least once a day",
   width = "450px"
@@
   choices = c("Never", "Sometimes", "Always"),
-  selected = "Always",
+  # selected = "Always",
   width = "450px"
@@
   choices = c("Not Often", "Often"),
-  selected = "Often",
+  # selected = "Often",
   width = "450px"
@@
   choices = c("Hasn't traveled to a developing country", "Traveled to a developing country"),
-  selected = "Traveled to a developing country",
+  # selected = "Traveled to a developing country",
   width = "450px"
@@
   ),
-  selected = "Somewhat liberal",
+  # selected = "Somewhat liberal",
   width = "450px"
@@
   ),
-  selected = "Complete trust in political institutions",
+  # selected = "Complete trust in political institutions",
   width = "450px"
@@
   ),
-  selected = "Strongly agree",
+  # selected = "Strongly agree",
   width = "450px"
@@
   ),
-  selected = "Attend at least once a month",
+  # selected = "Attend at least once a month",
   width = "450px"
@@
   choices = c("Not important", "Important"),
-  selected = "Important",
+  # selected = "Important",
   width = "450px"
@@
   ),
-  selected = 'Protestant',
+  # selected = 'Protestant',
   width = "450px"
@@
   ),
-  selected = "Somewhat unimportant",
+  # selected = "Somewhat unimportant",
   width = "450px"
@@
   ),
-  selected = "Complete trust in charities",
+  # selected = "Complete trust in charities",
   width = "450px"
@@
   choices = c('Donate more than once a month, less than once a year', 'Donate at least once a month'),
-  selected = "Donate at least once a month",
+  # selected = "Donate at least once a month",
   width = "450px"
@@
   ),
-  selected = "$100-$499",
+  # selected = "$100-$499",
   width = "450px"
@@
   choices = c("Haven't volunteered in past 12 months", "Volunteered in past 12 months"),
-  selected = "Volunteered in past 12 months",
+  # selected = "Volunteered in past 12 months",
   width = "450px"
@@
   ),
-  selected = "Volunteer at least once a month",
+  # selected = "Volunteer at least once a month",
   width = "450px"
@@
   choices = c('Not personally involved', 'Personally involved'),
-  selected = "Personally involved",
+  # selected = "Personally involved",
   width = "450px"
@@
   choices = c('Family not involved', 'Family involved'),
-  selected = "Family involved",
+  # selected = "Family involved",
   width = "450px"
@@
   choices = c("Don't belong to church",'Inactive church member', 'Active church member'),
-  selected = "Don't belong to church",
+  # selected = "Don't belong to church",
   width = "450px"
@@
   ),
-  selected = "Don't belong to sports or rec organization",
+  # selected = "Don't belong to sports or rec organization",
   width = "450px"
@@
   ),
-  selected = "Don't belong to educational organization",
+  # selected = "Don't belong to educational organization",
   width = "450px"
@@
   choices = c("Don't belong to union", 'Inactive union member', 'Active union member'),
-  selected = "Don't belong to union",
+  # selected = "Don't belong to union",
   width = "450px"
@@
   ),
-  selected = "Active political party member",
+  # selected = "Active political party member",
   width = "450px"
@@
   ),
-  selected = "Don't belong to environmental organization",
+  # selected = "Don't belong to environmental organization",
   width = "450px"
@@
   ),
-  selected = "Don't belong to professional association",
+  # selected = "Don't belong to professional association",
   width = "450px"
@@
   ),
-  selected = "Active humanitarian or charitable organization member",
+  # selected = "Active humanitarian or charitable organization member",
   width = "450px"
@@
   ),
-  selected = "Don't belong to consumer organization",
+  # selected = "Don't belong to consumer organization",
   width = "450px"
@@
   ),
-  selected = "Don't belong to another organization",
+  # selected = "Don't belong to another organization",
   width = "450px"
@@
   ),
-  selected = "Male",
+  # selected = "Male",
   width = "450px"
@@
   ),
-  selected = "Married",
+  # selected = "Married",
   width = "450px"
@@
   ),
-  selected = "2 year degree",
+  # selected = "2 year degree",
   width = "450px"
@@
   choices = c('Less than median of $61,372', 'More than median of $61,372'),
-  selected = "More than median of $61,372",
+  # selected = "More than median of $61,372",
   width = "450px"
@@
   multiple = TRUE,
-  selected = "White",
+  # selected = "White",
+  selected = deframe(persona_data[105:110,][which(persona_data[105:110,2] == 1), 1]),
   width = "450px"
@@
   choices = c('Less than median age of 36', "More than median age of 36"),
-  selected = "Less than median age of 36",
+  # selected = "Less than median age of 36",
   width = "450px"

### 2020-10-08 analysis/05_market_simulator.Rmd
fixing persona selected values at Religious Importance

@@
   # selected = "At least once a day",
+  selected = ifelse(
+    sum(persona_data[2:3,2]) == 0, "Rarely",
+    as.character(persona_data[2:3,][which(persona_data[2:3,2] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Always",
+  selected = ifelse(
+    sum(persona_data[4:5,2]) == 0, "Never",
+    as.character(persona_data[4:5,][which(persona_data[4:5,2] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Often",
+  selected = ifelse(
+    sum(persona_data[13,2]) == 0, "Not Often",
+    as.character(persona_data[13,][which(persona_data[13,2] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Traveled to a developing country",
+  selected = ifelse(
+    sum(persona_data[14,2]) == 0, "Hasn't traveled to a developing country",
+    as.character(persona_data[14,][which(persona_data[14,2] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Somewhat liberal",
+  selected = ifelse(
+    sum(persona_data[15:20,2]) == 0, "Extremely liberal",
+    as.character(persona_data[15:20,][which(persona_data[15:20,2] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Complete trust in political institutions",
+  selected = ifelse(
+    sum(persona_data[21:26,2]) == 0, "No trust at all in political institutions",
+    as.character(persona_data[21:26,][which(persona_data[21:26,2] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Strongly agree",
+  selected = ifelse(
+    sum(persona_data[27:32,2]) == 0, "Strongly disagree",
+    as.character(persona_data[27:32,][which(persona_data[27:32,2] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Attend at least once a month",
+  selected = ifelse(
+    sum(persona_data[33:34,2]) == 0, "Not sure",
+    as.character(persona_data[33:34,][which(persona_data[33:34,2] == 1), 1])
+  ),
   width = "450px"

### 2020-10-08 analysis/05_market_simulator.Rmd
finished persona 1 input selected values

@@
   # selected = "Important",
+  selected = ifelse(
+    sum(persona_data[35,2]) == 0, "Not important",
+    as.character(persona_data[35,][which(persona_data[35,2] == 1), 1])
+  ),
   width = "450px"
@@
   "per1_religion",
+  label = "Religion:",
+  choices = c(
+    "Catholic",
+    'Protestant',
+    'Christian Orthodox',
+    'Jewish',
+    'Muslim',
+    'Sikh',
+    'Hindu',
+    'Buddhist',
+    'Atheist',
+    'Other religion'
+  ),
+  # selected = 'Protestant',
+  selected = ifelse(
+    sum(persona_data[36:44,2]) == 0, "Catholic",
+    as.character(persona_data[36:44,][which(persona_data[36:44,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Importance of trusting charities
+selectInput(
+  "per1_charity_importance",
+  label = "Charity Importance:",
+  choices = c(
+    "Not at all important",
+    "Very unimportant",
+    "Somewhat unimportant",
+    "Neutral importance",
+    "Somewhat important",
+    "Very important",
+    "Essential"
+  ),
+  # selected = "Somewhat unimportant",
+  selected = ifelse(
+    sum(persona_data[45:50,2]) == 0, "Not at all important",
+    as.character(persona_data[45:50,][which(persona_data[45:50,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Trust in charities
+selectInput(
+  "per1_trust_in_charity",
+  label = "Charity Trust:",
+  choices = c(
+    "No trust at all in charities",
+    "Very little trust in charities",
+    "Little trust in charities",
+    "Neutral trust in charities",
+    "Some trust in charities",
+    "A lot of trust in charities",
+    "Complete trust in charities"
+  ),
+  # selected = "Complete trust in charities",
+  selected = ifelse(
+    sum(persona_data[51:56,2]) == 0, "No trust at all in charities",
+    as.character(persona_data[51:56,][which(persona_data[51:56,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Donation frequency
+selectInput(
+  "per1_donation_frequency",
+  label = "Donation Frequency:",
+  choices = c('Donate more than once a month, less than once a year', 'Donate at least once a month'),
+  # selected = "Donate at least once a month",
+  selected = ifelse(
+    sum(persona_data[57,2]) == 0, "Donate more than once a month, less than once a year",
+    as.character(persona_data[57,][which(persona_data[57,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Donated last year
+selectInput(
+  "per1_donation_amount",
+  label = "Donation Amount Last Year:",
+  choices = c(
+    '$1-$49',
+    '$50-$99',
+    '$100-$499',
+    '$500-$999',
+    '$1,000-$4,999',
+    '$5,000-$9,999',
+    '$10,000+'
+  ),
+  # selected = "$100-$499",
+  selected = ifelse(
+    sum(persona_data[58:63,2]) == 0, "$1-$49",
+    as.character(persona_data[58:63,][which(persona_data[58:63,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Volunteered in past 12 months
+selectInput(
+  "per1_volunteer_12",
+  label = "Volunteered in last 12 Months:",
+  choices = c("Haven't volunteered in past 12 months", "Volunteered in past 12 months"),
+  # selected = "Volunteered in past 12 months",
+  selected = ifelse(
+    sum(persona_data[64,2]) == 0, "Haven't volunteered in past 12 months",
+    as.character(persona_data[64,][which(persona_data[64,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Volunteer frequency
+selectInput(
+  "per1_volunteer_frequency",
+  label = "Volunteer Frequency:",
+  choices = c(
+    "Haven't volunteered in past 12 months",
+    "Rarely volunteer",
+    "Volunteer more than once a month, less than once a year",
+    "Volunteer at least once a month"
+  ),
+  # selected = "Volunteer at least once a month",
+  selected = ifelse(
+    sum(persona_data[65:67,2]) == 0, "Haven't volunteered in past 12 months",
+    as.character(persona_data[65:67,][which(persona_data[65:67,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# History of activism
+selectInput(
+  "per1_personal_activism",
+  label = "Personal Activism:",
+  choices = c('Not personally involved', 'Personally involved'),
+  # selected = "Personally involved",
+  selected = ifelse(
+    sum(persona_data[68,2]) == 0, "Not personally involved",
+    as.character(persona_data[68,][which(persona_data[68,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# History of family activism
+selectInput(
+  "per1_family_activism",
+  label = "Family Activism:",
+  choices = c('Family not involved', 'Family involved'),
+  # selected = "Family involved",
+  selected = ifelse(
+    sum(persona_data[69,2]) == 0, "Family not involved",
+    as.character(persona_data[69,][which(persona_data[69,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Church or religious organization
+selectInput(
+  "per1_religious_member",
+  label = "Church Membership:",
+  choices = c("Don't belong to church",'Inactive church member', 'Active church member'),
+  # selected = "Don't belong to church",
+  selected = ifelse(
+    sum(persona_data[70:71,2]) == 0, "Don't belong to church",
+    as.character(persona_data[70:71,][which(persona_data[70:71,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Sport or recreational organization
+selectInput(
+  "per1_sport_member",
+  label = "Sport or Recreational Membership:",
+  choices = c(
+    "Don't belong to sports or rec organization", 
+    'Inactive sports or rec organization member',
+    'Active sports or rec organization member'
+  ),
+  # selected = "Don't belong to sports or rec organization",
+  selected = ifelse(
+    sum(persona_data[72:73,2]) == 0, "Don't belong to sports or rec organization",
+    as.character(persona_data[72:73,][which(persona_data[72:73,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Art, music, or educational organization
+selectInput(
+  "per1_art_member",
+  label = "Art, Music, or Educational Membership:",
+  choices = c(
+    "Don't belong to educational organization",
+    'Inactive art, music, or educational organization member',
+    'Active art, music, or educational organization member'
+  ),
+  # selected = "Don't belong to educational organization",
+  selected = ifelse(
+    sum(persona_data[74:75,2]) == 0, "Don't belong to educational organization",
+    as.character(persona_data[74:75,][which(persona_data[74:75,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Labor union
+selectInput(
+  "per1_labor_member",
+  label = "Labor Union Membership:",
+  choices = c(
+    "Don't belong to union",
+    'Inactive union member', 
+    'Active union member'
+  ),
+  # selected = "Don't belong to union",
+  selected = ifelse(
+    sum(persona_data[76:77,2]) == 0, "Don't belong to union",
+    as.character(persona_data[76:77,][which(persona_data[76:77,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Political party
+selectInput(
+  "per1_political_member",
+  label = "Political Party Membership:",
+  choices = c(
+    "Don't belong to political party",
+    'Inactive political party member',
+    'Active political party member'
+  ),
+  # selected = "Active political party member",
+  selected = ifelse(
+    sum(persona_data[78:79,2]) == 0, "Don't belong to political party",
+    as.character(persona_data[78:79,][which(persona_data[78:79,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Environmental organization
+selectInput(
+  "per1_environmental_member",
+  label = "Environmental Organization Membership:",
+  choices = c(
+    "Don't belong to environmental organization",
+    'Inactive environmental organization member',
+    'Active environmental organization member'
+  ),
+  # selected = "Don't belong to environmental organization",
+  selected = ifelse(
+    sum(persona_data[80:81,2]) == 0, "Don't belong to environmental organization",
+    as.character(persona_data[80:81,][which(persona_data[80:81,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Professional association
+selectInput(
+  "per1_professional_member",
+  label = "Professional Association Membership:",
+  choices = c(
+    "Don't belong to professional association",
+    'Inactive professional association member',
+    'Active professional association member'
+  ),
+  # selected = "Don't belong to professional association",
+  selected = ifelse(
+    sum(persona_data[82:83,2]) == 0, "Don't belong to professional association",
+    as.character(persona_data[82:83,][which(persona_data[82:83,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Humanitarian or charitable organization
+selectInput(
+  "per1_humanitarian_member",
+  label = "Humanitarian or Charitable Organization Membership:",
+  choices = c(
+    "Don't belong to humanitarian or charitable organization",
+    'Inactive humanitarian or charitable organization member',
+    'Active humanitarian or charitable organization member'
+  ),
+  # selected = "Active humanitarian or charitable organization member",
+  selected = ifelse(
+    sum(persona_data[84:85,2]) == 0, "Don't belong to humanitarian or charitable organization",
+    as.character(persona_data[84:85,][which(persona_data[84:85,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Consumer organization
+selectInput(
+  "per1_consumer_member",
+  label = "Consumer Organization Membership:",
+  choices = c(
+    "Don't belong to consumer organization",
+    'Inactive consumer organization member',
+    'Active consumer organization member'
+  ),
+  # selected = "Don't belong to consumer organization",
+  selected = ifelse(
+    sum(persona_data[86:87,2]) == 0, "Don't belong to consumer organization",
+    as.character(persona_data[86:87,][which(persona_data[86:87,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Other organization
+selectInput(
+  "per1_other_member",
+  label = "Other Organization Membership:",
+  choices = c(
+    "Don't belong to another organization",
+    'Inactive member in another organization',
+    'Active member in another organization'
+  ),
+  # selected = "Don't belong to another organization",
+  selected = ifelse(
+    sum(persona_data[88:89,2]) == 0, "Don't belong to another organization",
+    as.character(persona_data[88:89,][which(persona_data[88:89,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Gender
+selectInput(
+  "per1_gender",
+  label = "Gender:",
+  choices = c(
+    "Male",
+    "Female",
+    "Transgender",
+    "Prefer not to say",
+    "Other gender"
+  ),
+  # selected = "Male",
+  selected = ifelse(
+    sum(persona_data[90:93,2]) == 0, "Male",
+    as.character(persona_data[90:93,][which(persona_data[90:93,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Marital status
+selectInput(
+  "per1_marital_status",
+  label = "Marital Status:",
+  choices = c(
+    "Married",
+    "Widowed",
+    "Divorced",
+    "Separated",
+    "Never married"
+  ),
+  # selected = "Married",
+  selected = ifelse(
+    sum(persona_data[94:97,2]) == 0, "Married",
+    as.character(persona_data[94:97,][which(persona_data[94:97,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Education
+selectInput(
+  "per1_education",
+  label = "Education:",
+  choices = c(
+    "Less than high school",
+    "High school graduate",
+    "Some college",
+    "2 year degree",
+    "4 year degree",
+    "Graduate or professional degree",
+    "Doctorate"
+  ),
+  # selected = "2 year degree",
+  selected = ifelse(
+    sum(persona_data[98:103,2]) == 0, "Less than high school",
+    as.character(persona_data[98:103,][which(persona_data[98:103,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Income
+selectInput(
+  "per1_income",
+  label = "Income:",
+  choices = c('Less than median of $61,372', 'More than median of $61,372'),
+  # selected = "More than median of $61,372",
+  selected = ifelse(
+    sum(persona_data[104,2]) == 0, "Less than median of $61,372",
+    as.character(persona_data[104,][which(persona_data[104,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+# Race
+selectInput(
+  "per1_race",
+  label = "Race:",
+  choices = c(
+    'White',
+    'Black or African American',
+    'American Indian or Alaskan Native',
+    'Asian',
+    'Native Hawaiian or Pacific Islander',
+    'Other race'
+  ),
+  multiple = TRUE,
+  # selected = "White",
+  selected = deframe(persona_data[105:110,][which(persona_data[105:110,2] == 1), 1]),
+  width = "450px"
+)
+
+# Age
+selectInput(
+  "per1_age",
+  label = "Age:",
+  choices = c('Less than median age of 36', "More than median age of 36"),
+  # selected = "Less than median age of 36",
+  selected = ifelse(
+    sum(persona_data[111,2]) == 0, "Less than median age of 36",
+    as.character(persona_data[111,][which(persona_data[111,2] == 1), 1])
+  ),
+  width = "450px"
+)
+```
+
+### Persona 2
+
+```{r per2-inputs}
+# Naming
+textInput(
+  "per2_name",
+  label = "Persona Name:",
+  value = "Persona 2",
+  placeholder = "Enter Persona Name",
+  width = "450px"
+)
+
+# Follow national news
+selectInput(
+  "per2_national_news",
+  label = "Follow national news:",
+  choices = c("Rarely", "Once a week", "At least once a day"),
+  selected = "At least once a day",
+  width = "450px"
+)
+
+# Follow international news
+selectInput(
+  "per2_international_news",
+  label = "Follow international news:",
+  choices = c("Never", "Sometimes", "Always"),
+  selected = "Always",
+  width = "450px"
+)
+
+# Mediums to follow news
+selectInput(
+  "per2_news_medium",
+  label = "Medium to follow news:",
+  choices = c(
+    "TV",
+    "Print",
+    "Online (not social media)",
+    "Social media",
+    "Radio",
+    "Email newsletter",
+    "News app"
+  ),
+  multiple = TRUE,
+  selected = c("TV", "Print", "Social media"),
+  width = "450px"
+)
+
+# Follow government and public affairs
+selectInput(
+  "per2_follow_gov",
+  label = "Follow government & public affairs:",
+  choices = c("Not Often", "Often"),
+  selected = "Often",
+  width = "450px"
+)
+
+# Traveled to a developing country
+selectInput(
+  "per2_travel_developing",
+  label = "Travel to developing country:",
+  choices = c("Hasn't traveled to a developing country", "Traveled to a developing country"),
+  selected = "Traveled to a developing country",
+  width = "450px"
+)
+
+# Liberal to Conservative
+selectInput(
+  "per2_political_pref",
+  label = "Political views from liberal to conservative:",
+  choices = c(
+    "Extremely liberal",
+    "Somewhat liberal",
+    "Slightly liberal",
+    "Moderate",
+    "Slightly conservative",
+    "Somewhat conservative",
+    "Extremely conservative"
+  ),
+  selected = "Somewhat liberal",
+  width = "450px"
+)
+
+# Trust in political institutions
+selectInput(
+  "per2_institution_trust",
+  label = "Political institution trust from none to complete:",
+  choices = c(
+    "No trust at all in political institutions",
+    "Very little trust in political institutions",
+    "Little trust in political institutions",
+    "Neutral trust in political institutions",
+    "Some trust in political institutions",
+    "A lot of trust in political institutions",
+    "Complete trust in political institutions"
+  ),
+  selected = "Complete trust in political institutions",
+  width = "450px"
+)
+
+# People should be more charitable
+selectInput(
+  "per2_others_charitable",
+  label = "People should be more charitable:",
+  choices = c(
+    "Strongly disagree",
+    "Disagree",
+    "Somewhat disagree",
+    "Neutral",
+    "Somewhat agree",
+    "Agree",
+    "Strongly agree"
+  ),
+  selected = "Strongly agree",
+  width = "450px"
+)
+
+# Religious attendance
+selectInput(
+  "per2_worship_attendance",
+  label = "Worship service attendance:",
+  choices = c(
+    "Not sure",
+    "Rarely attend",
+    "Attend at least once a month"
+  ),
+  selected = "Attend at least once a month",
+  width = "450px"
+)
+
+# Importance of religion
+selectInput(
+  "per2_religion_importance",
+  label = "Importance of religion:",
+  choices = c("Not important", "Important"),
+  selected = "Important",
+  width = "450px"
+)
+
+# Religion
+selectInput(
+  "per2_religion",
   label = "Religion:",
@@
   ),
-  # selected = 'Protestant',
+  selected = 'Protestant',
   width = "450px"
@@
 selectInput(
-  "per1_charity_importance",
+  "per2_charity_importance",
   label = "Charity Importance:",
@@
   ),
-  # selected = "Somewhat unimportant",
+  selected = "Somewhat unimportant",
   width = "450px"
@@
 selectInput(
-  "per1_trust_in_charity",
+  "per2_trust_in_charity",
   label = "Charity Trust:",
@@
   ),
-  # selected = "Complete trust in charities",
+  selected = "Complete trust in charities",
   width = "450px"
@@
 selectInput(
-  "per1_donation_frequency",
+  "per2_donation_frequency",
   label = "Donation Frequency:",
   choices = c('Donate more than once a month, less than once a year', 'Donate at least once a month'),
-  # selected = "Donate at least once a month",
+  selected = "Donate at least once a month",
   width = "450px"
@@
 selectInput(
-  "per1_donation_amount",
+  "per2_donation_amount",
   label = "Donation Amount Last Year:",
@@
   ),
-  # selected = "$100-$499",
+  selected = "$100-$499",
   width = "450px"
@@
 selectInput(
-  "per1_volunteer_12",
+  "per2_volunteer_12",
   label = "Volunteered in last 12 Months:",
   choices = c("Haven't volunteered in past 12 months", "Volunteered in past 12 months"),
-  # selected = "Volunteered in past 12 months",
+  selected = "Volunteered in past 12 months",
   width = "450px"
@@
 selectInput(
-  "per1_volunteer_frequency",
+  "per2_volunteer_frequency",
   label = "Volunteer Frequency:",
@@
   ),
-  # selected = "Volunteer at least once a month",
+  selected = "Volunteer at least once a month",
   width = "450px"
@@
 selectInput(
-  "per1_personal_activism",
+  "per2_personal_activism",
   label = "Personal Activism:",
   choices = c('Not personally involved', 'Personally involved'),
-  # selected = "Personally involved",
+  selected = "Personally involved",
   width = "450px"
@@
 selectInput(
-  "per1_family_activism",
+  "per2_family_activism",
   label = "Family Activism:",
   choices = c('Family not involved', 'Family involved'),
-  # selected = "Family involved",
+  selected = "Family involved",
   width = "450px"
@@
 selectInput(
-  "per1_religious_member",
+  "per2_religious_member",
   label = "Church Membership:",
   choices = c("Don't belong to church",'Inactive church member', 'Active church member'),
-  # selected = "Don't belong to church",
+  selected = "Don't belong to church",
   width = "450px"
@@
 selectInput(
-  "per1_sport_member",
+  "per2_sport_member",
   label = "Sport or Recreational Membership:",
@@
   ),
-  # selected = "Don't belong to sports or rec organization",
+  selected = "Don't belong to sports or rec organization",
   width = "450px"
@@
 selectInput(
-  "per1_art_member",
+  "per2_art_member",
   label = "Art, Music, or Educational Membership:",
@@
   ),
-  # selected = "Don't belong to educational organization",
+  selected = "Don't belong to educational organization",
   width = "450px"
@@
 selectInput(
-  "per1_labor_member",
+  "per2_labor_member",
   label = "Labor Union Membership:",
   choices = c("Don't belong to union", 'Inactive union member', 'Active union member'),
-  # selected = "Don't belong to union",
+  selected = "Don't belong to union",
   width = "450px"
@@
 selectInput(
-  "per1_political_member",
+  "per2_political_member",
   label = "Political Party Membership:",
@@
   ),
-  # selected = "Active political party member",
+  selected = "Active political party member",
   width = "450px"
@@
 selectInput(
-  "per1_environmental_member",
+  "per2_environmental_member",
   label = "Environmental Organization Membership:",
@@
   ),
-  # selected = "Don't belong to environmental organization",
+  selected = "Don't belong to environmental organization",
   width = "450px"
@@
 selectInput(
-  "per1_professional_member",
+  "per2_professional_member",
   label = "Professional Association Membership:",
@@
   ),
-  # selected = "Don't belong to professional association",
+  selected = "Don't belong to professional association",
   width = "450px"
@@
 selectInput(
-  "per1_humanitarian_member",
+  "per2_humanitarian_member",
   label = "Humanitarian or Charitable Organization Membership:",
@@
   ),
-  # selected = "Active humanitarian or charitable organization member",
+  selected = "Active humanitarian or charitable organization member",
   width = "450px"
@@
 selectInput(
-  "per1_consumer_member",
+  "per2_consumer_member",
   label = "Consumer Organization Membership:",
@@
   ),
-  # selected = "Don't belong to consumer organization",
+  selected = "Don't belong to consumer organization",
   width = "450px"
@@
 selectInput(
-  "per1_other_member",
+  "per2_other_member",
   label = "Other Organization Membership:",
@@
   ),
-  # selected = "Don't belong to another organization",
+  selected = "Don't belong to another organization",
   width = "450px"
@@
 selectInput(
-  "per1_gender",
+  "per2_gender",
   label = "Gender:",
@@
   ),
-  # selected = "Male",
+  selected = "Male",
   width = "450px"
@@
 selectInput(
-  "per1_marital_status",
+  "per2_marital_status",
   label = "Marital Status:",
@@
   ),
-  # selected = "Married",
+  selected = "Married",
   width = "450px"
@@
 selectInput(
-  "per1_education",
+  "per2_education",
   label = "Education:",
@@
   ),
-  # selected = "2 year degree",
+  selected = "Some college",
   width = "450px"
@@
 selectInput(
-  "per1_income",
+  "per2_income",
   label = "Income:",
   choices = c('Less than median of $61,372', 'More than median of $61,372'),
-  # selected = "More than median of $61,372",
+  selected = "More than median of $61,372",
   width = "450px"
@@
 selectInput(
-  "per1_race",
+  "per2_race",
   label = "Race:",
@@
   multiple = TRUE,
-  # selected = "White",
-  selected = deframe(persona_data[105:110,][which(persona_data[105:110,2] == 1), 1]),
+  selected = "American Indian or Alaskan Native",
   width = "450px"
@@
 selectInput(
-  "per1_age",
+  "per2_age",
   label = "Age:",
   choices = c('Less than median age of 36', "More than median age of 36"),
-  # selected = "Less than median age of 36",
+  selected = "Less than median age of 36",
   width = "450px"
@@
 
-### Persona 2
-
-```{r per2-inputs}
+### Persona 3
+
+```{r per3-inputs}
 # Naming
 textInput(
-  "per2_name",
+  "per3_name",
   label = "Persona Name:",
-  value = "Persona 2",
+  value = "Persona 3",
   placeholder = "Enter Persona Name",
@@
 selectInput(
-  "per2_national_news",
+  "per3_national_news",
   label = "Follow national news:",
@@
 selectInput(
-  "per2_international_news",
+  "per3_international_news",
   label = "Follow international news:",
@@
 selectInput(
-  "per2_news_medium",
+  "per3_news_medium",
   label = "Medium to follow news:",
@@
 selectInput(
-  "per2_follow_gov",
+  "per3_follow_gov",
   label = "Follow government & public affairs:",
@@
 selectInput(
-  "per2_travel_developing",
+  "per3_travel_developing",
   label = "Travel to developing country:",
@@
 selectInput(
-  "per2_political_pref",
+  "per3_political_pref",
   label = "Political views from liberal to conservative:",
@@
 selectInput(
-  "per2_institution_trust",
+  "per3_institution_trust",
   label = "Political institution trust from none to complete:",
@@
 selectInput(
-  "per2_others_charitable",
+  "per3_others_charitable",
   label = "People should be more charitable:",
@@
 selectInput(
-  "per2_worship_attendance",
+  "per3_worship_attendance",
   label = "Worship service attendance:",
@@
 selectInput(
-  "per2_religion_importance",
+  "per3_religion_importance",
   label = "Importance of religion:",
@@
 selectInput(
-  "per2_religion",
+  "per3_religion",
   label = "Religion:",
@@
 selectInput(
-  "per2_charity_importance",
+  "per3_charity_importance",
   label = "Charity Importance:",
@@
 selectInput(
-  "per2_trust_in_charity",
+  "per3_trust_in_charity",
   label = "Charity Trust:",
@@
 selectInput(
-  "per2_donation_frequency",
+  "per3_donation_frequency",
   label = "Donation Frequency:",
@@
 selectInput(
-  "per2_donation_amount",
+  "per3_donation_amount",
   label = "Donation Amount Last Year:",
@@
 selectInput(
-  "per2_volunteer_12",
+  "per3_volunteer_12",
   label = "Volunteered in last 12 Months:",
@@
 selectInput(
-  "per2_volunteer_frequency",
+  "per3_volunteer_frequency",
   label = "Volunteer Frequency:",
@@
 selectInput(
-  "per2_personal_activism",
+  "per3_personal_activism",
   label = "Personal Activism:",
@@
 selectInput(
-  "per2_family_activism",
+  "per3_family_activism",
   label = "Family Activism:",
@@
 selectInput(
-  "per2_religious_member",
+  "per3_religious_member",
   label = "Church Membership:",
@@
 selectInput(
-  "per2_sport_member",
+  "per3_sport_member",
   label = "Sport or Recreational Membership:",
@@
 selectInput(
-  "per2_art_member",
+  "per3_art_member",
   label = "Art, Music, or Educational Membership:",
@@
 selectInput(
-  "per2_labor_member",
+  "per3_labor_member",
   label = "Labor Union Membership:",
@@
 selectInput(
-  "per2_political_member",
+  "per3_political_member",
   label = "Political Party Membership:",
@@
 selectInput(
-  "per2_environmental_member",
+  "per3_environmental_member",
   label = "Environmental Organization Membership:",
@@
 selectInput(
-  "per2_professional_member",
+  "per3_professional_member",
   label = "Professional Association Membership:",
@@
 selectInput(
-  "per2_humanitarian_member",
+  "per3_humanitarian_member",
   label = "Humanitarian or Charitable Organization Membership:",
@@
 selectInput(
-  "per2_consumer_member",
+  "per3_consumer_member",
   label = "Consumer Organization Membership:",
@@
 selectInput(
-  "per2_other_member",
+  "per3_other_member",
   label = "Other Organization Membership:",
@@
 selectInput(
-  "per2_gender",
+  "per3_gender",
   label = "Gender:",
@@
 selectInput(
-  "per2_marital_status",
+  "per3_marital_status",
   label = "Marital Status:",
@@
 selectInput(
-  "per2_education",
+  "per3_education",
   label = "Education:",
@@
   ),
-  selected = "Some college",
-  width = "450px"
-)
-
-# Income
-selectInput(
-  "per2_income",
-  label = "Income:",
-  choices = c('Less than median of $61,372', 'More than median of $61,372'),
-  selected = "More than median of $61,372",
-  width = "450px"
-)
-
-# Race
-selectInput(
-  "per2_race",
-  label = "Race:",
-  choices = c(
-    'White',
-    'Black or African American',
-    'American Indian or Alaskan Native',
-    'Asian',
-    'Native Hawaiian or Pacific Islander',
-    'Other race'
-  ),
-  multiple = TRUE,
-  selected = "American Indian or Alaskan Native",
-  width = "450px"
-)
-
-# Age
-selectInput(
-  "per2_age",
-  label = "Age:",
-  choices = c('Less than median age of 36', "More than median age of 36"),
-  selected = "Less than median age of 36",
-  width = "450px"
-)
-```
-
-### Persona 3
-
-```{r per3-inputs}
-# Naming
-textInput(
-  "per3_name",
-  label = "Persona Name:",
-  value = "Persona 3",
-  placeholder = "Enter Persona Name",
-  width = "450px"
-)
-
-# Follow national news
-selectInput(
-  "per3_national_news",
-  label = "Follow national news:",
-  choices = c("Rarely", "Once a week", "At least once a day"),
-  selected = "At least once a day",
-  width = "450px"
-)
-
-# Follow international news
-selectInput(
-  "per3_international_news",
-  label = "Follow international news:",
-  choices = c("Never", "Sometimes", "Always"),
-  selected = "Always",
-  width = "450px"
-)
-
-# Mediums to follow news
-selectInput(
-  "per3_news_medium",
-  label = "Medium to follow news:",
-  choices = c(
-    "TV",
-    "Print",
-    "Online (not social media)",
-    "Social media",
-    "Radio",
-    "Email newsletter",
-    "News app"
-  ),
-  multiple = TRUE,
-  selected = c("TV", "Print", "Social media"),
-  width = "450px"
-)
-
-# Follow government and public affairs
-selectInput(
-  "per3_follow_gov",
-  label = "Follow government & public affairs:",
-  choices = c("Not Often", "Often"),
-  selected = "Often",
-  width = "450px"
-)
-
-# Traveled to a developing country
-selectInput(
-  "per3_travel_developing",
-  label = "Travel to developing country:",
-  choices = c("Hasn't traveled to a developing country", "Traveled to a developing country"),
-  selected = "Traveled to a developing country",
-  width = "450px"
-)
-
-# Liberal to Conservative
-selectInput(
-  "per3_political_pref",
-  label = "Political views from liberal to conservative:",
-  choices = c(
-    "Extremely liberal",
-    "Somewhat liberal",
-    "Slightly liberal",
-    "Moderate",
-    "Slightly conservative",
-    "Somewhat conservative",
-    "Extremely conservative"
-  ),
-  selected = "Somewhat liberal",
-  width = "450px"
-)
-
-# Trust in political institutions
-selectInput(
-  "per3_institution_trust",
-  label = "Political institution trust from none to complete:",
-  choices = c(
-    "No trust at all in political institutions",
-    "Very little trust in political institutions",
-    "Little trust in political institutions",
-    "Neutral trust in political institutions",
-    "Some trust in political institutions",
-    "A lot of trust in political institutions",
-    "Complete trust in political institutions"
-  ),
-  selected = "Complete trust in political institutions",
-  width = "450px"
-)
-
-# People should be more charitable
-selectInput(
-  "per3_others_charitable",
-  label = "People should be more charitable:",
-  choices = c(
-    "Strongly disagree",
-    "Disagree",
-    "Somewhat disagree",
-    "Neutral",
-    "Somewhat agree",
-    "Agree",
-    "Strongly agree"
-  ),
-  selected = "Strongly agree",
-  width = "450px"
-)
-
-# Religious attendance
-selectInput(
-  "per3_worship_attendance",
-  label = "Worship service attendance:",
-  choices = c(
-    "Not sure",
-    "Rarely attend",
-    "Attend at least once a month"
-  ),
-  selected = "Attend at least once a month",
-  width = "450px"
-)
-
-# Importance of religion
-selectInput(
-  "per3_religion_importance",
-  label = "Importance of religion:",
-  choices = c("Not important", "Important"),
-  selected = "Important",
-  width = "450px"
-)
-
-# Religion
-selectInput(
-  "per3_religion",
-  label = "Religion:",
-  choices = c(
-    'Catholic',
-    'Protestant',
-    'Christian Orthodox',
-    'Jewish',
-    'Muslim',
-    'Sikh',
-    'Hindu',
-    'Buddhist',
-    'Atheist',
-    'Other religion'
-  ),
-  selected = 'Protestant',
-  width = "450px"
-)
-
-# Importance of trusting charities
-selectInput(
-  "per3_charity_importance",
-  label = "Charity Importance:",
-  choices = c(
-    "Not at all important",
-    "Very unimportant",
-    "Somewhat unimportant",
-    "Neutral importance",
-    "Somewhat important",
-    "Very important",
-    "Essential"
-  ),
-  selected = "Somewhat unimportant",
-  width = "450px"
-)
-
-# Trust in charities
-selectInput(
-  "per3_trust_in_charity",
-  label = "Charity Trust:",
-  choices = c(
-    "No trust at all in charities",
-    "Very little trust in charities",
-    "Little trust in charities",
-    "Neutral trust in charities",
-    "Some trust in charities",
-    "A lot of trust in charities",
-    "Complete trust in charities"
-  ),
-  selected = "Complete trust in charities",
-  width = "450px"
-)
-
-# Donation frequency
-selectInput(
-  "per3_donation_frequency",
-  label = "Donation Frequency:",
-  choices = c('Donate more than once a month, less than once a year', 'Donate at least once a month'),
-  selected = "Donate at least once a month",
-  width = "450px"
-)
-
-# Donated last year
-selectInput(
-  "per3_donation_amount",
-  label = "Donation Amount Last Year:",
-  choices = c(
-    '$1-$49',
-    '$50-$99',
-    '$100-$499',
-    '$500-$999',
-    '$1,000-$4,999',
-    '$5,000-$9,999',
-    '$10,000+'
-  ),
-  selected = "$100-$499",
-  width = "450px"
-)
-
-# Volunteered in past 12 months
-selectInput(
-  "per3_volunteer_12",
-  label = "Volunteered in last 12 Months:",
-  choices = c("Haven't volunteered in past 12 months", "Volunteered in past 12 months"),
-  selected = "Volunteered in past 12 months",
-  width = "450px"
-)
-
-# Volunteer frequency
-selectInput(
-  "per3_volunteer_frequency",
-  label = "Volunteer Frequency:",
-  choices = c(
-    "Haven't volunteered in past 12 months",
-    "Rarely volunteer",
-    "Volunteer more than once a month, less than once a year",
-    "Volunteer at least once a month"
-  ),
-  selected = "Volunteer at least once a month",
-  width = "450px"
-)
-
-# History of activism
-selectInput(
-  "per3_personal_activism",
-  label = "Personal Activism:",
-  choices = c('Not personally involved', 'Personally involved'),
-  selected = "Personally involved",
-  width = "450px"
-)
-
-# History of family activism
-selectInput(
-  "per3_family_activism",
-  label = "Family Activism:",
-  choices = c('Family not involved', 'Family involved'),
-  selected = "Family involved",
-  width = "450px"
-)
-
-# Church or religious organization
-selectInput(
-  "per3_religious_member",
-  label = "Church Membership:",
-  choices = c("Don't belong to church",'Inactive church member', 'Active church member'),
-  selected = "Don't belong to church",
-  width = "450px"
-)
-
-# Sport or recreational organization
-selectInput(
-  "per3_sport_member",
-  label = "Sport or Recreational Membership:",
-  choices = c(
-    "Don't belong to sports or rec organization", 
-    'Inactive sports or rec organization member',
-    'Active sports or rec organization member'
-  ),
-  selected = "Don't belong to sports or rec organization",
-  width = "450px"
-)
-
-# Art, music, or educational organization
-selectInput(
-  "per3_art_member",
-  label = "Art, Music, or Educational Membership:",
-  choices = c(
-    "Don't belong to educational organization",
-    'Inactive art, music, or educational organization member',
-    'Active art, music, or educational organization member'
-  ),
-  selected = "Don't belong to educational organization",
-  width = "450px"
-)
-
-# Labor union
-selectInput(
-  "per3_labor_member",
-  label = "Labor Union Membership:",
-  choices = c("Don't belong to union", 'Inactive union member', 'Active union member'),
-  selected = "Don't belong to union",
-  width = "450px"
-)
-
-# Political party
-selectInput(
-  "per3_political_member",
-  label = "Political Party Membership:",
-  choices = c(
-    "Don't belong to political party",
-    'Inactive political party member',
-    'Active political party member'
-  ),
-  selected = "Active political party member",
-  width = "450px"
-)
-
-# Environmental organization
-selectInput(
-  "per3_environmental_member",
-  label = "Environmental Organization Membership:",
-  choices = c(
-    "Don't belong to environmental organization",
-    'Inactive environmental organization member',
-    'Active environmental organization member'
-  ),
-  selected = "Don't belong to environmental organization",
-  width = "450px"
-)
-
-# Professional association
-selectInput(
-  "per3_professional_member",
-  label = "Professional Association Membership:",
-  choices = c(
-    "Don't belong to professional association",
-    'Inactive professional association member',
-    'Active professional association member'
-  ),
-  selected = "Don't belong to professional association",
-  width = "450px"
-)
-
-# Humanitarian or charitable organization
-selectInput(
-  "per3_humanitarian_member",
-  label = "Humanitarian or Charitable Organization Membership:",
-  choices = c(
-    "Don't belong to humanitarian or charitable organization",
-    'Inactive humanitarian or charitable organization member',
-    'Active humanitarian or charitable organization member'
-  ),
-  selected = "Active humanitarian or charitable organization member",
-  width = "450px"
-)
-
-# Consumer organization
-selectInput(
-  "per3_consumer_member",
-  label = "Consumer Organization Membership:",
-  choices = c(
-    "Don't belong to consumer organization",
-    'Inactive consumer organization member',
-    'Active consumer organization member'
-  ),
-  selected = "Don't belong to consumer organization",
-  width = "450px"
-)
-
-# Other organization
-selectInput(
-  "per3_other_member",
-  label = "Other Organization Membership:",
-  choices = c(
-    "Don't belong to another organization",
-    'Inactive member in another organization',
-    'Active member in another organization'
-  ),
-  selected = "Don't belong to another organization",
-  width = "450px"
-)
-
-# Gender
-selectInput(
-  "per3_gender",
-  label = "Gender:",
-  choices = c(
-    "Male",
-    "Female",
-    "Transgender",
-    "Prefer not to say",
-    "Other gender"
-  ),
-  selected = "Female",
-  width = "450px"
-)
-
-# Marital status
-selectInput(
-  "per3_marital_status",
-  label = "Marital Status:",
-  choices = c(
-    "Married",
-    "Widowed",
-    "Divorced",
-    "Separated",
-    "Never married"
-  ),
-  selected = "Married",
-  width = "450px"
-)
-
-# Education
-selectInput(
-  "per3_education",
-  label = "Education:",
-  choices = c(
-    "Less than high school",
-    "High school graduate",
-    "Some college",
-    "2 year degree",
-    "4 year degree",
-    "Graduate or professional degree",
-    "Doctorate"
-  ),
   selected = "Graduate or professional degree",

### 2020-10-09 analysis/05_market_simulator.Rmd
Persona 1 and 2 done for fixing selected values in Inputs

@@
   choices = c("Rarely", "Once a week", "At least once a day"),
-  selected = "At least once a day",
+  # selected = "At least once a day",
+  selected = ifelse(
+    sum(persona_data[2:3,3]) == 0, "Rarely",
+    as.character(persona_data[2:3,][which(persona_data[2:3,3] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Never", "Sometimes", "Always"),
-  selected = "Always",
+  # selected = "Always",
+  selected = ifelse(
+    sum(persona_data[4:5,3]) == 0, "Never",
+    as.character(persona_data[4:5,][which(persona_data[4:5,3] == 1), 1])
+  ),
   width = "450px"
@@
   multiple = TRUE,
-  selected = c("TV", "Print", "Social media"),
+  # selected = c("TV", "Print", "Social media"),
+  selected = deframe(persona_data[6:12,][which(persona_data[6:12,3] == 1), 1]),
   width = "450px"
@@
   choices = c("Not Often", "Often"),
-  selected = "Often",
+  # selected = "Often",
+  selected = ifelse(
+    sum(persona_data[13,3]) == 0, "Not Often",
+    as.character(persona_data[13,][which(persona_data[13,3] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Hasn't traveled to a developing country", "Traveled to a developing country"),
-  selected = "Traveled to a developing country",
+  # selected = "Traveled to a developing country",
+  selected = ifelse(
+    sum(persona_data[14,3]) == 0, "Hasn't traveled to a developing country",
+    as.character(persona_data[14,][which(persona_data[14,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "Somewhat liberal",
+  # selected = "Somewhat liberal",
+  selected = ifelse(
+    sum(persona_data[15:20,3]) == 0, "Extremely liberal",
+    as.character(persona_data[15:20,][which(persona_data[15:20,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "Complete trust in political institutions",
+  # selected = "Complete trust in political institutions",
+  selected = ifelse(
+    sum(persona_data[21:26,3]) == 0, "No trust at all in political institutions",
+    as.character(persona_data[21:26,][which(persona_data[21:26,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "Strongly agree",
+  # selected = "Strongly agree",
+  selected = ifelse(
+    sum(persona_data[27:32,3]) == 0, "Strongly disagree",
+    as.character(persona_data[27:32,][which(persona_data[27:32,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "Attend at least once a month",
+  # selected = "Attend at least once a month",
+  selected = ifelse(
+    sum(persona_data[33:34,3]) == 0, "Not sure",
+    as.character(persona_data[33:34,][which(persona_data[33:34,3] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Not important", "Important"),
-  selected = "Important",
+  # selected = "Important",
+  selected = ifelse(
+    sum(persona_data[35,3]) == 0, "Not important",
+    as.character(persona_data[35,][which(persona_data[35,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = 'Protestant',
+  # selected = 'Protestant',
+  selected = ifelse(
+    sum(persona_data[36:44,3]) == 0, "Catholic",
+    as.character(persona_data[36:44,][which(persona_data[36:44,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "Somewhat unimportant",
+  # selected = "Somewhat unimportant",
+  selected = ifelse(
+    sum(persona_data[45:50,3]) == 0, "Not at all important",
+    as.character(persona_data[45:50,][which(persona_data[45:50,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "Complete trust in charities",
+  # selected = "Complete trust in charities",
+  selected = ifelse(
+    sum(persona_data[51:56,3]) == 0, "No trust at all in charities",
+    as.character(persona_data[51:56,][which(persona_data[51:56,3] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c('Donate more than once a month, less than once a year', 'Donate at least once a month'),
-  selected = "Donate at least once a month",
+  # selected = "Donate at least once a month",
+  selected = ifelse(
+    sum(persona_data[57,3]) == 0, "Donate more than once a month, less than once a year",
+    as.character(persona_data[57,][which(persona_data[57,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "$100-$499",
+  # selected = "$100-$499",
+  selected = ifelse(
+    sum(persona_data[58:63,3]) == 0, "$1-$49",
+    as.character(persona_data[58:63,][which(persona_data[58:63,3] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Haven't volunteered in past 12 months", "Volunteered in past 12 months"),
-  selected = "Volunteered in past 12 months",
+  # selected = "Volunteered in past 12 months",
+  selected = ifelse(
+    sum(persona_data[64,3]) == 0, "Haven't volunteered in past 12 months",
+    as.character(persona_data[64,][which(persona_data[64,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "Volunteer at least once a month",
+  # selected = "Volunteer at least once a month",
+  selected = ifelse(
+    sum(persona_data[65:67,3]) == 0, "Haven't volunteered in past 12 months",
+    as.character(persona_data[65:67,][which(persona_data[65:67,3] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c('Not personally involved', 'Personally involved'),
-  selected = "Personally involved",
+  # selected = "Personally involved",
+  selected = ifelse(
+    sum(persona_data[68,3]) == 0, "Not personally involved",
+    as.character(persona_data[68,][which(persona_data[68,3] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c('Family not involved', 'Family involved'),
-  selected = "Family involved",
+  # selected = "Family involved",
+  selected = ifelse(
+    sum(persona_data[69,3]) == 0, "Family not involved",
+    as.character(persona_data[69,][which(persona_data[69,3] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Don't belong to church",'Inactive church member', 'Active church member'),
-  selected = "Don't belong to church",
+  # selected = "Don't belong to church",
+  selected = ifelse(
+    sum(persona_data[70:71,3]) == 0, "Don't belong to church",
+    as.character(persona_data[70:71,][which(persona_data[70:71,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "Don't belong to sports or rec organization",
+  # selected = "Don't belong to sports or rec organization",
+  selected = ifelse(
+    sum(persona_data[72:73,3]) == 0, "Don't belong to sports or rec organization",
+    as.character(persona_data[72:73,][which(persona_data[72:73,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "Don't belong to educational organization",
+  # selected = "Don't belong to educational organization",
+  selected = ifelse(
+    sum(persona_data[74:75,3]) == 0, "Don't belong to educational organization",
+    as.character(persona_data[74:75,][which(persona_data[74:75,3] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c("Don't belong to union", 'Inactive union member', 'Active union member'),
-  selected = "Don't belong to union",
+  # selected = "Don't belong to union",
+  selected = ifelse(
+    sum(persona_data[76:77,3]) == 0, "Don't belong to union",
+    as.character(persona_data[76:77,][which(persona_data[76:77,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "Active political party member",
+  # selected = "Active political party member",
+  selected = ifelse(
+    sum(persona_data[78:79,3]) == 0, "Don't belong to political party",
+    as.character(persona_data[78:79,][which(persona_data[78:79,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "Don't belong to environmental organization",
+  # selected = "Don't belong to environmental organization",
+  selected = ifelse(
+    sum(persona_data[80:81,3]) == 0, "Don't belong to environmental organization",
+    as.character(persona_data[80:81,][which(persona_data[80:81,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "Don't belong to professional association",
+  # selected = "Don't belong to professional association",
+  selected = ifelse(
+    sum(persona_data[82:83,3]) == 0, "Don't belong to professional association",
+    as.character(persona_data[82:83,][which(persona_data[82:83,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "Active humanitarian or charitable organization member",
+  # selected = "Active humanitarian or charitable organization member",
+  selected = ifelse(
+    sum(persona_data[84:85,3]) == 0, "Don't belong to humanitarian or charitable organization",
+    as.character(persona_data[84:85,][which(persona_data[84:85,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "Don't belong to consumer organization",
+  # selected = "Don't belong to consumer organization",
+  selected = ifelse(
+    sum(persona_data[86:87,3]) == 0, "Don't belong to consumer organization",
+    as.character(persona_data[86:87,][which(persona_data[86:87,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "Don't belong to another organization",
+  # selected = "Don't belong to another organization",
+  selected = ifelse(
+    sum(persona_data[88:89,3]) == 0, "Don't belong to another organization",
+    as.character(persona_data[88:89,][which(persona_data[88:89,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "Male",
+  # selected = "Male",
+  selected = ifelse(
+    sum(persona_data[90:93,3]) == 0, "Male",
+    as.character(persona_data[90:93,][which(persona_data[90:93,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "Married",
+  # selected = "Married",
+  selected = ifelse(
+    sum(persona_data[94:97,3]) == 0, "Married",
+    as.character(persona_data[94:97,][which(persona_data[94:97,3] == 1), 1])
+  ),
   width = "450px"
@@
   ),
-  selected = "Some college",
+  # selected = "Some college",
+  selected = ifelse(
+    sum(persona_data[98:103,3]) == 0, "Less than high school",
+    as.character(persona_data[98:103,][which(persona_data[98:103,3] == 1), 1])
+  ),
   width = "450px"
@@
   choices = c('Less than median of $61,372', 'More than median of $61,372'),
-  selected = "More than median of $61,372",
+  # selected = "More than median of $61,372",
+  selected = ifelse(
+    sum(persona_data[104,3]) == 0, "Less than median of $61,372",
+    as.character(persona_data[104,][which(persona_data[104,3] == 1), 1])
+  ),
   width = "450px"
@@
   multiple = TRUE,
-  selected = "American Indian or Alaskan Native",
+  # selected = "American Indian or Alaskan Native",
+  selected = deframe(persona_data[105:110,][which(persona_data[105:110,3] == 1), 1]),
   width = "450px"
@@
   choices = c('Less than median age of 36', "More than median age of 36"),
-  selected = "Less than median age of 36",
+  # selected = "Less than median age of 36",
+  selected = ifelse(
+    sum(persona_data[111,3]) == 0, "Less than median age of 36",
+    as.character(persona_data[111,][which(persona_data[111,3] == 1), 1])
+  ),
   width = "450px"
@@
   multiple = TRUE,
-  selected = c("TV", "Print", "Social media"),
+  # selected = c("TV", "Print", "Social media"),
   width = "450px"
@@
   ),
-  selected = "Female",
+  # selected = "Female",
   width = "450px"
@@
   ),
-  selected = "Graduate or professional degree",
+  # selected = "Graduate or professional degree",
   width = "450px"
@@
   multiple = TRUE,
-  selected = c("Black or African American", "American Indian or Alaskan Native"),
+  # selected = c("Black or African American", "American Indian or Alaskan Native"),
   width = "450px"

### 2020-10-09 analysis/05_market_simulator.Rmd
All selected values in persona and org inputs are updated

@@
   # selected = "At least once a day",
+  selected = ifelse(
+    sum(persona_data[2:3,4]) == 0, "Rarely",
+    as.character(persona_data[2:3,][which(persona_data[2:3,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Always",
+  elected = ifelse(
+    sum(persona_data[4:5,4]) == 0, "Never",
+    as.character(persona_data[4:5,][which(persona_data[4:5,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = c("TV", "Print", "Social media"),
+  selected = deframe(persona_data[6:12,][which(persona_data[6:12,4] == 1), 1]),
   width = "450px"
@@
   # selected = "Often",
+  selected = ifelse(
+    sum(persona_data[13,4]) == 0, "Not Often",
+    as.character(persona_data[13,][which(persona_data[13,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Traveled to a developing country",
+  selected = ifelse(
+    sum(persona_data[14,4]) == 0, "Hasn't traveled to a developing country",
+    as.character(persona_data[14,][which(persona_data[14,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Somewhat liberal",
+  selected = ifelse(
+    sum(persona_data[15:20,4]) == 0, "Extremely liberal",
+    as.character(persona_data[15:20,][which(persona_data[15:20,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Complete trust in political institutions",
+  selected = ifelse(
+    sum(persona_data[21:26,4]) == 0, "No trust at all in political institutions",
+    as.character(persona_data[21:26,][which(persona_data[21:26,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Strongly agree",
+  selected = ifelse(
+    sum(persona_data[27:32,4]) == 0, "Strongly disagree",
+    as.character(persona_data[27:32,][which(persona_data[27:32,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Attend at least once a month",
+  selected = ifelse(
+    sum(persona_data[33:34,4]) == 0, "Not sure",
+    as.character(persona_data[33:34,][which(persona_data[33:34,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Important",
+  selected = ifelse(
+    sum(persona_data[35,4]) == 0, "Not important",
+    as.character(persona_data[35,][which(persona_data[35,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = 'Protestant',
+  selected = ifelse(
+    sum(persona_data[36:44,4]) == 0, "Catholic",
+    as.character(persona_data[36:44,][which(persona_data[36:44,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Somewhat unimportant",
+  selected = ifelse(
+    sum(persona_data[45:50,4]) == 0, "Not at all important",
+    as.character(persona_data[45:50,][which(persona_data[45:50,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Complete trust in charities",
+  selected = ifelse(
+    sum(persona_data[51:56,4]) == 0, "No trust at all in charities",
+    as.character(persona_data[51:56,][which(persona_data[51:56,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Donate at least once a month",
+  selected = ifelse(
+    sum(persona_data[57,4]) == 0, "Donate more than once a month, less than once a year",
+    as.character(persona_data[57,][which(persona_data[57,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "$100-$499",
+  selected = ifelse(
+    sum(persona_data[58:63,4]) == 0, "$1-$49",
+    as.character(persona_data[58:63,][which(persona_data[58:63,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Volunteered in past 12 months",
+  selected = ifelse(
+    sum(persona_data[64,4]) == 0, "Haven't volunteered in past 12 months",
+    as.character(persona_data[64,][which(persona_data[64,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Volunteer at least once a month",
+  selected = ifelse(
+    sum(persona_data[65:67,4]) == 0, "Haven't volunteered in past 12 months",
+    as.character(persona_data[65:67,][which(persona_data[65:67,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Personally involved",
+  selected = ifelse(
+    sum(persona_data[68,4]) == 0, "Not personally involved",
+    as.character(persona_data[68,][which(persona_data[68,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Family involved",
+  selected = ifelse(
+    sum(persona_data[69,4]) == 0, "Family not involved",
+    as.character(persona_data[69,][which(persona_data[69,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Don't belong to church",
+  selected = ifelse(
+    sum(persona_data[70:71,4]) == 0, "Don't belong to church",
+    as.character(persona_data[70:71,][which(persona_data[70:71,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Don't belong to sports or rec organization",
+  selected = ifelse(
+    sum(persona_data[72:73,4]) == 0, "Don't belong to sports or rec organization",
+    as.character(persona_data[72:73,][which(persona_data[72:73,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Don't belong to educational organization",
+  selected = ifelse(
+    sum(persona_data[74:75,4]) == 0, "Don't belong to educational organization",
+    as.character(persona_data[74:75,][which(persona_data[74:75,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Don't belong to union",
+  selected = ifelse(
+    sum(persona_data[76:77,4]) == 0, "Don't belong to union",
+    as.character(persona_data[76:77,][which(persona_data[76:77,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Active political party member",
+  selected = ifelse(
+    sum(persona_data[78:79,4]) == 0, "Don't belong to political party",
+    as.character(persona_data[78:79,][which(persona_data[78:79,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Don't belong to environmental organization",
+  selected = ifelse(
+    sum(persona_data[80:81,4]) == 0, "Don't belong to environmental organization",
+    as.character(persona_data[80:81,][which(persona_data[80:81,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Don't belong to professional association",
+  selected = ifelse(
+    sum(persona_data[82:83,4]) == 0, "Don't belong to professional association",
+    as.character(persona_data[82:83,][which(persona_data[82:83,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Active humanitarian or charitable organization member",
+  selected = ifelse(
+    sum(persona_data[84:85,4]) == 0, "Don't belong to humanitarian or charitable organization",
+    as.character(persona_data[84:85,][which(persona_data[84:85,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Don't belong to consumer organization",
+  selected = ifelse(
+    sum(persona_data[86:87,4]) == 0, "Don't belong to consumer organization",
+    as.character(persona_data[86:87,][which(persona_data[86:87,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Don't belong to another organization",
+  selected = ifelse(
+    sum(persona_data[88:89,4]) == 0, "Don't belong to another organization",
+    as.character(persona_data[88:89,][which(persona_data[88:89,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Female",
+  selected = ifelse(
+    sum(persona_data[90:93,4]) == 0, "Male",
+    as.character(persona_data[90:93,][which(persona_data[90:93,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Married",
+  selected = ifelse(
+    sum(persona_data[94:97,4]) == 0, "Married",
+    as.character(persona_data[94:97,][which(persona_data[94:97,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "Graduate or professional degree",
+  selected = ifelse(
+    sum(persona_data[98:103,4]) == 0, "Less than high school",
+    as.character(persona_data[98:103,][which(persona_data[98:103,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = "More than median of $61,372",
+  selected = ifelse(
+    sum(persona_data[104,4]) == 0, "Less than median of $61,372",
+    as.character(persona_data[104,][which(persona_data[104,4] == 1), 1])
+  ),
   width = "450px"
@@
   # selected = c("Black or African American", "American Indian or Alaskan Native"),
+  selected = deframe(persona_data[105:110,][which(persona_data[105:110,4] == 1), 1]),
   width = "450px"
@@
   # selected = "Less than median age of 36",
+  selected = ifelse(
+    sum(persona_data[111,4]) == 0, "Less than median age of 36",
+    as.character(persona_data[111,][which(persona_data[111,4] == 1), 1])
+  ),
   width = "450px"

### 2020-10-09 analysis/05_market_simulator.Rmd
Testing the ability to import data to influence the defaults of the reactive table.

@@
 organization_data <- read_csv(
-  here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
-)
+  here::here('analysis', 'output', 'configurations', 'org_data_test1.csv')
+)
+
+org_update <- reactiveValues(data = NULL)
+org_update$data <- organization_data
 
@@
 ```{r organization-reactive-table}
-
-# Placeholder for organization reactive table
-org_table <- as.data.frame(matrix(0, nrow = nrow(organization_data)))
-# org_table <- reactive({read.csv(input$file_org$datapath)})
 
@@
 
-# I think what we need to do to import data to fill this reactive element we need it look something like this
-
-# org_table$org1_value[where (input$file_org == 1) and the corresponding level matches %in% org_table$levels] <- 1
-
 # Organization configuration reactive element
@@
 })
+
+per_update <- reactiveValues(data = NULL)
+per_update$data <- per_table
+
 ```
@@
 )
-
 # Organization
+renderUI({
   selectInput(
@@
     # selected = "Red Cross",
-  selected = as.character(organization_data[1:4,][which(organization_data[1:4,2] == 1), 1]),
-  width = "450px"
-)
+    selected = as.character(org_update$data[1:4,][which(org_update$data[1:4,2] == 1), 1]),
+    width = "450px"
+  )
+})
 
@@
   # selected = "Always",
-  elected = ifelse(
+  selected = ifelse(
     sum(persona_data[4:5,4]) == 0, "Never",
@@
   "file_org",
-  "Import Organization Data"
-)
+  "Import Organization Data",
+  accept = c("text/csv",
+             "text/comma-separated-values,text/plain",
+             ".csv")
+)
+
+actionButton(
+  inputId = "org_apply",
+  label = "Apply New Data",
+  icon = icon("play")
+)
+
+observeEvent(eventExpr = input$org_apply, 
+  handlerExpr = {
+      req(input$file_org)
+      file <- read_csv(input$file_org$datapath)
+      org_update$data <- file
+  }, ignoreNULL = FALSE)
 
@@
   "file_per",
-  "Import Persona Data"
-)
+  "Import Persona Data",
+  accept = c("text/csv",
+             "text/comma-separated-values,text/plain",
+             ".csv")
+)
+
+# observeEvent(eventExpr = input$apply, 
+#   handlerExpr = {
+#       req(input$file_per)
+#       file <- read_csv(input$file_per$datapath)
+#       per_update$data <- file
+#   }, ignoreNULL = FALSE)
 

### 2020-10-13 analysis/05_market_simulator.Rmd
Trying to get update button to work

@@
 # Initial organization configuration
-organization_data <- read_csv(
-  here::here('analysis', 'output', 'configurations', 'org_data_test1.csv')
-)
+organization_data <- reactive({ 
+  read_csv(
+    here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
+  )
+})
 

### 2020-10-16 analysis/05_market_simulator.Rmd
figuring out how to upload new data to update the selected values

--- 2020-10-09 analysis/05_market_simulator.Rmd
@@
 # Initial organization configuration
-organization_data <- read_csv(
-  here::here('analysis', 'output', 'configurations', 'org_data_test1.csv')
-)
-
-org_update <- reactiveValues(data = NULL)
-org_update$data <- organization_data
+# organization_data <- read_csv(
+#   here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
+# )
+
+organization_values <- reactiveValues()
+
+organization_data <- reactive({
+  if (is.null(input$org_update$datapath)) {
+    organization_reactive <- read.csv(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
+    organization_values$file_name = "organization_config01.csv"
+    organization_values$file_type = "csv"
+    organization_values$file_size = file.size(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
+    organization_values$file_path = here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
+  } else {
+    organization_data <- read.csv(input$org_update$datapath)
+    organization_values$file_name = input$org_update$name
+    organization_values$file_size = input$org_update$size
+    organization_values$file_type = input$org_update$type
+    organization_values$file_path = input$org_update$datapath
+  }
+})
 
@@
 
-per_update <- reactiveValues(data = NULL)
-per_update$data <- per_table
+# per_update <- reactiveValues(data = NULL)
+# per_update$data <- per_table
 
@@
     # selected = "Red Cross",
-    selected = as.character(org_update$data[1:4,][which(org_update$data[1:4,2] == 1), 1]),
-    width = "450px"
-  )
+    selected = as.character(organization_data()[1:4,][which(organization_data()[1:4,2] == 1), 1]),
+    width = "450px"
+  )
+
 })
+
+renderUI({
 
@@
   selected = ifelse(
-    sum(organization_data[5:7,2]) == 0, "Emergency response",
-    as.character(organization_data[5:7,][which(organization_data[5:7,2] == 1), 1])
+    sum(organization_data$data[5:7,2]) == 0, "Emergency response",
+    as.character(organization_data$data[5:7,][which(organization_data$data[5:7,2] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data[8,2]) == 0, "Doesn’t engage in financial transparency",
-    as.character(organization_data[8,][which(organization_data[8,2] == 1), 1])
+    sum(organization_data$data[8,2]) == 0, "Doesn’t engage in financial transparency",
+    as.character(organization_data$data[8,][which(organization_data$data[8,2] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data[9,2]) == 0, "Doesn’t engage in financial accountability",
-    as.character(organization_data[9,][which(organization_data[9,2] == 1), 1])
+    sum(organization_data$data[9,2]) == 0, "Doesn’t engage in financial accountability",
+    as.character(organization_data$data[9,][which(organization_data$data[9,2] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data[10:11,2]) == 0, "Many small private donations",
-    as.character(organization_data[10:11,][which(organization_data[10:11,2] == 1), 1])
+    sum(organization_data$data[10:11,2]) == 0, "Many small private donations",
+    as.character(organization_data$data[10:11,][which(organization_data$data[10:11,2] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data[12:13,2]) == 0, "Friendly relationship with government",
-    as.character(organization_data[12:13,][which(organization_data[12:13,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    sum(organization_data$data[12:13,2]) == 0, "Friendly relationship with government",
+    as.character(organization_data$data[12:13,][which(organization_data$data[12:13,2] == 1), 1])
+  ),
+  width = "450px"
+)
+
+})
 ```
@@
 
+renderUI({
+
 # Organization
@@
   # selected = "Red Cross",
-  selected = as.character(organization_data[1:4,][which(organization_data[1:4,3] == 1), 1]),
+  selected = as.character(organization_data$data[1:4,][which(organization_data$data[1:4,3] == 1), 1]),
   width = "450px"
@@
   selected = ifelse(
-    sum(organization_data[5:7,3]) == 0, "Emergency response",
-    as.character(organization_data[5:7,][which(organization_data[5:7,3] == 1), 1])
+    sum(organization_data$data[5:7,3]) == 0, "Emergency response",
+    as.character(organization_data$data[5:7,][which(organization_data$data[5:7,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data[8,3]) == 0, "Doesn’t engage in financial transparency",
-    as.character(organization_data[8,][which(organization_data[8,3] == 1), 1])
+    sum(organization_data$data[8,3]) == 0, "Doesn’t engage in financial transparency",
+    as.character(organization_data$data[8,][which(organization_data$data[8,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data[9,3]) == 0, "Doesn’t engage in financial accountability",
-    as.character(organization_data[9,][which(organization_data[9,3] == 1), 1])
+    sum(organization_data$data[9,3]) == 0, "Doesn’t engage in financial accountability",
+    as.character(organization_data$data[9,][which(organization_data$data[9,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data[10:11,3]) == 0, "Many small private donations",
-    as.character(organization_data[10:11,][which(organization_data[10:11,3] == 1), 1])
+    sum(organization_data$data[10:11,3]) == 0, "Many small private donations",
+    as.character(organization_data$data[10:11,][which(organization_data$data[10:11,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data[12:13,3]) == 0, "Friendly relationship with government",
-    as.character(organization_data[12:13,][which(organization_data[12:13,3] == 1), 1])
-  ),
-  width = "450px"
-)
+    sum(organization_data$data[12:13,3]) == 0, "Friendly relationship with government",
+    as.character(organization_data$data[12:13,][which(organization_data$data[12:13,3] == 1), 1])
+  ),
+  width = "450px"
+)
+})
 ```
@@
 )
+renderUI({
 
@@
   # selected = "Red Cross",
-  selected = as.character(organization_data[1:4,][which(organization_data[1:4,4] == 1), 1]),
+  selected = as.character(organization_data$data[1:4,][which(organization_data$data[1:4,4] == 1), 1]),
   width = "450px"
@@
   selected = ifelse(
-    sum(organization_data[5:7,4]) == 0, "Emergency response",
-    as.character(organization_data[5:7,][which(organization_data[5:7,4] == 1), 1])
+    sum(organization_data$data[5:7,4]) == 0, "Emergency response",
+    as.character(organization_data$data[5:7,][which(organization_data$data[5:7,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data[8,4]) == 0, "Doesn’t engage in financial transparency",
-    as.character(organization_data[8,][which(organization_data[8,4] == 1), 1])
+    sum(organization_data$data[8,4]) == 0, "Doesn’t engage in financial transparency",
+    as.character(organization_data$data[8,][which(organization_data$data[8,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data[9,4]) == 0, "Doesn’t engage in financial accountability",
-    as.character(organization_data[9,][which(organization_data[9,4] == 1), 1])
+    sum(organization_data$data[9,4]) == 0, "Doesn’t engage in financial accountability",
+    as.character(organization_data$data[9,][which(organization_data$data[9,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data[10:11,4]) == 0, "Many small private donations",
-    as.character(organization_data[10:11,][which(organization_data[10:11,4] == 1), 1])
+    sum(organization_data$data[10:11,4]) == 0, "Many small private donations",
+    as.character(organization_data$data[10:11,][which(organization_data$data[10:11,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data[12:13,4]) == 0, "Friendly relationship with government",
-    as.character(organization_data[12:13,][which(organization_data[12:13,4] == 1), 1])
-  ),
-  width = "450px"
-)
+    sum(organization_data$data[12:13,4]) == 0, "Friendly relationship with government",
+    as.character(organization_data$data[12:13,][which(organization_data$data[12:13,4] == 1), 1])
+  ),
+  width = "450px"
+)
+})
 ```
@@
   # selected = "Red Cross",
-  selected = as.character(organization_data[1:4,][which(organization_data[1:4,5] == 1), 1]),
+  selected = as.character(organization_data$data[1:4,][which(organization_data$data[1:4,5] == 1), 1]),
   width = "450px"
@@
   selected = ifelse(
-    sum(organization_data[5:7,5]) == 0, "Emergency response",
-    as.character(organization_data[5:7,][which(organization_data[5:7,5] == 1), 1])
+    sum(organization_data$data[5:7,5]) == 0, "Emergency response",
+    as.character(organization_data$data[5:7,][which(organization_data$data[5:7,5] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data[8,5]) == 0, "Doesn’t engage in financial transparency",
-    as.character(organization_data[8,][which(organization_data[8,5] == 1), 1])
+    sum(organization_data$data[8,5]) == 0, "Doesn’t engage in financial transparency",
+    as.character(organization_data$data[8,][which(organization_data$data[8,5] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data[9,5]) == 0, "Doesn’t engage in financial accountability",
-    as.character(organization_data[9,][which(organization_data[9,5] == 1), 1])
+    sum(organization_data$data[9,5]) == 0, "Doesn’t engage in financial accountability",
+    as.character(organization_data$data[9,][which(organization_data$data[9,5] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data[10:11,5]) == 0, "Many small private donations",
-    as.character(organization_data[10:11,][which(organization_data[10:11,5] == 1), 1])
+    sum(organization_data$data[10:11,5]) == 0, "Many small private donations",
+    as.character(organization_data$data[10:11,][which(organization_data$data[10:11,5] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data[12:13,5]) == 0, "Friendly relationship with government",
-    as.character(organization_data[12:13,][which(organization_data[12:13,5] == 1), 1])
-  ),
-  width = "450px"
-)
+    sum(organization_data$data[12:13,5]) == 0, "Friendly relationship with government",
+    as.character(organization_data$data[12:13,][which(organization_data$data[12:13,5] == 1), 1])
+  ),
+  width = "450px"
+)
+})
 ```
@@
 fileInput(
-  "file_org",
+  "org_update",
   "Import Organization Data",
@@
   handlerExpr = {
-      req(input$file_org)
-      file <- read_csv(input$file_org$datapath)
+      req(input$org_update)
+      file <- read_csv(input$org_update$datapath)
       org_update$data <- file

### 2020-10-16 analysis/05_market_simulator.Rmd
Some commit

@@
   if (is.null(input$org_update$datapath)) {
-    organization_reactive <- read.csv(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
+    organization_data <- read.csv(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
     organization_values$file_name = "organization_config01.csv"
@@
 renderUI({
+  organization_data = organization_data()
+
   selectInput(
@@
     # selected = "Red Cross",
-    selected = as.character(organization_data()[1:4,][which(organization_data()[1:4,2] == 1), 1]),
-    width = "450px"
-  )
-
+    selected = as.character(organization_data[1:4,][which(organization_data[1:4,2] == 1), 1]),
+    width = "450px"
+  )
 })

### 2020-10-16 analysis/05_market_simulator.Rmd
Changes from our meeting

--- 2020-10-16 analysis/05_market_simulator.Rmd
@@
   if (is.null(input$org_update$datapath)) {
-    organization_reactive <- read.csv(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
-    organization_values$file_name = "organization_config01.csv"
-    organization_values$file_type = "csv"
-    organization_values$file_size = file.size(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
-    organization_values$file_path = here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
+    organization_data <- read_csv(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
+    # organization_values$file_name = "organization_config01.csv"
+    # organization_values$file_type = "csv"
+    # organization_values$file_size = file.size(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
+    # organization_values$file_path = here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
   } else {
-    organization_data <- read.csv(input$org_update$datapath)
-    organization_values$file_name = input$org_update$name
-    organization_values$file_size = input$org_update$size
-    organization_values$file_type = input$org_update$type
-    organization_values$file_path = input$org_update$datapath
+    organization_data <- read_csv(input$org_update$datapath)
+    # organization_values$file_name = input$org_update$name
+    # organization_values$file_size = input$org_update$size
+    # organization_values$file_type = input$org_update$type
+    # organization_values$file_path = input$org_update$datapath
   }
@@
 renderUI({
+  # organization_data = organization_data()
+  org_data = organization_data()
+
   selectInput(
@@
     # selected = "Red Cross",
-    selected = as.character(organization_data()[1:4,][which(organization_data()[1:4,2] == 1), 1]),
-    width = "450px"
-  )
-
+    # selected = as.character(organization_data[1:4,][which(organization_data[1:4,2] == 1), 1]),
+    selected = as.character(org_data[1:4,][which(org_data[1:4,2] == 1), 1]),
+    width = "450px"
+  )
 })
@@
 renderUI({
+
+  # organization_data = organization_data()
+  org_data = organization_data()
 
@@
   selected = ifelse(
-    sum(organization_data$data[5:7,2]) == 0, "Emergency response",
-    as.character(organization_data$data[5:7,][which(organization_data$data[5:7,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # sum(organization_data$data[5:7,2]) == 0, "Emergency response",
+    # as.character(organization_data$data[5:7,][which(organization_data$data[5:7,2] == 1), 1])
+    sum(org_data[5:7,2]) == 0, "Emergency response",
+    as.character(org_data[5:7,][which(org_data[5:7,2] == 1), 1])
+  ),
+  width = "450px"
+)
+})
+
+renderUI({
+
+  # organization_data = organization_data()
+  org_data = organization_data()
 
@@
   selected = ifelse(
-    sum(organization_data$data[8,2]) == 0, "Doesn’t engage in financial transparency",
-    as.character(organization_data$data[8,][which(organization_data$data[8,2] == 1), 1])
+    # sum(organization_data$data[8,2]) == 0, "Doesn’t engage in financial transparency",
+    # as.character(organization_data$data[8,][which(organization_data$data[8,2] == 1), 1])
+    sum(org_data[8,2]) == 0, "Doesn’t engage in financial transparency",
+    as.character(org_data[8,][which(org_data[8,2] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data$data[9,2]) == 0, "Doesn’t engage in financial accountability",
-    as.character(organization_data$data[9,][which(organization_data$data[9,2] == 1), 1])
+    # sum(organization_data$data[9,2]) == 0, "Doesn’t engage in financial accountability",
+    # as.character(organization_data$data[9,][which(organization_data$data[9,2] == 1), 1])
+    sum(org_data[9,2]) == 0, "Doesn’t engage in financial accountability",
+    as.character(org_data[9,][which(org_data[9,2] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data$data[10:11,2]) == 0, "Many small private donations",
-    as.character(organization_data$data[10:11,][which(organization_data$data[10:11,2] == 1), 1])
+    # sum(organization_data$data[10:11,2]) == 0, "Many small private donations",
+    # as.character(organization_data$data[10:11,][which(organization_data$data[10:11,2] == 1), 1])
+    sum(org_data[10:11,2]) == 0, "Many small private donations",
+    as.character(org_data[10:11,][which(org_data[10:11,2] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data$data[12:13,2]) == 0, "Friendly relationship with government",
-    as.character(organization_data$data[12:13,][which(organization_data$data[12:13,2] == 1), 1])
+    # sum(organization_data$data[12:13,2]) == 0, "Friendly relationship with government",
+    # as.character(organization_data$data[12:13,][which(organization_data$data[12:13,2] == 1), 1])
+    sum(org_data[12:13,2]) == 0, "Friendly relationship with government",
+    as.character(org_data[12:13,][which(org_data[12:13,2] == 1), 1])
   ),

### 2020-10-21 analysis/05_market_simulator.Rmd
Fixing the organization Render UI's

@@
 renderUI({
-  # organization_data = organization_data()
   org_data = organization_data()
@@
   )
+
 })
 
+# Issue area
 renderUI({
-
-  # organization_data = organization_data()
   org_data = organization_data()
 
-# Issue area
   selectInput(
@@
   )
+
 })
 
+# Financial transparency
 renderUI({
-
-  # organization_data = organization_data()
   org_data = organization_data()
 
-# Financial transparency
   selectInput(
@@
 
+})
+
 # Financial accountability
+renderUI({
+  org_data = organization_data()
+
   selectInput(
@@
 
+})
+
 # Funding sources
+renderUI({
+  org_data = organization_data()
+
   selectInput(
@@
 
+})
+
 # Relationship with host government
+renderUI({
+  org_data = organization_data()
+
   selectInput(
@@
 
+# Organization
 renderUI({
-
-# Organization
+  org_data = organization_data()
+
   selectInput(
@@
     # selected = "Red Cross",
-  selected = as.character(organization_data$data[1:4,][which(organization_data$data[1:4,3] == 1), 1]),
-  width = "450px"
-)
+    selected = as.character(org_data[1:4,][which(org_data[1:4,3] == 1), 1]),
+    width = "450px"
+  )
+
+})
 
 # Issue area
+renderUI({
+  org_data = organization_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(organization_data$data[5:7,3]) == 0, "Emergency response",
-    as.character(organization_data$data[5:7,][which(organization_data$data[5:7,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(org_data[5:7,3]) == 0, "Emergency response",
+      as.character(org_data[5:7,][which(org_data[5:7,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Financial transparency
+renderUI({
+  org_data = organization_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(organization_data$data[8,3]) == 0, "Doesn’t engage in financial transparency",
-    as.character(organization_data$data[8,][which(organization_data$data[8,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(org_data[8,3]) == 0, "Doesn’t engage in financial transparency",
+      as.character(org_data[8,][which(org_data[8,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Financial accountability
+renderUI({
+  org_data = organization_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(organization_data$data[9,3]) == 0, "Doesn’t engage in financial accountability",
-    as.character(organization_data$data[9,][which(organization_data$data[9,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(org_data[9,3]) == 0, "Doesn’t engage in financial accountability",
+      as.character(org_data[9,][which(org_data[9,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Funding sources
+renderUI({
+  org_data = organization_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(organization_data$data[10:11,3]) == 0, "Many small private donations",
-    as.character(organization_data$data[10:11,][which(organization_data$data[10:11,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(org_data[10:11,3]) == 0, "Many small private donations",
+      as.character(org_data[10:11,][which(org_data[10:11,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Relationship with host government
+renderUI({
+  org_data = organization_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(organization_data$data[12:13,3]) == 0, "Friendly relationship with government",
-    as.character(organization_data$data[12:13,][which(organization_data$data[12:13,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(org_data[12:13,3]) == 0, "Friendly relationship with government",
+      as.character(org_data[12:13,][which(org_data[12:13,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
 })
+
 ```
@@
 )
+
+# Organization
 renderUI({
-
-# Organization
+  org_data = organization_data()
+
   selectInput(
@@
     # selected = "Red Cross",
-  selected = as.character(organization_data$data[1:4,][which(organization_data$data[1:4,4] == 1), 1]),
-  width = "450px"
-)
+    selected = as.character(org_data[1:4,][which(org_data[1:4,4] == 1), 1]),
+    width = "450px"
+  )
+
+})
 
 # Issue area
+renderUI({
+  org_data = organization_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(organization_data$data[5:7,4]) == 0, "Emergency response",
-    as.character(organization_data$data[5:7,][which(organization_data$data[5:7,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(org_data[5:7,4]) == 0, "Emergency response",
+      as.character(org_data[5:7,][which(org_data[5:7,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Financial transparency
+renderUI({
+  org_data = organization_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(organization_data$data[8,4]) == 0, "Doesn’t engage in financial transparency",
-    as.character(organization_data$data[8,][which(organization_data$data[8,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(org_data[8,4]) == 0, "Doesn’t engage in financial transparency",
+      as.character(org_data[8,][which(org_data[8,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Financial accountability
+renderUI({
+  org_data = organization_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(organization_data$data[9,4]) == 0, "Doesn’t engage in financial accountability",
-    as.character(organization_data$data[9,][which(organization_data$data[9,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(org_data[9,4]) == 0, "Doesn’t engage in financial accountability",
+      as.character(org_data[9,][which(org_data[9,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Funding sources
+renderUI({
+  org_data = organization_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(organization_data$data[10:11,4]) == 0, "Many small private donations",
-    as.character(organization_data$data[10:11,][which(organization_data$data[10:11,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(org_data[10:11,4]) == 0, "Many small private donations",
+      as.character(org_data[10:11,][which(org_data[10:11,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Relationship with host government
+renderUI({
+  org_data = organization_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(organization_data$data[12:13,4]) == 0, "Friendly relationship with government",
-    as.character(organization_data$data[12:13,][which(organization_data$data[12:13,4] == 1), 1])
+      sum(org_data[12:13,4]) == 0, "Friendly relationship with government",
+      as.character(org_data[12:13,][which(org_data[12:13,4] == 1), 1])
     ),
@@
   # selected = "Red Cross",
-  selected = as.character(organization_data$data[1:4,][which(organization_data$data[1:4,5] == 1), 1]),
+  selected = as.character(org_data[1:4,][which(org_data[1:4,5] == 1), 1]),
   width = "450px"
@@
   selected = ifelse(
-    sum(organization_data$data[5:7,5]) == 0, "Emergency response",
-    as.character(organization_data$data[5:7,][which(organization_data$data[5:7,5] == 1), 1])
+    sum(org_data[5:7,5]) == 0, "Emergency response",
+    as.character(org_data[5:7,][which(org_data[5:7,5] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data$data[8,5]) == 0, "Doesn’t engage in financial transparency",
-    as.character(organization_data$data[8,][which(organization_data$data[8,5] == 1), 1])
+    sum(org_data[8,5]) == 0, "Doesn’t engage in financial transparency",
+    as.character(org_data[8,][which(org_data[8,5] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data$data[9,5]) == 0, "Doesn’t engage in financial accountability",
-    as.character(organization_data$data[9,][which(organization_data$data[9,5] == 1), 1])
+    sum(org_data[9,5]) == 0, "Doesn’t engage in financial accountability",
+    as.character(org_data[9,][which(org_data[9,5] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data$data[10:11,5]) == 0, "Many small private donations",
-    as.character(organization_data$data[10:11,][which(organization_data$data[10:11,5] == 1), 1])
+    sum(org_data[10:11,5]) == 0, "Many small private donations",
+    as.character(org_data[10:11,][which(org_data[10:11,5] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(organization_data$data[12:13,5]) == 0, "Friendly relationship with government",
-    as.character(organization_data$data[12:13,][which(organization_data$data[12:13,5] == 1), 1])
+    sum(org_data[12:13,5]) == 0, "Friendly relationship with government",
+    as.character(org_data[12:13,][which(org_data[12:13,5] == 1), 1])
   ),

### 2020-10-21 analysis/05_market_simulator.Rmd
Org Inputs Finished

@@
 
+})
+
 # Issue area
+renderUI({
+  org_data = organization_data()
+
   selectInput(
@@
 
+})
+
 # Financial transparency
+renderUI({
+  org_data = organization_data()
+
   selectInput(
@@
   )
+
 })

### 2020-10-21 analysis/05_market_simulator.Rmd
added persona reactive data for updating with imported data

@@
 # Initial persona configuration
-persona_data <- read_csv(
-  here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
-)
+# persona_data <- read_csv(
+#   here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
+# )
+
+persona_values <- reactiveValues()
+
+persona_data <- reactive({
+  if (is.null(input$org_update$datapath)) {
+    persona_data <- read_csv(here::here('analysis', 'output', 'configurations', 'persona_config01.csv'))
+    # persona_values$file_name = "persona_config01.csv"
+    # persona_values$file_type = "csv"
+    # persona_values$file_size = file.size(here::here('analysis', 'output', 'configurations', 'persona_config01.csv'))
+    # persona_values$file_path = here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
+  } else {
+    persona_data <- read_csv(input$per_update$datapath)
+    # persona_values$file_name = input$per_update$name
+    # persona_values$file_size = input$per_update$size
+    # persona_values$file_type = input$per_update$type
+    # persona_values$file_path = input$per_update$datapath
+  }
+})
 
@@
 # Follow national news
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "At least once a day",
-  selected = ifelse(
-    sum(persona_data[2:3,2]) == 0, "Rarely",
-    as.character(persona_data[2:3,][which(persona_data[2:3,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[2:3,2]) == 0, "Rarely",
+    #   as.character(persona_data[2:3,][which(persona_data[2:3,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[2:3,2]) == 0, "Rarely",
+      as.character(per_data[2:3,][which(per_data[2:3,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
@@
   # selected = "Always",
-  selected = ifelse(
-    sum(persona_data[4:5,2]) == 0, "Never",
-    as.character(persona_data[4:5,][which(persona_data[4:5,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[4:5,2]) == 0, "Never",
+  #   as.character(persona_data[4:5,][which(persona_data[4:5,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[4:5,2]) == 0, "Never",
+    as.character(per_data[4:5,][which(per_data[4:5,2] == 1), 1])
   ),
@@
   # selected = c("TV", "Print", "Social media"),
-  selected = deframe(persona_data[6:12,][which(persona_data[6:12,2] == 1), 1]),
+  # selected = deframe(persona_data[6:12,][which(persona_data[6:12,2] == 1), 1]),
+  selected = deframe(per_data[6:12,][which(per_data[6:12,2] == 1), 1]),
   width = "450px"
@@
   # selected = "Often",
-  selected = ifelse(
-    sum(persona_data[13,2]) == 0, "Not Often",
-    as.character(persona_data[13,][which(persona_data[13,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[13,2]) == 0, "Not Often",
+  #   as.character(persona_data[13,][which(persona_data[13,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[13,2]) == 0, "Not Often",
+    as.character(per_data[13,][which(per_data[13,2] == 1), 1])
   ),
@@
   # selected = "Traveled to a developing country",
-  selected = ifelse(
-    sum(persona_data[14,2]) == 0, "Hasn't traveled to a developing country",
-    as.character(persona_data[14,][which(persona_data[14,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[14,2]) == 0, "Hasn't traveled to a developing country",
+  #   as.character(persona_data[14,][which(persona_data[14,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[14,2]) == 0, "Hasn't traveled to a developing country",
+    as.character(per_data[14,][which(per_data[14,2] == 1), 1])
   ),
@@
   # selected = "Somewhat liberal",
-  selected = ifelse(
-    sum(persona_data[15:20,2]) == 0, "Extremely liberal",
-    as.character(persona_data[15:20,][which(persona_data[15:20,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[15:20,2]) == 0, "Extremely liberal",
+  #   as.character(persona_data[15:20,][which(persona_data[15:20,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[15:20,2]) == 0, "Extremely liberal",
+    as.character(per_data[15:20,][which(per_data[15:20,2] == 1), 1])
   ),
@@
   # selected = "Complete trust in political institutions",
-  selected = ifelse(
-    sum(persona_data[21:26,2]) == 0, "No trust at all in political institutions",
-    as.character(persona_data[21:26,][which(persona_data[21:26,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[21:26,2]) == 0, "No trust at all in political institutions",
+  #   as.character(persona_data[21:26,][which(persona_data[21:26,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[21:26,2]) == 0, "No trust at all in political institutions",
+    as.character(per_data[21:26,][which(per_data[21:26,2] == 1), 1])
   ),
@@
   # selected = "Strongly agree",
-  selected = ifelse(
-    sum(persona_data[27:32,2]) == 0, "Strongly disagree",
-    as.character(persona_data[27:32,][which(persona_data[27:32,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[27:32,2]) == 0, "Strongly disagree",
+  #   as.character(persona_data[27:32,][which(persona_data[27:32,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[27:32,2]) == 0, "Strongly disagree",
+    as.character(per_data[27:32,][which(per_data[27:32,2] == 1), 1])
   ),
@@
   # selected = "Attend at least once a month",
-  selected = ifelse(
-    sum(persona_data[33:34,2]) == 0, "Not sure",
-    as.character(persona_data[33:34,][which(persona_data[33:34,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[33:34,2]) == 0, "Not sure",
+  #   as.character(persona_data[33:34,][which(persona_data[33:34,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[33:34,2]) == 0, "Not sure",
+    as.character(per_data[33:34,][which(per_data[33:34,2] == 1), 1])
   ),
@@
   # selected = "Important",
-  selected = ifelse(
-    sum(persona_data[35,2]) == 0, "Not important",
-    as.character(persona_data[35,][which(persona_data[35,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[35,2]) == 0, "Not important",
+  #   as.character(persona_data[35,][which(persona_data[35,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[35,2]) == 0, "Not important",
+    as.character(per_data[35,][which(per_data[35,2] == 1), 1])
   ),
@@
   # selected = 'Protestant',
-  selected = ifelse(
-    sum(persona_data[36:44,2]) == 0, "Catholic",
-    as.character(persona_data[36:44,][which(persona_data[36:44,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[36:44,2]) == 0, "Catholic",
+  #   as.character(persona_data[36:44,][which(persona_data[36:44,2] == 1), 1])
+  # ),
+   selected = ifelse(
+    sum(per_data[36:44,2]) == 0, "Catholic",
+    as.character(per_data[36:44,][which(per_data[36:44,2] == 1), 1])
   ),
@@
   # selected = "Somewhat unimportant",
-  selected = ifelse(
-    sum(persona_data[45:50,2]) == 0, "Not at all important",
-    as.character(persona_data[45:50,][which(persona_data[45:50,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[45:50,2]) == 0, "Not at all important",
+  #   as.character(persona_data[45:50,][which(persona_data[45:50,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[45:50,2]) == 0, "Not at all important",
+    as.character(per_data[45:50,][which(per_data[45:50,2] == 1), 1])
   ),
@@
   # selected = "Complete trust in charities",
-  selected = ifelse(
-    sum(persona_data[51:56,2]) == 0, "No trust at all in charities",
-    as.character(persona_data[51:56,][which(persona_data[51:56,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[51:56,2]) == 0, "No trust at all in charities",
+  #   as.character(persona_data[51:56,][which(persona_data[51:56,2] == 1), 1])
+  # ),
+   selected = ifelse(
+    sum(per_data[51:56,2]) == 0, "No trust at all in charities",
+    as.character(per_data[51:56,][which(per_data[51:56,2] == 1), 1])
   ),
@@
   # selected = "Donate at least once a month",
-  selected = ifelse(
-    sum(persona_data[57,2]) == 0, "Donate more than once a month, less than once a year",
-    as.character(persona_data[57,][which(persona_data[57,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[57,2]) == 0, "Donate more than once a month, less than once a year",
+  #   as.character(persona_data[57,][which(persona_data[57,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[57,2]) == 0, "Donate more than once a month, less than once a year",
+    as.character(per_data[57,][which(per_data[57,2] == 1), 1])
   ),
@@
   # selected = "$100-$499",
-  selected = ifelse(
-    sum(persona_data[58:63,2]) == 0, "$1-$49",
-    as.character(persona_data[58:63,][which(persona_data[58:63,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[58:63,2]) == 0, "$1-$49",
+  #   as.character(persona_data[58:63,][which(persona_data[58:63,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[58:63,2]) == 0, "$1-$49",
+    as.character(per_data[58:63,][which(per_data[58:63,2] == 1), 1])
   ),
@@
   # selected = "Volunteered in past 12 months",
-  selected = ifelse(
-    sum(persona_data[64,2]) == 0, "Haven't volunteered in past 12 months",
-    as.character(persona_data[64,][which(persona_data[64,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[64,2]) == 0, "Haven't volunteered in past 12 months",
+  #   as.character(persona_data[64,][which(persona_data[64,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[64,2]) == 0, "Haven't volunteered in past 12 months",
+    as.character(per_data[64,][which(per_data[64,2] == 1), 1])
   ),
@@
   # selected = "Volunteer at least once a month",
-  selected = ifelse(
-    sum(persona_data[65:67,2]) == 0, "Haven't volunteered in past 12 months",
-    as.character(persona_data[65:67,][which(persona_data[65:67,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[65:67,2]) == 0, "Haven't volunteered in past 12 months",
+  #   as.character(persona_data[65:67,][which(persona_data[65:67,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[65:67,2]) == 0, "Haven't volunteered in past 12 months",
+    as.character(per_data[65:67,][which(per_data[65:67,2] == 1), 1])
   ),
@@
   # selected = "Personally involved",
-  selected = ifelse(
-    sum(persona_data[68,2]) == 0, "Not personally involved",
-    as.character(persona_data[68,][which(persona_data[68,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[68,2]) == 0, "Not personally involved",
+  #   as.character(persona_data[68,][which(persona_data[68,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[68,2]) == 0, "Not personally involved",
+    as.character(per_data[68,][which(per_data[68,2] == 1), 1])
   ),
@@
   # selected = "Family involved",
-  selected = ifelse(
-    sum(persona_data[69,2]) == 0, "Family not involved",
-    as.character(persona_data[69,][which(persona_data[69,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[69,2]) == 0, "Family not involved",
+  #   as.character(persona_data[69,][which(persona_data[69,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[69,2]) == 0, "Family not involved",
+    as.character(per_data[69,][which(per_data[69,2] == 1), 1])
   ),
@@
   # selected = "Don't belong to church",
-  selected = ifelse(
-    sum(persona_data[70:71,2]) == 0, "Don't belong to church",
-    as.character(persona_data[70:71,][which(persona_data[70:71,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[70:71,2]) == 0, "Don't belong to church",
+  #   as.character(persona_data[70:71,][which(persona_data[70:71,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[70:71,2]) == 0, "Don't belong to church",
+    as.character(per_data[70:71,][which(per_data[70:71,2] == 1), 1])
   ),
@@
   # selected = "Don't belong to sports or rec organization",
-  selected = ifelse(
-    sum(persona_data[72:73,2]) == 0, "Don't belong to sports or rec organization",
-    as.character(persona_data[72:73,][which(persona_data[72:73,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[72:73,2]) == 0, "Don't belong to sports or rec organization",
+  #   as.character(persona_data[72:73,][which(persona_data[72:73,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[72:73,2]) == 0, "Don't belong to sports or rec organization",
+    as.character(per_data[72:73,][which(per_data[72:73,2] == 1), 1])
   ),
@@
   # selected = "Don't belong to educational organization",
-  selected = ifelse(
-    sum(persona_data[74:75,2]) == 0, "Don't belong to educational organization",
-    as.character(persona_data[74:75,][which(persona_data[74:75,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[74:75,2]) == 0, "Don't belong to educational organization",
+  #   as.character(persona_data[74:75,][which(persona_data[74:75,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[74:75,2]) == 0, "Don't belong to educational organization",
+    as.character(per_data[74:75,][which(per_data[74:75,2] == 1), 1])
   ),
@@
   # selected = "Don't belong to union",
-  selected = ifelse(
-    sum(persona_data[76:77,2]) == 0, "Don't belong to union",
-    as.character(persona_data[76:77,][which(persona_data[76:77,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[76:77,2]) == 0, "Don't belong to union",
+  #   as.character(persona_data[76:77,][which(persona_data[76:77,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[76:77,2]) == 0, "Don't belong to union",
+    as.character(per_data[76:77,][which(per_data[76:77,2] == 1), 1])
   ),
@@
   # selected = "Active political party member",
-  selected = ifelse(
-    sum(persona_data[78:79,2]) == 0, "Don't belong to political party",
-    as.character(persona_data[78:79,][which(persona_data[78:79,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[78:79,2]) == 0, "Don't belong to political party",
+  #   as.character(persona_data[78:79,][which(persona_data[78:79,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[78:79,2]) == 0, "Don't belong to political party",
+    as.character(per_data[78:79,][which(per_data[78:79,2] == 1), 1])
   ),
@@
   # selected = "Don't belong to environmental organization",
-  selected = ifelse(
-    sum(persona_data[80:81,2]) == 0, "Don't belong to environmental organization",
-    as.character(persona_data[80:81,][which(persona_data[80:81,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[80:81,2]) == 0, "Don't belong to environmental organization",
+  #   as.character(persona_data[80:81,][which(persona_data[80:81,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[80:81,2]) == 0, "Don't belong to environmental organization",
+    as.character(per_data[80:81,][which(per_data[80:81,2] == 1), 1])
   ),
@@
   # selected = "Don't belong to professional association",
-  selected = ifelse(
-    sum(persona_data[82:83,2]) == 0, "Don't belong to professional association",
-    as.character(persona_data[82:83,][which(persona_data[82:83,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[82:83,2]) == 0, "Don't belong to professional association",
+  #   as.character(persona_data[82:83,][which(persona_data[82:83,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[82:83,2]) == 0, "Don't belong to professional association",
+    as.character(per_data[82:83,][which(per_data[82:83,2] == 1), 1])
   ),
@@
   # selected = "Active humanitarian or charitable organization member",
-  selected = ifelse(
-    sum(persona_data[84:85,2]) == 0, "Don't belong to humanitarian or charitable organization",
-    as.character(persona_data[84:85,][which(persona_data[84:85,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[84:85,2]) == 0, "Don't belong to humanitarian or charitable organization",
+  #   as.character(persona_data[84:85,][which(persona_data[84:85,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[84:85,2]) == 0, "Don't belong to humanitarian or charitable organization",
+    as.character(per_data[84:85,][which(per_data[84:85,2] == 1), 1])
   ),
@@
   # selected = "Don't belong to consumer organization",
-  selected = ifelse(
-    sum(persona_data[86:87,2]) == 0, "Don't belong to consumer organization",
-    as.character(persona_data[86:87,][which(persona_data[86:87,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[86:87,2]) == 0, "Don't belong to consumer organization",
+  #   as.character(persona_data[86:87,][which(persona_data[86:87,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[86:87,2]) == 0, "Don't belong to consumer organization",
+    as.character(per_data[86:87,][which(per_data[86:87,2] == 1), 1])
   ),
@@
   # selected = "Don't belong to another organization",
-  selected = ifelse(
-    sum(persona_data[88:89,2]) == 0, "Don't belong to another organization",
-    as.character(persona_data[88:89,][which(persona_data[88:89,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[88:89,2]) == 0, "Don't belong to another organization",
+  #   as.character(persona_data[88:89,][which(persona_data[88:89,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[88:89,2]) == 0, "Don't belong to another organization",
+    as.character(per_data[88:89,][which(per_data[88:89,2] == 1), 1])
   ),
@@
   # selected = "Male",
-  selected = ifelse(
-    sum(persona_data[90:93,2]) == 0, "Male",
-    as.character(persona_data[90:93,][which(persona_data[90:93,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[90:93,2]) == 0, "Male",
+  #   as.character(persona_data[90:93,][which(persona_data[90:93,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[90:93,2]) == 0, "Male",
+    as.character(per_data[90:93,][which(per_data[90:93,2] == 1), 1])
   ),
@@
   # selected = "Married",
-  selected = ifelse(
-    sum(persona_data[94:97,2]) == 0, "Married",
-    as.character(persona_data[94:97,][which(persona_data[94:97,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[94:97,2]) == 0, "Married",
+  #   as.character(persona_data[94:97,][which(persona_data[94:97,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[94:97,2]) == 0, "Married",
+    as.character(per_data[94:97,][which(per_data[94:97,2] == 1), 1])
   ),
@@
   # selected = "2 year degree",
-  selected = ifelse(
-    sum(persona_data[98:103,2]) == 0, "Less than high school",
-    as.character(persona_data[98:103,][which(persona_data[98:103,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[98:103,2]) == 0, "Less than high school",
+  #   as.character(persona_data[98:103,][which(persona_data[98:103,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[98:103,2]) == 0, "Less than high school",
+    as.character(per_data[98:103,][which(per_data[98:103,2] == 1), 1])
   ),
@@
   # selected = "More than median of $61,372",
-  selected = ifelse(
-    sum(persona_data[104,2]) == 0, "Less than median of $61,372",
-    as.character(persona_data[104,][which(persona_data[104,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[104,2]) == 0, "Less than median of $61,372",
+  #   as.character(persona_data[104,][which(persona_data[104,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[104,2]) == 0, "Less than median of $61,372",
+    as.character(per_data[104,][which(per_data[104,2] == 1), 1])
   ),
@@
   # selected = "White",
-  selected = deframe(persona_data[105:110,][which(persona_data[105:110,2] == 1), 1]),
+  # selected = deframe(persona_data[105:110,][which(persona_data[105:110,2] == 1), 1]),
+  selected = deframe(per_data[105:110,][which(per_data[105:110,2] == 1), 1]),
   width = "450px"
@@
   # selected = "Less than median age of 36",
-  selected = ifelse(
-    sum(persona_data[111,2]) == 0, "Less than median age of 36",
-    as.character(persona_data[111,][which(persona_data[111,2] == 1), 1])
+  # selected = ifelse(
+  #   sum(persona_data[111,2]) == 0, "Less than median age of 36",
+  #   as.character(persona_data[111,][which(persona_data[111,2] == 1), 1])
+  # ),
+  selected = ifelse(
+    sum(per_data[111,2]) == 0, "Less than median age of 36",
+    as.character(per_data[111,][which(per_data[111,2] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[2:3,3]) == 0, "Rarely",
-    as.character(persona_data[2:3,][which(persona_data[2:3,3] == 1), 1])
+    sum(per_data[2:3,3]) == 0, "Rarely",
+    as.character(per_data[2:3,][which(per_data[2:3,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[4:5,3]) == 0, "Never",
-    as.character(persona_data[4:5,][which(persona_data[4:5,3] == 1), 1])
+    sum(per_data[4:5,3]) == 0, "Never",
+    as.character(per_data[4:5,][which(per_data[4:5,3] == 1), 1])
   ),
@@
   # selected = c("TV", "Print", "Social media"),
-  selected = deframe(persona_data[6:12,][which(persona_data[6:12,3] == 1), 1]),
+  selected = deframe(per_data[6:12,][which(per_data[6:12,3] == 1), 1]),
   width = "450px"
@@
   selected = ifelse(
-    sum(persona_data[13,3]) == 0, "Not Often",
-    as.character(persona_data[13,][which(persona_data[13,3] == 1), 1])
+    sum(per_data[13,3]) == 0, "Not Often",
+    as.character(per_data[13,][which(per_data[13,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[14,3]) == 0, "Hasn't traveled to a developing country",
-    as.character(persona_data[14,][which(persona_data[14,3] == 1), 1])
+    sum(per_data[14,3]) == 0, "Hasn't traveled to a developing country",
+    as.character(per_data[14,][which(per_data[14,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[15:20,3]) == 0, "Extremely liberal",
-    as.character(persona_data[15:20,][which(persona_data[15:20,3] == 1), 1])
+    sum(per_data[15:20,3]) == 0, "Extremely liberal",
+    as.character(per_data[15:20,][which(per_data[15:20,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[21:26,3]) == 0, "No trust at all in political institutions",
-    as.character(persona_data[21:26,][which(persona_data[21:26,3] == 1), 1])
+    sum(per_data[21:26,3]) == 0, "No trust at all in political institutions",
+    as.character(per_data[21:26,][which(per_data[21:26,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[27:32,3]) == 0, "Strongly disagree",
-    as.character(persona_data[27:32,][which(persona_data[27:32,3] == 1), 1])
+    sum(per_data[27:32,3]) == 0, "Strongly disagree",
+    as.character(per_data[27:32,][which(per_data[27:32,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[33:34,3]) == 0, "Not sure",
-    as.character(persona_data[33:34,][which(persona_data[33:34,3] == 1), 1])
+    sum(per_data[33:34,3]) == 0, "Not sure",
+    as.character(per_data[33:34,][which(per_data[33:34,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[35,3]) == 0, "Not important",
-    as.character(persona_data[35,][which(persona_data[35,3] == 1), 1])
+    sum(per_data[35,3]) == 0, "Not important",
+    as.character(per_data[35,][which(per_data[35,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[36:44,3]) == 0, "Catholic",
-    as.character(persona_data[36:44,][which(persona_data[36:44,3] == 1), 1])
+    sum(per_data[36:44,3]) == 0, "Catholic",
+    as.character(per_data[36:44,][which(per_data[36:44,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[45:50,3]) == 0, "Not at all important",
-    as.character(persona_data[45:50,][which(persona_data[45:50,3] == 1), 1])
+    sum(per_data[45:50,3]) == 0, "Not at all important",
+    as.character(per_data[45:50,][which(per_data[45:50,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[51:56,3]) == 0, "No trust at all in charities",
-    as.character(persona_data[51:56,][which(persona_data[51:56,3] == 1), 1])
+    sum(per_data[51:56,3]) == 0, "No trust at all in charities",
+    as.character(per_data[51:56,][which(per_data[51:56,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[57,3]) == 0, "Donate more than once a month, less than once a year",
-    as.character(persona_data[57,][which(persona_data[57,3] == 1), 1])
+    sum(per_data[57,3]) == 0, "Donate more than once a month, less than once a year",
+    as.character(per_data[57,][which(per_data[57,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[58:63,3]) == 0, "$1-$49",
-    as.character(persona_data[58:63,][which(persona_data[58:63,3] == 1), 1])
+    sum(per_data[58:63,3]) == 0, "$1-$49",
+    as.character(per_data[58:63,][which(per_data[58:63,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[64,3]) == 0, "Haven't volunteered in past 12 months",
-    as.character(persona_data[64,][which(persona_data[64,3] == 1), 1])
+    sum(per_data[64,3]) == 0, "Haven't volunteered in past 12 months",
+    as.character(per_data[64,][which(per_data[64,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[65:67,3]) == 0, "Haven't volunteered in past 12 months",
-    as.character(persona_data[65:67,][which(persona_data[65:67,3] == 1), 1])
+    sum(per_data[65:67,3]) == 0, "Haven't volunteered in past 12 months",
+    as.character(per_data[65:67,][which(per_data[65:67,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[68,3]) == 0, "Not personally involved",
-    as.character(persona_data[68,][which(persona_data[68,3] == 1), 1])
+    sum(per_data[68,3]) == 0, "Not personally involved",
+    as.character(per_data[68,][which(per_data[68,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[69,3]) == 0, "Family not involved",
-    as.character(persona_data[69,][which(persona_data[69,3] == 1), 1])
+    sum(per_data[69,3]) == 0, "Family not involved",
+    as.character(per_data[69,][which(per_data[69,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[70:71,3]) == 0, "Don't belong to church",
-    as.character(persona_data[70:71,][which(persona_data[70:71,3] == 1), 1])
+    sum(per_data[70:71,3]) == 0, "Don't belong to church",
+    as.character(per_data[70:71,][which(per_data[70:71,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[72:73,3]) == 0, "Don't belong to sports or rec organization",
-    as.character(persona_data[72:73,][which(persona_data[72:73,3] == 1), 1])
+    sum(per_data[72:73,3]) == 0, "Don't belong to sports or rec organization",
+    as.character(per_data[72:73,][which(per_data[72:73,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[74:75,3]) == 0, "Don't belong to educational organization",
-    as.character(persona_data[74:75,][which(persona_data[74:75,3] == 1), 1])
+    sum(per_data[74:75,3]) == 0, "Don't belong to educational organization",
+    as.character(per_data[74:75,][which(per_data[74:75,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[76:77,3]) == 0, "Don't belong to union",
-    as.character(persona_data[76:77,][which(persona_data[76:77,3] == 1), 1])
+    sum(per_data[76:77,3]) == 0, "Don't belong to union",
+    as.character(per_data[76:77,][which(per_data[76:77,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[78:79,3]) == 0, "Don't belong to political party",
-    as.character(persona_data[78:79,][which(persona_data[78:79,3] == 1), 1])
+    sum(per_data[78:79,3]) == 0, "Don't belong to political party",
+    as.character(per_data[78:79,][which(per_data[78:79,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[80:81,3]) == 0, "Don't belong to environmental organization",
-    as.character(persona_data[80:81,][which(persona_data[80:81,3] == 1), 1])
+    sum(per_data[80:81,3]) == 0, "Don't belong to environmental organization",
+    as.character(per_data[80:81,][which(per_data[80:81,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[82:83,3]) == 0, "Don't belong to professional association",
-    as.character(persona_data[82:83,][which(persona_data[82:83,3] == 1), 1])
+    sum(per_data[82:83,3]) == 0, "Don't belong to professional association",
+    as.character(per_data[82:83,][which(per_data[82:83,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[84:85,3]) == 0, "Don't belong to humanitarian or charitable organization",
-    as.character(persona_data[84:85,][which(persona_data[84:85,3] == 1), 1])
+    sum(per_data[84:85,3]) == 0, "Don't belong to humanitarian or charitable organization",
+    as.character(per_data[84:85,][which(per_data[84:85,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[86:87,3]) == 0, "Don't belong to consumer organization",
-    as.character(persona_data[86:87,][which(persona_data[86:87,3] == 1), 1])
+    sum(per_data[86:87,3]) == 0, "Don't belong to consumer organization",
+    as.character(per_data[86:87,][which(per_data[86:87,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[88:89,3]) == 0, "Don't belong to another organization",
-    as.character(persona_data[88:89,][which(persona_data[88:89,3] == 1), 1])
+    sum(per_data[88:89,3]) == 0, "Don't belong to another organization",
+    as.character(per_data[88:89,][which(per_data[88:89,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[90:93,3]) == 0, "Male",
-    as.character(persona_data[90:93,][which(persona_data[90:93,3] == 1), 1])
+    sum(per_data[90:93,3]) == 0, "Male",
+    as.character(per_data[90:93,][which(per_data[90:93,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[94:97,3]) == 0, "Married",
-    as.character(persona_data[94:97,][which(persona_data[94:97,3] == 1), 1])
+    sum(per_data[94:97,3]) == 0, "Married",
+    as.character(per_data[94:97,][which(per_data[94:97,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[98:103,3]) == 0, "Less than high school",
-    as.character(persona_data[98:103,][which(persona_data[98:103,3] == 1), 1])
+    sum(per_data[98:103,3]) == 0, "Less than high school",
+    as.character(per_data[98:103,][which(per_data[98:103,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[104,3]) == 0, "Less than median of $61,372",
-    as.character(persona_data[104,][which(persona_data[104,3] == 1), 1])
+    sum(per_data[104,3]) == 0, "Less than median of $61,372",
+    as.character(per_data[104,][which(per_data[104,3] == 1), 1])
   ),
@@
   # selected = "American Indian or Alaskan Native",
-  selected = deframe(persona_data[105:110,][which(persona_data[105:110,3] == 1), 1]),
+  selected = deframe(per_data[105:110,][which(per_data[105:110,3] == 1), 1]),
   width = "450px"
@@
   selected = ifelse(
-    sum(persona_data[111,3]) == 0, "Less than median age of 36",
-    as.character(persona_data[111,][which(persona_data[111,3] == 1), 1])
+    sum(per_data[111,3]) == 0, "Less than median age of 36",
+    as.character(per_data[111,][which(per_data[111,3] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[2:3,4]) == 0, "Rarely",
-    as.character(persona_data[2:3,][which(persona_data[2:3,4] == 1), 1])
+    sum(per_data[2:3,4]) == 0, "Rarely",
+    as.character(per_data[2:3,][which(per_data[2:3,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[4:5,4]) == 0, "Never",
-    as.character(persona_data[4:5,][which(persona_data[4:5,4] == 1), 1])
+    sum(per_data[4:5,4]) == 0, "Never",
+    as.character(per_data[4:5,][which(per_data[4:5,4] == 1), 1])
   ),
@@
   # selected = c("TV", "Print", "Social media"),
-  selected = deframe(persona_data[6:12,][which(persona_data[6:12,4] == 1), 1]),
+  selected = deframe(per_data[6:12,][which(per_data[6:12,4] == 1), 1]),
   width = "450px"
@@
   selected = ifelse(
-    sum(persona_data[13,4]) == 0, "Not Often",
-    as.character(persona_data[13,][which(persona_data[13,4] == 1), 1])
+    sum(per_data[13,4]) == 0, "Not Often",
+    as.character(per_data[13,][which(per_data[13,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[14,4]) == 0, "Hasn't traveled to a developing country",
-    as.character(persona_data[14,][which(persona_data[14,4] == 1), 1])
+    sum(per_data[14,4]) == 0, "Hasn't traveled to a developing country",
+    as.character(per_data[14,][which(per_data[14,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[15:20,4]) == 0, "Extremely liberal",
-    as.character(persona_data[15:20,][which(persona_data[15:20,4] == 1), 1])
+    sum(per_data[15:20,4]) == 0, "Extremely liberal",
+    as.character(per_data[15:20,][which(per_data[15:20,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[21:26,4]) == 0, "No trust at all in political institutions",
-    as.character(persona_data[21:26,][which(persona_data[21:26,4] == 1), 1])
+    sum(per_data[21:26,4]) == 0, "No trust at all in political institutions",
+    as.character(per_data[21:26,][which(per_data[21:26,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[27:32,4]) == 0, "Strongly disagree",
-    as.character(persona_data[27:32,][which(persona_data[27:32,4] == 1), 1])
+    sum(per_data[27:32,4]) == 0, "Strongly disagree",
+    as.character(per_data[27:32,][which(per_data[27:32,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[33:34,4]) == 0, "Not sure",
-    as.character(persona_data[33:34,][which(persona_data[33:34,4] == 1), 1])
+    sum(per_data[33:34,4]) == 0, "Not sure",
+    as.character(per_data[33:34,][which(per_data[33:34,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[35,4]) == 0, "Not important",
-    as.character(persona_data[35,][which(persona_data[35,4] == 1), 1])
+    sum(per_data[35,4]) == 0, "Not important",
+    as.character(per_data[35,][which(per_data[35,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[36:44,4]) == 0, "Catholic",
-    as.character(persona_data[36:44,][which(persona_data[36:44,4] == 1), 1])
+    sum(per_data[36:44,4]) == 0, "Catholic",
+    as.character(per_data[36:44,][which(per_data[36:44,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[45:50,4]) == 0, "Not at all important",
-    as.character(persona_data[45:50,][which(persona_data[45:50,4] == 1), 1])
+    sum(per_data[45:50,4]) == 0, "Not at all important",
+    as.character(per_data[45:50,][which(per_data[45:50,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[51:56,4]) == 0, "No trust at all in charities",
-    as.character(persona_data[51:56,][which(persona_data[51:56,4] == 1), 1])
+    sum(per_data[51:56,4]) == 0, "No trust at all in charities",
+    as.character(per_data[51:56,][which(per_data[51:56,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[57,4]) == 0, "Donate more than once a month, less than once a year",
-    as.character(persona_data[57,][which(persona_data[57,4] == 1), 1])
+    sum(per_data[57,4]) == 0, "Donate more than once a month, less than once a year",
+    as.character(per_data[57,][which(per_data[57,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[58:63,4]) == 0, "$1-$49",
-    as.character(persona_data[58:63,][which(persona_data[58:63,4] == 1), 1])
+    sum(per_data[58:63,4]) == 0, "$1-$49",
+    as.character(per_data[58:63,][which(per_data[58:63,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[64,4]) == 0, "Haven't volunteered in past 12 months",
-    as.character(persona_data[64,][which(persona_data[64,4] == 1), 1])
+    sum(per_data[64,4]) == 0, "Haven't volunteered in past 12 months",
+    as.character(per_data[64,][which(per_data[64,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[65:67,4]) == 0, "Haven't volunteered in past 12 months",
-    as.character(persona_data[65:67,][which(persona_data[65:67,4] == 1), 1])
+    sum(per_data[65:67,4]) == 0, "Haven't volunteered in past 12 months",
+    as.character(per_data[65:67,][which(per_data[65:67,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[68,4]) == 0, "Not personally involved",
-    as.character(persona_data[68,][which(persona_data[68,4] == 1), 1])
+    sum(per_data[68,4]) == 0, "Not personally involved",
+    as.character(per_data[68,][which(per_data[68,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[69,4]) == 0, "Family not involved",
-    as.character(persona_data[69,][which(persona_data[69,4] == 1), 1])
+    sum(per_data[69,4]) == 0, "Family not involved",
+    as.character(per_data[69,][which(per_data[69,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[70:71,4]) == 0, "Don't belong to church",
-    as.character(persona_data[70:71,][which(persona_data[70:71,4] == 1), 1])
+    sum(per_data[70:71,4]) == 0, "Don't belong to church",
+    as.character(per_data[70:71,][which(per_data[70:71,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[72:73,4]) == 0, "Don't belong to sports or rec organization",
-    as.character(persona_data[72:73,][which(persona_data[72:73,4] == 1), 1])
+    sum(per_data[72:73,4]) == 0, "Don't belong to sports or rec organization",
+    as.character(per_data[72:73,][which(per_data[72:73,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[74:75,4]) == 0, "Don't belong to educational organization",
-    as.character(persona_data[74:75,][which(persona_data[74:75,4] == 1), 1])
+    sum(per_data[74:75,4]) == 0, "Don't belong to educational organization",
+    as.character(per_data[74:75,][which(per_data[74:75,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[76:77,4]) == 0, "Don't belong to union",
-    as.character(persona_data[76:77,][which(persona_data[76:77,4] == 1), 1])
+    sum(per_data[76:77,4]) == 0, "Don't belong to union",
+    as.character(per_data[76:77,][which(per_data[76:77,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[78:79,4]) == 0, "Don't belong to political party",
-    as.character(persona_data[78:79,][which(persona_data[78:79,4] == 1), 1])
+    sum(per_data[78:79,4]) == 0, "Don't belong to political party",
+    as.character(per_data[78:79,][which(per_data[78:79,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[80:81,4]) == 0, "Don't belong to environmental organization",
-    as.character(persona_data[80:81,][which(persona_data[80:81,4] == 1), 1])
+    sum(per_data[80:81,4]) == 0, "Don't belong to environmental organization",
+    as.character(per_data[80:81,][which(per_data[80:81,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[82:83,4]) == 0, "Don't belong to professional association",
-    as.character(persona_data[82:83,][which(persona_data[82:83,4] == 1), 1])
+    sum(per_data[82:83,4]) == 0, "Don't belong to professional association",
+    as.character(per_data[82:83,][which(per_data[82:83,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[84:85,4]) == 0, "Don't belong to humanitarian or charitable organization",
-    as.character(persona_data[84:85,][which(persona_data[84:85,4] == 1), 1])
+    sum(per_data[84:85,4]) == 0, "Don't belong to humanitarian or charitable organization",
+    as.character(per_data[84:85,][which(per_data[84:85,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[86:87,4]) == 0, "Don't belong to consumer organization",
-    as.character(persona_data[86:87,][which(persona_data[86:87,4] == 1), 1])
+    sum(per_data[86:87,4]) == 0, "Don't belong to consumer organization",
+    as.character(per_data[86:87,][which(per_data[86:87,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[88:89,4]) == 0, "Don't belong to another organization",
-    as.character(persona_data[88:89,][which(persona_data[88:89,4] == 1), 1])
+    sum(per_data[88:89,4]) == 0, "Don't belong to another organization",
+    as.character(per_data[88:89,][which(per_data[88:89,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[90:93,4]) == 0, "Male",
-    as.character(persona_data[90:93,][which(persona_data[90:93,4] == 1), 1])
+    sum(per_data[90:93,4]) == 0, "Male",
+    as.character(per_data[90:93,][which(per_data[90:93,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[94:97,4]) == 0, "Married",
-    as.character(persona_data[94:97,][which(persona_data[94:97,4] == 1), 1])
+    sum(per_data[94:97,4]) == 0, "Married",
+    as.character(per_data[94:97,][which(per_data[94:97,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[98:103,4]) == 0, "Less than high school",
-    as.character(persona_data[98:103,][which(persona_data[98:103,4] == 1), 1])
+    sum(per_data[98:103,4]) == 0, "Less than high school",
+    as.character(per_data[98:103,][which(per_data[98:103,4] == 1), 1])
   ),
@@
   selected = ifelse(
-    sum(persona_data[104,4]) == 0, "Less than median of $61,372",
-    as.character(persona_data[104,][which(persona_data[104,4] == 1), 1])
+    sum(per_data[104,4]) == 0, "Less than median of $61,372",
+    as.character(per_data[104,][which(per_data[104,4] == 1), 1])
   ),
@@
   # selected = c("Black or African American", "American Indian or Alaskan Native"),
-  selected = deframe(persona_data[105:110,][which(persona_data[105:110,4] == 1), 1]),
+  selected = deframe(per_data[105:110,][which(per_data[105:110,4] == 1), 1]),
   width = "450px"
@@
   selected = ifelse(
-    sum(persona_data[111,4]) == 0, "Less than median age of 36",
-    as.character(persona_data[111,][which(persona_data[111,4] == 1), 1])
+    sum(per_data[111,4]) == 0, "Less than median age of 36",
+    as.character(per_data[111,][which(per_data[111,4] == 1), 1])
   ),
@@
   filename = function() {
-    paste0("persona_data_",Sys.time(),".csv")
+    paste0("per_data_",Sys.time(),".csv")
   },
@@
 
-actionButton(
-  inputId = "org_apply",
-  label = "Apply New Data",
-  icon = icon("play")
-)
-
-observeEvent(eventExpr = input$org_apply,
-  handlerExpr = {
-      req(input$org_update)
-      file <- read_csv(input$org_update$datapath)
-      org_update$data <- file
-  }, ignoreNULL = FALSE)
-
 # Persona file input
 fileInput(
-  "file_per",
+  "per_update",
   "Import Persona Data",
@@
 
-# observeEvent(eventExpr = input$apply, 
-#   handlerExpr = {
-#       req(input$file_per)
-#       file <- read_csv(input$file_per$datapath)
-#       per_update$data <- file
-#   }, ignoreNULL = FALSE)
-
 # Render the organization configurations as a table
 renderTable({
-  org_import = read_csv(input$file_org$datapath)
+  org_import = read_csv(input$org_update$datapath)
 
@@
 renderTable({
-  per_import = read_csv(input$file_per$datapath)
+  per_import = read_csv(input$per_update$datapath)
 
@@
 
-# Conditional argument to run IF new data is imported
-# organization_data <- file_org
-# persona_data <- file_per
 ```

### 2020-10-21 analysis/05_market_simulator.Rmd
finished persona inputs

--- 2020-10-21 analysis/05_market_simulator.Rmd
@@
 # Initial persona configuration
-persona_data <- read_csv(
-  here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
-)
+# persona_data <- read_csv(
+#   here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
+# )
+
+persona_values <- reactiveValues()
+
+persona_data <- reactive({
+  if (is.null(input$per_update$datapath)) {
+    persona_data <- read_csv(here::here('analysis', 'output', 'configurations', 'persona_config01.csv'))
+    # persona_values$file_name = "persona_config01.csv"
+    # persona_values$file_type = "csv"
+    # persona_values$file_size = file.size(here::here('analysis', 'output', 'configurations', 'persona_config01.csv'))
+    # persona_values$file_path = here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
+  } else {
+    persona_data <- read_csv(input$per_update$datapath)
+    # persona_values$file_name = input$per_update$name
+    # persona_values$file_size = input$per_update$size
+    # persona_values$file_type = input$per_update$type
+    # persona_values$file_path = input$per_update$datapath
+  }
+})
 
@@
     # selected = "At least once a day",
-  selected = ifelse(
-    sum(persona_data[2:3,2]) == 0, "Rarely",
-    as.character(persona_data[2:3,][which(persona_data[2:3,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[2:3,2]) == 0, "Rarely",
+    #   as.character(persona_data[2:3,][which(persona_data[2:3,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[2:3,2]) == 0, "Rarely",
+      as.character(per_data[2:3,][which(per_data[2:3,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Follow international news
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Always",
-  selected = ifelse(
-    sum(persona_data[4:5,2]) == 0, "Never",
-    as.character(persona_data[4:5,][which(persona_data[4:5,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[4:5,2]) == 0, "Never",
+    #   as.character(persona_data[4:5,][which(persona_data[4:5,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[4:5,2]) == 0, "Never",
+      as.character(per_data[4:5,][which(per_data[4:5,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Mediums to follow news
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = c("TV", "Print", "Social media"),
-  selected = deframe(persona_data[6:12,][which(persona_data[6:12,2] == 1), 1]),
-  width = "450px"
-)
+    # selected = deframe(persona_data[6:12,][which(persona_data[6:12,2] == 1), 1]),
+    selected = deframe(per_data[6:12,][which(per_data[6:12,2] == 1), 1]),
+    width = "450px"
+  )
+
+})
 
 # Follow government and public affairs
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Often",
-  selected = ifelse(
-    sum(persona_data[13,2]) == 0, "Not Often",
-    as.character(persona_data[13,][which(persona_data[13,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[13,2]) == 0, "Not Often",
+    #   as.character(persona_data[13,][which(persona_data[13,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[13,2]) == 0, "Not Often",
+      as.character(per_data[13,][which(per_data[13,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Traveled to a developing country
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Traveled to a developing country",
-  selected = ifelse(
-    sum(persona_data[14,2]) == 0, "Hasn't traveled to a developing country",
-    as.character(persona_data[14,][which(persona_data[14,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[14,2]) == 0, "Hasn't traveled to a developing country",
+    #   as.character(persona_data[14,][which(persona_data[14,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[14,2]) == 0, "Hasn't traveled to a developing country",
+      as.character(per_data[14,][which(per_data[14,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Liberal to Conservative
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Somewhat liberal",
-  selected = ifelse(
-    sum(persona_data[15:20,2]) == 0, "Extremely liberal",
-    as.character(persona_data[15:20,][which(persona_data[15:20,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[15:20,2]) == 0, "Extremely liberal",
+    #   as.character(persona_data[15:20,][which(persona_data[15:20,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[15:20,2]) == 0, "Extremely liberal",
+      as.character(per_data[15:20,][which(per_data[15:20,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Trust in political institutions
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Complete trust in political institutions",
-  selected = ifelse(
-    sum(persona_data[21:26,2]) == 0, "No trust at all in political institutions",
-    as.character(persona_data[21:26,][which(persona_data[21:26,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[21:26,2]) == 0, "No trust at all in political institutions",
+    #   as.character(persona_data[21:26,][which(persona_data[21:26,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[21:26,2]) == 0, "No trust at all in political institutions",
+      as.character(per_data[21:26,][which(per_data[21:26,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # People should be more charitable
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Strongly agree",
-  selected = ifelse(
-    sum(persona_data[27:32,2]) == 0, "Strongly disagree",
-    as.character(persona_data[27:32,][which(persona_data[27:32,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[27:32,2]) == 0, "Strongly disagree",
+    #   as.character(persona_data[27:32,][which(persona_data[27:32,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[27:32,2]) == 0, "Strongly disagree",
+      as.character(per_data[27:32,][which(per_data[27:32,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Religious attendance
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Attend at least once a month",
-  selected = ifelse(
-    sum(persona_data[33:34,2]) == 0, "Not sure",
-    as.character(persona_data[33:34,][which(persona_data[33:34,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[33:34,2]) == 0, "Not sure",
+    #   as.character(persona_data[33:34,][which(persona_data[33:34,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[33:34,2]) == 0, "Not sure",
+      as.character(per_data[33:34,][which(per_data[33:34,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Importance of religion
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Important",
-  selected = ifelse(
-    sum(persona_data[35,2]) == 0, "Not important",
-    as.character(persona_data[35,][which(persona_data[35,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[35,2]) == 0, "Not important",
+    #   as.character(persona_data[35,][which(persona_data[35,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[35,2]) == 0, "Not important",
+      as.character(per_data[35,][which(per_data[35,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Religion
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = 'Protestant',
-  selected = ifelse(
-    sum(persona_data[36:44,2]) == 0, "Catholic",
-    as.character(persona_data[36:44,][which(persona_data[36:44,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[36:44,2]) == 0, "Catholic",
+    #   as.character(persona_data[36:44,][which(persona_data[36:44,2] == 1), 1])
+    # ),
+     selected = ifelse(
+      sum(per_data[36:44,2]) == 0, "Catholic",
+      as.character(per_data[36:44,][which(per_data[36:44,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Importance of trusting charities
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Somewhat unimportant",
-  selected = ifelse(
-    sum(persona_data[45:50,2]) == 0, "Not at all important",
-    as.character(persona_data[45:50,][which(persona_data[45:50,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[45:50,2]) == 0, "Not at all important",
+    #   as.character(persona_data[45:50,][which(persona_data[45:50,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[45:50,2]) == 0, "Not at all important",
+      as.character(per_data[45:50,][which(per_data[45:50,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Trust in charities
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Complete trust in charities",
-  selected = ifelse(
-    sum(persona_data[51:56,2]) == 0, "No trust at all in charities",
-    as.character(persona_data[51:56,][which(persona_data[51:56,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[51:56,2]) == 0, "No trust at all in charities",
+    #   as.character(persona_data[51:56,][which(persona_data[51:56,2] == 1), 1])
+    # ),
+     selected = ifelse(
+      sum(per_data[51:56,2]) == 0, "No trust at all in charities",
+      as.character(per_data[51:56,][which(per_data[51:56,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Donation frequency
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Donate at least once a month",
-  selected = ifelse(
-    sum(persona_data[57,2]) == 0, "Donate more than once a month, less than once a year",
-    as.character(persona_data[57,][which(persona_data[57,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[57,2]) == 0, "Donate more than once a month, less than once a year",
+    #   as.character(persona_data[57,][which(persona_data[57,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[57,2]) == 0, "Donate more than once a month, less than once a year",
+      as.character(per_data[57,][which(per_data[57,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Donated last year
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "$100-$499",
-  selected = ifelse(
-    sum(persona_data[58:63,2]) == 0, "$1-$49",
-    as.character(persona_data[58:63,][which(persona_data[58:63,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[58:63,2]) == 0, "$1-$49",
+    #   as.character(persona_data[58:63,][which(persona_data[58:63,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[58:63,2]) == 0, "$1-$49",
+      as.character(per_data[58:63,][which(per_data[58:63,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Volunteered in past 12 months
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Volunteered in past 12 months",
-  selected = ifelse(
-    sum(persona_data[64,2]) == 0, "Haven't volunteered in past 12 months",
-    as.character(persona_data[64,][which(persona_data[64,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[64,2]) == 0, "Haven't volunteered in past 12 months",
+    #   as.character(persona_data[64,][which(persona_data[64,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[64,2]) == 0, "Haven't volunteered in past 12 months",
+      as.character(per_data[64,][which(per_data[64,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Volunteer frequency
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Volunteer at least once a month",
-  selected = ifelse(
-    sum(persona_data[65:67,2]) == 0, "Haven't volunteered in past 12 months",
-    as.character(persona_data[65:67,][which(persona_data[65:67,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[65:67,2]) == 0, "Haven't volunteered in past 12 months",
+    #   as.character(persona_data[65:67,][which(persona_data[65:67,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[65:67,2]) == 0, "Haven't volunteered in past 12 months",
+      as.character(per_data[65:67,][which(per_data[65:67,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # History of activism
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Personally involved",
-  selected = ifelse(
-    sum(persona_data[68,2]) == 0, "Not personally involved",
-    as.character(persona_data[68,][which(persona_data[68,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[68,2]) == 0, "Not personally involved",
+    #   as.character(persona_data[68,][which(persona_data[68,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[68,2]) == 0, "Not personally involved",
+      as.character(per_data[68,][which(per_data[68,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # History of family activism
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Family involved",
-  selected = ifelse(
-    sum(persona_data[69,2]) == 0, "Family not involved",
-    as.character(persona_data[69,][which(persona_data[69,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[69,2]) == 0, "Family not involved",
+    #   as.character(persona_data[69,][which(persona_data[69,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[69,2]) == 0, "Family not involved",
+      as.character(per_data[69,][which(per_data[69,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Church or religious organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Don't belong to church",
-  selected = ifelse(
-    sum(persona_data[70:71,2]) == 0, "Don't belong to church",
-    as.character(persona_data[70:71,][which(persona_data[70:71,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[70:71,2]) == 0, "Don't belong to church",
+    #   as.character(persona_data[70:71,][which(persona_data[70:71,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[70:71,2]) == 0, "Don't belong to church",
+      as.character(per_data[70:71,][which(per_data[70:71,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Sport or recreational organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Don't belong to sports or rec organization",
-  selected = ifelse(
-    sum(persona_data[72:73,2]) == 0, "Don't belong to sports or rec organization",
-    as.character(persona_data[72:73,][which(persona_data[72:73,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[72:73,2]) == 0, "Don't belong to sports or rec organization",
+    #   as.character(persona_data[72:73,][which(persona_data[72:73,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[72:73,2]) == 0, "Don't belong to sports or rec organization",
+      as.character(per_data[72:73,][which(per_data[72:73,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Art, music, or educational organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Don't belong to educational organization",
-  selected = ifelse(
-    sum(persona_data[74:75,2]) == 0, "Don't belong to educational organization",
-    as.character(persona_data[74:75,][which(persona_data[74:75,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[74:75,2]) == 0, "Don't belong to educational organization",
+    #   as.character(persona_data[74:75,][which(persona_data[74:75,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[74:75,2]) == 0, "Don't belong to educational organization",
+      as.character(per_data[74:75,][which(per_data[74:75,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Labor union
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Don't belong to union",
-  selected = ifelse(
-    sum(persona_data[76:77,2]) == 0, "Don't belong to union",
-    as.character(persona_data[76:77,][which(persona_data[76:77,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[76:77,2]) == 0, "Don't belong to union",
+    #   as.character(persona_data[76:77,][which(persona_data[76:77,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[76:77,2]) == 0, "Don't belong to union",
+      as.character(per_data[76:77,][which(per_data[76:77,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Political party
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Active political party member",
-  selected = ifelse(
-    sum(persona_data[78:79,2]) == 0, "Don't belong to political party",
-    as.character(persona_data[78:79,][which(persona_data[78:79,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[78:79,2]) == 0, "Don't belong to political party",
+    #   as.character(persona_data[78:79,][which(persona_data[78:79,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[78:79,2]) == 0, "Don't belong to political party",
+      as.character(per_data[78:79,][which(per_data[78:79,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Environmental organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Don't belong to environmental organization",
-  selected = ifelse(
-    sum(persona_data[80:81,2]) == 0, "Don't belong to environmental organization",
-    as.character(persona_data[80:81,][which(persona_data[80:81,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[80:81,2]) == 0, "Don't belong to environmental organization",
+    #   as.character(persona_data[80:81,][which(persona_data[80:81,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[80:81,2]) == 0, "Don't belong to environmental organization",
+      as.character(per_data[80:81,][which(per_data[80:81,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Professional association
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Don't belong to professional association",
-  selected = ifelse(
-    sum(persona_data[82:83,2]) == 0, "Don't belong to professional association",
-    as.character(persona_data[82:83,][which(persona_data[82:83,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[82:83,2]) == 0, "Don't belong to professional association",
+    #   as.character(persona_data[82:83,][which(persona_data[82:83,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[82:83,2]) == 0, "Don't belong to professional association",
+      as.character(per_data[82:83,][which(per_data[82:83,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Humanitarian or charitable organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Active humanitarian or charitable organization member",
-  selected = ifelse(
-    sum(persona_data[84:85,2]) == 0, "Don't belong to humanitarian or charitable organization",
-    as.character(persona_data[84:85,][which(persona_data[84:85,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[84:85,2]) == 0, "Don't belong to humanitarian or charitable organization",
+    #   as.character(persona_data[84:85,][which(persona_data[84:85,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[84:85,2]) == 0, "Don't belong to humanitarian or charitable organization",
+      as.character(per_data[84:85,][which(per_data[84:85,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Consumer organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Don't belong to consumer organization",
-  selected = ifelse(
-    sum(persona_data[86:87,2]) == 0, "Don't belong to consumer organization",
-    as.character(persona_data[86:87,][which(persona_data[86:87,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[86:87,2]) == 0, "Don't belong to consumer organization",
+    #   as.character(persona_data[86:87,][which(persona_data[86:87,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[86:87,2]) == 0, "Don't belong to consumer organization",
+      as.character(per_data[86:87,][which(per_data[86:87,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Other organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Don't belong to another organization",
-  selected = ifelse(
-    sum(persona_data[88:89,2]) == 0, "Don't belong to another organization",
-    as.character(persona_data[88:89,][which(persona_data[88:89,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[88:89,2]) == 0, "Don't belong to another organization",
+    #   as.character(persona_data[88:89,][which(persona_data[88:89,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[88:89,2]) == 0, "Don't belong to another organization",
+      as.character(per_data[88:89,][which(per_data[88:89,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Gender
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Male",
-  selected = ifelse(
-    sum(persona_data[90:93,2]) == 0, "Male",
-    as.character(persona_data[90:93,][which(persona_data[90:93,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[90:93,2]) == 0, "Male",
+    #   as.character(persona_data[90:93,][which(persona_data[90:93,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[90:93,2]) == 0, "Male",
+      as.character(per_data[90:93,][which(per_data[90:93,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Marital status
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Married",
-  selected = ifelse(
-    sum(persona_data[94:97,2]) == 0, "Married",
-    as.character(persona_data[94:97,][which(persona_data[94:97,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[94:97,2]) == 0, "Married",
+    #   as.character(persona_data[94:97,][which(persona_data[94:97,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[94:97,2]) == 0, "Married",
+      as.character(per_data[94:97,][which(per_data[94:97,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Education
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "2 year degree",
-  selected = ifelse(
-    sum(persona_data[98:103,2]) == 0, "Less than high school",
-    as.character(persona_data[98:103,][which(persona_data[98:103,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[98:103,2]) == 0, "Less than high school",
+    #   as.character(persona_data[98:103,][which(persona_data[98:103,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[98:103,2]) == 0, "Less than high school",
+      as.character(per_data[98:103,][which(per_data[98:103,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Income
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "More than median of $61,372",
-  selected = ifelse(
-    sum(persona_data[104,2]) == 0, "Less than median of $61,372",
-    as.character(persona_data[104,][which(persona_data[104,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[104,2]) == 0, "Less than median of $61,372",
+    #   as.character(persona_data[104,][which(persona_data[104,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[104,2]) == 0, "Less than median of $61,372",
+      as.character(per_data[104,][which(per_data[104,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Race
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "White",
-  selected = deframe(persona_data[105:110,][which(persona_data[105:110,2] == 1), 1]),
-  width = "450px"
-)
+    # selected = deframe(persona_data[105:110,][which(persona_data[105:110,2] == 1), 1]),
+    selected = deframe(per_data[105:110,][which(per_data[105:110,2] == 1), 1]),
+    width = "450px"
+  )
+
+})
 
 # Age
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "Less than median age of 36",
-  selected = ifelse(
-    sum(persona_data[111,2]) == 0, "Less than median age of 36",
-    as.character(persona_data[111,][which(persona_data[111,2] == 1), 1])
-  ),
-  width = "450px"
-)
+    # selected = ifelse(
+    #   sum(persona_data[111,2]) == 0, "Less than median age of 36",
+    #   as.character(persona_data[111,][which(persona_data[111,2] == 1), 1])
+    # ),
+    selected = ifelse(
+      sum(per_data[111,2]) == 0, "Less than median age of 36",
+      as.character(per_data[111,][which(per_data[111,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 ```
@@
     selected = ifelse(
-    sum(persona_data[2:3,3]) == 0, "Rarely",
-    as.character(persona_data[2:3,][which(persona_data[2:3,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[2:3,3]) == 0, "Rarely",
+      as.character(per_data[2:3,][which(per_data[2:3,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Follow international news
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[4:5,3]) == 0, "Never",
-    as.character(persona_data[4:5,][which(persona_data[4:5,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[4:5,3]) == 0, "Never",
+      as.character(per_data[4:5,][which(per_data[4:5,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Mediums to follow news
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = c("TV", "Print", "Social media"),
-  selected = deframe(persona_data[6:12,][which(persona_data[6:12,3] == 1), 1]),
-  width = "450px"
-)
+    selected = deframe(per_data[6:12,][which(per_data[6:12,3] == 1), 1]),
+    width = "450px"
+  )
+
+})
 
 # Follow government and public affairs
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[13,3]) == 0, "Not Often",
-    as.character(persona_data[13,][which(persona_data[13,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[13,3]) == 0, "Not Often",
+      as.character(per_data[13,][which(per_data[13,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Traveled to a developing country
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[14,3]) == 0, "Hasn't traveled to a developing country",
-    as.character(persona_data[14,][which(persona_data[14,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[14,3]) == 0, "Hasn't traveled to a developing country",
+      as.character(per_data[14,][which(per_data[14,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Liberal to Conservative
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[15:20,3]) == 0, "Extremely liberal",
-    as.character(persona_data[15:20,][which(persona_data[15:20,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[15:20,3]) == 0, "Extremely liberal",
+      as.character(per_data[15:20,][which(per_data[15:20,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Trust in political institutions
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[21:26,3]) == 0, "No trust at all in political institutions",
-    as.character(persona_data[21:26,][which(persona_data[21:26,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[21:26,3]) == 0, "No trust at all in political institutions",
+      as.character(per_data[21:26,][which(per_data[21:26,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # People should be more charitable
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[27:32,3]) == 0, "Strongly disagree",
-    as.character(persona_data[27:32,][which(persona_data[27:32,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[27:32,3]) == 0, "Strongly disagree",
+      as.character(per_data[27:32,][which(per_data[27:32,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Religious attendance
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[33:34,3]) == 0, "Not sure",
-    as.character(persona_data[33:34,][which(persona_data[33:34,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[33:34,3]) == 0, "Not sure",
+      as.character(per_data[33:34,][which(per_data[33:34,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Importance of religion
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[35,3]) == 0, "Not important",
-    as.character(persona_data[35,][which(persona_data[35,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[35,3]) == 0, "Not important",
+      as.character(per_data[35,][which(per_data[35,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Religion
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[36:44,3]) == 0, "Catholic",
-    as.character(persona_data[36:44,][which(persona_data[36:44,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[36:44,3]) == 0, "Catholic",
+      as.character(per_data[36:44,][which(per_data[36:44,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Importance of trusting charities
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[45:50,3]) == 0, "Not at all important",
-    as.character(persona_data[45:50,][which(persona_data[45:50,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[45:50,3]) == 0, "Not at all important",
+      as.character(per_data[45:50,][which(per_data[45:50,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Trust in charities
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[51:56,3]) == 0, "No trust at all in charities",
-    as.character(persona_data[51:56,][which(persona_data[51:56,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[51:56,3]) == 0, "No trust at all in charities",
+      as.character(per_data[51:56,][which(per_data[51:56,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Donation frequency
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[57,3]) == 0, "Donate more than once a month, less than once a year",
-    as.character(persona_data[57,][which(persona_data[57,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[57,3]) == 0, "Donate more than once a month, less than once a year",
+      as.character(per_data[57,][which(per_data[57,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Donated last year
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[58:63,3]) == 0, "$1-$49",
-    as.character(persona_data[58:63,][which(persona_data[58:63,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[58:63,3]) == 0, "$1-$49",
+      as.character(per_data[58:63,][which(per_data[58:63,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Volunteered in past 12 months
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[64,3]) == 0, "Haven't volunteered in past 12 months",
-    as.character(persona_data[64,][which(persona_data[64,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[64,3]) == 0, "Haven't volunteered in past 12 months",
+      as.character(per_data[64,][which(per_data[64,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Volunteer frequency
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[65:67,3]) == 0, "Haven't volunteered in past 12 months",
-    as.character(persona_data[65:67,][which(persona_data[65:67,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[65:67,3]) == 0, "Haven't volunteered in past 12 months",
+      as.character(per_data[65:67,][which(per_data[65:67,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # History of activism
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[68,3]) == 0, "Not personally involved",
-    as.character(persona_data[68,][which(persona_data[68,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[68,3]) == 0, "Not personally involved",
+      as.character(per_data[68,][which(per_data[68,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # History of family activism
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[69,3]) == 0, "Family not involved",
-    as.character(persona_data[69,][which(persona_data[69,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[69,3]) == 0, "Family not involved",
+      as.character(per_data[69,][which(per_data[69,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Church or religious organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[70:71,3]) == 0, "Don't belong to church",
-    as.character(persona_data[70:71,][which(persona_data[70:71,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[70:71,3]) == 0, "Don't belong to church",
+      as.character(per_data[70:71,][which(per_data[70:71,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Sport or recreational organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[72:73,3]) == 0, "Don't belong to sports or rec organization",
-    as.character(persona_data[72:73,][which(persona_data[72:73,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[72:73,3]) == 0, "Don't belong to sports or rec organization",
+      as.character(per_data[72:73,][which(per_data[72:73,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Art, music, or educational organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[74:75,3]) == 0, "Don't belong to educational organization",
-    as.character(persona_data[74:75,][which(persona_data[74:75,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[74:75,3]) == 0, "Don't belong to educational organization",
+      as.character(per_data[74:75,][which(per_data[74:75,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Labor union
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[76:77,3]) == 0, "Don't belong to union",
-    as.character(persona_data[76:77,][which(persona_data[76:77,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[76:77,3]) == 0, "Don't belong to union",
+      as.character(per_data[76:77,][which(per_data[76:77,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Political party
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[78:79,3]) == 0, "Don't belong to political party",
-    as.character(persona_data[78:79,][which(persona_data[78:79,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[78:79,3]) == 0, "Don't belong to political party",
+      as.character(per_data[78:79,][which(per_data[78:79,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Environmental organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[80:81,3]) == 0, "Don't belong to environmental organization",
-    as.character(persona_data[80:81,][which(persona_data[80:81,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[80:81,3]) == 0, "Don't belong to environmental organization",
+      as.character(per_data[80:81,][which(per_data[80:81,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Professional association
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[82:83,3]) == 0, "Don't belong to professional association",
-    as.character(persona_data[82:83,][which(persona_data[82:83,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[82:83,3]) == 0, "Don't belong to professional association",
+      as.character(per_data[82:83,][which(per_data[82:83,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Humanitarian or charitable organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[84:85,3]) == 0, "Don't belong to humanitarian or charitable organization",
-    as.character(persona_data[84:85,][which(persona_data[84:85,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[84:85,3]) == 0, "Don't belong to humanitarian or charitable organization",
+      as.character(per_data[84:85,][which(per_data[84:85,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Consumer organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[86:87,3]) == 0, "Don't belong to consumer organization",
-    as.character(persona_data[86:87,][which(persona_data[86:87,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[86:87,3]) == 0, "Don't belong to consumer organization",
+      as.character(per_data[86:87,][which(per_data[86:87,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Other organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[88:89,3]) == 0, "Don't belong to another organization",
-    as.character(persona_data[88:89,][which(persona_data[88:89,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[88:89,3]) == 0, "Don't belong to another organization",
+      as.character(per_data[88:89,][which(per_data[88:89,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Gender
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[90:93,3]) == 0, "Male",
-    as.character(persona_data[90:93,][which(persona_data[90:93,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[90:93,3]) == 0, "Male",
+      as.character(per_data[90:93,][which(per_data[90:93,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Marital status
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[94:97,3]) == 0, "Married",
-    as.character(persona_data[94:97,][which(persona_data[94:97,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[94:97,3]) == 0, "Married",
+      as.character(per_data[94:97,][which(per_data[94:97,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Education
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[98:103,3]) == 0, "Less than high school",
-    as.character(persona_data[98:103,][which(persona_data[98:103,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[98:103,3]) == 0, "Less than high school",
+      as.character(per_data[98:103,][which(per_data[98:103,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Income
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[104,3]) == 0, "Less than median of $61,372",
-    as.character(persona_data[104,][which(persona_data[104,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[104,3]) == 0, "Less than median of $61,372",
+      as.character(per_data[104,][which(per_data[104,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Race
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = "American Indian or Alaskan Native",
-  selected = deframe(persona_data[105:110,][which(persona_data[105:110,3] == 1), 1]),
-  width = "450px"
-)
+    selected = deframe(per_data[105:110,][which(per_data[105:110,3] == 1), 1]),
+    width = "450px"
+  )
+
+})
 
 # Age
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[111,3]) == 0, "Less than median age of 36",
-    as.character(persona_data[111,][which(persona_data[111,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[111,3]) == 0, "Less than median age of 36",
+      as.character(per_data[111,][which(per_data[111,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 ```
@@
     selected = ifelse(
-    sum(persona_data[2:3,4]) == 0, "Rarely",
-    as.character(persona_data[2:3,][which(persona_data[2:3,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[2:3,4]) == 0, "Rarely",
+      as.character(per_data[2:3,][which(per_data[2:3,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Follow international news
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[4:5,4]) == 0, "Never",
-    as.character(persona_data[4:5,][which(persona_data[4:5,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[4:5,4]) == 0, "Never",
+      as.character(per_data[4:5,][which(per_data[4:5,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Mediums to follow news
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = c("TV", "Print", "Social media"),
-  selected = deframe(persona_data[6:12,][which(persona_data[6:12,4] == 1), 1]),
-  width = "450px"
-)
+    selected = deframe(per_data[6:12,][which(per_data[6:12,4] == 1), 1]),
+    width = "450px"
+  )
+
+})
 
 # Follow government and public affairs
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[13,4]) == 0, "Not Often",
-    as.character(persona_data[13,][which(persona_data[13,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[13,4]) == 0, "Not Often",
+      as.character(per_data[13,][which(per_data[13,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Traveled to a developing country
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[14,4]) == 0, "Hasn't traveled to a developing country",
-    as.character(persona_data[14,][which(persona_data[14,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[14,4]) == 0, "Hasn't traveled to a developing country",
+      as.character(per_data[14,][which(per_data[14,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Liberal to Conservative
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[15:20,4]) == 0, "Extremely liberal",
-    as.character(persona_data[15:20,][which(persona_data[15:20,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[15:20,4]) == 0, "Extremely liberal",
+      as.character(per_data[15:20,][which(per_data[15:20,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Trust in political institutions
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[21:26,4]) == 0, "No trust at all in political institutions",
-    as.character(persona_data[21:26,][which(persona_data[21:26,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[21:26,4]) == 0, "No trust at all in political institutions",
+      as.character(per_data[21:26,][which(per_data[21:26,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # People should be more charitable
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[27:32,4]) == 0, "Strongly disagree",
-    as.character(persona_data[27:32,][which(persona_data[27:32,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[27:32,4]) == 0, "Strongly disagree",
+      as.character(per_data[27:32,][which(per_data[27:32,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Religious attendance
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[33:34,4]) == 0, "Not sure",
-    as.character(persona_data[33:34,][which(persona_data[33:34,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[33:34,4]) == 0, "Not sure",
+      as.character(per_data[33:34,][which(per_data[33:34,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Importance of religion
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[35,4]) == 0, "Not important",
-    as.character(persona_data[35,][which(persona_data[35,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[35,4]) == 0, "Not important",
+      as.character(per_data[35,][which(per_data[35,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Religion
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[36:44,4]) == 0, "Catholic",
-    as.character(persona_data[36:44,][which(persona_data[36:44,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[36:44,4]) == 0, "Catholic",
+      as.character(per_data[36:44,][which(per_data[36:44,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Importance of trusting charities
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[45:50,4]) == 0, "Not at all important",
-    as.character(persona_data[45:50,][which(persona_data[45:50,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[45:50,4]) == 0, "Not at all important",
+      as.character(per_data[45:50,][which(per_data[45:50,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Trust in charities
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[51:56,4]) == 0, "No trust at all in charities",
-    as.character(persona_data[51:56,][which(persona_data[51:56,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[51:56,4]) == 0, "No trust at all in charities",
+      as.character(per_data[51:56,][which(per_data[51:56,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Donation frequency
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[57,4]) == 0, "Donate more than once a month, less than once a year",
-    as.character(persona_data[57,][which(persona_data[57,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[57,4]) == 0, "Donate more than once a month, less than once a year",
+      as.character(per_data[57,][which(per_data[57,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Donated last year
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[58:63,4]) == 0, "$1-$49",
-    as.character(persona_data[58:63,][which(persona_data[58:63,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[58:63,4]) == 0, "$1-$49",
+      as.character(per_data[58:63,][which(per_data[58:63,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Volunteered in past 12 months
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[64,4]) == 0, "Haven't volunteered in past 12 months",
-    as.character(persona_data[64,][which(persona_data[64,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[64,4]) == 0, "Haven't volunteered in past 12 months",
+      as.character(per_data[64,][which(per_data[64,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Volunteer frequency
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[65:67,4]) == 0, "Haven't volunteered in past 12 months",
-    as.character(persona_data[65:67,][which(persona_data[65:67,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[65:67,4]) == 0, "Haven't volunteered in past 12 months",
+      as.character(per_data[65:67,][which(per_data[65:67,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # History of activism
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[68,4]) == 0, "Not personally involved",
-    as.character(persona_data[68,][which(persona_data[68,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[68,4]) == 0, "Not personally involved",
+      as.character(per_data[68,][which(per_data[68,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # History of family activism
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[69,4]) == 0, "Family not involved",
-    as.character(persona_data[69,][which(persona_data[69,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[69,4]) == 0, "Family not involved",
+      as.character(per_data[69,][which(per_data[69,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Church or religious organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[70:71,4]) == 0, "Don't belong to church",
-    as.character(persona_data[70:71,][which(persona_data[70:71,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[70:71,4]) == 0, "Don't belong to church",
+      as.character(per_data[70:71,][which(per_data[70:71,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Sport or recreational organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[72:73,4]) == 0, "Don't belong to sports or rec organization",
-    as.character(persona_data[72:73,][which(persona_data[72:73,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[72:73,4]) == 0, "Don't belong to sports or rec organization",
+      as.character(per_data[72:73,][which(per_data[72:73,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Art, music, or educational organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[74:75,4]) == 0, "Don't belong to educational organization",
-    as.character(persona_data[74:75,][which(persona_data[74:75,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[74:75,4]) == 0, "Don't belong to educational organization",
+      as.character(per_data[74:75,][which(per_data[74:75,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Labor union
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[76:77,4]) == 0, "Don't belong to union",
-    as.character(persona_data[76:77,][which(persona_data[76:77,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[76:77,4]) == 0, "Don't belong to union",
+      as.character(per_data[76:77,][which(per_data[76:77,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Political party
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[78:79,4]) == 0, "Don't belong to political party",
-    as.character(persona_data[78:79,][which(persona_data[78:79,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[78:79,4]) == 0, "Don't belong to political party",
+      as.character(per_data[78:79,][which(per_data[78:79,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Environmental organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[80:81,4]) == 0, "Don't belong to environmental organization",
-    as.character(persona_data[80:81,][which(persona_data[80:81,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[80:81,4]) == 0, "Don't belong to environmental organization",
+      as.character(per_data[80:81,][which(per_data[80:81,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Professional association
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[82:83,4]) == 0, "Don't belong to professional association",
-    as.character(persona_data[82:83,][which(persona_data[82:83,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[82:83,4]) == 0, "Don't belong to professional association",
+      as.character(per_data[82:83,][which(per_data[82:83,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Humanitarian or charitable organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[84:85,4]) == 0, "Don't belong to humanitarian or charitable organization",
-    as.character(persona_data[84:85,][which(persona_data[84:85,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[84:85,4]) == 0, "Don't belong to humanitarian or charitable organization",
+      as.character(per_data[84:85,][which(per_data[84:85,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Consumer organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[86:87,4]) == 0, "Don't belong to consumer organization",
-    as.character(persona_data[86:87,][which(persona_data[86:87,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[86:87,4]) == 0, "Don't belong to consumer organization",
+      as.character(per_data[86:87,][which(per_data[86:87,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Other organization
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[88:89,4]) == 0, "Don't belong to another organization",
-    as.character(persona_data[88:89,][which(persona_data[88:89,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[88:89,4]) == 0, "Don't belong to another organization",
+      as.character(per_data[88:89,][which(per_data[88:89,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Gender
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[90:93,4]) == 0, "Male",
-    as.character(persona_data[90:93,][which(persona_data[90:93,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[90:93,4]) == 0, "Male",
+      as.character(per_data[90:93,][which(per_data[90:93,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Marital status
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[94:97,4]) == 0, "Married",
-    as.character(persona_data[94:97,][which(persona_data[94:97,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[94:97,4]) == 0, "Married",
+      as.character(per_data[94:97,][which(per_data[94:97,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Education
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[98:103,4]) == 0, "Less than high school",
-    as.character(persona_data[98:103,][which(persona_data[98:103,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[98:103,4]) == 0, "Less than high school",
+      as.character(per_data[98:103,][which(per_data[98:103,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Income
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[104,4]) == 0, "Less than median of $61,372",
-    as.character(persona_data[104,][which(persona_data[104,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[104,4]) == 0, "Less than median of $61,372",
+      as.character(per_data[104,][which(per_data[104,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 
 # Race
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     # selected = c("Black or African American", "American Indian or Alaskan Native"),
-  selected = deframe(persona_data[105:110,][which(persona_data[105:110,4] == 1), 1]),
-  width = "450px"
-)
+    selected = deframe(per_data[105:110,][which(per_data[105:110,4] == 1), 1]),
+    width = "450px"
+  )
+
+})
 
 # Age
+renderUI({
+  per_data = persona_data()
+
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[111,4]) == 0, "Less than median age of 36",
-    as.character(persona_data[111,][which(persona_data[111,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[111,4]) == 0, "Less than median age of 36",
+      as.character(per_data[111,][which(per_data[111,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+
+})
 ```

### 2020-10-28 analysis/05_market_simulator.Rmd
figuring out a way to automatically update data with actionButton
Cleaned up code for all the new rendered objects for uploadable configurations

--- 2020-10-21 analysis/05_market_simulator.Rmd
@@
 
-# Initial organization configuration
-# organization_data <- read_csv(
-#   here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
-# )
-
-organization_values <- reactiveValues()
-
+# Organization configuration
 organization_data <- reactive({
   if (is.null(input$org_update$datapath)) {
-    organization_data <- read_csv(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
-    # organization_values$file_name = "organization_config01.csv"
-    # organization_values$file_type = "csv"
-    # organization_values$file_size = file.size(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
-    # organization_values$file_path = here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
+    organization_data <- read_csv(
+      here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
+    )
   } else {
     organization_data <- read_csv(input$org_update$datapath)
-    # organization_values$file_name = input$org_update$name
-    # organization_values$file_size = input$org_update$size
-    # organization_values$file_type = input$org_update$type
-    # organization_values$file_path = input$org_update$datapath
   }
@@
 
-# Initial persona configuration
+# Persona configuration
+persona_data <- reactive({
+  if (is.null(input$per_update$datapath)) {
     persona_data <- read_csv(
@@
     )
-
+  } else {
+    persona_data <- read_csv(input$per_update$datapath)
+  }
+})
 ```
@@
 ```{r organization-reactive-table}
-
 # Assign level labels
@@
 })
-
-# per_update <- reactiveValues(data = NULL)
-# per_update$data <- per_table
-
 ```
@@
 )
+
 # Organization
@@
   org_data = organization_data()
-
   selectInput(
@@
     # selected = "Red Cross",
-    # selected = as.character(organization_data[1:4,][which(organization_data[1:4,2] == 1), 1]),
     selected = as.character(org_data[1:4,][which(org_data[1:4,2] == 1), 1]),
@@
   )
-
 })
@@
     selected = ifelse(
-      # sum(organization_data$data[5:7,2]) == 0, "Emergency response",
-      # as.character(organization_data$data[5:7,][which(organization_data$data[5:7,2] == 1), 1])
       sum(org_data[5:7,2]) == 0, "Emergency response",
@@
     label = "Financial Transparency:",
-    choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
+    choices = c(
+      "Doesn’t engage in financial transparency", 
+      "Engages in financial transparency"
+    ),
     # selected = "Engages in financial transparency",
     selected = ifelse(
-      # sum(organization_data$data[8,2]) == 0, "Doesn’t engage in financial transparency",
-      # as.character(organization_data$data[8,][which(organization_data$data[8,2] == 1), 1])
       sum(org_data[8,2]) == 0, "Doesn’t engage in financial transparency",
@@
     label = "Financial Accountability:",
-    choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
+    choices = c(
+      "Doesn’t engage in financial accountability", 
+      "Engages in financial accountability"
+    ),
     # selected = "Engages in financial accountability",
     selected = ifelse(
-      # sum(organization_data$data[9,2]) == 0, "Doesn’t engage in financial accountability",
-      # as.character(organization_data$data[9,][which(organization_data$data[9,2] == 1), 1])
       sum(org_data[9,2]) == 0, "Doesn’t engage in financial accountability",
@@
     label = "Funding Source:",
-    choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
+    choices = c(
+      "Many small private donations", 
+      "Handful of wealthy private donors", 
+      "Government grants"
+    ),
     # selected = "Many small private donations",
     selected = ifelse(
-      # sum(organization_data$data[10:11,2]) == 0, "Many small private donations",
-      # as.character(organization_data$data[10:11,][which(organization_data$data[10:11,2] == 1), 1])
       sum(org_data[10:11,2]) == 0, "Many small private donations",
@@
     label = "Relationship With Host Government",
-    choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
+    choices = c(
+      "Friendly relationship with government", 
+      "Criticized by government",  
+      "Under government crackdown"
+    ),
     # selected = "Friendly relationship with government",
     selected = ifelse(
-      # sum(organization_data$data[12:13,2]) == 0, "Friendly relationship with government",
-      # as.character(organization_data$data[12:13,][which(organization_data$data[12:13,2] == 1), 1])
       sum(org_data[12:13,2]) == 0, "Friendly relationship with government",
@@
     label = "Financial Transparency:",
-    choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
+    choices = c(
+      "Doesn’t engage in financial transparency", 
+      "Engages in financial transparency"
+    ),
     # selected = "Engages in financial transparency",
@@
     label = "Financial Accountability:",
-    choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
+    choices = c(
+      "Doesn’t engage in financial accountability", 
+      "Engages in financial accountability"
+    ),
     # selected = "Engages in financial accountability",
@@
     label = "Funding Source:",
-    choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
+    choices = c(
+      "Many small private donations", 
+      "Handful of wealthy private donors", 
+      "Government grants"
+    ),
     # selected = "Many small private donations",
@@
     label = "Relationship With Host Government",
-    choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
+    choices = c(
+      "Friendly relationship with government", 
+      "Criticized by government",  
+      "Under government crackdown"
+    ),
     # selected = "Friendly relationship with government",
@@
   )
-
-})
-
+})
 ```
@@
 # Follow national news
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[2:3,2]) == 0, "Rarely",
-    as.character(persona_data[2:3,][which(persona_data[2:3,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[2:3,2]) == 0, "Rarely",
+      as.character(per_data[2:3,][which(per_data[2:3,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Follow international news
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[4:5,2]) == 0, "Never",
-    as.character(persona_data[4:5,][which(persona_data[4:5,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[4:5,2]) == 0, "Never",
+      as.character(per_data[4:5,][which(per_data[4:5,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Mediums to follow news
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     # selected = c("TV", "Print", "Social media"),
-  selected = deframe(persona_data[6:12,][which(persona_data[6:12,2] == 1), 1]),
-  width = "450px"
-)
+    selected = deframe(per_data[6:12,][which(per_data[6:12,2] == 1), 1]),
+    width = "450px"
+  )
+})
 
 # Follow government and public affairs
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[13,2]) == 0, "Not Often",
-    as.character(persona_data[13,][which(persona_data[13,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[13,2]) == 0, "Not Often",
+      as.character(per_data[13,][which(per_data[13,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Traveled to a developing country
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[14,2]) == 0, "Hasn't traveled to a developing country",
-    as.character(persona_data[14,][which(persona_data[14,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[14,2]) == 0, "Hasn't traveled to a developing country",
+      as.character(per_data[14,][which(per_data[14,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Liberal to Conservative
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[15:20,2]) == 0, "Extremely liberal",
-    as.character(persona_data[15:20,][which(persona_data[15:20,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[15:20,2]) == 0, "Extremely liberal",
+      as.character(per_data[15:20,][which(per_data[15:20,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Trust in political institutions
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[21:26,2]) == 0, "No trust at all in political institutions",
-    as.character(persona_data[21:26,][which(persona_data[21:26,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[21:26,2]) == 0, "No trust at all in political institutions",
+      as.character(per_data[21:26,][which(per_data[21:26,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # People should be more charitable
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[27:32,2]) == 0, "Strongly disagree",
-    as.character(persona_data[27:32,][which(persona_data[27:32,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[27:32,2]) == 0, "Strongly disagree",
+      as.character(per_data[27:32,][which(per_data[27:32,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Religious attendance
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[33:34,2]) == 0, "Not sure",
-    as.character(persona_data[33:34,][which(persona_data[33:34,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[33:34,2]) == 0, "Not sure",
+      as.character(per_data[33:34,][which(per_data[33:34,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Importance of religion
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[35,2]) == 0, "Not important",
-    as.character(persona_data[35,][which(persona_data[35,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[35,2]) == 0, "Not important",
+      as.character(per_data[35,][which(per_data[35,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Religion
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
      selected = ifelse(
-    sum(persona_data[36:44,2]) == 0, "Catholic",
-    as.character(persona_data[36:44,][which(persona_data[36:44,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[36:44,2]) == 0, "Catholic",
+      as.character(per_data[36:44,][which(per_data[36:44,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Importance of trusting charities
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[45:50,2]) == 0, "Not at all important",
-    as.character(persona_data[45:50,][which(persona_data[45:50,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[45:50,2]) == 0, "Not at all important",
+      as.character(per_data[45:50,][which(per_data[45:50,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Trust in charities
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
      selected = ifelse(
-    sum(persona_data[51:56,2]) == 0, "No trust at all in charities",
-    as.character(persona_data[51:56,][which(persona_data[51:56,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[51:56,2]) == 0, "No trust at all in charities",
+      as.character(per_data[51:56,][which(per_data[51:56,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Donation frequency
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[57,2]) == 0, "Donate more than once a month, less than once a year",
-    as.character(persona_data[57,][which(persona_data[57,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[57,2]) == 0, "Donate more than once a month, less than once a year",
+      as.character(per_data[57,][which(per_data[57,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Donated last year
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[58:63,2]) == 0, "$1-$49",
-    as.character(persona_data[58:63,][which(persona_data[58:63,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[58:63,2]) == 0, "$1-$49",
+      as.character(per_data[58:63,][which(per_data[58:63,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Volunteered in past 12 months
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[64,2]) == 0, "Haven't volunteered in past 12 months",
-    as.character(persona_data[64,][which(persona_data[64,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[64,2]) == 0, "Haven't volunteered in past 12 months",
+      as.character(per_data[64,][which(per_data[64,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Volunteer frequency
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[65:67,2]) == 0, "Haven't volunteered in past 12 months",
-    as.character(persona_data[65:67,][which(persona_data[65:67,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[65:67,2]) == 0, "Haven't volunteered in past 12 months",
+      as.character(per_data[65:67,][which(per_data[65:67,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # History of activism
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[68,2]) == 0, "Not personally involved",
-    as.character(persona_data[68,][which(persona_data[68,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[68,2]) == 0, "Not personally involved",
+      as.character(per_data[68,][which(per_data[68,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # History of family activism
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[69,2]) == 0, "Family not involved",
-    as.character(persona_data[69,][which(persona_data[69,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[69,2]) == 0, "Family not involved",
+      as.character(per_data[69,][which(per_data[69,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Church or religious organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[70:71,2]) == 0, "Don't belong to church",
-    as.character(persona_data[70:71,][which(persona_data[70:71,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[70:71,2]) == 0, "Don't belong to church",
+      as.character(per_data[70:71,][which(per_data[70:71,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Sport or recreational organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[72:73,2]) == 0, "Don't belong to sports or rec organization",
-    as.character(persona_data[72:73,][which(persona_data[72:73,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[72:73,2]) == 0, "Don't belong to sports or rec organization",
+      as.character(per_data[72:73,][which(per_data[72:73,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Art, music, or educational organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[74:75,2]) == 0, "Don't belong to educational organization",
-    as.character(persona_data[74:75,][which(persona_data[74:75,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[74:75,2]) == 0, "Don't belong to educational organization",
+      as.character(per_data[74:75,][which(per_data[74:75,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Labor union
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[76:77,2]) == 0, "Don't belong to union",
-    as.character(persona_data[76:77,][which(persona_data[76:77,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[76:77,2]) == 0, "Don't belong to union",
+      as.character(per_data[76:77,][which(per_data[76:77,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Political party
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[78:79,2]) == 0, "Don't belong to political party",
-    as.character(persona_data[78:79,][which(persona_data[78:79,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[78:79,2]) == 0, "Don't belong to political party",
+      as.character(per_data[78:79,][which(per_data[78:79,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Environmental organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[80:81,2]) == 0, "Don't belong to environmental organization",
-    as.character(persona_data[80:81,][which(persona_data[80:81,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[80:81,2]) == 0, "Don't belong to environmental organization",
+      as.character(per_data[80:81,][which(per_data[80:81,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Professional association
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[82:83,2]) == 0, "Don't belong to professional association",
-    as.character(persona_data[82:83,][which(persona_data[82:83,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[82:83,2]) == 0, "Don't belong to professional association",
+      as.character(per_data[82:83,][which(per_data[82:83,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Humanitarian or charitable organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[84:85,2]) == 0, "Don't belong to humanitarian or charitable organization",
-    as.character(persona_data[84:85,][which(persona_data[84:85,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[84:85,2]) == 0, "Don't belong to humanitarian or charitable organization",
+      as.character(per_data[84:85,][which(per_data[84:85,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Consumer organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[86:87,2]) == 0, "Don't belong to consumer organization",
-    as.character(persona_data[86:87,][which(persona_data[86:87,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[86:87,2]) == 0, "Don't belong to consumer organization",
+      as.character(per_data[86:87,][which(per_data[86:87,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Other organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[88:89,2]) == 0, "Don't belong to another organization",
-    as.character(persona_data[88:89,][which(persona_data[88:89,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[88:89,2]) == 0, "Don't belong to another organization",
+      as.character(per_data[88:89,][which(per_data[88:89,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Gender
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[90:93,2]) == 0, "Male",
-    as.character(persona_data[90:93,][which(persona_data[90:93,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[90:93,2]) == 0, "Male",
+      as.character(per_data[90:93,][which(per_data[90:93,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Marital status
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[94:97,2]) == 0, "Married",
-    as.character(persona_data[94:97,][which(persona_data[94:97,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[94:97,2]) == 0, "Married",
+      as.character(per_data[94:97,][which(per_data[94:97,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Education
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[98:103,2]) == 0, "Less than high school",
-    as.character(persona_data[98:103,][which(persona_data[98:103,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[98:103,2]) == 0, "Less than high school",
+      as.character(per_data[98:103,][which(per_data[98:103,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Income
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[104,2]) == 0, "Less than median of $61,372",
-    as.character(persona_data[104,][which(persona_data[104,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[104,2]) == 0, "Less than median of $61,372",
+      as.character(per_data[104,][which(per_data[104,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Race
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     # selected = "White",
-  selected = deframe(persona_data[105:110,][which(persona_data[105:110,2] == 1), 1]),
-  width = "450px"
-)
+    selected = deframe(per_data[105:110,][which(per_data[105:110,2] == 1), 1]),
+    width = "450px"
+  )
+})
 
 # Age
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[111,2]) == 0, "Less than median age of 36",
-    as.character(persona_data[111,][which(persona_data[111,2] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[111,2]) == 0, "Less than median age of 36",
+      as.character(per_data[111,][which(per_data[111,2] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 ```
@@
     selected = ifelse(
-    sum(persona_data[2:3,3]) == 0, "Rarely",
-    as.character(persona_data[2:3,][which(persona_data[2:3,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[2:3,3]) == 0, "Rarely",
+      as.character(per_data[2:3,][which(per_data[2:3,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Follow international news
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[4:5,3]) == 0, "Never",
-    as.character(persona_data[4:5,][which(persona_data[4:5,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[4:5,3]) == 0, "Never",
+      as.character(per_data[4:5,][which(per_data[4:5,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Mediums to follow news
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     # selected = c("TV", "Print", "Social media"),
-  selected = deframe(persona_data[6:12,][which(persona_data[6:12,3] == 1), 1]),
-  width = "450px"
-)
+    selected = deframe(per_data[6:12,][which(per_data[6:12,3] == 1), 1]),
+    width = "450px"
+  )
+})
 
 # Follow government and public affairs
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[13,3]) == 0, "Not Often",
-    as.character(persona_data[13,][which(persona_data[13,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[13,3]) == 0, "Not Often",
+      as.character(per_data[13,][which(per_data[13,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Traveled to a developing country
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[14,3]) == 0, "Hasn't traveled to a developing country",
-    as.character(persona_data[14,][which(persona_data[14,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[14,3]) == 0, "Hasn't traveled to a developing country",
+      as.character(per_data[14,][which(per_data[14,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Liberal to Conservative
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[15:20,3]) == 0, "Extremely liberal",
-    as.character(persona_data[15:20,][which(persona_data[15:20,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[15:20,3]) == 0, "Extremely liberal",
+      as.character(per_data[15:20,][which(per_data[15:20,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Trust in political institutions
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[21:26,3]) == 0, "No trust at all in political institutions",
-    as.character(persona_data[21:26,][which(persona_data[21:26,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[21:26,3]) == 0, "No trust at all in political institutions",
+      as.character(per_data[21:26,][which(per_data[21:26,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # People should be more charitable
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[27:32,3]) == 0, "Strongly disagree",
-    as.character(persona_data[27:32,][which(persona_data[27:32,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[27:32,3]) == 0, "Strongly disagree",
+      as.character(per_data[27:32,][which(per_data[27:32,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Religious attendance
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[33:34,3]) == 0, "Not sure",
-    as.character(persona_data[33:34,][which(persona_data[33:34,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[33:34,3]) == 0, "Not sure",
+      as.character(per_data[33:34,][which(per_data[33:34,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Importance of religion
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[35,3]) == 0, "Not important",
-    as.character(persona_data[35,][which(persona_data[35,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[35,3]) == 0, "Not important",
+      as.character(per_data[35,][which(per_data[35,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Religion
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[36:44,3]) == 0, "Catholic",
-    as.character(persona_data[36:44,][which(persona_data[36:44,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[36:44,3]) == 0, "Catholic",
+      as.character(per_data[36:44,][which(per_data[36:44,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Importance of trusting charities
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[45:50,3]) == 0, "Not at all important",
-    as.character(persona_data[45:50,][which(persona_data[45:50,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[45:50,3]) == 0, "Not at all important",
+      as.character(per_data[45:50,][which(per_data[45:50,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Trust in charities
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[51:56,3]) == 0, "No trust at all in charities",
-    as.character(persona_data[51:56,][which(persona_data[51:56,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[51:56,3]) == 0, "No trust at all in charities",
+      as.character(per_data[51:56,][which(per_data[51:56,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Donation frequency
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[57,3]) == 0, "Donate more than once a month, less than once a year",
-    as.character(persona_data[57,][which(persona_data[57,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[57,3]) == 0, "Donate more than once a month, less than once a year",
+      as.character(per_data[57,][which(per_data[57,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Donated last year
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[58:63,3]) == 0, "$1-$49",
-    as.character(persona_data[58:63,][which(persona_data[58:63,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[58:63,3]) == 0, "$1-$49",
+      as.character(per_data[58:63,][which(per_data[58:63,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Volunteered in past 12 months
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[64,3]) == 0, "Haven't volunteered in past 12 months",
-    as.character(persona_data[64,][which(persona_data[64,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[64,3]) == 0, "Haven't volunteered in past 12 months",
+      as.character(per_data[64,][which(per_data[64,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Volunteer frequency
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[65:67,3]) == 0, "Haven't volunteered in past 12 months",
-    as.character(persona_data[65:67,][which(persona_data[65:67,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[65:67,3]) == 0, "Haven't volunteered in past 12 months",
+      as.character(per_data[65:67,][which(per_data[65:67,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # History of activism
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[68,3]) == 0, "Not personally involved",
-    as.character(persona_data[68,][which(persona_data[68,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[68,3]) == 0, "Not personally involved",
+      as.character(per_data[68,][which(per_data[68,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # History of family activism
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[69,3]) == 0, "Family not involved",
-    as.character(persona_data[69,][which(persona_data[69,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[69,3]) == 0, "Family not involved",
+      as.character(per_data[69,][which(per_data[69,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Church or religious organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[70:71,3]) == 0, "Don't belong to church",
-    as.character(persona_data[70:71,][which(persona_data[70:71,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[70:71,3]) == 0, "Don't belong to church",
+      as.character(per_data[70:71,][which(per_data[70:71,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Sport or recreational organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[72:73,3]) == 0, "Don't belong to sports or rec organization",
-    as.character(persona_data[72:73,][which(persona_data[72:73,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[72:73,3]) == 0, "Don't belong to sports or rec organization",
+      as.character(per_data[72:73,][which(per_data[72:73,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Art, music, or educational organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[74:75,3]) == 0, "Don't belong to educational organization",
-    as.character(persona_data[74:75,][which(persona_data[74:75,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[74:75,3]) == 0, "Don't belong to educational organization",
+      as.character(per_data[74:75,][which(per_data[74:75,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Labor union
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[76:77,3]) == 0, "Don't belong to union",
-    as.character(persona_data[76:77,][which(persona_data[76:77,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[76:77,3]) == 0, "Don't belong to union",
+      as.character(per_data[76:77,][which(per_data[76:77,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Political party
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[78:79,3]) == 0, "Don't belong to political party",
-    as.character(persona_data[78:79,][which(persona_data[78:79,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[78:79,3]) == 0, "Don't belong to political party",
+      as.character(per_data[78:79,][which(per_data[78:79,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Environmental organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[80:81,3]) == 0, "Don't belong to environmental organization",
-    as.character(persona_data[80:81,][which(persona_data[80:81,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[80:81,3]) == 0, "Don't belong to environmental organization",
+      as.character(per_data[80:81,][which(per_data[80:81,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Professional association
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[82:83,3]) == 0, "Don't belong to professional association",
-    as.character(persona_data[82:83,][which(persona_data[82:83,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[82:83,3]) == 0, "Don't belong to professional association",
+      as.character(per_data[82:83,][which(per_data[82:83,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Humanitarian or charitable organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[84:85,3]) == 0, "Don't belong to humanitarian or charitable organization",
-    as.character(persona_data[84:85,][which(persona_data[84:85,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[84:85,3]) == 0, "Don't belong to humanitarian or charitable organization",
+      as.character(per_data[84:85,][which(per_data[84:85,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Consumer organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[86:87,3]) == 0, "Don't belong to consumer organization",
-    as.character(persona_data[86:87,][which(persona_data[86:87,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[86:87,3]) == 0, "Don't belong to consumer organization",
+      as.character(per_data[86:87,][which(per_data[86:87,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Other organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[88:89,3]) == 0, "Don't belong to another organization",
-    as.character(persona_data[88:89,][which(persona_data[88:89,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[88:89,3]) == 0, "Don't belong to another organization",
+      as.character(per_data[88:89,][which(per_data[88:89,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Gender
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[90:93,3]) == 0, "Male",
-    as.character(persona_data[90:93,][which(persona_data[90:93,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[90:93,3]) == 0, "Male",
+      as.character(per_data[90:93,][which(per_data[90:93,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Marital status
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[94:97,3]) == 0, "Married",
-    as.character(persona_data[94:97,][which(persona_data[94:97,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[94:97,3]) == 0, "Married",
+      as.character(per_data[94:97,][which(per_data[94:97,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Education
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[98:103,3]) == 0, "Less than high school",
-    as.character(persona_data[98:103,][which(persona_data[98:103,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[98:103,3]) == 0, "Less than high school",
+      as.character(per_data[98:103,][which(per_data[98:103,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Income
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[104,3]) == 0, "Less than median of $61,372",
-    as.character(persona_data[104,][which(persona_data[104,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[104,3]) == 0, "Less than median of $61,372",
+      as.character(per_data[104,][which(per_data[104,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Race
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     # selected = "American Indian or Alaskan Native",
-  selected = deframe(persona_data[105:110,][which(persona_data[105:110,3] == 1), 1]),
-  width = "450px"
-)
+    selected = deframe(per_data[105:110,][which(per_data[105:110,3] == 1), 1]),
+    width = "450px"
+  )
+})
 
 # Age
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[111,3]) == 0, "Less than median age of 36",
-    as.character(persona_data[111,][which(persona_data[111,3] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[111,3]) == 0, "Less than median age of 36",
+      as.character(per_data[111,][which(per_data[111,3] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 ```
@@
     selected = ifelse(
-    sum(persona_data[2:3,4]) == 0, "Rarely",
-    as.character(persona_data[2:3,][which(persona_data[2:3,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[2:3,4]) == 0, "Rarely",
+      as.character(per_data[2:3,][which(per_data[2:3,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Follow international news
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[4:5,4]) == 0, "Never",
-    as.character(persona_data[4:5,][which(persona_data[4:5,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[4:5,4]) == 0, "Never",
+      as.character(per_data[4:5,][which(per_data[4:5,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Mediums to follow news
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     # selected = c("TV", "Print", "Social media"),
-  selected = deframe(persona_data[6:12,][which(persona_data[6:12,4] == 1), 1]),
-  width = "450px"
-)
+    selected = deframe(per_data[6:12,][which(per_data[6:12,4] == 1), 1]),
+    width = "450px"
+  )
+})
 
 # Follow government and public affairs
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[13,4]) == 0, "Not Often",
-    as.character(persona_data[13,][which(persona_data[13,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[13,4]) == 0, "Not Often",
+      as.character(per_data[13,][which(per_data[13,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Traveled to a developing country
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[14,4]) == 0, "Hasn't traveled to a developing country",
-    as.character(persona_data[14,][which(persona_data[14,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[14,4]) == 0, "Hasn't traveled to a developing country",
+      as.character(per_data[14,][which(per_data[14,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Liberal to Conservative
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[15:20,4]) == 0, "Extremely liberal",
-    as.character(persona_data[15:20,][which(persona_data[15:20,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[15:20,4]) == 0, "Extremely liberal",
+      as.character(per_data[15:20,][which(per_data[15:20,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Trust in political institutions
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[21:26,4]) == 0, "No trust at all in political institutions",
-    as.character(persona_data[21:26,][which(persona_data[21:26,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[21:26,4]) == 0, "No trust at all in political institutions",
+      as.character(per_data[21:26,][which(per_data[21:26,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # People should be more charitable
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[27:32,4]) == 0, "Strongly disagree",
-    as.character(persona_data[27:32,][which(persona_data[27:32,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[27:32,4]) == 0, "Strongly disagree",
+      as.character(per_data[27:32,][which(per_data[27:32,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Religious attendance
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[33:34,4]) == 0, "Not sure",
-    as.character(persona_data[33:34,][which(persona_data[33:34,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[33:34,4]) == 0, "Not sure",
+      as.character(per_data[33:34,][which(per_data[33:34,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Importance of religion
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[35,4]) == 0, "Not important",
-    as.character(persona_data[35,][which(persona_data[35,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[35,4]) == 0, "Not important",
+      as.character(per_data[35,][which(per_data[35,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Religion
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[36:44,4]) == 0, "Catholic",
-    as.character(persona_data[36:44,][which(persona_data[36:44,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[36:44,4]) == 0, "Catholic",
+      as.character(per_data[36:44,][which(per_data[36:44,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Importance of trusting charities
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[45:50,4]) == 0, "Not at all important",
-    as.character(persona_data[45:50,][which(persona_data[45:50,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[45:50,4]) == 0, "Not at all important",
+      as.character(per_data[45:50,][which(per_data[45:50,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Trust in charities
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[51:56,4]) == 0, "No trust at all in charities",
-    as.character(persona_data[51:56,][which(persona_data[51:56,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[51:56,4]) == 0, "No trust at all in charities",
+      as.character(per_data[51:56,][which(per_data[51:56,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Donation frequency
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[57,4]) == 0, "Donate more than once a month, less than once a year",
-    as.character(persona_data[57,][which(persona_data[57,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[57,4]) == 0, "Donate more than once a month, less than once a year",
+      as.character(per_data[57,][which(per_data[57,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Donated last year
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[58:63,4]) == 0, "$1-$49",
-    as.character(persona_data[58:63,][which(persona_data[58:63,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[58:63,4]) == 0, "$1-$49",
+      as.character(per_data[58:63,][which(per_data[58:63,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Volunteered in past 12 months
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[64,4]) == 0, "Haven't volunteered in past 12 months",
-    as.character(persona_data[64,][which(persona_data[64,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[64,4]) == 0, "Haven't volunteered in past 12 months",
+      as.character(per_data[64,][which(per_data[64,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Volunteer frequency
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[65:67,4]) == 0, "Haven't volunteered in past 12 months",
-    as.character(persona_data[65:67,][which(persona_data[65:67,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[65:67,4]) == 0, "Haven't volunteered in past 12 months",
+      as.character(per_data[65:67,][which(per_data[65:67,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # History of activism
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[68,4]) == 0, "Not personally involved",
-    as.character(persona_data[68,][which(persona_data[68,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[68,4]) == 0, "Not personally involved",
+      as.character(per_data[68,][which(per_data[68,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # History of family activism
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[69,4]) == 0, "Family not involved",
-    as.character(persona_data[69,][which(persona_data[69,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[69,4]) == 0, "Family not involved",
+      as.character(per_data[69,][which(per_data[69,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Church or religious organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[70:71,4]) == 0, "Don't belong to church",
-    as.character(persona_data[70:71,][which(persona_data[70:71,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[70:71,4]) == 0, "Don't belong to church",
+      as.character(per_data[70:71,][which(per_data[70:71,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Sport or recreational organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[72:73,4]) == 0, "Don't belong to sports or rec organization",
-    as.character(persona_data[72:73,][which(persona_data[72:73,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[72:73,4]) == 0, "Don't belong to sports or rec organization",
+      as.character(per_data[72:73,][which(per_data[72:73,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Art, music, or educational organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[74:75,4]) == 0, "Don't belong to educational organization",
-    as.character(persona_data[74:75,][which(persona_data[74:75,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[74:75,4]) == 0, "Don't belong to educational organization",
+      as.character(per_data[74:75,][which(per_data[74:75,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Labor union
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[76:77,4]) == 0, "Don't belong to union",
-    as.character(persona_data[76:77,][which(persona_data[76:77,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[76:77,4]) == 0, "Don't belong to union",
+      as.character(per_data[76:77,][which(per_data[76:77,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Political party
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[78:79,4]) == 0, "Don't belong to political party",
-    as.character(persona_data[78:79,][which(persona_data[78:79,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[78:79,4]) == 0, "Don't belong to political party",
+      as.character(per_data[78:79,][which(per_data[78:79,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Environmental organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[80:81,4]) == 0, "Don't belong to environmental organization",
-    as.character(persona_data[80:81,][which(persona_data[80:81,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[80:81,4]) == 0, "Don't belong to environmental organization",
+      as.character(per_data[80:81,][which(per_data[80:81,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Professional association
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[82:83,4]) == 0, "Don't belong to professional association",
-    as.character(persona_data[82:83,][which(persona_data[82:83,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[82:83,4]) == 0, "Don't belong to professional association",
+      as.character(per_data[82:83,][which(per_data[82:83,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Humanitarian or charitable organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[84:85,4]) == 0, "Don't belong to humanitarian or charitable organization",
-    as.character(persona_data[84:85,][which(persona_data[84:85,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[84:85,4]) == 0, "Don't belong to humanitarian or charitable organization",
+      as.character(per_data[84:85,][which(per_data[84:85,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Consumer organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[86:87,4]) == 0, "Don't belong to consumer organization",
-    as.character(persona_data[86:87,][which(persona_data[86:87,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[86:87,4]) == 0, "Don't belong to consumer organization",
+      as.character(per_data[86:87,][which(per_data[86:87,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Other organization
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[88:89,4]) == 0, "Don't belong to another organization",
-    as.character(persona_data[88:89,][which(persona_data[88:89,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[88:89,4]) == 0, "Don't belong to another organization",
+      as.character(per_data[88:89,][which(per_data[88:89,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Gender
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[90:93,4]) == 0, "Male",
-    as.character(persona_data[90:93,][which(persona_data[90:93,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[90:93,4]) == 0, "Male",
+      as.character(per_data[90:93,][which(per_data[90:93,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Marital status
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[94:97,4]) == 0, "Married",
-    as.character(persona_data[94:97,][which(persona_data[94:97,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[94:97,4]) == 0, "Married",
+      as.character(per_data[94:97,][which(per_data[94:97,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Education
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[98:103,4]) == 0, "Less than high school",
-    as.character(persona_data[98:103,][which(persona_data[98:103,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[98:103,4]) == 0, "Less than high school",
+      as.character(per_data[98:103,][which(per_data[98:103,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Income
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[104,4]) == 0, "Less than median of $61,372",
-    as.character(persona_data[104,][which(persona_data[104,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[104,4]) == 0, "Less than median of $61,372",
+      as.character(per_data[104,][which(per_data[104,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 
 # Race
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     # selected = c("Black or African American", "American Indian or Alaskan Native"),
-  selected = deframe(persona_data[105:110,][which(persona_data[105:110,4] == 1), 1]),
-  width = "450px"
-)
+    selected = deframe(per_data[105:110,][which(per_data[105:110,4] == 1), 1]),
+    width = "450px"
+  )
+})
 
 # Age
+renderUI({
+  per_data = persona_data()
   selectInput(
@@
     selected = ifelse(
-    sum(persona_data[111,4]) == 0, "Less than median age of 36",
-    as.character(persona_data[111,][which(persona_data[111,4] == 1), 1])
-  ),
-  width = "450px"
-)
+      sum(per_data[111,4]) == 0, "Less than median age of 36",
+      as.character(per_data[111,][which(per_data[111,4] == 1), 1])
+    ),
+    width = "450px"
+  )
+})
 ```
@@
   org_choice = org_reactive()
-
   org_choice
@@
   per_choice = per_reactive()
-
   per_choice
@@
 )
-
 ```
@@
 
-actionButton(
-  inputId = "org_apply",
-  label = "Apply New Data",
-  icon = icon("play")
-)
-
-observeEvent(eventExpr = input$org_apply,
-  handlerExpr = {
-      req(input$org_update)
-      file <- read_csv(input$org_update$datapath)
-      org_update$data <- file
-  }, ignoreNULL = FALSE)
+# actionButton(
+#   "org_button",
+#   label = "Update Organization Data"
+# )
 
@@
 fileInput(
-  "file_per",
+  "per_update",
   "Import Persona Data",
@@
 })
-
-# Conditional argument to run IF new data is imported
-# organization_data <- file_org
-# persona_data <- file_per
 ```

### 2020-10-30 analysis/05_market_simulator.Rmd

@@
   "Import Organization Data",
-  accept = c("text/csv",
+  accept = c(
+    "text/csv",
     "text/comma-separated-values,text/plain",
-             ".csv")
+    ".csv"
+  )
 )
@@
   "Import Persona Data",
-  accept = c("text/csv",
+  accept = c(
+    "text/csv",
     "text/comma-separated-values,text/plain",
-             ".csv")
+    ".csv"
+  )
 )

### 2020-10-30 analysis/05_market_simulator.Rmd
Added req() helps with initial loading of data

@@
   } else {
+    req(input$org_update)
     organization_data <- read_csv(input$org_update$datapath)
@@
   } else {
+    req(input$per_update)
     persona_data <- read_csv(input$per_update$datapath)
@@
 renderTable({
+  req(input$org_update)
+
   org_import = read_csv(input$org_update$datapath)
-
   org_import
@@
 renderTable({
+  req(input$per_update)
+
   per_import = read_csv(input$per_update$datapath)
-
   per_import

### 2020-11-11 analysis/05_market_simulator.Rmd
Testing update buttons
testing new way of importing data so we can use an apply button to change it with filInput

@@
 
+org_default <- read_csv(
+    here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
+  )
+
 # Organization configuration
@@
   if (is.null(input$org_update$datapath)) {
-    organization_data <- read_csv(
-      here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
-    )
+    organization_data <- org_default
   } else {
+    eventReactive()
     req(input$org_update)
@@
 })
+
+# organization_data <- reactive({
+#   if (is.null(input$org_update$datapath)) {
+#     organization_data <- org_default
+#   } else {
+#     req(input$org_update)
+#     eventReactive(input$org_button, {
+#       organization_data <- read_csv(input$org_update$datapath)
+#     })
+#   }
+# })
+
+# observeEvent(input$org_button, {
+#   req(input$org_update)
+#   organization_data$data <- read_csv(input$org_update$datapath)
+# })
 
@@
 
+Imports
+--------------------------------------
+
+```{r import}
+# Organization file input
+fileInput(
+  "org_update",
+  "Import Organization Data",
+  accept = c(
+    "text/csv",
+    "text/comma-separated-values,text/plain",
+    ".csv"
+  )
+)
+
+actionButton(
+  "org_button",
+  label = "Update Organization Data"
+)
+
+# organization_data <- reactive({
+#   eventReactive(input$org_button, {
+#       req(input$org_update)
+#       organization_data <- read_csv(input$org_update$datapath)
+#   })
+# })
+
+# observeEvent(input$org_button, {
+#     session$sendCustomMessage(type = 'testmessage',
+#       message = 'Thank you for clicking')
+#   })
+
+# Persona file input
+fileInput(
+  "per_update",
+  "Import Persona Data",
+  accept = c(
+    "text/csv",
+    "text/comma-separated-values,text/plain",
+    ".csv"
+  )
+)
+
+# Render the organization configurations as a table
+# renderTable({
+#   req(input$org_update)
+#   
+#   org_import = read_csv(input$org_update$datapath)
+#   org_import
+# })
+
+# Render the persona configurations as a table
+renderTable({
+  req(input$per_update)
+
+  per_import = read_csv(input$per_update$datapath)
+  per_import
+})
+```
+
 Market share
@@
 ```
-
-### Imports
-
-```{r import}
-# Organization file input
-fileInput(
-  "org_update",
-  "Import Organization Data",
-  accept = c(
-    "text/csv",
-    "text/comma-separated-values,text/plain",
-    ".csv"
-  )
-)
-
-# actionButton(
-#   "org_button",
-#   label = "Update Organization Data"
-# )
-
-# Persona file input
-fileInput(
-  "per_update",
-  "Import Persona Data",
-  accept = c(
-    "text/csv",
-    "text/comma-separated-values,text/plain",
-    ".csv"
-  )
-)
-
-# Render the organization configurations as a table
-renderTable({
-  req(input$org_update)
-
-  org_import = read_csv(input$org_update$datapath)
-  org_import
-})
-
-# Render the persona configurations as a table
-renderTable({
-  req(input$per_update)
-
-  per_import = read_csv(input$per_update$datapath)
-  per_import
-})
-```

### 2020-11-13 analysis/05_market_simulator.Rmd
Got a button to work finally

@@
 # Organization configuration
-organization_data <- reactive({
-  if (is.null(input$org_update$datapath)) {
-    organization_data <- org_default
-  } else {
-    eventReactive()
-    req(input$org_update)
-    organization_data <- read_csv(input$org_update$datapath)
-  }
-})
-
 # organization_data <- reactive({
 #   if (is.null(input$org_update$datapath)) {
+#     organization_data <- org_default
+#   } else {
+#     req(input$org_update)
+#     organization_data <- read_csv(input$org_update$datapath)
+#   }
+# })
+
+# organization_data <- reactive({
+#   org_file_input <- input$org_update
+#   if (is.null(org_file_input)) {
 #     organization_data <- org_default
@@
 # })
-
-# observeEvent(input$org_button, {
+# 
+# organization_data <- reactive({
+#   organizaiton_data <- org_default
+# })
+# 
+# eventReactive(input$org_button, {
 #   req(input$org_update)
@@
 ```{r import}
+# let the user choose the type of input file
+radioButtons(
+  inputId = "what_config",
+  label = "Choose Configuration",
+  choices = c("Default", "User input"),
+  selected = "Default",
+  inline = FALSE
+  )
+
+# render file input widgets conditioned on user choice
+
 # Organization file input
+conditionalPanel(condition = 'input.what_config == "User input"',
                  fileInput(
@@
                    )
-)
-
+                  ),
                  actionButton(
@@
                   )
-
-# organization_data <- reactive({
-#   eventReactive(input$org_button, {
-#       req(input$org_update)
-#       organization_data <- read_csv(input$org_update$datapath)
-#   })
-# })
-
-# observeEvent(input$org_button, {
-#     session$sendCustomMessage(type = 'testmessage',
-#       message = 'Thank you for clicking')
-#   })
+                 )
 
 # Persona file input
+conditionalPanel(condition = 'input.what_config == "User input"',               
                 fileInput(
@@
                   )
-)
+                ),
+                actionButton(
+                  "per_button",
+                  label = "Update Persona Data"
+                )
+              )
+
+ # observeEvent(input$org_button, {
+ #   req(input$org_update)
+ #    organization_data <- read_csv(input$org_update$datapath)
+ #  })
+
+# deal with the file selected by the user
+organization_data <- reactive({
+  if (input$what_config == "Default") {
+    x <- org_default
+  } else {
+    if (input$what_config == "User input") {
+      req(input$org_button)
+      req(input$org_update)
+      x <- read_csv(input$org_update$datapath)
+    }
+  }
+})
+
+# organization_data <- reactiveValues(data = NULL)
+
+# deal with the file selected by the user
+# organization_data <- reactive({
+#   if (input$what_config == "Default") {
+#     x <- org_default
+#   }
+# })
+# 
+# observeEvent(input$org_button, {
+#   req(input$org_update)
+#   organization_data$data <- read_csv(input$org_update$datapath)
+# })
+
+# deal with the file selected by the user
+# organization_data <- reactive({
+#   if (input$what_source == "Default") {
+#     x <- org_default
+#   }
+# })
+
+# fileInput(
+#   "org_update",
+#   "Import Organization Data",
+#   accept = c(
+#     "text/csv",
+#     "text/comma-separated-values,text/plain",
+#     ".csv"
+#   )
+# )
+
+# actionButton(
+#   "org_button",
+#   label = "Update Organization Data"
+# )
+
+# organization_data <- reactive({
+#   eventReactive(input$org_button, {
+#       req(input$org_update)
+#       organization_data <- read_csv(input$org_update$datapath)
+#   })
+# })
+
+# observeEvent(input$org_button, {
+#     session$sendCustomMessage(type = 'testmessage',
+#       message = 'Thank you for clicking')
+#   })
+
+# Persona file input
+# fileInput(
+#   "per_update",
+#   "Import Persona Data",
+#   accept = c(
+#     "text/csv",
+#     "text/comma-separated-values,text/plain",
+#     ".csv"
+#   )
+# )
 
@@
 # Render the persona configurations as a table
-renderTable({
-  req(input$per_update)
-
-  per_import = read_csv(input$per_update$datapath)
-  per_import
-})
+# renderTable({
+#   req(input$per_update)
+#   
+#   per_import = read_csv(input$per_update$datapath)
+#   per_import
+# })
 ```

### 2020-11-16 analysis/05_market_simulator.Rmd
Got rid of tabs and fixed persona fileInput

--- 2020-10-30 analysis/05_market_simulator.Rmd
@@
 ```{r load-data, message=FALSE}
+
 # Gammas of the "everything" model
@@
 
+# Default Configurations
+
+# Organization
+org_default <- read_csv(
+    here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
+  )
+
+# Persona
+per_default <- read_csv(
+    here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
+  )
+
 # Organization configuration
-organization_data <- reactive({
-  if (is.null(input$org_update$datapath)) {
-    organization_data <- read_csv(
-      here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
-    )
-  } else {
-    req(input$org_update)
-    organization_data <- read_csv(input$org_update$datapath)
-  }
-})
+# organization_data <- reactive({
+#   if (is.null(input$org_update$datapath)) {
+#     organization_data <- org_default
+#   } else {
+#     req(input$org_update)
+#     organization_data <- read_csv(input$org_update$datapath)
+#   }
+# })
 
 # Persona configuration
-persona_data <- reactive({
-  if (is.null(input$per_update$datapath)) {
-    persona_data <- read_csv(
-      here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
-    )
-  } else {
-    req(input$per_update)
-    persona_data <- read_csv(input$per_update$datapath)
-  }
-})
+# persona_data <- reactive({
+#   if (is.null(input$per_update$datapath)) {
+#     persona_data <- read_csv(
+#       here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
+#     )
+#   } else {
+#     req(input$per_update)
+#     persona_data <- read_csv(input$per_update$datapath)
+#   }
+# })
+
 ```
@@
 
-Configurations {.tabset .tabset-fade}
+Imports
+--------------------------------------
+
+```{r import}
+# let the user choose the type of input file
+radioButtons(
+  inputId = "what_config",
+  label = "Choose Configuration",
+  choices = c("Default", "User input"),
+  selected = "Default",
+  inline = FALSE
+  )
+
+# render file input widgets conditioned on user choice
+
+# Organization file input
+conditionalPanel(condition = 'input.what_config == "User input"',
+                 fileInput(
+                   "org_update",
+                   "Import Organization Data",
+                   accept = c(
+                     "text/csv",
+                     "text/comma-separated-values,text/plain",
+                     ".csv"
+                   )
+                  ),
+                 actionButton(
+                   "org_button",
+                   label = "Update Organization Data"
+                  )
+                 )
+
+# Persona file input
+conditionalPanel(condition = 'input.what_config == "User input"',               
+                fileInput(
+                  "per_update",
+                  "Import Persona Data",
+                  accept = c(
+                    "text/csv",
+                    "text/comma-separated-values,text/plain",
+                    ".csv"
+                  )
+                ),
+                actionButton(
+                  "per_button",
+                  label = "Update Persona Data"
+                )
+              )
+
+# deal with the file selected by the user
+
+# Organization Configuration
+organization_data <- reactive({
+  if (input$what_config == "Default") {
+    x <- org_default
+  } else {
+    if (input$what_config == "User input") {
+      req(input$org_button)
+      req(input$org_update)
+      x <- read_csv(input$org_update$datapath)
+    }
+  }
+})
+
+# Persona Configuration
+persona_data <- reactive({
+  if (input$what_config == "Default") {
+    x <- per_default
+  } else {
+    if (input$what_config == "User input") {
+      req(input$per_button)
+      req(input$per_update)
+      x <- read_csv(input$per_update$datapath)
+    }
+  }
+})
+
+```
+
+Configurations
 --------------------------------------------------
@@
 
-### Export
+Export
+--------------------------------------------------
 

### 2020-11-20 analysis/05_market_simulator.Rmd
minor edits
took out radioButtons

@@
 Market share
---------------------------------------
+-------------------------------------------------
 
@@
 
-Imports
---------------------------------------
-
-```{r import}
-# let the user choose the type of input file
-radioButtons(
-  inputId = "what_config",
-  label = "Choose Configuration",
-  choices = c("Default", "User input"),
-  selected = "Default",
-  inline = FALSE
-  )
-
-# render file input widgets conditioned on user choice
-
-# Organization file input
-conditionalPanel(condition = 'input.what_config == "User input"',
-                 fileInput(
-                   "org_update",
-                   "Import Organization Data",
-                   accept = c(
-                     "text/csv",
-                     "text/comma-separated-values,text/plain",
-                     ".csv"
-                   )
-                  ),
-                 actionButton(
-                   "org_button",
-                   label = "Update Organization Data"
-                  )
-                 )
-
-# Persona file input
-conditionalPanel(condition = 'input.what_config == "User input"',               
-                fileInput(
-                  "per_update",
-                  "Import Persona Data",
-                  accept = c(
-                    "text/csv",
-                    "text/comma-separated-values,text/plain",
-                    ".csv"
-                  )
-                ),
-                actionButton(
-                  "per_button",
-                  label = "Update Persona Data"
-                )
-              )
-
-# deal with the file selected by the user
-
-# Organization Configuration
-organization_data <- reactive({
-  if (input$what_config == "Default") {
-    x <- org_default
-  } else {
-    if (input$what_config == "User input") {
-      req(input$org_button)
-      req(input$org_update)
-      x <- read_csv(input$org_update$datapath)
-    }
-  }
-})
-
-# Persona Configuration
-persona_data <- reactive({
-  if (input$what_config == "Default") {
-    x <- per_default
-  } else {
-    if (input$what_config == "User input") {
-      req(input$per_button)
-      req(input$per_update)
-      x <- read_csv(input$per_update$datapath)
-    }
-  }
-})
-
-```
-
 Configurations
---------------------------------------------------
+-------------------------------------------------
 
@@
 
+Import
+-------------------------------------------------
+
+```{r import}
+# # let the user choose the type of input file
+# radioButtons(
+#   inputId = "what_config",
+#   label = "Choose Configuration",
+#   choices = c("Default", "Organization", "Persona"),
+#   selected = "Default",
+#   inline = FALSE
+#   )
+
+# render file input widgets conditioned on user choice
+
+# Organization file input
+# conditionalPanel(condition = 'input.what_config == "User input"',
+#                  fileInput(
+#                    "org_update",
+#                    "Import Organization Data",
+#                    accept = c(
+#                      "text/csv",
+#                      "text/comma-separated-values,text/plain",
+#                      ".csv"
+#                    )
+#                   ),
+#                  actionButton(
+#                    "org_button",
+#                    label = "Update Organization Data"
+#                   )
+#                  )
+
+fileInput(
+ "org_update",
+ "Import Organization Data",
+ accept = c(
+   "text/csv",
+   "text/comma-separated-values,text/plain",
+   ".csv"
+ )
+)
+
+actionButton(
+ "org_button",
+ label = "Update Organization Data"
+)
+
+# Persona file input
+# conditionalPanel(condition = 'input.what_config == "User input"',               
+#                 fileInput(
+#                   "per_update",
+#                   "Import Persona Data",
+#                   accept = c(
+#                     "text/csv",
+#                     "text/comma-separated-values,text/plain",
+#                     ".csv"
+#                   )
+#                 ),
+#                 actionButton(
+#                   "per_button",
+#                   label = "Update Persona Data"
+#                 )
+#               )
+
+fileInput(
+  "per_update",
+  "Import Persona Data",
+  accept = c(
+    "text/csv",
+    "text/comma-separated-values,text/plain",
+    ".csv"
+  )
+)
+actionButton(
+  "per_button",
+  label = "Update Persona Data"
+)
+
+# deal with the file selected by the user
+
+# Organization Configuration
+organization_data <- reactive({
+  if (is.null(input$org_update$datapath)) {
+    x <- org_default
+  } else {
+    req(input$org_button)
+    req(input$org_update)
+    x <- read_csv(input$org_update$datapath)
+  }
+})
+
+# Persona Configuration
+persona_data <- reactive({
+  if (is.null(input$per_update$datapath)) {
+    x <- per_default
+  } else {
+    req(input$per_button)
+    req(input$per_update)
+    x <- read_csv(input$per_update$datapath)
+  }
+})
+
+```
+
 Export

### 2020-11-28 analysis/05_market_simulator.Rmd
Changed default configuration file names and cleaned up some of the comments after testing

--- 2020-11-16 analysis/05_market_simulator.Rmd
@@
 ```{r load-data, message=FALSE}
-
 # Gammas of the "everything" model
@@
 
-# Default Configurations
-
-# Organization
+# Default configurations
 org_default <- read_csv(
-    here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
-  )
-
-# Persona
+    here::here('analysis', 'output', 'configurations', 'org_data_default.csv')
+  )
 per_default <- read_csv(
-    here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
-  )
-
-# Organization configuration
-# organization_data <- reactive({
-#   if (is.null(input$org_update$datapath)) {
-#     organization_data <- org_default
-#   } else {
-#     req(input$org_update)
-#     organization_data <- read_csv(input$org_update$datapath)
-#   }
-# })
-
-# Persona configuration
-# persona_data <- reactive({
-#   if (is.null(input$per_update$datapath)) {
-#     persona_data <- read_csv(
-#       here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
-#     )
-#   } else {
-#     req(input$per_update)
-#     persona_data <- read_csv(input$per_update$datapath)
-#   }
-# })
-
+    here::here('analysis', 'output', 'configurations', 'per_data_default.csv')
+  )
 ```
@@
 
+Import
+-------------------------------------------------
+
+```{r import}
+# Organization configuration import
+fileInput(
+ "org_update",
+ "Import Organization Data",
+ accept = c(
+   "text/csv",
+   "text/comma-separated-values,text/plain",
+   ".csv"
+ )
+)
+actionButton(
+ "org_button",
+ label = "Update Organization Data"
+)
+
+# Persona configuration import
+fileInput(
+  "per_update",
+  "Import Persona Data",
+  accept = c(
+    "text/csv",
+    "text/comma-separated-values,text/plain",
+    ".csv"
+  )
+)
+actionButton(
+  "per_button",
+  label = "Update Persona Data"
+)
+
+# Use the default configurations if no inputs are provided
+organization_data <- reactive({
+  if (is.null(input$org_update$datapath)) {
+    x <- org_default
+  } else {
+    req(input$org_button)
+    req(input$org_update)
+    x <- read_csv(input$org_update$datapath)
+  }
+})
+
+persona_data <- reactive({
+  if (is.null(input$per_update$datapath)) {
+    x <- per_default
+  } else {
+    req(input$per_button)
+    req(input$per_update)
+    x <- read_csv(input$per_update$datapath)
+  }
+})
+```
+
 Export
@@
 ```{r export}
-# Render the organization configurations as a table
+# Render the organization configuration as a table
 renderTable({
@@
 
-# Download Button
+# Download organization configuration
 downloadButton("download_org", label = "Download Organization Data")
@@
 
-# Render the persona configurations as a table
+# Render the persona configuration as a table
 renderTable({
@@
 
-# Download Button
+# Download persona configuration
 downloadButton("download_per", label = "Download Persona Data")

### 2020-11-29 analysis/02_clean-data.Rmd
Modified the labeling in 02_clean-data (again) so that it all lives there and no additional clean-up is needed in 04_figs-tables

--- 2020-09-02 analysis/02_clean-data.Rmd
@@
       ),
-      levels = c("Rarely", "Once a week", "At least once a day")
+      levels = c("Rarely", "Once a week", "At least once a day"),
+      labels = str_c(
+        "Follow national news: ",
+        c("Rarely", "Once a week", "At least once a day")
+      )
     ),
@@
     Q2.2 = fct_relevel(
-      factor(Q2.2, labels = c("Always", "Sometimes", "Never")), 
+      factor(
+        Q2.2, 
+        labels = str_c(
+          "Follow international news: ", 
+          c("Always", "Sometimes", "Never")
+        ),
+      ),
+      str_c(
+        "Follow international news: ", 
         c("Never", "Sometimes", "Always")
+      )
     )
@@
   mutate(
+    Q2.3_1 = factor(Q2.3_1, labels = str_c("Medium to follow news: ", c("No TV", "TV"))),
+    Q2.3_2 = factor(Q2.3_2, labels = str_c("Medium to follow news: ", c("No Print", "Print"))),
+    Q2.3_3 = factor(Q2.3_3, labels = str_c(
+      "Medium to follow news: ", 
+      c("No Online (excluding social media)", "Online (excluding social media)")
+    )),
+    Q2.3_4 = factor(Q2.3_4, labels = str_c(
+      "Medium to follow news: ", 
+      c("No Social media", "Social media")
+    )),
+    Q2.3_5 = factor(Q2.3_5, labels = str_c("Medium to follow news: ", c("No Radio", "Radio"))),
+    Q2.3_6 = factor(Q2.3_6, labels = str_c(
+      "Medium to follow news: ", 
+      c("No Email newsletters", "Email newsletters")
+    )),
+    Q2.3_7 = factor(Q2.3_7, labels = str_c(
+      "Medium to follow news: ", 
+      c("No News app", "News app")
+    )),
     # *Q2.4*: How often would you say you follow what's going on in government and public affairs?
@@
       ),
-      levels = c("Not often", "Often")
+      levels = c("Not often", "Often"),
+      labels = str_c(
+        "Follow government and public affairs: ",
+        c("Not often", "Often")
+      )
     ),
@@
       ),
-      levels = c("More than once a month, less than once a year", "At least once a month")
+      levels = c("More than once a month, less than once a year", "At least once a month"),
+      labels = str_c(
+        "Donation frequency: ",
+        c("More than once a month, less than once a year", "At least once a month")
+      )
     ),
@@
       Q2.6, 
-      labels = c(
+      labels = str_c("Donated last year: ", c(
         "$1-$49", "$50-$99", "$100-$499", "$500-$999", 
-        "$1000-$4,999", "$5000-$9,999", "$10,000+"),
+        "$1000-$4,999", "$5000-$9,999", "$10,000+")),
       ordered = TRUE
@@
       Q2.7,
-      labels = c(
+      labels = str_c("Importance of trusing charities: ", c(
         "Not at all important", "Very unimportant", "Somewhat unimportant", 
         "Neutral", "Somewhat important", "Very important", "Essential"
-      ),
+      )),
       ordered = TRUE
@@
       Q2.8,
-      labels = c(
+      labels = str_c("Trust in charities: ", c(
         "No trust at all", "Very little trust", "Little trust", 
         "Neutral", "Some trust", "A lot of trust", "Complete trust"
-      ),
+      )),
       ordered = TRUE
@@
     Q2.9 = fct_relevel(
-      factor(Q2.9, labels = c("Yes", "No")), 
-      c("No", "Yes")
+      factor(Q2.9, labels = str_c("Volunteered in past 12 months: ", c("Yes", "No"))), 
+      str_c("Volunteered in past 12 months: ", c("No", "Yes"))
     ),
@@
       ),
-      levels = c("Haven't volunteered in past 12 months", "Rarely", "More than once a month, less than once a year", "At least once a month")
+      levels = c("Haven't volunteered in past 12 months", "Rarely", "More than once a month, less than once a year", "At least once a month"),
+      labels = str_c(
+        "Volunteer frequency: ",
+        c("Haven't volunteered in past 12 months", "Rarely", "More than once a month, less than once a year", "At least once a month")
+      )
     ),
@@
     Q5.1 = fct_relevel(
-      factor(Q5.1, labels = c("Yes", "No")), 
-      c("No", "Yes")
+      factor(Q5.1, labels = str_c("Voted in last election: ", c("Yes", "No"))), 
+      str_c("Voted in last election: ", c("No", "Yes"))
     ),
@@
       Q5.2,
-      labels = c(
+      labels = str_c("Liberal to Conservative: ", c(
         "Extremely liberal", "Somewhat liberal", "Slightly liberal", "Moderate",
         "Slightly conservative", "Somewhat conservative", "Extremely conservative"
+      )),
+      ordered = TRUE
     ),
-      ordered = TRUE
+    # *Q5.3*: Here is a list of different types of voluntary organizations.
+For each organization, indicate whether you are an active member, an inactive member, or not a member of that type of organization:
+    # 
+    # |                                         | Active member | Inactive member | Don't belong |
+    # | --------------------------------------- | :-----------: | :-------------: | :----------: |
+    # | Church or religious organization        |       •       |        •        |      •       |
+    # | Sport or recreational organization      |       •       |        •        |      •       |
+    # | Art, music, or educational organization |       •       |        •        |      •       |
+    # | Labor union                             |       •       |        •        |      •       |
+    # | Political party                         |       •       |        •        |      •       |
+    # | Environmental organization              |       •       |        •        |      •       |
+    # | Professional association                |       •       |        •        |      •       |
+    # | Humanitarian or charitable organization |       •       |        •        |      •       |
+    # | Consumer organization                   |       •       |        •        |      •       |
+    # | Other organization                      |       •       |        •        |      •       |
+    Q5.3_1 = fct_relevel(
+      factor(Q5.3_1, labels = str_c(
+        "Church or religious organization: ", 
+        c("Active member", "Inactive member", "Don't belong"))
+      ), 
+      str_c(
+        "Church or religious organization: ", 
+        c("Don't belong", "Inactive member", "Active member")
+      )
+    ),
+    Q5.3_2 = fct_relevel(
+      factor(Q5.3_2, labels = str_c(
+        "Sport or recreational organization: ",
+        c("Active member", "Inactive member", "Don't belong"))
+      ), 
+      str_c(
+        "Sport or recreational organization: ",
+        c("Don't belong", "Inactive member", "Active member")
+      )
+    ),
+    Q5.3_3 = fct_relevel(
+      factor(Q5.3_3, labels = str_c(
+        "Art, music, or educational organization: ",
+        c("Active member", "Inactive member", "Don't belong"))
+      ), 
+      str_c(
+        "Art, music, or educational organization: ",
+        c("Don't belong", "Inactive member", "Active member")
+      )
+    ),
+    Q5.3_4 = fct_relevel(
+      factor(Q5.3_4, labels = str_c(
+        "Labor union: ",
+        c("Active member", "Inactive member", "Don't belong"))
+      ), 
+      str_c(
+        "Labor union: ",
+        c("Don't belong", "Inactive member", "Active member")
+      )
+    ),
+    Q5.3_5 = fct_relevel(
+      factor(Q5.3_5, labels = str_c(
+        "Political party: ",
+        c("Active member", "Inactive member", "Don't belong"))
+      ), 
+      str_c(
+        "Political party: ",
+        c("Don't belong", "Inactive member", "Active member")
+      )
+    ),
+    Q5.3_6 = fct_relevel(
+      factor(Q5.3_6, labels = str_c(
+        "Environmental organization: ",
+        c("Active member", "Inactive member", "Don't belong"))
+      ), 
+      str_c(
+        "Environmental organization: ",
+        c("Don't belong", "Inactive member", "Active member")
+      )
+    ),
+    Q5.3_7 = fct_relevel(
+      factor(Q5.3_7, labels = str_c(
+        "Professional association: ",
+        c("Active member", "Inactive member", "Don't belong"))
+      ), 
+      str_c(
+        "Professional association: ",
+        c("Don't belong", "Inactive member", "Active member")
+      )
+    ),
+    Q5.3_8 = fct_relevel(
+      factor(Q5.3_8, labels = str_c(
+        "Humanitarian or charitable organization: ",
+        c("Active member", "Inactive member", "Don't belong"))
+      ), 
+      str_c(
+        "Humanitarian or charitable organization: ",
+        c("Don't belong", "Inactive member", "Active member")
+      )
+    ),
+    Q5.3_9 = fct_relevel(
+      factor(Q5.3_9, labels = str_c(
+        "Consumer organization: ",
+        c("Active member", "Inactive member", "Don't belong"))
+      ), 
+      str_c(
+        "Consumer organization: ",
+        c("Don't belong", "Inactive member", "Active member")
+      )
+    ),
+    Q5.3_10 = fct_relevel(
+      factor(Q5.3_10, labels = str_c(
+        "Other organization: ",
+        c("Active member", "Inactive member", "Don't belong"))
+      ), 
+      str_c(
+        "Other organization: ",
+        c("Don't belong", "Inactive member", "Active member")
+      )
     ),
@@
       ),
-      levels = c("Not involved", "Involved")
+      levels = c("Not involved", "Involved"),
+      labels = str_c(
+        "History of activism: ",
+        c("Not involved", "Involved")
+      )
     ),
@@
       ),
-      levels = c("Not involved", "Involved")
+      levels = c("Not involved", "Involved"),
+      labels = str_c(
+        "History of family activism: ",
+        c("Not involved", "Involved")
+      )
     ),
@@
       Q5.6,
-      labels = c(
+      labels = str_c("Trust in political institutions: ",c(
         "No trust at all", "Very little trust", "Little trust", 
         "Neutral", "Some trust", "A lot of trust", "Complete trust"
-      ),
+      )),
       ordered = TRUE
@@
     Q5.7 = fct_relevel(
-      factor(Q5.7, labels = c("Yes", "No")), 
-      c("No", "Yes")
+      factor(Q5.7, labels = str_c("Traveled to a developing country: ", c("Yes", "No"))), 
+      str_c("Traveled to a developing country: ", c("No", "Yes"))
     ),
@@
       ),
-      levels = c("Not sure", "Rarely", "At least once a month")
+      levels = c("Not sure", "Rarely", "At least once a month"),
+      labels = str_c(
+        "Religious and worship service attendance: ",
+        c("Not sure", "Rarely", "At least once a month")
+      )
     ),
@@
       ),
-      levels = c("Not important", "Important")
+      levels = c("Not important", "Important"),
+      labels = str_c(
+        "Importance of religion: ",
+        c("Not important", "Important")
+      )
     ),
@@
       Q5.10, 
-      labels = c(
+      labels = str_c("Religion: ", c(
         "Catholic", "Protestant", "Christian Orthodox", "Jewish", 
-        "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other"), 
+        "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")), 
       ordered = TRUE
@@
         Q5.11,
-        labels = c(
+        labels = str_c("People should be more charitable: ", c(
           "Strongly agree", "Agree", "Somewhat agree", 
           "Neutral", "Somewhat disagree", "Disagree", "Strongly disagree"
+        ))
       ),
-        c(
+      str_c("People should be more charitable: ", c(
         "Strongly disagree", "Disagree", "Somewhat disagree",
         "Neutral", "Somewhat agree", "Agree", "Strongly agree"
-        )
-      )
+      ))
     ),
@@
       Q5.12, 
-      labels = c(
+      labels = str_c("Gender: ", c(
         "Male", "Female", "Transgender", 
         "Prefer not to say", "Other"
-      ), 
+      )), 
       ordered = TRUE
@@
       Q5.13, 
-      labels = c(
+      labels = str_c("Marital status: ", c(
         "Married", "Widowed", "Divorced", 
         "Separated", "Never married"
-      ), 
+      )), 
       ordered = TRUE
@@
       Q5.14, 
-      labels = c(
+      labels = str_c("Education: ", c(
         "Less than high school", "High school graduate", 
@@
         "Graduate or professional degree", "Doctorate"
-      ),
+      )),
       ordered = TRUE
@@
       ),
-      levels = c("Less than median", "More than median")
+      levels = c("Less than median", "More than median"),
+      labels = str_c(
+        "Income: ",
+        c("Less than median", "More than median")
+      )
     )
@@
   mutate(
+    Q5.16_1 = factor(Q5.16_1, labels = str_c("Race: ", c("Not White", "White"))),
+    Q5.16_2 = factor(Q5.16_2, labels = str_c(
+      "Race: ", c("Not Black or African American", "Black or African American"))
+    ),
+    Q5.16_3 = factor(Q5.16_3, labels = str_c(
+      "Race: ", c("Not American Indian or Alaska Native", "American Indian or Alaska Native"))
+    ),
+    Q5.16_4 = factor(Q5.16_4, labels = str_c("Race: ", c("Not Asian", "Asian"))),
+    Q5.16_5 = factor(Q5.16_5, labels = str_c(
+      "Race: ", 
+      c("Not Native Hawaiian or Pacific Islander", "Native Hawaiian or Pacific Islander")
+    )),
+    Q5.16_6 = factor(Q5.16_6, labels = str_c("Race: ", c("Not Other", "Other"))),
     # *Q5.17*: How old are you?
@@
       ),
-      levels = c("Less than median", "More than median")
+      levels = c("Less than median", "More than median"),
+      labels = str_c(
+        "Age: ", 
+        c("Less than median", "More than median")
+      )
     )

### 2020-11-29 analysis/04_figs-tables.Rmd
Moved all labeling to clean-data and followed the lookup scheme for covariates as well, hopefully simplifying all future plots and tables

--- 2020-01-14 analysis/04_figs_tables.Rmd
@@
 
+# Load packages, data, and draws
+
 ```{r setup, warning=FALSE, message=FALSE}
@@
 library(donorheuristics)
-# library(rstan)
-# library(bayesplot)
 library(tidybayes)
 library(broom)
-# library(bayesm)
 # library(ggridges)
@@
 
-# Name labels
+# Load draws
+intercept <- 0                            # Intercept-only
+public_affairs <- 1                       # Public affairs
+political_ideology <- 0                   # Political ideology
+social_views <- 0                         # Social views
+charity_voluntarism <- 0                  # Charity and voluntarism
+demographics <- 0                         # Demographics
+public_political <- 0                     # Public affairs + Political ideology
+public_political_social <- 0              # + Social views
+public_political_social_charity <- 0      # + Charity and voluntarism
+public_political_social_charity_demo <- 0 # + Demographics
+
+if (intercept == 1) {
+  draws <- read_rds(
+    here::here("analysis", "output", "posterior_draws", "intercept.rds")
+  ) %>% 
+    mutate(model = "Intercept only")
+}
+if (public_affairs == 1) {
+  draws <- read_rds(
+    here::here("analysis", "output", "posterior_draws", "public_affairs.rds")
+  ) %>% 
+    mutate(model = "Public affairs")
+  covariates <- results %>%
+    select(
+      Q2.1, Q2.2, Q2.3_1:Q2.3_7, Q2.4, Q5.7 # Public affairs
+    )
+}
+if (political_ideology == 1) {
+  draws <- read_rds(
+    here::here("analysis", "output", "posterior_draws", "political_ideology.rds")
+  ) %>% 
+    mutate(model = "Political ideology")
+  covariates <- results %>%
+    select(
+      Q5.2 # Political ideology
+    )
+}
+if (social_views == 1) {
+  draws <- read_rds(
+    here::here("analysis", "output", "posterior_draws", "social_views.rds")
+  ) %>% 
+    mutate(model = "Social views")
+  covariates <- results %>%
+    select(
+      Q5.6, Q5.11, Q5.8, Q5.9, Q5.10 # Social views
+    )
+}
+if (charity_voluntarism == 1) {
+  draws <- read_rds(
+    here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds")
+  ) %>% 
+    mutate(model = "Charity and voluntarism")
+  covariates <- results %>%
+    select(
+      Q2.7, Q2.8, Q2.5, Q2.6, Q2.9, Q2.10, Q5.4, Q5.5, Q5.3_1:Q5.3_10 # Charity and voluntarism
+    )
+}
+if (demographics == 1) {
+  draws <- read_rds(
+    here::here("analysis", "output", "posterior_draws", "demographics.rds")
+  ) %>% 
+    mutate(model = "Demographics")
+  covariates <- results %>%
+    select(
+      Q5.12, Q5.13, Q5.14, Q5.15, Q5.16_1:Q5.16_6, Q5.17 # Demographics
+    )
+}
+if (public_political == 1) {
+  draws <- read_rds(
+    here::here("analysis", "output", "posterior_draws", "public_political.rds")
+  ) %>% 
+    mutate(model = "Public affairs and political ideology")
+  covariates <- results %>%
+    select(
+      Q2.1, Q2.2, Q2.3_1:Q2.3_7, Q2.4, Q5.7, # Public affairs
+      Q5.2                                   # Political ideology
+    )
+}
+if (public_political_social == 1) {
+  draws <- read_rds(
+    here::here("analysis", "output", "posterior_draws", "public_political_social.rds")
+  ) %>% 
+    mutate(model = "Public affairs, political ideology, and social views")
+  covariates <- results %>%
+    select(
+      Q2.1, Q2.2, Q2.3_1:Q2.3_7, Q2.4, Q5.7, # Public affairs
+      Q5.2,                                  # Political ideology
+      Q5.6, Q5.11, Q5.8, Q5.9, Q5.10         # Social views
+    )
+}
+if (public_political_social_charity == 1) {
+  draws <- read_rds(
+    here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds")
+  ) %>% 
+    mutate(
+      model = "Public affairs, political ideology, social views, charity and voluntarism"
+    )
+  covariates <- results %>%
+    select(
+      Q2.1, Q2.2, Q2.3_1:Q2.3_7, Q2.4, Q5.7,                           # Public affairs
+      Q5.2,                                                            # Political ideology
+      Q5.6, Q5.11, Q5.8, Q5.9, Q5.10,                                  # Social views
+      Q2.7, Q2.8, Q2.5, Q2.6, Q2.9, Q2.10, Q5.4, Q5.5, Q5.3_1:Q5.3_10  # Charity and voluntarism
+    )
+}
+if (public_political_social_charity_demo == 1) {
+  draws <- read_rds(
+    here::here(
+      "analysis", 
+      "output", 
+      "posterior_draws", 
+      "public_political_social_charity_demo.rds"
+    )
+  ) %>% 
+    mutate(
+      model = "Public affairs, 
+      political ideology, 
+      social views, 
+      charity and voluntarism, 
+      and demographics"
+    )
+  covariates <- results %>%
+    select(
+      Q2.1, Q2.2, Q2.3_1:Q2.3_7, Q2.4, Q5.7,                           # Public affairs
+      Q5.2,                                                            # Political ideology
+      Q5.6, Q5.11, Q5.8, Q5.9, Q5.10,                                  # Social views
+      Q2.7, Q2.8, Q2.5, Q2.6, Q2.9, Q2.10, Q5.4, Q5.5, Q5.3_1:Q5.3_10, # Charity and voluntarism
+      Q5.12, Q5.13, Q5.14, Q5.15, Q5.16_1:Q5.16_6, Q5.17               # Demographics
+    )
+}
+
+# Name levels labels
 level_labels <- c(
@@
 level_lookup <- tibble(levels = level_labels) %>% 
-  separate(levels, c("category", "attribute"), sep = ": ") %>% 
-  mutate(attributes_long = paste0(category, ": ", attribute),
+  separate(levels, c("attribute", "level"), sep = ": ") %>% 
+  mutate(levels_long = paste0(attribute, ": ", level),
          i = 1:n()) %>% 
-  mutate_at(vars(category, attribute, attributes_long), list(fct_inorder))
+  mutate_at(vars(attribute, level, levels_long), list(fct_inorder))
 
-draws <- read_rds(here("analysis", "output", "posterior_draws", 
-                       "intercept_noncentered.rds")) %>% 
-  mutate(model = "Intercept only") %>% 
-  left_join(level_lookup, by = "i")
+# Extract covariate labels
+covariate_lookup <- covariates %>% 
+  pivot_longer(cols = starts_with("Q"), names_to = "question", values_to = "labels") %>% 
+  bind_cols(
+    covariates %>% 
+      mutate_all(as.integer) %>% 
+      rename_all(paste0, "_temp") %>% 
+      pivot_longer(cols = starts_with("Q"), names_to = "question_temp", values_to = "level")
+  ) %>% 
+  distinct() %>% 
+  filter(level != 1) %>% 
+  separate(labels, c("covariate", "label"), sep = ": ") %>% 
+  mutate(covariates_long = paste0(covariate, ": ", label), j = 2:(n() + 1)) %>% 
+  select(covariate, label, covariates_long, j) %>% 
+  bind_rows(
+    tibble(
+      covariate = "Intercept",
+      label = "Intercept",
+      covariates_long = "Intercept",
+      j = 1
+    )
+  ) %>% 
+  arrange(j) %>% 
+  mutate_at(vars(covariate, label, covariates_long), list(fct_inorder))
+
+# Join level and covariate labels to draws
+draws %>% 
+  left_join(level_lookup, by = "i") %>% 
+  left_join(covariate_lookup, by = "j")
 ```
@@
 ```
+
+## Plot marginals
+
+```{r plot-marginals}
+# Plot marginals
+if (intercept == 1) {
+  draws %>%
+    mutate(
+      levels = factor(i, labels = level_labels)
+    ) %>%
+    ggplot(aes(x = Gamma, y = levels)) +
+    stat_halfeye(.width = .95) +
+    geom_vline(xintercept = 0, color = "grey") +
+    labs(y = "Attribute Levels")
+}
+if (intercept != 1) {
+  draws %>%
+    filter(j != 1) %>%
+    mutate(
+      levels = factor(i, labels = level_labels),
+      covariates = factor(j, labels = covariate_labels)
+    ) %>%
+    ggplot(aes(x = Gamma, y = covariates)) +
+    stat_halfeye(.width = .95) +
+    geom_vline(xintercept = 0, color = "white") +
+    labs(y = "Covariates") +
+    facet_wrap(~ levels, ncol = 5)
+}
+
+# Save plot
+if (intercept == 1) file_name <- paste("marginal-posteriors_intercept.png")
+if (public_affairs == 1) file_name <- paste("marginal-posteriors_public-affairs.png")
+if (political_ideology == 1) file_name <- paste("marginal-posteriors_political-ideology.png")
+if (social_views == 1) file_name <- paste("marginal-posteriors_social-views.png")
+if (charity_voluntarism == 1) file_name <- paste("marginal-posteriors_charity-voluntarism.png")
+if (demographics == 1) file_name <- paste("marginal-posteriors_demographics.png")
+if (public_political == 1) file_name <- paste("marginal-posteriors_public-political.png")
+if (public_political_social == 1) file_name <- paste("marginal-posteriors_public-political-social.png")
+if (public_political_social_charity == 1) file_name <- paste("marginal-posteriors_public-political-social-charity.png")
+if (public_political_social_charity_demo == 1) file_name <- paste("marginal-posteriors_public-political-social-charity-demos.png")
+if (intercept == 1) width_length <- c(10, 10)
+if (intercept != 1) width_length <- c(20, 20)
+if (public_political_social_charity == 1) width_length <- c(20, 30)
+if (public_political_social_charity_demo == 1) width_length <- c(20, 30)
+ggsave(
+  file_name,
+  path = here::here("analysis", "output", "figures"),
+  width = width_length[1],
+  height = width_length[2],
+  units = "in"
+)
+```
+
+## Plot heatmaps
+
+Instead of plotting marginals, we can use a heatmap to identify where there are significant differences in the non-intercept models, which can then be narrowed down using the marginal plots.
+
+```{r plot-heatmaps}
+if (public_affairs == 1) plot_title <- paste("Public Affairs")
+if (political_ideology == 1) plot_title <- paste("Political Ideology")
+if (social_views == 1) plot_title <- paste("Social Views")
+if (charity_voluntarism == 1) plot_title <- paste("Covariates related to charity and voluntarism")
+if (demographics == 1) plot_title <- paste("Demographics")
+if (public_political == 1) plot_title <- paste("Public Affairs and Political Ideology")
+if (public_political_social == 1) plot_title <- paste("Public Affairs, Political Ideology, and Social Views")
+if (public_political_social_charity == 1) plot_title <- paste("Public Affairs, Political Ideology, Social Views, and Charity and Voluntarism")
+if (public_political_social_charity_demo == 1) plot_title <- paste("Public Affairs, Political Ideology, Social Views, Charity and Voluntarism, and Demographics")
+
+if (charity_voluntarism == 1) {
+  j_labels <- tribble(
+    ~j, ~j_label,
+    2, "Importance of trusting charities", 
+    3, "Trust charities", 
+    4, "Frequency of donation", 
+    5, "Amount of donation", 
+    6, "Volunteered", 
+    7, "Volunteer frequency", 
+    8, "Personal involvement in activism", 
+    9, "Family involvement in activism", 
+    10, "Membership in church", 
+    11, "Membership in sports", 
+    12, "Membership in art, music, or educational organization", 
+    13, "Membership in labor union", 
+    14, "Membership in political party", 
+    15, "Membership in envrionmental organization", 
+    16, "Membership in professional association", 
+    17, "Membership in humanitarian organization", 
+    18, "Membership in consumer organization", 
+    19, "Membership in other organization"
+  ) %>% 
+    mutate(j_label = fct_inorder(j_label))
+}
+
+if (intercept != 1) {
+  # Posterior means.
+  posterior_means <- draws %>% 
+    filter(j != 1) %>% 
+    left_join(j_labels, by = "j") %>% 
+    left_join(level_lookup, by = "i") %>% 
+    mutate(
+      levels = factor(i, labels = level_labels), 
+      covariates = factor(j, labels = 1:length(covariate_labels))
+    ) %>% 
+    group_by(category, attribute, j_label) %>% 
+    summarize(
+      mean = mean(Gamma),
+      ci_lower = quantile(Gamma, .025),
+      ci_upper = quantile(Gamma, .975),
+      gt_zero = if_else(ci_lower > 0 & ci_upper > 0, 1, 0),
+      lt_zero = if_else(ci_lower < 0 & ci_upper < 0, -1, 0)
+    )
+
+  # Heatmap of Gamma matrix.
+  plot_heatmap <- posterior_means %>% 
+    mutate(
+      gt_lt_zero = gt_zero + lt_zero,
+      Coefficients = factor(
+        gt_lt_zero, 
+        levels = -1:1,
+        labels = c("Negative", "Not Significant", "Positive"))
+    ) %>% 
+    ggplot(aes(x = j_label, y = attribute, fill = Coefficients)) +
+    geom_tile(color = "white", size = 0.25) +
+    # scale_fill_brewer(palette = "Blues") +
+    scale_fill_manual(values = c(clrs$orange, "grey80", clrs$olive)) +
+    scale_x_discrete(expand = c(0.001, 0.001)) +
+    scale_y_discrete(expand = c(0.001, 0.001)) +
+    # guides(fill = guide_legend(override.aes = list(key.height = 0.5, key.width = 0.5))) +
+    guides(fill = guide_legend(keywidth = 0.5, keyheight = 0.5)) +
+    theme_ngo(base_size = 14) +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
+          legend.position = "bottom",
+          strip.placement = "outside") +
+    labs(
+      title = plot_title,
+      x = "Covariates",
+      y = "Attribute Levels"
+    ) + 
+    # facet_wrap(~ category, ncol = 1, scales = "free_y")
+    facet_grid(vars(category), scales = "free_y", space = "free_y")
+}
+
+plot_heatmap
+ggsave(plot_heatmap, filename = here("analysis", "output", "figures", "q2-heatmap.pdf"),
+       width = 26/3, height = 6.5, units = "in", device = cairo_pdf)
+ggsave(plot_heatmap, filename = here("analysis", "output", "figures", "q2-heatmap.png"),
+       width = 26/3, height = 6.5, units = "in", type = "cairo", dpi = 300)
+
+# Save plot
+if (public_affairs == 1) file_name <- paste("public-affairs_coefficient-matrix.png")
+if (political_ideology == 1) file_name <- paste("political-ideology_coefficient-matrix.png")
+if (social_views == 1) file_name <- paste("social-views_coefficient-matrix.png")
+if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_coefficient-matrix.png")
+if (demographics == 1) file_name <- paste("demographics_coefficient-matrix.png")
+if (public_political == 1) file_name <- paste("public-political_coefficient-matrix.png")
+if (public_political_social == 1) file_name <- paste("public-political-social_coefficient-matrix.png")
+if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_coefficient-matrix.png")
+if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_coefficient-matrix.png")
+ggsave(
+  file_name,
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
+```
+
+## Plot contrasts
+
+A better approach to address the hypotheses (taken from the former 03b and 03c).
+
+- We theorize that structural characteristics like an NGO’s host-country political and legal environment can serve as heuristics and shortcuts for donors.
+- Donors who see that an NGO faces general legal trouble abroad will use that knowledge to decide whether or not to donate.
+- We also theorize that non-structural organizational characteristics like managerial practices, funding sources, and issue area also serve as heuristics and influence donation patterns.
+- In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics.
+We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we’re unsure of the direction of that effect.
+
+> In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics.
+We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we're unsure of the direction of that effect.
 
@@
 # Results
+
+## Model fit table
+
+```{r model-fit}
+# Load model fit table
+read_rds(model_fit, here::here("analysis", "output", "model_fit.rds"))
+```
+
+The intercept-only model works best in terms of PSIS-LOO, followed by models with political ideology, public affairs and demographics covariates.
+While PSIS-LOO doesn't properly account for the specific benefits of a hierarchical model, it suggests that political ideology above all other covariate sets specified, has the most explanatory power.
 
@@
 ```
+
+# Original computing environment
+
+<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>
+
+<div id="sessioninfo" class="collapse">
+
+```{r show-session-info, echo=TRUE, width=100}
+writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))
+
+devtools::session_info()
+```
+
+</div>

### 2020-12-18 dashboard_example.Rmd
added dashboard_example. Not finished yet

--- 2020-11-28 analysis/05_market_simulator.Rmd
@@
 ---
-title: "Market simulator"
+title: "Example of Market Simulator Dasbhaord"
 output: 
@@
 # Default configurations
-org_default <- read_csv(
+prod_default <- read_csv(
     here::here('analysis', 'output', 'configurations', 'org_data_default.csv')
@@
 
-```{r organization-reactive-table}
+```{r prod-reactive-table}
 # Assign level labels
@@
 
-# Organization configuration reactive element
-org_reactive <- reactive({
-  # Organization 1
+# prod configuration reactive element
+prod_reactive <- reactive({
+  # prod 1
   org_table$org1_value <- 0
@@
 
-  # Organization 2
+  # prod 2
   org_table$org2_value <- 0
@@
 
-  # Organization 3
+  # prod 3
   org_table$org3_value <- 0
@@
 
-  # Organization 4
+  # prod 4
   org_table$org4_value <- 0
@@
     "Intercept",
-    # Follow national news
-    "Once a week",
-    "At least once a day",
-    # Follow international news
-    "Sometimes",
-    "Always",
     # Mediums to follow news
@@
     "News app",
-    # Follow government and public affairs
-    "Often", 
-    # Traveled to a developing country
-    "Traveled to a developing country", 
-    # Liberal to Conservative
-    "Somewhat liberal",
-    "Slightly liberal",
-    "Moderate",
-    "Slightly conservative",
-    "Somewhat conservative",
-    "Extremely conservative",
-    # Trust in political institutions
-    "Very little trust in political institutions",
-    "Little trust in political institutions",
-    "Neutral trust in political institutions",
-    "Some trust in political institutions",
-    "A lot of trust in political institutions",
-    "Complete trust in political institutions",
-    # People should be more charitable
-    "Disagree",
-    "Somewhat disagree",
-    "Neutral",
-    "Somewhat agree",
-    "Agree",
-    "Strongly agree",
-    # Religious attendance
-    "Rarely attend",
-    "Attend at least once a month",
-    # Importance of religion
-    "Important",
-    # Religion
-    "Protestant",
-    "Christian Orthodox",
-    "Jewish",
-    "Muslim",
-    "Sikh",
-    "Hindu",
-    "Buddhist",
-    "Atheist",
-    "Other religion",
-    # Importance of trusting charities
-    "Very unimportant",
-    "Somewhat unimportant",
-    "Neutral importance",
-    "Somewhat important",
-    "Very important",
-    "Essential",
-    # Trust in charities
-    "Very little trust in charities",
-    "Little trust in charities",
-    "Neutral trust in charities",
-    "Some trust in charities",
-    "A lot of trust in charities",
-    "Complete trust in charities",
-    # Donation frequency
-    "Donate at least once a month", 
-    # Donated last year
-    "$50-$99",
-    "$100-$499",
-    "$500-$999",
-    "$1,000-$4,999",
-    "$5,000-$9,999",
-    "$10,000+",
-    # Volunteered in past 12 months
-    "Volunteered in past 12 months",
-    # Volunteer frequency
-    "Rarely volunteer",
-    "Volunteer more than once a month, less than once a year",
-    "Volunteer at least once a month",
-    # History of activism
-    "Personally involved",
-    # History of family activism
-    "Family involved",
-    # Church or religious organization
-    "Inactive church member",
-    "Active church member",
-    # Sport or recreational organization
-    "Inactive sports or rec organization member",
-    "Active sports or rec organization member", 
-    # Art, music, or educational organization
-    "Inactive art, music, or educational organization member",
-    "Active art, music, or educational organization member",
-    # Labor union
-    "Inactive union member",
-    "Active union member",
-    # Political party
-    "Inactive political party member",
-    "Active political party member",
-    # Environmental organization
-    "Inactive environmental organization member",
-    "Active environmental organization member",
-    # Professional association
-    "Inactive professional association member",
-    "Active professional association member",
-    # Humanitarian or charitable organization
-    "Inactive humanitarian or charitable organization member",
-    "Active humanitarian or charitable organization member",
-    # Consumer organization
-    "Inactive consumer organization member",
-    "Active consumer organization member",
-    # Other organization
-    "Inactive member in another organization",
-    "Active member in another organization",
     # Gender
@@
 
+## Test to subset the data
+per_join <- per_default %>% inner_join(per_table, by = "levels")
+
 # Persona configuration reactive element
@@
   per_table$per1_value[per_table$levels == 'Intercept'] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_national_news] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_international_news] <- 1
   per_table$per1_value[per_table$levels %in% input$per1_news_medium] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_follow_gov] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_travel_developing] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_political_pref] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_institution_trust] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_others_charitable] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_worship_attendance] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_religion_importance] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_religion] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_charity_importance] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_trust_in_charity] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_donation_frequency] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_donation_amount] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_volunteer_12] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_volunteer_frequency] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_personal_activism] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_family_activism] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_religious_member] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_sport_member] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_art_member] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_labor_member] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_political_member] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_environmental_member] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_professional_member] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_humanitarian_member] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_consumer_member] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_other_member] <- 1
   per_table$per1_value[per_table$levels %in% input$per1_gender] <- 1
@@
   per_table$per2_value[per_table$levels == 'Intercept'] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_national_news] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_international_news] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_news_medium] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_follow_gov] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_travel_developing] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_political_pref] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_institution_trust] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_others_charitable] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_worship_attendance] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_religion_importance] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_religion] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_charity_importance] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_trust_in_charity] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_donation_frequency] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_donation_amount] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_volunteer_12] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_volunteer_frequency] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_personal_activism] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_family_activism] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_religious_member] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_sport_member] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_art_member] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_labor_member] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_political_member] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_environmental_member] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_professional_member] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_humanitarian_member] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_consumer_member] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_other_member] <- 1
   per_table$per2_value[per_table$levels %in% input$per2_gender] <- 1
@@
   per_table$per3_value[per_table$levels == 'Intercept'] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_national_news] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_international_news] <- 1
   per_table$per3_value[per_table$levels %in% input$per3_news_medium] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_follow_gov] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_travel_developing] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_political_pref] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_institution_trust] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_others_charitable] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_worship_attendance] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_religion_importance] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_religion] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_charity_importance] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_trust_in_charity] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_donation_frequency] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_donation_amount] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_volunteer_12] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_volunteer_frequency] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_personal_activism] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_family_activism] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_religious_member] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_sport_member] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_art_member] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_labor_member] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_political_member] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_environmental_member] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_professional_member] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_humanitarian_member] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_consumer_member] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_other_member] <- 1
   per_table$per3_value[per_table$levels %in% input$per3_gender] <- 1
@@
     ),
-    Organization = c(input$org1_name, input$org2_name, input$org3_name, input$org4_name),
+    Product = c(input$org1_name, input$org2_name, input$org3_name, input$org4_name),
     Persona = c(
@@
     plot_data %>% 
-      # Factor Organization and Persona with ordered=TRUE
+      # Factor Product and Persona with ordered=TRUE
       mutate(
-        Organization = factor(
-          Organization, 
+        Product = factor(
+          Product, 
           levels = c(input$org1_name, input$org2_name, input$org3_name, input$org4_name), 
@@
       ) %>% 
-      ggplot(aes(y = Value, x = Organization, fill = Persona)) +
+      ggplot(aes(y = Value, x = Product, fill = Persona)) +
       geom_bar(position = "dodge", stat = "identity") +
@@
 
-### Organization 1
+### Product 1
 
@@
   "org1_name",
-  label = "Organization Name:",
-  value = "Organization 1",
-  placeholder = "Enter Organization Name",
-  width = "450px"
-)
-
-# Organization
-renderUI({
-  org_data = organization_data()
+  label = "Product Name:",
+  value = "Product 1",
+  placeholder = "Enter Product Name",
+  width = "450px"
+)
+
+# Product
+renderUI({
+  org_data = product_data()
   selectInput(
     "org1_org",
-    label = "Organization:",
+    label = "Product:",
     choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
@@
 renderUI({
-  org_data = organization_data()
+  org_data = product_data()
   selectInput(
@@
 
-### Organization 2
+### Product 2
 
@@
   "org2_name",
-  label = "Organization Name:",
-  value = "Organization 2",
-  placeholder = "Enter Organization Name",
-  width = "450px"
-)
-
-# Organization
-renderUI({
-  org_data = organization_data()
+  label = "Product Name:",
+  value = "Product 2",
+  placeholder = "Enter Product Name",
+  width = "450px"
+)
+
+# Product
+renderUI({
+  org_data = product_data()
   selectInput(
     "org2_org",
-    label = "Organization:",
+    label = "Product:",
     choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
@@
 
-### Organization 3
+### Product 3
 
@@
   "org3_name",
-  label = "Organization Name:",
-  value = "Organization 3",
-  placeholder = "Enter Organization Name",
-  width = "450px"
-)
-
-# Organization
-renderUI({
-  org_data = organization_data()
+  label = "Product Name:",
+  value = "Product 3",
+  placeholder = "Enter Product Name",
+  width = "450px"
+)
+
+# Product
+renderUI({
+  org_data = product_data()
   selectInput(
     "org3_org",
-    label = "Organization:",
+    label = "Product:",
     choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
@@
 
-### Organization 4
+### Product 4
 
@@
   "org4_name",
-  label = "Organization Name:",
-  value = "Organization 4",
-  placeholder = "Enter Organization Name",
-  width = "450px"
-)
-
-# Organization
-renderUI({
-  org_data = organization_data()
+  label = "Product Name:",
+  value = "Product 4",
+  placeholder = "Enter Product Name",
+  width = "450px"
+)
+
+# Product
+renderUI({
+  org_data = product_data()
   selectInput(
     "org4_org",
-    label = "Organization:",
+    label = "Product:",
     choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
@@
 
-# Follow national news
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_national_news",
-    label = "Follow national news:",
-    choices = c("Rarely", "Once a week", "At least once a day"),
-    # selected = "At least once a day",
-    selected = ifelse(
-      sum(per_data[2:3,2]) == 0, "Rarely",
-      as.character(per_data[2:3,][which(per_data[2:3,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Follow international news
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_international_news",
-    label = "Follow international news:",
-    choices = c("Never", "Sometimes", "Always"),
-    # selected = "Always",
-    selected = ifelse(
-      sum(per_data[4:5,2]) == 0, "Never",
-      as.character(per_data[4:5,][which(per_data[4:5,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
 # Mediums to follow news
@@
 
-# Follow government and public affairs
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_follow_gov",
-    label = "Follow government & public affairs:",
-    choices = c("Not Often", "Often"),
-    # selected = "Often",
-    selected = ifelse(
-      sum(per_data[13,2]) == 0, "Not Often",
-      as.character(per_data[13,][which(per_data[13,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Traveled to a developing country
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_travel_developing",
-    label = "Travel to developing country:",
-    choices = c("Hasn't traveled to a developing country", "Traveled to a developing country"),
-    # selected = "Traveled to a developing country",
-    selected = ifelse(
-      sum(per_data[14,2]) == 0, "Hasn't traveled to a developing country",
-      as.character(per_data[14,][which(per_data[14,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Liberal to Conservative
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_political_pref",
-    label = "Political views from liberal to conservative:",
-    choices = c(
-      "Extremely liberal",
-      "Somewhat liberal",
-      "Slightly liberal",
-      "Moderate",
-      "Slightly conservative",
-      "Somewhat conservative",
-      "Extremely conservative"
-    ),
-    # selected = "Somewhat liberal",
-    selected = ifelse(
-      sum(per_data[15:20,2]) == 0, "Extremely liberal",
-      as.character(per_data[15:20,][which(per_data[15:20,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Trust in political institutions
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_institution_trust",
-    label = "Political institution trust from none to complete:",
-    choices = c(
-      "No trust at all in political institutions",
-      "Very little trust in political institutions",
-      "Little trust in political institutions",
-      "Neutral trust in political institutions",
-      "Some trust in political institutions",
-      "A lot of trust in political institutions",
-      "Complete trust in political institutions"
-    ),
-    # selected = "Complete trust in political institutions",
-    selected = ifelse(
-      sum(per_data[21:26,2]) == 0, "No trust at all in political institutions",
-      as.character(per_data[21:26,][which(per_data[21:26,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# People should be more charitable
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_others_charitable",
-    label = "People should be more charitable:",
-    choices = c(
-      "Strongly disagree",
-      "Disagree",
-      "Somewhat disagree",
-      "Neutral",
-      "Somewhat agree",
-      "Agree",
-      "Strongly agree"
-    ),
-    # selected = "Strongly agree",
-    selected = ifelse(
-      sum(per_data[27:32,2]) == 0, "Strongly disagree",
-      as.character(per_data[27:32,][which(per_data[27:32,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Religious attendance
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_worship_attendance",
-    label = "Worship service attendance:",
-    choices = c(
-      "Not sure",
-      "Rarely attend",
-      "Attend at least once a month"
-    ),
-    # selected = "Attend at least once a month",
-    selected = ifelse(
-      sum(per_data[33:34,2]) == 0, "Not sure",
-      as.character(per_data[33:34,][which(per_data[33:34,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Importance of religion
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_religion_importance",
-    label = "Importance of religion:",
-    choices = c("Not important", "Important"),
-    # selected = "Important",
-    selected = ifelse(
-      sum(per_data[35,2]) == 0, "Not important",
-      as.character(per_data[35,][which(per_data[35,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Religion
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_religion",
-    label = "Religion:",
-    choices = c(
-      "Catholic",
-      'Protestant',
-      'Christian Orthodox',
-      'Jewish',
-      'Muslim',
-      'Sikh',
-      'Hindu',
-      'Buddhist',
-      'Atheist',
-      'Other religion'
-    ),
-    # selected = 'Protestant',
-     selected = ifelse(
-      sum(per_data[36:44,2]) == 0, "Catholic",
-      as.character(per_data[36:44,][which(per_data[36:44,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Importance of trusting charities
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_charity_importance",
-    label = "Charity Importance:",
-    choices = c(
-      "Not at all important",
-      "Very unimportant",
-      "Somewhat unimportant",
-      "Neutral importance",
-      "Somewhat important",
-      "Very important",
-      "Essential"
-    ),
-    # selected = "Somewhat unimportant",
-    selected = ifelse(
-      sum(per_data[45:50,2]) == 0, "Not at all important",
-      as.character(per_data[45:50,][which(per_data[45:50,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Trust in charities
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_trust_in_charity",
-    label = "Charity Trust:",
-    choices = c(
-      "No trust at all in charities",
-      "Very little trust in charities",
-      "Little trust in charities",
-      "Neutral trust in charities",
-      "Some trust in charities",
-      "A lot of trust in charities",
-      "Complete trust in charities"
-    ),
-    # selected = "Complete trust in charities",
-     selected = ifelse(
-      sum(per_data[51:56,2]) == 0, "No trust at all in charities",
-      as.character(per_data[51:56,][which(per_data[51:56,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Donation frequency
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_donation_frequency",
-    label = "Donation Frequency:",
-    choices = c('Donate more than once a month, less than once a year', 'Donate at least once a month'),
-    # selected = "Donate at least once a month",
-    selected = ifelse(
-      sum(per_data[57,2]) == 0, "Donate more than once a month, less than once a year",
-      as.character(per_data[57,][which(per_data[57,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Donated last year
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_donation_amount",
-    label = "Donation Amount Last Year:",
-    choices = c(
-      '$1-$49',
-      '$50-$99',
-      '$100-$499',
-      '$500-$999',
-      '$1,000-$4,999',
-      '$5,000-$9,999',
-      '$10,000+'
-    ),
-    # selected = "$100-$499",
-    selected = ifelse(
-      sum(per_data[58:63,2]) == 0, "$1-$49",
-      as.character(per_data[58:63,][which(per_data[58:63,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Volunteered in past 12 months
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_volunteer_12",
-    label = "Volunteered in last 12 Months:",
-    choices = c("Haven't volunteered in past 12 months", "Volunteered in past 12 months"),
-    # selected = "Volunteered in past 12 months",
-    selected = ifelse(
-      sum(per_data[64,2]) == 0, "Haven't volunteered in past 12 months",
-      as.character(per_data[64,][which(per_data[64,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Volunteer frequency
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_volunteer_frequency",
-    label = "Volunteer Frequency:",
-    choices = c(
-      "Haven't volunteered in past 12 months",
-      "Rarely volunteer",
-      "Volunteer more than once a month, less than once a year",
-      "Volunteer at least once a month"
-    ),
-    # selected = "Volunteer at least once a month",
-    selected = ifelse(
-      sum(per_data[65:67,2]) == 0, "Haven't volunteered in past 12 months",
-      as.character(per_data[65:67,][which(per_data[65:67,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# History of activism
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_personal_activism",
-    label = "Personal Activism:",
-    choices = c('Not personally involved', 'Personally involved'),
-    # selected = "Personally involved",
-    selected = ifelse(
-      sum(per_data[68,2]) == 0, "Not personally involved",
-      as.character(per_data[68,][which(per_data[68,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# History of family activism
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_family_activism",
-    label = "Family Activism:",
-    choices = c('Family not involved', 'Family involved'),
-    # selected = "Family involved",
-    selected = ifelse(
-      sum(per_data[69,2]) == 0, "Family not involved",
-      as.character(per_data[69,][which(per_data[69,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Church or religious organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_religious_member",
-    label = "Church Membership:",
-    choices = c("Don't belong to church",'Inactive church member', 'Active church member'),
-    # selected = "Don't belong to church",
-    selected = ifelse(
-      sum(per_data[70:71,2]) == 0, "Don't belong to church",
-      as.character(per_data[70:71,][which(per_data[70:71,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Sport or recreational organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_sport_member",
-    label = "Sport or Recreational Membership:",
-    choices = c(
-      "Don't belong to sports or rec organization", 
-      'Inactive sports or rec organization member',
-      'Active sports or rec organization member'
-    ),
-    # selected = "Don't belong to sports or rec organization",
-    selected = ifelse(
-      sum(per_data[72:73,2]) == 0, "Don't belong to sports or rec organization",
-      as.character(per_data[72:73,][which(per_data[72:73,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Art, music, or educational organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_art_member",
-    label = "Art, Music, or Educational Membership:",
-    choices = c(
-      "Don't belong to educational organization",
-      'Inactive art, music, or educational organization member',
-      'Active art, music, or educational organization member'
-    ),
-    # selected = "Don't belong to educational organization",
-    selected = ifelse(
-      sum(per_data[74:75,2]) == 0, "Don't belong to educational organization",
-      as.character(per_data[74:75,][which(per_data[74:75,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Labor union
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_labor_member",
-    label = "Labor Union Membership:",
-    choices = c(
-      "Don't belong to union",
-      'Inactive union member', 
-      'Active union member'
-    ),
-    # selected = "Don't belong to union",
-    selected = ifelse(
-      sum(per_data[76:77,2]) == 0, "Don't belong to union",
-      as.character(per_data[76:77,][which(per_data[76:77,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Political party
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_political_member",
-    label = "Political Party Membership:",
-    choices = c(
-      "Don't belong to political party",
-      'Inactive political party member',
-      'Active political party member'
-    ),
-    # selected = "Active political party member",
-    selected = ifelse(
-      sum(per_data[78:79,2]) == 0, "Don't belong to political party",
-      as.character(per_data[78:79,][which(per_data[78:79,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Environmental organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_environmental_member",
-    label = "Environmental Organization Membership:",
-    choices = c(
-      "Don't belong to environmental organization",
-      'Inactive environmental organization member',
-      'Active environmental organization member'
-    ),
-    # selected = "Don't belong to environmental organization",
-    selected = ifelse(
-      sum(per_data[80:81,2]) == 0, "Don't belong to environmental organization",
-      as.character(per_data[80:81,][which(per_data[80:81,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Professional association
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_professional_member",
-    label = "Professional Association Membership:",
-    choices = c(
-      "Don't belong to professional association",
-      'Inactive professional association member',
-      'Active professional association member'
-    ),
-    # selected = "Don't belong to professional association",
-    selected = ifelse(
-      sum(per_data[82:83,2]) == 0, "Don't belong to professional association",
-      as.character(per_data[82:83,][which(per_data[82:83,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Humanitarian or charitable organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_humanitarian_member",
-    label = "Humanitarian or Charitable Organization Membership:",
-    choices = c(
-      "Don't belong to humanitarian or charitable organization",
-      'Inactive humanitarian or charitable organization member',
-      'Active humanitarian or charitable organization member'
-    ),
-    # selected = "Active humanitarian or charitable organization member",
-    selected = ifelse(
-      sum(per_data[84:85,2]) == 0, "Don't belong to humanitarian or charitable organization",
-      as.character(per_data[84:85,][which(per_data[84:85,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Consumer organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_consumer_member",
-    label = "Consumer Organization Membership:",
-    choices = c(
-      "Don't belong to consumer organization",
-      'Inactive consumer organization member',
-      'Active consumer organization member'
-    ),
-    # selected = "Don't belong to consumer organization",
-    selected = ifelse(
-      sum(per_data[86:87,2]) == 0, "Don't belong to consumer organization",
-      as.character(per_data[86:87,][which(per_data[86:87,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Other organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per1_other_member",
-    label = "Other Organization Membership:",
-    choices = c(
-      "Don't belong to another organization",
-      'Inactive member in another organization',
-      'Active member in another organization'
-    ),
-    # selected = "Don't belong to another organization",
-    selected = ifelse(
-      sum(per_data[88:89,2]) == 0, "Don't belong to another organization",
-      as.character(per_data[88:89,][which(per_data[88:89,2] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
 # Gender
@@
 
-# Follow national news
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_national_news",
-    label = "Follow national news:",
-    choices = c("Rarely", "Once a week", "At least once a day"),
-    # selected = "At least once a day",
-    selected = ifelse(
-      sum(per_data[2:3,3]) == 0, "Rarely",
-      as.character(per_data[2:3,][which(per_data[2:3,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Follow international news
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_international_news",
-    label = "Follow international news:",
-    choices = c("Never", "Sometimes", "Always"),
-    # selected = "Always",
-    selected = ifelse(
-      sum(per_data[4:5,3]) == 0, "Never",
-      as.character(per_data[4:5,][which(per_data[4:5,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
 # Mediums to follow news
@@
 
-# Follow government and public affairs
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_follow_gov",
-    label = "Follow government & public affairs:",
-    choices = c("Not Often", "Often"),
-    # selected = "Often",
-    selected = ifelse(
-      sum(per_data[13,3]) == 0, "Not Often",
-      as.character(per_data[13,][which(per_data[13,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Traveled to a developing country
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_travel_developing",
-    label = "Travel to developing country:",
-    choices = c("Hasn't traveled to a developing country", "Traveled to a developing country"),
-    # selected = "Traveled to a developing country",
-    selected = ifelse(
-      sum(per_data[14,3]) == 0, "Hasn't traveled to a developing country",
-      as.character(per_data[14,][which(per_data[14,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Liberal to Conservative
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_political_pref",
-    label = "Political views from liberal to conservative:",
-    choices = c(
-      "Extremely liberal",
-      "Somewhat liberal",
-      "Slightly liberal",
-      "Moderate",
-      "Slightly conservative",
-      "Somewhat conservative",
-      "Extremely conservative"
-    ),
-    # selected = "Somewhat liberal",
-    selected = ifelse(
-      sum(per_data[15:20,3]) == 0, "Extremely liberal",
-      as.character(per_data[15:20,][which(per_data[15:20,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Trust in political institutions
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_institution_trust",
-    label = "Political institution trust from none to complete:",
-    choices = c(
-      "No trust at all in political institutions",
-      "Very little trust in political institutions",
-      "Little trust in political institutions",
-      "Neutral trust in political institutions",
-      "Some trust in political institutions",
-      "A lot of trust in political institutions",
-      "Complete trust in political institutions"
-    ),
-    # selected = "Complete trust in political institutions",
-    selected = ifelse(
-      sum(per_data[21:26,3]) == 0, "No trust at all in political institutions",
-      as.character(per_data[21:26,][which(per_data[21:26,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# People should be more charitable
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_others_charitable",
-    label = "People should be more charitable:",
-    choices = c(
-      "Strongly disagree",
-      "Disagree",
-      "Somewhat disagree",
-      "Neutral",
-      "Somewhat agree",
-      "Agree",
-      "Strongly agree"
-    ),
-    # selected = "Strongly agree",
-    selected = ifelse(
-      sum(per_data[27:32,3]) == 0, "Strongly disagree",
-      as.character(per_data[27:32,][which(per_data[27:32,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Religious attendance
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_worship_attendance",
-    label = "Worship service attendance:",
-    choices = c(
-      "Not sure",
-      "Rarely attend",
-      "Attend at least once a month"
-    ),
-    # selected = "Attend at least once a month",
-    selected = ifelse(
-      sum(per_data[33:34,3]) == 0, "Not sure",
-      as.character(per_data[33:34,][which(per_data[33:34,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Importance of religion
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_religion_importance",
-    label = "Importance of religion:",
-    choices = c("Not important", "Important"),
-    # selected = "Important",
-    selected = ifelse(
-      sum(per_data[35,3]) == 0, "Not important",
-      as.character(per_data[35,][which(per_data[35,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Religion
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_religion",
-    label = "Religion:",
-    choices = c(
-      'Catholic',
-      'Protestant',
-      'Christian Orthodox',
-      'Jewish',
-      'Muslim',
-      'Sikh',
-      'Hindu',
-      'Buddhist',
-      'Atheist',
-      'Other religion'
-    ),
-    # selected = 'Protestant',
-    selected = ifelse(
-      sum(per_data[36:44,3]) == 0, "Catholic",
-      as.character(per_data[36:44,][which(per_data[36:44,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Importance of trusting charities
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_charity_importance",
-    label = "Charity Importance:",
-    choices = c(
-      "Not at all important",
-      "Very unimportant",
-      "Somewhat unimportant",
-      "Neutral importance",
-      "Somewhat important",
-      "Very important",
-      "Essential"
-    ),
-    # selected = "Somewhat unimportant",
-    selected = ifelse(
-      sum(per_data[45:50,3]) == 0, "Not at all important",
-      as.character(per_data[45:50,][which(per_data[45:50,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Trust in charities
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_trust_in_charity",
-    label = "Charity Trust:",
-    choices = c(
-      "No trust at all in charities",
-      "Very little trust in charities",
-      "Little trust in charities",
-      "Neutral trust in charities",
-      "Some trust in charities",
-      "A lot of trust in charities",
-      "Complete trust in charities"
-    ),
-    # selected = "Complete trust in charities",
-    selected = ifelse(
-      sum(per_data[51:56,3]) == 0, "No trust at all in charities",
-      as.character(per_data[51:56,][which(per_data[51:56,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Donation frequency
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_donation_frequency",
-    label = "Donation Frequency:",
-    choices = c('Donate more than once a month, less than once a year', 'Donate at least once a month'),
-    # selected = "Donate at least once a month",
-    selected = ifelse(
-      sum(per_data[57,3]) == 0, "Donate more than once a month, less than once a year",
-      as.character(per_data[57,][which(per_data[57,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Donated last year
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_donation_amount",
-    label = "Donation Amount Last Year:",
-    choices = c(
-      '$1-$49',
-      '$50-$99',
-      '$100-$499',
-      '$500-$999',
-      '$1,000-$4,999',
-      '$5,000-$9,999',
-      '$10,000+'
-    ),
-    # selected = "$100-$499",
-    selected = ifelse(
-      sum(per_data[58:63,3]) == 0, "$1-$49",
-      as.character(per_data[58:63,][which(per_data[58:63,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Volunteered in past 12 months
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_volunteer_12",
-    label = "Volunteered in last 12 Months:",
-    choices = c("Haven't volunteered in past 12 months", "Volunteered in past 12 months"),
-    # selected = "Volunteered in past 12 months",
-    selected = ifelse(
-      sum(per_data[64,3]) == 0, "Haven't volunteered in past 12 months",
-      as.character(per_data[64,][which(per_data[64,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Volunteer frequency
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_volunteer_frequency",
-    label = "Volunteer Frequency:",
-    choices = c(
-      "Haven't volunteered in past 12 months",
-      "Rarely volunteer",
-      "Volunteer more than once a month, less than once a year",
-      "Volunteer at least once a month"
-    ),
-    # selected = "Volunteer at least once a month",
-    selected = ifelse(
-      sum(per_data[65:67,3]) == 0, "Haven't volunteered in past 12 months",
-      as.character(per_data[65:67,][which(per_data[65:67,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# History of activism
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_personal_activism",
-    label = "Personal Activism:",
-    choices = c('Not personally involved', 'Personally involved'),
-    # selected = "Personally involved",
-    selected = ifelse(
-      sum(per_data[68,3]) == 0, "Not personally involved",
-      as.character(per_data[68,][which(per_data[68,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# History of family activism
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_family_activism",
-    label = "Family Activism:",
-    choices = c('Family not involved', 'Family involved'),
-    # selected = "Family involved",
-    selected = ifelse(
-      sum(per_data[69,3]) == 0, "Family not involved",
-      as.character(per_data[69,][which(per_data[69,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Church or religious organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_religious_member",
-    label = "Church Membership:",
-    choices = c("Don't belong to church",'Inactive church member', 'Active church member'),
-    # selected = "Don't belong to church",
-    selected = ifelse(
-      sum(per_data[70:71,3]) == 0, "Don't belong to church",
-      as.character(per_data[70:71,][which(per_data[70:71,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Sport or recreational organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_sport_member",
-    label = "Sport or Recreational Membership:",
-    choices = c(
-      "Don't belong to sports or rec organization", 
-      'Inactive sports or rec organization member',
-      'Active sports or rec organization member'
-    ),
-    # selected = "Don't belong to sports or rec organization",
-    selected = ifelse(
-      sum(per_data[72:73,3]) == 0, "Don't belong to sports or rec organization",
-      as.character(per_data[72:73,][which(per_data[72:73,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Art, music, or educational organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_art_member",
-    label = "Art, Music, or Educational Membership:",
-    choices = c(
-      "Don't belong to educational organization",
-      'Inactive art, music, or educational organization member',
-      'Active art, music, or educational organization member'
-    ),
-    # selected = "Don't belong to educational organization",
-    selected = ifelse(
-      sum(per_data[74:75,3]) == 0, "Don't belong to educational organization",
-      as.character(per_data[74:75,][which(per_data[74:75,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Labor union
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_labor_member",
-    label = "Labor Union Membership:",
-    choices = c("Don't belong to union", 'Inactive union member', 'Active union member'),
-    # selected = "Don't belong to union",
-    selected = ifelse(
-      sum(per_data[76:77,3]) == 0, "Don't belong to union",
-      as.character(per_data[76:77,][which(per_data[76:77,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Political party
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_political_member",
-    label = "Political Party Membership:",
-    choices = c(
-      "Don't belong to political party",
-      'Inactive political party member',
-      'Active political party member'
-    ),
-    # selected = "Active political party member",
-    selected = ifelse(
-      sum(per_data[78:79,3]) == 0, "Don't belong to political party",
-      as.character(per_data[78:79,][which(per_data[78:79,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Environmental organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_environmental_member",
-    label = "Environmental Organization Membership:",
-    choices = c(
-      "Don't belong to environmental organization",
-      'Inactive environmental organization member',
-      'Active environmental organization member'
-    ),
-    # selected = "Don't belong to environmental organization",
-    selected = ifelse(
-      sum(per_data[80:81,3]) == 0, "Don't belong to environmental organization",
-      as.character(per_data[80:81,][which(per_data[80:81,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Professional association
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_professional_member",
-    label = "Professional Association Membership:",
-    choices = c(
-      "Don't belong to professional association",
-      'Inactive professional association member',
-      'Active professional association member'
-    ),
-    # selected = "Don't belong to professional association",
-    selected = ifelse(
-      sum(per_data[82:83,3]) == 0, "Don't belong to professional association",
-      as.character(per_data[82:83,][which(per_data[82:83,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Humanitarian or charitable organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_humanitarian_member",
-    label = "Humanitarian or Charitable Organization Membership:",
-    choices = c(
-      "Don't belong to humanitarian or charitable organization",
-      'Inactive humanitarian or charitable organization member',
-      'Active humanitarian or charitable organization member'
-    ),
-    # selected = "Active humanitarian or charitable organization member",
-    selected = ifelse(
-      sum(per_data[84:85,3]) == 0, "Don't belong to humanitarian or charitable organization",
-      as.character(per_data[84:85,][which(per_data[84:85,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Consumer organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_consumer_member",
-    label = "Consumer Organization Membership:",
-    choices = c(
-      "Don't belong to consumer organization",
-      'Inactive consumer organization member',
-      'Active consumer organization member'
-    ),
-    # selected = "Don't belong to consumer organization",
-    selected = ifelse(
-      sum(per_data[86:87,3]) == 0, "Don't belong to consumer organization",
-      as.character(per_data[86:87,][which(per_data[86:87,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Other organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per2_other_member",
-    label = "Other Organization Membership:",
-    choices = c(
-      "Don't belong to another organization",
-      'Inactive member in another organization',
-      'Active member in another organization'
-    ),
-    # selected = "Don't belong to another organization",
-    selected = ifelse(
-      sum(per_data[88:89,3]) == 0, "Don't belong to another organization",
-      as.character(per_data[88:89,][which(per_data[88:89,3] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
 # Gender
@@
 )
-
-# Follow national news
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_national_news",
-    label = "Follow national news:",
-    choices = c("Rarely", "Once a week", "At least once a day"),
-    # selected = "At least once a day",
-    selected = ifelse(
-      sum(per_data[2:3,4]) == 0, "Rarely",
-      as.character(per_data[2:3,][which(per_data[2:3,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Follow international news
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_international_news",
-    label = "Follow international news:",
-    choices = c("Never", "Sometimes", "Always"),
-    # selected = "Always",
-    selected = ifelse(
-      sum(per_data[4:5,4]) == 0, "Never",
-      as.character(per_data[4:5,][which(per_data[4:5,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
 # Mediums to follow news
@@
     selected = deframe(per_data[6:12,][which(per_data[6:12,4] == 1), 1]),
-    width = "450px"
-  )
-})
-
-# Follow government and public affairs
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_follow_gov",
-    label = "Follow government & public affairs:",
-    choices = c("Not Often", "Often"),
-    # selected = "Often",
-    selected = ifelse(
-      sum(per_data[13,4]) == 0, "Not Often",
-      as.character(per_data[13,][which(per_data[13,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Traveled to a developing country
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_travel_developing",
-    label = "Travel to developing country:",
-    choices = c("Hasn't traveled to a developing country", "Traveled to a developing country"),
-    # selected = "Traveled to a developing country",
-    selected = ifelse(
-      sum(per_data[14,4]) == 0, "Hasn't traveled to a developing country",
-      as.character(per_data[14,][which(per_data[14,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Liberal to Conservative
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_political_pref",
-    label = "Political views from liberal to conservative:",
-    choices = c(
-      "Extremely liberal",
-      "Somewhat liberal",
-      "Slightly liberal",
-      "Moderate",
-      "Slightly conservative",
-      "Somewhat conservative",
-      "Extremely conservative"
-    ),
-    # selected = "Somewhat liberal",
-    selected = ifelse(
-      sum(per_data[15:20,4]) == 0, "Extremely liberal",
-      as.character(per_data[15:20,][which(per_data[15:20,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Trust in political institutions
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_institution_trust",
-    label = "Political institution trust from none to complete:",
-    choices = c(
-      "No trust at all in political institutions",
-      "Very little trust in political institutions",
-      "Little trust in political institutions",
-      "Neutral trust in political institutions",
-      "Some trust in political institutions",
-      "A lot of trust in political institutions",
-      "Complete trust in political institutions"
-    ),
-    # selected = "Complete trust in political institutions",
-    selected = ifelse(
-      sum(per_data[21:26,4]) == 0, "No trust at all in political institutions",
-      as.character(per_data[21:26,][which(per_data[21:26,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# People should be more charitable
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_others_charitable",
-    label = "People should be more charitable:",
-    choices = c(
-      "Strongly disagree",
-      "Disagree",
-      "Somewhat disagree",
-      "Neutral",
-      "Somewhat agree",
-      "Agree",
-      "Strongly agree"
-    ),
-    # selected = "Strongly agree",
-    selected = ifelse(
-      sum(per_data[27:32,4]) == 0, "Strongly disagree",
-      as.character(per_data[27:32,][which(per_data[27:32,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Religious attendance
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_worship_attendance",
-    label = "Worship service attendance:",
-    choices = c(
-      "Not sure",
-      "Rarely attend",
-      "Attend at least once a month"
-    ),
-    # selected = "Attend at least once a month",
-    selected = ifelse(
-      sum(per_data[33:34,4]) == 0, "Not sure",
-      as.character(per_data[33:34,][which(per_data[33:34,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Importance of religion
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_religion_importance",
-    label = "Importance of religion:",
-    choices = c("Not important", "Important"),
-    # selected = "Important",
-    selected = ifelse(
-      sum(per_data[35,4]) == 0, "Not important",
-      as.character(per_data[35,][which(per_data[35,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Religion
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_religion",
-    label = "Religion:",
-    choices = c(
-      'Catholic',
-      'Protestant',
-      'Christian Orthodox',
-      'Jewish',
-      'Muslim',
-      'Sikh',
-      'Hindu',
-      'Buddhist',
-      'Atheist',
-      'Other religion'
-    ),
-    # selected = 'Protestant',
-    selected = ifelse(
-      sum(per_data[36:44,4]) == 0, "Catholic",
-      as.character(per_data[36:44,][which(per_data[36:44,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Importance of trusting charities
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_charity_importance",
-    label = "Charity Importance:",
-    choices = c(
-      "Not at all important",
-      "Very unimportant",
-      "Somewhat unimportant",
-      "Neutral importance",
-      "Somewhat important",
-      "Very important",
-      "Essential"
-    ),
-    # selected = "Somewhat unimportant",
-    selected = ifelse(
-      sum(per_data[45:50,4]) == 0, "Not at all important",
-      as.character(per_data[45:50,][which(per_data[45:50,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Trust in charities
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_trust_in_charity",
-    label = "Charity Trust:",
-    choices = c(
-      "No trust at all in charities",
-      "Very little trust in charities",
-      "Little trust in charities",
-      "Neutral trust in charities",
-      "Some trust in charities",
-      "A lot of trust in charities",
-      "Complete trust in charities"
-    ),
-    # selected = "Complete trust in charities",
-    selected = ifelse(
-      sum(per_data[51:56,4]) == 0, "No trust at all in charities",
-      as.character(per_data[51:56,][which(per_data[51:56,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Donation frequency
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_donation_frequency",
-    label = "Donation Frequency:",
-    choices = c('Donate more than once a month, less than once a year', 'Donate at least once a month'),
-    # selected = "Donate at least once a month",
-    selected = ifelse(
-      sum(per_data[57,4]) == 0, "Donate more than once a month, less than once a year",
-      as.character(per_data[57,][which(per_data[57,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Donated last year
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_donation_amount",
-    label = "Donation Amount Last Year:",
-    choices = c(
-      '$1-$49',
-      '$50-$99',
-      '$100-$499',
-      '$500-$999',
-      '$1,000-$4,999',
-      '$5,000-$9,999',
-      '$10,000+'
-    ),
-    # selected = "$100-$499",
-    selected = ifelse(
-      sum(per_data[58:63,4]) == 0, "$1-$49",
-      as.character(per_data[58:63,][which(per_data[58:63,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Volunteered in past 12 months
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_volunteer_12",
-    label = "Volunteered in last 12 Months:",
-    choices = c("Haven't volunteered in past 12 months", "Volunteered in past 12 months"),
-    # selected = "Volunteered in past 12 months",
-    selected = ifelse(
-      sum(per_data[64,4]) == 0, "Haven't volunteered in past 12 months",
-      as.character(per_data[64,][which(per_data[64,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Volunteer frequency
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_volunteer_frequency",
-    label = "Volunteer Frequency:",
-    choices = c(
-      "Haven't volunteered in past 12 months",
-      "Rarely volunteer",
-      "Volunteer more than once a month, less than once a year",
-      "Volunteer at least once a month"
-    ),
-    # selected = "Volunteer at least once a month",
-    selected = ifelse(
-      sum(per_data[65:67,4]) == 0, "Haven't volunteered in past 12 months",
-      as.character(per_data[65:67,][which(per_data[65:67,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# History of activism
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_personal_activism",
-    label = "Personal Activism:",
-    choices = c('Not personally involved', 'Personally involved'),
-    # selected = "Personally involved",
-    selected = ifelse(
-      sum(per_data[68,4]) == 0, "Not personally involved",
-      as.character(per_data[68,][which(per_data[68,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# History of family activism
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_family_activism",
-    label = "Family Activism:",
-    choices = c('Family not involved', 'Family involved'),
-    # selected = "Family involved",
-    selected = ifelse(
-      sum(per_data[69,4]) == 0, "Family not involved",
-      as.character(per_data[69,][which(per_data[69,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Church or religious organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_religious_member",
-    label = "Church Membership:",
-    choices = c("Don't belong to church",'Inactive church member', 'Active church member'),
-    # selected = "Don't belong to church",
-    selected = ifelse(
-      sum(per_data[70:71,4]) == 0, "Don't belong to church",
-      as.character(per_data[70:71,][which(per_data[70:71,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Sport or recreational organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_sport_member",
-    label = "Sport or Recreational Membership:",
-    choices = c(
-      "Don't belong to sports or rec organization", 
-      'Inactive sports or rec organization member',
-      'Active sports or rec organization member'
-    ),
-    # selected = "Don't belong to sports or rec organization",
-    selected = ifelse(
-      sum(per_data[72:73,4]) == 0, "Don't belong to sports or rec organization",
-      as.character(per_data[72:73,][which(per_data[72:73,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Art, music, or educational organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_art_member",
-    label = "Art, Music, or Educational Membership:",
-    choices = c(
-      "Don't belong to educational organization",
-      'Inactive art, music, or educational organization member',
-      'Active art, music, or educational organization member'
-    ),
-    # selected = "Don't belong to educational organization",
-    selected = ifelse(
-      sum(per_data[74:75,4]) == 0, "Don't belong to educational organization",
-      as.character(per_data[74:75,][which(per_data[74:75,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Labor union
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_labor_member",
-    label = "Labor Union Membership:",
-    choices = c("Don't belong to union", 'Inactive union member', 'Active union member'),
-    # selected = "Don't belong to union",
-    selected = ifelse(
-      sum(per_data[76:77,4]) == 0, "Don't belong to union",
-      as.character(per_data[76:77,][which(per_data[76:77,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Political party
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_political_member",
-    label = "Political Party Membership:",
-    choices = c(
-      "Don't belong to political party",
-      'Inactive political party member',
-      'Active political party member'
-    ),
-    # selected = "Active political party member",
-    selected = ifelse(
-      sum(per_data[78:79,4]) == 0, "Don't belong to political party",
-      as.character(per_data[78:79,][which(per_data[78:79,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Environmental organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_environmental_member",
-    label = "Environmental Organization Membership:",
-    choices = c(
-      "Don't belong to environmental organization",
-      'Inactive environmental organization member',
-      'Active environmental organization member'
-    ),
-    # selected = "Don't belong to environmental organization",
-    selected = ifelse(
-      sum(per_data[80:81,4]) == 0, "Don't belong to environmental organization",
-      as.character(per_data[80:81,][which(per_data[80:81,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Professional association
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_professional_member",
-    label = "Professional Association Membership:",
-    choices = c(
-      "Don't belong to professional association",
-      'Inactive professional association member',
-      'Active professional association member'
-    ),
-    # selected = "Don't belong to professional association",
-    selected = ifelse(
-      sum(per_data[82:83,4]) == 0, "Don't belong to professional association",
-      as.character(per_data[82:83,][which(per_data[82:83,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Humanitarian or charitable organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_humanitarian_member",
-    label = "Humanitarian or Charitable Organization Membership:",
-    choices = c(
-      "Don't belong to humanitarian or charitable organization",
-      'Inactive humanitarian or charitable organization member',
-      'Active humanitarian or charitable organization member'
-    ),
-    # selected = "Active humanitarian or charitable organization member",
-    selected = ifelse(
-      sum(per_data[84:85,4]) == 0, "Don't belong to humanitarian or charitable organization",
-      as.character(per_data[84:85,][which(per_data[84:85,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Consumer organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_consumer_member",
-    label = "Consumer Organization Membership:",
-    choices = c(
-      "Don't belong to consumer organization",
-      'Inactive consumer organization member',
-      'Active consumer organization member'
-    ),
-    # selected = "Don't belong to consumer organization",
-    selected = ifelse(
-      sum(per_data[86:87,4]) == 0, "Don't belong to consumer organization",
-      as.character(per_data[86:87,][which(per_data[86:87,4] == 1), 1])
-    ),
-    width = "450px"
-  )
-})
-
-# Other organization
-renderUI({
-  per_data = persona_data()
-  selectInput(
-    "per3_other_member",
-    label = "Other Organization Membership:",
-    choices = c(
-      "Don't belong to another organization",
-      'Inactive member in another organization',
-      'Active member in another organization'
-    ),
-    # selected = "Don't belong to another organization",
-    selected = ifelse(
-      sum(per_data[88:89,4]) == 0, "Don't belong to another organization",
-      as.character(per_data[88:89,][which(per_data[88:89,4] == 1), 1])
-    ),
     width = "450px"

### 2020-12-18 dashboard_example.Rmd
reformating for product and segments instead of org and persona

@@
   )
-per_default <- read_csv(
+seg_default <- read_csv(
     here::here('analysis', 'output', 'configurations', 'per_data_default.csv')
@@
 # Assign level labels
-org_table <- data.frame(
+prod_table <- data.frame(
   levels = c(
@@
   # prod 1
-  org_table$org1_value <- 0
-  org_table$org1_value[org_table$levels %in% input$org1_org] <- 1
-  org_table$org1_value[org_table$levels %in% input$org1_issue] <- 1
-  org_table$org1_value[org_table$levels %in% input$org1_fin_trans] <- 1
-  org_table$org1_value[org_table$levels %in% input$org1_fin_account] <- 1
-  org_table$org1_value[org_table$levels %in% input$org1_funding] <- 1
-  org_table$org1_value[org_table$levels %in% input$org1_host_gov] <- 1
+  prod_table$prod1_value <- 0
+  prod_table$prod1_value[prod_table$levels %in% input$prod1_prod] <- 1
+  prod_table$prod1_value[prod_table$levels %in% input$prod1_issue] <- 1
+  prod_table$prod1_value[prod_table$levels %in% input$prod1_fin_trans] <- 1
+  prod_table$prod1_value[prod_table$levels %in% input$prod1_fin_account] <- 1
+  prod_table$prod1_value[prod_table$levels %in% input$prod1_funding] <- 1
+  prod_table$prod1_value[prod_table$levels %in% input$prod1_host_gov] <- 1
 
   # prod 2
-  org_table$org2_value <- 0
-  org_table$org2_value[org_table$levels %in% input$org2_org] <- 1
-  org_table$org2_value[org_table$levels %in% input$org2_issue] <- 1
-  org_table$org2_value[org_table$levels %in% input$org2_fin_trans] <- 1
-  org_table$org2_value[org_table$levels %in% input$org2_fin_account] <- 1
-  org_table$org2_value[org_table$levels %in% input$org2_funding] <- 1
-  org_table$org2_value[org_table$levels %in% input$org2_host_gov] <- 1
+  prod_table$prod2_value <- 0
+  prod_table$prod2_value[prod_table$levels %in% input$prod2_prod] <- 1
+  prod_table$prod2_value[prod_table$levels %in% input$prod2_issue] <- 1
+  prod_table$prod2_value[prod_table$levels %in% input$prod2_fin_trans] <- 1
+  prod_table$prod2_value[prod_table$levels %in% input$prod2_fin_account] <- 1
+  prod_table$prod2_value[prod_table$levels %in% input$prod2_funding] <- 1
+  prod_table$prod2_value[prod_table$levels %in% input$prod2_host_gov] <- 1
 
   # prod 3
-  org_table$org3_value <- 0
-  org_table$org3_value[org_table$levels %in% input$org3_org] <- 1
-  org_table$org3_value[org_table$levels %in% input$org3_issue] <- 1
-  org_table$org3_value[org_table$levels %in% input$org3_fin_trans] <- 1
-  org_table$org3_value[org_table$levels %in% input$org3_fin_account] <- 1
-  org_table$org3_value[org_table$levels %in% input$org3_funding] <- 1
-  org_table$org3_value[org_table$levels %in% input$org3_host_gov] <- 1
+  prod_table$prod3_value <- 0
+  prod_table$prod3_value[prod_table$levels %in% input$prod3_prod] <- 1
+  prod_table$prod3_value[prod_table$levels %in% input$prod3_issue] <- 1
+  prod_table$prod3_value[prod_table$levels %in% input$prod3_fin_trans] <- 1
+  prod_table$prod3_value[prod_table$levels %in% input$prod3_fin_account] <- 1
+  prod_table$prod3_value[prod_table$levels %in% input$prod3_funding] <- 1
+  prod_table$prod3_value[prod_table$levels %in% input$prod3_host_gov] <- 1
 
   # prod 4
-  org_table$org4_value <- 0
-  org_table$org4_value[org_table$levels %in% input$org4_org] <- 1
-  org_table$org4_value[org_table$levels %in% input$org4_issue] <- 1
-  org_table$org4_value[org_table$levels %in% input$org4_fin_trans] <- 1
-  org_table$org4_value[org_table$levels %in% input$org4_fin_account] <- 1
-  org_table$org4_value[org_table$levels %in% input$org4_funding] <- 1
-  org_table$org4_value[org_table$levels %in% input$org4_host_gov] <- 1
-  org_table
+  prod_table$prod4_value <- 0
+  prod_table$prod4_value[prod_table$levels %in% input$prod4_prod] <- 1
+  prod_table$prod4_value[prod_table$levels %in% input$prod4_issue] <- 1
+  prod_table$prod4_value[prod_table$levels %in% input$prod4_fin_trans] <- 1
+  prod_table$prod4_value[prod_table$levels %in% input$prod4_fin_account] <- 1
+  prod_table$prod4_value[prod_table$levels %in% input$prod4_funding] <- 1
+  prod_table$prod4_value[prod_table$levels %in% input$prod4_host_gov] <- 1
+  prod_table
 })
@@
 # Assign covariate labels
-per_table <- data.frame(
+seg_table <- data.frame(
   levels = c(
@@
 ## Test to subset the data
-per_join <- per_default %>% inner_join(per_table, by = "levels")
+seg_join <- seg_default %>% inner_join(seg_table, by = "levels")
 
 # Persona configuration reactive element
-per_reactive <- reactive({
+seg_reactive <- reactive({
   # Persona 1
-  per_table$per1_value <- 0
-  per_table$per1_value[per_table$levels == 'Intercept'] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_news_medium] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_gender] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_marital_status] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_education] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_income] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_race] <- 1
-  per_table$per1_value[per_table$levels %in% input$per1_age] <- 1
+  seg_table$per1_value <- 0
+  seg_table$per1_value[seg_table$levels == 'Intercept'] <- 1
+  seg_table$per1_value[seg_table$levels %in% input$per1_news_medium] <- 1
+  seg_table$per1_value[seg_table$levels %in% input$per1_gender] <- 1
+  seg_table$per1_value[seg_table$levels %in% input$per1_marital_status] <- 1
+  seg_table$per1_value[seg_table$levels %in% input$per1_education] <- 1
+  seg_table$per1_value[seg_table$levels %in% input$per1_income] <- 1
+  seg_table$per1_value[seg_table$levels %in% input$per1_race] <- 1
+  seg_table$per1_value[seg_table$levels %in% input$per1_age] <- 1
 
   # Persona 2
-  per_table$per2_value <- 0
-  per_table$per2_value[per_table$levels == 'Intercept'] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_gender] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_marital_status] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_education] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_income] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_race] <- 1
-  per_table$per2_value[per_table$levels %in% input$per2_age] <- 1
+  seg_table$per2_value <- 0
+  seg_table$per2_value[seg_table$levels == 'Intercept'] <- 1
+  seg_table$per2_value[seg_table$levels %in% input$per2_gender] <- 1
+  seg_table$per2_value[seg_table$levels %in% input$per2_marital_status] <- 1
+  seg_table$per2_value[seg_table$levels %in% input$per2_education] <- 1
+  seg_table$per2_value[seg_table$levels %in% input$per2_income] <- 1
+  seg_table$per2_value[seg_table$levels %in% input$per2_race] <- 1
+  seg_table$per2_value[seg_table$levels %in% input$per2_age] <- 1
 
   # Persona 3
-  per_table$per3_value <- 0
-  per_table$per3_value[per_table$levels == 'Intercept'] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_news_medium] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_gender] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_marital_status] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_education] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_income] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_race] <- 1
-  per_table$per3_value[per_table$levels %in% input$per3_age] <- 1
-  per_table
+  seg_table$per3_value <- 0
+  seg_table$per3_value[seg_table$levels == 'Intercept'] <- 1
+  seg_table$per3_value[seg_table$levels %in% input$per3_news_medium] <- 1
+  seg_table$per3_value[seg_table$levels %in% input$per3_gender] <- 1
+  seg_table$per3_value[seg_table$levels %in% input$per3_marital_status] <- 1
+  seg_table$per3_value[seg_table$levels %in% input$per3_education] <- 1
+  seg_table$per3_value[seg_table$levels %in% input$per3_income] <- 1
+  seg_table$per3_value[seg_table$levels %in% input$per3_race] <- 1
+  seg_table$per3_value[seg_table$levels %in% input$per3_age] <- 1
+  seg_table
 })
@@
 renderPlotly({
-  org_choice = org_reactive()
-  per_choice = per_reactive()
-
-  # Persona 1 predicted betas
-  per1_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,2])
-
-  # Persona 1 expected utilities
-  per1_org1_exp <- exp(t(org_choice[,2]) %*% as.matrix(per1_betas))
-  per1_org2_exp <- exp(t(org_choice[,3]) %*% as.matrix(per1_betas))
-  per1_org3_exp <- exp(t(org_choice[,4]) %*% as.matrix(per1_betas))
-  per1_org4_exp <- exp(t(org_choice[,5]) %*% as.matrix(per1_betas))
-
-  # Persona 1 market shares
-  per1_share_denom <- sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)
-  per1_org1_share <- 100 * (per1_org1_exp / per1_share_denom)
-  per1_org2_share <- 100 * (per1_org2_exp / per1_share_denom)
-  per1_org3_share <- 100 * (per1_org3_exp / per1_share_denom)
-  per1_org4_share <- 100 * (per1_org4_exp / per1_share_denom)
-
-  # Persona 2 predicted betas
+  prod_choice = prod_reactive()
+  seg_choice = seg_reactive()
+
+  # Segment 1 predicted betas
+  seg1_betas <- as.matrix(gammas) %*% as.matrix(seg_choice[,2])
+
+  # Segment 1 expected utilities
+  seg1_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(seg1_betas))
+  seg1_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(seg1_betas))
+  seg1_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(seg1_betas))
+  seg1_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(seg1_betas))
+
+  # Segment 1 market shares
+  per1_share_denom <- sum(per1_prod1_exp, per1_prod2_exp, per1_prod3_exp, per1_prod4_exp)
+  per1_prod1_share <- 100 * (per1_prod1_exp / per1_share_denom)
+  per1_prod2_share <- 100 * (per1_prod2_exp / per1_share_denom)
+  per1_prod3_share <- 100 * (per1_prod3_exp / per1_share_denom)
+  per1_prod4_share <- 100 * (per1_prod4_exp / per1_share_denom)
+
+  # Segment 2 predicted betas
   per2_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,3])
 
-  # Persona 2 expected utilities
-  per2_org1_exp <- exp(t(org_choice[,2]) %*% as.matrix(per2_betas))
-  per2_org2_exp <- exp(t(org_choice[,3]) %*% as.matrix(per2_betas))
-  per2_org3_exp <- exp(t(org_choice[,4]) %*% as.matrix(per2_betas))
-  per2_org4_exp <- exp(t(org_choice[,5]) %*% as.matrix(per2_betas))
-
-  # Persona 2 market shares
-  per2_share_denom <- sum(per2_org1_exp, per2_org2_exp, per2_org3_exp, per2_org4_exp)
-  per2_org1_share <- 100 * (per2_org1_exp / per2_share_denom)
-  per2_org2_share <- 100 * (per2_org2_exp / per2_share_denom)
-  per2_org3_share <- 100 * (per2_org3_exp / per2_share_denom)
-  per2_org4_share <- 100 * (per2_org4_exp / per2_share_denom)
-
-  # Persona 3 predicted betas
+  # Segment 2 expected utilities
+  per2_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per2_betas))
+  per2_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per2_betas))
+  per2_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per2_betas))
+  per2_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per2_betas))
+
+  # Segment 2 market shares
+  per2_share_denom <- sum(per2_prod1_exp, per2_prod2_exp, per2_prod3_exp, per2_prod4_exp)
+  per2_prod1_share <- 100 * (per2_prod1_exp / per2_share_denom)
+  per2_prod2_share <- 100 * (per2_prod2_exp / per2_share_denom)
+  per2_prod3_share <- 100 * (per2_prod3_exp / per2_share_denom)
+  per2_prod4_share <- 100 * (per2_prod4_exp / per2_share_denom)
+
+  # Segment 3 predicted betas
   per3_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,4])
 
-  # Persona 3 expected utilities
-  per3_org1_exp <- exp(t(org_choice[,2]) %*% as.matrix(per3_betas))
-  per3_org2_exp <- exp(t(org_choice[,3]) %*% as.matrix(per3_betas))
-  per3_org3_exp <- exp(t(org_choice[,4]) %*% as.matrix(per3_betas))
-  per3_org4_exp <- exp(t(org_choice[,5]) %*% as.matrix(per3_betas))
-
-  # Persona 3 market shares
-  per3_share_denom <- sum(per3_org1_exp, per3_org2_exp, per3_org3_exp, per3_org4_exp)
-  per3_org1_share <- 100 * (per3_org1_exp / per3_share_denom)
-  per3_org2_share <- 100 * (per3_org2_exp / per3_share_denom)
-  per3_org3_share <- 100 * (per3_org3_exp / per3_share_denom)
-  per3_org4_share <- 100 * (per3_org4_exp / per3_share_denom)
+  # Segment 3 expected utilities
+  per3_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per3_betas))
+  per3_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per3_betas))
+  per3_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per3_betas))
+  per3_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per3_betas))
+
+  # Segment 3 market shares
+  per3_share_denom <- sum(per3_prod1_exp, per3_prod2_exp, per3_prod3_exp, per3_prod4_exp)
+  per3_prod1_share <- 100 * (per3_prod1_exp / per3_share_denom)
+  per3_prod2_share <- 100 * (per3_prod2_exp / per3_share_denom)
+  per3_prod3_share <- 100 * (per3_prod3_exp / per3_share_denom)
+  per3_prod4_share <- 100 * (per3_prod4_exp / per3_share_denom)
 
@@
     Value = c(
-      # Persona 1
-      per1_org1_share, per1_org2_share, per1_org3_share, per1_org4_share, 
-      # Persona 2
-      per2_org1_share, per2_org2_share, per2_org3_share, per2_org4_share,
-      # Persona 3
-      per3_org1_share, per3_org2_share, per3_org3_share, per3_org4_share
-    ),
-    Product = c(input$org1_name, input$org2_name, input$org3_name, input$org4_name),
+      # Segment 1
+      per1_prod1_share, per1_prod2_share, per1_prod3_share, per1_prod4_share, 
+      # Segment 2
+      per2_prod1_share, per2_prod2_share, per2_prod3_share, per2_prod4_share,
+      # Segment 3
+      per3_prod1_share, per3_prod2_share, per3_prod3_share, per3_prod4_share
+    ),
+    Product = c(input$prod1_name, input$prod2_name, input$prod3_name, input$prod4_name),
     Persona = c(
@@
     plot_data %>% 
-      # Factor Product and Persona with ordered=TRUE
+      # Factor Product and Segment with ordered=TRUE
       mutate(
@@
           Product, 
-          levels = c(input$org1_name, input$org2_name, input$org3_name, input$org4_name), 
+          levels = c(input$prod1_name, input$prod2_name, input$prod3_name, input$prod4_name), 
           ordered = TRUE
@@
 renderTable({
-  org_choice = org_reactive()
+  prod_choice = prod_reactive()
   per_choice = per_reactive()
 
-  # Persona 1 predicted betas
+  # Segment 1 predicted betas
   per1_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,2])
 
-  # Persona 1 expected utilities
-  per1_org1_exp <- exp(t(org_choice[,2]) %*% as.matrix(per1_betas))
-  per1_org2_exp <- exp(t(org_choice[,3]) %*% as.matrix(per1_betas))
-  per1_org3_exp <- exp(t(org_choice[,4]) %*% as.matrix(per1_betas))
-  per1_org4_exp <- exp(t(org_choice[,5]) %*% as.matrix(per1_betas))
-
-  # Persona 1 market shares
-  per1_share_denom <- sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)
-  per1_org1_share <- 100 * (per1_org1_exp / per1_share_denom)
-  per1_org2_share <- 100 * (per1_org2_exp / per1_share_denom)
-  per1_org3_share <- 100 * (per1_org3_exp / per1_share_denom)
-  per1_org4_share <- 100 * (per1_org4_exp / per1_share_denom)
-
-  # Persona 2 predicted betas
+  # Segment 1 expected utilities
+  per1_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per1_betas))
+  per1_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per1_betas))
+  per1_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per1_betas))
+  per1_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per1_betas))
+
+  # Segment 1 market shares
+  per1_share_denom <- sum(per1_prod1_exp, per1_prod2_exp, per1_prod3_exp, per1_prod4_exp)
+  per1_prod1_share <- 100 * (per1_prod1_exp / per1_share_denom)
+  per1_prod2_share <- 100 * (per1_prod2_exp / per1_share_denom)
+  per1_prod3_share <- 100 * (per1_prod3_exp / per1_share_denom)
+  per1_prod4_share <- 100 * (per1_prod4_exp / per1_share_denom)
+
+  # Segment 2 predicted betas
   per2_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,3])
 
-  # Persona 2 expected utilities
-  per2_org1_exp <- exp(t(org_choice[,2]) %*% as.matrix(per2_betas))
-  per2_org2_exp <- exp(t(org_choice[,3]) %*% as.matrix(per2_betas))
-  per2_org3_exp <- exp(t(org_choice[,4]) %*% as.matrix(per2_betas))
-  per2_org4_exp <- exp(t(org_choice[,5]) %*% as.matrix(per2_betas))
-
-  # Persona 2 market shares
-  per2_share_denom <- sum(per2_org1_exp, per2_org2_exp, per2_org3_exp, per2_org4_exp)
-  per2_org1_share <- 100 * (per2_org1_exp / per2_share_denom)
-  per2_org2_share <- 100 * (per2_org2_exp / per2_share_denom)
-  per2_org3_share <- 100 * (per2_org3_exp / per2_share_denom)
-  per2_org4_share <- 100 * (per2_org4_exp / per2_share_denom)
-
-  # Persona 3 predicted betas
+  # Segment 2 expected utilities
+  per2_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per2_betas))
+  per2_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per2_betas))
+  per2_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per2_betas))
+  per2_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per2_betas))
+
+  #  Segment 2 market shares
+  per2_share_denom <- sum(per2_prod1_exp, per2_prod2_exp, per2_prod3_exp, per2_prod4_exp)
+  per2_prod1_share <- 100 * (per2_prod1_exp / per2_share_denom)
+  per2_prod2_share <- 100 * (per2_prod2_exp / per2_share_denom)
+  per2_prod3_share <- 100 * (per2_prod3_exp / per2_share_denom)
+  per2_prod4_share <- 100 * (per2_prod4_exp / per2_share_denom)
+
+  # Segment 3 predicted betas
   per3_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,4])
 
-  # Persona 3 expected utilities
-  per3_org1_exp <- exp(t(org_choice[,2]) %*% as.matrix(per3_betas))
-  per3_org2_exp <- exp(t(org_choice[,3]) %*% as.matrix(per3_betas))
-  per3_org3_exp <- exp(t(org_choice[,4]) %*% as.matrix(per3_betas))
-  per3_org4_exp <- exp(t(org_choice[,5]) %*% as.matrix(per3_betas))
-
-  # Persona 3 market shares
-  per3_share_denom <- sum(per3_org1_exp, per3_org2_exp, per3_org3_exp, per3_org4_exp)
-  per3_org1_share <- 100 * (per3_org1_exp / per3_share_denom)
-  per3_org2_share <- 100 * (per3_org2_exp / per3_share_denom)
-  per3_org3_share <- 100 * (per3_org3_exp / per3_share_denom)
-  per3_org4_share <- 100 * (per3_org4_exp / per3_share_denom)
+  # Segment 3 expected utilities
+  per3_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per3_betas))
+  per3_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per3_betas))
+  per3_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per3_betas))
+  per3_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per3_betas))
+
+  # Segment 3 market shares
+  per3_share_denom <- sum(per3_prod1_exp, per3_prod2_exp, per3_prod3_exp, per3_prod4_exp)
+  per3_prod1_share <- 100 * (per3_prod1_exp / per3_share_denom)
+  per3_prod2_share <- 100 * (per3_prod2_exp / per3_share_denom)
+  per3_prod3_share <- 100 * (per3_prod3_exp / per3_share_denom)
+  per3_prod4_share <- 100 * (per3_prod4_exp / per3_share_denom)
 
@@
     Shares = c(
-      # Persona 1
-      per1_org1_share, per1_org2_share, per1_org3_share, per1_org4_share, 
-      # Persona 2
-      per2_org1_share, per2_org2_share, per2_org3_share, per2_org4_share,
-      # Persona 3
-      per3_org1_share, per3_org2_share, per3_org3_share, per3_org4_share
-    ),
-    Product = c(input$org1_name, input$org2_name, input$org3_name, input$org4_name),
+      # Segment 1
+      per1_prod1_share, per1_prod2_share, per1_prod3_share, per1_prod4_share, 
+      # Segment 2
+      per2_prod1_share, per2_prod2_share, per2_prod3_share, per2_prod4_share,
+      # Segment 3
+      per3_prod1_share, per3_prod2_share, per3_prod3_share, per3_prod4_share
+    ),
+    Product = c(input$prod1_name, input$prod2_name, input$prod3_name, input$prod4_name),
     Persona = c(
@@
 
-```{r org1-inputs}
+```{r prod1-inputs}
 # Naming
 textInput(
-  "org1_name",
+  "prod1_name",
   label = "Product Name:",
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org1_org",
+  prod_data = product_data()
+  selectInput(
+    "prod1_prod",
     label = "Product:",
@@
     # selected = "Red Cross",
-    selected = as.character(org_data[1:4,][which(org_data[1:4,2] == 1), 1]),
+    selected = as.character(prod_data[1:4,][which(prod_data[1:4,2] == 1), 1]),
     width = "450px"
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org1_issue", 
+  prod_data = product_data()
+  selectInput(
+    "prod1_issue", 
     label = "Issue Area:",
@@
     selected = ifelse(
-      sum(org_data[5:7,2]) == 0, "Emergency response",
-      as.character(org_data[5:7,][which(org_data[5:7,2] == 1), 1])
+      sum(prod_data[5:7,2]) == 0, "Emergency response",
+      as.character(prod_data[5:7,][which(prod_data[5:7,2] == 1), 1])
     ),
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org1_fin_trans",
+  prod_data = product_data()
+  selectInput(
+    "prod1_fin_trans",
     label = "Financial Transparency:",
@@
     selected = ifelse(
-      sum(org_data[8,2]) == 0, "Doesn’t engage in financial transparency",
-      as.character(org_data[8,][which(org_data[8,2] == 1), 1])
+      sum(prod_data[8,2]) == 0, "Doesn’t engage in financial transparency",
+      as.character(prod_data[8,][which(prod_data[8,2] == 1), 1])
     ),
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org1_fin_account",
+  prod_data = product_data()
+  selectInput(
+    "prod1_fin_account",
     label = "Financial Accountability:",
@@
     selected = ifelse(
-      sum(org_data[9,2]) == 0, "Doesn’t engage in financial accountability",
-      as.character(org_data[9,][which(org_data[9,2] == 1), 1])
+      sum(prod_data[9,2]) == 0, "Doesn’t engage in financial accountability",
+      as.character(prod_data[9,][which(prod_data[9,2] == 1), 1])
     ),
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org1_funding",
+  prod_data = product_data()
+  selectInput(
+    "prod1_funding",
     label = "Funding Source:",
@@
     selected = ifelse(
-      sum(org_data[10:11,2]) == 0, "Many small private donations",
-      as.character(org_data[10:11,][which(org_data[10:11,2] == 1), 1])
+      sum(prod_data[10:11,2]) == 0, "Many small private donations",
+      as.character(prod_data[10:11,][which(prod_data[10:11,2] == 1), 1])
     ),
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org1_host_gov",
+  prod_data = product_data()
+  selectInput(
+    "prod1_host_gov",
     label = "Relationship With Host Government",
@@
     selected = ifelse(
-      sum(org_data[12:13,2]) == 0, "Friendly relationship with government",
-      as.character(org_data[12:13,][which(org_data[12:13,2] == 1), 1])
+      sum(prod_data[12:13,2]) == 0, "Friendly relationship with government",
+      as.character(prod_data[12:13,][which(prod_data[12:13,2] == 1), 1])
     ),
@@
 
-```{r org2-inputs}
+```{r prod2-inputs}
 # Naming
 textInput(
-  "org2_name",
+  "prod2_name",
   label = "Product Name:",
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org2_org",
+  prod_data = product_data()
+  selectInput(
+    "prod2_prod",
     label = "Product:",
@@
     # selected = "Red Cross",
-    selected = as.character(org_data[1:4,][which(org_data[1:4,3] == 1), 1]),
+    selected = as.character(prod_data[1:4,][which(prod_data[1:4,3] == 1), 1]),
     width = "450px"
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org2_issue", 
+  prod_data = product_data()
+  selectInput(
+    "prod2_issue", 
     label = "Issue Area:",
@@
     selected = ifelse(
-      sum(org_data[5:7,3]) == 0, "Emergency response",
-      as.character(org_data[5:7,][which(org_data[5:7,3] == 1), 1])
+      sum(prod_data[5:7,3]) == 0, "Emergency response",
+      as.character(prod_data[5:7,][which(prod_data[5:7,3] == 1), 1])
     ),
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org2_fin_trans",
+  prod_data = product_data()
+  selectInput(
+    "prod2_fin_trans",
     label = "Financial Transparency:",
@@
     selected = ifelse(
-      sum(org_data[8,3]) == 0, "Doesn’t engage in financial transparency",
-      as.character(org_data[8,][which(org_data[8,3] == 1), 1])
+      sum(prod_data[8,3]) == 0, "Doesn’t engage in financial transparency",
+      as.character(prod_data[8,][which(prod_data[8,3] == 1), 1])
     ),
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org2_fin_account",
+  prod_data = product_data()
+  selectInput(
+    "prod2_fin_account",
     label = "Financial Accountability:",
@@
     selected = ifelse(
-      sum(org_data[9,3]) == 0, "Doesn’t engage in financial accountability",
-      as.character(org_data[9,][which(org_data[9,3] == 1), 1])
+      sum(prod_data[9,3]) == 0, "Doesn’t engage in financial accountability",
+      as.character(prod_data[9,][which(prod_data[9,3] == 1), 1])
     ),
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org2_funding",
+  prod_data = product_data()
+  selectInput(
+    "prod2_funding",
     label = "Funding Source:",
@@
     selected = ifelse(
-      sum(org_data[10:11,3]) == 0, "Many small private donations",
-      as.character(org_data[10:11,][which(org_data[10:11,3] == 1), 1])
+      sum(prod_data[10:11,3]) == 0, "Many small private donations",
+      as.character(prod_data[10:11,][which(prod_data[10:11,3] == 1), 1])
     ),
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org2_host_gov",
+  prod_data = product_data()
+  selectInput(
+    "prod2_host_gov",
     label = "Relationship With Host Government",
@@
     selected = ifelse(
-      sum(org_data[12:13,3]) == 0, "Friendly relationship with government",
-      as.character(org_data[12:13,][which(org_data[12:13,3] == 1), 1])
+      sum(prod_data[12:13,3]) == 0, "Friendly relationship with government",
+      as.character(prod_data[12:13,][which(prod_data[12:13,3] == 1), 1])
     ),
@@
 
-```{r org3-inputs}
+```{r prod3-inputs}
 # Naming
 textInput(
-  "org3_name",
+  "prod3_name",
   label = "Product Name:",
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org3_org",
+  prod_data = product_data()
+  selectInput(
+    "prod3_prod",
     label = "Product:",
@@
     # selected = "Red Cross",
-    selected = as.character(org_data[1:4,][which(org_data[1:4,4] == 1), 1]),
+    selected = as.character(prod_data[1:4,][which(prod_data[1:4,4] == 1), 1]),
     width = "450px"
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org3_issue", 
+  prod_data = product_data()
+  selectInput(
+    "prod3_issue", 
     label = "Issue Area:",
@@
     selected = ifelse(
-      sum(org_data[5:7,4]) == 0, "Emergency response",
-      as.character(org_data[5:7,][which(org_data[5:7,4] == 1), 1])
+      sum(prod_data[5:7,4]) == 0, "Emergency response",
+      as.character(prod_data[5:7,][which(prod_data[5:7,4] == 1), 1])
     ),
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org3_fin_trans",
+  prod_data = product_data()
+  selectInput(
+    "prod3_fin_trans",
     label = "Financial Transparency:",
@@
     selected = ifelse(
-      sum(org_data[8,4]) == 0, "Doesn’t engage in financial transparency",
-      as.character(org_data[8,][which(org_data[8,4] == 1), 1])
+      sum(prod_data[8,4]) == 0, "Doesn’t engage in financial transparency",
+      as.character(prod_data[8,][which(prod_data[8,4] == 1), 1])
     ),
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org3_fin_account",
+  prod_data = product_data()
+  selectInput(
+    "prod3_fin_account",
     label = "Financial Accountability:",
@@
     selected = ifelse(
-      sum(org_data[9,4]) == 0, "Doesn’t engage in financial accountability",
-      as.character(org_data[9,][which(org_data[9,4] == 1), 1])
+      sum(prod_data[9,4]) == 0, "Doesn’t engage in financial accountability",
+      as.character(prod_data[9,][which(prod_data[9,4] == 1), 1])
     ),
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org3_funding",
+  prod_data = product_data()
+  selectInput(
+    "prod3_funding",
     label = "Funding Source:",
@@
     selected = ifelse(
-      sum(org_data[10:11,4]) == 0, "Many small private donations",
-      as.character(org_data[10:11,][which(org_data[10:11,4] == 1), 1])
+      sum(prod_data[10:11,4]) == 0, "Many small private donations",
+      as.character(prod_data[10:11,][which(prod_data[10:11,4] == 1), 1])
     ),
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org3_host_gov",
+  prod_data = product_data()
+  selectInput(
+    "prod3_host_gov",
     label = "Relationship With Host Government",
@@
     selected = ifelse(
-      sum(org_data[12:13,4]) == 0, "Friendly relationship with government",
-      as.character(org_data[12:13,][which(org_data[12:13,4] == 1), 1])
+      sum(prod_data[12:13,4]) == 0, "Friendly relationship with government",
+      as.character(prod_data[12:13,][which(prod_data[12:13,4] == 1), 1])
     ),
@@
 
-```{r org4-inputs}
+```{r prod4-inputs}
 # Naming
 textInput(
-  "org4_name",
+  "prod4_name",
   label = "Product Name:",
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org4_org",
+  prod_data = product_data()
+  selectInput(
+    "prod4_prod",
     label = "Product:",
@@
     # selected = "Red Cross",
-    selected = as.character(org_data[1:4,][which(org_data[1:4,5] == 1), 1]),
+    selected = as.character(prod_data[1:4,][which(prod_data[1:4,5] == 1), 1]),
     width = "450px"
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org4_issue", 
+  prod_data = product_data()
+  selectInput(
+    "prod4_issue", 
     label = "Issue Area:",
@@
     selected = ifelse(
-      sum(org_data[5:7,5]) == 0, "Emergency response",
-      as.character(org_data[5:7,][which(org_data[5:7,5] == 1), 1])
+      sum(prod_data[5:7,5]) == 0, "Emergency response",
+      as.character(prod_data[5:7,][which(prod_data[5:7,5] == 1), 1])
     ),
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org4_fin_trans",
+  prod_data = product_data()
+  selectInput(
+    "prod4_fin_trans",
     label = "Financial Transparency:",
@@
     selected = ifelse(
-      sum(org_data[8,5]) == 0, "Doesn’t engage in financial transparency",
-      as.character(org_data[8,][which(org_data[8,5] == 1), 1])
+      sum(prod_data[8,5]) == 0, "Doesn’t engage in financial transparency",
+      as.character(prod_data[8,][which(prod_data[8,5] == 1), 1])
     ),
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org4_fin_account",
+  prod_data = product_data()
+  selectInput(
+    "prod4_fin_account",
     label = "Financial Accountability:",
@@
     selected = ifelse(
-      sum(org_data[9,5]) == 0, "Doesn’t engage in financial accountability",
-      as.character(org_data[9,][which(org_data[9,5] == 1), 1])
+      sum(prod_data[9,5]) == 0, "Doesn’t engage in financial accountability",
+      as.character(prod_data[9,][which(prod_data[9,5] == 1), 1])
     ),
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org4_funding",
+  prod_data = product_data()
+  selectInput(
+    "prod4_funding",
     label = "Funding Source:",
@@
     selected = ifelse(
-      sum(org_data[10:11,5]) == 0, "Many small private donations",
-      as.character(org_data[10:11,][which(org_data[10:11,5] == 1), 1])
+      sum(prod_data[10:11,5]) == 0, "Many small private donations",
+      as.character(prod_data[10:11,][which(prod_data[10:11,5] == 1), 1])
     ),
@@
 renderUI({
-  org_data = product_data()
-  selectInput(
-    "org4_host_gov",
+  prod_data = product_data()
+  selectInput(
+    "prod4_host_gov",
     label = "Relationship With Host Government",
@@
     selected = ifelse(
-      sum(org_data[12:13,5]) == 0, "Friendly relationship with government",
-      as.character(org_data[12:13,][which(org_data[12:13,5] == 1), 1])
+      sum(prod_data[12:13,5]) == 0, "Friendly relationship with government",
+      as.character(prod_data[12:13,][which(prod_data[12:13,5] == 1), 1])
     ),
@@
 ```{r import}
-# Organization configuration import
+# prodanization configuration import
 fileInput(
- "org_update",
- "Import Organization Data",
+ "prod_update",
+ "Import prodanization Data",
  accept = c(
@@
 actionButton(
- "org_button",
- label = "Update Organization Data"
+ "prod_button",
+ label = "Update prodanization Data"
 )
@@
 # Use the default configurations if no inputs are provided
-organization_data <- reactive({
-  if (is.null(input$org_update$datapath)) {
-    x <- org_default
+productanization_data <- reactive({
+  if (is.null(input$prod_update$datapath)) {
+    x <- prod_default
   } else {
-    req(input$org_button)
-    req(input$org_update)
-    x <- read_csv(input$org_update$datapath)
+    req(input$prod_button)
+    req(input$prod_update)
+    x <- read_csv(input$prod_update$datapath)
   }
@@
 ```{r export}
-# Render the organization configuration as a table
+# Render the prodanization configuration as a table
 renderTable({
-  org_choice = org_reactive()
-  org_choice
-})
-
-# Download organization configuration
-downloadButton("download_org", label = "Download Organization Data")
+  prod_choice = prod_reactive()
+  prod_choice
+})
+
+# Download prodanization configuration
+downloadButton("download_prod", label = "Download prodanization Data")
 
@@
   filename = function() {
-    paste0("org_data_",Sys.time(),".csv")
+    paste0("prod_data_",Sys.time(),".csv")
   },
   content = function(file) {
-    write_csv(org_reactive(), file)
+    write_csv(prod_reactive(), file)
   }

### 2021-09-03 dashboard_example.Rmd

@@
   # Segment 1 market shares
-  per1_share_denom <- sum(per1_prod1_exp, per1_prod2_exp, per1_prod3_exp, per1_prod4_exp)
-  per1_prod1_share <- 100 * (per1_prod1_exp / per1_share_denom)
-  per1_prod2_share <- 100 * (per1_prod2_exp / per1_share_denom)
-  per1_prod3_share <- 100 * (per1_prod3_exp / per1_share_denom)
-  per1_prod4_share <- 100 * (per1_prod4_exp / per1_share_denom)
+  seg1_share_denom <- sum(seg1_prod1_exp, seg1_prod2_exp, seg1_prod3_exp, seg1_prod4_exp)
+  seg1_prod1_share <- 100 * (seg1_prod1_exp / seg1_share_denom)
+  seg1_prod2_share <- 100 * (seg1_prod2_exp / seg1_share_denom)
+  seg1_prod3_share <- 100 * (seg1_prod3_exp / seg1_share_denom)
+  seg1_prod4_share <- 100 * (seg1_prod4_exp / seg1_share_denom)
 
   # Segment 2 predicted betas
-  per2_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,3])
+  seg2_betas <- as.matrix(gammas) %*% as.matrix(seg_choice[,3])
 
   # Segment 2 expected utilities
-  per2_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per2_betas))
-  per2_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per2_betas))
-  per2_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per2_betas))
-  per2_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per2_betas))
+  seg2_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(seg2_betas))
+  seg2_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(seg2_betas))
+  seg2_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(seg2_betas))
+  seg2_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(seg2_betas))
 
   # Segment 2 market shares
-  per2_share_denom <- sum(per2_prod1_exp, per2_prod2_exp, per2_prod3_exp, per2_prod4_exp)
-  per2_prod1_share <- 100 * (per2_prod1_exp / per2_share_denom)
-  per2_prod2_share <- 100 * (per2_prod2_exp / per2_share_denom)
-  per2_prod3_share <- 100 * (per2_prod3_exp / per2_share_denom)
-  per2_prod4_share <- 100 * (per2_prod4_exp / per2_share_denom)
+  seg2_share_denom <- sum(seg2_prod1_exp, seg2_prod2_exp, seg2_prod3_exp, seg2_prod4_exp)
+  seg2_prod1_share <- 100 * (seg2_prod1_exp / seg2_share_denom)
+  seg2_prod2_share <- 100 * (seg2_prod2_exp / seg2_share_denom)
+  seg2_prod3_share <- 100 * (seg2_prod3_exp / seg2_share_denom)
+  seg2_prod4_share <- 100 * (seg2_prod4_exp / seg2_share_denom)
 
   # Segment 3 predicted betas
-  per3_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,4])
+  seg3_betas <- as.matrix(gammas) %*% as.matrix(seg_choice[,4])
 
   # Segment 3 expected utilities
-  per3_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per3_betas))
-  per3_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per3_betas))
-  per3_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per3_betas))
-  per3_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per3_betas))
+  seg3_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(seg3_betas))
+  seg3_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(seg3_betas))
+  seg3_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(seg3_betas))
+  seg3_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(seg3_betas))
 
   # Segment 3 market shares
-  per3_share_denom <- sum(per3_prod1_exp, per3_prod2_exp, per3_prod3_exp, per3_prod4_exp)
-  per3_prod1_share <- 100 * (per3_prod1_exp / per3_share_denom)
-  per3_prod2_share <- 100 * (per3_prod2_exp / per3_share_denom)
-  per3_prod3_share <- 100 * (per3_prod3_exp / per3_share_denom)
-  per3_prod4_share <- 100 * (per3_prod4_exp / per3_share_denom)
+  seg3_share_denom <- sum(seg3_prod1_exp, seg3_prod2_exp, seg3_prod3_exp, seg3_prod4_exp)
+  seg3_prod1_share <- 100 * (seg3_prod1_exp / seg3_share_denom)
+  seg3_prod2_share <- 100 * (seg3_prod2_exp / seg3_share_denom)
+  seg3_prod3_share <- 100 * (seg3_prod3_exp / seg3_share_denom)
+  seg3_prod4_share <- 100 * (seg3_prod4_exp / seg3_share_denom)
 
@@
       # Segment 1
-      per1_prod1_share, per1_prod2_share, per1_prod3_share, per1_prod4_share, 
+      seg1_prod1_share, seg1_prod2_share, seg1_prod3_share, seg1_prod4_share, 
       # Segment 2
-      per2_prod1_share, per2_prod2_share, per2_prod3_share, per2_prod4_share,
+      seg2_prod1_share, seg2_prod2_share, seg2_prod3_share, seg2_prod4_share,
       # Segment 3
-      per3_prod1_share, per3_prod2_share, per3_prod3_share, per3_prod4_share
+      seg3_prod1_share, seg3_prod2_share, seg3_prod3_share, seg3_prod4_share
     ),
     Product = c(input$prod1_name, input$prod2_name, input$prod3_name, input$prod4_name),
-    Persona = c(
+    Segment = c(
       rep(input$per1_name, 4), 
@@
         ),
-        Persona = factor(
-          Persona, 
+        Segment = factor(
+          Segment, 
           levels = c(input$per1_name, input$per2_name, input$per3_name), 
@@
       ) %>% 
-      ggplot(aes(y = Value, x = Product, fill = Persona)) +
+      ggplot(aes(y = Value, x = Product, fill = Segment)) +
       geom_bar(position = "dodge", stat = "identity") +
@@
    prod_choice = prod_reactive()
-  per_choice = per_reactive()
+   seg_choice = seg_reactive()
 
   # Segment 1 predicted betas
-  per1_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,2])
+  seg1_betas <- as.matrix(gammas) %*% as.matrix(seg_choice[,2])
 
   # Segment 1 expected utilities
-  per1_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per1_betas))
-  per1_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per1_betas))
-  per1_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per1_betas))
-  per1_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per1_betas))
+  seg1_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(seg1_betas))
+  seg1_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(seg1_betas))
+  seg1_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(seg1_betas))
+  seg1_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(seg1_betas))
 
   # Segment 1 market shares
-  per1_share_denom <- sum(per1_prod1_exp, per1_prod2_exp, per1_prod3_exp, per1_prod4_exp)
-  per1_prod1_share <- 100 * (per1_prod1_exp / per1_share_denom)
-  per1_prod2_share <- 100 * (per1_prod2_exp / per1_share_denom)
-  per1_prod3_share <- 100 * (per1_prod3_exp / per1_share_denom)
-  per1_prod4_share <- 100 * (per1_prod4_exp / per1_share_denom)
+  seg1_share_denom <- sum(seg1_prod1_exp, seg1_prod2_exp, seg1_prod3_exp, seg1_prod4_exp)
+  seg1_prod1_share <- 100 * (seg1_prod1_exp / seg1_share_denom)
+  seg1_prod2_share <- 100 * (seg1_prod2_exp / seg1_share_denom)
+  seg1_prod3_share <- 100 * (seg1_prod3_exp / seg1_share_denom)
+  seg1_prod4_share <- 100 * (seg1_prod4_exp / seg1_share_denom)
 
   # Segment 2 predicted betas
-  per2_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,3])
+  seg2_betas <- as.matrix(gammas) %*% as.matrix(seg_choice[,3])
 
   # Segment 2 expected utilities
-  per2_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per2_betas))
-  per2_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per2_betas))
-  per2_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per2_betas))
-  per2_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per2_betas))
+  seg2_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(seg2_betas))
+  seg2_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(seg2_betas))
+  seg2_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(seg2_betas))
+  seg2_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(seg2_betas))
 
   # Segment 2 market shares
-  per2_share_denom <- sum(per2_prod1_exp, per2_prod2_exp, per2_prod3_exp, per2_prod4_exp)
-  per2_prod1_share <- 100 * (per2_prod1_exp / per2_share_denom)
-  per2_prod2_share <- 100 * (per2_prod2_exp / per2_share_denom)
-  per2_prod3_share <- 100 * (per2_prod3_exp / per2_share_denom)
-  per2_prod4_share <- 100 * (per2_prod4_exp / per2_share_denom)
+  seg2_share_denom <- sum(seg2_prod1_exp, seg2_prod2_exp, seg2_prod3_exp, seg2_prod4_exp)
+  seg2_prod1_share <- 100 * (seg2_prod1_exp / seg2_share_denom)
+  seg2_prod2_share <- 100 * (seg2_prod2_exp / seg2_share_denom)
+  seg2_prod3_share <- 100 * (seg2_prod3_exp / seg2_share_denom)
+  seg2_prod4_share <- 100 * (seg2_prod4_exp / seg2_share_denom)
 
   # Segment 3 predicted betas
-  per3_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,4])
+  seg3_betas <- as.matrix(gammas) %*% as.matrix(seg_choice[,4])
 
   # Segment 3 expected utilities
-  per3_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per3_betas))
-  per3_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per3_betas))
-  per3_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per3_betas))
-  per3_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per3_betas))
+  seg3_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(seg3_betas))
+  seg3_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(seg3_betas))
+  seg3_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(seg3_betas))
+  seg3_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(seg3_betas))
 
   # Segment 3 market shares
-  per3_share_denom <- sum(per3_prod1_exp, per3_prod2_exp, per3_prod3_exp, per3_prod4_exp)
-  per3_prod1_share <- 100 * (per3_prod1_exp / per3_share_denom)
-  per3_prod2_share <- 100 * (per3_prod2_exp / per3_share_denom)
-  per3_prod3_share <- 100 * (per3_prod3_exp / per3_share_denom)
-  per3_prod4_share <- 100 * (per3_prod4_exp / per3_share_denom)
+  seg3_share_denom <- sum(seg3_prod1_exp, seg3_prod2_exp, seg3_prod3_exp, seg3_prod4_exp)
+  seg3_prod1_share <- 100 * (seg3_prod1_exp / seg3_share_denom)
+  seg3_prod2_share <- 100 * (seg3_prod2_exp / seg3_share_denom)
+  seg3_prod3_share <- 100 * (seg3_prod3_exp / seg3_share_denom)
+  seg3_prod4_share <- 100 * (seg3_prod4_exp / seg3_share_denom)
 
@@
   ) %>% 
-    pivot_wider(names_from = Persona, values_from = Shares)
+    pivot_wider(names_from = Segment, values_from = Shares)
 

### 2021-09-03 analysis/03_analysis.Rmd

--- 2020-09-12 analysis/03_analysis.Rmd
@@
 
-## Compute model fit
+## Compute and save model fit
 
@@
 
-```
-        elpd_diff se_diff
-model1     0.0       0.0 
-model3   -23.5       8.6 
-model2   -37.5      12.9 
-model6   -54.0      15.6 
-model7   -70.2      15.4 
-model4   -74.4      16.6 
-model8  -163.9      23.6 
-model5  -174.4      24.6 
-model9  -401.3      38.4 
-model10 -518.3      44.6
-```
-
-The intercept-only model works best in terms of PSIS-LOO, followed by models with political ideology, public affairs and demographics covariates.
-While PSIS-LOO doesn't properly account for the specific benefits of a hierarchical model, it suggests that political ideology above all other covariate sets specified, has the most explanatory power.
-
 ```{r save-fit, eval=FALSE}
@@
 # Save model output
-write_rds(model_fit, here::here("analysis", "output", "model_fit.rds"))
+write_rds(model_fit, here::here("analysis", "output", "tables", "model_fit.rds"))
 ```
 
-## Load model fit and extract and save draws
+## Load model fit objects and extract and save draws
 
 ```{r extract-draws, eval=FALSE}
-intercept <- 1                            # Intercept-only
-public_affairs <- 0                       # Public affairs
+intercept <- 0                            # Intercept-only
+public_affairs <- 1                       # Public affairs
 political_ideology <- 0                   # Political ideology
@@
 
-# Load draws and plot marginals, contrasts, and heatmaps
-
-Now that we have the draws extracted, we can load draws from the model of interest and plot marginals, contrasts, and heatmaps.
-
-## Load draws and assign labels
-
-```{r load-draws}
-intercept <- 0                            # Intercept-only
-public_affairs <- 0                       # Public affairs
-political_ideology <- 0                   # Political ideology
-social_views <- 0                         # Social views
-charity_voluntarism <- 0                  # Charity and voluntarism
-demographics <- 0                         # Demographics
-public_political <- 0                     # Public affairs + Political ideology
-public_political_social <- 0              # + Social views
-public_political_social_charity <- 1      # + Charity and voluntarism
-public_political_social_charity_demo <- 0 # + Demographics
-
-# Load draws
-if (intercept == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "intercept.rds"))
-if (public_affairs == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))
-if (political_ideology == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "political_ideology.rds"))
-if (social_views == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "social_views.rds"))
-if (charity_voluntarism == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds"))
-if (demographics == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "demographics.rds"))
-if (public_political == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political.rds"))
-if (public_political_social == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political_social.rds"))
-if (public_political_social_charity == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds"))
-if (public_political_social_charity_demo == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political_social_charity_demo.rds"))
-
-# Assign level labels
-level_labels <- c(
-  str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
-  str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
-  "Financial transparency: Yes",
-  "Accountability: Yes",
-  str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants")),
-  str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))
-)
-
-# Assign covariate covariates
-public_affairs_labels <- c(
-  # *Q2.1*: How often do you follow national news? 
-  str_c(
-    "Follow national news: ", 
-    c("Once a week", "At least once a day")
-  ),
-  # *Q2.2*: How often do you follow international news? 
-  str_c(
-    "Follow international news: ", 
-    c("Sometimes", "Always")
-  ),
-  # *Q2.3*: Which mediums do you use to follow news? (Select all that apply.)
-  str_c(
-    "Medium to follow news: ", 
-    c(
-      "TV", "Print", "Online (excluding social media)", "Social media", 
-      "Radio", "Email newsletters", "News app"
-    )
-  ),
-  # *Q2.4*: How often would you say you follow what's going on in government and public affairs?
-  "Follow government and public affairs: Often", 
-  # *Q5.7*: Have you ever traveled to a developing country? 
-  "Traveled to a developing country: No"
-)
-political_ideology_labels <- c(
-  # *Q5.2*: On a scale of extremely liberal (1) to extremely conservative (7), how would you describe your political views?
-  str_c(
-    "Liberal to Conservative: ", 
-    c(
-      "Somewhat liberal", "Slightly liberal", "Moderate",
-      "Slightly conservative", "Somewhat conservative", "Extremely conservative"
-    )
-  )
-)
-social_views_labels <- c(
-  # *Q5.6*: On a scale of no trust (1) to complete trust (7), how much do you trust political institutions and the state?
-  str_c(
-    "Trust in political institutions: ", 
-    c(
-      "Very little trust", "Little trust", 
-      "Neutral", "Some trust", "A lot of trust", "Complete trust"
-    )
-  ),
-  # *Q5.11*: On a scale of strongly agree (1) to strongly disagree (7), rate your response to the following statement: People should be more charitable towards others in society.
-  str_c(
-    "People should be more charitable: ", 
-    c(
-      "Agree", "Somewhat agree", "Neutral", 
-      "Somewhat disagree", "Disagree", "Strongly disagree"
-    )
-  ),
-  # *Q5.8*: How often do you attend religious or worship services, not including weddings and funerals?
-  str_c(
-    "Religious and worship service attendance: ", 
-    c("Rarely", "At least once a month")
-  ),
-  # *Q5.9*: How important is religion in your life?
-  "Importance of religion: Important",
-  # *Q5.10*: What is your current religion, if any?
-  str_c(
-    "Religion: ", 
-    c(
-      "Protestant", "Christian Orthodox", "Jewish", "Muslim", 
-      "Sikh", "Hindu", "Buddhist", "Atheist", "Other"
-    )
-  )
-)
-charity_voluntarism_labels <- c(
-  # *Q2.7*: On a scale of not at all important (1) to essential (7), how important is it for you to trust charities?
-  str_c(
-    "Importance of trusing charities: ", 
-    c(
-      "Very unimportant", "Somewhat unimportant", 
-      "Neutral", "Somewhat important", "Very important", "Essential"
-    )
-  ),
-  # *Q2.8*: On a scale of no trust at all (1) to complete trust (7), how much do you trust charities?
-  str_c(
-    "Trust in charities: ", 
-    c(
-      "Very little trust", "Little trust", 
-      "Neutral", "Some trust", "A lot of trust", "Complete trust"
-    )
-  ),
-  # *Q2.5*: How often do you donate to charity (with either cash or in-kind)?
-  "Donation frequency: At least once a month",
-  # *Q2.6*: How much did you donate to charity last year?
-  str_c(
-    "Donated last year: ",
-    c(
-      "$50-$99", "$100-$499", "$500-$999", 
-      "$1000-$4,999", "$5000-$9,999", "$10,000+"
-    )
-  ),
-  # *Q2.9*: Have you volunteered in the past 12 months?
-  "Volunteered in past 12 months: Yes", 
-  # *Q2.10*: How often do you volunteer?
-  str_c(
-    "Volunteer frequency: ",
-    c("Rarely", "More than once a month, less than once a year", "At least once a month")
-  ),
-  # *Q5.4*: Historically, how involved have you been in activist causes?
-  "History of activism: Involved",
-  # *Q5.5*: Historically, how involved has your family been in activist causes?
-  "History of family activism: Involved",
-  # *Q5.3*: Here is a list of different types of voluntary organizations.
-For each organization, indicate whether you are an active member, an inactive member, or not a member of that type of organization:
-  str_c(
-    "Church or religious organization: ",
-    c("Inactive member", "Active member")
-  ),
-  str_c(
-    "Sport or recreational organization: ",
-    c("Inactive member", "Active member")
-  ),
-  str_c(
-    "Art, music, or educational organization: ",
-    c("Inactive member", "Active member")
-  ),
-  str_c(
-    "Labor union: ",
-    c("Inactive member", "Active member")
-  ),
-  str_c(
-    "Political party: ",
-    c("Inactive member", "Active member")
-  ),
-  str_c(
-    "Environmental organization: ",
-    c("Inactive member", "Active member")
-  ),
-  str_c(
-    "Professional association: ",
-    c("Inactive member", "Active member")
-  ),
-  str_c(
-    "Humanitarian or charitable organization: ",
-    c("Inactive member", "Active member")
-  ),
-  str_c(
-    "Consumer organization: ",
-    c("Inactive member", "Active member")
-  ),
-  str_c(
-    "Other organization: ",
-    c("Inactive member", "Active member")
-  )
-)
-demographics_labels <- c(
-  # *Q5.12*: What is your gender?
-  str_c(
-    "Gender: ", 
-    c("Female", "Transgender", "Prefer not to say", "Other")
-  ), 
-  # *Q5.13*: Are you now married, widowed, divorced, separated, or never married?
-  str_c(
-    "Marital status: ", 
-    c("Widowed", "Divorced", "Separated", "Never married")
-  ), 
-  # *Q5.14*: What is the highest degree or level of school you have completed?
-  str_c(
-    "Education: ", 
-    c(
-      "High school graduate", 
-      "Some college", "2 year degree", "4 year degree", 
-      "Graduate or professional degree", "Doctorate"
-    )
-  ), 
-  # *Q5.15*: What is your annual household income before taxes?
-  "Income: More than median",
-  # *Q5.16*: Choose one or more races that you consider yourself to be:
-  str_c(
-    "Race/ethnicity: ",
-    c(
-      "White", "Black or African American", "American Indian or Alaska Native", 
-      "Asian", "Native Hawaiian or Pacific Islander", "Other"
-    )
-  ),
-  # *Q5.17*: How old are you?
-  "Age: More than median"
-)
-if (public_affairs == 1) covariate_labels <- public_affairs_labels
-if (political_ideology == 1) covariate_labels <- political_ideology_labels
-if (social_views == 1) covariate_labels <- social_views_labels
-if (charity_voluntarism == 1) covariate_labels <- charity_voluntarism_labels
-if (demographics == 1) covariate_labels <- demographics_labels
-if (public_political == 1) {
-  covariate_labels <- c(public_affairs_labels, political_ideology_labels)
-}
-if (public_political_social == 1) {
-  covariate_labels <- c(public_affairs_labels, political_ideology_labels, social_views_labels)
-}
-if (public_political_social_charity == 1) {
-  covariate_labels <- c(
-    public_affairs_labels, political_ideology_labels, 
-    social_views_labels, charity_voluntarism_labels
-  )
-}
-if (public_political_social_charity_demo == 1) {
-  covariate_labels <- c(
-    public_affairs_labels, political_ideology_labels, 
-    social_views_labels, charity_voluntarism_labels, demographics_labels
-  )
-}
-```
-
-## Plot marginals
-
-```{r plot-marginals}
-# Plot marginals
-if (intercept == 1) {
-  draws %>%
-    mutate(
-      levels = factor(i, labels = level_labels)
-    ) %>%
-    ggplot(aes(x = Gamma, y = levels)) +
-    stat_halfeye(.width = .95) +
-    geom_vline(xintercept = 0, color = "grey") +
-    labs(y = "Attribute Levels")
-}
-if (intercept != 1) {
-  draws %>%
-    filter(j != 1) %>%
-    mutate(
-      levels = factor(i, labels = level_labels),
-      covariates = factor(j, labels = covariate_labels)
-    ) %>%
-    ggplot(aes(x = Gamma, y = covariates)) +
-      stat_halfeye(.width = .95) +
-      geom_vline(xintercept = 0, color = "white") +
-      labs(y = "Covariates") +
-      facet_wrap(~ levels, ncol = 5)
-}
-
-# Save plot
-if (intercept == 1) file_name <- paste("marginal-posteriors_intercept.png")
-if (public_affairs == 1) file_name <- paste("marginal-posteriors_public-affairs.png")
-if (political_ideology == 1) file_name <- paste("marginal-posteriors_political-ideology.png")
-if (social_views == 1) file_name <- paste("marginal-posteriors_social-views.png")
-if (charity_voluntarism == 1) file_name <- paste("marginal-posteriors_charity-voluntarism.png")
-if (demographics == 1) file_name <- paste("marginal-posteriors_demographics.png")
-if (public_political == 1) file_name <- paste("marginal-posteriors_public-political.png")
-if (public_political_social == 1) file_name <- paste("marginal-posteriors_public-political-social.png")
-if (public_political_social_charity == 1) file_name <- paste("marginal-posteriors_public-political-social-charity.png")
-if (public_political_social_charity_demo == 1) file_name <- paste("marginal-posteriors_public-political-social-charity-demos.png")
-if (intercept == 1) width_length <- c(10, 10)
-if (intercept != 1) width_length <- c(20, 20)
-if (public_political_social_charity == 1) width_length <- c(20, 30)
-if (public_political_social_charity_demo == 1) width_length <- c(20, 30)
-ggsave(
-  file_name,
-  path = here::here("analysis", "output", "figures"),
-  width = width_length[1],
-  height = width_length[2],
-  units = "in"
-)
-```
-
-## Plot contrasts
-
-```{r plot-contrasts}
-
-```
-
-## Plot heatmaps
-
-Instead of plotting marginals or contrasts, we can use a heatmap to identify where there are significant differences in the non-intercept models, which can then be narrowed down using the marginal plots.
-
-```{r plot-heatmaps}
-if (public_affairs == 1) plot_title <- paste("Public Affairs")
-if (political_ideology == 1) plot_title <- paste("Political Ideology")
-if (social_views == 1) plot_title <- paste("Social Views")
-if (charity_voluntarism == 1) plot_title <- paste("Covariates related to charity and voluntarism")
-if (demographics == 1) plot_title <- paste("Demographics")
-if (public_political == 1) plot_title <- paste("Public Affairs and Political Ideology")
-if (public_political_social == 1) plot_title <- paste("Public Affairs, Political Ideology, and Social Views")
-if (public_political_social_charity == 1) plot_title <- paste("Public Affairs, Political Ideology, Social Views, and Charity and Voluntarism")
-if (public_political_social_charity_demo == 1) plot_title <- paste("Public Affairs, Political Ideology, Social Views, Charity and Voluntarism, and Demographics")
-
-if (charity_voluntarism == 1) {
-  j_labels <- tribble(
-    ~j, ~j_label,
-    2, "Importance of trusting charities", 
-    3, "Trust charities", 
-    4, "Frequency of donation", 
-    5, "Amount of donation", 
-    6, "Volunteered", 
-    7, "Volunteer frequency", 
-    8, "Personal involvement in activism", 
-    9, "Family involvement in activism", 
-    10, "Membership in church", 
-    11, "Membership in sports", 
-    12, "Membership in art, music, or educational organization", 
-    13, "Membership in labor union", 
-    14, "Membership in political party", 
-    15, "Membership in envrionmental organization", 
-    16, "Membership in professional association", 
-    17, "Membership in humanitarian organization", 
-    18, "Membership in consumer organization", 
-    19, "Membership in other organization"
-  ) %>% 
-    mutate(j_label = fct_inorder(j_label))
-}
-
-if (intercept != 1) {
-  # Posterior means.
-  posterior_means <- draws %>% 
-    filter(j != 1) %>% 
-    left_join(j_labels, by = "j") %>% 
-    left_join(level_lookup, by = "i") %>% 
-    mutate(
-      levels = factor(i, labels = level_labels), 
-      # covariates = factor(j, labels = covariate_labels)
-      covariates = factor(j, labels = 1:length(covariate_labels))
-    ) %>% 
-    group_by(category, attribute, j_label) %>% 
-    summarize(
-      mean = mean(Gamma),
-      ci_lower = quantile(Gamma, .025),
-      ci_upper = quantile(Gamma, .975),
-      gt_zero = if_else(ci_lower > 0 & ci_upper > 0, 1, 0),
-      lt_zero = if_else(ci_lower < 0 & ci_upper < 0, -1, 0)
-    )
-
-  # Heatmap of Gamma matrix.
-  plot_heatmap <- posterior_means %>% 
-    mutate(
-      gt_lt_zero = gt_zero + lt_zero,
-      Coefficients = factor(
-        gt_lt_zero, 
-        levels = -1:1,
-        labels = c("Negative", "Not Significant", "Positive"))
-    ) %>% 
-    ggplot(aes(x = j_label, y = attribute, fill = Coefficients)) +
-    geom_tile(color = "white", size = 0.25) +
-    # scale_fill_brewer(palette = "Blues") +
-    scale_fill_manual(values = c(clrs$orange, "grey80", clrs$olive)) +
-    scale_x_discrete(expand = c(0.001, 0.001)) +
-    scale_y_discrete(expand = c(0.001, 0.001)) +
-    # guides(fill = guide_legend(override.aes = list(key.height = 0.5, key.width = 0.5))) +
-    guides(fill = guide_legend(keywidth = 0.5, keyheight = 0.5)) +
-    theme_ngo(base_size = 14) +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-          legend.position = "bottom",
-          strip.placement = "outside") +
-    labs(
-      title = plot_title,
-      x = "Covariates",
-      y = "Attribute Levels"
-    ) + 
-    # facet_wrap(~ category, ncol = 1, scales = "free_y")
-    facet_grid(vars(category), scales = "free_y", space = "free_y")
-}
-
-plot_heatmap
-ggsave(plot_heatmap, filename = here("analysis", "output", "figures", "q2-heatmap.pdf"),
-       width = 26/3, height = 6.5, units = "in", device = cairo_pdf)
-ggsave(plot_heatmap, filename = here("analysis", "output", "figures", "q2-heatmap.png"),
-       width = 26/3, height = 6.5, units = "in", type = "cairo", dpi = 300)
-
-# Save plot
-if (public_affairs == 1) file_name <- paste("public-affairs_coefficient-matrix.png")
-if (political_ideology == 1) file_name <- paste("political-ideology_coefficient-matrix.png")
-if (social_views == 1) file_name <- paste("social-views_coefficient-matrix.png")
-if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_coefficient-matrix.png")
-if (demographics == 1) file_name <- paste("demographics_coefficient-matrix.png")
-if (public_political == 1) file_name <- paste("public-political_coefficient-matrix.png")
-if (public_political_social == 1) file_name <- paste("public-political-social_coefficient-matrix.png")
-if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_coefficient-matrix.png")
-if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_coefficient-matrix.png")
-ggsave(
-  file_name,
-  path = here::here("analysis", "output", "figures"),
-  width = 12,
-  height = 6,
-  units = "in"
-)
-```
-
 # Original computing environment

### 2021-09-03 analysis/04_figs-tables.Rmd

@@
 
+if (intercept != 1) {
   # Extract covariate labels
@@
     mutate_at(vars(covariate, label, covariates_long), list(fct_inorder))
+}
 
 # Join level and covariate labels to draws
-draws %>% 
-  left_join(level_lookup, by = "i") %>% 
+draws <- draws %>% 
+  left_join(level_lookup, by = "i")
+
+if (intercept != 1) {
+draws <- draws %>% 
   left_join(covariate_lookup, by = "j")
+}
 ```
@@
 
+# Causal pathway
+
+Our theory and hypotheses are laid out in the causal pathway below.
+Organizational factors (**O**, or organizational practices like financial disclosure and accountability practices; **I**, or issue area; and **F**, or funding) all influence the decision to donate (**D**).
+Structural factors like an NGO's relationship with its host government (**G**) also influence donation behavior, but the relationship itself is shaped by both funding and issue area.
+
+```{r causal-dag, fig.width=13/3, fig.height=2}
+node_colors <- tribble(
+  ~name, ~type,
+  "D", "Outcome",
+  "I", "Organizational factor",
+  "F", "Organizational factor",
+  "O", "Organizational factor",
+  "G", "Structural factor"
+) %>% 
+  mutate(type = fct_inorder(type))
+
+# Set up DAG structure
+theory_dag <- dagify(D ~ I + F + O + G,
+                     G ~ I + F,
+                     outcome = "D",
+                     exposure = "C") %>% 
+  tidy_dagitty(layout = "dh", seed = 1234)
+
+# Add node types/colors to DAG data
+theory_dag$data <- theory_dag$data %>% 
+  left_join(node_colors, by = "name")
+
+# Make DAG plot
+plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
+  geom_dag_point(size = 6, mapping = aes(color = type)) +
+  geom_dag_edges(start_cap = circle(4, "mm"),
+                 end_cap = circle(4, "mm")) +
+  geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
+  scale_color_manual(values = c(clrs$blue, clrs$red, clrs$orange), name = NULL) +
+  theme_ngo() +
+  theme(panel.grid = element_blank(),
+        panel.border = element_blank(),
+        axis.title = element_blank(),
+        axis.text = element_blank())
+
+# Show and save plot
+plot_dag
+ggsave(plot_dag, filename = here("analysis", "output", "figures", "causal-path.pdf"),
+       width = 13/3, height = 2, units = "in", device = cairo_pdf)
+ggsave(plot_dag, filename = here("analysis", "output", "figures", "causal-path.png"),
+       width = 13/3, height = 2, units = "in", type = "cairo", dpi = 300)
+```
+
+# Sample details
+
+```{r}
+vars_to_summarize <- tribble(
+  ~category, ~variable, ~clean_name,
+  "Demographics", "Q5.12", "Gender",
+  "Demographics", "Q5.17", "Age",
+  "Demographics", "Q5.13", "Marital status",
+  "Demographics", "Q5.14", "Education",
+  "Demographics", "Q5.15", "Income",
+  "Attitudes toward charity", "Q2.5", "Frequency of donating to charity",
+  "Attitudes toward charity", "Q2.6", "Amount of donations to charity last year",
+  "Attitudes toward charity", "Q2.7_f", "Importance of trusting charities",
+  "Attitudes toward charity", "Q2.8_f", "Level of trust in charities",
+  "Attitudes toward charity", "Q2.10", "Frequency of volunteering",
+  "Politics, ideology, and religion", "Q2.1", "Frequency of following national news",
+  "Politics, ideology, and religion", "Q5.7", "Traveled to a developing country",
+  "Politics, ideology, and religion", "Q5.1", "Voted in last election",
+  "Politics, ideology, and religion", "Q5.6_f", "Trust in political institutions and the state",
+  "Politics, ideology, and religion", "Q5.2_f", "Political ideology",
+  "Politics, ideology, and religion", "Q5.4", "Involvement in activist causes",
+  "Politics, ideology, and religion", "Q5.8", "Frequency of attending religious services",
+  "Politics, ideology, and religion", "Q5.9", "Importance of religion"
+)
+
+summarize_factor <- function(x) {
+  output <- table(x) %>% 
+    as_tibble() %>% 
+    magrittr::set_colnames(., c("level", "count")) %>% 
+    mutate(level = factor(level, levels = levels(x), ordered = TRUE)) %>%
+    mutate(prop = count / sum(count),
+           nice_prop = scales::percent(prop))
+
+  return(list(output))
+}
+
+participant_summary <- results %>% 
+  select(one_of(vars_to_summarize$variable)) %>% 
+  summarize_all(summarize_factor) %>% 
+  pivot_longer(cols = everything(), names_to = "variable", values_to = "details") %>% 
+  left_join(vars_to_summarize, by = "variable") %>% 
+  unnest(details) %>% 
+  mutate(level = as.character(level)) %>% 
+  mutate(level = case_when(
+    variable == "Q2.7_f" & level == "1" ~ "1 (not important)",
+    variable == "Q2.7_f" & level == "7" ~ "7 (important)",
+    variable == "Q2.8_f" & level == "1" ~ "1 (no trust)",
+    variable == "Q2.8_f" & level == "7" ~ "7 (complete trust)",
+    variable == "Q5.6_f" & level == "1" ~ "1 (no trust)",
+    variable == "Q5.6_f" & level == "7" ~ "7 (complete trust)",
+    variable == "Q5.2_f" & level == "1" ~ "1 (extremely liberal)",
+    variable == "Q5.2_f" & level == "7" ~ "7 (extremely conservative)",
+    variable == "Q5.15" & level == "Less than median" ~ "Less than 2017 national median ($61,372)",
+    variable == "Q5.17" & level == "Less than median" ~ "Less than 2017 national median (36)",
+    TRUE ~ level
+  )) %>% 
+  mutate(clean_name_shrunk = ifelse(clean_name == lag(clean_name), "", clean_name),
+         clean_name_shrunk = ifelse(is.na(clean_name_shrunk), 
+                                    clean_name[1], 
+                                    clean_name_shrunk),
+         category_shrunk = ifelse(category == lag(category), "", category),
+         category_shrunk = ifelse(is.na(category_shrunk), 
+                                    category[1], 
+                                    category_shrunk))
+```
+
+```{r results="asis"}
+participant_summary %>% 
+  select(" " = category_shrunk, "  " = clean_name_shrunk, 
+         "Response" = level, "N" = count, "%" = nice_prop) %>% 
+  pandoc.table.return(caption = 'Summary of individual respondent characteristics {#tbl:sample-details}',
+                      justify = "lllcc") %T>%
+  cat() %>%
+  cat(file = here("analysis", "output", "tables", "tbl-sample-details.md"))
+```
+
+# Results
+
 ## Plot marginals
@@
   draws %>%
-    mutate(
-      levels = factor(i, labels = level_labels)
-    ) %>%
-    ggplot(aes(x = Gamma, y = levels)) +
+    ggplot(aes(x = Gamma, y = levels_long)) +
     stat_halfeye(.width = .95) +
@@
     filter(j != 1) %>%
-    mutate(
-      levels = factor(i, labels = level_labels),
-      covariates = factor(j, labels = covariate_labels)
-    ) %>%
-    ggplot(aes(x = Gamma, y = covariates)) +
+    ggplot(aes(x = Gamma, y = covariates_long)) +
     stat_halfeye(.width = .95) +
@@
     labs(y = "Covariates") +
-    facet_wrap(~ levels, ncol = 5)
+    facet_wrap(~ levels_long, ncol = 5)
 }
@@
 We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we're unsure of the direction of that effect.
-
-# Causal pathway
-
-Our theory and hypotheses are laid out in the causal pathway below.
-Organizational factors (**O**, or organizational practices like financial disclosure and accountability practices; **I**, or issue area; and **F**, or funding) all influence the decision to donate (**D**).
-Structural factors like an NGO's relationship with its host government (**G**) also influence donation behavior, but the relationship itself is shaped by both funding and issue area.
-
-```{r causal-dag, fig.width=13/3, fig.height=2}
-node_colors <- tribble(
-  ~name, ~type,
-  "D", "Outcome",
-  "I", "Organizational factor",
-  "F", "Organizational factor",
-  "O", "Organizational factor",
-  "G", "Structural factor"
-) %>% 
-  mutate(type = fct_inorder(type))
-
-# Set up DAG structure
-theory_dag <- dagify(D ~ I + F + O + G,
-                     G ~ I + F,
-                     outcome = "D",
-                     exposure = "C") %>% 
-  tidy_dagitty(layout = "dh", seed = 1234)
-
-# Add node types/colors to DAG data
-theory_dag$data <- theory_dag$data %>% 
-  left_join(node_colors, by = "name")
-
-# Make DAG plot
-plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
-  geom_dag_point(size = 6, mapping = aes(color = type)) +
-  geom_dag_edges(start_cap = circle(4, "mm"),
-                 end_cap = circle(4, "mm")) +
-  geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
-  scale_color_manual(values = c(clrs$blue, clrs$red, clrs$orange), name = NULL) +
-  theme_ngo() +
-  theme(panel.grid = element_blank(),
-        panel.border = element_blank(),
-        axis.title = element_blank(),
-        axis.text = element_blank())
-
-# Show and save plot
-plot_dag
-ggsave(plot_dag, filename = here("analysis", "output", "figures", "causal-path.pdf"),
-       width = 13/3, height = 2, units = "in", device = cairo_pdf)
-ggsave(plot_dag, filename = here("analysis", "output", "figures", "causal-path.png"),
-       width = 13/3, height = 2, units = "in", type = "cairo", dpi = 300)
-```
-
-# Sample details
-
-```{r}
-vars_to_summarize <- tribble(
-  ~category, ~variable, ~clean_name,
-  "Demographics", "Q5.12", "Gender",
-  "Demographics", "Q5.17", "Age",
-  "Demographics", "Q5.13", "Marital status",
-  "Demographics", "Q5.14", "Education",
-  "Demographics", "Q5.15", "Income",
-  "Attitudes toward charity", "Q2.5", "Frequency of donating to charity",
-  "Attitudes toward charity", "Q2.6", "Amount of donations to charity last year",
-  "Attitudes toward charity", "Q2.7_f", "Importance of trusting charities",
-  "Attitudes toward charity", "Q2.8_f", "Level of trust in charities",
-  "Attitudes toward charity", "Q2.10", "Frequency of volunteering",
-  "Politics, ideology, and religion", "Q2.1", "Frequency of following national news",
-  "Politics, ideology, and religion", "Q5.7", "Traveled to a developing country",
-  "Politics, ideology, and religion", "Q5.1", "Voted in last election",
-  "Politics, ideology, and religion", "Q5.6_f", "Trust in political institutions and the state",
-  "Politics, ideology, and religion", "Q5.2_f", "Political ideology",
-  "Politics, ideology, and religion", "Q5.4", "Involvement in activist causes",
-  "Politics, ideology, and religion", "Q5.8", "Frequency of attending religious services",
-  "Politics, ideology, and religion", "Q5.9", "Importance of religion"
-)
-
-summarize_factor <- function(x) {
-  output <- table(x) %>% 
-    as_tibble() %>% 
-    magrittr::set_colnames(., c("level", "count")) %>% 
-    mutate(level = factor(level, levels = levels(x), ordered = TRUE)) %>%
-    mutate(prop = count / sum(count),
-           nice_prop = scales::percent(prop))
-
-  return(list(output))
-}
-
-participant_summary <- results %>% 
-  select(one_of(vars_to_summarize$variable)) %>% 
-  summarize_all(summarize_factor) %>% 
-  pivot_longer(cols = everything(), names_to = "variable", values_to = "details") %>% 
-  left_join(vars_to_summarize, by = "variable") %>% 
-  unnest(details) %>% 
-  mutate(level = as.character(level)) %>% 
-  mutate(level = case_when(
-    variable == "Q2.7_f" & level == "1" ~ "1 (not important)",
-    variable == "Q2.7_f" & level == "7" ~ "7 (important)",
-    variable == "Q2.8_f" & level == "1" ~ "1 (no trust)",
-    variable == "Q2.8_f" & level == "7" ~ "7 (complete trust)",
-    variable == "Q5.6_f" & level == "1" ~ "1 (no trust)",
-    variable == "Q5.6_f" & level == "7" ~ "7 (complete trust)",
-    variable == "Q5.2_f" & level == "1" ~ "1 (extremely liberal)",
-    variable == "Q5.2_f" & level == "7" ~ "7 (extremely conservative)",
-    variable == "Q5.15" & level == "Less than median" ~ "Less than 2017 national median ($61,372)",
-    variable == "Q5.17" & level == "Less than median" ~ "Less than 2017 national median (36)",
-    TRUE ~ level
-  )) %>% 
-  mutate(clean_name_shrunk = ifelse(clean_name == lag(clean_name), "", clean_name),
-         clean_name_shrunk = ifelse(is.na(clean_name_shrunk), 
-                                    clean_name[1], 
-                                    clean_name_shrunk),
-         category_shrunk = ifelse(category == lag(category), "", category),
-         category_shrunk = ifelse(is.na(category_shrunk), 
-                                    category[1], 
-                                    category_shrunk))
-```
-
-```{r results="asis"}
-participant_summary %>% 
-  select(" " = category_shrunk, "  " = clean_name_shrunk, 
-         "Response" = level, "N" = count, "%" = nice_prop) %>% 
-  pandoc.table.return(caption = 'Summary of individual respondent characteristics {#tbl:sample-details}',
-                      justify = "lllcc") %T>%
-  cat() %>%
-  cat(file = here("analysis", "output", "tables", "tbl-sample-details.md"))
-```
-
-# Results
 

### 2021-09-11 README.Rmd
De-packagify the project

@@
 
-1. Open the compendium as a project in RStudio (double click on `donorheuristics.proj`).
-2. Build the compendium package by clicking on the "Install and Restart" button in RStudio's "Build" panel.
-
-You should now be able to run `library(donorheuristics)` and reproduce all the findings in the paper (as well as the paper itself).
-
 To reproduce the analysis, run `make build` from RStudio's "Terminal" panel. Open `analysis/_site/` to see the results. Run `make serve` to serve the site at <http://localhost:7000>.
@@
 The most current version of this analysis notebook is accessible online at <https://stats.andrewheiss.com/why-donors-donate/>.
-- `/R`: Various project-specific R scripts and functions go here. These are built as part of the package and are accessible after loading `library(donorheuristics)`.
+- `/R`: Various project-specific R scripts and functions go here.
 - `/manuscript`: The actual writing goes here.
@@
     library(tidyverse)
-    library(donorheuristics)
     library(here)
+
+    # Load custom plot functions
+    source(here("R", "graphics.R"))
 

### 2021-09-11 analysis/03_analysis.Rmd
De-packagify the project

@@
 library(tidyverse)
-library(donorheuristics)
 library(rstan)

### 2021-09-11 analysis/04_figs-tables.Rmd
De-packagify the project

@@
 library(magrittr)
-library(donorheuristics)
 library(tidybayes)
@@
 library(here)
+
+# Load custom plot functions
+source(here("R", "graphics.R"))
 

### 2021-09-11 R/donorheuristics-package.R

@@ -1,9 +1,0 @@
-#' The 'donorheuristics' package.
-#'
-#' @description Research on how donors respond to organizational and structural
-#'   NGO characteristics
-#'
-#' @docType package
-#' @name donorheuristics-package
-#' @aliases donorheuristics
-NULL

### 2021-09-21 analysis/04_figs-tables.Rmd
Contrasts pt.1

--- 2021-09-03 analysis/04_figs-tables.Rmd
@@
 ## Plot contrasts
+```{r}
+
+# Organization Intercept Contrasts
+
+draws_A <- subset(intercept, i==1, select = Gamma)
+draws_G <- subset(intercept, i==2, select = Gamma)
+draws_O <- subset(intercept, i==3, select = Gamma)
+draws_R <- subset(intercept, i==4, select = Gamma)
+draws_con <- tibble(
+  "A-G" = draws_A-draws_G,
+  "A-O" = draws_A-draws_O,
+  "A-R" = draws_A-draws_R,
+  "G-O" = draws_G-draws_O,
+  "G-R" = draws_G-draws_R,
+  "O-R" = draws_O-draws_R
+)
+
+c1 <- bind_rows(draws_con$`A-G`, draws_con$`A-O`)
+c1 <- bind_rows(c1, draws_con$`A-R`)
+c1 <- bind_rows(c1, draws_con$`G-O`)
+c1 <- bind_rows(c1, draws_con$`G-R`)
+c1 <- bind_rows(c1, draws_con$`O-R`)
+
+c1$code[1:2000] <- 1
+c1$code[2001:4000] <- 2
+c1$code[4001:6000] <- 3
+c1$code[6001:8000] <- 4
+c1$code[8001:10000] <- 5
+c1$code[10001:12000] <- 6
+
+lcon <- c("A-G", "A-O", "A-R", "G-O", "G-R", "O-R")
+ggplot(c1, aes(x=Gamma)) +
+    stat_halfeye(.width = .95) +
+    geom_vline(xintercept = 0, color = "grey") +
+    labs(y = "Attribute Levels") + facet_wrap(~code)
+```
 

### 2021-09-21 analysis/04_figs-tables.Rmd
Cleaned up contrasts for hypothesis 1

--- 2021-09-03 analysis/04_figs-tables.Rmd
@@
 # Load draws
-intercept <- 0                            # Intercept-only
-public_affairs <- 1                       # Public affairs
+intercept <- 1                            # Intercept-only
+public_affairs <- 0                       # Public affairs
 political_ideology <- 0                   # Political ideology
@@
 
-A better approach to address the hypotheses (taken from the former 03b and 03c).
+Another approach to address the hypotheses is to plot contrasts.
 
-- We theorize that structural characteristics like an NGO’s host-country political and legal environment can serve as heuristics and shortcuts for donors.
-- Donors who see that an NGO faces general legal trouble abroad will use that knowledge to decide whether or not to donate.
-- We also theorize that non-structural organizational characteristics like managerial practices, funding sources, and issue area also serve as heuristics and influence donation patterns.
-- In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics.
-We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we’re unsure of the direction of that effect.
+### Hypothesis 1, Branding
 
-> In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics.
-We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we're unsure of the direction of that effect.
+```{r branding-contrasts}
+# Pull the posterior draws for the organizations and compute contrasts
+contrasts <- tibble(
+  amnesty = draws %>% filter(level == "Amnesty International") %>% select(Gamma) %>% pull(),
+  greenpeace = draws %>% filter(level == "Greenpeace") %>% select(Gamma) %>% pull(),
+  oxfam = draws %>% filter(level == "Oxfam") %>% select(Gamma) %>% pull(),
+  red_cross = draws %>% filter(level == "Red Cross") %>% select(Gamma) %>% pull()
+) %>% 
+  mutate(
+    oxfam_amnesty = oxfam - amnesty,
+    oxfam_greenpeace = oxfam - greenpeace,
+    red_cross_amnesty = red_cross - amnesty,
+    red_cross_greenpeace = red_cross - greenpeace,
+  )
+
+# Plot the contrasts
+contrasts %>%
+  pivot_longer(oxfam_amnesty:red_cross_greenpeace, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis01.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
+```
+
+> Donors will be more likely to donate to Oxfam and Red Cross compared to Amnesty International and Greenpeace [Mechanism: awareness of need and contentiousness of issue area]
+
+Donors are indeed more likely to donate to Red Cross compared to Amnesty International and Greenpeace.
+However, compared to Amnesty International and Greenpeace, donors are less likely to donate to Oxfam.
+In fact, there is a negligible difference between donors likelihood to donate to Oxfam and Amnesty International.
+
+### Hypothesis 2, Government Crackdown
+
+```{r crackdown-contrasts}
+
+```
+
+### Hypothesis 3, Issue Area
+
+```{r issue-contrasts}
+
+```
+
+### Hypothesis 4, Funding Sources
+
+```{r funding-contrasts}
+
+```
+
+### Hypothesis 5, Organizational Practices
+
+```{r practices-contrasts}
+
+```
 

### 2021-09-22 _targets.R
Use targets to download rds files from OSF so we don't track them in git

@@ -1,0 +1,35 @@
+# Packages,  options, settings, &c. ---------------------------------------
+
+# Packages accessible just for this _targets.R file
+library(targets)
+library(tarchetypes)
+library(tibble)
+suppressPackageStartupMessages(library(dplyr))
+
+# Packages accessible in every target
+tar_option_set(packages = c("tidyverse", "here", "fs", "withr"))
+
+# Options for this _targets.R file and all targets
+options(tidyverse.quiet = TRUE,
+        dplyr.summarise.inform = FALSE)
+
+set.seed(9059)  # From random.org
+
+
+# Functions ---------------------------------------------------------------
+
+source("R/funs_data.R")
+
+# here::here() returns an absolute path, which then gets stored in tar_meta and
+# becomes computer-specific (i.e. /Users/andrew/Research/blah/thing.Rmd).
+# There's no way to get a relative path directly out of here::here(), but
+# fs::path_rel() works fine with it (see
+# https://github.com/r-lib/here/issues/36#issuecomment-530894167)
+here_rel <- function(...) {fs::path_rel(here::here(...))}
+
+
+# Actual pipeline ---------------------------------------------------------
+
+list(
+  osf_file_targets
+)

### 2021-09-22 README.Rmd
Long-awaited README update

@@
 
-```{r, echo = FALSE}
+```{r setup, include=FALSE}
 knitr::opts_chunk$set(
@@
   comment = "#>",
-  fig.path = "README-"
+  fig.path = "README-",
+  fig.retina = 3
 )
@@
 Authors <- "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
-Year <- "2019"
+Year <- "2021"
 ```
@@
 
-[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Christopher Newport University  
+[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Lewis & Clark College  
 [Marc Dotson](https://marriottschool.byu.edu/directory/details?id=50683) • Brigham Young University  
-[Andrew Heiss](https://www.andrewheiss.com) • Brigham Young University
+[Andrew Heiss](https://www.andrewheiss.com) • Georgia State University
 
@@
 ## How to download and install
+
+**NB: These instructions are all out of date and will be updated to match how the project is actually run, eventually.
+We're converting this project from a `make`-based build system to a [{targets}](https://books.ropensci.org/targets/)-based build system, which is easier to manage and requires fewer external dependencies.**
+
+*This stuff is accurate*:
+
+Because the posterior draws from the models are large and take forever to make, we've saved the results as `.rds` files.
+However, because those files are fairly big and we don't want to track them with git, we've stored them at this project's [OSF page](https://osf.io/r59xz/) in [OSF's internal storage system](https://osf.io/r59xz/files/).
+Running `targets::tar_make(starts_with("file_"))` (or just `targets::tar_make()` in general) will trigger a function (`get_from_osf()`) that will automatically download all the `.rds` files and place them in `data/raw_data/posterior_draws`, which is not tracked by git (and which should be set to not sync in Dropbox).
+
+*This stuff is out of date*:
 

### 2021-09-22 _targets.R

@@ -31,5 +31,10 @@ here_rel <- function(...) {fs::path_rel(here::here(...))}
 # Actual pipeline ---------------------------------------------------------
 
 list(
-  osf_file_targets
+  # Download posterior draws data from OSF
+  osf_file_targets,
+
+  # Knit the README
+  tar_render(readme, here_rel("README.Rmd"),
+             output_options = list(html_preview = FALSE))
 )

### 2021-09-22 README.Rmd
Add instructions for ignoring Dropbox files

@@
 However, because those files are fairly big and we don't want to track them with git, we've stored them at this project's [OSF page](https://osf.io/r59xz/) in [OSF's internal storage system](https://osf.io/r59xz/files/).
-Running `targets::tar_make(starts_with("file_"))` (or just `targets::tar_make()` in general) will trigger a function (`get_from_osf()`) that will automatically download all the `.rds` files and place them in `data/raw_data/posterior_draws`, which is not tracked by git (and which should be set to not sync in Dropbox).
+Running `targets::tar_make(starts_with("file_"))` (or just `targets::tar_make()` in general) will trigger a function (`get_from_osf()`) that will automatically download all the `.rds` files and place them in `data/raw_data/posterior_draws`, which is not tracked by git.
+
+If you're part of the research team and using Dropbox, make sure you make it so that Dropbox ignores the `posterior_draws` folder.
+There are [complete instructions for doing that here](https://help.dropbox.com/files-folders/restore-delete/ignored-files).
+In short, run one of these commands in your terminal:
+
+```sh
+# On macOS
+cd path/to/this/project
+xattr -w com.dropbox.ignored 1 data/raw_data/posterior_draws
+
+# On Windows (with PowerShell)
+cd path/to/this/project
+Set-Content -Path 'data/raw_data/posterior_draws' -Stream com.dropbox.ignored -Value 1
+```
+
+The icon next to the `posterior_draws` folder should then change to a gray minus sign, which means that the folder is being ignored.
+
+---
 

### 2021-09-22 README.Rmd
Add note about RStudio terminal

@@
 # On macOS
-cd path/to/this/project
+cd path/to/this/project  # Not needed if you use the terminal panel in RStudio after opening the project
 xattr -w com.dropbox.ignored 1 data/raw_data/posterior_draws
@@
 # On Windows (with PowerShell)
-cd path/to/this/project
+cd path/to/this/project  # Not needed if you use the terminal panel in RStudio after opening the project
 Set-Content -Path 'data/raw_data/posterior_draws' -Stream com.dropbox.ignored -Value 1

### 2021-09-22 README.Rmd
Also ignore _targets

--- 2021-09-22 README.Rmd
@@
 
-If you're part of the research team and using Dropbox, make sure you make it so that Dropbox ignores the `posterior_draws` folder.
+### Ignoring things in Dropbox
+
+If you're part of the research team and using Dropbox, make sure you make it so that Dropbox ignores the `posterior_draws` folder and the `_targets` folder.
 There are [complete instructions for doing that here](https://help.dropbox.com/files-folders/restore-delete/ignored-files).
@@
 # On macOS
-cd path/to/this/project
+cd path/to/this/project  # Not needed if you use the terminal panel in RStudio after opening the project
+xattr -w com.dropbox.ignored 1 _targets
 xattr -w com.dropbox.ignored 1 data/raw_data/posterior_draws
@@
 # On Windows (with PowerShell)
-cd path/to/this/project
+cd path/to/this/project  # Not needed if you use the terminal panel in RStudio after opening the project
+Set-Content -Path '_targets' -Stream com.dropbox.ignored -Value 1
 Set-Content -Path 'data/raw_data/posterior_draws' -Stream com.dropbox.ignored -Value 1

### 2021-09-25 analysis/04_figs-tables.Rmd
Answers for main effect hypotheses.

@@
 
+> Donors will show increased willingness to donate to NGOs that are facing government crackdown or criticism [Mechanism: Governments wouldn't be cracking down on them if they didn't perceive a threat from them which means organizations implementing their missions effectively.
+This perception of efficacy leads to increased donations.]
+
+Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism.
+This decreased likelihood to donate is also greater for NGOs under crackdown compared to those under criticism.
+
 ### Hypothesis 3, Issue Area
@@
 ```
+> Donors will show increased willingness to donate to NGOs working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights)
+
+Donors appear to be sensitive to NGO issue area when they are considering to donate.
+Emergency response was the most favored issue area by donors, and experienced the highest likelihood of receiving donations.
+While this partially matches the claim of the hypothesis, donors showed the least likelihood to donate to refugee relief NGOs, which was contrary to our expectations.
+It is worth noting that there is some overlap between the intervals of the issue areas, which would suggest that their effect isn't as significant as other factors.
 
@@
 ```
+> Donors will show increased willingness to donate to NGOs that are funded primarily by numerous small private donors compared to NGOs that are funded by a handful of wealthy private donors and government grants [Mechanism: Perception of efficacy - your contribution matters as a small donor.
+Government funding may also imply lack of independence of government which can reduce the efficiency of an organization.]
+
+As stated in the hypothesis, donors show increased willingness to donate to NGOs funded by numerous small private donors, as opposed to those funded by a handful of wealthy private donors or government grants.
 
@@
 ```
+> Donors will show increased willingness to donate to NGOs that are financially transparent [Mechanism: Perception of efficacy]
+
+> Donors should be no more or less likely to donate to NGOs that are accountable and hold regular third party audits [Mechanism: Donors don't necessarily seek assurance through third-party programs/audits and charity watchdogs, but rather through word of mouth, personal scrutiny and local networks]
+
+When comparing organizational practices, donors show an increased likelihood to donate to NGOs that are financially transparent as well as NGOs that are accountable and hold regular third party audits.
+Although financial transparency was hypothesized to increase donor's willingness to donate, we believed accountability practices would have an insignificant effect on influencing donor's willingness to donate; our analysis indicates that this is not the case.
 

### 2021-10-02 analysis/04_figs-tables.Rmd
Added contrasts plots for remaining hypotheses, formatting for answering hypotheses.

@@
 ```{r crackdown-contrasts}
+# Pull the posterior draws for government crackdown
 
+# Reference Level = Friendly relationship with government
+contrasts <- tibble(
+  under_crackdown = draws %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
+  criticized = draws %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
+  )
+
+# Plot the contrasts
+contrasts %>%
+  pivot_longer(under_crackdown:criticized, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis02.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
 ```
@@
 
-### Hypothesis 3, Issue Area
+> Donors will show increased willingness to donate to Oxfam and Red Cross when they are facing government crackdown or criticism compared to when Amnesty or Greenpeace is facing crackdown.
+
+[Answer]
 
 ```{r issue-contrasts}
+# Pull the posterior draws for issue area
 
+# Reference Level = Emergency Response
+contrasts <- tibble(
+  environment = draws %>% filter(level == "Environment") %>% select(Gamma) %>% pull(),
+  human_rights = draws %>% filter(level == "Human rights") %>% select(Gamma) %>% pull(),
+  refugee_relief = draws %>% filter(level == "Refugee relief") %>% select(Gamma) %>% pull()
+  )
+
+# Plot the contrasts
+contrasts %>%
+  pivot_longer(environment:refugee_relief, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis03.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
 ```
@@
 
+> Donors will show increased willingness to donate to NGOs facing government crackdown/criticism working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights) [Mechanisms: Perceptions of deservingness of NGOs dealing with emergency response and refugee relief.
+Donors are also more likely to donate to programs that are compatible with government preferences and have easily measurable outputs, which environment and human rights programs often lack.
+NGOs working on more contentious issue areas may be expelled or shut down, which would be a waste of donor resources, make it less likely that they donate to these groups.]
+
+[Answer]
+
 ### Hypothesis 4, Funding Sources
@@
 ```{r funding-contrasts}
+# Pull the posterior draws for funding sources
+
+# Reference Level = Funded primarily by many small private donations
+contrasts <- tibble(
+  few_wealthy_private_donors = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
+  government_grants = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
+  )
+
+# Plot the contrasts
+contrasts %>%
+  pivot_longer(few_wealthy_private_donors:government_grants, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis04.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
 
@@
 
+> Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors
+
+[Answer]
+
 ### Hypothesis 5, Organizational Practices
@@
 ```{r practices-contrasts}
+
+# Pull the posterior draws for organizational practices
+
+contrasts <- tibble(
+  financial_transparency = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
+  accountibility = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
+  )
+
+# Plot the contrasts
+contrasts %>%
+  pivot_longer(few_wealthy_private_donors:government_grants, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis04.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
 
@@
 Although financial transparency was hypothesized to increase donor's willingness to donate, we believed accountability practices would have an insignificant effect on influencing donor's willingness to donate; our analysis indicates that this is not the case.
+
+> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and are funded primarily by numerous small private donors
+
+[Answer]
+
+> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief)
+
+[Answer]
+
+> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief) and are funded by numerous small donors
+
+[Answer]
+
+> Donors should be no more or less likely to donate to NGOs that are accountable and hold regular third party audits [Mechanism: Donors don't necessarily seek assurance through third-party programs/audits and charity watchdogs, but rather through word of mouth, personal scrutiny and local networks]
+
+[Answer]
 

### 2021-10-06 analysis/04_figs-tables.Rmd
More hypotheses answers using market simulator.

@@
 
-[Answer]
+Market share when criticized:
+A = 0.130767214
+G = 0.212870677
+O = 0.218368082
+R = 0.437994028
+
+Market share under crackdown:
+A = 0.130767214
+G = 0.212870677
+O = 0.218368082
+R = 0.437994028
+
+Tentative yes, O and R claim greater market share compared to A and G
 
@@
 
-[Answer]
+Market shares:
+
+ER = 0.318332453
+EV = 0.203877752
+HR = 0.159886134
+RR = 0.31790366
+
+ER>RR>EV>HR, evidence that hypothesis is correct
 
@@
 
-[Answer]
+Market shares:
+
+numerous donors/not under crackdown = 0.247967551
+numerous donors/under crackdown = 0.271016037
+few donors/under crackdown = 0.26213647
+government grants/under crackdown = 0.218879942
+
+Though numerous donors/under crackdown has the largest market share, the difference between them is almost insignificant. Personally, this evidence doesn't seem convincing.
 
@@
 contrasts <- tibble(
-  financial_transparency = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
-  accountibility = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
+  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
+  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
   )
@@
 contrasts %>%
-  pivot_longer(few_wealthy_private_donors:government_grants, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer(financial_transparency:accountability, names_to = "level", values_to = "Gamma") %>% 
   ggplot(aes(x = Gamma, y = level)) +
@@
 ggsave(
-  "contrasts_hypothesis04.png",
+  "contrasts_hypothesis05.png",
   path = here::here("analysis", "output", "figures"),
@@
 
-[Answer]
+Expected utility (Transparency/Few donors/Under crackdown):
+
+(1/0/1)	= 3.346877215
+(1/1/1)* =	3.237220167
+(1/1/0)	= 2.961911648
+(0/1/1)	= 2.174492071
+(0/0/1)	= 2.248150447
+(0/0/0)	= 2.056957096
+(1/0/0)	= 3.062242941
+
+Market shares: 
+(1/0/1)	= 0.175340698
+(1/1/1)* =	0.169595837
+(1/1/0)	= 0.155172605
+(0/1/1)	= 0.113920211
+(0/0/1)	= 0.117779124
+(0/0/0)	= 0.10776263
+(1/0/0)	= 0.160428895
+
+Not sure if this is the best way to do triple interaction, but I gave it a shot.
+I included expected utility as well as market share, as market share may understate the difference in willingness to donate (market share is split between 7 orgs instead of 4).
+
+NGOs that are financially transparent, are supported by few donors, and are under crackdown receive the second largest share of the market--they are topped by firms which are transparent and under crackdown, but are supported by numerous donors.
+This would contradict the hypothesis, assuming I did this correctly.
 
@@
 
-[Answer]
+Market share:
 
+Accountability = 0.566631341
+No Accountability = 0.433368659
+
+The difference is large enough to suggest that accountability increases donors likelihood to donate, contrary to the hypothesis.
 ## Model fit table

### 2021-10-15 analysis/01_experimental-design.Rmd
De-packagify the project
Included an index-coded design for computing contrasts

@@
 
-```{r check-design, warning=FALSE, message=FALSE}
+```{r load-data, warning=FALSE, message=FALSE}
 library(tidyverse)
 library(donorheuristics)
+library(fastDummies)
 library(here)
@@
 
-```{r check-design, warning=FALSE, message=FALSE}
+```{r dummy-design, warning=FALSE, message=FALSE}
 # Convert the attributes in design into factors
@@
 
+# Index-code the design
+
+We also need to consider how we are computing contrasts to answer our specified hypotheses.
+To do so, we index-code where every attribute level is included such that every attribute is its own implied intercept.
+Note that for a non-Bayesian model, index coding in this way would not be identified.
+However, for a Bayesian model with proper priors, all parameters are identified.
+Additionally, the contrasts even of unidentified parameters are identified.
+
+```{r index-design, warning=FALSE, message=FALSE}
+# Convert the attributes in design into factors
+index_design <- as.data.frame(design)
+for(i in 4:ncol(index_design)) {
+  index_design[,i] <- as.factor(index_design[,i])
+}
+
+# Rename the variables.
+colnames(index_design)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")
+
+# Use dummy_cols() to get a index-coded version of all the attribute levels.
+index_design <- dummy_cols(
+  index_design, 
+  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
+  remove_first_dummy = FALSE,
+  remove_selected_columns = TRUE
+)
+
+# Rename the index variables.
+colnames(index_design)[4:21] <- c(
+  str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
+  str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
+)
+
+# Save index-coded design output
+write.csv(index_design, here("data", "derived_data", "index_design.csv"))
+```
+
 # Original computing environment

### 2021-10-15 analysis/02_clean-data.Rmd
De-packagify the project
Cleaned and finalized a dummy-coded (including brand) design and an index-coded design

@@
 ```{r transform-design}
-# Load design
+# Load the dummy design.
 design <- read_csv(here::here("data", "derived_data", "dummy_design.csv")) %>%
-  select(-X1) %>%
+  select(-`...1`) %>%
   rename(
@@
 
-# Create the array for design X.
+# Create the arrays for a design with a brand intercept.
 X <- array(
@@
         as_vector()
-      # Fill in org1 to complte org intercept.
+      # Fill in org1 to complete org intercept.
       X_s[p, "org1"] <- ifelse(sum(X_p) == 1, 0, 1)
@@
     X[n, s,,] <- rbind(X_s, rep(0, ncol(X_s))) %>% as.matrix()
+  }
+}
+
+# Load the index design.
+index_design <- read_csv(here::here("data", "derived_data", "index_design.csv")) %>%
+  select(-`...1`) %>%
+  rename(
+    version = question_set,
+    task = question,
+    alt = choice
+  )
+
+# Create the arrays for the fully dummy and index designs.
+X_dummy <- array(
+  data = NA,
+  dim = c(
+    nrow(data),             # Number of respondents.
+    max(design$task),       # Number of choice tasks per respondent.
+    (max(design$alt) + 1),  # Number of product alternatives per choice task.
+    (ncol(design) - 3)      # Number of (estimable) attribute levels.
+  )
+)
+
+X_index <- array(
+  data = NA,
+  dim = c(
+    nrow(data),                  # Number of respondents.
+    max(index_design$task),      # Number of choice tasks per respondent.
+    (max(index_design$alt) + 1), # Number of product alternatives per choice task.
+    ncol(index_design) - 3       # Number of (estimable) attribute levels.
+  )
+)
+
+# Add the outside option coded as all zeros for the dummy and index designs.
+for (n in 1:dim(X_dummy)[1]) {
+  # Filter for respondent n.
+  X_dummy_n <- design %>% filter(version == data$version[n])
+  X_index_n <- index_design %>% filter(version == data$version[n])
+  for (s in 1:dim(X_dummy)[2]) {
+    # Filter for task s.
+    X_dummy_s <- X_dummy_n %>% 
+      filter(task == s) %>% 
+      select(org2:gov_rel3)
+    X_index_s <- X_index_n %>% 
+      filter(task == s) %>% 
+      select(org1:gov_rel3)
+    # Save modified design, including outside option.
+    X_dummy[n, s,,] <- rbind(X_dummy_s, rep(0, ncol(X_dummy_s))) %>% as.matrix()
+    X_index[n, s,,] <- rbind(X_index_s, rep(0, ncol(X_index_s))) %>% as.matrix()
   }
@@
 write_rds(X, here("data", "derived_data", "final_design.rds"))
+write_rds(X_dummy, here("data", "derived_data", "final_design_dummy.rds"))
+write_rds(X_index, here("data", "derived_data", "final_design_index.rds"))
 ```

### 2021-10-18 analysis/01_experimental-design.Rmd
Cleaned up dummy coding, removed index coding, and built out interactions for the design

--- 2020-09-01 analysis/01_experimental-design.Rmd
@@
 
-# Use the output of lm to get a dummy-coded version of the design
-dummy_design$y <- matrix(rnorm(nrow(dummy_design)), ncol=1)
-out <- lm(y ~ ., dummy_design, x = TRUE)
-dummy_design <- out$x[,-1]
-rownames(dummy_design) <- NULL
+# Use dummy_cols() to get a index-coded version of all the attribute levels.
+dummy_design <- dummy_cols(
+  dummy_design,
+  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
+  remove_first_dummy = TRUE,
+  remove_selected_columns = TRUE
+)
+
+# Rename the index variables.
+colnames(dummy_design)[4:15] <- c(
+  str_c("org", 2:4), str_c("issue", 2:4), str_c("transp", 2),
+  str_c("account", 2), str_c("fund", 2:3), str_c("gov_rel", 2:3)
+)
 
@@
 write.csv(dummy_design, here("data", "derived_data", "dummy_design.csv"))
+```
+
+# Interact-code the design
+
+We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need a specific intercept-only design with each of the needed interactions.
+
+```{r interact-design, warning=FALSE, message=FALSE}
+# Convert the attributes in design into factors
+interact_design <- as.data.frame(design)
+for(i in 4:ncol(interact_design)) {
+  interact_design[,i] <- as.factor(interact_design[,i])
+}
+
+# Rename the variables.
+colnames(interact_design)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")
+
+# Use dummy_cols() to get a dummy-coded version of all the attribute levels.
+interact_design <- dummy_cols(
+  interact_design, 
+  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
+  remove_first_dummy = FALSE,
+  remove_selected_columns = TRUE
+)
+
+# Rename the dummy-coded variables.
+colnames(interact_design)[4:21] <- c(
+  str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
+  str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
+)
+
+# Build out all the necessary interactions.
+interact_design %>% 
+  as_tibble() %>% 
+  mutate(
+    # Hypothesis 2b.
+    amnesty_criticized = org1 * gov_rel2,
+    amnesty_crackdown = org1 * gov_rel3,
+    greenpeace_criticized = org2 * gov_rel2,
+    greenpeace_crackdown = org2 * gov_rel3,
+    oxfam_criticized = org3 * gov_rel2,
+    oxfam_crackdown = org3 * gov_rel3,
+    redcross_criticized = org4 * gov_rel2,
+    redcross_crackdown = org4 * gov_rel3,
+    # Hypothesis 3b.
+    emergency_criticized = issue1 * gov_rel2,
+    emergency_crackdown = issue1 * gov_rel3,
+    environment_criticized = issue2 * gov_rel2,
+    environment_crackdown = issue2 * gov_rel3,
+    humanrights_criticized = issue3 * gov_rel2,
+    humanrights_crackdown = issue3 * gov_rel3,
+    refugees_criticized = issue4 * gov_rel2,
+    refugees_crackdown = issue4 * gov_rel3,
+    # Hypothesis 4b.
+    smalldonors_criticized = fund1 * gov_rel2,
+    smalldonors_crackdown = fund1 * gov_rel3,
+    wealthydonors_criticized = fund2 * gov_rel2,
+    wealthydonors_crackdown = fund2 * gov_rel3,
+    govgrants_criticized = fund3 * gov_rel2,
+    govgrants_crackdown = fund3 * gov_rel3,
+    # Hypothesis 4c.
+    emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
+    emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3,
+    emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,
+    environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
+    environment_wealthydonors_crackdown = issue2 * fund2 * gov_rel3,
+    environment_govgrants_crackdown = issue2 * fund3 * gov_rel3,
+    humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
+    humanrights_wealthydonors_crackdown = issue3 * fund2 * gov_rel3,
+    humanrights_govgrants_crackdown = issue3 * fund3 * gov_rel3,
+    refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
+    refugees_wealthydonors_crackdown = issue4 * fund2 * gov_rel3,
+    refugees_govgrants_crackdown = issue4 * fund3 * gov_rel3,
+    # Hypothesis 5b.
+    transp_criticized = transp1 * gov_rel2,
+    transp_crackdown = transp1 * gov_rel3,
+    nottransp = ifelse(transp1 == 0, 1, 0),
+    nottransp_criticized = nottransp * gov_rel2,
+    nottransp_crackdown = nottransp * gov_rel3,
+    # Hypothesis 5c.
+    transp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
+    transp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
+    transp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
+    transp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
+    transp_govgrants_criticized = transp1 * fund3 * gov_rel2,
+    transp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
+    nottransp_smalldonors_criticized = nottransp * fund1 * gov_rel2,
+    nottransp_smalldonors_crackdown = nottransp * fund1 * gov_rel3,
+    nottransp_wealthydonors_criticized = nottransp * fund2 * gov_rel2,
+    nottransp_wealthydonors_crackdown = nottransp * fund2 * gov_rel3,
+    nottransp_govgrants_criticized = nottransp * fund3 * gov_rel2,
+    nottransp_govgrants_crackdown = nottransp * fund3 * gov_rel3,
+    # Hypothesis 5d.
+    transp_emergency_criticized = transp1 * issue1 * gov_rel2,
+    transp_emergency_crackdown = transp1 * issue1 * gov_rel3,
+    transp_environment_criticized = transp1 * issue2 * gov_rel2,
+    transp_environment_crackdown = transp1 * issue2 * gov_rel3,
+    transp_humanrights_criticized = transp1 * issue3 * gov_rel2,
+    transp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
+    transp_refugees_criticized = transp1 * issue4 * gov_rel2,
+    transp_refugees_crackdown = transp1 * issue4 * gov_rel3,
+    nottransp_emergency_criticized = nottransp * issue1 * gov_rel2,
+    nottransp_emergency_crackdown = nottransp * issue1 * gov_rel3,
+    nottransp_environment_criticized = nottransp * issue2 * gov_rel2,
+    nottransp_environment_crackdown = nottransp * issue2 * gov_rel3,
+    nottransp_humanrights_criticized = nottransp * issue3 * gov_rel2,
+    nottransp_humanrights_crackdown = nottransp * issue3 * gov_rel3,
+    nottransp_refugees_criticized = nottransp * issue4 * gov_rel2,
+    nottransp_refugees_crackdown = nottransp * issue4 * gov_rel3,
+    # Hypothesis 5e.
+    transp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
+    transp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
+    transp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
+    transp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
+    transp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
+    transp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
+    transp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
+    transp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
+    nottransp_smalldonors_emergency_criticized = nottransp * fund1 * issue1 * gov_rel2,
+    nottransp_smalldonors_emergency_crackdown = nottransp * fund1 * issue1 * gov_rel3,
+    nottransp_smalldonors_environment_criticized = nottransp * fund1 * issue2 * gov_rel2,
+    nottransp_smalldonors_environment_crackdown = nottransp * fund1 * issue2 * gov_rel3,
+    nottransp_smalldonors_humanrights_criticized = nottransp * fund1 * issue3 * gov_rel2,
+    nottransp_smalldonors_humanrights_crackdown = nottransp * fund1 * issue3 * gov_rel3,
+    nottransp_smalldonors_refugees_criticized = nottransp * fund1 * issue4 * gov_rel2,
+    nottransp_smalldonors_refugees_crackdown = nottransp * fund1 * issue4 * gov_rel3
+  ) %>% 
+  # Drop first levels and the nottransp helper variable.
+  select(-c(contains("1"), nottransp))
+
+# Save interact-coded design output
+write.csv(interact_design, here("data", "derived_data", "interact_design.csv"))
 ```

### 2021-10-18 analysis/02_clean-data.Rmd
More cleaning up dummy-coding, removing index-coding, and adding interactions

--- 2020-11-29 analysis/02_clean-data.Rmd
@@
 ```{r transform-design}
-# Load design
-design <- read_csv(here::here("data", "derived_data", "dummy_design.csv")) %>%
-  select(-X1) %>%
+# Load the dummy design.
+dummy_design <- read_csv(here::here("data", "derived_data", "dummy_design.csv")) %>%
+  select(-`...1`) %>%
   rename(
@@
 
-# Create the array for design X.
-X <- array(
+# Create the arrays for a design with a brand intercept.
+dummy_X <- array(
   data = NA,
@@
     nrow(data),                   # Number of respondents.
-    max(design$task),       # Number of choice tasks per respondent.
-    (max(design$alt) + 1),  # Number of product alternatives per choice task.
-    (ncol(design) - 3 + 1)  # Number of (estimable) attribute levels.
+    max(dummy_design$task),       # Number of choice tasks per respondent.
+    (max(dummy_design$alt) + 1),  # Number of product alternatives per choice task.
+    (ncol(dummy_design) - 3 + 1)  # Number of (estimable) attribute levels.
+  )
+)
+
+# Load the interactions and join to the design.
+interactions_design <- dummy_design %>% 
+  left_join(
+    read_csv(here::here("data", "derived_data", "interactions.csv")) %>%
+    select(-`...1`) %>%
+    rename(
+      version = question_set,
+      task = question,
+      alt = choice
+    )
+  )
+
+# Create the arrays for a design with a brand intercept and interactions.
+interactions_X <- array(
+  data = NA,
+  dim = c(
+    nrow(data),                          # Number of respondents.
+    max(interactions_design$task),       # Number of choice tasks per respondent.
+    (max(interactions_design$alt) + 1),  # Number of product alternatives per choice task.
+    (ncol(interactions_design) - 3 + 1)  # Number of (estimable) attribute levels.
   )
@@
 # Reintroduce org1 and add the outside option coded as all zeros.
-for (n in 1:dim(X)[1]) {
+for (n in 1:dim(dummy_X)[1]) {
   # Filter for respondent n.
-  X_n <- design %>% filter(version == data$version[n])
-  for (s in 1:dim(X)[2]) {
+  dummy_X_n <- dummy_design %>% filter(version == data$version[n])
+  interactions_X_n <- interactions_design %>% filter(version == data$version[n])
+  for (s in 1:dim(dummy_X)[2]) {
     # Filter for task s and include placeholder for org1.
-    X_s <- X_n %>%
+    dummy_X_s <- dummy_X_n %>%
       filter(task == s) %>%
@@
       select(org1, org2:gov_rel3)
-    for (p in 1:(dim(X)[3]-1)) {
+    interactions_X_s <- interactions_X_n %>%
+      filter(task == s) %>%
+      mutate(org1 = 0) %>%
+      select(org1, org2:nottransp_smalldonors_refugees_crackdown)
+    for (p in 1:(dim(dummy_X)[3]-1)) {
       # Filter for task s and alt p orgs.
-      X_p <- X_n %>%
+      dummy_X_p <- dummy_X_n %>%
         filter(task == s, alt == p) %>%
@@
         as_vector()
-      # Fill in org1 to complte org intercept.
-      X_s[p, "org1"] <- ifelse(sum(X_p) == 1, 0, 1)
+      interactions_X_p <- interactions_X_n %>%
+        filter(task == s, alt == p) %>%
+        select(org2:org4) %>%
+        as_vector()
+      # Fill in org1 to complete org intercept.
+      dummy_X_s[p, "org1"] <- ifelse(sum(dummy_X_p) == 1, 0, 1)
+      interactions_X_s[p, "org1"] <- ifelse(sum(interactions_X_p) == 1, 0, 1)
     }
     # Save modified design, including outside option.
-    X[n, s,,] <- rbind(X_s, rep(0, ncol(X_s))) %>% as.matrix()
+    dummy_X[n, s,,] <- rbind(dummy_X_s, rep(0, ncol(dummy_X_s))) %>% as.matrix()
+    interactions_X[n, s,,] <- rbind(interactions_X_s, rep(0, ncol(interactions_X_s))) %>% as.matrix()
   }
@@
 write_rds(data, here("data", "derived_data", "final_data.rds"))
-write_rds(X, here("data", "derived_data", "final_design.rds"))
+write_rds(dummy_X, here("data", "derived_data", "final_design.rds"))
+write_rds(interactions_X, here("data", "derived_data", "final_interactions.rds"))
 ```

### 2021-10-18 analysis/03_analysis.Rmd
MORE!

--- 2021-09-03 analysis/03_analysis.Rmd
@@
 ```{r model-calibration, eval=FALSE}
-intercept <- 0                            # Intercept-only
-public_affairs <- 1                       # Public affairs
+intercept <- 1                            # Intercept-only
+interactions <- 1                         # Include interactions with the intercept-only model?
+public_affairs <- 0                       # Public affairs
 political_ideology <- 0                   # Political ideology
@@
 X <- read_rds(here::here("data", "derived_data", "final_design.rds"))
+if (interactions == 1) X <- read_rds(here::here("data", "derived_data", "final_interactions.rds"))
 
@@
 
+if (intercept == 0) {
   # Replace factor labels with levels
@@
     as.matrix()
+}
 
@@
 run <- list(data = data, fit = fit)
-if (intercept == 1) write_rds(run, here::here("analysis", "output", "model_runs", "intercept.rds"))
+if (intercept == 1 & interactions == 0) write_rds(run, here::here("analysis", "output", "model_runs", "intercept.rds"))
+if (intercept == 1 & interactions == 1) write_rds(run, here::here("analysis", "output", "model_runs", "interactions.rds"))
 if (public_affairs == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_affairs.rds"))

### 2021-10-18 analysis/04_figs-tables.Rmd
Prepped code for interaction contrasts

--- 2021-10-02 analysis/04_figs-tables.Rmd
@@
 
+> Donors will be more likely to donate to Oxfam and Red Cross compared to Amnesty International and Greenpeace [Mechanism: awareness of need and contentiousness of issue area]
+
 ```{r branding-contrasts}
@@
 
-> Donors will be more likely to donate to Oxfam and Red Cross compared to Amnesty International and Greenpeace [Mechanism: awareness of need and contentiousness of issue area]
-
 Donors are indeed more likely to donate to Red Cross compared to Amnesty International and Greenpeace.
@@
 
-```{r crackdown-contrasts}
+# Hypothesis 2a, Relationship with Host Government
+
+> Donors will show increased willingness to donate to NGOs that are facing government crackdown or criticism [Mechanism: Governments wouldn't be cracking down on them if they didn't perceive a threat from them which means organizations implementing their missions effectively.
+This perception of efficacy leads to increased donations.]
+
+```{r crackdown-contrasts-a}
 # Pull the posterior draws for government crackdown
@@
 ggsave(
-  "contrasts_hypothesis02.png",
+  "contrasts_hypothesis02a.png",
   path = here::here("analysis", "output", "figures"),
@@
 
-> Donors will show increased willingness to donate to NGOs that are facing government crackdown or criticism [Mechanism: Governments wouldn't be cracking down on them if they didn't perceive a threat from them which means organizations implementing their missions effectively.
-This perception of efficacy leads to increased donations.]
-
 Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism.
@@
 
+# Hypothesis 2b, Organization and Relationship with Host Government
+
 > Donors will show increased willingness to donate to Oxfam and Red Cross when they are facing government crackdown or criticism compared to when Amnesty or Greenpeace is facing crackdown.
 
+```{r crackdown-contrasts-b}
+
+# Pull the posterior draws for organization*government crackdown interaction
+
+# Reference Level = Friendly relationship with government
+#  contrasts <- tibble(
+#    under_crackdown = draws %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
+#    criticized = draws %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
+#    )
+
+# Plot the contrasts
+# contrasts %>%
+#  pivot_longer(under_crackdown:criticized, names_to = "level", values_to = "Gamma") %>% 
+#  ggplot(aes(x = Gamma, y = level)) +
+#  stat_halfeye(.width = .95) +
+#  geom_vline(xintercept = 0, color = "grey") +
+#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+# ggsave(
+#  "contrasts_hypothesis02b.png",
+#  path = here::here("analysis", "output", "figures"),
+#  width = 12,
+#  height = 6,
+#  units = "in"
+# )
+```
+
 [Answer]
 
-```{r issue-contrasts}
+### Hypothesis 3, Issue Area
+
+# Hypothesis 3a, Issue Area
+
+> Donors will show increased willingness to donate to NGOs working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights)
+
+```{r issue-contrasts-a}
 # Pull the posterior draws for issue area
@@
 ggsave(
-  "contrasts_hypothesis03.png",
+  "contrasts_hypothesis03a.png",
   path = here::here("analysis", "output", "figures"),
@@
 ```
-> Donors will show increased willingness to donate to NGOs working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights)
 
@@
 
+# Hypothesis 3b, Relationship with Host Government and Issue Area
+
 > Donors will show increased willingness to donate to NGOs facing government crackdown/criticism working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights) [Mechanisms: Perceptions of deservingness of NGOs dealing with emergency response and refugee relief.
@@
 
+```{r issue-contrasts-b}
+
+# Pull the posterior draws for government crackdown*issue area interaction
+
+# Reference Level = Friendly relationship with government
+# Reference Level = Emergency Response
+# contrasts <- tibble(
+#  environment = draws %>% filter(level == "Environment") %>% select(Gamma) %>% pull(),
+#  human_rights = draws %>% filter(level == "Human rights") %>% select(Gamma) %>% pull(),
+#  refugee_relief = draws %>% filter(level == "Refugee relief") %>% select(Gamma) %>% pull()
+#  )
+
+# Plot the contrasts
+#contrasts %>%
+# pivot_longer(environment:refugee_relief, names_to = "level", values_to = "Gamma") %>% 
+#  ggplot(aes(x = Gamma, y = level)) +
+#  stat_halfeye(.width = .95) +
+#  geom_vline(xintercept = 0, color = "grey") +
+#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+#ggsave(
+# "contrasts_hypothesis03b.png",
+#  path = here::here("analysis", "output", "figures"),
+#  width = 12,
+#  height = 6,
+#  units = "in"
+#)
+```
+
 [Answer]
@@
 
-```{r funding-contrasts}
+# Hypothesis 4a, Funding Sources
+
+> Donors will show increased willingness to donate to NGOs that are funded primarily by numerous small private donors compared to NGOs that are funded by a handful of wealthy private donors and government grants [Mechanism: Perception of efficacy - your contribution matters as a small donor.
+Government funding may also imply lack of independence of government which can reduce the efficiency of an organization.]
+
+```{r funding-contrasts-a}
 # Pull the posterior draws for funding sources
@@
 ggsave(
-  "contrasts_hypothesis04.png",
+  "contrasts_hypothesis04a.png",
   path = here::here("analysis", "output", "figures"),
@@
 ```
-> Donors will show increased willingness to donate to NGOs that are funded primarily by numerous small private donors compared to NGOs that are funded by a handful of wealthy private donors and government grants [Mechanism: Perception of efficacy - your contribution matters as a small donor.
-Government funding may also imply lack of independence of government which can reduce the efficiency of an organization.]
 
@@
 
+# Hypothesis 4b, Relationship with Host Government and Funding Sources
+
 > Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors
 
+```{r funding-contrasts-b}
+# Pull the posterior draws for government crackdown*funding sources interaction
+
+# Reference Level = Friendly relationship with government
+# Reference Level = Funded primarily by many small private donations
+#contrasts <- tibble(
+#  few_wealthy_private_donors = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
+#  government_grants = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
+#  )
+
+# Plot the contrasts
+#contrasts %>%
+#  pivot_longer(few_wealthy_private_donors:government_grants, names_to = "level", values_to = "Gamma") %>% 
+#  ggplot(aes(x = Gamma, y = level)) +
+#  stat_halfeye(.width = .95) +
+#  geom_vline(xintercept = 0, color = "grey") +
+#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+#ggsave(
+#  "contrasts_hypothesis04b.png",
+#  path = here::here("analysis", "output", "figures"),
+#  width = 12,
+#  height = 6,
+#  units = "in"
+#)
+
+```
+
 [Answer]
 
+# Hypothesis 4c, Relationship with Host Government, Funding Sources, and Issue Area
+
+> Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors and work in less contentious areas (emergency response and refugee relief)
+
+```{r funding-contrasts-c}
+# Pull the posterior draws for funding sources*government crackdown*issue area interaction
+
+# Reference Level = Funded primarily by many small private donations
+# Reference Level = Friendly relationship with government
+#contrasts <- tibble(
+#  few_wealthy_private_donors = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
+#  government_grants = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
+#  )
+
+# Plot the contrasts
+#contrasts %>%
+#  pivot_longer(few_wealthy_private_donors:government_grants, names_to = "level", values_to = "Gamma") %>% 
+#  ggplot(aes(x = Gamma, y = level)) +
+#  stat_halfeye(.width = .95) +
+#  geom_vline(xintercept = 0, color = "grey") +
+#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+#ggsave(
+#  "contrasts_hypothesis04c.png",
+#  path = here::here("analysis", "output", "figures"),
+#  width = 12,
+#  height = 6,
+#  units = "in"
+#)
+
+```
+
+[Answer]
+
 ### Hypothesis 5, Organizational Practices
 
-```{r practices-contrasts}
+# Hypothesis 5a, Organizational Practices
+
+> Donors will show increased willingness to donate to NGOs that are financially transparent [Mechanism: Perception of efficacy]
+
+```{r practices-contrasts-a}
 
@@
 contrasts %>%
-  pivot_longer(few_wealthy_private_donors:government_grants, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer(financial_transparency, names_to = "level", values_to = "Gamma") %>% 
   ggplot(aes(x = Gamma, y = level)) +
@@
 ggsave(
-  "contrasts_hypothesis04.png",
+  "contrasts_hypothesis05a.png",
   path = here::here("analysis", "output", "figures"),
@@
 ```
-> Donors will show increased willingness to donate to NGOs that are financially transparent [Mechanism: Perception of efficacy]
+
+Donors show an increased likelihood to donate to NGOs that are financially transparent, as hypothesized.
+
+# Hypothesis 5b, Organizational Practices
 
@@
 
-When comparing organizational practices, donors show an increased likelihood to donate to NGOs that are financially transparent as well as NGOs that are accountable and hold regular third party audits.
-Although financial transparency was hypothesized to increase donor's willingness to donate, we believed accountability practices would have an insignificant effect on influencing donor's willingness to donate; our analysis indicates that this is not the case.
+```{r practices-contrasts-b}
+# Pull the posterior draws for organizational practices
+
+contrasts <- tibble(
+  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
+  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
+  )
+
+# Plot the contrasts
+contrasts %>%
+  pivot_longer(accountability, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis05b.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
+
+```
+
+Donors show a similar increase in willingness to donate to accountable NGOs in comparison to NGOs that are financially transparent.
+However, this is contrary to what was hypothesized--we predicted that donor's willingness to donate wouldn't be affected by accountability practices.
+
+# Hypothesis 5c, Relationship with Host Government, Organizational Practices, and Funding Sources
 
@@
 
+```{r practices-contrasts-c}
+# Pull the posterior draws for government crackdown*organizational practices*funding sources interaction
+
+# Reference Level = Friendly relationship with government
+# Reference Level = Funded primarily by many small private donations
+
+#contrasts <- tibble(
+#  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
+#  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
+#  )
+
+# Plot the contrasts
+#contrasts %>%
+#  pivot_longer(accountability, names_to = "level", values_to = "Gamma") %>% 
+#  ggplot(aes(x = Gamma, y = level)) +
+#  stat_halfeye(.width = .95) +
+#  geom_vline(xintercept = 0, color = "grey") +
+#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+#ggsave(
+#  "contrasts_hypothesis05c.png",
+#  path = here::here("analysis", "output", "figures"),
+#  width = 12,
+#  height = 6,
+#  units = "in"
+#)
+
+```
+
 [Answer]
 
+# Hypothesis 5d, Relationship with Host Government, Organizational Practices, and Issue Area
+
 > Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief)
 
+```{r practices-contrasts-d}
+# Pull the posterior draws for government crackdown*organizational practices*issue area interaction
+
+# Reference Level = Friendly relationship with government
+# Reference Level = Emergency Response
+
+#contrasts <- tibble(
+#  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
+#  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
+#  )
+
+# Plot the contrasts
+#contrasts %>%
+#  pivot_longer(accountability, names_to = "level", values_to = "Gamma") %>% 
+#  ggplot(aes(x = Gamma, y = level)) +
+#  stat_halfeye(.width = .95) +
+#  geom_vline(xintercept = 0, color = "grey") +
+#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+#ggsave(
+#  "contrasts_hypothesis05d.png",
+#  path = here::here("analysis", "output", "figures"),
+#  width = 12,
+#  height = 6,
+#  units = "in"
+#)
+
+```
+
 [Answer]
 
+# Hypothesis 5e, Relationship with Host Government, Organizational Practices, Issue Area, and Funding Sources
+
 > Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief) and are funded by numerous small donors
 
-[Answer]
-
-> Donors should be no more or less likely to donate to NGOs that are accountable and hold regular third party audits [Mechanism: Donors don't necessarily seek assurance through third-party programs/audits and charity watchdogs, but rather through word of mouth, personal scrutiny and local networks]
+```{r practices-contrasts-e}
+# Pull the posterior draws for government crackdown*organizational practices*issue area*funding sources interaction
+
+# Reference Level = Friendly relationship with government
+# Reference Level = Emergency Response
+# Reference Level = Funded primarily by many small private donations
+
+#contrasts <- tibble(
+#  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
+#  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
+#  )
+
+# Plot the contrasts
+#contrasts %>%
+#  pivot_longer(accountability, names_to = "level", values_to = "Gamma") %>% 
+#  ggplot(aes(x = Gamma, y = level)) +
+#  stat_halfeye(.width = .95) +
+#  geom_vline(xintercept = 0, color = "grey") +
+#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+#ggsave(
+#  "contrasts_hypothesis05e.png",
+#  path = here::here("analysis", "output", "figures"),
+#  width = 12,
+#  height = 6,
+#  units = "in"
+#)
+
+```
 

### 2021-10-18 analysis/01_experimental-design.Rmd

@@
 
-# Interact-code the design
+# Interactions
 
-We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need a specific intercept-only design with each of the needed interactions.
+We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need to specific each of the needed interactions.
 
-```{r interact-design, warning=FALSE, message=FALSE}
+```{r interactions, warning=FALSE, message=FALSE}
 # Convert the attributes in design into factors
-interact_design <- as.data.frame(design)
-for(i in 4:ncol(interact_design)) {
-  interact_design[,i] <- as.factor(interact_design[,i])
+interactions <- as.data.frame(design)
+for(i in 4:ncol(interactions)) {
+  interactions[,i] <- as.factor(interactions[,i])
 }
@@
 # Rename the variables.
-colnames(interact_design)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")
+colnames(interactions)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")
 
 # Use dummy_cols() to get a dummy-coded version of all the attribute levels.
-interact_design <- dummy_cols(
-  interact_design, 
+interactions <- dummy_cols(
+  interactions, 
   select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
@@
 # Rename the dummy-coded variables.
-colnames(interact_design)[4:21] <- c(
+colnames(interactions)[4:21] <- c(
   str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
@@
 # Build out all the necessary interactions.
-interact_design %>% 
+interactions <- interactions %>% 
   as_tibble() %>% 
@@
   ) %>% 
-  # Drop first levels and the nottransp helper variable.
-  select(-c(contains("1"), nottransp))
+  # Drop the design and the nottransp helper variable.
+  select(-c(org1:gov_rel3, nottransp))
 
 # Save interact-coded design output
-write.csv(interact_design, here("data", "derived_data", "interact_design.csv"))
+write.csv(interactions, here("data", "derived_data", "interactions.csv"))
 ```

### 2021-10-20 analysis/01_experimental-design.Rmd
Added an intercept + interactions model (I know the files are still too big, I'll move them to OSF soon)

@@
     amnesty_criticized = org1 * gov_rel2,
+    greenpeace_criticized = org2 * gov_rel2,
+    oxfam_criticized = org3 * gov_rel2,
+    redcross_criticized = org4 * gov_rel2,
     amnesty_crackdown = org1 * gov_rel3,
-    greenpeace_criticized = org2 * gov_rel2,
     greenpeace_crackdown = org2 * gov_rel3,
-    oxfam_criticized = org3 * gov_rel2,
     oxfam_crackdown = org3 * gov_rel3,
-    redcross_criticized = org4 * gov_rel2,
     redcross_crackdown = org4 * gov_rel3,
     # Hypothesis 3b.
-    emergency_criticized = issue1 * gov_rel2,
-    emergency_crackdown = issue1 * gov_rel3,
+    # emergency_criticized = issue1 * gov_rel2,
     environment_criticized = issue2 * gov_rel2,
+    humanrights_criticized = issue3 * gov_rel2,
+    refugees_criticized = issue4 * gov_rel2,
+    # emergency_crackdown = issue1 * gov_rel3,
     environment_crackdown = issue2 * gov_rel3,
-    humanrights_criticized = issue3 * gov_rel2,
     humanrights_crackdown = issue3 * gov_rel3,
-    refugees_criticized = issue4 * gov_rel2,
     refugees_crackdown = issue4 * gov_rel3,
     # Hypothesis 4b.
-    smalldonors_criticized = fund1 * gov_rel2,
-    smalldonors_crackdown = fund1 * gov_rel3,
+    # smalldonors_criticized = fund1 * gov_rel2,
     wealthydonors_criticized = fund2 * gov_rel2,
+    govgrants_criticized = fund3 * gov_rel2,
+    # smalldonors_crackdown = fund1 * gov_rel3,
     wealthydonors_crackdown = fund2 * gov_rel3,
-    govgrants_criticized = fund3 * gov_rel2,
     govgrants_crackdown = fund3 * gov_rel3,
     # Hypothesis 4c.
-    emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
-    emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3,
-    emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,
-    environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
+    # emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
+    emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3, # ??????
+    emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,     # ??????
+    # environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
     environment_wealthydonors_crackdown = issue2 * fund2 * gov_rel3,
     environment_govgrants_crackdown = issue2 * fund3 * gov_rel3,
-    humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
+    # humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
     humanrights_wealthydonors_crackdown = issue3 * fund2 * gov_rel3,
     humanrights_govgrants_crackdown = issue3 * fund3 * gov_rel3,
-    refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
+    # refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
     refugees_wealthydonors_crackdown = issue4 * fund2 * gov_rel3,
@@
     # Hypothesis 5b.
-    transp_criticized = transp1 * gov_rel2,
-    transp_crackdown = transp1 * gov_rel3,
-    nottransp = ifelse(transp1 == 0, 1, 0),
-    nottransp_criticized = nottransp * gov_rel2,
-    nottransp_crackdown = nottransp * gov_rel3,
+    # nottransp_criticized = transp1 * gov_rel2,
+    transp_criticized = transp2 * gov_rel2,
+    # nottransp_crackdown = transp1 * gov_rel3,
+    transp_crackdown = transp2 * gov_rel3,
     # Hypothesis 5c.
-    transp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
-    transp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
-    transp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
-    transp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
-    transp_govgrants_criticized = transp1 * fund3 * gov_rel2,
-    transp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
-    nottransp_smalldonors_criticized = nottransp * fund1 * gov_rel2,
-    nottransp_smalldonors_crackdown = nottransp * fund1 * gov_rel3,
-    nottransp_wealthydonors_criticized = nottransp * fund2 * gov_rel2,
-    nottransp_wealthydonors_crackdown = nottransp * fund2 * gov_rel3,
-    nottransp_govgrants_criticized = nottransp * fund3 * gov_rel2,
-    nottransp_govgrants_crackdown = nottransp * fund3 * gov_rel3,
+    # nottransp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
+    transp_smalldonors_criticized = transp2 * fund1 * gov_rel2,
+    # nottransp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
+    transp_wealthydonors_criticized = transp2 * fund2 * gov_rel2,
+    # nottransp_govgrants_criticized = transp1 * fund3 * gov_rel2,
+    transp_govgrants_criticized = transp2 * fund3 * gov_rel2,
+    # nottransp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
+    transp_smalldonors_crackdown = transp2 * fund1 * gov_rel3,
+    # nottransp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
+    transp_wealthydonors_crackdown = transp2 * fund2 * gov_rel3,
+    # nottransp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
+    transp_govgrants_crackdown = transp2 * fund3 * gov_rel3,
     # Hypothesis 5d.
-    transp_emergency_criticized = transp1 * issue1 * gov_rel2,
-    transp_emergency_crackdown = transp1 * issue1 * gov_rel3,
-    transp_environment_criticized = transp1 * issue2 * gov_rel2,
-    transp_environment_crackdown = transp1 * issue2 * gov_rel3,
-    transp_humanrights_criticized = transp1 * issue3 * gov_rel2,
-    transp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
-    transp_refugees_criticized = transp1 * issue4 * gov_rel2,
-    transp_refugees_crackdown = transp1 * issue4 * gov_rel3,
-    nottransp_emergency_criticized = nottransp * issue1 * gov_rel2,
-    nottransp_emergency_crackdown = nottransp * issue1 * gov_rel3,
-    nottransp_environment_criticized = nottransp * issue2 * gov_rel2,
-    nottransp_environment_crackdown = nottransp * issue2 * gov_rel3,
-    nottransp_humanrights_criticized = nottransp * issue3 * gov_rel2,
-    nottransp_humanrights_crackdown = nottransp * issue3 * gov_rel3,
-    nottransp_refugees_criticized = nottransp * issue4 * gov_rel2,
-    nottransp_refugees_crackdown = nottransp * issue4 * gov_rel3,
+    # nottransp_emergency_criticized = transp1 * issue1 * gov_rel2,
+    transp_emergency_criticized = transp2 * issue1 * gov_rel2,
+    # nottransp_emergency_crackdown = transp1 * issue1 * gov_rel3,
+    transp_emergency_crackdown = transp2 * issue1 * gov_rel3,
+    # nottransp_environment_criticized = transp1 * issue2 * gov_rel2,
+    transp_environment_criticized = transp2 * issue2 * gov_rel2,
+    # nottransp_environment_crackdown = transp1 * issue2 * gov_rel3,
+    transp_environment_crackdown = transp2 * issue2 * gov_rel3,
+    # nottransp_humanrights_criticized = transp1 * issue3 * gov_rel2,
+    transp_humanrights_criticized = transp2 * issue3 * gov_rel2,
+    # nottransp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
+    transp_humanrights_crackdown = transp2 * issue3 * gov_rel3,
+    # nottransp_refugees_criticized = transp1 * issue4 * gov_rel2,
+    transp_refugees_criticized = transp2 * issue4 * gov_rel2,
+    # nottransp_refugees_crackdown = transp1 * issue4 * gov_rel3,
+    transp_refugees_crackdown = transp2 * issue4 * gov_rel3,
     # Hypothesis 5e.
-    transp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
-    transp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
-    transp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
-    transp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
-    transp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
-    transp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
-    transp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
-    transp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
-    nottransp_smalldonors_emergency_criticized = nottransp * fund1 * issue1 * gov_rel2,
-    nottransp_smalldonors_emergency_crackdown = nottransp * fund1 * issue1 * gov_rel3,
-    nottransp_smalldonors_environment_criticized = nottransp * fund1 * issue2 * gov_rel2,
-    nottransp_smalldonors_environment_crackdown = nottransp * fund1 * issue2 * gov_rel3,
-    nottransp_smalldonors_humanrights_criticized = nottransp * fund1 * issue3 * gov_rel2,
-    nottransp_smalldonors_humanrights_crackdown = nottransp * fund1 * issue3 * gov_rel3,
-    nottransp_smalldonors_refugees_criticized = nottransp * fund1 * issue4 * gov_rel2,
-    nottransp_smalldonors_refugees_crackdown = nottransp * fund1 * issue4 * gov_rel3
+    # nottransp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
+    transp_smalldonors_emergency_criticized = transp2 * fund1 * issue1 * gov_rel2,
+    # nottransp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
+    transp_smalldonors_emergency_crackdown = transp2 * fund1 * issue1 * gov_rel3,
+    # nottransp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
+    transp_smalldonors_environment_criticized = transp2 * fund1 * issue2 * gov_rel2,
+    # nottransp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
+    transp_smalldonors_environment_crackdown = transp2 * fund1 * issue2 * gov_rel3,
+    # nottransp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
+    transp_smalldonors_humanrights_criticized = transp2 * fund1 * issue3 * gov_rel2,
+    # nottransp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
+    transp_smalldonors_humanrights_crackdown = transp2 * fund1 * issue3 * gov_rel3,
+    # nottransp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
+    transp_smalldonors_refugees_criticized = transp2 * fund1 * issue4 * gov_rel2,
+    # nottransp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
+    transp_smalldonors_refugees_crackdown = transp2 * fund1 * issue4 * gov_rel3
   ) %>% 
-  # Drop the design and the nottransp helper variable.
-  select(-c(org1:gov_rel3, nottransp))
+  select(-contains("1"))
 

### 2021-10-20 analysis/02_clean-data.Rmd
Added an intercept + interactions model (I know the files are still too big, I'll move them to OSF soon)

@@
 # Load the interactions and join to the design.
-interactions_design <- dummy_design %>% 
-  left_join(
-    read_csv(here::here("data", "derived_data", "interactions.csv")) %>%
+interactions_design <- read_csv(here::here("data", "derived_data", "interactions.csv")) %>%
   select(-`...1`) %>%
@@
     alt = choice
-    )
   )
@@
       mutate(org1 = 0) %>%
-      select(org1, org2:nottransp_smalldonors_refugees_crackdown)
+      select(org1, org2:transp_smalldonors_refugees_crackdown)
     for (p in 1:(dim(dummy_X)[3]-1)) {

### 2021-10-20 analysis/03_analysis.Rmd
Added an intercept + interactions model (I know the files are still too big, I'll move them to OSF soon)

@@
 if (interactions == 1) X <- read_rds(here::here("data", "derived_data", "final_interactions.rds"))
+
+# # ##############################
+# X_new <- array(NA, dim = c(dim(X)[1:3], 19)) # 13 + interactions
+# for (r in 1:dim(X)[1]) {
+#   for (s in 1:dim(X)[2]) {
+#     X_new[r,s,,] <- X[r,s,,c(1:13, 42:47)] # 13 + interactions
+#   }
+# }
+# X <- X_new
+# # ##############################
 
@@
   thin = 5,
-  seed = 42
+  init = 0,
+  seed = 1234
 )
@@
 ```{r extract-draws, eval=FALSE}
-intercept <- 0                            # Intercept-only
-public_affairs <- 1                       # Public affairs
+intercept <- 1                            # Intercept-only
+interactions <- 1                         # Include interactions with the intercept-only model?
+public_affairs <- 0                       # Public affairs
 political_ideology <- 0                   # Political ideology
@@
 if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept.rds"))
+if (intercept == 1 & interactions == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "interactions.rds"))
 if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
@@
 if (intercept == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept.rds"))
+if (intercept == 1 & interactions == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "interactions.rds"))
 if (public_affairs == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))

### 2021-10-20 analysis/04_figs-tables.Rmd
Added an intercept + interactions model (I know the files are still too big, I'll move them to OSF soon)

@@
 intercept <- 1                            # Intercept-only
+interactions <- 1                         # Include interactions with the intercept-only model?
 public_affairs <- 0                       # Public affairs
@@
 }
+if (intercept == 1 & interactions == 1) {
+  draws <- read_rds(
+    here::here("analysis", "output", "posterior_draws", "interactions.rds")
+  ) %>% 
+    mutate(model = "Intercept and interactions")
+}
 if (public_affairs == 1) {
@@
 )
+
+if (intercept == 1 & interactions == 1) {
+  interaction_labels <- c(
+    # Hypothesis 2b.
+    str_c("Interaction: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"), " Criticized"),
+    str_c("Interaction: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"), " Crackdown")
+  )
+  level_labels <- c(level_labels, interaction_labels)
+}
 
@@
 if (intercept == 1) file_name <- paste("marginal-posteriors_intercept.png")
+if (intercept == 1 & interactions == 1) file_name <- paste("marginal-posteriors_interactions.png")
 if (public_affairs == 1) file_name <- paste("marginal-posteriors_public-affairs.png")

### 2021-10-20 analysis/04_figs-tables.Rmd
Hypothesis 2b contrast plots, still need to write out answer

@@
 # Reference Level = Friendly relationship with government
-#  contrasts <- tibble(
-#    under_crackdown = draws %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
-#    criticized = draws %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
-#    )
-
+intib <- interactions_2b %>% filter(i >= 14) %>% select(i, Gamma)
+
+contrasts_int <- tibble(
+  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  red_cross_criticized = intib %>% filter(i == 17) %>% pull(),
+  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
+  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
+  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
+) %>% 
+  mutate(
+    oxfam_amnesty_criticized = oxfam_criticized - amnesty_criticized,
+    oxfam_greenpeace_criticized = oxfam_criticized - greenpeace_criticized,
+    red_cross_amnesty_criticized = red_cross_criticized - amnesty_criticized,
+    red_cross_greenpeace_criticized = red_cross_criticized - greenpeace_criticized,
+    oxfam_amnesty_crackdown = oxfam_crackdown - amnesty_crackdown,
+    oxfam_greenpeace_crackdown = oxfam_crackdown - greenpeace_crackdown,
+    red_cross_amnesty_crackdown = red_cross_crackdown - amnesty_crackdown,
+    red_cross_greenpeace_crackdown = red_cross_crackdown - greenpeace_crackdown
+  )
 # Plot the contrasts
-# contrasts %>%
-#  pivot_longer(under_crackdown:criticized, names_to = "level", values_to = "Gamma") %>% 
-#  ggplot(aes(x = Gamma, y = level)) +
-#  stat_halfeye(.width = .95) +
-#  geom_vline(xintercept = 0, color = "grey") +
-#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
-
-# Save plot
-# ggsave(
-#  "contrasts_hypothesis02b.png",
-#  path = here::here("analysis", "output", "figures"),
-#  width = 12,
-#  height = 6,
-#  units = "in"
-# )
+contrasts_int %>%
+  pivot_longer(oxfam_amnesty_criticized:red_cross_greenpeace_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis02b.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+ )
 ```

### 2021-10-26 analysis/04_figs-tables.Rmd
Added interaction lables, not including posterior draws

--- 2021-10-20 analysis/04_figs-tables.Rmd
@@
     str_c("Interaction: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"), " Criticized"),
-    str_c("Interaction: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"), " Crackdown")
+    str_c("Interaction: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"), " Crackdown"),
+    # Hypothesis 3b.
+    str_c("Interaction: ", c("Environment", "Human rights", "Refugee relief"), " Criticized"),
+    str_c("Interaction: ", c("Environment", "Human rights", "Refugee relief"), " Crackdown"),
+    # Hypothesis 4b.
+    str_c("Interaction: ", c("Handful of wealthy private donors", "Government grants"), " Criticized"),
+    str_c("Interaction: ", c("Handful of wealthy private donors", "Government grants"), " Crackdown"),
+    # Hypothesis 4c.
+    str_c("Interaction: Emergency ", c("Wealthy private donors", "Government grants"), " Crackdown"),
+    str_c("Interaction: Environment ", c("Wealthy private donors", "Government grants"), " Crackdown"),
+    str_c("Interaction: Human rights ", c("Wealthy private donors", "Government grants"), " Crackdown"),
+    str_c("Interaction: Refugee relief ", c("Wealthy private donors", "Government grants"), " Crackdown"),
+    # Hypothesis 5b.
+    str_c("Interaction: Financial transparency", c(" Criticized", " Crackdown")),
+    # Hypothesis 5c.
+    str_c("Interaction: Financial transparency ", c("Small private donors", "Wealthy private donors", "Government grants"), " Criticized"),
+    str_c("Interaction: Financial transparency ", c("Small private donors", "Wealthy private donors", "Government grants"), " Crackdown"),
+    # Hypothesis 5d.
+    str_c("Interaction: Financial transparency Emergency", c(" Criticized", " Crackdown")),
+    str_c("Interaction: Financial transparency Environment", c(" Criticized", " Crackdown")),
+    str_c("Interaction: Financial transparency Human rights", c(" Criticized", " Crackdown")),
+    str_c("Interaction: Financial transparency Refugee relief", c(" Criticized", " Crackdown")),
+    # Hypothesis 5e.
+    str_c("Interaction: Financial transparency Small private donoros Emergency", c(" Criticized", " Crackdown")),
+    str_c("Interaction: Financial transparency Small private donoros Environment", c(" Criticized", " Crackdown")),
+    str_c("Interaction: Financial transparency Small private donoros Human rights", c(" Criticized", " Crackdown")),
+    str_c("Interaction: Financial transparency Small private donoros Refugee relief", c(" Criticized", " Crackdown"))
   )

### 2021-10-26 analysis/03_analysis.Rmd
Avoid overwriting intercept-only model output and posterior draws

--- 2021-10-18 analysis/03_analysis.Rmd
@@
 if (interactions == 1) X <- read_rds(here::here("data", "derived_data", "final_interactions.rds"))
+
+# ##############################
+X_new <- array(NA, dim = c(dim(X)[1:3], 19)) # 13 + interactions
+for (r in 1:dim(X)[1]) {
+  for (s in 1:dim(X)[2]) {
+    X_new[r,s,,] <- X[r,s,,c(1:13, 22:27)] # 13 + interactions
+  }
+}
+X <- X_new
+# ##############################
 
@@
   Gamma_scale = 1,     # Scale of population-level means
-  Omega_shape = 5,     # Shape of population-level scale
+  # Omega_shape = 5,     # Shape of population-level scale
+  Omega_shape = 1,     # Shape of population-level scale
   tau_mean = 0,        # Mean of population-level scale
@@
 if (intercept == 1 & interactions == 0) write_rds(run, here::here("analysis", "output", "model_runs", "intercept.rds"))
-if (intercept == 1 & interactions == 1) write_rds(run, here::here("analysis", "output", "model_runs", "interactions.rds"))
+if (intercept == 1 & interactions == 1) write_rds(run, here::here("analysis", "output", "model_runs", "interactions_3b.rds"))
 if (public_affairs == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_affairs.rds"))
@@
 ```{r extract-draws, eval=FALSE}
-intercept <- 0                            # Intercept-only
-public_affairs <- 1                       # Public affairs
+intercept <- 1                            # Intercept-only
+interactions <- 0                         # Include interactions with the intercept-only model?
+public_affairs <- 0                       # Public affairs
 political_ideology <- 0                   # Political ideology
@@
 # Load and extract data and model output
-if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept.rds"))
+if (intercept == 1 & interactions == 0) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept.rds"))
+if (intercept == 1 & interactions == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "interactions.rds"))
 if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
@@
 # Save draws
-if (intercept == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept.rds"))
+if (intercept == 1 & interactions == 0) write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept.rds"))
+if (intercept == 1 & interactions == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "interactions.rds"))
 if (public_affairs == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))

### 2021-10-29 analysis/04_figs-tables.Rmd
partially complete contrasts

--- 2021-10-26 analysis/04_figs-tables.Rmd
@@
 # Reference Level = Friendly relationship with government
-#  contrasts <- tibble(
-#    under_crackdown = draws %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
-#    criticized = draws %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
-#    )
-
+intib <- read_rds(
+    here::here("analysis", "output", "posterior_draws", "interactions.rds")
+  )
+contrasts_int <- tibble(
+  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  red_cross_criticized = intib %>% filter(i == 17) %>% pull(),
+  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
+  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
+  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
+) %>% 
+  mutate(
+    oxfam_amnesty_criticized = oxfam_criticized - amnesty_criticized,
+    oxfam_greenpeace_criticized = oxfam_criticized - greenpeace_criticized,
+    red_cross_amnesty_criticized = red_cross_criticized - amnesty_criticized,
+    red_cross_greenpeace_criticized = red_cross_criticized - greenpeace_criticized,
+    oxfam_amnesty_crackdown = oxfam_crackdown - amnesty_crackdown,
+    oxfam_greenpeace_crackdown = oxfam_crackdown - greenpeace_crackdown,
+    red_cross_amnesty_crackdown = red_cross_crackdown - amnesty_crackdown,
+    red_cross_greenpeace_crackdown = red_cross_crackdown - greenpeace_crackdown
+  )
 # Plot the contrasts
-# contrasts %>%
-#  pivot_longer(under_crackdown:criticized, names_to = "level", values_to = "Gamma") %>% 
-#  ggplot(aes(x = Gamma, y = level)) +
-#  stat_halfeye(.width = .95) +
-#  geom_vline(xintercept = 0, color = "grey") +
-#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
-
-# Save plot
-# ggsave(
-#  "contrasts_hypothesis02b.png",
-#  path = here::here("analysis", "output", "figures"),
-#  width = 12,
-#  height = 6,
-#  units = "in"
-# )
+contrasts_int %>%
+  pivot_longer(oxfam_amnesty_criticized:red_cross_greenpeace_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis02b.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+ )
 ```
@@
 # Reference Level = Emergency Response
-# contrasts <- tibble(
-#  environment = draws %>% filter(level == "Environment") %>% select(Gamma) %>% pull(),
-#  human_rights = draws %>% filter(level == "Human rights") %>% select(Gamma) %>% pull(),
-#  refugee_relief = draws %>% filter(level == "Refugee relief") %>% select(Gamma) %>% pull()
-#  )
-
+contrasts_int <- tibble(
+  criticized_environment = intib %>% filter(i == 22) %>% select(Gamma) %>% pull(),
+  criticized_humanrights = intib %>% filter(i == 23) %>% select(Gamma) %>% pull(),
+  criticized_refugee = intib %>% filter(i == 24) %>% select(Gamma) %>% pull(),
+  crackdown_environment = intib %>% filter(i == 25) %>% select(Gamma) %>% pull(),
+  crackdown_humanrights = intib %>% filter(i == 26) %>% select(Gamma) %>% pull(),
+  crackdown_refugee = intib %>% filter(i == 27) %>% select(Gamma) %>% pull(),
+) %>% 
+  mutate(
+  criticized_refugee_environment = criticized_refugee - criticized_environment,
+  criticized_refugee_humanrights = criticized_refugee - criticized_humanrights,
+  crackdown_refugee_environment = crackdown_refugee - crackdown_environment,
+  crackdown_refugee_humanrights = crackdown_refugee - crackdown_humanrights
+  )
 # Plot the contrasts
-#contrasts %>%
-# pivot_longer(environment:refugee_relief, names_to = "level", values_to = "Gamma") %>% 
-#  ggplot(aes(x = Gamma, y = level)) +
-#  stat_halfeye(.width = .95) +
-#  geom_vline(xintercept = 0, color = "grey") +
-#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
-
-# Save plot
-#ggsave(
-# "contrasts_hypothesis03b.png",
-#  path = here::here("analysis", "output", "figures"),
-#  width = 12,
-#  height = 6,
-#  units = "in"
-#)
+contrasts_int %>%
+  pivot_longer(criticized_refugee_environment:crackdown_refugee_humanrights, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+ "contrasts_hypothesis03b.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
 ```
@@
 # Reference Level = Funded primarily by many small private donations
-#contrasts <- tibble(
-#  few_wealthy_private_donors = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
-#  government_grants = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
-#  )
-
+contrasts_int <- tibble(
+  criticized_wealthydonors = intib %>% filter(i == 28) %>% select(Gamma) %>% pull(),
+  criticized_grants = intib %>% filter(i == 29) %>% select(Gamma) %>% pull(),
+  crackdown_wealthydonors = intib %>% filter(i == 30) %>% select(Gamma) %>% pull(),
+  crackdown_grants = intib %>% filter(i == 31) %>% select(Gamma) %>% pull(),
+) %>% 
+  mutate(
+  criticized_wealthydonors_grants = criticized_wealthydonors - criticized_grants,
+  crackdown_wealthydonors_grants = crackdown_wealthydonors - crackdown_grants,
+  )
 # Plot the contrasts
-#contrasts %>%
-#  pivot_longer(few_wealthy_private_donors:government_grants, names_to = "level", values_to = "Gamma") %>% 
-#  ggplot(aes(x = Gamma, y = level)) +
-#  stat_halfeye(.width = .95) +
-#  geom_vline(xintercept = 0, color = "grey") +
-#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
-
-# Save plot
-#ggsave(
-#  "contrasts_hypothesis04b.png",
-#  path = here::here("analysis", "output", "figures"),
-#  width = 12,
-#  height = 6,
-#  units = "in"
-#)
+contrasts_int %>%
+  pivot_longer(criticized_wealthydonors_grants:crackdown_wealthydonors_grants, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis04b.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
 

### 2021-10-29 analysis/04_figs-tables.Rmd
Contrast code complete

--- 2021-10-26 analysis/04_figs-tables.Rmd
@@
 
+```{r}
+# Read in interaction draws for contrasts
+
+intib <- read_rds(
+    here::here("analysis", "output", "posterior_draws", "interactions.rds")
+  )
+```
+
 ### Hypothesis 1, Branding
@@
 # Pull the posterior draws for the organizations and compute contrasts
+
 contrasts <- tibble(
@@
 # Reference Level = Friendly relationship with government
+
 contrasts <- tibble(
@@
 ```{r crackdown-contrasts-b}
-
 # Pull the posterior draws for organization*government crackdown interaction
@@
 # Reference Level = Friendly relationship with government
-#  contrasts <- tibble(
-#    under_crackdown = draws %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
-#    criticized = draws %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
-#    )
-
+
+contrasts_int <- tibble(
+  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  red_cross_criticized = intib %>% filter(i == 17)%>% select(Gamma) %>% pull(),
+  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
+  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
+  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
+) %>% 
+  mutate(
+    oxfam_amnesty_criticized = oxfam_criticized - amnesty_criticized,
+    oxfam_greenpeace_criticized = oxfam_criticized - greenpeace_criticized,
+    red_cross_amnesty_criticized = red_cross_criticized - amnesty_criticized,
+    red_cross_greenpeace_criticized = red_cross_criticized - greenpeace_criticized,
+    oxfam_amnesty_crackdown = oxfam_crackdown - amnesty_crackdown,
+    oxfam_greenpeace_crackdown = oxfam_crackdown - greenpeace_crackdown,
+    red_cross_amnesty_crackdown = red_cross_crackdown - amnesty_crackdown,
+    red_cross_greenpeace_crackdown = red_cross_crackdown - greenpeace_crackdown
+  )
 # Plot the contrasts
-# contrasts %>%
-#  pivot_longer(under_crackdown:criticized, names_to = "level", values_to = "Gamma") %>% 
-#  ggplot(aes(x = Gamma, y = level)) +
-#  stat_halfeye(.width = .95) +
-#  geom_vline(xintercept = 0, color = "grey") +
-#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
-
-# Save plot
-# ggsave(
-#  "contrasts_hypothesis02b.png",
-#  path = here::here("analysis", "output", "figures"),
-#  width = 12,
-#  height = 6,
-#  units = "in"
-# )
-```
-
-[Answer]
+contrasts_int %>%
+  pivot_longer(oxfam_amnesty_criticized:red_cross_greenpeace_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis02b.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+ )
+```
+
+These data don't support our hypothesis; the Red Cross brand has an insignificant impact on likelihood to donate compared to both Greenpeace and Amnesty.
+While the contrasts for Oxfam are closer to being statistically significant, the effect is working in the other direction--Greenpeace and Amnesty both induce increased likelihood to donate on behalf of donors.
 
@@
 # Reference Level = Emergency Response
+
 contrasts <- tibble(
@@
 # Reference Level = Emergency Response
-# contrasts <- tibble(
-#  environment = draws %>% filter(level == "Environment") %>% select(Gamma) %>% pull(),
-#  human_rights = draws %>% filter(level == "Human rights") %>% select(Gamma) %>% pull(),
-#  refugee_relief = draws %>% filter(level == "Refugee relief") %>% select(Gamma) %>% pull()
-#  )
-
+
+contrasts_int <- tibble(
+  criticized_environment = intib %>% filter(i == 22) %>% select(Gamma) %>% pull(),
+  criticized_humanrights = intib %>% filter(i == 23) %>% select(Gamma) %>% pull(),
+  criticized_refugee = intib %>% filter(i == 24) %>% select(Gamma) %>% pull(),
+  crackdown_environment = intib %>% filter(i == 25) %>% select(Gamma) %>% pull(),
+  crackdown_humanrights = intib %>% filter(i == 26) %>% select(Gamma) %>% pull(),
+  crackdown_refugee = intib %>% filter(i == 27) %>% select(Gamma) %>% pull(),
+) %>% 
+  mutate(
+  criticized_refugee_environment = criticized_refugee - criticized_environment,
+  criticized_refugee_humanrights = criticized_refugee - criticized_humanrights,
+  crackdown_refugee_environment = crackdown_refugee - crackdown_environment,
+  crackdown_refugee_humanrights = crackdown_refugee - crackdown_humanrights
+)
 # Plot the contrasts
-#contrasts %>%
-# pivot_longer(environment:refugee_relief, names_to = "level", values_to = "Gamma") %>% 
-#  ggplot(aes(x = Gamma, y = level)) +
-#  stat_halfeye(.width = .95) +
-#  geom_vline(xintercept = 0, color = "grey") +
-#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
-
-# Save plot
-#ggsave(
-# "contrasts_hypothesis03b.png",
-#  path = here::here("analysis", "output", "figures"),
-#  width = 12,
-#  height = 6,
-#  units = "in"
-#)
-```
-
-[Answer]
+contrasts_int %>%
+  pivot_longer(criticized_refugee_environment:crackdown_refugee_humanrights, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+ "contrasts_hypothesis03b.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
+```
+
+The generated contrasts don't provides results which are statistically significant. 0 is found within all intervals.
 
@@
 # Reference Level = Funded primarily by many small private donations
+
 contrasts <- tibble(
@@
 # Reference Level = Funded primarily by many small private donations
-#contrasts <- tibble(
-#  few_wealthy_private_donors = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
-#  government_grants = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
-#  )
-
+
+contrasts_int <- tibble(
+  criticized_wealthydonors = intib %>% filter(i == 28) %>% select(Gamma) %>% pull(),
+  criticized_grants = intib %>% filter(i == 29) %>% select(Gamma) %>% pull(),
+  crackdown_wealthydonors = intib %>% filter(i == 30) %>% select(Gamma) %>% pull(),
+  crackdown_grants = intib %>% filter(i == 31) %>% select(Gamma) %>% pull(),
+)
 # Plot the contrasts
-#contrasts %>%
-#  pivot_longer(few_wealthy_private_donors:government_grants, names_to = "level", values_to = "Gamma") %>% 
-#  ggplot(aes(x = Gamma, y = level)) +
-#  stat_halfeye(.width = .95) +
-#  geom_vline(xintercept = 0, color = "grey") +
-#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
-
-# Save plot
-#ggsave(
-#  "contrasts_hypothesis04b.png",
-#  path = here::here("analysis", "output", "figures"),
-#  width = 12,
-#  height = 6,
-#  units = "in"
-#)
-
-```
-
-[Answer]
+contrasts_int %>%
+  pivot_longer(criticized_wealthydonors:crackdown_grants, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis04b.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
+
+```
+
+The marginal posteriors for these contrasts are strange, but still tell us that the interaction between funding sources and government relationship produce no significant effects.
 
@@
 ```{r funding-contrasts-c}
-# Pull the posterior draws for funding sources*government crackdown*issue area interaction
+# Pull the posterior draws for issue area*government crackdown*funding sources interaction
 
@@
 # Reference Level = Friendly relationship with government
-#contrasts <- tibble(
-#  few_wealthy_private_donors = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
-#  government_grants = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
-#  )
+
+contrasts_int <- tibble(
+  emergency_crackdown_wealthydonors = intib %>% filter(i == 32) %>% select(Gamma) %>% pull(),
+  emergency_crackdown_grants = intib %>% filter(i == 33) %>% select(Gamma) %>% pull(),
+  environment_crackdown_wealthydonors = intib %>% filter(i == 34) %>% select(Gamma) %>% pull(),
+  environment_crackdown_grants = intib %>% filter(i == 35) %>% select(Gamma) %>% pull(),
+  humanrights_crackdown_wealthydonors = intib %>% filter(i == 36) %>% select(Gamma) %>% pull(),
+  humanrights_crackdown_grants = intib %>% filter(i == 37) %>% select(Gamma) %>% pull(),
+  refugee_crackdown_wealthydonors = intib %>% filter(i == 38) %>% select(Gamma) %>% pull(),
+  refugee_crackdown_grants = intib %>% filter(i == 39) %>% select(Gamma) %>% pull(),
+) %>% 
+  mutate(
+  emergency_humanrights_wealthydonors = emergency_crackdown_wealthydonors - humanrights_crackdown_wealthydonors ,
+  emergency_environment_wealthydonors = emergency_crackdown_wealthydonors - environment_crackdown_wealthydonors,
+  emergency_grants_wealthydonors = emergency_crackdown_wealthydonors - emergency_crackdown_grants,
+  refugee_humanrights_wealthydonors = refugee_crackdown_wealthydonors - humanrights_crackdown_wealthydonors,
+  refugee_environment_wealthydonors = refugee_crackdown_wealthydonors - environment_crackdown_wealthydonors,
+  refugee_grants_wealthydonors = refugee_crackdown_grants - refugee_crackdown_wealthydonors
+  )
 
 # Plot the contrasts
-#contrasts %>%
-#  pivot_longer(few_wealthy_private_donors:government_grants, names_to = "level", values_to = "Gamma") %>% 
-#  ggplot(aes(x = Gamma, y = level)) +
-#  stat_halfeye(.width = .95) +
-#  geom_vline(xintercept = 0, color = "grey") +
-#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
-
-# Save plot
-#ggsave(
-#  "contrasts_hypothesis04c.png",
-#  path = here::here("analysis", "output", "figures"),
-#  width = 12,
-#  height = 6,
-#  units = "in"
-#)
-
-```
-
-[Answer]
+contrasts_int %>%
+  pivot_longer(emergency_humanrights_wealthydonors:refugee_grants_wealthydonors, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis04c.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
+
+```
+
+Once again, we see some interesting distributions, but no results significant enough to confirm our hypothesis.
 
@@
 
-# Hypothesis 5b, Organizational Practices
+# Hypothesis 5b, Relationship with Host Government, Organizational Practices
+
+> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent
+
+```{r practices-contrasts-b}
+
+# Pull the posterior draws for organizational practices*government crackdown interaction
+
+# Reference Level = Friendly relationship with government
+
+contrasts_int <- tibble(
+  financial_transparency_criticized = intib %>% filter(i == 40) %>% select(Gamma) %>% pull(),
+  financial_transparency_crackdown = intib %>% filter(i == 41) %>% select(Gamma) %>% pull(),
+  )
+
+# Plot the contrasts
+contrasts_int %>%
+  pivot_longer(financial_transparency_criticized:financial_transparency_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis05b.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
+
+```
+
+Donors show a similar increase in willingness to donate to accountable NGOs in comparison to NGOs that are financially transparent.
+However, this is contrary to what was hypothesized--we predicted that donor's willingness to donate wouldn't be affected by accountability practices.
+
+# Hypothesis 5c, Relationship with Host Government, Organizational Practices, and Funding Sources
+
+> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and are funded primarily by numerous small private donors
+
+```{r practices-contrasts-c}
+# Pull the posterior draws for organizational practices*funding sources*government crackdown interaction
+
+# Reference Level = Friendly relationship with government
+# Reference Level = Funded primarily by many small private donations
+# All interactions include financial transparency
+
+contrasts_int <- tibble(
+  fin_smalldonors_criticized = intib %>% filter(i == 42) %>% select(Gamma) %>% pull(),
+  fin_wealthydonors_criticized = intib %>% filter(i == 43) %>% select(Gamma) %>% pull(),
+  fin_grants_criticized = intib %>% filter(i == 44) %>% select(Gamma) %>% pull(),
+  fin_smalldonors_crackdown = intib %>% filter(i == 45) %>% select(Gamma) %>% pull(),
+  fin_wealthydonors_crackdown = intib %>% filter(i == 46) %>% select(Gamma) %>% pull(),
+  fin_grants_crackdown = intib %>% filter(i == 47) %>% select(Gamma) %>% pull(),
+  ) %>%
+  mutate(
+  fin_smalldonors_wealthydonors_criticized = fin_smalldonors_criticized - fin_wealthydonors_criticized,
+  fin_smalldonors_grants_criticized = fin_smalldonors_criticized - fin_grants_criticized,
+  fin_smalldonors_wealthydonors_crackdown = fin_smalldonors_crackdown - fin_wealthydonors_crackdown,
+  fin_smalldonors_grants_crackdown = fin_smalldonors_crackdown - fin_grants_crackdown
+  )
+
+# Plot the contrasts
+contrasts_int %>%
+  pivot_longer(fin_smalldonors_wealthydonors_criticized:fin_smalldonors_grants_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis05c.png",#
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
+
+```
+
+These intervals are massive; 0 is well within them, leaving us with insufficient evidence to confirm the hypothesis.
+
+# Hypothesis 5d, Relationship with Host Government, Organizational Practices, and Issue Area
+
+> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief)
+
+```{r practices-contrasts-d}
+
+# Pull the posterior draws for organizational practices*issue area*government crackdown interaction
+
+# Reference Level = Friendly relationship with government
+# Reference Level = Emergency Response
+# All interactions include financial transparency
+
+contrasts_int <- tibble(
+  fin_emergency_criticized = intib %>% filter(i == 48) %>% select(Gamma) %>% pull(),
+  fin_emergency_crackdown = intib %>% filter(i == 49) %>% select(Gamma) %>% pull(),
+  fin_environment_criticized = intib %>% filter(i == 50) %>% select(Gamma) %>% pull(),
+  fin_environment_crackdown = intib %>% filter(i == 51) %>% select(Gamma) %>% pull(),
+  fin_humanrights_criticized = intib %>% filter(i == 52) %>% select(Gamma) %>% pull(),
+  fin_humanrights_crackdown = intib %>% filter(i == 53) %>% select(Gamma) %>% pull(),
+  fin_refugee_criticized = intib %>% filter(i == 54) %>% select(Gamma) %>% pull(),
+  fin_refugee_crackdown = intib %>% filter(i == 55) %>% select(Gamma) %>% pull()
+  ) %>%
+  mutate(
+  fin_emergency_environment_criticized = fin_emergency_criticized - fin_environment_criticized,
+  fin_emergency_humanrights_criticized = fin_emergency_criticized - fin_humanrights_criticized,
+  fin_emergency_environment_crackdown = fin_emergency_crackdown - fin_environment_crackdown,
+  fin_emergency_humanright_crackdown = fin_emergency_crackdown - fin_humanrights_crackdown,
+  fin_refugee_environment_criticized = fin_refugee_criticized - fin_environment_criticized,
+  fin_refugee_humanright_criticized = fin_refugee_criticized - fin_humanrights_criticized,
+  fin_refugee_environment_crackdown = fin_refugee_crackdown - fin_environment_crackdown,
+  fin_refugee_humanright_crackdown = fin_refugee_crackdown - fin_humanrights_crackdown
+
+  )
+
+# Plot the contrasts
+contrasts_int %>%
+  pivot_longer(fin_emergency_environment_criticized:fin_refugee_humanright_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis05d.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
+
+```
+
+The contrasts don't support the hypothesis, however, there is an interesting difference between emergency_environment_crackdown and emergency_environment_criticized.
+
+# Hypothesis 5e, Relationship with Host Government, Organizational Practices, Issue Area, and Funding Sources
+
+> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief) and are funded by numerous small donors
+
+```{r practices-contrasts-e}
+# Pull the posterior draws for organizational practices*funding*issue area*government crackdown interaction
+
+# Reference Level = Friendly relationship with government
+# Reference Level = Emergency Response
+# All interactions include small donors
+# All interactions include financial transparency
+
+contrasts_int <- tibble(
+  fin_sd_emergency_criticized = intib %>% filter(i == 56) %>% select(Gamma) %>% pull(),
+  fin_sd_emergency_crackdown = intib %>% filter(i == 57) %>% select(Gamma) %>% pull(),
+  fin_sd_environment_criticized = intib %>% filter(i == 58) %>% select(Gamma) %>% pull(),
+  fin_sd_environment_crackdown = intib %>% filter(i == 59) %>% select(Gamma) %>% pull(),
+  fin_sd_humanrights_criticized = intib %>% filter(i == 60) %>% select(Gamma) %>% pull(),
+  fin_sd_humanrights_crackdown = intib %>% filter(i == 61) %>% select(Gamma) %>% pull(),
+  fin_sd_refugee_criticized = intib %>% filter(i == 62) %>% select(Gamma) %>% pull(),
+  fin_sd_refugee_crackdown = intib %>% filter(i == 63) %>% select(Gamma) %>% pull()
+  ) %>%
+  mutate(
+  fin_sd_emergency_environment_criticized = fin_sd_emergency_criticized - fin_sd_environment_criticized,
+  fin_sd_emergency_humanrights_criticized = fin_sd_emergency_criticized - fin_sd_humanrights_criticized,
+  fin_sd_emergency_environment_crackdown = fin_sd_emergency_crackdown - fin_sd_environment_crackdown,
+  fin_sd_emergency_humanright_crackdown = fin_sd_emergency_crackdown - fin_sd_humanrights_crackdown,
+  fin_sd_refugee_environment_criticized = fin_sd_refugee_criticized - fin_sd_environment_criticized,
+  fin_sd_refugee_humanright_criticized = fin_sd_refugee_criticized - fin_sd_humanrights_criticized,
+  fin_sd_refugee_environment_crackdown = fin_sd_refugee_crackdown - fin_sd_environment_crackdown,
+  fin_sd_refugee_humanright_crackdown = fin_sd_refugee_crackdown - fin_sd_humanrights_crackdown
+
+  )
+# Plot the contrasts
+contrasts_int %>%
+  pivot_longer(fin_sd_emergency_environment_criticized:fin_sd_refugee_humanright_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis05e.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
+
+```
+
+These marginal posteriors don't support our hypothesis, but again show an interesting difference between emergency_environment_criticized and emergency_environment_crackdown.
+
+# Hypothesis 5f, Organizational Practices
 
@@
 ggsave(
-  "contrasts_hypothesis05b.png",
+  "contrasts_hypothesis05f.png",
   path = here::here("analysis", "output", "figures"),
@@
 However, this is contrary to what was hypothesized--we predicted that donor's willingness to donate wouldn't be affected by accountability practices.
-
-# Hypothesis 5c, Relationship with Host Government, Organizational Practices, and Funding Sources
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and are funded primarily by numerous small private donors
-
-```{r practices-contrasts-c}
-# Pull the posterior draws for government crackdown*organizational practices*funding sources interaction
-
-# Reference Level = Friendly relationship with government
-# Reference Level = Funded primarily by many small private donations
-
-#contrasts <- tibble(
-#  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
-#  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
-#  )
-
-# Plot the contrasts
-#contrasts %>%
-#  pivot_longer(accountability, names_to = "level", values_to = "Gamma") %>% 
-#  ggplot(aes(x = Gamma, y = level)) +
-#  stat_halfeye(.width = .95) +
-#  geom_vline(xintercept = 0, color = "grey") +
-#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
-
-# Save plot
-#ggsave(
-#  "contrasts_hypothesis05c.png",
-#  path = here::here("analysis", "output", "figures"),
-#  width = 12,
-#  height = 6,
-#  units = "in"
-#)
-
-```
-
-[Answer]
-
-# Hypothesis 5d, Relationship with Host Government, Organizational Practices, and Issue Area
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief)
-
-```{r practices-contrasts-d}
-# Pull the posterior draws for government crackdown*organizational practices*issue area interaction
-
-# Reference Level = Friendly relationship with government
-# Reference Level = Emergency Response
-
-#contrasts <- tibble(
-#  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
-#  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
-#  )
-
-# Plot the contrasts
-#contrasts %>%
-#  pivot_longer(accountability, names_to = "level", values_to = "Gamma") %>% 
-#  ggplot(aes(x = Gamma, y = level)) +
-#  stat_halfeye(.width = .95) +
-#  geom_vline(xintercept = 0, color = "grey") +
-#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
-
-# Save plot
-#ggsave(
-#  "contrasts_hypothesis05d.png",
-#  path = here::here("analysis", "output", "figures"),
-#  width = 12,
-#  height = 6,
-#  units = "in"
-#)
-
-```
-
-[Answer]
-
-# Hypothesis 5e, Relationship with Host Government, Organizational Practices, Issue Area, and Funding Sources
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief) and are funded by numerous small donors
-
-```{r practices-contrasts-e}
-# Pull the posterior draws for government crackdown*organizational practices*issue area*funding sources interaction
-
-# Reference Level = Friendly relationship with government
-# Reference Level = Emergency Response
-# Reference Level = Funded primarily by many small private donations
-
-#contrasts <- tibble(
-#  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
-#  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
-#  )
-
-# Plot the contrasts
-#contrasts %>%
-#  pivot_longer(accountability, names_to = "level", values_to = "Gamma") %>% 
-#  ggplot(aes(x = Gamma, y = level)) +
-#  stat_halfeye(.width = .95) +
-#  geom_vline(xintercept = 0, color = "grey") +
-#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
-
-# Save plot
-#ggsave(
-#  "contrasts_hypothesis05e.png",
-#  path = here::here("analysis", "output", "figures"),
-#  width = 12,
-#  height = 6,
-#  units = "in"
-#)
-
-```
-
-[Answer]
 

### 2021-12-02 analysis/03_analysis.Rmd
Modifications to analysis for working with interaction models

--- 2021-10-20 analysis/03_analysis.Rmd
@@
 library(donorheuristics)
+library(fastDummies)
 library(rstan)
@@
 ```{r model-calibration, eval=FALSE}
-intercept <- 1                            # Intercept-only
-interactions <- 1                         # Include interactions with the intercept-only model?
-public_affairs <- 0                       # Public affairs
+intercept <- 0                            # Intercept-only
+interactions <- 0                         # Include interactions with the intercept-only model?
+public_affairs <- 1                       # Public affairs
 political_ideology <- 0                   # Political ideology
@@
 # # ##############################
-# X_new <- array(NA, dim = c(dim(X)[1:3], 19)) # 13 + interactions
+# X_new <- array(NA, dim = c(dim(X)[1:3], 21)) # 13 + interactions
 # for (r in 1:dim(X)[1]) {
 #   for (s in 1:dim(X)[2]) {
-#     X_new[r,s,,] <- X[r,s,,c(1:13, 42:47)] # 13 + interactions
+#     X_new[r,s,,] <- X[r,s,,c(1:13, 56:63)] # 13 + interactions
 #   }
@@
 
-if (intercept == 0) {
 # Replace factor labels with levels
@@
   as.matrix()
-}
+
+# ####################################################################################
+# # if (intercept == 0) {
+#   # OLD...
+#   # Replace factor labels with levels
+#   Z_old <- Z %>%
+#   # Z <- Z %>%
+#     mutate_if(is.factor, as.integer) %>%
+#     mutate_if(is.integer, as.factor)
+#   
+#   # Pad the variables names with _
+#   # colnames(Z) <- str_c(colnames(Z), "_")
+#   colnames(Z_old) <- str_c(colnames(Z_old), "_")
+#   
+#   # Use the output of lm to get a dummy-coded version of the covariate matrix Z
+#   # Z$y <- matrix(rnorm(nrow(Z)), ncol = 1)
+#   # out <- lm(y ~ ., Z, x = TRUE)
+#   Z_old$y <- matrix(rnorm(nrow(Z_old)), ncol = 1)
+#   out <- lm(y ~ ., Z_old, x = TRUE)
+#   
+#   # Save out Z as a matrix, including an intercept
+#   Z_old <- tibble(intercept = rep(1, dim(X)[1])) %>%
+#   # Z <- tibble(intercept = rep(1, dim(X)[1])) %>%
+#     bind_cols(as_tibble(out$x[,-1])) %>%
+#     as.matrix()
+#   
+#   # NEW...
+#   # Replace factor labels with levels and NAs with 0s
+#   Z_new <- Z %>%
+#     mutate_if(is.factor, as.integer) %>%
+#     mutate_if(is.integer, as.factor) %>% 
+#     replace(is.na(.), 0) %>% 
+#     # Use dummy_cols() to get a dummy-coded version of factors
+#     dummy_cols(
+#       remove_first_dummy = TRUE,
+#       remove_selected_columns = TRUE
+#     ) %>% 
+#     # Include an intercept, sort columns numerically, save as matrix
+#     bind_cols(tibble(intercept = rep(1, dim(X)[1]))) %>% 
+#     relocate(intercept, sort(colnames(.))) %>% 
+#     as.matrix()
+# # }
+# 
+# 
+# 
+# 
+# ####################################################################################
 
@@
   thin = 5,
-  init = 0,
   seed = 1234
@@
 if (intercept == 1 & interactions == 0) write_rds(run, here::here("analysis", "output", "model_runs", "intercept.rds"))
-if (intercept == 1 & interactions == 1) write_rds(run, here::here("analysis", "output", "model_runs", "interactions.rds"))
+if (intercept == 1 & interactions == 1) write_rds(run, here::here("analysis", "output", "model_runs", "interactions_5e.rds"))
 if (public_affairs == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_affairs.rds"))
@@
 # Load and extract data and model output
-if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept.rds"))
-if (intercept == 1 & interactions == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "interactions.rds"))
+if (intercept == 1 & interactions == 0) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept.rds"))
+if (intercept == 1 & interactions == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "interactions_5d.rds"))
 if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
@@
 # Save draws
-if (intercept == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept.rds"))
-if (intercept == 1 & interactions == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "interactions.rds"))
+if (intercept == 1 & interactions == 0) write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept.rds"))
+if (intercept == 1 & interactions == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "interactions_5d.rds"))
 if (public_affairs == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))

### 2021-12-02 analysis/04_figs-tables.Rmd

@@
   )
+
+# Storing intercept draws in a different tibble for easier use; emergency response, no financial transparency, no accountability, many private donors and friendly relationship with government are all reference levels for their respective groups, and thus are not found in the tibble.
+dtib <- tibble(
+  amnesty = draws %>% filter(i == 1) %>% select(Gamma) %>% pull(),
+  greenpeace = draws %>% filter(i == 2) %>% select(Gamma) %>% pull(),
+  oxfam = draws %>% filter(i == 3) %>% select(Gamma) %>% pull(),
+  red_cross = draws %>% filter(i == 4)%>% select(Gamma) %>% pull(),
+  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
+  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
+  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
+  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
+  accountability = draws %>% filter(i == 9) %>% select(Gamma) %>% pull(),
+  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
+  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
+  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
+  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull()
+)
 ```
@@
   mutate(
-    oxfam_amnesty_criticized = oxfam_criticized - amnesty_criticized,
-    oxfam_greenpeace_criticized = oxfam_criticized - greenpeace_criticized,
-    red_cross_amnesty_criticized = red_cross_criticized - amnesty_criticized,
-    red_cross_greenpeace_criticized = red_cross_criticized - greenpeace_criticized,
-    oxfam_amnesty_crackdown = oxfam_crackdown - amnesty_crackdown,
-    oxfam_greenpeace_crackdown = oxfam_crackdown - greenpeace_crackdown,
-    red_cross_amnesty_crackdown = red_cross_crackdown - amnesty_crackdown,
-    red_cross_greenpeace_crackdown = red_cross_crackdown - greenpeace_crackdown
+    oxfam_amnesty_criticized = ((dtib$oxfam + oxfam_criticized) - (dtib$amnesty + amnesty_criticized) + dtib$criticized),
+    oxfam_greenpeace_criticized = ((dtib$oxfam + oxfam_criticized) - (dtib$greenpeace + greenpeace_criticized) + dtib$criticized),
+    red_cross_amnesty_criticized = ((dtib$red_cross + red_cross_criticized) - (dtib$amnesty + amnesty_criticized) + dtib$criticized),
+    red_cross_greenpeace_criticized = ((dtib$red_cross + red_cross_criticized) - (dtib$greenpeace + greenpeace_criticized) + dtib$criticized),
+    oxfam_amnesty_crackdown = ((dtib$oxfam + oxfam_crackdown) - (dtib$amnesty + amnesty_crackdown) + dtib$crackdown),
+    oxfam_greenpeace_crackdown = ((dtib$oxfam + oxfam_crackdown) - (dtib$greenpeace + greenpeace_crackdown) + dtib$crackdown),
+    red_cross_amnesty_crackdown = ((dtib$red_cross + red_cross_crackdown) - (dtib$amnesty + amnesty_crackdown) + dtib$crackdown),
+    red_cross_greenpeace_crackdown = ((dtib$red_cross + red_cross_crackdown) - (dtib$greenpeace + greenpeace_crackdown) + dtib$crackdown)
   )
@@
   "contrasts_hypothesis02b.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+ )
+```
+
+```{r crackdown-contrasts-b-alt}
+# Pull the posterior draws for organization*government crackdown interaction
+
+# Reference Level = Friendly relationship with government
+
+contrasts_int <- tibble(
+  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  red_cross_criticized = intib %>% filter(i == 17)%>% select(Gamma) %>% pull(),
+  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
+  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
+  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
+) %>% 
+  mutate(
+    oxfam_amnesty_criticized = (dtib$oxfam + oxfam_criticized) - (dtib$amnesty + amnesty_criticized),
+    oxfam_greenpeace_criticized = (dtib$oxfam + oxfam_criticized) - (dtib$greenpeace + greenpeace_criticized),
+    red_cross_amnesty_criticized = (dtib$red_cross + red_cross_criticized) - (dtib$amnesty + amnesty_criticized),
+    red_cross_greenpeace_criticized = (dtib$red_cross + red_cross_criticized) - (dtib$greenpeace + greenpeace_criticized),
+    oxfam_amnesty_crackdown = (dtib$oxfam + oxfam_crackdown) - (dtib$amnesty + amnesty_crackdown),
+    oxfam_greenpeace_crackdown = (dtib$oxfam + oxfam_crackdown) - (dtib$greenpeace + greenpeace_crackdown),
+    red_cross_amnesty_crackdown = (dtib$red_cross + red_cross_crackdown) - (dtib$amnesty + amnesty_crackdown),
+    red_cross_greenpeace_crackdown = (dtib$red_cross + red_cross_crackdown) - (dtib$greenpeace + greenpeace_crackdown)
+  )
+# Plot the contrasts
+contrasts_int %>%
+  pivot_longer(oxfam_amnesty_criticized:red_cross_greenpeace_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis02b_alt.png",
   path = here::here("analysis", "output", "figures"),

### 2021-12-02 analysis/04_figs-tables.Rmd
Added import code specific to each subset of hypotheses

--- 2021-10-29 analysis/04_figs-tables.Rmd
@@
 
-if (intercept == 1) {
+if (intercept == 1 & interactions == 0) {
   draws <- read_rds(
@@
 # Read in interaction draws for contrasts
-
 intib <- read_rds(
@@
 # Pull the posterior draws for the organizations and compute contrasts
-
 contrasts <- tibble(
@@
 
-# Hypothesis 2a, Relationship with Host Government
+#### Hypothesis 2a, Relationship with Host Government
 
@@
 # Pull the posterior draws for government crackdown
-
 # Reference Level = Friendly relationship with government
@@
 
-# Hypothesis 2b, Organization and Relationship with Host Government
+#### Hypothesis 2b, Organization and Relationship with Host Government
 
@@
 ```{r crackdown-contrasts-b}
+# Overwrite draws with the appropriate interaction data
+draws <- here::here("analysis", "output", "posterior_draws", "interactions_2b.rds")
+
 # Pull the posterior draws for organization*government crackdown interaction
-
 # Reference Level = Friendly relationship with government
@@
   mutate(
-    oxfam_amnesty_criticized = oxfam_criticized - amnesty_criticized,
-    oxfam_greenpeace_criticized = oxfam_criticized - greenpeace_criticized,
-    red_cross_amnesty_criticized = red_cross_criticized - amnesty_criticized,
-    red_cross_greenpeace_criticized = red_cross_criticized - greenpeace_criticized,
-    oxfam_amnesty_crackdown = oxfam_crackdown - amnesty_crackdown,
-    oxfam_greenpeace_crackdown = oxfam_crackdown - greenpeace_crackdown,
-    red_cross_amnesty_crackdown = red_cross_crackdown - amnesty_crackdown,
-    red_cross_greenpeace_crackdown = red_cross_crackdown - greenpeace_crackdown
-  )
+    oxfam_amnesty_criticized = ((dtib$oxfam + oxfam_criticized) - (dtib$amnesty + amnesty_criticized) + dtib$criticized),
+    oxfam_greenpeace_criticized = ((dtib$oxfam + oxfam_criticized) - (dtib$greenpeace + greenpeace_criticized) + dtib$criticized),
+    red_cross_amnesty_criticized = ((dtib$red_cross + red_cross_criticized) - (dtib$amnesty + amnesty_criticized) + dtib$criticized),
+    red_cross_greenpeace_criticized = ((dtib$red_cross + red_cross_criticized) - (dtib$greenpeace + greenpeace_criticized) + dtib$criticized),
+    oxfam_amnesty_crackdown = ((dtib$oxfam + oxfam_crackdown) - (dtib$amnesty + amnesty_crackdown) + dtib$crackdown),
+    oxfam_greenpeace_crackdown = ((dtib$oxfam + oxfam_crackdown) - (dtib$greenpeace + greenpeace_crackdown) + dtib$crackdown),
+    red_cross_amnesty_crackdown = ((dtib$red_cross + red_cross_crackdown) - (dtib$amnesty + amnesty_crackdown) + dtib$crackdown),
+    red_cross_greenpeace_crackdown = ((dtib$red_cross + red_cross_crackdown) - (dtib$greenpeace + greenpeace_crackdown) + dtib$crackdown)
+  )
+
 # Plot the contrasts
@@
 
+```{r crackdown-contrasts-b-alt}
+# Overwrite draws with the appropriate interaction data
+draws <- here::here("analysis", "output", "posterior_draws", "interactions_2b.rds")
+
+# Pull the posterior draws for organization*government crackdown interaction
+# Reference Level = Friendly relationship with government
+
+contrasts_int <- tibble(
+  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  red_cross_criticized = intib %>% filter(i == 17)%>% select(Gamma) %>% pull(),
+  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
+  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
+  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
+) %>% 
+  mutate(
+    oxfam_amnesty_criticized = (dtib$oxfam + oxfam_criticized) - (dtib$amnesty + amnesty_criticized),
+    oxfam_greenpeace_criticized = (dtib$oxfam + oxfam_criticized) - (dtib$greenpeace + greenpeace_criticized),
+    red_cross_amnesty_criticized = (dtib$red_cross + red_cross_criticized) - (dtib$amnesty + amnesty_criticized),
+    red_cross_greenpeace_criticized = (dtib$red_cross + red_cross_criticized) - (dtib$greenpeace + greenpeace_criticized),
+    oxfam_amnesty_crackdown = (dtib$oxfam + oxfam_crackdown) - (dtib$amnesty + amnesty_crackdown),
+    oxfam_greenpeace_crackdown = (dtib$oxfam + oxfam_crackdown) - (dtib$greenpeace + greenpeace_crackdown),
+    red_cross_amnesty_crackdown = (dtib$red_cross + red_cross_crackdown) - (dtib$amnesty + amnesty_crackdown),
+    red_cross_greenpeace_crackdown = (dtib$red_cross + red_cross_crackdown) - (dtib$greenpeace + greenpeace_crackdown)
+  )
+
+# Plot the contrasts
+contrasts_int %>%
+  pivot_longer(oxfam_amnesty_criticized:red_cross_greenpeace_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis02b_alt.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+ )
+```
+
 These data don't support our hypothesis; the Red Cross brand has an insignificant impact on likelihood to donate compared to both Greenpeace and Amnesty.
@@
 
-# Hypothesis 3a, Issue Area
+#### Hypothesis 3a, Issue Area
 
@@
 # Pull the posterior draws for issue area
-
 # Reference Level = Emergency Response
@@
 
-# Hypothesis 3b, Relationship with Host Government and Issue Area
+#### Hypothesis 3b, Relationship with Host Government and Issue Area
 
@@
 ```{r issue-contrasts-b}
+# Overwrite draws with the appropriate interaction data
+draws <- here::here("analysis", "output", "posterior_draws", "interactions_3b.rds")
 
 # Pull the posterior draws for government crackdown*issue area interaction
-
 # Reference Level = Friendly relationship with government
@@
 )
+
 # Plot the contrasts
@@
 
-# Hypothesis 4a, Funding Sources
+#### Hypothesis 4a, Funding Sources
 
@@
 # Pull the posterior draws for funding sources
-
 # Reference Level = Funded primarily by many small private donations
@@
 
-# Hypothesis 4b, Relationship with Host Government and Funding Sources
+#### Hypothesis 4b, Relationship with Host Government and Funding Sources
 
@@
 ```{r funding-contrasts-b}
+# Overwrite draws with the appropriate interaction data
+draws <- here::here("analysis", "output", "posterior_draws", "interactions_4b.rds")
+
 # Pull the posterior draws for government crackdown*funding sources interaction
-
 # Reference Level = Friendly relationship with government
@@
 
-# Hypothesis 4c, Relationship with Host Government, Funding Sources, and Issue Area
+#### Hypothesis 4c, Relationship with Host Government, Funding Sources, and Issue Area
 
@@
 ```{r funding-contrasts-c}
+# Overwrite draws with the appropriate interaction data
+draws <- here::here("analysis", "output", "posterior_draws", "interactions_4c.rds")
+
 # Pull the posterior draws for issue area*government crackdown*funding sources interaction
-
 # Reference Level = Funded primarily by many small private donations
@@
 
-# Hypothesis 5a, Organizational Practices
+#### Hypothesis 5a, Organizational Practices
 
@@
 ```{r practices-contrasts-a}
-
 # Pull the posterior draws for organizational practices
@@
 
-# Hypothesis 5b, Relationship with Host Government, Organizational Practices
+#### Hypothesis 5b, Relationship with Host Government, Organizational Practices
 
@@
 ```{r practices-contrasts-b}
+# Overwrite draws with the appropriate interaction data
+draws <- here::here("analysis", "output", "posterior_draws", "interactions_5b.rds")
 
 # Pull the posterior draws for organizational practices*government crackdown interaction
-
 # Reference Level = Friendly relationship with government
@@
 
-# Hypothesis 5c, Relationship with Host Government, Organizational Practices, and Funding Sources
+#### Hypothesis 5c, Relationship with Host Government, Organizational Practices, and Funding Sources
 
@@
 ```{r practices-contrasts-c}
+# Overwrite draws with the appropriate interaction data
+draws <- here::here("analysis", "output", "posterior_draws", "interactions_5c.rds")
+
 # Pull the posterior draws for organizational practices*funding sources*government crackdown interaction
-
 # Reference Level = Friendly relationship with government
@@
 
-# Hypothesis 5d, Relationship with Host Government, Organizational Practices, and Issue Area
+#### Hypothesis 5d, Relationship with Host Government, Organizational Practices, and Issue Area
 
@@
 ```{r practices-contrasts-d}
+# Overwrite draws with the appropriate interaction data
+draws <- here::here("analysis", "output", "posterior_draws", "interactions_5d.rds")
 
 # Pull the posterior draws for organizational practices*issue area*government crackdown interaction
-
 # Reference Level = Friendly relationship with government
@@
   fin_refugee_humanright_crackdown = fin_refugee_crackdown - fin_humanrights_crackdown
-
 )
@@
 
-# Hypothesis 5e, Relationship with Host Government, Organizational Practices, Issue Area, and Funding Sources
+#### Hypothesis 5e, Relationship with Host Government, Organizational Practices, Issue Area, and Funding Sources
 
@@
 ```{r practices-contrasts-e}
+# Overwrite draws with the appropriate interaction data
+draws <- here::here("analysis", "output", "posterior_draws", "interactions_5e.rds")
+
 # Pull the posterior draws for organizational practices*funding*issue area*government crackdown interaction
-
 # Reference Level = Friendly relationship with government
@@
   fin_sd_refugee_humanright_crackdown = fin_sd_refugee_crackdown - fin_sd_humanrights_crackdown
-
-  )
+)
+
 # Plot the contrasts
@@
 
-# Hypothesis 5f, Organizational Practices
+#### Hypothesis 5f, Organizational Practices
 
@@
 # Pull the posterior draws for organizational practices
-
 contrasts <- tibble(

### 2021-12-02 analysis/03_analysis.Rmd

@@
 library(tidyverse)
-library(donorheuristics)
 library(fastDummies)

### 2021-12-04 analysis/04_figs-tables.Rmd
Attempt #1 at contrasts with main effects. Hypotheses 4c, 5d and 5e need to be fixed.
I forgot to commit the actual coding changes, somehow. This should do it.

@@
 ```{r}
-# Read in interaction draws for contrasts
-intib <- read_rds(
-    here::here("analysis", "output", "posterior_draws", "interactions.rds")
-  )
-
-# Storing intercept draws in a different tibble for easier use; emergency response, no financial transparency, no accountability, many private donors and friendly relationship with government are all reference levels for their respective groups, and thus are not found in the tibble.
-dtib <- tibble(
+#storing intercept draws for easier reference
+draws_intercepts <- draws
+```
+
+### Hypothesis 1, Branding
+
+> Donors will be more likely to donate to Oxfam and Red Cross compared to Amnesty International and Greenpeace [Mechanism: awareness of need and contentiousness of issue area]
+
+```{r branding-contrasts}
+# Pull the posterior draws for the organizations and compute contrasts
+contrasts <- tibble(
+  amnesty = draws %>% filter(level == "Amnesty International") %>% select(Gamma) %>% pull(),
+  greenpeace = draws %>% filter(level == "Greenpeace") %>% select(Gamma) %>% pull(),
+  oxfam = draws %>% filter(level == "Oxfam") %>% select(Gamma) %>% pull(),
+  red_cross = draws %>% filter(level == "Red Cross") %>% select(Gamma) %>% pull()
+) %>% 
+  mutate(
+    oxfam_amnesty = oxfam - amnesty,
+    oxfam_greenpeace = oxfam - greenpeace,
+    red_cross_amnesty = red_cross - amnesty,
+    red_cross_greenpeace = red_cross - greenpeace,
+  )
+
+# Plot the contrasts
+contrasts %>%
+  pivot_longer(oxfam_amnesty:red_cross_greenpeace, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis01.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
+```
+
+Donors are indeed more likely to donate to Red Cross compared to Amnesty International and Greenpeace.
+However, compared to Amnesty International and Greenpeace, donors are less likely to donate to Oxfam.
+In fact, there is a negligible difference between donors likelihood to donate to Oxfam and Amnesty International.
+
+### Hypothesis 2, Government Crackdown
+
+#### Hypothesis 2a, Relationship with Host Government
+
+> Donors will show increased willingness to donate to NGOs that are facing government crackdown or criticism [Mechanism: Governments wouldn't be cracking down on them if they didn't perceive a threat from them which means organizations implementing their missions effectively.
+This perception of efficacy leads to increased donations.]
+
+```{r crackdown-contrasts-a}
+# Pull the posterior draws for government crackdown
+# Reference Level = Friendly relationship with government
+
+contrasts <- tibble(
+  under_crackdown = draws %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
+  criticized = draws %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
+  )
+
+# Plot the contrasts
+contrasts %>%
+  pivot_longer(under_crackdown:criticized, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis02a.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
+```
+
+Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism.
+This decreased likelihood to donate is also greater for NGOs under crackdown compared to those under criticism.
+
+#### Hypothesis 2b, Organization and Relationship with Host Government
+
+> Donors will show increased willingness to donate to Oxfam and Red Cross when they are facing government crackdown or criticism compared to when Amnesty or Greenpeace is facing crackdown.
+
+```{r crackdown-contrasts-b}
+# Overwrite draws with the appropriate interaction data
+
+draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_2b.rds"))
+
+# Pull the posterior draws for organization*government crackdown interaction
+# Reference Level = Friendly relationship with government
+
+contrasts_int <- tibble(
   amnesty = draws %>% filter(i == 1) %>% select(Gamma) %>% pull(),
@@
   criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
-  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull()
-)
-```
-
-### Hypothesis 1, Branding
-
-> Donors will be more likely to donate to Oxfam and Red Cross compared to Amnesty International and Greenpeace [Mechanism: awareness of need and contentiousness of issue area]
-
-```{r branding-contrasts}
-# Pull the posterior draws for the organizations and compute contrasts
-contrasts <- tibble(
-  amnesty = draws %>% filter(level == "Amnesty International") %>% select(Gamma) %>% pull(),
-  greenpeace = draws %>% filter(level == "Greenpeace") %>% select(Gamma) %>% pull(),
-  oxfam = draws %>% filter(level == "Oxfam") %>% select(Gamma) %>% pull(),
-  red_cross = draws %>% filter(level == "Red Cross") %>% select(Gamma) %>% pull()
+  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
+  amnesty_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  greenpeace_criticized = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  oxfam_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  red_cross_criticized = draws %>% filter(i == 17)%>% select(Gamma) %>% pull(),
+  amnesty_crackdown = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  greenpeace_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
+  oxfam_crackdown = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
+  red_cross_crackdown = draws %>% filter(i == 21)%>% select(Gamma) %>% pull()
 ) %>% 
   mutate(
-    oxfam_amnesty = oxfam - amnesty,
-    oxfam_greenpeace = oxfam - greenpeace,
-    red_cross_amnesty = red_cross - amnesty,
-    red_cross_greenpeace = red_cross - greenpeace,
-  )
-
-# Plot the contrasts
-contrasts %>%
-  pivot_longer(oxfam_amnesty:red_cross_greenpeace, names_to = "level", values_to = "Gamma") %>% 
-  ggplot(aes(x = Gamma, y = level)) +
-  stat_halfeye(.width = .95) +
-  geom_vline(xintercept = 0, color = "grey") +
-  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
-
-# Save plot
-ggsave(
-  "contrasts_hypothesis01.png",
-  path = here::here("analysis", "output", "figures"),
-  width = 12,
-  height = 6,
-  units = "in"
-)
-```
-
-Donors are indeed more likely to donate to Red Cross compared to Amnesty International and Greenpeace.
-However, compared to Amnesty International and Greenpeace, donors are less likely to donate to Oxfam.
-In fact, there is a negligible difference between donors likelihood to donate to Oxfam and Amnesty International.
-
-### Hypothesis 2, Government Crackdown
-
-#### Hypothesis 2a, Relationship with Host Government
-
-> Donors will show increased willingness to donate to NGOs that are facing government crackdown or criticism [Mechanism: Governments wouldn't be cracking down on them if they didn't perceive a threat from them which means organizations implementing their missions effectively.
-This perception of efficacy leads to increased donations.]
-
-```{r crackdown-contrasts-a}
-# Pull the posterior draws for government crackdown
-# Reference Level = Friendly relationship with government
-
-contrasts <- tibble(
-  under_crackdown = draws %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
-  criticized = draws %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
-  )
-
-# Plot the contrasts
-contrasts %>%
-  pivot_longer(under_crackdown:criticized, names_to = "level", values_to = "Gamma") %>% 
-  ggplot(aes(x = Gamma, y = level)) +
-  stat_halfeye(.width = .95) +
-  geom_vline(xintercept = 0, color = "grey") +
-  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
-
-# Save plot
-ggsave(
-  "contrasts_hypothesis02a.png",
-  path = here::here("analysis", "output", "figures"),
-  width = 12,
-  height = 6,
-  units = "in"
-)
-```
-
-Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism.
-This decreased likelihood to donate is also greater for NGOs under crackdown compared to those under criticism.
-
-#### Hypothesis 2b, Organization and Relationship with Host Government
-
-> Donors will show increased willingness to donate to Oxfam and Red Cross when they are facing government crackdown or criticism compared to when Amnesty or Greenpeace is facing crackdown.
-
-```{r crackdown-contrasts-b}
-# Overwrite draws with the appropriate interaction data
-draws <- here::here("analysis", "output", "posterior_draws", "interactions_2b.rds")
-
-# Pull the posterior draws for organization*government crackdown interaction
-# Reference Level = Friendly relationship with government
-
-contrasts_int <- tibble(
-  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
-  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
-  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
-  red_cross_criticized = intib %>% filter(i == 17)%>% select(Gamma) %>% pull(),
-  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
-  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
-  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
-  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
-) %>% 
-  mutate(
-    oxfam_amnesty_criticized = ((dtib$oxfam + oxfam_criticized) - (dtib$amnesty + amnesty_criticized) + dtib$criticized),
-    oxfam_greenpeace_criticized = ((dtib$oxfam + oxfam_criticized) - (dtib$greenpeace + greenpeace_criticized) + dtib$criticized),
-    red_cross_amnesty_criticized = ((dtib$red_cross + red_cross_criticized) - (dtib$amnesty + amnesty_criticized) + dtib$criticized),
-    red_cross_greenpeace_criticized = ((dtib$red_cross + red_cross_criticized) - (dtib$greenpeace + greenpeace_criticized) + dtib$criticized),
-    oxfam_amnesty_crackdown = ((dtib$oxfam + oxfam_crackdown) - (dtib$amnesty + amnesty_crackdown) + dtib$crackdown),
-    oxfam_greenpeace_crackdown = ((dtib$oxfam + oxfam_crackdown) - (dtib$greenpeace + greenpeace_crackdown) + dtib$crackdown),
-    red_cross_amnesty_crackdown = ((dtib$red_cross + red_cross_crackdown) - (dtib$amnesty + amnesty_crackdown) + dtib$crackdown),
-    red_cross_greenpeace_crackdown = ((dtib$red_cross + red_cross_crackdown) - (dtib$greenpeace + greenpeace_crackdown) + dtib$crackdown)
+    oxfam_amnesty_criticized = (oxfam + criticized + oxfam_criticized) - (amnesty + criticized + amnesty_criticized),
+
+    oxfam_greenpeace_criticized = (oxfam + criticized + oxfam_criticized) - (greenpeace + criticized + greenpeace_criticized),
+
+    red_cross_amnesty_criticized = (red_cross + criticized + red_cross_criticized) - (amnesty + criticized + amnesty_criticized),
+
+    red_cross_greenpeace_criticized = (red_cross + criticized + red_cross_criticized) - (greenpeace + criticized + greenpeace_criticized),
+
+    oxfam_amnesty_crackdown = (oxfam + crackdown + oxfam_crackdown) - (amnesty + crackdown +  amnesty_crackdown),
+
+    oxfam_greenpeace_crackdown = (oxfam + crackdown + oxfam_crackdown) - (greenpeace + crackdown +  greenpeace_crackdown),
+
+    red_cross_amnesty_crackdown = (red_cross + crackdown + red_cross_crackdown) - (amnesty + crackdown +  amnesty_crackdown),
+
+    red_cross_greenpeace_crackdown = (red_cross + crackdown + red_cross_crackdown) - (greenpeace + crackdown + greenpeace_crackdown)
   )
@@
 
-```{r crackdown-contrasts-b-alt}
-# Overwrite draws with the appropriate interaction data
-draws <- here::here("analysis", "output", "posterior_draws", "interactions_2b.rds")
-
-# Pull the posterior draws for organization*government crackdown interaction
-# Reference Level = Friendly relationship with government
-
-contrasts_int <- tibble(
-  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
-  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
-  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
-  red_cross_criticized = intib %>% filter(i == 17)%>% select(Gamma) %>% pull(),
-  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
-  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
-  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
-  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
-) %>% 
-  mutate(
-    oxfam_amnesty_criticized = (dtib$oxfam + oxfam_criticized) - (dtib$amnesty + amnesty_criticized),
-    oxfam_greenpeace_criticized = (dtib$oxfam + oxfam_criticized) - (dtib$greenpeace + greenpeace_criticized),
-    red_cross_amnesty_criticized = (dtib$red_cross + red_cross_criticized) - (dtib$amnesty + amnesty_criticized),
-    red_cross_greenpeace_criticized = (dtib$red_cross + red_cross_criticized) - (dtib$greenpeace + greenpeace_criticized),
-    oxfam_amnesty_crackdown = (dtib$oxfam + oxfam_crackdown) - (dtib$amnesty + amnesty_crackdown),
-    oxfam_greenpeace_crackdown = (dtib$oxfam + oxfam_crackdown) - (dtib$greenpeace + greenpeace_crackdown),
-    red_cross_amnesty_crackdown = (dtib$red_cross + red_cross_crackdown) - (dtib$amnesty + amnesty_crackdown),
-    red_cross_greenpeace_crackdown = (dtib$red_cross + red_cross_crackdown) - (dtib$greenpeace + greenpeace_crackdown)
-  )
-
-# Plot the contrasts
-contrasts_int %>%
-  pivot_longer(oxfam_amnesty_criticized:red_cross_greenpeace_crackdown, names_to = "level", values_to = "Gamma") %>% 
-  ggplot(aes(x = Gamma, y = level)) +
-  stat_halfeye(.width = .95) +
-  geom_vline(xintercept = 0, color = "grey") +
-  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
-
-# Save plot
-ggsave(
-  "contrasts_hypothesis02b_alt.png",
-  path = here::here("analysis", "output", "figures"),
-  width = 12,
-  height = 6,
-  units = "in"
- )
-```
-
 These data don't support our hypothesis; the Red Cross brand has an insignificant impact on likelihood to donate compared to both Greenpeace and Amnesty.
@@
 # Reference Level = Emergency Response
-
+draws <- draws_intercepts
 contrasts <- tibble(
@@
 # Overwrite draws with the appropriate interaction data
-draws <- here::here("analysis", "output", "posterior_draws", "interactions_3b.rds")
+draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))
 
@@
 contrasts_int <- tibble(
-  criticized_environment = intib %>% filter(i == 22) %>% select(Gamma) %>% pull(),
-  criticized_humanrights = intib %>% filter(i == 23) %>% select(Gamma) %>% pull(),
-  criticized_refugee = intib %>% filter(i == 24) %>% select(Gamma) %>% pull(),
-  crackdown_environment = intib %>% filter(i == 25) %>% select(Gamma) %>% pull(),
-  crackdown_humanrights = intib %>% filter(i == 26) %>% select(Gamma) %>% pull(),
-  crackdown_refugee = intib %>% filter(i == 27) %>% select(Gamma) %>% pull(),
+  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
+  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
+  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
+  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
+  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
+  criticized_environment = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  criticized_humanrights = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  criticized_refugee = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  crackdown_environment = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
+  crackdown_humanrights = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  crackdown_refugee = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
 ) %>% 
   mutate(
-  criticized_refugee_environment = criticized_refugee - criticized_environment,
-  criticized_refugee_humanrights = criticized_refugee - criticized_humanrights,
-  crackdown_refugee_environment = crackdown_refugee - crackdown_environment,
-  crackdown_refugee_humanrights = crackdown_refugee - crackdown_humanrights
+  criticized_refugee_environment = (criticized + refugee_relief + criticized_refugee) - (criticized + environment + criticized_environment),
+
+  criticized_refugee_humanrights = (criticized + refugee_relief + criticized_refugee) - (criticized + human_rights + criticized_humanrights),
+
+  crackdown_refugee_environment = (crackdown + refugee_relief + crackdown_refugee - crackdown + environment + crackdown_environment),
+
+  crackdown_refugee_humanrights = (crackdown + refugee_relief + crackdown_refugee - crackdown + human_rights + crackdown_humanrights)
 )
@@
 # Reference Level = Funded primarily by many small private donations
-
+draws <- draws_intercepts
 contrasts <- tibble(
@@
 # Overwrite draws with the appropriate interaction data
-draws <- here::here("analysis", "output", "posterior_draws", "interactions_4b.rds")
+draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds"))
 
@@
 contrasts_int <- tibble(
-  criticized_wealthydonors = intib %>% filter(i == 28) %>% select(Gamma) %>% pull(),
-  criticized_grants = intib %>% filter(i == 29) %>% select(Gamma) %>% pull(),
-  crackdown_wealthydonors = intib %>% filter(i == 30) %>% select(Gamma) %>% pull(),
-  crackdown_grants = intib %>% filter(i == 31) %>% select(Gamma) %>% pull(),
+  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
+  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
+  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
+  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
+  criticized_wealthydonors = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  criticized_grants = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  crackdown_wealthydonors = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  crackdown_grants = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
+) %>% mutate(
+  criticized_wealthydonors = (criticized + few_wealthy_private_donors + criticized_wealthydonors) - criticized,
+
+  criticized_grants = (criticized + government_grants + criticized_grants) - criticized,
+
+  crackdown_wealthydonors = (crackdown + few_wealthy_private_donors + crackdown_wealthydonors) - crackdown,
+
+  crackdown_grants = (crackdown + government_grants + crackdown_grants) - crackdown
 )
@@
 # Overwrite draws with the appropriate interaction data
-draws <- here::here("analysis", "output", "posterior_draws", "interactions_4c.rds")
+draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4c.rds"))
 
@@
 contrasts_int <- tibble(
-  emergency_crackdown_wealthydonors = intib %>% filter(i == 32) %>% select(Gamma) %>% pull(),
-  emergency_crackdown_grants = intib %>% filter(i == 33) %>% select(Gamma) %>% pull(),
-  environment_crackdown_wealthydonors = intib %>% filter(i == 34) %>% select(Gamma) %>% pull(),
-  environment_crackdown_grants = intib %>% filter(i == 35) %>% select(Gamma) %>% pull(),
-  humanrights_crackdown_wealthydonors = intib %>% filter(i == 36) %>% select(Gamma) %>% pull(),
-  humanrights_crackdown_grants = intib %>% filter(i == 37) %>% select(Gamma) %>% pull(),
-  refugee_crackdown_wealthydonors = intib %>% filter(i == 38) %>% select(Gamma) %>% pull(),
-  refugee_crackdown_grants = intib %>% filter(i == 39) %>% select(Gamma) %>% pull(),
+  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
+  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
+  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
+  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
+  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
+  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
+  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
+  emergency_crackdown_wealthydonors = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  emergency_crackdown_grants = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  environment_crackdown_wealthydonors = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  environment_crackdown_grants = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
+  humanrights_crackdown_wealthydonors = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  humanrights_crackdown_grants = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
+  refugee_crackdown_wealthydonors = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
+  refugee_crackdown_grants = draws %>% filter(i == 21) %>% select(Gamma) %>% pull(),
 ) %>% 
   mutate(
-  emergency_humanrights_wealthydonors = emergency_crackdown_wealthydonors - humanrights_crackdown_wealthydonors ,
-  emergency_environment_wealthydonors = emergency_crackdown_wealthydonors - environment_crackdown_wealthydonors,
-  emergency_grants_wealthydonors = emergency_crackdown_wealthydonors - emergency_crackdown_grants,
-  refugee_humanrights_wealthydonors = refugee_crackdown_wealthydonors - humanrights_crackdown_wealthydonors,
-  refugee_environment_wealthydonors = refugee_crackdown_wealthydonors - environment_crackdown_wealthydonors,
-  refugee_grants_wealthydonors = refugee_crackdown_grants - refugee_crackdown_wealthydonors
+  emergency_humanrights_wealthydonors = (crackdown + emergency_crackdown_wealthydonors) - (crackdown + few_wealthy_private_donors + human_rights + humanrights_crackdown_wealthydonors),
+
+  emergency_humanrights_grants = (crackdown + emergency_crackdown_grants) - (crackdown + government_grants + human_rights + humanrights_crackdown_grants),
+
+  emergency_environment_wealthydonors = (crackdown + emergency_crackdown_wealthydonors) - (crackdown + few_wealthy_private_donors + environment + environment_crackdown_wealthydonors),
+
+  emergency_environment_grants = (crackdown + emergency_crackdown_grants) - (crackdown + government_grants + environment + environment_crackdown_wealthydonors),
+
+  refugee_humanrights_wealthydonors = (crackdown + refugee_relief + refugee_crackdown_wealthydonors) - (crackdown + few_wealthy_private_donors + human_rights + humanrights_crackdown_wealthydonors),
+
+  refugee_humanrights_grants = (crackdown + refugee_relief + refugee_crackdown_grants) - (crackdown + government_grants +  human_rights + humanrights_crackdown_grants),
+
+  refugee_environment_wealthydonors = (crackdown + refugee_relief + refugee_crackdown_wealthydonors) - (crackdown + few_wealthy_private_donors + environment + environment_crackdown_wealthydonors),
+
+  refugee_environment_grants = (crackdown + refugee_relief + refugee_crackdown_grants) - (crackdown + government_grants + environment + environment_crackdown_grants),
+
   )
@@
 contrasts_int %>%
-  pivot_longer(emergency_humanrights_wealthydonors:refugee_grants_wealthydonors, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer(emergency_humanrights_wealthydonors:refugee_environment_grants, names_to = "level", values_to = "Gamma") %>% 
   ggplot(aes(x = Gamma, y = level)) +
@@
 # Pull the posterior draws for organizational practices
-
+draws <- draws_intercepts
 contrasts <- tibble(
@@
 # Overwrite draws with the appropriate interaction data
-draws <- here::here("analysis", "output", "posterior_draws", "interactions_5b.rds")
+draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
 
@@
 contrasts_int <- tibble(
-  financial_transparency_criticized = intib %>% filter(i == 40) %>% select(Gamma) %>% pull(),
-  financial_transparency_crackdown = intib %>% filter(i == 41) %>% select(Gamma) %>% pull(),
+  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
+  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
+  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
+  financial_transparency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  financial_transparency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  ) %>% mutate(
+    financial_transparency_criticized = fin_transparency + criticized + financial_transparency_criticized,
+    financial_transparency_crackdown = fin_transparency + crackdown + financial_transparency_crackdown
   )
@@
 # Overwrite draws with the appropriate interaction data
-draws <- here::here("analysis", "output", "posterior_draws", "interactions_5c.rds")
+draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5c.rds"))
 
@@
 contrasts_int <- tibble(
-  fin_smalldonors_criticized = intib %>% filter(i == 42) %>% select(Gamma) %>% pull(),
-  fin_wealthydonors_criticized = intib %>% filter(i == 43) %>% select(Gamma) %>% pull(),
-  fin_grants_criticized = intib %>% filter(i == 44) %>% select(Gamma) %>% pull(),
-  fin_smalldonors_crackdown = intib %>% filter(i == 45) %>% select(Gamma) %>% pull(),
-  fin_wealthydonors_crackdown = intib %>% filter(i == 46) %>% select(Gamma) %>% pull(),
-  fin_grants_crackdown = intib %>% filter(i == 47) %>% select(Gamma) %>% pull(),
+  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
+  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
+  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
+  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
+  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
+  fin_smalldonors_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  fin_wealthydonors_criticized = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  fin_grants_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  fin_smalldonors_crackdown = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
+  fin_wealthydonors_crackdown = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  fin_grants_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
   ) %>%
   mutate(
-  fin_smalldonors_wealthydonors_criticized = fin_smalldonors_criticized - fin_wealthydonors_criticized,
-  fin_smalldonors_grants_criticized = fin_smalldonors_criticized - fin_grants_criticized,
-  fin_smalldonors_wealthydonors_crackdown = fin_smalldonors_crackdown - fin_wealthydonors_crackdown,
-  fin_smalldonors_grants_crackdown = fin_smalldonors_crackdown - fin_grants_crackdown
+  fin_smalldonors_wealthydonors_criticized = (fin_transparency + criticized + fin_smalldonors_criticized) - (fin_transparency + criticized + few_wealthy_private_donors + fin_wealthydonors_criticized),
+
+  fin_smalldonors_grants_criticized = (fin_transparency + criticized + fin_smalldonors_criticized) -  (fin_transparency + criticized + government_grants + fin_grants_criticized),
+
+  fin_smalldonors_wealthydonors_crackdown = (fin_transparency + crackdown + fin_smalldonors_crackdown) - (fin_transparency + crackdown + few_wealthy_private_donors + fin_wealthydonors_crackdown),
+
+  fin_smalldonors_grants_crackdown = (fin_transparency + crackdown + fin_smalldonors_crackdown) - (fin_transparency + crackdown + government_grants + fin_grants_crackdown)
   )
@@
 # Overwrite draws with the appropriate interaction data
-draws <- here::here("analysis", "output", "posterior_draws", "interactions_5d.rds")
+draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds"))
 
@@
 contrasts_int <- tibble(
-  fin_emergency_criticized = intib %>% filter(i == 48) %>% select(Gamma) %>% pull(),
-  fin_emergency_crackdown = intib %>% filter(i == 49) %>% select(Gamma) %>% pull(),
-  fin_environment_criticized = intib %>% filter(i == 50) %>% select(Gamma) %>% pull(),
-  fin_environment_crackdown = intib %>% filter(i == 51) %>% select(Gamma) %>% pull(),
-  fin_humanrights_criticized = intib %>% filter(i == 52) %>% select(Gamma) %>% pull(),
-  fin_humanrights_crackdown = intib %>% filter(i == 53) %>% select(Gamma) %>% pull(),
-  fin_refugee_criticized = intib %>% filter(i == 54) %>% select(Gamma) %>% pull(),
-  fin_refugee_crackdown = intib %>% filter(i == 55) %>% select(Gamma) %>% pull()
+  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
+  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
+  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
+  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
+  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
+  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
+  fin_emergency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  fin_emergency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  fin_environment_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  fin_environment_crackdown = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
+  fin_humanrights_criticized = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  fin_humanrights_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
+  fin_refugee_criticized = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
+  fin_refugee_crackdown = draws %>% filter(i == 21) %>% select(Gamma) %>% pull()
   ) %>%
   mutate(
-  fin_emergency_environment_criticized = fin_emergency_criticized - fin_environment_criticized,
-  fin_emergency_humanrights_criticized = fin_emergency_criticized - fin_humanrights_criticized,
-  fin_emergency_environment_crackdown = fin_emergency_crackdown - fin_environment_crackdown,
-  fin_emergency_humanright_crackdown = fin_emergency_crackdown - fin_humanrights_crackdown,
-  fin_refugee_environment_criticized = fin_refugee_criticized - fin_environment_criticized,
-  fin_refugee_humanright_criticized = fin_refugee_criticized - fin_humanrights_criticized,
-  fin_refugee_environment_crackdown = fin_refugee_crackdown - fin_environment_crackdown,
-  fin_refugee_humanright_crackdown = fin_refugee_crackdown - fin_humanrights_crackdown
+  fin_emergency_environment_criticized = (fin_transparency + criticized + fin_emergency_criticized) - (fin_transparency + criticized + environment + fin_environment_criticized),
+
+  fin_emergency_humanrights_criticized = (fin_transparency + criticized + fin_emergency_criticized) - fin_transparency + criticized + human_rights + fin_humanrights_criticized,
+
+  fin_emergency_environment_crackdown = (fin_transparency + crackdown + fin_emergency_crackdown) - (fin_transparency + crackdown + environment + fin_environment_crackdown),
+
+  fin_emergency_humanright_crackdown = (fin_transparency + crackdown + fin_emergency_crackdown) - (fin_transparency + crackdown + human_rights + fin_humanrights_crackdown),
+
+  fin_refugee_environment_criticized = (fin_transparency + criticized + fin_refugee_criticized) - (fin_transparency + criticized + environment + fin_environment_criticized),
+
+  fin_refugee_humanright_criticized = (fin_transparency + criticized + fin_refugee_criticized) - (fin_transparency + criticized + human_rights + fin_humanrights_criticized),
+
+  fin_refugee_environment_crackdown = (fin_transparency + crackdown + fin_refugee_crackdown) - (fin_transparency + crackdown + environment + fin_environment_crackdown),
+
+  fin_refugee_humanright_crackdown = (fin_transparency + crackdown + fin_refugee_crackdown) - (fin_transparency + crackdown + human_rights + fin_humanrights_crackdown)
 )
@@
 # Overwrite draws with the appropriate interaction data
-draws <- here::here("analysis", "output", "posterior_draws", "interactions_5e.rds")
+draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5e.rds"))
 
@@
 contrasts_int <- tibble(
-  fin_sd_emergency_criticized = intib %>% filter(i == 56) %>% select(Gamma) %>% pull(),
-  fin_sd_emergency_crackdown = intib %>% filter(i == 57) %>% select(Gamma) %>% pull(),
-  fin_sd_environment_criticized = intib %>% filter(i == 58) %>% select(Gamma) %>% pull(),
-  fin_sd_environment_crackdown = intib %>% filter(i == 59) %>% select(Gamma) %>% pull(),
-  fin_sd_humanrights_criticized = intib %>% filter(i == 60) %>% select(Gamma) %>% pull(),
-  fin_sd_humanrights_crackdown = intib %>% filter(i == 61) %>% select(Gamma) %>% pull(),
-  fin_sd_refugee_criticized = intib %>% filter(i == 62) %>% select(Gamma) %>% pull(),
-  fin_sd_refugee_crackdown = intib %>% filter(i == 63) %>% select(Gamma) %>% pull()
-  ) %>%
-  mutate(
-  fin_sd_emergency_environment_criticized = fin_sd_emergency_criticized - fin_sd_environment_criticized,
-  fin_sd_emergency_humanrights_criticized = fin_sd_emergency_criticized - fin_sd_humanrights_criticized,
-  fin_sd_emergency_environment_crackdown = fin_sd_emergency_crackdown - fin_sd_environment_crackdown,
-  fin_sd_emergency_humanright_crackdown = fin_sd_emergency_crackdown - fin_sd_humanrights_crackdown,
-  fin_sd_refugee_environment_criticized = fin_sd_refugee_criticized - fin_sd_environment_criticized,
-  fin_sd_refugee_humanright_criticized = fin_sd_refugee_criticized - fin_sd_humanrights_criticized,
-  fin_sd_refugee_environment_crackdown = fin_sd_refugee_crackdown - fin_sd_environment_crackdown,
-  fin_sd_refugee_humanright_crackdown = fin_sd_refugee_crackdown - fin_sd_humanrights_crackdown
-)
+  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
+  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
+  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
+  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
+  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
+  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
+  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
+  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
+  fin_sd_emergency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  fin_sd_emergency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  fin_sd_environment_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  fin_sd_environment_crackdown = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
+  fin_sd_humanrights_criticized = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  fin_sd_humanrights_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
+  fin_sd_refugee_criticized = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
+  fin_sd_refugee_crackdown = draws %>% filter(i == 21) %>% select(Gamma) %>% pull()
+  ) %>% mutate(
+  fin_sd_emergency_environment_criticized = (fin_transparency + criticized + fin_sd_emergency_criticized) - (fin_transparency + criticized + environment +  fin_sd_environment_criticized),
+
+  fin_sd_emergency_humanrights_criticized = (fin_transparency + criticized + fin_sd_emergency_criticized) - (fin_transparency + criticized + human_rights +  fin_sd_humanrights_criticized),
+
+  fin_sd_emergency_environment_crackdown = (fin_transparency + crackdown + fin_sd_emergency_crackdown) - (fin_transparency + crackdown + environment +  fin_sd_environment_crackdown),
+
+  fin_sd_emergency_humanright_crackdown = (fin_transparency + crackdown + fin_sd_emergency_crackdown) - (fin_transparency + crackdown + human_rights + fin_sd_humanrights_crackdown),
+
+  fin_sd_refugee_environment_criticized = (fin_transparency + criticized + refugee_relief +  fin_sd_refugee_criticized) - (fin_transparency + criticized + environment +  fin_sd_environment_criticized),
+
+  fin_sd_refugee_humanright_criticized = (fin_transparency + criticized + refugee_relief +  fin_sd_refugee_criticized) - (fin_transparency + criticized + human_rights +  fin_sd_humanrights_criticized),
+
+  fin_sd_refugee_environment_crackdown = (fin_transparency + crackdown + refugee_relief + fin_sd_refugee_crackdown) - (fin_transparency + crackdown + environment + fin_sd_environment_crackdown),
+
+  fin_sd_refugee_humanright_crackdown = (fin_transparency + crackdown + refugee_relief + fin_sd_refugee_crackdown) - (fin_transparency + crackdown + human_rights + fin_sd_humanrights_crackdown
+))
 
@@
 # Pull the posterior draws for organizational practices
+draws <- draws_intercepts
 contrasts <- tibble(

### 2021-12-04 analysis/04_figs-tables.Rmd
Attempt #1 at contrasts with main effects. Hypotheses 4c, 5d and 5e need to be fixed.

--- 2021-12-02 analysis/04_figs-tables.Rmd
@@
 
-```{r}
-# Read in interaction draws for contrasts
-intib <- read_rds(
-    here::here("analysis", "output", "posterior_draws", "interactions.rds")
-  )
-
-# Storing intercept draws in a different tibble for easier use; emergency response, no financial transparency, no accountability, many private donors and friendly relationship with government are all reference levels for their respective groups, and thus are not found in the tibble.
-dtib <- tibble(
+### Hypothesis 1, Branding
+
+> Donors will be more likely to donate to Oxfam and Red Cross compared to Amnesty International and Greenpeace [Mechanism: awareness of need and contentiousness of issue area]
+
+```{r branding-contrasts}
+# Pull the posterior draws for the organizations and compute contrasts
+contrasts <- tibble(
+  amnesty = draws %>% filter(level == "Amnesty International") %>% select(Gamma) %>% pull(),
+  greenpeace = draws %>% filter(level == "Greenpeace") %>% select(Gamma) %>% pull(),
+  oxfam = draws %>% filter(level == "Oxfam") %>% select(Gamma) %>% pull(),
+  red_cross = draws %>% filter(level == "Red Cross") %>% select(Gamma) %>% pull()
+) %>% 
+  mutate(
+    oxfam_amnesty = oxfam - amnesty,
+    oxfam_greenpeace = oxfam - greenpeace,
+    red_cross_amnesty = red_cross - amnesty,
+    red_cross_greenpeace = red_cross - greenpeace,
+  )
+
+# Plot the contrasts
+contrasts %>%
+  pivot_longer(oxfam_amnesty:red_cross_greenpeace, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis01.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
+```
+
+Donors are indeed more likely to donate to Red Cross compared to Amnesty International and Greenpeace.
+However, compared to Amnesty International and Greenpeace, donors are less likely to donate to Oxfam.
+In fact, there is a negligible difference between donors likelihood to donate to Oxfam and Amnesty International.
+
+### Hypothesis 2, Government Crackdown
+
+#### Hypothesis 2a, Relationship with Host Government
+
+> Donors will show increased willingness to donate to NGOs that are facing government crackdown or criticism [Mechanism: Governments wouldn't be cracking down on them if they didn't perceive a threat from them which means organizations implementing their missions effectively.
+This perception of efficacy leads to increased donations.]
+
+```{r crackdown-contrasts-a}
+# Pull the posterior draws for government crackdown
+# Reference Level = Friendly relationship with government
+
+contrasts <- tibble(
+  under_crackdown = draws %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
+  criticized = draws %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
+  )
+
+# Plot the contrasts
+contrasts %>%
+  pivot_longer(under_crackdown:criticized, names_to = "level", values_to = "Gamma") %>% 
+  ggplot(aes(x = Gamma, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+
+# Save plot
+ggsave(
+  "contrasts_hypothesis02a.png",
+  path = here::here("analysis", "output", "figures"),
+  width = 12,
+  height = 6,
+  units = "in"
+)
+```
+
+Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism.
+This decreased likelihood to donate is also greater for NGOs under crackdown compared to those under criticism.
+
+#### Hypothesis 2b, Organization and Relationship with Host Government
+
+> Donors will show increased willingness to donate to Oxfam and Red Cross when they are facing government crackdown or criticism compared to when Amnesty or Greenpeace is facing crackdown.
+
+```{r crackdown-contrasts-b}
+# Overwrite draws with the appropriate interaction data
+
+draws <- here::here("data", "raw_data", "posterior_draws", "interactions_2b.rds")
+
+# Pull the posterior draws for organization*government crackdown interaction
+# Reference Level = Friendly relationship with government
+
+contrasts_int <- tibble(
   amnesty = draws %>% filter(i == 1) %>% select(Gamma) %>% pull(),
@@
   criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
-  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull()
-)
-```
-
-### Hypothesis 1, Branding
-
-> Donors will be more likely to donate to Oxfam and Red Cross compared to Amnesty International and Greenpeace [Mechanism: awareness of need and contentiousness of issue area]
-
-```{r branding-contrasts}
-# Pull the posterior draws for the organizations and compute contrasts
-contrasts <- tibble(
-  amnesty = draws %>% filter(level == "Amnesty International") %>% select(Gamma) %>% pull(),
-  greenpeace = draws %>% filter(level == "Greenpeace") %>% select(Gamma) %>% pull(),
-  oxfam = draws %>% filter(level == "Oxfam") %>% select(Gamma) %>% pull(),
-  red_cross = draws %>% filter(level == "Red Cross") %>% select(Gamma) %>% pull()
+  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
+  amnesty_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  greenpeace_criticized = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  oxfam_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  red_cross_criticized = draws %>% filter(i == 17)%>% select(Gamma) %>% pull(),
+  amnesty_crackdown = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  greenpeace_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
+  oxfam_crackdown = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
+  red_cross_crackdown = draws %>% filter(i == 21)%>% select(Gamma) %>% pull()
 ) %>% 
   mutate(
-    oxfam_amnesty = oxfam - amnesty,
-    oxfam_greenpeace = oxfam - greenpeace,
-    red_cross_amnesty = red_cross - amnesty,
-    red_cross_greenpeace = red_cross - greenpeace,
-  )
-
-# Plot the contrasts
-contrasts %>%
-  pivot_longer(oxfam_amnesty:red_cross_greenpeace, names_to = "level", values_to = "Gamma") %>% 
-  ggplot(aes(x = Gamma, y = level)) +
-  stat_halfeye(.width = .95) +
-  geom_vline(xintercept = 0, color = "grey") +
-  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
-
-# Save plot
-ggsave(
-  "contrasts_hypothesis01.png",
-  path = here::here("analysis", "output", "figures"),
-  width = 12,
-  height = 6,
-  units = "in"
-)
-```
-
-Donors are indeed more likely to donate to Red Cross compared to Amnesty International and Greenpeace.
-However, compared to Amnesty International and Greenpeace, donors are less likely to donate to Oxfam.
-In fact, there is a negligible difference between donors likelihood to donate to Oxfam and Amnesty International.
-
-### Hypothesis 2, Government Crackdown
-
-#### Hypothesis 2a, Relationship with Host Government
-
-> Donors will show increased willingness to donate to NGOs that are facing government crackdown or criticism [Mechanism: Governments wouldn't be cracking down on them if they didn't perceive a threat from them which means organizations implementing their missions effectively.
-This perception of efficacy leads to increased donations.]
-
-```{r crackdown-contrasts-a}
-# Pull the posterior draws for government crackdown
-# Reference Level = Friendly relationship with government
-
-contrasts <- tibble(
-  under_crackdown = draws %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
-  criticized = draws %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
-  )
-
-# Plot the contrasts
-contrasts %>%
-  pivot_longer(under_crackdown:criticized, names_to = "level", values_to = "Gamma") %>% 
-  ggplot(aes(x = Gamma, y = level)) +
-  stat_halfeye(.width = .95) +
-  geom_vline(xintercept = 0, color = "grey") +
-  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
-
-# Save plot
-ggsave(
-  "contrasts_hypothesis02a.png",
-  path = here::here("analysis", "output", "figures"),
-  width = 12,
-  height = 6,
-  units = "in"
-)
-```
-
-Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism.
-This decreased likelihood to donate is also greater for NGOs under crackdown compared to those under criticism.
-
-#### Hypothesis 2b, Organization and Relationship with Host Government
-
-> Donors will show increased willingness to donate to Oxfam and Red Cross when they are facing government crackdown or criticism compared to when Amnesty or Greenpeace is facing crackdown.
-
-```{r crackdown-contrasts-b}
-# Overwrite draws with the appropriate interaction data
-draws <- here::here("analysis", "output", "posterior_draws", "interactions_2b.rds")
-
-# Pull the posterior draws for organization*government crackdown interaction
-# Reference Level = Friendly relationship with government
-
-contrasts_int <- tibble(
-  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
-  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
-  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
-  red_cross_criticized = intib %>% filter(i == 17)%>% select(Gamma) %>% pull(),
-  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
-  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
-  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
-  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
-) %>% 
-  mutate(
-    oxfam_amnesty_criticized = ((dtib$oxfam + oxfam_criticized) - (dtib$amnesty + amnesty_criticized) + dtib$criticized),
-    oxfam_greenpeace_criticized = ((dtib$oxfam + oxfam_criticized) - (dtib$greenpeace + greenpeace_criticized) + dtib$criticized),
-    red_cross_amnesty_criticized = ((dtib$red_cross + red_cross_criticized) - (dtib$amnesty + amnesty_criticized) + dtib$criticized),
-    red_cross_greenpeace_criticized = ((dtib$red_cross + red_cross_criticized) - (dtib$greenpeace + greenpeace_criticized) + dtib$criticized),
-    oxfam_amnesty_crackdown = ((dtib$oxfam + oxfam_crackdown) - (dtib$amnesty + amnesty_crackdown) + dtib$crackdown),
-    oxfam_greenpeace_crackdown = ((dtib$oxfam + oxfam_crackdown) - (dtib$greenpeace + greenpeace_crackdown) + dtib$crackdown),
-    red_cross_amnesty_crackdown = ((dtib$red_cross + red_cross_crackdown) - (dtib$amnesty + amnesty_crackdown) + dtib$crackdown),
-    red_cross_greenpeace_crackdown = ((dtib$red_cross + red_cross_crackdown) - (dtib$greenpeace + greenpeace_crackdown) + dtib$crackdown)
+    oxfam_amnesty_criticized = (oxfam + criticized + oxfam_criticized) - (amnesty + criticized + amnesty_criticized),
+    oxfam_greenpeace_criticized = (oxfam + criticized + oxfam_criticized) - (greenpeace + criticized + greenpeace_criticized),
+    red_cross_amnesty_criticized = (red_cross + criticized + red_cross_criticized) - (amnesty + criticized + amnesty_criticized),
+    red_cross_greenpeace_criticized = (red_cross + criticized + red_cross_criticized) - (greenpeace + criticized + greenpeace_criticized),
+    oxfam_amnesty_crackdown = (oxfam + crackdown + oxfam_crackdown) - (amnesty + crackdown +  amnesty_crackdown),
+    oxfam_greenpeace_crackdown = (oxfam + crackdown + oxfam_crackdown) - (greenpeace + crackdown +  greenpeace_crackdown),
+    red_cross_amnesty_crackdown = (red_cross + crackdown + red_cross_crackdown) - (amnesty + crackdown +  amnesty_crackdown),
+    red_cross_greenpeace_crackdown = (red_cross + crackdown + red_cross_crackdown) - (greenpeace + crackdown + greenpeace_crackdown)
   )
@@
 # Overwrite draws with the appropriate interaction data
-draws <- here::here("analysis", "output", "posterior_draws", "interactions_3b.rds")
+draws <- here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds")
 
@@
 contrasts_int <- tibble(
-  criticized_environment = intib %>% filter(i == 22) %>% select(Gamma) %>% pull(),
-  criticized_humanrights = intib %>% filter(i == 23) %>% select(Gamma) %>% pull(),
-  criticized_refugee = intib %>% filter(i == 24) %>% select(Gamma) %>% pull(),
-  crackdown_environment = intib %>% filter(i == 25) %>% select(Gamma) %>% pull(),
-  crackdown_humanrights = intib %>% filter(i == 26) %>% select(Gamma) %>% pull(),
-  crackdown_refugee = intib %>% filter(i == 27) %>% select(Gamma) %>% pull(),
+  criticized_environment = draws %>% filter(i == 22) %>% select(Gamma) %>% pull(),
+  criticized_humanrights = draws %>% filter(i == 23) %>% select(Gamma) %>% pull(),
+  criticized_refugee = draws %>% filter(i == 24) %>% select(Gamma) %>% pull(),
+  crackdown_environment = draws %>% filter(i == 25) %>% select(Gamma) %>% pull(),
+  crackdown_humanrights = draws %>% filter(i == 26) %>% select(Gamma) %>% pull(),
+  crackdown_refugee = draws %>% filter(i == 27) %>% select(Gamma) %>% pull(),
 ) %>% 
@@
 # Overwrite draws with the appropriate interaction data
-draws <- here::here("analysis", "output", "posterior_draws", "interactions_4b.rds")
+draws <- here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds")
 
@@
 contrasts_int <- tibble(
-  criticized_wealthydonors = intib %>% filter(i == 28) %>% select(Gamma) %>% pull(),
-  criticized_grants = intib %>% filter(i == 29) %>% select(Gamma) %>% pull(),
-  crackdown_wealthydonors = intib %>% filter(i == 30) %>% select(Gamma) %>% pull(),
-  crackdown_grants = intib %>% filter(i == 31) %>% select(Gamma) %>% pull(),
+  criticized_wealthydonors = draws %>% filter(i == 28) %>% select(Gamma) %>% pull(),
+  criticized_grants = draws %>% filter(i == 29) %>% select(Gamma) %>% pull(),
+  crackdown_wealthydonors = draws %>% filter(i == 30) %>% select(Gamma) %>% pull(),
+  crackdown_grants = draws %>% filter(i == 31) %>% select(Gamma) %>% pull(),
 )
@@
 # Overwrite draws with the appropriate interaction data
-draws <- here::here("analysis", "output", "posterior_draws", "interactions_4c.rds")
+draws <- here::here("data", "raw_data", "posterior_draws", "interactions_4c.rds")
 
@@
 contrasts_int <- tibble(
-  emergency_crackdown_wealthydonors = intib %>% filter(i == 32) %>% select(Gamma) %>% pull(),
-  emergency_crackdown_grants = intib %>% filter(i == 33) %>% select(Gamma) %>% pull(),
-  environment_crackdown_wealthydonors = intib %>% filter(i == 34) %>% select(Gamma) %>% pull(),
-  environment_crackdown_grants = intib %>% filter(i == 35) %>% select(Gamma) %>% pull(),
-  humanrights_crackdown_wealthydonors = intib %>% filter(i == 36) %>% select(Gamma) %>% pull(),
-  humanrights_crackdown_grants = intib %>% filter(i == 37) %>% select(Gamma) %>% pull(),
-  refugee_crackdown_wealthydonors = intib %>% filter(i == 38) %>% select(Gamma) %>% pull(),
-  refugee_crackdown_grants = intib %>% filter(i == 39) %>% select(Gamma) %>% pull(),
+  emergency_crackdown_wealthydonors = draws %>% filter(i == 32) %>% select(Gamma) %>% pull(),
+  emergency_crackdown_grants = draws %>% filter(i == 33) %>% select(Gamma) %>% pull(),
+  environment_crackdown_wealthydonors = draws %>% filter(i == 34) %>% select(Gamma) %>% pull(),
+  environment_crackdown_grants = draws %>% filter(i == 35) %>% select(Gamma) %>% pull(),
+  humanrights_crackdown_wealthydonors = draws %>% filter(i == 36) %>% select(Gamma) %>% pull(),
+  humanrights_crackdown_grants = draws %>% filter(i == 37) %>% select(Gamma) %>% pull(),
+  refugee_crackdown_wealthydonors = draws %>% filter(i == 38) %>% select(Gamma) %>% pull(),
+  refugee_crackdown_grants = draws %>% filter(i == 39) %>% select(Gamma) %>% pull(),
 ) %>% 
@@
 # Overwrite draws with the appropriate interaction data
-draws <- here::here("analysis", "output", "posterior_draws", "interactions_5b.rds")
+draws <- here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds")
 
@@
 contrasts_int <- tibble(
-  financial_transparency_criticized = intib %>% filter(i == 40) %>% select(Gamma) %>% pull(),
-  financial_transparency_crackdown = intib %>% filter(i == 41) %>% select(Gamma) %>% pull(),
+  financial_transparency_criticized = draws %>% filter(i == 40) %>% select(Gamma) %>% pull(),
+  financial_transparency_crackdown = draws %>% filter(i == 41) %>% select(Gamma) %>% pull(),
   )
@@
 # Overwrite draws with the appropriate interaction data
-draws <- here::here("analysis", "output", "posterior_draws", "interactions_5c.rds")
+draws <- here::here("data", "raw_data", "posterior_draws", "interactions_5c.rds")
 
@@
 contrasts_int <- tibble(
-  fin_smalldonors_criticized = intib %>% filter(i == 42) %>% select(Gamma) %>% pull(),
-  fin_wealthydonors_criticized = intib %>% filter(i == 43) %>% select(Gamma) %>% pull(),
-  fin_grants_criticized = intib %>% filter(i == 44) %>% select(Gamma) %>% pull(),
-  fin_smalldonors_crackdown = intib %>% filter(i == 45) %>% select(Gamma) %>% pull(),
-  fin_wealthydonors_crackdown = intib %>% filter(i == 46) %>% select(Gamma) %>% pull(),
-  fin_grants_crackdown = intib %>% filter(i == 47) %>% select(Gamma) %>% pull(),
+  fin_smalldonors_criticized = draws %>% filter(i == 42) %>% select(Gamma) %>% pull(),
+  fin_wealthydonors_criticized = draws %>% filter(i == 43) %>% select(Gamma) %>% pull(),
+  fin_grants_criticized = draws %>% filter(i == 44) %>% select(Gamma) %>% pull(),
+  fin_smalldonors_crackdown = draws %>% filter(i == 45) %>% select(Gamma) %>% pull(),
+  fin_wealthydonors_crackdown = draws %>% filter(i == 46) %>% select(Gamma) %>% pull(),
+  fin_grants_crackdown = draws %>% filter(i == 47) %>% select(Gamma) %>% pull(),
   ) %>%
@@
 # Overwrite draws with the appropriate interaction data
-draws <- here::here("analysis", "output", "posterior_draws", "interactions_5d.rds")
+draws <- here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds")
 
@@
 contrasts_int <- tibble(
-  fin_emergency_criticized = intib %>% filter(i == 48) %>% select(Gamma) %>% pull(),
-  fin_emergency_crackdown = intib %>% filter(i == 49) %>% select(Gamma) %>% pull(),
-  fin_environment_criticized = intib %>% filter(i == 50) %>% select(Gamma) %>% pull(),
-  fin_environment_crackdown = intib %>% filter(i == 51) %>% select(Gamma) %>% pull(),
-  fin_humanrights_criticized = intib %>% filter(i == 52) %>% select(Gamma) %>% pull(),
-  fin_humanrights_crackdown = intib %>% filter(i == 53) %>% select(Gamma) %>% pull(),
-  fin_refugee_criticized = intib %>% filter(i == 54) %>% select(Gamma) %>% pull(),
-  fin_refugee_crackdown = intib %>% filter(i == 55) %>% select(Gamma) %>% pull()
+  fin_emergency_criticized = draws %>% filter(i == 48) %>% select(Gamma) %>% pull(),
+  fin_emergency_crackdown = draws %>% filter(i == 49) %>% select(Gamma) %>% pull(),
+  fin_environment_criticized = draws %>% filter(i == 50) %>% select(Gamma) %>% pull(),
+  fin_environment_crackdown = draws %>% filter(i == 51) %>% select(Gamma) %>% pull(),
+  fin_humanrights_criticized = draws %>% filter(i == 52) %>% select(Gamma) %>% pull(),
+  fin_humanrights_crackdown = draws %>% filter(i == 53) %>% select(Gamma) %>% pull(),
+  fin_refugee_criticized = draws %>% filter(i == 54) %>% select(Gamma) %>% pull(),
+  fin_refugee_crackdown = draws %>% filter(i == 55) %>% select(Gamma) %>% pull()
   ) %>%
@@
 # Overwrite draws with the appropriate interaction data
-draws <- here::here("analysis", "output", "posterior_draws", "interactions_5e.rds")
+draws <- here::here("data", "raw_data", "posterior_draws", "interactions_5e.rds")
 
@@
 contrasts_int <- tibble(
-  fin_sd_emergency_criticized = intib %>% filter(i == 56) %>% select(Gamma) %>% pull(),
-  fin_sd_emergency_crackdown = intib %>% filter(i == 57) %>% select(Gamma) %>% pull(),
-  fin_sd_environment_criticized = intib %>% filter(i == 58) %>% select(Gamma) %>% pull(),
-  fin_sd_environment_crackdown = intib %>% filter(i == 59) %>% select(Gamma) %>% pull(),
-  fin_sd_humanrights_criticized = intib %>% filter(i == 60) %>% select(Gamma) %>% pull(),
-  fin_sd_humanrights_crackdown = intib %>% filter(i == 61) %>% select(Gamma) %>% pull(),
-  fin_sd_refugee_criticized = intib %>% filter(i == 62) %>% select(Gamma) %>% pull(),
-  fin_sd_refugee_crackdown = intib %>% filter(i == 63) %>% select(Gamma) %>% pull()
+  fin_sd_emergency_criticized = draws %>% filter(i == 56) %>% select(Gamma) %>% pull(),
+  fin_sd_emergency_crackdown = draws %>% filter(i == 57) %>% select(Gamma) %>% pull(),
+  fin_sd_environment_criticized = draws %>% filter(i == 58) %>% select(Gamma) %>% pull(),
+  fin_sd_environment_crackdown = draws %>% filter(i == 59) %>% select(Gamma) %>% pull(),
+  fin_sd_humanrights_criticized = draws %>% filter(i == 60) %>% select(Gamma) %>% pull(),
+  fin_sd_humanrights_crackdown = draws %>% filter(i == 61) %>% select(Gamma) %>% pull(),
+  fin_sd_refugee_criticized = draws %>% filter(i == 62) %>% select(Gamma) %>% pull(),
+  fin_sd_refugee_crackdown = draws %>% filter(i == 63) %>% select(Gamma) %>% pull()
   ) %>%

### 2021-12-04 analysis/04_figs-tables.Rmd

--- 2021-12-04 analysis/04_figs-tables.Rmd
@@
 # Pull the posterior draws for the organizations and compute contrasts
+draws_intercepts <- draws
+
 contrasts <- tibble(
@@
 # Reference Level = Friendly relationship with government
+draws_intercepts <- draws
 
@@
 
-These data don't support our hypothesis; the Red Cross brand has an insignificant impact on likelihood to donate compared to both Greenpeace and Amnesty.
-While the contrasts for Oxfam are closer to being statistically significant, the effect is working in the other direction--Greenpeace and Amnesty both induce increased likelihood to donate on behalf of donors.
+Although donors show significantly more willingness to donate to Red Cross when they are criticized or under crackdown from the host government, donors are less likely to donate to Oxfam under the same conditions.
+The only contrast which isn't statistically significant is the difference between Oxfam and Amnesty when both are under crackdown.
+All other contrasts do not contain 0 within their credibility interval.
 
@@
 draws <- draws_intercepts
+
 contrasts <- tibble(
@@
   mutate(
+    criticized_emergency_environment = (criticized) - (criticized + environment + criticized_environment),
+
+  criticized_emergency_humanrights = (criticized) - (criticized + human_rights + criticized_humanrights),
+
+  crackdown_emergency_environment = (crackdown) - (crackdown + environment + crackdown_environment),
+
+  crackdown_emergency_humanrights = (crackdown) - (crackdown + human_rights + crackdown_humanrights),
+
   criticized_refugee_environment = (criticized + refugee_relief + criticized_refugee) - (criticized + environment + criticized_environment),
@@
 
-  crackdown_refugee_environment = (crackdown + refugee_relief + crackdown_refugee - crackdown + environment + crackdown_environment),
-
-  crackdown_refugee_humanrights = (crackdown + refugee_relief + crackdown_refugee - crackdown + human_rights + crackdown_humanrights)
+  crackdown_refugee_environment = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + environment + crackdown_environment),
+
+  crackdown_refugee_humanrights = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + human_rights + crackdown_humanrights)
 )
@@
 contrasts_int %>%
-  pivot_longer(criticized_refugee_environment:crackdown_refugee_humanrights, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer(criticized_emergency_environment:crackdown_refugee_humanrights, names_to = "level", values_to = "Gamma") %>% 
   ggplot(aes(x = Gamma, y = level)) +
@@
 
-The generated contrasts don't provides results which are statistically significant. 0 is found within all intervals.
+Per our hypothesis, we expected to see the contrasts of the posterior distributions to be positive.
+However, only the contrasts between emergency response and the more contentious issue areas (environment and human rights) were positive, while contrasts between refugee relief and the more contentious issue areas were negative.
+Looking at all the contrasts, crackdown_refugee_environment, criticized_refugee_environment, and crackdown_emergency_humanrights contained 0 within their credibility interval.
 
@@
 ) %>% mutate(
-  criticized_wealthydonors = (criticized + few_wealthy_private_donors + criticized_wealthydonors) - criticized,
-
-  criticized_grants = (criticized + government_grants + criticized_grants) - criticized,
-
-  crackdown_wealthydonors = (crackdown + few_wealthy_private_donors + crackdown_wealthydonors) - crackdown,
-
-  crackdown_grants = (crackdown + government_grants + crackdown_grants) - crackdown
+  criticized_wealthydonors = (criticized) - (criticized + few_wealthy_private_donors + criticized_wealthydonors),
+
+  criticized_grants = (criticized) - (criticized + government_grants + criticized_grants),
+
+  crackdown_wealthydonors = (crackdown) - (crackdown + few_wealthy_private_donors + crackdown_wealthydonors),
+
+  crackdown_grants = crackdown - (crackdown + government_grants + crackdown_grants)
 )
@@
 
-The marginal posteriors for these contrasts are strange, but still tell us that the interaction between funding sources and government relationship produce no significant effects.
+All of the contrasts are positive and none of them contain 0 within their credibility interval, which supports our hypothesis that donors are more willing to donate to organizations supported by many small private donors and are under criticism or crackdown.
 
@@
 draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4c.rds"))
+# Draws for lower order interactions
+draws_4b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds"))
+draws_3b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))
 
@@
   government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
-  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
   crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
+  crackdown_environment = draws_3b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
+  crackdown_humanrights = draws_3b %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  crackdown_refugee = draws_3b %>% filter(i == 19) %>% select(Gamma) %>% pull(),
+  crackdown_wealthydonors = draws_4b %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  crackdown_grants = draws_4b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
   emergency_crackdown_wealthydonors = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
@@
   mutate(
-  emergency_humanrights_wealthydonors = (crackdown + emergency_crackdown_wealthydonors) - (crackdown + few_wealthy_private_donors + human_rights + humanrights_crackdown_wealthydonors),
-
-  emergency_humanrights_grants = (crackdown + emergency_crackdown_grants) - (crackdown + government_grants + human_rights + humanrights_crackdown_grants),
-
-  emergency_environment_wealthydonors = (crackdown + emergency_crackdown_wealthydonors) - (crackdown + few_wealthy_private_donors + environment + environment_crackdown_wealthydonors),
-
-  emergency_environment_grants = (crackdown + emergency_crackdown_grants) - (crackdown + government_grants + environment + environment_crackdown_wealthydonors),
-
-  refugee_humanrights_wealthydonors = (crackdown + refugee_relief + refugee_crackdown_wealthydonors) - (crackdown + few_wealthy_private_donors + human_rights + humanrights_crackdown_wealthydonors),
-
-  refugee_humanrights_grants = (crackdown + refugee_relief + refugee_crackdown_grants) - (crackdown + government_grants +  human_rights + humanrights_crackdown_grants),
-
-  refugee_environment_wealthydonors = (crackdown + refugee_relief + refugee_crackdown_wealthydonors) - (crackdown + few_wealthy_private_donors + environment + environment_crackdown_wealthydonors),
-
-  refugee_environment_grants = (crackdown + refugee_relief + refugee_crackdown_grants) - (crackdown + government_grants + environment + environment_crackdown_grants),
-
+  emergency_humanrights_wealthydonors = (crackdown) - (crackdown + few_wealthy_private_donors + human_rights + crackdown_humanrights + crackdown_wealthydonors + humanrights_crackdown_wealthydonors),
+
+  emergency_humanrights_grants = (crackdown) - (crackdown + government_grants + human_rights + crackdown_humanrights + crackdown_grants + humanrights_crackdown_grants),
+
+  emergency_environment_wealthydonors = (crackdown) - (crackdown + few_wealthy_private_donors + environment + crackdown_environment + crackdown_wealthydonors + environment_crackdown_wealthydonors),
+
+  emergency_environment_grants = (crackdown) - (crackdown + government_grants + environment + crackdown_environment + crackdown_grants + environment_crackdown_grants),
+
+  refugee_humanrights_wealthydonors = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + few_wealthy_private_donors + human_rights + crackdown_humanrights + crackdown_wealthydonors + humanrights_crackdown_wealthydonors),
+
+  refugee_humanrights_grants = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + government_grants + human_rights + crackdown_humanrights + crackdown_grants + humanrights_crackdown_grants),
+
+  refugee_environment_wealthydonors = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + few_wealthy_private_donors + environment + crackdown_environment + crackdown_wealthydonors + environment_crackdown_wealthydonors),
+
+  refugee_environment_grants = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + government_grants + environment + crackdown_environment + crackdown_grants + environment_crackdown_grants),
   )
@@
 
-Once again, we see some interesting distributions, but no results significant enough to confirm our hypothesis.
+Contrast is most likely improperly coded, gammas are all over the place, so no conclusions can be made regarding the hypothesis
 
@@
 contrasts <- tibble(
-  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
+  fin_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
   accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
@@
 contrasts %>%
-  pivot_longer(financial_transparency, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer(fin_transparency, names_to = "level", values_to = "Gamma") %>% 
   ggplot(aes(x = Gamma, y = level)) +
@@
   crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
-  financial_transparency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
-  financial_transparency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  fin_transparency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  fin_transparency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
   ) %>% mutate(
-    financial_transparency_criticized = fin_transparency + criticized + financial_transparency_criticized,
-    financial_transparency_crackdown = fin_transparency + crackdown + financial_transparency_crackdown
+    fin_transparency_criticized = (fin_transparency + criticized + fin_transparency_criticized) - (criticized),
+    fin_transparency_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown) - (crackdown)
   )
@@
 
-Donors show a similar increase in willingness to donate to accountable NGOs in comparison to NGOs that are financially transparent.
-However, this is contrary to what was hypothesized--we predicted that donor's willingness to donate wouldn't be affected by accountability practices.
+The contrasts for hypothesis 5b provide evidence that donors are more willing to donate to organizations which are criticized or under crackdown and are also financially transparent.
 
@@
 draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5c.rds"))
+# Lower order interaction draws
+draws_5b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
+draws_4b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds"))
 
@@
   crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
+  criticized_wealthydonors = draws_4b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  criticized_grants = draws_4b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  crackdown_wealthydonors = draws_4b %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  crackdown_grants = draws_4b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
+  fin_transparency_criticized = draws_5b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  fin_transparency_crackdown = draws_5b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
   fin_smalldonors_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
@@
   mutate(
-  fin_smalldonors_wealthydonors_criticized = (fin_transparency + criticized + fin_smalldonors_criticized) - (fin_transparency + criticized + few_wealthy_private_donors + fin_wealthydonors_criticized),
-
-  fin_smalldonors_grants_criticized = (fin_transparency + criticized + fin_smalldonors_criticized) -  (fin_transparency + criticized + government_grants + fin_grants_criticized),
-
-  fin_smalldonors_wealthydonors_crackdown = (fin_transparency + crackdown + fin_smalldonors_crackdown) - (fin_transparency + crackdown + few_wealthy_private_donors + fin_wealthydonors_crackdown),
-
-  fin_smalldonors_grants_crackdown = (fin_transparency + crackdown + fin_smalldonors_crackdown) - (fin_transparency + crackdown + government_grants + fin_grants_crackdown)
+  fin_smalldonors_wealthydonors_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized) - (fin_transparency + criticized + few_wealthy_private_donors + criticized_wealthydonors + fin_transparency_criticized + fin_wealthydonors_criticized),
+
+  fin_smalldonors_grants_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized) -  (fin_transparency + criticized + government_grants + criticized_grants + fin_transparency_criticized + fin_grants_criticized),
+
+  fin_smalldonors_wealthydonors_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown) - (fin_transparency + crackdown + few_wealthy_private_donors + crackdown_wealthydonors + fin_transparency_crackdown + fin_wealthydonors_crackdown),
+
+  fin_smalldonors_grants_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown) - (fin_transparency + crackdown + government_grants + crackdown_grants + fin_transparency_crackdown + fin_grants_crackdown),
+
+# additional contrasts to compare financial transparency to no transparency    
+  not_fin_smalldonors_wealthydonors_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized) - (criticized + few_wealthy_private_donors + criticized_wealthydonors),
+
+  not_fin_smalldonors_grants_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized) -  (criticized + government_grants + criticized_grants),
+
+  not_fin_smalldonors_wealthydonors_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown) - (crackdown + few_wealthy_private_donors + crackdown_wealthydonors),
+
+  not_fin_smalldonors_grants_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown) - (crackdown + government_grants + fin_transparency_crackdown + fin_grants_crackdown)
   )
@@
 contrasts_int %>%
-  pivot_longer(fin_smalldonors_wealthydonors_criticized:fin_smalldonors_grants_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer(fin_smalldonors_wealthydonors_criticized:not_fin_smalldonors_grants_crackdown, names_to = "level", values_to = "Gamma") %>% 
   ggplot(aes(x = Gamma, y = level)) +
@@
 
-These intervals are massive; 0 is well within them, leaving us with insufficient evidence to confirm the hypothesis.
+Only fin_smalldonors_grants_crackdown contains 0 within its credibility interval.
+Since all other contrasts are positive and do not contain 0 within their credibility intervals, there is evidence supporting that donors are more willing to donate to NGOs that are criticized by the government/under government crackdown, are financially transparent, and are funded primarily by numerous small private donors.
 
@@
 draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds"))
+# Lower-order interactions
+draws_5b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
+draws_3b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))
 
@@
   refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
+  criticized_environment = draws_3b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  criticized_humanrights = draws_3b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  criticized_refugee = draws_3b %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  crackdown_environment = draws_3b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
+  crackdown_humanrights = draws_3b %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  crackdown_refugee = draws_3b %>% filter(i == 19) %>% select(Gamma) %>% pull(),
+  fin_transparency_criticized = draws_5b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  fin_transparency_crackdown = draws_5b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
   fin_emergency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
@@
   mutate(
-  fin_emergency_environment_criticized = (fin_transparency + criticized + fin_emergency_criticized) - (fin_transparency + criticized + environment + fin_environment_criticized),
-
-  fin_emergency_humanrights_criticized = (fin_transparency + criticized + fin_emergency_criticized) - fin_transparency + criticized + human_rights + fin_humanrights_criticized,
-
-  fin_emergency_environment_crackdown = (fin_transparency + crackdown + fin_emergency_crackdown) - (fin_transparency + crackdown + environment + fin_environment_crackdown),
-
-  fin_emergency_humanright_crackdown = (fin_transparency + crackdown + fin_emergency_crackdown) - (fin_transparency + crackdown + human_rights + fin_humanrights_crackdown),
-
-  fin_refugee_environment_criticized = (fin_transparency + criticized + fin_refugee_criticized) - (fin_transparency + criticized + environment + fin_environment_criticized),
-
-  fin_refugee_humanright_criticized = (fin_transparency + criticized + fin_refugee_criticized) - (fin_transparency + criticized + human_rights + fin_humanrights_criticized),
-
-  fin_refugee_environment_crackdown = (fin_transparency + crackdown + fin_refugee_crackdown) - (fin_transparency + crackdown + environment + fin_environment_crackdown),
-
-  fin_refugee_humanright_crackdown = (fin_transparency + crackdown + fin_refugee_crackdown) - (fin_transparency + crackdown + human_rights + fin_humanrights_crackdown)
+  fin_emergency_environment_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_emergency_criticized) - (fin_transparency + criticized + environment + fin_transparency_criticized + criticized_environment + fin_environment_criticized),
+
+  fin_emergency_humanrights_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_emergency_criticized) - (fin_transparency + criticized + human_rights + fin_transparency_criticized + criticized_humanrights + fin_humanrights_criticized),
+
+  fin_emergency_environment_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_emergency_crackdown) - (fin_transparency + crackdown + environment + fin_transparency_crackdown + crackdown_environment + fin_environment_crackdown),
+
+  fin_emergency_humanright_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_emergency_crackdown) - (fin_transparency + crackdown + human_rights + fin_transparency_crackdown + crackdown_humanrights + fin_humanrights_crackdown),
+
+  fin_refugee_environment_criticized = (fin_transparency + criticized + fin_transparency_criticized + criticized_refugee + fin_refugee_criticized) - (fin_transparency + criticized + environment + fin_transparency_criticized + criticized_environment + fin_environment_criticized),
+
+  fin_refugee_humanright_criticized = (fin_transparency + criticized + fin_transparency_criticized + criticized_refugee + fin_refugee_criticized) - (fin_transparency + criticized + human_rights + fin_transparency_criticized + criticized_humanrights + fin_humanrights_criticized),
+
+  fin_refugee_environment_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + crackdown_refugee + fin_refugee_crackdown) - (fin_transparency + crackdown + environment + crackdown_environment + fin_transparency_crackdown + fin_environment_crackdown),
+
+  fin_refugee_humanright_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + crackdown_refugee + fin_refugee_crackdown) - (fin_transparency + crackdown + human_rights + fin_transparency_crackdown + crackdown_humanrights + fin_humanrights_crackdown)
 )
@@
 
-The contrasts don't support the hypothesis, however, there is an interesting difference between emergency_environment_crackdown and emergency_environment_criticized.
+The contrasts don't seem to be properly calculated, so no conclusion at this time.
 
@@
 draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5e.rds"))
-
+# Lower-order interactions
+draws_5b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
+draws_3b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))
+draws_5c <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5c.rds"))
+draws_5d <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds"))
 # Pull the posterior draws for organizational practices*funding*issue area*government crackdown interaction
@@
   crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
+  criticized_environment = draws_3b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  criticized_humanrights = draws_3b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  criticized_refugee = draws_3b %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  crackdown_environment = draws_3b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
+  crackdown_humanrights = draws_3b %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  crackdown_refugee = draws_3b %>% filter(i == 19) %>% select(Gamma) %>% pull(),
+  fin_transparency_criticized = draws_5b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  fin_transparency_crackdown = draws_5b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  fin_emergency_criticized = draws_5d %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  fin_emergency_crackdown = draws_5d %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  fin_environment_criticized = draws_5d %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  fin_environment_crackdown = draws_5d %>% filter(i == 17) %>% select(Gamma) %>% pull(),
+  fin_humanrights_criticized = draws_5d %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  fin_humanrights_crackdown = draws_5d %>% filter(i == 19) %>% select(Gamma) %>% pull(),
+  fin_refugee_criticized = draws_5d %>% filter(i == 20) %>% select(Gamma) %>% pull(),
+  fin_refugee_crackdown = draws_5d %>% filter(i == 21) %>% select(Gamma) %>% pull(),
+  fin_smalldonors_criticized = draws_5c %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  fin_wealthydonors_criticized = draws_5c %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  fin_grants_criticized = draws_5c %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  fin_smalldonors_crackdown = draws_5c %>% filter(i == 17) %>% select(Gamma) %>% pull(),
+  fin_wealthydonors_crackdown = draws_5c %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  fin_grants_crackdown = draws_5c %>% filter(i == 19) %>% select(Gamma) %>% pull(),
   fin_sd_emergency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
@@
   ) %>% mutate(
-  fin_sd_emergency_environment_criticized = (fin_transparency + criticized + fin_sd_emergency_criticized) - (fin_transparency + criticized + environment +  fin_sd_environment_criticized),
-
-  fin_sd_emergency_humanrights_criticized = (fin_transparency + criticized + fin_sd_emergency_criticized) - (fin_transparency + criticized + human_rights +  fin_sd_humanrights_criticized),
-
-  fin_sd_emergency_environment_crackdown = (fin_transparency + crackdown + fin_sd_emergency_crackdown) - (fin_transparency + crackdown + environment +  fin_sd_environment_crackdown),
-
-  fin_sd_emergency_humanright_crackdown = (fin_transparency + crackdown + fin_sd_emergency_crackdown) - (fin_transparency + crackdown + human_rights + fin_sd_humanrights_crackdown),
-
-  fin_sd_refugee_environment_criticized = (fin_transparency + criticized + refugee_relief +  fin_sd_refugee_criticized) - (fin_transparency + criticized + environment +  fin_sd_environment_criticized),
-
-  fin_sd_refugee_humanright_criticized = (fin_transparency + criticized + refugee_relief +  fin_sd_refugee_criticized) - (fin_transparency + criticized + human_rights +  fin_sd_humanrights_criticized),
-
-  fin_sd_refugee_environment_crackdown = (fin_transparency + crackdown + refugee_relief + fin_sd_refugee_crackdown) - (fin_transparency + crackdown + environment + fin_sd_environment_crackdown),
-
-  fin_sd_refugee_humanright_crackdown = (fin_transparency + crackdown + refugee_relief + fin_sd_refugee_crackdown) - (fin_transparency + crackdown + human_rights + fin_sd_humanrights_crackdown
-))
+  fin_sd_emergency_environment_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized + fin_emergency_criticized + fin_sd_emergency_criticized) - (fin_transparency + criticized + environment + criticized_environment + fin_transparency_criticized + fin_smalldonors_criticized + fin_environment_criticized + fin_sd_environment_criticized),
+
+  fin_sd_emergency_humanrights_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized + fin_emergency_criticized + fin_sd_emergency_criticized) - (fin_transparency + criticized + human_rights + criticized_humanrights + fin_transparency_criticized + fin_smalldonors_criticized + fin_humanrights_criticized + fin_sd_humanrights_criticized) ,
+
+  fin_sd_emergency_environment_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown + fin_emergency_crackdown + fin_sd_emergency_crackdown) - (fin_transparency + crackdown + environment + crackdown_environment + fin_transparency_crackdown + fin_smalldonors_crackdown + fin_environment_crackdown + fin_sd_environment_crackdown),
+
+  fin_sd_emergency_humanrights_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown + fin_emergency_crackdown + fin_sd_emergency_crackdown) - (fin_transparency + crackdown + human_rights + crackdown_humanrights + fin_transparency_crackdown + fin_smalldonors_crackdown + fin_humanrights_crackdown + fin_sd_humanrights_crackdown) ,
+
+  fin_sd_refugee_environment_criticized = (fin_transparency + criticized + refugee_relief + fin_transparency_criticized + criticized_refugee + fin_smalldonors_criticized + fin_refugee_criticized + fin_sd_refugee_criticized) - (fin_transparency + criticized + environment + criticized_environment + fin_transparency_criticized + fin_smalldonors_criticized + fin_environment_criticized + fin_sd_environment_criticized) ,
+
+  fin_sd_refugee_humanrights_criticized = (fin_transparency + criticized + refugee_relief + fin_transparency_criticized + criticized_refugee + fin_smalldonors_criticized + fin_refugee_criticized + fin_sd_refugee_criticized) - (fin_transparency + criticized + human_rights + criticized_humanrights + fin_transparency_criticized + fin_smalldonors_criticized + fin_humanrights_criticized + fin_sd_humanrights_criticized) ,
+
+  fin_sd_refugee_environment_crackdown = (fin_transparency + crackdown + refugee_relief + fin_transparency_crackdown + crackdown_refugee + fin_smalldonors_crackdown + fin_refugee_crackdown + fin_sd_refugee_crackdown) - (fin_transparency + crackdown + environment + crackdown_environment + fin_transparency_crackdown + fin_smalldonors_crackdown + fin_environment_crackdown + fin_sd_environment_crackdown) ,
+
+  fin_sd_refugee_humanrights_crackdown = (fin_transparency + crackdown + refugee_relief + fin_transparency_crackdown + crackdown_refugee + fin_smalldonors_crackdown + fin_refugee_crackdown + fin_sd_refugee_crackdown) - (fin_transparency + crackdown + human_rights + crackdown_humanrights + fin_transparency_crackdown + fin_smalldonors_crackdown + fin_humanrights_crackdown + fin_sd_humanrights_crackdown),
+  )
 
@@
 contrasts_int %>%
-  pivot_longer(fin_sd_emergency_environment_criticized:fin_sd_refugee_humanright_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer(fin_sd_emergency_environment_criticized:fin_sd_refugee_humanrights_crackdown, names_to = "level", values_to = "Gamma") %>% 
   ggplot(aes(x = Gamma, y = level)) +
@@
 
-These marginal posteriors don't support our hypothesis, but again show an interesting difference between emergency_environment_criticized and emergency_environment_crackdown.
+These contrasts don't provide conclusive results, need fixing.
 

### 2021-12-08 analysis/03_analysis.Rmd
Cleaned up import/export to match new location for model runs and posterior draws

@@
 run <- list(data = data, fit = fit)
-if (intercept == 1 & interactions == 0) write_rds(run, here::here("analysis", "output", "model_runs", "intercept.rds"))
-if (intercept == 1 & interactions == 1) write_rds(run, here::here("analysis", "output", "model_runs", "interactions_5e.rds"))
-if (public_affairs == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_affairs.rds"))
-if (political_ideology == 1) write_rds(run, here::here("analysis", "output", "model_runs", "political_ideology.rds"))
-if (social_views == 1) write_rds(run, here::here("analysis", "output", "model_runs", "social_views.rds"))
-if (charity_voluntarism == 1) write_rds(run, here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
-if (demographics == 1) write_rds(run, here::here("analysis", "output", "model_runs", "demographics.rds"))
-if (public_political == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political.rds"))
-if (public_political_social == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social.rds"))
-if (public_political_social_charity == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
-if (public_political_social_charity_demo == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
+if (intercept == 1 & interactions == 0) write_rds(run, here::here("data", "raw_data", "model_runs", "intercept.rds"))
+if (intercept == 1 & interactions == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "interactions_5e.rds"))
+if (public_affairs == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "public_affairs.rds"))
+if (political_ideology == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "political_ideology.rds"))
+if (social_views == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "social_views.rds"))
+if (charity_voluntarism == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "charity_voluntarism.rds"))
+if (demographics == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "demographics.rds"))
+if (public_political == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "public_political.rds"))
+if (public_political_social == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "public_political_social.rds"))
+if (public_political_social_charity == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "public_political_social_charity.rds"))
+if (public_political_social_charity_demo == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "public_political_social_charity_demo.rds"))
 ```
@@
 # Load all model output
-intercept_run <- read_rds(here::here("analysis", "output", "model_runs", "intercept.rds"))
-public_affairs_run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
-political_ideology_run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
-social_views_run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
-charity_voluntarism_run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
-demographics_run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
-public_political_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
-public_political_social_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
-public_political_social_charity_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
-public_political_social_charity_demo_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
+intercept_run <- read_rds(here::here("data", "raw_data", "model_runs", "intercept.rds"))
+public_affairs_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_affairs.rds"))
+political_ideology_run <- read_rds(here::here("data", "raw_data", "model_runs", "political_ideology.rds"))
+social_views_run <- read_rds(here::here("data", "raw_data", "model_runs", "social_views.rds"))
+charity_voluntarism_run <- read_rds(here::here("data", "raw_data", "model_runs", "charity_voluntarism.rds"))
+demographics_run <- read_rds(here::here("data", "raw_data", "model_runs", "demographics.rds"))
+public_political_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political.rds"))
+public_political_social_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social.rds"))
+public_political_social_charity_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity.rds"))
+public_political_social_charity_demo_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity_demo.rds"))
 ```
@@
 # Load and extract data and model output
-if (intercept == 1 & interactions == 0) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept.rds"))
-if (intercept == 1 & interactions == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "interactions_5d.rds"))
-if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
-if (political_ideology == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
-if (social_views == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
-if (charity_voluntarism == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
-if (demographics == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
-if (public_political == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
-if (public_political_social == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
-if (public_political_social_charity == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
-if (public_political_social_charity_demo == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
+if (intercept == 1 & interactions == 0) run <- read_rds(here::here("data", "raw_data", "model_runs", "intercept.rds"))
+if (intercept == 1 & interactions == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "interactions_5d.rds"))
+if (public_affairs == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "public_affairs.rds"))
+if (political_ideology == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "political_ideology.rds"))
+if (social_views == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "social_views.rds"))
+if (charity_voluntarism == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "charity_voluntarism.rds"))
+if (demographics == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "demographics.rds"))
+if (public_political == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political.rds"))
+if (public_political_social == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social.rds"))
+if (public_political_social_charity == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity.rds"))
+if (public_political_social_charity_demo == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity_demo.rds"))
 data <- run$data
@@
 # Save draws
-if (intercept == 1 & interactions == 0) write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept.rds"))
-if (intercept == 1 & interactions == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "interactions_5d.rds"))
-if (public_affairs == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))
-if (political_ideology == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "political_ideology.rds"))
-if (social_views == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "social_views.rds"))
-if (charity_voluntarism == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds"))
-if (demographics == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "demographics.rds"))
-if (public_political == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political.rds"))
-if (public_political_social == 1)  write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social.rds"))
-if (public_political_social_charity == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds"))
-if (public_political_social_charity_demo == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity_demo.rds"))
+if (intercept == 1 & interactions == 0) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "intercept.rds"))
+if (intercept == 1 & interactions == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds"))
+if (public_affairs == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_affairs.rds"))
+if (political_ideology == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "political_ideology.rds"))
+if (social_views == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "social_views.rds"))
+if (charity_voluntarism == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "charity_voluntarism.rds"))
+if (demographics == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "demographics.rds"))
+if (public_political == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_political.rds"))
+if (public_political_social == 1)  write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_political_social.rds"))
+if (public_political_social_charity == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_political_social_charity.rds"))
+if (public_political_social_charity_demo == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_political_social_charity_demo.rds"))
 ```

### 2021-12-08 analysis/04_figs-tables.Rmd
Cleaned up import/export to match new location for model runs and posterior draws

@@
   draws <- read_rds(
-    here::here("analysis", "output", "posterior_draws", "intercept.rds")
+    here::here("data", "raw_data", "posterior_draws", "intercept.rds")
   ) %>% 
@@
   draws <- read_rds(
-    here::here("analysis", "output", "posterior_draws", "interactions.rds")
+    here::here("data", "raw_data", "posterior_draws", "interactions.rds")
   ) %>% 
@@
   draws <- read_rds(
-    here::here("analysis", "output", "posterior_draws", "public_affairs.rds")
+    here::here("data", "raw_data", "posterior_draws", "public_affairs.rds")
   ) %>% 
@@
   draws <- read_rds(
-    here::here("analysis", "output", "posterior_draws", "political_ideology.rds")
+    here::here("data", "raw_data", "posterior_draws", "political_ideology.rds")
   ) %>% 
@@
   draws <- read_rds(
-    here::here("analysis", "output", "posterior_draws", "social_views.rds")
+    here::here("data", "raw_data", "posterior_draws", "social_views.rds")
   ) %>% 
@@
   draws <- read_rds(
-    here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds")
+    here::here("data", "raw_data", "posterior_draws", "charity_voluntarism.rds")
   ) %>% 
@@
   draws <- read_rds(
-    here::here("analysis", "output", "posterior_draws", "demographics.rds")
+    here::here("data", "raw_data", "posterior_draws", "demographics.rds")
   ) %>% 
@@
   draws <- read_rds(
-    here::here("analysis", "output", "posterior_draws", "public_political.rds")
+    here::here("data", "raw_data", "posterior_draws", "public_political.rds")
   ) %>% 
@@
   draws <- read_rds(
-    here::here("analysis", "output", "posterior_draws", "public_political_social.rds")
+    here::here("data", "raw_data", "posterior_draws", "public_political_social.rds")
   ) %>% 
@@
   draws <- read_rds(
-    here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds")
+    here::here("data", "raw_data", "posterior_draws", "public_political_social_charity.rds")
   ) %>% 

### 2021-12-08 analysis/03_analysis.Rmd
Cleaned up analysis markdown

@@
 intercept <- 0                            # Intercept-only
-interactions <- 0                         # Include interactions with the intercept-only model?
+interactions <- 0                         # Include interactions with the intercept-only model
 public_affairs <- 1                       # Public affairs
@@
 if (interactions == 1) X <- read_rds(here::here("data", "derived_data", "final_interactions.rds"))
-
-# # ##############################
-# X_new <- array(NA, dim = c(dim(X)[1:3], 21)) # 13 + interactions
-# for (r in 1:dim(X)[1]) {
-#   for (s in 1:dim(X)[2]) {
-#     X_new[r,s,,] <- X[r,s,,c(1:13, 56:63)] # 13 + interactions
-#   }
-# }
-# X <- X_new
-# # ##############################
 
@@
 
-# ####################################################################################
-# # if (intercept == 0) {
-#   # OLD...
-#   # Replace factor labels with levels
-#   Z_old <- Z %>%
-#   # Z <- Z %>%
-#     mutate_if(is.factor, as.integer) %>%
-#     mutate_if(is.integer, as.factor)
-#   
-#   # Pad the variables names with _
-#   # colnames(Z) <- str_c(colnames(Z), "_")
-#   colnames(Z_old) <- str_c(colnames(Z_old), "_")
-#   
-#   # Use the output of lm to get a dummy-coded version of the covariate matrix Z
-#   # Z$y <- matrix(rnorm(nrow(Z)), ncol = 1)
-#   # out <- lm(y ~ ., Z, x = TRUE)
-#   Z_old$y <- matrix(rnorm(nrow(Z_old)), ncol = 1)
-#   out <- lm(y ~ ., Z_old, x = TRUE)
-#   
-#   # Save out Z as a matrix, including an intercept
-#   Z_old <- tibble(intercept = rep(1, dim(X)[1])) %>%
-#   # Z <- tibble(intercept = rep(1, dim(X)[1])) %>%
-#     bind_cols(as_tibble(out$x[,-1])) %>%
-#     as.matrix()
-#   
-#   # NEW...
-#   # Replace factor labels with levels and NAs with 0s
-#   Z_new <- Z %>%
-#     mutate_if(is.factor, as.integer) %>%
-#     mutate_if(is.integer, as.factor) %>% 
-#     replace(is.na(.), 0) %>% 
-#     # Use dummy_cols() to get a dummy-coded version of factors
-#     dummy_cols(
-#       remove_first_dummy = TRUE,
-#       remove_selected_columns = TRUE
-#     ) %>% 
-#     # Include an intercept, sort columns numerically, save as matrix
-#     bind_cols(tibble(intercept = rep(1, dim(X)[1]))) %>% 
-#     relocate(intercept, sort(colnames(.))) %>% 
-#     as.matrix()
-# # }
-# 
-# 
-# 
-# 
-# ####################################################################################
+if (intercept == 0) {
+  # Replace factor labels with levels
+  Z <- Z %>%
+    mutate_if(is.factor, as.integer) %>%
+    mutate_if(is.integer, as.factor)
+
+  # Pad the variables names with _
+  colnames(Z) <- str_c(colnames(Z), "_")
+
+  # Use the output of lm to get a dummy-coded version of the covariate matrix Z
+  Z$y <- matrix(rnorm(nrow(Z)), ncol = 1)
+  out <- lm(y ~ ., Z, x = TRUE)
+
+  # Save out Z as a matrix, including an intercept
+  Z <- tibble(intercept = rep(1, dim(X)[1])) %>%
+    bind_cols(as_tibble(out$x[,-1])) %>%
+    as.matrix()
+}
 
@@
 intercept <- 1                            # Intercept-only
-interactions <- 1                         # Include interactions with the intercept-only model?
+interactions <- 1                         # Include interactions with the intercept-only model
 public_affairs <- 0                       # Public affairs

### 2021-12-09 analysis/04_figs-tables.Rmd
Completing contrasts

@@
 library(broom)
-# library(ggridges)
+library(ggridges)
 library(ggraph)
@@
 intercept <- 1                            # Intercept-only
-interactions <- 1                         # Include interactions with the intercept-only model?
+interactions <- 0                         # Include interactions with the intercept-only model
 public_affairs <- 0                       # Public affairs
@@
 
-Another approach to address the hypotheses is to plot contrasts.
-
-```{r}
-#storing intercept draws for easier reference
-draws_intercepts <- draws
+To formally answer the hypotheses, we compute contrasts of the marginal posteriors. First, we need the intercept-only draws and associated levels.
+
+```{r intercept-draws}
+# Import draws
+draws_intercept <- read_rds(here::here("data", "raw_data", "posterior_draws", "intercept.rds")) %>% 
+  mutate(model = "Intercept only")
+
+# Name levels labels
+level_labels <- c(
+  str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
+  str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
+  str_c("Organizational practices: ", c("Financial transparency", "Accountability")),
+  str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants")),
+  str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))
+)
+
+level_lookup <- tibble(levels = level_labels) %>% 
+  separate(levels, c("attribute", "level"), sep = ": ") %>% 
+  mutate(levels_long = paste0(attribute, ": ", level),
+         i = 1:n()) %>% 
+  mutate_at(vars(attribute, level, levels_long), list(fct_inorder))
+
+# Join level and covariate labels to draws
+draws_intercept <- draws_intercept %>% 
+  left_join(level_lookup, by = "i")
 ```
@@
 
-```{r branding-contrasts}
-# Pull the posterior draws for the organizations and compute contrasts
-draws_intercepts <- draws
-
+```{r contrasts-hypothesis01}
+# Compute the contrasts
 contrasts <- tibble(
-  amnesty = draws %>% filter(level == "Amnesty International") %>% select(Gamma) %>% pull(),
-  greenpeace = draws %>% filter(level == "Greenpeace") %>% select(Gamma) %>% pull(),
-  oxfam = draws %>% filter(level == "Oxfam") %>% select(Gamma) %>% pull(),
-  red_cross = draws %>% filter(level == "Red Cross") %>% select(Gamma) %>% pull()
+  amnesty = draws_intercept %>% filter(level == "Amnesty International") %>% select(Gamma) %>% pull(),
+  greenpeace = draws_intercept %>% filter(level == "Greenpeace") %>% select(Gamma) %>% pull(),
+  oxfam = draws_intercept %>% filter(level == "Oxfam") %>% select(Gamma) %>% pull(),
+  red_cross = draws_intercept %>% filter(level == "Red Cross") %>% select(Gamma) %>% pull()
 ) %>% 
   mutate(
-    oxfam_amnesty = oxfam - amnesty,
-    oxfam_greenpeace = oxfam - greenpeace,
-    red_cross_amnesty = red_cross - amnesty,
-    red_cross_greenpeace = red_cross - greenpeace,
+    "oxfam - amnesty" = oxfam - amnesty,
+    "oxfam - greenpeace" = oxfam - greenpeace,
+    "red cross - amnesty" = red_cross - amnesty,
+    "red cross - greenpeace" = red_cross - greenpeace,
   )
@@
 contrasts %>%
-  pivot_longer(oxfam_amnesty:red_cross_greenpeace, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer("oxfam - amnesty":"red cross - greenpeace", names_to = "level", values_to = "Gamma") %>% 
   ggplot(aes(x = Gamma, y = level)) +
@@
   geom_vline(xintercept = 0, color = "grey") +
-  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")
+  labs(y = "Contrasts", x = "Difference in Gammas")
 
@@
 In fact, there is a negligible difference between donors likelihood to donate to Oxfam and Amnesty International.
+This might be because the population we sampled from was specifically in the United States, where Oxfam and Amnesty may be less well known.
 
@@
 
-```{r crackdown-contrasts-a}
-# Pull the posterior draws for government crackdown
+```{r contrasts-hypothesis02a}
 # Reference Level = Friendly relationship with government
-draws_intercepts <- draws
-
+# Compute the contrasts
 contrasts <- tibble(
-  under_crackdown = draws %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
-  criticized = draws %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
+  "crackdown - friendly" = draws_intercept %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
+  "criticized - friendly" = draws_intercept %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
 )
@@
 contrasts %>%
-  pivot_longer(under_crackdown:criticized, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer("crackdown - friendly":"criticized - friendly", names_to = "level", values_to = "Gamma") %>% 
   ggplot(aes(x = Gamma, y = level)) +
@@
 
-Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism.
-This decreased likelihood to donate is also greater for NGOs under crackdown compared to those under criticism.
+Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism relative to NGOs that have a friendly relationship with the government, with this decreased likelihood to donate greater for NGOs under crackdown compared to those being criticized.
 
@@
 
-```{r crackdown-contrasts-b}
-# Overwrite draws with the appropriate interaction data
-
+```{r contrasts-hypothesis02b}
+# Import the appropriate interaction draws
 draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_2b.rds"))
 
-# Pull the posterior draws for organization*government crackdown interaction
 # Reference Level = Friendly relationship with government
-
+# Compute the contrasts
 contrasts_int <- tibble(
@@
   red_cross = draws %>% filter(i == 4)%>% select(Gamma) %>% pull(),
-  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
-  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
-  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
-  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
-  accountability = draws %>% filter(i == 9) %>% select(Gamma) %>% pull(),
-  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
-  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
   criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
@@
   mutate(
-    oxfam_amnesty_criticized = (oxfam + criticized + oxfam_criticized) - (amnesty + criticized + amnesty_criticized),
-
-    oxfam_greenpeace_criticized = (oxfam + criticized + oxfam_criticized) - (greenpeace + criticized + greenpeace_criticized),
-
-    red_cross_amnesty_criticized = (red_cross + criticized + red_cross_criticized) - (amnesty + criticized + amnesty_criticized),
-
-    red_cross_greenpeace_criticized = (red_cross + criticized + red_cross_criticized) - (greenpeace + criticized + greenpeace_criticized),
-
-    oxfam_amnesty_crackdown = (oxfam + crackdown + oxfam_crackdown) - (amnesty + crackdown +  amnesty_crackdown),
-
-    oxfam_greenpeace_crackdown = (oxfam + crackdown + oxfam_crackdown) - (greenpeace + crackdown +  greenpeace_crackdown),
-
-    red_cross_amnesty_crackdown = (red_cross + crackdown + red_cross_crackdown) - (amnesty + crackdown +  amnesty_crackdown),
-
-    red_cross_greenpeace_crackdown = (red_cross + crackdown + red_cross_crackdown) - (greenpeace + crackdown + greenpeace_crackdown)
+    "criticized oxfam - criticized amnesty" = 
+      (oxfam + criticized + oxfam_criticized) - (amnesty + criticized + amnesty_criticized),
+    "criticized oxfam - criticized greenpeace" = 
+      (oxfam + criticized + oxfam_criticized) - (greenpeace + criticized + greenpeace_criticized),
+    "criticized red cross - criticized amnesty" = 
+      (red_cross + criticized + red_cross_criticized) - (amnesty + criticized + amnesty_criticized),
+    "criticized red cross - criticized green peace" = 
+      (red_cross + criticized + red_cross_criticized) - (greenpeace + criticized + greenpeace_criticized),
+    "crackdown oxfam - crackdown amnesty" = 
+      (oxfam + crackdown + oxfam_crackdown) - (amnesty + crackdown +  amnesty_crackdown),
+    "crackdown oxfam - crackdown greenpeace" = 
+      (oxfam + crackdown + oxfam_crackdown) - (greenpeace + crackdown +  greenpeace_crackdown),
+    "crackdown red cross - crackdown amnesty" = 
+      (red_cross + crackdown + red_cross_crackdown) - (amnesty + crackdown +  amnesty_crackdown),
+    "crackdown red cross - crackdown greenpeace" = 
+      (red_cross + crackdown + red_cross_crackdown) - (greenpeace + crackdown + greenpeace_crackdown)
   )
@@
 contrasts_int %>%
-  pivot_longer(oxfam_amnesty_criticized:red_cross_greenpeace_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer(
+    "criticized oxfam - criticized amnesty":"crackdown red cross - crackdown greenpeace", 
+    names_to = "level", values_to = "Gamma"
+  ) %>% 
   ggplot(aes(x = Gamma, y = level)) +
@@
 The only contrast which isn't statistically significant is the difference between Oxfam and Amnesty when both are under crackdown.
-All other contrasts do not contain 0 within their credibility interval.
 
@@
 
-```{r issue-contrasts-a}
-# Pull the posterior draws for issue area
+```{r contrasts-hypothesis03a}
 # Reference Level = Emergency Response
-draws <- draws_intercepts
-
+# Compute the contrasts
 contrasts <- tibble(
-  environment = draws %>% filter(level == "Environment") %>% select(Gamma) %>% pull(),
-  human_rights = draws %>% filter(level == "Human rights") %>% select(Gamma) %>% pull(),
-  refugee_relief = draws %>% filter(level == "Refugee relief") %>% select(Gamma) %>% pull()
+  "environment - emergency" = draws_intercept %>% filter(level == "Environment") %>% select(Gamma) %>% pull(),
+  "human rights - emergency" = draws_intercept %>% filter(level == "Human rights") %>% select(Gamma) %>% pull(),
+  "refugee relief - emergency" = draws_intercept %>% filter(level == "Refugee relief") %>% select(Gamma) %>% pull()
 )
@@
 contrasts %>%
-  pivot_longer(environment:refugee_relief, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer(
+    "environment - emergency":"refugee relief - emergency", 
+    names_to = "level", values_to = "Gamma"
+  ) %>% 
   ggplot(aes(x = Gamma, y = level)) +
@@
 Emergency response was the most favored issue area by donors, and experienced the highest likelihood of receiving donations.
-While this partially matches the claim of the hypothesis, donors showed the least likelihood to donate to refugee relief NGOs, which was contrary to our expectations.
-It is worth noting that there is some overlap between the intervals of the issue areas, which would suggest that their effect isn't as significant as other factors.
+While this partially matches the claim of the hypothesis, donors showed the least likelihood to donate to refugee relief NGOs, although this is not significantly different from their likelihood of donating for environmental causes.
+In other words, refugee relief appears to be as contentious as environment.
 
@@
 
-```{r issue-contrasts-b}
-# Overwrite draws with the appropriate interaction data
+```{r contrasts-hypothesis03b}
+# Import the appropriate interaction draws
 draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))
 
-# Pull the posterior draws for government crackdown*issue area interaction
-# Reference Level = Friendly relationship with government
 # Reference Level = Emergency Response
-
+# Compute the contrasts
 contrasts_int <- tibble(
@@
   criticized_environment = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
-  criticized_humanrights = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  criticized_human_rights = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
   criticized_refugee = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
   crackdown_environment = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
-  crackdown_humanrights = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  crackdown_human_rights = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
   crackdown_refugee = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
@@
   mutate(
-    criticized_emergency_environment = (criticized) - (criticized + environment + criticized_environment),
-
-  criticized_emergency_humanrights = (criticized) - (criticized + human_rights + criticized_humanrights),
-
-  crackdown_emergency_environment = (crackdown) - (crackdown + environment + crackdown_environment),
-
-  crackdown_emergency_humanrights = (crackdown) - (crackdown + human_rights + crackdown_humanrights),
-
-  criticized_refugee_environment = (criticized + refugee_relief + criticized_refugee) - (criticized + environment + criticized_environment),
-
-  criticized_refugee_humanrights = (criticized + refugee_relief + criticized_refugee) - (criticized + human_rights + criticized_humanrights),
-
-  crackdown_refugee_environment = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + environment + crackdown_environment),
-
-  crackdown_refugee_humanrights = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + human_rights + crackdown_humanrights)
+    "criticized emergency - criticized environment" = 
+      (criticized) - (criticized + environment + criticized_environment),
+    "criticized emergency - criticized human rights" = 
+      (criticized) - (criticized + human_rights + criticized_human_rights),
+    "crackdown emergency - crackdown environment" = 
+      (crackdown) - (crackdown + environment + crackdown_environment),
+    "crackdown emergency - crackdown human rights" = 
+      (crackdown) - (crackdown + human_rights + crackdown_human_rights),
+    "criticized refugee relief - criticized environment" = 
+      (criticized + refugee_relief + criticized_refugee) - (criticized + environment + criticized_environment),
+    "criticized refugee relief - criticized human rights" = 
+      (criticized + refugee_relief + criticized_refugee) - (criticized + human_rights + criticized_human_rights),
+    "crackdown refugee relief - crackdown environment" = 
+      (crackdown + refugee_relief + crackdown_refugee) - (crackdown + environment + crackdown_environment),
+    "crackdown refugee relief - crackdown human rights" = 
+      (crackdown + refugee_relief + crackdown_refugee) - (crackdown + human_rights + crackdown_human_rights)
   )
@@
 contrasts_int %>%
-  pivot_longer(criticized_emergency_environment:crackdown_refugee_humanrights, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer(
+    "criticized emergency - criticized environment":"crackdown refugee relief - crackdown human rights", 
+    names_to = "level", values_to = "Gamma"
+  ) %>% 
   ggplot(aes(x = Gamma, y = level)) +
@@
 However, only the contrasts between emergency response and the more contentious issue areas (environment and human rights) were positive, while contrasts between refugee relief and the more contentious issue areas were negative.
-Looking at all the contrasts, crackdown_refugee_environment, criticized_refugee_environment, and crackdown_emergency_humanrights contained 0 within their credibility interval.
+Here the issue area itself matters far more than the relationship with the host government.
 
@@
 
-```{r funding-contrasts-a}
-# Pull the posterior draws for funding sources
+```{r contrasts-hypothesis04a}
 # Reference Level = Funded primarily by many small private donations
-draws <- draws_intercepts
+# Compute the contrasts
 contrasts <- tibble(
-  few_wealthy_private_donors = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
-  government_grants = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
+  "wealthy donors - small donors" = draws_intercept %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
+  "government grants - small donors" = draws_intercept %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
 )
@@
 contrasts %>%
-  pivot_longer(few_wealthy_private_donors:government_grants, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer(
+    "wealthy donors - small donors":"government grants - small donors", 
+    names_to = "level", values_to = "Gamma"
+  ) %>% 
   ggplot(aes(x = Gamma, y = level)) +
@@
 )
-
-```
-
-As stated in the hypothesis, donors show increased willingness to donate to NGOs funded by numerous small private donors, as opposed to those funded by a handful of wealthy private donors or government grants.
+```
+
+Donors indeed show increased willingness to donate to NGOs funded by numerous small private donors, as opposed to those funded by a handful of wealthy private donors or government grants.
 
@@
 
-```{r funding-contrasts-b}
-# Overwrite draws with the appropriate interaction data
+```{r contrasts-hypothesis04b}
+# Import the appropriate interaction draws
 draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds"))
 
-# Pull the posterior draws for government crackdown*funding sources interaction
-# Reference Level = Friendly relationship with government
 # Reference Level = Funded primarily by many small private donations
-
+# Compute the contrasts
 contrasts_int <- tibble(
@@
 ) %>% mutate(
-  criticized_wealthydonors = (criticized) - (criticized + few_wealthy_private_donors + criticized_wealthydonors),
-
-  criticized_grants = (criticized) - (criticized + government_grants + criticized_grants),
-
-  crackdown_wealthydonors = (crackdown) - (crackdown + few_wealthy_private_donors + crackdown_wealthydonors),
-
-  crackdown_grants = crackdown - (crackdown + government_grants + crackdown_grants)
+  "criticized small donors - criticized wealthy donors" = 
+    (criticized) - (few_wealthy_private_donors + criticized + criticized_wealthydonors),
+  "criticized small donors - criticized government grants" = 
+    (criticized) - (government_grants + criticized + criticized_grants),
+  "crackdown small donors - crackdown wealthy donors" = 
+    (crackdown) - (few_wealthy_private_donors + crackdown + crackdown_wealthydonors),
+  "crackdown small donors - crackdown government grants" = 
+    (crackdown) - (government_grants + crackdown + crackdown_grants)
   )
@@
 contrasts_int %>%
-  pivot_longer(criticized_wealthydonors:crackdown_grants, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer(
+    "criticized small donors - criticized wealthy donors":"crackdown small donors - crackdown government grants", 
+    names_to = "level", values_to = "Gamma"
+  ) %>% 
   ggplot(aes(x = Gamma, y = level)) +
@@
 )
-
-```
-
-All of the contrasts are positive and none of them contain 0 within their credibility interval, which supports our hypothesis that donors are more willing to donate to organizations supported by many small private donors and are under criticism or crackdown.
+```
+
+All of the contrasts are positive and significant, which supports our hypothesis that donors are more willing to donate to organizations supported by many small private donors and are under criticism or crackdown.
 
@@
 
-```{r funding-contrasts-c}
-# Overwrite draws with the appropriate interaction data
+```{r contrasts-hypothesis04c}
+# Import the appropriate interaction draws
 draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4c.rds"))
-# Draws for lower order interactions
 draws_4b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds"))
@@
 
-# Pull the posterior draws for issue area*government crackdown*funding sources interaction
 # Reference Level = Funded primarily by many small private donations
 # Reference Level = Friendly relationship with government
-
+# Compute the contrasts
 contrasts_int <- tibble(
@@
   mutate(
-  emergency_humanrights_wealthydonors = (crackdown) - (crackdown + few_wealthy_private_donors + human_rights + crackdown_humanrights + crackdown_wealthydonors + humanrights_crackdown_wealthydonors),
-
-  emergency_humanrights_grants = (crackdown) - (crackdown + government_grants + human_rights + crackdown_humanrights + crackdown_grants + humanrights_crackdown_grants),
-
-  emergency_environment_wealthydonors = (crackdown) - (crackdown + few_wealthy_private_donors + environment + crackdown_environment + crackdown_wealthydonors + environment_crackdown_wealthydonors),
-
-  emergency_environment_grants = (crackdown) - (crackdown + government_grants + environment + crackdown_environment + crackdown_grants + environment_crackdown_grants),
-
-  refugee_humanrights_wealthydonors = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + few_wealthy_private_donors + human_rights + crackdown_humanrights + crackdown_wealthydonors + humanrights_crackdown_wealthydonors),
-
-  refugee_humanrights_grants = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + government_grants + human_rights + crackdown_humanrights + crackdown_grants + humanrights_crackdown_grants),
-
-  refugee_environment_wealthydonors = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + few_wealthy_private_donors + environment + crackdown_environment + crackdown_wealthydonors + environment_crackdown_wealthydonors),
-
-  refugee_environment_grants = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + government_grants + environment + crackdown_environment + crackdown_grants + environment_crackdown_grants),
+    "crackdown emergency small donors - crackdown human rights wealthy donors" = 
+      (crackdown) - 
+      (crackdown + few_wealthy_private_donors + human_rights + crackdown_humanrights + crackdown_wealthydonors +
+         humanrights_crackdown_wealthydonors),
+    "crackdown emergency small donors - crackdown human rights government grants" = 
+      (crackdown) - 
+      (crackdown + government_grants + human_rights + crackdown_humanrights + crackdown_grants +
+         humanrights_crackdown_grants),
+    emergency_environment_wealthydonors = 
+      (crackdown) - 
+      (crackdown + few_wealthy_private_donors + environment + crackdown_environment + crackdown_wealthydonors +
+         environment_crackdown_wealthydonors),
+    emergency_environment_grants = 
+      (crackdown) - 
+      (crackdown + government_grants + environment + crackdown_environment + crackdown_grants +
+         environment_crackdown_grants),
+    refugee_humanrights_wealthydonors = 
+      (crackdown + refugee_relief + crackdown_refugee) - 
+      (crackdown + few_wealthy_private_donors + human_rights + crackdown_humanrights + crackdown_wealthydonors +
+         humanrights_crackdown_wealthydonors),
+    refugee_humanrights_grants = 
+      (crackdown + refugee_relief + crackdown_refugee) - 
+      (crackdown + government_grants + human_rights + crackdown_humanrights + crackdown_grants +
+         humanrights_crackdown_grants),
+    refugee_environment_wealthydonors = 
+      (crackdown + refugee_relief + crackdown_refugee) - 
+      (crackdown + few_wealthy_private_donors + environment + crackdown_environment + crackdown_wealthydonors +
+         environment_crackdown_wealthydonors),
+    refugee_environment_grants = 
+      (crackdown + refugee_relief + crackdown_refugee) - 
+      (crackdown + government_grants + environment + crackdown_environment + crackdown_grants +
+         environment_crackdown_grants)
   )
@@
 contrasts_int %>%
-  pivot_longer(emergency_humanrights_wealthydonors:refugee_environment_grants, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer(
+    emergency_humanrights_wealthydonors:refugee_environment_grants, 
+    names_to = "level", values_to = "Gamma"
+  ) %>% 
   ggplot(aes(x = Gamma, y = level)) +
@@
 )
-
-```
-
-Contrast is most likely improperly coded, gammas are all over the place, so no conclusions can be made regarding the hypothesis
+```
 
@@
 # Pull the posterior draws for organizational practices
-draws <- draws_intercepts
+# Pull the relevant posterior draws
+draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "intercept.rds"))
+
+# Compute the contrasts
 contrasts <- tibble(

### 2021-12-11 analysis/04_figs-tables.Rmd
Finished contrasts through hypothesis 4b

@@
 
-To formally answer the hypotheses, we compute contrasts of the marginal posteriors. First, we need the intercept-only draws and associated levels.
+To formally answer the hypotheses, we compute contrasts of marginal posteriors. First, we need the intercept-only draws and associated levels.
 
@@
 
-# Join level and covariate labels to draws
+# Join levels and labels to draws
 draws_intercept <- draws_intercept %>% 
@@
     "red cross - amnesty" = red_cross - amnesty,
-    "red cross - greenpeace" = red_cross - greenpeace,
+    "red cross - greenpeace" = red_cross - greenpeace
   )
@@
   pivot_longer("oxfam - amnesty":"red cross - greenpeace", names_to = "level", values_to = "Gamma") %>% 
+  mutate(level = fct_rev(fct_inorder(level))) %>%
   ggplot(aes(x = Gamma, y = level)) +
@@
 
-Donors are indeed more likely to donate to Red Cross compared to Amnesty International and Greenpeace.
+Donors are indeed more likely to donate to Red Cross compared to Amnesty International and Greenpeace, holding every other attribute constant.
 However, compared to Amnesty International and Greenpeace, donors are less likely to donate to Oxfam.
@@
 contrasts <- tibble(
-  "crackdown - friendly" = draws_intercept %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
-  "criticized - friendly" = draws_intercept %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
+  "criticized - friendly" = draws_intercept %>% filter(level == "Criticized") %>% select(Gamma) %>% pull(),
+  "crackdown - friendly" = draws_intercept %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull()
 )
@@
   pivot_longer("crackdown - friendly":"criticized - friendly", names_to = "level", values_to = "Gamma") %>% 
+  mutate(level = fct_rev(fct_inorder(level))) %>%
   ggplot(aes(x = Gamma, y = level)) +
@@
 
-Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism relative to NGOs that have a friendly relationship with the government, with this decreased likelihood to donate greater for NGOs under crackdown compared to those being criticized.
+Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism relative to NGOs that have a friendly relationship with the government, holding every other attribute constant, with this decreased likelihood to donate greater for NGOs under crackdown compared to those being criticized.
 
@@
 contrasts_int <- tibble(
+  # Attribute levels
   amnesty = draws %>% filter(i == 1) %>% select(Gamma) %>% pull(),
@@
   crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
+  # Hypothesis 2b
   amnesty_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
@@
       (oxfam + criticized + oxfam_criticized) - (greenpeace + criticized + greenpeace_criticized),
-    "criticized red cross - criticized amnesty" = 
-      (red_cross + criticized + red_cross_criticized) - (amnesty + criticized + amnesty_criticized),
-    "criticized red cross - criticized green peace" = 
-      (red_cross + criticized + red_cross_criticized) - (greenpeace + criticized + greenpeace_criticized),
     "crackdown oxfam - crackdown amnesty" = 
@@
       (oxfam + crackdown + oxfam_crackdown) - (greenpeace + crackdown +  greenpeace_crackdown),
+    "criticized red cross - criticized amnesty" = 
+      (red_cross + criticized + red_cross_criticized) - (amnesty + criticized + amnesty_criticized),
+    "criticized red cross - criticized greenpeace" = 
+      (red_cross + criticized + red_cross_criticized) - (greenpeace + criticized + greenpeace_criticized),
     "crackdown red cross - crackdown amnesty" = 
@@
   ) %>% 
+  mutate(level = fct_rev(fct_inorder(level))) %>%
   ggplot(aes(x = Gamma, y = level)) +
@@
 
-Although donors show significantly more willingness to donate to Red Cross when they are criticized or under crackdown from the host government, donors are less likely to donate to Oxfam under the same conditions.
+Although donors show significantly more willingness to donate to Red Cross when they are criticized or under crackdown from the host government, donors are less likely to donate to Oxfam under the same conditions, holding every other attribute constant.
 The only contrast which isn't statistically significant is the difference between Oxfam and Amnesty when both are under crackdown.
@@
 Donors appear to be sensitive to NGO issue area when they are considering to donate.
-Emergency response was the most favored issue area by donors, and experienced the highest likelihood of receiving donations.
-While this partially matches the claim of the hypothesis, donors showed the least likelihood to donate to refugee relief NGOs, although this is not significantly different from their likelihood of donating for environmental causes.
-In other words, refugee relief appears to be as contentious as environment.
+Emergency response was the most favored issue area by donors, and experienced the highest likelihood of receiving donations, holding every other attribute constant.
+While this partially matches the claim of the hypothesis, donors showed the least likelihood to donate to refugee relief NGOs relative to emergency response, although this is not significantly different from their likelihood of donating for environmental causes with the same reference.
+In other words, refugee relief appears to be as contentious as environmental issues.
 
@@
 # Reference Level = Emergency Response
+# Reference Level = Friendly relationship with government
 # Compute the contrasts
 contrasts_int <- tibble(
+  # Attribute levels
   environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
@@
   crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
+  # Hypothesis 3b
   criticized_environment = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
@@
   crackdown_human_rights = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
-  crackdown_refugee = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
+  crackdown_refugee = draws %>% filter(i == 19) %>% select(Gamma) %>% pull()
 ) %>% 
   mutate(
-    "criticized emergency - criticized environment" = 
-      (criticized) - (criticized + environment + criticized_environment),
-    "criticized emergency - criticized human rights" = 
-      (criticized) - (criticized + human_rights + criticized_human_rights),
-    "crackdown emergency - crackdown environment" = 
-      (crackdown) - (crackdown + environment + crackdown_environment),
-    "crackdown emergency - crackdown human rights" = 
-      (crackdown) - (crackdown + human_rights + crackdown_human_rights),
-    "criticized refugee relief - criticized environment" = 
-      (criticized + refugee_relief + criticized_refugee) - (criticized + environment + criticized_environment),
-    "criticized refugee relief - criticized human rights" = 
-      (criticized + refugee_relief + criticized_refugee) - (criticized + human_rights + criticized_human_rights),
-    "crackdown refugee relief - crackdown environment" = 
-      (crackdown + refugee_relief + crackdown_refugee) - (crackdown + environment + crackdown_environment),
-    "crackdown refugee relief - crackdown human rights" = 
-      (crackdown + refugee_relief + crackdown_refugee) - (crackdown + human_rights + crackdown_human_rights)
+    "environment - emergency" = environment,
+    "human rights - emergency" = human_rights,
+    "refugee relief - emergency" = refugee_relief,
+    "criticized environment - criticized emergency" = 
+      (criticized + environment + criticized_environment) - (criticized),
+    "criticized human rights - criticized emergency" = 
+      (criticized + human_rights + criticized_human_rights) - (criticized),
+    "criticized refugee relief - criticized emergency" = 
+      (criticized + refugee_relief + criticized_refugee) - (criticized),
+    "crackdown environment - crackdown emergency" = 
+      (crackdown + environment + crackdown_environment) - (crackdown),
+    "crackdown human rights - crackdown emergency" = 
+      (crackdown + human_rights + crackdown_human_rights) - (crackdown),
+    "crackdown refugee relief - crackdown emergency" = 
+      (crackdown + human_rights + crackdown_human_rights) - (crackdown)
   )
@@
   pivot_longer(
-    "criticized emergency - criticized environment":"crackdown refugee relief - crackdown human rights", 
+    "environment - emergency":"crackdown refugee relief - crackdown emergency", 
     names_to = "level", values_to = "Gamma"
   ) %>% 
+  mutate(level = fct_rev(fct_inorder(level))) %>%
   ggplot(aes(x = Gamma, y = level)) +
@@
 
-Per our hypothesis, we expected to see the contrasts of the posterior distributions to be positive.
-However, only the contrasts between emergency response and the more contentious issue areas (environment and human rights) were positive, while contrasts between refugee relief and the more contentious issue areas were negative.
-Here the issue area itself matters far more than the relationship with the host government.
+When NGOs are criticized by the government, we see the same pattern as before, with emergency response being most preferred followed by human rights, environment, and refugee relief, holding every other attribute constant.
+However, we do not see an increase in likelihood to donate relative to an emergency response NGO being criticized.
+However, when NGOs are under crackdown by the government, we see that human rights, environment, and refugee relief all increase in their likelihood relative to an emergency response NGO under crackdown.
+In fact, both human rights and refugee relief NGOs under crackdown are indistinguishable from an emergency response NGO under crackdown in terms of propensity to donate.
 
@@
 
-Donors indeed show increased willingness to donate to NGOs funded by numerous small private donors, as opposed to those funded by a handful of wealthy private donors or government grants.
+Donors indeed show increased willingness to donate to NGOs funded by numerous small private donors, as opposed to those funded by a handful of wealthy private donors or government grants, holding every other attribute constant, with government grants preferred to a small handful of wealthy donors relative to numerous small private donors.
 
@@
 # Reference Level = Funded primarily by many small private donations
+# Reference Level = Friendly relationship with government
 # Compute the contrasts
@@
 ) %>% mutate(
-  "criticized small donors - criticized wealthy donors" = 
-    (criticized) - (few_wealthy_private_donors + criticized + criticized_wealthydonors),
-  "criticized small donors - criticized government grants" = 
-    (criticized) - (government_grants + criticized + criticized_grants),
-  "crackdown small donors - crackdown wealthy donors" = 
-    (crackdown) - (few_wealthy_private_donors + crackdown + crackdown_wealthydonors),
-  "crackdown small donors - crackdown government grants" = 
-    (crackdown) - (government_grants + crackdown + crackdown_grants)
+  "wealthy donors - small donors" = few_wealthy_private_donors,
+  "government grants - small donors" = government_grants,
+  "criticized wealthy donors - criticized small donors" = 
+    (few_wealthy_private_donors + criticized + criticized_wealthydonors) - (criticized),
+  "criticized government grants - criticized small donors" = 
+    (government_grants + criticized + criticized_grants) - (criticized),
+  "crackdown wealthy donors - crackdown small donors" = 
+    (few_wealthy_private_donors + crackdown + crackdown_wealthydonors) - (crackdown),
+  "crackdown government grants - crackdown small donors" = 
+    (government_grants + crackdown + crackdown_grants) - (crackdown)
   )
@@
   pivot_longer(
-    "criticized small donors - criticized wealthy donors":"crackdown small donors - crackdown government grants", 
+    "wealthy donors - small donors":"crackdown government grants - crackdown small donors", 
     names_to = "level", values_to = "Gamma"
   ) %>% 
+  mutate(level = fct_rev(fct_inorder(level))) %>%
   ggplot(aes(x = Gamma, y = level)) +
@@
 
-All of the contrasts are positive and significant, which supports our hypothesis that donors are more willing to donate to organizations supported by many small private donors and are under criticism or crackdown.
+There is no significant increase in willingness to donate to NGOs facing government criticism or crackdown that are funded primarily by small private donors, holding every other attribute constant.
+The same pattern holds with small private donors most preferred, followed by government grants and wealthy donors, with their relative importance held constant.
 
@@
 
+holding every other attribute constant
+
 ### Hypothesis 5, Organizational Practices
@@
 
-```{r practices-contrasts-a}
+```{r contrasts-hypothesis05a}
 # Pull the posterior draws for organizational practices
@@
   pivot_longer(fin_transparency, names_to = "level", values_to = "Gamma") %>% 
+  mutate(level = fct_rev(fct_inorder(level))) %>%
   ggplot(aes(x = Gamma, y = level)) +
@@
 
+holding every other attribute constant
+
 Donors show an increased likelihood to donate to NGOs that are financially transparent, as hypothesized.
@@
 
-```{r practices-contrasts-b}
+```{r contrasts-hypothesis05b}
 # Overwrite draws with the appropriate interaction data
@@
   pivot_longer(financial_transparency_criticized:financial_transparency_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  mutate(level = fct_rev(fct_inorder(level))) %>%
   ggplot(aes(x = Gamma, y = level)) +
@@
 
+holding every other attribute constant
+
 The contrasts for hypothesis 5b provide evidence that donors are more willing to donate to organizations which are criticized or under crackdown and are also financially transparent.
@@
 
-```{r practices-contrasts-c}
+```{r contrasts-hypothesis05c}
 # Overwrite draws with the appropriate interaction data
@@
   pivot_longer(fin_smalldonors_wealthydonors_criticized:not_fin_smalldonors_grants_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  mutate(level = fct_rev(fct_inorder(level))) %>%
   ggplot(aes(x = Gamma, y = level)) +
@@
 
+holding every other attribute constant
+
 Only fin_smalldonors_grants_crackdown contains 0 within its credibility interval.
@@
 
-```{r practices-contrasts-d}
+```{r contrasts-hypothesis05d}
 # Overwrite draws with the appropriate interaction data
@@
   pivot_longer(fin_emergency_environment_criticized:fin_refugee_humanright_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  mutate(level = fct_rev(fct_inorder(level))) %>%
   ggplot(aes(x = Gamma, y = level)) +
@@
 
+holding every other attribute constant
+
 #### Hypothesis 5e, Relationship with Host Government, Organizational Practices, Issue Area, and Funding Sources
@@
 
-```{r practices-contrasts-e}
+```{r contrasts-hypothesis05e}
 # Overwrite draws with the appropriate interaction data
@@
   pivot_longer(fin_sd_emergency_environment_criticized:fin_sd_refugee_humanrights_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  mutate(level = fct_rev(fct_inorder(level))) %>%
   ggplot(aes(x = Gamma, y = level)) +
@@
 
+holding every other attribute constant
+
 #### Hypothesis 5f, Organizational Practices
@@
 
-```{r practices-contrasts-b}
+```{r contrasts-hypothesis05f}
 # Pull the posterior draws for organizational practices
@@
   pivot_longer(accountability, names_to = "level", values_to = "Gamma") %>% 
+  mutate(level = fct_rev(fct_inorder(level))) %>%
   ggplot(aes(x = Gamma, y = level)) +
@@
 ```
+
+holding every other attribute constant
 

### 2021-12-14 analysis/04_figs-tables.Rmd
Finished remaining contrasts through 5f

@@
   crackdown_grants = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
-) %>% mutate(
+) %>% 
+  mutate(
     "wealthy donors - small donors" = few_wealthy_private_donors,
@@
 draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4c.rds"))
-draws_4b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds"))
-draws_3b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))
-
+
+# Reference Level = Emergency Response
 # Reference Level = Funded primarily by many small private donations
@@
 contrasts_int <- tibble(
+  # Attribute levels
   environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
@@
   crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
-  crackdown_environment = draws_3b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
-  crackdown_humanrights = draws_3b %>% filter(i == 18) %>% select(Gamma) %>% pull(),
-  crackdown_refugee = draws_3b %>% filter(i == 19) %>% select(Gamma) %>% pull(),
-  crackdown_wealthydonors = draws_4b %>% filter(i == 16) %>% select(Gamma) %>% pull(),
-  crackdown_grants = draws_4b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
+  # Hypothesis 4c
   emergency_crackdown_wealthydonors = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
@@
   refugee_crackdown_wealthydonors = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
-  refugee_crackdown_grants = draws %>% filter(i == 21) %>% select(Gamma) %>% pull(),
+  refugee_crackdown_grants = draws %>% filter(i == 21) %>% select(Gamma) %>% pull()
 ) %>% 
   mutate(
-    "crackdown emergency small donors - crackdown human rights wealthy donors" = 
-      (crackdown) - 
-      (crackdown + few_wealthy_private_donors + human_rights + crackdown_humanrights + crackdown_wealthydonors +
-         humanrights_crackdown_wealthydonors),
-    "crackdown emergency small donors - crackdown human rights government grants" = 
-      (crackdown) - 
-      (crackdown + government_grants + human_rights + crackdown_humanrights + crackdown_grants +
-         humanrights_crackdown_grants),
-    emergency_environment_wealthydonors = 
-      (crackdown) - 
-      (crackdown + few_wealthy_private_donors + environment + crackdown_environment + crackdown_wealthydonors +
-         environment_crackdown_wealthydonors),
-    emergency_environment_grants = 
-      (crackdown) - 
-      (crackdown + government_grants + environment + crackdown_environment + crackdown_grants +
-         environment_crackdown_grants),
-    refugee_humanrights_wealthydonors = 
-      (crackdown + refugee_relief + crackdown_refugee) - 
-      (crackdown + few_wealthy_private_donors + human_rights + crackdown_humanrights + crackdown_wealthydonors +
-         humanrights_crackdown_wealthydonors),
-    refugee_humanrights_grants = 
-      (crackdown + refugee_relief + crackdown_refugee) - 
-      (crackdown + government_grants + human_rights + crackdown_humanrights + crackdown_grants +
-         humanrights_crackdown_grants),
-    refugee_environment_wealthydonors = 
-      (crackdown + refugee_relief + crackdown_refugee) - 
-      (crackdown + few_wealthy_private_donors + environment + crackdown_environment + crackdown_wealthydonors +
-         environment_crackdown_wealthydonors),
-    refugee_environment_grants = 
-      (crackdown + refugee_relief + crackdown_refugee) - 
-      (crackdown + government_grants + environment + crackdown_environment + crackdown_grants +
-         environment_crackdown_grants)
+    "wealthy donors environment - small donors emergency" = 
+      few_wealthy_private_donors + environment,
+    "wealthy donors human rights - small donors emergency" = 
+      few_wealthy_private_donors + human_rights,
+    "wealthy donors refugee relief - small donors emergency" = 
+      few_wealthy_private_donors + refugee_relief,
+    "crackdown wealthy donors environment - crackdown small donors emergency" = 
+      (few_wealthy_private_donors + environment + crackdown + environment_crackdown_wealthydonors) - (crackdown + emergency_crackdown_wealthydonors),
+    "crackdown wealthy donors human rights - crackdown small donors emergency" = 
+      (few_wealthy_private_donors + human_rights + crackdown + humanrights_crackdown_wealthydonors) - (crackdown + emergency_crackdown_wealthydonors),
+    "crackdown wealthy donors refugee relief - crackdown small donors emergency" = 
+      (few_wealthy_private_donors + refugee_relief + crackdown + refugee_crackdown_wealthydonors) - (crackdown + emergency_crackdown_wealthydonors),
+    "government grants environment - small donors emergency" = 
+      government_grants + environment,
+    "government grants human rights - small donors emergency" = 
+      government_grants + human_rights,
+    "government grants refugee relief - small donors emergency" = 
+      government_grants + refugee_relief,
+    "crackdown government grants environment - crackdown small donors emergency" = 
+      (government_grants + environment + crackdown + environment_crackdown_grants) - (crackdown + emergency_crackdown_grants),
+    "crackdown government grants human rights - crackdown small donors emergency" = 
+      (government_grants + human_rights + crackdown + humanrights_crackdown_grants) - (crackdown + emergency_crackdown_grants),
+    "crackdown government grants refugee relief - crackdown small donors emergency" = 
+      (government_grants + refugee_relief + crackdown + refugee_crackdown_grants) - (crackdown + emergency_crackdown_grants)
   )
@@
   pivot_longer(
-    emergency_humanrights_wealthydonors:refugee_environment_grants, 
+    "wealthy donors environment - small donors emergency":"crackdown government grants refugee relief - crackdown small donors emergency", 
     names_to = "level", values_to = "Gamma"
@@
 
-holding every other attribute constant
+There an increase in likelihood to donate in general when NGOs are funded by government grants, which we've seen separately, though the difference isn't significant when accounting for the NGOs being under crackdown, holding every other attribute constant.
+We also see that refugee relief continues to be seen as contentious as the environment.
+Interestingly, the median likelihood to donate is somewhat normalized across issue areas when the NGOs are under crackdown and all funded by wealthy donors.
 
@@
 
-#### Hypothesis 5a, Organizational Practices
+#### Hypothesis 5a, Financial Transparency
 
@@
 ```{r contrasts-hypothesis05a}
-# Pull the posterior draws for organizational practices
-# Pull the relevant posterior draws
-draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "intercept.rds"))
-
+# Reference Level = No financial transparency
 # Compute the contrasts
 contrasts <- tibble(
-  fin_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
-  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
+  "financial transparency - no financial transparency" = draws_intercept %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull()
 )
@@
 contrasts %>%
-  pivot_longer(fin_transparency, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer("financial transparency - no financial transparency", names_to = "level", values_to = "Gamma") %>% 
   mutate(level = fct_rev(fct_inorder(level))) %>%
@@
 
-holding every other attribute constant
-
-Donors show an increased likelihood to donate to NGOs that are financially transparent, as hypothesized.
-
-#### Hypothesis 5b, Relationship with Host Government, Organizational Practices
+Donors show an increased likelihood to donate to NGOs that are financially transparent, holding every other attribute constant.
+
+#### Hypothesis 5b, Relationship with Host Government and Financial Transparency
 
@@
 ```{r contrasts-hypothesis05b}
-# Overwrite draws with the appropriate interaction data
+# Import the appropriate interaction draws
 draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
 
-# Pull the posterior draws for organizational practices*government crackdown interaction
+# Reference Level = No financial transparency
 # Reference Level = Friendly relationship with government
-
 contrasts_int <- tibble(
+  # Attribute levels
   fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
@@
   crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
+  # Hypothesis 5b
   fin_transparency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
-  fin_transparency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
-  ) %>% mutate(
-    fin_transparency_criticized = (fin_transparency + criticized + fin_transparency_criticized) - (criticized),
-    fin_transparency_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown) - (crackdown)
+  fin_transparency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull()
+) %>% 
+  mutate(
+    "financial transparency - no financial transparency" = fin_transparency,
+    "criticized financial transparency - criticized no financial transparency" = 
+      (fin_transparency + criticized + fin_transparency_criticized) - (criticized),
+    "crackdown financial transparency - crackdown no financial transparency" = 
+      (fin_transparency + crackdown + fin_transparency_crackdown) - (crackdown)
   )
@@
 contrasts_int %>%
-  pivot_longer(financial_transparency_criticized:financial_transparency_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer(
+    "financial transparency - no financial transparency":"crackdown financial transparency - crackdown no financial transparency", 
+    names_to = "level", values_to = "Gamma"
+  ) %>% 
   mutate(level = fct_rev(fct_inorder(level))) %>%
@@
 )
-
-```
-
-holding every other attribute constant
-
-The contrasts for hypothesis 5b provide evidence that donors are more willing to donate to organizations which are criticized or under crackdown and are also financially transparent.
-
-#### Hypothesis 5c, Relationship with Host Government, Organizational Practices, and Funding Sources
+```
+
+There is no increased willingness to donate to NGOs that are criticized or under government crackdown that are also financially transparent, holding every other attribute constant.
+
+#### Hypothesis 5c, Relationship with Host Government, Financial Transparency, and Funding Sources
 
@@
 ```{r contrasts-hypothesis05c}
-# Overwrite draws with the appropriate interaction data
+# Import the appropriate interaction draws
 draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5c.rds"))
-# Lower order interaction draws
-draws_5b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
-draws_4b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds"))
-
-# Pull the posterior draws for organizational practices*funding sources*government crackdown interaction
+
+# Reference Level = No financial transparency
 # Reference Level = Friendly relationship with government
 # Reference Level = Funded primarily by many small private donations
-# All interactions include financial transparency
-
 contrasts_int <- tibble(
+  # Attribute levels
   fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
@@
   crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
-  criticized_wealthydonors = draws_4b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
-  criticized_grants = draws_4b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
-  crackdown_wealthydonors = draws_4b %>% filter(i == 16) %>% select(Gamma) %>% pull(),
-  crackdown_grants = draws_4b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
-  fin_transparency_criticized = draws_5b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
-  fin_transparency_crackdown = draws_5b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  # Hypothesis 5c
   fin_smalldonors_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
@@
   fin_wealthydonors_crackdown = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
-  fin_grants_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
+  fin_grants_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull()
 ) %>% 
   mutate(
-  fin_smalldonors_wealthydonors_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized) - (fin_transparency + criticized + few_wealthy_private_donors + criticized_wealthydonors + fin_transparency_criticized + fin_wealthydonors_criticized),
-
-  fin_smalldonors_grants_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized) -  (fin_transparency + criticized + government_grants + criticized_grants + fin_transparency_criticized + fin_grants_criticized),
-
-  fin_smalldonors_wealthydonors_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown) - (fin_transparency + crackdown + few_wealthy_private_donors + crackdown_wealthydonors + fin_transparency_crackdown + fin_wealthydonors_crackdown),
-
-  fin_smalldonors_grants_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown) - (fin_transparency + crackdown + government_grants + crackdown_grants + fin_transparency_crackdown + fin_grants_crackdown),
-
-# additional contrasts to compare financial transparency to no transparency    
-  not_fin_smalldonors_wealthydonors_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized) - (criticized + few_wealthy_private_donors + criticized_wealthydonors),
-
-  not_fin_smalldonors_grants_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized) -  (criticized + government_grants + criticized_grants),
-
-  not_fin_smalldonors_wealthydonors_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown) - (crackdown + few_wealthy_private_donors + crackdown_wealthydonors),
-
-  not_fin_smalldonors_grants_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown) - (crackdown + government_grants + fin_transparency_crackdown + fin_grants_crackdown)
+    "financially transparent small donors - not financially transparent small donors" = 
+      (fin_transparency),
+    "financially transparent wealthy donors - not financially transparent wealthy donors" = 
+      (fin_transparency + few_wealthy_private_donors) - (few_wealthy_private_donors),
+    "financially transparent government grants - not financially transparent government grants" = 
+      (fin_transparency + government_grants) - (government_grants),
+    "criticized financially transparent small donors - criticized not financially transparent small donors" = 
+      (fin_transparency + criticized + fin_smalldonors_criticized) - (criticized),
+    "criticized financially transparent wealthy donors - criticized not financially transparent wealthy donors" =
+      (fin_transparency + few_wealthy_private_donors + criticized + fin_wealthydonors_criticized) - (few_wealthy_private_donors + criticized),
+    "criticized financially transparent government grants - criticized not financially transparent government grants" = 
+      (fin_transparency + government_grants + criticized + fin_grants_criticized) - (government_grants + criticized),
+    "crackdown financially transparent small donors - crackdown not financially transparent small donors" = 
+      (fin_transparency + crackdown + fin_smalldonors_crackdown) - (crackdown),
+    "crackdown financially transparent wealthy donors - crackdown not financially transparent wealthy donors" =
+      (fin_transparency + few_wealthy_private_donors + crackdown + fin_wealthydonors_crackdown) - (few_wealthy_private_donors + crackdown),
+    "crackdown financially transparent government grants - crackdown not financially transparent government grants" = 
+      (fin_transparency + government_grants + crackdown + fin_grants_crackdown) - (government_grants + crackdown),
   )
@@
 contrasts_int %>%
-  pivot_longer(fin_smalldonors_wealthydonors_criticized:not_fin_smalldonors_grants_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer(
+    "financially transparent small donors - not financially transparent small donors":"crackdown financially transparent government grants - crackdown not financially transparent government grants", 
+    names_to = "level", values_to = "Gamma"
+  ) %>% 
   mutate(level = fct_rev(fct_inorder(level))) %>%
@@
 ggsave(
-  "contrasts_hypothesis05c.png",#
+  "contrasts_hypothesis05c.png",
   path = here::here("analysis", "output", "figures"),
@@
 
-holding every other attribute constant
-
-Only fin_smalldonors_grants_crackdown contains 0 within its credibility interval.
-Since all other contrasts are positive and do not contain 0 within their credibility intervals, there is evidence supporting that donors are more willing to donate to NGOs that are criticized by the government/under government crackdown, are financially transparent, and are funded primarily by numerous small private donors.
-
-#### Hypothesis 5d, Relationship with Host Government, Organizational Practices, and Issue Area
+There is no increased willingness to donate to NGOs that are criticized or under government crackdown when they are also financially transparent and funded by numerous small private donors, holding every other attribute constant.
+
+#### Hypothesis 5d, Relationship with Host Government, Financial Transparency, and Issue Area
 
@@
 ```{r contrasts-hypothesis05d}
-# Overwrite draws with the appropriate interaction data
+# Import the appropriate interaction draws
 draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds"))
-# Lower-order interactions
-draws_5b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
-draws_3b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))
-
-# Pull the posterior draws for organizational practices*issue area*government crackdown interaction
+
+# Reference Level = No financial transparency
 # Reference Level = Friendly relationship with government
 # Reference Level = Emergency Response
-# All interactions include financial transparency
-
 contrasts_int <- tibble(
+  # Attribute levels
+  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
+  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
+  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
   fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
@@
   crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
-  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
-  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
-  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
-  criticized_environment = draws_3b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
-  criticized_humanrights = draws_3b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
-  criticized_refugee = draws_3b %>% filter(i == 16) %>% select(Gamma) %>% pull(),
-  crackdown_environment = draws_3b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
-  crackdown_humanrights = draws_3b %>% filter(i == 18) %>% select(Gamma) %>% pull(),
-  crackdown_refugee = draws_3b %>% filter(i == 19) %>% select(Gamma) %>% pull(),
-  fin_transparency_criticized = draws_5b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
-  fin_transparency_crackdown = draws_5b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  # Hypothesis 5d
   fin_emergency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
@@
   mutate(
-  fin_emergency_environment_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_emergency_criticized) - (fin_transparency + criticized + environment + fin_transparency_criticized + criticized_environment + fin_environment_criticized),
-
-  fin_emergency_humanrights_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_emergency_criticized) - (fin_transparency + criticized + human_rights + fin_transparency_criticized + criticized_humanrights + fin_humanrights_criticized),
-
-  fin_emergency_environment_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_emergency_crackdown) - (fin_transparency + crackdown + environment + fin_transparency_crackdown + crackdown_environment + fin_environment_crackdown),
-
-  fin_emergency_humanright_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_emergency_crackdown) - (fin_transparency + crackdown + human_rights + fin_transparency_crackdown + crackdown_humanrights + fin_humanrights_crackdown),
-
-  fin_refugee_environment_criticized = (fin_transparency + criticized + fin_transparency_criticized + criticized_refugee + fin_refugee_criticized) - (fin_transparency + criticized + environment + fin_transparency_criticized + criticized_environment + fin_environment_criticized),
-
-  fin_refugee_humanright_criticized = (fin_transparency + criticized + fin_transparency_criticized + criticized_refugee + fin_refugee_criticized) - (fin_transparency + criticized + human_rights + fin_transparency_criticized + criticized_humanrights + fin_humanrights_criticized),
-
-  fin_refugee_environment_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + crackdown_refugee + fin_refugee_crackdown) - (fin_transparency + crackdown + environment + crackdown_environment + fin_transparency_crackdown + fin_environment_crackdown),
-
-  fin_refugee_humanright_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + crackdown_refugee + fin_refugee_crackdown) - (fin_transparency + crackdown + human_rights + fin_transparency_crackdown + crackdown_humanrights + fin_humanrights_crackdown)
+    "financially transparent environment - not financially transparent emergency" = 
+      (fin_transparency + environment),
+    "financially transparent human rights - not financially transparent emergency" = 
+      (fin_transparency + human_rights),
+    "financially transparent refugee relief - not financially transparent emergency" = 
+      (fin_transparency + refugee_relief),
+    "criticized financially transparent environment - criticized not financially transparent emergency" = 
+      (fin_transparency + environment + criticized + fin_environment_criticized) - (criticized),
+    "criticized financially transparent human rights - criticized not financially transparent emergency" = 
+      (fin_transparency + human_rights + criticized + fin_humanrights_criticized) - (criticized),
+    "criticized financially transparent refugee relief - criticized not financially transparent emergency" = 
+      (fin_transparency + refugee_relief + criticized + fin_refugee_criticized) - (criticized),
+    "crackdown financially transparent environment - crackdown not financially transparent emergency" = 
+      (fin_transparency + environment + crackdown + fin_environment_crackdown) - (crackdown),
+    "crackdown financially transparent human rights - crackdown not financially transparent emergency" = 
+      (fin_transparency + human_rights + crackdown + fin_humanrights_crackdown) - (crackdown),
+    "crackdown financially transparent refugee relief - crackdown not financially transparent emergency" = 
+      (fin_transparency + refugee_relief + crackdown + fin_refugee_crackdown) - (crackdown)
   )
@@
 contrasts_int %>%
-  pivot_longer(fin_emergency_environment_criticized:fin_refugee_humanright_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer(
+    "financially transparent environment - not financially transparent emergency":"crackdown financially transparent refugee relief - crackdown not financially transparent emergency", 
+    names_to = "level", values_to = "Gamma") %>% 
   mutate(level = fct_rev(fct_inorder(level))) %>%
@@
 
-The contrasts don't seem to be properly calculated, so no conclusion at this time.
-
-holding every other attribute constant
-
-#### Hypothesis 5e, Relationship with Host Government, Organizational Practices, Issue Area, and Funding Sources
+There is no increased willingness to donate to NGOs that are criticized or under government crackdown when they are also financially transparent and work in less contentious areas, holding every other attribute constant.
+
+#### Hypothesis 5e, Relationship with Host Government, Financial Transparency, Issue Area, and Funding Sources
 
@@
 ```{r contrasts-hypothesis05e}
-# Overwrite draws with the appropriate interaction data
+# Import the appropriate interaction draws
 draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5e.rds"))
-# Lower-order interactions
-draws_5b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
-draws_3b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))
-draws_5c <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5c.rds"))
-draws_5d <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds"))
-# Pull the posterior draws for organizational practices*funding*issue area*government crackdown interaction
+
+# Reference Level = No financial transparency
 # Reference Level = Friendly relationship with government
 # Reference Level = Emergency Response
-# All interactions include small donors
-# All interactions include financial transparency
-
+# Reference Level = Funded primarily by many small private donations
 contrasts_int <- tibble(
+  # Attribute levels
   environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
@@
   crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
-  criticized_environment = draws_3b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
-  criticized_humanrights = draws_3b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
-  criticized_refugee = draws_3b %>% filter(i == 16) %>% select(Gamma) %>% pull(),
-  crackdown_environment = draws_3b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
-  crackdown_humanrights = draws_3b %>% filter(i == 18) %>% select(Gamma) %>% pull(),
-  crackdown_refugee = draws_3b %>% filter(i == 19) %>% select(Gamma) %>% pull(),
-  fin_transparency_criticized = draws_5b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
-  fin_transparency_crackdown = draws_5b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
-  fin_emergency_criticized = draws_5d %>% filter(i == 14) %>% select(Gamma) %>% pull(),
-  fin_emergency_crackdown = draws_5d %>% filter(i == 15) %>% select(Gamma) %>% pull(),
-  fin_environment_criticized = draws_5d %>% filter(i == 16) %>% select(Gamma) %>% pull(),
-  fin_environment_crackdown = draws_5d %>% filter(i == 17) %>% select(Gamma) %>% pull(),
-  fin_humanrights_criticized = draws_5d %>% filter(i == 18) %>% select(Gamma) %>% pull(),
-  fin_humanrights_crackdown = draws_5d %>% filter(i == 19) %>% select(Gamma) %>% pull(),
-  fin_refugee_criticized = draws_5d %>% filter(i == 20) %>% select(Gamma) %>% pull(),
-  fin_refugee_crackdown = draws_5d %>% filter(i == 21) %>% select(Gamma) %>% pull(),
-  fin_smalldonors_criticized = draws_5c %>% filter(i == 14) %>% select(Gamma) %>% pull(),
-  fin_wealthydonors_criticized = draws_5c %>% filter(i == 15) %>% select(Gamma) %>% pull(),
-  fin_grants_criticized = draws_5c %>% filter(i == 16) %>% select(Gamma) %>% pull(),
-  fin_smalldonors_crackdown = draws_5c %>% filter(i == 17) %>% select(Gamma) %>% pull(),
-  fin_wealthydonors_crackdown = draws_5c %>% filter(i == 18) %>% select(Gamma) %>% pull(),
-  fin_grants_crackdown = draws_5c %>% filter(i == 19) %>% select(Gamma) %>% pull(),
-  fin_sd_emergency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
-  fin_sd_emergency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
-  fin_sd_environment_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
-  fin_sd_environment_crackdown = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
-  fin_sd_humanrights_criticized = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
-  fin_sd_humanrights_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
-  fin_sd_refugee_criticized = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
-  fin_sd_refugee_crackdown = draws %>% filter(i == 21) %>% select(Gamma) %>% pull()
-  ) %>% mutate(
-  fin_sd_emergency_environment_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized + fin_emergency_criticized + fin_sd_emergency_criticized) - (fin_transparency + criticized + environment + criticized_environment + fin_transparency_criticized + fin_smalldonors_criticized + fin_environment_criticized + fin_sd_environment_criticized),
-
-  fin_sd_emergency_humanrights_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized + fin_emergency_criticized + fin_sd_emergency_criticized) - (fin_transparency + criticized + human_rights + criticized_humanrights + fin_transparency_criticized + fin_smalldonors_criticized + fin_humanrights_criticized + fin_sd_humanrights_criticized) ,
-
-  fin_sd_emergency_environment_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown + fin_emergency_crackdown + fin_sd_emergency_crackdown) - (fin_transparency + crackdown + environment + crackdown_environment + fin_transparency_crackdown + fin_smalldonors_crackdown + fin_environment_crackdown + fin_sd_environment_crackdown),
-
-  fin_sd_emergency_humanrights_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown + fin_emergency_crackdown + fin_sd_emergency_crackdown) - (fin_transparency + crackdown + human_rights + crackdown_humanrights + fin_transparency_crackdown + fin_smalldonors_crackdown + fin_humanrights_crackdown + fin_sd_humanrights_crackdown) ,
-
-  fin_sd_refugee_environment_criticized = (fin_transparency + criticized + refugee_relief + fin_transparency_criticized + criticized_refugee + fin_smalldonors_criticized + fin_refugee_criticized + fin_sd_refugee_criticized) - (fin_transparency + criticized + environment + criticized_environment + fin_transparency_criticized + fin_smalldonors_criticized + fin_environment_criticized + fin_sd_environment_criticized) ,
-
-  fin_sd_refugee_humanrights_criticized = (fin_transparency + criticized + refugee_relief + fin_transparency_criticized + criticized_refugee + fin_smalldonors_criticized + fin_refugee_criticized + fin_sd_refugee_criticized) - (fin_transparency + criticized + human_rights + criticized_humanrights + fin_transparency_criticized + fin_smalldonors_criticized + fin_humanrights_criticized + fin_sd_humanrights_criticized) ,
-
-  fin_sd_refugee_environment_crackdown = (fin_transparency + crackdown + refugee_relief + fin_transparency_crackdown + crackdown_refugee + fin_smalldonors_crackdown + fin_refugee_crackdown + fin_sd_refugee_crackdown) - (fin_transparency + crackdown + environment + crackdown_environment + fin_transparency_crackdown + fin_smalldonors_crackdown + fin_environment_crackdown + fin_sd_environment_crackdown) ,
-
-  fin_sd_refugee_humanrights_crackdown = (fin_transparency + crackdown + refugee_relief + fin_transparency_crackdown + crackdown_refugee + fin_smalldonors_crackdown + fin_refugee_crackdown + fin_sd_refugee_crackdown) - (fin_transparency + crackdown + human_rights + crackdown_humanrights + fin_transparency_crackdown + fin_smalldonors_crackdown + fin_humanrights_crackdown + fin_sd_humanrights_crackdown),
+  # Hypothesis 5e
+  fin_emergency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
+  fin_emergency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
+  fin_environment_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
+  fin_environment_crackdown = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
+  fin_humanrights_criticized = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
+  fin_humanrights_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
+  fin_refugee_criticized = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
+  fin_refugee_crackdown = draws %>% filter(i == 21) %>% select(Gamma) %>% pull()
+) %>% 
+  mutate(
+    "financially transparent environment small donors - not financially transparent emergency small donors" = 
+      (fin_transparency + environment),
+    "financially transparent human rights small donors - not financially transparent emergency small donors" = 
+      (fin_transparency + human_rights),
+    "financially transparent refugee relief small donors - not financially transparent emergency small donors" = 
+      (fin_transparency + refugee_relief),
+    "criticized financially transparent environment small donors - criticized not financially transparent emergency small donors" = 
+      (fin_transparency + environment + criticized + fin_environment_criticized) - (criticized),
+    "criticized financially transparent human rights small donors - criticized not financially transparent emergency small donors" = 
+      (fin_transparency + human_rights + criticized + fin_humanrights_criticized) - (criticized),
+    "criticized financially transparent refugee relief small donors - criticized not financially transparent emergency small donors" = 
+      (fin_transparency + refugee_relief + criticized + fin_refugee_criticized) - (criticized),
+    "crackdown financially transparent environment small donors - crackdown not financially transparent emergency small donors" = 
+      (fin_transparency + environment + crackdown + fin_environment_crackdown) - (crackdown),
+    "crackdown financially transparent human rights small donors - crackdown not financially transparent emergency small donors" = 
+      (fin_transparency + human_rights + crackdown + fin_humanrights_crackdown) - (crackdown),
+    "crackdown financially transparent refugee relief small donors - crackdown not financially transparent emergency small donors" = 
+      (fin_transparency + refugee_relief + crackdown + fin_refugee_crackdown) - (crackdown),
+    "financially transparent environment wealthy donors - not financially transparent emergency wealthy donors" = 
+      (fin_transparency + environment + few_wealthy_private_donors) - (few_wealthy_private_donors),
+    "financially transparent human rights wealthy donors - not financially transparent emergency wealthy donors" = 
+      (fin_transparency + human_rights + few_wealthy_private_donors) - (few_wealthy_private_donors),
+    "financially transparent refugee relief wealthy donors - not financially transparent emergency wealthy donors" = 
+      (fin_transparency + refugee_relief + few_wealthy_private_donors) - (few_wealthy_private_donors),
+    "criticized financially transparent environment wealthy donors - criticized not financially transparent emergency wealthy donors" = 
+      (fin_transparency + environment + criticized + fin_environment_criticized + few_wealthy_private_donors) - (criticized + few_wealthy_private_donors),
+    "criticized financially transparent human rights wealthy donors - criticized not financially transparent emergency wealthy donors" = 
+      (fin_transparency + human_rights + criticized + fin_humanrights_criticized + few_wealthy_private_donors) - (criticized + few_wealthy_private_donors),
+    "criticized financially transparent refugee relief wealthy donors - criticized not financially transparent emergency wealthy donors" = 
+      (fin_transparency + refugee_relief + criticized + fin_refugee_criticized + few_wealthy_private_donors) - (criticized + few_wealthy_private_donors),
+    "crackdown financially transparent environment wealthy donors - crackdown not financially transparent emergency wealthy donors" = 
+      (fin_transparency + environment + crackdown + fin_environment_crackdown + few_wealthy_private_donors) - (crackdown + few_wealthy_private_donors),
+    "crackdown financially transparent human rights wealthy donors - crackdown not financially transparent emergency wealthy donors" = 
+      (fin_transparency + human_rights + crackdown + fin_humanrights_crackdown + few_wealthy_private_donors) - (crackdown + few_wealthy_private_donors),
+    "crackdown financially transparent refugee relief wealthy donors - crackdown not financially transparent emergency wealthy donors" = 
+      (fin_transparency + refugee_relief + crackdown + fin_refugee_crackdown + few_wealthy_private_donors) - (crackdown + few_wealthy_private_donors),
+    "financially transparent environment government grants - not financially transparent emergency government grants" = 
+      (fin_transparency + environment + government_grants) - (government_grants),
+    "financially transparent human rights government grants - not financially transparent emergency government grants" = 
+      (fin_transparency + human_rights + government_grants) - (government_grants),
+    "financially transparent refugee relief government grants - not financially transparent emergency government grants" = 
+      (fin_transparency + refugee_relief + government_grants) - (government_grants),
+    "criticized financially transparent environment government grants - criticized not financially transparent emergency government grants" = 
+      (fin_transparency + environment + criticized + fin_environment_criticized + government_grants) - (criticized + government_grants),
+    "criticized financially transparent human rights government grants - criticized not financially transparent emergency government grants" = 
+      (fin_transparency + human_rights + criticized + fin_humanrights_criticized + government_grants) - (criticized + government_grants),
+    "criticized financially transparent refugee relief government grants - criticized not financially transparent emergency government grants" = 
+      (fin_transparency + refugee_relief + criticized + fin_refugee_criticized + government_grants) - (criticized + government_grants),
+    "crackdown financially transparent environment government grants - crackdown not financially transparent emergency government grants" = 
+      (fin_transparency + environment + crackdown + fin_environment_crackdown + government_grants) - (crackdown + government_grants),
+    "crackdown financially transparent human rights government grants - crackdown not financially transparent emergency government grants" = 
+      (fin_transparency + human_rights + crackdown + fin_humanrights_crackdown + government_grants) - (crackdown + government_grants),
+    "crackdown financially transparent refugee relief government grants - crackdown not financially transparent emergency government grants" = 
+      (fin_transparency + refugee_relief + crackdown + fin_refugee_crackdown + government_grants) - (crackdown + government_grants)
   )
@@
 contrasts_int %>%
-  pivot_longer(fin_sd_emergency_environment_criticized:fin_sd_refugee_humanrights_crackdown, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer(
+    "financially transparent environment small donors - not financially transparent emergency small donors":"crackdown financially transparent refugee relief government grants - crackdown not financially transparent emergency government grants",
+    names_to = "level", values_to = "Gamma") %>% 
   mutate(level = fct_rev(fct_inorder(level))) %>%
@@
 
-These contrasts don't provide conclusive results, need fixing.
-
-holding every other attribute constant
-
-#### Hypothesis 5f, Organizational Practices
+There is no increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief) and are funded by numerous small donors, holding every other attribute constant.
+
+#### Hypothesis 5f, Accountability
 
@@
 ```{r contrasts-hypothesis05f}
-# Pull the posterior draws for organizational practices
-draws <- draws_intercepts
+# Reference Level = No accountability
+# Compute the contrasts
 contrasts <- tibble(
-  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
-  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
+  "accountability - no accountability" = draws_intercept %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
 )
@@
 contrasts %>%
-  pivot_longer(accountability, names_to = "level", values_to = "Gamma") %>% 
+  pivot_longer("accountability - no accountability", names_to = "level", values_to = "Gamma") %>% 
   mutate(level = fct_rev(fct_inorder(level))) %>%
@@
 
-holding every other attribute constant
-
-Donors show a similar increase in willingness to donate to accountable NGOs in comparison to NGOs that are financially transparent.
-However, this is contrary to what was hypothesized--we predicted that donor's willingness to donate wouldn't be affected by accountability practices.
+Donors show a similar increase in willingness to donate to accountable NGOs in comparison to NGOs that are financially transparent, holding every other attribute constant.
 

### 2023-05-04 analysis/01_experimental-design.Rmd
Included an index-coded design and set of interaction terms

@@
 
-# Use dummy_cols() to get a index-coded version of all the attribute levels.
+# Use dummy_cols() to get a dummy-coded version of all the attribute levels
 dummy_design <- dummy_cols(
@@
 
-# Rename the index variables.
+# Rename the index variables
 colnames(dummy_design)[4:15] <- c(
@@
 
-# Interactions
+# Dummy-coded interactions
 
@@
 
-```{r interactions, warning=FALSE, message=FALSE}
+```{r dummy-interactions, warning=FALSE, message=FALSE}
 # Convert the attributes in design into factors
@@
 
-# Use dummy_cols() to get a dummy-coded version of all the attribute levels.
+# Use dummy_cols() to get a dummy-coded version of all the attribute levels
 interactions <- dummy_cols(
@@
 
-# Rename the dummy-coded variables.
+# Rename the dummy-coded variables
 colnames(interactions)[4:21] <- c(
@@
 
-# Build out all the necessary interactions.
+# Build out all the necessary interactions
 interactions <- interactions %>% 
@@
 # Save interact-coded design output
-write.csv(interactions, here("data", "derived_data", "interactions.csv"))
+write.csv(interactions, here("data", "derived_data", "dummy_interactions.csv"))
+```
+
+# Index-code the design
+
+Now we prepare the experimental design for use in estimating the model by keeping each level of each attribute, which are all discrete. An index-coded design has no reference levels.
+
+```{r index-design, warning=FALSE, message=FALSE}
+# Convert the attributes in design into factors
+index_design <- as.data.frame(design)
+for(i in 4:ncol(index_design)) {
+  index_design[,i] <- as.factor(index_design[,i])
+}
+
+# Rename the variables.
+colnames(index_design)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")
+
+# Use dummy_cols() to get an index-coded version of all the attribute levels
+index_design <- dummy_cols(
+  index_design,
+  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
+  remove_first_dummy = FALSE,
+  remove_selected_columns = TRUE
+)
+
+# Rename the index-coded variables
+colnames(index_design)[4:21] <- c(
+  str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
+  str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
+)
+
+# Save index-coded design output
+write.csv(index_design, here("data", "derived_data", "index_design.csv"))
+```
+
+# Index-coded interactions
+
+We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need to specific each of the needed interactions.
+
+```{r index-interactions, warning=FALSE, message=FALSE}
+# Convert the attributes in design into factors
+interactions <- as.data.frame(design)
+for(i in 4:ncol(interactions)) {
+  interactions[,i] <- as.factor(interactions[,i])
+}
+
+# Rename the variables
+colnames(interactions)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")
+
+# Use dummy_cols() to get an index-coded version of all the attribute levels
+interactions <- dummy_cols(
+  interactions, 
+  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
+  remove_first_dummy = FALSE,
+  remove_selected_columns = TRUE
+)
+
+# Rename the index-coded variables
+colnames(interactions)[4:21] <- c(
+  str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
+  str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
+)
+
+# Build out all the necessary interactions
+interactions <- interactions %>% 
+  as_tibble() %>% 
+  mutate(
+    # Hypothesis 2b.
+    amnesty_criticized = org1 * gov_rel2,
+    greenpeace_criticized = org2 * gov_rel2,
+    oxfam_criticized = org3 * gov_rel2,
+    redcross_criticized = org4 * gov_rel2,
+    amnesty_crackdown = org1 * gov_rel3,
+    greenpeace_crackdown = org2 * gov_rel3,
+    oxfam_crackdown = org3 * gov_rel3,
+    redcross_crackdown = org4 * gov_rel3,
+    # Hypothesis 3b.
+    emergency_criticized = issue1 * gov_rel2,
+    environment_criticized = issue2 * gov_rel2,
+    humanrights_criticized = issue3 * gov_rel2,
+    refugees_criticized = issue4 * gov_rel2,
+    emergency_crackdown = issue1 * gov_rel3,
+    environment_crackdown = issue2 * gov_rel3,
+    humanrights_crackdown = issue3 * gov_rel3,
+    refugees_crackdown = issue4 * gov_rel3,
+    # Hypothesis 4b.
+    smalldonors_criticized = fund1 * gov_rel2,
+    wealthydonors_criticized = fund2 * gov_rel2,
+    govgrants_criticized = fund3 * gov_rel2,
+    smalldonors_crackdown = fund1 * gov_rel3,
+    wealthydonors_crackdown = fund2 * gov_rel3,
+    govgrants_crackdown = fund3 * gov_rel3,
+    # Hypothesis 4c.
+    emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
+    emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3, # ??????
+    emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,     # ??????
+    environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
+    environment_wealthydonors_crackdown = issue2 * fund2 * gov_rel3,
+    environment_govgrants_crackdown = issue2 * fund3 * gov_rel3,
+    humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
+    humanrights_wealthydonors_crackdown = issue3 * fund2 * gov_rel3,
+    humanrights_govgrants_crackdown = issue3 * fund3 * gov_rel3,
+    refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
+    refugees_wealthydonors_crackdown = issue4 * fund2 * gov_rel3,
+    refugees_govgrants_crackdown = issue4 * fund3 * gov_rel3,
+    # Hypothesis 5b.
+    nottransp_criticized = transp1 * gov_rel2,
+    transp_criticized = transp2 * gov_rel2,
+    nottransp_crackdown = transp1 * gov_rel3,
+    transp_crackdown = transp2 * gov_rel3,
+    # Hypothesis 5c.
+    nottransp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
+    transp_smalldonors_criticized = transp2 * fund1 * gov_rel2,
+    nottransp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
+    transp_wealthydonors_criticized = transp2 * fund2 * gov_rel2,
+    nottransp_govgrants_criticized = transp1 * fund3 * gov_rel2,
+    transp_govgrants_criticized = transp2 * fund3 * gov_rel2,
+    nottransp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
+    transp_smalldonors_crackdown = transp2 * fund1 * gov_rel3,
+    nottransp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
+    transp_wealthydonors_crackdown = transp2 * fund2 * gov_rel3,
+    nottransp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
+    transp_govgrants_crackdown = transp2 * fund3 * gov_rel3,
+    # Hypothesis 5d.
+    nottransp_emergency_criticized = transp1 * issue1 * gov_rel2,
+    transp_emergency_criticized = transp2 * issue1 * gov_rel2,
+    nottransp_emergency_crackdown = transp1 * issue1 * gov_rel3,
+    transp_emergency_crackdown = transp2 * issue1 * gov_rel3,
+    nottransp_environment_criticized = transp1 * issue2 * gov_rel2,
+    transp_environment_criticized = transp2 * issue2 * gov_rel2,
+    nottransp_environment_crackdown = transp1 * issue2 * gov_rel3,
+    transp_environment_crackdown = transp2 * issue2 * gov_rel3,
+    nottransp_humanrights_criticized = transp1 * issue3 * gov_rel2,
+    transp_humanrights_criticized = transp2 * issue3 * gov_rel2,
+    nottransp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
+    transp_humanrights_crackdown = transp2 * issue3 * gov_rel3,
+    nottransp_refugees_criticized = transp1 * issue4 * gov_rel2,
+    transp_refugees_criticized = transp2 * issue4 * gov_rel2,
+    nottransp_refugees_crackdown = transp1 * issue4 * gov_rel3,
+    transp_refugees_crackdown = transp2 * issue4 * gov_rel3,
+    # Hypothesis 5e.
+    nottransp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
+    transp_smalldonors_emergency_criticized = transp2 * fund1 * issue1 * gov_rel2,
+    nottransp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
+    transp_smalldonors_emergency_crackdown = transp2 * fund1 * issue1 * gov_rel3,
+    nottransp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
+    transp_smalldonors_environment_criticized = transp2 * fund1 * issue2 * gov_rel2,
+    nottransp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
+    transp_smalldonors_environment_crackdown = transp2 * fund1 * issue2 * gov_rel3,
+    nottransp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
+    transp_smalldonors_humanrights_criticized = transp2 * fund1 * issue3 * gov_rel2,
+    nottransp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
+    transp_smalldonors_humanrights_crackdown = transp2 * fund1 * issue3 * gov_rel3,
+    nottransp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
+    transp_smalldonors_refugees_criticized = transp2 * fund1 * issue4 * gov_rel2,
+    nottransp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
+    transp_smalldonors_refugees_crackdown = transp2 * fund1 * issue4 * gov_rel3
+  )
+
+# Save interact-coded design output
+write.csv(interactions, here("data", "derived_data", "index_interactions.csv"))
 ```

### 2023-05-04 analysis/02_clean-data.Rmd
Cleaned/transformed an index-coded design and set of interaction terms

@@
 library(tidyverse)
-library(donorheuristics)
 library(here)
@@
 
+Select a dummy or index-coded version of the design.
+
 ```{r transform-design}
+dummy_coded <- 0 # Dummy-coded design and associated interactions.
+index_coded <- 1 # Index-coded design and associated interactions.
+
+if (dummy_coded == 1) {
   # Load the dummy design.
@@
 
-# Load the interactions and join to the design.
-interactions_design <- read_csv(here::here("data", "derived_data", "interactions.csv")) %>%
+  # Load the dummy interactions and join to the design.
+  dummy_interactions_design <- read_csv(here::here("data", "derived_data", "dummy_interactions.csv")) %>%
     select(-`...1`) %>%
@@
   # Create the arrays for a design with a brand intercept and interactions.
-interactions_X <- array(
+  dummy_interactions_X <- array(
     data = NA,
@@
       nrow(data),                                # Number of respondents.
-    max(interactions_design$task),       # Number of choice tasks per respondent.
-    (max(interactions_design$alt) + 1),  # Number of product alternatives per choice task.
-    (ncol(interactions_design) - 3 + 1)  # Number of (estimable) attribute levels.
+      max(dummy_interactions_design$task),       # Number of choice tasks per respondent.
+      (max(dummy_interactions_design$alt) + 1),  # Number of product alternatives per choice task.
+      (ncol(dummy_interactions_design) - 3 + 1)  # Number of (estimable) attribute levels.
     )
@@
     dummy_X_n <- dummy_design %>% filter(version == data$version[n])
-  interactions_X_n <- interactions_design %>% filter(version == data$version[n])
+    interactions_X_n <- dummy_interactions_design %>% filter(version == data$version[n])
     for (s in 1:dim(dummy_X)[2]) {
@@
         mutate(org1 = 0) %>%
-      select(org1, org2:transp_smalldonors_refugees_crackdown)
+        select(org1, org2:transp_smalldonors_refugees_crackdown) # NOTE DIMENSIONS OF INTERACTIONS HARD-CODED.
       for (p in 1:(dim(dummy_X)[3]-1)) {
@@
       dummy_X[n, s,,] <- rbind(dummy_X_s, rep(0, ncol(dummy_X_s))) %>% as.matrix()
-    interactions_X[n, s,,] <- rbind(interactions_X_s, rep(0, ncol(interactions_X_s))) %>% as.matrix()
+      dummy_interactions_X[n, s,,] <- rbind(interactions_X_s, rep(0, ncol(interactions_X_s))) %>% as.matrix()
+    }
+  }
+}
+if (index_coded == 1) {
+  # Load the index-coded design.
+  index_design <- read_csv(here::here("data", "derived_data", "index_design.csv")) %>%
+    select(-`...1`) %>%
+    rename(
+      version = question_set,
+      task = question,
+      alt = choice
+    )
+
+  # Create the arrays for the design, including a brand intercept.
+  index_X <- array(
+    data = NA,
+    dim = c(
+      nrow(data),                   # Number of respondents.
+      max(index_design$task),       # Number of choice tasks per respondent.
+      (max(index_design$alt) + 1),  # Number of product alternatives per choice task.
+      (ncol(index_design) - 3)      # Number of (estimable) attribute levels.
+    )
+  )
+
+  # Load the index-coded interactions and join to the design.
+  index_interactions_design <- read_csv(here::here("data", "derived_data", "index_interactions.csv")) %>%
+    select(-`...1`) %>%
+    rename(
+      version = question_set,
+      task = question,
+      alt = choice
+    )
+
+  # Create the arrays for a design, including a brand intercept and interactions.
+  index_interactions_X <- array(
+    data = NA,
+    dim = c(
+      nrow(data),                                # Number of respondents.
+      max(index_interactions_design$task),       # Number of choice tasks per respondent.
+      (max(index_interactions_design$alt) + 1),  # Number of product alternatives per choice task.
+      (ncol(index_interactions_design) - 3)      # Number of (estimable) attribute levels.
+    )
+  )
+
+  # Add the outside option coded as all zeros (org1 and former reference levels already included).
+  for (n in 1:dim(index_X)[1]) {
+    # Filter for respondent n.
+    index_X_n <- index_design %>% filter(version == data$version[n])
+    interactions_X_n <- index_interactions_design %>% filter(version == data$version[n])
+    for (s in 1:dim(index_X)[2]) {
+      # Filter for task s.
+      index_X_s <- index_X_n %>%
+        filter(task == s) %>%
+        select(org1:gov_rel3)
+      interactions_X_s <- interactions_X_n %>%
+        filter(task == s) %>%
+        select(org1:transp_smalldonors_refugees_crackdown) # NOTE DIMENSIONS OF INTERACTIONS HARD-CODED.
+      # Save modified design, including outside option.
+      index_X[n, s,,] <- rbind(index_X_s, rep(0, ncol(index_X_s))) %>% as.matrix()
+      index_interactions_X[n, s,,] <- rbind(interactions_X_s, rep(0, ncol(interactions_X_s))) %>% as.matrix()
+    }
   }
@@
 write_rds(data, here("data", "derived_data", "final_data.rds"))
+if (dummy_coded == 1) {
   write_rds(dummy_X, here("data", "derived_data", "final_design.rds"))
-write_rds(interactions_X, here("data", "derived_data", "final_interactions.rds"))
+  write_rds(dummy_interactions_X, here("data", "derived_data", "final_interactions.rds"))
+}
+if (index_coded == 1) {
+  write_rds(index_X, here("data", "derived_data", "final_design.rds"))
+  write_rds(index_interactions_X, here("data", "derived_data", "final_interactions.rds"))
+}
 ```

### 2023-05-04 analysis/03_analysis.Rmd
Setup an index-coded, intercept-only model

@@
 ```{r model-calibration, eval=FALSE}
-intercept <- 0                            # Intercept-only
+intercept <- 1                            # Intercept-only
 interactions <- 0                         # Include interactions with the intercept-only model
-public_affairs <- 1                       # Public affairs
+public_affairs <- 0                       # Public affairs
 political_ideology <- 0                   # Political ideology
@@
 
-# Replace factor labels with levels
-Z <- Z %>%
-  mutate_if(is.factor, as.integer) %>%
-  mutate_if(is.integer, as.factor)
-
-# Pad the variables names with _
-colnames(Z) <- str_c(colnames(Z), "_")
-
-# Use the output of lm to get a dummy-coded version of the covariate matrix Z
-Z$y <- matrix(rnorm(nrow(Z)), ncol = 1)
-out <- lm(y ~ ., Z, x = TRUE)
-
-# Save out Z as a matrix, including an intercept
-Z <- tibble(intercept = rep(1, dim(X)[1])) %>%
-  bind_cols(as_tibble(out$x[,-1])) %>%
-  as.matrix()
-
 if (intercept == 0) {
@@
 run <- list(data = data, fit = fit)
-if (intercept == 1 & interactions == 0) write_rds(run, here::here("data", "raw_data", "model_runs", "intercept.rds"))
+# if (intercept == 1 & interactions == 0) write_rds(run, here::here("data", "raw_data", "model_runs", "intercept.rds"))
+if (intercept == 1 & interactions == 0) write_rds(run, here::here("data", "raw_data", "model_runs", "index_intercept.rds"))
 if (intercept == 1 & interactions == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "interactions_5e.rds"))

### 2023-05-08 analysis/01_experimental-design.Rmd
Confirming working with index-coded variables

@@
   mutate(
-    # Hypothesis 2b.
-    amnesty_criticized = org1 * gov_rel2,
-    greenpeace_criticized = org2 * gov_rel2,
-    oxfam_criticized = org3 * gov_rel2,
-    redcross_criticized = org4 * gov_rel2,
-    amnesty_crackdown = org1 * gov_rel3,
-    greenpeace_crackdown = org2 * gov_rel3,
-    oxfam_crackdown = org3 * gov_rel3,
-    redcross_crackdown = org4 * gov_rel3,
+    # # Hypothesis 2b.
+    # amnesty_criticized = org1 * gov_rel2,
+    # greenpeace_criticized = org2 * gov_rel2,
+    # oxfam_criticized = org3 * gov_rel2,
+    # redcross_criticized = org4 * gov_rel2,
+    # amnesty_crackdown = org1 * gov_rel3,
+    # greenpeace_crackdown = org2 * gov_rel3,
+    # oxfam_crackdown = org3 * gov_rel3,
+    # redcross_crackdown = org4 * gov_rel3,
     # Hypothesis 3b.
@@
     humanrights_crackdown = issue3 * gov_rel3,
-    refugees_crackdown = issue4 * gov_rel3,
-    # Hypothesis 4b.
-    smalldonors_criticized = fund1 * gov_rel2,
-    wealthydonors_criticized = fund2 * gov_rel2,
-    govgrants_criticized = fund3 * gov_rel2,
-    smalldonors_crackdown = fund1 * gov_rel3,
-    wealthydonors_crackdown = fund2 * gov_rel3,
-    govgrants_crackdown = fund3 * gov_rel3,
-    # Hypothesis 4c.
-    emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
-    emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3, # ??????
-    emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,     # ??????
-    environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
-    environment_wealthydonors_crackdown = issue2 * fund2 * gov_rel3,
-    environment_govgrants_crackdown = issue2 * fund3 * gov_rel3,
-    humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
-    humanrights_wealthydonors_crackdown = issue3 * fund2 * gov_rel3,
-    humanrights_govgrants_crackdown = issue3 * fund3 * gov_rel3,
-    refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
-    refugees_wealthydonors_crackdown = issue4 * fund2 * gov_rel3,
-    refugees_govgrants_crackdown = issue4 * fund3 * gov_rel3,
-    # Hypothesis 5b.
-    nottransp_criticized = transp1 * gov_rel2,
-    transp_criticized = transp2 * gov_rel2,
-    nottransp_crackdown = transp1 * gov_rel3,
-    transp_crackdown = transp2 * gov_rel3,
-    # Hypothesis 5c.
-    nottransp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
-    transp_smalldonors_criticized = transp2 * fund1 * gov_rel2,
-    nottransp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
-    transp_wealthydonors_criticized = transp2 * fund2 * gov_rel2,
-    nottransp_govgrants_criticized = transp1 * fund3 * gov_rel2,
-    transp_govgrants_criticized = transp2 * fund3 * gov_rel2,
-    nottransp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
-    transp_smalldonors_crackdown = transp2 * fund1 * gov_rel3,
-    nottransp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
-    transp_wealthydonors_crackdown = transp2 * fund2 * gov_rel3,
-    nottransp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
-    transp_govgrants_crackdown = transp2 * fund3 * gov_rel3,
-    # Hypothesis 5d.
-    nottransp_emergency_criticized = transp1 * issue1 * gov_rel2,
-    transp_emergency_criticized = transp2 * issue1 * gov_rel2,
-    nottransp_emergency_crackdown = transp1 * issue1 * gov_rel3,
-    transp_emergency_crackdown = transp2 * issue1 * gov_rel3,
-    nottransp_environment_criticized = transp1 * issue2 * gov_rel2,
-    transp_environment_criticized = transp2 * issue2 * gov_rel2,
-    nottransp_environment_crackdown = transp1 * issue2 * gov_rel3,
-    transp_environment_crackdown = transp2 * issue2 * gov_rel3,
-    nottransp_humanrights_criticized = transp1 * issue3 * gov_rel2,
-    transp_humanrights_criticized = transp2 * issue3 * gov_rel2,
-    nottransp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
-    transp_humanrights_crackdown = transp2 * issue3 * gov_rel3,
-    nottransp_refugees_criticized = transp1 * issue4 * gov_rel2,
-    transp_refugees_criticized = transp2 * issue4 * gov_rel2,
-    nottransp_refugees_crackdown = transp1 * issue4 * gov_rel3,
-    transp_refugees_crackdown = transp2 * issue4 * gov_rel3,
-    # Hypothesis 5e.
-    nottransp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
-    transp_smalldonors_emergency_criticized = transp2 * fund1 * issue1 * gov_rel2,
-    nottransp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
-    transp_smalldonors_emergency_crackdown = transp2 * fund1 * issue1 * gov_rel3,
-    nottransp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
-    transp_smalldonors_environment_criticized = transp2 * fund1 * issue2 * gov_rel2,
-    nottransp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
-    transp_smalldonors_environment_crackdown = transp2 * fund1 * issue2 * gov_rel3,
-    nottransp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
-    transp_smalldonors_humanrights_criticized = transp2 * fund1 * issue3 * gov_rel2,
-    nottransp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
-    transp_smalldonors_humanrights_crackdown = transp2 * fund1 * issue3 * gov_rel3,
-    nottransp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
-    transp_smalldonors_refugees_criticized = transp2 * fund1 * issue4 * gov_rel2,
-    nottransp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
-    transp_smalldonors_refugees_crackdown = transp2 * fund1 * issue4 * gov_rel3
+    refugees_crackdown = issue4 * gov_rel3
+    # # Hypothesis 4b.
+    # smalldonors_criticized = fund1 * gov_rel2,
+    # wealthydonors_criticized = fund2 * gov_rel2,
+    # govgrants_criticized = fund3 * gov_rel2,
+    # smalldonors_crackdown = fund1 * gov_rel3,
+    # wealthydonors_crackdown = fund2 * gov_rel3,
+    # govgrants_crackdown = fund3 * gov_rel3,
+    # # Hypothesis 4c.
+    # emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
+    # emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3, # ??????
+    # emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,     # ??????
+    # environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
+    # environment_wealthydonors_crackdown = issue2 * fund2 * gov_rel3,
+    # environment_govgrants_crackdown = issue2 * fund3 * gov_rel3,
+    # humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
+    # humanrights_wealthydonors_crackdown = issue3 * fund2 * gov_rel3,
+    # humanrights_govgrants_crackdown = issue3 * fund3 * gov_rel3,
+    # refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
+    # refugees_wealthydonors_crackdown = issue4 * fund2 * gov_rel3,
+    # refugees_govgrants_crackdown = issue4 * fund3 * gov_rel3,
+    # # Hypothesis 5b.
+    # nottransp_criticized = transp1 * gov_rel2,
+    # transp_criticized = transp2 * gov_rel2,
+    # nottransp_crackdown = transp1 * gov_rel3,
+    # transp_crackdown = transp2 * gov_rel3,
+    # # Hypothesis 5c.
+    # nottransp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
+    # transp_smalldonors_criticized = transp2 * fund1 * gov_rel2,
+    # nottransp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
+    # transp_wealthydonors_criticized = transp2 * fund2 * gov_rel2,
+    # nottransp_govgrants_criticized = transp1 * fund3 * gov_rel2,
+    # transp_govgrants_criticized = transp2 * fund3 * gov_rel2,
+    # nottransp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
+    # transp_smalldonors_crackdown = transp2 * fund1 * gov_rel3,
+    # nottransp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
+    # transp_wealthydonors_crackdown = transp2 * fund2 * gov_rel3,
+    # nottransp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
+    # transp_govgrants_crackdown = transp2 * fund3 * gov_rel3,
+    # # Hypothesis 5d.
+    # nottransp_emergency_criticized = transp1 * issue1 * gov_rel2,
+    # transp_emergency_criticized = transp2 * issue1 * gov_rel2,
+    # nottransp_emergency_crackdown = transp1 * issue1 * gov_rel3,
+    # transp_emergency_crackdown = transp2 * issue1 * gov_rel3,
+    # nottransp_environment_criticized = transp1 * issue2 * gov_rel2,
+    # transp_environment_criticized = transp2 * issue2 * gov_rel2,
+    # nottransp_environment_crackdown = transp1 * issue2 * gov_rel3,
+    # transp_environment_crackdown = transp2 * issue2 * gov_rel3,
+    # nottransp_humanrights_criticized = transp1 * issue3 * gov_rel2,
+    # transp_humanrights_criticized = transp2 * issue3 * gov_rel2,
+    # nottransp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
+    # transp_humanrights_crackdown = transp2 * issue3 * gov_rel3,
+    # nottransp_refugees_criticized = transp1 * issue4 * gov_rel2,
+    # transp_refugees_criticized = transp2 * issue4 * gov_rel2,
+    # nottransp_refugees_crackdown = transp1 * issue4 * gov_rel3,
+    # transp_refugees_crackdown = transp2 * issue4 * gov_rel3,
+    # # Hypothesis 5e.
+    # nottransp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
+    # transp_smalldonors_emergency_criticized = transp2 * fund1 * issue1 * gov_rel2,
+    # nottransp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
+    # transp_smalldonors_emergency_crackdown = transp2 * fund1 * issue1 * gov_rel3,
+    # nottransp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
+    # transp_smalldonors_environment_criticized = transp2 * fund1 * issue2 * gov_rel2,
+    # nottransp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
+    # transp_smalldonors_environment_crackdown = transp2 * fund1 * issue2 * gov_rel3,
+    # nottransp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
+    # transp_smalldonors_humanrights_criticized = transp2 * fund1 * issue3 * gov_rel2,
+    # nottransp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
+    # transp_smalldonors_humanrights_crackdown = transp2 * fund1 * issue3 * gov_rel3,
+    # nottransp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
+    # transp_smalldonors_refugees_criticized = transp2 * fund1 * issue4 * gov_rel2,
+    # nottransp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
+    # transp_smalldonors_refugees_crackdown = transp2 * fund1 * issue4 * gov_rel3
   )

### 2023-05-08 analysis/02_clean-data.Rmd
Confirming working with index-coded variables

@@
         mutate(org1 = 0) %>%
-        select(org1, org2:transp_smalldonors_refugees_crackdown) # NOTE DIMENSIONS OF INTERACTIONS HARD-CODED.
+        # select(org1, org2:transp_smalldonors_refugees_crackdown) # HARD-CODED
+        select(org1, which(names(interactions_X_n) == "org2"):ncol(interactions_X_n))
       for (p in 1:(dim(dummy_X)[3]-1)) {
@@
         filter(task == s) %>%
-        select(org1:transp_smalldonors_refugees_crackdown) # NOTE DIMENSIONS OF INTERACTIONS HARD-CODED.
+        # select(org1:transp_smalldonors_refugees_crackdown) # HARD-CODED
+        select(which(names(interactions_X_n) == "org1"):ncol(interactions_X_n))
       # Save modified design, including outside option.

### 2023-05-08 analysis/01_experimental-design.Rmd
Set-up for aggregate-coded interaction terms

@@
 
+# Aggregate-coded interactions
+
+We have a number of hypotheses referencing specific interactions.
+To answer these hypotheses, we need to specific each of the needed interactions.
+Here we do it by aggregating up the interaction terms.
+
+```{r aggregate-interactions, warning=FALSE, message=FALSE}
+# Convert the attributes in design into factors
+interactions <- as.data.frame(design)
+for(i in 4:ncol(interactions)) {
+  interactions[,i] <- as.factor(interactions[,i])
+}
+
+# Rename the variables
+colnames(interactions)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")
+
+# Use dummy_cols() to get an index-coded version of all the attribute levels
+interactions <- dummy_cols(
+  interactions, 
+  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
+  remove_first_dummy = FALSE,
+  remove_selected_columns = TRUE
+)
+
+# Rename the index-coded variables
+colnames(interactions)[4:21] <- c(
+  str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
+  str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
+)
+
+# Build out all the necessary interactions...
+# ...by multiplying together the needed index-coded levels.
+
+# Build out all the necessary interactions
+interactions <- interactions %>% 
+  as_tibble() %>% 
+  mutate(
+    # Hypothesis 2b.
+    amnesty_criticized = org1 * gov_rel2,
+    greenpeace_criticized = org2 * gov_rel2,
+    oxfam_criticized = org3 * gov_rel2,
+    redcross_criticized = org4 * gov_rel2,
+    amnesty_crackdown = org1 * gov_rel3,
+    greenpeace_crackdown = org2 * gov_rel3,
+    oxfam_crackdown = org3 * gov_rel3,
+    redcross_crackdown = org4 * gov_rel3,
+    # Hypothesis 3b.
+    emergency_criticized = issue1 * gov_rel2,
+    environment_criticized = issue2 * gov_rel2,
+    humanrights_criticized = issue3 * gov_rel2,
+    refugees_criticized = issue4 * gov_rel2,
+    emergency_crackdown = issue1 * gov_rel3,
+    environment_crackdown = issue2 * gov_rel3,
+    humanrights_crackdown = issue3 * gov_rel3,
+    refugees_crackdown = issue4 * gov_rel3,
+    # Hypothesis 4b.
+    smalldonors_criticized = fund1 * gov_rel2,
+    wealthydonors_criticized = fund2 * gov_rel2,
+    govgrants_criticized = fund3 * gov_rel2,
+    smalldonors_crackdown = fund1 * gov_rel3,
+    wealthydonors_crackdown = fund2 * gov_rel3,
+    govgrants_crackdown = fund3 * gov_rel3,
+    # Hypothesis 4c.
+    emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
+    emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3, # ??????
+    emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,     # ??????
+    environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
+    environment_wealthydonors_crackdown = issue2 * fund2 * gov_rel3,
+    environment_govgrants_crackdown = issue2 * fund3 * gov_rel3,
+    humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
+    humanrights_wealthydonors_crackdown = issue3 * fund2 * gov_rel3,
+    humanrights_govgrants_crackdown = issue3 * fund3 * gov_rel3,
+    refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
+    refugees_wealthydonors_crackdown = issue4 * fund2 * gov_rel3,
+    refugees_govgrants_crackdown = issue4 * fund3 * gov_rel3,
+    # Hypothesis 5b.
+    nottransp_criticized = transp1 * gov_rel2,
+    transp_criticized = transp2 * gov_rel2,
+    nottransp_crackdown = transp1 * gov_rel3,
+    transp_crackdown = transp2 * gov_rel3,
+    # Hypothesis 5c.
+    nottransp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
+    transp_smalldonors_criticized = transp2 * fund1 * gov_rel2,
+    nottransp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
+    transp_wealthydonors_criticized = transp2 * fund2 * gov_rel2,
+    nottransp_govgrants_criticized = transp1 * fund3 * gov_rel2,
+    transp_govgrants_criticized = transp2 * fund3 * gov_rel2,
+    nottransp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
+    transp_smalldonors_crackdown = transp2 * fund1 * gov_rel3,
+    nottransp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
+    transp_wealthydonors_crackdown = transp2 * fund2 * gov_rel3,
+    nottransp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
+    transp_govgrants_crackdown = transp2 * fund3 * gov_rel3,
+    # Hypothesis 5d.
+    nottransp_emergency_criticized = transp1 * issue1 * gov_rel2,
+    transp_emergency_criticized = transp2 * issue1 * gov_rel2,
+    nottransp_emergency_crackdown = transp1 * issue1 * gov_rel3,
+    transp_emergency_crackdown = transp2 * issue1 * gov_rel3,
+    nottransp_environment_criticized = transp1 * issue2 * gov_rel2,
+    transp_environment_criticized = transp2 * issue2 * gov_rel2,
+    nottransp_environment_crackdown = transp1 * issue2 * gov_rel3,
+    transp_environment_crackdown = transp2 * issue2 * gov_rel3,
+    nottransp_humanrights_criticized = transp1 * issue3 * gov_rel2,
+    transp_humanrights_criticized = transp2 * issue3 * gov_rel2,
+    nottransp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
+    transp_humanrights_crackdown = transp2 * issue3 * gov_rel3,
+    nottransp_refugees_criticized = transp1 * issue4 * gov_rel2,
+    transp_refugees_criticized = transp2 * issue4 * gov_rel2,
+    nottransp_refugees_crackdown = transp1 * issue4 * gov_rel3,
+    transp_refugees_crackdown = transp2 * issue4 * gov_rel3,
+    # Hypothesis 5e.
+    nottransp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
+    transp_smalldonors_emergency_criticized = transp2 * fund1 * issue1 * gov_rel2,
+    nottransp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
+    transp_smalldonors_emergency_crackdown = transp2 * fund1 * issue1 * gov_rel3,
+    nottransp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
+    transp_smalldonors_environment_criticized = transp2 * fund1 * issue2 * gov_rel2,
+    nottransp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
+    transp_smalldonors_environment_crackdown = transp2 * fund1 * issue2 * gov_rel3,
+    nottransp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
+    transp_smalldonors_humanrights_criticized = transp2 * fund1 * issue3 * gov_rel2,
+    nottransp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
+    transp_smalldonors_humanrights_crackdown = transp2 * fund1 * issue3 * gov_rel3,
+    nottransp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
+    transp_smalldonors_refugees_criticized = transp2 * fund1 * issue4 * gov_rel2,
+    nottransp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
+    transp_smalldonors_refugees_crackdown = transp2 * fund1 * issue4 * gov_rel3
+  )
+
+# Save interact-coded design output
+write.csv(interactions, here("data", "derived_data", "aggregate_interactions.csv"))
+```
+
 # Original computing environment

### 2023-05-08 analysis/01_experimental-design.Rmd
aggregated-coded variables

--- 2023-05-08 analysis/01_experimental-design.Rmd
@@
 
+# Aggregate-coded interactions
+
+We have a number of hypotheses referencing specific interactions.
+To answer these hypotheses, we need to specific each of the needed interactions.
+Here we do it by aggregating up the interaction terms.
+
+```{r aggregate-interactions, warning=FALSE, message=FALSE}
+# Convert the attributes in design into factors
+interactions <- as.data.frame(design)
+for(i in 4:ncol(interactions)) {
+  interactions[,i] <- as.factor(interactions[,i])
+}
+
+# # Rename the variables
+# colnames(interactions)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")
+# 
+# # Use dummy_cols() to get an index-coded version of all the attribute levels
+# interactions <- dummy_cols(
+#   interactions, 
+#   select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
+#   remove_first_dummy = FALSE,
+#   remove_selected_columns = TRUE
+# )
+# 
+# # Rename the index-coded variables
+# colnames(interactions)[4:21] <- c(
+#   str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
+#   str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
+# )
+#
+# org1 = amnesty
+# org2 = greenpeace
+# org3 = oxfam
+# org4 = redcross
+# gov_rel1 = friendly
+# gov_rel2 = criticized
+# gov_rel3 = crackdown
+
+# Build out all the necessary interactions...
+# ...by multiplying together the needed index-coded levels.
+interactions <- interactions %>% 
+  as_tibble() %>% 
+  mutate(
+    h2b_1 = ifelse(Organization ==3|Organization==4, 1, 0), # 1 if org is oxfam or redcross
+    h2b_2 = ifelse(`Relationship with host government` == 2|`Relationship with host government` == 3, 1, 0), # 1 if gov_rel is criticized or crackdown
+    h2b_3 = h2b_1*h2b_2 # interaction term
+    )
+
+# Build out all the necessary interactions
+# interactions <- interactions %>% 
+#   as_tibble() %>% 
+#   mutate(
+#     # Hypothesis 2b.
+#     amnesty_criticized = org1 * gov_rel2,
+#     greenpeace_criticized = org2 * gov_rel2,
+#     oxfam_criticized = org3 * gov_rel2,
+#     redcross_criticized = org4 * gov_rel2,
+#     amnesty_crackdown = org1 * gov_rel3,
+#     greenpeace_crackdown = org2 * gov_rel3,
+#     oxfam_crackdown = org3 * gov_rel3,
+#     redcross_crackdown = org4 * gov_rel3,
+#     # Hypothesis 3b.
+#     emergency_criticized = issue1 * gov_rel2,
+#     environment_criticized = issue2 * gov_rel2,
+#     humanrights_criticized = issue3 * gov_rel2,
+#     refugees_criticized = issue4 * gov_rel2,
+#     emergency_crackdown = issue1 * gov_rel3,
+#     environment_crackdown = issue2 * gov_rel3,
+#     humanrights_crackdown = issue3 * gov_rel3,
+#     refugees_crackdown = issue4 * gov_rel3,
+#     # Hypothesis 4b.
+#     smalldonors_criticized = fund1 * gov_rel2,
+#     wealthydonors_criticized = fund2 * gov_rel2,
+#     govgrants_criticized = fund3 * gov_rel2,
+#     smalldonors_crackdown = fund1 * gov_rel3,
+#     wealthydonors_crackdown = fund2 * gov_rel3,
+#     govgrants_crackdown = fund3 * gov_rel3,
+#     # Hypothesis 4c.
+#     emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
+#     emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3, # ??????
+#     emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,     # ??????
+#     environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
+#     environment_wealthydonors_crackdown = issue2 * fund2 * gov_rel3,
+#     environment_govgrants_crackdown = issue2 * fund3 * gov_rel3,
+#     humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
+#     humanrights_wealthydonors_crackdown = issue3 * fund2 * gov_rel3,
+#     humanrights_govgrants_crackdown = issue3 * fund3 * gov_rel3,
+#     refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
+#     refugees_wealthydonors_crackdown = issue4 * fund2 * gov_rel3,
+#     refugees_govgrants_crackdown = issue4 * fund3 * gov_rel3,
+#     # Hypothesis 5b.
+#     nottransp_criticized = transp1 * gov_rel2,
+#     transp_criticized = transp2 * gov_rel2,
+#     nottransp_crackdown = transp1 * gov_rel3,
+#     transp_crackdown = transp2 * gov_rel3,
+#     # Hypothesis 5c.
+#     nottransp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
+#     transp_smalldonors_criticized = transp2 * fund1 * gov_rel2,
+#     nottransp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
+#     transp_wealthydonors_criticized = transp2 * fund2 * gov_rel2,
+#     nottransp_govgrants_criticized = transp1 * fund3 * gov_rel2,
+#     transp_govgrants_criticized = transp2 * fund3 * gov_rel2,
+#     nottransp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
+#     transp_smalldonors_crackdown = transp2 * fund1 * gov_rel3,
+#     nottransp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
+#     transp_wealthydonors_crackdown = transp2 * fund2 * gov_rel3,
+#     nottransp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
+#     transp_govgrants_crackdown = transp2 * fund3 * gov_rel3,
+#     # Hypothesis 5d.
+#     nottransp_emergency_criticized = transp1 * issue1 * gov_rel2,
+#     transp_emergency_criticized = transp2 * issue1 * gov_rel2,
+#     nottransp_emergency_crackdown = transp1 * issue1 * gov_rel3,
+#     transp_emergency_crackdown = transp2 * issue1 * gov_rel3,
+#     nottransp_environment_criticized = transp1 * issue2 * gov_rel2,
+#     transp_environment_criticized = transp2 * issue2 * gov_rel2,
+#     nottransp_environment_crackdown = transp1 * issue2 * gov_rel3,
+#     transp_environment_crackdown = transp2 * issue2 * gov_rel3,
+#     nottransp_humanrights_criticized = transp1 * issue3 * gov_rel2,
+#     transp_humanrights_criticized = transp2 * issue3 * gov_rel2,
+#     nottransp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
+#     transp_humanrights_crackdown = transp2 * issue3 * gov_rel3,
+#     nottransp_refugees_criticized = transp1 * issue4 * gov_rel2,
+#     transp_refugees_criticized = transp2 * issue4 * gov_rel2,
+#     nottransp_refugees_crackdown = transp1 * issue4 * gov_rel3,
+#     transp_refugees_crackdown = transp2 * issue4 * gov_rel3,
+#     # Hypothesis 5e.
+#     nottransp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
+#     transp_smalldonors_emergency_criticized = transp2 * fund1 * issue1 * gov_rel2,
+#     nottransp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
+#     transp_smalldonors_emergency_crackdown = transp2 * fund1 * issue1 * gov_rel3,
+#     nottransp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
+#     transp_smalldonors_environment_criticized = transp2 * fund1 * issue2 * gov_rel2,
+#     nottransp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
+#     transp_smalldonors_environment_crackdown = transp2 * fund1 * issue2 * gov_rel3,
+#     nottransp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
+#     transp_smalldonors_humanrights_criticized = transp2 * fund1 * issue3 * gov_rel2,
+#     nottransp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
+#     transp_smalldonors_humanrights_crackdown = transp2 * fund1 * issue3 * gov_rel3,
+#     nottransp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
+#     transp_smalldonors_refugees_criticized = transp2 * fund1 * issue4 * gov_rel2,
+#     nottransp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
+#     transp_smalldonors_refugees_crackdown = transp2 * fund1 * issue4 * gov_rel3
+#   )
+
+# Save interact-coded design output
+write.csv(interactions, here("data", "derived_data", "aggregate_interactions.csv"))
+```
+
 # Original computing environment

### 2023-05-10 analysis/mnl-model-calibration.R
Set-up for non-hierarchical MNL experiment for interaction-based hypotheses contrasts

@@ -1,0 +1,165 @@
+# Preamble ----------------------------------------------------------------
+# Load packages
+library(tidyverse)
+library(rstan)
+
+# Set Stan options
+options(mc.cores = parallel::detectCores())
+rstan_options(auto_write = TRUE)
+
+# Choose the Model to Run -------------------------------------------------
+intercept <- 0                            # Intercept-only
+public_affairs <- 0                       # Public affairs: Public affairs knowledge + Public affairs activity
+political_ideology <- 0                   # Political ideology
+social_views <- 0                         # Social views: Public affairs trust + Social ideology + Religiosity
+charity_voluntarism <- 1                  # Charity and voluntarism: Charity trust, Charity activity, Volunteer activity, etc
+demographics <- 0                         # Demographics: Gender, Marital status, Education, Income, Race, Age
+public_political <- 0                     # Public affairs + Political ideology
+public_political_social <- 0              # Public affairs + Political ideology + Social views
+public_political_social_charity <- 0      # Public affairs + Political ideology + Social views + Charity and voluntarism
+public_political_social_charity_demo <- 0 # Public affairs + Political ideology + Social views + Charity and voluntarism + Demographics
+
+# Import and Restructure Data ---------------------------------------------
+# Load data and design
+final_data <- read_rds(here::here("data", "derived_data", "final_data.rds"))
+X <- read_rds(here::here("data", "derived_data", "final_design.rds"))
+
+# Restructure choice data Y
+Y <- final_data %>%
+  select(contains("Q4")) %>%
+  as.matrix()
+
+# Restructure covariate matrix Z
+if (intercept == 1) {
+  Z <- matrix(data = 1, nrow = dim(X)[1], ncol = 1)
+}
+if (public_affairs == 1) {
+  Z <- final_data %>%
+    select(
+      Q2.1, Q2.2, Q2.3_1:Q2.3_7, Q2.4, Q5.7 # Public affairs
+    )
+}
+if (political_ideology == 1) {
+  Z <- final_data %>%
+    select(
+      Q5.2 # Political ideology
+    )
+}
+if (social_views == 1) {
+  Z <- final_data %>%
+    select(
[…]

### 2023-05-11 analysis/mnl-model-calibration.R
MNL model calibration and data prep for dummy-coded interactions

@@ -8,11 +8,11 @@ options(mc.cores = parallel::detectCores())
 rstan_options(auto_write = TRUE)
 
 # Choose the Model to Run -------------------------------------------------
-intercept <- 0                            # Intercept-only
+intercept <- 1                            # Intercept-only
 public_affairs <- 0                       # Public affairs: Public affairs knowledge + Public affairs activity
 political_ideology <- 0                   # Political ideology
 social_views <- 0                         # Social views: Public affairs trust + Social ideology + Religiosity
-charity_voluntarism <- 1                  # Charity and voluntarism: Charity trust, Charity activity, Volunteer activity, etc
+charity_voluntarism <- 0                  # Charity and voluntarism: Charity trust, Charity activity, Volunteer activity, etc
 demographics <- 0                         # Demographics: Gender, Marital status, Education, Income, Race, Age
 public_political <- 0                     # Public affairs + Political ideology
 public_political_social <- 0              # Public affairs + Political ideology + Social views
@@ -21,129 +21,131 @@ public_political_social_charity_demo <- 0 # Public affairs + Political ideology 
 
 # Import and Restructure Data ---------------------------------------------
 # Load data and design
-final_data <- read_rds(here::here("data", "derived_data", "final_data.rds"))
-X <- read_rds(here::here("data", "derived_data", "final_design.rds"))
+# final_data <- read_rds(here::here("data", "derived_data", "final_data.rds"))
+# X <- read_rds(here::here("data", "derived_data", "final_design.rds"))
+# #
+# # Restructure choice data Y
+# Y <- final_data %>%
+#   select(contains("Q4")) %>%
+#   as.matrix()
+#
+# # Restructure covariate matrix Z
+# if (intercept == 1) {
+#   Z <- matrix(data = 1, nrow = dim(X)[1], ncol = 1)
+# }
+# if (public_affairs == 1) {
+#   Z <- final_data %>%
+#     select(
[…]

### 2023-05-11 analysis/mnl_data_prep.R

@@ -1,0 +1,799 @@
+library(tidyverse)
+library(fastDummies)
+library(here)
+
+# Start here for all MNL models
+
+
+# Experimental Design -----------------------------------------------------
+
+# Load design
+
+# Clean Data --------------------------------------------------------------
+
+# Start here for all MNL models
+
+library(tidyverse)
+library(here)
+
+data <- read_csv(
+  here::here("data", "raw_data", "conjointqsf_final.csv"),
+  guess_max = 1500
+)
+
+# Skipping a lot of the code to check the data
+
+data_clean <- data %>%
+  filter(V10 == 1) %>%         # Keep respondents who completed the entire survey
+  filter(Q1.1 == 1) %>%        # Keep respondents who gave consent
+  filter(Q2.5 %in% c(1:5)) %>% # Keep respondents who passed the screener
+  filter(Q2.11 == 3)           # Keep respondents who passed the attention check
+
+data_clean %>%
+  select(Q4.1:Q4.12) %>%
+  gather(key = "task", value = "choice") %>%
+  count(choice)
+
+
+design_orig <- read_csv(here("data", "derived_data", "design.csv")) %>%
+  rename(
+    version = question_set,
+    task = question,
+    alt = choice
+  ) %>%
+  gather(key = "atts", value = "levels", -c(version:alt))
+
+design_surv <- data_clean %>%
+  select(contains("CBCONJOINT"), -revision_CBCONJOINT) %>%
+  gather(key = "temp", value = "level_names", -vers_CBCONJOINT) %>%
+  separate(temp, into = c("atts", "task", "alt"), sep = "\\.") %>%
+  separate(alt, into = c("alt", "temp")) %>%
+  select(vers_CBCONJOINT, task, alt, atts, level_names) %>%
+  rename(version = vers_CBCONJOINT) %>%
+  mutate(
+    task = as.numeric(task),
+    alt = as.numeric(alt),
+    atts = recode(
+      atts,
+      "732d72a6-25a3-4194-8416-461acae30837" = "Organization",
+      "bd54b90a-efb3-4ac8-b65a-1ebeefcaf703" = "Issue area",
+      "a6836e28-fd7a-4b71-b65e-f6269e5c883f" = "Financial transparency",
+      "c2249c1a-11fa-4395-a0a3-61d9648a2e55" = "Accountability",
[…]

### 2023-05-11 analysis/mnl_figs_and_tables.R

@@ -1,0 +1,24 @@
+library(tidyverse)
+library(magrittr)
+library(tidybayes)
+library(broom)
+library(ggridges)
+library(ggraph)
+library(ggdag)
+library(pander)
+library(patchwork)
+library(scales)
+library(here)
+
+# Load custom plot functions
+source(here("R", "graphics.R"))
+
+# General settings
+source(here("analysis", "options.R"))
+
+# Make all the randomness reproducible
+set.seed(1234)
+
+fitted_model = read_rds(here::here("analysis", "output", "model_runs", "mnl_dummy_intercept.rds"))
+
+draws = as.tibble(fitted_model)

### 2023-05-15 analysis/01_experimental-design.Rmd
More flat multinomial logit code, as well as plots of main effects for flat and multilevel models

--- 2023-05-08 analysis/01_experimental-design.Rmd
@@
 
+# Aggregate-coded interactions
+
+We have a number of hypotheses referencing specific interactions.
+To answer these hypotheses, we need to specific each of the needed interactions.
+Here we do it by aggregating up the interaction terms.
+
+```{r aggregate-interactions, warning=FALSE, message=FALSE}
+# Convert the attributes in design into factors
+interactions <- as.data.frame(design)
+for(i in 4:ncol(interactions)) {
+  interactions[,i] <- as.factor(interactions[,i])
+}
+
+# Rename the variables
+colnames(interactions)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")
+
+# Use dummy_cols() to get an index-coded version of all the attribute levels
+interactions <- dummy_cols(
+  interactions,
+  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
+  remove_first_dummy = FALSE,
+  remove_selected_columns = TRUE
+)
+
+# Rename the index-coded variables
+colnames(interactions)[4:21] <- c(
+  str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2),
+  str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
+)
+
+# org1 = amnesty
+# org2 = greenpeace
+# org3 = oxfam
+# org4 = redcross
+# gov_rel1 = friendly
+# gov_rel2 = criticized
+# gov_rel3 = crackdown
+# issue1 = emergency
+# issue2 = environment
+# issue3 = human rights
+# issue4 = refugee
+# transp1 = not transparent
+# transp2 = transparent
+# account1 = not accountable
+# account2 = accountable
+# fund1 = smalldonors
+# fund2 = wealthydonors
+# fund3 = gov grants
+#
+
+# Build out all the necessary interactions...
+# ...by multiplying together the needed index-coded levels.
+# Sticking exactly to the hypotheses
+interactions_exact <- interactions %>% 
+  as_tibble() %>% 
+  rowwise() %>% 
+  mutate(
+    # Main Effects
+    h1_high = sum(org3, org4), # oxfam and red cross
+    h1_low = sum(org1, org2), # amnesty and greenpeace
+    h2a_high = sum(gov_rel2,gov_rel3), # criticized and crackdown
+    h2a_low = gov_rel1, # friendly
+    h3a_high = sum(issue1, issue4), # emergency and refugee
+    h3a_low = sum(issue2, issue3), # environment and human rights
+    h4a_high = fund1, # small donors
+    h4a_low = sum(fund2, fund3), # wealthy donors and gov grants
+    h5a_high = transp2, # transparent
+    h5a_low = transp1, # not transparent
+    # First Order Interactions
+    h2b_high = h1_high*h2a_high, #  oxfam and red cross * criticized and crackdown
+    h2b_low = h1_low*gov_rel3, # amnesty and greenpeace * criticized
+    h3b_high = h2a_high*h3a_high, # criticized and crackdown * emergency and refugee
+    h3b_low = h2a_high*h3a_low, # criticized and crackdown * environment and human rights
+    h4b_high = gov_rel3*fund1, # crackdown * small donors
+    h4b_low = sum(gov_rel1, gov_rel2)*h4a_high, # not crackdown * not small donors
+    h5b_high = h2a_high*h5a_high, # criticized and crackdown * transparent
+    h5b_low = h5a_low + h2a_low*h5a_high, # not transparent + friendly * transparent + 
+    # Second Order Interactions
+    h4c_high = gov_rel3*h4a_high*h3a_high, # crackdown * small donors * emergency and refugee
+    h4c_low = ifelse(h4c_high==1, 0, 1), # everything else
+    h5c_high = h2a_high*h5a_high*h4a_high, # criticized and crackdown * transparent * small donors
+    h5c_low = ifelse(h5c_high==1, 0, 1), # everything else
+    h5d_high = h2a_high*h5a_high*h3a_high, # criticized and crackdown * transparent * emergency and refugee
+    h5d_low = ifelse(h5d_high==1, 0, 1), # everything else
+    # Third Order Interaction
+    h5e_high = h2a_high*h5a_high*h3a_high*h4a_high, # criticized and crackdown * transparent * emergency and refugee * small donors
+    h5e_low = ifelse(h5e_high==1, 0, 1)) %>% 
+  ungroup()
+
+# Build out all the necessary interactions
+# interactions <- interactions %>% 
+#   as_tibble() %>% 
+#   mutate(
+#     # Hypothesis 2b.
+#     amnesty_criticized = org1 * gov_rel2,
+#     greenpeace_criticized = org2 * gov_rel2,
+#     oxfam_criticized = org3 * gov_rel2,
+#     redcross_criticized = org4 * gov_rel2,
+#     amnesty_crackdown = org1 * gov_rel3,
+#     greenpeace_crackdown = org2 * gov_rel3,
+#     oxfam_crackdown = org3 * gov_rel3,
+#     redcross_crackdown = org4 * gov_rel3,
+#     # Hypothesis 3b.
+#     emergency_criticized = issue1 * gov_rel2,
+#     environment_criticized = issue2 * gov_rel2,
+#     humanrights_criticized = issue3 * gov_rel2,
+#     refugees_criticized = issue4 * gov_rel2,
+#     emergency_crackdown = issue1 * gov_rel3,
+#     environment_crackdown = issue2 * gov_rel3,
+#     humanrights_crackdown = issue3 * gov_rel3,
+#     refugees_crackdown = issue4 * gov_rel3,
+#     # Hypothesis 4b.
+#     smalldonors_criticized = fund1 * gov_rel2,
+#     wealthydonors_criticized = fund2 * gov_rel2,
+#     govgrants_criticized = fund3 * gov_rel2,
+#     smalldonors_crackdown = fund1 * gov_rel3,
+#     wealthydonors_crackdown = fund2 * gov_rel3,
+#     govgrants_crackdown = fund3 * gov_rel3,
+#     # Hypothesis 4c.
+#     emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
+#     emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3, # ??????
+#     emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,     # ??????
+#     environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
+#     environment_wealthydonors_crackdown = issue2 * fund2 * gov_rel3,
+#     environment_govgrants_crackdown = issue2 * fund3 * gov_rel3,
+#     humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
+#     humanrights_wealthydonors_crackdown = issue3 * fund2 * gov_rel3,
+#     humanrights_govgrants_crackdown = issue3 * fund3 * gov_rel3,
+#     refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
+#     refugees_wealthydonors_crackdown = issue4 * fund2 * gov_rel3,
+#     refugees_govgrants_crackdown = issue4 * fund3 * gov_rel3,
+#     # Hypothesis 5b.
+#     nottransp_criticized = transp1 * gov_rel2,
+#     transp_criticized = transp2 * gov_rel2,
+#     nottransp_crackdown = transp1 * gov_rel3,
+#     transp_crackdown = transp2 * gov_rel3,
+#     # Hypothesis 5c.
+#     nottransp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
+#     transp_smalldonors_criticized = transp2 * fund1 * gov_rel2,
+#     nottransp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
+#     transp_wealthydonors_criticized = transp2 * fund2 * gov_rel2,
+#     nottransp_govgrants_criticized = transp1 * fund3 * gov_rel2,
+#     transp_govgrants_criticized = transp2 * fund3 * gov_rel2,
+#     nottransp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
+#     transp_smalldonors_crackdown = transp2 * fund1 * gov_rel3,
+#     nottransp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
+#     transp_wealthydonors_crackdown = transp2 * fund2 * gov_rel3,
+#     nottransp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
+#     transp_govgrants_crackdown = transp2 * fund3 * gov_rel3,
+#     # Hypothesis 5d.
+#     nottransp_emergency_criticized = transp1 * issue1 * gov_rel2,
+#     transp_emergency_criticized = transp2 * issue1 * gov_rel2,
+#     nottransp_emergency_crackdown = transp1 * issue1 * gov_rel3,
+#     transp_emergency_crackdown = transp2 * issue1 * gov_rel3,
+#     nottransp_environment_criticized = transp1 * issue2 * gov_rel2,
+#     transp_environment_criticized = transp2 * issue2 * gov_rel2,
+#     nottransp_environment_crackdown = transp1 * issue2 * gov_rel3,
+#     transp_environment_crackdown = transp2 * issue2 * gov_rel3,
+#     nottransp_humanrights_criticized = transp1 * issue3 * gov_rel2,
+#     transp_humanrights_criticized = transp2 * issue3 * gov_rel2,
+#     nottransp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
+#     transp_humanrights_crackdown = transp2 * issue3 * gov_rel3,
+#     nottransp_refugees_criticized = transp1 * issue4 * gov_rel2,
+#     transp_refugees_criticized = transp2 * issue4 * gov_rel2,
+#     nottransp_refugees_crackdown = transp1 * issue4 * gov_rel3,
+#     transp_refugees_crackdown = transp2 * issue4 * gov_rel3,
+#     # Hypothesis 5e.
+#     nottransp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
+#     transp_smalldonors_emergency_criticized = transp2 * fund1 * issue1 * gov_rel2,
+#     nottransp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
+#     transp_smalldonors_emergency_crackdown = transp2 * fund1 * issue1 * gov_rel3,
+#     nottransp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
+#     transp_smalldonors_environment_criticized = transp2 * fund1 * issue2 * gov_rel2,
+#     nottransp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
+#     transp_smalldonors_environment_crackdown = transp2 * fund1 * issue2 * gov_rel3,
+#     nottransp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
+#     transp_smalldonors_humanrights_criticized = transp2 * fund1 * issue3 * gov_rel2,
+#     nottransp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
+#     transp_smalldonors_humanrights_crackdown = transp2 * fund1 * issue3 * gov_rel3,
+#     nottransp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
+#     transp_smalldonors_refugees_criticized = transp2 * fund1 * issue4 * gov_rel2,
+#     nottransp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
+#     transp_smalldonors_refugees_crackdown = transp2 * fund1 * issue4 * gov_rel3
+#   )
+
+# Save interact-coded design output
+# write.csv(interactions, here("data", "derived_data", "aggregate_interactions.csv"))
+write.csv(interactions_exact, here("data", "derived_data", "aggregate_interactions_exact.csv"))
+```
+
 # Original computing environment

### 2023-05-15 analysis/mnl_data_prep.R

@@ -764,6 +764,66 @@ write_rds(dummy_X, here("data", "derived_data", "final_data_mnl_dummy.rds"))
 write_rds(dummy_Y, here("data", "derived_data", "final_outcome_mnl_dummy.rds"))
 
 
+# Interactions
+dummy_design <- read_csv(here::here("data", "derived_data", "dummy_interactions.csv")) %>%
+  select(-`...1`) %>%
+  rename(
+    version = question_set,
+    task = question,
+    alt = choice
+  )
+
+# Outcomes for mnl, can probably be used for indexed as well
+Y_mnl = data %>%
+  select(id, version, contains("Q4.")) %>% # Selecting NGO choice questions
+  pivot_longer(Q4.1:Q4.12) %>%
+  group_by(id) %>%
+  mutate(task = row_number()) %>%
+  ungroup() %>%
+  rename(alt = value)
+
+
+# Attributes for mnl
+# Definitely a better way to do this but my brain hurts
+# Just doing hypothesis 2b for now
+dummy_X_mnl = tibble(
+  id = rep(Y_mnl$id, each=4),
+  version = rep(Y_mnl$version, each = 4),
+  task = rep(Y_mnl$task, each = 4),
+  alt = rep(1:4, times=nrow(Y_mnl))) %>%
+  left_join(dummy_design) %>%
+  mutate(org1 = ifelse(org2+org3+org4 == 0, 1, 0)) %>%
+  mutate(across(org2:org1, ~ replace_na(.x, 0))) %>%
+  select(id:alt, org1, org2:redcross_crackdown)
+
+
+dummy_X <- array(
+  data = NA,
+  dim = c(
+    nrow(Y_mnl), # Number of respondents multiplied by choice tasks per respondent
+    (max(dummy_design$alt) + 1),  # Number of choices
+    (ncol(dummy_X_mnl) - 3 + 1)  # Number of (estimable) attribute levels, why plus 1>
+  ))
+
+# Look at me hardcoding like a champ
+for (i in 1:4) {
+  for(j in 1:13){
+    vector1 = dummy_X_mnl %>%
+      filter(alt ==i) %>%
+      select(org1:redcross_crackdown) %>%
+      select(j) %>%
+      pull()
+
+    dummy_X[1:12192,i, j] = vector1
+  }
+}
+
+dummy_Y = Y_mnl %>% select(alt) %>% pull()
+
+write_rds(dummy_X, here("data", "derived_data", "final_data_interaction_mnl_dummy.rds"))
[…]

### 2023-05-15 analysis/01_experimental-design.Rmd
Trying to build out aggregate interactions

--- 2023-05-08 analysis/01_experimental-design.Rmd
@@
 
-# # Rename the variables
-# colnames(interactions)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")
+# Rename the variables
+colnames(interactions)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")
+
+# Use dummy_cols() to get an index-coded version of all the attribute levels
+interactions <- dummy_cols(
+  interactions,
+  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
+  remove_first_dummy = FALSE,
+  remove_selected_columns = TRUE
+)
+
+# Rename the index-coded variables
+colnames(interactions)[4:21] <- c(
+  str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2),
+  str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
+)
+
+# # org1 = amnesty
+# # org2 = greenpeace
+# # org3 = oxfam
+# # org4 = redcross
+# # gov_rel1 = friendly
+# # gov_rel2 = criticized
+# # gov_rel3 = crackdown
 # 
-# # Use dummy_cols() to get an index-coded version of all the attribute levels
-# interactions <- dummy_cols(
-#   interactions, 
-#   select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
-#   remove_first_dummy = FALSE,
-#   remove_selected_columns = TRUE
+# # Build out all the necessary interactions...
+# # ...by multiplying together the needed index-coded levels.
+# interactions <- interactions %>% 
+#   as_tibble() %>% 
+#   mutate(
+#     h2b_1 = ifelse(Organization ==3|Organization==4, 1, 0), # 1 if org is oxfam or redcross
+#     h2b_2 = ifelse(`Relationship with host government` == 2|`Relationship with host government` == 3, 1, 0), # 1 if gov_rel is criticized or crackdown
+#     h2b_3 = h2b_1*h2b_2 # interaction term
 #     )
-# 
-# # Rename the index-coded variables
-# colnames(interactions)[4:21] <- c(
-#   str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
-#   str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
-# )
-#
-# org1 = amnesty
-# org2 = greenpeace
-# org3 = oxfam
-# org4 = redcross
-# gov_rel1 = friendly
-# gov_rel2 = criticized
-# gov_rel3 = crackdown
 
-# Build out all the necessary interactions...
-# ...by multiplying together the needed index-coded levels.
-interactions <- interactions %>% 
-  as_tibble() %>% 
+interactions <- interactions |> 
   mutate(
-    h2b_1 = ifelse(Organization ==3|Organization==4, 1, 0), # 1 if org is oxfam or redcross
-    h2b_2 = ifelse(`Relationship with host government` == 2|`Relationship with host government` == 3, 1, 0), # 1 if gov_rel is criticized or crackdown
-    h2b_3 = h2b_1*h2b_2 # interaction term
+    # Oxfam or Red Cross.
+    h2b_org_1 = ifelse(org3 == 1 | org4 == 1, 1, 0),
+    # Government crackdown or criticism.
+    h2b_gov_rel_1 = ifelse(gov_rel2 == 1 | gov_rel3 == 1, 1, 0),
+    # Oxfam or Red Cross facing government crackdown or criticism.
+    h2b_int_1 = ifelse(org3 == 1 | org4 == 1, 1, 0) * ifelse(gov_rel2 == 1 | gov_rel3 == 1, 1, 0),
+    # Amnesty or Greenpeace.
+    h2b_org_2 = ifelse(org1 == 1 | org2 == 1, 1, 0),
+    # Government crackdown.
+    h2b_gov_rel_2 = gov_rel3,
+    # Amnesty or Greenpeace is facing crackdown.
+    # h2b_2 = ifelse(org1 == 1 | org2 == 1, 1, 0) * gov_rel3
+    h2b_int_2 = ifelse(org1 == 1 | org2 == 1, 1, 0) * gov_rel3
   )
+  # select(1:3, contains("h2b"))
+
+# interactions |> 
+#   # select(org1:org4, gov_rel2:gov_rel3, h2b_1, h2b_2)
+#   # select(org3, org4, gov_rel2, gov_rel3, h2b_1)
+#   select(org1, org2, gov_rel3, h2b_2)
 

### 2023-05-15 analysis/01_experimental-design.Rmd

--- 2023-05-15 analysis/01_experimental-design.Rmd
@@
 
+# # Build out all the necessary interactions...
+# # ...by multiplying together the needed index-coded levels.
 # org1 = amnesty
@@
 # fund3 = gov grants
-#
 
-# Build out all the necessary interactions...
-# ...by multiplying together the needed index-coded levels.
+# interactions <- interactions |> 
+#   mutate(
+#     # Oxfam or Red Cross.
+#     h2b_org_1 = ifelse(org3 == 1 | org4 == 1, 1, 0),
+#     # Government crackdown or criticism.
+#     h2b_gov_rel_1 = ifelse(gov_rel2 == 1 | gov_rel3 == 1, 1, 0),
+#     # Oxfam or Red Cross facing government crackdown or criticism.
+#     h2b_int_1 = ifelse(org3 == 1 | org4 == 1, 1, 0) * ifelse(gov_rel2 == 1 | gov_rel3 == 1, 1, 0),
+#     # Amnesty or Greenpeace.
+#     h2b_org_2 = ifelse(org1 == 1 | org2 == 1, 1, 0),
+#     # Government crackdown.
+#     h2b_gov_rel_2 = gov_rel3,
+#     # Amnesty or Greenpeace is facing crackdown.
+#     # h2b_2 = ifelse(org1 == 1 | org2 == 1, 1, 0) * gov_rel3
+#     h2b_int_2 = ifelse(org1 == 1 | org2 == 1, 1, 0) * gov_rel3
+#   )
+#   # select(1:3, contains("h2b"))
+
 # Sticking exactly to the hypotheses

### 2023-05-16 analysis/03_mnl_model-calibration.R
Renamed scripts in preparation for integrating

@@ -1,7 +1,16 @@
 # Preamble ----------------------------------------------------------------
 # Load packages
 library(tidyverse)
+library(fastDummies)
 library(rstan)
+library(bayesplot)
+library(tidybayes)
+library(loo)
+library(ggridges)
+library(ggraph)
+library(ggdag)
+library(here)
+
 
 # Set Stan options
 options(mc.cores = parallel::detectCores())
@@ -115,7 +124,11 @@ public_political_social_charity_demo <- 0 # Public affairs + Political ideology 
 #   bind_cols(as_tibble(out$x[,-1])) %>%
 #   as.matrix()
 
-X = read_rds(here::here("data", "derived_data", "final_data_mnl_dummy.rds"))
+# Accidentally overwrote the dummy data, whoops
+# X = read_rds(here::here("data", "derived_data", "final_data_mnl_dummy.rds"))
+# X = read_rds(here::here("data", "derived_data", "final_data_mnl_dummy_aggregate.rds"))
+X = read_rds(here::here("data", "derived_data", "final_data_interaction_mnl_dummy.rds"))
+
 Y = read_rds(here::here("data", "derived_data", "final_outcome_mnl_dummy.rds"))
 
 # Model Calibration -------------------------------------------------------
@@ -144,8 +157,9 @@ fit <- stan(
   seed = 42
 )
 run <- list(data = data, fit = fit)
-write_rds(run, here::here("analysis", "output", "model_runs", "mnl_dummy_intercept.rds"))
-
+# write_rds(run, here::here("analysis", "output", "model_runs", "mnl_dummy_intercept.rds"))
+# write_rds(run, here::here("analysis", "output", "model_runs", "mnl_aggregate_dummy.rds"))
+write_rds(run, here::here("analysis", "output", "model_runs", "mnl_interaction_dummy.rds"))
 
 # Follow naming convention: mnl-intercept.rds (for example). What models to run:
 # - Dummy-coded mnl-intercept. Compare contrasts to main effect hypotheses.
@@ -165,3 +179,19 @@ write_rds(run, here::here("analysis", "output", "model_runs", "mnl_dummy_interce
 # if (public_political_social_charity == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
[…]

### 2023-05-16 analysis/04a_mnl_contrasts.R

@@ -1,0 +1,170 @@
+# All hypotheses
+
+draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "mnl_aggregate_dummy_draws.rds")) %>%
+  rename(i=l)
+
+
+# Reference Level = Friendly relationship with government
+# Compute the contrasts
+contrasts_int <- tibble(
+  # Attribute levels
+  h1_high = draws %>% filter(i == 1) %>% select(beta) %>% pull(),
+  h1_low = draws %>% filter(i == 2) %>% select(beta) %>% pull(),
+  # h2a_high = draws %>% filter(i == 3) %>% select(beta) %>% pull(),
+  h3a_high = draws %>% filter(i == 4)%>% select(beta) %>% pull(),
+  h4a_high = draws %>% filter(i == 5)%>% select(beta) %>% pull(),
+  h5a_high = draws %>% filter(i == 6) %>% select(beta) %>% pull(),
+  h2b_high = draws %>% filter(i == 7)%>% select(beta) %>% pull(),
+  h2b_low = draws %>% filter(i == 8)%>% select(beta) %>% pull(),
+  # h3b_high = draws %>% filter(i == 9)%>% select(beta) %>% pull(),
+  # h3b_low = draws %>% filter(i == 10)%>% select(beta) %>% pull(),
+  h4b_high = draws %>% filter(i == 11)%>% select(beta) %>% pull(),
+  h5b_high = draws %>% filter(i == 12)%>% select(beta) %>% pull(),
+  h4c_high = draws %>% filter(i == 13)%>% select(beta) %>% pull(),
+  h5c_high = draws %>% filter(i == 14)%>% select(beta) %>% pull(),
+  h5d_high = draws %>% filter(i == 15)%>% select(beta) %>% pull(),
+  h5e_high = draws %>% filter(i == 16)%>% select(beta) %>% pull()
+)
+
+# Plot the contrasts
+contrasts_int %>%
+  pivot_longer(
+    h1_high:h5e_high,
+    names_to = "level", values_to = "beta"
+  ) %>%
+  mutate(level = fct_rev(fct_inorder(level))) %>%
+  ggplot(aes(x = beta, y = level)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Contrasts", x = "Difference in betas")
+
+# Save plot
+
+
+
[…]

### 2023-05-16 analysis/02_clean-data.Rmd
Cleaned and restructured 02_clean-data

--- 2023-05-04 analysis/02_clean-data.Rmd
@@
 
-## Design matrix
-
-Select a dummy or index-coded version of the design.
-
-```{r transform-design}
-dummy_coded <- 0 # Dummy-coded design and associated interactions.
-index_coded <- 1 # Index-coded design and associated interactions.
-
-if (dummy_coded == 1) {
+## Dummy-coded design matrix
+
+Transform the dummy-coded design matrix conditioned on what version each respondent was assigned to, including the brand intercept and the outside option.
+
+```{r transform-dummy-design}
 # Load the dummy design.
@@
       mutate(org1 = 0) %>%
-        select(org1, org2:transp_smalldonors_refugees_crackdown) # NOTE DIMENSIONS OF INTERACTIONS HARD-CODED.
+      select(org1, which(names(interactions_X_n) == "org2"):ncol(interactions_X_n))
     for (p in 1:(dim(dummy_X)[3]-1)) {
@@
 }
-}
-if (index_coded == 1) {
+```
+
+## Index-coded experimental alternative
+
+```{r transform-index-design}
+################################################################################
+# This is an experimental alternative to the dummy-coded design.
+################################################################################
+
 # Load the index-coded design.
@@
       filter(task == s) %>%
-        select(org1:transp_smalldonors_refugees_crackdown) # NOTE DIMENSIONS OF INTERACTIONS HARD-CODED.
+      select(which(names(interactions_X_n) == "org1"):ncol(interactions_X_n))
     # Save modified design, including outside option.
@@
 }
+```
+
+## Flat MNL designs experimental alternative
+
+```{r transform-flat-designs}
+################################################################################
+# This is an experimental designs for a flat MNL.
+# We already have the data structured. We just need to collapse respondent
+# repeat observations into an observation dimension.
+################################################################################
+
+# Create the arrays for a design with a brand intercept.
+flat_dummy_X <- array(
+  data = NA,
+  dim = c(
+    nrow(data) * max(dummy_design$task), # Number of observations.
+    (max(dummy_design$alt) + 1),         # Number of product alternatives per observation.
+    (ncol(dummy_design) - 3 + 1)         # Number of (estimable) attribute levels.
+  )
+)
+
+# Create the arrays for a design with a brand intercept and interactions.
+flat_dummy_interactions_X <- array(
+  data = NA,
+  dim = c(
+    nrow(data) * max(dummy_interactions_design$task), # Number of respondents.
+    (max(dummy_interactions_design$alt) + 1),         # Number of product alternatives per observation.
+    (ncol(dummy_interactions_design) - 3 + 1)         # Number of (estimable) attribute levels.
+  )
+)
+
+# Create the arrays for the design, including a brand intercept.
+flat_index_X <- array(
+  data = NA,
+  dim = c(
+    nrow(data) * max(index_design$task), # Number of observations.
+    (max(index_design$alt) + 1),         # Number of product alternatives per observation.
+    (ncol(index_design) - 3)             # Number of (estimable) attribute levels.
+  )
+)
+
+# Create the arrays for a design, including a brand intercept and interactions.
+flat_index_interactions_X <- array(
+  data = NA,
+  dim = c(
+    nrow(data) * max(index_interactions_design$task), # Number of respondents.
+    (max(index_interactions_design$alt) + 1),         # Number of product alternatives per observation.
+    (ncol(index_interactions_design) - 3)             # Number of (estimable) attribute levels.
+  )
+)
+
+# Restructure design matrices.
+n <- 0
+for (r in 1:dim(dummy_X)[1]) {
+  for (s in 1:dim(dummy_X)[2]) {
+    n <- n + 1
+    flat_dummy_X[n,,] <- dummy_X[r, s,,]
+    flat_dummy_interactions_X[n,,] <- dummy_interactions_X[r, s,,]
+    flat_index_X[n,,] <- index_X[r, s,,]
+    flat_index_interactions_X[n,,] <- index_interactions_X[r, s,,]
   }
+}
 ```
@@
 ```{r save-clean-data}
-write_rds(data, here("data", "derived_data", "final_data.rds"))
-if (dummy_coded == 1) {
-  write_rds(dummy_X, here("data", "derived_data", "final_design.rds"))
-  write_rds(dummy_interactions_X, here("data", "derived_data", "final_interactions.rds"))
-}
-if (index_coded == 1) {
-  write_rds(index_X, here("data", "derived_data", "final_design.rds"))
-  write_rds(index_interactions_X, here("data", "derived_data", "final_interactions.rds"))
-}
+write_rds(data, here("data", "derived_data", "data.rds"))
+write_rds(dummy_X, here("data", "derived_data", "hmnl_dummy_design.rds"))
+write_rds(dummy_interactions_X, here("data", "derived_data", "hmnl_dummy_interactions.rds"))
+
+################################################################################
+# Save the experimental alternative to the dummy-coded design.
+################################################################################
+
+write_rds(index_X, here("data", "derived_data", "hmnl_index_design.rds"))
+write_rds(index_interactions_X, here("data", "derived_data", "hmnl_index_interactions.rds"))
+
+################################################################################
+# Save the experimental designs for a flat MNL.
+################################################################################
+
+write_rds(flat_dummy_X, here("data", "derived_data", "mnl_dummy_design.rds"))
+write_rds(flat_dummy_interactions_X, here("data", "derived_data", "mnl_dummy_interactions.rds"))
+write_rds(flat_index_X, here("data", "derived_data", "mnl_index_design.rds"))
+write_rds(flat_index_interactions_X, here("data", "derived_data", "mnl_index_interactions.rds"))
 ```

### 2023-05-16 analysis/02_mnl_data-prep.R

@@ -1,989 +1,0 @@
-library(tidyverse)
-library(fastDummies)
-library(here)
-
-# Start here for all MNL models
-
-
-# Experimental Design -----------------------------------------------------
-
-# Load design
-
-# Clean Data --------------------------------------------------------------
-
-# Start here for all MNL models
-
-library(tidyverse)
-library(here)
-
-data <- read_csv(
-  here::here("data", "raw_data", "conjointqsf_final.csv"),
-  guess_max = 1500
-)
-
-# Skipping a lot of the code to check the data
-
-data_clean <- data %>%
-  filter(V10 == 1) %>%         # Keep respondents who completed the entire survey
-  filter(Q1.1 == 1) %>%        # Keep respondents who gave consent
-  filter(Q2.5 %in% c(1:5)) %>% # Keep respondents who passed the screener
-  filter(Q2.11 == 3)           # Keep respondents who passed the attention check
-
-data_clean %>%
-  select(Q4.1:Q4.12) %>%
-  gather(key = "task", value = "choice") %>%
-  count(choice)
-
-
-design_orig <- read_csv(here("data", "derived_data", "design.csv")) %>%
-  rename(
-    version = question_set,
-    task = question,
-    alt = choice
-  ) %>%
-  gather(key = "atts", value = "levels", -c(version:alt))
-
-design_surv <- data_clean %>%
-  select(contains("CBCONJOINT"), -revision_CBCONJOINT) %>%
-  gather(key = "temp", value = "level_names", -vers_CBCONJOINT) %>%
-  separate(temp, into = c("atts", "task", "alt"), sep = "\\.") %>%
-  separate(alt, into = c("alt", "temp")) %>%
-  select(vers_CBCONJOINT, task, alt, atts, level_names) %>%
-  rename(version = vers_CBCONJOINT) %>%
-  mutate(
-    task = as.numeric(task),
-    alt = as.numeric(alt),
-    atts = recode(
-      atts,
-      "732d72a6-25a3-4194-8416-461acae30837" = "Organization",
-      "bd54b90a-efb3-4ac8-b65a-1ebeefcaf703" = "Issue area",
-      "a6836e28-fd7a-4b71-b65e-f6269e5c883f" = "Financial transparency",
-      "c2249c1a-11fa-4395-a0a3-61d9648a2e55" = "Accountability",
[…]

### 2023-05-16 analysis/04_figs-tables.Rmd
Moved model fit to 04_figs-table

@@
   draws <- read_rds(
-    here::here("data", "raw_data", "posterior_draws", "intercept.rds")
+    # here::here("data", "raw_data", "posterior_draws", "intercept.rds")
+    here::here("data", "raw_data", "posterior_draws", "index_intercept.rds")
   ) %>% 
@@
 # Name levels labels
+# level_labels <- c(
+#   str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
+#   str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
+#   str_c("Organizational practices: ", c("Financial transparency", "Accountability")),
+#   str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants")),
+#   str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))
+# )
+
+# Name levels labels (index-coded)
 level_labels <- c(
   str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
-  str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
+  str_c("Issue area: ", c("Emergency response", "Environment", "Human rights", "Refugee relief")),
   str_c("Organizational practices: ", c("Financial transparency", "Accountability")),
-  str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants")),
-  str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))
+  str_c("Funding sources: ", c("Many small private donations", "Handful of wealthy private donors", "Government grants")),
+  str_c("Relationship with host government: ", c("Friendly", "Criticized", "Under crackdown"))
 )
@@
 }
+```
+
+# Compute model fit
+
+## Load model output
+
+```{r load-data-output, warning=FALSE, message=FALSE, eval=FALSE}
+# Load all model output
+intercept_run <- read_rds(here::here("data", "raw_data", "model_runs", "intercept.rds"))
+public_affairs_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_affairs.rds"))
+political_ideology_run <- read_rds(here::here("data", "raw_data", "model_runs", "political_ideology.rds"))
+social_views_run <- read_rds(here::here("data", "raw_data", "model_runs", "social_views.rds"))
+charity_voluntarism_run <- read_rds(here::here("data", "raw_data", "model_runs", "charity_voluntarism.rds"))
+demographics_run <- read_rds(here::here("data", "raw_data", "model_runs", "demographics.rds"))
+public_political_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political.rds"))
+public_political_social_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social.rds"))
+public_political_social_charity_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity.rds"))
+public_political_social_charity_demo_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity_demo.rds"))
+```
+
+## Compute and save model fit
+
+```{r compute-fit, eval=FALSE}
+# Compute fit using PSIS-LOO
+intercept_loo <- loo(intercept_run$fit, save_psis = TRUE)
+public_affairs_loo <- loo(public_affairs_run$fit, save_psis = TRUE)
+political_ideology_loo <- loo(political_ideology_run$fit, save_psis = TRUE)
+social_views_loo <- loo(social_views_run$fit, save_psis = TRUE)
+charity_voluntarism_loo <- loo(charity_voluntarism_run$fit, save_psis = TRUE)
+demographics_loo <- loo(demographics_run$fit, save_psis = TRUE)
+public_political_loo <- loo(public_political_run$fit, save_psis = TRUE)
+public_political_social_loo <- loo(public_political_social_run$fit, save_psis = TRUE)
+public_political_social_charity_loo <- loo(public_political_social_charity_run$fit, save_psis = TRUE)
+public_political_social_charity_demo_loo <- loo(public_political_social_charity_demo_run$fit, save_psis = TRUE)
+
+# Compare model fit
+loo_compare(intercept_loo, public_affairs_loo, political_ideology_loo, social_views_loo, charity_voluntarism_loo, demographics_loo, public_political_loo, public_political_social_loo, public_political_social_charity_loo, public_political_social_charity_demo_loo)
+```
+
+```{r save-fit, eval=FALSE}
+# Create data frame
+model_fit <- tibble(model = rep(NA, 10), elpd_loo = rep(NA, 10))
+
+# Extract PSIS-LOO fit
+model_fit$model[1] <- "intercept"; model_fit$loo[1] <- intercept_loo$elpd_loo
+model_fit$model[2] <- "public_affairs"; model_fit$loo[2] <- public_affairs_loo$elpd_loo
+model_fit$model[3] <- "political_ideology"; model_fit$loo[3] <- political_ideology_loo$elpd_loo
+model_fit$model[4] <- "social_views"; model_fit$loo[4] <- social_views_loo$elpd_loo
+model_fit$model[5] <- "charity_voluntarism"; model_fit$loo[5] <- charity_voluntarism_loo$elpd_loo
+model_fit$model[6] <- "demographics"; model_fit$loo[6] <- demographics_loo$elpd_loo
+model_fit$model[7] <- "public_political"; model_fit$loo[7] <- public_political_loo$elpd_loo
+model_fit$model[8] <- "public_political_social"; model_fit$loo[8] <- public_political_social_loo$elpd_loo
+model_fit$model[9] <- "public_political_social_charity"; model_fit$loo[9] <- public_political_social_charity_loo$elpd_loo
+model_fit$model[10] <- "public_political_social_charity_demo"; model_fit$loo[10] <- public_political_social_charity_demo_loo$elpd_loo
+
+# Save model output
+write_rds(model_fit, here::here("analysis", "output", "tables", "model_fit.rds"))
 ```

### 2023-05-16 analysis/03_analysis.Rmd
Updated 03_analysis to handle MNL as well, including saving draws in-line

@@
 
-# Model calibration
+# HMNL model calibration
 
-After selecting the model we'd like to run, model calibration proceeds as follows. Note that model calibration is run in a separate R script given how long it takes to run each model.
+After selecting the model we'd like to run, model calibration proceeds as follows.
 
-```{r model-calibration, eval=FALSE}
+```{r hmnl-model-calibration, eval=FALSE}
 intercept <- 1                            # Intercept-only
@@
 # Load data and design
-final_data <- read_rds(here::here("data", "derived_data", "final_data.rds"))
-X <- read_rds(here::here("data", "derived_data", "final_design.rds"))
-if (interactions == 1) X <- read_rds(here::here("data", "derived_data", "final_interactions.rds"))
+data <- read_rds(here::here("data", "derived_data", "data.rds"))
+X <- read_rds(here::here("data", "derived_data", "hmnl_dummy_design.rds"))
+if (interactions == 1) X <- read_rds(here::here("data", "derived_data", "hmnl_dummy_interactions.rds"))
 
 # Restructure choice data Y
-Y <- final_data %>%
+Y <- data %>%
   select(contains("Q4")) %>%
@@
 if (public_affairs == 1) {
-  Z <- final_data %>%
+  Z <- data %>%
     select(
@@
 if (political_ideology == 1) {
-  Z <- final_data %>%
+  Z <- data %>%
     select(
@@
 if (social_views == 1) {
-  Z <- final_data %>%
+  Z <- data %>%
     select(
@@
 if (charity_voluntarism == 1) {
-  Z <- final_data %>%
+  Z <- data %>%
     select(
@@
 if (demographics == 1) {
-  Z <- final_data %>%
+  Z <- data %>%
     select(
@@
 if (public_political == 1) {
-  Z <- final_data %>%
+  Z <- data %>%
     select(
@@
 if (public_political_social == 1) {
-  Z <- final_data %>%
+  Z <- data %>%
     select(
@@
 if (public_political_social_charity == 1) {
-  Z <- final_data %>%
+  Z <- data %>%
     select(
@@
 if (public_political_social_charity_demo == 1) {
-  Z <- final_data %>%
+  Z <- data %>%
     select(
@@
 # Specify the data for calibration in a list
-data <- list(
+data_list <- list(
   R = dim(X)[1],      # Number of respondents
@@
   file = here::here("src", "stan_files", "hmnl_noncentered.stan"),
-  data = data,
+  data = data_list,
   iter = 10000,
@@
 )
-run <- list(data = data, fit = fit)
-# if (intercept == 1 & interactions == 0) write_rds(run, here::here("data", "raw_data", "model_runs", "intercept.rds"))
-if (intercept == 1 & interactions == 0) write_rds(run, here::here("data", "raw_data", "model_runs", "index_intercept.rds"))
-if (intercept == 1 & interactions == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "interactions_5e.rds"))
+run <- list(data = data_list, fit = fit)
+if (intercept == 1 & interactions == 0) write_rds(run, here::here("data", "raw_data", "model_runs", "intercept.rds"))
+if (intercept == 1 & interactions == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "interactions.rds"))
 if (public_affairs == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "public_affairs.rds"))
@@
 if (public_political_social_charity_demo == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "public_political_social_charity_demo.rds"))
+
+# Extract and save posterior draws
+draws <- fit %>% 
+  spread_draws(Gamma[i, j]) %>% 
+  ungroup() %>% 
+  filter(.iteration > 500) %>% 
+  rename(
+    i = j,
+    j = i
+  )
+
+# Save draws
+if (intercept == 1 & interactions == 0) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "intercept.rds"))
+if (intercept == 1 & interactions == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "interactions.rds"))
+if (public_affairs == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_affairs.rds"))
+if (political_ideology == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "political_ideology.rds"))
+if (social_views == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "social_views.rds"))
+if (charity_voluntarism == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "charity_voluntarism.rds"))
+if (demographics == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "demographics.rds"))
+if (public_political == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_political.rds"))
+if (public_political_social == 1)  write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_political_social.rds"))
+if (public_political_social_charity == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_political_social_charity.rds"))
+if (public_political_social_charity_demo == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_political_social_charity_demo.rds"))
 ```
@@
 
-# Compute model fit and extract draws
+# MNL model calibration experimental alternative
 
-The following analysis follows specifying the model we'd like to evaluate. Note that the output of the model calibration is too large to push to GitHub, but we can push the draws once we extract them.
+```{r mnl-model-calibration, eval=FALSE}
+################################################################################
+# A flat MNL is an experimental alternative for dealing with interactions.
+################################################################################
 
-## Load model output
+interactions <- 0 # Include interactions
 
-```{r load-data-output, warning=FALSE, message=FALSE, eval=FALSE}
-# Load all model output
-intercept_run <- read_rds(here::here("data", "raw_data", "model_runs", "intercept.rds"))
-public_affairs_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_affairs.rds"))
-political_ideology_run <- read_rds(here::here("data", "raw_data", "model_runs", "political_ideology.rds"))
-social_views_run <- read_rds(here::here("data", "raw_data", "model_runs", "social_views.rds"))
-charity_voluntarism_run <- read_rds(here::here("data", "raw_data", "model_runs", "charity_voluntarism.rds"))
-demographics_run <- read_rds(here::here("data", "raw_data", "model_runs", "demographics.rds"))
-public_political_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political.rds"))
-public_political_social_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social.rds"))
-public_political_social_charity_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity.rds"))
-public_political_social_charity_demo_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity_demo.rds"))
-```
+# Load data and design
+data <- read_rds(here::here("data", "derived_data", "data.rds"))
+X <- read_rds(here::here("data", "derived_data", "mnl_dummy_design.rds"))
+if (interactions == 1) X <- read_rds(here::here("data", "derived_data", "mnl_dummy_interactions.rds"))
 
-## Compute and save model fit
+# Restructure choice data Y
+Y <- data %>%
+  select(contains("Q4")) %>%
+  pivot_longer(contains("Q4"), names_to = "values") %>%
+  select(value) %>%
+  as.matrix() %>%
+  as.vector()
 
-```{r compute-fit, eval=FALSE}
-# Compute fit using PSIS-LOO
-intercept_loo <- loo(intercept_run$fit, save_psis = TRUE)
-public_affairs_loo <- loo(public_affairs_run$fit, save_psis = TRUE)
-political_ideology_loo <- loo(political_ideology_run$fit, save_psis = TRUE)
-social_views_loo <- loo(social_views_run$fit, save_psis = TRUE)
-charity_voluntarism_loo <- loo(charity_voluntarism_run$fit, save_psis = TRUE)
-demographics_loo <- loo(demographics_run$fit, save_psis = TRUE)
-public_political_loo <- loo(public_political_run$fit, save_psis = TRUE)
-public_political_social_loo <- loo(public_political_social_run$fit, save_psis = TRUE)
-public_political_social_charity_loo <- loo(public_political_social_charity_run$fit, save_psis = TRUE)
-public_political_social_charity_demo_loo <- loo(public_political_social_charity_demo_run$fit, save_psis = TRUE)
+# Specify the data for calibration in a list
+data_list <- list(
+  N = dim(X)[1],      # Number of observations
+  A = dim(X)[2],      # Number of choice alternatives
+  L = dim(X)[3],      # Number of (estimable) attribute levels
+  Y = Y,              # Vector of observations
+  X = X               # Array of observation-level covariates.
+)
 
-# Compare model fit
-loo_compare(intercept_loo, public_affairs_loo, political_ideology_loo, social_views_loo, charity_voluntarism_loo, demographics_loo, public_political_loo, public_political_social_loo, public_political_social_charity_loo, public_political_social_charity_demo_loo)
-```
+# Run the model and save data and model output
+fit <- stan(
+  file = here::here("src", "stan_files", "mnl.stan"),
+  data = data_list,
+  iter = 10000,
+  thin = 5,
+  seed = 1234
+)
+run <- list(data = data_list, fit = fit)
+write_rds(run, here::here("data", "raw_data", "model_runs", "mnl.rds"))
+if (interactions == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "mnl_interactions.rds"))
 
-```{r save-fit, eval=FALSE}
-# Create data frame
-model_fit <- tibble(model = rep(NA, 10), elpd_loo = rep(NA, 10))
-
-# Extract PSIS-LOO fit
-model_fit$model[1] <- "intercept"; model_fit$loo[1] <- intercept_loo$elpd_loo
-model_fit$model[2] <- "public_affairs"; model_fit$loo[2] <- public_affairs_loo$elpd_loo
-model_fit$model[3] <- "political_ideology"; model_fit$loo[3] <- political_ideology_loo$elpd_loo
-model_fit$model[4] <- "social_views"; model_fit$loo[4] <- social_views_loo$elpd_loo
-model_fit$model[5] <- "charity_voluntarism"; model_fit$loo[5] <- charity_voluntarism_loo$elpd_loo
-model_fit$model[6] <- "demographics"; model_fit$loo[6] <- demographics_loo$elpd_loo
-model_fit$model[7] <- "public_political"; model_fit$loo[7] <- public_political_loo$elpd_loo
-model_fit$model[8] <- "public_political_social"; model_fit$loo[8] <- public_political_social_loo$elpd_loo
-model_fit$model[9] <- "public_political_social_charity"; model_fit$loo[9] <- public_political_social_charity_loo$elpd_loo
-model_fit$model[10] <- "public_political_social_charity_demo"; model_fit$loo[10] <- public_political_social_charity_demo_loo$elpd_loo
-
-# Save model output
-write_rds(model_fit, here::here("analysis", "output", "tables", "model_fit.rds"))
-```
-
-## Load model fit objects and extract and save draws
-
-```{r extract-draws, eval=FALSE}
-intercept <- 1                            # Intercept-only
-interactions <- 1                         # Include interactions with the intercept-only model
-public_affairs <- 0                       # Public affairs
-political_ideology <- 0                   # Political ideology
-social_views <- 0                         # Social views
-charity_voluntarism <- 0                  # Charity and voluntarism
-demographics <- 0                         # Demographics
-public_political <- 0                     # Public affairs + Political ideology
-public_political_social <- 0              # + Social views
-public_political_social_charity <- 0      # + Charity and voluntarism
-public_political_social_charity_demo <- 0 # + Demographics
-
-# Load and extract data and model output
-if (intercept == 1 & interactions == 0) run <- read_rds(here::here("data", "raw_data", "model_runs", "intercept.rds"))
-if (intercept == 1 & interactions == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "interactions_5d.rds"))
-if (public_affairs == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "public_affairs.rds"))
-if (political_ideology == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "political_ideology.rds"))
-if (social_views == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "social_views.rds"))
-if (charity_voluntarism == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "charity_voluntarism.rds"))
-if (demographics == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "demographics.rds"))
-if (public_political == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political.rds"))
-if (public_political_social == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social.rds"))
-if (public_political_social_charity == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity.rds"))
-if (public_political_social_charity_demo == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity_demo.rds"))
-data <- run$data
-fit <- run$fit
-
-# Extract posterior draws
+# Extract and save posterior draws
 draws <- fit %>% 
@@
 # Save draws
-if (intercept == 1 & interactions == 0) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "intercept.rds"))
-if (intercept == 1 & interactions == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds"))
-if (public_affairs == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_affairs.rds"))
-if (political_ideology == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "political_ideology.rds"))
-if (social_views == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "social_views.rds"))
-if (charity_voluntarism == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "charity_voluntarism.rds"))
-if (demographics == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "demographics.rds"))
-if (public_political == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_political.rds"))
-if (public_political_social == 1)  write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_political_social.rds"))
-if (public_political_social_charity == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_political_social_charity.rds"))
-if (public_political_social_charity_demo == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_political_social_charity_demo.rds"))
+write_rds(draws, here::here("data", "raw_data", "posterior_draws", "mnl.rds"))
+if (interactions == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "mnl_interactions.rds"))
+```
+
+The model is calibrated using a multinomial logit model. Each model passed diagnostics checks, including the absence of divergent transitions, as part of model calibration.
+
+```{stan mnl, output.var="mnl", eval=FALSE}
+// Index values, observations, and covariates.
+data {
+  int<lower = 1> N;                  // Number of observations.
+  int<lower = 2> A;                  // Number of choice alternatives.
+  int<lower = 1> L;                  // Number of (estimable) attribute levels.
+
+  int<lower = 1, upper = A> Y[N];    // Vector of observations.
+  matrix[A, L] X[N];                 // Array of observation-level covariates.
+}
+
+// Parameters for the multinomial logit.
+parameters {
+  vector[L] beta;                    // Vector of aggregate beta coefficients.
+}
+
+// Multinomial logit model.
+model {
+  // Standard normal prior for beta.
+  beta ~ normal(0, 5);
+
+  // Multinomial logit.
+  for (n in 1:N) {
+    Y[n] ~ categorical_logit(X[n] * beta);
+  }
+}
+
+// Quantities conditioned on parameter draws.
+generated quantities {
+  // vector[N] Y_new;   // Vector of predicted choices.
+  vector[N] log_lik; // Log likelihood to estimate loo.
+
+  // Multinomial logit draws and log likelihood per observation.
+  for (n in 1:N) {
+    log_lik[n] = categorical_logit_lpmf(Y[n] | X[n] * beta);
+  }
+}
 ```

### 2023-05-16 analysis/03_mnl_model-calibration.R

@@ -1,197 +1,0 @@
-# Preamble ----------------------------------------------------------------
-# Load packages
-library(tidyverse)
-library(fastDummies)
-library(rstan)
-library(bayesplot)
-library(tidybayes)
-library(loo)
-library(ggridges)
-library(ggraph)
-library(ggdag)
-library(here)
-
-
-# Set Stan options
-options(mc.cores = parallel::detectCores())
-rstan_options(auto_write = TRUE)
-
-# Choose the Model to Run -------------------------------------------------
-intercept <- 1                            # Intercept-only
-public_affairs <- 0                       # Public affairs: Public affairs knowledge + Public affairs activity
-political_ideology <- 0                   # Political ideology
-social_views <- 0                         # Social views: Public affairs trust + Social ideology + Religiosity
-charity_voluntarism <- 0                  # Charity and voluntarism: Charity trust, Charity activity, Volunteer activity, etc
-demographics <- 0                         # Demographics: Gender, Marital status, Education, Income, Race, Age
-public_political <- 0                     # Public affairs + Political ideology
-public_political_social <- 0              # Public affairs + Political ideology + Social views
-public_political_social_charity <- 0      # Public affairs + Political ideology + Social views + Charity and voluntarism
-public_political_social_charity_demo <- 0 # Public affairs + Political ideology + Social views + Charity and voluntarism + Demographics
-
-# Import and Restructure Data ---------------------------------------------
-# Load data and design
-# final_data <- read_rds(here::here("data", "derived_data", "final_data.rds"))
-# X <- read_rds(here::here("data", "derived_data", "final_design.rds"))
-# #
-# # Restructure choice data Y
-# Y <- final_data %>%
-#   select(contains("Q4")) %>%
-#   as.matrix()
-#
-# # Restructure covariate matrix Z
-# if (intercept == 1) {
-#   Z <- matrix(data = 1, nrow = dim(X)[1], ncol = 1)
-# }
-# if (public_affairs == 1) {
-#   Z <- final_data %>%
-#     select(
[…]

### 2023-05-19 analysis/03_analysis.Rmd
Attempting an mnl-index model

@@
 data <- read_rds(here::here("data", "derived_data", "data.rds"))
-X <- read_rds(here::here("data", "derived_data", "mnl_dummy_design.rds"))
+# X <- read_rds(here::here("data", "derived_data", "mnl_dummy_design.rds"))
+X <- read_rds(here::here("data", "derived_data", "mnl_index_design.rds"))
 if (interactions == 1) X <- read_rds(here::here("data", "derived_data", "mnl_dummy_interactions.rds"))
@@
 run <- list(data = data_list, fit = fit)
-write_rds(run, here::here("data", "raw_data", "model_runs", "mnl.rds"))
+# write_rds(run, here::here("data", "raw_data", "model_runs", "mnl.rds"))
+write_rds(run, here::here("data", "raw_data", "model_runs", "mnl_index.rds"))
 if (interactions == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "mnl_interactions.rds"))
@@
 draws <- fit %>% 
-  spread_draws(Gamma[i, j]) %>% 
+  spread_draws(beta[l]) %>% 
   ungroup() %>% 
-  filter(.iteration > 500) %>% 
-  rename(
-    i = j,
-    j = i
-  )
+  filter(.iteration > 500)
 
 # Save draws
-write_rds(draws, here::here("data", "raw_data", "posterior_draws", "mnl.rds"))
+# write_rds(draws, here::here("data", "raw_data", "posterior_draws", "mnl.rds"))
+write_rds(draws, here::here("data", "raw_data", "posterior_draws", "mnl_index.rds"))
 if (interactions == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "mnl_interactions.rds"))

### 2023-05-24 analysis/04_figs-tables.Rmd
Confirmed equivalence between HMNL and MNL draws for the dummy-coded experimental design

@@
 
-# Load packages, data, and draws
+# Load packages and data
 
@@
 results <- read_rds(here("data", "derived_data", "final_data.rds"))
-
+```
+
+# Causal pathway
+
+Our theory and hypotheses are laid out in the causal pathway below.
+Organizational factors (**O**, or organizational practices like financial disclosure and accountability practices; **I**, or issue area; and **F**, or funding) all influence the decision to donate (**D**).
+Structural factors like an NGO's relationship with its host government (**G**) also influence donation behavior, but the relationship itself is shaped by both funding and issue area.
+
+```{r causal-dag, fig.width=13/3, fig.height=2}
+node_colors <- tribble(
+  ~name, ~type,
+  "D", "Outcome",
+  "I", "Organizational factor",
+  "F", "Organizational factor",
+  "O", "Organizational factor",
+  "G", "Structural factor"
+) %>% 
+  mutate(type = fct_inorder(type))
+
+# Set up DAG structure
+theory_dag <- dagify(D ~ I + F + O + G,
+                     G ~ I + F,
+                     outcome = "D",
+                     exposure = "C") %>% 
+  tidy_dagitty(layout = "dh", seed = 1234)
+
+# Add node types/colors to DAG data
+theory_dag$data <- theory_dag$data %>% 
+  left_join(node_colors, by = "name")
+
+# Make DAG plot
+plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
+  geom_dag_point(size = 6, mapping = aes(color = type)) +
+  geom_dag_edges(start_cap = circle(4, "mm"),
+                 end_cap = circle(4, "mm")) +
+  geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
+  scale_color_manual(values = c(clrs$blue, clrs$red, clrs$orange), name = NULL) +
+  theme_ngo() +
+  theme(panel.grid = element_blank(),
+        panel.border = element_blank(),
+        axis.title = element_blank(),
+        axis.text = element_blank())
+
+# Show and save plot
+plot_dag
+ggsave(plot_dag, filename = here("analysis", "output", "figures", "causal-path.pdf"),
+       width = 13/3, height = 2, units = "in", device = cairo_pdf)
+ggsave(plot_dag, filename = here("analysis", "output", "figures", "causal-path.png"),
+       width = 13/3, height = 2, units = "in", type = "cairo", dpi = 300)
+```
+
+# Sample details
+
+```{r}
+vars_to_summarize <- tribble(
+  ~category, ~variable, ~clean_name,
+  "Demographics", "Q5.12", "Gender",
+  "Demographics", "Q5.17", "Age",
+  "Demographics", "Q5.13", "Marital status",
+  "Demographics", "Q5.14", "Education",
+  "Demographics", "Q5.15", "Income",
+  "Attitudes toward charity", "Q2.5", "Frequency of donating to charity",
+  "Attitudes toward charity", "Q2.6", "Amount of donations to charity last year",
+  "Attitudes toward charity", "Q2.7_f", "Importance of trusting charities",
+  "Attitudes toward charity", "Q2.8_f", "Level of trust in charities",
+  "Attitudes toward charity", "Q2.10", "Frequency of volunteering",
+  "Politics, ideology, and religion", "Q2.1", "Frequency of following national news",
+  "Politics, ideology, and religion", "Q5.7", "Traveled to a developing country",
+  "Politics, ideology, and religion", "Q5.1", "Voted in last election",
+  "Politics, ideology, and religion", "Q5.6_f", "Trust in political institutions and the state",
+  "Politics, ideology, and religion", "Q5.2_f", "Political ideology",
+  "Politics, ideology, and religion", "Q5.4", "Involvement in activist causes",
+  "Politics, ideology, and religion", "Q5.8", "Frequency of attending religious services",
+  "Politics, ideology, and religion", "Q5.9", "Importance of religion"
+)
+
+summarize_factor <- function(x) {
+  output <- table(x) %>% 
+    as_tibble() %>% 
+    magrittr::set_colnames(., c("level", "count")) %>% 
+    mutate(level = factor(level, levels = levels(x), ordered = TRUE)) %>%
+    mutate(prop = count / sum(count),
+           nice_prop = scales::percent(prop))
+
+  return(list(output))
+}
+
+participant_summary <- results %>% 
+  select(one_of(vars_to_summarize$variable)) %>% 
+  summarize_all(summarize_factor) %>% 
+  pivot_longer(cols = everything(), names_to = "variable", values_to = "details") %>% 
+  left_join(vars_to_summarize, by = "variable") %>% 
+  unnest(details) %>% 
+  mutate(level = as.character(level)) %>% 
+  mutate(level = case_when(
+    variable == "Q2.7_f" & level == "1" ~ "1 (not important)",
+    variable == "Q2.7_f" & level == "7" ~ "7 (important)",
+    variable == "Q2.8_f" & level == "1" ~ "1 (no trust)",
+    variable == "Q2.8_f" & level == "7" ~ "7 (complete trust)",
+    variable == "Q5.6_f" & level == "1" ~ "1 (no trust)",
+    variable == "Q5.6_f" & level == "7" ~ "7 (complete trust)",
+    variable == "Q5.2_f" & level == "1" ~ "1 (extremely liberal)",
+    variable == "Q5.2_f" & level == "7" ~ "7 (extremely conservative)",
+    variable == "Q5.15" & level == "Less than median" ~ "Less than 2017 national median ($61,372)",
+    variable == "Q5.17" & level == "Less than median" ~ "Less than 2017 national median (36)",
+    TRUE ~ level
+  )) %>% 
+  mutate(clean_name_shrunk = ifelse(clean_name == lag(clean_name), "", clean_name),
+         clean_name_shrunk = ifelse(is.na(clean_name_shrunk), 
+                                    clean_name[1], 
+                                    clean_name_shrunk),
+         category_shrunk = ifelse(category == lag(category), "", category),
+         category_shrunk = ifelse(is.na(category_shrunk), 
+                                    category[1], 
+                                    category_shrunk))
+```
+
+```{r results="asis"}
+participant_summary %>% 
+  select(" " = category_shrunk, "  " = clean_name_shrunk, 
+         "Response" = level, "N" = count, "%" = nice_prop) %>% 
+  pandoc.table.return(caption = 'Summary of individual respondent characteristics {#tbl:sample-details}',
+                      justify = "lllcc") %T>%
+  cat() %>%
+  cat(file = here("analysis", "output", "tables", "tbl-sample-details.md"))
+```
+
+# Compute model fit
+
+## Load model output
+
+```{r load-data-output, warning=FALSE, message=FALSE, eval=FALSE}
+# Load all model output
+intercept_run <- read_rds(here::here("data", "raw_data", "model_runs", "intercept.rds"))
+public_affairs_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_affairs.rds"))
+political_ideology_run <- read_rds(here::here("data", "raw_data", "model_runs", "political_ideology.rds"))
+social_views_run <- read_rds(here::here("data", "raw_data", "model_runs", "social_views.rds"))
+charity_voluntarism_run <- read_rds(here::here("data", "raw_data", "model_runs", "charity_voluntarism.rds"))
+demographics_run <- read_rds(here::here("data", "raw_data", "model_runs", "demographics.rds"))
+public_political_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political.rds"))
+public_political_social_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social.rds"))
+public_political_social_charity_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity.rds"))
+public_political_social_charity_demo_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity_demo.rds"))
+```
+
+## Compute and save model fit
+
+```{r compute-fit, eval=FALSE}
+# Compute fit using PSIS-LOO
+intercept_loo <- loo(intercept_run$fit, save_psis = TRUE)
+public_affairs_loo <- loo(public_affairs_run$fit, save_psis = TRUE)
+political_ideology_loo <- loo(political_ideology_run$fit, save_psis = TRUE)
+social_views_loo <- loo(social_views_run$fit, save_psis = TRUE)
+charity_voluntarism_loo <- loo(charity_voluntarism_run$fit, save_psis = TRUE)
+demographics_loo <- loo(demographics_run$fit, save_psis = TRUE)
+public_political_loo <- loo(public_political_run$fit, save_psis = TRUE)
+public_political_social_loo <- loo(public_political_social_run$fit, save_psis = TRUE)
+public_political_social_charity_loo <- loo(public_political_social_charity_run$fit, save_psis = TRUE)
+public_political_social_charity_demo_loo <- loo(public_political_social_charity_demo_run$fit, save_psis = TRUE)
+
+# Compare model fit
+loo_compare(intercept_loo, public_affairs_loo, political_ideology_loo, social_views_loo, charity_voluntarism_loo, demographics_loo, public_political_loo, public_political_social_loo, public_political_social_charity_loo, public_political_social_charity_demo_loo)
+```
+
+```{r save-fit, eval=FALSE}
+# Create data frame
+model_fit <- tibble(model = rep(NA, 10), elpd_loo = rep(NA, 10))
+
+# Extract PSIS-LOO fit
+model_fit$model[1] <- "intercept"; model_fit$loo[1] <- intercept_loo$elpd_loo
+model_fit$model[2] <- "public_affairs"; model_fit$loo[2] <- public_affairs_loo$elpd_loo
+model_fit$model[3] <- "political_ideology"; model_fit$loo[3] <- political_ideology_loo$elpd_loo
+model_fit$model[4] <- "social_views"; model_fit$loo[4] <- social_views_loo$elpd_loo
+model_fit$model[5] <- "charity_voluntarism"; model_fit$loo[5] <- charity_voluntarism_loo$elpd_loo
+model_fit$model[6] <- "demographics"; model_fit$loo[6] <- demographics_loo$elpd_loo
+model_fit$model[7] <- "public_political"; model_fit$loo[7] <- public_political_loo$elpd_loo
+model_fit$model[8] <- "public_political_social"; model_fit$loo[8] <- public_political_social_loo$elpd_loo
+model_fit$model[9] <- "public_political_social_charity"; model_fit$loo[9] <- public_political_social_charity_loo$elpd_loo
+model_fit$model[10] <- "public_political_social_charity_demo"; model_fit$loo[10] <- public_political_social_charity_demo_loo$elpd_loo
+
+# Save model output
+write_rds(model_fit, here::here("analysis", "output", "tables", "model_fit.rds"))
+```
+
+# Results
+
+## Load draws
+
+```{r hmnl-draws}
 # Load draws
@@
 
-```{r}
+```{r diff-function}
 diff_cols <- function(col1, col2) {
@@
 ```
-
-# Compute model fit
-
-## Load model output
-
-```{r load-data-output, warning=FALSE, message=FALSE, eval=FALSE}
-# Load all model output
-intercept_run <- read_rds(here::here("data", "raw_data", "model_runs", "intercept.rds"))
-public_affairs_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_affairs.rds"))
-political_ideology_run <- read_rds(here::here("data", "raw_data", "model_runs", "political_ideology.rds"))
-social_views_run <- read_rds(here::here("data", "raw_data", "model_runs", "social_views.rds"))
-charity_voluntarism_run <- read_rds(here::here("data", "raw_data", "model_runs", "charity_voluntarism.rds"))
-demographics_run <- read_rds(here::here("data", "raw_data", "model_runs", "demographics.rds"))
-public_political_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political.rds"))
-public_political_social_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social.rds"))
-public_political_social_charity_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity.rds"))
-public_political_social_charity_demo_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity_demo.rds"))
-```
-
-## Compute and save model fit
-
-```{r compute-fit, eval=FALSE}
-# Compute fit using PSIS-LOO
-intercept_loo <- loo(intercept_run$fit, save_psis = TRUE)
-public_affairs_loo <- loo(public_affairs_run$fit, save_psis = TRUE)
-political_ideology_loo <- loo(political_ideology_run$fit, save_psis = TRUE)
-social_views_loo <- loo(social_views_run$fit, save_psis = TRUE)
-charity_voluntarism_loo <- loo(charity_voluntarism_run$fit, save_psis = TRUE)
-demographics_loo <- loo(demographics_run$fit, save_psis = TRUE)
-public_political_loo <- loo(public_political_run$fit, save_psis = TRUE)
-public_political_social_loo <- loo(public_political_social_run$fit, save_psis = TRUE)
-public_political_social_charity_loo <- loo(public_political_social_charity_run$fit, save_psis = TRUE)
-public_political_social_charity_demo_loo <- loo(public_political_social_charity_demo_run$fit, save_psis = TRUE)
-
-# Compare model fit
-loo_compare(intercept_loo, public_affairs_loo, political_ideology_loo, social_views_loo, charity_voluntarism_loo, demographics_loo, public_political_loo, public_political_social_loo, public_political_social_charity_loo, public_political_social_charity_demo_loo)
-```
-
-```{r save-fit, eval=FALSE}
-# Create data frame
-model_fit <- tibble(model = rep(NA, 10), elpd_loo = rep(NA, 10))
-
-# Extract PSIS-LOO fit
-model_fit$model[1] <- "intercept"; model_fit$loo[1] <- intercept_loo$elpd_loo
-model_fit$model[2] <- "public_affairs"; model_fit$loo[2] <- public_affairs_loo$elpd_loo
-model_fit$model[3] <- "political_ideology"; model_fit$loo[3] <- political_ideology_loo$elpd_loo
-model_fit$model[4] <- "social_views"; model_fit$loo[4] <- social_views_loo$elpd_loo
-model_fit$model[5] <- "charity_voluntarism"; model_fit$loo[5] <- charity_voluntarism_loo$elpd_loo
-model_fit$model[6] <- "demographics"; model_fit$loo[6] <- demographics_loo$elpd_loo
-model_fit$model[7] <- "public_political"; model_fit$loo[7] <- public_political_loo$elpd_loo
-model_fit$model[8] <- "public_political_social"; model_fit$loo[8] <- public_political_social_loo$elpd_loo
-model_fit$model[9] <- "public_political_social_charity"; model_fit$loo[9] <- public_political_social_charity_loo$elpd_loo
-model_fit$model[10] <- "public_political_social_charity_demo"; model_fit$loo[10] <- public_political_social_charity_demo_loo$elpd_loo
-
-# Save model output
-write_rds(model_fit, here::here("analysis", "output", "tables", "model_fit.rds"))
-```
-
-# Causal pathway
-
-Our theory and hypotheses are laid out in the causal pathway below.
-Organizational factors (**O**, or organizational practices like financial disclosure and accountability practices; **I**, or issue area; and **F**, or funding) all influence the decision to donate (**D**).
-Structural factors like an NGO's relationship with its host government (**G**) also influence donation behavior, but the relationship itself is shaped by both funding and issue area.
-
-```{r causal-dag, fig.width=13/3, fig.height=2}
-node_colors <- tribble(
-  ~name, ~type,
-  "D", "Outcome",
-  "I", "Organizational factor",
-  "F", "Organizational factor",
-  "O", "Organizational factor",
-  "G", "Structural factor"
-) %>% 
-  mutate(type = fct_inorder(type))
-
-# Set up DAG structure
-theory_dag <- dagify(D ~ I + F + O + G,
-                     G ~ I + F,
-                     outcome = "D",
-                     exposure = "C") %>% 
-  tidy_dagitty(layout = "dh", seed = 1234)
-
-# Add node types/colors to DAG data
-theory_dag$data <- theory_dag$data %>% 
-  left_join(node_colors, by = "name")
-
-# Make DAG plot
-plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
-  geom_dag_point(size = 6, mapping = aes(color = type)) +
-  geom_dag_edges(start_cap = circle(4, "mm"),
-                 end_cap = circle(4, "mm")) +
-  geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
-  scale_color_manual(values = c(clrs$blue, clrs$red, clrs$orange), name = NULL) +
-  theme_ngo() +
-  theme(panel.grid = element_blank(),
-        panel.border = element_blank(),
-        axis.title = element_blank(),
-        axis.text = element_blank())
-
-# Show and save plot
-plot_dag
-ggsave(plot_dag, filename = here("analysis", "output", "figures", "causal-path.pdf"),
-       width = 13/3, height = 2, units = "in", device = cairo_pdf)
-ggsave(plot_dag, filename = here("analysis", "output", "figures", "causal-path.png"),
-       width = 13/3, height = 2, units = "in", type = "cairo", dpi = 300)
-```
-
-# Sample details
-
-```{r}
-vars_to_summarize <- tribble(
-  ~category, ~variable, ~clean_name,
-  "Demographics", "Q5.12", "Gender",
-  "Demographics", "Q5.17", "Age",
-  "Demographics", "Q5.13", "Marital status",
-  "Demographics", "Q5.14", "Education",
-  "Demographics", "Q5.15", "Income",
-  "Attitudes toward charity", "Q2.5", "Frequency of donating to charity",
-  "Attitudes toward charity", "Q2.6", "Amount of donations to charity last year",
-  "Attitudes toward charity", "Q2.7_f", "Importance of trusting charities",
-  "Attitudes toward charity", "Q2.8_f", "Level of trust in charities",
-  "Attitudes toward charity", "Q2.10", "Frequency of volunteering",
-  "Politics, ideology, and religion", "Q2.1", "Frequency of following national news",
-  "Politics, ideology, and religion", "Q5.7", "Traveled to a developing country",
-  "Politics, ideology, and religion", "Q5.1", "Voted in last election",
-  "Politics, ideology, and religion", "Q5.6_f", "Trust in political institutions and the state",
-  "Politics, ideology, and religion", "Q5.2_f", "Political ideology",
-  "Politics, ideology, and religion", "Q5.4", "Involvement in activist causes",
-  "Politics, ideology, and religion", "Q5.8", "Frequency of attending religious services",
-  "Politics, ideology, and religion", "Q5.9", "Importance of religion"
-)
-
-summarize_factor <- function(x) {
-  output <- table(x) %>% 
-    as_tibble() %>% 
-    magrittr::set_colnames(., c("level", "count")) %>% 
-    mutate(level = factor(level, levels = levels(x), ordered = TRUE)) %>%
-    mutate(prop = count / sum(count),
-           nice_prop = scales::percent(prop))
-
-  return(list(output))
-}
-
-participant_summary <- results %>% 
-  select(one_of(vars_to_summarize$variable)) %>% 
-  summarize_all(summarize_factor) %>% 
-  pivot_longer(cols = everything(), names_to = "variable", values_to = "details") %>% 
-  left_join(vars_to_summarize, by = "variable") %>% 
-  unnest(details) %>% 
-  mutate(level = as.character(level)) %>% 
-  mutate(level = case_when(
-    variable == "Q2.7_f" & level == "1" ~ "1 (not important)",
-    variable == "Q2.7_f" & level == "7" ~ "7 (important)",
-    variable == "Q2.8_f" & level == "1" ~ "1 (no trust)",
-    variable == "Q2.8_f" & level == "7" ~ "7 (complete trust)",
-    variable == "Q5.6_f" & level == "1" ~ "1 (no trust)",
-    variable == "Q5.6_f" & level == "7" ~ "7 (complete trust)",
-    variable == "Q5.2_f" & level == "1" ~ "1 (extremely liberal)",
-    variable == "Q5.2_f" & level == "7" ~ "7 (extremely conservative)",
-    variable == "Q5.15" & level == "Less than median" ~ "Less than 2017 national median ($61,372)",
-    variable == "Q5.17" & level == "Less than median" ~ "Less than 2017 national median (36)",
-    TRUE ~ level
-  )) %>% 
-  mutate(clean_name_shrunk = ifelse(clean_name == lag(clean_name), "", clean_name),
-         clean_name_shrunk = ifelse(is.na(clean_name_shrunk), 
-                                    clean_name[1], 
-                                    clean_name_shrunk),
-         category_shrunk = ifelse(category == lag(category), "", category),
-         category_shrunk = ifelse(is.na(category_shrunk), 
-                                    category[1], 
-                                    category_shrunk))
-```
-
-```{r results="asis"}
-participant_summary %>% 
-  select(" " = category_shrunk, "  " = clean_name_shrunk, 
-         "Response" = level, "N" = count, "%" = nice_prop) %>% 
-  pandoc.table.return(caption = 'Summary of individual respondent characteristics {#tbl:sample-details}',
-                      justify = "lllcc") %T>%
-  cat() %>%
-  cat(file = here("analysis", "output", "tables", "tbl-sample-details.md"))
-```
-
-# Results
 
@@
 )
+```
+
+## Plot MNL draws, experimental alternative
+
+```{r plot-mnl-marginals}
+################################################################################
+# A flat MNL is an experimental alternative for dealing with interactions.
+################################################################################
+
+mnl_dummy_draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "mnl.rds"))
+mnl_index_draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "mnl_index.rds"))
+
+# Name levels labels
+dummy_level_labels <- c(
+  str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
+  str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
+  str_c("Organizational practices: ", c("Financial transparency", "Accountability")),
+  str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants")),
+  str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))
+)
+
+dummy_level_lookup <- tibble(levels = dummy_level_labels) %>%
+  separate(levels, c("attribute", "level"), sep = ": ") %>%
+  mutate(levels_long = paste0(attribute, ": ", level),
+         i = 1:n()) %>%
+  mutate_at(vars(attribute, level, levels_long), list(fct_inorder))
+
+# Name levels labels (index-coded)
+index_level_labels <- c(
+  str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
+  str_c("Issue area: ", c("Emergency response", "Environment", "Human rights", "Refugee relief")),
+  str_c("Organizational practices: ", c("Financial transparency", "Accountability")),
+  str_c("Funding sources: ", c("Many small private donations", "Handful of wealthy private donors", "Government grants")),
+  str_c("Relationship with host government: ", c("Friendly", "Criticized", "Under crackdown"))
+)
+
+index_level_lookup <- tibble(levels = index_level_labels) %>%
+  separate(levels, c("attribute", "level"), sep = ": ") %>%
+  mutate(levels_long = paste0(attribute, ": ", level),
+         i = 1:n()) %>%
+  mutate_at(vars(attribute, level, levels_long), list(fct_inorder))
+
+# Join level and covariate labels to draws
+mnl_dummy_draws <- mnl_dummy_draws %>%
+  rename(i = l) %>%
+  left_join(dummy_level_lookup, by = "i")
+
+mnl_index_draws <- mnl_index_draws %>%
+  rename(i = l) %>%
+  left_join(index_level_lookup, by = "i")
+
+# Plot marginals.
+mnl_dummy_draws %>%
+  ggplot(aes(x = beta, y = levels_long)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Attribute Levels")
+
+ggsave(
+  "marginal-posteriors_mnl-intercept.png",
+  path = here::here("analysis", "output", "figures"),
+  width = width_length[1],
+  height = width_length[2],
+  units = "in"
+)
+
+mnl_index_draws %>%
+  ggplot(aes(x = beta, y = levels_long)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Attribute Levels")
 ```

### 2023-05-24 analysis/04a_mnl_contrasts.R

@@ -1,170 +1,0 @@
-# All hypotheses
-
-draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "mnl_aggregate_dummy_draws.rds")) %>%
-  rename(i=l)
-
-
-# Reference Level = Friendly relationship with government
-# Compute the contrasts
-contrasts_int <- tibble(
-  # Attribute levels
-  h1_high = draws %>% filter(i == 1) %>% select(beta) %>% pull(),
-  h1_low = draws %>% filter(i == 2) %>% select(beta) %>% pull(),
-  # h2a_high = draws %>% filter(i == 3) %>% select(beta) %>% pull(),
-  h3a_high = draws %>% filter(i == 4)%>% select(beta) %>% pull(),
-  h4a_high = draws %>% filter(i == 5)%>% select(beta) %>% pull(),
-  h5a_high = draws %>% filter(i == 6) %>% select(beta) %>% pull(),
-  h2b_high = draws %>% filter(i == 7)%>% select(beta) %>% pull(),
-  h2b_low = draws %>% filter(i == 8)%>% select(beta) %>% pull(),
-  # h3b_high = draws %>% filter(i == 9)%>% select(beta) %>% pull(),
-  # h3b_low = draws %>% filter(i == 10)%>% select(beta) %>% pull(),
-  h4b_high = draws %>% filter(i == 11)%>% select(beta) %>% pull(),
-  h5b_high = draws %>% filter(i == 12)%>% select(beta) %>% pull(),
-  h4c_high = draws %>% filter(i == 13)%>% select(beta) %>% pull(),
-  h5c_high = draws %>% filter(i == 14)%>% select(beta) %>% pull(),
-  h5d_high = draws %>% filter(i == 15)%>% select(beta) %>% pull(),
-  h5e_high = draws %>% filter(i == 16)%>% select(beta) %>% pull()
-)
-
-# Plot the contrasts
-contrasts_int %>%
-  pivot_longer(
-    h1_high:h5e_high,
-    names_to = "level", values_to = "beta"
-  ) %>%
-  mutate(level = fct_rev(fct_inorder(level))) %>%
-  ggplot(aes(x = beta, y = level)) +
-  stat_halfeye(.width = .95) +
-  geom_vline(xintercept = 0, color = "grey") +
-  labs(y = "Contrasts", x = "Difference in betas")
-
-# Save plot
-
-
-
[…]

### 2023-05-24 analysis/04b_mnl_figs-tables.R

@@ -1,24 +1,0 @@
-library(tidyverse)
-library(magrittr)
-library(tidybayes)
-library(broom)
-library(ggridges)
-library(ggraph)
-library(ggdag)
-library(pander)
-library(patchwork)
-library(scales)
-library(here)
-
-# Load custom plot functions
-source(here("R", "graphics.R"))
-
-# General settings
-source(here("analysis", "options.R"))
-
-# Make all the randomness reproducible
-set.seed(1234)
-
-fitted_model = read_rds(here::here("analysis", "output", "model_runs", "mnl_dummy_intercept.rds"))
-
-draws = as.tibble(fitted_model)

### 2023-05-25 analysis/02_clean-data.Rmd
Updated indexed designs with an outside good indicator

@@
 
-# Create the arrays for the design, including a brand intercept.
+# Create the arrays for the design, including a brand intercept and the outside option coded as an indicator.
 index_X <- array(
@@
     (max(index_design$alt) + 1),  # Number of product alternatives per choice task.
-    (ncol(index_design) - 3)      # Number of (estimable) attribute levels.
+    # (ncol(index_design) - 3)      # Number of (estimable) attribute levels.
+    (ncol(index_design) - 3 + 1)  # Number of (estimable) attribute levels.
   )
@@
 
-# Create the arrays for a design, including a brand intercept and interactions.
+# Create the arrays for a design, including a brand intercept, 
+# interactions, and the outside option coded as an indicator.
 index_interactions_X <- array(
@@
     (max(index_interactions_design$alt) + 1),  # Number of product alternatives per choice task.
-    (ncol(index_interactions_design) - 3)      # Number of (estimable) attribute levels.
-  )
-)
-
-# Add the outside option coded as all zeros (org1 and former reference levels already included).
+    # (ncol(index_interactions_design) - 3)      # Number of (estimable) attribute levels.
+    (ncol(index_interactions_design) - 3 + 1)  # Number of (estimable) attribute levels.
+  )
+)
+
+# Add the outside option coded as an indicator (org1 and former reference levels already included).
 for (n in 1:dim(index_X)[1]) {
@@
       filter(task == s) %>%
-      select(org1:gov_rel3)
+      mutate(out = 0) %>% # Add out column
+      select(out, org1:gov_rel3)
     interactions_X_s <- interactions_X_n %>%
       filter(task == s) %>%
-      select(which(names(interactions_X_n) == "org1"):ncol(interactions_X_n))
+      mutate(out = 0) %>% # Add out column
+      select(out, which(names(interactions_X_n) == "org1"):ncol(interactions_X_n))
     # Save modified design, including outside option.
-    index_X[n, s,,] <- rbind(index_X_s, rep(0, ncol(index_X_s))) %>% as.matrix()
-    index_interactions_X[n, s,,] <- rbind(interactions_X_s, rep(0, ncol(interactions_X_s))) %>% as.matrix()
+    # index_X[n, s,,] <- rbind(index_X_s, rep(0, ncol(index_X_s))) %>% as.matrix()
+    # index_interactions_X[n, s,,] <- rbind(interactions_X_s, rep(0, ncol(interactions_X_s))) %>% as.matrix()
+    index_X[n, s,,] <- rbind(index_X_s, c(1, rep(0, ncol(index_X_s) - 1))) %>% as.matrix()
+    index_interactions_X[n, s,,] <- rbind(interactions_X_s, c(1, rep(0, ncol(interactions_X_s) - 1))) %>% 
+      as.matrix()
   }
@@
 
-# Create the arrays for the design, including a brand intercept.
+# Create the arrays for the design, including a brand intercept and the outside option coded as an indicator.
 flat_index_X <- array(
@@
     (max(index_design$alt) + 1),         # Number of product alternatives per observation.
-    (ncol(index_design) - 3)             # Number of (estimable) attribute levels.
-  )
-)
-
-# Create the arrays for a design, including a brand intercept and interactions.
+    # (ncol(index_design) - 3)             # Number of (estimable) attribute levels.
+    (ncol(index_design) - 3 + 1)         # Number of (estimable) attribute levels.
+  )
+)
+
+# Create the arrays for a design, including a brand intercept, 
+# interactions, and the outside option coded as an indicator.
 flat_index_interactions_X <- array(
@@
     (max(index_interactions_design$alt) + 1),         # Number of product alternatives per observation.
-    (ncol(index_interactions_design) - 3)             # Number of (estimable) attribute levels.
+    # (ncol(index_interactions_design) - 3)             # Number of (estimable) attribute levels.
+    (ncol(index_interactions_design) - 3 + 1)         # Number of (estimable) attribute levels.
   )

### 2023-06-10 analysis/02_clean-data.Rmd
Experimenting with new priors and old encoding of outside good

--- 2023-05-16 analysis/02_clean-data.Rmd
@@
     (ncol(index_design) - 3)      # Number of (estimable) attribute levels.
+    # (ncol(index_design) - 3 + 1)  # Number of (estimable) attribute levels. OUTSIDE GOOD DUMMY.
   )
@@
 
-# Create the arrays for a design, including a brand intercept and interactions.
+# Create the arrays for a design, including interactions.
 index_interactions_X <- array(
@@
     (ncol(index_interactions_design) - 3)      # Number of (estimable) attribute levels.
-  )
-)
-
-# Add the outside option coded as all zeros (org1 and former reference levels already included).
+    # (ncol(index_interactions_design) - 3 + 1)  # Number of (estimable) attribute levels. OUTSIDE GOOD DUMMY.
+  )
+)
+
+# Add the outside option (org1 and former reference levels already included).
 for (n in 1:dim(index_X)[1]) {
@@
       select(org1:gov_rel3)
+      # ADD OutSIDE GOOD DUMMY COLUMN  
+      # mutate(out = 0) %>% 
+      # select(out, org1:gov_rel3)
     interactions_X_s <- interactions_X_n %>%
@@
       select(which(names(interactions_X_n) == "org1"):ncol(interactions_X_n))
+      # ADD OutSIDE GOOD DUMMY COLUMN
+      # mutate(out = 0) %>% 
+      # select(out, which(names(interactions_X_n) == "org1"):ncol(interactions_X_n))
     # Save modified design, including outside option.
@@
     index_interactions_X[n, s,,] <- rbind(interactions_X_s, rep(0, ncol(interactions_X_s))) %>% as.matrix()
+    # OUTSIDE GOOD DUMMY.
+    # index_X[n, s,,] <- rbind(index_X_s, c(1, rep(0, ncol(index_X_s) - 1))) %>% as.matrix()
+    # index_interactions_X[n, s,,] <- rbind(interactions_X_s, c(1, rep(0, ncol(interactions_X_s) - 1))) %>% 
+    #   as.matrix()
   }
@@
 
-# Create the arrays for the design, including a brand intercept.
+# Create the arrays for the design.
 flat_index_X <- array(
@@
     (ncol(index_design) - 3)             # Number of (estimable) attribute levels.
-  )
-)
-
-# Create the arrays for a design, including a brand intercept and interactions.
+    # (ncol(index_design) - 3 + 1)         # Number of (estimable) attribute levels. OUTSIDE GOOD DUMMY.
+  )
+)
+
+# Create the arrays for a design, including interactions.
 flat_index_interactions_X <- array(
@@
     (ncol(index_interactions_design) - 3)             # Number of (estimable) attribute levels.
+    # (ncol(index_interactions_design) - 3 + 1)         # Number of (estimable) attribute levels. OUTSIDE GOOD DUMMY.
   )

### 2023-06-10 analysis/03_analysis.Rmd
Experimenting with new priors and old encoding of outside good

@@
 # write_rds(run, here::here("data", "raw_data", "model_runs", "mnl.rds"))
-write_rds(run, here::here("data", "raw_data", "model_runs", "mnl_index.rds"))
+write_rds(run, here::here("data", "raw_data", "model_runs", "mnl_index_02.rds"))
 if (interactions == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "mnl_interactions.rds"))
@@
 # write_rds(draws, here::here("data", "raw_data", "posterior_draws", "mnl.rds"))
-write_rds(draws, here::here("data", "raw_data", "posterior_draws", "mnl_index.rds"))
+write_rds(draws, here::here("data", "raw_data", "posterior_draws", "mnl_index_02.rds"))
 if (interactions == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "mnl_interactions.rds"))

### 2023-06-15 analysis/04_figs-tables.Rmd
Renamed final_data

@@
 # Load data
-results <- read_rds(here("data", "derived_data", "final_data.rds"))
+results <- read_rds(here("data", "derived_data", "data.rds"))
 ```
@@
 mnl_index_draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "mnl_index.rds"))
+mnl_index_02_draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "mnl_index_02.rds"))
 
@@
 
+mnl_index_02_draws <- mnl_index_02_draws %>%
+  rename(i = l) %>%
+  left_join(index_level_lookup, by = "i")
+
 # Plot marginals.
@@
 mnl_index_draws %>%
+  ggplot(aes(x = beta, y = levels_long)) +
+  stat_halfeye(.width = .95) +
+  geom_vline(xintercept = 0, color = "grey") +
+  labs(y = "Attribute Levels")
+
+mnl_index_02_draws %>%
   ggplot(aes(x = beta, y = levels_long)) +

### 2023-08-03 analysis/02_clean-data.Rmd
Included tidy data, where each choice alternative has its own row for each respondent

@@
 
+# Tidy joined data
+
+Creating a tidy version of the joined data -- the cleaned data and the dummy-coded design.
+
+```{r tidy-joined-data}
+# Create a data frame with one row per respondent choice and a list-column for the design.
+tidy_dummy_X <- tibble(
+  id = rep(1:dim(dummy_X)[1], dim(dummy_X)[2]) %>% sort(),
+  choice = rep(1:dim(dummy_X)[2], dim(dummy_X)[1]),
+  X = vector(mode = "list", length = dim(dummy_X)[1] * dim(dummy_X)[2])
+)
+ind <- 0
+for (i in 1:dim(dummy_X)[1]) {
+  for (j in 1:dim(dummy_X)[2]) {
+    ind = ind + 1
+    tidy_dummy_X$X[[ind]] = dummy_X[i,j,,]
+  }
+}
+
+# test_id = 425; test_choice = 9
+# test_01 <- tidy_dummy_X |> 
+#   filter(id == test_id, choice == test_choice) |> 
+#   select(X) |> unnest(cols = c(X)) |> as.matrix()
+# sum(test_01 != dummy_X[test_id,test_choice,,])
+
+# Unnest each design matrix X.
+tidy_dummy_X <- tidy_dummy_X %>%
+  unnest(X) %>% 
+  mutate(alt = rep(1:dim(dummy_X)[3], dim(dummy_X)[1] * dim(dummy_X)[2])) %>%
+  relocate(alt, .after = choice)
+
+# Pivot the data by choice and create a unique id for each row and join.
+tidy_data <- tidy_dummy_X %>%
+  left_join(
+    data %>%
+      pivot_longer(cols = contains("Q4"), names_to = "choice", values_to = "Y") %>%
+      # select(id, choice, Y) |>
+      separate(choice, into = c("temp", "choice")) %>%
+      mutate(choice = as.integer(choice)) %>%
+      select(-temp),
+    by = c("id", "choice")) %>%
+  relocate(Y, .after = alt)
+
+tidy_data
+```
+
 # Save clean data with transformations
@@
 write_rds(data, here("data", "derived_data", "data.rds"))
+write_rds(tidy_data, here("data", "derived_data", "tidy_data.rds"))
 write_rds(dummy_X, here("data", "derived_data", "hmnl_dummy_design.rds"))

### 2023-08-26 analysis/01_experimental-design.Rmd

--- 2023-05-15 analysis/01_experimental-design.Rmd
@@
 
-# Dummy-coded interactions
+# Code all possible interactions
 
-We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need to specific each of the needed interactions.
+We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need to specify each of the needed interactions.
 
@@
 
-# Index-code the design
+# Index-coded experimental alternative
 
-Now we prepare the experimental design for use in estimating the model by keeping each level of each attribute, which are all discrete. An index-coded design has no reference levels.
+It's possible an index-coded design will serve us better, allowing us to compute whatever contrasts are needed from a single model. An index-coded design has no reference levels.
 
 ```{r index-design, warning=FALSE, message=FALSE}
+################################################################################
+# This is an experimental alternative to the dummy-coded design.
+################################################################################
+
 # Convert the attributes in design into factors
@@
 
-# Index-coded interactions
-
-We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need to specific each of the needed interactions.
+We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need to specify each of the needed interactions.
 
 ```{r index-interactions, warning=FALSE, message=FALSE}
+################################################################################
+# This is an experimental alternative to the interactions based on the 
+# dummy-coded design.
+################################################################################
+
 # Convert the attributes in design into factors
@@
   mutate(
-    # # Hypothesis 2b.
-    # amnesty_criticized = org1 * gov_rel2,
-    # greenpeace_criticized = org2 * gov_rel2,
-    # oxfam_criticized = org3 * gov_rel2,
-    # redcross_criticized = org4 * gov_rel2,
-    # amnesty_crackdown = org1 * gov_rel3,
-    # greenpeace_crackdown = org2 * gov_rel3,
-    # oxfam_crackdown = org3 * gov_rel3,
-    # redcross_crackdown = org4 * gov_rel3,
+    # Hypothesis 2b.
+    amnesty_criticized = org1 * gov_rel2,
+    greenpeace_criticized = org2 * gov_rel2,
+    oxfam_criticized = org3 * gov_rel2,
+    redcross_criticized = org4 * gov_rel2,
+    amnesty_crackdown = org1 * gov_rel3,
+    greenpeace_crackdown = org2 * gov_rel3,
+    oxfam_crackdown = org3 * gov_rel3,
+    redcross_crackdown = org4 * gov_rel3,
     # Hypothesis 3b.
@@
     humanrights_crackdown = issue3 * gov_rel3,
-    refugees_crackdown = issue4 * gov_rel3
-    # # Hypothesis 4b.
-    # smalldonors_criticized = fund1 * gov_rel2,
-    # wealthydonors_criticized = fund2 * gov_rel2,
-    # govgrants_criticized = fund3 * gov_rel2,
-    # smalldonors_crackdown = fund1 * gov_rel3,
-    # wealthydonors_crackdown = fund2 * gov_rel3,
-    # govgrants_crackdown = fund3 * gov_rel3,
-    # # Hypothesis 4c.
-    # emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
-    # emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3, # ??????
-    # emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,     # ??????
-    # environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
-    # environment_wealthydonors_crackdown = issue2 * fund2 * gov_rel3,
-    # environment_govgrants_crackdown = issue2 * fund3 * gov_rel3,
-    # humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
-    # humanrights_wealthydonors_crackdown = issue3 * fund2 * gov_rel3,
-    # humanrights_govgrants_crackdown = issue3 * fund3 * gov_rel3,
-    # refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
-    # refugees_wealthydonors_crackdown = issue4 * fund2 * gov_rel3,
-    # refugees_govgrants_crackdown = issue4 * fund3 * gov_rel3,
-    # # Hypothesis 5b.
-    # nottransp_criticized = transp1 * gov_rel2,
-    # transp_criticized = transp2 * gov_rel2,
-    # nottransp_crackdown = transp1 * gov_rel3,
-    # transp_crackdown = transp2 * gov_rel3,
-    # # Hypothesis 5c.
-    # nottransp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
-    # transp_smalldonors_criticized = transp2 * fund1 * gov_rel2,
-    # nottransp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
-    # transp_wealthydonors_criticized = transp2 * fund2 * gov_rel2,
-    # nottransp_govgrants_criticized = transp1 * fund3 * gov_rel2,
-    # transp_govgrants_criticized = transp2 * fund3 * gov_rel2,
-    # nottransp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
-    # transp_smalldonors_crackdown = transp2 * fund1 * gov_rel3,
-    # nottransp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
-    # transp_wealthydonors_crackdown = transp2 * fund2 * gov_rel3,
-    # nottransp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
-    # transp_govgrants_crackdown = transp2 * fund3 * gov_rel3,
-    # # Hypothesis 5d.
-    # nottransp_emergency_criticized = transp1 * issue1 * gov_rel2,
-    # transp_emergency_criticized = transp2 * issue1 * gov_rel2,
-    # nottransp_emergency_crackdown = transp1 * issue1 * gov_rel3,
-    # transp_emergency_crackdown = transp2 * issue1 * gov_rel3,
-    # nottransp_environment_criticized = transp1 * issue2 * gov_rel2,
-    # transp_environment_criticized = transp2 * issue2 * gov_rel2,
-    # nottransp_environment_crackdown = transp1 * issue2 * gov_rel3,
-    # transp_environment_crackdown = transp2 * issue2 * gov_rel3,
-    # nottransp_humanrights_criticized = transp1 * issue3 * gov_rel2,
-    # transp_humanrights_criticized = transp2 * issue3 * gov_rel2,
-    # nottransp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
-    # transp_humanrights_crackdown = transp2 * issue3 * gov_rel3,
-    # nottransp_refugees_criticized = transp1 * issue4 * gov_rel2,
-    # transp_refugees_criticized = transp2 * issue4 * gov_rel2,
-    # nottransp_refugees_crackdown = transp1 * issue4 * gov_rel3,
-    # transp_refugees_crackdown = transp2 * issue4 * gov_rel3,
-    # # Hypothesis 5e.
-    # nottransp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
-    # transp_smalldonors_emergency_criticized = transp2 * fund1 * issue1 * gov_rel2,
-    # nottransp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
-    # transp_smalldonors_emergency_crackdown = transp2 * fund1 * issue1 * gov_rel3,
-    # nottransp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
-    # transp_smalldonors_environment_criticized = transp2 * fund1 * issue2 * gov_rel2,
-    # nottransp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
-    # transp_smalldonors_environment_crackdown = transp2 * fund1 * issue2 * gov_rel3,
-    # nottransp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
-    # transp_smalldonors_humanrights_criticized = transp2 * fund1 * issue3 * gov_rel2,
-    # nottransp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
-    # transp_smalldonors_humanrights_crackdown = transp2 * fund1 * issue3 * gov_rel3,
-    # nottransp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
-    # transp_smalldonors_refugees_criticized = transp2 * fund1 * issue4 * gov_rel2,
-    # nottransp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
-    # transp_smalldonors_refugees_crackdown = transp2 * fund1 * issue4 * gov_rel3
+    refugees_crackdown = issue4 * gov_rel3,
+    # Hypothesis 4b.
+    smalldonors_criticized = fund1 * gov_rel2,
+    wealthydonors_criticized = fund2 * gov_rel2,
+    govgrants_criticized = fund3 * gov_rel2,
+    smalldonors_crackdown = fund1 * gov_rel3,
+    wealthydonors_crackdown = fund2 * gov_rel3,
+    govgrants_crackdown = fund3 * gov_rel3,
+    # Hypothesis 4c.
+    emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
+    emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3, # ??????
+    emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,     # ??????
+    environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
+    environment_wealthydonors_crackdown = issue2 * fund2 * gov_rel3,
+    environment_govgrants_crackdown = issue2 * fund3 * gov_rel3,
+    humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
+    humanrights_wealthydonors_crackdown = issue3 * fund2 * gov_rel3,
+    humanrights_govgrants_crackdown = issue3 * fund3 * gov_rel3,
+    refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
+    refugees_wealthydonors_crackdown = issue4 * fund2 * gov_rel3,
+    refugees_govgrants_crackdown = issue4 * fund3 * gov_rel3,
+    # Hypothesis 5b.
+    nottransp_criticized = transp1 * gov_rel2,
+    transp_criticized = transp2 * gov_rel2,
+    nottransp_crackdown = transp1 * gov_rel3,
+    transp_crackdown = transp2 * gov_rel3,
+    # Hypothesis 5c.
+    nottransp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
+    transp_smalldonors_criticized = transp2 * fund1 * gov_rel2,
+    nottransp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
+    transp_wealthydonors_criticized = transp2 * fund2 * gov_rel2,
+    nottransp_govgrants_criticized = transp1 * fund3 * gov_rel2,
+    transp_govgrants_criticized = transp2 * fund3 * gov_rel2,
+    nottransp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
+    transp_smalldonors_crackdown = transp2 * fund1 * gov_rel3,
+    nottransp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
+    transp_wealthydonors_crackdown = transp2 * fund2 * gov_rel3,
+    nottransp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
+    transp_govgrants_crackdown = transp2 * fund3 * gov_rel3,
+    # Hypothesis 5d.
+    nottransp_emergency_criticized = transp1 * issue1 * gov_rel2,
+    transp_emergency_criticized = transp2 * issue1 * gov_rel2,
+    nottransp_emergency_crackdown = transp1 * issue1 * gov_rel3,
+    transp_emergency_crackdown = transp2 * issue1 * gov_rel3,
+    nottransp_environment_criticized = transp1 * issue2 * gov_rel2,
+    transp_environment_criticized = transp2 * issue2 * gov_rel2,
+    nottransp_environment_crackdown = transp1 * issue2 * gov_rel3,
+    transp_environment_crackdown = transp2 * issue2 * gov_rel3,
+    nottransp_humanrights_criticized = transp1 * issue3 * gov_rel2,
+    transp_humanrights_criticized = transp2 * issue3 * gov_rel2,
+    nottransp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
+    transp_humanrights_crackdown = transp2 * issue3 * gov_rel3,
+    nottransp_refugees_criticized = transp1 * issue4 * gov_rel2,
+    transp_refugees_criticized = transp2 * issue4 * gov_rel2,
+    nottransp_refugees_crackdown = transp1 * issue4 * gov_rel3,
+    transp_refugees_crackdown = transp2 * issue4 * gov_rel3,
+    # Hypothesis 5e.
+    nottransp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
+    transp_smalldonors_emergency_criticized = transp2 * fund1 * issue1 * gov_rel2,
+    nottransp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
+    transp_smalldonors_emergency_crackdown = transp2 * fund1 * issue1 * gov_rel3,
+    nottransp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
+    transp_smalldonors_environment_criticized = transp2 * fund1 * issue2 * gov_rel2,
+    nottransp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
+    transp_smalldonors_environment_crackdown = transp2 * fund1 * issue2 * gov_rel3,
+    nottransp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
+    transp_smalldonors_humanrights_criticized = transp2 * fund1 * issue3 * gov_rel2,
+    nottransp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
+    transp_smalldonors_humanrights_crackdown = transp2 * fund1 * issue3 * gov_rel3,
+    nottransp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
+    transp_smalldonors_refugees_criticized = transp2 * fund1 * issue4 * gov_rel2,
+    nottransp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
+    transp_smalldonors_refugees_crackdown = transp2 * fund1 * issue4 * gov_rel3
   )
@@
 
-# Aggregate-coded interactions
-
-We have a number of hypotheses referencing specific interactions.
-To answer these hypotheses, we need to specific each of the needed interactions.
-Here we do it by aggregating up the interaction terms.
+## Aggregate-coded interaction alternative
 
 ```{r aggregate-interactions, warning=FALSE, message=FALSE}
+################################################################################
+# This is an experimental alternative where specific contrasts are estimated
+# as part of the model (hence aggregate-coded) rather than computed using
+# marginal posteriors after estimation.
+################################################################################
+
 # Convert the attributes in design into factors
@@
 
-# # org1 = amnesty
-# # org2 = greenpeace
-# # org3 = oxfam
-# # org4 = redcross
-# # gov_rel1 = friendly
-# # gov_rel2 = criticized
-# # gov_rel3 = crackdown
-# 
+################################################################################
+# Are we sure this is encoding the needed contrasts exactly??
+################################################################################
+
 # # Build out all the necessary interactions...
 # # ...by multiplying together the needed index-coded levels.
-# interactions <- interactions %>% 
-#   as_tibble() %>% 
-#   mutate(
-#     h2b_1 = ifelse(Organization ==3|Organization==4, 1, 0), # 1 if org is oxfam or redcross
-#     h2b_2 = ifelse(`Relationship with host government` == 2|`Relationship with host government` == 3, 1, 0), # 1 if gov_rel is criticized or crackdown
-#     h2b_3 = h2b_1*h2b_2 # interaction term
-#     )
+# org1 = amnesty
+# org2 = greenpeace
+# org3 = oxfam
+# org4 = redcross
+# gov_rel1 = friendly
+# gov_rel2 = criticized
+# gov_rel3 = crackdown
+# issue1 = emergency
+# issue2 = environment
+# issue3 = human rights
+# issue4 = refugee
+# transp1 = not transparent
+# transp2 = transparent
+# account1 = not accountable
+# account2 = accountable
+# fund1 = smalldonors
+# fund2 = wealthydonors
+# fund3 = gov grants
 
-interactions <- interactions |> 
+# Sticking exactly to the hypotheses where each contrasts will 
+# consist of h*_high - h*_low
+interactions <- interactions %>% 
+  as_tibble() %>% 
+  rowwise() %>% 
   mutate(
-    # Oxfam or Red Cross.
-    h2b_org_1 = ifelse(org3 == 1 | org4 == 1, 1, 0),
-    # Government crackdown or criticism.
-    h2b_gov_rel_1 = ifelse(gov_rel2 == 1 | gov_rel3 == 1, 1, 0),
-    # Oxfam or Red Cross facing government crackdown or criticism.
-    h2b_int_1 = ifelse(org3 == 1 | org4 == 1, 1, 0) * ifelse(gov_rel2 == 1 | gov_rel3 == 1, 1, 0),
-    # Amnesty or Greenpeace.
-    h2b_org_2 = ifelse(org1 == 1 | org2 == 1, 1, 0),
-    # Government crackdown.
-    h2b_gov_rel_2 = gov_rel3,
-    # Amnesty or Greenpeace is facing crackdown.
-    # h2b_2 = ifelse(org1 == 1 | org2 == 1, 1, 0) * gov_rel3
-    h2b_int_2 = ifelse(org1 == 1 | org2 == 1, 1, 0) * gov_rel3
-  )
-  # select(1:3, contains("h2b"))
-
-# interactions |> 
-#   # select(org1:org4, gov_rel2:gov_rel3, h2b_1, h2b_2)
-#   # select(org3, org4, gov_rel2, gov_rel3, h2b_1)
-#   select(org1, org2, gov_rel3, h2b_2)
-
-# Build out all the necessary interactions
-# interactions <- interactions %>% 
-#   as_tibble() %>% 
-#   mutate(
-#     # Hypothesis 2b.
-#     amnesty_criticized = org1 * gov_rel2,
-#     greenpeace_criticized = org2 * gov_rel2,
-#     oxfam_criticized = org3 * gov_rel2,
-#     redcross_criticized = org4 * gov_rel2,
-#     amnesty_crackdown = org1 * gov_rel3,
-#     greenpeace_crackdown = org2 * gov_rel3,
-#     oxfam_crackdown = org3 * gov_rel3,
-#     redcross_crackdown = org4 * gov_rel3,
-#     # Hypothesis 3b.
-#     emergency_criticized = issue1 * gov_rel2,
-#     environment_criticized = issue2 * gov_rel2,
-#     humanrights_criticized = issue3 * gov_rel2,
-#     refugees_criticized = issue4 * gov_rel2,
-#     emergency_crackdown = issue1 * gov_rel3,
-#     environment_crackdown = issue2 * gov_rel3,
-#     humanrights_crackdown = issue3 * gov_rel3,
-#     refugees_crackdown = issue4 * gov_rel3,
-#     # Hypothesis 4b.
-#     smalldonors_criticized = fund1 * gov_rel2,
-#     wealthydonors_criticized = fund2 * gov_rel2,
-#     govgrants_criticized = fund3 * gov_rel2,
-#     smalldonors_crackdown = fund1 * gov_rel3,
-#     wealthydonors_crackdown = fund2 * gov_rel3,
-#     govgrants_crackdown = fund3 * gov_rel3,
-#     # Hypothesis 4c.
-#     emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
-#     emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3, # ??????
-#     emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,     # ??????
-#     environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
-#     environment_wealthydonors_crackdown = issue2 * fund2 * gov_rel3,
-#     environment_govgrants_crackdown = issue2 * fund3 * gov_rel3,
-#     humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
-#     humanrights_wealthydonors_crackdown = issue3 * fund2 * gov_rel3,
-#     humanrights_govgrants_crackdown = issue3 * fund3 * gov_rel3,
-#     refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
-#     refugees_wealthydonors_crackdown = issue4 * fund2 * gov_rel3,
-#     refugees_govgrants_crackdown = issue4 * fund3 * gov_rel3,
-#     # Hypothesis 5b.
-#     nottransp_criticized = transp1 * gov_rel2,
-#     transp_criticized = transp2 * gov_rel2,
-#     nottransp_crackdown = transp1 * gov_rel3,
-#     transp_crackdown = transp2 * gov_rel3,
-#     # Hypothesis 5c.
-#     nottransp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
-#     transp_smalldonors_criticized = transp2 * fund1 * gov_rel2,
-#     nottransp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
-#     transp_wealthydonors_criticized = transp2 * fund2 * gov_rel2,
-#     nottransp_govgrants_criticized = transp1 * fund3 * gov_rel2,
-#     transp_govgrants_criticized = transp2 * fund3 * gov_rel2,
-#     nottransp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
-#     transp_smalldonors_crackdown = transp2 * fund1 * gov_rel3,
-#     nottransp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
-#     transp_wealthydonors_crackdown = transp2 * fund2 * gov_rel3,
-#     nottransp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
-#     transp_govgrants_crackdown = transp2 * fund3 * gov_rel3,
-#     # Hypothesis 5d.
-#     nottransp_emergency_criticized = transp1 * issue1 * gov_rel2,
-#     transp_emergency_criticized = transp2 * issue1 * gov_rel2,
-#     nottransp_emergency_crackdown = transp1 * issue1 * gov_rel3,
-#     transp_emergency_crackdown = transp2 * issue1 * gov_rel3,
-#     nottransp_environment_criticized = transp1 * issue2 * gov_rel2,
-#     transp_environment_criticized = transp2 * issue2 * gov_rel2,
-#     nottransp_environment_crackdown = transp1 * issue2 * gov_rel3,
-#     transp_environment_crackdown = transp2 * issue2 * gov_rel3,
-#     nottransp_humanrights_criticized = transp1 * issue3 * gov_rel2,
-#     transp_humanrights_criticized = transp2 * issue3 * gov_rel2,
-#     nottransp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
-#     transp_humanrights_crackdown = transp2 * issue3 * gov_rel3,
-#     nottransp_refugees_criticized = transp1 * issue4 * gov_rel2,
-#     transp_refugees_criticized = transp2 * issue4 * gov_rel2,
-#     nottransp_refugees_crackdown = transp1 * issue4 * gov_rel3,
-#     transp_refugees_crackdown = transp2 * issue4 * gov_rel3,
-#     # Hypothesis 5e.
-#     nottransp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
-#     transp_smalldonors_emergency_criticized = transp2 * fund1 * issue1 * gov_rel2,
-#     nottransp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
-#     transp_smalldonors_emergency_crackdown = transp2 * fund1 * issue1 * gov_rel3,
-#     nottransp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
-#     transp_smalldonors_environment_criticized = transp2 * fund1 * issue2 * gov_rel2,
-#     nottransp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
-#     transp_smalldonors_environment_crackdown = transp2 * fund1 * issue2 * gov_rel3,
-#     nottransp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
-#     transp_smalldonors_humanrights_criticized = transp2 * fund1 * issue3 * gov_rel2,
-#     nottransp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
-#     transp_smalldonors_humanrights_crackdown = transp2 * fund1 * issue3 * gov_rel3,
-#     nottransp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
-#     transp_smalldonors_refugees_criticized = transp2 * fund1 * issue4 * gov_rel2,
-#     nottransp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
-#     transp_smalldonors_refugees_crackdown = transp2 * fund1 * issue4 * gov_rel3
-#   )
+    # Main effects
+    h1_high = sum(org3, org4), # oxfam and red cross
+    h1_low = sum(org1, org2), # amnesty and greenpeace
+    h2a_high = sum(gov_rel2,gov_rel3), # criticized and crackdown
+    h2a_low = gov_rel1, # friendly
+    h3a_high = sum(issue1, issue4), # emergency and refugee
+    h3a_low = sum(issue2, issue3), # environment and human rights
+    h4a_high = fund1, # small donors
+    h4a_low = sum(fund2, fund3), # wealthy donors and gov grants
+    h5a_high = transp2, # transparent
+    h5a_low = transp1, # not transparent
+    # First-order Interactions
+    h2b_high = h1_high*h2a_high, #  oxfam and red cross * criticized and crackdown
+    h2b_low = h1_low*gov_rel3, # amnesty and greenpeace * criticized
+    h3b_high = h2a_high*h3a_high, # criticized and crackdown * emergency and refugee
+    h3b_low = h2a_high*h3a_low, # criticized and crackdown * environment and human rights
+    h4b_high = gov_rel3*fund1, # crackdown * small donors
+    h4b_low = sum(gov_rel1, gov_rel2)*h4a_high, # not crackdown * not small donors
+    h5b_high = h2a_high*h5a_high, # criticized and crackdown * transparent
+    h5b_low = h5a_low + h2a_low*h5a_high, # not transparent + friendly * transparent + 
+    # Second-order interactions
+    h4c_high = gov_rel3*h4a_high*h3a_high, # crackdown * small donors * emergency and refugee
+    h4c_low = ifelse(h4c_high==1, 0, 1), # everything else
+    h5c_high = h2a_high*h5a_high*h4a_high, # criticized and crackdown * transparent * small donors
+    h5c_low = ifelse(h5c_high==1, 0, 1), # everything else
+    h5d_high = h2a_high*h5a_high*h3a_high, # criticized and crackdown * transparent * emergency and refugee
+    h5d_low = ifelse(h5d_high==1, 0, 1), # everything else
+    # Third-order interaction
+    h5e_high = h2a_high*h5a_high*h3a_high*h4a_high, # criticized and crackdown * transparent * emergency and refugee * small donors
+    h5e_low = ifelse(h5e_high==1, 0, 1)) %>% 
+  ungroup()
 

### 2023-08-26 analysis/02_clean-data.Rmd

@@
 
+# # If I could rename the 13 X columns
+# dummy_level_labels <- c(
+#   str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
+#   str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
+#   str_c("Organizational practices: ", c("Financial transparency", "Accountability")),
+#   str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants")),
+#   str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))
+# )
+
 tidy_data

### 2023-08-26 analysis/05_market-simulator.Rmd

--- 2020-11-28 analysis/05_market_simulator.Rmd
@@
 gammas <- read_rds(
-    here::here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')
+    here::here('data', 'raw_data', 'posterior_draws', 'public_political_social_charity_demo.rds')
   ) %>% 
